### 2019-12-01 glossary.tex
Initial Overleaf Import

\newacronym{wdias}{WDIAS}{Weather Data Integration and Assimilation System}

\newacronym{fews}{Delft-FEWS} {Delft-FEWS, Deltares}
\newacronym{lead}{LEAD}{Linked Environments for Atmospheric Discovery}
\newacronym{dias}{DIAS}{Data Integration and Assimilation System}
\newacronym{madis}{MADIS}{Meteorological Assimilation Data Ingest System}

\newacronym{nwm}{NWMs}{Numerical Weather Models}
\newacronym{NetCDF}{NetCDF}{Network Common Data Form}
\newacronym{soa}{SOA}{Service Oriented Architecture}
\newacronym{wrf}{WRf}{Weather Research and Forecast}
\newacronym{esb}{ESB}{Enterprise Service Bus}
\newacronym{microservice}{Microservice}{Microservice Architectire}

\newacronym{curw}{CUrW SL}{Urban Center for Water, Sri Lanka}

### 2019-12-01 lit/sec_1-fews.tex
Initial Overleaf Import

\section{The Delft-FEWS flow forecasting system}
 \acrshort{fews} is developed by Deltares in the Nethaland with targeted for use by operational forecasting agencies. The software is freely available to download and setup. Tutorials and User setup guide \cite{DeltaresPublicWikiDelft-FEWSGuide} are available with well documentations. For non-commercial users need to have the licence agreement to use the system. And get new system updates. However, investments in new developments in the system are normally paid for by its users. The code base of \acrshort{fews} is currently not fully open source. But configuration guides and generic adapter module integration code examples are available for the users.

Most if the models are using model-centric approach such as inputs need to be in the format of specific to the model. Also the outputs produced by the model are specific to the model and hard to utilize by another systems (e.g. FLO2D). For the \acrshort{fews} is using much more modular approach, hence it is easy to integrate models into the \acrshort{fews} system. Thus \acrshort{fews} can be consider as an integration framework or a middle ware for the models.

Forecasting processes are constructed as a combination of modelling steps and data transformation algorithms. These are then combined to provide required forecast capabilities. Flexibility is achieved through integrating new models and algorithms into the code base \cite{Werner2013TheSystem}. Delft-FEWS system contains no inherent hydrological modelling capabilities within its code base. Rather it is a framework which can use to integrate into the system and create work flows for forecasting.

The key elements of a forecasting system are summarized by Haggett \cite{Haggett1998AnWales} as four main steps;
\begin{enumerate}
    \item Detection
    \item Forecasting
    \item Dissemination and Warning
    \item Response
\end{enumerate}
Within these four steps, \acrshort{fews} focuses on the forecasting step. The primary objective of this step is to provide additional lead time through predictions of short term future hydro-meteorological conditions \cite{Werner2005FloodCatchments}. It is true that, with providing accurate predictions with greater lead time can reduce the level of destruction. In order to do the forecasting, the system should be capable of integrating real-time data from hydrological and meteorological observation networks, and the dissemination of prediction results through appropriate products to the warning process.

In figure \ref{fi:fews_schematic} show a schematic view of the connection between the forecasting system to real time data acquisition systems and dissemination systems. The widely using concept is using meteorological forecast data to get precipitation and, then using hydrological and hydraulic model chain to predict the level affect on the ground. The hydrological and hydraulic model should be design based on the ground. Basically ground should be analyze geographically and divide into the catchments. Based on the affected catchment, it can be further divide into sub areas in order to reduce the complexity of the simulation task. Ideally the forecasting system should therefore be flexible to allow change to models and data, while keeping the way forecasters work with it as constant as possible.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.7\textwidth]{fews/Schematic-structure-of-a-fl-ood-forecasting-system-showing-the-position-of-Delft-FEWS_W640.jpg}
    \caption{Schematic structure of a flood forecasting system, showing the position of \acrshort{fews} and links to other primary systems within the operational environment. \cite{Werner2013TheSystem} }
    \label{fi:fews_schematic}
\end{figure}
The foundation of \acrshort{fews} is data-centric, with a common data-model through which all components interact. All time series data (both scalar and gridded) are stored in this common data-model in a database. Modeling capabilities are then linked to the system through one of the interfaces provided to the data-model \cite{Werner2013TheSystem}. As mention in the paper, having a common data-model make easy to store data in an efficient way. Operations like reporting and sharing the data also make it easy for integrate models. But the problem with this approach is, handling the multiple data formats. \acrshort{fews} overcome this issue with introducing adapters for most of commonly used data formats. This is a good feature which enable users to easily import data into the system. But at the same time, it's adding additional complexity into the system.

Time series data is additionally either scalar, vector, or gridded data, though all different types are uniformly stored as binary objects in a time series table. None of the functional components (including the linked models) have direct access to the times series table, which is accessible only through the data access module \cite{Werner2013TheSystem}. As it explained in the system interpretation, every time all the data access need to go through the data access module which causing to adding more cost in data access. Since it is storing the different data types as binary objects, there is a penalty in converting data into binary objects and vice a versa. Storing all the data in a time series table causing all the request come into a single data point. Even it gives the advantage of accessing all the data at one place. Since screaming big amount of data is causing a heavy load on the system, causing to slow down the performance on trying to use the system on large set of data.

Given above drawback on storing the data in the system, within the \acrshort{fews} data model, time series are uniquely identified by their location and data type, as well as an id related to the source of the data (e.g. the external source or hydrological model of which the time series are a result) \cite{Werner2013TheSystem}. This gives an opportunity to index the data base on above key fields and store the data separately, in order to take the advantage of putting multiple data resources into the system. As an example, instead of storing the data at a single timeseries table, it is possible to separate and index the database based on source such as external source or hydrological model of which the time series are a result. Or separate by data type and store in multiple storage give the capability for the system to scale with factor of identical types that can be identified. Example of separation by data types of scalar, vector and gridded will increase the scaling factor by 3x.

Data processing and manipulation is a required process in weather forecasting. Most of the data that is imported from external sources is not at the appropriate temporal and spatial scale to be applied as an input to a forecasting model, or to be used directly in product generation. As a consequence, generic data processing steps form the predominant effort in most applications of models in the forecast environment. Some examples include data validation, serial and spatial interpolation, aggregation and dis-aggregation, and merging data \cite{Werner2013TheSystem}. This a vital feature in a forecasting system, and affect on the quality and accuracy of the predicted data outputs. Because of the common data model concept in the \acrshort{fews}, data processing via these function is much effective. The system is self provided some of the generic functions for data processing, but for more complex algorithms can be developed as a new Java class coded to communicate with the application programming interface (API). It obvious that for additional feature integration, user should implement the new functional extensions via Java programming language. Users does not have the flexibility of develop with some other languages they are familiar with or use the support from another language. As an example, Python language is easy to use for beginners and many of data scientists are using this programming language for development and it has many data available libraries for data processing. But in the \acrshort{fews} users do not ave the capability to take the advantage of such existing things.

\begin{figure}[htp]
    \centering
    \includegraphics[width=1.0\textwidth]{fews/Architecture-of-Delft-FEWS-showing-the-data-base-the-data-access-layers-and-examples-of_W640.jpg}\\
    \caption{Architecture of \acrshort{fews} showing the data base, the data access layers and examples of functional modules that communicate through the data access layer. \cite{Werner2013TheSystem} }
    \label{fi:fews_data_layer}
\end{figure}
Most of the library of functions provided work equally on scalar and gridded time series. As with all other modules this communicates with the database solely through the data access layer as shown in \ref{fi:fews_data_layer} \cite{Werner2013TheSystem}. As it shown in the figure, it is clearly showing that, the system is depends on single database and via the data access layer all the requests are coming to the database though a connection. It is possible to setup and connect to a enterprise level database with clustering and shading as a paid solution, in order to serve many requests as possible. But the design it self inherently suffer with the database bottleneck which effected on running a large set of timeseries or models.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{fews/Linking-Delft-FEWS-with-external-models-The-fi-gure-shows-the-fl-ow-of-data-through-XML_W640.jpg}\\
    \caption{ Linking \acrshort{fews} with external models. The figure shows the flow of data through XML and native model formats using solid lines, while executable commands are shown by dashed lines. \cite{Werner2013TheSystem} }
    \label{fi:fews_general_adapter}
\end{figure}
On of the simple and most effective feature in the \acrshort{fews} is open approach to integration of models and data. This approaches the concept of the open modeling framework proposed by \cite{Kokkonen2003InterfacingXML}. It simply gives the flexibility to allow operators to integrate more models as well as variations of the same model and come up with new integration flows as much as possible.
\acrshort{fews} generates the input data as a set of XML files to a defined location; an adapter developed specifically for the model in question transforms this to the required native format in a pre-processing step; \acrshort{fews} executes the model; and the adapter to that model then converts the native formatted results into XML formatted files in a post processing step. \acrshort{fews} subsequently imports the results into the database from the XML files (see Fig. \ref{fi:fews_general_adapter}) \cite{Werner2013TheSystem}. The process is simple and consistence through out all the model integration. The model execution is done by the \acrshort{fews} or the model adapter which is causing tide coupling into the execution process in the system. Users does not have the flexibility to run the models with different configurations such as running with parallel execution. That may be overcome by triggering a external process at the execution time, but it introducing more difficulty for handling after model executed successfully, preceding to the next step in the process. This part of the system feature is not focus on the \acrshort{wdias} and user has to come up with own flow or use existing scientific flow management system. But it is a concept that need to be discuss and understand properly in order to design a data integration and assimilation system.

Exchanging data with the model is primarily through XML files. In some cases these XML files may become very large, which may lead to I/O bottlenecks and subsequent performance issues \cite{Werner2013TheSystem}. This issue is thoroughly discussed previous paragraphs and the authors of the \cite{Werner2013TheSystem} seems to be notice and accept it here. For overcome this issue they introduced the file-based exchange of data. This includes the use of binary-XML files, streaming files through memory, and the use of \acrshort{NetCDF}-CF files. But far as for users it seems to be adding more complexity and context in order to get higher performance via the system.

If particular adapter for a model is not present in the list of \acrshort{fews} adapter, user has the flexibility to implement an adapter for it. The effort of developing an adapter for a model code not previously integrated with \acrshort{fews} will vary depending on the complexity of the model I/O formats \cite{Werner2013TheSystem}. If user wants to use existing adapter and need to configure something not supported via the existing adapter, it is hard to get done. Also there are some cases it is hard to develop an adapter or running alongside with the \acrshort{fews}. As an example FLO2D model is using for hydrologic modeling and the model is only support only on Windows based operating systems. If you setup the system on Linux base operating system and using Linux based models, it is hard for users to come up with a solution for integrating the FLO2D models.
The final step and one of important feature is exporting the data from the system in useful manner. In the \acrshort{fews}, it is supporting three main forms of product generation.
\begin{itemize}
\item Generate web reports with graphs, tables as well as summary reports
\item Export time series in a variety of formats
\item External applications actively retrieve data from the system
\end{itemize}
The forecasting process is often a sequence of steps, starting with the import of data, a number of data processing and modeling steps, and culminating in the generation of products to be disseminated to the warning process. This is supported via the work flow process in the \acrshort{fews}. The scope of the \acrshort{wdias} is not focus on adding such a feature in the system, rather user have to use scientific work flow management system or come up with own version of work flow.

When running sequential steps within a work flow in \acrshort{fews}, each step is run for the full time window required (e.g. the lead time of the forecast) before moving on to the next step. This precludes tightly coupling of models, even explicitly \cite{Werner2013TheSystem}. As it mentioned above, users can run multiple models parallel or run those sequentially as needed.

### 2019-12-01 lit/sec_2-lead.tex
Initial Overleaf Import

\section{Linked Environments for Atmospheric Discovery}

The reason behind developing \acrfull{lead} by US National Science Foundation (NSF)  is to addresses the fundamental research challenges needed to create an integrated, scalable framework for adaptive analyzing and predicting the atmosphere \cite{Droegemeier2005Service-OrientedWeather}. In order to predict and analysis weather models by researchers, it required many resources. Rather than each researcher is running and handling own computer resources to do the weather experiments, \acrshort{lead} is providing pool of resources, then the researchers can use this resource pool to run their experiment in shorter amounts of time and in higher scale. At the time, researchers are developing their experiment flow, they are not using the resources many, and other are using it at the same time. LEAD’s foundation is dynamic work flow orchestration and data management in a Web services framework \cite{Droegemeier2005Service-OrientedWeather}.

The most relevant and important analysis for designing \acrshort{lead} is understanding and analyzing the \acrfull{lead} architecture of it. LEAD’s complex array of services, applications, interfaces, and local and remote computing, networking, and storage resources is assembled by users in work flows to study mesoscale weather as it evolves \cite{Droegemeier2005Service-OrientedWeather}. As it follows the \acrshort{soa}, everything is implemented as independent services. This enable \acrshort{lead} to scale each service as required, and update each service without affecting other services. New models which are required for implementing a new forecast flow also has to be implement as a service and then integrate into the system.

In the \ref{fi:lead_system} shows the fundamental capabilities of the \acrshort{lead} system. 
From the high-level view, \acrshort{lead} lets users query for and acquire information, simulate and predict weather by using numerical atmospheric models, assimilate data, analyze, mine, and visualize data and model output.

\begin{figure}[htp]
    \centering
    \includegraphics[width=1.0\textwidth]{lead/LEAD-system-Fundamental-capabilities-familiar-to-meteorologists-are-shown-in-the-top_W640.jpg}\\
    \caption{LEAD system. Fundamental capabilities familiar to meteorologists are shown in the top level, below which are the associated tools for enacting these capabilities and the middle-ware that links everything together. System-generated products appear at the bottom. \cite{Droegemeier2005Service-OrientedWeather} }
    \label{fi:lead_system}
\end{figure}

The second level in \ref{fi:lead_system} contains the fundamental tools that help to link services together. This include following tools in brief \cite{Droegemeier2005Service-OrientedWeather};
\begin{itemize}
    \item a Web portal, the primary (though not exclusive) user entry point
    \item the ARPS Data Assimilation System (ADAS), a sophisticated tool for data quality control and assimilation
    \item myLEAD, a flexible metadata catalog service
    \item \acrfull{wrf} a next-generation atmospheric prediction and simulation model
    \item ADaM (Algorithm Development and Mining), a powerful suite of tools for mining observational data, assimilated data sets, and model output 
    \item Integrated Data Viewer (IDV) 
\end{itemize}

\begin{figure}[htp]
    \centering
    \includegraphics[width=1.0\textwidth]{lead/LEAD-system-framework-LEAD-is-composed-of-several-interacting-subsystems-with-the-LEAD_W640.jpg}\\
    \caption{ LEAD system framework. LEAD is composed of several interacting subsystems, with the LEAD grid representing a stable, secure environment for development and testing. \cite{Droegemeier2005Service-OrientedWeather} }
    \label{fi:lead_framework}
\end{figure}

The Concept of the \acrshort{lead} is, the workflow orchestration for on-demand, real-time, dynamically adaptive systems, called as WOORDS. The system is doing the work flow orchestration as given in each procedure. Those procedural rules are define by researcher and feed into the system. The system is trying to perform the action immediate after the submission, and also it transmit the data, run the models and send back the put put with lower time delay as possible. According to the load and other requirement, the system will respond to those requirements automatically.

Lead System is consist of following sub components, as shown in the \ref{fi:lead_soa}. As a brief summary of the subsystems is \cite{Droegemeier2005Service-OrientedWeather};
\begin{itemize}
\item User subsystem - comprises the LEAD portal and enable user can access services
\item Data subsystem - handles data and metadata, any numerical model output produced by operational or experimental models, and user generated information.
\item Tools subsystem - consists of all meteorological and IT tools
\item Orchestration subsystem - provides the technologies that let users manage data flows and model execution streams, and create and mine output. It also provides linkages to other software and processes for continuous or on-demand applications. 
\end{itemize}

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.9\textwidth]{lead/LEADs-service-oriented-architecture-A-wide-variety-of-services-and-resources-grouped_W640.jpg}\\
    \caption{LEAD’s service-oriented architecture. A wide variety of services and resources, grouped here according to general functionality, comprise the LEAD architecture, including services that cut across all aspects of the system. \cite{Droegemeier2005Service-OrientedWeather} }
    \label{fi:lead_soa}
\end{figure}

The distributed computing systems in the LEAD grid represent a distributed test bed for developing, integrating, and testing LEAD’s components.

\acrshort{soa}s are widely deployed in the commercial enterprise sector, and they form the foundation of many scientific “grid” technologies at the time of \acrshort{lead} design and developed. A variant of \acrshort{soa} is evolved later called as microservice architecture, and widely use in the industry nowadays. The \acrshort{lead} \acrshort{soa} has five distinct yet highly interconnected layers.

The bottom layer represents raw computation, application, and data resources distributed throughout the LEAD grid and elsewhere. The next level up holds the Web services that provide access to raw services \cite{Droegemeier2005Service-OrientedWeather}. These two layers are working together, since \acrshort{lead} system resources are distributed over multiple locations and creating a pool of resources. The upper layer to the raw resources is abstracting the complexity of managing and accessing the resources, and provide a simplified access to the upper layer. In the Upper layers, it view as a unlimited resource pool for storing and handling data.

The configuration and execution services in the middle layer, consisting of five elements, represent services invoked by LEAD workflows. These are some critical aspects on a weather data management system. Most of the services listed here are required for creating work flows for weather data forecasting. Thus it is important to review them and understand the basic needs of a weather data management system.

\begin{itemize}
\item The application-oriented configuration service that manages the deployment and execution of real applications such as the \acrshort{wrf} simulation model, ADAS, and the ADaM tools \cite{Droegemeier2005Service-OrientedWeather}. When creating weather work flow, it is required to change the behaviour of model by changing some of the configurations of the model or run a different version of the model.
\item The application resource broker, which matches the appropriate host for execution to each application task, based on the execution’s time constraints \cite{}. This service is a critical part of the system, and responsible of using the resources of the system in optimized manner. When designing the weather data system, it is required to increase the capacity of the system automatically, and adopt into the system.
\item The workflow engine service, which drives experimental workflow instances, invokes both the configuration service and application resource broker \cite{Droegemeier2005Service-OrientedWeather}. This is a part of work flow orchestration.
\item The catalog services, represents the manner in which a user or application service discovers public-domain data products, or \acrshort{lead} services \cite{Droegemeier2005Service-OrientedWeather}. This is an important feature that should be available in a weather data system, and it is important to users to search for the availability of the data. Further wants to analyze the existing data for decision making.
\item Users require a host of data services to support rich query, access, and transformation operations on data products. An important goal behind LEAD is access transparency—facilitating user queries across all available heterogeneous data sources without adverse affects from different formats and naming schemes \cite{Droegemeier2005Service-OrientedWeather}. Users need to have transformation services to read data in different format. The query service gives the capability to search via available data without any affect on the data formats.
\end{itemize}
The top of the \ref{fi:lead_soa}, shows the user interface to the system. This give the access to individual services. When user logs into the system, based on the authentication and authorization setting bind to the individual account, the portlets can access the services on behalf of the user. Look into further details is not relevant to developing the \acrshort{wdias}, since the focus is not about workflow orchestration.

\acrshort{lead} is a more advanced system which can support for mesoscale weather prediction with the effort of multiple universities in the United State America with the effort of many of researchers and using many of computer resources. At the time it was building, it uses the \acrshort{soa} architecture as into its depth, and with the implementation each service can scale as needed and possible to enhance the service without interrupting other services. In the \acrshort{wdias} only focus on creating a framework that is extendable as system need more features as like \acrshort{lead} services.

### 2019-12-01 method/sec_0_introduction.tex
Initial Overleaf Import

\section{Introduction}

- Model data
multiple data formats in weather data
GRIB WRF model, out netCDF
netCDF to CSV then feed to HEC-HMS, out CSV
CSV + Rain cell Grid to FLO2D, out water level Grid ASCII files
ASCII files to ArcGIS create Raster files, then use t LOSS Estimation

- Observed data
Automated weather station sending data in higher frequent intervals via HTTP protocol
Automated water level stations send data in higher frequency

Other than above there are many data formats using for handling data based on devices and standards which are using. Also for data modeling, it needs to convert the data into model compatible data format, then after successfully run the model it needs to collect data from the model output data formats.

- Timeseries
A timeseries is simply a series of data points ordered in time. In weather domain, it interest in timeseries in perspective of observations to forecasting.
Each timeseries, the data points can be form in different formats as well.
- Scalar - 0D
- Vector - 1D
- Grid - 2D
- Polygon - 2D

WDIAS is focus on handling Scalar, Vector and Grid data timeseries via the thesis. But the system is capable of extending to handle polygon timeseries as well.

- Base of WDIAS architecture
The base of WDIAS architecture origins based on attributes of a timeseries. There are many attributes to differentiate timeseries one from another. But following can be consider as key attributes to uniquely identify a timeseries from another.
- Module - module that generate the timeseries
- Value Type - Scalar, Vector, Grid, Polygon
- Location 
- Parameter - measuring parameter of timeseries
- Timeseries type
  - sources - External, Simulated
  - category - Historical, forecast
- Time step

- Key components of the system
- Integration
System should be able to store data from multiple sources which come in different formats
- Assimilation
System should be able to provide functionalities for pre-possessing data and validating before using. 
- Dissemination
System should be able to export data in different data formats

### 2019-12-01 method/sec_1-soa.tex
Initial Overleaf Import

\section{Service Oriented Architecture}

In the initial phase of WDIAS architecture, it proposed with a \acrfull{soa} as shown in the \ref{fi:proposed_soa}. Mainly it consist of 4 modules;
- Import modules
Import modules are using for integration of data from different source which come in different data formats.
- Export modules
Export modules are using for data dissemination with different format which may required for different type of operations.
- Extension modules
Extension modules are capable of providing the data assimilation functionalities by providing some of key functionalities such as transformation, interpolation and validation. While data assimilation, existing timeseries may be modified or create new timeseries based on the system configurations.
- Adapter module
Adapter module is handling the complexity of integrating different data formats and storing them in the way that easy to search and retrieve.

\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{soa/soa_v1.jpg}
    \caption{Proposed Service Oriented Architecture.}
    \label{fi:proposed_soa}
\end{figure}

- \acrfull{esb}
While implementing a \acrfull{soa}, the \acrfull{esb} can provide capability to integrate different modules, since it is acting as a common layer for all of modules.
By default, \acrshort{esb} provides pub sub capabilities.
\acrshort{esb} mediator can be used to integrate the import, export and extension modules. \acrshort{esb} also support different transportation protocols such as HTTP and Web-Socket etc.

But \acrshort{esb} is not a better solution for data streaming or bulk data processing. Also \acrshort{esb} suffer from single point of failure, since all the messages are going though a common bus.

### 2019-12-01 method/sec_2-actor_model.tex
Initial Overleaf Import

\section{Actor Model}

In the second phase of \acrshort{wdias}, the proposed architecture changed to use with Actor model after consider into the disadvantage of using \acrshort{esb}.

Brief about using actor model:
https://doc.akka.io/docs/akka/2.5.5/scala/guide/actors-motivation.html

The typical SOA model, for example, usually has more dependent ESBs, with microservices using faster messaging mechanisms.  SOA also focuses on imperative programming, whereas microservices architecture focuses on a responsive-actor programming style.  Moreover, SOA models tend to have an outsized relational database, while microservices frequently use NoSQL or micro-SQL databases (which can be connected to conventional databases).  But the real difference has to do with the architecture methods used to arrive at an integrated set of services in the first place. (Refer:https://smartbear.com/learn/api-design/what-are-microservices/ )

- Add diagrams for handle on demand
- Add diagram for handle Async

AKKA vs ESB
ESB support to implement SOA. But SOA has limitations such as single point of failure, slower communication (can’t use for transfer data) etc. So, the microservice architecture get evolved and demanding for the moment. It has following benefits,
Follow the Single Responsibility Principle
Resilient/Flexible – failure in one service does not impact other services. If you have monolithic or bulky service errors in one service/module it can impact other modules/functionality.
High scalability – demanding services can be deployed in multiple servers to enhance performance and keep away from other services so that they don’t impact other services. Will be difficult to achieve the same with single, large monolithic service.
Easy to enhance – less dependency and easy to change and test
Low impact on other services – being an independent service, this has less chance to impact other services
Easy to understand since they represent the small piece of functionality
Ease of deployment
Freedom to choose technology – allows you to choose technology that is best suited for a particular functionality

### 2019-12-01 method/sec_3-microservice.tex
Initial Overleaf Import

\section{Microservice Architecture}

The microservice architectural style is an approach to developing a single application as a suite of small services, each running in its own process and communicating with lightweight mechanisms, often an HTTP resource API. These services are built around business capabilities and independently deployable by fully automated deployment machinery. There is a bare minimum of centralized management of these services, which may be written in different programming languages and use different data storage technologies. https://martinfowler.com/articles/microservices.html

Among the characteristics of \acrfull{microservice}, few characteristics heavily affect while moving from \acrshort{soa} to \acrshort{microservice}.
- Smart endpoints and dumb pipes \cite{LewisMicroservicesPipes}

- Pattern: Database per service \cite{LewisMicroservicesManagement}

  \acrshort{microservice} prefer letting each service manages its own database, either different instances of the same database technology, or entirely different database systems - an approach called Polyglot Persistence.

  \cite{RichardsonMicroservicesService}
  Keep each microservice’s persistent data private to that service and accessible only via its API. 
There are a few different ways to keep a service’s persistent data private. You do not need to provision a database server for each service. For example, if you are using a relational database then the options are:
Private-tables-per-service – each service owns a set of tables that must only be accessed by that service
Schema-per-service – each service has a database schema that’s private to that service
Database-server-per-service – each service has its own database server.
Private-tables-per-service and schema-per-service have the lowest overhead. Using a schema per service is appealing since it makes ownership clearer. Some high throughput services might need their own database server.

- Pattern: Sagas \cite{RichardsonMicroservicesSagas}
  In order to ensure loose coupling, each service has its own database. Maintaining data consistency between services is a challenge because 2 phase-commit/distributed transactions is not an option for many applications. An application must instead use the Saga pattern. A service publishes an event when its data changes. Other services consume that event and update their data.

Even AKKA.io actor model support the microservice architecture, as it explained in the documentation \cite{Akka.ioWhenCluster}, it has own advantages and disadvantage over the system that needs to be built.

- The Scale cube
The microservice architecture is an application of Y-axis scaling but let’s also look at X-axis and Z-axis scaling.

X-axis scaling
X-axis scaling consists of running multiple copies of an application behind a load balancer. If there are N copies then each copy handles 1/N of the load. This is a simple, commonly used approach of scaling an application.
One drawback of this approach is that because each copy potentially accesses all of the data, caches require more memory to be effective. Another problem with this approach is that it does not tackle the problems of increasing development and application complexity.

Y-axis scaling
Unlike X-axis and Z-axis, which consist of running multiple, identical copies of the application, Y-axis axis scaling splits the application into multiple, different services. Each service is responsible for one or more closely related functions. There are a couple of different ways of decomposing the application into services.
verb-based decomposition ex: checkout
decompose the application by noun ex: customer management. 
An application might use a combination of verb-based and noun-based decomposition.

Z-axis scaling
When using Z-axis scaling each server runs an identical copy of the code (similar to X-axis scaling). The big difference is that each server is responsible for only a subset of the data.

Some component of the system is responsible for routing each request to the appropriate server. Ex;
One commonly used routing criteria is an attribute of the request such as the primary key of the entity being accessed. 
Another common routing criteria is the customer type. For example, an application might provide paying customers with a higher SLA than free customers by routing their requests to a different set of servers with more capacity.

Z-axis splits are commonly used to scale databases. Data is partitioned (a.k.a. sharded) across a set of servers based on an attribute of each record. (Ex: the primary key of the RESTAURANT table is used to partition the rows between two different database servers)

Note that X-axis cloning might be applied to each partition by deploying one or more servers as replicas/slaves. Z-axis scaling can also be applied to applications.
(Example of apply Z-axis scaling: the search service consists of a number of partitions. A router sends each content item to the appropriate partition, where it is indexed and stored. A query aggregator sends each query to all of the partitions, and combines the results from each of them.)

<explain how each one is used while designing the WDIAS architecture>

\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/microservice_architecture-handle_on_demand-v3.jpg}
    \caption{Weather Data Integration and Assimilation System Architecture for Server Requests on Demand}
    \label{fi:wdias_micro_on_demand}
\end{figure}

\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/microservice_architecture-handle_on_async-v3.jpg}
    \caption{Weather Data Integration and Assimilation System Architecture for Handle Request Asynchronously}
    \label{fi:wdias_micro_async}
\end{figure}

\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/separation_microservices-v3.jpg}
    \caption{Separation of WDIAS microservices}
    \label{fi:wdias_micro_separation}
\end{figure}

<add the API description and how it related to moduels>
- Import
- Export
- Timeseries
- Extensions

### 2019-12-01 method/sec_4-db_struct.tex
Initial Overleaf Import

\section{Hierarchical Database Structure}

- Module ID
- Value Type
  - Scalar, Vector, Grid
- Location 
- Parameter
- Timeseries Type
  - sources - External, Simulated
  - category - Historical, forecast
- Time Step

\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/hierarchical_database.jpg}
    \caption{Hierarchical Database}
    \label{fi:hierarchical_database}
\end{figure}

- MySQL
Relational Database Management System (RDBMS)

- InfluxDB \cite{influxdbInfluxDBDocumentation}
Open timeseries DB with MIT license
Support SQL-Like query language
Clustering available with a commercial version

- NetCDF \cite{unidataUnidataNetCDF}
Network Common Data Form
Self-describing, machine-independent data formats that support creation, access, and sharing of array-oriented scientific data
Support parallel file access

- MongoDB
  MongoDB is a general purpose, document-based, distributed database
  Supports query operations on geo-spatial data \cite{mongodbMongoDBManual}
  Clustering and Sharding available for scalability and reliability

- Redis \cite{redisRedisDocumentation}
  Redis is an open source (BSD licensed), in-memory data structure store, used as a database, cache.
  Clustering is available for scalability

### 2019-12-01 method/sec_5-data_preprocess.tex
Initial Overleaf Import

\section{Extensions (Weather Data Prepossessing)}

\subsection{Interpolation}

\subsubsection{Serial Interpolation}

\subsubsection{Spatial Interpolation}

\subsection{Transformation}

\subsection{Validation}

\subsection{Extension API}

\subsubsection{Extension Handler}

\subsubsection{Extension Scheduler}

### 2019-12-01 method/sec_6-query.tex
Initial Overleaf Import

\section{Query Timeseries}

- Explain adapter query
How MongoDB is using for Geo Spatial search.

<Search API>

### 2019-12-01 results/sec_2-work_load.tex
Initial Overleaf Import

\section{Work Load Creation}

Precipitation
\lstinputlisting[language=Octave, firstline=1, lastline=10]{https://raw.githubusercontent.com/wdias/wdias-performance-test/master/data/locations.csv}

Water level

### 2019-12-01 struct.tex
Initial Overleaf Import

\documentclass[a4paper,oneside,12pt]{report}
\usepackage{graphicx,mathptmx}
\usepackage{geometry}
 \geometry{
 a4paper,
 %total={160mm,227mm},
 left=40mm,
 top=25mm,
 bottom=40mm, 
 right=25mm,
}
\renewcommand{\baselinestretch}{1.5}

\usepackage{setspace}
\usepackage{tabu}

\begin{document}
\begin{titlepage}
    \begin{center}
        \Large{
        \textbf{WEATHER DATA INTEGRATION AND ASSIMILATION SYSTEM}}\\
        \vspace{144pt}
  \large      
        %\vspace{1cm}
      % by

        %\vspace{1.0cm}

        Gihan Chanuka Karunarathne\\
        \vspace{24pt}
       % \normalsize
      178004U\\
         \vspace{72pt}
        %\normalsize
        Degree of Master of Science\\

        %\centering
         %\includegraphics[width=0.4\textwidth]{0.Title_Page/uom.png}\\
            %\vspace{0.8cm}
         %\normalsize

        %\vfill
       \vspace{72pt}
        \large
        Department of Computer Science and Engineering\\
        \vspace{24pt}
        University of Moratuwa\\
        Sri Lanka\\
        \vspace{32pt}
        April 2019

    \end{center}
\end{titlepage}

\begin{titlepage}
    \begin{center}
       % \vspace*{1cm}
        \Large{
        \textbf{WEATHER DATA INTEGRATION AND ASSIMILATION SYSTEM}}\\
        \vspace{144pt}
  \large

        Herath Mudiyanselage Gihan Chanuka Karunarathne\\
        \vspace{24pt}
       % \normalsize
        178008U\\
         \vspace{72pt}
        \normalsize
        Thesis submitted in partial fulfillment of the requirements for the degree Master of Science in Computer Science and Engineering\\

        %\vfill
       \vspace{72pt}
        \large
        Department of Computer Science and Engineering\\
        \vspace{24pt}
        University of Moratuwa\\
        Sri Lanka\\
        \vspace{32pt}
        April 2019

    \end{center}
\end{titlepage}

\pagenumbering{roman}

\newgeometry{left=4cm,top=0.5cm,right=2.5cm}
\chapter*{Declaration}
\addcontentsline{toc}{chapter}{Declaration}

I declare that this is my own work and this thesis does not
incorporate without acknowledgement any material previously submitted for a
Degree or Diploma in any other University or institute of higher learning and to
the best of my knowledge and belief it does not contain any material previously
published or written by another person except where the acknowledgement is
made in the text.

Also, I hereby grant to University of Moratuwa the non-exclusive right to
reproduce and distribute my thesis/dissertation, in whole or in part in print,
electronic or other medium. I retain the right to use this content in whole or part
in future works (such as articles or books).

\vspace{0.5in}
\noindent
\begin{tabu} to 1.0\textwidth { X[l] X[l] }
    Signature: & Date:
\end{tabu}

\vspace{0.5in}
\noindent
The above candidate has carried out research for the Masters thesis under our supervision.

\vspace{0.5in}
\noindent
\begin{tabu} to 1.0\textwidth { X[l] X[l] }
    Name of the supervisor: & Dr. HMN Dilum Bandara\\ [1.5ex]
    Signature of the supervisor: & Date:
\end{tabu}

\restoregeometry
\normalsize

\newgeometry{left=2.5cm,top=0.2cm,right=2cm}
\addcontentsline{toc}{chapter}{Abstract} 
{\setstretch{1.0} 
\chapter*{Abstract}
%\chapter*{\hspace{1cm} Abstract}

To enhance the accuracy of weather predictions, it is necessary to provide reliable and detailed weather data as inputs to Numerical Weather Models (NWM). These NWMs utilize weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images. Prior to feeding such diverse data (collected from different sources that belongs to different stakeholders) into respective NWMs, it is necessary to integrate data into a common format. Moreover, the data integration system’s response time need to be relatively low to accommodate critical situations like hurricanes, storms, and floods which require rapid and frequent execution of NWMs.

Providing public to access weather data is also useful to enable many third-party applications and research. For example, logistic companies can use those data with their own model to plan and schedule their deliveries. Agricultural insurance companies can warn the farmers in advance, as well as calculate premiums based on anticipated weather patterns.

While Data Integration and Analysis System (DIAS) and Meteorological Assimilation Data Ingest System (MADIS) are some of well-known Weather Data Integration and Assimilation (WDIA) systems, they are proprietary. Further Delft-FEWS is free to use, it is not open source. Hence, users of WDIA are forced to pay heavy licenses and are unable to extend the solutions to cater to their country-specific requirements. Therefore, the objective of this research is to develop a WDIA system for Sri Lanka, as well as make it open source, so that others could user and contribute to the solution.

\vspace{4mm}

\textbf{Keywords:} WDIAS, Weather, Timeseries, Distributed, Scalable

}
\restoregeometry
\normalsize

\addcontentsline{toc}{chapter}{Dedication} 
\chapter*{Dedication}
I dedicate my thesis work to my family, teachers and specialy friends at CUrW. A special feeling of gratitude to my loving parents, Nandawathi Dissanayake and H.M.K. Karunarathne whose words of encouragement and push for tenacity ring in my ears. My wife Jayani Kumarasinghe have never left my side and are very special.

I also dedicate this thesis to my many friends at CUrW SL who have supported and be with me during this period of time. Also special thanks to Dr. Dilum Bandara and Dr. Srikantha Herath for giving me this wonderful oppotunity to expore this new domain.

\addcontentsline{toc}{chapter}{Acknowledgements} 
\chapter*{Acknowledgements}
I wish to thank my evaluation panel members who were more than generous with their expertise and precious time. A special thanks to Dr. Dilum Bandara, my research supervisor for his countless hours of reflecting, reading, encouraging, and most of all patience throughout the entire process. Thank you Dr. Dilika Peris, and Dr. Indika Perera for agreeing to serve on my evaluation panel and Dr. Srikantha Herath for agreeing to serve as my external supervisor.

I would like to acknowledge and thank Department of Computer Science and Engineering, University of Moratuwa, for allowing me to conduct my research and providing any assistance requested. Special thanks goes to both academic and non-academic staff of the department for their continued support. I also gratitude to the University of Moratuwa for the financial support as the research was supported in part by the Senate Research Grant of the University of Moratuwa under award number SRC/LT/2017/01.

Finally, I would like to thank the teachers, evaluators and colleagues that assisted me with this project. Their excitement and willingness to provide feedback made the completion of this research an enjoyable experience.

\tableofcontents

\addcontentsline{toc}{chapter}{List of Figures} 
\listoffigures

\addcontentsline{toc}{chapter}{List of Tables} 
\listoftables

\addcontentsline{toc}{chapter}{List of Abbreviations} 
\chapter*{List of Abbreviations}

\pagenumbering{arabic}

\chapter{Introduction}
\label{ch:intro}

\section{Motivation}

\section{Problem}

\section{Objectives}

\section{Outline}

Introduce your thesis here.
\begin{figure}
\begin{center}
  \includegraphics[width=1in]{orchids.jpg}\\
  \caption{A picture of an orchid.}\label{fi:orchid}
\end{center}
\end{figure}
Figure \ref{fi:orchid} shows an orchid.

\chapter{Literature Review}
\label{ch:literature}

Reviews literature and place your work within the existing body of literature here. In chapter \ref{ch:intro} you introduced your thesis.

We can refer to books, journal articles, papers in conference proceeding etc. like this: Leslie Lamport \cite{Akka.ioWhenCluster} invented \LaTeX, based on \TeX.

\section{Delft-FEWS}

\section{LEAD}

\section{DIAS}

\section{MADIS}

\section{Summary}

\chapter{Method}
\label{ch:method}

Describe your method here so that the reader will be able to implement your system, if needed. 
\section{Introduction}
This is a section.
\label{se:method introduction}
Here is an equation:
\begin{equation}\label{eq:staright line}
    y = mx + c,
\end{equation}
where $m$ and $c$ are constants. Sometimes we use the form $ax + by + c = 0$, where $a$, $b$ and $c$ are constants. Equation \ref{eq:staright line} represents a straight line.

\subsection{Basics}
This is a subsection.

\section{Service Oriented Architecture}

\section{Microservice Architecture}

\section{Hierarchical Database Structure}

\section{Weather Data Prepossessing}

\subsection{Interpolation}

\subsection{Transformation}

\subsection{Validation}

\section{Query Timeseries}

\chapter{Results}
\label{ch:results}

Present your results here.

Table \ref{ta:results} show some results.
\begin{table}
  \centering
  \begin{tabular}{|l|l|}
    \hline
    Day & Rainfall \\
    \hline
    Monday & 10\\
    Tuesday & 12\\
    Wednesday & 0\\
    \hline
  \end{tabular}
  \caption{Daily rainfall in millimeters.}\label{ta:results}
\end{table}

\section{Test Plan}

\section{Work Load Creation}

\section{Observations}

\chapter{Conclusions}
\label{ch:conc}

Discuss your results and system and conclude.

\section{Summary}

\section{Future Work}

\appendix
\chapter{First Appendix}
Type out your first appendix here.
\section{Basics}

\chapter{First Appendix}
Type out your second appendix here.

% \bibliographystyle{plain}
% \bibliography{references}
% \end{document}

\bibliographystyle{plain}
\bibliography{mendeley}
\end{document}

### 2019-12-01 thesis-backup.tex
Initial Overleaf Import

\documentclass[a4paper,oneside,12pt]{report}
\usepackage{graphicx,mathptmx}
\usepackage{geometry}
 \geometry{
 a4paper,
 %total={160mm,227mm},
 left=40mm,
 top=25mm,
 bottom=40mm, 
 right=25mm,
}
\renewcommand{\baselinestretch}{1.5}

\usepackage{setspace}
\usepackage{tabu}
\usepackage[acronym]{glossaries}
\makeglossaries
\usepackage{import}

\begin{document}
\begin{titlepage}
    \begin{center}
        \Large{
        \textbf{WEATHER DATA INTEGRATION AND ASSIMILATION SYSTEM}}\\
        \vspace{144pt}
  \large      
        %\vspace{1cm}
      % by

        %\vspace{1.0cm}

        Gihan Chanuka Karunarathne\\
        \vspace{24pt}
       % \normalsize
      178004U\\
         \vspace{72pt}
        %\normalsize
        Degree of Master of Science\\

        %\centering
         %\includegraphics[width=0.4\textwidth]{0.Title_Page/uom.png}\\
            %\vspace{0.8cm}
         %\normalsize

        %\vfill
       \vspace{72pt}
        \large
        Department of Computer Science and Engineering\\
        \vspace{24pt}
        University of Moratuwa\\
        Sri Lanka\\
        \vspace{32pt}
        April 2019

    \end{center}
\end{titlepage}

\begin{titlepage}
    \begin{center}
       % \vspace*{1cm}
        \Large{
        \textbf{WEATHER DATA INTEGRATION AND ASSIMILATION SYSTEM}}\\
        \vspace{144pt}
  \large

        Herath Mudiyanselage Gihan Chanuka Karunarathne\\
        \vspace{24pt}
       % \normalsize
        178008U\\
         \vspace{72pt}
        \normalsize
        Thesis submitted in partial fulfillment of the requirements for the degree Master of Science in Computer Science and Engineering\\

        %\vfill
       \vspace{72pt}
        \large
        Department of Computer Science and Engineering\\
        \vspace{24pt}
        University of Moratuwa\\
        Sri Lanka\\
        \vspace{32pt}
        April 2019

    \end{center}
\end{titlepage}

\pagenumbering{roman}

\newgeometry{left=4cm,top=0.5cm,right=2.5cm}
\chapter*{Declaration}
\addcontentsline{toc}{chapter}{Declaration}

I declare that this is my own work and this thesis does not
incorporate without acknowledgement any material previously submitted for a
Degree or Diploma in any other University or institute of higher learning and to
the best of my knowledge and belief it does not contain any material previously
published or written by another person except where the acknowledgement is
made in the text.

Also, I hereby grant to University of Moratuwa the non-exclusive right to
reproduce and distribute my thesis/dissertation, in whole or in part in print,
electronic or other medium. I retain the right to use this content in whole or part
in future works (such as articles or books).

\vspace{0.5in}
\noindent
\begin{tabu} to 1.0\textwidth { X[l] X[l] }
    Signature: & Date:
\end{tabu}

\vspace{0.5in}
\noindent
The above candidate has carried out research for the Masters thesis under our supervision.

\vspace{0.5in}
\noindent
\begin{tabu} to 1.0\textwidth { X[l] X[l] }
    Name of the supervisor: & Dr. HMN Dilum Bandara\\ [1.5ex]
    Signature of the supervisor: & Date:
\end{tabu}

\restoregeometry
\normalsize

\newgeometry{left=2.5cm,top=0.2cm,right=2cm}
\addcontentsline{toc}{chapter}{Abstract} 
{\setstretch{1.0} 
\chapter*{Abstract}
%\chapter*{\hspace{1cm} Abstract}

To enhance the accuracy of weather predictions, it is necessary to provide reliable and detailed weather data as inputs to \acrfull{nwm}. These \acrshort{nwm} utilize weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images. Prior to feeding such diverse data (collected from different sources that belongs to different stakeholders) into respective \acrshort{nwm}, it is necessary to integrate data into a common format. Moreover, the data integration system’s response time need to be relatively low to accommodate critical situations like hurricanes, storms, and floods which require rapid and frequent execution of \acrshort{nwm}.

Providing public to access weather data is also useful to enable many third-party applications and research. For example, logistic companies can use those data with their own model to plan and schedule their deliveries. Agricultural insurance companies can warn the farmers in advance, as well as calculate premiums based on anticipated weather patterns.

While \acrfull{dias} and \acrfull{madis} are some of well-known Weather Data Integration and Assimilation (WDIA) systems, they are proprietary. Further Delft-FEWS is free to use, it is not open source. Hence, users of WDIA are forced to pay heavy licenses and are unable to extend the solutions to cater to their country-specific requirements. Therefore, the objective of this research is to develop a WDIA system for Sri Lanka, as well as make it open source, so that others could user and contribute to the solution.

\vspace{4mm}

\textbf{Keywords:} WDIAS, Weather, Timeseries, Distributed, Scalable

}
\restoregeometry
\normalsize

\addcontentsline{toc}{chapter}{Dedication} 
\chapter*{Dedication}
I dedicate my thesis work to my family, teachers and specially friends at \acrfull{curw}. A special feeling of gratitude to my loving parents, Nandawathi Dissanayake and H.M.K. Karunarathne whose words of encouragement and push for tenacity ring in my ears. My wife Jayani Kumarasinghe have never left my side and are very special.

I also dedicate this thesis to my many friends at \acrshort{curw} who have supported and be with me during this period of time. Also special thanks to Dr. Dilum Bandara and Dr. Srikantha Herath for giving me this wonderful opportunity to explore this new domain.

\addcontentsline{toc}{chapter}{Acknowledgements} 
\chapter*{Acknowledgements}
I wish to thank my evaluation panel members who were more than generous with their expertise and precious time. A special thanks to Dr. Dilum Bandara, my research supervisor for his countless hours of reflecting, reading, encouraging, and most of all patience throughout the entire process. Thank you Dr. Dilika Peris, and Dr. Indika Perera for agreeing to serve on my evaluation panel and Dr. Srikantha Herath for agreeing to serve as my external supervisor.

I would like to acknowledge and thank Department of Computer Science and Engineering, University of Moratuwa, for allowing me to conduct my research and providing any assistance requested. Special thanks goes to both academic and non-academic staff of the department for their continued support. I also gratitude to the University of Moratuwa for the financial support as the research was supported in part by the Senate Research Grant of the University of Moratuwa under award number SRC/LT/2017/01.

Finally, I would like to thank the teachers, evaluating panel and colleagues that assisted me with this project. Their excitement and willingness to provide feedback made the completion of this research an enjoyable experience.

\tableofcontents

\addcontentsline{toc}{chapter}{List of Figures} 
\listoffigures

\addcontentsline{toc}{chapter}{List of Tables} 
\listoftables

\addcontentsline{toc}{chapter}{List of Abbreviations} 
\printglossary[type=\acronymtype, title=List of Abbreviations, toctitle=List of Abbreviations, nonumberlist]

\pagenumbering{arabic}

\chapter{Introduction}
\label{ch:intro}
To enhance the accuracy of weather predictions, it is necessary to provide reliable and detailed weather data as inputs to \acrfull{nwm}. These NWMs utilize weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images. Prior to feeding such diverse data (collected from different sources that belongs to different stakeholders) into respective NWMs, it is necessary to integrate data into a common format. Moreover, the data integration system’s response time need to be relatively low to accommodate critical situations like hurricanes, storms, and floods which require rapid and frequent execution of NWMs.

\section{Motivation}
Providing public to access weather data is also useful to enable many third-party applications and research. For example, logistic companies can use those data with their own model to plan and schedule their deliveries. Agricultural insurance companies can warn the farmers in advance, as well as calculate premiums based on anticipated weather patterns.

While Data Integration and Analysis System (DIAS) and Meteorological Assimilation Data Ingest System (MADIS) are some of well-known Weather Data Integration and Assimilation (WDIA) systems, they are proprietary. Further Delft-FEWS is free to use, it is not open source. Hence, users of WDIA are forced to pay heavy licenses and are unable to extend the solutions to cater to their country-specific requirements. Therefore, the objective of this research is to develop a WDIA system for Sri Lanka, as well as make it open source, so that others could user and contribute to the solution.

\section{Problem}
\begin{itemize}
    \item Handling spatio-temporal weather data is challenging
    \item Need an extendable system to support weather models by efficiently storing and retrieving data
    \item Goal is to design and develop a Weather Data Integration and Assimilation System that,
    \begin{itemize}
        \item Integrates weather data from different sources with quality control
        \item Efficiently store spatio-temporal weather data with multiple dimensions
        \item Support geographical and time-base queries
    \end{itemize}
\end{itemize}

\section{Objectives}
\begin{itemize}
    \item To develop an open platform to integrate weather data from different sources in different formats
    \item To design and develop a schema to store multidimensional weather timeseries data while optimizing,
    \begin{itemize}
        \item Disk space
        \item Availability
        \item Access time
    \end{itemize}
    \item To optimize schema to support data queries based on geography and time
    \item To develop an API to share data while providing role-based access control
\end{itemize}

\section{Outline}
The rest of the thesis is organized as follows. Literature review is presented in Chapter \ref{ch:literature}. Solution approach with the proposed system architectures and adaptation with problem occurred are presented in Chapter \ref{ch:method}. Performance analysis is presented in Chapter \ref{ch:results} while summary and future work are presented in Chapter \ref{ch:conc}.

\chapter{Literature Review}
\label{ch:literature}
There are many of Weather forecasting, assimilation and dissemination systems developed by some of developed countries around the world as a result of trying to reduce the damage causing by natural disasters such as flood, storms, hurricanes and even for drought. Above kind of natural disasters heavily affected on the economy and the life conditions of the country, researchers have developed systems and many of these systems are using as proprietary systems. Other countries also using those systems and adopt with own version of system which effective for the specific weather condition in a particular country.
Though out this chapter includes a Literature review about existing systems and their architecture approach and design with available resources. Most influenced systems for \acrshort{wdias} is \acrshort{fews} and \acrfull{lead} system. \acrshort{fews} is an open data handling platform, but it distributed as Closed Source software. \acrshort{lead} is following the Service Oriented Architecture for system architecture. Under each system we explore both system architecture, scalability and flexibility of the system.

\section{The Delft-FEWS flow forecasting system}
 \acrshort{fews} is developed by Deltares in the Nethaland with targeted for use by operational forecasting agencies. The software is freely available to download and setup. Tutorials and User setup guide \cite{DeltaresPublicWikiDelft-FEWSGuide} are available with well documentations. For non-commercial users need to have the licence agreement to use the system. And get new system updates. However, investments in new developments in the system are normally paid for by its users. The code base of \acrshort{fews} is currently not fully open source. But configuration guides and generic adapter module integration code examples are available for the users.

Most if the models are using model-centric approach such as inputs need to be in the format of specific to the model. Also the outputs produced by the model are specific to the model and hard to utilize by another systems (e.g. FLO2D). For the \acrshort{fews} is using much more modular approach, hence it is easy to integrate models into the \acrshort{fews} system. Thus \acrshort{fews} can be consider as an integration framework or a middle ware for the models.

Forecasting processes are constructed as a combination of modelling steps and data transformation algorithms. These are then combined to provide required forecast capabilities. Flexibility is achieved through integrating new models and algorithms into the code base \cite{Werner2013TheSystem}. Delft-FEWS system contains no inherent hydrological modelling capabilities within its code base. Rather it is a framework which can use to integrate into the system and create work flows for forecasting.

The key elements of a forecasting system are summarized by Haggett \cite{Haggett1998AnWales} as four main steps;
\begin{enumerate}
\item Detection
\item Forecasting
\item Dissemination and Warning
\item Response
\end{enumerate}
Within these four steps, \acrshort{fews} focuses on the forecasting step. The primary objective of this step is to provide additional lead time through predictions of short term future hydro-meteorological conditions \cite{Werner2005FloodCatchments}. It is true that, with providing accurate predictions with greater lead time can reduce the level of destruction. In order to do the forecasting, the system should be capable of integrating real-time data from hydrological and meteorological observation networks, and the dissemination of prediction results through appropriate products to the warning process.

In figure \ref{fi:fews_schematic} show a schematic view of the connection between the forecasting system to real time data acquisition systems and dissemination systems. The widely using concept is using meteorological forecast data to get precipitation and, then using hydrological and hydraulic model chain to predict the level affect on the ground. The hydrological and hydraulic model should be design based on the ground. Basically ground should be analyze geographically and divide into the catchments. Based on the affected catchment, it can be further divide into sub areas in order to reduce the complexity of the simulation task. Ideally the forecasting system should therefore be flexible to allow change to models and data, while keeping the way forecasters work with it as constant as possible.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.7\textwidth]{images/fews/Schematic-structure-of-a-fl-ood-forecasting-system-showing-the-position-of-Delft-FEWS_W640.jpg}\\
    \caption{Schematic structure of a flood forecasting system, showing the position of \acrshort{fews} and links to other primary systems within the operational environment. \cite{Werner2013TheSystem} }
    \label{fi:fews_schematic}
\end{figure}
The foundation of \acrshort{fews} is data-centric, with a common data-model through which all components interact. All time series data (both scalar and gridded) are stored in this common data-model in a database. Modeling capabilities are then linked to the system through one of the interfaces provided to the data-model \cite{Werner2013TheSystem}. As mention in the paper, having a common data-model make easy to store data in an efficient way. Operations like reporting and sharing the data also make it easy for integrate models. But the problem with this approach is, handling the multiple data formats. \acrshort{fews} overcome this issue with introducing adapters for most of commonly used data formats. This is a good feature which enable users to easily import data into the system. But at the same time, it's adding additional complexity into the system.

Time series data is additionally either scalar, vector, or gridded data, though all different types are uniformly stored as binary objects in a time series table. None of the functional components (including the linked models) have direct access to the times series table, which is accessible only through the data access module \cite{Werner2013TheSystem}. As it explained in the system interpretation, every time all the data access need to go through the data access module which causing to adding more cost in data access. Since it is storing the different data types as binary objects, there is a penalty in converting data into binary objects and vice a versa. Storing all the data in a time series table causing all the request come into a single data point. Even it gives the advantage of accessing all the data at one place. Since screaming big amount of data is causing a heavy load on the system, causing to slow down the performance on trying to use the system on large set of data.

Given above drawback on storing the data in the system, within the \acrshort{fews} data model, time series are uniquely identified by their location and data type, as well as an id related to the source of the data (e.g. the external source or hydrological model of which the time series are a result) \cite{Werner2013TheSystem}. This gives an opportunity to index the data base on above key fields and store the data separately, in order to take the advantage of putting multiple data resources into the system. As an example, instead of storing the data at a single timeseries table, it is possible to separate and index the database based on source such as external source or hydrological model of which the time series are a result. Or separate by data type and store in multiple storage give the capability for the system to scale with factor of identical types that can be identified. Example of separation by data types of scalar, vector and gridded will increase the scaling factor by 3x.

Data processing and manipulation is a required process in weather forecasting. Most of the data that is imported from external sources is not at the appropriate temporal and spatial scale to be applied as an input to a forecasting model, or to be used directly in product generation. As a consequence, generic data processing steps form the predominant effort in most applications of models in the forecast environment. Some examples include data validation, serial and spatial interpolation, aggregation and dis-aggregation, and merging data \cite{Werner2013TheSystem}. This a vital feature in a forecasting system, and affect on the quality and accuracy of the predicted data outputs. Because of the common data model concept in the \acrshort{fews}, data processing via these function is much effective. The system is self provided some of the generic functions for data processing, but for more complex algorithms can be developed as a new Java class coded to communicate with the application programming interface (API). It obvious that for additional feature integration, user should implement the new functional extensions via Java programming language. Users does not have the flexibility of develop with some other languages they are familiar with or use the support from another language. As an example, Python language is easy to use for beginners and many of data scientists are using this programming language for development and it has many data available libraries for data processing. But in the \acrshort{fews} users do not ave the capability to take the advantage of such existing things.

\begin{figure}[htp]
    \centering
    \includegraphics[width=1.0\textwidth]{images/fews/Architecture-of-Delft-FEWS-showing-the-data-base-the-data-access-layers-and-examples-of_W640.jpg}\\
    \caption{Architecture of \acrshort{fews} showing the data base, the data access layers and examples of functional modules that communicate through the data access layer. \cite{Werner2013TheSystem} }
    \label{fi:fews_data_layer}
\end{figure}
Most of the library of functions provided work equally on scalar and gridded time series. As with all other modules this communicates with the database solely through the data access layer as shown in \ref{fi:fews_data_layer} \cite{Werner2013TheSystem}. As it shown in the figure, it is clearly showing that, the system is depends on single database and via the data access layer all the requests are coming to the database though a connection. It is possible to setup and connect to a enterprise level database with clustering and shading as a paid solution, in order to serve many requests as possible. But the design it self inherently suffer with the database bottleneck which effected on running a large set of timeseries or models.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{images/fews/Linking-Delft-FEWS-with-external-models-The-fi-gure-shows-the-fl-ow-of-data-through-XML_W640.jpg}\\
    \caption{ Linking \acrshort{fews} with external models. The figure shows the flow of data through XML and native model formats using solid lines, while executable commands are shown by dashed lines. \cite{Werner2013TheSystem} }
    \label{fi:fews_general_adapter}
\end{figure}
On of the simple and most effective feature in the \acrshort{fews} is open approach to integration of models and data. This approaches the concept of the open modeling framework proposed by \cite{Kokkonen2003InterfacingXML}. It simply gives the flexibility to allow operators to integrate more models as well as variations of the same model and come up with new integration flows as much as possible.
\acrshort{fews} generates the input data as a set of XML files to a defined location; an adapter developed specifically for the model in question transforms this to the required native format in a pre-processing step; \acrshort{fews} executes the model; and the adapter to that model then converts the native formatted results into XML formatted files in a post processing step. \acrshort{fews} subsequently imports the results into the database from the XML files (see Fig. \ref{fi:fews_general_adapter}) \cite{Werner2013TheSystem}. The process is simple and consistence through out all the model integration. The model execution is done by the \acrshort{fews} or the model adapter which is causing tide coupling into the execution process in the system. Users does not have the flexibility to run the models with different configurations such as running with parallel execution. That may be overcome by triggering a external process at the execution time, but it introducing more difficulty for handling after model executed successfully, preceding to the next step in the process. This part of the system feature is not focus on the \acrshort{wdias} and user has to come up with own flow or use existing scientific flow management system. But it is a concept that need to be discuss and understand properly in order to design a data integration and assimilation system.

Exchanging data with the model is primarily through XML files. In some cases these XML files may become very large, which may lead to I/O bottlenecks and subsequent performance issues \cite{Werner2013TheSystem}. This issue is thoroughly discussed previous paragraphs and the authors of the \cite{Werner2013TheSystem} seems to be notice and accept it here. For overcome this issue they introduced the file-based exchange of data. This includes the use of binary-XML files, streaming files through memory, and the use of \acrshort{NetCDF}-CF files. But far as for users it seems to be adding more complexity and context in order to get higher performance via the system.

If particular adapter for a model is not present in the list of \acrshort{fews} adapter, user has the flexibility to implement an adapter for it. The effort of developing an adapter for a model code not previously integrated with \acrshort{fews} will vary depending on the complexity of the model I/O formats \cite{Werner2013TheSystem}. If user wants to use existing adapter and need to configure something not supported via the existing adapter, it is hard to get done. Also there are some cases it is hard to develop an adapter or running alongside with the \acrshort{fews}. As an example FLO2D model is using for hydrologic modeling and the model is only support only on Windows based operating systems. If you setup the system on Linux base operating system and using Linux based models, it is hard for users to come up with a solution for integrating the FLO2D models.
The final step and one of important feature is exporting the data from the system in useful manner. In the \acrshort{fews}, it is supporting three main forms of product generation.
\begin{itemize}
\item Generate web reports with graphs, tables as well as summary reports
\item Export time series in a variety of formats
\item External applications actively retrieve data from the system
\end{itemize}
The forecasting process is often a sequence of steps, starting with the import of data, a number of data processing and modeling steps, and culminating in the generation of products to be disseminated to the warning process. This is supported via the work flow process in the \acrshort{fews}. The scope of the \acrshort{wdias} is not focus on adding such a feature in the system, rather user have to use scientific work flow management system or come up with own version of work flow.

When running sequential steps within a work flow in \acrshort{fews}, each step is run for the full time window required (e.g. the lead time of the forecast) before moving on to the next step. This precludes tightly coupling of models, even explicitly \cite{Werner2013TheSystem}. As it mentioned above, users can run multiple models parallel or run those sequentially as needed.

\section{Linked Environments for Atmospheric Discovery}

The reason behind developing \acrfull{lead} by US National Science Foundation (NSF)  is to addresses the fundamental research challenges needed to create an integrated, scalable framework for adaptive analyzing and predicting the atmosphere \cite{Droegemeier2005Service-OrientedWeather}. In order to predict and analysis weather models by researchers, it required many resources. Rather than each researcher is running and handling own computer resources to do the weather experiments, \acrshort{lead} is providing pool of resources, then the researchers can use this resource pool to run their experiment in shorter amounts of time and in higher scale. At the time, researchers are developing their experiment flow, they are not using the resources many, and other are using it at the same time. LEAD’s foundation is dynamic work flow orchestration and data management in a Web services framework \cite{Droegemeier2005Service-OrientedWeather}.

The most relevant and important analysis for designing \acrshort{lead} is understanding and analyzing the \acrfull{lead} architecture of it. LEAD’s complex array of services, applications, interfaces, and local and remote computing, networking, and storage resources is assembled by users in work flows to study mesoscale weather as it evolves \cite{Droegemeier2005Service-OrientedWeather}. As it follows the \acrshort{soa}, everything is implemented as independent services. This enable \acrshort{lead} to scale each service as required, and update each service without affecting other services. New models which are required for implementing a new forecast flow also has to be implement as a service and then integrate into the system.

In the \ref{fi:lead_system} shows the fundamental capabilities of the \acrshort{lead} system. 
From the high-level view, \acrshort{lead} lets users query for and acquire information, simulate and predict weather by using numerical atmospheric models, assimilate data, analyze, mine, and visualize data and model output.

\begin{figure}[htp]
    \centering
    \includegraphics[width=1.0\textwidth]{images/lead/LEAD-system-Fundamental-capabilities-familiar-to-meteorologists-are-shown-in-the-top_W640.jpg}\\
    \caption{LEAD system. Fundamental capabilities familiar to meteorologists are shown in the top level, below which are the associated tools for enacting these capabilities and the middle-ware that links everything together. System-generated products appear at the bottom. \cite{Droegemeier2005Service-OrientedWeather} }
    \label{fi:lead_system}
\end{figure}

The second level in \ref{fi:lead_system} contains the fundamental tools that help to link services together. This include following tools in brief \cite{Droegemeier2005Service-OrientedWeather};
\begin{itemize}
    \item a Web portal, the primary (though not exclusive) user entry point
    \item the ARPS Data Assimilation System (ADAS), a sophisticated tool for data quality control and assimilation
    \item myLEAD, a flexible metadata catalog service
    \item \acrfull{wrf} a next-generation atmospheric prediction and simulation model
    \item ADaM (Algorithm Development and Mining), a powerful suite of tools for mining observational data, assimilated data sets, and model output 
    \item Integrated Data Viewer (IDV) 
\end{itemize}

\begin{figure}[htp]
    \centering
    \includegraphics[width=1.0\textwidth]{images/lead/LEAD-system-framework-LEAD-is-composed-of-several-interacting-subsystems-with-the-LEAD_W640.jpg}\\
    \caption{ LEAD system framework. LEAD is composed of several interacting subsystems, with the LEAD grid representing a stable, secure environment for development and testing. \cite{Droegemeier2005Service-OrientedWeather} }
    \label{fi:lead_framework}
\end{figure}

The Concept of the \acrshort{lead} is, the workflow orchestration for on-demand, real-time, dynamically adaptive systems, called as WOORDS. The system is doing the work flow orchestration as given in each procedure. Those procedural rules are define by researcher and feed into the system. The system is trying to perform the action immediate after the submission, and also it transmit the data, run the models and send back the put put with lower time delay as possible. According to the load and other requirement, the system will respond to those requirements automatically.

Lead System is consist of following sub components, as shown in the \ref{fi:lead_soa}. As a brief summary of the subsystems is \cite{Droegemeier2005Service-OrientedWeather};
\begin{itemize}
\item User subsystem - comprises the LEAD portal and enable user can access services
\item Data subsystem - handles data and metadata, any numerical model output produced by operational or experimental models, and user generated information.
\item Tools subsystem - consists of all meteorological and IT tools
\item Orchestration subsystem - provides the technologies that let users manage data flows and model execution streams, and create and mine output. It also provides linkages to other software and processes for continuous or on-demand applications. 
\end{itemize}

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.9\textwidth]{images/lead/LEADs-service-oriented-architecture-A-wide-variety-of-services-and-resources-grouped_W640.jpg}\\
    \caption{LEAD’s service-oriented architecture. A wide variety of services and resources, grouped here according to general functionality, comprise the LEAD architecture, including services that cut across all aspects of the system. \cite{Droegemeier2005Service-OrientedWeather} }
    \label{fi:lead_soa}
\end{figure}

The distributed computing systems in the LEAD grid represent a distributed test bed for developing, integrating, and testing LEAD’s components.

\acrshort{soa}s are widely deployed in the commercial enterprise sector, and they form the foundation of many scientific “grid” technologies at the time of \acrshort{lead} design and developed. A variant of \acrshort{soa} is evolved later called as microservice architecture, and widely use in the industry nowadays. The \acrshort{lead} \acrshort{soa} has five distinct yet highly interconnected layers.

The bottom layer represents raw computation, application, and data resources distributed throughout the LEAD grid and elsewhere. The next level up holds the Web services that provide access to raw services \cite{Droegemeier2005Service-OrientedWeather}. These two layers are working together, since \acrshort{lead} system resources are distributed over multiple locations and creating a pool of resources. The upper layer to the raw resources is abstracting the complexity of managing and accessing the resources, and provide a simplified access to the upper layer. In the Upper layers, it view as a unlimited resource pool for storing and handling data.

The configuration and execution services in the middle layer, consisting of five elements, represent services invoked by LEAD workflows. These are some critical aspects on a weather data management system. Most of the services listed here are required for creating work flows for weather data forecasting. Thus it is important to review them and understand the basic needs of a weather data management system.

\begin{itemize}
\item The application-oriented configuration service that manages the deployment and execution of real applications such as the \acrshort{wrf} simulation model, ADAS, and the ADaM tools \cite{Droegemeier2005Service-OrientedWeather}. When creating weather work flow, it is required to change the behaviour of model by changing some of the configurations of the model or run a different version of the model.
\item The application resource broker, which matches the appropriate host for execution to each application task, based on the execution’s time constraints \cite{}. This service is a critical part of the system, and responsible of using the resources of the system in optimized manner. When designing the weather data system, it is required to increase the capacity of the system automatically, and adopt into the system.
\item The workflow engine service, which drives experimental workflow instances, invokes both the configuration service and application resource broker \cite{Droegemeier2005Service-OrientedWeather}. This is a part of work flow orchestration.
\item The catalog services, represents the manner in which a user or application service discovers public-domain data products, or \acrshort{lead} services \cite{Droegemeier2005Service-OrientedWeather}. This is an important feature that should be available in a weather data system, and it is important to users to search for the availability of the data. Further wants to analyze the existing data for decision making.
\item Users require a host of data services to support rich query, access, and transformation operations on data products. An important goal behind LEAD is access transparency—facilitating user queries across all available heterogeneous data sources without adverse affects from different formats and naming schemes \cite{Droegemeier2005Service-OrientedWeather}. Users need to have transformation services to read data in different format. The query service gives the capability to search via available data without any affect on the data formats.
\end{itemize}
The top of the \ref{fi:lead_soa}, shows the user interface to the system. This give the access to individual services. When user logs into the system, based on the authentication and authorization setting bind to the individual account, the portlets can access the services on behalf of the user. Look into further details is not relevant to developing the \acrshort{wdias}, since the focus is not about workflow orchestration.

\acrshort{lead} is a more advanced system which can support for mesoscale weather prediction with the effort of multiple universities in the United State America with the effort of many of researchers and using many of computer resources. At the time it was building, it uses the \acrshort{soa} architecture as into its depth, and with the implementation each service can scale as needed and possible to enhance the service without interrupting other services. In the \acrshort{wdias} only focus on creating a framework that is extendable as system need more features as like \acrshort{lead} services.

\section{Data Integration and Assimilation System}
\label{se:dias}

\section{Meteorological Assimilation Data Ingest System}
\label{se:madis}

\section{Summary}

\chapter{Method}
\label{ch:method}

Reviews literature and place your work within the existing body of literature here. In chapter \ref{ch:intro} you introduced your thesis.

\section{Introduction}

\section{Service Oriented Architecture}

\section{Microservice Architecture}

\section{Hierarchical Database Structure}

\section{Weather Data Prepossessing}

\subsection{Interpolation}

\subsection{Transformation}

\subsection{Validation}

\section{Query Timeseries}

\chapter{Results}
\label{ch:results}

\section{Test Plan}

\section{Work Load Creation}

\section{Observations}

\chapter{Conclusions}
\label{ch:conc}

Discuss your results and system and conclude.

\section{Summary}

\section{Future Work}

\appendix
\chapter{First Appendix}
Type out your first appendix here.
\section{Basics}

\chapter{First Appendix}
Type out your second appendix here.

\graphicspath{ {./images/} }
\input{glossary.tex}
\bibliographystyle{plain}
\bibliography{mendeley}
\end{document}

### 2019-12-01 thesis.tex
Initial Overleaf Import

--- 2019-12-01 thesis-backup.tex
@@
 \usepackage{import}
+\usepackage{listings}
 
@@
 
-\section{The Delft-FEWS flow forecasting system}
- \acrshort{fews} is developed by Deltares in the Nethaland with targeted for use by operational forecasting agencies.
-The software is freely available to download and setup.
-Tutorials and User setup guide \cite{DeltaresPublicWikiDelft-FEWSGuide} are available with well documentations.
-For non-commercial users need to have the licence agreement to use the system.
-And get new system updates.
-However, investments in new developments in the system are normally paid for by its users.
-The code base of \acrshort{fews} is currently not fully open source.
-But configuration guides and generic adapter module integration code examples are available for the users.
+\import{lit/}{sec_1-fews.tex}
 
-Most if the models are using model-centric approach such as inputs need to be in the format of specific to the model.
-Also the outputs produced by the model are specific to the model and hard to utilize by another systems (e.g.
-FLO2D).
-For the \acrshort{fews} is using much more modular approach, hence it is easy to integrate models into the \acrshort{fews} system.
-Thus \acrshort{fews} can be consider as an integration framework or a middle ware for the models.
-
-Forecasting processes are constructed as a combination of modelling steps and data transformation algorithms.
-These are then combined to provide required forecast capabilities.
-Flexibility is achieved through integrating new models and algorithms into the code base \cite{Werner2013TheSystem}.
-Delft-FEWS system contains no inherent hydrological modelling capabilities within its code base.
-Rather it is a framework which can use to integrate into the system and create work flows for forecasting.
-
-The key elements of a forecasting system are summarized by Haggett \cite{Haggett1998AnWales} as four main steps;
-\begin{enumerate}
-\item Detection
-\item Forecasting
-\item Dissemination and Warning
-\item Response
-\end{enumerate}
-Within these four steps, \acrshort{fews} focuses on the forecasting step.
-The primary objective of this step is to provide additional lead time through predictions of short term future hydro-meteorological conditions \cite{Werner2005FloodCatchments}.
-It is true that, with providing accurate predictions with greater lead time can reduce the level of destruction.
-In order to do the forecasting, the system should be capable of integrating real-time data from hydrological and meteorological observation networks, and the dissemination of prediction results through appropriate products to the warning process.
-
-In figure \ref{fi:fews_schematic} show a schematic view of the connection between the forecasting system to real time data acquisition systems and dissemination systems.
-The widely using concept is using meteorological forecast data to get precipitation and, then using hydrological and hydraulic model chain to predict the level affect on the ground.
-The hydrological and hydraulic model should be design based on the ground.
-Basically ground should be analyze geographically and divide into the catchments.
-Based on the affected catchment, it can be further divide into sub areas in order to reduce the complexity of the simulation task.
-Ideally the forecasting system should therefore be flexible to allow change to models and data, while keeping the way forecasters work with it as constant as possible.
-
-\begin{figure}[htp]
-    \centering
-    \includegraphics[width=0.7\textwidth]{images/fews/Schematic-structure-of-a-fl-ood-forecasting-system-showing-the-position-of-Delft-FEWS_W640.jpg}\\
-    \caption{Schematic structure of a flood forecasting system, showing the position of \acrshort{fews} and links to other primary systems within the operational environment.
-\cite{Werner2013TheSystem} }
-    \label{fi:fews_schematic}
-\end{figure}
-The foundation of \acrshort{fews} is data-centric, with a common data-model through which all components interact.
-All time series data (both scalar and gridded) are stored in this common data-model in a database.
-Modeling capabilities are then linked to the system through one of the interfaces provided to the data-model \cite{Werner2013TheSystem}.
-As mention in the paper, having a common data-model make easy to store data in an efficient way.
-Operations like reporting and sharing the data also make it easy for integrate models.
-But the problem with this approach is, handling the multiple data formats.
-\acrshort{fews} overcome this issue with introducing adapters for most of commonly used data formats.
-This is a good feature which enable users to easily import data into the system.
-But at the same time, it's adding additional complexity into the system.
-
-Time series data is additionally either scalar, vector, or gridded data, though all different types are uniformly stored as binary objects in a time series table.
-None of the functional components (including the linked models) have direct access to the times series table, which is accessible only through the data access module \cite{Werner2013TheSystem}.
-As it explained in the system interpretation, every time all the data access need to go through the data access module which causing to adding more cost in data access.
-Since it is storing the different data types as binary objects, there is a penalty in converting data into binary objects and vice a versa.
-Storing all the data in a time series table causing all the request come into a single data point.
-Even it gives the advantage of accessing all the data at one place.
-Since screaming big amount of data is causing a heavy load on the system, causing to slow down the performance on trying to use the system on large set of data.
-
-Given above drawback on storing the data in the system, within the \acrshort{fews} data model, time series are uniquely identified by their location and data type, as well as an id related to the source of the data (e.g.
-the external source or hydrological model of which the time series are a result) \cite{Werner2013TheSystem}.
-This gives an opportunity to index the data base on above key fields and store the data separately, in order to take the advantage of putting multiple data resources into the system.
-As an example, instead of storing the data at a single timeseries table, it is possible to separate and index the database based on source such as external source or hydrological model of which the time series are a result.
-Or separate by data type and store in multiple storage give the capability for the system to scale with factor of identical types that can be identified.
-Example of separation by data types of scalar, vector and gridded will increase the scaling factor by 3x.
-
-Data processing and manipulation is a required process in weather forecasting.
-Most of the data that is imported from external sources is not at the appropriate temporal and spatial scale to be applied as an input to a forecasting model, or to be used directly in product generation.
-As a consequence, generic data processing steps form the predominant effort in most applications of models in the forecast environment.
-Some examples include data validation, serial and spatial interpolation, aggregation and dis-aggregation, and merging data \cite{Werner2013TheSystem}.
-This a vital feature in a forecasting system, and affect on the quality and accuracy of the predicted data outputs.
-Because of the common data model concept in the \acrshort{fews}, data processing via these function is much effective.
-The system is self provided some of the generic functions for data processing, but for more complex algorithms can be developed as a new Java class coded to communicate with the application programming interface (API).
-It obvious that for additional feature integration, user should implement the new functional extensions via Java programming language.
-Users does not have the flexibility of develop with some other languages they are familiar with or use the support from another language.
-As an example, Python language is easy to use for beginners and many of data scientists are using this programming language for development and it has many data available libraries for data processing.
-But in the \acrshort{fews} users do not ave the capability to take the advantage of such existing things.
-
-\begin{figure}[htp]
-    \centering
-    \includegraphics[width=1.0\textwidth]{images/fews/Architecture-of-Delft-FEWS-showing-the-data-base-the-data-access-layers-and-examples-of_W640.jpg}\\
-    \caption{Architecture of \acrshort{fews} showing the data base, the data access layers and examples of functional modules that communicate through the data access layer.
-\cite{Werner2013TheSystem} }
-    \label{fi:fews_data_layer}
-\end{figure}
-Most of the library of functions provided work equally on scalar and gridded time series.
-As with all other modules this communicates with the database solely through the data access layer as shown in \ref{fi:fews_data_layer} \cite{Werner2013TheSystem}.
-As it shown in the figure, it is clearly showing that, the system is depends on single database and via the data access layer all the requests are coming to the database though a connection.
-It is possible to setup and connect to a enterprise level database with clustering and shading as a paid solution, in order to serve many requests as possible.
-But the design it self inherently suffer with the database bottleneck which effected on running a large set of timeseries or models.
-
-\begin{figure}[htp]
-    \centering
-    \includegraphics[width=0.8\textwidth]{images/fews/Linking-Delft-FEWS-with-external-models-The-fi-gure-shows-the-fl-ow-of-data-through-XML_W640.jpg}\\
-    \caption{ Linking \acrshort{fews} with external models.
-The figure shows the flow of data through XML and native model formats using solid lines, while executable commands are shown by dashed lines.
-\cite{Werner2013TheSystem} }
-    \label{fi:fews_general_adapter}
-\end{figure}
-On of the simple and most effective feature in the \acrshort{fews} is open approach to integration of models and data.
-This approaches the concept of the open modeling framework proposed by \cite{Kokkonen2003InterfacingXML}.
-It simply gives the flexibility to allow operators to integrate more models as well as variations of the same model and come up with new integration flows as much as possible.
-\acrshort{fews} generates the input data as a set of XML files to a defined location; an adapter developed specifically for the model in question transforms this to the required native format in a pre-processing step; \acrshort{fews} executes the model; and the adapter to that model then converts the native formatted results into XML formatted files in a post processing step.
-\acrshort{fews} subsequently imports the results into the database from the XML files (see Fig.
-\ref{fi:fews_general_adapter}) \cite{Werner2013TheSystem}.
-The process is simple and consistence through out all the model integration.
-The model execution is done by the \acrshort{fews} or the model adapter which is causing tide coupling into the execution process in the system.
-Users does not have the flexibility to run the models with different configurations such as running with parallel execution.
-That may be overcome by triggering a external process at the execution time, but it introducing more difficulty for handling after model executed successfully, preceding to the next step in the process.
-This part of the system feature is not focus on the \acrshort{wdias} and user has to come up with own flow or use existing scientific flow management system.
-But it is a concept that need to be discuss and understand properly in order to design a data integration and assimilation system.
-
-Exchanging data with the model is primarily through XML files.
-In some cases these XML files may become very large, which may lead to I/O bottlenecks and subsequent performance issues \cite{Werner2013TheSystem}.
-This issue is thoroughly discussed previous paragraphs and the authors of the \cite{Werner2013TheSystem} seems to be notice and accept it here.
-For overcome this issue they introduced the file-based exchange of data.
-This includes the use of binary-XML files, streaming files through memory, and the use of \acrshort{NetCDF}-CF files.
-But far as for users it seems to be adding more complexity and context in order to get higher performance via the system.
-
-If particular adapter for a model is not present in the list of \acrshort{fews} adapter, user has the flexibility to implement an adapter for it.
-The effort of developing an adapter for a model code not previously integrated with \acrshort{fews} will vary depending on the complexity of the model I/O formats \cite{Werner2013TheSystem}.
-If user wants to use existing adapter and need to configure something not supported via the existing adapter, it is hard to get done.
-Also there are some cases it is hard to develop an adapter or running alongside with the \acrshort{fews}.
-As an example FLO2D model is using for hydrologic modeling and the model is only support only on Windows based operating systems.
-If you setup the system on Linux base operating system and using Linux based models, it is hard for users to come up with a solution for integrating the FLO2D models.
-The final step and one of important feature is exporting the data from the system in useful manner. In the \acrshort{fews}, it is supporting three main forms of product generation.
-\begin{itemize}
-\item Generate web reports with graphs, tables as well as summary reports
-\item Export time series in a variety of formats
-\item External applications actively retrieve data from the system
-\end{itemize}
-The forecasting process is often a sequence of steps, starting with the import of data, a number of data processing and modeling steps, and culminating in the generation of products to be disseminated to the warning process.
-This is supported via the work flow process in the \acrshort{fews}.
-The scope of the \acrshort{wdias} is not focus on adding such a feature in the system, rather user have to use scientific work flow management system or come up with own version of work flow.
-
-When running sequential steps within a work flow in \acrshort{fews}, each step is run for the full time window required (e.g.
-the lead time of the forecast) before moving on to the next step.
-This precludes tightly coupling of models, even explicitly \cite{Werner2013TheSystem}.
-As it mentioned above, users can run multiple models parallel or run those sequentially as needed.
-
-\section{Linked Environments for Atmospheric Discovery}
-
-The reason behind developing \acrfull{lead} by US National Science Foundation (NSF)  is to addresses the fundamental research challenges needed to create an integrated, scalable framework for adaptive analyzing and predicting the atmosphere \cite{Droegemeier2005Service-OrientedWeather}.
-In order to predict and analysis weather models by researchers, it required many resources.
-Rather than each researcher is running and handling own computer resources to do the weather experiments, \acrshort{lead} is providing pool of resources, then the researchers can use this resource pool to run their experiment in shorter amounts of time and in higher scale.
-At the time, researchers are developing their experiment flow, they are not using the resources many, and other are using it at the same time.
-LEAD’s foundation is dynamic work flow orchestration and data management in a Web services framework \cite{Droegemeier2005Service-OrientedWeather}.
-
-The most relevant and important analysis for designing \acrshort{lead} is understanding and analyzing the \acrfull{lead} architecture of it.
-LEAD’s complex array of services, applications, interfaces, and local and remote computing, networking, and storage resources is assembled by users in work flows to study mesoscale weather as it evolves \cite{Droegemeier2005Service-OrientedWeather}.
-As it follows the \acrshort{soa}, everything is implemented as independent services.
-This enable \acrshort{lead} to scale each service as required, and update each service without affecting other services.
-New models which are required for implementing a new forecast flow also has to be implement as a service and then integrate into the system.
-
-In the \ref{fi:lead_system} shows the fundamental capabilities of the \acrshort{lead} system. 
-From the high-level view, \acrshort{lead} lets users query for and acquire information, simulate and predict weather by using numerical atmospheric models, assimilate data, analyze, mine, and visualize data and model output.
-
-\begin{figure}[htp]
-    \centering
-    \includegraphics[width=1.0\textwidth]{images/lead/LEAD-system-Fundamental-capabilities-familiar-to-meteorologists-are-shown-in-the-top_W640.jpg}\\
-    \caption{LEAD system.
-Fundamental capabilities familiar to meteorologists are shown in the top level, below which are the associated tools for enacting these capabilities and the middle-ware that links everything together.
-System-generated products appear at the bottom.
-\cite{Droegemeier2005Service-OrientedWeather} }
-    \label{fi:lead_system}
-\end{figure}
-
-The second level in \ref{fi:lead_system} contains the fundamental tools that help to link services together. This include following tools in brief \cite{Droegemeier2005Service-OrientedWeather};
-\begin{itemize}
-    \item a Web portal, the primary (though not exclusive) user entry point
-    \item the ARPS Data Assimilation System (ADAS), a sophisticated tool for data quality control and assimilation
-    \item myLEAD, a flexible metadata catalog service
-    \item \acrfull{wrf} a next-generation atmospheric prediction and simulation model
-    \item ADaM (Algorithm Development and Mining), a powerful suite of tools for mining observational data, assimilated data sets, and model output 
-    \item Integrated Data Viewer (IDV) 
-\end{itemize}
-
-\begin{figure}[htp]
-    \centering
-    \includegraphics[width=1.0\textwidth]{images/lead/LEAD-system-framework-LEAD-is-composed-of-several-interacting-subsystems-with-the-LEAD_W640.jpg}\\
-    \caption{ LEAD system framework.
-LEAD is composed of several interacting subsystems, with the LEAD grid representing a stable, secure environment for development and testing.
-\cite{Droegemeier2005Service-OrientedWeather} }
-    \label{fi:lead_framework}
-\end{figure}
-
-The Concept of the \acrshort{lead} is, the workflow orchestration for on-demand, real-time, dynamically adaptive systems, called as WOORDS.
-The system is doing the work flow orchestration as given in each procedure.
-Those procedural rules are define by researcher and feed into the system.
-The system is trying to perform the action immediate after the submission, and also it transmit the data, run the models and send back the put put with lower time delay as possible.
-According to the load and other requirement, the system will respond to those requirements automatically.
-
-Lead System is consist of following sub components, as shown in the \ref{fi:lead_soa}. As a brief summary of the subsystems is \cite{Droegemeier2005Service-OrientedWeather};
-\begin{itemize}
-\item User subsystem - comprises the LEAD portal and enable user can access services
-\item Data subsystem - handles data and metadata, any numerical model output produced by operational or experimental models, and user generated information.
-\item Tools subsystem - consists of all meteorological and IT tools
-\item Orchestration subsystem - provides the technologies that let users manage data flows and model execution streams, and create and mine output.
-It also provides linkages to other software and processes for continuous or on-demand applications.
-\end{itemize}
-
-\begin{figure}[htp]
-    \centering
-    \includegraphics[width=0.9\textwidth]{images/lead/LEADs-service-oriented-architecture-A-wide-variety-of-services-and-resources-grouped_W640.jpg}\\
-    \caption{LEAD’s service-oriented architecture.
-A wide variety of services and resources, grouped here according to general functionality, comprise the LEAD architecture, including services that cut across all aspects of the system.
-\cite{Droegemeier2005Service-OrientedWeather} }
-    \label{fi:lead_soa}
-\end{figure}
-
-The distributed computing systems in the LEAD grid represent a distributed test bed for developing, integrating, and testing LEAD’s components.
-
-\acrshort{soa}s are widely deployed in the commercial enterprise sector, and they form the foundation of many scientific “grid” technologies at the time of \acrshort{lead} design and developed.
-A variant of \acrshort{soa} is evolved later called as microservice architecture, and widely use in the industry nowadays.
-The \acrshort{lead} \acrshort{soa} has five distinct yet highly interconnected layers.
-
-The bottom layer represents raw computation, application, and data resources distributed throughout the LEAD grid and elsewhere.
-The next level up holds the Web services that provide access to raw services \cite{Droegemeier2005Service-OrientedWeather}.
-These two layers are working together, since \acrshort{lead} system resources are distributed over multiple locations and creating a pool of resources.
-The upper layer to the raw resources is abstracting the complexity of managing and accessing the resources, and provide a simplified access to the upper layer.
-In the Upper layers, it view as a unlimited resource pool for storing and handling data.
-
-The configuration and execution services in the middle layer, consisting of five elements, represent services invoked by LEAD workflows.
-These are some critical aspects on a weather data management system.
-Most of the services listed here are required for creating work flows for weather data forecasting.
-Thus it is important to review them and understand the basic needs of a weather data management system.
-
-\begin{itemize}
-\item The application-oriented configuration service that manages the deployment and execution of real applications such as the \acrshort{wrf} simulation model, ADAS, and the ADaM tools \cite{Droegemeier2005Service-OrientedWeather}.
-When creating weather work flow, it is required to change the behaviour of model by changing some of the configurations of the model or run a different version of the model.
-\item The application resource broker, which matches the appropriate host for execution to each application task, based on the execution’s time constraints \cite{}.
-This service is a critical part of the system, and responsible of using the resources of the system in optimized manner.
-When designing the weather data system, it is required to increase the capacity of the system automatically, and adopt into the system.
-\item The workflow engine service, which drives experimental workflow instances, invokes both the configuration service and application resource broker \cite{Droegemeier2005Service-OrientedWeather}.
-This is a part of work flow orchestration.
-\item The catalog services, represents the manner in which a user or application service discovers public-domain data products, or \acrshort{lead} services \cite{Droegemeier2005Service-OrientedWeather}.
-This is an important feature that should be available in a weather data system, and it is important to users to search for the availability of the data.
-Further wants to analyze the existing data for decision making.
-\item Users require a host of data services to support rich query, access, and transformation operations on data products.
-An important goal behind LEAD is access transparency—facilitating user queries across all available heterogeneous data sources without adverse affects from different formats and naming schemes \cite{Droegemeier2005Service-OrientedWeather}.
-Users need to have transformation services to read data in different format.
-The query service gives the capability to search via available data without any affect on the data formats.
-\end{itemize}
-The top of the \ref{fi:lead_soa}, shows the user interface to the system.
-This give the access to individual services.
-When user logs into the system, based on the authentication and authorization setting bind to the individual account, the portlets can access the services on behalf of the user.
-Look into further details is not relevant to developing the \acrshort{wdias}, since the focus is not about workflow orchestration.
-
-\acrshort{lead} is a more advanced system which can support for mesoscale weather prediction with the effort of multiple universities in the United State America with the effort of many of researchers and using many of computer resources.
-At the time it was building, it uses the \acrshort{soa} architecture as into its depth, and with the implementation each service can scale as needed and possible to enhance the service without interrupting other services.
-In the \acrshort{wdias} only focus on creating a framework that is extendable as system need more features as like \acrshort{lead} services.
+\import{lit/}{sec_2-lead.tex}
 
@@
 \label{ch:method}
-
-Reviews literature and place your work within the existing body of literature here. In chapter \ref{ch:intro} you introduced your thesis.
+This chapter includes the design decision taken while implementing the \acrfull{wdias}, and how is the system got adapted from the systems analyzed in Chapter \ref{ch:literature}, then how is it trying to propose a better system with overcoming the issues.
 
@@
 
-\section{Service Oriented Architecture}
+\import{method/}{sec_0_introduction.tex}
 
-\section{Microservice Architecture}
+\import{method/}{sec_1-soa.tex}
 
-\section{Hierarchical Database Structure}
+\import{method/}{sec_2-actor_model.tex}
 
-\section{Weather Data Prepossessing}
+\import{method/}{sec_3-microservice.tex}
 
-\subsection{Interpolation}
+\import{method/}{sec_4-db_struct.tex}
 
-\subsection{Transformation}
+\import{method/}{sec_5-data_preprocess.tex}
 
-\subsection{Validation}
-
-\section{Query Timeseries}
+\import{method/}{sec_6-query.tex}
 
@@
 
-\section{Test Plan}
+\import{results/}{sec_1-test_plan.tex}
 
-\section{Work Load Creation}
+\import{results/}{sec_2-work_load.tex}
 
-\section{Observations}
+\import{results/}{sec_3-observations.tex}
+
+\import{results/}{sec_4-conclusion.tex}
 
@@
 
-\section{Summary}
+\import{summary/}{sec_1-summary.tex}
 
-\section{Future Work}
+\import{summary/}{sec_2-future_work.tex}
 

### 2019-12-04 method/sec_4-db_struct.tex
Added Database Structure details

@@
 
+The database structure of WDIAS mainly depends on the key attributes of the timeseries. A brief summary of possible value for timeseries can be describe as below;
+
 - Module ID
+  String field which describe the source of the data generated. Example of hec-hms, flow2d, weather-station etc
 - Value Type
-  - Scalar, Vector, Grid
+  - Scalar, Vector, Grid are the Value Types which are interested in the WDIAS.
 - Location
-- Parameter
+  Location of the timeseries. All locations have unique String identifier called locationId. Further, there are two type of location types that is interested in the WDIAS.
+  - Point locations - Contains a name which is human readable. lat and lon of the location on earth surface.
+  \begin{lstlisting}[language=Python]
+    {
+        "locationId": "wdias-hanwella",
+        "name": "Hanwella",
+        "lat": 6.909722222,
+        "lon": 80.08166667
+    }
+  \end{lstlisting}
+  - Regualr Grid locations - Contains a name which is human readable. The grid presents by deviding into equal size cells. Thus, it need the number of rows and columns. 
+  And the location of the firt cell and the width and height of it.
+  \begin{lstlisting}[language=Python]
+      {
+        "locationId": "wdias_kelani_basin",
+        "description": "Kelani Basin",
+        "rows": 120,
+        "columns": 139,
+        "geoDatum": "Kandawala",
+        "gridFirstCell": {
+            "firstCellCenter": {
+                "x": 397074.0,
+                "y": 504875.0
+            },
+            "xCellSize": 250.0,
+            "yCellSize": 250.0
+        }
+    }
+\end{lstlisting}
+  - Irregualr Grid locations (endpoints are available with in the WDIAS system, but skipped since it is out of the interest of the scope.)
+
+- Parameter - Parameter describe the variable measuring against a location. All parameters ahve a unique String identifier called as parameterId. A parameter can be use in multiple locations.
+While defining a parameter, there are three required fields which need to be provided such as variable, unit and parametertype.
+- Variable - Nature of the variable measuring. Example Precipitation, Temperature and WaterLevel etc
+- Unit - metric unit of measuring
+- Parameter Type - Should be one of 'Instantaneous', 'Accumulative', 'Mean'
+  \begin{lstlisting}[language=Python]
+  {
+      "parameterId": "O.Precipitation",
+      "variable": "Precipitation",
+      "unit": "mm",
+      "parameterType": "Instantaneous"
+  }
+  \end{lstlisting}
+
 - Timeseries Type
-  - sources - External, Simulated
-  - category - Historical, forecast
+Timeseries Type can be combination of Source followed by Category.
+  - Sources - External, Simulated
+  - Category - Historical, Forecast
+
 - Time Step
+All Time Steps has an uniqie String identifier called as timeStepId.
+Unit should be one of 'Second', 'Minute', 'Hour', 'Day', 'Week', 'Month', 'Year', 'NonEquidistant'.
+One of multiplier or divider can be use to define the interval between each measurement.
+\begin{lstlisting}[language=Python]
+{
+    "timeStepId": "each_min",
+    "unit": "Minute",
+    "multiplier": 1,
+    "divider": 0
+}
+\end{lstlisting}
+
+Among above key attributes; Location, Parameter and Time Step attributes are composite attributes. But each of them have an unique identifier.
+Given that, a timeseries can uniquely indentify by moduleId, valueType, parameterId, locationId, timeseriesType and timeStepId.
+\begin{lstlisting}[language=Python]
+{
+	"moduleId": "HEC-HMS",
+	"valueType": "Scalar",
+	"parameterId": "O.Precipitation",
+	"locationId": "wdias_hanwella",
+	"timeseriesType": "External_Historical",
+	"timeStepId": "each_hour",
+}
+\end{lstlisting}
 
@@
 
+WDIAS is using a hierarchical database, with following the concept of Database per Service which is described in the \ref{micro_database_per_service}.
+Following chapters described the usage of databases in WDIAS and reason behind the selection.
+
 - MySQL
-Relational Database Management System (RDBMS)
+Relational Database Management System (RDBMS).
+SQL database has fewer version of open source and it is also possible to gain better performance with commercial versions. 
+Since WDIAS scope is to using open source tools, it is using MySQL as persistent database for storing timeseries metadata described above.
+One instance of MySQL is using only by adapter-metadata service.
+Other than that, another instance of MySQL is using for adapter-extension which will be describe in more detail \ref{data_preprocess}.
+MySQL is used only for these services, those will only keep the consistency of the schema for timeseries metadata and extension metadata.
+\ref{db_struct_redis} instance is using for caching the data from MySQL, since the MySQL database instances, itself not going to get much load.
+Other than MySQL, there are many open source databases can be used to replace the same functionality.
 
@@
 Clustering available with a commercial version
+Among the other timeseries open source databases available, InfluxDB has higher number of usage and support. Database is written in Golang programming language,
+and has higher performance. Other than InfluxDB, another Database is Elastic Search which is mainly using for indexing for searching.
+With changing the configurations of the InfluxDB, it is possible to adapt as required. As mention in \cite{influxdbInfluxDBDocumentation}, 
+InfluxDB can setup on a computer which will give the required performance. Going further, users can use commercial version of InfluxDB in order to gain more performance.
+
+Two instance of InfluxDB is using in the WDIAS system by adapter-scalar and adapter-vector services. For the scalability, the system uses \ref{micro_database_per_service}.
+But further, it split into two services, refering to the \ref{micro_z_axis_scaling} data is partitioned among few servers based on valueType key attribute of timeseries.
+Which also conclude the concept of splitting into more services based on other key attributes such as timeseriesType, if further performance required.
 
@@
 Support parallel file access
+NetCDF is widely using in sciencetific domain due to it's capability of storing data in multi dementions easily and flexibility with storing many of the sciencetific data.
+Python wrapper for NetCDF-C library using in the WDIAS system, and use by adapter-grid service.
 
@@
   Clustering and Sharding available for scalability and reliability
+MongoDB geo-spatial features are using for support Geo queries in the WDIAS. Other than that, external timeseries metadata queries are served by the indexed timeseries metadata data.
+If metadata not present in the adapter-query, if fetch data from the adapter-metadata, then indexed and cache in the MongoDB. Vise a versa, if new timeseries create in the adapter-metadata,
+it trigger an event to adapter-query to index the new timeseries.
+\ref{micro_y_axis_scaling} concept is using here by splitting into the multiple services based on the functionality and scale the system.
 
@@
   Clustering is available for scalability
+Redis uses as in-memory caching for fast access of repreative access data in adapter-metadata and adapter-extension.
+Other than that, adapter-status uses Redis as key value pair store for getting the status for async handling requests such as storing Grid data.
+In adapter-extension uses Redis's Publisher Subscriber capabilities in order to create a cron job in extension-scheduler when new extension create on \ref{data_preprocess}

### 2019-12-04 results/sec_2-work_load.tex
Added Database Structure details

@@
 Precipitation
-\lstinputlisting[language=Octave, firstline=1, lastline=10]{https://raw.githubusercontent.com/wdias/wdias-performance-test/master/data/locations.csv}
+\begin{lstlisting}[language=sh, caption=Test Plan Help]
+-h | --help: Usage
+    <ROOT_DIR> <COMMAND> <REQ_SIZE>
+    - REQ_SIZE (optional): 24(1) | 288(2) | 1044(3)
+  NOTE: Modify test.conf as necessary
+  e.g.
+  test_plan.sh ~/wdias/wdias-performance-test run
+  test_plan.sh ~/wdias/wdias-performance-test run 2
+  - Run all the steps in order of setup, import, 
+    create_extension, extension, export, all, query
+
+  test_plan.sh ~/wdias/wdias-performance-test setup
+  test_plan.sh ~/wdias/wdias-performance-test import 24
+  test_plan.sh ~/wdias/wdias-performance-test create_extension 24
+  test_plan.sh ~/wdias/wdias-performance-test extension 24
+  test_plan.sh ~/wdias/wdias-performance-test export 24
+  test_plan.sh ~/wdias/wdias-performance-test all 24
+  test_plan.sh ~/wdias/wdias-performance-test query 24
+
+  Distributed Mode
+  SERVER_IPS=<IP1,IP2...> test_plan.sh ~/wdias/wdias-performance-test run
+
+\end{lstlisting}
 

### 2019-12-04 results/sec_4-conclusion.tex
Added Database Structure details

\section{Conclusion}

Throughput

Latency

Resource Utilization

Auto Scaling/Scalability

Risk of unable to process data

### 2019-12-05 method/sec_5-data_preprocess.tex
Added Preprocessing

@@
 \section{Extensions (Weather Data Prepossessing)}
+The data imported via imported modules may have incorrect data, missing data and not compatible with directly feed into simulation modules. 
+Thus it required to preprocess data before going to use in such cases. The WDIAS supports these capabilities via Extensions. Current system has
+in build few extensions such as Interpolation, Transformation and Validation. Other than those, it possible to add more extensions as required.
+\begin{figure}[htp]
+    \centering
+    \includegraphics[width=0.5\textwidth]{method/data_preprocess/weather_data_preprocessing.jpg}
+    \caption{Weather Data Preprocessing}
+    \label{fig:weather_data_preprocessing}
+\end{figure}
+The WDIAS provides the support via in build simple generic mathematical function structure. Each extension is considering as a mathematical function which can take p 
+number of input timeseries variables and output n number of timeseries variables. Other than that, at the time of processing the system can configure to provide
+bind constant which can provide while configuring an extension. Which means, it is possible to change the behaviour of a existing function by providing different bind
+constant at the time of creating new tiggers for an extension.
 
 \subsection{Interpolation}
+The Interpolation module generates data at desired locations or at desired points in time by means of either a serial or spatial interpolation technique.
+It is applied for the filling in of data gaps in measured on-line data, as well as to derive spatially distributed data for meteorological time series, such as precipitation and temperature, based on information available at neighbouring locations.
 
 \subsubsection{Serial Interpolation}
+In serial interpolation mode, interpolation is done to fill any gaps in a time series. The interpolation module will only consider the time series itself in filling these gaps.
+\begin{figure}[htp]
+    \centering
+    \includegraphics[width=0.6\textwidth]{method/data_preprocess/serial_interpolation.jpg}
+    \caption{Serial Interpolation}
+    \label{fig:serial_interpolation}
+\end{figure}
 
 \subsubsection{Spatial Interpolation}
+In spatial interpolation mode, the interpolation can be either applied to fill gaps in time series, or to create a new time series for a location using data from other (spatially distributed) locations.
+Spatial interpolation can also be applied for sampling scalar time series from grid time series, for re-sampling grids, or for creating grids from time series data.
+\begin{figure}[htp]
+    \centering
+    \includegraphics[width=0.6\textwidth]{method/data_preprocess/spatial_interpolation.jpg}
+    \caption{Spatial Interpolation}
+    \label{fig:spatial_interpolation}
+\end{figure}
 
 \subsection{Transformation}
+Simple arithmetic manipulation, Time interval transformation and Shifting the series in time
+Specific hydro-meteorological transformation such as stage discharge relationships
+\begin{figure}[htp]
+    \centering
+    \includegraphics[width=0.6\textwidth]{method/data_preprocess/transformation.jpg}
+    \caption{Transformation}
+    \label{fig:transformation}
+\end{figure}
 
 \subsection{Validation}
+Checks for counting reliable, doubtful, unreliable, and missing values
+\begin{figure}[htp]
+    \centering
+    \includegraphics[width=0.6\textwidth]{method/data_preprocess/validation.jpg}
+    \caption{Validation}
+    \label{fig:validation}
+\end{figure}
 
 \subsection{Extension API}
+In the WDIAS, it is possible to create new trigger for an extension via POST request to /extension endpoint.
+\begin{lstlisting}[language=Python]
+{
+    "extensionId": "",
+    "extension": "Interpolation/Transformation/Validation",
+    "function": "",
+    "variables": [
+        {
+            "variableId": "",
+            "metadata/metadtaIds": {
+            }
+        }
+    ],
+    "inputVariables": [],
+    "outputVariables": [],
+    "trigger": [
+        {
+            "trigger_type": "OnChange/OnTime",
+            "trigger_on": []
+        }
+    ],
+    "options": {
+    }
+}
+\end{lstlisting}
+\begin{itemize}
+    \item extensionId - An unique identifier for new extension trigger. Should be unique among all extensions.
+    \item extension - The main extension category which is responsible for handling the extension with extracting data required and storing the output.
+Interpolation/Transformation/Validation support for the moment.
+    \item function - Name of the microservice which is handling the input to output mapping. Fn() function in the \ref{fig:weather_data_preprocessing}.
+    \item variables - Array timeseries mapping to variables.
+Multiple variables can be define with metadata or metadataIds of timeseries.
+Can be use same variable on inputVariables and outputVariables below.
+    \item inputVariables - Timeseries that need to be provide into the function
+    \item outputVariables - Timeseries that output from the function
+    \item trigger - Type of trigger for the extension. Should be one of OnTime or OnChange.
+    \begin{itemize}
+        \item trigger - OnChange
+        \item trigger\_on - List of timeseries to listen on change and trigger the extension
+    \end{itemize}
+    \begin{itemize}
+        \item trigger - OnTime
+        \item trigger\_on - List of schedules that need to be trigger the extension in cronjob string format
+    \end{itemize}
+    \item options - Bind Constant which is bind at the time of creating new extension trigger and pass on triggering the extension.
+\end{itemize}
 

### 2019-12-07 method/sec_4-db_struct.tex
Added Data Preprocess

@@
 
+\subsection{Timeseries Key Attributes}
 - Module ID
@@
 
-- MySQL
+\subsection{MySQL}
 Relational Database Management System (RDBMS).
@@
 
-- InfluxDB \cite{influxdbInfluxDBDocumentation}
+\subsection{InfluxDB} \cite{influxdbInfluxDBDocumentation}
 Open timeseries DB with MIT license
@@
 
-- NetCDF \cite{unidataUnidataNetCDF}
+\subsection{netCDF} \cite{unidataUnidataNetCDF}
+\label{sub:netcdf}
 Network Common Data Form
@@
 
-- MongoDB
+\subsection{MongoDB}
+\label{sub:mongodb}
   MongoDB is a general purpose, document-based, distributed database
@@
 
-- Redis \cite{redisRedisDocumentation}
-  Redis is an open source (BSD licensed), in-memory data structure store, used as a database, cache.
+\subsection{Redis}
+\label{sub:redis}
+  Redis\cite{redisRedisDocumentation} is an open source (BSD licensed), in-memory data structure store, used as a database, cache.
   Clustering is available for scalability
@@
 Other than that, adapter-status uses Redis as key value pair store for getting the status for async handling requests such as storing Grid data.
-In adapter-extension uses Redis's Publisher Subscriber capabilities in order to create a cron job in extension-scheduler when new extension create on \ref{data_preprocess}
+In adapter-extension uses Redis's Publisher Subscriber capabilities in order to create a cron job in extension-scheduler when new extension create on \ref{se:data_preprocess}

### 2019-12-07 method/sec_5-data_preprocess.tex
Added Data Preprocess

@@
 \subsubsection{Extension Handler}
+Extension Handler is responsible for triggering the correct Extension with metadata when there is any change on subscribed extension trigger's OnChange timeseries.
+\begin{figure}[htp]
+    \centering
+    \includegraphics[width=0.6\textwidth]{method/data_preprocess/validation.jpg}
+    \caption{Extension Handler}
+    \label{fig:extension_handler}
+\end{figure}
+
+In further elaboration, when new data imported into one of adapter-scalar or adapter-vector, those notify the extension-handler.
+Then extension handler check whether there is any extension subscribed for particular timeseries, and trigger it via triggering an event on particular extensions.
+
+In order to improve the performance of matching triggers against a timeseries, the WDIAS added two mechanisms.
+For the separation of service responsibilities, those functionalities reside in the adapter-extension and expose via an endpoint.
+First, other than storing extension metadata in MySQL instance of adapter-extension, it also store the data in reverse lookup table called triggers.
+Using this reverse lookup table, for a given trigger\_type and timeseries, it can retrieve the extensions which are part of given timeseries.
+Thus the response which is received by the
+extension-handler only contains the extensions to be triggered. No additional filtering need to be done at the extension-handler service.
+Second, cache the resulting trigger\_type and timeseries data in \acrshort{redis} database for fast access and avoid too much queries on \acrshort{mysql} database.
 
 \subsubsection{Extension Scheduler}
+Extension Handler is responsible for triggering the correct Extension with metadata at given time which is provided at the creation on extension trigger's with the value of OnTime cronjob string value.
+
+In order to improve the performance of triggering cronjobs at given time schedules, the WDIAS added few optimization mechanisms.
+Same as for extension-handler, the adapter-extension expose an endpoint to retrieve extension metadata grouped by cronjob time.
+Then use \acrshort{go} to implement the extension-handler to fast processing the extensions.
+After retrieve extension which are grouped by cronjob time; within the extension-handler, it schedules programatic cronjobs to trigger at given times.
+When each cronjob triggers at given time, it also contains the extensions to be triggered.
+Fetching extension data and creating cronjobs occur with long period of time in order to avoid heavy overhead.
+When a new extension trigger created, those data push into a \acrshort{redis} List.
+Then pulling from the extension-handler in regular time intervals and create new cronjobs for mentioned cronjob time.
+As mentioned above, in order to avoid the expansion of the programmatic cronjob list which are created for new extension triggers, all cronjobs fetch again in long period of time and flush the previously scheduled cronjobs.
+The extension-handler should be run as a single entity for the atrocity, in order to avoid triggering same extension twice.

### 2019-12-07 method/sec_6-query.tex
Added Data Preprocess

@@
 
-- Explain adapter query
-How MongoDB is using for Geo Spatial search.
+As described in \ref{sub:mongodb}, adapter-query is primarily using for support Geo-spatial queries.
+Other than that, as the primary service for searching for timeseries, it also supports for retrieval of timeseries metadata for external queries as well.
 
-<Search API>
+\subsubsection{Timeseries Metadata}
+\begin{lstlisting}
+GET <HOST_NAME>/metadata/timeseries/<TIMESERIES_ID>
+\end{lstlisting}
+
+\begin{lstlisting}
+GET <HOST_NAME>/metadata/timeseries?<QUERY_STRING>
+QUERY_STRING can be consist of zero to many 
+moduleId(Optional) HEC-HMS
+valueType(Optional) Scalar
+parameterId(Optional) O.Precipitation
+locationId(Optional) wdias_hanwella
+timeseriesType(Optional) ExternalHistorical
+timeStepId(Optional) each_15_min
+\end{lstlisting}
+
+\subsubsection{Timeseries Geo Queries}

### 2019-12-07 method/sec_6-query.tex
Added Query Timeseries

@@
 
-\subsubsection{Timeseries Metadata}
+\subsection{Timeseries Metadata}
+Get timeseries metadata by timeseriesID.
 \begin{lstlisting}
@@
 \end{lstlisting}
-
+Search for timeseries metadata with key attributes of the timeseries.
 \begin{lstlisting}
     GET <HOST_NAME>/metadata/timeseries?<QUERY_STRING>
-QUERY_STRING can be consist of zero to many 
-moduleId(Optional) HEC-HMS
-valueType(Optional) Scalar
-parameterId(Optional) O.Precipitation
-locationId(Optional) wdias_hanwella
-timeseriesType(Optional) ExternalHistorical
-timeStepId(Optional) each_15_min
+\end{lstlisting}
+QUERY\_STRING can be consist of zero to multiple parameters. Multiple query parameters are separated by the ampersand, "\&".
+\begin{itemize}
+    \item moduleId(Optional) - E.g. HEC-HMS
+    \item valueType(Optional) - E.g. Scalar
+    \item parameterId(Optional) - E.g. O.Precipitation
+    \item locationId(Optional) - E.g. wdias\_hanwella
+    \item timeseriesType(Optional) - E.g. ExternalHistorical
+    \item timeStepId(Optional) - E.g. each\_15\_min
+\end{itemize}
+For the moment, query are only support by strict matching with above parameter values.
+
+\subsection{Timeseries Geo Queries}
+
+\subsubsection{Query Locations within Area}
+Using following API endpoint, it is possible to query the locations which are exists within the area provided by the geoJson data in the JSON payload.
+\begin{lstlisting}
+    POST <HOST_NAME>/query/location
+    JSON Body:
+    {
+        "geoJson": {
+            "type": "Polygon",
+            "coordinates": [
+                [
+                    [
+                        <longitude>,
+                        <latitude>
+                    ],
+                    ...
+                ]
+            ]
+        }
+    }
 \end{lstlisting}
 
-\subsubsection{Timeseries Geo Queries}
+\subsubsection{Query parameters in Locations}
+Using the following API endpoint, it is possible to query the parameters stored against given locations. Location IDs should be provide as list of JSON payload.
+\begin{lstlisting}
+    POST <HOST_NAME>/query/parameter
+    JSON Body:
+    ["<locationId1>", ...]
+\end{lstlisting}
+
+\subsubsection{Query Timeseries by Location}
+Using the following API endpoint, it is possible to query the timeseries metadata for a given location.
+\begin{lstlisting}
+    POST <HOST_NAME>/query/timeseries
+    JSON Body:
+    {
+        "location": "<LOCATION_ID>"
+    }
+\end{lstlisting}
+
+\subsubsection{Query Timeseries by Locations}
+Using the following API endpoint, it is possible to query the timeseries metadata for a given location set. Location IDs should be provide as list in the locations field.
+\begin{lstlisting}
+    POST <HOST_NAME>/query/timeseries
+    JSON Body:
+    {
+        "locations": ["LOCATION_ID", ...]
+    }
+\end{lstlisting}
+
+\subsubsection{Query Timeseries by Parameter}
+Using the following API endpoint, it is possible to query the timeseries metadata by parameter for given location/locations.
+\begin{lstlisting}
+    POST <HOST_NAME>/query/timeseries
+    JSON Body:
+    {
+        "locations": [""],
+        "parameter": ""
+    }
+\end{lstlisting}
+
+\subsubsection{Query Timeseries in Area}
+Using the following API endpoint, it is possible to query the timeseries metadata within a given area. This operation uses geoWithin \acrshort{mongodb} operator for the simplicity.
+\begin{lstlisting}
+    POST <HOST_NAME>/query/timeseries
+    JSON Body:
+    {
+        "geoJson": {
+            "type": "Polygon",
+            "coordinates": [
+                [
+                    [
+                        <longitude>,
+                        <latitude>
+                    ],
+                    ...
+                ]
+            ]
+        }
+    }
+\end{lstlisting}
+
+\subsubsection{Query Timeseries in Area by Parameter}
+Using the following API endpoint, it is possible to query the timeseries metadata within a given area for given parameter. This is an extension to the above endpoint.
+\begin{lstlisting}
+    POST <HOST_NAME>/query/timeseries
+    JSON Body:
+    {
+        "geoJson": {
+            "type": "Polygon",
+            "coordinates": [
+                [
+                    [
+                        <longitude>,
+                        <latitude>
+                    ],
+                    ...
+                ]
+            ]
+        },
+        "parameter": "<PARAMETER_ID>"
+    }
+\end{lstlisting}
+
+\subsubsection{Query All Timeseries}
+Send a request with empty JSON body will respond with all the timeseries.
+\begin{lstlisting}
+    POST <HOST_NAME>/query/timeseries
+    JSON Body:
+    {}
+\end{lstlisting}

### 2019-12-28 results/sec_1-test_plan.tex
Before Test plan

\section{Test Plan}

1. Test Setup to create timeseries in 1hr, 5min and 1min intervals and create metadata of the timeseries
2. Import Timeseries
  - Plan for test run of 1 hour. In each test run change the request size from 1hr, 5min to 1min. (total 3 hours)
  - Have mixture of data: Scalar - 70%(max 2100 requests), Vector (Multi-Scalar) - 20% (max 600 requests), Grid - 10% (max 300 requests)
3. Extensions
  - Create Extensions for /Aggregation\_Accumulative, /Interpolation Linear, /Validation Missing Values (OnChange and OnTime)
  - 1 hour of test run. Just for 1min data. (total 1 hours)
  - Do with Import Timeseries with error data which will go through extensions.
4. Export Timeseries
  - 1 hour test run. Change request size from 1hr, 5min to 1min. (total 3 hours)
  - Have mixture of data: Scalar - 70%, Vector (Multi-Scalar) - 20%, Grid - 10% (Use the Imported - - - Data before and verify against Extensions)
5. Import + Extension + Export + Timeseries Queries
  - 1 hour test run. Change with request size from 1hr, 5min to 1min. (total 3 hours)

Throughput
Latency
Resource Utilization
Auto Scaling

### 2019-12-28 results/sec_0-introduction.tex
Added test plan

\section{Introduction}
The chapter \ref{ch:results} includes performance study of the \acrshort{wdias}. In the first section \ref{se:test_plan} describes the planned method of testing the system.
In the next section \ref{se:work_load} describes the logic behind creating the work load to do the performance testing planned in \ref{se:test_plan}.
Following section \ref{se:observations} includes the results observed while performance study. And summarised the observations in the next section \ref{se:conclusion}.

### 2019-12-28 results/sec_1-test_plan.tex
Added test plan

@@
 \section{Test Plan}
+The system consists of three modules in functionality perspective of interacting with the \acrshort{wdias}.
+\begin{enumerate}
+    \item Import modules
+    \item Export modules
+    \item Extension modules
+\end{enumerate}
+Other than above, adapter modules act as the core modules and the base of the system. Also query modules allow the users to query for the timeseries
+based on the metadata, and enable performing Geo based queries based on the locations.
 
-1. Test Setup to create timeseries in 1hr, 5min and 1min intervals and create metadata of the timeseries
-2. Import Timeseries
-  - Plan for test run of 1 hour. In each test run change the request size from 1hr, 5min to 1min. (total 3 hours)
-  - Have mixture of data: Scalar - 70%(max 2100 requests), Vector (Multi-Scalar) - 20% (max 600 requests), Grid - 10% (max 300 requests)
-3. Extensions
-  - Create Extensions for /Aggregation\_Accumulative, /Interpolation Linear, /Validation Missing Values (OnChange and OnTime)
-  - 1 hour of test run. Just for 1min data. (total 1 hours)
-  - Do with Import Timeseries with error data which will go through extensions.
-4. Export Timeseries
-  - 1 hour test run. Change request size from 1hr, 5min to 1min. (total 3 hours)
-  - Have mixture of data: Scalar - 70%, Vector (Multi-Scalar) - 20%, Grid - 10% (Use the Imported - - - Data before and verify against Extensions)
-5. Import + Extension + Export + Timeseries Queries
-  - 1 hour test run. Change with request size from 1hr, 5min to 1min. (total 3 hours)
+The test plan is to perform the load test on each above module as separate entity in order to analyse the individual module scalability.
+Then perform load testing on whole system, and analyse the scalability in the system. There are two variables that can vary while doing the performance testing.
+\begin{enumerate}
+    \item Number of requests that can handle at a given time (\acrfull{rps})
+    \item Request size
+\end{enumerate}
+A timeseries is a series of data points in time order. The system may receive the data points in multiple requests.
+The request size can vary based on the use case from one data point to multiple data points. As few examples;
+\begin{itemize}
+    \item A weather station may send current water level in a regular period of 1 minute. In such case, it always comes as a request with one data point with higher frequency.
+    \item Due to resource issue such as batteries, a weather station can collect data points for a given period of time and send as a batch. Another example would be,
+A weather station can collect the precipitation at each 5 minute period and send all the data in 1 hour intervals.
+    \item The forecast precipitation data from \acrshort{wrf} model can be extract for a day in one hour interval and store in the system.
+\end{itemize}
+
+As a upper limit of such scenarios while designing the performance testing, it uses following;
+\begin{itemize}
+    \item Hourly (24 data points) 
+    \item Every 30 minutes (48 data points)
+    \item Every 5 minutes (288 data points) - One request is equivalent to a data points send by a weather station in 5 minutes interval for a whole day
+\end{itemize}
+
+Following are the test cases which are planned to perform;
+\begin{enumerate}
+    \item Test Setup to create timeseries in 1hr, 30min and 5min intervals and create metadata of the timeseries
+    \item Import Timeseries
+    \begin{itemize}
+        \item Plan for test run of 30 minutes. In each test run change the request size from 1hr, 30min and 5min. (total 1.5 hours)
+        \item Have mixture of data: Scalar - 70%(max 210 requests), Vector (Multi-Scalar) - 20% (max 60 requests), Grid - 10% (max 30 requests)
+    \end{itemize}
+    \item Extensions
+    \begin{itemize}
+        \item Create Extensions for /Aggregation\_Accumulative, /Interpolation Linear, /Validation Missing Values (OnChange and OnTime)
+        \item 30min of test run. Just for 5min data. (total 0.5 hours)
+        \item Do with Import Timeseries with error data which will go through extensions.
+    \end{itemize}
+    \item Export Timeseries
+    \begin{itemize}
+        \item 30min test run. Change request size from 1hr, 30min and 5min. (total 1.5 hours)
+        \item Have mixture of data: Scalar - 70%, Vector (Multi-Scalar) - 20%, Grid - 10% (Use the Imported - Data before and verify against Extensions)
+    \end{itemize}
+    \item Import + Extension + Export + Timeseries Queries (All)
+    \begin{itemize}
+        \item 30min test run. Change with request size from 1hr, 30min and 5min. (total 1.5 hours)
+    \end{itemize}
+\end{enumerate}
 

### 2020-01-01 method/sec_4-db_struct.tex
Work load precipitation and water level

@@
   \end{lstlisting}
-  - Regualr Grid locations - Contains a name which is human readable. The grid presents by deviding into equal size cells. Thus, it need the number of rows and columns. 
-  And the location of the firt cell and the width and height of it.
+  - Regular Grid locations - Contains a name which is human readable. The grid presents by dividing into equal size cells. Thus, it need the number of rows and columns. 
+  And the location of the first cell and the width and height of it.
   \begin{lstlisting}[language=Python]
@@
 \end{lstlisting}
-  - Irregualr Grid locations (endpoints are available with in the WDIAS system, but skipped since it is out of the interest of the scope.)
+  - Irregular Grid locations (endpoints are available with in the WDIAS system, but skipped since it is out of the interest of the scope.)
 

### 2020-01-01 results/sec_1-test_plan.tex
Work load precipitation and water level

@@
 
+The percentage of each data type can be vary depend on the situation.
+But most of the applications collect many data from the weather stations in order to correct and validate the models data.
+These weather stations can send the data in different frequencies with different parameters such as precipitation, temperature, humidity, wind direction etc.
+Most of these are scalar data.
+Parameters such as wind direct are vector data which has less percentage compared to scalar data.
+On other side, most of the grid data generate from models and simulations.
+Those produce in less frequency due to cost of the computer resource to produce results.
+After considering those factor, it is logical to come with following percentages;
+\begin{itemize}
+    \item Scalar - 70\%
+    \item Vector - 20\%
+    \item Grid - 10\%
+\end{itemize}
+
 As a upper limit of such scenarios while designing the performance testing, it uses following;
@@
 
-Following are the test cases which are planned to perform;
+Following are the test cases which are planned to performance test cases;
 \begin{enumerate}
@@
         \item Plan for test run of 30 minutes. In each test run change the request size from 1hr, 30min and 5min. (total 1.5 hours)
-        \item Have mixture of data: Scalar - 70%(max 210 requests), Vector (Multi-Scalar) - 20% (max 60 requests), Grid - 10% (max 30 requests)
+        \item Have mixture of data: Scalar - 70\%(max 210 requests), Vector (Multi-Scalar) - 20\% (max 60 requests), Grid - 10\% (max 30 requests)
     \end{itemize}
@@
         \item 30min test run. Change request size from 1hr, 30min and 5min. (total 1.5 hours)
-        \item Have mixture of data: Scalar - 70%, Vector (Multi-Scalar) - 20%, Grid - 10% (Use the Imported - Data before and verify against Extensions)
+        \item Have mixture of data: Scalar - 70\%, Vector (Multi-Scalar) - 20\%, Grid - 10\% (Use the Imported - Data before and verify against Extensions)
     \end{itemize}
@@
 
-Throughput
-Latency
-Resource Utilization
-Auto Scaling
+While performance analysis following metrics are use to measure the performance of the system.
+\begin{itemize}
+    \item Throughput
+    \item Latency
+    \item Resource Utilization
+    \item Auto Scaling
+\end{itemize}

### 2020-01-01 results/sec_2-work_load.tex
Work load precipitation and water level

@@
 \section{Work Load Creation}
+do I need to talk about system setup with EKS?
+add another section for performance tuning?
 
-Precipitation
+== Starts with how locations are created
+As explained in the \ref{ch:method}, timeseries has six primary attributes. In order to create a timeseries for performance testing, it needs data for each key attribute.
+While generating the timeseries for performance testing, it selected locations all over the world as a generic case to include all the locations without binding to a specific area.
+
+These locations https://developers.google.com/public-data/docs/canonical/countries\_csv are static though out the testing, and data added to the wdias-performance-test.
+During the performance test, it creates 1000 timeseries and keep adding data against those timeseries.
+For each location, it creates four timeseries with vary with module Id key attribute with four values.
+Thus combining all together, those creates 1000 timeseries.
+But test cases generate these values before starts the performance tests, and able to increase the timeseries as wanted.
+
+For grid data, it uses static 100 grid locations which based on how is \acrshort{api} exposed.
+Since grid locations have different metadata structure as described in \ref{se:db_struct}, those data handle separately.
+But the locationId of grid and scalar data types have the same effect when define a timeseries.
+
+> Then using those, create timeseries metadata (how it assure 10% of Grid data)
+In the \acrshort{jmeter} Best Practices, \say{If your test needs large amounts of data - particularly if it needs to be \say{randomised} - create the test data in a file that can be read with CSV Data set.
+This avoids wasting resources at run-time.
+- https://jmeter.apache.org/usermanual/best-practices.html\#lean_mean}.
+Rather providing the randomness in run time, the timeseries stored with the random order which satisfy the percentage of 70\% Scalar, 20\% Vector and 10\% Grid as mentioned in \ref{se:test_plan}.
+Before running the test cases, it generate the metadata for timeseries and write into a CSV file which is shared among the threads in the \acrshort{jmeter}.
+This is occurred in the setup phase of the test cases.
+The metadata CSV file arrange in a way that within each 10 lines, 7 lines are Scalar timeseries, 2 lines are Vector timeseries, and 1 line is a Grid timeseries.
+
+== Then how precipitation data for each time period created
+The system is capable of storing any numeric value up to 3 decimal points.
+It does not make any different based on the parameter type whether it is the precipitation or the temperature.
+Thus during the performance testing, \acrshort{jmeter} is using real precipitation data from \acrshort{curw}.
+One month period of data for five weather stations have been using for prepare the test data.
+The script to cleanup and prepare the precipitation data is available as \emph{setup\_precipitation.sh} in wdias-performance.
+
+\begin{lstlisting}[language=sh, caption=Precipitation Data Preparation]
+Set ROOT_DIR=~/wdias/wdias-performance-test
+-h | --help: Usage
+  setup_precipitation.sh  <COMMAND>
+    - COMMAND: help | extract | prepare | cleanup | populate
+  e.g.
+  setup_precipitation.sh prepare
+    Segregate single file data into multiple files based on date. And Separate into main dirs of 15min, 30min, 60min and create tar files
+  setup_precipitation.sh extract
+    Extract the tar files into 15min, 30min and 60min
+  setup_precipitation.sh cleanup
+    Clean up extracted dirs
+\end{lstlisting}
+When preparing the data, it create three set of data based on the time interval such as hourly (60min), 30min, and 15min data with modifying the replicated data.
+This will reduce the overhead in performance testing and increase the performance itself.
+Extract function use while creating the containers, and extract the data into the container. This reduce the context loading while creating the container images.
+While performing the load testing, \acrshort{jmeter} keep update a date counter, and create over the one month data.
+At the end of current month, the date counter advance to the next month.
+But data is repeat using from the beginning.
+In order to provide more randomness, it switch over five locations as well.
+The JSR223 scripts were written in a generic way such that is possible to tweak and use if there are more location data available.
+
+> Then how water level data for Grid time series created
+Almost similar to how was the precipitation data proceed, the water level are prepared for Grid data.
+One exception with Grid data during this test cases was, the maximum time step is 30min, instead of 15min due to larger size of the data.
+But the \acrshort{wdias} is capable of supporting such request.
+The main purpose of the \acrshort{wdias} is to provide a extensible architecture framework, during the performance testing it is not much consider about scaling the Grid data handling as it using \acrshort{netcdf}, and it is another domain with an attraction up to some extend.
+
+\begin{lstlisting}[language=sh, caption=Water level Data Preparation]
+Set ROOT_DIR=~/wdias/wdias-performance-test
+-h | --help: Usage
+  setup_water-level.sh  <COMMAND>
+    - COMMAND: help | extract | prepare | cleanup | populate
+  e.g.
+  setup_water-level.sh prepare
+    Segregate single file data into multiple grid file dirs based on date. And Separate into main dirs of 15min, 30min, 60min and create tar files
+  setup_water-level.sh extract
+    Extract the tar files into 15min, 30min and 60min
+  setup_water-level.sh cleanup
+    Clean up extracted dirs
+\end{lstlisting}
+The water level also contains the real data for one month of period, and \emph{setup\_waterlevel.sh} script provide the functionality of prepare, cleanup and extract.
+Also it reset and repeat reading from the beginning when the \acrshort{jmeter} date counter keep increasing.
+
+> Talk about the test test up - JMeter
+ -> mentioned distributed setup test data collect issue and continue with one server coz it can support what is required
+> Talk about Stepping timer with concurrent thread group
+> Add screenshot of jmeter setup
+> Add prod req graph
+> talk about how test cases are enabled
+> talk about test plans can run
 \begin{lstlisting}[language=sh, caption=Test Plan Help]
@@
 
-Water level
+> JMeter performance tuning
+  Use CSV files rather Random generates
+  Use JSR223 scripts with Grrovy
+  Using Stepping Timer

### 2020-01-02 results/sec_2-work_load.tex
Work plan - Data preparation

@@
 > Then using those, create timeseries metadata (how it assure 10% of Grid data)
-In the \acrshort{jmeter} Best Practices, \say{If your test needs large amounts of data - particularly if it needs to be \say{randomised} - create the test data in a file that can be read with CSV Data set.
+In the \acrshort{jmeter} Best Practices, \say{If your test needs large amounts of data - particularly if it needs to be \emph{randomised} create the test data in a file that can be read with CSV Data set.
 This avoids wasting resources at run-time.
-- https://jmeter.apache.org/usermanual/best-practices.html\#lean_mean}.
+jmeter best practices lean\_mean}.
 Rather providing the randomness in run time, the timeseries stored with the random order which satisfy the percentage of 70\% Scalar, 20\% Vector and 10\% Grid as mentioned in \ref{se:test_plan}.
@@
 But the \acrshort{wdias} is capable of supporting such request.
-The main purpose of the \acrshort{wdias} is to provide a extensible architecture framework, during the performance testing it is not much consider about scaling the Grid data handling as it using \acrshort{netcdf}, and it is another domain with an attraction up to some extend.
+The main purpose of the \acrshort{wdias} is to provide a extensible architecture framework, during the performance testing it is not much consider about scaling the Grid data handling as it using \acrshort{netCDF}, and it is another domain with an attraction up to some extend.
 
@@
   setup_water-level.sh prepare
-    Segregate single file data into multiple grid file dirs based on date. And Separate into main dirs of 15min, 30min, 60min and create tar files
+    Segregate single file data into multiple grid file directories based on date. And Separate into main directories of 15min, 30min, 60min and create tar files
   setup_water-level.sh extract
@@
   setup_water-level.sh cleanup
-    Clean up extracted dirs
+    Clean up extracted directories
 \end{lstlisting}
@@
  -> mentioned distributed setup test data collect issue and continue with one server coz it can support what is required
+\subsection{Experimental Setup}
+In order to create higher work load using the \acrshort{jmeter}, it has Distributed Testing feature.
+It is using the master slave approach and it allowed to handle all the test cases via single instance, rather handling separate instances.
+But it has following limitation;
+\say{Note: The same test plan is run by all the servers.
+JMeter does not distribute the load between servers, each runs the full test plan.
+So if you set 1000 Threads and have 6 JMeter server, you end up injecting 6000 Threads.}
+
+\begin{figure}[htp]
+    \centering
+    \includegraphics[width=0.6\textwidth]{results/work_load/experimental_setup_v3.jpg}
+    \caption{Experimental Setup with JMeter}
+    \label{fi:experimental_setup}
+\end{figure}
+\begin{figure}[htp]
+    \centering
+    \includegraphics[width=1\textwidth]{method/microservice/microservice_architecture-handle_on_async-v3.jpg}
+    \caption{Weather Data Integration and Assimilation System Architecture for Handle Request Asynchronously}
+    \label{fi:wdias_micro_async}
+\end{figure}
+
 > Talk about Stepping timer with concurrent thread group
+
 > Add screenshot of jmeter setup

### 2020-01-03 results/sec_2-work_load.tex
Work Load creation

@@
 
-> Then using those, create timeseries metadata (how it assure 10% of Grid data)
+== Then using those, create timeseries metadata (how it assure 10% of Grid data)
 In the \acrshort{jmeter} Best Practices, \say{If your test needs large amounts of data - particularly if it needs to be \emph{randomised} create the test data in a file that can be read with CSV Data set.
@@
   setup_precipitation.sh prepare
-    Segregate single file data into multiple files based on date. And Separate into main dirs of 15min, 30min, 60min and create tar files
+    Segregate single file data into multiple files based on date. And Separate into main directories of 15min, 30min, 60min and create tar files
   setup_precipitation.sh extract
@@
   setup_precipitation.sh cleanup
-    Clean up extracted dirs
+    Clean up extracted directories
 \end{lstlisting}
@@
 
-> Then how water level data for Grid time series created
+== Then how water level data for Grid time series created
 Almost similar to how was the precipitation data proceed, the water level are prepared for Grid data.
@@
 
-> Talk about the test test up - JMeter
- -> mentioned distributed setup test data collect issue and continue with one server coz it can support what is required
+== Talk about the test test up - JMeter
+=== mentioned distributed setup test data collect issue and continue with one server coz it can support what is required
 \subsection{Experimental Setup}
@@
 JMeter does not distribute the load between servers, each runs the full test plan.
-So if you set 1000 Threads and have 6 JMeter server, you end up injecting 6000 Threads.}
+So if you set 1000 Threads and have 6 JMeter server, you end up injecting 6000 Threads}.
+When test cases runs with \acrshort{jmeter} Distributed mode, the server node trigger same copy of test case on configured slave nodes parallel.
+At the end of the test cases, it gather results into the master node.
 
@@
 \end{figure}
+
+== Talk about Stepping timer with concurrent thread group
+When implementing load test cases with \acrshort{jmeter}, it uses threads to simulate the users.
+The root component of a test create is a thread group.
+There are different kind of thread groups are available such as Thread Group (Basic thread group), Arrivals Thread Group, Free Form Arrivals Thread Group, Stepping Thread Group, Concurrency Thread Group and Ultimate Thread Group etc.
+
+TODO
+\subsubsection{closed vs. open workload models} \cite{Haggett1998AnWales}
+\begin{itemize}
+    \item \emph{closed system model} a new request is only triggered by the completion of a previous request, following by a think time.
+System has negative feedback that makes it impossible to bury-out the service, so users wait for the responses before making new requests.
+    \item \emph{open system model} new requests arrival independently of completions, e.g. according to a stochastic process or fixed trace. System has no negative feedback.
+\end{itemize}
+While implementing the test cases for \acrshort{wdias}, it uses Concurrency Thread Group with Throughput Shaping Timer because of it support the open workload approach.
+Using other thread groups, it required to find exact number of threads and timer delays that produce desired number of requests per second (RPS) to server.
+Which is known as the \emph{closed workload}.
+With using Throughput Shaping Timer, it only need to configure the \acrfull{rps}.
+When combine this \acrshort{jmeter} plugin with Concurrency Thread Group using Schedule Feedback Function to dynamically maintain thread count required to achieve target RPS \cite{Haggett1998AnWales} TODO.
+
+== Add screenshot of jmeter setup
+The test plans mentioned in \ref{se:test_plan} are implemented via the \acrshort{jmeter}. The \ref{fi:wdias_performance_test} shows the overall figure of all the test cases.
 \begin{figure}[htp]
     \centering
-    \includegraphics[width=1\textwidth]{method/microservice/microservice_architecture-handle_on_async-v3.jpg}
-    \caption{Weather Data Integration and Assimilation System Architecture for Handle Request Asynchronously}
-    \label{fi:wdias_micro_async}
+    \includegraphics[width=0.6\textwidth]{results/work_load/wdias_performance_test.png}
+    \caption{WDIAS Performance Test Cases}
+    \label{fi:wdias_performance_test}
+\end{figure}
+In the first step of the plan consist of setting up the timeseries metadata.
+At the same time, it creates the timeseries entry in the \acrshort{wdias} system as well as shown in the \ref{fi:test_create_timeseries}.
+By creating the timeseries before help to reduce the overhead during the performance testing, and cause to more accurate \acrshort{rps} at the run time.
+Otherwise \acrshort{jmeter} need to allocate another set of threads for timeseries creation.
+Since the test cases insert data again set of timeseries, most of the time it about retrieving the timeseries metadata, rather creation a new timeseries in the \acrshort{wdias} system.
+\begin{figure}[htp]
+    \centering
+    \includegraphics[width=0.6\textwidth]{results/work_load/test_create_timeseries.png}
+    \caption{WDIAS Performance Test - Create timeseries}
+    \label{fi:test_create_timeseries}
+\end{figure}
+The \ref{fi:test_all_cases} shows the test cases of other steps of Import, Extensions, Export and combination of All of them as per the detail steps in \ref{se:test_plan}.
+\begin{figure}[htp]
+    \centering
+    \includegraphics[width=0.6\textwidth]{results/work_load/test_all_cases.png}
+    \caption{WDIAS Performance Test - Import, Export, Extension and Query test cases}
+    \label{fi:test_all_cases}
+\end{figure}
+Following test case \ref{fi:test_query_timeseries} for intensively test the query timeseries features.
+\begin{figure}[htp]
+    \centering
+    \includegraphics[width=0.6\textwidth]{results/work_load/test_query_timeseries.png}
+    \caption{WDIAS Performance Test - Query Timeseries}
+    \label{fi:test_query_timeseries}
+\end{figure}
+In the \ref{fi:test_prod_throughtput_shaping_timer} shows the Throughput Shaping Timer configurations for the All test case.
+\begin{figure}[htp]
+    \centering
+    \includegraphics[width=0.6\textwidth]{results/work_load/test_prod_throughtput_shaping_timer.png}
+    \caption{WDIAS Performance Test - Throughput Shaping Timer Graph}
+    \label{fi:test_prod_throughtput_shaping_timer}
 \end{figure}
 
-> Talk about Stepping timer with concurrent thread group
+== talk about how test cases are enabled
+With the above \acrshort{jmeter} test case setup, it need to enable each test case separately and before running via the command line in the server.
+In order to do it in much efficient way, a scripting tool has implemented, and accessible with the code base \cite{Haggett1998AnWales} as \emph{test-dev} TODO.
+\begin{lstlisting}[language=sh, caption=Performance Test Help]
+-h | --help: Usage
+  test-dev enable <MODULE>
+    - MODULE: import(i) | export(e) | extension(x) | all(a)
 
-> Add screenshot of jmeter setup
-> Add prod req graph
-> talk about how test cases are enabled
-> talk about test plans can run
+  test-dev run <REQ_SIZE>
+    First need to enable module that need to be run
+    - REQ_SIZE: 24(1) | 288(2) | 1440(3)
+    NOTE: Modify test.conf as necessary
+    e.g.
+    test-dev run 24
+    or
+    test-dev run 1
+
+  test-dev once <REQ_SIZE> <SEARCH_PHASE>
+    This will enable the test case first. Then run the test case, and at the end disable and exit.
+    - SEARCH_PHASE: Thread Group level name that matches
+    e.g.
+    test-dev once 24 CreateExtensions
+    or
+    test-dev once 1 CreateExtensions
+
+  test-dev disable <MODULE>
+    - MODULE: import(i) | export(e) | extension(x) | all(a)
+\end{lstlisting}
+
+== talk about test plans can run
+As per the usage description of test-dev, it has the features of enable a test case, disable a test case, and run the test case while enabled.
+Another wrapper was implemented around the test-dev as \emph{test-plan.sh} which is also available with the code base \cite{Haggett1998AnWales} TODO.
 \begin{lstlisting}[language=sh, caption=Test Plan Help]
@@
     <ROOT_DIR> <COMMAND> <REQ_SIZE>
+    - COMMAND: setup | import | create_extension | extension | export | all | query
     - REQ_SIZE (optional): 24(1) | 288(2) | 1044(3)
@@
   e.g.
+  test_plan.sh ~/wdias/wdias-performance-test run 2
+  - Run all the steps in order of setup, import, create_extension, extension, export, all, query
   test_plan.sh ~/wdias/wdias-performance-test run
-  test_plan.sh ~/wdias/wdias-performance-test run 2
-  - Run all the steps in order of setup, import, 
-    create_extension, extension, export, all, query
+  - Run all steps for all REQ_SIZE
 
@@
   test_plan.sh ~/wdias/wdias-performance-test import 24
-  test_plan.sh ~/wdias/wdias-performance-test create_extension 24
-  test_plan.sh ~/wdias/wdias-performance-test extension 24
-  test_plan.sh ~/wdias/wdias-performance-test export 24
   test_plan.sh ~/wdias/wdias-performance-test all 24
-  test_plan.sh ~/wdias/wdias-performance-test query 24
 
@@
   SERVER_IPS=<IP1,IP2...> test_plan.sh ~/wdias/wdias-performance-test run
+\end{lstlisting}
+It allows to run particular test plan which are described in \ref{se:test_plan}. Also possible to run the all the test plans in order with given \emph{REQ\_SIZE} or for all the \emph{REQ\_SIZE}.
 
-\end{lstlisting}
+\subsubsection{JMeter performance tuning}
+\begin{itemize}
+    \item Use CSV files rather Random number generation
+    \item Use JSR223 scripts with Groovy for data processing for test cases
+    \item Using Throughput Shaping Timer in order to get more accurate \acrshort{rps}
+\end{itemize}
 
-> JMeter performance tuning
-  Use CSV files rather Random generates
-  Use JSR223 scripts with Grrovy
-  Using Stepping Timer
+\subsection{System Configuration}

### 2020-01-04 results/sec_2-work_load.tex
Work Load - System Configuration

@@
 Before running the test cases, it generate the metadata for timeseries and write into a CSV file which is shared among the threads in the \acrshort{jmeter}.
-This is occurred in the setup phase of the test cases.
+This occurs in the setup phase of the test cases.
 The metadata CSV file arrange in a way that within each 10 lines, 7 lines are Scalar timeseries, 2 lines are Vector timeseries, and 1 line is a Grid timeseries.
@@
 It does not make any different based on the parameter type whether it is the precipitation or the temperature.
-Thus during the performance testing, \acrshort{jmeter} is using real precipitation data from \acrshort{curw}.
+Thus during the performance testing, \acrshort{jmeter} uses real precipitation data from \acrshort{curw}.
 One month period of data for five weather stations have been using for prepare the test data.
@@
 In order to create higher work load using the \acrshort{jmeter}, it has Distributed Testing feature.
-It is using the master slave approach and it allowed to handle all the test cases via single instance, rather handling separate instances.
+It uses the master slave approach and it allowed to handle all the test cases via single instance, rather handling separate instances.
 But it has following limitation;
-\say{Note: The same test plan is run by all the servers.
+\say{Note: The same test plan runs by all the servers.
 JMeter does not distribute the load between servers, each runs the full test plan.
@@
 The test plans mentioned in \ref{se:test_plan} are implemented via the \acrshort{jmeter}. The \ref{fi:wdias_performance_test} shows the overall figure of all the test cases.
+
 \begin{figure}[htp]
@@
 \end{figure}
+
 In the first step of the plan consist of setting up the timeseries metadata.
@@
 Since the test cases insert data again set of timeseries, most of the time it about retrieving the timeseries metadata, rather creation a new timeseries in the \acrshort{wdias} system.
+
 \begin{figure}[htp]
@@
 \end{figure}
+
 The \ref{fi:test_all_cases} shows the test cases of other steps of Import, Extensions, Export and combination of All of them as per the detail steps in \ref{se:test_plan}.
+
 \begin{figure}[htp]
@@
 \end{figure}
+
 Following test case \ref{fi:test_query_timeseries} for intensively test the query timeseries features.
+
 \begin{figure}[htp]
@@
 \end{figure}
+
 In the \ref{fi:test_prod_throughtput_shaping_timer} shows the Throughput Shaping Timer configurations for the All test case.
+
 \begin{figure}[htp]
@@
 In order to do it in much efficient way, a scripting tool has implemented, and accessible with the code base \cite{Haggett1998AnWales} as \emph{test-dev} TODO.
+
 \begin{lstlisting}[language=sh, caption=Performance Test Help]
@@
 Another wrapper was implemented around the test-dev as \emph{test-plan.sh} which is also available with the code base \cite{Haggett1998AnWales} TODO.
+
 \begin{lstlisting}[language=sh, caption=Test Plan Help]
@@
 \end{lstlisting}
+
 It allows to run particular test plan which are described in \ref{se:test_plan}. Also possible to run the all the test plans in order with given \emph{REQ\_SIZE} or for all the \emph{REQ\_SIZE}.
@@
 \subsection{System Configuration}
+As described in the \ref{se:microservice}, the \acrshort{wdias} is mainly focus on microservice architecture and implemented on top of kubernetes.
+\acrfull{k8s} is an open-source system for automating deployment, scaling, and management of containerized applications.
+For the performance study uses \acrfull{eks}.
+There are many \acrshort{k8s} solutions available such as GCP, Azure, Digital Ocean etc on the cloud.
+
+A detailed description of setting up the \acrshort{eks} available as \cite{KarunarathneWdias/Amazon_EKS.md:EKS} within the main repository of the \acrshort{wdias}.
+\acrshort{k8s} is a planet scaling tool \cite{LinuxFoundationProduction-GradeKubernetes}, and users can tweak the configuration to run the \acrshort{wdias} as per the required level of load on the system.
+During the performance test of the \acrshort{wdias}, it uses maximum of 300 \acrshort{rps} with providing to the system with increasing load, and monitor the auto scalability of the system with measuring other performance parameters mentioned in the \ref{se:test_plan}.
+
+\begin{table}[]
+\begin{tabular}{lccccl}
+\hline
+\multicolumn{1}{c}{\textbf{Node Label}} & \textbf{vCPU} & \textbf{RAM (GB)} & \textbf{Storage (GB)} & \textbf{Quantity} & \multicolumn{1}{c}{\textbf{EC2 Name}} \\ \hline
+core & 16 & 32 & 15 & 1 & c5.4xlarge \\
+grid & 8 & 16 & 25 & 1 & c5.2xlarge \\
+scalar & 8 & 16 & 20 & 1 & c5.2xlarge \\
+test & 4 & 10.5 & 5 & 1 & c5n.xlarge \\ \hline
+\end{tabular}
+\caption{\acrshort{eks} nodes}
+\label{tab:aws_eks_nodes}
+\end{table}
+
+The \acrshort{wdias} uses the Helm \cite{CNCFHelmDocs} which is a package manager for \acrshort{k8s}.
+Each microservice within the system deploy and maintain as a helm chart, and the Helm Charts \cite{KarunarathneWdias-helm-charts:Deployments} can be found within the code base.
+For the databases, it uses the official helm charts.
+
+\subsubsection{Performance Tuning}
+In order to get better performance using the available resources, it is possible to schedule each microservice into a predefined set of nodes. There are few ways to do in the \acrshort{k8s};
+\begin{itemize}
+    \item \emph{nodeSelector} - Hard rules match for node schedule. If not match, pods will not schedule.
+    \item \emph{node Affinity and Anti-Affinity} - Soft rules for node schedule. Based on the rules, pods will schedule on most appropriate node.
+    \item \emph{Taints and Tolerations} - Opposite of nodeSelector, repel mismatching pods away from the nodes.
+\end{itemize}
+Users can use one of above features to fine-tune the \acrshort{wdias} to perform better.
+For the moment, \acrshort{wdias} helm charts uses node Affinity in order to use the same charts within local setup with one node and work the same charts on a \acrshort{k8s} cluster with multiple nodes.
+Pods are assigned to the nodes \ref{tab:aws_eks_nodes} based on the node label as below;
+\begin{itemize}
+    \item \emph{core}: metadata, extensions, query, status and extension services
+    \item \emph{grid}: grid adapter, import and export grid data
+    \item \emph{scalar}: scalar and vector adapters, import and export of same data types
+    \item \emph{test}: jmeter and metric server
+\end{itemize}
+The databases uses for data consistency and performance in storage optimization with search capabilities.
+But because of that, it only possible to run one instance of those.
+In the \acrshort{wdias}, the MySQL and MongoDb are not getting higher load as adapter databases such as InfluxDB for scalar and vector data types, and netCDF for grid data type.
+In order to keep up with the pace, those microservice pods are assign to dedicated nodes in order to increase the performance of inter-service communication.

### 2020-02-06 method/sec_5-data_preprocess.tex
Added All 1440 result graphs

@@
 bind constant which can provide while configuring an extension. Which means, it is possible to change the behaviour of a existing function by providing different bind
-constant at the time of creating new tiggers for an extension.
+constant at the time of creating new triggers for an extension.
 

### 2020-02-06 results/sec_2-work_load.tex
Added All 1440 result graphs

@@
 \end{itemize}
+
+- e.g., diagram indicating the nodes and their connectivity (load generator, target, storage, etc.), Then briefly describe the diagram.
+
 Users can use one of above features to fine-tune the \acrshort{wdias} to perform better.

### 2020-02-06 results/sec_3-observations.tex
Added All 1440 result graphs

\section{Observations}

\subsection{Full work load test}

\subsubsection{Test with hourly (24) data}
\begin{table}[]
\begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
\hline
Label & \# Samples & Avg & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
Insert Timeseries & 71826 & 28 & 13 & 2773 & 31 & 58.74 & 0.00\% & 40.5 \\ \hline
Retrieve Timeseries & 71796 & 8 & 7 & 242 & 10 & 4.18 & 0.00\% & 40.7 \\ \hline
Insert Grid & 7982 & 23 & 21 & 126 & 26 & 4.23 & 0.06\% & 4.5 \\ \hline
Retrieve Grid & 7979 & 68 & 59 & 238 & 75 & 10.11 & 0.00\% & 4.5 \\ \hline
Query: Location & 71804 & 3 & 2 & 109 & 3 & 1.52 & 0.00\% & 40.5 \\ \hline
\textbf{TOTAL} & 311182 & 127 & 0 & 2773 & 503 & 207.80 & 0.00\% & 175.4 \\ \hline
\end{tabulary}
\caption{Throughput and Latency of All test cases with 60min data}
\label{tab:obs_all_60_min_summary}
\end{table}

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_60m_transaction_throughtput_vs_threads.png}
    \caption{Performance All Test 60 minutes - Transaction Throughput vs Threads}
    \label{fi:test_obs_all_60m_throughtput}
\end{figure}

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_60m_response_times_percentiles.png}
    \caption{Performance All Test 60 minutes - Response times Percentiles}
    \label{fi:test_obs_all_60m_latency_percentile}
\end{figure}

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_60m_res_latencies_against_hits.png}
    \caption{Performance All Test 60 minutes - Latency against server hits}
    \label{fi:test_obs_all_60m_latency}
\end{figure}

\subsubsection{Test with 30min (48) data}
\begin{table}[]
\begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
\hline
Label & \# Samples & Average & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
Insert Timeseries & 71759 & 29 & 14 & 1699 & 32 & 50.97 & 0.00\% & 40.5 \\ \hline
Retrieve Timeseries & 71730 & 9 & 7 & 1033 & 10 & 6.04 & 0.00\% & 40.6 \\ \hline
Insert Grid & 7972 & 44 & 40 & 162 & 49 & 8.17 & 0.08\% & 4.5 \\ \hline
Retrieve Grid & 7971 & 81 & 67 & 284 & 93 & 15.15 & 0.00\% & 4.5 \\ \hline
Query: Location & 71734 & 3 & 2 & 110 & 3 & 1.90 & 0.00\% & 40.5 \\ \hline
TOTAL & 310878 & 129 & 0 & 1699 & 503 & 207.10 & 0.00\% & 175.3 \\ \hline
\end{tabulary}
\caption{Throughput and Latency of All test cases with 30min data}
\label{tab:obs_all_30_min_summary}
\end{table}

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_30m_transaction_throughtput_vs_threads.png}
    \caption{Performance All Test 30 minutes - Transaction Throughput vs Threads}
    \label{fi:test_obs_all_30m_throughtput}
\end{figure}

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_30m_response_times_percentiles.png}
    \caption{Performance All Test 30 minutes - Response times Percentiles}
    \label{fi:test_obs_all_30m_latency_percentile}
\end{figure}

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_30m_res_latencies_against_hits.png}
    \caption{Performance All Test 30 minutes - Latency against server hits}
    \label{fi:test_obs_all_30m_latency}
\end{figure}

\subsubsection{Test with 15min (96) data}
\begin{table}[]
\begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
\hline
Label & \# Samples & Average & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
Insert Timeseries & 71775 & 30 & 12 & 1719 & 41 & 51.71 & 0.00\% & 40.5 \\ \hline
Query: Location & 71749 & 3 & 2 & 130 & 4 & 2.32 & 0.00\% & 40.5 \\ \hline
Insert Grid & 7975 & 91 & 77 & 279 & 112 & 19.58 & 1.42\% & 4.5 \\ \hline
Retrieve Timeseries & 71736 & 23 & 8 & 1623 & 32 & 50.18 & 0.00\% & 40.6 \\ \hline
Retrieve Grid & 7972 & 118 & 80 & 876 & 165 & 56.15 & 0.00\% & 4.5 \\ \hline
\textbf{TOTAL} & 310934 & 134 & 0 & 1719 & 503 & 206.40 & 0.04\% & 175.4 \\ \hline
\end{tabulary}
\caption{Throughput and Latency of All test cases with 15min data}
\label{tab:obs_all_15_min_summary}
\end{table}

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_15m_transaction_throughtput_vs_threads.png}
    \caption{Performance Test - Transaction Throughput vs Threads}
    \label{fi:test_obs_all_15m_throughtput}
\end{figure}

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_15m_response_times_percentiles.png}
    \caption{Performance Test - Response times Percentiles}
    \label{fi:test_obs_all_15m_latency_percentile}
\end{figure}

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_15m_res_latencies_against_hits.png}
    \caption{Performance Test - Latency against server hits}
    \label{fi:test_obs_all_15m_latency}
\end{figure}

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_15m_resource_utilization.png}
    \caption{Performance Test - Resource Utilization}
    \label{fi:test_obs_all_15m_resources}
\end{figure}

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_15m_resource_pods.png}
    \caption{Performance Test - Number of Active pods}
    \label{fi:test_obs_all_15m_pods}
\end{figure}

\subsubsection{Load test with \acrfull{k8s} auto pod scaling}
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_import_export_res.png}
    \caption{Performance All Test 15min Interval - Auto Scaling Resource Usage of Import and Export Modules }
    \label{fi:obs_all_auto_15m_import_export_res}
\end{figure}

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_import_grid_pod.png}
    \caption{Performance All Test 15min Interval - Auto Scaling Import ASCII Grid Number of Pods Over Time }
    \label{fi:obs_all_auto_15m_import_grid_pod}
\end{figure}

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_adapter_dbs_res.png}
    \caption{Performance All Test 15min Interval - Auto Scaling Resource Usage of Database Adapters }
    \label{fi:obs_all_auto_15m_adapter_dbs_res}
\end{figure}

\subsection{Import module load test}
\begin{table}[]
\begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
\hline
Label & \# Samples & Average & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
Insert Timeseries & 91345 & 212 & 15 & 5288 & 241 & 556.05 & 0.01\% & 123.4 \\ \hline
Insert Grid Timeseries & 10189 & 108 & 76 & 330 & 148 & 30.98 & 0.00\% & 13.8 \\ \hline
\textbf{TOTAL} & 101534 & 202 & 15 & 5288 & 212 & 528.43 & 0.01\% & 137.2 \\ \hline
\end{tabulary}
\caption{Throughput and Latency of Import test cases with 15min data}
\label{tab:obs_import_15_min_summary}
\end{table}

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/import/obs_import_15m_transaction_throughtput_vs_threads.png}
    \caption{Performance Import Test 15 minutes Interval - Transaction Throughput vs Threads}
    \label{fi:test_obs_import_15m_throughtput}
\end{figure}

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/import/obs_import_15m_res_latencies_against_hits.png}
    \caption{Performance Import Test 15 minutes Interval - Latency against server hits}
    \label{fi:test_obs_import_15m_latency}
\end{figure}

\subsection{Export module load test}
Need to redo just after the import
\begin{table}[]
\begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
\hline
Label & \# Samples & Average & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
Retrieve Timeseries & 136310 & 9 & 7 & 287 & 11 & 6.37 & 0.00\% & 156.1 \\ \hline
Retrieve Grid Timeseries & 15147 & 265 & 10 & 4044 & 488 & 691.69 & 46.36\% & 17.4 \\ \hline
\textbf{TOTAL} & 151457 & 35 & 7 & 4044 & 13 & 231.92 & 4.64\% & 173.4 \\ \hline
\end{tabulary}
\caption{Throughput and Latency of Export test cases with 15min data}
\label{tab:obs_export_15_min_summary}
\end{table}

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/export/obs_export_15m_transaction_throughtput_vs_threads.png}
    \caption{Performance Export Test 15 minutes Interval - Transaction Throughput vs Threads}
    \label{fi:test_obs_export_15m_throughtput}
\end{figure}

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/export/obs_export_15m_res_latencies_against_hits.png}
    \caption{Performance Export Test 15 minutes Interval - Latency against server hits}
    \label{fi:test_obs_export_15m_latency}
\end{figure}

\subsection{Extension module load test}

\subsection{Query module load test}

\subsection{Compare with other systems}

Throughput
Latency
Resource Utilization
Auto Scaling/Scalability

### 2020-02-06 summary/sec_2-future_work.tex
Added All 1440 result graphs

\section{Future Work}
- Lack of data prepossessing modules
- Supporting Irregular Grids
- Grid performance
- Define infrastructure as code - Teraform
- Improve test cases - correct RPS
- Further improve hierarchical database performance
- Add Alerting extension modules
- Add pubsub extension modules

### 2020-02-08 results/sec_1-test_plan.tex
Update Obs Full test 24 and 48 request size

@@
 
+\subsection{Test Plan Flow}
+\label{subse:test_plan_flow}
 Following are the test cases which are planned to performance test cases;
 \begin{enumerate}
-    \item Test Setup to create timeseries in 1hr, 30min and 5min intervals and create metadata of the timeseries
+    \item Test Setup to create timeseries in 1hr, 30min and 15min intervals and create metadata of the timeseries
     \item Import Timeseries
     \begin{itemize}
-        \item Plan for test run of 30 minutes. In each test run change the request size from 1hr, 30min and 5min. (total 1.5 hours)
-        \item Have mixture of data: Scalar - 70\%(max 210 requests), Vector (Multi-Scalar) - 20\% (max 60 requests), Grid - 10\% (max 30 requests)
+        \item Plan for test run of 15 minutes with the request size of 15min data.(total 0.25 hours)
+        \item Have mixture of data: Scalar - 70\%(max 210 requests per second), Vector (Multi-Scalar) - 20\% (max 60 requests per second), Grid - 10\% (max 30 requests per second)
     \end{itemize}
@@
         \item Create Extensions for /Aggregation\_Accumulative, /Interpolation Linear, /Validation Missing Values (OnChange and OnTime)
-        \item 30min of test run. Just for 5min data. (total 0.5 hours)
+        \item Plan for the 15 minutes of test run with the request size of 15min data. (total 0.25 hours)
         \item Do with Import Timeseries with error data which will go through extensions.
@@
     \begin{itemize}
-        \item 30min test run. Change request size from 1hr, 30min and 5min. (total 1.5 hours)
+        \item Plan for 15 minutes of test run with the request size of 15min data. (total 0.25 hours)
         \item Have mixture of data: Scalar - 70\%, Vector (Multi-Scalar) - 20\%, Grid - 10\% (Use the Imported - Data before and verify against Extensions)
@@
     \begin{itemize}
-        \item 30min test run. Change with request size from 1hr, 30min and 5min. (total 1.5 hours)
+        \item Plan for 30 minutes of test run with the request size of 1hr (60min) data.
+        \item Plan for 30 minutes of test run with the request size of 30min data.
+        \item Plan for 30 minutes of test run with the request size of 15min data.
+        \item Plan for 30 minutes of test run with the request size of 15min data with Auto Scaling.
+        \item All test plan run against 60min, 30min and 15min request size of data. Another test plan run with enabling the Auto Scaling. (total 2 hours)
     \end{itemize}
@@
 
-While performance analysis following metrics are use to measure the performance of the system.
+\subsection{Test Plan Observe Metrics}
+\label{subse:test_plan_metrics}
+During the performance analysis, following metrics are use to measure the performance of the system.
 \begin{itemize}
-    \item Throughput
-    \item Latency
-    \item Resource Utilization
-    \item Auto Scaling
+    \item Throughput - Number of requests that can be process per unit time. Normally for \acrshort{wdias} performance observations, it uses \acrfull{rps} in order to measure the throughput.
+    \item Latency - Time taken for response back to the sent request to the system.
+Normally it measures with milliseconds (ms) in the \acrshort{wdias}.
+During the performance analysis, it measures the minimum response time, maximum response time, the average response time, and standard deviation.
+The standard deviation measures the mean distance of the values to their average.It gives an idea of the dispersion or variability of the measures to their mean value.
+So, if the deviation value is low compared to the mean value, it will indicate that the measures are not dispersed (or mostly close to the mean value) and that the mean value is significant.
+Other than that, it measure the response time into 90\% percentile, while gives best response time up to 90\% percent of the responses.
+    \item Resource Utilization - Resource Utilization is calculated based on the CPU and Memory usage via \acrshort{k8s} metrics server.
+It calculates the resource utilization over 60 seconds of time window.
+Network usage is getting based on the actual physical machines.
+    \item Auto Scaling - The \acrshort{wdias} is running with two configurations.
+First is, since it is running the microservice as docker containers, it allow to increase or shrink the resource usage and share the resources within a physical machine.
+Second is, running with auto scaling enabled for the microservice which are using higher resources.
 \end{itemize}

### 2020-02-08 results/sec_3-observations.tex
Update Obs Full test 24 and 48 request size

@@
 \section{Observations}
+According the \ref{se:test_plan} section, this section includes the observations after performing the test plans on the \acrshort{wdias} system setup and test plan test up which is explained in the \ref{se:work_load}.
 
-\subsection{Full work load test}
+Following \ref{subse:obs_test_plan_all_60min}, \ref{subse:obs_test_plan_all_30min}, \ref{subse:obs_test_plan_all_15min} and \ref{subse:obs_test_plan_all_auto_15min} sections discussed about the observations collected with performing the Full test plan (also known as All test plan) over 60 minutes (24 data points), 30 minutes (48 data points) and 15 minutes (96 data points) by variate the request size.
+Then another performance test with enabling Auto Scaling as explained in \ref{subse:test_plan_metrics} for high resource utilized microservice.
 
-\subsubsection{Test with hourly (24) data}
+\subsection{Full Test with hourly data (24 Request Size)}
+\label{subse:obs_test_plan_all_60min}
+After running the All test plan with 60 minutes (24 data points), it observed the data summary of \ref{tab:obs_all_60_min_summary}. It performed 311k of sample requests.
 \begin{table}[]
@@
 \end{table}
+Insert Timeseries performed over Scalar and Vector data types with each request send with 24 data points.
+On average it takes 28ms to insert data into the \acrshort{wdias}, and up to 90\% percentile inserted data within 31ms.
+Noticeably it has 0\% of errors which means that all the request are completed successfully.
+On average, \acrshort{wdias} handled 40.5 \acrshort{rps} with the given workload.
+The performance of the Retrieve of Scalar and Vector Timeseries are similar to insert timeseries due to it depends on it.
+On the other hand, Insert Grid Timeseries data perform with 23ms with almost all the request perform within same amount of time, hence the standard deviation is smaller.
+Retrieve Grid Timeseries data perform the same but with bit higher value of latency of 68ms.
+Both of insert and retrieve grid timeseries data have 4.5 \acrshort{rps} since it only get 10\% of the number of request per given time via the test plan as explain in the data ration in \ref{se:test_plan}.
 
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_60m_transaction_throughtput_vs_threads.png}
-    \caption{Performance All Test 60 minutes - Transaction Throughput vs Threads}
-    \label{fi:test_obs_all_60m_throughtput}
+    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_60m_response_times_vs_threads.png}
+    \caption{Performance All Test 60 minutes - Response Time vs Threads}
+    \label{fi:test_obs_all_60m_response_vs_threads}
 \end{figure}
-
-\begin{figure}[htp]
-    \centering
-    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_60m_response_times_percentiles.png}
-    \caption{Performance All Test 60 minutes - Response times Percentiles}
-    \label{fi:test_obs_all_60m_latency_percentile}
-\end{figure}
+\ref{fi:test_obs_all_60m_response_vs_threads} show the response time against the number of active threads.
+As the graph show, the response time kept same while increasing the number of active threads against each test case.
+This shows the scalability of the \acrshort{wdias}, since the system able to process more requests without a significant change in the latency.
+When number of active threads increased more than 122, the \ref{fi:test_obs_all_60m_response_vs_threads} show uncertainty in the inserting and retrieving Scalar and Vector data.
 
@@
 \end{figure}
+\ref{fi:test_obs_all_60m_latency} graph provides a better overview of the variation of latency over elapsed time of the test plan against number of server hits per second.
+The conclusion of giving static latency while increasing the number of requests in \ref{fi:test_obs_all_60m_response_vs_threads} can further prove with this graph, since \ref{fi:test_obs_all_60m_latency} graph gives in details overview over the test plan time span.
 
-\subsubsection{Test with 30min (48) data}
+\subsection{Full Test with 30min data (48 Request Size)}
+\label{subse:obs_test_plan_all_30min}
+This section \ref{subse:obs_test_plan_all_30min} discussed about the All test plan performance with 30 minutes data which means 48 data points per each request in Scalar and Vector timeseries, and 48 ASCII Grid files per each insert request.
+It performed 310k of sample requests which is almost similar to \ref{subse:obs_test_plan_all_60min} processed samples.
 \begin{table}[]
@@
 \end{table}
+\ref{tab:obs_all_30_min_summary} shows the response latency summary details and \acrshort{rps} as explained in \ref{subse:obs_test_plan_all_60min}.
+And the results are almost similar to the observations in \ref{tab:obs_all_60_min_summary}.
+This implies that, even the request size is increased, the \acrshort{wdias} can perform better same as the with smaller size of data.
 
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_30m_transaction_throughtput_vs_threads.png}
-    \caption{Performance All Test 30 minutes - Transaction Throughput vs Threads}
-    \label{fi:test_obs_all_30m_throughtput}
+    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_30m_response_times_vs_threads.png}
+    \caption{Performance All Test 30 minutes - Response Time vs Threads}
+    \label{fi:test_obs_all_30m_response_vs_threads}
 \end{figure}
-
-\begin{figure}[htp]
-    \centering
-    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_30m_response_times_percentiles.png}
-    \caption{Performance All Test 30 minutes - Response times Percentiles}
-    \label{fi:test_obs_all_30m_latency_percentile}
-\end{figure}
+\ref{fi:test_obs_all_30m_response_vs_threads} show the response time against the number of active threads.
+As the graph show, the response time kept same while increasing the number of active threads against each test case.
+This shows the scalability of the \acrshort{wdias}, since the system able to process more requests without a significant change in the latency.
+When number of active threads increased more than 110, the \ref{fi:test_obs_all_60m_response_vs_threads} show uncertainty in the inserting and retrieving Scalar and Vector data.
+This graph is similar to the \ref{fi:test_obs_all_60m_response_vs_threads}, but the active thread count goes down as a result of increasing the request size.
 
@@
 \end{figure}
+\ref{fi:test_obs_all_30m_latency} graph provides a better overview of the variation of latency over elapsed time of the test plan against number of server hits per second.
+This graph also conclude that, over the time latency does not change very much. But during the peak load, it shows some variation in insert and retrieve of Grid timeseries.
+When compared to \ref{fi:test_obs_all_60m_latency}, the latencies for insert and retrieve Grid timeseries increase by some amount.
 
-\subsubsection{Test with 15min (96) data}
+\subsection{Full Test with 15min data (96 Request Size)}
+\label{subse:obs_test_plan_all_15min}
 \begin{table}[]
@@
 
-\subsubsection{Load test with \acrfull{k8s} auto pod scaling}
+\subsection{Full Load test with \acrfull{k8s} auto pod scaling}
+\label{subse:obs_test_plan_all_auto_15min}
 \begin{figure}[htp]
@@
 \subsection{Query module load test}
-
-\subsection{Compare with other systems}
-
-Throughput
-Latency
-Resource Utilization
-Auto Scaling/Scalability

### 2020-02-08 results/sec_3-observations.tex
Updated Test All 15min

@@
 This section \ref{subse:obs_test_plan_all_30min} discussed about the All test plan performance with 30 minutes data which means 48 data points per each request in Scalar and Vector timeseries, and 48 ASCII Grid files per each insert request.
-It performed 310k of sample requests which is almost similar to \ref{subse:obs_test_plan_all_60min} processed samples.
+It performed round up to 311k of sample requests which is almost similar to \ref{subse:obs_test_plan_all_60min} processed samples.
 \begin{table}[]
@@
 \end{figure}
-\ref{fi:test_obs_all_30m_response_vs_threads} show the response time against the number of active threads.
+\ref{fi:test_obs_all_30m_response_vs_threads} show the response time against the number of active threads for 30min data.
 As the graph show, the response time kept same while increasing the number of active threads against each test case.
 This shows the scalability of the \acrshort{wdias}, since the system able to process more requests without a significant change in the latency.
-When number of active threads increased more than 110, the \ref{fi:test_obs_all_60m_response_vs_threads} show uncertainty in the inserting and retrieving Scalar and Vector data.
+When number of active threads increased more than 110, the \ref{fi:test_obs_all_30m_response_vs_threads} show uncertainty in the inserting and retrieving Scalar and Vector data.
 This graph is similar to the \ref{fi:test_obs_all_60m_response_vs_threads}, but the active thread count goes down as a result of increasing the request size.
@@
 This graph also conclude that, over the time latency does not change very much. But during the peak load, it shows some variation in insert and retrieve of Grid timeseries.
-When compared to \ref{fi:test_obs_all_60m_latency}, the latencies for insert and retrieve Grid timeseries increase by some amount.
+When compared to \ref{fi:test_obs_all_60m_latency}, the latency for insert and retrieve Grid timeseries increase by some amount.
 
@@
 \label{subse:obs_test_plan_all_15min}
+This section \ref{subse:obs_test_plan_all_15min} discussed about the All test plan performance with 15 minutes data which means 96 data points per each request in Scalar and Vector timeseries, and 48 ASCII Grid files per each insert Grid timeseries request.
+These requests are four times larger than the \ref{subse:obs_test_plan_all_60min} request size.
+It performed approximately 311k of sample requests which is almost similar to \ref{subse:obs_test_plan_all_30min} processed samples.
 \begin{table}[]
@@
 Insert Timeseries & 71775 & 30 & 12 & 1719 & 41 & 51.71 & 0.00\% & 40.5 \\ \hline
+Retrieve Timeseries & 71736 & 23 & 8 & 1623 & 32 & 50.18 & 0.00\% & 40.6 \\ \hline
+Insert Grid & 7975 & 91 & 77 & 279 & 112 & 19.58 & 1.42\% & 4.5 \\ \hline
+Retrieve Grid & 7972 & 118 & 80 & 876 & 165 & 56.15 & 0.00\% & 4.5 \\ \hline
 Query: Location & 71749 & 3 & 2 & 130 & 4 & 2.32 & 0.00\% & 40.5 \\ \hline
-Insert Grid & 7975 & 91 & 77 & 279 & 112 & 19.58 & 1.42\% & 4.5 \\ \hline
-Retrieve Timeseries & 71736 & 23 & 8 & 1623 & 32 & 50.18 & 0.00\% & 40.6 \\ \hline
-Retrieve Grid & 7972 & 118 & 80 & 876 & 165 & 56.15 & 0.00\% & 4.5 \\ \hline
 \textbf{TOTAL} & 310934 & 134 & 0 & 1719 & 503 & 206.40 & 0.04\% & 175.4 \\ \hline
@@
 \end{table}
+\ref{tab:obs_all_15_min_summary} shows the response latency summary details and \acrshort{rps} as same as explained in \ref{subse:obs_test_plan_all_30min}.
+And the latency observations are increased by some amount when compared to the observations in \ref{tab:obs_all_30_min_summary}.
+Noticeably retrieving latency of all type of data types increased by considerable amount.
+Same following the trend, standard deviation of retrieve timeseries data increased my considerable amount for all the types.
+We can assume that more writing to the databases affected on reads as well.
+Event the request data size increased by 4x time, the \acrshort{wdias} were able to handle them without any significant performance issues.
+And the system able to provide the same throughput as \ref{tab:obs_all_30_min_summary}.
+
+\begin{figure}[htp]
+    \centering
+    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_15m_response_times_vs_threads.png}
+    \caption{Performance Test - Response Time vs Active Threads}
+    \label{fi:test_obs_all_15m_response_vs_threads}
+\end{figure}
+\ref{fi:test_obs_all_15m_response_vs_threads} show the response time against the number of active threads for 15min data.
+As the graph show, the response time kept same while increasing the number of active threads against each test case.
+When number of active threads increased more than 140, the \ref{fi:test_obs_all_15m_response_vs_threads} show uncertainty in the inserting and retrieving all data types.
+The latency of insert and retrieve Grid timeseries data goes up compared to \ref{fi:test_obs_all_30m_response_vs_threads}.
+With higher request size, it become to notice the latency also increase by a small factor when the number of active thread increased.
+This can clearly notice on with insert and retrieval of Grid timeseries data.
+
+\begin{figure}[htp]
+    \centering
+    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_15m_res_latencies_against_hits.png}
+    \caption{Performance Test - Latency against server hits}
+    \label{fi:test_obs_all_15m_latency}
+\end{figure}
+\ref{fi:test_obs_all_15m_latency} graph provides a overview of the variation of latency over elapsed time of the test plan against number of server hits per second for 15min data.
+This graph show that over the time \acrshort{wdias} were able to keep the latency constant over the test plan. But at the peak time, it tend to vary from the mean value a lot.
+One noticeable fact is, throw out the test time period, it shows spikes in latency when compared to \ref{fi:test_obs_all_60m_latency} and \ref{fi:test_obs_all_30m_latency}.
 
@@
 \end{figure}
+\ref{fi:test_obs_import_15m_throughtput} shows the total server's transaction throughput against number of active threads.
+The formula for total server transaction throughput is \(<active threads> * 1 second / <1  thread response time>\) \cite{JMeterPluginsDocumentationJMeter-Plugins.org}.
+Basically, it shows the statistical maximum possible number of transactions based on number of users accessing the application.
+With combining the \ref{fi:test_obs_all_15m_latency}, this graph show that the throughput of the system get increased without much change in the latency, thus it proves the scalability of the \acrshort{wdias}.
 
@@
 \end{figure}
-
-\begin{figure}[htp]
-    \centering
-    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_15m_res_latencies_against_hits.png}
-    \caption{Performance Test - Latency against server hits}
-    \label{fi:test_obs_all_15m_latency}
-\end{figure}
-
-\begin{figure}[htp]
-    \centering
-    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_15m_resource_utilization.png}
-    \caption{Performance Test - Resource Utilization}
-    \label{fi:test_obs_all_15m_resources}
-\end{figure}
-
-\begin{figure}[htp]
-    \centering
-    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_15m_resource_pods.png}
-    \caption{Performance Test - Number of Active pods}
-    \label{fi:test_obs_all_15m_pods}
-\end{figure}
+\ref{fi:test_obs_all_15m_latency_percentile} visually shows the summary of \ref{tab:obs_all_15_min_summary} latency up to 90\% percentile.
+With a higher request size data, the \acrshort{wdias} able to process the requests without significant change in latency up to 90\% percentile.
 

### 2020-02-08 results/sec_3-observations.tex
Updated All test with Auto

@@
 \label{subse:obs_test_plan_all_15min}
-This section \ref{subse:obs_test_plan_all_15min} discussed about the All test plan performance with 15 minutes data which means 96 data points per each request in Scalar and Vector timeseries, and 48 ASCII Grid files per each insert Grid timeseries request.
+This section \ref{subse:obs_test_plan_all_15min} discussed about the All test plan performance with 15 minutes data which means 96 data points per each request in Scalar and Vector timeseries, and 96 ASCII Grid files per each insert Grid timeseries request.
 These requests are four times larger than the \ref{subse:obs_test_plan_all_60min} request size.
@@
 \end{figure}
-\ref{fi:test_obs_import_15m_throughtput} shows the total server's transaction throughput against number of active threads.
-The formula for total server transaction throughput is \(<active threads> * 1 second / <1  thread response time>\) \cite{JMeterPluginsDocumentationJMeter-Plugins.org}.
+\ref{fi:test_obs_all_15m_throughtput} shows the total server's transaction throughput against number of active threads.
+The formula for total server transaction throughput is \(<active threads> * 1 second / <1  thread response time>\) \cite{JMeterPluginsTransactionPlugin}.
 Basically, it shows the statistical maximum possible number of transactions based on number of users accessing the application.
@@
 \label{subse:obs_test_plan_all_auto_15min}
+This section \ref{subse:obs_test_plan_all_auto_15min} discussed about the All test plan performance with 15 minutes data which means 96 data points per each request in Scalar and Vector timeseries, and 96 ASCII Grid files per each insert Grid timeseries request.
+These requests are four times larger than the \ref{subse:obs_test_plan_all_60min} request size.
+It performed approximately 311k of sample requests which is almost similar to \ref{subse:obs_test_plan_all_15min} processed samples.
+Other than that, this test plan runs with enabling \acrshort{k8s} Auto Scaling for the high resource utilized microservice as explained in the \ref{subse:test_plan_metrics}.
+With the test load used for the performance test, import-ascii-grid-upload microservice is using lots of CPU, and adapter-grid microservice is using lots of Memory.
+During this test plan, \acrshort{wdias} start with the auto scaling enabled for import-ascii-grid-upload microservice.
+Since adapter-grid is a consistence service for storing netCDF files, it is not possible to auto scale, since \acrshort{eks} does not support multiple read write support volumes \cite{LinuxFoundationPersistentKubernetes}.
+
+\begin{table}[]
+\begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
+\hline
+Label & \# Samples & Average & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
+Insert Timeseries & 71727 & 34 & 13 & 1777 & 27 & 118.78 & 0.00\% & 40.5 \\ \hline
+Retrieve Timeseries & 71693 & 7 & 5 & 1608 & 9 & 18.72 & 0.00\% & 40.5 \\ \hline
+Insert Grid & 7968 & 87 & 77 & 233 & 98 & 14.07 & 0.18\% & 4.5 \\ \hline
+Retrieve Grid & 7965 & 89 & 63 & 1694 & 110 & 37.79 & 0.00\% & 4.5 \\ \hline
+Query: Location & 71704 & 1 & 0 & 203 & 2 & 2.05 & 0.00\% & 40.5 \\ \hline
+\textbf{TOTAL} & 310734 & 130 & 0 & 1777 & 501 & 212.35 & 0.00\% & 175.3 \\ \hline
+\end{tabulary}
+\caption{Throughput and Latency of All test cases with 15min data while enabled \acrshort{k8s} Auto Scaling}
+\label{tab:obs_all_auto_15_min_summary}
+\end{table}
+\ref{tab:obs_all_auto_15_min_summary} shows the response latency summary details and \acrshort{rps} as same as explained in \ref{subse:obs_all_15_min_summary}.
+During this test plan.
+the main focus on the auto scaling enabled microservice.
+As per the insert grid latency in the \ref{tab:obs_all_auto_15_min_summary}, the average insert latency is reduced from 91ms to 87ms.
+Also error percentage reduced from 1.42\% to 0.18\%.
+Standard deviation reduced from 19.58 to 14.07 which means the latency is much closer to the average latency.
+These improvements in insert Grid timeseries data seems to affect on out put of retrieve Grid timeseries data as well.
+
+\begin{figure}[htp]
+    \centering
+    \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_transaction_throughtput_vs_threads.png}
+    \caption{Performance Import Test 15 minutes data while enabled \acrshort{k8s} Auto Scaling - Latency against server hits}
+    \label{fi:test_obs_all_auto_15m_latency}
+\end{figure}
+\ref{fi:test_obs_all_auto_15m_latency} graph provides an overview of the variation of latency over elapsed time of the test plan against number of server hits per second for 15min data while auto scaling enabled for \acrshort{k8s}.
+This graph show that over the time \acrshort{wdias} were able to keep the latency constant over the test plan.
+When compared to \ref{fi:test_obs_all_15m_latency}, throw out the test time period, the latency spikes become less.
+
+\begin{figure}[htp]
+    \centering
+    \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_transaction_throughtput_vs_threads.png}
+    \caption{Performance Import Test 15 minutes data while enabled \acrshort{k8s} Auto Scaling - Transaction Throughput vs Threads}
+    \label{fi:test_obs_all_auto_15m_throughtput}
+\end{figure}
+\ref{fi:test_obs_all_auto_15m_throughtput} shows the total server's transaction throughput against number of active threads.
+When compared to \ref{fi:test_obs_all_15m_throughtput}, estimated throughput with higher number of active threads become stable at the graph.
+Which means enabling auto scaling improve the throughput with higher number of active users as well.
+
+Following charts show the resource usage while running the all test plan while enabling the auto scaling.
 \begin{figure}[htp]
@@
     \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_import_export_res.png}
-    \caption{Performance All Test 15min Interval - Auto Scaling Resource Usage of Import and Export Modules }
+    \caption{Performance All Test 15min data - Auto Scaling Resource Usage of Import and Export Modules }
     \label{fi:obs_all_auto_15m_import_export_res}
 \end{figure}
+\ref{fi:obs_all_auto_15m_import_export_res} show the CPU usage and Memory usage for import timeseries modules and export timeseries modules.
+The CPU usage shown with milli CPUs \cite{LinuxFoundationManagingKubernetes} (1 CPU = 1000m CPUs) and the Memory usage shown with Megabytes (Mi) \cite{LinuxFoundationManagingKubernetes}.
+Noticeable, the import-ascii-grid-upload microservice used around 10 CPUs at the peak time while using 3.6 Gb of Memory.
+Another important fact is, after the test cases finished, the \acrshort{wdias} cool down the system via \acrshort{k8s} auto scaling and release the resources.
+This clearly shows the elasticity of the \acrshort{wdias} according to the work load.
 
@@
 \end{figure}
+\ref{fi:obs_all_auto_15m_import_grid_pod} shows the number of import-ascii-grid-upload pods scheduled over time.
+The auto scaling enabled with the configurations of 1 to 10 pods with the recommended CPU usage with 80\%.
+And the pods scheduled with 1 CPU requested, and limit with 2 CPUs per pod.
+As the graph shows, 3 pods scheduled at the initial as per the configuration of the helm chart.
+While increasing the work load, new pods get spawn while keeping the constraint of 80\% of recommended CPU utilization.
+After \acrshort{k8s} spawn 10 maximum pods, it stop spawning new pods.
+But the pods were able to perform with vertical scaling, since those are not hit the CPU limit of 2.
 
@@
 \end{figure}
+\ref{fi:obs_all_auto_15m_adapter_dbs_res} shows the resource utilization of database adapters in the \acrshort{wdias}.
 

### 2020-02-08 results/sec_3-observations.tex
Updated Query obs

@@
 \hline
-Label & \# Samples & Average & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
+Label & Samples & Avg & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
 Insert Timeseries & 71727 & 34 & 13 & 1777 & 27 & 118.78 & 0.00\% & 40.5 \\ \hline
@@
 \end{table}
-\ref{tab:obs_all_auto_15_min_summary} shows the response latency summary details and \acrshort{rps} as same as explained in \ref{subse:obs_all_15_min_summary}.
+\ref{tab:obs_all_auto_15_min_summary} shows the response latency summary details and \acrshort{rps} as same as explained in \ref{subse:obs_test_plan_all_15min}.
 During this test plan.
@@
 
-\subsection{Import module load test}
+\subsection{Query module load test}
+\label{subse:obs_test_plan_query_15min}
+This section \ref{subse:obs_test_plan_query_15min} discussed about the Query test plan performance.
+It performs multiple information retrieval queries such as query over locations, parameters and timeseries etc which are described over \ref{se:query}.
+It performed approximately 123k of sample requests.
+Query test plan perform over 5 minutes of time period, and with a higher number of requests than other test plan with a peak of 600 hits per seconds.
+
 \begin{table}[]
@@
 \hline
-Label & \# Samples & Average & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
-Insert Timeseries & 91345 & 212 & 15 & 5288 & 241 & 556.05 & 0.01\% & 123.4 \\ \hline
-Insert Grid Timeseries & 10189 & 108 & 76 & 330 & 148 & 30.98 & 0.00\% & 13.8 \\ \hline
-\textbf{TOTAL} & 101534 & 202 & 15 & 5288 & 212 & 528.43 & 0.01\% & 137.2 \\ \hline
+Label & Samples & Avg & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
+* → Locations & 11462 & 992 & 5 & 17569 & 1740 & 704.67 & 0.00\% & 38.3 \\ \hline
+Area → Locations & 11390 & 599 & 2 & 16755 & 1047 & 514.68 & 0.00\% & 38.1 \\ \hline
+Location → Parameters & 11350 & 666 & 1 & 16821 & 1179 & 632.86 & 0.00\% & 38.0 \\ \hline
+Locations → Parameters & 11305 & 659 & 1 & 17459 & 1149 & 678.55 & 0.00\% & 37.8 \\ \hline
+Location → Timeseries & 11269 & 647 & 2 & 32693 & 1102 & 746.51 & 0.00\% & 37.7 \\ \hline
+Locations → Timeseries & 11237 & 669 & 1 & 32651 & 1162 & 889.18 & 0.00\% & 37.6 \\ \hline
+Locations, Parameter → Timeseries & 11192 & 662 & 2 & 32806 & 1152 & 789.49 & 0.00\% & 37.4 \\ \hline
+Area → Timeseries & 11135 & 820 & 2 & 33235 & 1461 & 877.68 & 0.00\% & 37.3 \\ \hline
+Area, Parameter → Timeseries & 11084 & 864 & 1 & 16699 & 1584 & 751.00 & 0.00\% & 37.1 \\ \hline
+*, Parameter → Timeseries & 11011 & 696 & 2 & 16689 & 1216 & 693.33 & 0.00\% & 36.8 \\ \hline
+* → Timeseries & 10968 & 1473 & 24 & 18283 & 2467 & 912.45 & 0.00\% & 36.7 \\ \hline
+\textbf{TOTAL} & 123403 & 794 & 1 & 33235 & 1536 & 789.76 & 0.00\% & 412.6 \\ \hline
 \end{tabulary}
-\caption{Throughput and Latency of Import test cases with 15min data}
-\label{tab:obs_import_15_min_summary}
+\caption{Throughput and Latency of Query test cases with 15min data}
+\label{tab:obs_query_15_min_summary}
 \end{table}
+\ref{tab:obs_query_15_min_summary} shows the response latency summary details.
+The average latency is much higher than the minimum value.
+Also it reported higher maximum values as well.
+Standard deviation showed as quiet higher value which means the response latency values are not closer to the average value.
+Noticeably, it does not reported any errors, which means all the requests successfully process.
+The throughput for each test case is much higher and similar to all the requests.
+This is happening since all of these requests are handle via the adapter-query, it depends on the \acrshort{mongodb} database performance.
 
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{results/obs/import/obs_import_15m_transaction_throughtput_vs_threads.png}
-    \caption{Performance Import Test 15 minutes Interval - Transaction Throughput vs Threads}
-    \label{fi:test_obs_import_15m_throughtput}
+    \includegraphics[width=0.8\textwidth]{results/obs/query/obs_query_5m_latency_over_time.png}
+    \caption{Performance Query Test over 5 minutes - Response Latency over Time}
+    \label{fi:test_obs_query_5m_response_latency}
 \end{figure}
+\ref{fi:test_obs_query_5m_response_latency} shows the response latency over time for the query test plan.
+When the number of request get higher, the latency also get increased.
+That means adapter-query is not very much scalable with the current configurations.
 
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{results/obs/import/obs_import_15m_res_latencies_against_hits.png}
-    \caption{Performance Import Test 15 minutes Interval - Latency against server hits}
-    \label{fi:test_obs_import_15m_latency}
+    \includegraphics[width=0.8\textwidth]{results/obs/query/obs_query_5m_response_times_vs_threads.png}
+    \caption{Performance Query Test over 5 minutes - Response Latency Times vs Threads}
+    \label{fi:test_obs_query_5m_response_times_vs_threads}
 \end{figure}
+\ref{fi:test_obs_query_5m_response_times_vs_threads} shows the response latency against number of active threads for the query test plan.
+When the number of server hits get higher, the latency also get increased.
+That means adapter-query is not very much scalable with the current configurations.
 
-\subsection{Export module load test}
-Need to redo just after the import
-\begin{table}[]
-\begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
-\hline
-Label & \# Samples & Average & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
-Retrieve Timeseries & 136310 & 9 & 7 & 287 & 11 & 6.37 & 0.00\% & 156.1 \\ \hline
-Retrieve Grid Timeseries & 15147 & 265 & 10 & 4044 & 488 & 691.69 & 46.36\% & 17.4 \\ \hline
-\textbf{TOTAL} & 151457 & 35 & 7 & 4044 & 13 & 231.92 & 4.64\% & 173.4 \\ \hline
-\end{tabulary}
-\caption{Throughput and Latency of Export test cases with 15min data}
-\label{tab:obs_export_15_min_summary}
-\end{table}
-
-\begin{figure}[htp]
-    \centering
-    \includegraphics[width=0.8\textwidth]{results/obs/export/obs_export_15m_transaction_throughtput_vs_threads.png}
-    \caption{Performance Export Test 15 minutes Interval - Transaction Throughput vs Threads}
-    \label{fi:test_obs_export_15m_throughtput}
-\end{figure}
-
-\begin{figure}[htp]
-    \centering
-    \includegraphics[width=0.8\textwidth]{results/obs/export/obs_export_15m_res_latencies_against_hits.png}
-    \caption{Performance Export Test 15 minutes Interval - Latency against server hits}
-    \label{fi:test_obs_export_15m_latency}
-\end{figure}
-
-\subsection{Extension module load test}
-
-\subsection{Query module load test}
+When ever the timeseries data not found in the adapter-query, it read data from adapter-metadata and index for search over timeseries metadata.
+This will cause to higher performance with geo timeseries searches.
+The performance of the \acrshort{mongodb} can further improve with using it features like Replication for high availability, and Sharding for higher throughput.
+Those attempts are beyond the scope of \acrshort{wdias} performance test and users can use those to get higher results from the \acrshort{wdias}.

### 2020-02-08 results/sec_3-observations_other.tex
Updated Query obs

\subsection{Import module load test}
\label{subse:obs_test_plan_import_15min}
\begin{table}[]
\begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
\hline
Label & \# Samples & Average & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
Insert Timeseries & 91345 & 212 & 15 & 5288 & 241 & 556.05 & 0.01\% & 123.4 \\ \hline
Insert Grid Timeseries & 10189 & 108 & 76 & 330 & 148 & 30.98 & 0.00\% & 13.8 \\ \hline
\textbf{TOTAL} & 101534 & 202 & 15 & 5288 & 212 & 528.43 & 0.01\% & 137.2 \\ \hline
\end{tabulary}
\caption{Throughput and Latency of Import test cases with 15min data}
\label{tab:obs_import_15_min_summary}
\end{table}

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/import/obs_import_15m_transaction_throughtput_vs_threads.png}
    \caption{Performance Import Test 15 minutes Interval - Transaction Throughput vs Threads}
    \label{fi:test_obs_import_15m_throughtput}
\end{figure}

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/import/obs_import_15m_res_latencies_against_hits.png}
    \caption{Performance Import Test 15 minutes Interval - Latency against server hits}
    \label{fi:test_obs_import_15m_latency}
\end{figure}

\subsection{Export module load test}
\label{subse:obs_test_plan_export_15min}
Need to redo just after the import
\begin{table}[]
\begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
\hline
Label & \# Samples & Average & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
Retrieve Timeseries & 136310 & 9 & 7 & 287 & 11 & 6.37 & 0.00\% & 156.1 \\ \hline
Retrieve Grid Timeseries & 15147 & 265 & 10 & 4044 & 488 & 691.69 & 46.36\% & 17.4 \\ \hline
\textbf{TOTAL} & 151457 & 35 & 7 & 4044 & 13 & 231.92 & 4.64\% & 173.4 \\ \hline
\end{tabulary}
\caption{Throughput and Latency of Export test cases with 15min data}
\label{tab:obs_export_15_min_summary}
\end{table}

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/export/obs_export_15m_transaction_throughtput_vs_threads.png}
    \caption{Performance Export Test 15 minutes Interval - Transaction Throughput vs Threads}
    \label{fi:test_obs_export_15m_throughtput}
\end{figure}

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/export/obs_export_15m_res_latencies_against_hits.png}
    \caption{Performance Export Test 15 minutes Interval - Latency against server hits}
    \label{fi:test_obs_export_15m_latency}
\end{figure}

\subsection{Extension module load test}
\label{subse:obs_test_plan_extension_15min}

### 2020-02-08 results/sec_4-conclusion.tex
Added All 1440 result graphs
Update the conclusion

@@
 
-Throughput
+In this section concludes the observations in \ref{se:observations} section against the performance metrics defines in \ref{subse:test_plan_metrics}.
 
-Latency
+\paragraph{Latency}
+The latency for each operation type kept constant over the whole test plan run time without any significant change.
+When the request size increased from 24 data points to 96 data points, the latency increase throw out the whole test plan with a smaller number.
+But for each test run the latency kept constant over the time.
+During the \ref{subse:obs_test_plan_all_auto_15min} test run, the performance of the Grid data got better when compared to the \ref{subse:obs_test_plan_all_15min}.
+Which means by adding more resources to the \acrshort{wdias}, it can handle more work load on the system.
 
-Resource Utilization
+\paragraph{Throughput}
+While keeping the latency constant without significant change, the throughput of the \acrshort{wdias} kept constant while increasing the request size from 60min data (24 data points) to 15min data (96 data points) for all the data types such as Scalar, Vector and Grid.
+When number of active threads increased, the \acrshort{wdias} able to provide the same throughput with maintaining the latency stable.
 
-Auto Scaling/Scalability
+One of the reason to having deviations at the peak time due to use of single instance for the data consistency such as \acrshort{influxdb} for Scalar and Vector data, and netCDF with parallel support for Grid data.
+Further it is possible to increase the performance of these bottlenecks much higher such as using \acrshort{influxdb} Commercial cluster support for high availability or horizontal scaling of \acrshort{influxdb}.
+With \acrshort{influxdb} cluster, it is possible to run multiple pods of adapter-scalar and adapter-vector for support more server hits per second.
 
-Risk of unable to process data
+Adapter-grid is using a Python wrapper for netCDF FORTRAN implementation with parallel IO enabled.
+This has some performance issues as well as memory leak issues.
+Since each microservice in the \acrshort{wdias} independent of technology that can use to implement the service, it will increase the performance if the adapter-grid directly ported to netCDF with a low level language such as C or FORTRAN.
+Other than \acrshort{eks}, if users can use a \acrshort{k8s} cluster which support Persistent Volumes with the access of Read Write  Many \cite{LinuxFoundationPersistentKubernetes} , then it is possible to run multiple pods of adapter-grid and increase the throughput of the \acrshort{wdias}.
+
+\paragraph{Resource Utilization}
+Since \acrshort{wdias} using the \acrshort{k8s} as the container orchestration system, it allows to scale up and cool down the system as required based on the work load.
+This demonstrate on the test plan of \ref{subse:obs_test_plan_all_auto_15min}, and the system get scale up to the maximum at the peak time.
+Then cool down to single pod after finishing the test cases.
+Given above \acrshort{wdias} can run from 1 CPU node to nodes with 100 CPUs.
+As described in the \ref{se:microservice}, it uses the many of the concept of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities.
+
+\paragraph{Auto Scaling}
+The \acrshort{wdias} supports auto scaling by out of the box with \acrshort{k8s}.
+Services can configure with maximum number of pods in order to avoid over resource usage.
+When there is not much work load on the system, system cool down to less pods in order to save more resources.
+When there is any issue with a pod, \acrshort{k8s} auto schedule another pod and remove the unhealthy pod.
+Also it allows to update the system without any down time with rollback updates.
+
+\paragraph{Risk of Unable to Process Data}
+During the test performance, the \acrshort{wdias} processed many requests with higher request size than the normal usage with lower rate of failures to process the requests, mainly with insert Grid data.
+If the usage of \acrshort{wdias} want to reduce the risk of unable to process data, then system can configure to run with redundant pods in order to handle spike of work loads.
+Also while configure for the auto scaling, the \acrshort{k8s} can configure to maintain lower amount of CPU usage such as 50\% to 60\% rather 80\%.
+Such configuration with always spawn new pods to handle double of current peak load.

### 2020-02-08 method/sec_4-db_struct.tex
Updated future works

@@
 \subsection{Timeseries Key Attributes}
+\label{sub:timeseries_key_attributes}
 - Module ID
@@
 \subsection{MySQL}
+\label{sub:mysql}
 Relational Database Management System (RDBMS).
@@
 \subsection{InfluxDB} \cite{influxdbInfluxDBDocumentation}
+\label{sub:influxdb}
 Open timeseries DB with MIT license

### 2020-02-08 summary/sec_1-summary.tex
Updated future works

\section{Summary}

As summary of the proposed system, it's performance and conclusion over the results.

### 2020-02-08 summary/sec_2-future_work.tex
Updated future works

@@
 \section{Future Work}
-- Lack of data prepossessing modules
-- Supporting Irregular Grids
-- Grid performance
-- Define infrastructure as code - Teraform
-- Improve test cases - correct RPS
-- Further improve hierarchical database performance
-- Add Alerting extension modules
-- Add pubsub extension modules
+This section discussed about the lacking features in the \acrshort{wdias}, and some of the improvement that can add for improve the performance and usability of the system.
+
+\paragraph{Lack of data preprossessing modules}
+The extension module enable plugin system to integrate prepossessing modules which can use for process the data which are inserted to the system or based on regular intervals.
+Also \acrshort{wdias} provide a more generic open interface approach to create more preprocessing modules.
+Since \acrshort{wdias} is an open source system, it expect more modules to be create by the community.
+When compared to other system like \acrshort{fews}, current system only have few extension for the testing purpose.
+This is one of the major area that need to be improved.
+
+\paragraph{Supporting Irregular Grids}
+At the moment \acrshort{wdias} does not support Irregular Grids, but it has the API endpoints define for the implementation which can follow the same microservice architecture.
+The scope of the \acrshort{wdias} does not belong such level of implementation and the scope has reduced by removing such components from the system.
+
+\paragraph{Grid data performance}
+As mentioned in the \ref{se:conclusion}, the adapter-grid is using a Python wrapper for netCDF FORTRAN implementation with parallel IO enabled.
+This has some performance issues as well as memory leak issues.
+Since each microservice in the \acrshort{wdias} independent of technology that can use to implement the service, it will increase the performance if the adapter-grid directly ported to netCDF with a low level language such as C or FORTRAN.
+They are some future work that can focus on improving the performance of grid data.
+
+\paragraph{Define infrastructure as code}
+Physical nodes for the \acrshort{k8s} cluster created using Cloud Computing provider such as \acrshort{eks}.
+And defining the each pod resource limitations at the helm chart level.
+But the infrastructure that need to deploy the \acrshort{wdias} can define as code such as using tools like Teraform which is independent of the Cloud Computing provider.
+Using such tool, users will able to easy deploy the \acrshort{wdias} on any Cloud provider without much hassle.
+
+\paragraph{Improve test cases}
+As described in detail with \ref{subse:closed_vs_open_workload}, for \acrshort{wdias} performance test uses Time Stepping Feedback loop with Concurrent Threads which is the best approach support by \acrshort{jmeter} at the moment.
+But using that it is not possible to get desired \acrshort{rps} for each test case within the test plan.
+Because of this issue, the \acrshort{wdias} test plans further improved by removing redundant test cases such as create timeseries at the beginning.
+Having create timeseries at the beginning causes some issues such as most of the thread are working on that test case rather on required test cases.
+Still there may be some improvement that can be done.
+
+\paragraph{Further improve hierarchical database performance}
+As further described in \ref{se:conclusion}, it is possible to increase the performance of these bottlenecks much higher such as using \acrshort{influxdb} Commercial cluster support for high availability or horizontal scaling of \acrshort{influxdb}.
+With \acrshort{influxdb} cluster, it is possible to run multiple pods of adapter-scalar and adapter-vector for support more server hits per second.
+Other than that, the \acrshort{wdias} performance can improve via partitioning the timeseries key space into multiple \acrshort{influxdb} instances.
+The adapter-scalar or adapter-vector can improve to plug multiple instance of \acrshort{influxdb} instances by changing the configurations.
+As an example, based on the key attribute \ref{sub:timeseries_key_attributes} Timeseries Type, the adapter-scalar can connect to four instance of \acrshort{influxdb} instances such as  External Historical, External Forecast, Simulated Historical, and Simulated Forecast etc.
+
+\paragraph{Add Alerting extension modules}
+At the moment, extensions only support On Change and On Time events. But it will be good to have event trigger support based on reconfigured alert level.
+
+\paragraph{Add Publisher Subscriber extension modules}
+The \acrshort{wdias} better to be capable of triggering external systems based on the events such as webhooks.

### 2020-02-08 glossary.tex
Added Data Preprocess
Added test plan
Work load precipitation and water level
Work Load creation
Work Load - System Configuration
Update the summary

@@
 \newacronym{nwm}{NWMs}{Numerical Weather Models}
-\newacronym{NetCDF}{NetCDF}{Network Common Data Form}
+\newacronym{netCDF}{netCDF}{Network Common Data Form}
 \newacronym{soa}{SOA}{Service Oriented Architecture}
-\newacronym{wrf}{WRf}{Weather Research and Forecast}
+\newacronym{wrf}{WRF}{Weather Research and Forecast}
 \newacronym{esb}{ESB}{Enterprise Service Bus}
-\newacronym{microservice}{Microservice}{Microservice Architectire}
+\newacronym{microservice}{Microservice}{Microservice Architecture}
+
+\newacronym{mysql}{MySQL}{MySQL}
+\newacronym{influxdb}{InfluxDB}{InfluxDB}
+\newacronym{redis}{Redis}{Redis}
+\newacronym{mongodb}{MongoDB}{MongoDB}
+\newacronym{k8s}{K8s}{Kubernetes}
+\newacronym{eks}{AWS EKS}{Amazon Elastic Kubernetes Service}
+
+\newacronym{go}{Go Lang}{Go Programming Language}
+\newacronym{rps}{RPS}{Requests Per Second}
+\newacronym{api}{API}{Application Programming Interface}
+\newacronym{jmeter}{JMeter}{Apache JMeter}
+\newacronym{rps}{RPS}{Request per Second}
 

### 2020-02-08 results/sec_2-work_load.tex
Update Obs Full test 24 and 48 request size
Update the summary

@@
 \subsubsection{closed vs. open workload models} \cite{Haggett1998AnWales}
+\label{subse:closed_vs_open_workload}
 \begin{itemize}
@@
 \subsection{System Configuration}
+\label{sub:test_sys_config}
 As described in the \ref{se:microservice}, the \acrshort{wdias} is mainly focus on microservice architecture and implemented on top of kubernetes.

### 2020-02-08 summary/sec_1-summary.tex
Update the summary

@@
 
-As summary of the proposed system, it's performance and conclusion over the results.
+In order to enhance the accuracy of the weather prediction, it is required to have reliable weather data for \acrshort{nwm}s.
+Most of existing weather data systems are proprietary or close sourced, or not up to date with the existing cloud computing technologies.
+We proposed an extendable open source Weather Data Integration and Assimilation Systems which is known as \acrshort{wdias}.
+It focused on providing efficiently integrates weather data from different sources with quality control and supporting steaming large size of data.
+And compatible with current cloud computing technologies and architecture patterns.
+
+First the architecture starts with Service Oriented Architecture using a \acrfull{esb}, and then moved to Actor model based architecture.
+After comparing the disadvantages of using such architecture with the system requirements, final architecture come up with modern microservice architecture.
+Based on the microservice architecture patterns and the nature of the weather metadata, the \acrshort{wdias} came up with the idea of hierarchical database structure in order to provide higher performance while store the weather data.
+The system uses \acrshort{influxdb} timeseries database for storing Scalar and Vector timeseries data, and using \acrshort{netcdf} for storing Grid timeseries data.
+Also the system provide a generic open mechanism to integrate new modules as extension in order to enhance the features of the system.
+This capability enable to integrate weather data preprocessing flows as extension modules.
+The extension API provide easy access to create and modify the extension triggers on the fly without stopping the system or any downtime in order to change the configurations.
+The system provides extensive timeseries query endpoints to easy search over the system timeseries metadata with supporting geo based queries.
+
+\acrshort{wdias} performance test is perform using the \acrshort{jmeter} tool's distributed testing capabilities which separately testing each modules.
+Then the test plans are performed with increasing the request size, and monitored the performance metrics.
+The system is setup on the \acrfull{eks} as per the configurations of \ref{sub:test_sys_config}.
+During the performance test plans, the system were able to provide constant throughput by keeping the latency constant while increasing the work load. Which exhibit the scalability of the system.
+With the \acrshort{k8s} auto scaling, the \acrshort{wdias} were able to elastically adjust the number of pods according to the work load with the given configurations.

### 2020-02-08 summary/sec_2-future_work.tex
Update the summary

@@
 
-\paragraph{Add Alerting extension modules}
+\paragraph{Alerting extension modules}
 At the moment, extensions only support On Change and On Time events. But it will be good to have event trigger support based on reconfigured alert level.
 
-\paragraph{Add Publisher Subscriber extension modules}
-The \acrshort{wdias} better to be capable of triggering external systems based on the events such as webhooks.
+\paragraph{Publisher Subscriber extension modules}
+The \acrshort{wdias} better to be capable of triggering external systems based on the events such as web hooks.

### 2020-02-09 Paper.tex
Paper - update abstract

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage[acronym]{glossaries}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Weather Data Integration and Assimilation System\\
% \thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{Gihan Karunarathne}
\IEEEauthorblockA{\textit{dept. computer science and Engineering} \\
\textit{university of moratuwa}\\
Moratuwa, Sri Lanka \\
gihan.09@cse.mrt.ac.lk}
\and
\IEEEauthorblockN{Dr. Dilum Bandara}
\IEEEauthorblockA{\textit{dept. computer science and Engineering} \\
\textit{university of moratuwa}\\
Moratuwa, Sri Lanka \\
dilumb@cse.mrt.ac.lk}
}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
We describe our experience with implementing an extendable open source Weather Data Integration and Assimilation System, which is known as \acrshort{wdias}. It uses the modern architecture pattern such as microservice in order to achieve the scalability, rather using monolithic architecture or client service architecture. It provides a modular approach to integration data from different sources and export into different formats. Also the inbuilt extension module system allow users to add new features. The open source tools that are using for \acrshort{wdias} allows to run on Cloud Computing platforms without much hassle with the auto scaling feature allow to run \acrshort{wdias} from 1 CPU node to nodes with few hundred CPUs. The paper describes the initial design goals, evolve over few architectures to get desired performance, and explains how the system in way to achieve scalability. Later we analyse the performance test observations with the performance metrics.
\end{abstract}

\begin{IEEEkeywords}
\acrshort{wdias}, weather, microservice, kubernetes, hierarchical database 
\end{IEEEkeywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INTRODUCTION}
I'm going to do this today \cite{Haggett1998AnWales}.

\section{Literature Review}

\subsection{Method}

\subsection{Performance Analysis}

\section{Conclusions}

\section{Summary}

\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in America is without 
an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
acknowledgments in the unnumbered footnote on the first page.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\graphicspath{ {./images/} }
\bibliographystyle{plain}
\bibliography{mendeley}

\end{document}

### 2020-02-09 lit/sec_1-fews.tex
Before Test plan
Paper - update abstract

@@
-\section{The Delft-FEWS flow forecasting system}
+\section{Delft-FEWS flow forecasting system}
 \acrshort{fews} is developed by Deltares in the Nethaland with targeted for use by operational forecasting agencies.
-The software is freely available to download and setup.
+%The software is freely available to download and setup.
 Tutorials and User setup guide \cite{DeltaresPublicWikiDelft-FEWSGuide} are available with well documentations.
@@
 However, investments in new developments in the system are normally paid for by its users.
-The code base of \acrshort{fews} is currently not fully open source.
-But configuration guides and generic adapter module integration code examples are available for the users.
-
+The code base of \acrshort{fews} is currently not fully open source. %But configuration guides and generic adapter module integration code examples are available for the users.
 Most if the models are using model-centric approach such as inputs need to be in the format of specific to the model.
-Also the outputs produced by the model are specific to the model and hard to utilize by another systems (e.g.
-FLO2D).
-For the \acrshort{fews} is using much more modular approach, hence it is easy to integrate models into the \acrshort{fews} system.
-Thus \acrshort{fews} can be consider as an integration framework or a middle ware for the models.
+Also, the outputs produced by the model are specific to the model and hard to utilize by another systems (e.g., FLO2D).
+As \acrshort{fews} %is using much more
+uses a modular approach it is easier to integrate new models.% into the \acrshort{fews} system. 
+Thus, \acrshort{fews} can be consider as an integration framework or a middleware for the models.
+\dbc{Cite Fews. Provide only the key details. It's sufficient say whether its commercial or open source. Do this for all other solutions discussed. Middleware is a single word. Check other places.}
 
@@
 
-The key elements of a forecasting system are summarized by Haggett \cite{Haggett1998AnWales} as four main steps;
-\begin{enumerate}
-    \item Detection
-    \item Forecasting
-    \item Dissemination and Warning
-    \item Response
-\end{enumerate}
+Are proposed by Haggett \cite{Haggett1998AnWales} key elements of a forecasting system include detection, forecasting, dissemination and warning, and response.
 Within these four steps, \acrshort{fews} focuses on the forecasting step.
@@
     \includegraphics[width=0.7\textwidth]{fews/Schematic-structure-of-a-fl-ood-forecasting-system-showing-the-position-of-Delft-FEWS_W640.jpg}
-    \caption{Schematic structure of a flood forecasting system, showing the position of \acrshort{fews} and links to other primary systems within the operational environment.
-\cite{Werner2013TheSystem} }
+    \caption{Schematic structure of a flood forecasting system including \acrshort{fews} and links to other primary systems within the operational environment \cite{Werner2013TheSystem}.}
     \label{fi:fews_schematic}
 \end{figure}
+\dbc{Most figures are of low quality. You need to make sure figure resolution/quality is not lost. Dot should come after reference no. Fix all places.}
+
 The foundation of \acrshort{fews} is data-centric, with a common data-model through which all components interact.
@@
     \includegraphics[width=1.0\textwidth]{fews/Architecture-of-Delft-FEWS-showing-the-data-base-the-data-access-layers-and-examples-of_W640.jpg}\\
-    \caption{Architecture of \acrshort{fews} showing the data base, the data access layers and examples of functional modules that communicate through the data access layer.
+    \caption{Architecture of \acrshort{fews} % showing the data base, the data access layers and examples of functional modules that communicate through the data access layer. 
     \cite{Werner2013TheSystem} }
@@
 For overcome this issue they introduced the file-based exchange of data.
-This includes the use of binary-XML files, streaming files through memory, and the use of \acrshort{NetCDF}-CF files.
+This includes the use of binary-XML files, streaming files through memory, and the use of \acrshort{netCDF} files.
 But far as for users it seems to be adding more complexity and context in order to get higher performance via the system.
@@
 If you setup the system on Linux base operating system and using Linux based models, it is hard for users to come up with a solution for integrating the FLO2D models.
-The final step and one of important feature is exporting the data from the system in useful manner. In the \acrshort{fews}, it is supporting three main forms of product generation.
-\begin{itemize}
-\item Generate web reports with graphs, tables as well as summary reports
-\item Export time series in a variety of formats
-\item External applications actively retrieve data from the system
-\end{itemize}
+The final step and one of important feature is exporting the data from the system in useful manner. %\acrshort{fews} supports three main forms of product generation, namely:
+%\begin{itemize}
+%\item Generate web reports with graphs, tables as well as summary reports
+%\item Export time series in a variety of formats
+%\item External applications actively retrieve data from the system
+%\end{itemize}
 The forecasting process is often a sequence of steps, starting with the import of data, a number of data processing and modeling steps, and culminating in the generation of products to be disseminated to the warning process.
@@
 As it mentioned above, users can run multiple models parallel or run those sequentially as needed.
+\dbc{It's "e.g.,". Fix all places. }

### 2020-02-09 lit/sec_2-lead.tex
Added All 1440 result graphs
Paper - update abstract

@@
 
-The reason behind developing \acrfull{lead} by US National Science Foundation (NSF)  is to addresses the fundamental research challenges needed to create an integrated, scalable framework for adaptive analyzing and predicting the atmosphere \cite{Droegemeier2005Service-OrientedWeather}.
-In order to predict and analysis weather models by researchers, it required many resources.
+%The reason behind developing \acrfull{lead} by US National Science Foundation (NSF)  is to
+\acrfull{lead} addresses the fundamental research challenges needed to create an integrated, scalable framework for adaptive analyzing and predicting the atmosphere \cite{Droegemeier2005Service-OrientedWeather}.
+To predict and analysis weather models by researchers, it required many resources.
 Rather than each researcher is running and handling own computer resources to do the weather experiments, \acrshort{lead} is providing pool of resources, then the researchers can use this resource pool to run their experiment in shorter amounts of time and in higher scale.
@@
 
-The most relevant and important analysis for designing \acrshort{lead} is understanding and analyzing the \acrfull{lead} architecture of it.
-LEAD’s complex array of services, applications, interfaces, and local and remote computing, networking, and storage resources is assembled by users in work flows to study mesoscale weather as it evolves \cite{Droegemeier2005Service-OrientedWeather}.
+%The most relevant and important analysis for designing \acrshort{lead} is understanding and analyzing the \acrfull{lead} architecture of it. 
+LEAD's complex array of services, applications, interfaces, and local and remote computing, networking, and storage resources is assembled by users in work flows to study mesoscale weather as it evolves \cite{Droegemeier2005Service-OrientedWeather}.
 As it follows the \acrshort{soa}, everything is implemented as independent services.
@@
 New models which are required for implementing a new forecast flow also has to be implement as a service and then integrate into the system.
+\dbc{Check the use of apostrophe s. You need to use ' not ’.}
 
-In the \ref{fi:lead_system} shows the fundamental capabilities of the \acrshort{lead} system. 
+Figure \ref{fi:lead_system} shows the fundamental capabilities of the \acrshort{lead} system.
 From the high-level view, \acrshort{lead} lets users query for and acquire information, simulate and predict weather by using numerical atmospheric models, assimilate data, analyze, mine, and visualize data and model output.
+\dbc{Make sure each reference to a figure or table is given as Figure x.y and Table x.y.}
 
@@
     \includegraphics[width=1.0\textwidth]{lead/LEAD-system-Fundamental-capabilities-familiar-to-meteorologists-are-shown-in-the-top_W640.jpg}\\
-    \caption{LEAD system.
-Fundamental capabilities familiar to meteorologists are shown in the top level, below which are the associated tools for enacting these capabilities and the middle-ware that links everything together.
-System-generated products appear at the bottom.
-\cite{Droegemeier2005Service-OrientedWeather} }
+    \caption{Layered architecture of LEAD.
+Fundamental capabilities familiar to meteorologists are shown in the top level, next are the tools for enacting these capabilities and the middleware that links everything together.
+System-generated products appear at the bottom \cite{Droegemeier2005Service-OrientedWeather}.
+}
     \label{fi:lead_system}
@@
 
-The second level in \ref{fi:lead_system} contains the fundamental tools that help to link services together. This include following tools in brief \cite{Droegemeier2005Service-OrientedWeather};
+\dbc{Fig. 2.4 should use full text width.}
+
+The second level contains the fundamental tools that help to link services together. This include following tools \cite{Droegemeier2005Service-OrientedWeather};
 \begin{itemize}
@@
     \includegraphics[width=1.0\textwidth]{lead/LEAD-system-framework-LEAD-is-composed-of-several-interacting-subsystems-with-the-LEAD_W640.jpg}\\
-    \caption{ LEAD system framework.
-LEAD is composed of several interacting subsystems, with the LEAD grid representing a stable, secure environment for development and testing.
-\cite{Droegemeier2005Service-OrientedWeather} }
+    \caption{LEAD system framework %. LEAD is composed of several interacting subsystems, with the LEAD grid representing a stable, secure environment for development and testing. 
+    \cite{Droegemeier2005Service-OrientedWeather} .}
     \label{fi:lead_framework}
@@
 
-Lead System is consist of following sub components, as shown in the \ref{fi:lead_soa}. As a brief summary of the subsystems is \cite{Droegemeier2005Service-OrientedWeather};
+As shown in the \ref{fi:lead_soa} LEAD consists of the following sub components:
 \begin{itemize}
-\item User subsystem - comprises the LEAD portal and enable user can access services
-\item Data subsystem - handles data and metadata, any numerical model output produced by operational or experimental models, and user generated information.
-\item Tools subsystem - consists of all meteorological and IT tools
-\item Orchestration subsystem - provides the technologies that let users manage data flows and model execution streams, and create and mine output.
+\item User subsystem -- comprises the LEAD portal and enable user can access services
+\item Data subsystem -- handles data and metadata, any numerical model output produced by operational or experimental models, and user generated information.
+\item Tools subsystem -- consists of all meteorological and IT tools
+\item Orchestration subsystem -- provides the technologies that let users manage data flows and model execution streams, and create and mine output.
 It also provides linkages to other software and processes for continuous or on-demand applications.
@@
     \centering
-    \includegraphics[width=0.9\textwidth]{lead/LEADs-service-oriented-architecture-A-wide-variety-of-services-and-resources-grouped_W640.jpg}\\
-    \caption{LEAD’s service-oriented architecture.
+    \includegraphics[width=1\textwidth]{lead/LEADs-service-oriented-architecture-A-wide-variety-of-services-and-resources-grouped_W640.jpg}\\
+    \caption{LEAD’s service-oriented architecture %.
 A wide variety of services and resources, grouped here according to general functionality, comprise the LEAD architecture, including services that cut across all aspects of the system.
-\cite{Droegemeier2005Service-OrientedWeather} }
+    \cite{Droegemeier2005Service-OrientedWeather}.}
     \label{fi:lead_soa}
@@
 The distributed computing systems in the LEAD grid represent a distributed test bed for developing, integrating, and testing LEAD’s components.
+\dbc{Try to avoid singe sentence paras.}
 

### 2020-02-09 method/sec_1-soa.tex
Paper - update abstract

@@
 \section{Service Oriented Architecture}
+\dbc{Use a more meaningful title that reflect the solution.
+Also, why are we talking about an initial phase?
+You can mention that we iterate through several designs.
+But it's not important to discuss each design in detail unless once design is essential to understand the other design.
+Ideally, present only the finalized design while adding a single para for each of the previous attempts.}
 
-In the initial phase of WDIAS architecture, it proposed with a \acrfull{soa} as shown in the \ref{fi:proposed_soa}. Mainly it consist of 4 modules;
+In the initial phase of WDIAS architecture, it proposed with a \acrfull{soa} as shown in the \ref{fi:proposed_soa}. Mainly it consist of 4 modules, namely:
 - Import modules
@@
     \includegraphics[width=1\textwidth]{soa/soa_v1.jpg}
-    \caption{Proposed Service Oriented Architecture.}
+    \caption{Service oriented architecture of WADIS.}
     \label{fi:proposed_soa}

### 2020-02-09 method/sec_3-microservice.tex
Added Database Structure details
Paper - update abstract

@@
 
+- Brief introduction to the Kubernetes
+
+\begin{figure}[htp]
+    \centering
+    \includegraphics[width=1\textwidth]{method/microservice/microservice_architecture-handle_on_async-v3.jpg}
+    \caption{WDIAS architecture to handle request asynchronously.}
+    \label{fi:wdias_micro_async}
+\end{figure}
+
+\dbc{Dont' use title case of figure captions. Capitalize only the proper nouns. Also, WDIAS can be shorten in figure captions.}
+
+- Explain how k8s support microservice architecture
+
 <explain how each one is used while designing the WDIAS architecture>
@@
 
-<add the API description and how it related to moduels>
+<add the API description and how it related to modules>
 - Import

### 2020-02-09 summary/sec_1-summary.tex
Paper - update abstract

@@
 Based on the microservice architecture patterns and the nature of the weather metadata, the \acrshort{wdias} came up with the idea of hierarchical database structure in order to provide higher performance while store the weather data.
-The system uses \acrshort{influxdb} timeseries database for storing Scalar and Vector timeseries data, and using \acrshort{netcdf} for storing Grid timeseries data.
+The system uses \acrshort{influxdb} timeseries database for storing Scalar and Vector timeseries data, and using \acrshort{netCDF} for storing Grid timeseries data.
 Also the system provide a generic open mechanism to integrate new modules as extension in order to enhance the features of the system.
@@
 The extension API provide easy access to create and modify the extension triggers on the fly without stopping the system or any downtime in order to change the configurations.
-The system provides extensive timeseries query endpoints to easy search over the system timeseries metadata with supporting geo based queries.
+The system provides extensive timeseries query endpoints to easy search over the system timeseries metadata with supporting Geo based queries.
 

### 2020-02-09 thesis.tex
Added Data Preprocess
Added test plan
Work load precipitation and water level
Added All 1440 result graphs
Update the summary
Paper - update abstract

@@
 \usepackage{listings}
+\usepackage{dirtytalk}
+\usepackage{tabulary}
+
+\usepackage{todonotes}
+\newcommand{\db}[1]{\textcolor{blue!40}{#1}}
+\newcommand{\dbc}[1]{\todo[author=Dilum, inline, color=blue!40]{#1}}
 
@@
         \vspace{32pt}
-        April 2019
+        February 2020
 
@@
 
-To enhance the accuracy of weather predictions, it is necessary to provide reliable and detailed weather data as inputs to \acrfull{nwm}.
-These \acrshort{nwm} utilize weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images.
-Prior to feeding such diverse data (collected from different sources that belongs to different stakeholders) into respective \acrshort{nwm}, it is necessary to integrate data into a common format.
-Moreover, the data integration system’s response time need to be relatively low to accommodate critical situations like hurricanes, storms, and floods which require rapid and frequent execution of \acrshort{nwm}.
-
+%To enhance the accuracy of weather predictions, it is necessary to provide reliable and detailed weather data as inputs to \acrfull{nwm}. These \acrshort{nwm} 
+\acrfull{nwm} utilize data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images. Prior to feeding such %diverse 
+multimodal data (collected from different sources that belong to different stakeholders) into respective \acrshort{nwm}, it is necessary to integrate data into a common format.
+Moreover, the data integration system’s response time need to be relatively low to %accommodate critical situations
+forecast and monitor time-sensitive weather events like hurricanes, storms, and flash floods that require rapid and frequent execution of \acrshort{nwm}.
 Providing public to access weather data is also useful to enable many third-party applications and research.
-For example, logistic companies can use those data with their own model to plan and schedule their deliveries.
+For example, logistic companies could use those data within their models to plan and schedule deliveries.
 Agricultural insurance companies can warn the farmers in advance, as well as calculate premiums based on anticipated weather patterns.
 
-While \acrfull{dias} and \acrfull{madis} are some of well-known Weather Data Integration and Assimilation (WDIA) systems, they are proprietary.
+%While \acrfull{dias} and \acrfull{madis} are some of well-known Weather Data Integration and Assimilation (WDIA) systems, they are proprietary.
 Further Delft-FEWS is free to use, it is not open source.
@@
 
+\dbc{Add a set of sentences covering the why a new solution is needed, what sort of a solution we propose, how does the proposed solution work, why it's unique, and its performance.
+Abstract should not exceed 300 words.
+Typically background given in above para should not be more than 1/3 of abstract.}
+
 \vspace{4mm}
@@
 \textbf{Keywords:} WDIAS, Weather, Timeseries, Distributed, Scalable
-
+\dbc{Sort these. Add 2 more CS related terms. Remove WDIAS.}
 }
@@
 \addcontentsline{toc}{chapter}{List of Figures}
+\dbc{Reference numbers should ideally not be listed with Figure names.}
 \listoffigures
@@
 \printglossary[type=\acronymtype, title=List of Abbreviations, toctitle=List of Abbreviations, nonumberlist]
-
+\dbc{There has to be a space/tab between abbreviation and its expansion.} 
 \pagenumbering{arabic}
@@
 \label{ch:intro}
-To enhance the accuracy of weather predictions, it is necessary to provide reliable and detailed weather data as inputs to \acrfull{nwm}.
-These NWMs utilize weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images.
-Prior to feeding such diverse data (collected from different sources that belongs to different stakeholders) into respective NWMs, it is necessary to integrate data into a common format.
-Moreover, the data integration system’s response time need to be relatively low to accommodate critical situations like hurricanes, storms, and floods which require rapid and frequent execution of NWMs.
+
+\dbc{It could have been much more easier to modify and compile thesis if each chapter was on a separate file. Page nos should be Roman numerals until Chap 1 beings.}
+
+...
+\dbc{Start the para with a couple of sentences/para on weather prediction and NWMs.
+In another para mention about CUrW and its need to integrate and share data.
+Give citations of 1-2 good introductory sources on NWMs and another citation to CUrW website.}
 
 \section{Motivation}
+To enhance the accuracy of weather predictions, it is necessary to provide reliable and detailed weather data as inputs to \acrfull{nwm}.
+These NWMs utilize \db{multimodal} weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images.
+Prior to feeding such diverse data (collected from different sources that belongs to different stakeholders) into respective NWMs, it is necessary to integrate data into a common format.
+Moreover, the data integration system’s response time need to be relatively low to %accommodate critical situations
+\db{forecast and monitor time-sensitive weather events} like hurricanes, storms, and floods which require rapid and frequent execution of NWMs.
+
+\dbc{We are not developing this platform only because we need to have a common data format or need to share with 3rd parties.
+These are secondary reasons.
+Highlight key reason why we need a weather data assimilation system.
+Key reason should be indicated in Abstract too.}
+
 Providing public to access weather data is also useful to enable many third-party applications and research.
-For example, logistic companies can use those data with their own model to plan and schedule their deliveries.
+For example, logistic companies could use those data with their models to plan and schedule their deliveries.
 Agricultural insurance companies can warn the farmers in advance, as well as calculate premiums based on anticipated weather patterns.
+\dbc{Highlight why we need a platform to provide such 3rd party access. Should be indicated in Abstract too.}
 
@@
 Therefore, the objective of this research is to develop a WDIA system for Sri Lanka, as well as make it open source, so that others could user and contribute to the solution.
+\dbc{Saying something proprietary is not good reason to do research.
+You should highlight the context under which these solutions are developed and differences between CUrW and Sri Lanka in general.
+Also, give a bit more details than saying "to cater to their country-specific requirements".
+All key systems such as DIAS, MADIS, Delf, etc.
+need to be properly cited.}
 
-\section{Problem}
+\section{Problem \db{Statement}}
+\dbc{Convert following bullets to a paragraph.
+Goals belongs to next section.
+What we need here is a set of sentences highlighting the needs that are used to derive goals.
+Then provide a single sentence problem statement.
+Look at some of the thesis I shared via OneNote and my website for example problem statements.}
 \begin{itemize}
@@
 \section{Objectives}
+\db{We address above problem statement by  achieving the following objectives:}
 \begin{itemize}
     \item To develop an open platform to integrate weather data from different sources in different formats
-    \item To design and develop a schema to store multidimensional weather timeseries data while optimizing,
-    \begin{itemize}
-        \item Disk space
-        \item Availability
-        \item Access time
-    \end{itemize}
+    \item To design and develop a schema to store multidimensional weather timeseries data while optimizing access time, availability, and storage.
     \item To optimize schema to support data queries based on geography and time
@@
 Performance analysis is presented in Chapter \ref{ch:results} while summary and future work are presented in Chapter \ref{ch:conc}.
+\dbc{Expand a bit by adding at least 1 more sentence for each chapter.}
 
@@
 \label{ch:literature}
-There are many of Weather forecasting, assimilation and dissemination systems developed by some of developed countries around the world as a result of trying to reduce the damage causing by natural disasters such as flood, storms, hurricanes and even for drought.
-Above kind of natural disasters heavily affected on the economy and the life conditions of the country, researchers have developed systems and many of these systems are using as proprietary systems.
+There are many of Weather forecasting, assimilation and dissemination systems developed by some of developed countries around the world as a result of trying to reduce the damage causing by natural disasters such as flood, storms, hurricanes, and even for drought.
+%Above kind of
+Such natural disasters heavily affected on the economy and the life conditions of the country, researchers have developed systems and many of these systems are using as proprietary systems.
 Other countries also using those systems and adopt with own version of system which effective for the specific weather condition in a particular country.
-Though out this chapter includes a Literature review about existing systems and their architecture approach and design with available resources.
-Most influenced systems for \acrshort{wdias} is \acrshort{fews} and \acrfull{lead} system.
-\acrshort{fews} is an open data handling platform, but it distributed as Closed Source software.
-\acrshort{lead} is following the Service Oriented Architecture for system architecture.
+%Though out 
+This chapter presents a Literature review on existing systems and their architecture approach and design with available resources.
+\db{In Section 2.x we present ...} Most influenced systems for \acrshort{wdias} is \acrshort{fews} and \acrfull{lead} system.
+\acrshort{fews}, \db{an open data handling platform distributed as closed-source software, is presented in Section 2.x}.
+\db{In Section 2.x ...
+} \acrshort{lead} is following the Service Oriented Architecture for system architecture.
 Under each system we explore both system architecture, scalability and flexibility of the system.
+\dbc{Complete above while refering to all major sections with chapter.}
 
@@
 
-\section{Data Integration and Assimilation System}
+\section{Data Integration and Assimilation Systems}
 \label{se:dias}
@@
 
-\chapter{Method}
+\chapter{\db{Research Methodology}}
 \label{ch:method}
 This chapter includes the design decision taken while implementing the \acrfull{wdias}, and how is the system got adapted from the systems analyzed in Chapter \ref{ch:literature}, then how is it trying to propose a better system with overcoming the issues.
-
-\section{Introduction}
+\dbc{Add a couple of sentences to indicate what is covered in each Section. Do this in all chapters except in Chap 1.}
 
 \import{method/}{sec_0_introduction.tex}
+\label{se:method_intro}
 
 \import{method/}{sec_1-soa.tex}
+\label{se:soa}
 
 \import{method/}{sec_2-actor_model.tex}
+\label{se:actor_model}
 
 \import{method/}{sec_3-microservice.tex}
+\label{se:microservice}
 
 \import{method/}{sec_4-db_struct.tex}
+\label{se:db_struct}
 
 \import{method/}{sec_5-data_preprocess.tex}
+\label{se:data_preprocess}
 
 \import{method/}{sec_6-query.tex}
+\label{se:query}
 
@@
 
+\import{results/}{sec_0-introduction.tex}
+\label{se:results_intro}
+
 \import{results/}{sec_1-test_plan.tex}
+\label{se:test_plan}
 
 \import{results/}{sec_2-work_load.tex}
+\label{se:work_load}
 
 \import{results/}{sec_3-observations.tex}
+\label{se:observations}
 
 \import{results/}{sec_4-conclusion.tex}
+\label{se:conclusion}
 
@@
 \label{ch:conc}
-
-Discuss your results and system and conclude.
 

### 2020-02-09 method/sec_4-db_struct.tex
Paper - update abstract
Paper - Updated the Structure of the paper

@@
 \section{Hierarchical Database Structure}
+\dbc{Use a more meaningful title.}
 
@@
   \end{lstlisting}
+ \dbc{Line spacing is too high. Use simple monospace format in latex.}
+
   - Regular Grid locations - Contains a name which is human readable. The grid presents by dividing into equal size cells. Thus, it need the number of rows and columns. 
@@
 \label{sub:mysql}
-Relational Database Management System (RDBMS).
+
+\dbc{Use a term like relational DB tham MySQL}
+
+%Relational Database Management System (RDBMS)
 SQL database has fewer version of open source and it is also possible to gain better performance with commercial versions. 
@@
 \label{sub:mongodb}
+\dbc{Use a technology independent term. Same with InfluxDB. MongoDB is used for 2 section names.}
+
 MongoDB is a general purpose, document-based, distributed database

### 2020-02-09 method/sec_5-data_preprocess.tex
Paper - Updated the Structure of the paper

@@
 \section{Extensions (Weather Data Prepossessing)}
+\dbc{Section title?}
+
 The data imported via imported modules may have incorrect data, missing data and not compatible with directly feed into simulation modules. 

### 2020-02-09 method/sec_6-query.tex
Before Test plan
Paper - Updated the Structure of the paper

@@
 
-As described in \ref{sub:mongodb}, adapter-query is primarily using for support Geo-spatial queries.
+As described in \db{Section} \ref{sub:mongodb}, adapter-query is primarily using for support Geo-spatial queries.
 Other than that, as the primary service for searching for timeseries, it also supports for retrieval of timeseries metadata for external queries as well.
@@
 \end{lstlisting}
+\dbc{Use monospace formatting.}
+
 Search for timeseries metadata with key attributes of the timeseries.
@@
 \begin{itemize}
-    \item moduleId(Optional) - E.g. HEC-HMS
-    \item valueType(Optional) - E.g. Scalar
-    \item parameterId(Optional) - E.g. O.Precipitation
-    \item locationId(Optional) - E.g. wdias\_hanwella
-    \item timeseriesType(Optional) - E.g. ExternalHistorical
-    \item timeStepId(Optional) - E.g. each\_15\_min
+    \item moduleId(Optional), e.g., HEC-HMS
+    \item valueType(Optional), e.g., Scalar
+    \item parameterId(Optional), e.g., O.Precipitation
+    \item locationId(Optional), e.g., wdias\_hanwella
+    \item timeseriesType(Optional), e.g., ExternalHistorical
+    \item timeStepId(Optional), e.g., each\_15\_min
 \end{itemize}
@@
     JSON Body:
-    ["<locationId1>", ...]
+    ["<locationID>", ...]
 \end{lstlisting}

### 2020-02-09 results/sec_3-observations.tex
Paper - Updated the Structure of the paper

@@
 
-Following \ref{subse:obs_test_plan_all_60min}, \ref{subse:obs_test_plan_all_30min}, \ref{subse:obs_test_plan_all_15min} and \ref{subse:obs_test_plan_all_auto_15min} sections discussed about the observations collected with performing the Full test plan (also known as All test plan) over 60 minutes (24 data points), 30 minutes (48 data points) and 15 minutes (96 data points) by variate the request size.
+%Following \ref{subse:obs_test_plan_all_60min}, \ref{subse:obs_test_plan_all_30min}, \ref{subse:obs_test_plan_all_15min} and \ref{subse:obs_test_plan_all_auto_15min} sections
+\db{Sections \ref{subse:obs_test_plan_all_60min} to \ref{subse:obs_test_plan_all_auto_15min} discuss} the observations collected with performing the Full test plan (also known as All test plan) over 60 minutes (24 data points), 30 minutes (48 data points) and 15 minutes (96 data points) by variate the request size.
 Then another performance test with enabling Auto Scaling as explained in \ref{subse:test_plan_metrics} for high resource utilized microservice.
@@
 \label{subse:obs_test_plan_all_60min}
+
+\dbc{"Full Test"is a not a good term}
+
 After running the All test plan with 60 minutes (24 data points), it observed the data summary of \ref{tab:obs_all_60_min_summary}. It performed 311k of sample requests.
+
+\dbc{Fonts for tables should be 10pt.}
+
 \begin{table}[]

### 2020-02-09 Paper.tex
Paper - Updated the Structure of the paper
Paper - Added figures and table data for discuss

@@
 I'm going to do this today \cite{Haggett1998AnWales}.
+Give general idea on weather data integration systems.
+Talk about the existing systems. And they're proprietary or close source.
+(Don't dedicate another section, otherwise need to do a comparison at the performance analysis)
+At the end the structure of rest of the paper
 
-\section{Literature Review}
+To enhance the accuracy of weather predictions, it is necessary to provide reliable and detailed weather data as inputs to \acrfull{nwm}.
+These NWMs utilize weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images.
+Prior to feeding such diverse data (collected from different sources that belong to different stakeholders) into respective NWMs, it is necessary to integrate data into a common format.
+Moreover, the data integration system’s response time needs to be relatively low to accommodate critical situations like hurricanes, storms, and floods which require rapid and frequent execution of NWMs.
 
-\subsection{Method}
+Providing public access to weather data is also useful to enable many third-party applications and research.
+For example, logistic companies can use that data with their own model to plan and schedule their deliveries.
+Agricultural insurance companies can warn the farmers in advance, as well as calculate premiums based on anticipated weather patterns.
 
-\subsection{Performance Analysis}
+While Data Integration and Analysis System (DIAS) and Meteorological Assimilation Data Ingest System (MADIS) are some of well-known Weather Data Integration and Assimilation (WDIA) systems, they are proprietary.
+Further Delft-FEWS is free to use, it is not open source.
+Hence, users of WDIA are forced to pay heavy licenses and are unable to extend the solutions to cater to their country-specific requirements.
+Therefore, the objective of this research is to develop a WDIA system for Sri Lanka, as well as make it open source, so that others could use and contribute to the solution.
 
-\section{Conclusions}
+TODO: Specify the \acrshort{lead} service as a building block approach. \acrshort{fews} more modular approach with general adapter. And \acrshort{wdias} using microservice as module.
+Similar to the \acrfull{fews} \cite{WERNER2004DELFT-FEWS:SYSTEM}
 
+The main purpose of this framework is to provide a platform through which opera- tional forecasting systems can be constructed, and that allows flexibility in the integration of models and data.
+In contrast to the NWSRFS and the RFFS systems that also follow a modular approach, the Delft-FEWS system contains no inherent hydrological model- ling capabilities within its code base.
+I
+
+TODO: Update content as below, overview of rest of the paper
+This paper first provides a short review of the operational forecasting process and the role of Delft-FEWS within that process.
+Section 3 provides an overview of the philosophy and the most important components and features of Delft-FEWS, while Section 4 discusses some example applications of the Delft-FEWS system in research and operations.
+A discussion of the systems strengths and limitations is provided in Section 5.
+Section 6 finally provides a summary of the paper, as well as an outlook on the future development of Delft-FEWS.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Modules of Weather Data System}
+The figure \ref{fi:wdia_components} shows the basic functions of a Weather data integration and assimilation system.
+\begin{figure}[htbp]
+\centerline{\includegraphics[width=0.5\textwidth]{method/misc/weather_data_system_components.jpg}}
+\caption{Components of a Weather Data System.}
+\label{fi:wdia_components}
+\end{figure}
+\paragraph{Integration} The system should capable of integrating data from different source such as satellite data, high end and low end weather station etc.
+And the system should be able to handle multidimensional spatial and temporal weather data efficiently and optimally.
+\paragraph{Assimilation} Then the system should be able to fulfill weather models varying data requirements.
+Also those models reproduce large set of redundant data, thus system should store the bulk data while optimizing the disk space.
+\paragraph{Dissemination} Then different users should be able to retrieve data as they required.
+Also the users should be able to easy to search into the available that in the system base on timeseries metadata or based on Geo queries.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Different Architectures}
+
+\subsection{\acrfull{soa}}
+\begin{figure}[htbp]
+\centerline{\includegraphics[width=0.5\textwidth]{method/soa/soa_v1.jpg}}
+\caption{Proposed \acrshort{soa} Architecture for \acrshort{wdias}.}
+\label{fi:wdias_soa_architecture}
+\end{figure}
+
+\subsection{Actor Model}
+
+\subsection{Microservice Architecture}
+\begin{figure}[htbp]
+\centerline{\includegraphics[width=0.5\textwidth]{method/microservice/k8s_architecture_v3.jpg}}
+\caption{\acrfull{k8s} Architecture.}
+\label{fi:k8s_architecture}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Structure of \acrshort{wdias}}
+\begin{figure}[htbp]
+\centerline{\includegraphics[width=0.5\textwidth]{method/microservice/microservice_architecture-handle_on_demand-v3.jpg}}
+\caption{microservice Architecture - Handle on Demand.}
+\label{fi:microservice_architecture_on_demand}
+\end{figure}
+
+\begin{figure}[htbp]
+\centerline{\includegraphics[width=0.5\textwidth]{method/microservice/microservice_architecture-handle_on_async-v3.jpg}}
+\caption{microservice Architecture - Handle Asynchronously.}
+\label{fi:microservice_architecture_async}
+\end{figure}
+
+\subsection{Hierarchical Database Structure}
+\begin{figure}[htbp]
+\centerline{\includegraphics[width=0.4\textwidth]{method/microservice/hierarchical_database.jpg}}
+\caption{Hierarchical Database.}
+\label{fi:hierarchical_database}
+\end{figure}
+
+\subsection{Weather Data Preprocessing}
+\begin{figure}[htbp]
+\centerline{\includegraphics[width=0.5\textwidth]{method/data_preprocess/weather_data_preprocessing.jpg}}
+\caption{Generic Functional Approach to Weather data preprocessing.}
+\label{fi:weather_Data_preprocessing}
+\end{figure}
+
+\subsection{Query Timeseries Metadata}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Performance Analysis}
+
+\subsection{Test Plan and Work Load}
+\begin{figure}[htbp]
+\centerline{\includegraphics[width=0.5\textwidth]{results/work_load/performance_study_v4.jpg}}
+\caption{Performance Study.}
+\label{fi:performance_Study}
+\end{figure}
+
+\subsection{Observations}
+\begin{table}[htbp]
+\caption{Table Type Styles}
+\begin{center}
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline
+\textbf{Label} & \textbf{Samples} & \textbf{Avg} & \textbf{Min} & \textbf{Max} & \textbf{Std} & \textbf{90\% Line} \\ \hline
+Insert Scalar & 71727 & 34 & 13 & 1777 & 118.78 & 27 \\ \hline
+Retrieve Scalar & 71693 & 7 & 5 & 1608 & 18.72 & 9 \\ \hline
+Insert Grid & 7968 & 87 & 77 & 233 & 14.07 & 98 \\ \hline
+Retrieve Grid & 7965 & 89 & 63 & 1694 & 37.79 & 110 \\ \hline
+Query & 71704 & 1 & 0 & 203 & 2.05 & 2 \\ \hline
+\textbf{TOTAL} & 310734 & 130 & 0 & 1777 & 212.35 & 501 \\ \hline
+\multicolumn{4}{l}{$^{\mathrm{a}}$Avg: Average Latency, Std: Standard Deviation.}
+\end{tabular}
+\label{tab:obs_all_auto_15_min_summary_latency}
+\end{center}
+\end{table}
+
+\begin{table}[htbp]
+\caption{Table Type Styles}
+\begin{center}
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline
+\textbf{Label} & \textbf{Samples} & \textbf{Avg} & \textbf{Std. Dev.} & \textbf{Error \%} & \textbf{RPS} \\ \hline
+Insert Scalar & 71727 & 34 & 118.78 & 0.00\% & 40.5 \\ \hline
+Retrieve Vector & 71693 & 7 & 18.72 & 0.00\% & 40.5 \\ \hline
+Insert Grid & 7968 & 87 & 14.07 & 0.18\% & 4.5 \\ \hline
+Retrieve Grid & 7965 & 89 & 37.79 & 0.00\% & 4.5 \\ \hline
+Query & 71704 & 1 & 2.05 & 0.00\% & 40.5 \\ \hline
+\textbf{TOTAL} & 310734 & 130 & 212.35 & 0.00\% & 175.3 \\ \hline
+\multicolumn{4}{l}{$^{\mathrm{a}}$Avg: Average Latency.}
+\end{tabular}
+\label{tab:obs_all_auto_15_min_summary_throughput}
+\end{center}
+\end{table}
+
+\begin{figure}[htbp]
+\centerline{\includegraphics[width=0.5\textwidth]{results/obs/all_auto/obs_all_auto_15m_res_latencies_against_hits.png}}
+\caption{Performance Test 15min data enabled Auto Scaling - Response Latencies against Server Hits over the elapsed time.}
+\label{fi:test_obs_auto_all_15_min_latency_vs_hits}
+\end{figure}
+
+\begin{figure}[htbp]
+\centerline{\includegraphics[width=0.5\textwidth]{results/obs/all_auto/obs_all_auto_15m_transaction_throughtput_vs_threads.png}}
+\caption{Performance Test 15min data enabled Auto Scaling - Transnational Throughput vs Number of Active Threads.}
+\label{fi:test_obs_auto_all_15_min_throughput_vs_threads}
+\end{figure}
+
+\subsection{Conclusion}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Strengths and Limitations}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Summary}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{Acknowledgment}

### 2020-02-09 Paper.tex
Move back to the Thesis

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Different Architectures}
-
-\subsection{\acrfull{soa}}
-\begin{figure}[htbp]
-\centerline{\includegraphics[width=0.5\textwidth]{method/soa/soa_v1.jpg}}
-\caption{Proposed \acrshort{soa} Architecture for \acrshort{wdias}.}
-\label{fi:wdias_soa_architecture}
-\end{figure}
-
-\subsection{Actor Model}
-
 \subsection{Microservice Architecture}
+Brief mentioned about soa and Actor model and why moved away from them.
 \begin{figure}[htbp]
@@
 
-\subsection{Hierarchical Database Structure}
+\subsection{Hierarchical Database}
 \begin{figure}[htbp]
@@
 \begin{figure}[htbp]
-\centerline{\includegraphics[width=0.5\textwidth]{method/data_preprocess/weather_data_preprocessing.jpg}}
+\centerline{\includegraphics[width=0.4\textwidth]{method/data_preprocess/summary_weather_data_preprocessing.jpg}}
 \caption{Generic Functional Approach to Weather data preprocessing.}
-\label{fi:weather_Data_preprocessing}
+\label{fi:summary_weather_data_preprocessing}
 \end{figure}
@@
 
-\subsection{Conclusion}
+\subsection{Discussion}
+\paragraph{Latency}
+The latency for each operation type kept constant over the whole test plan run time without any significant change.
+When the request size increased from 24 data points to 96 data points, the latency increase throw out the whole test plan with a smaller number.
+But for each test run the latency kept constant over the time.
+During the \ref{subse:obs_test_plan_all_auto_15min} test run, the performance of the Grid data got better when compared to the \ref{subse:obs_test_plan_all_15min}.
+Which means by adding more resources to the \acrshort{wdias}, it can handle more work load on the system.
+
+\paragraph{Throughput}
+While keeping the latency constant without significant change, the throughput of the \acrshort{wdias} kept constant while increasing the request size from 60min data (24 data points) to 15min data (96 data points) for all the data types such as Scalar, Vector and Grid.
+When number of active threads increased, the \acrshort{wdias} able to provide the same throughput with maintaining the latency stable.
+
+One of the reason to having deviations at the peak time due to use of single instance for the data consistency such as \acrshort{influxdb} for Scalar and Vector data, and netCDF with parallel support for Grid data.
+Further it is possible to increase the performance of these bottlenecks much higher such as using \acrshort{influxdb} Commercial cluster support for high availability or horizontal scaling of \acrshort{influxdb}.
+With \acrshort{influxdb} cluster, it is possible to run multiple pods of adapter-scalar and adapter-vector for support more server hits per second.
+
+Adapter-grid is using a Python wrapper for netCDF FORTRAN implementation with parallel IO enabled.
+This has some performance issues as well as memory leak issues.
+Since each microservice in the \acrshort{wdias} independent of technology that can use to implement the service, it will increase the performance if the adapter-grid directly ported to netCDF with a low level language such as C or FORTRAN.
+Other than \acrshort{eks}, if users can use a \acrshort{k8s} cluster which support Persistent Volumes with the access of Read Write  Many \cite{LinuxFoundationPersistentKubernetes} , then it is possible to run multiple pods of adapter-grid and increase the throughput of the \acrshort{wdias}.
+
+\paragraph{Resource Utilization}
+Since \acrshort{wdias} using the \acrshort{k8s} as the container orchestration system, it allows to scale up and cool down the system as required based on the work load.
+This demonstrate on the test plan of \ref{subse:obs_test_plan_all_auto_15min}, and the system get scale up to the maximum at the peak time.
+Then cool down to single pod after finishing the test cases.
+Given above \acrshort{wdias} can run from 1 CPU node to nodes with 100 CPUs.
+As described in the \ref{se:microservice}, it uses the many of the concept of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities.
+
+\paragraph{Auto Scaling}
+The \acrshort{wdias} supports auto scaling by out of the box with \acrshort{k8s}.
+Services can configure with maximum number of pods in order to avoid over resource usage.
+When there is not much work load on the system, system cool down to less pods in order to save more resources.
+When there is any issue with a pod, \acrshort{k8s} auto schedule another pod and remove the unhealthy pod.
+Also it allows to update the system without any down time with rollback updates.
+
+\paragraph{Risk of Unable to Process Data}
+During the test performance, the \acrshort{wdias} processed many requests with higher request size than the normal usage with lower rate of failures to process the requests, mainly with insert Grid data.
+If the usage of \acrshort{wdias} want to reduce the risk of unable to process data, then system can configure to run with redundant pods in order to handle spike of work loads.
+Also while configure for the auto scaling, the \acrshort{k8s} can configure to maintain lower amount of CPU usage such as 50\% to 60\% rather 80\%.
+Such configuration with always spawn new pods to handle double of current peak load.
 
@@
 \section{Strengths and Limitations}
+\paragraph{Lack of data preprossessing modules}
+The extension module enable plugin system to integrate prepossessing modules which can use for process the data which are inserted to the system or based on regular intervals.
+Also \acrshort{wdias} provide a more generic open interface approach to create more preprocessing modules.
+Since \acrshort{wdias} is an open source system, it expect more modules to be create by the community.
+When compared to other system like \acrshort{fews}, current system only have few extension for the testing purpose.
+This is one of the major area that need to be improved.
+
+\paragraph{Supporting Irregular Grids}
+At the moment \acrshort{wdias} does not support Irregular Grids, but it has the API endpoints define for the implementation which can follow the same microservice architecture.
+The scope of the \acrshort{wdias} does not belong such level of implementation and the scope has reduced by removing such components from the system.
+
+\paragraph{Grid data performance}
+As mentioned in the \ref{se:conclusion}, the adapter-grid is using a Python wrapper for netCDF FORTRAN implementation with parallel IO enabled.
+This has some performance issues as well as memory leak issues.
+Since each microservice in the \acrshort{wdias} independent of technology that can use to implement the service, it will increase the performance if the adapter-grid directly ported to netCDF with a low level language such as C or FORTRAN.
+They are some future work that can focus on improving the performance of grid data.
+
+\paragraph{Define infrastructure as code}
+Physical nodes for the \acrshort{k8s} cluster created using Cloud Computing provider such as \acrshort{eks}.
+And defining the each pod resource limitations at the helm chart level.
+But the infrastructure that need to deploy the \acrshort{wdias} can define as code such as using tools like Teraform which is independent of the Cloud Computing provider.
+Using such tool, users will able to easy deploy the \acrshort{wdias} on any Cloud provider without much hassle.
+
+\paragraph{Further improve hierarchical database performance}
+As further described in \ref{se:conclusion}, it is possible to increase the performance of these bottlenecks much higher such as using \acrshort{influxdb} Commercial cluster support for high availability or horizontal scaling of \acrshort{influxdb}.
+With \acrshort{influxdb} cluster, it is possible to run multiple pods of adapter-scalar and adapter-vector for support more server hits per second.
+Other than that, the \acrshort{wdias} performance can improve via partitioning the timeseries key space into multiple \acrshort{influxdb} instances.
+The adapter-scalar or adapter-vector can improve to plug multiple instance of \acrshort{influxdb} instances by changing the configurations.
+As an example, based on the key attribute \ref{sub:timeseries_key_attributes} Timeseries Type, the adapter-scalar can connect to four instance of \acrshort{influxdb} instances such as  External Historical, External Forecast, Simulated Historical, and Simulated Forecast etc.
 
@@
 \section{Summary}
+To enhance the accuracy of the weather prediction, it is required to have reliable weather data for \acrshort{nwm}.
+Most of existing weather data systems are proprietary or close sourced, or not up to date with the existing cloud computing technologies.
+We proposed an extendable open source Weather Data Integration and Assimilation Systems which is known as \acrshort{wdias}.
+It focused on providing efficiently integrates weather data from different sources with quality control and supporting steaming large size of data.
+And compatible with current cloud computing technologies and architecture patterns.
+
+First the architecture starts with SOA using a \acrfull{esb}, and then moved to Actor model based architecture.
+After comparing the disadvantages of using such architecture with the system requirements, final architecture come up with modern microservice architecture.
+Based on the microservice architecture patterns and the nature of the weather metadata, the \acrshort{wdias} came up with the idea of hierarchical database structure in order to provide higher performance while store the weather data.
+The system uses \acrshort{influxdb} timeseries database for storing Scalar and Vector timeseries data, and using \acrshort{netCDF} for storing Grid timeseries data.
+Also the system provide a generic open mechanism to integrate new modules as extension in order to enhance the features of the system.
+This capability enable to integrate weather data preprocessing flows as extension modules.
+The extension API provide easy access to create and modify the extension triggers on the fly without stopping the system or any downtime in order to change the configurations.
+The system provides extensive timeseries query endpoints to easy search over the system timeseries metadata with supporting Geo based queries.
+
+\acrshort{wdias} performance test is perform using the \acrshort{jmeter} tool's distributed testing capabilities which separately testing each modules.
+Then the test plans are performed with increasing the request size, and monitored the performance metrics.
+The system is setup on the \acrfull{eks} as per the configurations of \ref{sub:test_sys_config}.
+During the performance test plans, the system were able to provide constant throughput by keeping the latency constant while increasing the work load. Which exhibit the scalability of the system.
+With the \acrshort{k8s} auto scaling, the \acrshort{wdias} were able to elastically adjust the number of pods according to the work load with the given configurations.
 
@@
 \graphicspath{ {./images/} }
+\input{glossary.tex}
 \bibliographystyle{plain}

### 2020-02-09 summary/sec_1-conclusions.tex
Move back to the Thesis

--- 2020-02-09 Paper.tex
@@
-\documentclass[conference]{IEEEtran}
-\IEEEoverridecommandlockouts
-% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
-\usepackage{cite}
-\usepackage[acronym]{glossaries}
-\usepackage{amsmath,amssymb,amsfonts}
-\usepackage{algorithmic}
-\usepackage{graphicx}
-\usepackage{textcomp}
-\usepackage{xcolor}
-\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
-    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
-\begin{document}
+%\section{Summary}
+\section{Conclusions}
+\dbc{Expand this section while highlighting key design details and performance}
+\dbc{Sec. 5.2 should be "Research Limitations"}
 
-\title{Weather Data Integration and Assimilation System\\
-% \thanks{Identify applicable funding agency here. If none, delete this.}
-}
+To enhance the accuracy of the weather prediction, it is required to have reliable weather data for \acrshort{nwm}.
+\db{Most of existing weather data systems are proprietary or close sourced, or not up to date with the existing cloud computing technologies.}
+We proposed an extendable open source Weather Data Integration and Assimilation Systems which is known as \acrshort{wdias}.
+It focused on providing efficiently integrates weather data from different sources with quality control and supporting steaming large size of data.
+And compatible with current cloud computing technologies and architecture patterns.
+\dbc{fix highlighted above}
 
-\author{\IEEEauthorblockN{Gihan Karunarathne}
-\IEEEauthorblockA{\textit{dept. computer science and Engineering} \\
-\textit{university of moratuwa}\\
-Moratuwa, Sri Lanka \\
-gihan.09@cse.mrt.ac.lk}
-\and
-\IEEEauthorblockN{Dr. Dilum Bandara}
-\IEEEauthorblockA{\textit{dept. computer science and Engineering} \\
-\textit{university of moratuwa}\\
-Moratuwa, Sri Lanka \\
-dilumb@cse.mrt.ac.lk}
-}
+First the architecture starts with SOA using a \acrfull{esb}, and then moved to Actor model based architecture.
+After comparing the disadvantages of using such architecture with the system requirements, final architecture come up with modern microservice architecture.
+Based on the microservice architecture patterns and the nature of the weather metadata, the \acrshort{wdias} came up with the idea of hierarchical database structure in order to provide higher performance while store the weather data.
+The system uses \acrshort{influxdb} timeseries database for storing Scalar and Vector timeseries data, and using \acrshort{netCDF} for storing Grid timeseries data.
+Also the system provide a generic open mechanism to integrate new modules as extension in order to enhance the features of the system.
+This capability enable to integrate weather data preprocessing flows as extension modules.
+The extension API provide easy access to create and modify the extension triggers on the fly without stopping the system or any downtime in order to change the configurations.
+The system provides extensive timeseries query endpoints to easy search over the system timeseries metadata with supporting Geo based queries.
 
-\maketitle
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{abstract}
-We describe our experience with implementing an extendable open source Weather Data Integration and Assimilation System, which is known as \acrshort{wdias}.
-It uses the modern architecture pattern such as microservice in order to achieve the scalability, rather using monolithic architecture or client service architecture.
-It provides a modular approach to integration data from different sources and export into different formats.
-Also the inbuilt extension module system allow users to add new features.
-The open source tools that are using for \acrshort{wdias} allows to run on Cloud Computing platforms without much hassle with the auto scaling feature allow to run \acrshort{wdias} from 1 CPU node to nodes with few hundred CPUs.
-The paper describes the initial design goals, evolve over few architectures to get desired performance, and explains how the system in way to achieve scalability.
-Later we analyse the performance test observations with the performance metrics.
-\end{abstract}
-
-\begin{IEEEkeywords}
-\acrshort{wdias}, weather, microservice, kubernetes, hierarchical database 
-\end{IEEEkeywords}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{INTRODUCTION}
-I'm going to do this today \cite{Haggett1998AnWales}.
-
-\section{Literature Review}
-
-\subsection{Method}
-
-\subsection{Performance Analysis}
-
-\section{Conclusions}
-
-\section{Summary}
-
-\section*{Acknowledgment}
-
-The preferred spelling of the word ``acknowledgment'' in America is without 
-an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
-G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
-acknowledgments in the unnumbered footnote on the first page.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\graphicspath{ {./images/} }
-\bibliographystyle{plain}
-\bibliography{mendeley}
-
-\end{document}
+\acrshort{wdias} performance test is perform using the \acrshort{jmeter} tool's distributed testing capabilities which separately testing each modules.
+Then the test plans are performed with increasing the request size, and monitored the performance metrics.
+The system is setup on the \acrfull{eks} as per the configurations of \ref{sub:test_sys_config}.
+During the performance test plans, the system were able to provide constant throughput by keeping the latency constant while increasing the work load. Which exhibit the scalability of the system.
+With the \acrshort{k8s} auto scaling, the \acrshort{wdias} were able to elastically adjust the number of pods according to the work load with the given configurations.

### 2020-02-09 summary/sec_2-research_limitations.tex
Move back to the Thesis

--- 2020-02-08 summary/sec_2-future_work.tex
@@
-\section{Future Work}
+\section{Research Limitations}
 This section discussed about the lacking features in the \acrshort{wdias}, and some of the improvement that can add for improve the performance and usability of the system.
+
+\dbc{Use italics to emphasize, not bold.}
 

### 2020-02-09 introduction/sec_1-motivation.tex
thesis - Move introduction into multiple files

--- 2019-12-01 thesis.tex
@@
-\documentclass[a4paper,oneside,12pt]{report}
-\usepackage{graphicx,mathptmx}
-\usepackage{geometry}
- \geometry{
- a4paper,
- %total={160mm,227mm},
- left=40mm,
- top=25mm,
- bottom=40mm, 
- right=25mm,
-}
-\renewcommand{\baselinestretch}{1.5}
+\section{Motivation}
+To enhance the accuracy of weather predictions, it is necessary to provide reliable and detailed weather data as inputs to \acrfull{nwm}.
+These NWMs utilize \db{multimodal} weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images.
+Prior to feeding such diverse data (collected from different sources that belongs to different stakeholders) into respective NWMs, it is necessary to integrate data into a common format.
+Moreover, the data integration system’s response time need to be relatively low to %accommodate critical situations
+\db{forecast and monitor time-sensitive weather events} like hurricanes, storms, and floods which require rapid and frequent execution of NWMs.
 
-\usepackage{setspace}
-\usepackage{tabu}
-\usepackage[acronym]{glossaries}
-\makeglossaries
-\usepackage{import}
-\usepackage{listings}
-
-\begin{document}
-\begin{titlepage}
-    \begin{center}
-        \Large{
-        \textbf{WEATHER DATA INTEGRATION AND ASSIMILATION SYSTEM}}\\
-        \vspace{144pt}
-  \large      
-        %\vspace{1cm}
-      % by
-
-        %\vspace{1.0cm}
-
-        Gihan Chanuka Karunarathne\\
-        \vspace{24pt}
-       % \normalsize
-      178004U\\
-         \vspace{72pt}
-        %\normalsize
-        Degree of Master of Science\\
-
-        %\centering
-         %\includegraphics[width=0.4\textwidth]{0.Title_Page/uom.png}\\
-            %\vspace{0.8cm}
-         %\normalsize
-
-        %\vfill
-       \vspace{72pt}
-        \large
-        Department of Computer Science and Engineering\\
-        \vspace{24pt}
-        University of Moratuwa\\
-        Sri Lanka\\
-        \vspace{32pt}
-        April 2019
-
-    \end{center}
-\end{titlepage}
-
-\begin{titlepage}
-    \begin{center}
-       % \vspace*{1cm}
-        \Large{
-        \textbf{WEATHER DATA INTEGRATION AND ASSIMILATION SYSTEM}}\\
-        \vspace{144pt}
-  \large
-
-        Herath Mudiyanselage Gihan Chanuka Karunarathne\\
-        \vspace{24pt}
-       % \normalsize
-        178008U\\
-         \vspace{72pt}
-        \normalsize
-        Thesis submitted in partial fulfillment of the requirements for the degree Master of Science in Computer Science and Engineering\\
-
-        %\vfill
-       \vspace{72pt}
-        \large
-        Department of Computer Science and Engineering\\
-        \vspace{24pt}
-        University of Moratuwa\\
-        Sri Lanka\\
-        \vspace{32pt}
-        April 2019
-
-    \end{center}
-\end{titlepage}
-
-\pagenumbering{roman}
-
-\newgeometry{left=4cm,top=0.5cm,right=2.5cm}
-\chapter*{Declaration}
-\addcontentsline{toc}{chapter}{Declaration}
-
-I declare that this is my own work and this thesis does not
-incorporate without acknowledgement any material previously submitted for a
-Degree or Diploma in any other University or institute of higher learning and to
-the best of my knowledge and belief it does not contain any material previously
-published or written by another person except where the acknowledgement is
-made in the text.
-
-Also, I hereby grant to University of Moratuwa the non-exclusive right to
-reproduce and distribute my thesis/dissertation, in whole or in part in print,
-electronic or other medium. I retain the right to use this content in whole or part
-in future works (such as articles or books).
-
-\vspace{0.5in}
-\noindent
-\begin{tabu} to 1.0\textwidth { X[l] X[l] }
-    Signature: & Date:
-\end{tabu}
-
-\vspace{0.5in}
-\noindent
-The above candidate has carried out research for the Masters thesis under our supervision.
-
-\vspace{0.5in}
-\noindent
-\begin{tabu} to 1.0\textwidth { X[l] X[l] }
-    Name of the supervisor: & Dr. HMN Dilum Bandara\\ [1.5ex]
-    Signature of the supervisor: & Date:
-\end{tabu}
-
-\restoregeometry
-\normalsize
-
-\newgeometry{left=2.5cm,top=0.2cm,right=2cm}
-\addcontentsline{toc}{chapter}{Abstract} 
-{\setstretch{1.0} 
-\chapter*{Abstract}
-%\chapter*{\hspace{1cm} Abstract}
-
-To enhance the accuracy of weather predictions, it is necessary to provide reliable and detailed weather data as inputs to \acrfull{nwm}.
-These \acrshort{nwm} utilize weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images.
-Prior to feeding such diverse data (collected from different sources that belongs to different stakeholders) into respective \acrshort{nwm}, it is necessary to integrate data into a common format.
-Moreover, the data integration system’s response time need to be relatively low to accommodate critical situations like hurricanes, storms, and floods which require rapid and frequent execution of \acrshort{nwm}.
+\dbc{We are not developing this platform only because we need to have a common data format or need to share with 3rd parties.
+These are secondary reasons.
+Highlight key reason why we need a weather data assimilation system.
+Key reason should be indicated in Abstract too.}
 
 Providing public to access weather data is also useful to enable many third-party applications and research.
-For example, logistic companies can use those data with their own model to plan and schedule their deliveries.
+For example, logistic companies could use those data with their models to plan and schedule their deliveries.
 Agricultural insurance companies can warn the farmers in advance, as well as calculate premiums based on anticipated weather patterns.
-
-While \acrfull{dias} and \acrfull{madis} are some of well-known Weather Data Integration and Assimilation (WDIA) systems, they are proprietary.
-Further Delft-FEWS is free to use, it is not open source.
-Hence, users of WDIA are forced to pay heavy licenses and are unable to extend the solutions to cater to their country-specific requirements.
-Therefore, the objective of this research is to develop a WDIA system for Sri Lanka, as well as make it open source, so that others could user and contribute to the solution.
-
-\vspace{4mm}
-
-\textbf{Keywords:} WDIAS, Weather, Timeseries, Distributed, Scalable
-
-}
-\restoregeometry
-\normalsize
-
-\addcontentsline{toc}{chapter}{Dedication} 
-\chapter*{Dedication}
-I dedicate my thesis work to my family, teachers and specially friends at \acrfull{curw}.
-A special feeling of gratitude to my loving parents, Nandawathi Dissanayake and H.M.K.
-Karunarathne whose words of encouragement and push for tenacity ring in my ears.
-My wife Jayani Kumarasinghe have never left my side and are very special.
-
-I also dedicate this thesis to my many friends at \acrshort{curw} who have supported and be with me during this period of time.
-Also special thanks to Dr.
-Dilum Bandara and Dr.
-Srikantha Herath for giving me this wonderful opportunity to explore this new domain.
-
-\addcontentsline{toc}{chapter}{Acknowledgements} 
-\chapter*{Acknowledgements}
-I wish to thank my evaluation panel members who were more than generous with their expertise and precious time.
-A special thanks to Dr.
-Dilum Bandara, my research supervisor for his countless hours of reflecting, reading, encouraging, and most of all patience throughout the entire process.
-Thank you Dr.
-Dilika Peris, and Dr.
-Indika Perera for agreeing to serve on my evaluation panel and Dr.
-Srikantha Herath for agreeing to serve as my external supervisor.
-
-I would like to acknowledge and thank Department of Computer Science and Engineering, University of Moratuwa, for allowing me to conduct my research and providing any assistance requested.
-Special thanks goes to both academic and non-academic staff of the department for their continued support.
-I also gratitude to the University of Moratuwa for the financial support as the research was supported in part by the Senate Research Grant of the University of Moratuwa under award number SRC/LT/2017/01.
-
-Finally, I would like to thank the teachers, evaluating panel and colleagues that assisted me with this project.
-Their excitement and willingness to provide feedback made the completion of this research an enjoyable experience.
-
-\tableofcontents
-
-\addcontentsline{toc}{chapter}{List of Figures} 
-\listoffigures
-
-\addcontentsline{toc}{chapter}{List of Tables} 
-\listoftables
-
-\addcontentsline{toc}{chapter}{List of Abbreviations} 
-\printglossary[type=\acronymtype, title=List of Abbreviations, toctitle=List of Abbreviations, nonumberlist]
-
-\pagenumbering{arabic}
-
-\chapter{Introduction}
-\label{ch:intro}
-To enhance the accuracy of weather predictions, it is necessary to provide reliable and detailed weather data as inputs to \acrfull{nwm}.
-These NWMs utilize weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images.
-Prior to feeding such diverse data (collected from different sources that belongs to different stakeholders) into respective NWMs, it is necessary to integrate data into a common format.
-Moreover, the data integration system’s response time need to be relatively low to accommodate critical situations like hurricanes, storms, and floods which require rapid and frequent execution of NWMs.
-
-\section{Motivation}
-Providing public to access weather data is also useful to enable many third-party applications and research.
-For example, logistic companies can use those data with their own model to plan and schedule their deliveries.
-Agricultural insurance companies can warn the farmers in advance, as well as calculate premiums based on anticipated weather patterns.
+\dbc{Highlight why we need a platform to provide such 3rd party access. Should be indicated in Abstract too.}
 
@@
 Therefore, the objective of this research is to develop a WDIA system for Sri Lanka, as well as make it open source, so that others could user and contribute to the solution.
-
-\section{Problem}
-\begin{itemize}
-    \item Handling spatio-temporal weather data is challenging
-    \item Need an extendable system to support weather models by efficiently storing and retrieving data
-    \item Goal is to design and develop a Weather Data Integration and Assimilation System that,
-    \begin{itemize}
-        \item Integrates weather data from different sources with quality control
-        \item Efficiently store spatio-temporal weather data with multiple dimensions
-        \item Support geographical and time-base queries
-    \end{itemize}
-\end{itemize}
-
-\section{Objectives}
-\begin{itemize}
-    \item To develop an open platform to integrate weather data from different sources in different formats
-    \item To design and develop a schema to store multidimensional weather timeseries data while optimizing,
-    \begin{itemize}
-        \item Disk space
-        \item Availability
-        \item Access time
-    \end{itemize}
-    \item To optimize schema to support data queries based on geography and time
-    \item To develop an API to share data while providing role-based access control
-\end{itemize}
-
-\section{Outline}
-The rest of the thesis is organized as follows.
-Literature review is presented in Chapter \ref{ch:literature}.
-Solution approach with the proposed system architectures and adaptation with problem occurred are presented in Chapter \ref{ch:method}.
-Performance analysis is presented in Chapter \ref{ch:results} while summary and future work are presented in Chapter \ref{ch:conc}.
-
-\chapter{Literature Review}
-\label{ch:literature}
-There are many of Weather forecasting, assimilation and dissemination systems developed by some of developed countries around the world as a result of trying to reduce the damage causing by natural disasters such as flood, storms, hurricanes and even for drought.
-Above kind of natural disasters heavily affected on the economy and the life conditions of the country, researchers have developed systems and many of these systems are using as proprietary systems.
-Other countries also using those systems and adopt with own version of system which effective for the specific weather condition in a particular country.
-Though out this chapter includes a Literature review about existing systems and their architecture approach and design with available resources.
-Most influenced systems for \acrshort{wdias} is \acrshort{fews} and \acrfull{lead} system.
-\acrshort{fews} is an open data handling platform, but it distributed as Closed Source software.
-\acrshort{lead} is following the Service Oriented Architecture for system architecture.
-Under each system we explore both system architecture, scalability and flexibility of the system.
-
-\import{lit/}{sec_1-fews.tex}
-
-\import{lit/}{sec_2-lead.tex}
-
-\section{Data Integration and Assimilation System}
-\label{se:dias}
-
-\section{Meteorological Assimilation Data Ingest System}
-\label{se:madis}
-
-\section{Summary}
-
-\chapter{Method}
-\label{ch:method}
-This chapter includes the design decision taken while implementing the \acrfull{wdias}, and how is the system got adapted from the systems analyzed in Chapter \ref{ch:literature}, then how is it trying to propose a better system with overcoming the issues.
-
-\section{Introduction}
-
-\import{method/}{sec_0_introduction.tex}
-
-\import{method/}{sec_1-soa.tex}
-
-\import{method/}{sec_2-actor_model.tex}
-
-\import{method/}{sec_3-microservice.tex}
-
-\import{method/}{sec_4-db_struct.tex}
-
-\import{method/}{sec_5-data_preprocess.tex}
-
-\import{method/}{sec_6-query.tex}
-
-\chapter{Results}
-\label{ch:results}
-
-\import{results/}{sec_1-test_plan.tex}
-
-\import{results/}{sec_2-work_load.tex}
-
-\import{results/}{sec_3-observations.tex}
-
-\import{results/}{sec_4-conclusion.tex}
-
-\chapter{Conclusions}
-\label{ch:conc}
-
-Discuss your results and system and conclude.
-
-\import{summary/}{sec_1-summary.tex}
-
-\import{summary/}{sec_2-future_work.tex}
-
-\appendix
-\chapter{First Appendix}
-Type out your first appendix here.
-\section{Basics}
-
-\chapter{First Appendix}
-Type out your second appendix here.
-
-\graphicspath{ {./images/} }
-\input{glossary.tex}
-\bibliographystyle{plain}
-\bibliography{mendeley}
-\end{document}
+\dbc{Saying something proprietary is not good reason to do research.
+You should highlight the context under which these solutions are developed and differences between CUrW and Sri Lanka in general.
+Also, give a bit more details than saying "to cater to their country-specific requirements".
+All key systems such as DIAS, MADIS, Delf, etc.
+need to be properly cited.}

### 2020-02-09 introduction/sec_2-problem_statement.tex
thesis - Move introduction into multiple files

--- 2019-12-01 thesis.tex
@@
-\documentclass[a4paper,oneside,12pt]{report}
-\usepackage{graphicx,mathptmx}
-\usepackage{geometry}
- \geometry{
- a4paper,
- %total={160mm,227mm},
- left=40mm,
- top=25mm,
- bottom=40mm, 
- right=25mm,
-}
-\renewcommand{\baselinestretch}{1.5}
-
-\usepackage{setspace}
-\usepackage{tabu}
-\usepackage[acronym]{glossaries}
-\makeglossaries
-\usepackage{import}
-\usepackage{listings}
-
-\begin{document}
-\begin{titlepage}
-    \begin{center}
-        \Large{
-        \textbf{WEATHER DATA INTEGRATION AND ASSIMILATION SYSTEM}}\\
-        \vspace{144pt}
-  \large      
-        %\vspace{1cm}
-      % by
-
-        %\vspace{1.0cm}
-
-        Gihan Chanuka Karunarathne\\
-        \vspace{24pt}
-       % \normalsize
-      178004U\\
-         \vspace{72pt}
-        %\normalsize
-        Degree of Master of Science\\
-
-        %\centering
-         %\includegraphics[width=0.4\textwidth]{0.Title_Page/uom.png}\\
-            %\vspace{0.8cm}
-         %\normalsize
-
-        %\vfill
-       \vspace{72pt}
-        \large
-        Department of Computer Science and Engineering\\
-        \vspace{24pt}
-        University of Moratuwa\\
-        Sri Lanka\\
-        \vspace{32pt}
-        April 2019
-
-    \end{center}
-\end{titlepage}
-
-\begin{titlepage}
-    \begin{center}
-       % \vspace*{1cm}
-        \Large{
-        \textbf{WEATHER DATA INTEGRATION AND ASSIMILATION SYSTEM}}\\
-        \vspace{144pt}
-  \large
-
-        Herath Mudiyanselage Gihan Chanuka Karunarathne\\
-        \vspace{24pt}
-       % \normalsize
-        178008U\\
-         \vspace{72pt}
-        \normalsize
-        Thesis submitted in partial fulfillment of the requirements for the degree Master of Science in Computer Science and Engineering\\
-
-        %\vfill
-       \vspace{72pt}
-        \large
-        Department of Computer Science and Engineering\\
-        \vspace{24pt}
-        University of Moratuwa\\
-        Sri Lanka\\
-        \vspace{32pt}
-        April 2019
-
-    \end{center}
-\end{titlepage}
-
-\pagenumbering{roman}
-
-\newgeometry{left=4cm,top=0.5cm,right=2.5cm}
-\chapter*{Declaration}
-\addcontentsline{toc}{chapter}{Declaration}
-
-I declare that this is my own work and this thesis does not
-incorporate without acknowledgement any material previously submitted for a
-Degree or Diploma in any other University or institute of higher learning and to
-the best of my knowledge and belief it does not contain any material previously
-published or written by another person except where the acknowledgement is
-made in the text.
-
-Also, I hereby grant to University of Moratuwa the non-exclusive right to
-reproduce and distribute my thesis/dissertation, in whole or in part in print,
-electronic or other medium. I retain the right to use this content in whole or part
-in future works (such as articles or books).
-
-\vspace{0.5in}
-\noindent
-\begin{tabu} to 1.0\textwidth { X[l] X[l] }
-    Signature: & Date:
-\end{tabu}
-
-\vspace{0.5in}
-\noindent
-The above candidate has carried out research for the Masters thesis under our supervision.
-
-\vspace{0.5in}
-\noindent
-\begin{tabu} to 1.0\textwidth { X[l] X[l] }
-    Name of the supervisor: & Dr. HMN Dilum Bandara\\ [1.5ex]
-    Signature of the supervisor: & Date:
-\end{tabu}
-
-\restoregeometry
-\normalsize
-
-\newgeometry{left=2.5cm,top=0.2cm,right=2cm}
-\addcontentsline{toc}{chapter}{Abstract} 
-{\setstretch{1.0} 
-\chapter*{Abstract}
-%\chapter*{\hspace{1cm} Abstract}
-
-To enhance the accuracy of weather predictions, it is necessary to provide reliable and detailed weather data as inputs to \acrfull{nwm}.
-These \acrshort{nwm} utilize weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images.
-Prior to feeding such diverse data (collected from different sources that belongs to different stakeholders) into respective \acrshort{nwm}, it is necessary to integrate data into a common format.
-Moreover, the data integration system’s response time need to be relatively low to accommodate critical situations like hurricanes, storms, and floods which require rapid and frequent execution of \acrshort{nwm}.
-
-Providing public to access weather data is also useful to enable many third-party applications and research.
-For example, logistic companies can use those data with their own model to plan and schedule their deliveries.
-Agricultural insurance companies can warn the farmers in advance, as well as calculate premiums based on anticipated weather patterns.
-
-While \acrfull{dias} and \acrfull{madis} are some of well-known Weather Data Integration and Assimilation (WDIA) systems, they are proprietary.
-Further Delft-FEWS is free to use, it is not open source.
-Hence, users of WDIA are forced to pay heavy licenses and are unable to extend the solutions to cater to their country-specific requirements.
-Therefore, the objective of this research is to develop a WDIA system for Sri Lanka, as well as make it open source, so that others could user and contribute to the solution.
-
-\vspace{4mm}
-
-\textbf{Keywords:} WDIAS, Weather, Timeseries, Distributed, Scalable
-
-}
-\restoregeometry
-\normalsize
-
-\addcontentsline{toc}{chapter}{Dedication} 
-\chapter*{Dedication}
-I dedicate my thesis work to my family, teachers and specially friends at \acrfull{curw}.
-A special feeling of gratitude to my loving parents, Nandawathi Dissanayake and H.M.K.
-Karunarathne whose words of encouragement and push for tenacity ring in my ears.
-My wife Jayani Kumarasinghe have never left my side and are very special.
-
-I also dedicate this thesis to my many friends at \acrshort{curw} who have supported and be with me during this period of time.
-Also special thanks to Dr.
-Dilum Bandara and Dr.
-Srikantha Herath for giving me this wonderful opportunity to explore this new domain.
-
-\addcontentsline{toc}{chapter}{Acknowledgements} 
-\chapter*{Acknowledgements}
-I wish to thank my evaluation panel members who were more than generous with their expertise and precious time.
-A special thanks to Dr.
-Dilum Bandara, my research supervisor for his countless hours of reflecting, reading, encouraging, and most of all patience throughout the entire process.
-Thank you Dr.
-Dilika Peris, and Dr.
-Indika Perera for agreeing to serve on my evaluation panel and Dr.
-Srikantha Herath for agreeing to serve as my external supervisor.
-
-I would like to acknowledge and thank Department of Computer Science and Engineering, University of Moratuwa, for allowing me to conduct my research and providing any assistance requested.
-Special thanks goes to both academic and non-academic staff of the department for their continued support.
-I also gratitude to the University of Moratuwa for the financial support as the research was supported in part by the Senate Research Grant of the University of Moratuwa under award number SRC/LT/2017/01.
-
-Finally, I would like to thank the teachers, evaluating panel and colleagues that assisted me with this project.
-Their excitement and willingness to provide feedback made the completion of this research an enjoyable experience.
-
-\tableofcontents
-
-\addcontentsline{toc}{chapter}{List of Figures} 
-\listoffigures
-
-\addcontentsline{toc}{chapter}{List of Tables} 
-\listoftables
-
-\addcontentsline{toc}{chapter}{List of Abbreviations} 
-\printglossary[type=\acronymtype, title=List of Abbreviations, toctitle=List of Abbreviations, nonumberlist]
-
-\pagenumbering{arabic}
-
-\chapter{Introduction}
-\label{ch:intro}
-To enhance the accuracy of weather predictions, it is necessary to provide reliable and detailed weather data as inputs to \acrfull{nwm}.
-These NWMs utilize weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images.
-Prior to feeding such diverse data (collected from different sources that belongs to different stakeholders) into respective NWMs, it is necessary to integrate data into a common format.
-Moreover, the data integration system’s response time need to be relatively low to accommodate critical situations like hurricanes, storms, and floods which require rapid and frequent execution of NWMs.
-
-\section{Motivation}
-Providing public to access weather data is also useful to enable many third-party applications and research.
-For example, logistic companies can use those data with their own model to plan and schedule their deliveries.
-Agricultural insurance companies can warn the farmers in advance, as well as calculate premiums based on anticipated weather patterns.
-
-While Data Integration and Analysis System (DIAS) and Meteorological Assimilation Data Ingest System (MADIS) are some of well-known Weather Data Integration and Assimilation (WDIA) systems, they are proprietary.
-Further Delft-FEWS is free to use, it is not open source.
-Hence, users of WDIA are forced to pay heavy licenses and are unable to extend the solutions to cater to their country-specific requirements.
-Therefore, the objective of this research is to develop a WDIA system for Sri Lanka, as well as make it open source, so that others could user and contribute to the solution.
-
-\section{Problem}
+\section{Problem Statement}
+\dbc{Convert following bullets to a paragraph.
+Goals belongs to next section.
+What we need here is a set of sentences highlighting the needs that are used to derive goals.
+Then provide a single sentence problem statement.
+Look at some of the thesis I shared via OneNote and my website for example problem statements.}
 \begin{itemize}
@@
 \end{itemize}
-
-\section{Objectives}
-\begin{itemize}
-    \item To develop an open platform to integrate weather data from different sources in different formats
-    \item To design and develop a schema to store multidimensional weather timeseries data while optimizing,
-    \begin{itemize}
-        \item Disk space
-        \item Availability
-        \item Access time
-    \end{itemize}
-    \item To optimize schema to support data queries based on geography and time
-    \item To develop an API to share data while providing role-based access control
-\end{itemize}
-
-\section{Outline}
-The rest of the thesis is organized as follows.
-Literature review is presented in Chapter \ref{ch:literature}.
-Solution approach with the proposed system architectures and adaptation with problem occurred are presented in Chapter \ref{ch:method}.
-Performance analysis is presented in Chapter \ref{ch:results} while summary and future work are presented in Chapter \ref{ch:conc}.
-
-\chapter{Literature Review}
-\label{ch:literature}
-There are many of Weather forecasting, assimilation and dissemination systems developed by some of developed countries around the world as a result of trying to reduce the damage causing by natural disasters such as flood, storms, hurricanes and even for drought.
-Above kind of natural disasters heavily affected on the economy and the life conditions of the country, researchers have developed systems and many of these systems are using as proprietary systems.
-Other countries also using those systems and adopt with own version of system which effective for the specific weather condition in a particular country.
-Though out this chapter includes a Literature review about existing systems and their architecture approach and design with available resources.
-Most influenced systems for \acrshort{wdias} is \acrshort{fews} and \acrfull{lead} system.
-\acrshort{fews} is an open data handling platform, but it distributed as Closed Source software.
-\acrshort{lead} is following the Service Oriented Architecture for system architecture.
-Under each system we explore both system architecture, scalability and flexibility of the system.
-
-\import{lit/}{sec_1-fews.tex}
-
-\import{lit/}{sec_2-lead.tex}
-
-\section{Data Integration and Assimilation System}
-\label{se:dias}
-
-\section{Meteorological Assimilation Data Ingest System}
-\label{se:madis}
-
-\section{Summary}
-
-\chapter{Method}
-\label{ch:method}
-This chapter includes the design decision taken while implementing the \acrfull{wdias}, and how is the system got adapted from the systems analyzed in Chapter \ref{ch:literature}, then how is it trying to propose a better system with overcoming the issues.
-
-\section{Introduction}
-
-\import{method/}{sec_0_introduction.tex}
-
-\import{method/}{sec_1-soa.tex}
-
-\import{method/}{sec_2-actor_model.tex}
-
-\import{method/}{sec_3-microservice.tex}
-
-\import{method/}{sec_4-db_struct.tex}
-
-\import{method/}{sec_5-data_preprocess.tex}
-
-\import{method/}{sec_6-query.tex}
-
-\chapter{Results}
-\label{ch:results}
-
-\import{results/}{sec_1-test_plan.tex}
-
-\import{results/}{sec_2-work_load.tex}
-
-\import{results/}{sec_3-observations.tex}
-
-\import{results/}{sec_4-conclusion.tex}
-
-\chapter{Conclusions}
-\label{ch:conc}
-
-Discuss your results and system and conclude.
-
-\import{summary/}{sec_1-summary.tex}
-
-\import{summary/}{sec_2-future_work.tex}
-
-\appendix
-\chapter{First Appendix}
-Type out your first appendix here.
-\section{Basics}
-
-\chapter{First Appendix}
-Type out your second appendix here.
-
-\graphicspath{ {./images/} }
-\input{glossary.tex}
-\bibliographystyle{plain}
-\bibliography{mendeley}
-\end{document}

### 2020-02-09 introduction/sec_3-objectives.tex
thesis - Move introduction into multiple files

--- 2019-12-01 thesis.tex
@@
-\documentclass[a4paper,oneside,12pt]{report}
-\usepackage{graphicx,mathptmx}
-\usepackage{geometry}
- \geometry{
- a4paper,
- %total={160mm,227mm},
- left=40mm,
- top=25mm,
- bottom=40mm, 
- right=25mm,
-}
-\renewcommand{\baselinestretch}{1.5}
-
-\usepackage{setspace}
-\usepackage{tabu}
-\usepackage[acronym]{glossaries}
-\makeglossaries
-\usepackage{import}
-\usepackage{listings}
-
-\begin{document}
-\begin{titlepage}
-    \begin{center}
-        \Large{
-        \textbf{WEATHER DATA INTEGRATION AND ASSIMILATION SYSTEM}}\\
-        \vspace{144pt}
-  \large      
-        %\vspace{1cm}
-      % by
-
-        %\vspace{1.0cm}
-
-        Gihan Chanuka Karunarathne\\
-        \vspace{24pt}
-       % \normalsize
-      178004U\\
-         \vspace{72pt}
-        %\normalsize
-        Degree of Master of Science\\
-
-        %\centering
-         %\includegraphics[width=0.4\textwidth]{0.Title_Page/uom.png}\\
-            %\vspace{0.8cm}
-         %\normalsize
-
-        %\vfill
-       \vspace{72pt}
-        \large
-        Department of Computer Science and Engineering\\
-        \vspace{24pt}
-        University of Moratuwa\\
-        Sri Lanka\\
-        \vspace{32pt}
-        April 2019
-
-    \end{center}
-\end{titlepage}
-
-\begin{titlepage}
-    \begin{center}
-       % \vspace*{1cm}
-        \Large{
-        \textbf{WEATHER DATA INTEGRATION AND ASSIMILATION SYSTEM}}\\
-        \vspace{144pt}
-  \large
-
-        Herath Mudiyanselage Gihan Chanuka Karunarathne\\
-        \vspace{24pt}
-       % \normalsize
-        178008U\\
-         \vspace{72pt}
-        \normalsize
-        Thesis submitted in partial fulfillment of the requirements for the degree Master of Science in Computer Science and Engineering\\
-
-        %\vfill
-       \vspace{72pt}
-        \large
-        Department of Computer Science and Engineering\\
-        \vspace{24pt}
-        University of Moratuwa\\
-        Sri Lanka\\
-        \vspace{32pt}
-        April 2019
-
-    \end{center}
-\end{titlepage}
-
-\pagenumbering{roman}
-
-\newgeometry{left=4cm,top=0.5cm,right=2.5cm}
-\chapter*{Declaration}
-\addcontentsline{toc}{chapter}{Declaration}
-
-I declare that this is my own work and this thesis does not
-incorporate without acknowledgement any material previously submitted for a
-Degree or Diploma in any other University or institute of higher learning and to
-the best of my knowledge and belief it does not contain any material previously
-published or written by another person except where the acknowledgement is
-made in the text.
-
-Also, I hereby grant to University of Moratuwa the non-exclusive right to
-reproduce and distribute my thesis/dissertation, in whole or in part in print,
-electronic or other medium. I retain the right to use this content in whole or part
-in future works (such as articles or books).
-
-\vspace{0.5in}
-\noindent
-\begin{tabu} to 1.0\textwidth { X[l] X[l] }
-    Signature: & Date:
-\end{tabu}
-
-\vspace{0.5in}
-\noindent
-The above candidate has carried out research for the Masters thesis under our supervision.
-
-\vspace{0.5in}
-\noindent
-\begin{tabu} to 1.0\textwidth { X[l] X[l] }
-    Name of the supervisor: & Dr. HMN Dilum Bandara\\ [1.5ex]
-    Signature of the supervisor: & Date:
-\end{tabu}
-
-\restoregeometry
-\normalsize
-
-\newgeometry{left=2.5cm,top=0.2cm,right=2cm}
-\addcontentsline{toc}{chapter}{Abstract} 
-{\setstretch{1.0} 
-\chapter*{Abstract}
-%\chapter*{\hspace{1cm} Abstract}
-
-To enhance the accuracy of weather predictions, it is necessary to provide reliable and detailed weather data as inputs to \acrfull{nwm}.
-These \acrshort{nwm} utilize weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images.
-Prior to feeding such diverse data (collected from different sources that belongs to different stakeholders) into respective \acrshort{nwm}, it is necessary to integrate data into a common format.
-Moreover, the data integration system’s response time need to be relatively low to accommodate critical situations like hurricanes, storms, and floods which require rapid and frequent execution of \acrshort{nwm}.
-
-Providing public to access weather data is also useful to enable many third-party applications and research.
-For example, logistic companies can use those data with their own model to plan and schedule their deliveries.
-Agricultural insurance companies can warn the farmers in advance, as well as calculate premiums based on anticipated weather patterns.
-
-While \acrfull{dias} and \acrfull{madis} are some of well-known Weather Data Integration and Assimilation (WDIA) systems, they are proprietary.
-Further Delft-FEWS is free to use, it is not open source.
-Hence, users of WDIA are forced to pay heavy licenses and are unable to extend the solutions to cater to their country-specific requirements.
-Therefore, the objective of this research is to develop a WDIA system for Sri Lanka, as well as make it open source, so that others could user and contribute to the solution.
-
-\vspace{4mm}
-
-\textbf{Keywords:} WDIAS, Weather, Timeseries, Distributed, Scalable
-
-}
-\restoregeometry
-\normalsize
-
-\addcontentsline{toc}{chapter}{Dedication} 
-\chapter*{Dedication}
-I dedicate my thesis work to my family, teachers and specially friends at \acrfull{curw}.
-A special feeling of gratitude to my loving parents, Nandawathi Dissanayake and H.M.K.
-Karunarathne whose words of encouragement and push for tenacity ring in my ears.
-My wife Jayani Kumarasinghe have never left my side and are very special.
-
-I also dedicate this thesis to my many friends at \acrshort{curw} who have supported and be with me during this period of time.
-Also special thanks to Dr.
-Dilum Bandara and Dr.
-Srikantha Herath for giving me this wonderful opportunity to explore this new domain.
-
-\addcontentsline{toc}{chapter}{Acknowledgements} 
-\chapter*{Acknowledgements}
-I wish to thank my evaluation panel members who were more than generous with their expertise and precious time.
-A special thanks to Dr.
-Dilum Bandara, my research supervisor for his countless hours of reflecting, reading, encouraging, and most of all patience throughout the entire process.
-Thank you Dr.
-Dilika Peris, and Dr.
-Indika Perera for agreeing to serve on my evaluation panel and Dr.
-Srikantha Herath for agreeing to serve as my external supervisor.
-
-I would like to acknowledge and thank Department of Computer Science and Engineering, University of Moratuwa, for allowing me to conduct my research and providing any assistance requested.
-Special thanks goes to both academic and non-academic staff of the department for their continued support.
-I also gratitude to the University of Moratuwa for the financial support as the research was supported in part by the Senate Research Grant of the University of Moratuwa under award number SRC/LT/2017/01.
-
-Finally, I would like to thank the teachers, evaluating panel and colleagues that assisted me with this project.
-Their excitement and willingness to provide feedback made the completion of this research an enjoyable experience.
-
-\tableofcontents
-
-\addcontentsline{toc}{chapter}{List of Figures} 
-\listoffigures
-
-\addcontentsline{toc}{chapter}{List of Tables} 
-\listoftables
-
-\addcontentsline{toc}{chapter}{List of Abbreviations} 
-\printglossary[type=\acronymtype, title=List of Abbreviations, toctitle=List of Abbreviations, nonumberlist]
-
-\pagenumbering{arabic}
-
-\chapter{Introduction}
-\label{ch:intro}
-To enhance the accuracy of weather predictions, it is necessary to provide reliable and detailed weather data as inputs to \acrfull{nwm}.
-These NWMs utilize weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images.
-Prior to feeding such diverse data (collected from different sources that belongs to different stakeholders) into respective NWMs, it is necessary to integrate data into a common format.
-Moreover, the data integration system’s response time need to be relatively low to accommodate critical situations like hurricanes, storms, and floods which require rapid and frequent execution of NWMs.
-
-\section{Motivation}
-Providing public to access weather data is also useful to enable many third-party applications and research.
-For example, logistic companies can use those data with their own model to plan and schedule their deliveries.
-Agricultural insurance companies can warn the farmers in advance, as well as calculate premiums based on anticipated weather patterns.
-
-While Data Integration and Analysis System (DIAS) and Meteorological Assimilation Data Ingest System (MADIS) are some of well-known Weather Data Integration and Assimilation (WDIA) systems, they are proprietary.
-Further Delft-FEWS is free to use, it is not open source.
-Hence, users of WDIA are forced to pay heavy licenses and are unable to extend the solutions to cater to their country-specific requirements.
-Therefore, the objective of this research is to develop a WDIA system for Sri Lanka, as well as make it open source, so that others could user and contribute to the solution.
-
-\section{Problem}
-\begin{itemize}
-    \item Handling spatio-temporal weather data is challenging
-    \item Need an extendable system to support weather models by efficiently storing and retrieving data
-    \item Goal is to design and develop a Weather Data Integration and Assimilation System that,
-    \begin{itemize}
-        \item Integrates weather data from different sources with quality control
-        \item Efficiently store spatio-temporal weather data with multiple dimensions
-        \item Support geographical and time-base queries
-    \end{itemize}
-\end{itemize}
-
 \section{Objectives}
+\db{We address above problem statement by  achieving the following objectives:}
 \begin{itemize}
     \item To develop an open platform to integrate weather data from different sources in different formats
-    \item To design and develop a schema to store multidimensional weather timeseries data while optimizing,
-    \begin{itemize}
-        \item Disk space
-        \item Availability
-        \item Access time
-    \end{itemize}
+    \item To design and develop a schema to store multidimensional weather timeseries data while optimizing access time, availability, and storage.
     \item To optimize schema to support data queries based on geography and time
@@
 \end{itemize}
-
-\section{Outline}
-The rest of the thesis is organized as follows.
-Literature review is presented in Chapter \ref{ch:literature}.
-Solution approach with the proposed system architectures and adaptation with problem occurred are presented in Chapter \ref{ch:method}.
-Performance analysis is presented in Chapter \ref{ch:results} while summary and future work are presented in Chapter \ref{ch:conc}.
-
-\chapter{Literature Review}
-\label{ch:literature}
-There are many of Weather forecasting, assimilation and dissemination systems developed by some of developed countries around the world as a result of trying to reduce the damage causing by natural disasters such as flood, storms, hurricanes and even for drought.
-Above kind of natural disasters heavily affected on the economy and the life conditions of the country, researchers have developed systems and many of these systems are using as proprietary systems.
-Other countries also using those systems and adopt with own version of system which effective for the specific weather condition in a particular country.
-Though out this chapter includes a Literature review about existing systems and their architecture approach and design with available resources.
-Most influenced systems for \acrshort{wdias} is \acrshort{fews} and \acrfull{lead} system.
-\acrshort{fews} is an open data handling platform, but it distributed as Closed Source software.
-\acrshort{lead} is following the Service Oriented Architecture for system architecture.
-Under each system we explore both system architecture, scalability and flexibility of the system.
-
-\import{lit/}{sec_1-fews.tex}
-
-\import{lit/}{sec_2-lead.tex}
-
-\section{Data Integration and Assimilation System}
-\label{se:dias}
-
-\section{Meteorological Assimilation Data Ingest System}
-\label{se:madis}
-
-\section{Summary}
-
-\chapter{Method}
-\label{ch:method}
-This chapter includes the design decision taken while implementing the \acrfull{wdias}, and how is the system got adapted from the systems analyzed in Chapter \ref{ch:literature}, then how is it trying to propose a better system with overcoming the issues.
-
-\section{Introduction}
-
-\import{method/}{sec_0_introduction.tex}
-
-\import{method/}{sec_1-soa.tex}
-
-\import{method/}{sec_2-actor_model.tex}
-
-\import{method/}{sec_3-microservice.tex}
-
-\import{method/}{sec_4-db_struct.tex}
-
-\import{method/}{sec_5-data_preprocess.tex}
-
-\import{method/}{sec_6-query.tex}
-
-\chapter{Results}
-\label{ch:results}
-
-\import{results/}{sec_1-test_plan.tex}
-
-\import{results/}{sec_2-work_load.tex}
-
-\import{results/}{sec_3-observations.tex}
-
-\import{results/}{sec_4-conclusion.tex}
-
-\chapter{Conclusions}
-\label{ch:conc}
-
-Discuss your results and system and conclude.
-
-\import{summary/}{sec_1-summary.tex}
-
-\import{summary/}{sec_2-future_work.tex}
-
-\appendix
-\chapter{First Appendix}
-Type out your first appendix here.
-\section{Basics}
-
-\chapter{First Appendix}
-Type out your second appendix here.
-
-\graphicspath{ {./images/} }
-\input{glossary.tex}
-\bibliographystyle{plain}
-\bibliography{mendeley}
-\end{document}

### 2020-02-09 introduction/sec_4-outline.tex
thesis - Move introduction into multiple files

--- 2019-12-01 thesis.tex
@@
-\documentclass[a4paper,oneside,12pt]{report}
-\usepackage{graphicx,mathptmx}
-\usepackage{geometry}
- \geometry{
- a4paper,
- %total={160mm,227mm},
- left=40mm,
- top=25mm,
- bottom=40mm, 
- right=25mm,
-}
-\renewcommand{\baselinestretch}{1.5}
-
-\usepackage{setspace}
-\usepackage{tabu}
-\usepackage[acronym]{glossaries}
-\makeglossaries
-\usepackage{import}
-\usepackage{listings}
-
-\begin{document}
-\begin{titlepage}
-    \begin{center}
-        \Large{
-        \textbf{WEATHER DATA INTEGRATION AND ASSIMILATION SYSTEM}}\\
-        \vspace{144pt}
-  \large      
-        %\vspace{1cm}
-      % by
-
-        %\vspace{1.0cm}
-
-        Gihan Chanuka Karunarathne\\
-        \vspace{24pt}
-       % \normalsize
-      178004U\\
-         \vspace{72pt}
-        %\normalsize
-        Degree of Master of Science\\
-
-        %\centering
-         %\includegraphics[width=0.4\textwidth]{0.Title_Page/uom.png}\\
-            %\vspace{0.8cm}
-         %\normalsize
-
-        %\vfill
-       \vspace{72pt}
-        \large
-        Department of Computer Science and Engineering\\
-        \vspace{24pt}
-        University of Moratuwa\\
-        Sri Lanka\\
-        \vspace{32pt}
-        April 2019
-
-    \end{center}
-\end{titlepage}
-
-\begin{titlepage}
-    \begin{center}
-       % \vspace*{1cm}
-        \Large{
-        \textbf{WEATHER DATA INTEGRATION AND ASSIMILATION SYSTEM}}\\
-        \vspace{144pt}
-  \large
-
-        Herath Mudiyanselage Gihan Chanuka Karunarathne\\
-        \vspace{24pt}
-       % \normalsize
-        178008U\\
-         \vspace{72pt}
-        \normalsize
-        Thesis submitted in partial fulfillment of the requirements for the degree Master of Science in Computer Science and Engineering\\
-
-        %\vfill
-       \vspace{72pt}
-        \large
-        Department of Computer Science and Engineering\\
-        \vspace{24pt}
-        University of Moratuwa\\
-        Sri Lanka\\
-        \vspace{32pt}
-        April 2019
-
-    \end{center}
-\end{titlepage}
-
-\pagenumbering{roman}
-
-\newgeometry{left=4cm,top=0.5cm,right=2.5cm}
-\chapter*{Declaration}
-\addcontentsline{toc}{chapter}{Declaration}
-
-I declare that this is my own work and this thesis does not
-incorporate without acknowledgement any material previously submitted for a
-Degree or Diploma in any other University or institute of higher learning and to
-the best of my knowledge and belief it does not contain any material previously
-published or written by another person except where the acknowledgement is
-made in the text.
-
-Also, I hereby grant to University of Moratuwa the non-exclusive right to
-reproduce and distribute my thesis/dissertation, in whole or in part in print,
-electronic or other medium. I retain the right to use this content in whole or part
-in future works (such as articles or books).
-
-\vspace{0.5in}
-\noindent
-\begin{tabu} to 1.0\textwidth { X[l] X[l] }
-    Signature: & Date:
-\end{tabu}
-
-\vspace{0.5in}
-\noindent
-The above candidate has carried out research for the Masters thesis under our supervision.
-
-\vspace{0.5in}
-\noindent
-\begin{tabu} to 1.0\textwidth { X[l] X[l] }
-    Name of the supervisor: & Dr. HMN Dilum Bandara\\ [1.5ex]
-    Signature of the supervisor: & Date:
-\end{tabu}
-
-\restoregeometry
-\normalsize
-
-\newgeometry{left=2.5cm,top=0.2cm,right=2cm}
-\addcontentsline{toc}{chapter}{Abstract} 
-{\setstretch{1.0} 
-\chapter*{Abstract}
-%\chapter*{\hspace{1cm} Abstract}
-
-To enhance the accuracy of weather predictions, it is necessary to provide reliable and detailed weather data as inputs to \acrfull{nwm}.
-These \acrshort{nwm} utilize weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images.
-Prior to feeding such diverse data (collected from different sources that belongs to different stakeholders) into respective \acrshort{nwm}, it is necessary to integrate data into a common format.
-Moreover, the data integration system’s response time need to be relatively low to accommodate critical situations like hurricanes, storms, and floods which require rapid and frequent execution of \acrshort{nwm}.
-
-Providing public to access weather data is also useful to enable many third-party applications and research.
-For example, logistic companies can use those data with their own model to plan and schedule their deliveries.
-Agricultural insurance companies can warn the farmers in advance, as well as calculate premiums based on anticipated weather patterns.
-
-While \acrfull{dias} and \acrfull{madis} are some of well-known Weather Data Integration and Assimilation (WDIA) systems, they are proprietary.
-Further Delft-FEWS is free to use, it is not open source.
-Hence, users of WDIA are forced to pay heavy licenses and are unable to extend the solutions to cater to their country-specific requirements.
-Therefore, the objective of this research is to develop a WDIA system for Sri Lanka, as well as make it open source, so that others could user and contribute to the solution.
-
-\vspace{4mm}
-
-\textbf{Keywords:} WDIAS, Weather, Timeseries, Distributed, Scalable
-
-}
-\restoregeometry
-\normalsize
-
-\addcontentsline{toc}{chapter}{Dedication} 
-\chapter*{Dedication}
-I dedicate my thesis work to my family, teachers and specially friends at \acrfull{curw}.
-A special feeling of gratitude to my loving parents, Nandawathi Dissanayake and H.M.K.
-Karunarathne whose words of encouragement and push for tenacity ring in my ears.
-My wife Jayani Kumarasinghe have never left my side and are very special.
-
-I also dedicate this thesis to my many friends at \acrshort{curw} who have supported and be with me during this period of time.
-Also special thanks to Dr.
-Dilum Bandara and Dr.
-Srikantha Herath for giving me this wonderful opportunity to explore this new domain.
-
-\addcontentsline{toc}{chapter}{Acknowledgements} 
-\chapter*{Acknowledgements}
-I wish to thank my evaluation panel members who were more than generous with their expertise and precious time.
-A special thanks to Dr.
-Dilum Bandara, my research supervisor for his countless hours of reflecting, reading, encouraging, and most of all patience throughout the entire process.
-Thank you Dr.
-Dilika Peris, and Dr.
-Indika Perera for agreeing to serve on my evaluation panel and Dr.
-Srikantha Herath for agreeing to serve as my external supervisor.
-
-I would like to acknowledge and thank Department of Computer Science and Engineering, University of Moratuwa, for allowing me to conduct my research and providing any assistance requested.
-Special thanks goes to both academic and non-academic staff of the department for their continued support.
-I also gratitude to the University of Moratuwa for the financial support as the research was supported in part by the Senate Research Grant of the University of Moratuwa under award number SRC/LT/2017/01.
-
-Finally, I would like to thank the teachers, evaluating panel and colleagues that assisted me with this project.
-Their excitement and willingness to provide feedback made the completion of this research an enjoyable experience.
-
-\tableofcontents
-
-\addcontentsline{toc}{chapter}{List of Figures} 
-\listoffigures
-
-\addcontentsline{toc}{chapter}{List of Tables} 
-\listoftables
-
-\addcontentsline{toc}{chapter}{List of Abbreviations} 
-\printglossary[type=\acronymtype, title=List of Abbreviations, toctitle=List of Abbreviations, nonumberlist]
-
-\pagenumbering{arabic}
-
-\chapter{Introduction}
-\label{ch:intro}
-To enhance the accuracy of weather predictions, it is necessary to provide reliable and detailed weather data as inputs to \acrfull{nwm}.
-These NWMs utilize weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images.
-Prior to feeding such diverse data (collected from different sources that belongs to different stakeholders) into respective NWMs, it is necessary to integrate data into a common format.
-Moreover, the data integration system’s response time need to be relatively low to accommodate critical situations like hurricanes, storms, and floods which require rapid and frequent execution of NWMs.
-
-\section{Motivation}
-Providing public to access weather data is also useful to enable many third-party applications and research.
-For example, logistic companies can use those data with their own model to plan and schedule their deliveries.
-Agricultural insurance companies can warn the farmers in advance, as well as calculate premiums based on anticipated weather patterns.
-
-While Data Integration and Analysis System (DIAS) and Meteorological Assimilation Data Ingest System (MADIS) are some of well-known Weather Data Integration and Assimilation (WDIA) systems, they are proprietary.
-Further Delft-FEWS is free to use, it is not open source.
-Hence, users of WDIA are forced to pay heavy licenses and are unable to extend the solutions to cater to their country-specific requirements.
-Therefore, the objective of this research is to develop a WDIA system for Sri Lanka, as well as make it open source, so that others could user and contribute to the solution.
-
-\section{Problem}
-\begin{itemize}
-    \item Handling spatio-temporal weather data is challenging
-    \item Need an extendable system to support weather models by efficiently storing and retrieving data
-    \item Goal is to design and develop a Weather Data Integration and Assimilation System that,
-    \begin{itemize}
-        \item Integrates weather data from different sources with quality control
-        \item Efficiently store spatio-temporal weather data with multiple dimensions
-        \item Support geographical and time-base queries
-    \end{itemize}
-\end{itemize}
-
-\section{Objectives}
-\begin{itemize}
-    \item To develop an open platform to integrate weather data from different sources in different formats
-    \item To design and develop a schema to store multidimensional weather timeseries data while optimizing,
-    \begin{itemize}
-        \item Disk space
-        \item Availability
-        \item Access time
-    \end{itemize}
-    \item To optimize schema to support data queries based on geography and time
-    \item To develop an API to share data while providing role-based access control
-\end{itemize}
-
 \section{Outline}
@@
 Performance analysis is presented in Chapter \ref{ch:results} while summary and future work are presented in Chapter \ref{ch:conc}.
-
-\chapter{Literature Review}
-\label{ch:literature}
-There are many of Weather forecasting, assimilation and dissemination systems developed by some of developed countries around the world as a result of trying to reduce the damage causing by natural disasters such as flood, storms, hurricanes and even for drought.
-Above kind of natural disasters heavily affected on the economy and the life conditions of the country, researchers have developed systems and many of these systems are using as proprietary systems.
-Other countries also using those systems and adopt with own version of system which effective for the specific weather condition in a particular country.
-Though out this chapter includes a Literature review about existing systems and their architecture approach and design with available resources.
-Most influenced systems for \acrshort{wdias} is \acrshort{fews} and \acrfull{lead} system.
-\acrshort{fews} is an open data handling platform, but it distributed as Closed Source software.
-\acrshort{lead} is following the Service Oriented Architecture for system architecture.
-Under each system we explore both system architecture, scalability and flexibility of the system.
-
-\import{lit/}{sec_1-fews.tex}
-
-\import{lit/}{sec_2-lead.tex}
-
-\section{Data Integration and Assimilation System}
-\label{se:dias}
-
-\section{Meteorological Assimilation Data Ingest System}
-\label{se:madis}
-
-\section{Summary}
-
-\chapter{Method}
-\label{ch:method}
-This chapter includes the design decision taken while implementing the \acrfull{wdias}, and how is the system got adapted from the systems analyzed in Chapter \ref{ch:literature}, then how is it trying to propose a better system with overcoming the issues.
-
-\section{Introduction}
-
-\import{method/}{sec_0_introduction.tex}
-
-\import{method/}{sec_1-soa.tex}
-
-\import{method/}{sec_2-actor_model.tex}
-
-\import{method/}{sec_3-microservice.tex}
-
-\import{method/}{sec_4-db_struct.tex}
-
-\import{method/}{sec_5-data_preprocess.tex}
-
-\import{method/}{sec_6-query.tex}
-
-\chapter{Results}
-\label{ch:results}
-
-\import{results/}{sec_1-test_plan.tex}
-
-\import{results/}{sec_2-work_load.tex}
-
-\import{results/}{sec_3-observations.tex}
-
-\import{results/}{sec_4-conclusion.tex}
-
-\chapter{Conclusions}
-\label{ch:conc}
-
-Discuss your results and system and conclude.
-
-\import{summary/}{sec_1-summary.tex}
-
-\import{summary/}{sec_2-future_work.tex}
-
-\appendix
-\chapter{First Appendix}
-Type out your first appendix here.
-\section{Basics}
-
-\chapter{First Appendix}
-Type out your second appendix here.
-
-\graphicspath{ {./images/} }
-\input{glossary.tex}
-\bibliographystyle{plain}
-\bibliography{mendeley}
-\end{document}
+\dbc{Expand a bit by adding at least 1 more sentence for each chapter.}

### 2020-02-09 thesis.tex
Paper - Updated the Structure of the paper
Move back to the Thesis
thesis - Move introduction into multiple files

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \tableofcontents
@@
 \dbc{There has to be a space/tab between abbreviation and its expansion.}
-\pagenumbering{arabic}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \chapter{Introduction}
 \label{ch:intro}
+\pagenumbering{arabic}
 
@@
 
-\section{Motivation}
-To enhance the accuracy of weather predictions, it is necessary to provide reliable and detailed weather data as inputs to \acrfull{nwm}.
-These NWMs utilize \db{multimodal} weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images.
-Prior to feeding such diverse data (collected from different sources that belongs to different stakeholders) into respective NWMs, it is necessary to integrate data into a common format.
-Moreover, the data integration system’s response time need to be relatively low to %accommodate critical situations
-\db{forecast and monitor time-sensitive weather events} like hurricanes, storms, and floods which require rapid and frequent execution of NWMs.
+\import{introduction/}{sec_1-motivation.tex}
 
-\dbc{We are not developing this platform only because we need to have a common data format or need to share with 3rd parties.
-These are secondary reasons.
-Highlight key reason why we need a weather data assimilation system.
-Key reason should be indicated in Abstract too.}
+\import{introduction/}{sec_2-problem_statement.tex}
 
-Providing public to access weather data is also useful to enable many third-party applications and research.
-For example, logistic companies could use those data with their models to plan and schedule their deliveries.
-Agricultural insurance companies can warn the farmers in advance, as well as calculate premiums based on anticipated weather patterns.
-\dbc{Highlight why we need a platform to provide such 3rd party access. Should be indicated in Abstract too.}
+\import{introduction/}{sec_3-objectives.tex}
 
-While Data Integration and Analysis System (DIAS) and Meteorological Assimilation Data Ingest System (MADIS) are some of well-known Weather Data Integration and Assimilation (WDIA) systems, they are proprietary.
-Further Delft-FEWS is free to use, it is not open source.
-Hence, users of WDIA are forced to pay heavy licenses and are unable to extend the solutions to cater to their country-specific requirements.
-Therefore, the objective of this research is to develop a WDIA system for Sri Lanka, as well as make it open source, so that others could user and contribute to the solution.
-\dbc{Saying something proprietary is not good reason to do research.
-You should highlight the context under which these solutions are developed and differences between CUrW and Sri Lanka in general.
-Also, give a bit more details than saying "to cater to their country-specific requirements".
-All key systems such as DIAS, MADIS, Delf, etc.
-need to be properly cited.}
+\import{introduction/}{sec_4-outline.tex}
 
-\section{Problem \db{Statement}}
-\dbc{Convert following bullets to a paragraph.
-Goals belongs to next section.
-What we need here is a set of sentences highlighting the needs that are used to derive goals.
-Then provide a single sentence problem statement.
-Look at some of the thesis I shared via OneNote and my website for example problem statements.}
-\begin{itemize}
-    \item Handling spatio-temporal weather data is challenging
-    \item Need an extendable system to support weather models by efficiently storing and retrieving data
-    \item Goal is to design and develop a Weather Data Integration and Assimilation System that,
-    \begin{itemize}
-        \item Integrates weather data from different sources with quality control
-        \item Efficiently store spatio-temporal weather data with multiple dimensions
-        \item Support geographical and time-base queries
-    \end{itemize}
-\end{itemize}
-
-\section{Objectives}
-\db{We address above problem statement by  achieving the following objectives:}
-\begin{itemize}
-    \item To develop an open platform to integrate weather data from different sources in different formats
-    \item To design and develop a schema to store multidimensional weather timeseries data while optimizing access time, availability, and storage.
-    \item To optimize schema to support data queries based on geography and time
-    \item To develop an API to share data while providing role-based access control
-\end{itemize}
-
-\section{Outline}
-The rest of the thesis is organized as follows.
-Literature review is presented in Chapter \ref{ch:literature}.
-Solution approach with the proposed system architectures and adaptation with problem occurred are presented in Chapter \ref{ch:method}.
-Performance analysis is presented in Chapter \ref{ch:results} while summary and future work are presented in Chapter \ref{ch:conc}.
-\dbc{Expand a bit by adding at least 1 more sentence for each chapter.}
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \chapter{Literature Review}
@@
 Under each system we explore both system architecture, scalability and flexibility of the system.
-\dbc{Complete above while refering to all major sections with chapter.}
+\dbc{Complete above while referring to all major sections with chapter.}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \chapter{\db{Research Methodology}}
@@
 \dbc{Add a couple of sentences to indicate what is covered in each Section. Do this in all chapters except in Chap 1.}
+
+\dbc{It should be References not Bibliography. This must follow IEEE style}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \chapter{Results}
@@
 
-\import{results/}{sec_4-conclusion.tex}
-\label{se:conclusion}
+\import{results/}{sec_4-discussion.tex}
+\label{se:discussion}
 
-\chapter{Conclusions}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\chapter{\db{Summary}}
 \label{ch:conc}
 
-\import{summary/}{sec_1-summary.tex}
+\import{summary/}{sec_1-conclusions.tex}
 
-\import{summary/}{sec_2-future_work.tex}
+\import{summary/}{sec_2-research_limitations.tex}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \appendix

### 2020-02-09 thesis.tex
Thesis - There has to be a space/tab between abbreviation and its expansion.

@@
 
+\newglossarystyle{custom-glossary-style}{%
+  \setglossarystyle{long}%
+  \renewenvironment{theglossary}%
+    {\begin{longtable}[l]{@{}p{\dimexpr 4cm-\tabcolsep}p{0.8\hsize}}}% <-- change the value here
+    {\end{longtable}}%
+}
+
 \addcontentsline{toc}{chapter}{List of Abbreviations} 
-\printglossary[type=\acronymtype, title=List of Abbreviations, toctitle=List of Abbreviations, nonumberlist]
-\dbc{There has to be a space/tab between abbreviation and its expansion.}
+\printglossary[style=custom-glossary-style, type=\acronymtype, title=List of Abbreviations, toctitle=List of Abbreviations, nonumberlist]
 

### 2020-02-09 lit/sec_1-fews.tex
Fix: Reference numbers should ideally not be listed with Figure names.

@@
     \includegraphics[width=0.7\textwidth]{fews/Schematic-structure-of-a-fl-ood-forecasting-system-showing-the-position-of-Delft-FEWS_W640.jpg}
-    \caption{Schematic structure of a flood forecasting system including \acrshort{fews} and links to other primary systems within the operational environment \cite{Werner2013TheSystem}.}
+    \caption[Schematic structure of a flood forecasting system including \acrshort{fews} and links to other primary systems within the operational environment]{Schematic structure of a flood forecasting system including \acrshort{fews} and links to other primary systems within the operational environment \cite{Werner2013TheSystem}.}
     \label{fi:fews_schematic}
@@
     \includegraphics[width=1.0\textwidth]{fews/Architecture-of-Delft-FEWS-showing-the-data-base-the-data-access-layers-and-examples-of_W640.jpg}\\
-    \caption{Architecture of \acrshort{fews} % showing the data base, the data access layers and examples of functional modules that communicate through the data access layer. 
-    \cite{Werner2013TheSystem} }
+    \caption[Architecture of \acrshort{fews}]{Architecture of \acrshort{fews} \cite{Werner2013TheSystem}.}
     \label{fi:fews_data_layer}
@@
     \includegraphics[width=0.8\textwidth]{fews/Linking-Delft-FEWS-with-external-models-The-fi-gure-shows-the-fl-ow-of-data-through-XML_W640.jpg}\\
-    \caption{ Linking \acrshort{fews} with external models.
-The figure shows the flow of data through XML and native model formats using solid lines, while executable commands are shown by dashed lines.
-\cite{Werner2013TheSystem} }
+    \caption[Linking \acrshort{fews} with external models]{Linking \acrshort{fews} with external models \cite{Werner2013TheSystem}.}
     \label{fi:fews_general_adapter}

### 2020-02-09 lit/sec_2-lead.tex
Fix: Reference numbers should ideally not be listed with Figure names.

@@
     \includegraphics[width=1.0\textwidth]{lead/LEAD-system-Fundamental-capabilities-familiar-to-meteorologists-are-shown-in-the-top_W640.jpg}\\
-    \caption{Layered architecture of LEAD.
-Fundamental capabilities familiar to meteorologists are shown in the top level, next are the tools for enacting these capabilities and the middleware that links everything together.
-System-generated products appear at the bottom \cite{Droegemeier2005Service-OrientedWeather}.
-}
+    \caption[Layered architecture of LEAD]{Layered architecture of LEAD \cite{Droegemeier2005Service-OrientedWeather}.}
     \label{fi:lead_system}
@@
     \includegraphics[width=1.0\textwidth]{lead/LEAD-system-framework-LEAD-is-composed-of-several-interacting-subsystems-with-the-LEAD_W640.jpg}\\
-    \caption{LEAD system framework %. LEAD is composed of several interacting subsystems, with the LEAD grid representing a stable, secure environment for development and testing. 
-    \cite{Droegemeier2005Service-OrientedWeather} .}
+    \caption[LEAD system framework]{LEAD system framework \cite{Droegemeier2005Service-OrientedWeather}.}
     \label{fi:lead_framework}
@@
     \includegraphics[width=1\textwidth]{lead/LEADs-service-oriented-architecture-A-wide-variety-of-services-and-resources-grouped_W640.jpg}\\
-    \caption{LEAD’s service-oriented architecture %.
-A wide variety of services and resources, grouped here according to general functionality, comprise the LEAD architecture, including services that cut across all aspects of the system.
-    \cite{Droegemeier2005Service-OrientedWeather}.}
+    \caption[LEAD’s service-oriented architecture]{LEAD’s service-oriented architecture \cite{Droegemeier2005Service-OrientedWeather}.}
     \label{fi:lead_soa}

### 2020-02-09 thesis.tex
Fix: Reference numbers should ideally not be listed with Figure names.
Updated the abstract

@@
 
-%To enhance the accuracy of weather predictions, it is necessary to provide reliable and detailed weather data as inputs to \acrfull{nwm}. These \acrshort{nwm} 
-\acrfull{nwm} utilize data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images. Prior to feeding such %diverse 
-multimodal data (collected from different sources that belong to different stakeholders) into respective \acrshort{nwm}, it is necessary to integrate data into a common format.
-Moreover, the data integration system’s response time need to be relatively low to %accommodate critical situations
-forecast and monitor time-sensitive weather events like hurricanes, storms, and flash floods that require rapid and frequent execution of \acrshort{nwm}.
-Providing public to access weather data is also useful to enable many third-party applications and research.
+\acrfull{nwm} utilize data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images.
+Prior to using such multimodal data into respective \acrshort{nwm}, it is necessary to transcode into a format that can be ingested by the \acrshort{nwm} modal.
+Moreover, the data integration system's response time needs to be relatively low to forecast and monitor time-sensitive weather events like hurricanes, storms, and flash floods that require rapid and frequent execution of \acrshort{nwm}.
+Later such weather data needs to be accessed by many third-party applications and research in order to make use of them.
+Thus the system should provide easy protocol to integrate with external systems, and should be capable of handling the workload.
 For example, logistic companies could use those data within their models to plan and schedule deliveries.
@@
 
-%While \acrfull{dias} and \acrfull{madis} are some of well-known Weather Data Integration and Assimilation (WDIA) systems, they are proprietary.
-Further Delft-FEWS is free to use, it is not open source.
-Hence, users of WDIA are forced to pay heavy licenses and are unable to extend the solutions to cater to their country-specific requirements.
-Therefore, the objective of this research is to develop a WDIA system for Sri Lanka, as well as make it open source, so that others could user and contribute to the solution.
+Even though there are many data integration systems, most of them are proprietary or close sourced.
+Which means for an island like Sri Lanka that having different kinds of weather seasons over the year than those software originated need to be highly customized.
+Throughout the operations and maintenance, it is required to get support with paying lots of charges, and difficult to debug into a closed source system without maintenance support from the vendors.
+And most of the software existing out there is not up to date with the latest technology concepts such as Cloud Computing.
+\acrfull{wdias} uses the modern architecture pattern such as microservice in order to achieve scalability, rather using monolithic architecture or client service architecture.
 
-\dbc{Add a set of sentences covering the why a new solution is needed, what sort of a solution we propose, how does the proposed solution work, why it's unique, and its performance.
-Abstract should not exceed 300 words.
-Typically background given in above para should not be more than 1/3 of abstract.}
+It provides a modular approach to integration of data from different sources and export into different formats, and inbuilt extension module system allow users to add new features.
+Since each module follows the stateless and failover microservice integrate with new Cloud Computing tools, the proposed solution comes with the scalability and high availability into large extend out of the box.
+The proposed solution is independent of the platform which most software out there is not and independent of Cloud Platform providers which give much flexibility for the users to decide the best cost effective way to host it.
+And the auto scaling feature allows users to run \acrshort{wdias} from 1 CPU node to nodes with a few hundred CPUs.
+Unlike most existing systems \acrshort{wdias} does not require a shutdown in order to update the system configuration, and it allows to add new features on the fly with rollover capabilities.
 
@@
 
-\textbf{Keywords:} WDIAS, Weather, Timeseries, Distributed, Scalable
-\dbc{Sort these. Add 2 more CS related terms. Remove WDIAS.}
+\textbf{Keywords:} Cloud Computing, Data Management system, Distributed,  Highly Available, Scalable, Timeseries, Weather
 }
@@
 \addcontentsline{toc}{chapter}{List of Figures}
-\dbc{Reference numbers should ideally not be listed with Figure names.}
 \listoffigures

### 2020-02-09 thesis.tex
It could have been much more easier to modify and compile thesis if each chapter was on a separate file. Page nos should be Roman numerals until Chap 1 beings.
Moved Other Lit Review Sys to diff file

@@
 
-\dbc{It could have been much more easier to modify and compile thesis if each chapter was on a separate file. Page nos should be Roman numerals until Chap 1 beings.}
-
-...
-\dbc{Start the para with a couple of sentences/para on weather prediction and NWMs.
-In another para mention about CUrW and its need to integrate and share data.
-Give citations of 1-2 good introductory sources on NWMs and another citation to CUrW website.}
-
 \import{introduction/}{sec_1-motivation.tex}
@@
 
-\section{Data Integration and Assimilation Systems}
-\label{se:dias}
-
-\section{Meteorological Assimilation Data Ingest System}
-\label{se:madis}
-
-\section{Summary}
+\import{lit/}{sec_3-other-systems.tex}
 

### 2020-02-09 introduction/sec_2-problem_and_objectives.tex
Merged problem and objectives

--- 2020-02-09 introduction/sec_2-problem_statement.tex
@@
 \end{itemize}
+
+\section{Objectives}
+\db{We address above problem statement by  achieving the following objectives:}
+\begin{itemize}
+    \item To develop an open platform to integrate weather data from different sources in different formats
+    \item To design and develop a schema to store multidimensional weather timeseries data while optimizing access time, availability, and storage.
+    \item To optimize schema to support data queries based on geography and time
+    \item To develop an API to share data while providing role-based access control
+\end{itemize}

### 2020-02-09 introduction/sec_2-problem_and_objectives.tex
Update problem statement

--- 2020-02-09 introduction/sec_2-problem_statement.tex
@@
 \section{Problem Statement}
-\dbc{Convert following bullets to a paragraph.
-Goals belongs to next section.
-What we need here is a set of sentences highlighting the needs that are used to derive goals.
-Then provide a single sentence problem statement.
-Look at some of the thesis I shared via OneNote and my website for example problem statements.}
+Handling spatio-temporal weather data is challenging.
+Need an extendable system to support weather models by efficiently storing and retrieving data.
+Therefore, in this context the problem can be state as;
+\emph{necessaty of a Data Integration System which is scalable, highly available and capable of 
+interact with different data formats including spatio-temporal bulk stream data, 
+store efficiently while optimizing the disk space,
+support geographical and time-base queries,
+third parties can access the data with easy integration, and
+able to easy modify and use based on the requirements.
+}
+
+\section{Objectives}
+We address above problem statement by achieving the following objectives:
 \begin{itemize}
-    \item Handling spatio-temporal weather data is challenging
-    \item Need an extendable system to support weather models by efficiently storing and retrieving data
-    \item Goal is to design and develop a Weather Data Integration and Assimilation System that,
-    \begin{itemize}
-        \item Integrates weather data from different sources with quality control
-        \item Efficiently store spatio-temporal weather data with multiple dimensions
-        \item Support geographical and time-base queries
+    \item To develop an open platform to integrate weather data from different sources in different formats
+    \item To design and develop a schema to store multidimensional weather timeseries data while optimizing access time, availability, and storage
+    \item To optimize schema to support data queries based on geography and time
+    \item To develop an API to share data
+    \item To use open source tools and provide the source publicly with appropriate liecense.
 \end{itemize}
-\end{itemize}

### 2020-02-09 introduction/sec_4-outline.tex
Updated outline

@@
 The rest of the thesis is organized as follows.
-Literature review is presented in Chapter \ref{ch:literature}.
+Literature review is presented in chapter \ref{ch:literature}, and discuss about the existing Weather Data Integration Systems such as \acrshort{lead}, \acrshort{few}, \acrshort{madis}, and \acrshort{dias} etc.
 Solution approach with the proposed system architectures and adaptation with problem occurred are presented in Chapter \ref{ch:method}.
-Performance analysis is presented in Chapter \ref{ch:results} while summary and future work are presented in Chapter \ref{ch:conc}.
-\dbc{Expand a bit by adding at least 1 more sentence for each chapter.}
+It provides more details about how the \acrshort{wdias} is design with following the microservice architecture, and the date preprocessing capabilities of the system.
+Performance analysis is presented in Chapter \ref{ch:results}, and there we discussed about experiment setup of the \acrshort{wdias} and the observations.
+Then analyze the observations with respect to performance metrics.
+At the last chapter \ref{ch:conc}, it concludes and summarize the work, and further discussed about the research limitations.

### 2020-02-09 introduction/sec_1-motivation.tex

@@
+Weather prediction can use to reduce the lost in natural disasters and in order to gain more advantage over the natural resources like water management.
+The weather predictions are performed via \acrfull{nwm} by providing different configurations and the current status of the environment such as temperature, rainfall, and wind direction etc.
+For weather prediction \acrfull{wrf} model is used for predicting the rain fall, temperature, and wind direction etc.
+Then using the real time observations, the correct model is selected and after removing the bias, extract the information and feed into the next models.
+There are lots of \acrshort{nwm} available there, but another example can be taken as FLO2D which can be used to predict the water level on the ground.
+For the corresponding model developed based on the geo data, giving the current status of water levels and forecasted rainfall, the model predict the forecasted water level.
+
+CUrW SL is a government ministry which is working on weather data forecasting for Sri Lanka in order to reduce the natural disaster effects in Sri Lanka.
+In order to do that, it is implementing its own system with the idea of long term maintainability rather depend on existing vendors.
+It collected real time weather data from weather stations and other government entities, and do the forecasting daily.
+Then the generated results are shared to the thrusted parties.
+One of the future goals of CUrW SL to open up to the public to share the data, and use of the processed data via their system for the betterment of the society.
+The institute is operating via the paid TAX of Sri Lankan, and its trying to improve the quality of the life and the economic losts which are effected on the country via sharing the data for external parties to use of them.
+
 \section{Motivation}
@@
 Prior to feeding such diverse data (collected from different sources that belongs to different stakeholders) into respective NWMs, it is necessary to integrate data into a common format.
-Moreover, the data integration system’s response time need to be relatively low to %accommodate critical situations
-\db{forecast and monitor time-sensitive weather events} like hurricanes, storms, and floods which require rapid and frequent execution of NWMs.
+Moreover, the data integration system’s response time need to be relatively low to forecast and monitor time-sensitive weather events like hurricanes, storms, and floods which require rapid and frequent execution of NWMs.
 
-\dbc{We are not developing this platform only because we need to have a common data format or need to share with 3rd parties.
-These are secondary reasons.
-Highlight key reason why we need a weather data assimilation system.
-Key reason should be indicated in Abstract too.}
-
-Providing public to access weather data is also useful to enable many third-party applications and research.
+Processed weather data needs to be accessed by many third-party applications and research in order to make use of them.
 For example, logistic companies could use those data with their models to plan and schedule their deliveries.
 Agricultural insurance companies can warn the farmers in advance, as well as calculate premiums based on anticipated weather patterns.
-\dbc{Highlight why we need a platform to provide such 3rd party access. Should be indicated in Abstract too.}
+Also farmers rely on weather forecasts to decide what work to do on any particular day.
+For example, drying hay is only feasible in dry weather.
+Furhter the aviation industry is especially sensitive to the weather, accurate weather forecasting is essential, since prior to takeoff on the conditions to expect en route and at their destination.
+Thus it is required a platform to provide such 3rd party access, and use the data or process those based on their applications.
 
@@
 Therefore, the objective of this research is to develop a WDIA system for Sri Lanka, as well as make it open source, so that others could user and contribute to the solution.
+
 \dbc{Saying something proprietary is not good reason to do research.
@@
 need to be properly cited.}
+
+Even though there are many data integration systems, most of them are proprietary or close sourced.
+Which means for an island like Sri Lanka that having different kinds of weather seasons over the year than those software originated need to be highly customized.
+Throughout the operations and maintenance, it is required to get support with paying lots of charges, and difficult to debug into a closed source system without maintenance support from the vendors.
+As an example, \acrshort{fews} does not support FLO2D model integration, and CUrW SL is using FLO2D for water level forecasting in the data flow.
+In such a cases, it required to get the support from the vendor in order to integrate and configure the system.
+And most of the software existing out there is not up to date with the latest technology concepts such as Cloud Computing.
+\acrfull{wdias} uses the modern architecture pattern such as microservice in order to achieve scalability, rather using monolithic architecture or client service architecture.
+Most existing systems required to shutdown in order to update the system configuration such as \acrshort{fews}, but a systems which is access by many third parties should be operate 99.9\% without any downtime and should allows to add new features on the fly with rollover capabilities.
+The proposed system should be independent of the platform.
+But most software out there is not, as example \acrshort{fews} can run on Windows and Linux.
+And should be independent underline infrastructure providers which give much flexibility for the users to decide the best cost effective way to host it.
+Given the above facts, there is a necessary for such a systems to be implemented.

### 2020-02-09 introduction/sec_3-outline.tex

--- 2019-12-01 thesis-backup.tex
@@
-\documentclass[a4paper,oneside,12pt]{report}
-\usepackage{graphicx,mathptmx}
-\usepackage{geometry}
- \geometry{
- a4paper,
- %total={160mm,227mm},
- left=40mm,
- top=25mm,
- bottom=40mm, 
- right=25mm,
-}
-\renewcommand{\baselinestretch}{1.5}
-
-\usepackage{setspace}
-\usepackage{tabu}
-\usepackage[acronym]{glossaries}
-\makeglossaries
-\usepackage{import}
-
-\begin{document}
-\begin{titlepage}
-    \begin{center}
-        \Large{
-        \textbf{WEATHER DATA INTEGRATION AND ASSIMILATION SYSTEM}}\\
-        \vspace{144pt}
-  \large      
-        %\vspace{1cm}
-      % by
-
-        %\vspace{1.0cm}
-
-        Gihan Chanuka Karunarathne\\
-        \vspace{24pt}
-       % \normalsize
-      178004U\\
-         \vspace{72pt}
-        %\normalsize
-        Degree of Master of Science\\
-
-        %\centering
-         %\includegraphics[width=0.4\textwidth]{0.Title_Page/uom.png}\\
-            %\vspace{0.8cm}
-         %\normalsize
-
-        %\vfill
-       \vspace{72pt}
-        \large
-        Department of Computer Science and Engineering\\
-        \vspace{24pt}
-        University of Moratuwa\\
-        Sri Lanka\\
-        \vspace{32pt}
-        April 2019
-
-    \end{center}
-\end{titlepage}
-
-\begin{titlepage}
-    \begin{center}
-       % \vspace*{1cm}
-        \Large{
-        \textbf{WEATHER DATA INTEGRATION AND ASSIMILATION SYSTEM}}\\
-        \vspace{144pt}
-  \large
-
-        Herath Mudiyanselage Gihan Chanuka Karunarathne\\
-        \vspace{24pt}
-       % \normalsize
-        178008U\\
-         \vspace{72pt}
-        \normalsize
-        Thesis submitted in partial fulfillment of the requirements for the degree Master of Science in Computer Science and Engineering\\
-
-        %\vfill
-       \vspace{72pt}
-        \large
-        Department of Computer Science and Engineering\\
-        \vspace{24pt}
-        University of Moratuwa\\
-        Sri Lanka\\
-        \vspace{32pt}
-        April 2019
-
-    \end{center}
-\end{titlepage}
-
-\pagenumbering{roman}
-
-\newgeometry{left=4cm,top=0.5cm,right=2.5cm}
-\chapter*{Declaration}
-\addcontentsline{toc}{chapter}{Declaration}
-
-I declare that this is my own work and this thesis does not
-incorporate without acknowledgement any material previously submitted for a
-Degree or Diploma in any other University or institute of higher learning and to
-the best of my knowledge and belief it does not contain any material previously
-published or written by another person except where the acknowledgement is
-made in the text.
-
-Also, I hereby grant to University of Moratuwa the non-exclusive right to
-reproduce and distribute my thesis/dissertation, in whole or in part in print,
-electronic or other medium. I retain the right to use this content in whole or part
-in future works (such as articles or books).
-
-\vspace{0.5in}
-\noindent
-\begin{tabu} to 1.0\textwidth { X[l] X[l] }
-    Signature: & Date:
-\end{tabu}
-
-\vspace{0.5in}
-\noindent
-The above candidate has carried out research for the Masters thesis under our supervision.
-
-\vspace{0.5in}
-\noindent
-\begin{tabu} to 1.0\textwidth { X[l] X[l] }
-    Name of the supervisor: & Dr. HMN Dilum Bandara\\ [1.5ex]
-    Signature of the supervisor: & Date:
-\end{tabu}
-
-\restoregeometry
-\normalsize
-
-\newgeometry{left=2.5cm,top=0.2cm,right=2cm}
-\addcontentsline{toc}{chapter}{Abstract} 
-{\setstretch{1.0} 
-\chapter*{Abstract}
-%\chapter*{\hspace{1cm} Abstract}
-
-To enhance the accuracy of weather predictions, it is necessary to provide reliable and detailed weather data as inputs to \acrfull{nwm}.
-These \acrshort{nwm} utilize weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images.
-Prior to feeding such diverse data (collected from different sources that belongs to different stakeholders) into respective \acrshort{nwm}, it is necessary to integrate data into a common format.
-Moreover, the data integration system’s response time need to be relatively low to accommodate critical situations like hurricanes, storms, and floods which require rapid and frequent execution of \acrshort{nwm}.
-
-Providing public to access weather data is also useful to enable many third-party applications and research.
-For example, logistic companies can use those data with their own model to plan and schedule their deliveries.
-Agricultural insurance companies can warn the farmers in advance, as well as calculate premiums based on anticipated weather patterns.
-
-While \acrfull{dias} and \acrfull{madis} are some of well-known Weather Data Integration and Assimilation (WDIA) systems, they are proprietary.
-Further Delft-FEWS is free to use, it is not open source.
-Hence, users of WDIA are forced to pay heavy licenses and are unable to extend the solutions to cater to their country-specific requirements.
-Therefore, the objective of this research is to develop a WDIA system for Sri Lanka, as well as make it open source, so that others could user and contribute to the solution.
-
-\vspace{4mm}
-
-\textbf{Keywords:} WDIAS, Weather, Timeseries, Distributed, Scalable
-
-}
-\restoregeometry
-\normalsize
-
-\addcontentsline{toc}{chapter}{Dedication} 
-\chapter*{Dedication}
-I dedicate my thesis work to my family, teachers and specially friends at \acrfull{curw}.
-A special feeling of gratitude to my loving parents, Nandawathi Dissanayake and H.M.K.
-Karunarathne whose words of encouragement and push for tenacity ring in my ears.
-My wife Jayani Kumarasinghe have never left my side and are very special.
-
-I also dedicate this thesis to my many friends at \acrshort{curw} who have supported and be with me during this period of time.
-Also special thanks to Dr.
-Dilum Bandara and Dr.
-Srikantha Herath for giving me this wonderful opportunity to explore this new domain.
-
-\addcontentsline{toc}{chapter}{Acknowledgements} 
-\chapter*{Acknowledgements}
-I wish to thank my evaluation panel members who were more than generous with their expertise and precious time.
-A special thanks to Dr.
-Dilum Bandara, my research supervisor for his countless hours of reflecting, reading, encouraging, and most of all patience throughout the entire process.
-Thank you Dr.
-Dilika Peris, and Dr.
-Indika Perera for agreeing to serve on my evaluation panel and Dr.
-Srikantha Herath for agreeing to serve as my external supervisor.
-
-I would like to acknowledge and thank Department of Computer Science and Engineering, University of Moratuwa, for allowing me to conduct my research and providing any assistance requested.
-Special thanks goes to both academic and non-academic staff of the department for their continued support.
-I also gratitude to the University of Moratuwa for the financial support as the research was supported in part by the Senate Research Grant of the University of Moratuwa under award number SRC/LT/2017/01.
-
-Finally, I would like to thank the teachers, evaluating panel and colleagues that assisted me with this project.
-Their excitement and willingness to provide feedback made the completion of this research an enjoyable experience.
-
-\tableofcontents
-
-\addcontentsline{toc}{chapter}{List of Figures} 
-\listoffigures
-
-\addcontentsline{toc}{chapter}{List of Tables} 
-\listoftables
-
-\addcontentsline{toc}{chapter}{List of Abbreviations} 
-\printglossary[type=\acronymtype, title=List of Abbreviations, toctitle=List of Abbreviations, nonumberlist]
-
-\pagenumbering{arabic}
-
-\chapter{Introduction}
-\label{ch:intro}
-To enhance the accuracy of weather predictions, it is necessary to provide reliable and detailed weather data as inputs to \acrfull{nwm}.
-These NWMs utilize weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images.
-Prior to feeding such diverse data (collected from different sources that belongs to different stakeholders) into respective NWMs, it is necessary to integrate data into a common format.
-Moreover, the data integration system’s response time need to be relatively low to accommodate critical situations like hurricanes, storms, and floods which require rapid and frequent execution of NWMs.
-
-\section{Motivation}
-Providing public to access weather data is also useful to enable many third-party applications and research.
-For example, logistic companies can use those data with their own model to plan and schedule their deliveries.
-Agricultural insurance companies can warn the farmers in advance, as well as calculate premiums based on anticipated weather patterns.
-
-While Data Integration and Analysis System (DIAS) and Meteorological Assimilation Data Ingest System (MADIS) are some of well-known Weather Data Integration and Assimilation (WDIA) systems, they are proprietary.
-Further Delft-FEWS is free to use, it is not open source.
-Hence, users of WDIA are forced to pay heavy licenses and are unable to extend the solutions to cater to their country-specific requirements.
-Therefore, the objective of this research is to develop a WDIA system for Sri Lanka, as well as make it open source, so that others could user and contribute to the solution.
-
-\section{Problem}
-\begin{itemize}
-    \item Handling spatio-temporal weather data is challenging
-    \item Need an extendable system to support weather models by efficiently storing and retrieving data
-    \item Goal is to design and develop a Weather Data Integration and Assimilation System that,
-    \begin{itemize}
-        \item Integrates weather data from different sources with quality control
-        \item Efficiently store spatio-temporal weather data with multiple dimensions
-        \item Support geographical and time-base queries
-    \end{itemize}
-\end{itemize}
-
-\section{Objectives}
-\begin{itemize}
-    \item To develop an open platform to integrate weather data from different sources in different formats
-    \item To design and develop a schema to store multidimensional weather timeseries data while optimizing,
-    \begin{itemize}
-        \item Disk space
-        \item Availability
-        \item Access time
-    \end{itemize}
-    \item To optimize schema to support data queries based on geography and time
-    \item To develop an API to share data while providing role-based access control
-\end{itemize}
-
 \section{Outline}
@@
 Performance analysis is presented in Chapter \ref{ch:results} while summary and future work are presented in Chapter \ref{ch:conc}.
-
-\chapter{Literature Review}
-\label{ch:literature}
-There are many of Weather forecasting, assimilation and dissemination systems developed by some of developed countries around the world as a result of trying to reduce the damage causing by natural disasters such as flood, storms, hurricanes and even for drought.
-Above kind of natural disasters heavily affected on the economy and the life conditions of the country, researchers have developed systems and many of these systems are using as proprietary systems.
-Other countries also using those systems and adopt with own version of system which effective for the specific weather condition in a particular country.
-Though out this chapter includes a Literature review about existing systems and their architecture approach and design with available resources.
-Most influenced systems for \acrshort{wdias} is \acrshort{fews} and \acrfull{lead} system.
-\acrshort{fews} is an open data handling platform, but it distributed as Closed Source software.
-\acrshort{lead} is following the Service Oriented Architecture for system architecture.
-Under each system we explore both system architecture, scalability and flexibility of the system.
-
-\section{The Delft-FEWS flow forecasting system}
- \acrshort{fews} is developed by Deltares in the Nethaland with targeted for use by operational forecasting agencies.
-The software is freely available to download and setup.
-Tutorials and User setup guide \cite{DeltaresPublicWikiDelft-FEWSGuide} are available with well documentations.
-For non-commercial users need to have the licence agreement to use the system.
-And get new system updates.
-However, investments in new developments in the system are normally paid for by its users.
-The code base of \acrshort{fews} is currently not fully open source.
-But configuration guides and generic adapter module integration code examples are available for the users.
-
-Most if the models are using model-centric approach such as inputs need to be in the format of specific to the model.
-Also the outputs produced by the model are specific to the model and hard to utilize by another systems (e.g.
-FLO2D).
-For the \acrshort{fews} is using much more modular approach, hence it is easy to integrate models into the \acrshort{fews} system.
-Thus \acrshort{fews} can be consider as an integration framework or a middle ware for the models.
-
-Forecasting processes are constructed as a combination of modelling steps and data transformation algorithms.
-These are then combined to provide required forecast capabilities.
-Flexibility is achieved through integrating new models and algorithms into the code base \cite{Werner2013TheSystem}.
-Delft-FEWS system contains no inherent hydrological modelling capabilities within its code base.
-Rather it is a framework which can use to integrate into the system and create work flows for forecasting.
-
-The key elements of a forecasting system are summarized by Haggett \cite{Haggett1998AnWales} as four main steps;
-\begin{enumerate}
-\item Detection
-\item Forecasting
-\item Dissemination and Warning
-\item Response
-\end{enumerate}
-Within these four steps, \acrshort{fews} focuses on the forecasting step.
-The primary objective of this step is to provide additional lead time through predictions of short term future hydro-meteorological conditions \cite{Werner2005FloodCatchments}.
-It is true that, with providing accurate predictions with greater lead time can reduce the level of destruction.
-In order to do the forecasting, the system should be capable of integrating real-time data from hydrological and meteorological observation networks, and the dissemination of prediction results through appropriate products to the warning process.
-
-In figure \ref{fi:fews_schematic} show a schematic view of the connection between the forecasting system to real time data acquisition systems and dissemination systems.
-The widely using concept is using meteorological forecast data to get precipitation and, then using hydrological and hydraulic model chain to predict the level affect on the ground.
-The hydrological and hydraulic model should be design based on the ground.
-Basically ground should be analyze geographically and divide into the catchments.
-Based on the affected catchment, it can be further divide into sub areas in order to reduce the complexity of the simulation task.
-Ideally the forecasting system should therefore be flexible to allow change to models and data, while keeping the way forecasters work with it as constant as possible.
-
-\begin{figure}[htp]
-    \centering
-    \includegraphics[width=0.7\textwidth]{images/fews/Schematic-structure-of-a-fl-ood-forecasting-system-showing-the-position-of-Delft-FEWS_W640.jpg}\\
-    \caption{Schematic structure of a flood forecasting system, showing the position of \acrshort{fews} and links to other primary systems within the operational environment.
-\cite{Werner2013TheSystem} }
-    \label{fi:fews_schematic}
-\end{figure}
-The foundation of \acrshort{fews} is data-centric, with a common data-model through which all components interact.
-All time series data (both scalar and gridded) are stored in this common data-model in a database.
-Modeling capabilities are then linked to the system through one of the interfaces provided to the data-model \cite{Werner2013TheSystem}.
-As mention in the paper, having a common data-model make easy to store data in an efficient way.
-Operations like reporting and sharing the data also make it easy for integrate models.
-But the problem with this approach is, handling the multiple data formats.
-\acrshort{fews} overcome this issue with introducing adapters for most of commonly used data formats.
-This is a good feature which enable users to easily import data into the system.
-But at the same time, it's adding additional complexity into the system.
-
-Time series data is additionally either scalar, vector, or gridded data, though all different types are uniformly stored as binary objects in a time series table.
-None of the functional components (including the linked models) have direct access to the times series table, which is accessible only through the data access module \cite{Werner2013TheSystem}.
-As it explained in the system interpretation, every time all the data access need to go through the data access module which causing to adding more cost in data access.
-Since it is storing the different data types as binary objects, there is a penalty in converting data into binary objects and vice a versa.
-Storing all the data in a time series table causing all the request come into a single data point.
-Even it gives the advantage of accessing all the data at one place.
-Since screaming big amount of data is causing a heavy load on the system, causing to slow down the performance on trying to use the system on large set of data.
-
-Given above drawback on storing the data in the system, within the \acrshort{fews} data model, time series are uniquely identified by their location and data type, as well as an id related to the source of the data (e.g.
-the external source or hydrological model of which the time series are a result) \cite{Werner2013TheSystem}.
-This gives an opportunity to index the data base on above key fields and store the data separately, in order to take the advantage of putting multiple data resources into the system.
-As an example, instead of storing the data at a single timeseries table, it is possible to separate and index the database based on source such as external source or hydrological model of which the time series are a result.
-Or separate by data type and store in multiple storage give the capability for the system to scale with factor of identical types that can be identified.
-Example of separation by data types of scalar, vector and gridded will increase the scaling factor by 3x.
-
-Data processing and manipulation is a required process in weather forecasting.
-Most of the data that is imported from external sources is not at the appropriate temporal and spatial scale to be applied as an input to a forecasting model, or to be used directly in product generation.
-As a consequence, generic data processing steps form the predominant effort in most applications of models in the forecast environment.
-Some examples include data validation, serial and spatial interpolation, aggregation and dis-aggregation, and merging data \cite{Werner2013TheSystem}.
-This a vital feature in a forecasting system, and affect on the quality and accuracy of the predicted data outputs.
-Because of the common data model concept in the \acrshort{fews}, data processing via these function is much effective.
-The system is self provided some of the generic functions for data processing, but for more complex algorithms can be developed as a new Java class coded to communicate with the application programming interface (API).
-It obvious that for additional feature integration, user should implement the new functional extensions via Java programming language.
-Users does not have the flexibility of develop with some other languages they are familiar with or use the support from another language.
-As an example, Python language is easy to use for beginners and many of data scientists are using this programming language for development and it has many data available libraries for data processing.
-But in the \acrshort{fews} users do not ave the capability to take the advantage of such existing things.
-
-\begin{figure}[htp]
-    \centering
-    \includegraphics[width=1.0\textwidth]{images/fews/Architecture-of-Delft-FEWS-showing-the-data-base-the-data-access-layers-and-examples-of_W640.jpg}\\
-    \caption{Architecture of \acrshort{fews} showing the data base, the data access layers and examples of functional modules that communicate through the data access layer.
-\cite{Werner2013TheSystem} }
-    \label{fi:fews_data_layer}
-\end{figure}
-Most of the library of functions provided work equally on scalar and gridded time series.
-As with all other modules this communicates with the database solely through the data access layer as shown in \ref{fi:fews_data_layer} \cite{Werner2013TheSystem}.
-As it shown in the figure, it is clearly showing that, the system is depends on single database and via the data access layer all the requests are coming to the database though a connection.
-It is possible to setup and connect to a enterprise level database with clustering and shading as a paid solution, in order to serve many requests as possible.
-But the design it self inherently suffer with the database bottleneck which effected on running a large set of timeseries or models.
-
-\begin{figure}[htp]
-    \centering
-    \includegraphics[width=0.8\textwidth]{images/fews/Linking-Delft-FEWS-with-external-models-The-fi-gure-shows-the-fl-ow-of-data-through-XML_W640.jpg}\\
-    \caption{ Linking \acrshort{fews} with external models.
-The figure shows the flow of data through XML and native model formats using solid lines, while executable commands are shown by dashed lines.
-\cite{Werner2013TheSystem} }
-    \label{fi:fews_general_adapter}
-\end{figure}
-On of the simple and most effective feature in the \acrshort{fews} is open approach to integration of models and data.
-This approaches the concept of the open modeling framework proposed by \cite{Kokkonen2003InterfacingXML}.
-It simply gives the flexibility to allow operators to integrate more models as well as variations of the same model and come up with new integration flows as much as possible.
-\acrshort{fews} generates the input data as a set of XML files to a defined location; an adapter developed specifically for the model in question transforms this to the required native format in a pre-processing step; \acrshort{fews} executes the model; and the adapter to that model then converts the native formatted results into XML formatted files in a post processing step.
-\acrshort{fews} subsequently imports the results into the database from the XML files (see Fig.
-\ref{fi:fews_general_adapter}) \cite{Werner2013TheSystem}.
-The process is simple and consistence through out all the model integration.
-The model execution is done by the \acrshort{fews} or the model adapter which is causing tide coupling into the execution process in the system.
-Users does not have the flexibility to run the models with different configurations such as running with parallel execution.
-That may be overcome by triggering a external process at the execution time, but it introducing more difficulty for handling after model executed successfully, preceding to the next step in the process.
-This part of the system feature is not focus on the \acrshort{wdias} and user has to come up with own flow or use existing scientific flow management system.
-But it is a concept that need to be discuss and understand properly in order to design a data integration and assimilation system.
-
-Exchanging data with the model is primarily through XML files.
-In some cases these XML files may become very large, which may lead to I/O bottlenecks and subsequent performance issues \cite{Werner2013TheSystem}.
-This issue is thoroughly discussed previous paragraphs and the authors of the \cite{Werner2013TheSystem} seems to be notice and accept it here.
-For overcome this issue they introduced the file-based exchange of data.
-This includes the use of binary-XML files, streaming files through memory, and the use of \acrshort{NetCDF}-CF files.
-But far as for users it seems to be adding more complexity and context in order to get higher performance via the system.
-
-If particular adapter for a model is not present in the list of \acrshort{fews} adapter, user has the flexibility to implement an adapter for it.
-The effort of developing an adapter for a model code not previously integrated with \acrshort{fews} will vary depending on the complexity of the model I/O formats \cite{Werner2013TheSystem}.
-If user wants to use existing adapter and need to configure something not supported via the existing adapter, it is hard to get done.
-Also there are some cases it is hard to develop an adapter or running alongside with the \acrshort{fews}.
-As an example FLO2D model is using for hydrologic modeling and the model is only support only on Windows based operating systems.
-If you setup the system on Linux base operating system and using Linux based models, it is hard for users to come up with a solution for integrating the FLO2D models.
-The final step and one of important feature is exporting the data from the system in useful manner. In the \acrshort{fews}, it is supporting three main forms of product generation.
-\begin{itemize}
-\item Generate web reports with graphs, tables as well as summary reports
-\item Export time series in a variety of formats
-\item External applications actively retrieve data from the system
-\end{itemize}
-The forecasting process is often a sequence of steps, starting with the import of data, a number of data processing and modeling steps, and culminating in the generation of products to be disseminated to the warning process.
-This is supported via the work flow process in the \acrshort{fews}.
-The scope of the \acrshort{wdias} is not focus on adding such a feature in the system, rather user have to use scientific work flow management system or come up with own version of work flow.
-
-When running sequential steps within a work flow in \acrshort{fews}, each step is run for the full time window required (e.g.
-the lead time of the forecast) before moving on to the next step.
-This precludes tightly coupling of models, even explicitly \cite{Werner2013TheSystem}.
-As it mentioned above, users can run multiple models parallel or run those sequentially as needed.
-
-\section{Linked Environments for Atmospheric Discovery}
-
-The reason behind developing \acrfull{lead} by US National Science Foundation (NSF)  is to addresses the fundamental research challenges needed to create an integrated, scalable framework for adaptive analyzing and predicting the atmosphere \cite{Droegemeier2005Service-OrientedWeather}.
-In order to predict and analysis weather models by researchers, it required many resources.
-Rather than each researcher is running and handling own computer resources to do the weather experiments, \acrshort{lead} is providing pool of resources, then the researchers can use this resource pool to run their experiment in shorter amounts of time and in higher scale.
-At the time, researchers are developing their experiment flow, they are not using the resources many, and other are using it at the same time.
-LEAD’s foundation is dynamic work flow orchestration and data management in a Web services framework \cite{Droegemeier2005Service-OrientedWeather}.
-
-The most relevant and important analysis for designing \acrshort{lead} is understanding and analyzing the \acrfull{lead} architecture of it.
-LEAD’s complex array of services, applications, interfaces, and local and remote computing, networking, and storage resources is assembled by users in work flows to study mesoscale weather as it evolves \cite{Droegemeier2005Service-OrientedWeather}.
-As it follows the \acrshort{soa}, everything is implemented as independent services.
-This enable \acrshort{lead} to scale each service as required, and update each service without affecting other services.
-New models which are required for implementing a new forecast flow also has to be implement as a service and then integrate into the system.
-
-In the \ref{fi:lead_system} shows the fundamental capabilities of the \acrshort{lead} system. 
-From the high-level view, \acrshort{lead} lets users query for and acquire information, simulate and predict weather by using numerical atmospheric models, assimilate data, analyze, mine, and visualize data and model output.
-
-\begin{figure}[htp]
-    \centering
-    \includegraphics[width=1.0\textwidth]{images/lead/LEAD-system-Fundamental-capabilities-familiar-to-meteorologists-are-shown-in-the-top_W640.jpg}\\
-    \caption{LEAD system.
-Fundamental capabilities familiar to meteorologists are shown in the top level, below which are the associated tools for enacting these capabilities and the middle-ware that links everything together.
-System-generated products appear at the bottom.
-\cite{Droegemeier2005Service-OrientedWeather} }
-    \label{fi:lead_system}
-\end{figure}
-
-The second level in \ref{fi:lead_system} contains the fundamental tools that help to link services together. This include following tools in brief \cite{Droegemeier2005Service-OrientedWeather};
-\begin{itemize}
-    \item a Web portal, the primary (though not exclusive) user entry point
-    \item the ARPS Data Assimilation System (ADAS), a sophisticated tool for data quality control and assimilation
-    \item myLEAD, a flexible metadata catalog service
-    \item \acrfull{wrf} a next-generation atmospheric prediction and simulation model
-    \item ADaM (Algorithm Development and Mining), a powerful suite of tools for mining observational data, assimilated data sets, and model output 
-    \item Integrated Data Viewer (IDV) 
-\end{itemize}
-
-\begin{figure}[htp]
-    \centering
-    \includegraphics[width=1.0\textwidth]{images/lead/LEAD-system-framework-LEAD-is-composed-of-several-interacting-subsystems-with-the-LEAD_W640.jpg}\\
-    \caption{ LEAD system framework.
-LEAD is composed of several interacting subsystems, with the LEAD grid representing a stable, secure environment for development and testing.
-\cite{Droegemeier2005Service-OrientedWeather} }
-    \label{fi:lead_framework}
-\end{figure}
-
-The Concept of the \acrshort{lead} is, the workflow orchestration for on-demand, real-time, dynamically adaptive systems, called as WOORDS.
-The system is doing the work flow orchestration as given in each procedure.
-Those procedural rules are define by researcher and feed into the system.
-The system is trying to perform the action immediate after the submission, and also it transmit the data, run the models and send back the put put with lower time delay as possible.
-According to the load and other requirement, the system will respond to those requirements automatically.
-
-Lead System is consist of following sub components, as shown in the \ref{fi:lead_soa}. As a brief summary of the subsystems is \cite{Droegemeier2005Service-OrientedWeather};
-\begin{itemize}
-\item User subsystem - comprises the LEAD portal and enable user can access services
-\item Data subsystem - handles data and metadata, any numerical model output produced by operational or experimental models, and user generated information.
-\item Tools subsystem - consists of all meteorological and IT tools
-\item Orchestration subsystem - provides the technologies that let users manage data flows and model execution streams, and create and mine output.
-It also provides linkages to other software and processes for continuous or on-demand applications.
-\end{itemize}
-
-\begin{figure}[htp]
-    \centering
-    \includegraphics[width=0.9\textwidth]{images/lead/LEADs-service-oriented-architecture-A-wide-variety-of-services-and-resources-grouped_W640.jpg}\\
-    \caption{LEAD’s service-oriented architecture.
-A wide variety of services and resources, grouped here according to general functionality, comprise the LEAD architecture, including services that cut across all aspects of the system.
-\cite{Droegemeier2005Service-OrientedWeather} }
-    \label{fi:lead_soa}
-\end{figure}
-
-The distributed computing systems in the LEAD grid represent a distributed test bed for developing, integrating, and testing LEAD’s components.
-
-\acrshort{soa}s are widely deployed in the commercial enterprise sector, and they form the foundation of many scientific “grid” technologies at the time of \acrshort{lead} design and developed.
-A variant of \acrshort{soa} is evolved later called as microservice architecture, and widely use in the industry nowadays.
-The \acrshort{lead} \acrshort{soa} has five distinct yet highly interconnected layers.
-
-The bottom layer represents raw computation, application, and data resources distributed throughout the LEAD grid and elsewhere.
-The next level up holds the Web services that provide access to raw services \cite{Droegemeier2005Service-OrientedWeather}.
-These two layers are working together, since \acrshort{lead} system resources are distributed over multiple locations and creating a pool of resources.
-The upper layer to the raw resources is abstracting the complexity of managing and accessing the resources, and provide a simplified access to the upper layer.
-In the Upper layers, it view as a unlimited resource pool for storing and handling data.
-
-The configuration and execution services in the middle layer, consisting of five elements, represent services invoked by LEAD workflows.
-These are some critical aspects on a weather data management system.
-Most of the services listed here are required for creating work flows for weather data forecasting.
-Thus it is important to review them and understand the basic needs of a weather data management system.
-
-\begin{itemize}
-\item The application-oriented configuration service that manages the deployment and execution of real applications such as the \acrshort{wrf} simulation model, ADAS, and the ADaM tools \cite{Droegemeier2005Service-OrientedWeather}.
-When creating weather work flow, it is required to change the behaviour of model by changing some of the configurations of the model or run a different version of the model.
-\item The application resource broker, which matches the appropriate host for execution to each application task, based on the execution’s time constraints \cite{}.
-This service is a critical part of the system, and responsible of using the resources of the system in optimized manner.
-When designing the weather data system, it is required to increase the capacity of the system automatically, and adopt into the system.
-\item The workflow engine service, which drives experimental workflow instances, invokes both the configuration service and application resource broker \cite{Droegemeier2005Service-OrientedWeather}.
-This is a part of work flow orchestration.
-\item The catalog services, represents the manner in which a user or application service discovers public-domain data products, or \acrshort{lead} services \cite{Droegemeier2005Service-OrientedWeather}.
-This is an important feature that should be available in a weather data system, and it is important to users to search for the availability of the data.
-Further wants to analyze the existing data for decision making.
-\item Users require a host of data services to support rich query, access, and transformation operations on data products.
-An important goal behind LEAD is access transparency—facilitating user queries across all available heterogeneous data sources without adverse affects from different formats and naming schemes \cite{Droegemeier2005Service-OrientedWeather}.
-Users need to have transformation services to read data in different format.
-The query service gives the capability to search via available data without any affect on the data formats.
-\end{itemize}
-The top of the \ref{fi:lead_soa}, shows the user interface to the system.
-This give the access to individual services.
-When user logs into the system, based on the authentication and authorization setting bind to the individual account, the portlets can access the services on behalf of the user.
-Look into further details is not relevant to developing the \acrshort{wdias}, since the focus is not about workflow orchestration.
-
-\acrshort{lead} is a more advanced system which can support for mesoscale weather prediction with the effort of multiple universities in the United State America with the effort of many of researchers and using many of computer resources.
-At the time it was building, it uses the \acrshort{soa} architecture as into its depth, and with the implementation each service can scale as needed and possible to enhance the service without interrupting other services.
-In the \acrshort{wdias} only focus on creating a framework that is extendable as system need more features as like \acrshort{lead} services.
-
-\section{Data Integration and Assimilation System}
-\label{se:dias}
-
-\section{Meteorological Assimilation Data Ingest System}
-\label{se:madis}
-
-\section{Summary}
-
-\chapter{Method}
-\label{ch:method}
-
-Reviews literature and place your work within the existing body of literature here. In chapter \ref{ch:intro} you introduced your thesis.
-
-\section{Introduction}
-
-\section{Service Oriented Architecture}
-
-\section{Microservice Architecture}
-
-\section{Hierarchical Database Structure}
-
-\section{Weather Data Prepossessing}
-
-\subsection{Interpolation}
-
-\subsection{Transformation}
-
-\subsection{Validation}
-
-\section{Query Timeseries}
-
-\chapter{Results}
-\label{ch:results}
-
-\section{Test Plan}
-
-\section{Work Load Creation}
-
-\section{Observations}
-
-\chapter{Conclusions}
-\label{ch:conc}
-
-Discuss your results and system and conclude.
-
-\section{Summary}
-
-\section{Future Work}
-
-\appendix
-\chapter{First Appendix}
-Type out your first appendix here.
-\section{Basics}
-
-\chapter{First Appendix}
-Type out your second appendix here.
-
-\graphicspath{ {./images/} }
-\input{glossary.tex}
-\bibliographystyle{plain}
-\bibliography{mendeley}
-\end{document}
+\dbc{Expand a bit by adding at least 1 more sentence for each chapter.}

### 2020-02-09 lit/sec_3-other-systems.tex

--- 2019-12-01 thesis-backup.tex
@@
-\documentclass[a4paper,oneside,12pt]{report}
-\usepackage{graphicx,mathptmx}
-\usepackage{geometry}
- \geometry{
- a4paper,
- %total={160mm,227mm},
- left=40mm,
- top=25mm,
- bottom=40mm, 
- right=25mm,
-}
-\renewcommand{\baselinestretch}{1.5}
-
-\usepackage{setspace}
-\usepackage{tabu}
-\usepackage[acronym]{glossaries}
-\makeglossaries
-\usepackage{import}
-
-\begin{document}
-\begin{titlepage}
-    \begin{center}
-        \Large{
-        \textbf{WEATHER DATA INTEGRATION AND ASSIMILATION SYSTEM}}\\
-        \vspace{144pt}
-  \large      
-        %\vspace{1cm}
-      % by
-
-        %\vspace{1.0cm}
-
-        Gihan Chanuka Karunarathne\\
-        \vspace{24pt}
-       % \normalsize
-      178004U\\
-         \vspace{72pt}
-        %\normalsize
-        Degree of Master of Science\\
-
-        %\centering
-         %\includegraphics[width=0.4\textwidth]{0.Title_Page/uom.png}\\
-            %\vspace{0.8cm}
-         %\normalsize
-
-        %\vfill
-       \vspace{72pt}
-        \large
-        Department of Computer Science and Engineering\\
-        \vspace{24pt}
-        University of Moratuwa\\
-        Sri Lanka\\
-        \vspace{32pt}
-        April 2019
-
-    \end{center}
-\end{titlepage}
-
-\begin{titlepage}
-    \begin{center}
-       % \vspace*{1cm}
-        \Large{
-        \textbf{WEATHER DATA INTEGRATION AND ASSIMILATION SYSTEM}}\\
-        \vspace{144pt}
-  \large
-
-        Herath Mudiyanselage Gihan Chanuka Karunarathne\\
-        \vspace{24pt}
-       % \normalsize
-        178008U\\
-         \vspace{72pt}
-        \normalsize
-        Thesis submitted in partial fulfillment of the requirements for the degree Master of Science in Computer Science and Engineering\\
-
-        %\vfill
-       \vspace{72pt}
-        \large
-        Department of Computer Science and Engineering\\
-        \vspace{24pt}
-        University of Moratuwa\\
-        Sri Lanka\\
-        \vspace{32pt}
-        April 2019
-
-    \end{center}
-\end{titlepage}
-
-\pagenumbering{roman}
-
-\newgeometry{left=4cm,top=0.5cm,right=2.5cm}
-\chapter*{Declaration}
-\addcontentsline{toc}{chapter}{Declaration}
-
-I declare that this is my own work and this thesis does not
-incorporate without acknowledgement any material previously submitted for a
-Degree or Diploma in any other University or institute of higher learning and to
-the best of my knowledge and belief it does not contain any material previously
-published or written by another person except where the acknowledgement is
-made in the text.
-
-Also, I hereby grant to University of Moratuwa the non-exclusive right to
-reproduce and distribute my thesis/dissertation, in whole or in part in print,
-electronic or other medium. I retain the right to use this content in whole or part
-in future works (such as articles or books).
-
-\vspace{0.5in}
-\noindent
-\begin{tabu} to 1.0\textwidth { X[l] X[l] }
-    Signature: & Date:
-\end{tabu}
-
-\vspace{0.5in}
-\noindent
-The above candidate has carried out research for the Masters thesis under our supervision.
-
-\vspace{0.5in}
-\noindent
-\begin{tabu} to 1.0\textwidth { X[l] X[l] }
-    Name of the supervisor: & Dr. HMN Dilum Bandara\\ [1.5ex]
-    Signature of the supervisor: & Date:
-\end{tabu}
-
-\restoregeometry
-\normalsize
-
-\newgeometry{left=2.5cm,top=0.2cm,right=2cm}
-\addcontentsline{toc}{chapter}{Abstract} 
-{\setstretch{1.0} 
-\chapter*{Abstract}
-%\chapter*{\hspace{1cm} Abstract}
-
-To enhance the accuracy of weather predictions, it is necessary to provide reliable and detailed weather data as inputs to \acrfull{nwm}.
-These \acrshort{nwm} utilize weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images.
-Prior to feeding such diverse data (collected from different sources that belongs to different stakeholders) into respective \acrshort{nwm}, it is necessary to integrate data into a common format.
-Moreover, the data integration system’s response time need to be relatively low to accommodate critical situations like hurricanes, storms, and floods which require rapid and frequent execution of \acrshort{nwm}.
-
-Providing public to access weather data is also useful to enable many third-party applications and research.
-For example, logistic companies can use those data with their own model to plan and schedule their deliveries.
-Agricultural insurance companies can warn the farmers in advance, as well as calculate premiums based on anticipated weather patterns.
-
-While \acrfull{dias} and \acrfull{madis} are some of well-known Weather Data Integration and Assimilation (WDIA) systems, they are proprietary.
-Further Delft-FEWS is free to use, it is not open source.
-Hence, users of WDIA are forced to pay heavy licenses and are unable to extend the solutions to cater to their country-specific requirements.
-Therefore, the objective of this research is to develop a WDIA system for Sri Lanka, as well as make it open source, so that others could user and contribute to the solution.
-
-\vspace{4mm}
-
-\textbf{Keywords:} WDIAS, Weather, Timeseries, Distributed, Scalable
-
-}
-\restoregeometry
-\normalsize
-
-\addcontentsline{toc}{chapter}{Dedication} 
-\chapter*{Dedication}
-I dedicate my thesis work to my family, teachers and specially friends at \acrfull{curw}.
-A special feeling of gratitude to my loving parents, Nandawathi Dissanayake and H.M.K.
-Karunarathne whose words of encouragement and push for tenacity ring in my ears.
-My wife Jayani Kumarasinghe have never left my side and are very special.
-
-I also dedicate this thesis to my many friends at \acrshort{curw} who have supported and be with me during this period of time.
-Also special thanks to Dr.
-Dilum Bandara and Dr.
-Srikantha Herath for giving me this wonderful opportunity to explore this new domain.
-
-\addcontentsline{toc}{chapter}{Acknowledgements} 
-\chapter*{Acknowledgements}
-I wish to thank my evaluation panel members who were more than generous with their expertise and precious time.
-A special thanks to Dr.
-Dilum Bandara, my research supervisor for his countless hours of reflecting, reading, encouraging, and most of all patience throughout the entire process.
-Thank you Dr.
-Dilika Peris, and Dr.
-Indika Perera for agreeing to serve on my evaluation panel and Dr.
-Srikantha Herath for agreeing to serve as my external supervisor.
-
-I would like to acknowledge and thank Department of Computer Science and Engineering, University of Moratuwa, for allowing me to conduct my research and providing any assistance requested.
-Special thanks goes to both academic and non-academic staff of the department for their continued support.
-I also gratitude to the University of Moratuwa for the financial support as the research was supported in part by the Senate Research Grant of the University of Moratuwa under award number SRC/LT/2017/01.
-
-Finally, I would like to thank the teachers, evaluating panel and colleagues that assisted me with this project.
-Their excitement and willingness to provide feedback made the completion of this research an enjoyable experience.
-
-\tableofcontents
-
-\addcontentsline{toc}{chapter}{List of Figures} 
-\listoffigures
-
-\addcontentsline{toc}{chapter}{List of Tables} 
-\listoftables
-
-\addcontentsline{toc}{chapter}{List of Abbreviations} 
-\printglossary[type=\acronymtype, title=List of Abbreviations, toctitle=List of Abbreviations, nonumberlist]
-
-\pagenumbering{arabic}
-
-\chapter{Introduction}
-\label{ch:intro}
-To enhance the accuracy of weather predictions, it is necessary to provide reliable and detailed weather data as inputs to \acrfull{nwm}.
-These NWMs utilize weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images.
-Prior to feeding such diverse data (collected from different sources that belongs to different stakeholders) into respective NWMs, it is necessary to integrate data into a common format.
-Moreover, the data integration system’s response time need to be relatively low to accommodate critical situations like hurricanes, storms, and floods which require rapid and frequent execution of NWMs.
-
-\section{Motivation}
-Providing public to access weather data is also useful to enable many third-party applications and research.
-For example, logistic companies can use those data with their own model to plan and schedule their deliveries.
-Agricultural insurance companies can warn the farmers in advance, as well as calculate premiums based on anticipated weather patterns.
-
-While Data Integration and Analysis System (DIAS) and Meteorological Assimilation Data Ingest System (MADIS) are some of well-known Weather Data Integration and Assimilation (WDIA) systems, they are proprietary.
-Further Delft-FEWS is free to use, it is not open source.
-Hence, users of WDIA are forced to pay heavy licenses and are unable to extend the solutions to cater to their country-specific requirements.
-Therefore, the objective of this research is to develop a WDIA system for Sri Lanka, as well as make it open source, so that others could user and contribute to the solution.
-
-\section{Problem}
-\begin{itemize}
-    \item Handling spatio-temporal weather data is challenging
-    \item Need an extendable system to support weather models by efficiently storing and retrieving data
-    \item Goal is to design and develop a Weather Data Integration and Assimilation System that,
-    \begin{itemize}
-        \item Integrates weather data from different sources with quality control
-        \item Efficiently store spatio-temporal weather data with multiple dimensions
-        \item Support geographical and time-base queries
-    \end{itemize}
-\end{itemize}
-
-\section{Objectives}
-\begin{itemize}
-    \item To develop an open platform to integrate weather data from different sources in different formats
-    \item To design and develop a schema to store multidimensional weather timeseries data while optimizing,
-    \begin{itemize}
-        \item Disk space
-        \item Availability
-        \item Access time
-    \end{itemize}
-    \item To optimize schema to support data queries based on geography and time
-    \item To develop an API to share data while providing role-based access control
-\end{itemize}
-
-\section{Outline}
-The rest of the thesis is organized as follows.
-Literature review is presented in Chapter \ref{ch:literature}.
-Solution approach with the proposed system architectures and adaptation with problem occurred are presented in Chapter \ref{ch:method}.
-Performance analysis is presented in Chapter \ref{ch:results} while summary and future work are presented in Chapter \ref{ch:conc}.
-
-\chapter{Literature Review}
-\label{ch:literature}
-There are many of Weather forecasting, assimilation and dissemination systems developed by some of developed countries around the world as a result of trying to reduce the damage causing by natural disasters such as flood, storms, hurricanes and even for drought.
-Above kind of natural disasters heavily affected on the economy and the life conditions of the country, researchers have developed systems and many of these systems are using as proprietary systems.
-Other countries also using those systems and adopt with own version of system which effective for the specific weather condition in a particular country.
-Though out this chapter includes a Literature review about existing systems and their architecture approach and design with available resources.
-Most influenced systems for \acrshort{wdias} is \acrshort{fews} and \acrfull{lead} system.
-\acrshort{fews} is an open data handling platform, but it distributed as Closed Source software.
-\acrshort{lead} is following the Service Oriented Architecture for system architecture.
-Under each system we explore both system architecture, scalability and flexibility of the system.
-
-\section{The Delft-FEWS flow forecasting system}
- \acrshort{fews} is developed by Deltares in the Nethaland with targeted for use by operational forecasting agencies.
-The software is freely available to download and setup.
-Tutorials and User setup guide \cite{DeltaresPublicWikiDelft-FEWSGuide} are available with well documentations.
-For non-commercial users need to have the licence agreement to use the system.
-And get new system updates.
-However, investments in new developments in the system are normally paid for by its users.
-The code base of \acrshort{fews} is currently not fully open source.
-But configuration guides and generic adapter module integration code examples are available for the users.
-
-Most if the models are using model-centric approach such as inputs need to be in the format of specific to the model.
-Also the outputs produced by the model are specific to the model and hard to utilize by another systems (e.g.
-FLO2D).
-For the \acrshort{fews} is using much more modular approach, hence it is easy to integrate models into the \acrshort{fews} system.
-Thus \acrshort{fews} can be consider as an integration framework or a middle ware for the models.
-
-Forecasting processes are constructed as a combination of modelling steps and data transformation algorithms.
-These are then combined to provide required forecast capabilities.
-Flexibility is achieved through integrating new models and algorithms into the code base \cite{Werner2013TheSystem}.
-Delft-FEWS system contains no inherent hydrological modelling capabilities within its code base.
-Rather it is a framework which can use to integrate into the system and create work flows for forecasting.
-
-The key elements of a forecasting system are summarized by Haggett \cite{Haggett1998AnWales} as four main steps;
-\begin{enumerate}
-\item Detection
-\item Forecasting
-\item Dissemination and Warning
-\item Response
-\end{enumerate}
-Within these four steps, \acrshort{fews} focuses on the forecasting step.
-The primary objective of this step is to provide additional lead time through predictions of short term future hydro-meteorological conditions \cite{Werner2005FloodCatchments}.
-It is true that, with providing accurate predictions with greater lead time can reduce the level of destruction.
-In order to do the forecasting, the system should be capable of integrating real-time data from hydrological and meteorological observation networks, and the dissemination of prediction results through appropriate products to the warning process.
-
-In figure \ref{fi:fews_schematic} show a schematic view of the connection between the forecasting system to real time data acquisition systems and dissemination systems.
-The widely using concept is using meteorological forecast data to get precipitation and, then using hydrological and hydraulic model chain to predict the level affect on the ground.
-The hydrological and hydraulic model should be design based on the ground.
-Basically ground should be analyze geographically and divide into the catchments.
-Based on the affected catchment, it can be further divide into sub areas in order to reduce the complexity of the simulation task.
-Ideally the forecasting system should therefore be flexible to allow change to models and data, while keeping the way forecasters work with it as constant as possible.
-
-\begin{figure}[htp]
-    \centering
-    \includegraphics[width=0.7\textwidth]{images/fews/Schematic-structure-of-a-fl-ood-forecasting-system-showing-the-position-of-Delft-FEWS_W640.jpg}\\
-    \caption{Schematic structure of a flood forecasting system, showing the position of \acrshort{fews} and links to other primary systems within the operational environment.
-\cite{Werner2013TheSystem} }
-    \label{fi:fews_schematic}
-\end{figure}
-The foundation of \acrshort{fews} is data-centric, with a common data-model through which all components interact.
-All time series data (both scalar and gridded) are stored in this common data-model in a database.
-Modeling capabilities are then linked to the system through one of the interfaces provided to the data-model \cite{Werner2013TheSystem}.
-As mention in the paper, having a common data-model make easy to store data in an efficient way.
-Operations like reporting and sharing the data also make it easy for integrate models.
-But the problem with this approach is, handling the multiple data formats.
-\acrshort{fews} overcome this issue with introducing adapters for most of commonly used data formats.
-This is a good feature which enable users to easily import data into the system.
-But at the same time, it's adding additional complexity into the system.
-
-Time series data is additionally either scalar, vector, or gridded data, though all different types are uniformly stored as binary objects in a time series table.
-None of the functional components (including the linked models) have direct access to the times series table, which is accessible only through the data access module \cite{Werner2013TheSystem}.
-As it explained in the system interpretation, every time all the data access need to go through the data access module which causing to adding more cost in data access.
-Since it is storing the different data types as binary objects, there is a penalty in converting data into binary objects and vice a versa.
-Storing all the data in a time series table causing all the request come into a single data point.
-Even it gives the advantage of accessing all the data at one place.
-Since screaming big amount of data is causing a heavy load on the system, causing to slow down the performance on trying to use the system on large set of data.
-
-Given above drawback on storing the data in the system, within the \acrshort{fews} data model, time series are uniquely identified by their location and data type, as well as an id related to the source of the data (e.g.
-the external source or hydrological model of which the time series are a result) \cite{Werner2013TheSystem}.
-This gives an opportunity to index the data base on above key fields and store the data separately, in order to take the advantage of putting multiple data resources into the system.
-As an example, instead of storing the data at a single timeseries table, it is possible to separate and index the database based on source such as external source or hydrological model of which the time series are a result.
-Or separate by data type and store in multiple storage give the capability for the system to scale with factor of identical types that can be identified.
-Example of separation by data types of scalar, vector and gridded will increase the scaling factor by 3x.
-
-Data processing and manipulation is a required process in weather forecasting.
-Most of the data that is imported from external sources is not at the appropriate temporal and spatial scale to be applied as an input to a forecasting model, or to be used directly in product generation.
-As a consequence, generic data processing steps form the predominant effort in most applications of models in the forecast environment.
-Some examples include data validation, serial and spatial interpolation, aggregation and dis-aggregation, and merging data \cite{Werner2013TheSystem}.
-This a vital feature in a forecasting system, and affect on the quality and accuracy of the predicted data outputs.
-Because of the common data model concept in the \acrshort{fews}, data processing via these function is much effective.
-The system is self provided some of the generic functions for data processing, but for more complex algorithms can be developed as a new Java class coded to communicate with the application programming interface (API).
-It obvious that for additional feature integration, user should implement the new functional extensions via Java programming language.
-Users does not have the flexibility of develop with some other languages they are familiar with or use the support from another language.
-As an example, Python language is easy to use for beginners and many of data scientists are using this programming language for development and it has many data available libraries for data processing.
-But in the \acrshort{fews} users do not ave the capability to take the advantage of such existing things.
-
-\begin{figure}[htp]
-    \centering
-    \includegraphics[width=1.0\textwidth]{images/fews/Architecture-of-Delft-FEWS-showing-the-data-base-the-data-access-layers-and-examples-of_W640.jpg}\\
-    \caption{Architecture of \acrshort{fews} showing the data base, the data access layers and examples of functional modules that communicate through the data access layer.
-\cite{Werner2013TheSystem} }
-    \label{fi:fews_data_layer}
-\end{figure}
-Most of the library of functions provided work equally on scalar and gridded time series.
-As with all other modules this communicates with the database solely through the data access layer as shown in \ref{fi:fews_data_layer} \cite{Werner2013TheSystem}.
-As it shown in the figure, it is clearly showing that, the system is depends on single database and via the data access layer all the requests are coming to the database though a connection.
-It is possible to setup and connect to a enterprise level database with clustering and shading as a paid solution, in order to serve many requests as possible.
-But the design it self inherently suffer with the database bottleneck which effected on running a large set of timeseries or models.
-
-\begin{figure}[htp]
-    \centering
-    \includegraphics[width=0.8\textwidth]{images/fews/Linking-Delft-FEWS-with-external-models-The-fi-gure-shows-the-fl-ow-of-data-through-XML_W640.jpg}\\
-    \caption{ Linking \acrshort{fews} with external models.
-The figure shows the flow of data through XML and native model formats using solid lines, while executable commands are shown by dashed lines.
-\cite{Werner2013TheSystem} }
-    \label{fi:fews_general_adapter}
-\end{figure}
-On of the simple and most effective feature in the \acrshort{fews} is open approach to integration of models and data.
-This approaches the concept of the open modeling framework proposed by \cite{Kokkonen2003InterfacingXML}.
-It simply gives the flexibility to allow operators to integrate more models as well as variations of the same model and come up with new integration flows as much as possible.
-\acrshort{fews} generates the input data as a set of XML files to a defined location; an adapter developed specifically for the model in question transforms this to the required native format in a pre-processing step; \acrshort{fews} executes the model; and the adapter to that model then converts the native formatted results into XML formatted files in a post processing step.
-\acrshort{fews} subsequently imports the results into the database from the XML files (see Fig.
-\ref{fi:fews_general_adapter}) \cite{Werner2013TheSystem}.
-The process is simple and consistence through out all the model integration.
-The model execution is done by the \acrshort{fews} or the model adapter which is causing tide coupling into the execution process in the system.
-Users does not have the flexibility to run the models with different configurations such as running with parallel execution.
-That may be overcome by triggering a external process at the execution time, but it introducing more difficulty for handling after model executed successfully, preceding to the next step in the process.
-This part of the system feature is not focus on the \acrshort{wdias} and user has to come up with own flow or use existing scientific flow management system.
-But it is a concept that need to be discuss and understand properly in order to design a data integration and assimilation system.
-
-Exchanging data with the model is primarily through XML files.
-In some cases these XML files may become very large, which may lead to I/O bottlenecks and subsequent performance issues \cite{Werner2013TheSystem}.
-This issue is thoroughly discussed previous paragraphs and the authors of the \cite{Werner2013TheSystem} seems to be notice and accept it here.
-For overcome this issue they introduced the file-based exchange of data.
-This includes the use of binary-XML files, streaming files through memory, and the use of \acrshort{NetCDF}-CF files.
-But far as for users it seems to be adding more complexity and context in order to get higher performance via the system.
-
-If particular adapter for a model is not present in the list of \acrshort{fews} adapter, user has the flexibility to implement an adapter for it.
-The effort of developing an adapter for a model code not previously integrated with \acrshort{fews} will vary depending on the complexity of the model I/O formats \cite{Werner2013TheSystem}.
-If user wants to use existing adapter and need to configure something not supported via the existing adapter, it is hard to get done.
-Also there are some cases it is hard to develop an adapter or running alongside with the \acrshort{fews}.
-As an example FLO2D model is using for hydrologic modeling and the model is only support only on Windows based operating systems.
-If you setup the system on Linux base operating system and using Linux based models, it is hard for users to come up with a solution for integrating the FLO2D models.
-The final step and one of important feature is exporting the data from the system in useful manner. In the \acrshort{fews}, it is supporting three main forms of product generation.
-\begin{itemize}
-\item Generate web reports with graphs, tables as well as summary reports
-\item Export time series in a variety of formats
-\item External applications actively retrieve data from the system
-\end{itemize}
-The forecasting process is often a sequence of steps, starting with the import of data, a number of data processing and modeling steps, and culminating in the generation of products to be disseminated to the warning process.
-This is supported via the work flow process in the \acrshort{fews}.
-The scope of the \acrshort{wdias} is not focus on adding such a feature in the system, rather user have to use scientific work flow management system or come up with own version of work flow.
-
-When running sequential steps within a work flow in \acrshort{fews}, each step is run for the full time window required (e.g.
-the lead time of the forecast) before moving on to the next step.
-This precludes tightly coupling of models, even explicitly \cite{Werner2013TheSystem}.
-As it mentioned above, users can run multiple models parallel or run those sequentially as needed.
-
-\section{Linked Environments for Atmospheric Discovery}
-
-The reason behind developing \acrfull{lead} by US National Science Foundation (NSF)  is to addresses the fundamental research challenges needed to create an integrated, scalable framework for adaptive analyzing and predicting the atmosphere \cite{Droegemeier2005Service-OrientedWeather}.
-In order to predict and analysis weather models by researchers, it required many resources.
-Rather than each researcher is running and handling own computer resources to do the weather experiments, \acrshort{lead} is providing pool of resources, then the researchers can use this resource pool to run their experiment in shorter amounts of time and in higher scale.
-At the time, researchers are developing their experiment flow, they are not using the resources many, and other are using it at the same time.
-LEAD’s foundation is dynamic work flow orchestration and data management in a Web services framework \cite{Droegemeier2005Service-OrientedWeather}.
-
-The most relevant and important analysis for designing \acrshort{lead} is understanding and analyzing the \acrfull{lead} architecture of it.
-LEAD’s complex array of services, applications, interfaces, and local and remote computing, networking, and storage resources is assembled by users in work flows to study mesoscale weather as it evolves \cite{Droegemeier2005Service-OrientedWeather}.
-As it follows the \acrshort{soa}, everything is implemented as independent services.
-This enable \acrshort{lead} to scale each service as required, and update each service without affecting other services.
-New models which are required for implementing a new forecast flow also has to be implement as a service and then integrate into the system.
-
-In the \ref{fi:lead_system} shows the fundamental capabilities of the \acrshort{lead} system. 
-From the high-level view, \acrshort{lead} lets users query for and acquire information, simulate and predict weather by using numerical atmospheric models, assimilate data, analyze, mine, and visualize data and model output.
-
-\begin{figure}[htp]
-    \centering
-    \includegraphics[width=1.0\textwidth]{images/lead/LEAD-system-Fundamental-capabilities-familiar-to-meteorologists-are-shown-in-the-top_W640.jpg}\\
-    \caption{LEAD system.
-Fundamental capabilities familiar to meteorologists are shown in the top level, below which are the associated tools for enacting these capabilities and the middle-ware that links everything together.
-System-generated products appear at the bottom.
-\cite{Droegemeier2005Service-OrientedWeather} }
-    \label{fi:lead_system}
-\end{figure}
-
-The second level in \ref{fi:lead_system} contains the fundamental tools that help to link services together. This include following tools in brief \cite{Droegemeier2005Service-OrientedWeather};
-\begin{itemize}
-    \item a Web portal, the primary (though not exclusive) user entry point
-    \item the ARPS Data Assimilation System (ADAS), a sophisticated tool for data quality control and assimilation
-    \item myLEAD, a flexible metadata catalog service
-    \item \acrfull{wrf} a next-generation atmospheric prediction and simulation model
-    \item ADaM (Algorithm Development and Mining), a powerful suite of tools for mining observational data, assimilated data sets, and model output 
-    \item Integrated Data Viewer (IDV) 
-\end{itemize}
-
-\begin{figure}[htp]
-    \centering
-    \includegraphics[width=1.0\textwidth]{images/lead/LEAD-system-framework-LEAD-is-composed-of-several-interacting-subsystems-with-the-LEAD_W640.jpg}\\
-    \caption{ LEAD system framework.
-LEAD is composed of several interacting subsystems, with the LEAD grid representing a stable, secure environment for development and testing.
-\cite{Droegemeier2005Service-OrientedWeather} }
-    \label{fi:lead_framework}
-\end{figure}
-
-The Concept of the \acrshort{lead} is, the workflow orchestration for on-demand, real-time, dynamically adaptive systems, called as WOORDS.
-The system is doing the work flow orchestration as given in each procedure.
-Those procedural rules are define by researcher and feed into the system.
-The system is trying to perform the action immediate after the submission, and also it transmit the data, run the models and send back the put put with lower time delay as possible.
-According to the load and other requirement, the system will respond to those requirements automatically.
-
-Lead System is consist of following sub components, as shown in the \ref{fi:lead_soa}. As a brief summary of the subsystems is \cite{Droegemeier2005Service-OrientedWeather};
-\begin{itemize}
-\item User subsystem - comprises the LEAD portal and enable user can access services
-\item Data subsystem - handles data and metadata, any numerical model output produced by operational or experimental models, and user generated information.
-\item Tools subsystem - consists of all meteorological and IT tools
-\item Orchestration subsystem - provides the technologies that let users manage data flows and model execution streams, and create and mine output.
-It also provides linkages to other software and processes for continuous or on-demand applications.
-\end{itemize}
-
-\begin{figure}[htp]
-    \centering
-    \includegraphics[width=0.9\textwidth]{images/lead/LEADs-service-oriented-architecture-A-wide-variety-of-services-and-resources-grouped_W640.jpg}\\
-    \caption{LEAD’s service-oriented architecture.
-A wide variety of services and resources, grouped here according to general functionality, comprise the LEAD architecture, including services that cut across all aspects of the system.
-\cite{Droegemeier2005Service-OrientedWeather} }
-    \label{fi:lead_soa}
-\end{figure}
-
-The distributed computing systems in the LEAD grid represent a distributed test bed for developing, integrating, and testing LEAD’s components.
-
-\acrshort{soa}s are widely deployed in the commercial enterprise sector, and they form the foundation of many scientific “grid” technologies at the time of \acrshort{lead} design and developed.
-A variant of \acrshort{soa} is evolved later called as microservice architecture, and widely use in the industry nowadays.
-The \acrshort{lead} \acrshort{soa} has five distinct yet highly interconnected layers.
-
-The bottom layer represents raw computation, application, and data resources distributed throughout the LEAD grid and elsewhere.
-The next level up holds the Web services that provide access to raw services \cite{Droegemeier2005Service-OrientedWeather}.
-These two layers are working together, since \acrshort{lead} system resources are distributed over multiple locations and creating a pool of resources.
-The upper layer to the raw resources is abstracting the complexity of managing and accessing the resources, and provide a simplified access to the upper layer.
-In the Upper layers, it view as a unlimited resource pool for storing and handling data.
-
-The configuration and execution services in the middle layer, consisting of five elements, represent services invoked by LEAD workflows.
-These are some critical aspects on a weather data management system.
-Most of the services listed here are required for creating work flows for weather data forecasting.
-Thus it is important to review them and understand the basic needs of a weather data management system.
-
-\begin{itemize}
-\item The application-oriented configuration service that manages the deployment and execution of real applications such as the \acrshort{wrf} simulation model, ADAS, and the ADaM tools \cite{Droegemeier2005Service-OrientedWeather}.
-When creating weather work flow, it is required to change the behaviour of model by changing some of the configurations of the model or run a different version of the model.
-\item The application resource broker, which matches the appropriate host for execution to each application task, based on the execution’s time constraints \cite{}.
-This service is a critical part of the system, and responsible of using the resources of the system in optimized manner.
-When designing the weather data system, it is required to increase the capacity of the system automatically, and adopt into the system.
-\item The workflow engine service, which drives experimental workflow instances, invokes both the configuration service and application resource broker \cite{Droegemeier2005Service-OrientedWeather}.
-This is a part of work flow orchestration.
-\item The catalog services, represents the manner in which a user or application service discovers public-domain data products, or \acrshort{lead} services \cite{Droegemeier2005Service-OrientedWeather}.
-This is an important feature that should be available in a weather data system, and it is important to users to search for the availability of the data.
-Further wants to analyze the existing data for decision making.
-\item Users require a host of data services to support rich query, access, and transformation operations on data products.
-An important goal behind LEAD is access transparency—facilitating user queries across all available heterogeneous data sources without adverse affects from different formats and naming schemes \cite{Droegemeier2005Service-OrientedWeather}.
-Users need to have transformation services to read data in different format.
-The query service gives the capability to search via available data without any affect on the data formats.
-\end{itemize}
-The top of the \ref{fi:lead_soa}, shows the user interface to the system.
-This give the access to individual services.
-When user logs into the system, based on the authentication and authorization setting bind to the individual account, the portlets can access the services on behalf of the user.
-Look into further details is not relevant to developing the \acrshort{wdias}, since the focus is not about workflow orchestration.
-
-\acrshort{lead} is a more advanced system which can support for mesoscale weather prediction with the effort of multiple universities in the United State America with the effort of many of researchers and using many of computer resources.
-At the time it was building, it uses the \acrshort{soa} architecture as into its depth, and with the implementation each service can scale as needed and possible to enhance the service without interrupting other services.
-In the \acrshort{wdias} only focus on creating a framework that is extendable as system need more features as like \acrshort{lead} services.
-
-\section{Data Integration and Assimilation System}
+\section{Data Integration and Assimilation Systems}
 \label{se:dias}
@@
 \section{Summary}
-
-\chapter{Method}
-\label{ch:method}
-
-Reviews literature and place your work within the existing body of literature here. In chapter \ref{ch:intro} you introduced your thesis.
-
-\section{Introduction}
-
-\section{Service Oriented Architecture}
-
-\section{Microservice Architecture}
-
-\section{Hierarchical Database Structure}
-
-\section{Weather Data Prepossessing}
-
-\subsection{Interpolation}
-
-\subsection{Transformation}
-
-\subsection{Validation}
-
-\section{Query Timeseries}
-
-\chapter{Results}
-\label{ch:results}
-
-\section{Test Plan}
-
-\section{Work Load Creation}
-
-\section{Observations}
-
-\chapter{Conclusions}
-\label{ch:conc}
-
-Discuss your results and system and conclude.
-
-\section{Summary}
-
-\section{Future Work}
-
-\appendix
-\chapter{First Appendix}
-Type out your first appendix here.
-\section{Basics}
-
-\chapter{First Appendix}
-Type out your second appendix here.
-
-\graphicspath{ {./images/} }
-\input{glossary.tex}
-\bibliographystyle{plain}
-\bibliography{mendeley}
-\end{document}

### 2020-02-09 introduction/sec_1-motivation.tex
Minor changes

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Motivation}
@@
 
-\dbc{Saying something proprietary is not good reason to do research.
-You should highlight the context under which these solutions are developed and differences between CUrW and Sri Lanka in general.
-Also, give a bit more details than saying "to cater to their country-specific requirements".
-All key systems such as DIAS, MADIS, Delf, etc.
-need to be properly cited.}
-
 Even though there are many data integration systems, most of them are proprietary or close sourced.

### 2020-02-09 introduction/sec_2-problem_and_objectives.tex
Minor changes

@@
 Therefore, in this context the problem can be state as;
-\emph{necessaty of a Data Integration System which is scalable, highly available and capable of 
-interact with different data formats including spatio-temporal bulk stream data, 
-store efficiently while optimizing the disk space,
-support geographical and time-base queries,
-third parties can access the data with easy integration, and
-able to easy modify and use based on the requirements.
-}
+
+\emph{necessaty of a Data Integration System which is scalable, highly available and capable of }
+\emph{interact with different data formats including spatio-temporal bulk stream data, }
+\emph{store efficiently while optimizing the disk space, }
+\emph{support geographical and time-base queries, }
+\emph{third parties can access the data with easy integration, and }
+\emph{able to easy modify and use based on the requirements.}
 

### 2020-02-09 introduction/sec_3-outline.tex
Change Bib to References

@@
 The rest of the thesis is organized as follows.
-Literature review is presented in Chapter \ref{ch:literature}.
+Literature review is presented in chapter \ref{ch:literature}, and discuss about the existing Weather Data Integration Systems such as \acrshort{lead}, \acrshort{fews}, \acrshort{madis}, and \acrshort{dias} etc.
 Solution approach with the proposed system architectures and adaptation with problem occurred are presented in Chapter \ref{ch:method}.
-Performance analysis is presented in Chapter \ref{ch:results} while summary and future work are presented in Chapter \ref{ch:conc}.
-\dbc{Expand a bit by adding at least 1 more sentence for each chapter.}
+It provides more details about how the \acrshort{wdias} is design with following the microservice architecture, and the date preprocessing capabilities of the system.
+Performance analysis is presented in Chapter \ref{ch:results}, and there we discussed about experiment setup of the \acrshort{wdias} and the observations.
+Then analyze the observations with respect to performance metrics.
+At the last chapter \ref{ch:conc}, it concludes and summarize the work, and further discussed about the research limitations.

### 2020-02-09 lit/sec_1-fews.tex
It's "e.g.,". Fix all places.

@@
 
-Given above drawback on storing the data in the system, within the \acrshort{fews} data model, time series are uniquely identified by their location and data type, as well as an id related to the source of the data (e.g.
-the external source or hydrological model of which the time series are a result) \cite{Werner2013TheSystem}.
+Given above drawback on storing the data in the system, within the \acrshort{fews} data model, time series are uniquely identified by their location and data type, as well as an id related to the source of the data (e.g.,the external source or hydrological model of which the time series are a result) \cite{Werner2013TheSystem}.
 This gives an opportunity to index the data base on above key fields and store the data separately, in order to take the advantage of putting multiple data resources into the system.
@@
 
-When running sequential steps within a work flow in \acrshort{fews}, each step is run for the full time window required (e.g.
-the lead time of the forecast) before moving on to the next step.
+When running sequential steps within a work flow in \acrshort{fews}, each step is run for the full time window required (e.g.,the lead time of the forecast) before moving on to the next step.
 This precludes tightly coupling of models, even explicitly \cite{Werner2013TheSystem}.
 As it mentioned above, users can run multiple models parallel or run those sequentially as needed.
-\dbc{It's "e.g.,". Fix all places. }

### 2020-02-09 results/sec_2-work_load.tex
Paper - Updated the Structure of the paper
It's "e.g.,". Fix all places.

@@
-\section{Work Load Creation}
+\section{Workload Creation}
+
+\dbc{Workload is a single word.}
+
 do I need to talk about system setup with EKS?
 add another section for performance tuning?
+\dbc{Sifficient details need to be given.}
 
@@
 System has negative feedback that makes it impossible to bury-out the service, so users wait for the responses before making new requests.
-    \item \emph{open system model} new requests arrival independently of completions, e.g. according to a stochastic process or fixed trace. System has no negative feedback.
+    \item \emph{open system model} new requests arrival independently of completions, e.g.,according to a stochastic process or fixed trace. System has no negative feedback.
 \end{itemize}
@@
 \end{figure}
+
+\dbc{Try to list names of test cases than having these black screenshots. Same for other places.}
 

### 2020-02-09 thesis-backup.tex
It's "e.g.,". Fix all places.

@@
 Most if the models are using model-centric approach such as inputs need to be in the format of specific to the model.
-Also the outputs produced by the model are specific to the model and hard to utilize by another systems (e.g.
-FLO2D).
+Also the outputs produced by the model are specific to the model and hard to utilize by another systems (e.g.,FLO2D).
 For the \acrshort{fews} is using much more modular approach, hence it is easy to integrate models into the \acrshort{fews} system.
@@
 
-When running sequential steps within a work flow in \acrshort{fews}, each step is run for the full time window required (e.g.
-the lead time of the forecast) before moving on to the next step.
+When running sequential steps within a work flow in \acrshort{fews}, each step is run for the full time window required (e.g.,the lead time of the forecast) before moving on to the next step.
 This precludes tightly coupling of models, even explicitly \cite{Werner2013TheSystem}.

### 2020-02-09 lit/sec_2-lead.tex
Check the use of apostrophe s. You need to use ' not ’.

@@
 At the time, researchers are developing their experiment flow, they are not using the resources many, and other are using it at the same time.
-LEAD’s foundation is dynamic work flow orchestration and data management in a Web services framework \cite{Droegemeier2005Service-OrientedWeather}.
+LEAD's foundation is dynamic work flow orchestration and data management in a Web services framework \cite{Droegemeier2005Service-OrientedWeather}.
 
@@
 New models which are required for implementing a new forecast flow also has to be implement as a service and then integrate into the system.
-\dbc{Check the use of apostrophe s. You need to use ' not ’.}
 
@@
     \includegraphics[width=1\textwidth]{lead/LEADs-service-oriented-architecture-A-wide-variety-of-services-and-resources-grouped_W640.jpg}\\
-    \caption[LEAD’s service-oriented architecture]{LEAD’s service-oriented architecture \cite{Droegemeier2005Service-OrientedWeather}.}
+    \caption[LEAD's service-oriented architecture]{LEAD's service-oriented architecture \cite{Droegemeier2005Service-OrientedWeather}.}
     \label{fi:lead_soa}
@@
 
-The distributed computing systems in the LEAD grid represent a distributed test bed for developing, integrating, and testing LEAD’s components.
+The distributed computing systems in the LEAD grid represent a distributed test bed for developing, integrating, and testing LEAD's components.
 \dbc{Try to avoid singe sentence paras.}

### 2020-02-09 thesis-backup.tex
Check the use of apostrophe s. You need to use ' not ’.

@@
 At the time, researchers are developing their experiment flow, they are not using the resources many, and other are using it at the same time.
-LEAD’s foundation is dynamic work flow orchestration and data management in a Web services framework \cite{Droegemeier2005Service-OrientedWeather}.
+LEAD's foundation is dynamic work flow orchestration and data management in a Web services framework \cite{Droegemeier2005Service-OrientedWeather}.
 
 The most relevant and important analysis for designing \acrshort{lead} is understanding and analyzing the \acrfull{lead} architecture of it.
-LEAD’s complex array of services, applications, interfaces, and local and remote computing, networking, and storage resources is assembled by users in work flows to study mesoscale weather as it evolves \cite{Droegemeier2005Service-OrientedWeather}.
+LEAD's complex array of services, applications, interfaces, and local and remote computing, networking, and storage resources is assembled by users in work flows to study mesoscale weather as it evolves \cite{Droegemeier2005Service-OrientedWeather}.
 As it follows the \acrshort{soa}, everything is implemented as independent services.
@@
     \includegraphics[width=0.9\textwidth]{images/lead/LEADs-service-oriented-architecture-A-wide-variety-of-services-and-resources-grouped_W640.jpg}\\
-    \caption{LEAD’s service-oriented architecture.
+    \caption{LEAD's service-oriented architecture.
 A wide variety of services and resources, grouped here according to general functionality, comprise the LEAD architecture, including services that cut across all aspects of the system.
@@
 
-The distributed computing systems in the LEAD grid represent a distributed test bed for developing, integrating, and testing LEAD’s components.
+The distributed computing systems in the LEAD grid represent a distributed test bed for developing, integrating, and testing LEAD's components.
 

### 2020-02-09 Paper.tex
Workload is a single word

@@
 
-\subsection{Test Plan and Work Load}
+\subsection{Test Plan and Workload}
 \begin{figure}[htbp]
@@
 During the \ref{subse:obs_test_plan_all_auto_15min} test run, the performance of the Grid data got better when compared to the \ref{subse:obs_test_plan_all_15min}.
-Which means by adding more resources to the \acrshort{wdias}, it can handle more work load on the system.
+Which means by adding more resources to the \acrshort{wdias}, it can handle more workload on the system.
 
@@
 \paragraph{Resource Utilization}
-Since \acrshort{wdias} using the \acrshort{k8s} as the container orchestration system, it allows to scale up and cool down the system as required based on the work load.
+Since \acrshort{wdias} using the \acrshort{k8s} as the container orchestration system, it allows to scale up and cool down the system as required based on the workload.
 This demonstrate on the test plan of \ref{subse:obs_test_plan_all_auto_15min}, and the system get scale up to the maximum at the peak time.
@@
 Services can configure with maximum number of pods in order to avoid over resource usage.
-When there is not much work load on the system, system cool down to less pods in order to save more resources.
+When there is not much workload on the system, system cool down to less pods in order to save more resources.
 When there is any issue with a pod, \acrshort{k8s} auto schedule another pod and remove the unhealthy pod.
@@
 During the test performance, the \acrshort{wdias} processed many requests with higher request size than the normal usage with lower rate of failures to process the requests, mainly with insert Grid data.
-If the usage of \acrshort{wdias} want to reduce the risk of unable to process data, then system can configure to run with redundant pods in order to handle spike of work loads.
+If the usage of \acrshort{wdias} want to reduce the risk of unable to process data, then system can configure to run with redundant pods in order to handle spike of workloads.
 Also while configure for the auto scaling, the \acrshort{k8s} can configure to maintain lower amount of CPU usage such as 50\% to 60\% rather 80\%.
@@
 The system is setup on the \acrfull{eks} as per the configurations of \ref{sub:test_sys_config}.
-During the performance test plans, the system were able to provide constant throughput by keeping the latency constant while increasing the work load. Which exhibit the scalability of the system.
-With the \acrshort{k8s} auto scaling, the \acrshort{wdias} were able to elastically adjust the number of pods according to the work load with the given configurations.
+During the performance test plans, the system were able to provide constant throughput by keeping the latency constant while increasing the workload. Which exhibit the scalability of the system.
+With the \acrshort{k8s} auto scaling, the \acrshort{wdias} were able to elastically adjust the number of pods according to the workload with the given configurations.
 

### 2020-02-09 method/sec_0_introduction.tex
Paper - update abstract
Workload is a single word

@@
+This chapter includes the design decision taken while implementing the \acrfull{wdias}, and how is the system got adapted from the systems analyzed in Chapter \ref{ch:literature}, then how is it trying to propose a better system with overcoming the issues.
+\dbc{Add a couple of sentences to indicate what is covered in each Section. Do this in all chapters except in Chap 1.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction}
+
+\dbc{What's this? Are you trying to give a high-kevel idea of the solution. If so, name it as high-level design.}
 

### 2020-02-09 results/sec_0-introduction.tex
Paper - Updated the Structure of the paper
Workload is a single word

@@
-\section{Introduction}
-The chapter \ref{ch:results} includes performance study of the \acrshort{wdias}. In the first section \ref{se:test_plan} describes the planned method of testing the system.
-In the next section \ref{se:work_load} describes the logic behind creating the work load to do the performance testing planned in \ref{se:test_plan}.
+%\section{Introduction}
+
+This chapter includes performance study of the \acrshort{wdias}. In the first section \ref{se:test_plan} describes the planned method of testing the system.
+In the next section \ref{se:work_load} describes the logic behind creating the workload to do the performance testing planned in \ref{se:test_plan}.
 Following section \ref{se:observations} includes the results observed while performance study. And summarised the observations in the next section \ref{se:conclusion}.
+
+\dbc{Use formal titles like experimental setup, workload, performance analysis.}

### 2020-02-09 results/sec_3-observations.tex
Workload is a single word

@@
 Another important fact is, after the test cases finished, the \acrshort{wdias} cool down the system via \acrshort{k8s} auto scaling and release the resources.
-This clearly shows the elasticity of the \acrshort{wdias} according to the work load.
+This clearly shows the elasticity of the \acrshort{wdias} according to the workload.
 
@@
 As the graph shows, 3 pods scheduled at the initial as per the configuration of the helm chart.
-While increasing the work load, new pods get spawn while keeping the constraint of 80\% of recommended CPU utilization.
+While increasing the workload, new pods get spawn while keeping the constraint of 80\% of recommended CPU utilization.
 After \acrshort{k8s} spawn 10 maximum pods, it stop spawning new pods.

### 2020-02-09 results/sec_4-discussion.tex
Move back to the Thesis
Workload is a single word

--- 2020-02-08 results/sec_4-conclusion.tex
@@
-\section{Conclusion}
+\section{Discussion}
+
+\dbc{It's odd to add a conclusion only for this chapter. If this is more of a discussion, name it as Discussion.}
 

### 2020-02-09 summary/sec_1-conclusions.tex
Workload is a single word

@@
 The system is setup on the \acrfull{eks} as per the configurations of \ref{sub:test_sys_config}.
-During the performance test plans, the system were able to provide constant throughput by keeping the latency constant while increasing the work load. Which exhibit the scalability of the system.
-With the \acrshort{k8s} auto scaling, the \acrshort{wdias} were able to elastically adjust the number of pods according to the work load with the given configurations.
+During the performance test plans, the system were able to provide constant throughput by keeping the latency constant while increasing the workload. Which exhibit the scalability of the system.
+With the \acrshort{k8s} auto scaling, the \acrshort{wdias} were able to elastically adjust the number of pods according to the workload with the given configurations.

### 2020-02-09 thesis.tex
Merged problem and objectives
Change Bib to References
Workload is a single word

@@
 \usepackage{tabulary}
+\usepackage{biblatex}
 
@@
 \newcommand{\dbc}[1]{\todo[author=Dilum, inline, color=blue!40]{#1}}
+
+\addbibresource{mendeley.bib}
 
@@
 
-\import{introduction/}{sec_2-problem_statement.tex}
+\import{introduction/}{sec_2-problem_and_objectives.tex}
 
-\import{introduction/}{sec_3-objectives.tex}
-
-\import{introduction/}{sec_4-outline.tex}
+\import{introduction/}{sec_3-outline.tex}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\chapter{\db{Research Methodology}}
+\chapter{Research Methodology}
 \label{ch:method}
-This chapter includes the design decision taken while implementing the \acrfull{wdias}, and how is the system got adapted from the systems analyzed in Chapter \ref{ch:literature}, then how is it trying to propose a better system with overcoming the issues.
-\dbc{Add a couple of sentences to indicate what is covered in each Section. Do this in all chapters except in Chap 1.}
-
-\dbc{It should be References not Bibliography. This must follow IEEE style}
 
@@
 \input{glossary.tex}
-\bibliographystyle{plain}
-\bibliography{mendeley}
+% \bibliographystyle{plain}
+% \addbibresource{mendeley.bib}
+\printbibliography[title={References}]
 \end{document}

### 2020-02-09 results/sec_2-work_load.tex
Workload is a single word
Cleanup TODOs

@@
 
-\dbc{Workload is a single word.}
-
-do I need to talk about system setup with EKS?
-add another section for performance tuning?
-\dbc{Sifficient details need to be given.}
-
-== Starts with how locations are created
 As explained in the \ref{ch:method}, timeseries has six primary attributes. In order to create a timeseries for performance testing, it needs data for each key attribute.
@@
 
-These locations https://developers.google.com/public-data/docs/canonical/countries\_csv are static though out the testing, and data added to the wdias-performance-test.
+These locations are taken from Google's Countries Public Dataset \cite{GoogleCountriesPublicDataset}, and consider static though out the testing, and data added to the wdias-performance-test.
 During the performance test, it creates 1000 timeseries and keep adding data against those timeseries.
@@
 
-== Then using those, create timeseries metadata (how it assure 10% of Grid data)
 In the \acrshort{jmeter} Best Practices, \say{If your test needs large amounts of data - particularly if it needs to be \emph{randomised} create the test data in a file that can be read with CSV Data set.
@@
 
-== Then how precipitation data for each time period created
 The system is capable of storing any numeric value up to 3 decimal points.
@@
 
-== Then how water level data for Grid time series created
 Almost similar to how was the precipitation data proceed, the water level are prepared for Grid data.
@@
 
-== Talk about the test test up - JMeter
-=== mentioned distributed setup test data collect issue and continue with one server coz it can support what is required
 \subsection{Experimental Setup}
-In order to create higher work load using the \acrshort{jmeter}, it has Distributed Testing feature.
+In order to create higher workload using the \acrshort{jmeter}, it has Distributed Testing feature.
 It uses the master slave approach and it allowed to handle all the test cases via single instance, rather handling separate instances.
@@
 
-== Talk about Stepping timer with concurrent thread group
 When implementing load test cases with \acrshort{jmeter}, it uses threads to simulate the users.
@@
 
-TODO
 \subsubsection{closed vs. open workload models} \cite{Haggett1998AnWales}
@@
 
-== Add screenshot of jmeter setup
 The test plans mentioned in \ref{se:test_plan} are implemented via the \acrshort{jmeter}. The \ref{fi:wdias_performance_test} shows the overall figure of all the test cases.
@@
 
-== talk about test plans can run
 As per the usage description of test-dev, it has the features of enable a test case, disable a test case, and run the test case while enabled.
@@
 
-- e.g., diagram indicating the nodes and their connectivity (load generator, target, storage, etc.), Then briefly describe the diagram.
+\dbc{- e.g., diagram indicating the nodes and their connectivity (load generator, target, storage, etc.), Then briefly describe the diagram.}
 

### 2020-02-09 results/sec_2-work_load.tex
Reduce the size of codes

@@
 
-These locations are taken from Google's Countries Public Dataset \cite{GoogleCountriesPublicDataset}, and consider static though out the testing, and data added to the wdias-performance-test.
+These locations are taken from Google's Countries Public Data set \cite{GoogleGoogleCounties}, and consider static though out the testing, and data added to the wdias-performance-test.
 During the performance test, it creates 1000 timeseries and keep adding data against those timeseries.
@@
 
-\subsubsection{closed vs. open workload models} \cite{Haggett1998AnWales}
+\subsubsection{closed vs. open workload models}
 \label{subse:closed_vs_open_workload}
 \begin{itemize}
-    \item \emph{closed system model} a new request is only triggered by the completion of a previous request, following by a think time.
+    \item \emph{closed system model} \cite{Haggett1998AnWales} a new request is only triggered by the completion of a previous request, following by a think time.
 System has negative feedback that makes it impossible to bury-out the service, so users wait for the responses before making new requests.
@@
 With using Throughput Shaping Timer, it only need to configure the \acrfull{rps}.
-When combine this \acrshort{jmeter} plugin with Concurrency Thread Group using Schedule Feedback Function to dynamically maintain thread count required to achieve target RPS \cite{Haggett1998AnWales} TODO.
+When combine this \acrshort{jmeter} plugin with Concurrency Thread Group using Schedule Feedback Function to dynamically maintain thread count required to achieve target RPS \cite{KarunarathneGihanWdias/wdias-performance-test:JMeter.}.
 
@@
 
-== talk about how test cases are enabled
 With the above \acrshort{jmeter} test case setup, it need to enable each test case separately and before running via the command line in the server.
-In order to do it in much efficient way, a scripting tool has implemented, and accessible with the code base \cite{Haggett1998AnWales} as \emph{test-dev} TODO.
+In order to do it in much efficient way, a scripting tool has implemented, and accessible with the code base \cite{KarunarathneWdias-performance-test/TEST_PLAN.md:Plan} as \emph{test-dev}.
 
@@
 As per the usage description of test-dev, it has the features of enable a test case, disable a test case, and run the test case while enabled.
-Another wrapper was implemented around the test-dev as \emph{test-plan.sh} which is also available with the code base \cite{Haggett1998AnWales} TODO.
+Another wrapper was implemented around the test-dev as \emph{test-plan.sh} which is also available with the code base \cite{KarunarathneWdias-performance-test/TEST_PLAN.md:Plan}.
 

### 2020-02-09 thesis.tex
Reduce the size of codes

@@
 \usepackage{listings}
+\usepackage{xcolor}
 \usepackage{dirtytalk}
@@
 \addbibresource{mendeley.bib}
+
+\definecolor{codegreen}{rgb}{0,0.6,0}
+\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
+
+\lstdefinestyle{code-style}{
+  backgroundcolor=\color{backcolour}, commentstyle=\color{codegreen},
+  basicstyle=\ttfamily\footnotesize,
+  breakatwhitespace=false,         
+  breaklines=true,                 
+  captionpos=b,                    
+  keepspaces=true,                 
+  numbers=left,                    
+  numbersep=5pt,
+  showspaces=false,
+  showstringspaces=false,
+  showtabs=false,                  
+  tabsize=2
+}
+
+\lstset{style=code-style}
 

### 2020-02-10 results/sec_3-observations.tex
Change table font size
Reduce table font size all
change to footnotesize table font size
Change Full Test

@@
 
-%Following \ref{subse:obs_test_plan_all_60min}, \ref{subse:obs_test_plan_all_30min}, \ref{subse:obs_test_plan_all_15min} and \ref{subse:obs_test_plan_all_auto_15min} sections
-\db{Sections \ref{subse:obs_test_plan_all_60min} to \ref{subse:obs_test_plan_all_auto_15min} discuss} the observations collected with performing the Full test plan (also known as All test plan) over 60 minutes (24 data points), 30 minutes (48 data points) and 15 minutes (96 data points) by variate the request size.
+\db{Sections \ref{subse:obs_test_plan_all_60min} to \ref{subse:obs_test_plan_all_auto_15min} discuss} the observations collected with performing the Load test plans over 60 minutes (24 data points), 30 minutes (48 data points) and 15 minutes (96 data points) by variate the request size.
 Then another performance test with enabling Auto Scaling as explained in \ref{subse:test_plan_metrics} for high resource utilized microservice.
 
-\subsection{Full Test with hourly data (24 Request Size)}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Load Testing with hourly data (24 Request Size)}
 \label{subse:obs_test_plan_all_60min}
-
-\dbc{"Full Test"is a not a good term}
 
@@
 
-\dbc{Fonts for tables should be 10pt.}
-
-\begin{table}[]
+\begin{table}[ht]
+\footnotesize
 \begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
@@
 
-\subsection{Full Test with 30min data (48 Request Size)}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Load Testing with 30min data (48 Request Size)}
 \label{subse:obs_test_plan_all_30min}
@@
 It performed round up to 311k of sample requests which is almost similar to \ref{subse:obs_test_plan_all_60min} processed samples.
-\begin{table}[]
+\begin{table}[ht]
+\footnotesize
 \begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
@@
 
-\subsection{Full Test with 15min data (96 Request Size)}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Load Testing with 15min data (96 Request Size)}
 \label{subse:obs_test_plan_all_15min}
@@
 It performed approximately 311k of sample requests which is almost similar to \ref{subse:obs_test_plan_all_30min} processed samples.
-\begin{table}[]
+\begin{table}[ht]
+\footnotesize
 \begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Full Load test with \acrfull{k8s} auto pod scaling}
@@
 
-\begin{table}[]
+\begin{table}[ht]
+\footnotesize
 \begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Query module load test}

### 2020-02-10 results/sec_4-discussion.tex
Change Full Test

@@
-\section{Discussion}
-
-\dbc{It's odd to add a conclusion only for this chapter. If this is more of a discussion, name it as Discussion.}
+\section{Performance Metrics Analysis}
 
@@
 
-\paragraph{Latency}
-The latency for each operation type kept constant over the whole test plan run time without any significant change.
+The \emph{Latency} for each operation type kept constant over the whole test plan run time without any significant change.
 When the request size increased from 24 data points to 96 data points, the latency increase throw out the whole test plan with a smaller number.
@@
 
-\paragraph{Throughput}
-While keeping the latency constant without significant change, the throughput of the \acrshort{wdias} kept constant while increasing the request size from 60min data (24 data points) to 15min data (96 data points) for all the data types such as Scalar, Vector and Grid.
+While keeping the latency constant without significant change, the \emph{throughput} of the \acrshort{wdias} kept constant while increasing the request size from 60min data (24 data points) to 15min data (96 data points) for all the data types such as Scalar, Vector and Grid.
 When number of active threads increased, the \acrshort{wdias} able to provide the same throughput with maintaining the latency stable.
@@
 
-\paragraph{Resource Utilization}
-Since \acrshort{wdias} using the \acrshort{k8s} as the container orchestration system, it allows to scale up and cool down the system as required based on the workload.
+When look into the \emph{resource utilization} of \acrshort{wdias}; since it is using the \acrshort{k8s} as the container orchestration system, it allows to scale up and cool down the system as required based on the workload.
 This demonstrate on the test plan of \ref{subse:obs_test_plan_all_auto_15min}, and the system get scale up to the maximum at the peak time.
@@
 
-\paragraph{Auto Scaling}
-The \acrshort{wdias} supports auto scaling by out of the box with \acrshort{k8s}.
+The \acrshort{wdias} supports \emph{auto scaling} by out of the box with \acrshort{k8s}.
 Services can configure with maximum number of pods in order to avoid over resource usage.
@@
 
-\paragraph{Risk of Unable to Process Data}
-During the test performance, the \acrshort{wdias} processed many requests with higher request size than the normal usage with lower rate of failures to process the requests, mainly with insert Grid data.
+\emph{Risk of unable to process data} during the test performance, the \acrshort{wdias} processed many requests with higher request size than the normal usage with lower rate of failures to process the requests, mainly with insert Grid data.
 If the usage of \acrshort{wdias} want to reduce the risk of unable to process data, then system can configure to run with redundant pods in order to handle spike of workloads.

### 2020-02-10 results/sec_2-workload.tex
Add test cases as list

--- 2020-02-09 results/sec_2-work_load.tex
@@
 
-The test plans mentioned in \ref{se:test_plan} are implemented via the \acrshort{jmeter}. The \ref{fi:wdias_performance_test} shows the overall figure of all the test cases.
+The test plans mentioned in \ref{se:test_plan} are implemented via the \acrshort{jmeter}. The following list shows the all the test cases using for the performance testing.
 
-\begin{figure}[htp]
-    \centering
-    \includegraphics[width=0.6\textwidth]{results/work_load/wdias_performance_test.png}
-    \caption{WDIAS Performance Test Cases}
-    \label{fi:wdias_performance_test}
-\end{figure}
-
-\dbc{Try to list names of test cases than having these black screenshots. Same for other places.}
+\begin{itemize}
+    \item User Defined Variables
+    \item Setup thread group
+    \item Create Timeseries thread group
+    \item Create Extensions thread group
+    \item Load Test Timeseries Concurrency thread group
+    \item Load Test Timeseries Concurrency thread group
+    \item Test Flow thread group
+\end{itemize}
 
@@
 
-\begin{table}[]
+\begin{table}[ht]
+\footnotesize
 \begin{tabular}{lccccl}

### 2020-02-10 results/sec_2-workload.tex
Removed all jmeter screenshots

@@
 In the first step of the plan consist of setting up the timeseries metadata.
-At the same time, it creates the timeseries entry in the \acrshort{wdias} system as well as shown in the \ref{fi:test_create_timeseries}.
+At the same time, it creates the timeseries entry in the \acrshort{wdias} system as well as shown in following list of test steps and configurations.
+
+\begin{itemize}
+    \item HTTP Request Defaults
+    \item HTTP Header Manager
+    \item Timeseries Metadata CSV
+    \item Create Timeseries
+    \item Get Timeseries
+    \item Query Timeseries
+\end{itemize}
+
 By creating the timeseries before help to reduce the overhead during the performance testing, and cause to more accurate \acrshort{rps} at the run time.
@@
 
-\begin{figure}[htp]
-    \centering
-    \includegraphics[width=0.6\textwidth]{results/work_load/test_create_timeseries.png}
-    \caption{WDIAS Performance Test - Create timeseries}
-    \label{fi:test_create_timeseries}
-\end{figure}
+The \ref{fi:test_all_cases} shows the test cases of other steps of Import, Extensions, Export and combination of All of them as per the detail steps in \ref{se:test_plan}.
+Following list shows the test steps of \acrshort{jmeter} while performing the load testing and the configurations.
 
-The \ref{fi:test_all_cases} shows the test cases of other steps of Import, Extensions, Export and combination of All of them as per the detail steps in \ref{se:test_plan}.
+\begin{itemize}
+    \item HTTP Request Defaults
+    \item HTTP Header Manager
+    \item Timeseries Metadata CSV
+    \item If Scalar or Vector
+        \begin{itemize}
+            \item Insert Timeseries
+        \end{itemize}
+    \item If a Grid
+    \begin{itemize}
+        \item Insert Grid Timeseries
+    \end{itemize}
+    \item wait for extensions timeseries
+    \item Interest Area preprocessor
+    \item Query If Scalar Or Vector
+    \item Retrieve If Scalar or Vector
+        \begin{itemize}
+            \item Retrieve Timeseries
+        \end{itemize}
+    \item Retrieve If a Grid
+    \begin{itemize}
+        \item Retrieve Grid Timeseries
+    \end{itemize}
+    \item increment date
+    \item throughput shaping timer prod
+\end{itemize}
 
-\begin{figure}[htp]
-    \centering
-    \includegraphics[width=0.6\textwidth]{results/work_load/test_all_cases.png}
-    \caption{WDIAS Performance Test - Import, Export, Extension and Query test cases}
-    \label{fi:test_all_cases}
-\end{figure}
+Following list of test steps shows intensively test the query timeseries features.
 
-Following test case \ref{fi:test_query_timeseries} for intensively test the query timeseries features.
-
-\begin{figure}[htp]
-    \centering
-    \includegraphics[width=0.6\textwidth]{results/work_load/test_query_timeseries.png}
-    \caption{WDIAS Performance Test - Query Timeseries}
-    \label{fi:test_query_timeseries}
-\end{figure}
+\begin{itemize}
+    \item HTTP Request Defaults
+    \item HTTP Header Manager
+    \item Locations CSV
+    \item Interest Area preprocessor
+    \begin{itemize}
+        \item /Location: * → Locations
+    	\item /Location: Area → Locations
+    	\item /Parameter: Location → Parameters
+    	\item /Parameter: Locations → Parameters
+    	\item /Timeseries: Location → Timeseries
+    	\item /Timeseries: Locations → Timeseries
+    	\item /Timeseries: Locations, Parameter → Timeseries
+    	\item /Timeseries: Area → Timeseries
+    	\item /Timeseries: Area, Parameter → Timeseries
+    	\item /Timeseries: *, Parameter → Timeseries
+    	\item /Timeseries: * → Timeseries
+	\end{itemize}
+\end{itemize}
 

### 2020-02-10 results/sec_1-test_plan.tex
Update the summary
Wrap Results chapter

@@
-\section{Test Plan}
+\section{Load Testing Plan}
+
 The system consists of three modules in functionality perspective of interacting with the \acrshort{wdias}.
@@
     \item Every 30 minutes (48 data points)
-    \item Every 5 minutes (288 data points) - One request is equivalent to a data points send by a weather station in 5 minutes interval for a whole day
+    \item Every 15 minutes (96 data points) - One request is equivalent to a data points send by a weather station in 15 minutes interval for a single day
 \end{itemize}
 
-\subsection{Test Plan Flow}
+\subsection{Load Testing Flow}
 \label{subse:test_plan_flow}
@@
     \item Test Setup to create timeseries in 1hr, 30min and 15min intervals and create metadata of the timeseries
-    \item Import Timeseries
-    \begin{itemize}
-        \item Plan for test run of 15 minutes with the request size of 15min data.(total 0.25 hours)
-        \item Have mixture of data: Scalar - 70\%(max 210 requests per second), Vector (Multi-Scalar) - 20\% (max 60 requests per second), Grid - 10\% (max 30 requests per second)
-    \end{itemize}
-    \item Extensions
-    \begin{itemize}
-        \item Create Extensions for /Aggregation\_Accumulative, /Interpolation Linear, /Validation Missing Values (OnChange and OnTime)
-        \item Plan for the 15 minutes of test run with the request size of 15min data. (total 0.25 hours)
-        \item Do with Import Timeseries with error data which will go through extensions.
-    \end{itemize}
-    \item Export Timeseries
-    \begin{itemize}
-        \item Plan for 15 minutes of test run with the request size of 15min data. (total 0.25 hours)
-        \item Have mixture of data: Scalar - 70\%, Vector (Multi-Scalar) - 20\%, Grid - 10\% (Use the Imported - Data before and verify against Extensions)
-    \end{itemize}
-    \item Import + Extension + Export + Timeseries Queries (All)
+    % \item Extensions
+    % \begin{itemize}
+    %     \item Create Extensions for /Aggregation\_Accumulative, /Interpolation Linear, /Validation Missing Values (OnChange and OnTime)
+    %     \item Plan for the 15 minutes of test run with the request size of 15min data. (total 0.25 hours)
+    %     \item Do with Import Timeseries with error data which will go through extensions.
+    % \end{itemize}
+    \item Import + Extension + Export + Timeseries Queries
     \begin{itemize}
@@
     \end{itemize}
+    \item Query
+    \begin{itemize}
+        \item Query Timeseries
+        \item Plan for the 5 minutes of test run. (total 1/12 hours)
+    \end{itemize}
 \end{enumerate}
 
-\subsection{Test Plan Observe Metrics}
+\subsection{Performance Metrics of Load Testing}
 \label{subse:test_plan_metrics}

### 2020-02-10 results/sec_2-workload.tex
Wrap Results chapter

@@
-\section{Workload Creation}
+\section{Workload}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Experimental Setup}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{closed vs. open workload models}
@@
 
-The \ref{fi:test_all_cases} shows the test cases of other steps of Import, Extensions, Export and combination of All of them as per the detail steps in \ref{se:test_plan}.
 Following list shows the test steps of \acrshort{jmeter} while performing the load testing and the configurations.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{System Configuration}
@@
 
-\subsubsection{Performance Tuning}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Performance Tuning}
+\label{se:performance_tuning}
 In order to get better performance using the available resources, it is possible to schedule each microservice into a predefined set of nodes. There are few ways to do in the \acrshort{k8s};

### 2020-02-10 results/sec_3-observations.tex
Add test cases as list
Wrap Results chapter

@@
 \section{Observations}
+
 According the \ref{se:test_plan} section, this section includes the observations after performing the test plans on the \acrshort{wdias} system setup and test plan test up which is explained in the \ref{se:work_load}.
 
-\db{Sections \ref{subse:obs_test_plan_all_60min} to \ref{subse:obs_test_plan_all_auto_15min} discuss} the observations collected with performing the Load test plans over 60 minutes (24 data points), 30 minutes (48 data points) and 15 minutes (96 data points) by variate the request size.
+Sections \ref{subse:obs_test_plan_all_60min} to \ref{subse:obs_test_plan_all_auto_15min} discuss the observations collected with performing the Load test plans over 60 minutes (24 data points), 30 minutes (48 data points) and 15 minutes (96 data points) by variate the request size.
 Then another performance test with enabling Auto Scaling as explained in \ref{subse:test_plan_metrics} for high resource utilized microservice.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Full Load test with \acrfull{k8s} auto pod scaling}
+\subsection{Load Testing with Auto Pod Scaling}
 \label{subse:obs_test_plan_all_auto_15min}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Query module load test}
+\subsection{Query Module Load Test}
 \label{subse:obs_test_plan_query_15min}

### 2020-02-10 results/sec_0-introduction.tex
Wrap Results chapter
Replaced work_load

@@
 This chapter includes performance study of the \acrshort{wdias}. In the first section \ref{se:test_plan} describes the planned method of testing the system.
-In the next section \ref{se:work_load} describes the logic behind creating the workload to do the performance testing planned in \ref{se:test_plan}.
-Following section \ref{se:observations} includes the results observed while performance study. And summarised the observations in the next section \ref{se:conclusion}.
-
-\dbc{Use formal titles like experimental setup, workload, performance analysis.}
+In the next section \ref{se:workload} describes the logic behind creating the workload to do the performance testing planned in \ref{se:test_plan}.
+Following section \ref{se:observations} includes the results observed while performance study. And summarised the observations in the next section \ref{se:discussion}.

### 2020-02-10 results/sec_3-observations.tex
Replaced work_load

@@
 
-According the \ref{se:test_plan} section, this section includes the observations after performing the test plans on the \acrshort{wdias} system setup and test plan test up which is explained in the \ref{se:work_load}.
+According the \ref{se:test_plan} section, this section includes the observations after performing the test plans on the \acrshort{wdias} system setup and test plan test up which is explained in the \ref{se:workload}.
 

### 2020-02-10 method/sec_3-microservice.tex
Capitalize only the proper nouns

@@
     \includegraphics[width=1\textwidth]{method/microservice/microservice_architecture-handle_on_async-v3.jpg}
-    \caption{WDIAS architecture to handle request asynchronously.}
+    \caption{\acrshort{wdias} architecture to handle request asynchronously.}
     \label{fi:wdias_micro_async}
@@
     \includegraphics[width=1\textwidth]{method/microservice/microservice_architecture-handle_on_demand-v3.jpg}
-    \caption{Weather Data Integration and Assimilation System Architecture for Server Requests on Demand}
+    \caption{\acrshort{wdias} architecture for server requests on demand}
     \label{fi:wdias_micro_on_demand}
@@
     \includegraphics[width=1\textwidth]{method/microservice/microservice_architecture-handle_on_async-v3.jpg}
-    \caption{Weather Data Integration and Assimilation System Architecture for Handle Request Asynchronously}
+    \caption{\acrshort{wdias} architecture for handle request asynchronously}
     \label{fi:wdias_micro_async}
@@
     \includegraphics[width=1\textwidth]{method/microservice/separation_microservices-v3.jpg}
-    \caption{Separation of WDIAS microservices}
+    \caption{Separation \acrshort{wdias} microservices}
     \label{fi:wdias_micro_separation}

### 2020-02-10 Paper.tex
Dont' use title case of figure captions. Capitalize only the proper nouns. Also, WDIAS can be shorten in figure captions.

@@
 \centerline{\includegraphics[width=0.5\textwidth]{method/misc/weather_data_system_components.jpg}}
-\caption{Components of a Weather Data System.}
+\caption{Components of a weather data system.}
 \label{fi:wdia_components}
@@
 \centerline{\includegraphics[width=0.5\textwidth]{method/microservice/k8s_architecture_v3.jpg}}
-\caption{\acrfull{k8s} Architecture.}
+\caption{\acrfull{k8s} architecture.}
 \label{fi:k8s_architecture}
@@
 \centerline{\includegraphics[width=0.5\textwidth]{method/microservice/microservice_architecture-handle_on_demand-v3.jpg}}
-\caption{microservice Architecture - Handle on Demand.}
+\caption{microservice architecture - handle on demand.}
 \label{fi:microservice_architecture_on_demand}
@@
 \centerline{\includegraphics[width=0.5\textwidth]{method/microservice/microservice_architecture-handle_on_async-v3.jpg}}
-\caption{microservice Architecture - Handle Asynchronously.}
+\caption{microservice architecture - handle asynchronously.}
 \label{fi:microservice_architecture_async}
@@
 \centerline{\includegraphics[width=0.4\textwidth]{method/microservice/hierarchical_database.jpg}}
-\caption{Hierarchical Database.}
+\caption{Hierarchical database.}
 \label{fi:hierarchical_database}
@@
 \centerline{\includegraphics[width=0.4\textwidth]{method/data_preprocess/summary_weather_data_preprocessing.jpg}}
-\caption{Generic Functional Approach to Weather data preprocessing.}
+\caption{Generic functional approach to weather data preprocessing.}
 \label{fi:summary_weather_data_preprocessing}
@@
 \centerline{\includegraphics[width=0.5\textwidth]{results/work_load/performance_study_v4.jpg}}
-\caption{Performance Study.}
+\caption{Performance study.}
 \label{fi:performance_Study}
@@
 \centerline{\includegraphics[width=0.5\textwidth]{results/obs/all_auto/obs_all_auto_15m_res_latencies_against_hits.png}}
-\caption{Performance Test 15min data enabled Auto Scaling - Response Latencies against Server Hits over the elapsed time.}
+\caption{Performance test 15min data enabled auto scaling - response latencies against server hits over the elapsed time.}
 \label{fi:test_obs_auto_all_15_min_latency_vs_hits}
@@
 \centerline{\includegraphics[width=0.5\textwidth]{results/obs/all_auto/obs_all_auto_15m_transaction_throughtput_vs_threads.png}}
-\caption{Performance Test 15min data enabled Auto Scaling - Transnational Throughput vs Number of Active Threads.}
+\caption{Performance test 15min data enabled auto scaling - transnational throughput vs number of active threads.}
 \label{fi:test_obs_auto_all_15_min_throughput_vs_threads}

### 2020-02-10 results/sec_3-observations.tex
Dont' use title case of figure captions. Capitalize only the proper nouns. Also, WDIAS can be shorten in figure captions.

@@
     \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_60m_response_times_vs_threads.png}
-    \caption{Performance All Test 60 minutes - Response Time vs Threads}
+    \caption{Load testing with hourly data - Response Time vs Threads}
     \label{fi:test_obs_all_60m_response_vs_threads}
@@
     \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_60m_res_latencies_against_hits.png}
-    \caption{Performance All Test 60 minutes - Latency against server hits}
+    \caption{Load testing with hourly data - Latency against server hits}
     \label{fi:test_obs_all_60m_latency}
@@
     \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_30m_response_times_vs_threads.png}
-    \caption{Performance All Test 30 minutes - Response Time vs Threads}
+    \caption{Load testing with 30 minutes data - Response Time vs Threads}
     \label{fi:test_obs_all_30m_response_vs_threads}
@@
     \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_30m_res_latencies_against_hits.png}
-    \caption{Performance All Test 30 minutes - Latency against server hits}
+    \caption{Load testing with 30 minutes data - Latency against server hits}
     \label{fi:test_obs_all_30m_latency}
@@
     \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_15m_response_times_vs_threads.png}
-    \caption{Performance Test - Response Time vs Active Threads}
+    \caption{Load testing with 15 minutes data - Response Time vs Active Threads}
     \label{fi:test_obs_all_15m_response_vs_threads}
@@
     \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_15m_res_latencies_against_hits.png}
-    \caption{Performance Test - Latency against server hits}
+    \caption{Load testing with 15 minutes data - Latency against server hits}
     \label{fi:test_obs_all_15m_latency}
@@
     \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_15m_transaction_throughtput_vs_threads.png}
-    \caption{Performance Test - Transaction Throughput vs Threads}
+    \caption{Load testing with 15 minutes data - Transaction Throughput vs Threads}
     \label{fi:test_obs_all_15m_throughtput}
@@
     \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_15m_response_times_percentiles.png}
-    \caption{Performance Test - Response times Percentiles}
+    \caption{Load testing with 15 minutes data - Response times Percentiles}
     \label{fi:test_obs_all_15m_latency_percentile}
@@
     \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_transaction_throughtput_vs_threads.png}
-    \caption{Performance Import Test 15 minutes data while enabled \acrshort{k8s} Auto Scaling - Latency against server hits}
+    \caption{Load testing with 15 minutes data with enabled auto scaling - Latency against server hits}
     \label{fi:test_obs_all_auto_15m_latency}
@@
     \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_transaction_throughtput_vs_threads.png}
-    \caption{Performance Import Test 15 minutes data while enabled \acrshort{k8s} Auto Scaling - Transaction Throughput vs Threads}
+    \caption{Load testing with 15 minutes data with enabled auto scaling - Transaction Throughput vs Threads}
     \label{fi:test_obs_all_auto_15m_throughtput}
@@
     \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_import_export_res.png}
-    \caption{Performance All Test 15min data - Auto Scaling Resource Usage of Import and Export Modules }
+    \caption{Load testing with auto scaling resource usage of import and export modules.}
     \label{fi:obs_all_auto_15m_import_export_res}
@@
     \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_import_grid_pod.png}
-    \caption{Performance All Test 15min Interval - Auto Scaling Import ASCII Grid Number of Pods Over Time }
+    \caption{Load testing with auto scaling import ascii grid number of pods over time.}
     \label{fi:obs_all_auto_15m_import_grid_pod}
@@
     \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_adapter_dbs_res.png}
-    \caption{Performance All Test 15min Interval - Auto Scaling Resource Usage of Database Adapters }
+    \caption{Load testing with auto scaling resource usage of database adapters.}
     \label{fi:obs_all_auto_15m_adapter_dbs_res}
@@
     \includegraphics[width=0.8\textwidth]{results/obs/query/obs_query_5m_latency_over_time.png}
-    \caption{Performance Query Test over 5 minutes - Response Latency over Time}
+    \caption{Load testing query test over 5 minutes - Response Latency over Time}
     \label{fi:test_obs_query_5m_response_latency}
@@
     \includegraphics[width=0.8\textwidth]{results/obs/query/obs_query_5m_response_times_vs_threads.png}
-    \caption{Performance Query Test over 5 minutes - Response Latency Times vs Threads}
+    \caption{Load testing query test over 5 minutes - Response Latency Times vs Threads}
     \label{fi:test_obs_query_5m_response_times_vs_threads}

### 2020-02-10 method/sec_4-db_struct.tex
Dont' use title case of figure captions. Capitalize only the proper nouns. Also, WDIAS can be shorten in figure captions.
Removed commercial database names

--- 2020-02-08 method/sec_4-db_struct.tex
@@
-\section{Hierarchical Database Structure}
+\section{Hierarchical Database}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Timeseries Key Attributes}
 \label{sub:timeseries_key_attributes}
-- Module ID
-  String field which describe the source of the data generated. Example of hec-hms, flow2d, weather-station etc
-- Value Type
-  - Scalar, Vector, Grid are the Value Types which are interested in the WDIAS.
-- Location
+\emph{Module ID}
+String field which describe the source of the data generated. e.g., hec-hms, flow2d, weather-station etc
+
+\emph{Value Type}
+Scalar, Vector, Grid are the Value Types which are interested in the \acrshort{wdias}.
+
+\emph{Location}
 Location of the timeseries. All locations have unique String identifier called locationId. Further, there are two type of location types that is interested in the WDIAS.
-  - Point locations - Contains a name which is human readable. lat and lon of the location on earth surface.
+\begin{itemize}
+  \item \emph{Point locations} - Contains a name which is human readable. lat and lon of the location on earth surface.
   \begin{lstlisting}[language=Python]
@@
   \end{lstlisting}
-  - Regular Grid locations - Contains a name which is human readable. The grid presents by dividing into equal size cells. Thus, it need the number of rows and columns. 
+  \item \emph{Regular Grid locations} - Contains a name which is human readable. The grid presents by dividing into equal size cells. Thus, it need the number of rows and columns. 
   And the location of the first cell and the width and height of it.
@@
   \end{lstlisting}
-  - Irregular Grid locations (endpoints are available with in the WDIAS system, but skipped since it is out of the interest of the scope.)
+  \item \emph{Irregular Grid locations} - (endpoints are available with in the WDIAS system, but skipped since it is out of the interest of the scope.)
+\end{itemize}
 
-- Parameter - Parameter describe the variable measuring against a location. All parameters ahve a unique String identifier called as parameterId. A parameter can be use in multiple locations.
+\emph{Parameter} - Parameter describe the variable measuring against a location. All parameters ahve a unique String identifier called as parameterId. A parameter can be use in multiple locations.
 While defining a parameter, there are three required fields which need to be provided such as variable, unit and parametertype.
-- Variable - Nature of the variable measuring. Example Precipitation, Temperature and WaterLevel etc
-- Unit - metric unit of measuring
-- Parameter Type - Should be one of 'Instantaneous', 'Accumulative', 'Mean'
+\begin{itemize}  
+  \item \emph{Variable} - Nature of the variable measuring. Example Precipitation, Temperature and WaterLevel etc
+  \item \emph{Unit} - metric unit of measuring
+  \item \emph{Parameter Type} - Should be one of 'Instantaneous', 'Accumulative', 'Mean'
   \begin{lstlisting}[language=Python]
@@
   \end{lstlisting}
+\end{itemize}
 
-- Timeseries Type
+\emph{Timeseries Type}
 Timeseries Type can be combination of Source followed by Category.
-  - Sources - External, Simulated
-  - Category - Historical, Forecast
+\begin{itemize}
+  \item Sources - External, Simulated
+  \item Category - Historical, Forecast
+\end{itemize}
 
-- Time Step
+\emph{Time Step}
 All Time Steps has an uniqie String identifier called as timeStepId.
@@
     \includegraphics[width=1\textwidth]{method/microservice/hierarchical_database.jpg}
-    \caption{Hierarchical Database}
+    \caption{Hierarchical database}
     \label{fi:hierarchical_database}
@@
 
-\subsection{MySQL}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{\acrshort{rdbms}}
 \label{sub:mysql}
-Relational Database Management System (RDBMS).
+
+There are lots of \acrshort{rdbms} available and for \acrshort{wdias} is using SQL as the \acrfull{rdbms}.
 SQL database has fewer version of open source and it is also possible to gain better performance with commercial versions. 
-Since WDIAS scope is to using open source tools, it is using MySQL as persistent database for storing timeseries metadata described above.
-One instance of MySQL is using only by adapter-metadata service.
-Other than that, another instance of MySQL is using for adapter-extension which will be describe in more detail \ref{data_preprocess}.
-MySQL is used only for these services, those will only keep the consistency of the schema for timeseries metadata and extension metadata.
-\ref{db_struct_redis} instance is using for caching the data from MySQL, since the MySQL database instances, itself not going to get much load.
+Since WDIAS scope is to using open source tools, it is using \acrshort{mysql} as persistent database for storing timeseries metadata described above.
+One instance of \acrshort{mysql} is using only by adapter-metadata service.
+Other than that, another instance of \acrshort{mysql} is using for adapter-extension which will be describe in more detail \ref{data_preprocess}.
+\acrshort{mysql} is used only for these services, those will only keep the consistency of the schema for timeseries metadata and extension metadata.
+\ref{db_struct_redis} instance is using for caching the data from \acrshort{mysql}, since the \acrshort{mysql} database instances, itself not going to get much load.
 Other than MySQL, there are many open source databases can be used to replace the same functionality.
 
-\subsection{InfluxDB} \cite{influxdbInfluxDBDocumentation}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Timeseries Database}
 \label{sub:influxdb}
-Open timeseries DB with MIT license
-Support SQL-Like query language
-Clustering available with a commercial version
-Among the other timeseries open source databases available, InfluxDB has higher number of usage and support. Database is written in Golang programming language,
-and has higher performance. Other than InfluxDB, another Database is Elastic Search which is mainly using for indexing for searching.
-With changing the configurations of the InfluxDB, it is possible to adapt as required. As mention in \cite{influxdbInfluxDBDocumentation}, 
-InfluxDB can setup on a computer which will give the required performance. Going further, users can use commercial version of InfluxDB in order to gain more performance.
+Among the other timeseries open source databases available, \acrshort{influxdb} \cite{influxdbInfluxDBDocumentation} has higher number of usage and support.
+Database is written in Golang programming language, and has higher performance, and has following supports;
+\begin{itemize}
+  \item Open timeseries DB with MIT license
+  \item Support SQL-Like query language
+  \item Clustering available with a commercial version
+\end{itemize}
+Other than \acrshort{influxdb}, another Database is Elastic Search which is mainly using for indexing for searching.
+With changing the configurations of the \acrshort{influxdb}, it is possible to adapt as required. As mention in \cite{influxdbInfluxDBDocumentation}, 
+\acrshort{influxdb} can setup on a computer which will give the required performance. Going further, users can use commercial version of \acrshort{influxdb} in order to gain more performance.
 
-Two instance of InfluxDB is using in the WDIAS system by adapter-scalar and adapter-vector services. For the scalability, the system uses \ref{micro_database_per_service}.
+Two instance of \acrshort{influxdb} is using in the WDIAS system by adapter-scalar and adapter-vector services. For the scalability, the system uses \ref{micro_database_per_service}.
 But further, it split into two services, refering to the \ref{micro_z_axis_scaling} data is partitioned among few servers based on valueType key attribute of timeseries.
@@
 
-\subsection{netCDF} \cite{unidataUnidataNetCDF}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{\acrfull{netCDF}} 
 \label{sub:netcdf}
-Network Common Data Form
-Self-describing, machine-independent data formats that support creation, access, and sharing of array-oriented scientific data
-Support parallel file access
+\acrshort{netCDF} \cite{unidataUnidataNetCDF} is a self-describing, machine-independent data formats that support creation, access, and sharing of array-oriented scientific data.
+And it also has the support for parallel file access.
 NetCDF is widely using in sciencetific domain due to it's capability of storing data in multi dementions easily and flexibility with storing many of the sciencetific data.
@@
 
-\subsection{MongoDB}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Document-oriented Database}
 \label{sub:mongodb}
-  MongoDB is a general purpose, document-based, distributed database
-  Supports query operations on geo-spatial data \cite{mongodbMongoDBManual}
-  Clustering and Sharding available for scalability and reliability
-MongoDB geo-spatial features are using for support Geo queries in the WDIAS. Other than that, external timeseries metadata queries are served by the indexed timeseries metadata data.
-If metadata not present in the adapter-query, if fetch data from the adapter-metadata, then indexed and cache in the MongoDB. Vise a versa, if new timeseries create in the adapter-metadata,
-it trigger an event to adapter-query to index the new timeseries.
+
+\acrshort{wdias} is using \acrshort{mongodb} as the Document-oriented databse, since it has the Geo searching capabilities.
+\acrshort{mongodb} \cite{mongodbMongoDBManual} is a general purpose, document-based, distributed database. And it supports;
+\begin{itemize}
+  \item Supports query operations on geo-spatial data \cite{mongodbMongoDBManual}
+  \item Clustering and Sharding available for scalability and reliability
+\end{itemize}
+\acrshort{mongodb} geo-spatial features are using for support Geo queries in the WDIAS. Other than that, external timeseries metadata queries are served by the indexed timeseries metadata data.
+If metadata not present in the adapter-query, if fetch data from the adapter-metadata, then indexed and cache in the \acrshort{mongodb}.
+Vise a versa, if new timeseries create in the adapter-metadata, it trigger an event to adapter-query to index the new timeseries.
 \ref{micro_y_axis_scaling} concept is using here by splitting into the multiple services based on the functionality and scale the system.
 
-\subsection{Redis}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{In-Memory Database}
 \label{sub:redis}
-  Redis\cite{redisRedisDocumentation} is an open source (BSD licensed), in-memory data structure store, used as a database, cache.
-  Clustering is available for scalability
-Redis uses as in-memory caching for fast access of repreative access data in adapter-metadata and adapter-extension.
-Other than that, adapter-status uses Redis as key value pair store for getting the status for async handling requests such as storing Grid data.
+\acrshort{wdias} is using \acrshort{redis} \cite{redisRedisDocumentation} as the In-Memory database, since it's widely using tool with good support, and it support few other features such as Publisher Subscriber capabilities.
+\acrshort{redis} is an open source (BSD licensed), used as a database, cache. Clustering is available for scalability.
+\acrshort{redis} uses as in-memory caching for fast access of repreative access data in adapter-metadata and adapter-extension.
+Other than that, adapter-status uses \acrshort{redis} as key value pair store for getting the status for async handling requests such as storing Grid data.
 In adapter-extension uses Redis's Publisher Subscriber capabilities in order to create a cron job in extension-scheduler when new extension create on \ref{se:data_preprocess}

### 2020-02-10 method/sec_4-db_struct.tex
change to subsubsection

@@
 \label{sub:timeseries_key_attributes}
-\emph{Module ID}
+\subsubsection{Module ID}
 String field which describe the source of the data generated. e.g., hec-hms, flow2d, weather-station etc
 
-\emph{Value Type}
+\subsubsection{Value Type}
 Scalar, Vector, Grid are the Value Types which are interested in the \acrshort{wdias}.
 
-\emph{Location}
+\subsubsection{Location}
 Location of the timeseries. All locations have unique String identifier called locationId. Further, there are two type of location types that is interested in the WDIAS.
@@
 
-\emph{Parameter} - Parameter describe the variable measuring against a location. All parameters ahve a unique String identifier called as parameterId. A parameter can be use in multiple locations.
+\subsubsection{Parameter} - Parameter describe the variable measuring against a location.
+All parameters ahve a unique String identifier called as parameterId.
+A parameter can be use in multiple locations.
 While defining a parameter, there are three required fields which need to be provided such as variable, unit and parametertype.
@@
 
-\emph{Timeseries Type}
+\subsubsection{Timeseries Type}
 Timeseries Type can be combination of Source followed by Category.
@@
 
-\emph{Time Step}
+\subsubsection{Time Step}
 All Time Steps has an uniqie String identifier called as timeStepId.

### 2020-02-10 method/sec_0_introduction.tex
Updated method introductions
- Added high-level design

@@
 This chapter includes the design decision taken while implementing the \acrfull{wdias}, and how is the system got adapted from the systems analyzed in Chapter \ref{ch:literature}, then how is it trying to propose a better system with overcoming the issues.
-\dbc{Add a couple of sentences to indicate what is covered in each Section. Do this in all chapters except in Chap 1.}
+In the section \ref{se:high_level_design}, it give a brief disussion on how the weather forecasting is happening, and why it need to interact with multiple data formats.
+Then following subsections define few termelogy which are using in the \acrshort{wdias}, and scope of the thesis.
+Following section \ref{se:architectural_decisions} that we evolve over while designing and implementing the \acrshort{wdias}.
+The section \ref{se:microservice} gives better understanding of the microservice architectural concepts follows while implementing the \acrshort{wdias}.
+Then the reason behind developing Heirarchital Database and technologies use for that discussed in the section \ref{se:db_struct}.
+Throw out the section \ref{se:data_preprocess} discussed about how the \acrshort{wdias} enable for data preprocessing and adding capabilities via concept of Extensions.
+Last section \ref{se:query} includes details on how to perform timeseries search and geo based queries.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
+\section{High-level Design}
+\label{se:high_level_design}
 
-\dbc{What's this? Are you trying to give a high-kevel idea of the solution. If so, name it as high-level design.}
-
-- Model data
-multiple data formats in weather data
-GRIB WRF model, out netCDF
-netCDF to CSV then feed to HEC-HMS, out CSV
-CSV + Rain cell Grid to FLO2D, out water level Grid ASCII files
-ASCII files to ArcGIS create Raster files, then use t LOSS Estimation
-
-- Observed data
-Automated weather station sending data in higher frequent intervals via HTTP protocol
-Automated water level stations send data in higher frequency
-
+In order to get overall idea on the flow of weather prediction, lets look into one of flows using in \acrshort{curw} \cite{CUrWSL2017SL}.
+\begin{itemize}
+    \item Extract GRIB WRF model data to netCDF
+    \item From netCDF to CSV of each location data, then feed to HEC-HMS and get the output as CSV
+    \item CSV + Rain cell Grid feed into the FLO2D, and get the water level as Grid ASCII files after completion of simulation
+    \item Upload ASCII files to ArcGIS create Raster files, then use for the LOSS Estimation
+\end{itemize}
+When looked into the above flow, it clear understanding on multiple data formats using while weather predictions.
+Other than that, in order to correct the model outputs, it required to collect real time data such as;
+\begin{itemize}
+    \item Automated weather station sending data in higher frequent intervals via HTTP protocol
+    \item Automated water level stations send data in higher frequency
+\end{itemize}
 Other than above there are many data formats using for handling data based on devices and standards which are using.
@@
 
-- Timeseries
+\subsection{Modules of Weather Data System}
+The figure \ref{fi:wdia_components} shows the basic functions of a Weather data integration and assimilation system.
+\begin{figure}[htbp]
+\centerline{\includegraphics[width=0.5\textwidth]{method/misc/weather_data_system_components.jpg}}
+\caption{Components of a weather data system.}
+\label{fi:wdia_components}
+\end{figure}
+\subsubsection{Integration}
+The system should capable of integrating data from different source such as satellite data, high end and low end weather station etc.
+And the system should be able to handle multidimensional spatial and temporal weather data efficiently and optimally.
+\subsubsection{Assimilation}
+Then the system should be able to fulfill weather models varying data requirements.
+Also those models reproduce large set of redundant data, thus system should store the bulk data while optimizing the disk space.
+\subsubsection{Dissemination}
+Then different users should be able to retrieve data as they required.
+Also the users should be able to easy to search into the available that in the system base on timeseries metadata or based on Geo queries.
+
+\subsubsection{Timeseries}
 A timeseries is simply a series of data points ordered in time. In weather domain, it interest in timeseries in perspective of observations to forecasting.
 Each timeseries, the data points can be form in different formats as well.
-- Scalar - 0D
-- Vector - 1D
-- Grid - 2D
-- Polygon - 2D
+\begin{itemize} 
+    \item Scalar - 0D
+    \item Vector - 1D
+    \item Grid - 2D
+    \item Polygon - 2D
+\end{itemize}
 
@@
 
-- Base of WDIAS architecture
+\subsubsection{Base of WDIAS architecture}
 The base of WDIAS architecture origins based on attributes of a timeseries.
 There are many attributes to differentiate timeseries one from another.
-But following can be consider as key attributes to uniquely identify a timeseries from another.
-- Module - module that generate the timeseries
-- Value Type - Scalar, Vector, Grid, Polygon
-- Location 
-- Parameter - measuring parameter of timeseries
-- Timeseries type
-  - sources - External, Simulated
-  - category - Historical, forecast
-- Time step
-
-- Key components of the system
-- Integration
-System should be able to store data from multiple sources which come in different formats
-- Assimilation
-System should be able to provide functionalities for pre-possessing data and validating before using. 
-- Dissemination
-System should be able to export data in different data formats
+But following can be consider as key attributes to uniquely identify a timeseries from another for the \acrshort{wdias}.
+In detail description available at the section \ref{se:db_struct}.
+\begin{itemize}
+    \item Module - module that generate the timeseries
+    \item Value Type - Scalar, Vector, Grid, Polygon
+    \item Location 
+    \item Parameter - measuring parameter of timeseries
+    \item Timeseries type
+    \begin{itemize}
+        \item sources - External, Simulated
+        \item category - Historical, forecast
+    \end{itemize}
+    \item Time step
+\end{itemize}

### 2020-02-10 method/sec_0_introduction.tex
Updated architectural decisions

@@
 
-\subsection{Modules of Weather Data System}
+\subsection{Modules of Weather Data Integration System}
+\label{subse:modules_weather_data_integration_sys}
+
 The figure \ref{fi:wdia_components} shows the basic functions of a Weather data integration and assimilation system.

### 2020-02-10 method/sec_1-architectural_decisions.tex
Updated architectural decisions

\section{Architectural Desicions}
\label{se:architectural_decisions}

Initial design of \acrshort{wdias} used the \acrfull{soa}, and try to use the \acrfull{esb} which can provide capability to integrate different modules, since it is acting as a common layer for all of modules. By default, \acrshort{esb} provides pub sub capabilities.
Since \acrshort{esb} mediator can be used to integrate the modules which are described in \ref{subse:modules_weather_data_integration_sys}. \acrshort{esb} also support different transportation protocols such as HTTP and Web-Socket etc.

But \acrshort{esb} is not a better solution for data streaming or bulk data processing. Also \acrshort{esb} suffer from single point of failure, since all the messages are going though a common bus.

In the second phase of \acrshort{wdias}, the proposed architecture changed to use with Actor model using AKKA framework \cite{HewittWhyDocumentation} after consider into the disadvantage of using \acrshort{esb}. Using the Actors we tried to implement the microservice architecture. In that case, an Actor or An Actor with slave Actors map into each microservice in the \acrshort{wdias}.

The typical \acrshort{soa} model, for example, usually has more dependent \acrshort{esb}s, with microservices using faster messaging mechanisms. \acrshort{soa} also focuses on imperative programming, whereas microservices architecture focuses on a responsive-actor programming style. Moreover, \acrshort{soa} models tend to have an outsized relational database, while microservices frequently use NoSQL or micro-SQL databases (which can be connected to conventional databases). But the real difference has to do with the architecture methods used to arrive at an integrated set of services in the first place.

As mentioned above, \acrshort{esb} support to implement \acrshort{soa}. But \acrshort{soa} has limitations such as single point of failure, slower communication (can’t use for transfer data) etc. So, the microservice architecture get evolved and demanding for the moment. When compare to \acrshort{soa}, microservice architecture has some advantages;
\begin{itemize}
    \item Follow the Single Responsibility Principle
    \item Resilient/Flexible – failure in one service does not impact other services. If you have monolithic or bulky service errors in one service/module it can impact other modules/functionality.
    \item High scalability – demanding services can be deployed in multiple servers to enhance performance and keep away from other services so that they don’t impact other services. Will be difficult to achieve the same with single, large monolithic service.
    \item Easy to enhance – less dependency and easy to change and test
    \item Low impact on other services – being an independent service, this has less chance to impact other services
    \item Easy to understand since they represent the small piece of functionality
    \item Ease of deployment
\end{itemize}

Even with using AKKA framework, it has some of the disadvantage as described in AKKA documentation \cite{Akka.ioWhenCluster}. Even Actor model capable of implementing a microservice architecture, it has few disadvantage. In order to overcome these issues, we moved to the \acrfull{k8s} \cite{LinuxFoundationProduction-GradeKubernetes}.;
\begin{itemize}
    \item Unable to choose technology. But \acrshort{k8s} allows you to choose technology that is best suited for a particular functionality
    \item As mentioned in the AKKA documentation \cite{Akka.ioWhenCluster}, it's better for developing one microservice within the whole \acrshort{wdias} design.
\end{itemize}

### 2020-02-10 method/sec_1-architectural_decisions.tex
fix akka ref issues

@@
 
-In the second phase of \acrshort{wdias}, the proposed architecture changed to use with Actor model using AKKA framework \cite{HewittWhyDocumentation} after consider into the disadvantage of using \acrshort{esb}.
+In the second phase of \acrshort{wdias}, the proposed architecture changed to use with Actor model using AKKA framework \cite{HewittWhyModel} after consider into the disadvantage of using \acrshort{esb}.
 Using the Actors we tried to implement the microservice architecture.

### 2020-02-10 Paper.tex
Fixed: sub section labels

@@
 The adapter-scalar or adapter-vector can improve to plug multiple instance of \acrshort{influxdb} instances by changing the configurations.
-As an example, based on the key attribute \ref{sub:timeseries_key_attributes} Timeseries Type, the adapter-scalar can connect to four instance of \acrshort{influxdb} instances such as  External Historical, External Forecast, Simulated Historical, and Simulated Forecast etc.
+As an example, based on the key attribute \ref{subse:timeseries_key_attributes} Timeseries Type, the adapter-scalar can connect to four instance of \acrshort{influxdb} instances such as  External Historical, External Forecast, Simulated Historical, and Simulated Forecast etc.
 
@@
 Then the test plans are performed with increasing the request size, and monitored the performance metrics.
-The system is setup on the \acrfull{eks} as per the configurations of \ref{sub:test_sys_config}.
+The system is setup on the \acrfull{eks} as per the configurations of \ref{subse:test_sys_config}.
 During the performance test plans, the system were able to provide constant throughput by keeping the latency constant while increasing the workload. Which exhibit the scalability of the system.

### 2020-02-10 method/sec_4-db_struct.tex
Fixed: sub section labels

@@
 \subsection{Timeseries Key Attributes}
-\label{sub:timeseries_key_attributes}
+\label{subse:timeseries_key_attributes}
 \subsubsection{Module ID}
@@
 \subsection{\acrshort{rdbms}}
-\label{sub:mysql}
+\label{subse:mysql}
 
@@
 One instance of \acrshort{mysql} is using only by adapter-metadata service.
-Other than that, another instance of \acrshort{mysql} is using for adapter-extension which will be describe in more detail \ref{data_preprocess}.
+Other than that, another instance of \acrshort{mysql} is using for adapter-extension which will be describe in more detail \ref{se:data_preprocess}.
 \acrshort{mysql} is used only for these services, those will only keep the consistency of the schema for timeseries metadata and extension metadata.
-\ref{db_struct_redis} instance is using for caching the data from \acrshort{mysql}, since the \acrshort{mysql} database instances, itself not going to get much load.
+\ref{subse:redis} instance is using for caching the data from \acrshort{mysql}, since the \acrshort{mysql} database instances, itself not going to get much load.
 Other than MySQL, there are many open source databases can be used to replace the same functionality.
@@
 \subsection{Timeseries Database}
-\label{sub:influxdb}
+\label{subse:influxdb}
 Among the other timeseries open source databases available, \acrshort{influxdb} \cite{influxdbInfluxDBDocumentation} has higher number of usage and support.
@@
 \subsection{\acrfull{netCDF}} 
-\label{sub:netcdf}
+\label{subse:netcdf}
 \acrshort{netCDF} \cite{unidataUnidataNetCDF} is a self-describing, machine-independent data formats that support creation, access, and sharing of array-oriented scientific data.
@@
 \subsection{Document-oriented Database}
-\label{sub:mongodb}
+\label{subse:mongodb}
 
@@
 \subsection{In-Memory Database}
-\label{sub:redis}
+\label{subse:redis}
 \acrshort{wdias} is using \acrshort{redis} \cite{redisRedisDocumentation} as the In-Memory database, since it's widely using tool with good support, and it support few other features such as Publisher Subscriber capabilities.

### 2020-02-10 results/sec_2-workload.tex
Dont' use title case of figure captions. Capitalize only the proper nouns. Also, WDIAS can be shorten in figure captions.
Fixed: sub section labels

@@
     \includegraphics[width=0.6\textwidth]{results/work_load/experimental_setup_v3.jpg}
-    \caption{Experimental Setup with JMeter}
+    \caption{Experimental setup with JMeter}
     \label{fi:experimental_setup}
@@
     \includegraphics[width=0.6\textwidth]{results/work_load/test_prod_throughtput_shaping_timer.png}
-    \caption{WDIAS Performance Test - Throughput Shaping Timer Graph}
+    \caption{\acrshort{wdias} performance test - Throughput Shaping Timer graph}
     \label{fi:test_prod_throughtput_shaping_timer}
@@
 \subsection{System Configuration}
-\label{sub:test_sys_config}
+\label{subse:test_sys_config}
 As described in the \ref{se:microservice}, the \acrshort{wdias} is mainly focus on microservice architecture and implemented on top of kubernetes.

### 2020-02-10 method/sec_3-microservice.tex
Dont' use title case of figure captions. Capitalize only the proper nouns. Also, WDIAS can be shorten in figure captions.
Rearrange microservice doc

@@
 These services are built around business capabilities and independently deployable by fully automated deployment machinery.
-There is a bare minimum of centralized management of these services, which may be written in different programming languages and use different data storage technologies.
-https://martinfowler.com/articles/microservices.html
+There is a bare minimum of centralized management of these services, which may be written in different programming languages and use different data storage technologies \cite{LewisMicroservices}.
 
 Among the characteristics of \acrfull{microservice}, few characteristics heavily affect while moving from \acrshort{soa} to \acrshort{microservice}.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Smart Endpoints And Dumb Pipes}
+\label{subse:smart_endpoints}
 - Smart endpoints and dumb pipes \cite{LewisMicroservicesPipes}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Database per Service}
+\label{subse:database_per_service}
 - Pattern: Database per service \cite{LewisMicroservicesManagement}
@@
 For example, if you are using a relational database then the options are:
-Private-tables-per-service – each service owns a set of tables that must only be accessed by that service
-Schema-per-service – each service has a database schema that’s private to that service
-Database-server-per-service – each service has its own database server.
-Private-tables-per-service and schema-per-service have the lowest overhead.
+\begin{itemize}
+    \item Private-tables-per-service – each service owns a set of tables that must only be accessed by that service
+    \item Schema-per-service – each service has a database schema that’s private to that service
+    \item Database-server-per-service – each service has its own database server.
+    \item Private-tables-per-service and schema-per-service have the lowest overhead.
 Using a schema per service is appealing since it makes ownership clearer.
 Some high throughput services might need their own database server.
+\end{itemize}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Sagas}
+\label{subse:sagas}
 - Pattern: Sagas \cite{RichardsonMicroservicesSagas}
@@
 
-Even AKKA.io actor model support the microservice architecture, as it explained in the documentation \cite{Akka.ioWhenCluster}, it has own advantages and disadvantage over the system that needs to be built.
-
-- The Scale cube
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{The Scale Cube}
+\label{subse:scale_cube}
 The microservice architecture is an application of Y-axis scaling but let’s also look at X-axis and Z-axis scaling.
 
-X-axis scaling
+\subsubsection{X-axis Saling}
 X-axis scaling consists of running multiple copies of an application behind a load balancer.
@@
 
-Y-axis scaling
+\subsubsection{Y-axis Scaling}
 Unlike X-axis and Z-axis, which consist of running multiple, identical copies of the application, Y-axis axis scaling splits the application into multiple, different services.
@@
 
-Z-axis scaling
+\subsubsection{Z-axis Scaling}
 When using Z-axis scaling each server runs an identical copy of the code (similar to X-axis scaling). The big difference is that each server is responsible for only a subset of the data.
@@
 
-- Brief introduction to the Kubernetes
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Brief introduction to the \acrfull{k8s}}
+\label{sebse:k8s_intro}
 
@@
     \centering
-    \includegraphics[width=1\textwidth]{method/microservice/microservice_architecture-handle_on_async-v3.jpg}
-    \caption{\acrshort{wdias} architecture to handle request asynchronously.}
-    \label{fi:wdias_micro_async}
+    \includegraphics[width=1\textwidth]{method/microservice/k8s_architecture_v3.jpg}
+    \caption{\acrfull{k8s} architecture.}
+    \label{fi:k8s_architecture}
 \end{figure}
-
-\dbc{Dont' use title case of figure captions. Capitalize only the proper nouns. Also, WDIAS can be shorten in figure captions.}
 

### 2020-02-10 method/sec_3-microservice.tex
Updated micro service patterns

@@
 \label{subse:smart_endpoints}
-- Smart endpoints and dumb pipes \cite{LewisMicroservicesPipes}
+When building communication endpoints, many architecture approach with putting significant smart into the communication mechanism.
+One good example is \acrshort{esb} what we discussed in section \ref{se:architectural_decisions}.
+But microservice follows alternative approach: \emph{Smart endpoints and dumb pipes} \cite{LewisMicroservicesPipes}.
+Applications built from microservices aim to be as decoupled and as cohesive as possible.
+They own their own domain logic and act more as filters in the classical Unix sense.
+After receiving a request, applying logic as appropriate and producing a response.
+And it uses simple RESTish protocols rather than complex protocols.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Database per Service}
+\subsection{Pattern: Database per Service}
 \label{subse:database_per_service}
-- Pattern: Database per service \cite{LewisMicroservicesManagement}
+- Pattern: Database per service
 
-  \acrshort{microservice} prefer letting each service manages its own database, either different instances of the same database technology, or entirely different database systems - an approach called Polyglot Persistence.
+\acrshort{microservice} prefer letting each service manages its own database, either different instances of the same database technology, or entirely different database systems - an approach called \emph{Polyglot Persistence} \cite{LewisMicroservicesManagement}.
 
-  \cite{RichardsonMicroservicesService}
 Keep each microservice’s persistent data private to that service and accessible only via its API. 
@@
 You do not need to provision a database server for each service.
-For example, if you are using a relational database then the options are:
+For example, if you are using a relational database then the options are \cite{RichardsonMicroservicesService}:
 \begin{itemize}
-    \item Private-tables-per-service – each service owns a set of tables that must only be accessed by that service
-    \item Schema-per-service – each service has a database schema that’s private to that service
-    \item Database-server-per-service – each service has its own database server.
-    \item Private-tables-per-service and schema-per-service have the lowest overhead.
+    \item \emph{Private-tables-per-service} – each service owns a set of tables that must only be accessed by that service
+    \item \emph{Schema-per-service} – each service has a database schema that’s private to that service
+    \item \emph{Database-server-per-service} – each service has its own database server.
+\end{itemize}
+Private-tables-per-service and schema-per-service have the lowest overhead.
 Using a schema per service is appealing since it makes ownership clearer.
 Some high throughput services might need their own database server.
-\end{itemize}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Sagas}
+\subsection{Pattern: Sagas}
 \label{subse:sagas}
-- Pattern: Sagas \cite{RichardsonMicroservicesSagas}
 In order to ensure loose coupling, each service has its own database.
@@
 A service publishes an event when its data changes.
-Other services consume that event and update their data.
+Other services consume that event and update their data \cite{RichardsonMicroservicesSagas}.
 

### 2020-02-10 method/sec_3-microservice.tex
Scale cube

@@
 \label{subse:scale_cube}
-The microservice architecture is an application of Y-axis scaling but let’s also look at X-axis and Z-axis scaling.
+The scalability of a system can explain via a concept called \emph{Scale Cube} which talk about the scalability of the application throw X, Y and Z axis.
 
@@
 If there are N copies then each copy handles 1/N of the load.
-This is a simple, commonly used approach of scaling an application.
-One drawback of this approach is that because each copy potentially accesses all of the data, caches require more memory to be effective.
-Another problem with this approach is that it does not tackle the problems of increasing development and application complexity.
+This is a simple, commonly used approach of scaling an application TODO.
 
@@
 There are a couple of different ways of decomposing the application into services.
-verb-based decomposition ex: checkout
-decompose the application by noun ex: customer management. 
-An application might use a combination of verb-based and noun-based decomposition.
+\begin{itemize}
+    \item verb-based decomposition ex: checkout.
+    \item decompose the application by noun ex: customer management. 
+    \item An application might use a combination of verb-based and noun-based decomposition.
+\end{itemize}
+
+The microservice architecture is an application of Y-axis scaling.
 
@@
 When using Z-axis scaling each server runs an identical copy of the code (similar to X-axis scaling). The big difference is that each server is responsible for only a subset of the data. 
+Z-axis splits are commonly used to scale databases. Data is partitioned (a.k.a. sharded) across a set of servers based on an attribute of each record.
 
-Some component of the system is responsible for routing each request to the appropriate server. Ex;
-One commonly used routing criteria is an attribute of the request such as the primary key of the entity being accessed. 
-Another common routing criteria is the customer type.
-For example, an application might provide paying customers with a higher SLA than free customers by routing their requests to a different set of servers with more capacity.
-
-Z-axis splits are commonly used to scale databases.
-Data is partitioned (a.k.a.
-sharded) across a set of servers based on an attribute of each record.
-(Ex: the primary key of the RESTAURANT table is used to partition the rows between two different database servers)
-
-Note that X-axis cloning might be applied to each partition by deploying one or more servers as replicas/slaves. Z-axis scaling can also be applied to applications.
-(Example of apply Z-axis scaling: the search service consists of a number of partitions.
-A router sends each content item to the appropriate partition, where it is indexed and stored.
-A query aggregator sends each query to all of the partitions, and combines the results from each of them.)
+Even \acrshort{wdias} is design based on the Y-axis scaling, it's possible to use the Z-axis scaling to scalibility of the system further. This will be more discuss in the section \ref{se:discussion}.
 

### 2020-02-10 method/sec_3-microservice.tex
K8s intro

@@
 
+\acrfull{k8s} is an open-source system for automating deployment, scaling, and management of containerized applications \cite{LinuxFoundationProduction-GradeKubernetes}.
+It groups containers that make up an application into logical units for easy management and discovery.
 \begin{figure}[htp]
@@
 \end{figure}
-
-- Explain how k8s support microservice architecture
+Components of \acrshort{k8s},
+\begin{itemize}
+    \item Pods – Cluster of containers that can group other container images in a single unit.
+    \item Nodes - the machines (VMs, physical servers, etc) in a cluster that run your applications and cloud workflows.
+    \item kubelet - An agent that runs on each node in the cluster. It makes sure that containers are running in a pod.
+    \item kube-proxy - A network proxy that runs on each node in the cluster, and maintains network rules on nodes.
+    \item Kubernetes master - Responsible for maintaining the desired state for your cluster.
+    \item etcd - Consistent and highly-available key value store used as Kubernetes’ backing store for all cluster data.
+\end{itemize}
+Users can add much as required Nodes into the \acrshort{k8s} cluster, and \acrshort{k8s} manage and deploy application as pods into cluster nodes.
+Each microservice can deploy as a Pod which is a group of containerize applications. And \acrshort{k8s} able to scale as much as user want as described above.
 

### 2020-02-10 method/sec_3-microservice.tex

@@
 <explain how each one is used while designing the WDIAS architecture>
-
+In the figures of \ref{fi:wdias_micro_on_demand} and \ref{fi:wdias_micro_async} each circle represent a microservice, and those are implemented as containerized applications.
 \begin{figure}[htp]

### 2020-02-10 method/sec_3-microservice.tex
Updated WDIAS API

--- 2020-02-10 method/sec_3-microservice.tex
@@
 \subsection{Smart Endpoints And Dumb Pipes}
-\label{subse:smart_endpoints}
+\label{subse:dumb_pipes}
 When building communication endpoints, many architecture approach with putting significant smart into the communication mechanism.
@@
 
-Even \acrshort{wdias} is design based on the Y-axis scaling, it's possible to use the Z-axis scaling to scalibility of the system further. This will be more discuss in the section \ref{se:discussion}.
+Even \acrshort{wdias} is design based on the Y-axis scaling, it's possible to use the Z-axis scaling to scalability of the system further. This will be more discuss in the section \ref{se:discussion}.
 
@@
 
-<explain how each one is used while designing the WDIAS architecture>
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{\acrshort{wdias} Microservices}
+\label{sebse:wdias_microservices}
+In the figures of \ref{fi:wdias_micro_on_demand} and \ref{fi:wdias_micro_async} each circle represent a microservice, and those are implemented as containerized applications.
 \begin{figure}[htp]
@@
 \end{figure}
+In left side of the figure \ref{fi:wdias_micro_on_demand} shows the import modules of the \acrshort{wdias}, and right side show the export modules.
+As it explained section \ref{subse:dumb_pipes}, each import microservice only do specific task of converting and forwarding the request to the correct data adapter module.
+For each data type, there is a adapter microservice is running which is optimized to storing such type of data.
+And the metadata data of the timeseries store using \acrshort{rdbms} which gives more performance over retrieving metadata data.
+The metadata is cached with In-Memory database in order to fast access as mentioned in section \ref{subse:redis}.
+The system generate a unique identifier for each timeseries, and throw out the \acrshort{wdias}, other microservice use it to handle data for fast access.
 
@@
 \end{figure}
+Export module microservice follows the same concepts and provide the capability to export the data into required formats of the weather models.
+Each adapter follows the concept of database per service as mentioned in the section \ref{subse:database_per_service}. This gives the freedom for \acrshort{wdias} to scale better with \acrshort{k8s}.
+As shown in the figure \ref{fi:wdias_micro_on_demand}, when a smaller size request come to the system, it handle on demand and response back.
+But as shown in figure \ref{fi:wdias_micro_async}, when a request with larger size come to the system, it store the data for asynchronously process the data and response with a unique id which can use to verify whether data processed successfully or not.
 
@@
 \end{figure}
+The figure \ref{fi:wdias_micro_on_demand} show the clear separation of microservices into the modules of the \acrshort{wdias}.
+As it shown, each adapter has isolated database, and database is hosted separately for the high performance.
+Apart from that, as we further discuss in section \ref{se:data_preprocess}, the extension modules are running separately such as Interpolation, Transformation and Validation etc.
+The Extension Adapter allow users to register new triggers for the extensions. And extension scheduler triggers the events based on time and extension handler triggers event based on data change.
 
-<add the API description and how it related to modules>
-- Import
-- Export
-- Timeseries
-- Extensions
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{\acrshort{wdias} API Convention}
+\label{sebse:wdias_api}
+One of the main design consideration in \acrshort{wdias} is the convention of defining the APIs. It follows the simple RESTful API, and allow users to interact with HTTP methods.
+
+\emph{Timeseries} endpoints allow to interact with Metadata Adapter, and those are cache on the Query Handler in order to perform search queries.
+\begin{itemize}
+    \item parameter
+    \begin{itemize}
+        \item \emph{/parameter}
+    \end{itemize}
+    \item timeStep
+    \begin{itemize}
+        \item \emph{/timestep}
+    \end{itemize}
+    \item location
+    \begin{itemize}
+        \item \emph{/location/point}
+        \item \emph{/location/regularGrid}
+    \end{itemize}
+    \item timeseries
+\end{itemize}
+
+\emph{Import} endpoints allow to upload data into the \acrshort{wdias} system.
+\begin{itemize}
+    \item \emph{/import/json/raw}
+    \item \emph{/import/ascii-grid/upload}
+\end{itemize}
+
+\emph{Export} endpoints allow to get/download data from the \acrshort{wdias} system.
+\begin{itemize}
+    \item \emph{/export/json/raw}
+    \item \emph{/export/ascii-grid/binary}
+\end{itemize}
+
+\emph{Extensions} endpoints for configure extensions.
+
+These details describes in the section \ref{se:data_preprocess}.
+
+The API convention of \emph{/<MODULE>/<DATA_FORMAT>/<DATA_OPERATION_TYPE>} allows users to integrate new import or export modules into the system as well as add new data types.

### 2020-02-10 method/sec_3-microservice.tex
syntax

@@
 
-The API convention of \emph{/<MODULE>/<DATA_FORMAT>/<DATA_OPERATION_TYPE>} allows users to integrate new import or export modules into the system as well as add new data types.
+The API convention of \texttt{/MODULE/DATA\_FORMAT/DATA\_OPERATION\_TYPE} allows users to integrate new import or export modules into the system as well as add new data types.

### 2020-02-10 summary/sec_2-research_limitations.tex
use emph

@@
 
-\dbc{Use italics to emphasize, not bold.}
-
-\paragraph{Lack of data preprossessing modules}
+\emph{Lack of data preprossessing modules}:
 The extension module enable plugin system to integrate prepossessing modules which can use for process the data which are inserted to the system or based on regular intervals.
@@
 
-\paragraph{Supporting Irregular Grids}
+\emph{Supporting Irregular Grids}:
 At the moment \acrshort{wdias} does not support Irregular Grids, but it has the API endpoints define for the implementation which can follow the same microservice architecture.
@@
 
-\paragraph{Grid data performance}
+\emph{Grid data performance}:
 As mentioned in the \ref{se:conclusion}, the adapter-grid is using a Python wrapper for netCDF FORTRAN implementation with parallel IO enabled.
@@
 
-\paragraph{Define infrastructure as code}
+\emph{Define infrastructure as code}:
 Physical nodes for the \acrshort{k8s} cluster created using Cloud Computing provider such as \acrshort{eks}.
@@
 
-\paragraph{Improve test cases}
+\emph{Improve test cases}:
 As described in detail with \ref{subse:closed_vs_open_workload}, for \acrshort{wdias} performance test uses Time Stepping Feedback loop with Concurrent Threads which is the best approach support by \acrshort{jmeter} at the moment.
@@
 
-\paragraph{Further improve hierarchical database performance}
+\emph{Further improve hierarchical database performance}:
 As further described in \ref{se:conclusion}, it is possible to increase the performance of these bottlenecks much higher such as using \acrshort{influxdb} Commercial cluster support for high availability or horizontal scaling of \acrshort{influxdb}.
@@
 
-\paragraph{Alerting extension modules}
+\emph{Alerting extension modules}:
 At the moment, extensions only support On Change and On Time events. But it will be good to have event trigger support based on reconfigured alert level.
 
-\paragraph{Publisher Subscriber extension modules}
+\emph{Publisher Subscriber extension modules}:
 The \acrshort{wdias} better to be capable of triggering external systems based on the events such as web hooks.

### 2020-02-10 introduction/sec_1-motivation.tex
blabla

@@
 It collected real time weather data from weather stations and other government entities, and do the forecasting daily.
-Then the generated results are shared to the thrusted parties.
+Then the generated results are shared to the trusted parties.
 One of the future goals of CUrW SL to open up to the public to share the data, and use of the processed data via their system for the betterment of the society.
-The institute is operating via the paid TAX of Sri Lankan, and its trying to improve the quality of the life and the economic losts which are effected on the country via sharing the data for external parties to use of them.
+The institute is operating via the paid TAX of Sri Lankan, and its trying to improve the quality of the life and the economic lost which are effected on the country via sharing the data for external parties to use of them.
 
@@
 To enhance the accuracy of weather predictions, it is necessary to provide reliable and detailed weather data as inputs to \acrfull{nwm}.
-These NWMs utilize \db{multimodal} weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images.
+These NWMs utilize multi-modal weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images.
 Prior to feeding such diverse data (collected from different sources that belongs to different stakeholders) into respective NWMs, it is necessary to integrate data into a common format.
@@
 For example, drying hay is only feasible in dry weather.
-Furhter the aviation industry is especially sensitive to the weather, accurate weather forecasting is essential, since prior to takeoff on the conditions to expect en route and at their destination.
+Further the aviation industry is especially sensitive to the weather, accurate weather forecasting is essential, since prior to takeoff on the conditions to expect en route and at their destination.
 Thus it is required a platform to provide such 3rd party access, and use the data or process those based on their applications.
@@
 Further Delft-FEWS is free to use, it is not open source.
-Hence, users of WDIA are forced to pay heavy licenses and are unable to extend the solutions to cater to their country-specific requirements.
-Therefore, the objective of this research is to develop a WDIA system for Sri Lanka, as well as make it open source, so that others could user and contribute to the solution.
-
 Even though there are many data integration systems, most of them are proprietary or close sourced.

### 2020-02-10 summary/sec_1-conclusions.tex
Fixed: sub section labels
Updated conclusion

@@
-%\section{Summary}
 \section{Conclusions}
+\label{se:summary_conclusion}
+
 \dbc{Expand this section while highlighting key design details and performance}
-\dbc{Sec. 5.2 should be "Research Limitations"}
 
 To enhance the accuracy of the weather prediction, it is required to have reliable weather data for \acrshort{nwm}.
-\db{Most of existing weather data systems are proprietary or close sourced, or not up to date with the existing cloud computing technologies.}
+Even though there are many data integration systems, most of them are proprietary or close sourced.
+Which means for an island like Sri Lanka that having different kinds of weather seasons over the year than those software originated need to be highly customized.
+Throughout the operations and maintenance, it is required to get support with paying lots of charges, and difficult to debug into a closed source system without maintenance support from the vendors.
+Also most of existing systems are not up to date with the existing cloud computing technologies, or bias to some research community.
 We proposed an extendable open source Weather Data Integration and Assimilation Systems which is known as \acrshort{wdias}.
@@
 And compatible with current cloud computing technologies and architecture patterns.
-\dbc{fix highlighted above}
 
-First the architecture starts with SOA using a \acrfull{esb}, and then moved to Actor model based architecture.
-After comparing the disadvantages of using such architecture with the system requirements, final architecture come up with modern microservice architecture.
-Based on the microservice architecture patterns and the nature of the weather metadata, the \acrshort{wdias} came up with the idea of hierarchical database structure in order to provide higher performance while store the weather data.
-The system uses \acrshort{influxdb} timeseries database for storing Scalar and Vector timeseries data, and using \acrshort{netCDF} for storing Grid timeseries data.
+First the architecture of \acrshort{wdias} starts with \acrshort{soa} using a \acrfull{esb}, and then moved to Actor model based architecture.
+After comparing the disadvantages of using such architectures with the system requirements, final architecture come up with modern microservice architecture.
+\acrshort{wdias} implemented the microservice architecture on top of the \acrshort{k8s}.
+Each microservice of \acrshort{wdias} is mapped to a pod in the \acrshort{k8s}.
+Also each microservice follows the concept of Smart endpoints dumb pipes, and do specific operations which are related to the data format that responsible for handling.
+
+Based on the microservice architecture patterns and the nature of the weather metadata, the \acrshort{wdias} came up with the idea of hierarchical database structure in order to provide higher performance while store the weather data optimum.
+The system uses timeseries database for storing Scalar and Vector timeseries data, and using \acrshort{netCDF} for storing Grid timeseries data.
+And each database adapter uses concept of database per service which allows each microservice service to scale without inteferance from other microservices.
+And it uses microservice sagas pattern for asynchronous data handling for requests with higher size.
+According to the section \ref{se:microservice}, it uses the many of the concept of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities.
+
 Also the system provide a generic open mechanism to integrate new modules as extension in order to enhance the features of the system.
@@
 
-\acrshort{wdias} performance test is perform using the \acrshort{jmeter} tool's distributed testing capabilities which separately testing each modules.
+\acrshort{wdias} load testing is perform using the \acrshort{jmeter} tool's distributed testing capabilities.
 Then the test plans are performed with increasing the request size, and monitored the performance metrics.
-The system is setup on the \acrfull{eks} as per the configurations of \ref{sub:test_sys_config}.
-During the performance test plans, the system were able to provide constant throughput by keeping the latency constant while increasing the workload. Which exhibit the scalability of the system.
-With the \acrshort{k8s} auto scaling, the \acrshort{wdias} were able to elastically adjust the number of pods according to the workload with the given configurations.
+The system is setup on the \acrfull{eks} as per the configurations of \ref{subse:test_sys_config}.
+Based on the observations, the system were able to handle 300 \acrshort{rps} (which means 18,000 requests per minute) successfully with minimizing the error rate to zero.
+Also while increasing the request size from 24 to 96 data points per Scalar and Vector timeseries, and number of ASCII Grid files from 24 to 96, the \acrshort{wdias} was able to perform same while keeping the latency constant without any significant change.
+During the performance test plans, the system were able to provide increase the throughput by keeping the latency constant while increasing the workload. Which exhibit the scalability of the system.
+With the \acrshort{k8s} auto scaling, the \acrshort{wdias} were able to elastically adjust the number of pods according to the workload with auto scaling configurations. 
+The results of \acrshort{wdias} shows that the system can run from 1 CPU node to nodes with few hundred CPUs.

### 2020-02-10 lit/sec_1-fews.tex
Review FEWS lit

@@
-\section{Delft-FEWS flow forecasting system}
-\acrshort{fews} is developed by Deltares in the Nethaland with targeted for use by operational forecasting agencies.
-%The software is freely available to download and setup.
-Tutorials and User setup guide \cite{DeltaresPublicWikiDelft-FEWSGuide} are available with well documentations.
-For non-commercial users need to have the licence agreement to use the system.
-And get new system updates.
-However, investments in new developments in the system are normally paid for by its users.
-The code base of \acrshort{fews} is currently not fully open source. %But configuration guides and generic adapter module integration code examples are available for the users.
+There are many of Weather forecasting, assimilation and dissemination systems developed by some of developed countries around the world as a result of trying to reduce the damage causing by natural disasters such as flood, storms, hurricanes, and even for drought.
+Such natural disasters heavily affected on the economy and the life conditions of the country, researchers have developed systems and many of these systems are using as proprietary systems.
+Other countries also using those systems and adopt with own version of system which effective for the specific weather condition in a particular country.
+This chapter \ref{ch:literature} presents a Literature review on existing systems and their architecture approach and design with available resources.
+In Section \ref{se:fews}, we present Most influenced systems for \acrshort{wdias} is \acrshort{fews}.
+\acrfull{lead}, \db{an open data handling platform distributed as closed-source software, is presented in Section \ref{se:lead}}.
+\acrshort{lead} is following the \acrfull{soa} for system architecture.
+Under each system we explore both system architecture, scalability and flexibility of the system.
+
+\dbc{Complete above while referring to all major sections with chapter.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{\acrshort{fews} flow forecasting system}
+\label{se:fews}
+
+\acrshort{fews} \cite{Werner2013TheSystem} is developed by Deltares in the Nethaland with targeted for use by operational forecasting agencies.
+The code base of \acrshort{fews} is currently not fully open source.
 Most if the models are using model-centric approach such as inputs need to be in the format of specific to the model.
 Also, the outputs produced by the model are specific to the model and hard to utilize by another systems (e.g., FLO2D).
-As \acrshort{fews} %is using much more
-uses a modular approach it is easier to integrate new models.% into the \acrshort{fews} system. 
+As \acrshort{fews} uses a modular approach it is easier to integrate new models.
 Thus, \acrshort{fews} can be consider as an integration framework or a middleware for the models.
-\dbc{Cite Fews. Provide only the key details. It's sufficient say whether its commercial or open source. Do this for all other solutions discussed. Middleware is a single word. Check other places.}
 
@@
 Flexibility is achieved through integrating new models and algorithms into the code base \cite{Werner2013TheSystem}.
-Delft-FEWS system contains no inherent hydrological modelling capabilities within its code base.
+\acrshort{fews} system contains no inherent hydrological modelling capabilities within its code base.
 Rather it is a framework which can use to integrate into the system and create work flows for forecasting.
@@
 
-Given above drawback on storing the data in the system, within the \acrshort{fews} data model, time series are uniquely identified by their location and data type, as well as an id related to the source of the data (e.g.,the external source or hydrological model of which the time series are a result) \cite{Werner2013TheSystem}.
+Given above drawback on storing the data in the system, within the \acrshort{fews} data model, time series are uniquely identified by their location and data type, as well as an id related to the source of the data (e.g., the external source or hydrological model of which the time series are a result) \cite{Werner2013TheSystem}.
 This gives an opportunity to index the data base on above key fields and store the data separately, in order to take the advantage of putting multiple data resources into the system.
@@
 \acrshort{fews} generates the input data as a set of XML files to a defined location; an adapter developed specifically for the model in question transforms this to the required native format in a pre-processing step; \acrshort{fews} executes the model; and the adapter to that model then converts the native formatted results into XML formatted files in a post processing step.
-\acrshort{fews} subsequently imports the results into the database from the XML files (see Fig.
-\ref{fi:fews_general_adapter}) \cite{Werner2013TheSystem}.
+\acrshort{fews} subsequently imports the results into the database from the XML files (see Figure \ref{fi:fews_general_adapter}) \cite{Werner2013TheSystem}.
 The process is simple and consistence through out all the model integration.
@@
 If you setup the system on Linux base operating system and using Linux based models, it is hard for users to come up with a solution for integrating the FLO2D models.
-The final step and one of important feature is exporting the data from the system in useful manner. %\acrshort{fews} supports three main forms of product generation, namely:
-%\begin{itemize}
-%\item Generate web reports with graphs, tables as well as summary reports
-%\item Export time series in a variety of formats
-%\item External applications actively retrieve data from the system
-%\end{itemize}
+The final step and one of important feature is exporting the data from the system in useful manner.
 The forecasting process is often a sequence of steps, starting with the import of data, a number of data processing and modeling steps, and culminating in the generation of products to be disseminated to the warning process.

### 2020-02-10 thesis.tex
Change Full Test
Add test cases as list
Replaced work_load
Updated method introductions
- Added high-level design
conc to summary
Review FEWS lit

@@
 \definecolor{backcolour}{rgb}{0.95,0.95,0.92}
-
 \lstdefinestyle{code-style}{
@@
 }
+\lstset{style=code-style}
 
-\lstset{style=code-style}
+\usepackage{newfloat} % Caption Lists: https://tex.stackexchange.com/a/239114/181545
+\DeclareFloatingEnvironment[placement={!ht},name=List]{customlist}
 
@@
 \label{ch:literature}
-There are many of Weather forecasting, assimilation and dissemination systems developed by some of developed countries around the world as a result of trying to reduce the damage causing by natural disasters such as flood, storms, hurricanes, and even for drought.
-%Above kind of
-Such natural disasters heavily affected on the economy and the life conditions of the country, researchers have developed systems and many of these systems are using as proprietary systems.
-Other countries also using those systems and adopt with own version of system which effective for the specific weather condition in a particular country.
-%Though out 
-This chapter presents a Literature review on existing systems and their architecture approach and design with available resources.
-\db{In Section 2.x we present ...} Most influenced systems for \acrshort{wdias} is \acrshort{fews} and \acrfull{lead} system.
-\acrshort{fews}, \db{an open data handling platform distributed as closed-source software, is presented in Section 2.x}.
-\db{In Section 2.x ...
-} \acrshort{lead} is following the Service Oriented Architecture for system architecture.
-Under each system we explore both system architecture, scalability and flexibility of the system.
-\dbc{Complete above while referring to all major sections with chapter.}
 
@@
 
-\import{method/}{sec_1-soa.tex}
-\label{se:soa}
+\import{method/}{sec_1-architectural_decisions.tex}
 
-\import{method/}{sec_2-actor_model.tex}
-\label{se:actor_model}
+% \import{method/}{sec_1-soa.tex}
+% \label{se:soa}
+% \import{method/}{sec_2-actor_model.tex}
+% \label{se:actor_model}
 
@@
 
-\import{results/}{sec_2-work_load.tex}
-\label{se:work_load}
+\import{results/}{sec_2-workload.tex}
+\label{se:workload}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\chapter{\db{Summary}}
-\label{ch:conc}
+\chapter{Summary}
+\label{ch:summary}
 

### 2020-02-10 lit/sec_2-lead.tex
Review FEWS lit
Review LEAD again

@@
 \section{Linked Environments for Atmospheric Discovery}
+\label{se:lead}
 
-%The reason behind developing \acrfull{lead} by US National Science Foundation (NSF)  is to
 \acrfull{lead} addresses the fundamental research challenges needed to create an integrated, scalable framework for adaptive analyzing and predicting the atmosphere \cite{Droegemeier2005Service-OrientedWeather}.
@@
 
-%The most relevant and important analysis for designing \acrshort{lead} is understanding and analyzing the \acrfull{lead} architecture of it. 
 LEAD's complex array of services, applications, interfaces, and local and remote computing, networking, and storage resources is assembled by users in work flows to study mesoscale weather as it evolves \cite{Droegemeier2005Service-OrientedWeather}.
@@
 From the high-level view, \acrshort{lead} lets users query for and acquire information, simulate and predict weather by using numerical atmospheric models, assimilate data, analyze, mine, and visualize data and model output.
-\dbc{Make sure each reference to a figure or table is given as Figure x.y and Table x.y.}
 
@@
 
+The Concept of the \acrshort{lead} is, the workflow orchestration for on-demand, real-time, dynamically adaptive systems, called as WOORDS.
+The system is doing the work flow orchestration as given in each procedure.
+Those procedural rules are define by researcher and feed into the system.
+The system is trying to perform the action immediate after the submission, and also it transmit the data, run the models and send back the put put with lower time delay as possible.
+According to the load and other requirement, the system will respond to those requirements automatically.
+
 \begin{figure}[htp]
@@
 
-The Concept of the \acrshort{lead} is, the workflow orchestration for on-demand, real-time, dynamically adaptive systems, called as WOORDS.
-The system is doing the work flow orchestration as given in each procedure.
-Those procedural rules are define by researcher and feed into the system.
-The system is trying to perform the action immediate after the submission, and also it transmit the data, run the models and send back the put put with lower time delay as possible.
-According to the load and other requirement, the system will respond to those requirements automatically.
-
-As shown in the \ref{fi:lead_soa} LEAD consists of the following sub components:
+As shown in the figure \ref{fi:lead_framework} LEAD consists of the following sub components, and it provides a distributed test bed for developing, integrating, and testing LEAD's components.
 \begin{itemize}
@@
 
-The distributed computing systems in the LEAD grid represent a distributed test bed for developing, integrating, and testing LEAD's components.
-\dbc{Try to avoid singe sentence paras.}
+\acrshort{soa}s are widely deployed in the commercial enterprise sector, and they form the foundation of many scientific "grid" technologies at the time of \acrshort{lead} design and developed.
+A variant of \acrshort{soa} is evolved later called as microservice architecture, and widely use in the industry nowadays.
 
-\acrshort{soa}s are widely deployed in the commercial enterprise sector, and they form the foundation of many scientific “grid” technologies at the time of \acrshort{lead} design and developed.
-A variant of \acrshort{soa} is evolved later called as microservice architecture, and widely use in the industry nowadays.
-The \acrshort{lead} \acrshort{soa} has five distinct yet highly interconnected layers.
-
+As shown in figure \ref{fi:lead_soa}, \acrshort{lead} \acrshort{soa} has five distinct yet highly interconnected layers. 
 The bottom layer represents raw computation, application, and data resources distributed throughout the LEAD grid and elsewhere.
@@
 When creating weather work flow, it is required to change the behaviour of model by changing some of the configurations of the model or run a different version of the model.
-\item The application resource broker, which matches the appropriate host for execution to each application task, based on the execution’s time constraints \cite{}.
+\item The application resource broker, which matches the appropriate host for execution to each application task, based on the execution’s time constraints \cite{Droegemeier2005Service-OrientedWeather}.
 This service is a critical part of the system, and responsible of using the resources of the system in optimized manner.
@@
 \end{itemize}
-The top of the \ref{fi:lead_soa}, shows the user interface to the system.
+The top of the figure \ref{fi:lead_soa}, shows the user interface to the system.
 This give the access to individual services.

### 2020-02-10 lit/sec_1-fews.tex
Add MADIS

@@
     \centering
-    \includegraphics[width=0.7\textwidth]{fews/Schematic-structure-of-a-fl-ood-forecasting-system-showing-the-position-of-Delft-FEWS_W640.jpg}
+    \includegraphics[width=0.7\textwidth]{lit/fews/Schematic-structure-of-a-fl-ood-forecasting-system-showing-the-position-of-Delft-FEWS_W640.jpg}
     \caption[Schematic structure of a flood forecasting system including \acrshort{fews} and links to other primary systems within the operational environment]{Schematic structure of a flood forecasting system including \acrshort{fews} and links to other primary systems within the operational environment \cite{Werner2013TheSystem}.}
@@
     \centering
-    \includegraphics[width=1.0\textwidth]{fews/Architecture-of-Delft-FEWS-showing-the-data-base-the-data-access-layers-and-examples-of_W640.jpg}\\
+    \includegraphics[width=1.0\textwidth]{lit/fews/Architecture-of-Delft-FEWS-showing-the-data-base-the-data-access-layers-and-examples-of_W640.jpg}
     \caption[Architecture of \acrshort{fews}]{Architecture of \acrshort{fews} \cite{Werner2013TheSystem}.}
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{fews/Linking-Delft-FEWS-with-external-models-The-fi-gure-shows-the-fl-ow-of-data-through-XML_W640.jpg}\\
+    \includegraphics[width=0.8\textwidth]{lit/fews/Linking-Delft-FEWS-with-external-models-The-fi-gure-shows-the-fl-ow-of-data-through-XML_W640.jpg}
     \caption[Linking \acrshort{fews} with external models]{Linking \acrshort{fews} with external models \cite{Werner2013TheSystem}.}

### 2020-02-10 lit/sec_2-lead.tex
Add MADIS

@@
     \centering
-    \includegraphics[width=1.0\textwidth]{lead/LEAD-system-Fundamental-capabilities-familiar-to-meteorologists-are-shown-in-the-top_W640.jpg}\\
+    \includegraphics[width=1.0\textwidth]{lit/lead/LEAD-system-Fundamental-capabilities-familiar-to-meteorologists-are-shown-in-the-top_W640.jpg}
     \caption[Layered architecture of LEAD]{Layered architecture of LEAD \cite{Droegemeier2005Service-OrientedWeather}.}
@@
     \centering
-    \includegraphics[width=1.0\textwidth]{lead/LEAD-system-framework-LEAD-is-composed-of-several-interacting-subsystems-with-the-LEAD_W640.jpg}\\
+    \includegraphics[width=1.0\textwidth]{lit/lead/LEAD-system-framework-LEAD-is-composed-of-several-interacting-subsystems-with-the-LEAD_W640.jpg}
     \caption[LEAD system framework]{LEAD system framework \cite{Droegemeier2005Service-OrientedWeather}.}
@@
     \centering
-    \includegraphics[width=1\textwidth]{lead/LEADs-service-oriented-architecture-A-wide-variety-of-services-and-resources-grouped_W640.jpg}\\
+    \includegraphics[width=1\textwidth]{lit/lead/LEADs-service-oriented-architecture-A-wide-variety-of-services-and-resources-grouped_W640.jpg}
     \caption[LEAD's service-oriented architecture]{LEAD's service-oriented architecture \cite{Droegemeier2005Service-OrientedWeather}.}

### 2020-02-10 lit/sec_3-other-systems.tex
Review FEWS lit
Add MADIS

@@
 \label{se:madis}
+\acrfull{madis} is a data ingest and assimilation system, which is collecting data over dozen of providers, then quality control over the data and store in \acrshort{netCDF} format.
+Later allow users to access the data via supporting different type of protocols.
+
+\begin{figure}[htp]
+    \centering
+    \includegraphics[width=1\textwidth]{lit/other/madis_flow.png}
+    \caption[\acrshort{madis} flow]{\acrshort{madis} flow \cite{Macdermaid2005ARCHITECTUREP2.39}.}
+    \label{fi:madis_flow}
+\end{figure}
+
+\acrshort{madis} comprises a distributed architecture for ingest, processing, and data distribution functions.
+In addition, in a recent architectural advance, the various functional hosts are arranged in pairs using High-Availability (HA) Linux to provide auto mated failover in case of system failure.
+Real-time data distribution methods include FTP, Local Data Manager (LDM), and the Web-based OPeNDAP (OPen source project for Network Data Access Protocol) \cite{Macdermaid2005ARCHITECTUREP2.39}.
+As it mentioned above, the \acrshort{madis} is implemented based on a distributed architecture which is available at the time of it's development.
+Even it is not clear mentioned, it is using functional call like Remote procedure call (RPC) in order to invoke among a cluster of nodes as shown in figure \ref{fi:madis_flow}.
+In order to get High Availability, it has added some update to it's architecture.
+The conclusion of this statement is, these kind of functionalities are available at the modern the Cloud Computing tools, and out of the box those tools are providing the scalability and high availability.
+Using those tools, it possible to implement a such system with less effort and high confidence.
+
+MADIS routinely acquires mesonet data from several dozen network providers representing over 14,000 stations.
+This translates into over 30,000 station reports each hour.
+Several systems running both inside and outside the firewall acquire the data.
+These data are sent to the Central Facility's Advanced Weather Interactive Processing System (AWIPS) data server for preprocessing and conversion to a common format, NetCDF.
+The NetCDF files are then transferred to the MADIS compute nodes \cite{Macdermaid2005ARCHITECTUREP2.39}.
+This provide an overview of the level of data that \acrshort{madis} handling.
+This could be a good reference for implementing \acrshort{wdias}, and it's performance testing.
+As same as \acrshort{fews}, it is also converting the data into a common format which is \acrshort{netCDF}.
+Those files are transferred to the computer nodes, and allow users to access via OPeNDAP.
+
+The MADIS compute platforms comprise Intel based servers running the Red Hat Enterprise Linux operating system.
+Many of these computers are configured using High-Availability Linux clustering \cite{Macdermaid2005ARCHITECTUREP2.39}.
+As it indicated above, the system is heavily depend on the platform.
+There is a cost involving purchasing those license.
+
+Since some MADIS data are considered proprietary by the provider, access to these data need to be controlled.
+To accommodate this, MADIS data are split into six different versions based on the level of access allowed by the data provider \cite{Macdermaid2005ARCHITECTUREP2.39}.
+When compared to \acrshort{fews}, \acrshort{madis} provide a control based access to the data.
 
 \section{Summary}
+\label{se:lit_summary}

### 2020-02-10 lit/sec_3-other-systems.tex
Added DIAS

@@
 
+\acrshort{dias} collects and files data from satellites, ground observation stations, numerical weather prediction models and climate change projection models.
+Once this data is integrated with geographic and socio-economic information, DIAS generates results for managing global environmental issues and natural disasters \cite{Kawasaki2018DataReduction}.
+As mentioned above, \acrshort{dias} has the capability of collecting weather data form multiple data sources which are inherently in different formats.
+After successfully ingest the data, it generate results which can use for different kind of purposes.
+
+\begin{figure}[htp]
+    \centering
+    \includegraphics[width=1\textwidth]{lit/other/dias_common_base_application_platform.png}
+    \caption[DIAS’s common base application platform.]{DIAS’s common base application platform \cite{Kawasaki2018DataReduction}.}
+    \label{fi:dias_common_platform}
+\end{figure}
+
+The mechanism of storing data in \acrshort{dias}, similar to the other systems discussed.
+These data sets are stored in an extra large volume disk array system with API (Application Programming Interface) software used to import the data.
+APIs work to convert or re-format data into manageable forms and are useful in creating the DIAS storage archive.
+API software consists of several tools, including the "Real-time data crawling and archiving system", "Data upload system", "Quality control system", and "Metadata management system" \cite{Kawasaki2018DataReduction}.
+In order to store on the large volume of disk space, it convert the data via provided set of APIs.
+This can be consider same as the open data model provide by the \acrshort{fews}.
+Other than that, \acrshort{dias} consist of additional tools which provide the functionality of quality control of the data, and metadata management which is similar to some of services in \acrshort{lead}.
+
+As shown in figure \ref{fi:dias_common_platform}, it provides an application layer which allows domain scientists to working on research tasks, and to develop specific tools and applications by working together with Information Technology experts.
+\cite{Kawasaki2018DataReduction}.
+Once the data is achieved on the \acrshort{dias} system, it share those details via Shared API layer.
+Thus it allows users to remote access to the data, and easy integration via the APIs.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Meteorological Assimilation Data Ingest System}

### 2020-02-10 lit/sec_3-other-systems.tex
Updated lit summary

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Summary}
 \label{se:lit_summary}
+Several related work that discussed above in this chapter, mainly focus on issue of storing data which are ingest from different sources with different formats efficiently.
+The \acrshort{fews} and \acrshort{madis} are using the \acrshort{netCDF} as the common data format to store the data which is one of best solution available with modern technologies as well.
+Even it is not clearly mentioned, the \acrshort{dias} and \acrshort{lead} also following a method of having common storage space in order to store bulk data.
+\acrshort{fews} and \acrshort{lead} have the capability of handling workflow of forecasting, but other system are mainly focus on providing a weather data management system.
+\acrshort{fews} provide a modular approach via it's general adapter which is shown on figure \ref{fi:fews_general_adapter}, and according to the \acrshort{soa} architecture of \acrshort{lead} provide the same functionality via services.
+
+Most of the above systems develop by many developers and researcher via many of funding.
+And most of them are depend on underline platform, and not up to date with the modern technologies such as Cloud Computing.

### 2020-02-10 lit/sec_1-fews.tex
Updated lit review introduction

@@
 This chapter \ref{ch:literature} presents a Literature review on existing systems and their architecture approach and design with available resources.
-In Section \ref{se:fews}, we present Most influenced systems for \acrshort{wdias} is \acrshort{fews}.
-\acrfull{lead}, \db{an open data handling platform distributed as closed-source software, is presented in Section \ref{se:lead}}.
+In Section \ref{se:fews}, we present most influenced systems for \acrshort{wdias} is \acrshort{fews}.
+\acrfull{lead}, an open data handling platform distributed as closed-source software, is presented in Section \ref{se:lead}.
 \acrshort{lead} is following the \acrfull{soa} for system architecture.
+In Section \ref{se:dias}, we discussed about \acrfull{dias} which is developed by Japanese, and support as a common data platform other than weather data.
+\acrfull{madis} is another widely use data integration system, which also provide data access with quality control, and we discuss in the last Section \ref{se:madis}.
 Under each system we explore both system architecture, scalability and flexibility of the system.
-
-\dbc{Complete above while referring to all major sections with chapter.}
 

### 2020-02-10 method/sec_4-db_struct.tex
Misc fixes on references

@@
 
-\subsubsection{Parameter} - Parameter describe the variable measuring against a location.
-All parameters ahve a unique String identifier called as parameterId.
-A parameter can be use in multiple locations.
+\subsubsection{Parameter}
+Parameter describe the variable measuring against a location. All parameters ahve a unique String identifier called as parameterId. A parameter can be use in multiple locations.
 While defining a parameter, there are three required fields which need to be provided such as variable, unit and parametertype.
@@
     \centering
-    \includegraphics[width=1\textwidth]{method/microservice/hierarchical_database.jpg}
+    \includegraphics[width=0.6\textwidth]{method/microservice/hierarchical_database.jpg}
     \caption{Hierarchical database}
@@
 
-WDIAS is using a hierarchical database, with following the concept of Database per Service which is described in the \ref{micro_database_per_service}.
+WDIAS is using a hierarchical database, with following the concept of Database per Service which is described in the \emph{Database per Service} in Section \ref{subse:database_per_service}.
 Following chapters described the usage of databases in WDIAS and reason behind the selection.
@@
 
-Two instance of \acrshort{influxdb} is using in the WDIAS system by adapter-scalar and adapter-vector services. For the scalability, the system uses \ref{micro_database_per_service}.
-But further, it split into two services, refering to the \ref{micro_z_axis_scaling} data is partitioned among few servers based on valueType key attribute of timeseries.
+Two instance of \acrshort{influxdb} is using in the WDIAS system by adapter-scalar and adapter-vector services.
+For the scalability, the system uses \emph{Database per Service} as mentioned in Section \ref{subse:database_per_service}.
+But further, it split into two services, referring to the Section \ref{subse:scale_cube}, the Z-axis scaling, the data is partitioned among few servers based on valueType key attribute of timeseries.
 Which also conclude the concept of splitting into more services based on other key attributes such as timeseriesType, if further performance required.
@@
 Vise a versa, if new timeseries create in the adapter-metadata, it trigger an event to adapter-query to index the new timeseries.
-\ref{micro_y_axis_scaling} concept is using here by splitting into the multiple services based on the functionality and scale the system.
+In Section \ref{subse:scale_cube}, the Y-axis scaling concept is using here by splitting into the multiple services based on the functionality and scale the system.
 

### 2020-02-10 Appendix/app_1_soa_and_actor_model.tex
Added appendix

--- 2019-12-01 method/sec_2-actor_model.tex
@@
+\section{Service Oriented Architecture}
+\dbc{Use a more meaningful title that reflect the solution.
+Also, why are we talking about an initial phase?
+You can mention that we iterate through several designs.
+But it's not important to discuss each design in detail unless once design is essential to understand the other design.
+Ideally, present only the finalized design while adding a single para for each of the previous attempts.}
+
+In the initial phase of WDIAS architecture, it proposed with a \acrfull{soa} as shown in the \ref{fi:proposed_soa}. Mainly it consist of 4 modules, namely:
+- Import modules
+Import modules are using for integration of data from different source which come in different data formats.
+- Export modules
+Export modules are using for data dissemination with different format which may required for different type of operations.
+- Extension modules
+Extension modules are capable of providing the data assimilation functionalities by providing some of key functionalities such as transformation, interpolation and validation.
+While data assimilation, existing timeseries may be modified or create new timeseries based on the system configurations.
+- Adapter module
+Adapter module is handling the complexity of integrating different data formats and storing them in the way that easy to search and retrieve.
+
+\begin{figure}[htp]
+    \centering
+    \includegraphics[width=1\textwidth]{soa/soa_v1.jpg}
+    \caption{Service oriented architecture of \acrshort{wdias}.}
+    \label{fi:proposed_soa}
+\end{figure}
+
+- \acrfull{esb}
+While implementing a \acrfull{soa}, the \acrfull{esb} can provide capability to integrate different modules, since it is acting as a common layer for all of modules.
+By default, \acrshort{esb} provides pub sub capabilities.
+\acrshort{esb} mediator can be used to integrate the import, export and extension modules. \acrshort{esb} also support different transportation protocols such as HTTP and Web-Socket etc.
+
+But \acrshort{esb} is not a better solution for data streaming or bulk data processing. Also \acrshort{esb} suffer from single point of failure, since all the messages are going though a common bus.
+
 \section{Actor Model}
@@
 https://doc.akka.io/docs/akka/2.5.5/scala/guide/actors-motivation.html
+\dbc{Give the URL as a reference.}
 

### 2020-02-10 summary/sec_1-conclusions.tex
..

@@
 \label{se:summary_conclusion}
-
-\dbc{Expand this section while highlighting key design details and performance}
 
@@
 The system uses timeseries database for storing Scalar and Vector timeseries data, and using \acrshort{netCDF} for storing Grid timeseries data.
-And each database adapter uses concept of database per service which allows each microservice service to scale without inteferance from other microservices.
+And each database adapter uses concept of database per service which allows each microservice service to scale without interference from other microservices.
 And it uses microservice sagas pattern for asynchronous data handling for requests with higher size.

### 2020-02-10 Appendix/app_1_soa_and_actor_model.tex
Removed appendix

--- 2019-12-01 method/sec_2-actor_model.tex
@@
-\section{Actor Model}
+\section{\acrfull{soa} Design}
+
+In the initial phase of WDIAS architecture, it proposed with a \acrfull{soa} as shown in the \ref{fi:proposed_soa_arch_design}. Mainly it consist of 4 modules, namely:
+- Import modules
+Import modules are using for integration of data from different source which come in different data formats.
+- Export modules
+Export modules are using for data dissemination with different format which may required for different type of operations.
+- Extension modules
+Extension modules are capable of providing the data assimilation functionalities by providing some of key functionalities such as transformation, interpolation and validation.
+While data assimilation, existing timeseries may be modified or create new timeseries based on the system configurations.
+- Adapter module
+Adapter module is handling the complexity of integrating different data formats and storing them in the way that easy to search and retrieve.
+
+\begin{figure}[htp]
+    \centering
+    \includegraphics[width=1\textwidth]{method/soa/soa_v1.jpg}
+    \caption{Service oriented architecture of \acrshort{wdias}.}
+    \label{fi:proposed_soa_arch_design}
+\end{figure}
 
 In the second phase of \acrshort{wdias}, the proposed architecture changed to use with Actor model after consider into the disadvantage of using \acrshort{esb}.
-
-Brief about using actor model:
-https://doc.akka.io/docs/akka/2.5.5/scala/guide/actors-motivation.html
-
-The typical SOA model, for example, usually has more dependent ESBs, with microservices using faster messaging mechanisms.
-SOA also focuses on imperative programming, whereas microservices architecture focuses on a responsive-actor programming style.
-Moreover, SOA models tend to have an outsized relational database, while microservices frequently use NoSQL or micro-SQL databases (which can be connected to conventional databases).
-But the real difference has to do with the architecture methods used to arrive at an integrated set of services in the first place.
-(Refer:https://smartbear.com/learn/api-design/what-are-microservices/ )
-
-- Add diagrams for handle on demand
-- Add diagram for handle Async
-
-AKKA vs ESB
-ESB support to implement SOA.
-But SOA has limitations such as single point of failure, slower communication (can’t use for transfer data) etc.
-So, the microservice architecture get evolved and demanding for the moment.
-It has following benefits,
-Follow the Single Responsibility Principle
-Resilient/Flexible – failure in one service does not impact other services. If you have monolithic or bulky service errors in one service/module it can impact other modules/functionality.
-High scalability – demanding services can be deployed in multiple servers to enhance performance and keep away from other services so that they don’t impact other services.
-Will be difficult to achieve the same with single, large monolithic service.
-Easy to enhance – less dependency and easy to change and test
-Low impact on other services – being an independent service, this has less chance to impact other services
-Easy to understand since they represent the small piece of functionality
-Ease of deployment
-Freedom to choose technology – allows you to choose technology that is best suited for a particular functionality

### 2020-02-10 method/sec_3-microservice.tex
use emph
Misc fixes on references
update api

@@
 Each adapter follows the concept of database per service as mentioned in the section \ref{subse:database_per_service}. This gives the freedom for \acrshort{wdias} to scale better with \acrshort{k8s}.
+
 As shown in the figure \ref{fi:wdias_micro_on_demand}, when a smaller size request come to the system, it handle on demand and response back.
 But as shown in figure \ref{fi:wdias_micro_async}, when a request with larger size come to the system, it store the data for asynchronously process the data and response with a unique id which can use to verify whether data processed successfully or not.
+Here is uses the microservice pattern of \ref{subse:sagas} while processing the Grid data.
+First it store the data and respond back to the user.
+Then publish an event, and another service listen to those events and process the data and update the system status.
 
@@
     \begin{itemize}
-        \item \emph{/parameter}
+        \item \emph{GET /parameter} - Get parameters
+        \item \emph{POST /parameter} - Create parameter
+        \item \emph{PUT /parameter/id} - Update parameter
+        \item \emph{DELETE /parameter/id} - Delete parameter
     \end{itemize}
@@
     \begin{itemize}
-        \item \emph{/timestep}
+        \item \emph{GET timestep} - Get TimeSteps
+        \item \emph{POST timestep} - Create TimeStep
+        \item \emph{PUT timestep/id} - Update TimeStep
+        \item \emph{DELETE timestep/id} - Delete TimeStep
     \end{itemize}
@@
     \begin{itemize}
-        \item \emph{/location/point}
-        \item \emph{/location/regularGrid}
+        \item \emph{GET /location} - Get location points
+        \item \emph{POST /location} - Create location point
+        \item \emph{PUT /location/id} - Update location point
+        \item \emph{DELETE /location/id} - Delete location point
+        \item \emph{GET /location/regular-grid} - Get regular grids
+        \item \emph{POST /location/regular-grid} - Create regular grid
+        \item \emph{PUT /location/regular-grid/id} - Update regular grid
+        \item \emph{DELETE /location/regular-grid/id} - Delete regular grid
     \end{itemize}
     \item timeseries
+    \begin{itemize}
+        \item \emph{GET /timeseries} - Get timeseries
+        \item \emph{POST /timeseries} - Create timeseries
+        \item \emph{PUT /timeseries/id} - Update timeseries
+        \item \emph{DELETE /timeseries/id} - Delete timeseries
+    \end{itemize}
 \end{itemize}
@@
 
-\emph{Extensions} endpoints for configure extensions.
-
-These details describes in the section \ref{se:data_preprocess}.
+\emph{Extensions} endpoints for configure extensions. These details describes in the section \ref{se:data_preprocess}.
 

### 2020-02-10 results/sec_1-test_plan.tex
..

@@
 \begin{itemize}
-    \item Throughput - Number of requests that can be process per unit time. Normally for \acrshort{wdias} performance observations, it uses \acrfull{rps} in order to measure the throughput.
-    \item Latency - Time taken for response back to the sent request to the system.
+    \item \emph{Throughput} - Number of requests that can be process per unit time. Normally for \acrshort{wdias} performance observations, it uses \acrfull{rps} in order to measure the throughput.
+    \item \emph{Latency} - Time taken for response back to the sent request to the system.
 Normally it measures with milliseconds (ms) in the \acrshort{wdias}.
@@
 Other than that, it measure the response time into 90\% percentile, while gives best response time up to 90\% percent of the responses.
-    \item Resource Utilization - Resource Utilization is calculated based on the CPU and Memory usage via \acrshort{k8s} metrics server.
+    \item \emph{Resource Utilization} - Resource Utilization is calculated based on the CPU and Memory usage via \acrshort{k8s} metrics server.
 It calculates the resource utilization over 60 seconds of time window.
 Network usage is getting based on the actual physical machines.
-    \item Auto Scaling - The \acrshort{wdias} is running with two configurations.
+    \item \emph{Auto Scaling} - The \acrshort{wdias} is running with two configurations.
 First is, since it is running the microservice as docker containers, it allow to increase or shrink the resource usage and share the resources within a physical machine.

### 2020-02-10 lit/sec_1-fews.tex
Misc fixes on references
image size fix

@@
     \centering
-    \includegraphics[width=0.7\textwidth]{lit/fews/Schematic-structure-of-a-fl-ood-forecasting-system-showing-the-position-of-Delft-FEWS_W640.jpg}
+    \includegraphics[width=0.7\textwidth]{lit/fews/Schematic-structure-of-a-fl-ood-forecasting-system-showing-the-position-of-Delft-FEWS_W640.png}
     \caption[Schematic structure of a flood forecasting system including \acrshort{fews} and links to other primary systems within the operational environment]{Schematic structure of a flood forecasting system including \acrshort{fews} and links to other primary systems within the operational environment \cite{Werner2013TheSystem}.}
@@
 \end{figure}
-\dbc{Most figures are of low quality. You need to make sure figure resolution/quality is not lost. Dot should come after reference no. Fix all places.}
 
@@
     \centering
-    \includegraphics[width=1.0\textwidth]{lit/fews/Architecture-of-Delft-FEWS-showing-the-data-base-the-data-access-layers-and-examples-of_W640.jpg}
+    \includegraphics[width=1.0\textwidth]{lit/fews/Architecture-of-Delft-FEWS-showing-the-data-base-the-data-access-layers-and-examples-of_W640.png}
     \caption[Architecture of \acrshort{fews}]{Architecture of \acrshort{fews} \cite{Werner2013TheSystem}.}
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{lit/fews/Linking-Delft-FEWS-with-external-models-The-fi-gure-shows-the-fl-ow-of-data-through-XML_W640.jpg}
+    \includegraphics[width=0.6\textwidth]{lit/fews/Linking-Delft-FEWS-with-external-models-The-fi-gure-shows-the-fl-ow-of-data-through-XML_W640.png}
     \caption[Linking \acrshort{fews} with external models]{Linking \acrshort{fews} with external models \cite{Werner2013TheSystem}.}

### 2020-02-10 lit/sec_2-lead.tex
image size fix

--- 2020-02-10 lit/sec_2-lead.tex
@@
     \centering
-    \includegraphics[width=1.0\textwidth]{lead/LEAD-system-Fundamental-capabilities-familiar-to-meteorologists-are-shown-in-the-top_W640.jpg}\\
+    \includegraphics[width=1.0\textwidth]{lit/lead/LEAD-system-Fundamental-capabilities-familiar-to-meteorologists-are-shown-in-the-top_W640.png}
     \caption[Layered architecture of LEAD]{Layered architecture of LEAD \cite{Droegemeier2005Service-OrientedWeather}.}
@@
 \end{figure}
-
-\dbc{Fig. 2.4 should use full text width.}
 
@@
     \centering
-    \includegraphics[width=1.0\textwidth]{lead/LEAD-system-framework-LEAD-is-composed-of-several-interacting-subsystems-with-the-LEAD_W640.jpg}\\
+    \includegraphics[width=1.0\textwidth]{lit/lead/LEAD-system-framework-LEAD-is-composed-of-several-interacting-subsystems-with-the-LEAD_W640.png}
     \caption[LEAD system framework]{LEAD system framework \cite{Droegemeier2005Service-OrientedWeather}.}
@@
     \centering
-    \includegraphics[width=1\textwidth]{lead/LEADs-service-oriented-architecture-A-wide-variety-of-services-and-resources-grouped_W640.jpg}\\
+    \includegraphics[width=1\textwidth]{lit/lead/LEADs-service-oriented-architecture-A-wide-variety-of-services-and-resources-grouped_W640.png}
     \caption[LEAD's service-oriented architecture]{LEAD's service-oriented architecture \cite{Droegemeier2005Service-OrientedWeather}.}

### 2020-02-10 results/sec_3-observations.tex
Caption top of table
to lower case

@@
 \begin{table}[ht]
+\caption{Throughput and Latency of load testing with 60min data}
 \footnotesize
@@
 \end{tabulary}
-\caption{Throughput and Latency of All test cases with 60min data}
 \label{tab:obs_all_60_min_summary}
@@
 It performed round up to 311k of sample requests which is almost similar to \ref{subse:obs_test_plan_all_60min} processed samples.
+
 \begin{table}[ht]
+\caption{Throughput and Latency of load test with 30min data}
 \footnotesize
@@
 \end{tabulary}
-\caption{Throughput and Latency of All test cases with 30min data}
 \label{tab:obs_all_30_min_summary}
@@
 \begin{table}[ht]
+\caption{Throughput and Latency of load testing with 15min data}
 \footnotesize
@@
 \end{tabulary}
-\caption{Throughput and Latency of All test cases with 15min data}
 \label{tab:obs_all_15_min_summary}
@@
 \begin{table}[ht]
+\caption{Throughput and Latency of load testing with 15min data while enabled \acrshort{k8s} Auto Scaling}
 \footnotesize
@@
 \end{tabulary}
-\caption{Throughput and Latency of All test cases with 15min data while enabled \acrshort{k8s} Auto Scaling}
 \label{tab:obs_all_auto_15_min_summary}
@@
 \begin{table}[ht]
+\caption{Throughput and Latency of Query test cases with 15min data}
 \footnotesize
@@
 \end{tabulary}
-\caption{Throughput and Latency of Query test cases with 15min data}
 \label{tab:obs_query_15_min_summary}

### 2020-02-10 summary/sec_2-research_limitations.tex
Finalize the Thesis

@@
 \emph{Grid data performance}:
-As mentioned in the \ref{se:conclusion}, the adapter-grid is using a Python wrapper for netCDF FORTRAN implementation with parallel IO enabled.
+As mentioned in the \ref{se:discussion}, the adapter-grid is using a Python wrapper for netCDF FORTRAN implementation with parallel IO enabled.
 This has some performance issues as well as memory leak issues.
@@
 \emph{Further improve hierarchical database performance}:
-As further described in \ref{se:conclusion}, it is possible to increase the performance of these bottlenecks much higher such as using \acrshort{influxdb} Commercial cluster support for high availability or horizontal scaling of \acrshort{influxdb}.
+As further described in \ref{se:discussion}, it is possible to increase the performance of these bottlenecks much higher such as using \acrshort{influxdb} Commercial cluster support for high availability or horizontal scaling of \acrshort{influxdb}.
 With \acrshort{influxdb} cluster, it is possible to run multiple pods of adapter-scalar and adapter-vector for support more server hits per second.

### 2020-02-10 Paper.tex
to lower case
Fix: paper compilation

@@
 % The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
-\usepackage{cite}
 \usepackage[acronym]{glossaries}
@@
 \usepackage{xcolor}
+\usepackage{listings}
+\usepackage{biblatex}
+
+\addbibresource{mendeley.bib}
+
+\definecolor{codegreen}{rgb}{0,0.6,0}
+\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
+\lstdefinestyle{code-style}{
+  backgroundcolor=\color{backcolour}, commentstyle=\color{codegreen},
+  basicstyle=\ttfamily\footnotesize,
+  breakatwhitespace=false,         
+  breaklines=true,                 
+  captionpos=b,                    
+  keepspaces=true,                 
+  numbers=left,                    
+  numbersep=5pt,
+  showspaces=false,
+  showstringspaces=false,
+  showtabs=false,                  
+  tabsize=2
+}
+\lstset{style=code-style}
+
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 \begin{table}[htbp]
-\caption{Table Type Styles}
+\caption{Table type styles}
 \begin{center}
@@
 \input{glossary.tex}
-\bibliographystyle{plain}
-\bibliography{mendeley}
+% \bibliographystyle{plain}
+% \addbibresource{mendeley.bib}
+\printbibliography[title={References}]
 

### 2020-02-11 Paper.tex
After 2nd review

@@
 \usepackage{biblatex}
+
+\usepackage{todonotes}
+\newcommand{\db}[1]{\textcolor{blue!40}{#1}}
+\newcommand{\dbc}[1]{\todo[author=Dilum, inline, color=blue!40]{#1}}
 
@@
 \author{\IEEEauthorblockN{Gihan Karunarathne}
-\IEEEauthorblockA{\textit{dept. computer science and Engineering} \\
-\textit{university of moratuwa}\\
-Moratuwa, Sri Lanka \\
+\IEEEauthorblockA{\textit{Dept. Computer Science and Engineering} \\
+\textit{University of Moratuwa}\\
+Katubedda, Sri Lanka \\
 gihan.09@cse.mrt.ac.lk}
 \and
-\IEEEauthorblockN{Dr. Dilum Bandara}
-\IEEEauthorblockA{\textit{dept. computer science and Engineering} \\
-\textit{university of moratuwa}\\
-Moratuwa, Sri Lanka \\
+\IEEEauthorblockN{H.M.N. Dilum Bandara}
+\IEEEauthorblockA{\textit{Dept. Computer Science and Engineering} \\
+\textit{University of Moratuwa}\\
+Katubedda, Sri Lanka \\
 dilumb@cse.mrt.ac.lk}
+\and
+\IEEEauthorblockN{Srikantha Herath}
+\IEEEauthorblockA{\textit{Center for Urban Water, Sri Lanka} \\
+%\textit{Center for Urban Water, Sri Lanka}\\
+Battaramulla, Sri Lanka \\
+admin@curwsl.org}
 }
@@
 \begin{abstract}
-We describe our experience with implementing an extendable open source Weather Data Integration and Assimilation System, which is known as \acrshort{wdias}.
+%We describe our experience with implementing an extendable open source Weather Data Integration and Assimilation System, which is known as \acrshort{wdias}.
 It uses the modern architecture pattern such as microservice in order to achieve the scalability, rather using monolithic architecture or client service architecture.
@@
 Later we analyse the performance test observations with the performance metrics.
+
+\db{Numerical Weather Models (NWMs) utilize data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images.
+Prior to using such multimodal data into a NWM, it is necessary to transcode data into a format that can be ingested by the NWM.
+Moreover, the data integration system’s response time needs to be relatively low to forecast and monitor time-sensitive weather events like hurricanes, storms, and flash floods that require rapid and frequent execution of NWMs.
+The resulting weather data also need to be accessed by many researchers and third-party applications.
+Even though there are several weather data integration systems, they are based on monolithic or client-server architectures and are unable to benefit from novel computational models such as cloud computing and containers.
+Moreover, most of this software is proprietary or closed sourced; hence, it is difficult to customize such software for an island like Sri Lanka with different weather seasons.
+Therefore, in this research, we propose Weather Data Integration and Assimilation System (WDIAS) that utilizes modern architecture pattern such as microservices to achieve scalability, high availability, and low-cost operation based on cloud computing.
+WDIAS provides a modular architecture to integrate data from different sources, export into different formats, and the inbuilt extension module system allow users to add new features.
+We demonstrate the utility of WDIAS using cloud-based experimental setup and weather-related synthetic workloads.}
 \end{abstract}
@@
 \begin{IEEEkeywords}
-\acrshort{wdias}, weather, microservice, kubernetes, hierarchical database 
+\db{Data assimilation, data integration, hierarchical databases, microservice, weather}
 \end{IEEEkeywords}
@@
 \section{INTRODUCTION}
-I'm going to do this today \cite{Haggett1998AnWales}.
+%I'm going to do this today \cite{Haggett1998AnWales}.
 Give general idea on weather data integration systems.
@@
 TODO: Specify the \acrshort{lead} service as a building block approach. \acrshort{fews} more modular approach with general adapter. And \acrshort{wdias} using microservice as module.
-Similar to the \acrfull{fews} \cite{WERNER2004DELFT-FEWS:SYSTEM}
+Similar to the \acrfull{fews} \cite{Werner2013TheSystem}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Modules of Weather Data System}
-The figure \ref{fi:wdia_components} shows the basic functions of a Weather data integration and assimilation system.
+\section{\db{Background}}
+%\section{Modules of Weather Data System}
+Fig. \ref{fi:wdia_components} shows the basic functions of a Weather data integration and assimilation system.
 \begin{figure}[htbp]
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Structure of \acrshort{wdias}}
+\section{\acrfull{wdias} Architecture}
+%\section{Structure of \acrshort{wdias}}
 \begin{figure}[htbp]
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Performance Analysis}
-
+\section{Performance \db{Evaluation}}
+%\section{Performance Analysis}
 \subsection{Test Plan and Workload}
@@
 \section{Strengths and Limitations}
+\dbc{Make this the dicussion and a sub-section of Sec. 4}
+
 \paragraph{Lack of data preprossessing modules}
@@
 \section{Summary}
+\dbc{Summary is too long. Should not be more than a single para}
 To enhance the accuracy of the weather prediction, it is required to have reliable weather data for \acrshort{nwm}.
@@
 \section*{Acknowledgment}
-
-The preferred spelling of the word ``acknowledgment'' in America is without 
-an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
-G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
-acknowledgments in the unnumbered footnote on the first page.
+\db{This research is supported in part by the grant from the Center for Urban Water, Sri Lanka.}
 

### 2020-02-11 introduction/sec_1-motivation.tex
After 2nd review

@@
-Weather prediction can use to reduce the lost in natural disasters and in order to gain more advantage over the natural resources like water management.
-The weather predictions are performed via \acrfull{nwm} by providing different configurations and the current status of the environment such as temperature, rainfall, and wind direction etc.
-For weather prediction \acrfull{wrf} model is used for predicting the rain fall, temperature, and wind direction etc.
-Then using the real time observations, the correct model is selected and after removing the bias, extract the information and feed into the next models.
-There are lots of \acrshort{nwm} available there, but another example can be taken as FLO2D which can be used to predict the water level on the ground.
-For the corresponding model developed based on the geo data, giving the current status of water levels and forecasted rainfall, the model predict the forecasted water level.
+Weather prediction is essential to reduce impact due to natural disasters and to gain effectively manage natural resources like water.
+The weather predictions/forecasts are performed using \acrfull{nwm} that use a set of configuration parameters and the current status of the environment such as temperature, rainfall, and wind direction as the input.
+For example, the \acrfull{wrf} model is used to predict the rainfall, temperature, and wind direction.
+Typically multiple \acrshort{nwm} are executed on the same data with different configuration parameters.
+Then using the real-time observations, the correct model is selected.
+After removing the bias, the extract information is then fed into the next set of models.
+\db{There are lots of \acrshort{nwm} available there, but another example can be taken as FLO2D which can be used to predict the water level on the ground.
+For the corresponding model developed based on the geo data, giving the current status of water levels and forecasted rainfall, the model predicts the forecasted water level.}
+\dbc{Highighted part doesn't make much sense to me. Need to be reworded.}
+\dbc{cite both NWM and WRF}
 
-CUrW SL is a government ministry which is working on weather data forecasting for Sri Lanka in order to reduce the natural disaster effects in Sri Lanka.
-In order to do that, it is implementing its own system with the idea of long term maintainability rather depend on existing vendors.
-It collected real time weather data from weather stations and other government entities, and do the forecasting daily.
-Then the generated results are shared to the trusted parties.
-One of the future goals of CUrW SL to open up to the public to share the data, and use of the processed data via their system for the betterment of the society.
+Center for Urban Water, Sri Lanka (CUrW-SL) is tasked with the mission to reduce water-related natural disasters in Sri Lanka.
+CURW-SL is implementing its own system with the idea of long-term maintainability rather depend on existing weather data integration systems.
+It collected real-time data from weather stations and other government entities and generates daily forecasts.
+Then the generated results are shared with relevant public departments responsible for disaster planning, mitigation, and management.
+One of the future goals of CUrW-SL is to open up data to the public enabling both societal and commercial use cases.
+% and , and use of the processed data via their system for the betterment of the society.
 The institute is operating via the paid TAX of Sri Lankan, and its trying to improve the quality of the life and the economic lost which are effected on the country via sharing the data for external parties to use of them.
@@
 \section{Motivation}
-To enhance the accuracy of weather predictions, it is necessary to provide reliable and detailed weather data as inputs to \acrfull{nwm}.
+To enhance the accuracy of weather predictions, it is necessary to provide reliable and detailed weather data as inputs to \acrshort{nwm}.
 These NWMs utilize multi-modal weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images.
@@
 Given the above facts, there is a necessary for such a systems to be implemented.
+
+\dbc{Citations need to be given for DIAS, WDIA, FEWS, FLOW2D, etc.
+By the way, don't remove my comments (you are welcome to comment on them).
+I need them to check whether those are addressed.
+When I see them addressed, I'll remove comments.}

### 2020-02-11 introduction/sec_2-problem_and_objectives.tex
After 2nd review

--- 2020-02-09 introduction/sec_2-problem_and_objectives.tex
@@
 \section{Problem Statement}
-Handling spatio-temporal weather data is challenging.
-Need an extendable system to support weather models by efficiently storing and retrieving data.
-Therefore, in this context the problem can be state as;
-\emph{necessaty of a Data Integration System which is scalable, highly available and capable of 
-interact with different data formats including spatio-temporal bulk stream data, 
-store efficiently while optimizing the disk space,
-support geographical and time-base queries,
-third parties can access the data with easy integration, and
-able to easy modify and use based on the requirements.
-}
+Handling spatio-temporal weather data is challenging \db{as ...}.
+Moreover, the data integration system needs to be capable of interacting with different data formats including spatio-temporal bulk stream data.
+Furthermore, it should support geographical and time-base queries, as well as provide third-party access to data with easy integration.
+Scalability and high availability are also essential to support different use cases and mission-critical nature of applications.
+Therefore, we need an extendable system to support weather models by efficiently ingesting, storing, and retrieving data.
+In this context, the research problem can be stated as follows:
+
+\emph{....}
+\dbc{Give a proper problem statement.}
 
 \section{Objectives}
-We address above problem statement by achieving the following objectives:
+We address above problem statement by achieving the following research objectives:
 \begin{itemize}
@@
     \item To optimize schema to support data queries based on geography and time
-    \item To develop an API to share data
-    \item To use open source tools and provide the source publicly with appropriate liecense.
+    \item To develop an API for third-party data sharing
+%    \item To use open source tools and provide the source publicly with appropriate liecense.
 \end{itemize}

### 2020-02-11 introduction/sec_3-outline.tex
conc to summary
Misc fixes on references
After 2nd review

--- 2020-02-09 introduction/sec_3-outline.tex
@@
 The rest of the thesis is organized as follows.
-Literature review is presented in Chapter \ref{ch:literature}.
+Literature review is presented in Chapter \ref{ch:literature}, and discuss about the existing Weather Data Integration Systems such as \acrshort{lead}, \acrshort{fews}, \acrshort{madis}, and \acrshort{dias}.
 Solution approach with the proposed system architectures and adaptation with problem occurred are presented in Chapter \ref{ch:method}.
-Performance analysis is presented in Chapter \ref{ch:results} while summary and future work are presented in Chapter \ref{ch:conc}.
-\dbc{Expand a bit by adding at least 1 more sentence for each chapter.}
+It provides details about how the \acrshort{wdias} is design by following a microservice architecture and the date preprocessing capabilities of the system.
+Performance analysis is presented in Chapter \ref{ch:results}.
+Here we discuss experiment setup of the \acrshort{wdias} and analyze the observations with respect to performance metrics.
+Finally, in Chapter \ref{ch:summary}, we conclude and summarize the work and further discussed about the research limitations and future work.

### 2020-02-11 lit/sec_1-fews.tex
Updates from Overleaf
After 2nd review

@@
-There are many of Weather forecasting, assimilation and dissemination systems developed by some of developed countries around the world as a result of trying to reduce the damage causing by natural disasters such as flood, storms, hurricanes, and even for drought.
-Such natural disasters heavily affected on the economy and the life conditions of the country, researchers have developed systems and many of these systems are using as proprietary systems.
-Other countries also using those systems and adopt with own version of system which effective for the specific weather condition in a particular country.
-This chapter \ref{ch:literature} presents a Literature review on existing systems and their architecture approach and design with available resources.
-In Section \ref{se:fews}, we present most influenced systems for \acrshort{wdias} is \acrshort{fews}.
+Several weather forecasting, assimilation, and dissemination systems are developed to reduce the damage causing by natural disasters such as flood, storms, hurricanes, and even droughts.
+%Such natural disasters heavily affected on the economy and the life conditions of the country, researchers have developed systems and many of these systems are using as proprietary systems.
+Other countries are also using those systems while adopting them %with own version of system which effective for the 
+to specific weather condition.% in a particular country.
+This chapter presents a literature review on existing systems and their architecture approach and design.
+In Section \ref{se:fews}, we present \acrshort{fews}.
 \acrfull{lead}, an open data handling platform distributed as closed-source software, is presented in Section \ref{se:lead}.
-\acrshort{lead} is following the \acrfull{soa} for system architecture.
-In Section \ref{se:dias}, we discussed about \acrfull{dias} which is developed by Japanese, and support as a common data platform other than weather data.
-\acrfull{madis} is another widely use data integration system, which also provide data access with quality control, and we discuss in the last Section \ref{se:madis}.
-Under each system we explore both system architecture, scalability and flexibility of the system.
+% \acrshort{lead} is following the \acrfull{soa} for system architecture.
+In Section \ref{se:dias}, we discussed about \acrfull{dias} which is a common data platform that can work with weather data.
+\acrfull{madis} is another widely use data integration system, which also provide data access with quality control, whihc we discuss in Section \ref{se:madis}.
+Under each system we explore both system architecture, scalability, and flexibility of the system.
 
@@
 
-In figure \ref{fi:fews_schematic} show a schematic view of the connection between the forecasting system to real time data acquisition systems and dissemination systems.
+In \db{Figure} \ref{fi:fews_schematic} show a schematic view of the connection between the forecasting system to real time data acquisition systems and dissemination systems.
 The widely using concept is using meteorological forecast data to get precipitation and, then using hydrological and hydraulic model chain to predict the level affect on the ground.
@@
 Basically ground should be analyze geographically and divide into the catchments.
-Based on the affected catchment, it can be further divide into sub areas in order to reduce the complexity of the simulation task.
+Based on the affected catchment, it can be further divide into sub areas to reduce the complexity of the simulation task.
 Ideally the forecasting system should therefore be flexible to allow change to models and data, while keeping the way forecasters work with it as constant as possible.
+\dbc{F is capital and T is capital when referring to Figures and Tables. Fix all other places.}
 
@@
 Given above drawback on storing the data in the system, within the \acrshort{fews} data model, time series are uniquely identified by their location and data type, as well as an id related to the source of the data (e.g., the external source or hydrological model of which the time series are a result) \cite{Werner2013TheSystem}.
-This gives an opportunity to index the data base on above key fields and store the data separately, in order to take the advantage of putting multiple data resources into the system.
+This gives an opportunity to index the data base on above key fields and store the data separately, to take the advantage of putting multiple data resources into the system.
 As an example, instead of storing the data at a single timeseries table, it is possible to separate and index the database based on source such as external source or hydrological model of which the time series are a result.
@@
 This a vital feature in a forecasting system, and affect on the quality and accuracy of the predicted data outputs.
-Because of the common data model concept in the \acrshort{fews}, data processing via these function is much effective.
-The system is self provided some of the generic functions for data processing, but for more complex algorithms can be developed as a new Java class coded to communicate with the application programming interface (API).
-It obvious that for additional feature integration, user should implement the new functional extensions via Java programming language.
+Because of the common data model concept in \acrshort{fews}, data processing via these function is much effective.
+The system is self provided some of the generic functions for data processing, but for more complex algorithms can be developed as a new Java class coded to communicate with the {application programming interface (API)}.
+It is obvious that for additional feature integration, user should implement the new functional extensions via Java programming language.
 Users does not have the flexibility of develop with some other languages they are familiar with or use the support from another language.
 As an example, Python language is easy to use for beginners and many of data scientists are using this programming language for development and it has many data available libraries for data processing.
-But in the \acrshort{fews} users do not ave the capability to take the advantage of such existing things.
+But in \acrshort{fews}, users do not ave the capability to take the advantage of such existing things.
+\dbc{Define Abb. for API in Chapter 1.}
 
@@
 Most of the library of functions provided work equally on scalar and gridded time series.
-As with all other modules this communicates with the database solely through the data access layer as shown in \ref{fi:fews_data_layer} \cite{Werner2013TheSystem}.
+As with all other modules this communicates with the database solely through the data access layer as shown in \db{Section} \ref{fi:fews_data_layer} \cite{Werner2013TheSystem}.
 As it shown in the figure, it is clearly showing that, the system is depends on single database and via the data access layer all the requests are coming to the database though a connection.
-It is possible to setup and connect to a enterprise level database with clustering and shading as a paid solution, in order to serve many requests as possible.
+It is possible to setup and connect to a enterprise level database with clustering and shading as a paid solution, to serve many requests as possible.
 But the design it self inherently suffer with the database bottleneck which effected on running a large set of timeseries or models.
+\dbc{When referring to a section you need to use the word "Section" as highlighted above. Fix all other places.}
 
@@
     \centering
-    \includegraphics[width=0.6\textwidth]{lit/fews/Linking-Delft-FEWS-with-external-models-The-fi-gure-shows-the-fl-ow-of-data-through-XML_W640.png}
+    \includegraphics[width=0.8\textwidth]{lit/fews/Linking-Delft-FEWS-with-external-models-The-fi-gure-shows-the-fl-ow-of-data-through-XML_W640.png}
     \caption[Linking \acrshort{fews} with external models]{Linking \acrshort{fews} with external models \cite{Werner2013TheSystem}.}
@@
 This part of the system feature is not focus on the \acrshort{wdias} and user has to come up with own flow or use existing scientific flow management system.
-But it is a concept that need to be discuss and understand properly in order to design a data integration and assimilation system.
+But it is a concept that need to be discuss and understand properly to design a data integration and assimilation system.
 
@@
 This includes the use of binary-XML files, streaming files through memory, and the use of \acrshort{netCDF} files.
-But far as for users it seems to be adding more complexity and context in order to get higher performance via the system.
+But far as for users it seems to be adding more complexity and context to get higher performance via the system.
 
@@
 The forecasting process is often a sequence of steps, starting with the import of data, a number of data processing and modeling steps, and culminating in the generation of products to be disseminated to the warning process.
-This is supported via the work flow process in the \acrshort{fews}.
+This is supported via the work flow process in \acrshort{fews}.
 The scope of the \acrshort{wdias} is not focus on adding such a feature in the system, rather user have to use scientific work flow management system or come up with own version of work flow.
 
-When running sequential steps within a work flow in \acrshort{fews}, each step is run for the full time window required (e.g.,the lead time of the forecast) before moving on to the next step.
+When running sequential steps within a work flow in \acrshort{fews}, each step is run for the full time window required (e.g., the lead time of the forecast) before moving on to the next step.
 This precludes tightly coupling of models, even explicitly \cite{Werner2013TheSystem}.

### 2020-02-11 lit/sec_3-other-systems.tex
After 2nd review

@@
 APIs work to convert or re-format data into manageable forms and are useful in creating the DIAS storage archive.
-API software consists of several tools, including the "Real-time data crawling and archiving system", "Data upload system", "Quality control system", and "Metadata management system" \cite{Kawasaki2018DataReduction}.
-In order to store on the large volume of disk space, it convert the data via provided set of APIs.
+API software consists of several tools, including the real-time data crawling and archiving system, data upload system, quality control system, and metadata management system \cite{Kawasaki2018DataReduction}.
+To store on the large volume of disk space, it convert the data via provided set of APIs.
 This can be consider same as the open data model provide by the \acrshort{fews}.
@@
 
-As shown in figure \ref{fi:dias_common_platform}, it provides an application layer which allows domain scientists to working on research tasks, and to develop specific tools and applications by working together with Information Technology experts.
-\cite{Kawasaki2018DataReduction}.
+As shown in figure \ref{fi:dias_common_platform}, it provides an application layer which allows domain scientists to working on research tasks, and to develop specific tools and applications by working together with Information Technology experts \cite{Kawasaki2018DataReduction}.
 Once the data is achieved on the \acrshort{dias} system, it share those details via Shared API layer.
@@
 
+\dbc{In Fig. 2.8, is it the data flow?}
+
 \acrshort{madis} comprises a distributed architecture for ingest, processing, and data distribution functions.
@@
 As it mentioned above, the \acrshort{madis} is implemented based on a distributed architecture which is available at the time of it's development.
-Even it is not clear mentioned, it is using functional call like Remote procedure call (RPC) in order to invoke among a cluster of nodes as shown in figure \ref{fi:madis_flow}.
-In order to get High Availability, it has added some update to it's architecture.
+Even it is not clear mentioned, it is using functional call like Remote Procedure Call (RPC) to invoke among a cluster of nodes as shown in figure \ref{fi:madis_flow}.
+To get high availability, it has added some update to it's architecture.
 The conclusion of this statement is, these kind of functionalities are available at the modern the Cloud Computing tools, and out of the box those tools are providing the scalability and high availability.
@@
 Most of the above systems develop by many developers and researcher via many of funding.
-And most of them are depend on underline platform, and not up to date with the modern technologies such as Cloud Computing.
+And most of them are depend on underline platform, and not up to date with the modern technologies such as cloud computing.

### 2020-02-11 method/sec_0_introduction.tex
Misc fixes on references
After 2nd review

@@
-This chapter includes the design decision taken while implementing the \acrfull{wdias}, and how is the system got adapted from the systems analyzed in Chapter \ref{ch:literature}, then how is it trying to propose a better system with overcoming the issues.
-In the section \ref{se:high_level_design}, it give a brief disussion on how the weather forecasting is happening, and why it need to interact with multiple data formats.
+This chapter includes the design decision taken while implementing the \acrfull{wdias}, and how is the system got adapted from the systems analyzed in Chapter \ref{ch:literature}.
+%, then how is it trying to propose a better system with overcoming the issues.
+In Section \ref{se:high_level_design} a brief discussion on how the weather forecasting is happening and why it need to interact with multiple data formats is presented.
 Then following subsections define few termelogy which are using in the \acrshort{wdias}, and scope of the thesis.
-Following section \ref{se:architectural_decisions} that we evolve over while designing and implementing the \acrshort{wdias}.
+Section \ref{se:architectural_decisions} that we evolve over while designing and implementing the \acrshort{wdias}.
 The section \ref{se:microservice} gives better understanding of the microservice architectural concepts follows while implementing the \acrshort{wdias}.
@@
 Throw out the section \ref{se:data_preprocess} discussed about how the \acrshort{wdias} enable for data preprocessing and adding capabilities via concept of Extensions.
-Last section \ref{se:query} includes details on how to perform timeseries search and geo based queries.
+Finally, in Section \ref{se:query} includes details on how to perform timeseries search and geo based queries.
 
@@
 
-In order to get overall idea on the flow of weather prediction, lets look into one of flows using in \acrshort{curw} \cite{CUrWSL2017SL}.
-\begin{itemize}
+To get overall idea on the flow of weather prediction, let us look into one of flows using in \acrshort{curw} \cite{CUrWSL2017SL}.
+\dbc{Use CUrW-SL}
+
+\begin{enumerate}
     \item Extract GRIB WRF model data to netCDF
     \item From netCDF to CSV of each location data, then feed to HEC-HMS and get the output as CSV
-    \item CSV + Rain cell Grid feed into the FLO2D, and get the water level as Grid ASCII files after completion of simulation
+    \item CSV and Rain cell Grid feed into the FLO2D, and get the water level as Grid ASCII files after completion of simulation
     \item Upload ASCII files to ArcGIS create Raster files, then use for the LOSS Estimation
-\end{itemize}
+\end{enumerate}
 When looked into the above flow, it clear understanding on multiple data formats using while weather predictions.
-Other than that, in order to correct the model outputs, it required to collect real time data such as;
+Other than that, to correct the model outputs, it required to collect real time data such as;
 \begin{itemize}
@@
 Other than above there are many data formats using for handling data based on devices and standards which are using.
-Also for data modeling, it needs to convert the data into model compatible data format, then after successfully run the model it needs to collect data from the model output data formats.
+Also, for data modeling, it needs to convert the data into model compatible data format, then after successfully run the model it needs to collect data from the model output data formats.
 
-\subsection{Modules of Weather Data Integration System}
+\subsection{Modules of Weather Data System}
 \label{subse:modules_weather_data_integration_sys}
 
-The figure \ref{fi:wdia_components} shows the basic functions of a Weather data integration and assimilation system.
+Figure \ref{fi:wdia_components} shows the basic functions of a Weather data integration and assimilation system which consists of the following modules:
 \begin{figure}[htbp]
-\centerline{\includegraphics[width=0.5\textwidth]{method/misc/weather_data_system_components.jpg}}
+\centerline{\includegraphics[width=0.8\textwidth]{method/misc/weather_data_system_components.jpg}}
 \caption{Components of a weather data system.}
@@
 \end{figure}
-\subsubsection{Integration}
-The system should capable of integrating data from different source such as satellite data, high end and low end weather station etc.
+
+\paragraph{Integration}-- The system should capable of integrating data from different source such as satellite data, high end and low end weather station etc.
 And the system should be able to handle multidimensional spatial and temporal weather data efficiently and optimally.
@@
 Also those models reproduce large set of redundant data, thus system should store the bulk data while optimizing the disk space.
-\subsubsection{Dissemination}
-Then different users should be able to retrieve data as they required.
+\paragraph{Dissemination}-- Then different users should be able to retrieve data as they required.
 Also the users should be able to easy to search into the available that in the system base on timeseries metadata or based on Geo queries.
 
-\subsubsection{Timeseries}
-A timeseries is simply a series of data points ordered in time. In weather domain, it interest in timeseries in perspective of observations to forecasting.
+\paragraph{Timeseries}-- A timeseries is simply a series of data points ordered in time.
+In weather domain, it interest in timeseries in perspective of observations to forecasting.
 Each timeseries, the data points can be form in different formats as well.
-\begin{itemize} 
-    \item Scalar - 0D
-    \item Vector - 1D
-    \item Grid - 2D
-    \item Polygon - 2D
-\end{itemize}
+For example, Scalar (0D), Vector (1D), Grid (2D), and Polygon (2D).
 
@@
 \subsubsection{Base of WDIAS architecture}
+\dbc{What's Base of WDIAS architecture?}
 The base of WDIAS architecture origins based on attributes of a timeseries.
@@
 \begin{itemize}
-    \item Module - module that generate the timeseries
-    \item Value Type - Scalar, Vector, Grid, Polygon
+    \item Module -- module that generate the timeseries
+    \item Value type -- Scalar, Vector, Grid, Polygon
     \item Location 
-    \item Parameter - measuring parameter of timeseries
+    \item Parameter -- measuring parameter of timeseries
     \item Timeseries type
     \begin{itemize}
-        \item sources - External, Simulated
-        \item category - Historical, forecast
+        \item sources -- External, Simulated
+        \item category -- Historical, forecast
     \end{itemize}
@@
 \end{itemize}
+\dbc{Use bullets only when essential. Other places use paragraphs.}

### 2020-02-11 results/sec_2-workload.tex
Caption top of table
After 2nd review

@@
 \begin{table}[ht]
+\caption{\acrshort{eks} nodes}
 \footnotesize
@@
 \end{tabular}
-\caption{\acrshort{eks} nodes}
 \label{tab:aws_eks_nodes}
@@
 
-\dbc{- e.g., diagram indicating the nodes and their connectivity (load generator, target, storage, etc.), Then briefly describe the diagram.}
+\begin{figure}[htp]
+    \centering
+    \includegraphics[width=0.6\textwidth]{results/work_load/eks_node_setup.jpg}
+    \caption{\acrfull{eks} node setup}
+    \label{fi:eks_node_setup}
+\end{figure}
 
@@
 \end{itemize}
+Figure \ref{fi:eks_node_setup} show the overview of show the nodes are setup and each microservices are assigned to each node, the connectivity of the nodes, and the data interactions via the arrows.
 The databases uses for data consistency and performance in storage optimization with search capabilities.

### 2020-02-11 thesis.tex
Misc fixes on references
Added appendix
Removed appendix
After 2nd review

@@
 \acrfull{nwm} utilize data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images.
-Prior to using such multimodal data into respective \acrshort{nwm}, it is necessary to transcode into a format that can be ingested by the \acrshort{nwm} modal.
+Before using such multimodal data into a NWM, it is necessary to transcode data into a format that can be ingested by the NWM.
 Moreover, the data integration system's response time needs to be relatively low to forecast and monitor time-sensitive weather events like hurricanes, storms, and flash floods that require rapid and frequent execution of \acrshort{nwm}.
-Later such weather data needs to be accessed by many third-party applications and research in order to make use of them.
-Thus the system should provide easy protocol to integrate with external systems, and should be capable of handling the workload.
-For example, logistic companies could use those data within their models to plan and schedule deliveries.
+The resulting weather data also need to be accessed by many researchers and third-party applications such as logistic companies and agricultural insurance.
+%Thus, the system should provide a simple protocol to integrate with external systems.
+%For example, logistic companies could use those data within their models to plan and schedule deliveries.
 Agricultural insurance companies can warn the farmers in advance, as well as calculate premiums based on anticipated weather patterns.
-
-Even though there are many data integration systems, most of them are proprietary or close sourced.
-Which means for an island like Sri Lanka that having different kinds of weather seasons over the year than those software originated need to be highly customized.
+Even though there are several weather data integration systems, they are based on monolithic or client-server architectures and are unable to benefit from novel computational models such as cloud computing and containers.
+Moreover, most of this software is proprietary or closed sourced; hence, it is difficult to customize such software for an island like Sri Lanka with different weather seasons.
+%than those software originated need to be highly customized.
 Throughout the operations and maintenance, it is required to get support with paying lots of charges, and difficult to debug into a closed source system without maintenance support from the vendors.
 And most of the software existing out there is not up to date with the latest technology concepts such as Cloud Computing.
-\acrfull{wdias} uses the modern architecture pattern such as microservice in order to achieve scalability, rather using monolithic architecture or client service architecture.
-
-It provides a modular approach to integration of data from different sources and export into different formats, and inbuilt extension module system allow users to add new features.
-Since each module follows the stateless and failover microservice integrate with new Cloud Computing tools, the proposed solution comes with the scalability and high availability into large extend out of the box.
-The proposed solution is independent of the platform which most software out there is not and independent of Cloud Platform providers which give much flexibility for the users to decide the best cost effective way to host it.
+\db{Therefore, in this research, we propose \acrfull{wdias} that utilizes modern architecture pattern such as microservices to achieve scalability, high availability, and low-cost operation based on cloud computing.
+\acrshort{wdias} provides a modular architecture to integrate data from different sources, export into different formats, and the inbuilt extension module system allow users to add new features.
+Due to the use of stateless microservices, \acrshort{wdias} achieves high scalability, availability, and enables the addition of new features on the fly with rollover capabilities.
+We demonstrate the utility of \acrshort{wdias} using cloud-based experimental setup and weather-related synthetic workloads.}
+%Because each module follows the stateless and failover microservices integrate with new Cloud Computing tools, the proposed solution comes with the scalability and high availability into large extend out of the box.
+The proposed solution is independent of the cloud platform which most software out there is not and independent of Cloud Platform providers which give much flexibility for the users to decide the best cost effective way to host it.
 And the auto scaling feature allows users to run \acrshort{wdias} from 1 CPU node to nodes with a few hundred CPUs.
@@
 
+\dbc{Increase line space to 1.5}
 \vspace{4mm}
 
-\textbf{Keywords:} Cloud Computing, Data Management system, Distributed,  Highly Available, Scalable, Timeseries, Weather
+\textbf{Keywords:} Cloud computing, \db{data assimilation, data integration, hierarchical databases, microservice, weather}
+%Cloud Computing, Data Management system, Distributed,  Highly Available, Scalable, Timeseries, Weather
 }
@@
 
+\dbc{Need to ACK CUrW for grant.}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \printglossary[style=custom-glossary-style, type=\acronymtype, title=List of Abbreviations, toctitle=List of Abbreviations, nonumberlist]
-
+\dbc{Make sure line spacing is consistent here.}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\appendix
-\chapter{First Appendix}
-Type out your first appendix here.
-\section{Basics}
-
-\chapter{First Appendix}
-Type out your second appendix here.
+% \appendix
+% \import{Appendix/}{app_1_soa_and_actor_model.tex}
 

### 2020-02-11 method/sec_3-microservice.tex
Reviewed again after PGS reject

@@
 
-The microservice architectural style is an approach to developing a single application as a suite of small services, each running in its own process and communicating with lightweight mechanisms, often an HTTP resource API.
+The microservice architectural style is an approach to developing a single application as a suite of small services, each running in its own process and communicating with lightweight mechanisms, often \hl{an HTTP resource API}.
 These services are built around business capabilities and independently deployable by fully automated deployment machinery.
-There is a bare minimum of centralized management of these services, which may be written in different programming languages and use different data storage technologies \cite{LewisMicroservices}.
+\hl{There is a bare minimum of centralized management of these services, which may be written in different programming languages and use different data storage technologies} \cite{LewisMicroservices}.
 
-Among the characteristics of \acrfull{microservice}, few characteristics heavily affect while moving from \acrshort{soa} to \acrshort{microservice}.
+\hl{Among the characteristics of microservice, a few characteristics heavily affect while moving from} \acrshort{soa} to microservice.
+\dbc{M in Microservice should be capitalized only on begining of a sentence.}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Smart Endpoints And Dumb Pipes}
+\subsection{Smart Endpoints and Dumb Pipes}
 \label{subse:dumb_pipes}
-When building communication endpoints, many architecture approach with putting significant smart into the communication mechanism.
-One good example is \acrshort{esb} what we discussed in section \ref{se:architectural_decisions}.
+\dbc{At the end of previous para tell what will be discussed in the next set of sub-section. A single sentence like "Next, we will discusss ...." is enough}
+
+When building communication endpoints, \hl{many architecture approach with putting significant smart into the communication mechanism.} One good example is \acrshort{esb} what we discussed in section \ref{se:architectural_decisions}.
 But microservice follows alternative approach: \emph{Smart endpoints and dumb pipes} \cite{LewisMicroservicesPipes}.
@@
 And it uses simple RESTish protocols rather than complex protocols.
+\dbc{RESTish or RESTful?}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Pattern: Database per Service}
+\subsection{\hl{Pattern: Database per Service}}
 \label{subse:database_per_service}
-- Pattern: Database per service
+\hl{- Pattern: Database per service}
 
@@
 \begin{itemize}
-    \item \emph{Private-tables-per-service} – each service owns a set of tables that must only be accessed by that service
-    \item \emph{Schema-per-service} – each service has a database schema that’s private to that service
-    \item \emph{Database-server-per-service} – each service has its own database server.
+    \item \emph{Private-tables-per-service} –- each service owns a set of tables that must only be accessed by that service
+    \item \emph{Schema-per-service} –- each service has a database schema that’s private to that service
+    \item \emph{Database-server-per-service} -– each service has its own database server.
 \end{itemize}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Pattern: Sagas}
+\subsection{\hl{Pattern: Sagas}}
 \label{subse:sagas}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{The Scale Cube}
+\subsection{\hl{The Scale Cube}}
 \label{subse:scale_cube}
@@
 
-\subsubsection{X-axis Saling}
-X-axis scaling consists of running multiple copies of an application behind a load balancer.
-If there are N copies then each copy handles 1/N of the load.
-This is a simple, commonly used approach of scaling an application TODO.
+\paragraph{x-axis Saling}-- x-axis scaling consists of running multiple copies of an application behind a load balancer.
+If there are \textit{n} copies then each copy handles 1/\textit{n} of the load.
+This is a simple, commonly used approach of scaling an application \hl{TODO}.
 
-\subsubsection{Y-axis Scaling}
-Unlike X-axis and Z-axis, which consist of running multiple, identical copies of the application, Y-axis axis scaling splits the application into multiple, different services.
+\paragraph{y-axis Scaling}-- Unlike x-axis and x-axis, which consist of running multiple, identical copies of the application, y-axis axis scaling splits the application into multiple, different services.
 Each service is responsible for one or more closely related functions.
@@
     \item verb-based decomposition ex: checkout.
-    \item decompose the application by noun ex: customer management. 
+    \item decompose the application by noun, for e.g., customer management. 
     \item An application might use a combination of verb-based and noun-based decomposition.
@@
 
-\subsubsection{Z-axis Scaling}
-When using Z-axis scaling each server runs an identical copy of the code (similar to X-axis scaling). The big difference is that each server is responsible for only a subset of the data. 
+\\paragraph{Z-axis Scaling}-- When using x-axis scaling each server runs an identical copy of the code (similar to X-axis scaling).
+The big difference is that each server is responsible for only a subset of the data.
 Z-axis splits are commonly used to scale databases. Data is partitioned (a.k.a. sharded) across a set of servers based on an attribute of each record.
@@
 \label{sebse:k8s_intro}
+\dbc{Don't present this as a separate section. Either this need to be in the literature survey, or integrate key ideas into another section as a paragraph.}
 
@@
 \begin{itemize}
-    \item Pods – Cluster of containers that can group other container images in a single unit.
-    \item Nodes - the machines (VMs, physical servers, etc) in a cluster that run your applications and cloud workflows.
-    \item kubelet - An agent that runs on each node in the cluster. It makes sure that containers are running in a pod.
-    \item kube-proxy - A network proxy that runs on each node in the cluster, and maintains network rules on nodes.
-    \item Kubernetes master - Responsible for maintaining the desired state for your cluster.
-    \item etcd - Consistent and highly-available key value store used as Kubernetes’ backing store for all cluster data.
+    \item Pods -- Cluster of containers that can group other container images in a single unit.
+    \item Nodes -- the machines (VMs, physical servers, etc) in a cluster that run your applications and cloud workflows.
+    \item kubelet -- An agent that runs on each node in the cluster. It makes sure that containers are running in a pod.
+    \item kube-proxy -- A network proxy that runs on each node in the cluster, and maintains network rules on nodes.
+    \item Kubernetes master -- Responsible for maintaining the desired state for your cluster.
+    \item etcd -- Consistent and highly-available key value store used as Kubernetes’ backing store for all cluster data.
 \end{itemize}
@@
 \label{sebse:wdias_microservices}
-In the figures of \ref{fi:wdias_micro_on_demand} and \ref{fi:wdias_micro_async} each circle represent a microservice, and those are implemented as containerized applications.
+As seen in Figure of \ref{fi:wdias_micro_on_demand} and \ref{fi:wdias_micro_async} each circle represents a microservice, and those are implemented as containerized applications.
 \begin{figure}[htp]
@@
     \includegraphics[width=1\textwidth]{method/microservice/microservice_architecture-handle_on_demand-v3.jpg}
-    \caption{\acrshort{wdias} architecture for server requests on demand}
+    \caption{\acrshort{wdias} architecture \hl{for server requests on demand}}
     \label{fi:wdias_micro_on_demand}
 \end{figure}
-In left side of the figure \ref{fi:wdias_micro_on_demand} shows the import modules of the \acrshort{wdias}, and right side show the export modules.
+Left side of Figure \ref{fi:wdias_micro_on_demand} shows the import modules of the \acrshort{wdias}, and right side shows the export modules.
 As it explained section \ref{subse:dumb_pipes}, each import microservice only do specific task of converting and forwarding the request to the correct data adapter module.
@@
 And the metadata data of the timeseries store using \acrshort{rdbms} which gives more performance over retrieving metadata data.
-The metadata is cached with In-Memory database in order to fast access as mentioned in section \ref{subse:redis}.
+The metadata is cached with In-Memory database to fast access as mentioned in section \ref{subse:redis}.
 The system generate a unique identifier for each timeseries, and throw out the \acrshort{wdias}, other microservice use it to handle data for fast access.
@@
     \includegraphics[width=1\textwidth]{method/microservice/microservice_architecture-handle_on_async-v3.jpg}
-    \caption{\acrshort{wdias} architecture for handle request asynchronously}
+    \caption{\acrshort{wdias} architecture for handling requests asynchronously.}
     \label{fi:wdias_micro_async}
@@
 
-As shown in the figure \ref{fi:wdias_micro_on_demand}, when a smaller size request come to the system, it handle on demand and response back.
-But as shown in figure \ref{fi:wdias_micro_async}, when a request with larger size come to the system, it store the data for asynchronously process the data and response with a unique id which can use to verify whether data processed successfully or not.
+As shown in Figure \ref{fi:wdias_micro_on_demand}, when a smaller size request come to the system, it handle on demand and response back.
+However, as shown in Figure \ref{fi:wdias_micro_async}, when a request with larger size come to the system, it store the data for asynchronously process the data and response with a unique id which can use to verify whether data processed successfully or not.
 Here is uses the microservice pattern of \ref{subse:sagas} while processing the Grid data.
@@
     \includegraphics[width=1\textwidth]{method/microservice/separation_microservices-v3.jpg}
-    \caption{Separation \acrshort{wdias} microservices}
+    \caption{Separation of \acrshort{wdias} microservices.}
     \label{fi:wdias_micro_separation}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{\acrshort{wdias} API Convention}
+\subsection{\acrshort{wdias} API}
 \label{sebse:wdias_api}
@@
     \begin{itemize}
-        \item \emph{GET /parameter} - Get parameters
-        \item \emph{POST /parameter} - Create parameter
-        \item \emph{PUT /parameter/id} - Update parameter
-        \item \emph{DELETE /parameter/id} - Delete parameter
+        \item \texttt{GET /parameter} -- Get parameters
+        \item \texttt{POST /parameter} -- Create parameter
+        \item \texttt{PUT /parameter/id} -- Update parameter
+        \item \texttt{DELETE /parameter/id} -- Delete parameter
     \end{itemize}
@@
     \begin{itemize}
-        \item \emph{GET timestep} - Get TimeSteps
-        \item \emph{POST timestep} - Create TimeStep
-        \item \emph{PUT timestep/id} - Update TimeStep
-        \item \emph{DELETE timestep/id} - Delete TimeStep
+        \item \texttt{GET timestep} -- Get TimeSteps
+        \item \texttt{POST timestep} -- Create TimeStep
+        \item \texttt{PUT timestep/id} -- Update TimeStep
+        \item \texttt{DELETE timestep/id} -- Delete TimeStep
     \end{itemize}
+\dbc{Format others as above}
     \item location
@@
 
-The API convention of \texttt{/MODULE/DATA\_FORMAT/DATA\_OPERATION\_TYPE}  allows users to integrate new import or export modules into the system as well as add new data types.
+The API convention of \texttt{\hl{/MODULE/DATA\_FORMAT/DATA\_OPERATION\_TYPE}}  allows users to integrate new import or export modules into the system as well as add new data types.

### 2020-02-11 method/sec_5-data_preprocess.tex
Change to fi: label
Removed commercial database names
Reviewed again after PGS reject

@@
-\section{Extensions (Weather Data Prepossessing)}
-\dbc{Section title?}
+\section{Data Prepossessing}
 
@@
     \includegraphics[width=0.5\textwidth]{method/data_preprocess/weather_data_preprocessing.jpg}
-    \caption{Weather Data Preprocessing}
-    \label{fig:weather_data_preprocessing}
+    \caption{\hl{Weather data preprocessing}}
+    \label{fi:weather_data_preprocessing}
 \end{figure}
+
 The WDIAS provides the support via in build simple generic mathematical function structure. Each extension is considering as a mathematical function which can take p 
@@
 
-\subsubsection{Serial Interpolation}
-In serial interpolation mode, interpolation is done to fill any gaps in a time series. The interpolation module will only consider the time series itself in filling these gaps.
+\paragraphSerial Interpolation}-- In serial interpolation mode, interpolation is done to fill any gaps in a time series.
+The interpolation module will only consider the time series itself in filling these gaps.
 \begin{figure}[htp]
@@
     \includegraphics[width=0.6\textwidth]{method/data_preprocess/serial_interpolation.jpg}
-    \caption{Serial Interpolation}
-    \label{fig:serial_interpolation}
+    \caption{Serial interpolation.}
+    \label{fi:serial_interpolation}
 \end{figure}
 
-\subsubsection{Spatial Interpolation}
-In spatial interpolation mode, the interpolation can be either applied to fill gaps in time series, or to create a new time series for a location using data from other (spatially distributed) locations.
+\paragraph{Spatial Interpolation}-- In spatial interpolation mode, the interpolation can be either applied to fill gaps in time series, or to create a new time series for a location using data from other (spatially distributed) locations.
 Spatial interpolation can also be applied for sampling scalar time series from grid time series, for re-sampling grids, or for creating grids from time series data.
@@
     \includegraphics[width=0.6\textwidth]{method/data_preprocess/spatial_interpolation.jpg}
-    \caption{Spatial Interpolation}
-    \label{fig:spatial_interpolation}
+    \caption{Spatial interpolation.}
+    \label{fi:spatial_interpolation}
 \end{figure}
 
-\subsection{Transformation}
-Simple arithmetic manipulation, Time interval transformation and Shifting the series in time
-Specific hydro-meteorological transformation such as stage discharge relationships
+\subsection{Transformation}-- Simple arithmetic manipulation, Time interval transformation and Shifting the series in time Specific hydro-meteorological transformation such as stage discharge relationships.
 \begin{figure}[htp]
@@
     \includegraphics[width=0.6\textwidth]{method/data_preprocess/transformation.jpg}
-    \caption{Transformation}
-    \label{fig:transformation}
+    \caption{\hl{Transformation}}
+    \label{fi:transformation}
 \end{figure}
 
-\subsection{Validation}
-Checks for counting reliable, doubtful, unreliable, and missing values
+\subsection{Validation}-- Checks for counting reliable, doubtful, unreliable, and missing values
 \begin{figure}[htp]
@@
     \includegraphics[width=0.6\textwidth]{method/data_preprocess/validation.jpg}
-    \caption{Validation}
-    \label{fig:validation}
+    \caption{\hl{Validation}}
+    \label{fi:validation}
 \end{figure}
 
-\subsection{Extension API}
+\subsection{\hl{Extension API}}
 In the WDIAS, it is possible to create new trigger for an extension via POST request to /extension endpoint.
@@
 \begin{itemize}
-    \item extensionId - An unique identifier for new extension trigger. Should be unique among all extensions.
-    \item extension - The main extension category which is responsible for handling the extension with extracting data required and storing the output.
+    \item extensionId -- An unique identifier for new extension trigger. Should be unique among all extensions.
+    \item extension -- The main extension category which is responsible for handling the extension with extracting data required and storing the output.
 Interpolation/Transformation/Validation support for the moment.
-    \item function - Name of the microservice which is handling the input to output mapping. Fn() function in the \ref{fig:weather_data_preprocessing}.
-    \item variables - Array timeseries mapping to variables.
+    \item function -- Name of the microservice which is handling the input to output mapping. Fn() function in the \ref{fi:weather_data_preprocessing}.
+    \item variables -- Array timeseries mapping to variables.
 Multiple variables can be define with metadata or metadataIds of timeseries.
 Can be use same variable on inputVariables and outputVariables below.
-    \item inputVariables - Timeseries that need to be provide into the function
-    \item outputVariables - Timeseries that output from the function
-    \item trigger - Type of trigger for the extension. Should be one of OnTime or OnChange.
+    \item inputVariables -- Timeseries that need to be provide into the function
+    \item outputVariables -- Timeseries that output from the function
+    \item trigger -- Type of trigger for the extension. Should be one of OnTime or OnChange.
     \begin{itemize}
-        \item trigger - OnChange
-        \item trigger\_on - List of timeseries to listen on change and trigger the extension
+        \item trigger -- OnChange
+        \item trigger\_on -- List of timeseries to listen on change and trigger the extension
     \end{itemize}
     \begin{itemize}
-        \item trigger - OnTime
-        \item trigger\_on - List of schedules that need to be trigger the extension in cronjob string format
+        \item trigger -- OnTime
+        \item trigger\_on -- List of schedules that need to be trigger the extension in cronjob string format
     \end{itemize}
-    \item options - Bind Constant which is bind at the time of creating new extension trigger and pass on triggering the extension.
+    \item options -- Bind Constant which is bind at the time of creating new extension trigger and pass on triggering the extension.
 \end{itemize}
@@
     \includegraphics[width=0.6\textwidth]{method/data_preprocess/validation.jpg}
-    \caption{Extension Handler}
-    \label{fig:extension_handler}
+    \caption{Extension handler.}
+    \label{fi:extension_handler}
 \end{figure}
 
-In further elaboration, when new data imported into one of adapter-scalar or adapter-vector, those notify the extension-handler.
+\hl{In further elaboration,} when new data imported into one of adapter-scalar or adapter-vector, those notify the extension-handler.
 Then extension handler check whether there is any extension subscribed for particular timeseries, and trigger it via triggering an event on particular extensions.
 
-In order to improve the performance of matching triggers against a timeseries, the WDIAS added two mechanisms.
+To improve the performance of matching triggers against a timeseries, the WDIAS added two mechanisms.
 For the separation of service responsibilities, those functionalities reside in the adapter-extension and expose via an endpoint.
@@
 Using this reverse lookup table, for a given trigger\_type and timeseries, it can retrieve the extensions which are part of given timeseries.
-Thus the response which is received by the
+Thus, the response which is received by the
 extension-handler only contains the extensions to be triggered. No additional filtering need to be done at the extension-handler service.
@@
 
-\subsubsection{Extension Scheduler}
-Extension Handler is responsible for triggering the correct Extension with metadata at given time which is provided at the creation on extension trigger's with the value of OnTime cronjob string value.
-
-In order to improve the performance of triggering cronjobs at given time schedules, the WDIAS added few optimization mechanisms.
+\paragraph{Extension Scheduler}-- Extension Handler is responsible for triggering the correct Extension with metadata at given time which is provided at the creation on extension trigger's with the value of OnTime cronjob string value.
+To improve the performance of triggering cronjobs at given time schedules, the WDIAS added few optimization mechanisms.
 Same as for extension-handler, the adapter-extension expose an endpoint to retrieve extension metadata grouped by cronjob time.

### 2020-02-11 results/sec_1-test_plan.tex
Reviewed again after PGS reject

--- 2020-02-10 results/sec_1-test_plan.tex
@@
 
-The system consists of three modules in functionality perspective of interacting with the \acrshort{wdias}.
+\hl{The system consists of three modules in functionality perspective of interacting with the} \acrshort{wdias}.
 \begin{enumerate}
@@
 \end{enumerate}
-Other than above, adapter modules act as the core modules and the base of the system. Also query modules allow the users to query for the timeseries
-based on the metadata, and enable performing Geo based queries based on the locations.
+Other than above, adapter modules act as the core modules and the base of the system.
+Also, query modules allow the users to query for the timeseries based on the metadata, and enable performing Geo based queries based on the locations.
 
@@
 \begin{enumerate}
-    \item Number of requests that can handle at a given time (\acrfull{rps})
+    \item Number of requests made to the system at a given time (\acrfull{rps})
     \item Request size
@@
 Those produce in less frequency due to cost of the computer resource to produce results.
-After considering those factor, it is logical to come with following percentages;
-\begin{itemize}
-    \item Scalar - 70\%
-    \item Vector - 20\%
-    \item Grid - 10\%
-\end{itemize}
+After considering those factor we came up with 70\% scalar, 20\% vector, and 10\% grid values.
+%\begin{itemize}
+%    \item Scalar - 70\%
+%    \item Vector - 20\%
+%    \item Grid - 10\%
+%\end{itemize}
 
@@
 
-\subsection{Load Testing Flow}
+\subsection{\hl{Load Testing Flow}}
 \label{subse:test_plan_flow}
@@
 
-\subsection{Performance Metrics of Load Testing}
+\subsection{Performance Metrics}% of Load Testing}
 \label{subse:test_plan_metrics}
@@
 \begin{itemize}
-    \item Throughput - Number of requests that can be process per unit time. Normally for \acrshort{wdias} performance observations, it uses \acrfull{rps} in order to measure the throughput.
-    \item Latency - Time taken for response back to the sent request to the system.
+    \item \emph{Throughput} -- Number of requests that can be process per unit time. Normally for \acrshort{wdias} performance observations, it uses \acrfull{rps} in order to measure the throughput.
+    \item \emph{Latency} -- Time taken for response back to the sent request to the system.
 Normally it measures with milliseconds (ms) in the \acrshort{wdias}.
@@
 Other than that, it measure the response time into 90\% percentile, while gives best response time up to 90\% percent of the responses.
-    \item Resource Utilization - Resource Utilization is calculated based on the CPU and Memory usage via \acrshort{k8s} metrics server.
+    \item \emph{Resource utilization} -- Resource Utilization is calculated based on the CPU and Memory usage via \acrshort{k8s} metrics server.
 It calculates the resource utilization over 60 seconds of time window.
 Network usage is getting based on the actual physical machines.
-    \item Auto Scaling - The \acrshort{wdias} is running with two configurations.
+    \item \emph{Auto scaling} -- The \acrshort{wdias} is running with two configurations.
 First is, since it is running the microservice as docker containers, it allow to increase or shrink the resource usage and share the resources within a physical machine.

### 2020-02-11 results/sec_2-workload.tex
Reviewed again after PGS reject

@@
-\section{Workload}
+\section{Workload Generation}
 
-As explained in the \ref{ch:method}, timeseries has six primary attributes. In order to create a timeseries for performance testing, it needs data for each key attribute.
+As explained in Section \ref{ch:method}, timeseries has six primary attributes. In order to create a timeseries for performance testing, it needs data for each key attribute.
 While generating the timeseries for performance testing, it selected locations all over the world as a generic case to include all the locations without binding to a specific area.
@@
 During the performance test, it creates 1000 timeseries and keep adding data against those timeseries.
-For each location, it creates four timeseries with vary with module Id key attribute with four values.
+For each location, it creates four timeseries \hl{with vary with module Id} key attribute with four values.
 Thus combining all together, those creates 1000 timeseries.
@@
 
-\begin{lstlisting}[language=sh, caption=Precipitation Data Preparation]
+\begin{lstlisting}[language=sh, caption=Preparation of precipitation data.]
 Set ROOT_DIR=~/wdias/wdias-performance-test
@@
 
-\begin{lstlisting}[language=sh, caption=Water level Data Preparation]
+\begin{lstlisting}[language=sh, caption= Preparation of water-level data.]
 Set ROOT_DIR=~/wdias/wdias-performance-test
@@
 But it has following limitation;
-\say{Note: The same test plan runs by all the servers.
+The same test plan runs by all the servers.
 JMeter does not distribute the load between servers, each runs the full test plan.
-So if you set 1000 Threads and have 6 JMeter server, you end up injecting 6000 Threads}.
+So if you set 1,000 threads and have 6 JMeter server, you end up injecting 6,000 threads.
 When test cases runs with \acrshort{jmeter} Distributed mode, the server node trigger same copy of test case on configured slave nodes parallel.
@@
 The root component of a test create is a thread group.
-There are different kind of thread groups are available such as Thread Group (Basic thread group), Arrivals Thread Group, Free Form Arrivals Thread Group, Stepping Thread Group, Concurrency Thread Group and Ultimate Thread Group etc.
+There are different kind of thread groups are available such as thread group (basic thread group), arrivals thread Group, free form arrivals thread group, stepping thread group, concurrency thread group, and ultimate thread group.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{closed vs. open workload models}
+\subsubsection{Closed vs. open workload models}
 \label{subse:closed_vs_open_workload}
@@
 
-The test plans mentioned in \ref{se:test_plan} are implemented via the \acrshort{jmeter}. The following list shows the all the test cases using for the performance testing.
+The test plans mentioned in \ref{se:test_plan} are implemented via the \acrshort{jmeter}. The following list shows the all the test cases used for the performance testing:
 
 \begin{itemize}
-    \item User Defined Variables
+    \item User-defined variables
     \item Setup thread group
-    \item Create Timeseries thread group
-    \item Create Extensions thread group
-    \item Load Test Timeseries Concurrency thread group
-    \item Load Test Timeseries Concurrency thread group
-    \item Test Flow thread group
+    \item Create timeseries thread group
+    \item Create extensions thread group
+    \item Load test timeseries concurrency thread group
+    \item Load test timeseries concurrency thread group
+    \item Test flow thread group
 \end{itemize}
@@
 \begin{itemize}
-    \item HTTP Request Defaults
-    \item HTTP Header Manager
-    \item Timeseries Metadata CSV
-    \item Create Timeseries
-    \item Get Timeseries
-    \item Query Timeseries
+    \item HTTP request defaults
+    \item HTTP header manager
+    \item Timeseries metadata CSV
+    \item Create timeseries
+    \item Get timeseries
+    \item Query timeseries
 \end{itemize}
@@
     \end{itemize}
-    \item wait for extensions timeseries
+    \item Wait for extensions timeseries
     \item Interest Area preprocessor
@@
     \end{itemize}
-    \item increment date
-    \item throughput shaping timer prod
+    \item Increment date
+    \item Throughput shaping timer prod
 \end{itemize}
 
-Following list of test steps shows intensively test the query timeseries features.
+\hl{Following list of test steps shows intensively test the query timeseries features.}
 
@@
     \includegraphics[width=0.6\textwidth]{results/work_load/test_prod_throughtput_shaping_timer.png}
-    \caption{\acrshort{wdias} performance test - Throughput Shaping Timer graph}
+    \caption{\acrshort{wdias} performance test - Throughput \hl{shaping timer graph}}
     \label{fi:test_prod_throughtput_shaping_timer}
@@
 
+\dbc{Top of Fig. 4.2 useless as it's black. Anyway, this figure isn't needed}
+
 With the above \acrshort{jmeter} test case setup, it need to enable each test case separately and before running via the command line in the server.
-In order to do it in much efficient way, a scripting tool has implemented, and accessible with the code base \cite{KarunarathneWdias-performance-test/TEST_PLAN.md:Plan} as \emph{test-dev}.
+To do it in much efficient way, a scripting tool has implemented, and accessible with the code base \cite{KarunarathneWdias-performance-test/TEST_PLAN.md:Plan} as \emph{test-dev}.
 
@@
 \begin{itemize}
-    \item Use CSV files rather Random number generation
+    \item Use CSV files rather thanrandom number generation
     \item Use JSR223 scripts with Groovy for data processing for test cases
-    \item Using Throughput Shaping Timer in order to get more accurate \acrshort{rps}
+    \item Using Throughput Shaping Timer to get more accurate \acrshort{rps}
 \end{itemize}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{System Configuration}
+\subsection{\hl{System Configuration}}
 \label{subse:test_sys_config}
@@
 For the performance study uses \acrfull{eks}.
-There are many \acrshort{k8s} solutions available such as GCP, Azure, Digital Ocean etc on the cloud.
+There are many \acrshort{k8s} solutions available such as GCP, Azure, and Digital Ocean on the cloud.
 
@@
 \acrshort{k8s} is a planet scaling tool \cite{LinuxFoundationProduction-GradeKubernetes}, and users can tweak the configuration to run the \acrshort{wdias} as per the required level of load on the system.
-During the performance test of the \acrshort{wdias}, it uses maximum of 300 \acrshort{rps} with providing to the system with increasing load, and monitor the auto scalability of the system with measuring other performance parameters mentioned in the \ref{se:test_plan}.
+During the performance test of the \acrshort{wdias}, it uses maximum of 300 \acrshort{rps} with providing to the system with increasing load, and monitor the auto scalability of the system with measuring other performance parameters mentioned in Table \ref{se:test_plan}.
 
@@
 \end{table}
+\dbc{Center table on page}
 
@@
 \label{se:performance_tuning}
-In order to get better performance using the available resources, it is possible to schedule each microservice into a predefined set of nodes. There are few ways to do in the \acrshort{k8s};
+To get better performance using the available resources, it is possible to schedule each microservice into a predefined set of nodes. There are few ways to do in the \acrshort{k8s};
 \begin{itemize}
-    \item \emph{nodeSelector} - Hard rules match for node schedule. If not match, pods will not schedule.
-    \item \emph{node Affinity and Anti-Affinity} - Soft rules for node schedule. Based on the rules, pods will schedule on most appropriate node.
-    \item \emph{Taints and Tolerations} - Opposite of nodeSelector, repel mismatching pods away from the nodes.
+    \item \emph{nodeSelector} -- Hard rules match for node schedule. If not match, pods will not schedule.
+    \item \emph{node Affinity and Anti-Affinity} -- Soft rules for node schedule. Based on the rules, pods will schedule on most appropriate node.
+    \item \emph{Taints and Tolerations} -- Opposite of nodeSelector, repel mismatching pods away from the nodes.
 \end{itemize}
@@
     \centering
-    \includegraphics[width=0.6\textwidth]{results/work_load/eks_node_setup.jpg}
+    \includegraphics[width=0.75\textwidth]{results/work_load/eks_node_setup.jpg}
     \caption{\acrfull{eks} node setup}
@@
 \begin{itemize}
-    \item \emph{core}: metadata, extensions, query, status and extension services
-    \item \emph{grid}: grid adapter, import and export grid data
-    \item \emph{scalar}: scalar and vector adapters, import and export of same data types
-    \item \emph{test}: jmeter and metric server
+    \item \emph{core} -- metadata, extensions, query, status and extension services
+    \item \emph{grid} -- grid adapter, import and export grid data
+    \item \emph{scalar} -- scalar and vector adapters, import and export of same data types
+    \item \emph{test} -- jMeter and metric server
 \end{itemize}

### 2020-02-11 results/sec_3-observations.tex
Reviewed again after PGS reject

@@
-\section{Observations}
+\section{\hl{Observations}}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Load Testing with hourly data (24 Request Size)}
+\subsection{Load Testing with hourly data (\db{Request size = 24})}
 \label{subse:obs_test_plan_all_60min}
@@
 \end{figure}
-\ref{fi:test_obs_all_60m_response_vs_threads} show the response time against the number of active threads.
+Figure \ref{fi:test_obs_all_60m_response_vs_threads} shows the response time against the number of active threads.
 As the graph show, the response time kept same while increasing the number of active threads against each test case.
@@
 \end{figure}
-\ref{fi:test_obs_all_60m_latency} graph provides a better overview of the variation of latency over elapsed time of the test plan against number of server hits per second.
+
+Figure \ref{fi:test_obs_all_60m_latency} graph provides a better overview of the variation of latency over elapsed time of the test plan against number of server hits per second.
 The conclusion of giving static latency while increasing the number of requests in \ref{fi:test_obs_all_60m_response_vs_threads} can further prove with this graph, since \ref{fi:test_obs_all_60m_latency} graph gives in details overview over the test plan time span.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Load Testing with 30min data (48 Request Size)}
+\subsection{Load Testing with 30min data (Request size = 48)}
 \label{subse:obs_test_plan_all_30min}
-This section \ref{subse:obs_test_plan_all_30min} discussed about the All test plan performance with 30 minutes data which means 48 data points per each request in Scalar and Vector timeseries, and 48 ASCII Grid files per each insert request.
+This section \ref{subse:obs_test_plan_all_30min} discussed about the All test plan performance with 30 minutes data which means 48 data points per each request in Scalar and Vector timeseries, and 48 ASCII grid files per each insert request.
 It performed round up to 311k of sample requests which is almost similar to \ref{subse:obs_test_plan_all_60min} processed samples.

### 2020-02-11 lit/sec_1-fews.tex

@@
 Most of the library of functions provided work equally on scalar and gridded time series.
-As with all other modules this communicates with the database solely through the data access layer as shown in \db{Section} \ref{fi:fews_data_layer} \cite{Werner2013TheSystem}.
+As with all other modules this communicates with the database solely through the data access layer as shown in \hl{Section} \ref{fi:fews_data_layer} \cite{Werner2013TheSystem}.
 As it shown in the figure, it is clearly showing that, the system is depends on single database and via the data access layer all the requests are coming to the database though a connection.

### 2020-02-11 method/sec_0_introduction.tex

@@
 
-\subsection{Modules of Weather Data System}
+\subsection{Modules of a Weather Data System}
 \label{subse:modules_weather_data_integration_sys}
@@
 \centerline{\includegraphics[width=0.8\textwidth]{method/misc/weather_data_system_components.jpg}}
-\caption{Components of a weather data system.}
+\caption{Modules of a weather data system.}
 \label{fi:wdia_components}
@@
 Each timeseries, the data points can be form in different formats as well.
-For example, Scalar (0D), Vector (1D), Grid (2D), and Polygon (2D).
+For example, scalar (0D), vector (1D), grid (2D), and polygon (2D).
+dbc{Why are you referring to timeseries here? It's not one of the 3 key components in Fig. 3.1.}
 
-WDIAS is focus on handling Scalar, Vector and Grid data timeseries via the thesis. But the system is capable of extending to handle polygon timeseries as well.
+In the proof of concept design described below, WDIAS focuses on handling scalar, vector and grid timeseries data. However, the system could be extended to handle polygon-based timeseries as well.
 
@@
 \dbc{What's Base of WDIAS architecture?}
-The base of WDIAS architecture origins based on attributes of a timeseries.
-There are many attributes to differentiate timeseries one from another.
-But following can be consider as key attributes to uniquely identify a timeseries from another for the \acrshort{wdias}.
-In detail description available at the section \ref{se:db_struct}.
+\hl{The base of WDIAS architecture origins based on attributes of a timeseries.} %There are many attributes to differentiate timeseries one from another. But 
+Among many attribute to differentiate a timeseries from another, the following can be consider as the key attributes in uniquely identify a timeseries from another: % for the \acrshort{wdias}.
+\dbc{Highlighted sentence doesn't make sense to me. All yellow highlights mean they are not clear.}
+
 \begin{itemize}
-    \item Module -- module that generate the timeseries
-    \item Value type -- Scalar, Vector, Grid, Polygon
-    \item Location 
-    \item Parameter -- measuring parameter of timeseries
-    \item Timeseries type
+    \item Module -- module that generates the timeseries
+    \item Value type -- Scalar, vector, grid, or polygon
+    \item Location of readings
+    \item Parameter -- measuared parameter
+    \item hl{Timeseries type}
     \begin{itemize}
-        \item sources -- External, Simulated
-        \item category -- Historical, forecast
+        \item Sources -- External or simulated
+        \item Category -- Historical or forecast
     \end{itemize}
@@
 \dbc{Use bullets only when essential. Other places use paragraphs.}
+
+A detail description of the above attributes are presented in Section \ref{se:db_struct}.

### 2020-02-11 method/sec_1-architectural_decisions.tex

@@
-\section{Architectural Desicions}
+\section{Architectural Decisions}
 \label{se:architectural_decisions}
 
-Initial design of \acrshort{wdias} used the \acrfull{soa}, and try to use the \acrfull{esb} which can provide capability to integrate different modules, since it is acting as a common layer for all of modules.
-By default, \acrshort{esb} provides pub sub capabilities.
-Since \acrshort{esb} mediator can be used to integrate the modules which are described in \ref{subse:modules_weather_data_integration_sys}.
-\acrshort{esb} also support different transportation protocols such as HTTP and Web-Socket etc.
+Initial design of \acrshort{wdias} used the \acrfull{soa}.
+Moreover, it tried to use an \acrfull{esb} to integrate different modules, as it is acting as a common layer for all of modules.
+By default, \acrshort{esb} provides publisher/subscribe (pub/sub) capabilities.
+\hl{Because} \acrshort{esb} \hl{mediator can be used to integrate the modules which are described in Section} \ref{subse:modules_weather_data_integration_sys}.
+\acrshort{esb} also support different transportation protocols such as HTTP and Web sockets.
+However, it turned out that \acrshort{esb} is not a suitable for data streaming or bulk data processing.
+Also, \acrshort{esb} suffer from single point of failure, as all the messages are going though a common bus.
 
-But \acrshort{esb} is not a better solution for data streaming or bulk data processing. Also \acrshort{esb} suffer from single point of failure, since all the messages are going though a common bus.
+In the second design round of \acrshort{wdias}, we attempted to use the actor model using AKKA framework \cite{HewittWhyModel}. %However, after consider into the disadvantage of using \acrshort{esb}. 
+Using the actors we tried to implement the microservice architecture. In that case, an actor or an actor with slave actors were map to each microservice in \acrshort{wdias}.
 
-In the second phase of \acrshort{wdias}, the proposed architecture changed to use with Actor model using AKKA framework \cite{HewittWhyModel} after consider into the disadvantage of using \acrshort{esb}.
-Using the Actors we tried to implement the microservice architecture.
-In that case, an Actor or An Actor with slave Actors map into each microservice in the \acrshort{wdias}.
-
-The typical \acrshort{soa} model, for example, usually has more dependent \acrshort{esb}s, with microservices using faster messaging mechanisms.
+/hl{The typical \acrshort{soa} model, for example, usually has more dependent \acrshort{esb}s, with microservices using faster messaging mechanisms.
 \acrshort{soa} also focuses on imperative programming, whereas microservices architecture focuses on a responsive-actor programming style.
 Moreover, \acrshort{soa} models tend to have an outsized relational database, while microservices frequently use NoSQL or micro-SQL databases (which can be connected to conventional databases).
-But the real difference has to do with the architecture methods used to arrive at an integrated set of services in the first place.
+But the real difference has to do with the architecture methods used to arrive at an integrated set of services in the first place.}
+\dbc{Multiple design rounds and decisions are mixed in the para. First finish discussing ESB. Then finish actor model in another para. Then focus on mircoservice details.}
 
-As mentioned above, \acrshort{esb} support to implement \acrshort{soa}.
+%As mentioned above, \acrshort{esb} support to implement \acrshort{soa}.
 But \acrshort{soa} has limitations such as single point of failure, slower communication (can’t use for transfer data) etc.
 So, the microservice architecture get evolved and demanding for the moment.
-When compare to \acrshort{soa}, microservice architecture has some advantages;
+When compare to \acrshort{soa}, the microservice architecture has several advantages such as the following:
 \begin{itemize}
-    \item Follow the Single Responsibility Principle
-    \item Resilient/Flexible – failure in one service does not impact other services. If you have monolithic or bulky service errors in one service/module it can impact other modules/functionality.
-    \item High scalability – demanding services can be deployed in multiple servers to enhance performance and keep away from other services so that they don’t impact other services.
+    \item Follow the Single Responsibility principle
+    \item Resilient/flexible as failure in one service does not impact other services. If you have monolithic or bulky service errors in one service/module it can impact other modules/functionality.
+    \item High scalable as demanding services can be deployed in multiple servers to enhance performance and keep away from other services so that they do not impact other services.
 Will be difficult to achieve the same with single, large monolithic service.
-    \item Easy to enhance – less dependency and easy to change and test
-    \item Low impact on other services – being an independent service, this has less chance to impact other services
-    \item Easy to understand since they represent the small piece of functionality
+    \item Easy to enhance as dependencies are less. Is also easier to change and test.
+    \item Low impact on other services as each service is independent. % service., this has less chance to impact other services
+    \item Easy to understand since they represent a small piece of functionality
     \item Ease of deployment
@@
 
-Even with using AKKA framework, it has some of the disadvantage as described in AKKA documentation \cite{Akka.ioWhenCluster}.
+Even with using the AKKA framework, it has some of the disadvantage as described in AKKA documentation \cite{Akka.ioWhenCluster}.
 Even Actor model capable of implementing a microservice architecture, it has few disadvantage.
-In order to overcome these issues, we moved to the \acrfull{k8s} \cite{LinuxFoundationProduction-GradeKubernetes}.;
+To overcome these issues, we moved to the \acrfull{k8s} \cite{LinuxFoundationProduction-GradeKubernetes}.
+\dbc{Kubernetes is a product. What you need to refer is to the concept of container-orchestration. Fix.}
+
 \begin{itemize}
-    \item Unable to choose technology. But \acrshort{k8s} allows you to choose technology that is best suited for a particular functionality
-    \item As mentioned in the AKKA documentation \cite{Akka.ioWhenCluster}, it's better for developing one microservice within the whole \acrshort{wdias} design.
+    \item \hl{Unable to choose technology. But} \acrshort{k8s} \hl{allows you to choose technology that is best suited for a particular functionality}
+    \item \hl{As mentioned in the AKKA documentation} \cite{Akka.ioWhenCluster}, \hl{it is better for developing one microservice within the whole} \acrshort{wdias} design.
 \end{itemize}
+
+\dbc{What are these 2 bullets?}
+\dbc{Don't use shortened words like it's, isn't, don't,... in writing}

### 2020-02-11 method/sec_4-db_struct.tex

@@
 
-The database structure of WDIAS mainly depends on the key attributes of the timeseries. A brief summary of possible value for timeseries can be describe as below;
+The database structure of WDIAS mainly depends on the key attributes of the timeseries. \hl{A brief summary of possible value for timeseries can be describe as below};
+\dbc{Clerly mention why a hierarchical design is needed.}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Timeseries Key Attributes}
+\subsection{Key Attributes of Timeseries}
 \label{subse:timeseries_key_attributes}
-\subsubsection{Module ID}
-String field which describe the source of the data generated. e.g., hec-hms, flow2d, weather-station etc
+\paragraph{Module ID}-- String field which describe the source of the data generated. e.g., hec-hms, flow2d, weather-station etc
 
-\subsubsection{Value Type}
-Scalar, Vector, Grid are the Value Types which are interested in the \acrshort{wdias}.
+\paragraph{Value Type}-- Scalar, Vector, Grid are the Value Types which are interested in the \acrshort{wdias}.
 
-\subsubsection{Location}
-Location of the timeseries. All locations have unique String identifier called locationId. Further, there are two type of location types that is interested in the WDIAS.
+\paragraph{Location}-- Location of the timeseries. All locations have unique String identifier called locationId. Further, there are two type of location types that is interested in the WDIAS, namely:
 \begin{itemize}
-  \item \emph{Point locations} - Contains a name which is human readable. lat and lon of the location on earth surface.
+  \item \emph{Point locations}-- Contains a name which is human readable. lat and lon of the location on earth surface.
   \begin{lstlisting}[language=Python]
@@
   \end{lstlisting}
-  \item \emph{Regular Grid locations} - Contains a name which is human readable. The grid presents by dividing into equal size cells. Thus, it need the number of rows and columns. 
+  \dbc{Remove additional line.}
+
+  \item \emph{Regular Grid locations} -- Contains a name which is human readable. The grid presents by dividing into equal size cells. Thus, it need the number of rows and columns. 
   And the location of the first cell and the width and height of it.
@@
   \end{lstlisting}
-  \item \emph{Irregular Grid locations} - (endpoints are available with in the WDIAS system, but skipped since it is out of the interest of the scope.)
+  \item \emph{Irregular Grid locations} -- (endpoints are available with in the WDIAS system, but skipped since it is out of the interest of the scope.)
 \end{itemize}
 
-\subsubsection{Parameter}
-Parameter describe the variable measuring against a location. All parameters ahve a unique String identifier called as parameterId. A parameter can be use in multiple locations.
-While defining a parameter, there are three required fields which need to be provided such as variable, unit and parametertype.
+\paragraph{Parameter}
+Parameter describe the variable measuring against a location. All parameters ahve a unique String identifier called as \textit{parameterId}. A parameter can be use in multiple locations.
+While defining a parameter, there are three required fields which need to be provided such as variable, unit and \textit{parametertype}.
 \begin{itemize}  
-  \item \emph{Variable} - Nature of the variable measuring. Example Precipitation, Temperature and WaterLevel etc
-  \item \emph{Unit} - metric unit of measuring
-  \item \emph{Parameter Type} - Should be one of 'Instantaneous', 'Accumulative', 'Mean'
+  \item \emph{Variable} -- Nature of the variable measuring. Example Precipitation, Temperature and WaterLevel etc
+  \item \emph{Unit} -- metric unit of measuring
+  \item \emph{Parameter Type} -- Should be one of Instantaneous, Accumulative, or Mean
   \begin{lstlisting}[language=Python]
@@
 \subsubsection{Timeseries Type}
-Timeseries Type can be combination of Source followed by Category.
+Timeseries Type can be combination of Source followed by category:
 \begin{itemize}
-  \item Sources - External, Simulated
-  \item Category - Historical, Forecast
+  \item Sources - External or simulated
+  \item Category - Historical or forecast
 \end{itemize}
+\dbc{Explain each with sufficient detail.}
 
-\subsubsection{Time Step}
-All Time Steps has an uniqie String identifier called as timeStepId.
-Unit should be one of 'Second', 'Minute', 'Hour', 'Day', 'Week', 'Month', 'Year', 'NonEquidistant'.
+\paragraph{Time Step}-- All Time Steps has an uniqie String identifier called as timeStepId.
+Unit should be one of Second, Minute, Hour, Day, Week, Month, Year, or NonEquidistant.
 One of multiplier or divider can be use to define the interval between each measurement.
@@
 
+\dbc{Fig. 3.6 needs a more meaningful title.}
+
 WDIAS is using a hierarchical database, with following the concept of Database per Service which is described in the \emph{Database per Service} in Section \ref{subse:database_per_service}.
@@
 \label{subse:mysql}
+\dbc{Needs a more meaningful Sec. title}
 
-There are lots of \acrshort{rdbms} available and for \acrshort{wdias} is using SQL as the \acrfull{rdbms}.
-SQL database has fewer version of open source and it is also possible to gain better performance with commercial versions. 
+%There are lots of \acrshort{rdbms} available and for 
+\acrshort{wdias} is using SQL as the \acrfull{rdbms}. 
+%SQL database has fewer version of open source and it is also possible to gain better performance with commercial versions. 
 Since WDIAS scope is to using open source tools, it is using \acrshort{mysql} as persistent database for storing timeseries metadata described above.
@@
 Other than MySQL, there are many open source databases can be used to replace the same functionality.
-
+\dbc{First start with a brief discussion on why a RDBMS is needed}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{subse:influxdb}
-Among the other timeseries open source databases available, \acrshort{influxdb} \cite{influxdbInfluxDBDocumentation} has higher number of usage and support.
-Database is written in Golang programming language, and has higher performance, and has following supports;
+Among several timeseries open source databases, \acrshort{influxdb} \cite{influxdbInfluxDBDocumentation} \hl{has higher number of usage and support.
+Database is written in Golang programming language, and} has higher performance, and has following supports;
 \begin{itemize}
@@
 \end{itemize}
-Other than \acrshort{influxdb}, another Database is Elastic Search which is mainly using for indexing for searching.
+Other than \acrshort{influxdb}, another database is Elastic Search which is mainly using for indexing for searching.
 With changing the configurations of the \acrshort{influxdb}, it is possible to adapt as required. As mention in \cite{influxdbInfluxDBDocumentation}, 
@@
 And it also has the support for parallel file access.
-NetCDF is widely using in sciencetific domain due to it's capability of storing data in multi dementions easily and flexibility with storing many of the sciencetific data.
-Python wrapper for NetCDF-C library using in the WDIAS system, and use by adapter-grid service.
+NetCDF is widely using in sciencetific domain due to it's capability of storing data in multi dementions easily and flexibility with storing many of the sciencetific data. \hl{
+Python wrapper for NetCDF-C library using in the WDIAS system, and use by adapter-grid service.}
 
@@
 
-\acrshort{wdias} is using \acrshort{mongodb} as the Document-oriented databse, since it has the Geo searching capabilities.
-\acrshort{mongodb} \cite{mongodbMongoDBManual} is a general purpose, document-based, distributed database. And it supports;
+\acrshort{wdias} is using \acrshort{mongodb} as the document-oriented databse, as it has the Geo searching capabilities.
+\acrshort{mongodb} \cite{mongodbMongoDBManual} is a general purpose, document-based, distributed database. And it supports:
+\dbc{Need for a mix of relational, time series, document stores, and in-memory need to be first mentioned and justified in high-level design of EDIAS above.}
 \begin{itemize}

### 2020-02-11 method/sec_6-query.tex
Fixed: sub section labels
Misc fixes on references

@@
 
-As described in \db{Section} \ref{sub:mongodb}, adapter-query is primarily using for support Geo-spatial queries.
+As described in Section \ref{subse:mongodb}, adapter-query is primarily using for support Geo-spatial queries.
 Other than that, as the primary service for searching for timeseries, it also supports for retrieval of timeseries metadata for external queries as well.
@@
 \end{lstlisting}
-\dbc{Use monospace formatting.}
 
@@
 \begin{lstlisting}
-    GET <HOST_NAME>/metadata/timeseries?<QUERY_STRING>
+    GET <HOST_NAME>/metadata/timeseries?<QUERY_STRING}
 \end{lstlisting}
+
 QUERY\_STRING can be consist of zero to multiple parameters. Multiple query parameters are separated by the ampersand, "\&".
@@
 
-\subsubsection{Query Locations within Area}
-Using following API endpoint, it is possible to query the locations which are exists within the area provided by the geoJson data in the JSON payload.
+\paragraph{Query Locations within Area}-- Using following API endpoint, it is possible to query the locations which are exists within the area provided by the geoJson data in the JSON payload.
 \begin{lstlisting}
@@
 
-\subsubsection{Query parameters in Locations}
-Using the following API endpoint, it is possible to query the parameters stored against given locations. Location IDs should be provide as list of JSON payload.
+paragraph{Query parameters in Locations}-- Using the following API endpoint, it is possible to query the parameters stored against given locations.
+Location IDs should be provide as list of JSON payload.
 \begin{lstlisting}
@@
 
-\subsubsection{Query Timeseries by Location}
-Using the following API endpoint, it is possible to query the timeseries metadata for a given location.
+\paragraph{Query Timeseries by Location}-- Using the following API endpoint, it is possible to query the timeseries metadata for a given location.
 \begin{lstlisting}
@@
 
-\subsubsection{Query Timeseries in Area}
-Using the following API endpoint, it is possible to query the timeseries metadata within a given area. This operation uses geoWithin \acrshort{mongodb} operator for the simplicity.
+\paragraph{Query Timeseries in Area} -- Using the following API endpoint, it is possible to query the timeseries metadata within a given area.
+This operation uses geoWithin \acrshort{mongodb} operator for the simplicity.
 \begin{lstlisting}
@@
 
-\subsubsection{Query Timeseries in Area by Parameter}
-Using the following API endpoint, it is possible to query the timeseries metadata within a given area for given parameter. This is an extension to the above endpoint.
+\paragraph{Query Timeseries in Area by Parameter}-- Using the following API endpoint, it is possible to query the timeseries metadata within a given area for given parameter.
+This is an extension to the above endpoint.
 \begin{lstlisting}
@@
 
-\subsubsection{Query All Timeseries}
-Send a request with empty JSON body will respond with all the timeseries.
+\paragraph{Query All Timeseries} -- Send a request with empty JSON body will respond with all the timeseries.
 \begin{lstlisting}
@@
 \end{lstlisting}
+
+\dbc{Need a chapter summary Sec.}

### 2020-02-11 summary/sec_1-conclusions.tex

@@
 
-To enhance the accuracy of the weather prediction, it is required to have reliable weather data for \acrshort{nwm}.
+To enhance the accuracy of the weather prediction, it is essential to provide reliable and timely weather data for \acrshort{nwm}.
 Even though there are many data integration systems, most of them are proprietary or close sourced.
-Which means for an island like Sri Lanka that having different kinds of weather seasons over the year than those software originated need to be highly customized.
-Throughout the operations and maintenance, it is required to get support with paying lots of charges, and difficult to debug into a closed source system without maintenance support from the vendors.
-Also most of existing systems are not up to date with the existing cloud computing technologies, or bias to some research community.
-We proposed an extendable open source Weather Data Integration and Assimilation Systems which is known as \acrshort{wdias}.
-It focused on providing efficiently integrates weather data from different sources with quality control and supporting steaming large size of data.
+Which means for an island like Sri Lanka that having different kinds of weather seasons over the year those software needs to be highly customized.
+\hl{Throughout the operations and maintenance, it is required to get support with paying lots of charges, and difficult to debug into a closed source system without maintenance support from the vendors.
+Also most of existing systems are not up to date with the cloud computing technologies, or bias to some research community.}
+/dbc{Look some of the changes in abstract and revise this para. However, don't repeat the same from abstract.}
+
+We proposed an extendable open source weather data integration and assimilation system known as \acrshort{wdias}.
+\acrshort{wdias} focuses on providing efficiently integrates weather data from different sources with quality control and supporting steaming large size of data.
 And compatible with current cloud computing technologies and architecture patterns.
@@
 First the architecture of \acrshort{wdias} starts with \acrshort{soa} using a \acrfull{esb}, and then moved to Actor model based architecture.
-After comparing the disadvantages of using such architectures with the system requirements, final architecture come up with modern microservice architecture.
+After comparing the disadvantages of using such architectures with the system requirements, we came up with a modern microservice architecture.
 \acrshort{wdias} implemented the microservice architecture on top of the \acrshort{k8s}.
 Each microservice of \acrshort{wdias} is mapped to a pod in the \acrshort{k8s}.
-Also each microservice follows the concept of Smart endpoints dumb pipes, and do specific operations which are related to the data format that responsible for handling.
+Also, each microservice follows the concept of Smart endpoints dumb pipes, and do specific operations which are related to the data format that responsible for handling.
 
@@
 
-Also the system provide a generic open mechanism to integrate new modules as extension in order to enhance the features of the system.
+Also, the system provide a generic open mechanism to integrate new modules as extension to enhance the features of the system.
 This capability enable to integrate weather data preprocessing flows as extension modules.
@@
 
-\acrshort{wdias} load testing is perform using the \acrshort{jmeter} tool's distributed testing capabilities.
+Load testing of \acrshort{wdias} was perform using the \acrshort{jmeter} tool's distributed testing capabilities.
 Then the test plans are performed with increasing the request size, and monitored the performance metrics.
@@
 Based on the observations, the system were able to handle 300 \acrshort{rps} (which means 18,000 requests per minute) successfully with minimizing the error rate to zero.
-Also while increasing the request size from 24 to 96 data points per Scalar and Vector timeseries, and number of ASCII Grid files from 24 to 96, the \acrshort{wdias} was able to perform same while keeping the latency constant without any significant change.
-During the performance test plans, the system were able to provide increase the throughput by keeping the latency constant while increasing the workload. Which exhibit the scalability of the system.
+Also, while increasing the request size from 24 to 96 data points per scalar and vector timeseries, and number of ASCII Grid files from 24 to 96, the \acrshort{wdias} was able to perform same while keeping the latency constant without any significant change.
+During the performance test plans, the system were able to provide increase the throughput by keeping the latency constant while increasing the workload.
+Which exhibit the scalability of the system.
 With the \acrshort{k8s} auto scaling, the \acrshort{wdias} were able to elastically adjust the number of pods according to the workload with auto scaling configurations. 

### 2020-02-12 introduction/sec_1-motivation.tex
Problem statement

@@
 The weather predictions/forecasts are performed using \acrfull{nwm} that use a set of configuration parameters and the current status of the environment such as temperature, rainfall, and wind direction as the input.
-For example, the \acrfull{wrf} model is used to predict the rainfall, temperature, and wind direction.
+For example, the \acrfull{wrf} \cite{MesoscaleMicroscaleMeteorologyLaboratoryWeatherModel} model is used to predict the rainfall, temperature, and wind direction.
 Typically multiple \acrshort{nwm} are executed on the same data with different configuration parameters.
 Then using the real-time observations, the correct model is selected.
-After removing the bias, the extract information is then fed into the next set of models.
-\db{There are lots of \acrshort{nwm} available there, but another example can be taken as FLO2D which can be used to predict the water level on the ground.
-For the corresponding model developed based on the geo data, giving the current status of water levels and forecasted rainfall, the model predicts the forecasted water level.}
+After removing the bias, the extract information is then fed into another set of models/simulators.
+As an example, FLO2D is a hydrologic model that can use to predict the surface water level.
+A given FLO2D model can simulate with the initial surface water levels and the sequence of forecasted rainfall for the corresponding modeled area from \acrshort{nwm} model to forecast future water levels.
 \dbc{Highighted part doesn't make much sense to me. Need to be reworded.}
 \dbc{cite both NWM and WRF}
+\gkc{FIXED BOTH}
 
-Center for Urban Water, Sri Lanka (CUrW-SL) is tasked with the mission to reduce water-related natural disasters in Sri Lanka.
-CURW-SL is implementing its own system with the idea of long-term maintainability rather depend on existing weather data integration systems.
+\acrfull{curw} \cite{CUrWSL2017SL} is tasked with the mission to reduce water-related natural disasters in Sri Lanka.
+\acrshort{curw} \cite{CUrWSLObservedSL} is implementing its own system with the idea of long-term maintainability rather depend on existing weather data integration systems.
 It collected real-time data from weather stations and other government entities and generates daily forecasts.
 Then the generated results are shared with relevant public departments responsible for disaster planning, mitigation, and management.
-One of the future goals of CUrW-SL is to open up data to the public enabling both societal and commercial use cases.
-% and , and use of the processed data via their system for the betterment of the society.
-The institute is operating via the paid TAX of Sri Lankan, and its trying to improve the quality of the life and the economic lost which are effected on the country via sharing the data for external parties to use of them.
+One of the future goals of \acrshort{curw} is to open up data to the public enabling both societal and commercial use cases.
 
@@
 
-While Data Integration and Analysis System (DIAS) and Meteorological Assimilation Data Ingest System (MADIS) are some of well-known Weather Data Integration and Assimilation (WDIA) systems, they are proprietary.
-Further Delft-FEWS is free to use, it is not open source.
+While Data Integration and Analysis System (DIAS) \cite{Kawasaki2018DataReduction} and Meteorological Assimilation Data Ingest System (MADIS) \cite{Macdermaid2005ARCHITECTUREP2.39} are some of well-known Weather Data Integration and Assimilation (WDIA) systems, they are proprietary.
+Further \acrfull{fews} \cite{Werner2013TheSystem} is free to use, it is not open source.
 Even though there are many data integration systems, most of them are proprietary or close sourced.
@@
 Throughout the operations and maintenance, it is required to get support with paying lots of charges, and difficult to debug into a closed source system without maintenance support from the vendors.
-As an example, \acrshort{fews} does not support FLO2D model integration, and CUrW SL is using FLO2D for water level forecasting in the data flow.
+As an example, \acrshort{fews} does not support FLO2D model integration, and \acrshort{curw} is using FLO2D for water level forecasting in the data flow.
 In such a cases, it required to get the support from the vendor in order to integrate and configure the system.
@@
 When I see them addressed, I'll remove comments.}
+\gkc{FIXED: Added citations}

### 2020-02-12 introduction/sec_2-problem_and_objectives.tex
Problem statement

@@
 
-\emph{....}
+\emph{design and implement an extendable weather data integration, assimilation and dissemination system which is capable of handling bulk data efficiently with providing scalability and high throughput with using open source tools and modern cloud computing technologies}
 \dbc{Give a proper problem statement.}
+\gkc{UPDATED. Looked into the OneNote samples. I  should follow one of them from the beginning. :( }
 

### 2020-02-12 thesis.tex
Problem statement

@@
 
+\usepackage{color,soul}
 \usepackage{todonotes}
@@
 \newcommand{\dbc}[1]{\todo[author=Dilum, inline, color=blue!40]{#1}}
+
+\newcommand{\gkc}[1]{\todo[author=Gihan, inline, color=green!50]{#1}}
 
@@
 \addcontentsline{toc}{chapter}{Abstract} 
-{\setstretch{1.0} 
+{\setstretch{1.5}
+
 \chapter*{Abstract}
-%\chapter*{\hspace{1cm} Abstract}
 
@@
 The resulting weather data also need to be accessed by many researchers and third-party applications such as logistic companies and agricultural insurance.
-%Thus, the system should provide a simple protocol to integrate with external systems.
-%For example, logistic companies could use those data within their models to plan and schedule deliveries.
-Agricultural insurance companies can warn the farmers in advance, as well as calculate premiums based on anticipated weather patterns.
 Even though there are several weather data integration systems, they are based on monolithic or client-server architectures and are unable to benefit from novel computational models such as cloud computing and containers.
 Moreover, most of this software is proprietary or closed sourced; hence, it is difficult to customize such software for an island like Sri Lanka with different weather seasons.
-%than those software originated need to be highly customized.
-Throughout the operations and maintenance, it is required to get support with paying lots of charges, and difficult to debug into a closed source system without maintenance support from the vendors.
-And most of the software existing out there is not up to date with the latest technology concepts such as Cloud Computing.
-\db{Therefore, in this research, we propose \acrfull{wdias} that utilizes modern architecture pattern such as microservices to achieve scalability, high availability, and low-cost operation based on cloud computing.
+Therefore, in this research, we propose \acrfull{wdias} that utilizes modern architecture pattern such as microservices to achieve scalability, high availability, and low-cost operation based on cloud computing.
 \acrshort{wdias} provides a modular architecture to integrate data from different sources, export into different formats, and the inbuilt extension module system allow users to add new features.
 Due to the use of stateless microservices, \acrshort{wdias} achieves high scalability, availability, and enables the addition of new features on the fly with rollover capabilities.
-We demonstrate the utility of \acrshort{wdias} using cloud-based experimental setup and weather-related synthetic workloads.}
-%Because each module follows the stateless and failover microservices integrate with new Cloud Computing tools, the proposed solution comes with the scalability and high availability into large extend out of the box.
-The proposed solution is independent of the cloud platform which most software out there is not and independent of Cloud Platform providers which give much flexibility for the users to decide the best cost effective way to host it.
-And the auto scaling feature allows users to run \acrshort{wdias} from 1 CPU node to nodes with a few hundred CPUs.
-Unlike most existing systems \acrshort{wdias} does not require a shutdown in order to update the system configuration, and it allows to add new features on the fly with rollover capabilities.
+We demonstrate the utility of \acrshort{wdias} using cloud-based experimental setup and weather-related synthetic workloads.
 
 \dbc{Increase line space to 1.5}
+\gkc{FIXED}
 \vspace{4mm}
 
-\textbf{Keywords:} Cloud computing, \db{data assimilation, data integration, hierarchical databases, microservice, weather}
+\textbf{Keywords:} Cloud computing, data assimilation, data integration, hierarchical databases, microservice, weather
 %Cloud Computing, Data Management system, Distributed,  Highly Available, Scalable, Timeseries, Weather
 }
+
 \restoregeometry
@@
 I would like to acknowledge and thank Department of Computer Science and Engineering, University of Moratuwa, for allowing me to conduct my research and providing any assistance requested.
-Special thanks goes to both academic and non-academic staff of the department for their continued support.
-I also gratitude to the University of Moratuwa for the financial support as the research was supported in part by the Senate Research Grant of the University of Moratuwa under award number SRC/LT/2017/01.
+Special thanks go to both academic and non-academic staff of the department for their continued support.
+I also gratitude to the University of Moratuwa for the financial support as the research was supported in part by the Senate Research Grant of the University of Moratuwa under award number SRC/LT/2017/01,  and \acrfull{curw} for providing the grant and financial support during the research period with providing required resources and learning opportunities.
 
@@
 \dbc{Need to ACK CUrW for grant.}
+\gkc{FIXED}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \newglossarystyle{custom-glossary-style}{%
-  \setglossarystyle{long}%
+  \setglossarystyle{list}%
   \renewenvironment{theglossary}%
-    {\begin{longtable}[l]{@{}p{\dimexpr 4cm-\tabcolsep}p{0.8\hsize}}}% <-- change the value here
+    % {\begin{longtable}[l]{@{}p{\dimexpr 2cm-\tabcolsep}p{0.8\hsize}}}% <-- change the value here
+    {\begin{longtable}{p{3cm}p{\glsdescwidth}}}%
     {\end{longtable}}%
@@
 \addcontentsline{toc}{chapter}{List of Abbreviations} 
-\printglossary[style=custom-glossary-style, type=\acronymtype, title=List of Abbreviations, toctitle=List of Abbreviations, nonumberlist]
+\printglossary[style=altlist, type=\acronymtype, title=List of Abbreviations, toctitle=List of Abbreviations, nonumberlist]
 \dbc{Make sure line spacing is consistent here.}
+\gkc{Could not figure out how to fix this.
+Those spaces are because of grouping by first letter with style long.
+What is needed is style list.
+styles are not working on list style: https://www.dickimaw-books.com/gallery/glossaries-styles/}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-% \import{method/}{sec_1-soa.tex}
-% \label{se:soa}
-% \import{method/}{sec_2-actor_model.tex}
-% \label{se:actor_model}
-
 \import{method/}{sec_3-microservice.tex}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\chapter{Results}
+\chapter{Performance Analysis}
 \label{ch:results}
 
-\import{results/}{sec_0-introduction.tex}
+% \import{results/}{sec_0-introduction.tex}
 \label{se:results_intro}
 
-\import{results/}{sec_1-test_plan.tex}
+% \import{results/}{sec_1-test_plan.tex}
 \label{se:test_plan}
 
-\import{results/}{sec_2-workload.tex}
+% \import{results/}{sec_2-workload.tex}
 \label{se:workload}
 
-\import{results/}{sec_3-observations.tex}
+% \import{results/}{sec_3-observations.tex}
 \label{se:observations}
 
-\import{results/}{sec_4-discussion.tex}
+% \import{results/}{sec_4-discussion.tex}
 \label{se:discussion}

### 2020-02-13 Paper.tex
Fixed: “Section”
- Add “Section”
- “section” -> “Section”

@@
 But for each test run the latency kept constant over the time.
-During the \ref{subse:obs_test_plan_all_auto_15min} test run, the performance of the Grid data got better when compared to the \ref{subse:obs_test_plan_all_15min}.
+During the Section \ref{subse:obs_test_plan_all_auto_15min} test run, the performance of the Grid data got better when compared to the Section \ref{subse:obs_test_plan_all_15min}.
 Which means by adding more resources to the \acrshort{wdias}, it can handle more workload on the system.
@@
 Since \acrshort{wdias} using the \acrshort{k8s} as the container orchestration system, it allows to scale up and cool down the system as required based on the workload.
-This demonstrate on the test plan of \ref{subse:obs_test_plan_all_auto_15min}, and the system get scale up to the maximum at the peak time.
+This demonstrate on the test plan of Section \ref{subse:obs_test_plan_all_auto_15min}, and the system get scale up to the maximum at the peak time.
 Then cool down to single pod after finishing the test cases.
 Given above \acrshort{wdias} can run from 1 CPU node to nodes with 100 CPUs.
-As described in the \ref{se:microservice}, it uses the many of the concept of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities.
+As described in the Section \ref{se:microservice}, it uses the many of the concept of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities.
 
@@
 \paragraph{Grid data performance}
-As mentioned in the \ref{se:conclusion}, the adapter-grid is using a Python wrapper for netCDF FORTRAN implementation with parallel IO enabled.
+As mentioned in the Section \ref{se:conclusion}, the adapter-grid is using a Python wrapper for netCDF FORTRAN implementation with parallel IO enabled.
 This has some performance issues as well as memory leak issues.
@@
 \paragraph{Further improve hierarchical database performance}
-As further described in \ref{se:conclusion}, it is possible to increase the performance of these bottlenecks much higher such as using \acrshort{influxdb} Commercial cluster support for high availability or horizontal scaling of \acrshort{influxdb}.
+As further described in Section \ref{se:conclusion}, it is possible to increase the performance of these bottlenecks much higher such as using \acrshort{influxdb} Commercial cluster support for high availability or horizontal scaling of \acrshort{influxdb}.
 With \acrshort{influxdb} cluster, it is possible to run multiple pods of adapter-scalar and adapter-vector for support more server hits per second.
@@
 The adapter-scalar or adapter-vector can improve to plug multiple instance of \acrshort{influxdb} instances by changing the configurations.
-As an example, based on the key attribute \ref{subse:timeseries_key_attributes} Timeseries Type, the adapter-scalar can connect to four instance of \acrshort{influxdb} instances such as  External Historical, External Forecast, Simulated Historical, and Simulated Forecast etc.
+As an example, based on the key attribute Section \ref{subse:timeseries_key_attributes} Timeseries Type, the adapter-scalar can connect to four instance of \acrshort{influxdb} instances such as  External Historical, External Forecast, Simulated Historical, and Simulated Forecast etc.
 
@@
 Then the test plans are performed with increasing the request size, and monitored the performance metrics.
-The system is setup on the \acrfull{eks} as per the configurations of \ref{subse:test_sys_config}.
+The system is setup on the \acrfull{eks} as per the configurations of Section \ref{subse:test_sys_config}.
 During the performance test plans, the system were able to provide constant throughput by keeping the latency constant while increasing the workload. Which exhibit the scalability of the system.

### 2020-02-13 method/sec_0_introduction.tex
Fixed: “Section”
- Add “Section”
- “section” -> “Section”

@@
 Section \ref{se:architectural_decisions} that we evolve over while designing and implementing the \acrshort{wdias}.
-The section \ref{se:microservice} gives better understanding of the microservice architectural concepts follows while implementing the \acrshort{wdias}.
-Then the reason behind developing Heirarchital Database and technologies use for that discussed in the section \ref{se:db_struct}.
-Throw out the section \ref{se:data_preprocess} discussed about how the \acrshort{wdias} enable for data preprocessing and adding capabilities via concept of Extensions.
+The Section \ref{se:microservice} gives better understanding of the microservice architectural concepts follows while implementing the \acrshort{wdias}.
+Then the reason behind developing Heirarchital Database and technologies use for that discussed in the Section \ref{se:db_struct}.
+Throw out the Section \ref{se:data_preprocess} discussed about how the \acrshort{wdias} enable for data preprocessing and adding capabilities via concept of Extensions.
 Finally, in Section \ref{se:query} includes details on how to perform timeseries search and geo based queries.

### 2020-02-13 method/sec_3-microservice.tex
Problem statement
Fixed: “Section”
- Add “Section”
- “section” -> “Section”

@@
 
-When building communication endpoints, \hl{many architecture approach with putting significant smart into the communication mechanism.} One good example is \acrshort{esb} what we discussed in section \ref{se:architectural_decisions}.
+When building communication endpoints, \hl{many architecture approach with putting significant smart into the communication mechanism.} One good example is \acrshort{esb} what we discussed in Section \ref{se:architectural_decisions}.
 But microservice follows alternative approach: \emph{Smart endpoints and dumb pipes} \cite{LewisMicroservicesPipes}.
@@
 
-\\paragraph{Z-axis Scaling}-- When using x-axis scaling each server runs an identical copy of the code (similar to X-axis scaling).
+\paragraph{Z-axis Scaling}-- When using x-axis scaling each server runs an identical copy of the code (similar to X-axis scaling).
 The big difference is that each server is responsible for only a subset of the data.
@@
 
-Even \acrshort{wdias} is design based on the Y-axis scaling, it's possible to use the Z-axis scaling to scalability of the system further. This will be more discuss in the section \ref{se:discussion}.
+Even \acrshort{wdias} is design based on the Y-axis scaling, it's possible to use the Z-axis scaling to scalability of the system further. This will be more discuss in the Section \ref{se:discussion}.
 
@@
 Left side of Figure \ref{fi:wdias_micro_on_demand} shows the import modules of the \acrshort{wdias}, and right side shows the export modules.
-As it explained section \ref{subse:dumb_pipes}, each import microservice only do specific task of converting and forwarding the request to the correct data adapter module.
+As it explained section Section \ref{subse:dumb_pipes}, each import microservice only do specific task of converting and forwarding the request to the correct data adapter module.
 For each data type, there is a adapter microservice is running which is optimized to storing such type of data.
 And the metadata data of the timeseries store using \acrshort{rdbms} which gives more performance over retrieving metadata data.
-The metadata is cached with In-Memory database to fast access as mentioned in section \ref{subse:redis}.
+The metadata is cached with In-Memory database to fast access as mentioned in Section \ref{subse:redis}.
 The system generate a unique identifier for each timeseries, and throw out the \acrshort{wdias}, other microservice use it to handle data for fast access.
@@
 Export module microservice follows the same concepts and provide the capability to export the data into required formats of the weather models.
-Each adapter follows the concept of database per service as mentioned in the section \ref{subse:database_per_service}. This gives the freedom for \acrshort{wdias} to scale better with \acrshort{k8s}.
+Each adapter follows the concept of database per service as mentioned in the section Section \ref{subse:database_per_service}.
+This gives the freedom for \acrshort{wdias} to scale better with \acrshort{k8s}.
 
@@
 However, as shown in Figure \ref{fi:wdias_micro_async}, when a request with larger size come to the system, it store the data for asynchronously process the data and response with a unique id which can use to verify whether data processed successfully or not.
-Here is uses the microservice pattern of \ref{subse:sagas} while processing the Grid data.
+Here is uses the microservice pattern of Section \ref{subse:sagas} while processing the Grid data.
 First it store the data and respond back to the user.
@@
 As it shown, each adapter has isolated database, and database is hosted separately for the high performance.
-Apart from that, as we further discuss in section \ref{se:data_preprocess}, the extension modules are running separately such as Interpolation, Transformation and Validation etc.
+Apart from that, as we further discuss in Section \ref{se:data_preprocess}, the extension modules are running separately such as Interpolation, Transformation and Validation etc.
 The Extension Adapter allow users to register new triggers for the extensions. And extension scheduler triggers the events based on time and extension handler triggers event based on data change.
@@
 
-\emph{Extensions} endpoints for configure extensions. These details describes in the section \ref{se:data_preprocess}.
+\emph{Extensions} endpoints for configure extensions. These details describes in the Section \ref{se:data_preprocess}.
 

### 2020-02-13 method/sec_4-db_struct.tex
Fixed: “Section”
- Add “Section”
- “section” -> “Section”

@@
 One instance of \acrshort{mysql} is using only by adapter-metadata service.
-Other than that, another instance of \acrshort{mysql} is using for adapter-extension which will be describe in more detail \ref{se:data_preprocess}.
+Other than that, another instance of \acrshort{mysql} is using for adapter-extension which will be describe in more detail Section \ref{se:data_preprocess}.
 \acrshort{mysql} is used only for these services, those will only keep the consistency of the schema for timeseries metadata and extension metadata.
-\ref{subse:redis} instance is using for caching the data from \acrshort{mysql}, since the \acrshort{mysql} database instances, itself not going to get much load.
+As mentioned in Section \ref{subse:redis}, it uses \acrshort{redis} instance is using for caching the data from \acrshort{mysql}, since the \acrshort{mysql} database instances, itself not going to get much load.
 Other than MySQL, there are many open source databases can be used to replace the same functionality.
@@
 Other than that, adapter-status uses \acrshort{redis} as key value pair store for getting the status for async handling requests such as storing Grid data.
-In adapter-extension uses Redis's Publisher Subscriber capabilities in order to create a cron job in extension-scheduler when new extension create on \ref{se:data_preprocess}
+In adapter-extension uses Redis's Publisher Subscriber capabilities in order to create a cron job in extension-scheduler when new extension create on Section \ref{se:data_preprocess}

### 2020-02-13 results/sec_0-introduction.tex
Reviewed again after PGS reject
Fixed: “Section”
- Add “Section”
- “section” -> “Section”

@@
 
-This chapter includes performance study of the \acrshort{wdias}. In the first section \ref{se:test_plan} describes the planned method of testing the system.
-In the next section \ref{se:workload} describes the logic behind creating the workload to do the performance testing planned in \ref{se:test_plan}.
-Following section \ref{se:observations} includes the results observed while performance study. And summarised the observations in the next section \ref{se:discussion}.
+This chapter includes performance study of the \acrshort{wdias}. In Section \ref{se:test_plan} describes the planned method of testing the system.
+In the next Section \ref{se:workload} describes the logic behind creating the workload to do the performance testing planned in Section \ref{se:test_plan}.
+Following Section \ref{se:observations} includes the results observed while performance study. And summarised the observations in the next Section \ref{se:discussion}.

### 2020-02-13 results/sec_2-workload.tex
Problem statement
Fixed: “Section”
- Add “Section”
- “section” -> “Section”

@@
 
-As explained in Section \ref{ch:method}, timeseries has six primary attributes. In order to create a timeseries for performance testing, it needs data for each key attribute.
+As explained in Chapter \ref{ch:method}, timeseries has six primary attributes. In order to create a timeseries for performance testing, it needs data for each key attribute.
 While generating the timeseries for performance testing, it selected locations all over the world as a generic case to include all the locations without binding to a specific area.
@@
 For grid data, it uses static 100 grid locations which based on how is \acrshort{api} exposed.
-Since grid locations have different metadata structure as described in \ref{se:db_struct}, those data handle separately.
+Since grid locations have different metadata structure as described in Section \ref{se:db_struct}, those data handle separately.
 But the locationId of grid and scalar data types have the same effect when define a timeseries.
@@
 jmeter best practices lean\_mean}.
-Rather providing the randomness in run time, the timeseries stored with the random order which satisfy the percentage of 70\% Scalar, 20\% Vector and 10\% Grid as mentioned in \ref{se:test_plan}.
+Rather providing the randomness in run time, the timeseries stored with the random order which satisfy the percentage of 70\% Scalar, 20\% Vector and 10\% Grid as mentioned in Section \ref{se:test_plan}.
 Before running the test cases, it generate the metadata for timeseries and write into a CSV file which is shared among the threads in the \acrshort{jmeter}.
@@
 
-The test plans mentioned in \ref{se:test_plan} are implemented via the \acrshort{jmeter}. The following list shows the all the test cases used for the performance testing:
+The test plans mentioned in Section \ref{se:test_plan} are implemented via the \acrshort{jmeter}. The following list shows the all the test cases used for the performance testing:
 
@@
 
-It allows to run particular test plan which are described in \ref{se:test_plan}. Also possible to run the all the test plans in order with given \emph{REQ\_SIZE} or for all the \emph{REQ\_SIZE}.
+It allows to run particular test plan which are described in Section \ref{se:test_plan}.
+Also possible to run the all the test plans in order with given \emph{REQ\_SIZE} or for all the \emph{REQ\_SIZE}.
 
@@
 \begin{itemize}
-    \item Use CSV files rather thanrandom number generation
+    \item Use CSV files rather than random number generation
     \item Use JSR223 scripts with Groovy for data processing for test cases
@@
 \label{subse:test_sys_config}
-As described in the \ref{se:microservice}, the \acrshort{wdias} is mainly focus on microservice architecture and implemented on top of kubernetes.
+As described in the Section \ref{se:microservice}, the \acrshort{wdias} is mainly focus on microservice architecture and implemented on top of kubernetes.
 \acrfull{k8s} is an open-source system for automating deployment, scaling, and management of containerized applications.
@@
 \acrshort{k8s} is a planet scaling tool \cite{LinuxFoundationProduction-GradeKubernetes}, and users can tweak the configuration to run the \acrshort{wdias} as per the required level of load on the system.
-During the performance test of the \acrshort{wdias}, it uses maximum of 300 \acrshort{rps} with providing to the system with increasing load, and monitor the auto scalability of the system with measuring other performance parameters mentioned in Table \ref{se:test_plan}.
+During the performance test of the \acrshort{wdias}, it uses maximum of 300 \acrshort{rps} with providing to the system with increasing load, and monitor the auto scalability of the system with measuring other performance parameters mentioned in Table \ref{tab:aws_eks_nodes}.
 

### 2020-02-13 results/sec_3-observations.tex
Fixed: “Section”
- Add “Section”
- “section” -> “Section”

@@
 
-According the \ref{se:test_plan} section, this section includes the observations after performing the test plans on the \acrshort{wdias} system setup and test plan test up which is explained in the \ref{se:workload}.
+According the Section \ref{se:test_plan} section, this section includes the observations after performing the test plans on the \acrshort{wdias} system setup and test plan test up which is explained in the Section \ref{se:workload}.
 
 Sections \ref{subse:obs_test_plan_all_60min} to \ref{subse:obs_test_plan_all_auto_15min} discuss the observations collected with performing the Load test plans over 60 minutes (24 data points), 30 minutes (48 data points) and 15 minutes (96 data points) by variate the request size.
-Then another performance test with enabling Auto Scaling as explained in \ref{subse:test_plan_metrics} for high resource utilized microservice.
+Then another performance test with enabling Auto Scaling as explained in Section \ref{subse:test_plan_metrics} for high resource utilized microservice.
 
@@
 Retrieve Grid Timeseries data perform the same but with bit higher value of latency of 68ms.
-Both of insert and retrieve grid timeseries data have 4.5 \acrshort{rps} since it only get 10\% of the number of request per given time via the test plan as explain in the data ration in \ref{se:test_plan}.
+Both of insert and retrieve grid timeseries data have 4.5 \acrshort{rps} since it only get 10\% of the number of request per given time via the test plan as explain in the data ration in Section \ref{se:test_plan}.
 
@@
 \label{subse:obs_test_plan_all_30min}
-This section \ref{subse:obs_test_plan_all_30min} discussed about the All test plan performance with 30 minutes data which means 48 data points per each request in Scalar and Vector timeseries, and 48 ASCII grid files per each insert request.
-It performed round up to 311k of sample requests which is almost similar to \ref{subse:obs_test_plan_all_60min} processed samples.
+This Section \ref{subse:obs_test_plan_all_30min} discussed about the All test plan performance with 30 minutes data which means 48 data points per each request in Scalar and Vector timeseries, and 48 ASCII grid files per each insert request.
+It performed round up to 311k of sample requests which is almost similar to Section \ref{subse:obs_test_plan_all_60min} processed samples.
 
@@
 \end{table}
-\ref{tab:obs_all_30_min_summary} shows the response latency summary details and \acrshort{rps} as explained in \ref{subse:obs_test_plan_all_60min}.
+\ref{tab:obs_all_30_min_summary} shows the response latency summary details and \acrshort{rps} as explained in Section \ref{subse:obs_test_plan_all_60min}.
 And the results are almost similar to the observations in \ref{tab:obs_all_60_min_summary}.
@@
 \label{subse:obs_test_plan_all_15min}
-This section \ref{subse:obs_test_plan_all_15min} discussed about the All test plan performance with 15 minutes data which means 96 data points per each request in Scalar and Vector timeseries, and 96 ASCII Grid files per each insert Grid timeseries request.
-These requests are four times larger than the \ref{subse:obs_test_plan_all_60min} request size.
-It performed approximately 311k of sample requests which is almost similar to \ref{subse:obs_test_plan_all_30min} processed samples.
+This Section \ref{subse:obs_test_plan_all_15min} discussed about the All test plan performance with 15 minutes data which means 96 data points per each request in Scalar and Vector timeseries, and 96 ASCII Grid files per each insert Grid timeseries request.
+These requests are four times larger than the Section \ref{subse:obs_test_plan_all_60min} request size.
+It performed approximately 311k of sample requests which is almost similar to Section \ref{subse:obs_test_plan_all_30min} processed samples.
 \begin{table}[ht]
@@
 \end{table}
-\ref{tab:obs_all_15_min_summary} shows the response latency summary details and \acrshort{rps} as same as explained in \ref{subse:obs_test_plan_all_30min}.
+\ref{tab:obs_all_15_min_summary} shows the response latency summary details and \acrshort{rps} as same as explained in Section \ref{subse:obs_test_plan_all_30min}.
 And the latency observations are increased by some amount when compared to the observations in \ref{tab:obs_all_30_min_summary}.
@@
 \label{subse:obs_test_plan_all_auto_15min}
-This section \ref{subse:obs_test_plan_all_auto_15min} discussed about the All test plan performance with 15 minutes data which means 96 data points per each request in Scalar and Vector timeseries, and 96 ASCII Grid files per each insert Grid timeseries request.
-These requests are four times larger than the \ref{subse:obs_test_plan_all_60min} request size.
-It performed approximately 311k of sample requests which is almost similar to \ref{subse:obs_test_plan_all_15min} processed samples.
-Other than that, this test plan runs with enabling \acrshort{k8s} Auto Scaling for the high resource utilized microservice as explained in the \ref{subse:test_plan_metrics}.
+This Section \ref{subse:obs_test_plan_all_auto_15min} discussed about the All test plan performance with 15 minutes data which means 96 data points per each request in Scalar and Vector timeseries, and 96 ASCII Grid files per each insert Grid timeseries request.
+These requests are four times larger than the Section \ref{subse:obs_test_plan_all_60min} request size.
+It performed approximately 311k of sample requests which is almost similar to Section \ref{subse:obs_test_plan_all_15min} processed samples.
+Other than that, this test plan runs with enabling \acrshort{k8s} Auto Scaling for the high resource utilized microservice as explained in the Section \ref{subse:test_plan_metrics}.
 With the test load used for the performance test, import-ascii-grid-upload microservice is using lots of CPU, and adapter-grid microservice is using lots of Memory.
@@
 \end{table}
-\ref{tab:obs_all_auto_15_min_summary} shows the response latency summary details and \acrshort{rps} as same as explained in \ref{subse:obs_test_plan_all_15min}.
+\ref{tab:obs_all_auto_15_min_summary} shows the response latency summary details and \acrshort{rps} as same as explained in Section \ref{subse:obs_test_plan_all_15min}.
 During this test plan.
@@
 \label{subse:obs_test_plan_query_15min}
-This section \ref{subse:obs_test_plan_query_15min} discussed about the Query test plan performance.
-It performs multiple information retrieval queries such as query over locations, parameters and timeseries etc which are described over \ref{se:query}.
+This Section \ref{subse:obs_test_plan_query_15min} discussed about the Query test plan performance.
+It performs multiple information retrieval queries such as query over locations, parameters and timeseries etc which are described over Section \ref{se:query}.
 It performed approximately 123k of sample requests.

### 2020-02-13 results/sec_4-discussion.tex
Fixed: “Section”
- Add “Section”
- “section” -> “Section”

@@
 
-In this section concludes the observations in \ref{se:observations} section against the performance metrics defines in \ref{subse:test_plan_metrics}.
+In this section concludes the observations in Section \ref{se:observations} section against the performance metrics defines in Section \ref{subse:test_plan_metrics}.
 
@@
 When look into the \emph{resource utilization} of \acrshort{wdias}; since it is using the \acrshort{k8s} as the container orchestration system, it allows to scale up and cool down the system as required based on the workload.
-This demonstrate on the test plan of \ref{subse:obs_test_plan_all_auto_15min}, and the system get scale up to the maximum at the peak time.
+This demonstrate on the test plan of Section \ref{subse:obs_test_plan_all_auto_15min}, and the system get scale up to the maximum at the peak time.
 Then cool down to single pod after finishing the test cases.
 Given above \acrshort{wdias} can run from 1 CPU node to nodes with 100 CPUs.
-As described in the \ref{se:microservice}, it uses the many of the concept of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities.
+As described in the Section \ref{se:microservice}, it uses the many of the concept of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities.
 

### 2020-02-13 summary/sec_1-conclusions.tex
Fixed: “Section”
- Add “Section”
- “section” -> “Section”

@@
 And it uses microservice sagas pattern for asynchronous data handling for requests with higher size.
-According to the section \ref{se:microservice}, it uses the many of the concept of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities.
+According to the Section \ref{se:microservice}, it uses the many of the concept of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities.
 
@@
 Then the test plans are performed with increasing the request size, and monitored the performance metrics.
-The system is setup on the \acrfull{eks} as per the configurations of \ref{subse:test_sys_config}.
+The system is setup on the \acrfull{eks} as per the configurations of Section \ref{subse:test_sys_config}.
 Based on the observations, the system were able to handle 300 \acrshort{rps} (which means 18,000 requests per minute) successfully with minimizing the error rate to zero.

### 2020-02-13 summary/sec_2-research_limitations.tex
Fixed: “Section”
- Add “Section”
- “section” -> “Section”

@@
 \emph{Grid data performance}:
-As mentioned in the \ref{se:discussion}, the adapter-grid is using a Python wrapper for netCDF FORTRAN implementation with parallel IO enabled.
+As mentioned in the Section \ref{se:discussion}, the adapter-grid is using a Python wrapper for netCDF FORTRAN implementation with parallel IO enabled.
 This has some performance issues as well as memory leak issues.
@@
 \emph{Improve test cases}:
-As described in detail with \ref{subse:closed_vs_open_workload}, for \acrshort{wdias} performance test uses Time Stepping Feedback loop with Concurrent Threads which is the best approach support by \acrshort{jmeter} at the moment.
+As described in detail with Section \ref{subse:closed_vs_open_workload}, for \acrshort{wdias} performance test uses Time Stepping Feedback loop with Concurrent Threads which is the best approach support by \acrshort{jmeter} at the moment.
 But using that it is not possible to get desired \acrshort{rps} for each test case within the test plan.
@@
 \emph{Further improve hierarchical database performance}:
-As further described in \ref{se:discussion}, it is possible to increase the performance of these bottlenecks much higher such as using \acrshort{influxdb} Commercial cluster support for high availability or horizontal scaling of \acrshort{influxdb}.
+As further described in Section \ref{se:discussion}, it is possible to increase the performance of these bottlenecks much higher such as using \acrshort{influxdb} Commercial cluster support for high availability or horizontal scaling of \acrshort{influxdb}.
 With \acrshort{influxdb} cluster, it is possible to run multiple pods of adapter-scalar and adapter-vector for support more server hits per second.
@@
 The \acrshort{wdias} better to be capable of triggering external systems based on the events such as web hooks.
+
+\dbc{Need a new section for Conclusions.}

### 2020-02-13 lit/sec_1-fews.tex
Fix with Figure

@@
 \dbc{F is capital and T is capital when referring to Figures and Tables. Fix all other places.}
+\gkc{FIXED}
 
@@
 Most of the library of functions provided work equally on scalar and gridded time series.
-As with all other modules this communicates with the database solely through the data access layer as shown in \hl{Section} \ref{fi:fews_data_layer} \cite{Werner2013TheSystem}.
+As with all other modules this communicates with the database solely through the data access layer as shown in Figure \ref{fi:fews_data_layer} \cite{Werner2013TheSystem}.
 As it shown in the figure, it is clearly showing that, the system is depends on single database and via the data access layer all the requests are coming to the database though a connection.

### 2020-02-13 lit/sec_2-lead.tex
After 2nd review
Fix with Figure

@@
 
-As shown in the figure \ref{fi:lead_framework} LEAD consists of the following sub components, and it provides a distributed test bed for developing, integrating, and testing LEAD's components.
+As shown in the Figure \ref{fi:lead_framework} LEAD consists of the following sub components, and it provides a distributed test bed for developing, integrating, and testing LEAD's components.
 \begin{itemize}
@@
 
-As shown in figure \ref{fi:lead_soa}, \acrshort{lead} \acrshort{soa} has five distinct yet highly interconnected layers. 
+As shown in Figure \ref{fi:lead_soa}, \acrshort{lead} \acrshort{soa} has five distinct yet highly interconnected layers. 
 The bottom layer represents raw computation, application, and data resources distributed throughout the LEAD grid and elsewhere.
@@
 \end{itemize}
-The top of the figure \ref{fi:lead_soa}, shows the user interface to the system.
+The top of the Figure \ref{fi:lead_soa}, shows the user interface to the system.
 This give the access to individual services.
@@
 At the time it was building, it uses the \acrshort{soa} architecture as into its depth, and with the implementation each service can scale as needed and possible to enhance the service without interrupting other services.
-In the \acrshort{wdias} only focus on creating a framework that is extendable as system need more features as like \acrshort{lead} services.
+\acrshort{wdias} only focuses on creating a framework that is extendable as system needs more features as like \acrshort{lead} services.

### 2020-02-13 lit/sec_3-other-systems.tex
Fix with Figure

@@
 
-As shown in figure \ref{fi:dias_common_platform}, it provides an application layer which allows domain scientists to working on research tasks, and to develop specific tools and applications by working together with Information Technology experts \cite{Kawasaki2018DataReduction}.
+As shown in Figure \ref{fi:dias_common_platform}, it provides an application layer which allows domain scientists to working on research tasks, and to develop specific tools and applications by working together with Information Technology experts \cite{Kawasaki2018DataReduction}.
 Once the data is achieved on the \acrshort{dias} system, it share those details via Shared API layer.
@@
 As it mentioned above, the \acrshort{madis} is implemented based on a distributed architecture which is available at the time of it's development.
-Even it is not clear mentioned, it is using functional call like Remote Procedure Call (RPC) to invoke among a cluster of nodes as shown in figure \ref{fi:madis_flow}.
+Even it is not clear mentioned, it is using functional call like Remote Procedure Call (RPC) to invoke among a cluster of nodes as shown in Figure \ref{fi:madis_flow}.
 To get high availability, it has added some update to it's architecture.
@@
 \acrshort{fews} and \acrshort{lead} have the capability of handling workflow of forecasting, but other system are mainly focus on providing a weather data management system.
-\acrshort{fews} provide a modular approach via it's general adapter which is shown on figure \ref{fi:fews_general_adapter}, and according to the \acrshort{soa} architecture of \acrshort{lead} provide the same functionality via services.
+\acrshort{fews} provide a modular approach via it's general adapter which is shown on Figure \ref{fi:fews_general_adapter}, and according to the \acrshort{soa} architecture of \acrshort{lead} provide the same functionality via services.
 

### 2020-02-13 method/sec_3-microservice.tex
Fix with Figure

@@
 \label{sebse:wdias_microservices}
-As seen in Figure of \ref{fi:wdias_micro_on_demand} and \ref{fi:wdias_micro_async} each circle represents a microservice, and those are implemented as containerized applications.
+As seen in Figure of Figure \ref{fi:wdias_micro_on_demand} and Figure \ref{fi:wdias_micro_async} each circle represents a microservice, and those are implemented as containerized applications.
 \begin{figure}[htp]
@@
 \end{figure}
-The figure \ref{fi:wdias_micro_on_demand} show the clear separation of microservices into the modules of the \acrshort{wdias}.
+The Figure \ref{fi:wdias_micro_on_demand} show the clear separation of microservices into the modules of the \acrshort{wdias}.
 As it shown, each adapter has isolated database, and database is hosted separately for the high performance.

### 2020-02-13 method/sec_5-data_preprocess.tex
Problem statement
Fix with Figure

@@
 
-\paragraphSerial Interpolation}-- In serial interpolation mode, interpolation is done to fill any gaps in a time series.
+\paragraph{Serial Interpolation}-- In serial interpolation mode, interpolation is done to fill any gaps in a time series.
 The interpolation module will only consider the time series itself in filling these gaps.
@@
 Interpolation/Transformation/Validation support for the moment.
-    \item function -- Name of the microservice which is handling the input to output mapping. Fn() function in the \ref{fi:weather_data_preprocessing}.
+    \item function -- Name of the microservice which is handling the input to output mapping. Fn() function in the Figure \ref{fi:weather_data_preprocessing}.
     \item variables -- Array timeseries mapping to variables.

### 2020-02-13 results/sec_3-observations.tex
Fix with Figure

@@
 This shows the scalability of the \acrshort{wdias}, since the system able to process more requests without a significant change in the latency.
-When number of active threads increased more than 122, the \ref{fi:test_obs_all_60m_response_vs_threads} show uncertainty in the inserting and retrieving Scalar and Vector data.
+When number of active threads increased more than 122, the Figure \ref{fi:test_obs_all_60m_response_vs_threads} show uncertainty in the inserting and retrieving Scalar and Vector data.
 
@@
 Figure \ref{fi:test_obs_all_60m_latency} graph provides a better overview of the variation of latency over elapsed time of the test plan against number of server hits per second.
-The conclusion of giving static latency while increasing the number of requests in \ref{fi:test_obs_all_60m_response_vs_threads} can further prove with this graph, since \ref{fi:test_obs_all_60m_latency} graph gives in details overview over the test plan time span.
+The conclusion of giving static latency while increasing the number of requests in Figure \ref{fi:test_obs_all_60m_response_vs_threads} can further prove with this graph, since Figure \ref{fi:test_obs_all_60m_latency} graph gives in details overview over the test plan time span.
 
@@
 \end{figure}
-\ref{fi:test_obs_all_30m_response_vs_threads} show the response time against the number of active threads for 30min data.
+Figure \ref{fi:test_obs_all_30m_response_vs_threads} show the response time against the number of active threads for 30min data.
 As the graph show, the response time kept same while increasing the number of active threads against each test case.
 This shows the scalability of the \acrshort{wdias}, since the system able to process more requests without a significant change in the latency.
-When number of active threads increased more than 110, the \ref{fi:test_obs_all_30m_response_vs_threads} show uncertainty in the inserting and retrieving Scalar and Vector data.
-This graph is similar to the \ref{fi:test_obs_all_60m_response_vs_threads}, but the active thread count goes down as a result of increasing the request size.
+When number of active threads increased more than 110, the Figure \ref{fi:test_obs_all_30m_response_vs_threads} show uncertainty in the inserting and retrieving Scalar and Vector data.
+This graph is similar to the Figure \ref{fi:test_obs_all_60m_response_vs_threads}, but the active thread count goes down as a result of increasing the request size.
 
@@
 \end{figure}
-\ref{fi:test_obs_all_30m_latency} graph provides a better overview of the variation of latency over elapsed time of the test plan against number of server hits per second.
+Figure \ref{fi:test_obs_all_30m_latency} graph provides a better overview of the variation of latency over elapsed time of the test plan against number of server hits per second.
 This graph also conclude that, over the time latency does not change very much. But during the peak load, it shows some variation in insert and retrieve of Grid timeseries.
-When compared to \ref{fi:test_obs_all_60m_latency}, the latency for insert and retrieve Grid timeseries increase by some amount.
+When compared to Figure \ref{fi:test_obs_all_60m_latency}, the latency for insert and retrieve Grid timeseries increase by some amount.
 
@@
 \end{figure}
-\ref{fi:test_obs_all_15m_response_vs_threads} show the response time against the number of active threads for 15min data.
+Figure \ref{fi:test_obs_all_15m_response_vs_threads} show the response time against the number of active threads for 15min data.
 As the graph show, the response time kept same while increasing the number of active threads against each test case.
@@
 This graph show that over the time \acrshort{wdias} were able to keep the latency constant over the test plan. But at the peak time, it tend to vary from the mean value a lot.
-One noticeable fact is, throw out the test time period, it shows spikes in latency when compared to \ref{fi:test_obs_all_60m_latency} and \ref{fi:test_obs_all_30m_latency}.
+One noticeable fact is, throw out the test time period, it shows spikes in latency when compared to \ref{fi:test_obs_all_60m_latency} and Figure \ref{fi:test_obs_all_30m_latency}.
 

### 2020-02-13 introduction/sec_2-problem_and_objectives.tex

--- 2020-02-11 introduction/sec_2-problem_and_objectives.tex
@@
 
-\emph{....}
+\emph{Design and implement an extendable weather data integration, assimilation and dissemination system which is capable of handling bulk data efficiently with providing scalability and high throughput with using open source tools and modern cloud computing technologies.}
 \dbc{Give a proper problem statement.}
+\gkc{UPDATED. Looked into the OneNote samples. I  should follow one of them from the beginning. :( }
 

### 2020-02-14 introduction/sec_3-outline.tex
Test with cref for the reference naming

@@
 The rest of the thesis is organized as follows.
-Literature review is presented in Chapter \ref{ch:literature}, and discuss about the existing Weather Data Integration Systems such as \acrshort{lead}, \acrshort{fews}, \acrshort{madis}, and \acrshort{dias}.
+Literature review is presented in \cref{ch:literature}, and discuss about the existing Weather Data Integration Systems such as \acrshort{lead}, \acrshort{fews}, \acrshort{madis}, and \acrshort{dias}.
 Solution approach with the proposed system architectures and adaptation with problem occurred are presented in Chapter \ref{ch:method}.

### 2020-02-14 lit/sec_1-fews.tex
Updates from Overleaf
Test with cref for the reference naming

@@
 This chapter presents a literature review on existing systems and their architecture approach and design.
-In Section \ref{se:fews}, we present \acrshort{fews}.
+In \cref{se:fews}, we present \acrshort{fews}.
 \acrfull{lead}, an open data handling platform distributed as closed-source software, is presented in Section \ref{se:lead}.
@@
 
-In \db{Figure} \ref{fi:fews_schematic} show a schematic view of the connection between the forecasting system to real time data acquisition systems and dissemination systems.
+In \db{Figure} \cref{fi:fews_schematic} show a schematic view of the connection between the forecasting system to real time data acquisition systems and dissemination systems.
 The widely using concept is using meteorological forecast data to get precipitation and, then using hydrological and hydraulic model chain to predict the level affect on the ground.
@@
 As an example, Python language is easy to use for beginners and many of data scientists are using this programming language for development and it has many data available libraries for data processing.
-But in \acrshort{fews}, users do not ave the capability to take the advantage of such existing things.
+But in \acrshort{fews}, users do not have the capability to take the advantage of such existing things.
 \dbc{Define Abb. for API in Chapter 1.}

### 2020-02-14 Paper.tex
Fix with Figure
Change all to \cref

--- 2020-02-11 Paper.tex
@@
 %\section{Modules of Weather Data System}
-Fig. \ref{fi:wdia_components} shows the basic functions of a Weather data integration and assimilation system.
+\cref{fi:wdia_components} shows the basic functions of a Weather data integration and assimilation system.
 \begin{figure}[htbp]
@@
 But for each test run the latency kept constant over the time.
-During the \ref{subse:obs_test_plan_all_auto_15min} test run, the performance of the Grid data got better when compared to the \ref{subse:obs_test_plan_all_15min}.
+During the \cref{subse:obs_test_plan_all_auto_15min} test run, the performance of the Grid data got better when compared to the \cref{subse:obs_test_plan_all_15min}.
 Which means by adding more resources to the \acrshort{wdias}, it can handle more workload on the system.
@@
 Since \acrshort{wdias} using the \acrshort{k8s} as the container orchestration system, it allows to scale up and cool down the system as required based on the workload.
-This demonstrate on the test plan of \ref{subse:obs_test_plan_all_auto_15min}, and the system get scale up to the maximum at the peak time.
+This demonstrate on the test plan of \cref{subse:obs_test_plan_all_auto_15min}, and the system get scale up to the maximum at the peak time.
 Then cool down to single pod after finishing the test cases.
 Given above \acrshort{wdias} can run from 1 CPU node to nodes with 100 CPUs.
-As described in the \ref{se:microservice}, it uses the many of the concept of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities.
+As described in the \cref{se:microservice}, it uses the many of the concept of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities.
 
@@
 \paragraph{Grid data performance}
-As mentioned in the \ref{se:conclusion}, the adapter-grid is using a Python wrapper for netCDF FORTRAN implementation with parallel IO enabled.
+As mentioned in the \cref{se:conclusion}, the adapter-grid is using a Python wrapper for netCDF FORTRAN implementation with parallel IO enabled.
 This has some performance issues as well as memory leak issues.
@@
 \paragraph{Further improve hierarchical database performance}
-As further described in \ref{se:conclusion}, it is possible to increase the performance of these bottlenecks much higher such as using \acrshort{influxdb} Commercial cluster support for high availability or horizontal scaling of \acrshort{influxdb}.
+As further described in \cref{se:conclusion}, it is possible to increase the performance of these bottlenecks much higher such as using \acrshort{influxdb} Commercial cluster support for high availability or horizontal scaling of \acrshort{influxdb}.
 With \acrshort{influxdb} cluster, it is possible to run multiple pods of adapter-scalar and adapter-vector for support more server hits per second.
@@
 The adapter-scalar or adapter-vector can improve to plug multiple instance of \acrshort{influxdb} instances by changing the configurations.
-As an example, based on the key attribute \ref{subse:timeseries_key_attributes} Timeseries Type, the adapter-scalar can connect to four instance of \acrshort{influxdb} instances such as  External Historical, External Forecast, Simulated Historical, and Simulated Forecast etc.
+As an example, based on the key attribute \cref{subse:timeseries_key_attributes} Timeseries Type, the adapter-scalar can connect to four instance of \acrshort{influxdb} instances such as  External Historical, External Forecast, Simulated Historical, and Simulated Forecast etc.
 
@@
 Then the test plans are performed with increasing the request size, and monitored the performance metrics.
-The system is setup on the \acrfull{eks} as per the configurations of \ref{subse:test_sys_config}.
+The system is setup on the \acrfull{eks} as per the configurations of \cref{subse:test_sys_config}.
 During the performance test plans, the system were able to provide constant throughput by keeping the latency constant while increasing the workload. Which exhibit the scalability of the system.

### 2020-02-14 lit/sec_1-fews.tex
Change all to \cref

@@
 In \cref{se:fews}, we present \acrshort{fews}.
-\acrfull{lead}, an open data handling platform distributed as closed-source software, is presented in Section \ref{se:lead}.
+\acrfull{lead}, an open data handling platform distributed as closed-source software, is presented in \cref{se:lead}.
 % \acrshort{lead} is following the \acrfull{soa} for system architecture.
-In Section \ref{se:dias}, we discussed about \acrfull{dias} which is a common data platform that can work with weather data.
-\acrfull{madis} is another widely use data integration system, which also provide data access with quality control, whihc we discuss in Section \ref{se:madis}.
+In \cref{se:dias}, we discussed about \acrfull{dias} which is a common data platform that can work with weather data.
+\acrfull{madis} is another widely use data integration system, which also provide data access with quality control, whihc we discuss in \cref{se:madis}.
 Under each system we explore both system architecture, scalability, and flexibility of the system.
@@
 Most of the library of functions provided work equally on scalar and gridded time series.
-As with all other modules this communicates with the database solely through the data access layer as shown in Figure \ref{fi:fews_data_layer} \cite{Werner2013TheSystem}.
+As with all other modules this communicates with the database solely through the data access layer as shown in \cref{fi:fews_data_layer} \cite{Werner2013TheSystem}.
 As it shown in the figure, it is clearly showing that, the system is depends on single database and via the data access layer all the requests are coming to the database though a connection.
@@
 \acrshort{fews} generates the input data as a set of XML files to a defined location; an adapter developed specifically for the model in question transforms this to the required native format in a pre-processing step; \acrshort{fews} executes the model; and the adapter to that model then converts the native formatted results into XML formatted files in a post processing step.
-\acrshort{fews} subsequently imports the results into the database from the XML files (see Figure \ref{fi:fews_general_adapter}) \cite{Werner2013TheSystem}.
+\acrshort{fews} subsequently imports the results into the database from the XML files (see \cref{fi:fews_general_adapter}) \cite{Werner2013TheSystem}.
 The process is simple and consistence through out all the model integration.

### 2020-02-14 lit/sec_2-lead.tex
Change all to \cref

@@
 
-Figure \ref{fi:lead_system} shows the fundamental capabilities of the \acrshort{lead} system.
+\cref{fi:lead_system} shows the fundamental capabilities of the \acrshort{lead} system.
 From the high-level view, \acrshort{lead} lets users query for and acquire information, simulate and predict weather by using numerical atmospheric models, assimilate data, analyze, mine, and visualize data and model output.
@@
 
-As shown in the Figure \ref{fi:lead_framework} LEAD consists of the following sub components, and it provides a distributed test bed for developing, integrating, and testing LEAD's components.
+As shown in the \cref{fi:lead_framework} LEAD consists of the following sub components, and it provides a distributed test bed for developing, integrating, and testing LEAD's components.
 \begin{itemize}
@@
 
-As shown in Figure \ref{fi:lead_soa}, \acrshort{lead} \acrshort{soa} has five distinct yet highly interconnected layers. 
+As shown in \cref{fi:lead_soa}, \acrshort{lead} \acrshort{soa} has five distinct yet highly interconnected layers. 
 The bottom layer represents raw computation, application, and data resources distributed throughout the LEAD grid and elsewhere.
@@
 \end{itemize}
-The top of the Figure \ref{fi:lead_soa}, shows the user interface to the system.
+The top of the \cref{fi:lead_soa}, shows the user interface to the system.
 This give the access to individual services.

### 2020-02-14 lit/sec_3-other-systems.tex
Change all to \cref

@@
 
-As shown in Figure \ref{fi:dias_common_platform}, it provides an application layer which allows domain scientists to working on research tasks, and to develop specific tools and applications by working together with Information Technology experts \cite{Kawasaki2018DataReduction}.
+As shown in \cref{fi:dias_common_platform}, it provides an application layer which allows domain scientists to working on research tasks, and to develop specific tools and applications by working together with Information Technology experts \cite{Kawasaki2018DataReduction}.
 Once the data is achieved on the \acrshort{dias} system, it share those details via Shared API layer.
@@
 As it mentioned above, the \acrshort{madis} is implemented based on a distributed architecture which is available at the time of it's development.
-Even it is not clear mentioned, it is using functional call like Remote Procedure Call (RPC) to invoke among a cluster of nodes as shown in Figure \ref{fi:madis_flow}.
+Even it is not clear mentioned, it is using functional call like Remote Procedure Call (RPC) to invoke among a cluster of nodes as shown in \cref{fi:madis_flow}.
 To get high availability, it has added some update to it's architecture.
@@
 \acrshort{fews} and \acrshort{lead} have the capability of handling workflow of forecasting, but other system are mainly focus on providing a weather data management system.
-\acrshort{fews} provide a modular approach via it's general adapter which is shown on Figure \ref{fi:fews_general_adapter}, and according to the \acrshort{soa} architecture of \acrshort{lead} provide the same functionality via services.
+\acrshort{fews} provide a modular approach via it's general adapter which is shown on \cref{fi:fews_general_adapter}, and according to the \acrshort{soa} architecture of \acrshort{lead} provide the same functionality via services.
 

### 2020-02-14 method/sec_0_introduction.tex
Change all to \cref

@@
 %, then how is it trying to propose a better system with overcoming the issues.
-In Section \ref{se:high_level_design} a brief discussion on how the weather forecasting is happening and why it need to interact with multiple data formats is presented.
+In \cref{se:high_level_design} a brief discussion on how the weather forecasting is happening and why it need to interact with multiple data formats is presented.
 Then following subsections define few termelogy which are using in the \acrshort{wdias}, and scope of the thesis.
-Section \ref{se:architectural_decisions} that we evolve over while designing and implementing the \acrshort{wdias}.
-The Section \ref{se:microservice} gives better understanding of the microservice architectural concepts follows while implementing the \acrshort{wdias}.
-Then the reason behind developing Heirarchital Database and technologies use for that discussed in the Section \ref{se:db_struct}.
-Throw out the Section \ref{se:data_preprocess} discussed about how the \acrshort{wdias} enable for data preprocessing and adding capabilities via concept of Extensions.
-Finally, in Section \ref{se:query} includes details on how to perform timeseries search and geo based queries.
+\cref{se:architectural_decisions} that we evolve over while designing and implementing the \acrshort{wdias}.
+The \cref{se:microservice} gives better understanding of the microservice architectural concepts follows while implementing the \acrshort{wdias}.
+Then the reason behind developing Heirarchital Database and technologies use for that discussed in the \cref{se:db_struct}.
+Throw out the \cref{se:data_preprocess} discussed about how the \acrshort{wdias} enable for data preprocessing and adding capabilities via concept of Extensions.
+Finally, in \cref{se:query} includes details on how to perform timeseries search and geo based queries.
 
@@
 
-Figure \ref{fi:wdia_components} shows the basic functions of a Weather data integration and assimilation system which consists of the following modules:
+\cref{fi:wdia_components} shows the basic functions of a Weather data integration and assimilation system which consists of the following modules:
 \begin{figure}[htbp]
@@
 
-A detail description of the above attributes are presented in Section \ref{se:db_struct}.
+A detail description of the above attributes are presented in \cref{se:db_struct}.

### 2020-02-14 method/sec_3-microservice.tex
Change all to \cref

--- 2020-02-13 method/sec_3-microservice.tex
@@
 
-When building communication endpoints, \hl{many architecture approach with putting significant smart into the communication mechanism.} One good example is \acrshort{esb} what we discussed in Section \ref{se:architectural_decisions}.
+When building communication endpoints, \hl{many architecture approach with putting significant smart into the communication mechanism.} One good example is \acrshort{esb} what we discussed in \cref{se:architectural_decisions}.
 But microservice follows alternative approach: \emph{Smart endpoints and dumb pipes} \cite{LewisMicroservicesPipes}.
@@
 
-Even \acrshort{wdias} is design based on the Y-axis scaling, it's possible to use the Z-axis scaling to scalability of the system further. This will be more discuss in the Section \ref{se:discussion}.
+Even \acrshort{wdias} is design based on the Y-axis scaling, it's possible to use the Z-axis scaling to scalability of the system further. This will be more discuss in the \cref{se:discussion}.
 
@@
 \label{sebse:wdias_microservices}
-As seen in Figure of \ref{fi:wdias_micro_on_demand} and \ref{fi:wdias_micro_async} each circle represents a microservice, and those are implemented as containerized applications.
+As seen in Figure of \cref{fi:wdias_micro_on_demand} and \cref{fi:wdias_micro_async} each circle represents a microservice, and those are implemented as containerized applications.
 \begin{figure}[htp]
@@
 \end{figure}
-Left side of Figure \ref{fi:wdias_micro_on_demand} shows the import modules of the \acrshort{wdias}, and right side shows the export modules.
-As it explained section Section \ref{subse:dumb_pipes}, each import microservice only do specific task of converting and forwarding the request to the correct data adapter module.
+Left side of \cref{fi:wdias_micro_on_demand} shows the import modules of the \acrshort{wdias}, and right side shows the export modules.
+As it explained section \cref{subse:dumb_pipes}, each import microservice only do specific task of converting and forwarding the request to the correct data adapter module.
 For each data type, there is a adapter microservice is running which is optimized to storing such type of data.
 And the metadata data of the timeseries store using \acrshort{rdbms} which gives more performance over retrieving metadata data.
-The metadata is cached with In-Memory database to fast access as mentioned in Section \ref{subse:redis}.
+The metadata is cached with In-Memory database to fast access as mentioned in \cref{subse:redis}.
 The system generate a unique identifier for each timeseries, and throw out the \acrshort{wdias}, other microservice use it to handle data for fast access.
@@
 Export module microservice follows the same concepts and provide the capability to export the data into required formats of the weather models.
-Each adapter follows the concept of database per service as mentioned in the section Section \ref{subse:database_per_service}.
-This gives the freedom for \acrshort{wdias} to scale better with \acrshort{k8s}.
+Each adapter follows the concept of database per service as mentioned in the section \cref{subse:database_per_service}. This gives the freedom for \acrshort{wdias} to scale better with \acrshort{k8s}.
 
-As shown in Figure \ref{fi:wdias_micro_on_demand}, when a smaller size request come to the system, it handle on demand and response back.
-However, as shown in Figure \ref{fi:wdias_micro_async}, when a request with larger size come to the system, it store the data for asynchronously process the data and response with a unique id which can use to verify whether data processed successfully or not.
-Here is uses the microservice pattern of Section \ref{subse:sagas} while processing the Grid data.
+As shown in \cref{fi:wdias_micro_on_demand}, when a smaller size request come to the system, it handle on demand and response back.
+However, as shown in \cref{fi:wdias_micro_async}, when a request with larger size come to the system, it store the data for asynchronously process the data and response with a unique id which can use to verify whether data processed successfully or not.
+Here is uses the microservice pattern of \cref{subse:sagas} while processing the Grid data.
 First it store the data and respond back to the user.
@@
 \end{figure}
-The figure \ref{fi:wdias_micro_on_demand} show the clear separation of microservices into the modules of the \acrshort{wdias}.
+The \cref{fi:wdias_micro_on_demand} show the clear separation of microservices into the modules of the \acrshort{wdias}.
 As it shown, each adapter has isolated database, and database is hosted separately for the high performance.
-Apart from that, as we further discuss in Section \ref{se:data_preprocess}, the extension modules are running separately such as Interpolation, Transformation and Validation etc.
+Apart from that, as we further discuss in \cref{se:data_preprocess}, the extension modules are running separately such as Interpolation, Transformation and Validation etc.
 The Extension Adapter allow users to register new triggers for the extensions. And extension scheduler triggers the events based on time and extension handler triggers event based on data change.
@@
 
-\emph{Extensions} endpoints for configure extensions. These details describes in the Section \ref{se:data_preprocess}.
+\emph{Extensions} endpoints for configure extensions. These details describes in the \cref{se:data_preprocess}.
 

### 2020-02-14 method/sec_4-db_struct.tex
Change all to \cref

--- 2020-02-11 method/sec_4-db_struct.tex
@@
 
-WDIAS is using a hierarchical database, with following the concept of Database per Service which is described in the \emph{Database per Service} in Section \ref{subse:database_per_service}.
+WDIAS is using a hierarchical database, with following the concept of Database per Service which is described in the \emph{Database per Service} in \cref{subse:database_per_service}.
 Following chapters described the usage of databases in WDIAS and reason behind the selection.
@@
 One instance of \acrshort{mysql} is using only by adapter-metadata service.
-Other than that, another instance of \acrshort{mysql} is using for adapter-extension which will be describe in more detail \ref{se:data_preprocess}.
+Other than that, another instance of \acrshort{mysql} is using for adapter-extension which will be describe in more detail \cref{se:data_preprocess}.
 \acrshort{mysql} is used only for these services, those will only keep the consistency of the schema for timeseries metadata and extension metadata.
-\ref{subse:redis} instance is using for caching the data from \acrshort{mysql}, since the \acrshort{mysql} database instances, itself not going to get much load.
+As mentioned in \cref{subse:redis}, it uses \acrshort{redis} instance is using for caching the data from \acrshort{mysql}, since the \acrshort{mysql} database instances, itself not going to get much load.
 Other than MySQL, there are many open source databases can be used to replace the same functionality.
@@
 Two instance of \acrshort{influxdb} is using in the WDIAS system by adapter-scalar and adapter-vector services.
-For the scalability, the system uses \emph{Database per Service} as mentioned in Section \ref{subse:database_per_service}.
-But further, it split into two services, referring to the Section \ref{subse:scale_cube}, the Z-axis scaling, the data is partitioned among few servers based on valueType key attribute of timeseries.
+For the scalability, the system uses \emph{Database per Service} as mentioned in \cref{subse:database_per_service}.
+But further, it split into two services, referring to the \cref{subse:scale_cube}, the Z-axis scaling, the data is partitioned among few servers based on valueType key attribute of timeseries.
 Which also conclude the concept of splitting into more services based on other key attributes such as timeseriesType, if further performance required.
@@
 Vise a versa, if new timeseries create in the adapter-metadata, it trigger an event to adapter-query to index the new timeseries.
-In Section \ref{subse:scale_cube}, the Y-axis scaling concept is using here by splitting into the multiple services based on the functionality and scale the system.
+In \cref{subse:scale_cube}, the Y-axis scaling concept is using here by splitting into the multiple services based on the functionality and scale the system.
 
@@
 Other than that, adapter-status uses \acrshort{redis} as key value pair store for getting the status for async handling requests such as storing Grid data.
-In adapter-extension uses Redis's Publisher Subscriber capabilities in order to create a cron job in extension-scheduler when new extension create on \ref{se:data_preprocess}
+In adapter-extension uses Redis's Publisher Subscriber capabilities in order to create a cron job in extension-scheduler when new extension create on \cref{se:data_preprocess}

### 2020-02-14 results/sec_0-introduction.tex
Change all to \cref

@@
 
-This chapter includes performance study of the \acrshort{wdias}. In Section \ref{se:test_plan} describes the planned method of testing the system.
-In the next Section \ref{se:workload} describes the logic behind creating the workload to do the performance testing planned in Section \ref{se:test_plan}.
-Following Section \ref{se:observations} includes the results observed while performance study. And summarised the observations in the next Section \ref{se:discussion}.
+This chapter includes performance study of the \acrshort{wdias}. In \cref{se:test_plan} describes the planned method of testing the system.
+In the next \cref{se:workload} describes the logic behind creating the workload to do the performance testing planned in \cref{se:test_plan}.
+Following \cref{se:observations} includes the results observed while performance study. And summarised the observations in the next \cref{se:discussion}.

### 2020-02-14 results/sec_2-workload.tex
Fix with Figure
Change all to \cref

@@
 For grid data, it uses static 100 grid locations which based on how is \acrshort{api} exposed.
-Since grid locations have different metadata structure as described in Section \ref{se:db_struct}, those data handle separately.
+Since grid locations have different metadata structure as described in \cref{se:db_struct}, those data handle separately.
 But the locationId of grid and scalar data types have the same effect when define a timeseries.
@@
 jmeter best practices lean\_mean}.
-Rather providing the randomness in run time, the timeseries stored with the random order which satisfy the percentage of 70\% Scalar, 20\% Vector and 10\% Grid as mentioned in Section \ref{se:test_plan}.
+Rather providing the randomness in run time, the timeseries stored with the random order which satisfy the percentage of 70\% Scalar, 20\% Vector and 10\% Grid as mentioned in \cref{se:test_plan}.
 Before running the test cases, it generate the metadata for timeseries and write into a CSV file which is shared among the threads in the \acrshort{jmeter}.
@@
 
-The test plans mentioned in Section \ref{se:test_plan} are implemented via the \acrshort{jmeter}. The following list shows the all the test cases used for the performance testing:
+The test plans mentioned in \cref{se:test_plan} are implemented via the \acrshort{jmeter}. The following list shows the all the test cases used for the performance testing:
 
@@
 
-In the \ref{fi:test_prod_throughtput_shaping_timer} shows the Throughput Shaping Timer configurations for the All test case.
+In the \cref{fi:test_prod_throughtput_shaping_timer} shows the Throughput Shaping Timer configurations for the All test case.
 
@@
 
-It allows to run particular test plan which are described in Section \ref{se:test_plan}.
-Also possible to run the all the test plans in order with given \emph{REQ\_SIZE} or for all the \emph{REQ\_SIZE}.
+It allows to run particular test plan which are described in \cref{se:test_plan}. Also possible to run the all the test plans in order with given \emph{REQ\_SIZE} or for all the \emph{REQ\_SIZE}.
 
@@
 \label{subse:test_sys_config}
-As described in the Section \ref{se:microservice}, the \acrshort{wdias} is mainly focus on microservice architecture and implemented on top of kubernetes.
+As described in the \cref{se:microservice}, the \acrshort{wdias} is mainly focus on microservice architecture and implemented on top of kubernetes.
 \acrfull{k8s} is an open-source system for automating deployment, scaling, and management of containerized applications.
@@
 \acrshort{k8s} is a planet scaling tool \cite{LinuxFoundationProduction-GradeKubernetes}, and users can tweak the configuration to run the \acrshort{wdias} as per the required level of load on the system.
-During the performance test of the \acrshort{wdias}, it uses maximum of 300 \acrshort{rps} with providing to the system with increasing load, and monitor the auto scalability of the system with measuring other performance parameters mentioned in Table \ref{tab:aws_eks_nodes}.
+During the performance test of the \acrshort{wdias}, it uses maximum of 300 \acrshort{rps} with providing to the system with increasing load, and monitor the auto scalability of the system with measuring other performance parameters mentioned in \cref{tab:aws_eks_nodes}.
 
@@
 For the moment, \acrshort{wdias} helm charts uses node Affinity in order to use the same charts within local setup with one node and work the same charts on a \acrshort{k8s} cluster with multiple nodes.
-Pods are assigned to the nodes \ref{tab:aws_eks_nodes} based on the node label as below;
+Pods are assigned to the nodes \cref{tab:aws_eks_nodes} based on the node label as below;
 \begin{itemize}
@@
 \end{itemize}
-Figure \ref{fi:eks_node_setup} show the overview of show the nodes are setup and each microservices are assigned to each node, the connectivity of the nodes, and the data interactions via the arrows.
+\cref{fi:eks_node_setup} show the overview of show the nodes are setup and each microservices are assigned to each node, the connectivity of the nodes, and the data interactions via the arrows.
 The databases uses for data consistency and performance in storage optimization with search capabilities.

### 2020-02-14 results/sec_3-observations.tex
Change all to \cref

--- 2020-02-11 results/sec_3-observations.tex
@@
 
-According the \ref{se:test_plan} section, this section includes the observations after performing the test plans on the \acrshort{wdias} system setup and test plan test up which is explained in the \ref{se:workload}.
+According the \cref{se:test_plan} section, this section includes the observations after performing the test plans on the \acrshort{wdias} system setup and test plan test up which is explained in the \cref{se:workload}.
 
 Sections \ref{subse:obs_test_plan_all_60min} to \ref{subse:obs_test_plan_all_auto_15min} discuss the observations collected with performing the Load test plans over 60 minutes (24 data points), 30 minutes (48 data points) and 15 minutes (96 data points) by variate the request size.
-Then another performance test with enabling Auto Scaling as explained in \ref{subse:test_plan_metrics} for high resource utilized microservice.
+Then another performance test with enabling Auto Scaling as explained in \cref{subse:test_plan_metrics} for high resource utilized microservice.
 
@@
 
-After running the All test plan with 60 minutes (24 data points), it observed the data summary of \ref{tab:obs_all_60_min_summary}. It performed 311k of sample requests.
+After running the All test plan with 60 minutes (24 data points), it observed the data summary of \cref{tab:obs_all_60_min_summary}. It performed 311k of sample requests.
 
@@
 Retrieve Grid Timeseries data perform the same but with bit higher value of latency of 68ms.
-Both of insert and retrieve grid timeseries data have 4.5 \acrshort{rps} since it only get 10\% of the number of request per given time via the test plan as explain in the data ration in \ref{se:test_plan}.
+Both of insert and retrieve grid timeseries data have 4.5 \acrshort{rps} since it only get 10\% of the number of request per given time via the test plan as explain in the data ration in \cref{se:test_plan}.
 
@@
 \end{figure}
-Figure \ref{fi:test_obs_all_60m_response_vs_threads} shows the response time against the number of active threads.
+\cref{fi:test_obs_all_60m_response_vs_threads} shows the response time against the number of active threads.
 As the graph show, the response time kept same while increasing the number of active threads against each test case.
 This shows the scalability of the \acrshort{wdias}, since the system able to process more requests without a significant change in the latency.
-When number of active threads increased more than 122, the \ref{fi:test_obs_all_60m_response_vs_threads} show uncertainty in the inserting and retrieving Scalar and Vector data.
+When number of active threads increased more than 122, the \cref{fi:test_obs_all_60m_response_vs_threads} show uncertainty in the inserting and retrieving Scalar and Vector data.
 
@@
 
-Figure \ref{fi:test_obs_all_60m_latency} graph provides a better overview of the variation of latency over elapsed time of the test plan against number of server hits per second.
-The conclusion of giving static latency while increasing the number of requests in \ref{fi:test_obs_all_60m_response_vs_threads} can further prove with this graph, since \ref{fi:test_obs_all_60m_latency} graph gives in details overview over the test plan time span.
+\cref{fi:test_obs_all_60m_latency} graph provides a better overview of the variation of latency over elapsed time of the test plan against number of server hits per second.
+The conclusion of giving static latency while increasing the number of requests in \cref{fi:test_obs_all_60m_response_vs_threads} can further prove with this graph, since \cref{fi:test_obs_all_60m_latency} graph gives in details overview over the test plan time span.
 
@@
 \label{subse:obs_test_plan_all_30min}
-This section \ref{subse:obs_test_plan_all_30min} discussed about the All test plan performance with 30 minutes data which means 48 data points per each request in Scalar and Vector timeseries, and 48 ASCII grid files per each insert request.
-It performed round up to 311k of sample requests which is almost similar to \ref{subse:obs_test_plan_all_60min} processed samples.
+This \cref{subse:obs_test_plan_all_30min} discussed about the All test plan performance with 30 minutes data which means 48 data points per each request in Scalar and Vector timeseries, and 48 ASCII grid files per each insert request.
+It performed round up to 311k of sample requests which is almost similar to \cref{subse:obs_test_plan_all_60min} processed samples.
 
@@
 \end{table}
-\ref{tab:obs_all_30_min_summary} shows the response latency summary details and \acrshort{rps} as explained in \ref{subse:obs_test_plan_all_60min}.
-And the results are almost similar to the observations in \ref{tab:obs_all_60_min_summary}.
+\cref{tab:obs_all_30_min_summary} shows the response latency summary details and \acrshort{rps} as explained in \cref{subse:obs_test_plan_all_60min}.
+And the results are almost similar to the observations in \cref{tab:obs_all_60_min_summary}.
 This implies that, even the request size is increased, the \acrshort{wdias} can perform better same as the with smaller size of data.
@@
 \end{figure}
-\ref{fi:test_obs_all_30m_response_vs_threads} show the response time against the number of active threads for 30min data.
+\cref{fi:test_obs_all_30m_response_vs_threads} show the response time against the number of active threads for 30min data.
 As the graph show, the response time kept same while increasing the number of active threads against each test case.
 This shows the scalability of the \acrshort{wdias}, since the system able to process more requests without a significant change in the latency.
-When number of active threads increased more than 110, the \ref{fi:test_obs_all_30m_response_vs_threads} show uncertainty in the inserting and retrieving Scalar and Vector data.
-This graph is similar to the \ref{fi:test_obs_all_60m_response_vs_threads}, but the active thread count goes down as a result of increasing the request size.
+When number of active threads increased more than 110, the \cref{fi:test_obs_all_30m_response_vs_threads} show uncertainty in the inserting and retrieving Scalar and Vector data.
+This graph is similar to the \cref{fi:test_obs_all_60m_response_vs_threads}, but the active thread count goes down as a result of increasing the request size.
 
@@
 \end{figure}
-\ref{fi:test_obs_all_30m_latency} graph provides a better overview of the variation of latency over elapsed time of the test plan against number of server hits per second.
+\cref{fi:test_obs_all_30m_latency} graph provides a better overview of the variation of latency over elapsed time of the test plan against number of server hits per second.
 This graph also conclude that, over the time latency does not change very much. But during the peak load, it shows some variation in insert and retrieve of Grid timeseries.
-When compared to \ref{fi:test_obs_all_60m_latency}, the latency for insert and retrieve Grid timeseries increase by some amount.
+When compared to \cref{fi:test_obs_all_60m_latency}, the latency for insert and retrieve Grid timeseries increase by some amount.
 
@@
 \label{subse:obs_test_plan_all_15min}
-This section \ref{subse:obs_test_plan_all_15min} discussed about the All test plan performance with 15 minutes data which means 96 data points per each request in Scalar and Vector timeseries, and 96 ASCII Grid files per each insert Grid timeseries request.
-These requests are four times larger than the \ref{subse:obs_test_plan_all_60min} request size.
-It performed approximately 311k of sample requests which is almost similar to \ref{subse:obs_test_plan_all_30min} processed samples.
+This \cref{subse:obs_test_plan_all_15min} discussed about the All test plan performance with 15 minutes data which means 96 data points per each request in Scalar and Vector timeseries, and 96 ASCII Grid files per each insert Grid timeseries request.
+These requests are four times larger than the \cref{subse:obs_test_plan_all_60min} request size.
+It performed approximately 311k of sample requests which is almost similar to \cref{subse:obs_test_plan_all_30min} processed samples.
 \begin{table}[ht]
@@
 \end{table}
-\ref{tab:obs_all_15_min_summary} shows the response latency summary details and \acrshort{rps} as same as explained in \ref{subse:obs_test_plan_all_30min}.
-And the latency observations are increased by some amount when compared to the observations in \ref{tab:obs_all_30_min_summary}.
+\cref{tab:obs_all_15_min_summary} shows the response latency summary details and \acrshort{rps} as same as explained in \cref{subse:obs_test_plan_all_30min}.
+And the latency observations are increased by some amount when compared to the observations in \cref{tab:obs_all_30_min_summary}.
 Noticeably retrieving latency of all type of data types increased by considerable amount.
@@
 Event the request data size increased by 4x time, the \acrshort{wdias} were able to handle them without any significant performance issues.
-And the system able to provide the same throughput as \ref{tab:obs_all_30_min_summary}.
+And the system able to provide the same throughput as \cref{tab:obs_all_30_min_summary}.
 
@@
 \end{figure}
-\ref{fi:test_obs_all_15m_response_vs_threads} show the response time against the number of active threads for 15min data.
+\cref{fi:test_obs_all_15m_response_vs_threads} show the response time against the number of active threads for 15min data.
 As the graph show, the response time kept same while increasing the number of active threads against each test case.
@@
 This graph show that over the time \acrshort{wdias} were able to keep the latency constant over the test plan. But at the peak time, it tend to vary from the mean value a lot.
-One noticeable fact is, throw out the test time period, it shows spikes in latency when compared to \ref{fi:test_obs_all_60m_latency} and \ref{fi:test_obs_all_30m_latency}.
+One noticeable fact is, throw out the test time period, it shows spikes in latency when compared to \ref{fi:test_obs_all_60m_latency} and \cref{fi:test_obs_all_30m_latency}.
 
@@
 \end{figure}
-\ref{fi:test_obs_all_15m_latency_percentile} visually shows the summary of \ref{tab:obs_all_15_min_summary} latency up to 90\% percentile.
+\ref{fi:test_obs_all_15m_latency_percentile} visually shows the summary of \cref{tab:obs_all_15_min_summary} latency up to 90\% percentile.
 With a higher request size data, the \acrshort{wdias} able to process the requests without significant change in latency up to 90\% percentile.
@@
 \label{subse:obs_test_plan_all_auto_15min}
-This section \ref{subse:obs_test_plan_all_auto_15min} discussed about the All test plan performance with 15 minutes data which means 96 data points per each request in Scalar and Vector timeseries, and 96 ASCII Grid files per each insert Grid timeseries request.
-These requests are four times larger than the \ref{subse:obs_test_plan_all_60min} request size.
-It performed approximately 311k of sample requests which is almost similar to \ref{subse:obs_test_plan_all_15min} processed samples.
-Other than that, this test plan runs with enabling \acrshort{k8s} Auto Scaling for the high resource utilized microservice as explained in the \ref{subse:test_plan_metrics}.
+This \cref{subse:obs_test_plan_all_auto_15min} discussed about the All test plan performance with 15 minutes data which means 96 data points per each request in Scalar and Vector timeseries, and 96 ASCII Grid files per each insert Grid timeseries request.
+These requests are four times larger than the \cref{subse:obs_test_plan_all_60min} request size.
+It performed approximately 311k of sample requests which is almost similar to \cref{subse:obs_test_plan_all_15min} processed samples.
+Other than that, this test plan runs with enabling \acrshort{k8s} Auto Scaling for the high resource utilized microservice as explained in the \cref{subse:test_plan_metrics}.
 With the test load used for the performance test, import-ascii-grid-upload microservice is using lots of CPU, and adapter-grid microservice is using lots of Memory.
@@
 \end{table}
-\ref{tab:obs_all_auto_15_min_summary} shows the response latency summary details and \acrshort{rps} as same as explained in \ref{subse:obs_test_plan_all_15min}.
+\cref{tab:obs_all_auto_15_min_summary} shows the response latency summary details and \acrshort{rps} as same as explained in \cref{subse:obs_test_plan_all_15min}.
 During this test plan.
 the main focus on the auto scaling enabled microservice.
-As per the insert grid latency in the \ref{tab:obs_all_auto_15_min_summary}, the average insert latency is reduced from 91ms to 87ms.
+As per the insert grid latency in the \cref{tab:obs_all_auto_15_min_summary}, the average insert latency is reduced from 91ms to 87ms.
 Also error percentage reduced from 1.42\% to 0.18\%.
@@
 \label{subse:obs_test_plan_query_15min}
-This section \ref{subse:obs_test_plan_query_15min} discussed about the Query test plan performance.
-It performs multiple information retrieval queries such as query over locations, parameters and timeseries etc which are described over \ref{se:query}.
+This \cref{subse:obs_test_plan_query_15min} discussed about the Query test plan performance.
+It performs multiple information retrieval queries such as query over locations, parameters and timeseries etc which are described over \cref{se:query}.
 It performed approximately 123k of sample requests.
@@
 \end{table}
-\ref{tab:obs_query_15_min_summary} shows the response latency summary details.
+\cref{tab:obs_query_15_min_summary} shows the response latency summary details.
 The average latency is much higher than the minimum value.

### 2020-02-14 results/sec_4-discussion.tex
Change all to \cref

--- 2020-02-10 results/sec_4-discussion.tex
@@
 
-In this section concludes the observations in \ref{se:observations} section against the performance metrics defines in \ref{subse:test_plan_metrics}.
+In this section concludes the observations in \cref{se:observations} section against the performance metrics defines in \cref{subse:test_plan_metrics}.
 
@@
 When look into the \emph{resource utilization} of \acrshort{wdias}; since it is using the \acrshort{k8s} as the container orchestration system, it allows to scale up and cool down the system as required based on the workload.
-This demonstrate on the test plan of \ref{subse:obs_test_plan_all_auto_15min}, and the system get scale up to the maximum at the peak time.
+This demonstrate on the test plan of \cref{subse:obs_test_plan_all_auto_15min}, and the system get scale up to the maximum at the peak time.
 Then cool down to single pod after finishing the test cases.
 Given above \acrshort{wdias} can run from 1 CPU node to nodes with 100 CPUs.
-As described in the \ref{se:microservice}, it uses the many of the concept of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities.
+As described in the \cref{se:microservice}, it uses the many of the concept of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities.
 

### 2020-02-14 summary/sec_1-conclusions.tex
Change all to \cref

--- 2020-02-11 summary/sec_1-conclusions.tex
@@
 And it uses microservice sagas pattern for asynchronous data handling for requests with higher size.
-According to the section \ref{se:microservice}, it uses the many of the concept of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities.
+According to the \cref{se:microservice}, it uses the many of the concept of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities.
 
@@
 Then the test plans are performed with increasing the request size, and monitored the performance metrics.
-The system is setup on the \acrfull{eks} as per the configurations of \ref{subse:test_sys_config}.
+The system is setup on the \acrfull{eks} as per the configurations of \cref{subse:test_sys_config}.
 Based on the observations, the system were able to handle 300 \acrshort{rps} (which means 18,000 requests per minute) successfully with minimizing the error rate to zero.

### 2020-02-14 summary/sec_2-research_limitations.tex
Change all to \cref

@@
 \emph{Grid data performance}:
-As mentioned in the Section \ref{se:discussion}, the adapter-grid is using a Python wrapper for netCDF FORTRAN implementation with parallel IO enabled.
+As mentioned in the \cref{se:discussion}, the adapter-grid is using a Python wrapper for netCDF FORTRAN implementation with parallel IO enabled.
 This has some performance issues as well as memory leak issues.
@@
 \emph{Improve test cases}:
-As described in detail with Section \ref{subse:closed_vs_open_workload}, for \acrshort{wdias} performance test uses Time Stepping Feedback loop with Concurrent Threads which is the best approach support by \acrshort{jmeter} at the moment.
+As described in detail with \cref{subse:closed_vs_open_workload}, for \acrshort{wdias} performance test uses Time Stepping Feedback loop with Concurrent Threads which is the best approach support by \acrshort{jmeter} at the moment.
 But using that it is not possible to get desired \acrshort{rps} for each test case within the test plan.
@@
 \emph{Further improve hierarchical database performance}:
-As further described in Section \ref{se:discussion}, it is possible to increase the performance of these bottlenecks much higher such as using \acrshort{influxdb} Commercial cluster support for high availability or horizontal scaling of \acrshort{influxdb}.
+As further described in \cref{se:discussion}, it is possible to increase the performance of these bottlenecks much higher such as using \acrshort{influxdb} Commercial cluster support for high availability or horizontal scaling of \acrshort{influxdb}.
 With \acrshort{influxdb} cluster, it is possible to run multiple pods of adapter-scalar and adapter-vector for support more server hits per second.
@@
 The adapter-scalar or adapter-vector can improve to plug multiple instance of \acrshort{influxdb} instances by changing the configurations.
-As an example, based on the key attribute Section \ref{subse:timeseries_key_attributes} Timeseries Type, the adapter-scalar can connect to four instance of \acrshort{influxdb} instances such as  External Historical, External Forecast, Simulated Historical, and Simulated Forecast etc.
+As an example, based on the key attribute \cref{subse:timeseries_key_attributes} Timeseries Type, the adapter-scalar can connect to four instance of \acrshort{influxdb} instances such as  External Historical, External Forecast, Simulated Historical, and Simulated Forecast etc.
 

### 2020-02-14 introduction/sec_2-problem_and_objectives.tex
Fixed upto lit review

@@
 \section{Problem Statement}
-Handling spatio-temporal weather data is challenging \db{as ...}.
+Handling spatio-temporal weather data is challenging \db{as} involve with large data volumes required to have higher number of resources such as computation, storage and network bandwidth.
 Moreover, the data integration system needs to be capable of interacting with different data formats including spatio-temporal bulk stream data.
@@
 Scalability and high availability are also essential to support different use cases and mission-critical nature of applications.
-Therefore, we need an extendable system to support weather models by efficiently ingesting, storing, and retrieving data.
+And users should be able to easily deployment and manage the system with modern technologies, and should be able get the advantage of technology advancement.
 In this context, the research problem can be stated as follows:

### 2020-02-14 lit/sec_1-fews.tex
Fixed upto lit review

@@
 Because of the common data model concept in \acrshort{fews}, data processing via these function is much effective.
-The system is self provided some of the generic functions for data processing, but for more complex algorithms can be developed as a new Java class coded to communicate with the {application programming interface (API)}.
+The system is self provided some of the generic functions for data processing, but for more complex algorithms can be developed as a new Java class coded to communicate with the \acrfull{api}.
 It is obvious that for additional feature integration, user should implement the new functional extensions via Java programming language.
@@
 \dbc{Define Abb. for API in Chapter 1.}
+\gkc{FIXED}
 
@@
 \dbc{When referring to a section you need to use the word "Section" as highlighted above. Fix all other places.}
+\gkc{FIXED}
 
@@
 On of the simple and most effective feature in the \acrshort{fews} is open approach to integration of models and data.
-This approaches the concept of the open modeling framework proposed by \cite{Kokkonen2003InterfacingXML}.
+This approaches the concept of the open modeling framework proposed by Open model integration \cite{Kokkonen2003InterfacingXML}.
 It simply gives the flexibility to allow operators to integrate more models as well as variations of the same model and come up with new integration flows as much as possible.
@@
 In some cases these XML files may become very large, which may lead to I/O bottlenecks and subsequent performance issues \cite{Werner2013TheSystem}.
-This issue is thoroughly discussed previous paragraphs and the authors of the \cite{Werner2013TheSystem} seems to be notice and accept it here.
+This issue is thoroughly discussed previous paragraphs and the authors of the \acrshort{fews} \cite{Werner2013TheSystem} seems to be notice and accept it here.
 For overcome this issue they introduced the file-based exchange of data.

### 2020-02-14 lit/sec_3-other-systems.tex
Fixed upto lit review

@@
 \dbc{In Fig. 2.8, is it the data flow?}
+\gkc{The paper is not very much clear. I think it shows data flow with including some of it integration functions.}
 
@@
 As it mentioned above, the \acrshort{madis} is implemented based on a distributed architecture which is available at the time of it's development.
-Even it is not clear mentioned, it is using functional call like Remote Procedure Call (RPC) to invoke among a cluster of nodes as shown in \cref{fi:madis_flow}.
-To get high availability, it has added some update to it's architecture.
+Even it is not clear mentioned, it is using functional call like Remote Procedure Call (RPC) to invoke among a cluster of nodes.
+In \cref{fi:madis_flow}, data are transported from input and preprocessing systems to the central compute systems and then out to other hosts for storage and distribution \cite{Macdermaid2005ARCHITECTUREP2.39}.
+To get high availability, it has added some update to it's architecture as mentioned in the paper.
 The conclusion of this statement is, these kind of functionalities are available at the modern the Cloud Computing tools, and out of the box those tools are providing the scalability and high availability.

### 2020-02-14 method/sec_0_introduction.tex
Fixed upto lit review

@@
 \dbc{Use CUrW-SL}
+\gkc{FIXED}
 
@@
 
-\paragraph{Timeseries}-- A timeseries is simply a series of data points ordered in time.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% \paragraph{Timeseries}-- A timeseries is simply a series of data points ordered in time.
 In weather domain, it interest in timeseries in perspective of observations to forecasting.
@@
 For example, scalar (0D), vector (1D), grid (2D), and polygon (2D).
+
 dbc{Why are you referring to timeseries here? It's not one of the 3 key components in Fig. 3.1.}
+\gkc{Move this to WDIAS microservices \cref{sebse:wdias_microservices}. It need to describe the reason behind decompose into microservices. Seems to be this is confusing at this point.}
 
-In the proof of concept design described below, WDIAS focuses on handling scalar, vector and grid timeseries data. However, the system could be extended to handle polygon-based timeseries as well.
+% In the proof of concept design described below, WDIAS focuses on handling scalar, vector and grid timeseries data. However, the system could be extended to handle polygon-based timeseries as well.
 
-\subsubsection{Base of WDIAS architecture}
+% \subsubsection{Base of WDIAS architecture}
 \dbc{What's Base of WDIAS architecture?}
-\hl{The base of WDIAS architecture origins based on attributes of a timeseries.} %There are many attributes to differentiate timeseries one from another. But 
-Among many attribute to differentiate a timeseries from another, the following can be consider as the key attributes in uniquely identify a timeseries from another: % for the \acrshort{wdias}.
+\gkc{Moved to WDIAS microservices section \cref{sebse:wdias_microservices}}
+
+% \hl{The base of WDIAS architecture origins based on attributes of a timeseries.} There are many attributes to differentiate timeseries one from another. But 
+% Among many attribute to differentiate a timeseries from another, the following can be consider as the key attributes in uniquely identify a timeseries from another: % for the \acrshort{wdias}.
 \dbc{Highlighted sentence doesn't make sense to me. All yellow highlights mean they are not clear.}
 
-\begin{itemize}
-    \item Module -- module that generates the timeseries
-    \item Value type -- Scalar, vector, grid, or polygon
-    \item Location of readings
-    \item Parameter -- measuared parameter
-    \item hl{Timeseries type}
-    \begin{itemize}
-        \item Sources -- External or simulated
-        \item Category -- Historical or forecast
-    \end{itemize}
-    \item Time step
-\end{itemize}
-\dbc{Use bullets only when essential. Other places use paragraphs.}
+% \begin{itemize}
+%     \item Module -- module that generates the timeseries
+%     \item Value type -- Scalar, vector, grid, or polygon
+%     \item Location of readings
+%     \item Parameter -- measuared parameter
+%     \item hl{Timeseries type}
+%     \begin{itemize}
+%         \item Sources -- External or simulated
+%         \item Category -- Historical or forecast
+%     \end{itemize}
+%     \item Time step
+% \end{itemize}
+% \dbc{Use bullets only when essential. Other places use paragraphs.}
 
-A detail description of the above attributes are presented in \cref{se:db_struct}.
+% A detail description of the above attributes are presented in \cref{se:db_struct}.

### 2020-02-14 lit/sec_1-fews.tex
Moved k8s to architectural decisions

@@
 In \cref{se:dias}, we discussed about \acrfull{dias} which is a common data platform that can work with weather data.
-\acrfull{madis} is another widely use data integration system, which also provide data access with quality control, whihc we discuss in \cref{se:madis}.
+\acrfull{madis} is another widely use data integration system, which also provide data access with quality control, which we discuss in \cref{se:madis}.
 Under each system we explore both system architecture, scalability, and flexibility of the system.

### 2020-02-14 lit/sec_3-other-systems.tex
Moved k8s to architectural decisions

@@
 
-\acrshort{dias} collects and files data from satellites, ground observation stations, numerical weather prediction models and climate change projection models.
+\acrfull{dias} collects and files data from satellites, ground observation stations, numerical weather prediction models and climate change projection models.
 Once this data is integrated with geographic and socio-economic information, DIAS generates results for managing global environmental issues and natural disasters \cite{Kawasaki2018DataReduction}.

### 2020-02-14 method/sec_0_introduction.tex
Moved k8s to architectural decisions

@@
 This chapter includes the design decision taken while implementing the \acrfull{wdias}, and how is the system got adapted from the systems analyzed in Chapter \ref{ch:literature}.
-%, then how is it trying to propose a better system with overcoming the issues.
 In \cref{se:high_level_design} a brief discussion on how the weather forecasting is happening and why it need to interact with multiple data formats is presented.
-Then following subsections define few termelogy which are using in the \acrshort{wdias}, and scope of the thesis.
-\cref{se:architectural_decisions} that we evolve over while designing and implementing the \acrshort{wdias}.
+\cref{se:architectural_decisions} that we evolve architectural design while designing and implementing the \acrshort{wdias}.
 The \cref{se:microservice} gives better understanding of the microservice architectural concepts follows while implementing the \acrshort{wdias}.
-Then the reason behind developing Heirarchital Database and technologies use for that discussed in the \cref{se:db_struct}.
-Throw out the \cref{se:data_preprocess} discussed about how the \acrshort{wdias} enable for data preprocessing and adding capabilities via concept of Extensions.
-Finally, in \cref{se:query} includes details on how to perform timeseries search and geo based queries.
+Then the reason behind developing Hierarchical Database and technologies use for that discussed in the \cref{se:db_struct}.
+Through out the \cref{se:data_preprocess} discussed about how the \acrshort{wdias} enable for data preprocessing and adding capabilities via concept of Extensions.
+Final \cref{se:query} includes details on how to perform timeseries search and Geo based queries.
 
@@
 \begin{enumerate}
-    \item Extract GRIB WRF model data to netCDF
-    \item From netCDF to CSV of each location data, then feed to HEC-HMS and get the output as CSV
-    \item CSV and Rain cell Grid feed into the FLO2D, and get the water level as Grid ASCII files after completion of simulation
+    \item Extract \acrshort{GRIB} \acrshort{wrf} model data to \acrshort{netCDF}
+    \item From \acrshort{netCDF} to \acrshort{csv} of each location data, then feed to HEC-HMS hydro-dynamic model and get the output as \acrshort{csv}
+    \item \acrshort{csv} and Rain cell Grid feed into the FLO2D hydro-logic model, and get the water level as ASCII Grid files after completion of simulation
     \item Upload ASCII files to ArcGIS create Raster files, then use for the LOSS Estimation
@@
 
-dbc{Why are you referring to timeseries here? It's not one of the 3 key components in Fig. 3.1.}
+\dbc{Why are you referring to timeseries here? It's not one of the 3 key components in Fig. 3.1.}
 \gkc{Move this to WDIAS microservices \cref{sebse:wdias_microservices}. It need to describe the reason behind decompose into microservices. Seems to be this is confusing at this point.}

### 2020-02-14 method/sec_1-architectural_decisions.tex
Moved k8s to architectural decisions

@@
 Initial design of \acrshort{wdias} used the \acrfull{soa}.
-Moreover, it tried to use an \acrfull{esb} to integrate different modules, as it is acting as a common layer for all of modules.
-By default, \acrshort{esb} provides publisher/subscribe (pub/sub) capabilities.
+Moreover, it tried to use an \acrfull{esb} to integrate different modules, as \acrshort{esb} is acting as a common layer for all of modules.
+By default, \acrshort{esb} also provides publisher/subscribe (pub/sub) capabilities.
 \hl{Because} \acrshort{esb} \hl{mediator can be used to integrate the modules which are described in Section} \ref{subse:modules_weather_data_integration_sys}. 
+\gkc{FIXED}
+The \acrshort{esb} has the processing units called \emph{mediators}.
+A mediator can take a message, carry out some predefined actions on it, and output the modified message.
+This mediator capabilities can use to integrate the modules of a weather data system as shown in \cref{fi:wdia_components}.
 \acrshort{esb} also support different transportation protocols such as HTTP and Web sockets.
 However, it turned out that \acrshort{esb} is not a suitable for data streaming or bulk data processing.
-Also, \acrshort{esb} suffer from single point of failure, as all the messages are going though a common bus.
+Also, \acrshort{esb} suffer from single point of failure, as all the messages are going though a common bus and slower communication (can’t use for transfer data).
 
-In the second design round of \acrshort{wdias}, we attempted to use the actor model using AKKA framework \cite{HewittWhyModel}. %However, after consider into the disadvantage of using \acrshort{esb}. 
-Using the actors we tried to implement the microservice architecture. In that case, an actor or an actor with slave actors were map to each microservice in \acrshort{wdias}.
+In the second design phase of \acrshort{wdias}, we attempted to use the actor model using AKKA framework \cite{HewittWhyModel} in order to overcome above \acrshort{esb} drawbacks.
+At the same time, we moved away from the \acrshort{soa} architecture design to the microservice architecture design.
+Thus we redesign the system architecture with decompose into microservices and used actors to implement each microservice in the system.
+In that case, an actor or an actor with slave actors were map to each microservice in \acrshort{wdias}.
+\acrshort{soa} focuses on imperative programming, whereas microservices architecture focuses on a responsive-actor programming style using faster messaging mechanisms.
 
-/hl{The typical \acrshort{soa} model, for example, usually has more dependent \acrshort{esb}s, with microservices using faster messaging mechanisms.
-\acrshort{soa} also focuses on imperative programming, whereas microservices architecture focuses on a responsive-actor programming style.
-Moreover, \acrshort{soa} models tend to have an outsized relational database, while microservices frequently use NoSQL or micro-SQL databases (which can be connected to conventional databases).
-But the real difference has to do with the architecture methods used to arrive at an integrated set of services in the first place.}
-\dbc{Multiple design rounds and decisions are mixed in the para. First finish discussing ESB. Then finish actor model in another para. Then focus on mircoservice details.}
-
-%As mentioned above, \acrshort{esb} support to implement \acrshort{soa}.
-But \acrshort{soa} has limitations such as single point of failure, slower communication (can’t use for transfer data) etc.
-So, the microservice architecture get evolved and demanding for the moment.
 When compare to \acrshort{soa}, the microservice architecture has several advantages such as the following:
@@
 
-Even with using the AKKA framework, it has some of the disadvantage as described in AKKA documentation \cite{Akka.ioWhenCluster}.
-Even Actor model capable of implementing a microservice architecture, it has few disadvantage.
-To overcome these issues, we moved to the \acrfull{k8s} \cite{LinuxFoundationProduction-GradeKubernetes}.
+% /hl{The typical \acrshort{soa} model, for example, usually has more dependent \acrshort{esb}s, with microservices using faster messaging mechanisms.
+\acrshort{soa} also focuses on imperative programming, whereas microservices architecture focuses on a responsive-actor programming style.}
+\dbc{Multiple design rounds and decisions are mixed in the para. First finish discussing ESB. Then finish actor model in another para. Then focus on mircoservice details.}
+
+Even with using the AKKA framework, it has some of the disadvantage with implementing each microservice as an actor as described in AKKA documentation \cite{Akka.ioWhenCluster}.
+One of the attractive feature of microservice architecture is independent nature of the microservices.
+This allows to choose a different technology for each microservice based on the advantage that could bring in.
+Also allowed to independently develop and maintain by multiple smaller and more focused teams/communities.
+But using the actors as microservice, the actors messaging between different services cause to result in a too tight code coupling between the services and difficulties deploying these independent of each other, which is one of the main reasons for using a microservices architecture \cite{Akka.ioWhenCluster}.
+To overcome these issues, we moved to the concept of container-orchestration based architecture.
+
 \dbc{Kubernetes is a product. What you need to refer is to the concept of container-orchestration. Fix.}
 
+% \begin{itemize}
+%     \item \hl{Unable to choose technology. But} \acrshort{k8s} \hl{allows you to choose technology that is best suited for a particular functionality}
+%     \item \hl{As mentioned in the AKKA documentation} \cite{Akka.ioWhenCluster}, \hl{it is better for developing one microservice within the whole} \acrshort{wdias} design.
+% \end{itemize}
+
+\dbc{What are these 2 bullets?}
+\gkc{Absorbed those two points into above paragraph}
+\dbc{Don't use shortened words like it's, isn't, don't,... in writing}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \subsection{Brief introduction to the \acrfull{k8s}}
+% \label{sebse:k8s_intro}
+
+Containerization is an alternative to the virtualization that supports via virtual machines or Hypervisors.
+It involves encapsulating or packaging up software code and all its dependencies so that it can run uniformly and consistently on any infrastructure \cite{IBMContainerizationExplained}.
+The concept of containerization and process isolation is emerged after the open source Docker Engine \cite{DockerAppContainerization}, an industry standard for package software into standardized units for development, shipment and deployment.
+
+\acrfull{k8s} is an open-source system for automating deployment, scaling, and management of containerized applications \cite{LinuxFoundationProduction-GradeKubernetes}.
+It groups containers that make up an application into logical units for easy management and discovery.
+While implementing the \acrshort{wdias}, we used \acrshort{k8s} as the container-orchestration system, in order to deploy each microservice as container and manage with providing scalability and availability.
+
+\begin{figure}[htp]
+    \centering
+    \includegraphics[width=1\textwidth]{method/microservice/k8s_architecture_v3.jpg}
+    \caption{\acrfull{k8s} architecture.}
+    \label{fi:k8s_architecture}
+\end{figure}
+\cref{fi:k8s_architecture} gives an overall idea on the components of \acrshort{k8s},
 \begin{itemize}
-    \item \hl{Unable to choose technology. But} \acrshort{k8s} \hl{allows you to choose technology that is best suited for a particular functionality}
-    \item \hl{As mentioned in the AKKA documentation} \cite{Akka.ioWhenCluster}, \hl{it is better for developing one microservice within the whole} \acrshort{wdias} design.
+    \item Pods -- Cluster of containers that can group other container images in a single unit.
+    \item Nodes -- the machines (VMs, physical servers, etc) in a cluster that run your applications and cloud workflows.
+    \item kubelet -- An agent that runs on each node in the cluster. It makes sure that containers are running in a pod.
+    \item kube-proxy -- A network proxy that runs on each node in the cluster, and maintains network rules on nodes.
+    \item Kubernetes master -- Responsible for maintaining the desired state for your cluster.
+    \item etcd -- Consistent and highly-available key value store used as Kubernetes’ backing store for all cluster data.
 \end{itemize}
 
-\dbc{What are these 2 bullets?}
-\dbc{Don't use shortened words like it's, isn't, don't,... in writing}
+Users can add much as required Nodes into the \acrshort{k8s} cluster, and \acrshort{k8s} manage and deploy application as pods into cluster nodes.
+Each microservice can deploy as a Pod which is a group of containerize applications. And \acrshort{k8s} able to scale as much as user want as described above.
+By separating each microservice as a container, and running them as multiple pods inside the \acrshort{k8s} removes the tight coupling of microservices when compared to the actors.
+This preserves the independent nature of the microservices which allows to high scale the system.

### 2020-02-14 method/sec_3-microservice.tex
Moved k8s to architectural decisions

@@
 \section{Microservice Architecture}
+\label{se:microservice}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Brief introduction to the \acrfull{k8s}}
-\label{sebse:k8s_intro}
+% \subsection{Brief introduction to the \acrfull{k8s}}
+% \label{sebse:k8s_intro}
 \dbc{Don't present this as a separate section. Either this need to be in the literature survey, or integrate key ideas into another section as a paragraph.}
-
-\acrfull{k8s} is an open-source system for automating deployment, scaling, and management of containerized applications \cite{LinuxFoundationProduction-GradeKubernetes}.
-It groups containers that make up an application into logical units for easy management and discovery.
-\begin{figure}[htp]
-    \centering
-    \includegraphics[width=1\textwidth]{method/microservice/k8s_architecture_v3.jpg}
-    \caption{\acrfull{k8s} architecture.}
-    \label{fi:k8s_architecture}
-\end{figure}
-Components of \acrshort{k8s},
-\begin{itemize}
-    \item Pods -- Cluster of containers that can group other container images in a single unit.
-    \item Nodes -- the machines (VMs, physical servers, etc) in a cluster that run your applications and cloud workflows.
-    \item kubelet -- An agent that runs on each node in the cluster. It makes sure that containers are running in a pod.
-    \item kube-proxy -- A network proxy that runs on each node in the cluster, and maintains network rules on nodes.
-    \item Kubernetes master -- Responsible for maintaining the desired state for your cluster.
-    \item etcd -- Consistent and highly-available key value store used as Kubernetes’ backing store for all cluster data.
-\end{itemize}
-Users can add much as required Nodes into the \acrshort{k8s} cluster, and \acrshort{k8s} manage and deploy application as pods into cluster nodes.
-Each microservice can deploy as a Pod which is a group of containerize applications. And \acrshort{k8s} able to scale as much as user want as described above.
+\gkc{Move this as a paragraph at the end of the architectural design}
 

### 2020-02-14 method/sec_3-microservice.tex
Fixed: microservice intro

@@
 
-The microservice architectural style is an approach to developing a single application as a suite of small services, each running in its own process and communicating with lightweight mechanisms, often \hl{an HTTP resource API}.
-These services are built around business capabilities and independently deployable by fully automated deployment machinery.
-\hl{There is a bare minimum of centralized management of these services, which may be written in different programming languages and use different data storage technologies} \cite{LewisMicroservices}.
+The microservice architectural style is an approach to developing a single application as a suite of small services, each running in its own process and communicating with lightweight mechanisms, often via providing \hl{an RESTful API}.
+These services are built around business capabilities and independently deployable by fully automated deployment machinery \cite{LewisMicroservices}.
+\hl{These services are implement independently with minimising the centralized dependencies.
+Thus each microservice may be written in different programming languages and use different data storage technologies}.
 
-\hl{Among the characteristics of microservice, a few characteristics heavily affect while moving from} \acrshort{soa} to microservice.
+% \hl{Among the characteristics of microservice, a few characteristics heavily affect while moving from} \acrshort{soa} to microservice.
 \dbc{M in Microservice should be capitalized only on begining of a sentence.}
+
+There are lots of microservice patterns developed and evolved over the time.
+Through out the following sections, we will discuss in brief about some of the microservice design patterns mostly used on the context of designing \acrshort{wdias} architecture.
+Next, we will discuss about how microservice architecture promote to only to create endpoints which are only belongs to each service logical domain.
+Next discuss about only using database per service which allows to loosely couple between system and achieve high scalability.
+In Sagas, we discuss about how distributed transaction can achieve over microservices.
+Next, we will discuss about a concept called as \emph{scale cube}, which explains the scalability in perspective of x,y and z axis.
 
@@
 \dbc{At the end of previous para tell what will be discussed in the next set of sub-section. A single sentence like "Next, we will discusss ...." is enough}
+\gkc{FIXED}
 

### 2020-02-14 method/sec_3-microservice.tex
Updated Microservice architecture

@@
 
-When building communication endpoints, \hl{many architecture approach with putting significant smart into the communication mechanism.} One good example is \acrshort{esb} what we discussed in \cref{se:architectural_decisions}.
+When building communication endpoints, \hl{many architectural approaches are adding significant smart by providing different protocol supports and complex logic support via the endpoints.} As an example \acrshort{esb} support multiple protocols and endpoints can use complex logic.
 But microservice follows alternative approach: \emph{Smart endpoints and dumb pipes} \cite{LewisMicroservicesPipes}.
@@
 After receiving a request, applying logic as appropriate and producing a response.
-And it uses simple RESTish protocols rather than complex protocols.
+And it uses simple RESTful protocols rather than complex protocols.
 \dbc{RESTish or RESTful?}
+\gkc{Yes. Changed.}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{\hl{Pattern: Database per Service}}
+\subsection{\hl{Database per Microservice}}
 \label{subse:database_per_service}
-\hl{- Pattern: Database per service}
 
@@
 
-Keep each microservice’s persistent data private to that service and accessible only via its API. 
-There are a few different ways to keep a service’s persistent data private.
-You do not need to provision a database server for each service.
-For example, if you are using a relational database then the options are \cite{RichardsonMicroservicesService}:
+The idea is to keep each microservice’s persistent data private to that service and accessible only via its \acrshort{api}. 
+There are a few different ways to keep a service's persistent data private.
+It is not need to provision a database server for each service.
+For example, in the case of using a relational database then following methods can be use to keep data private \cite{RichardsonMicroservicesService}:
 \begin{itemize}
-    \item \emph{Private-tables-per-service} –- each service owns a set of tables that must only be accessed by that service
-    \item \emph{Schema-per-service} –- each service has a database schema that’s private to that service
-    \item \emph{Database-server-per-service} -– each service has its own database server.
+    \item \emph{Private tables per service} –- each service owns a set of tables that must only be accessed by that service
+    \item \emph{Schema per service} –- each service has a database schema that’s private to that service
+    \item \emph{Database server per service} -– each service has its own database server.
 \end{itemize}
-Private-tables-per-service and schema-per-service have the lowest overhead.
-Using a schema per service is appealing since it makes ownership clearer.
+\emph{Private tables per service} and \emph{schema per service} have the lowest overhead.
+Using a \emph{schema per service} is appealing since it makes ownership clearer.
 Some high throughput services might need their own database server.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{\hl{Pattern: Sagas}}
+\subsection{\hl{Distributed Transactions over Microservices}}
 \label{subse:sagas}
-In order to ensure loose coupling, each service has its own database.
+In order to ensure loose coupling, each microservice better to have own database.
 Maintaining data consistency between services is a challenge because 2 phase-commit/distributed transactions is not an option for many applications.
-An application must instead use the Saga pattern.
 A service publishes an event when its data changes.
 Other services consume that event and update their data \cite{RichardsonMicroservicesSagas}.
+This is also called as \emph{Saga pattern}.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{\hl{The Scale Cube}}
+\subsection{\hl{Concept of Scale Cube}}
 \label{subse:scale_cube}
-The scalability of a system can explain via a concept called \emph{Scale Cube} which talk about the scalability of the application throw X, Y and Z axis.
+\gkc{I can not think about any other title than this.}
+The scalability of a system can explain via a concept called \emph{Scale Cube} which talk about the scalability of the application by defining over X, Y and Z axis.
 
-\paragraph{x-axis Saling}-- x-axis scaling consists of running multiple copies of an application behind a load balancer.
+\paragraph{X-axis Scaling}-- X-axis scaling consists of running multiple copies of an application behind a load balancer.
 If there are \textit{n} copies then each copy handles 1/\textit{n} of the load.
-This is a simple, commonly used approach of scaling an application \hl{TODO}.
+This is a simple, commonly used approach of scaling a service.
 
-\paragraph{y-axis Scaling}-- Unlike x-axis and x-axis, which consist of running multiple, identical copies of the application, y-axis axis scaling splits the application into multiple, different services.
+\paragraph{Y-axis Scaling}-- Unlike X-axis and Z-axis, which consist of running multiple, identical copies of the application, Y-axis axis scaling splits the application into multiple, different services.
 Each service is responsible for one or more closely related functions.
@@
 \begin{itemize}
-    \item verb-based decomposition ex: checkout.
+    \item verb-based decomposition e.g., checkout.
     \item decompose the application by noun, for e.g., customer management. 
-    \item An application might use a combination of verb-based and noun-based decomposition.
+    \item an application might use a combination of verb-based and noun-based decomposition.
 \end{itemize}
 
-The microservice architecture is an application of Y-axis scaling.
+\emph{The microservice architecture is an application of Y-axis scaling}.
 
-\paragraph{Z-axis Scaling}-- When using x-axis scaling each server runs an identical copy of the code (similar to X-axis scaling).
+\paragraph{Z-axis Scaling}-- When using Z-axis scaling each server runs an identical copy of the code (similar to X-axis scaling).
 The big difference is that each server is responsible for only a subset of the data.
@@
 \dbc{Don't present this as a separate section. Either this need to be in the literature survey, or integrate key ideas into another section as a paragraph.}
-\gkc{Move this as a paragraph at the end of the architectural design}
+\gkc{Move this as a paragraph at the end of the architectural decisions}
 

### 2020-02-14 thesis.tex
Test with cref for the reference naming
Moved k8s to architectural decisions
Updated Microservice architecture

@@
 \newcommand{\dbc}[1]{\todo[author=Dilum, inline, color=blue!40]{#1}}
+\newcommand{\gkc}[1]{\todo[author=Gihan, inline, color=green!50]{#1}}
 
-\newcommand{\gkc}[1]{\todo[author=Gihan, inline, color=green!50]{#1}}
+\usepackage[noabbrev,capitalise]{cleveref}
 
@@
   breaklines=true,
-  captionpos=b,                    
   keepspaces=true,
@@
   showtabs=false,
-  tabsize=2
+  tabsize=2,
+  framesep=0pt
 }
@@
 
-\import{introduction/}{sec_1-motivation.tex}
+% \import{introduction/}{sec_1-motivation.tex}
 
-\import{introduction/}{sec_2-problem_and_objectives.tex}
+% \import{introduction/}{sec_2-problem_and_objectives.tex}
 
-\import{introduction/}{sec_3-outline.tex}
+% \import{introduction/}{sec_3-outline.tex}
 
@@
 
-\import{lit/}{sec_1-fews.tex}
+% \import{lit/}{sec_1-fews.tex}
 
-\import{lit/}{sec_2-lead.tex}
+% \import{lit/}{sec_2-lead.tex}
 
-\import{lit/}{sec_3-other-systems.tex}
+% \import{lit/}{sec_3-other-systems.tex}
 
@@
 \import{method/}{sec_0_introduction.tex}
-\label{se:method_intro}
 
@@
 \import{method/}{sec_3-microservice.tex}
-\label{se:microservice}
 
 \import{method/}{sec_4-db_struct.tex}
-\label{se:db_struct}
 
 \import{method/}{sec_5-data_preprocess.tex}
-\label{se:data_preprocess}
 
 \import{method/}{sec_6-query.tex}
-\label{se:query}
 

### 2020-02-14 method/sec_3-microservice.tex
Explained API convention more

@@
     \includegraphics[width=1\textwidth]{method/microservice/microservice_architecture-handle_on_demand-v3.jpg}
-    \caption{\acrshort{wdias} architecture \hl{for server requests on demand}}
+    \caption{\acrshort{wdias} architecture for handling requests on demand}
     \label{fi:wdias_micro_on_demand}
@@
 \label{sebse:wdias_api}
-One of the main design consideration in \acrshort{wdias} is the convention of defining the APIs. It follows the simple RESTful API, and allow users to interact with HTTP methods.
+One of the main design consideration in \acrshort{wdias} is the convention of defining the \acrshort{api}. It follows a simple RESTful \acrshort{api}, and allow users to interact with HTTP methods.
 
 \emph{Timeseries} endpoints allow to interact with Metadata Adapter, and those are cache on the Query Handler in order to perform search queries.
+These are the main endpoints to handle timeseries metadata which defines unique timeseries identifier based on the metadata values.
+As an example, if it needs to extend the system to store irregular grid data, then it should add another set of location endpoints for storing irregular grid location details.
 \begin{itemize}
@@
 \begin{itemize}
-    \item \emph{/import/json/raw}
-    \item \emph{/import/ascii-grid/upload}
+    \item \texttt{POST import/json/raw} -- Insert Scalar/Vector timeseries data with JSON body
+    \item \texttt{POST import/csv/raw} -- Insert Scalar/Vector timeseries data in CSV format
+    \item \texttt{POST import/ascii-grid/upload} -- Upload set of ASCII Grid files
+    \item \texttt{POST import/ascii-grid/binary} -- Upload a single ASCII Grid file
 \end{itemize}
@@
 \begin{itemize}
-    \item \emph{/export/json/raw}
-    \item \emph{/export/ascii-grid/binary}
+    \item \texttt{GET export/json/raw} -- Get Scalar/Vector timeseries data in JSON format
+    \item \texttt{GET export/json/raw?start=2000-01-01\&end=2000-01-03} -- Get Scalar/Vector timeseries data in JSON format for given time period
+    \item \texttt{GET export/netcdf/binary} -- Download Grid data timeseries data in \acrshort{netCDF} format
 \end{itemize}
@@
 
-The API convention of \texttt{\hl{/MODULE/DATA\_FORMAT/DATA\_OPERATION\_TYPE}}  allows users to integrate new import or export modules into the system as well as add new data types.
+As it mentioned above, other than the timeseries metadata which is the core of the data system, other module endpoints start with the module name such as import, export and extension.
+This allows to add new module system if required.
+For import and export modules, then follows by the data format. This provide the flexibility to integrate new data format modules.
+Then the endpoint name ends with the data upload/insert data type.
+Data can upload as a single file with binary or multiple files with upload.
+Or in the body of the request as raw, and need to send the required headers has mentioned by particular module.
+Thus the \acrshort{api} convention of \texttt{\hl{/MODULE/DATA\_FORMAT/DATA\_DATA\_TYPE}} allows users to integrate new import or export modules into the system as well as add new data types.

### 2020-02-14 method/sec_3-microservice.tex
change API with texttt

@@
 The metadata is cached with In-Memory database to fast access as mentioned in \cref{subse:redis}.
-The system generate a unique identifier for each timeseries, and throw out the \acrshort{wdias}, other microservice use it to handle data for fast access.
+The system generate a unique identifier for each timeseries, and through out the \acrshort{wdias}, other microservice use it to handle data for fast access.
 
@@
     \begin{itemize}
-        \item \texttt{GET timestep} -- Get TimeSteps
-        \item \texttt{POST timestep} -- Create TimeStep
-        \item \texttt{PUT timestep/id} -- Update TimeStep
-        \item \texttt{DELETE timestep/id} -- Delete TimeStep
+        \item \texttt{GET /timestep} -- Get TimeSteps
+        \item \texttt{POST /timestep} -- Create TimeStep
+        \item \texttt{PUT /timestep/id} -- Update TimeStep
+        \item \texttt{DELETE /timestep/id} -- Delete TimeStep
     \end{itemize}
@@
     \begin{itemize}
-        \item \emph{GET /location} - Get location points
-        \item \emph{POST /location} - Create location point
-        \item \emph{PUT /location/id} - Update location point
-        \item \emph{DELETE /location/id} - Delete location point
-        \item \emph{GET /location/regular-grid} - Get regular grids
-        \item \emph{POST /location/regular-grid} - Create regular grid
-        \item \emph{PUT /location/regular-grid/id} - Update regular grid
-        \item \emph{DELETE /location/regular-grid/id} - Delete regular grid
+        \item \texttt{GET /location} -- Get location points
+        \item \texttt{POST /location} -- Create location point
+        \item \texttt{PUT /location/id} -- Update location point
+        \item \texttt{DELETE /location/id} -- Delete location point
+        \item \texttt{GET /location/regular-grid} -- Get regular grids
+        \item \texttt{POST /location/regular-grid} -- Create regular grid
+        \item \texttt{PUT /location/regular-grid/id} -- Update regular grid
+        \item \texttt{DELETE /location/regular-grid/id} -- Delete regular grid
     \end{itemize}
@@
     \begin{itemize}
-        \item \emph{GET /timeseries} - Get timeseries
-        \item \emph{POST /timeseries} - Create timeseries
-        \item \emph{PUT /timeseries/id} - Update timeseries
-        \item \emph{DELETE /timeseries/id} - Delete timeseries
+        \item \texttt{GET /timeseries} -- Get timeseries
+        \item \texttt{POST /timeseries} -- Create timeseries
+        \item \texttt{PUT /timeseries/id} -- Update timeseries
+        \item \texttt{DELETE /timeseries/id} -- Delete timeseries
     \end{itemize}
@@
 \begin{itemize}
-    \item \texttt{POST import/json/raw} -- Insert Scalar/Vector timeseries data with JSON body
-    \item \texttt{POST import/csv/raw} -- Insert Scalar/Vector timeseries data in CSV format
-    \item \texttt{POST import/ascii-grid/upload} -- Upload set of ASCII Grid files
-    \item \texttt{POST import/ascii-grid/binary} -- Upload a single ASCII Grid file
+    \item \texttt{POST /import/json/raw} -- Insert Scalar/Vector timeseries data with JSON body
+    \item \texttt{POST /import/csv/raw} -- Insert Scalar/Vector timeseries data in CSV format
+    \item \texttt{POST /import/ascii-grid/upload} -- Upload set of ASCII Grid files
+    \item \texttt{POST /import/ascii-grid/binary} -- Upload a single ASCII Grid file
 \end{itemize}
@@
 \begin{itemize}
-    \item \texttt{GET export/json/raw} -- Get Scalar/Vector timeseries data in JSON format
-    \item \texttt{GET export/json/raw?start=2000-01-01\&end=2000-01-03} -- Get Scalar/Vector timeseries data in JSON format for given time period
-    \item \texttt{GET export/netcdf/binary} -- Download Grid data timeseries data in \acrshort{netCDF} format
+    \item \texttt{GET /export/json/raw} -- Get Scalar/Vector timeseries data in JSON format
+    \item \texttt{GET /export/json/raw?start=2000-01-01\&end=2000-01-03} -- Get Scalar/Vector timeseries data in JSON format for given time period
+    \item \texttt{GET /export/netcdf/binary} -- Download Grid data timeseries data in \acrshort{netCDF} format
 \end{itemize}

### 2020-02-14 results/sec_3-observations.tex
change API with texttt

@@
 This graph show that over the time \acrshort{wdias} were able to keep the latency constant over the test plan. But at the peak time, it tend to vary from the mean value a lot.
-One noticeable fact is, throw out the test time period, it shows spikes in latency when compared to \ref{fi:test_obs_all_60m_latency} and \cref{fi:test_obs_all_30m_latency}.
+One noticeable fact is, through out the test time period, it shows spikes in latency when compared to \ref{fi:test_obs_all_60m_latency} and \cref{fi:test_obs_all_30m_latency}.
 
@@
 This graph show that over the time \acrshort{wdias} were able to keep the latency constant over the test plan.
-When compared to \ref{fi:test_obs_all_15m_latency}, throw out the test time period, the latency spikes become less.
+When compared to \ref{fi:test_obs_all_15m_latency}, through out the test time period, the latency spikes become less.
 

### 2020-02-14 method/sec_3-microservice.tex
Updates from Overleaf
Complete performance analysis

@@
 \dbc{Format others as above}
+\gkc{FIXED}
     \item location
@@
 Or in the body of the request as raw, and need to send the required headers has mentioned by particular module.
-Thus the \acrshort{api} convention of \texttt{\hl{/MODULE/DATA\_FORMAT/DATA\_DATA\_TYPE}} allows users to integrate new import or export modules into the system as well as add new data types.
+Thus the \acrshort{api} convention of \texttt{\hl{/MODULE/DATA\_FORMAT/DATA\_TYPE}} allows users to integrate new import or export modules into the system as well as add new data types.

### 2020-02-14 method/sec_4-db_struct.tex
Moved k8s to architectural decisions
Updated Microservice architecture
Complete performance analysis

@@
-\section{Hierarchical Database}
+\section{\acrshort{wdias} Database Structure}
+\label{se:db_struct}
 
-The database structure of WDIAS mainly depends on the key attributes of the timeseries. \hl{A brief summary of possible value for timeseries can be describe as below};
-\dbc{Clerly mention why a hierarchical design is needed.}
+In order to understand the underline design decisions of \acrshort{wdias} database structure, it need to deeply look into the weather data timeseries.
+\paragraph{Timeseries}-- \emph{A timeseries is simply a series of data points ordered in time}.
+In weather domain, it interest in timeseries in perspective of observations to forecasting.
+Each timeseries, the data points can be form in different formats as well.
+For example, scalar (0D), vector (1D), grid (2D), and polygon (2D).
+
+As per the above interpretation, a timeseries have data points ordered in time.
+Other than that, timeseries have other information which are known as \emph{timeseries metadata} which can use to uniquely identify one timeseries from another.
+As an example, a weather station can placed on a location and it can keep measure variables which are called as \emph{parameters} such as temperature, precipitation and wind direction which can produce different timeseries.
+Even we can use the location as metadata to identify the timeseries, that is not enough to separately identify the parameters.
+Thus we need to use set of attributes to uniquely identify a timeseries.
+In the next \cref{subse:timeseries_key_attributes}, we describe about key attributes which are using by the \acrshort{wdias} to uniquely identify a timeseries.
+
+\dbc{Clearly mention why a hierarchical design is needed.}
+\gkc{Added it after the \cref{subse:timeseries_key_attributes}}
 
@@
   \dbc{Remove additional line.}
-
+  \gkc{This space is adding by itemize. I applied in all the places. Could not find how to remove it. Otherwise, need to remove itemize.}
   \item \emph{Regular Grid locations} -- Contains a name which is human readable. The grid presents by dividing into equal size cells. Thus, it need the number of rows and columns. 
@@
 \paragraph{Parameter}
-Parameter describe the variable measuring against a location. All parameters ahve a unique String identifier called as \textit{parameterId}. A parameter can be use in multiple locations.
-While defining a parameter, there are three required fields which need to be provided such as variable, unit and \textit{parametertype}.
+Parameter describe the variable measuring against a location. All parameters have a unique String identifier called as \textit{parameterId}. A parameter can be use in multiple locations.
+While defining a parameter, there are three required fields which need to be provided such as variable, unit and \textit{parameterType}.
 \begin{itemize}  
-  \item \emph{Variable} -- Nature of the variable measuring. Example Precipitation, Temperature and WaterLevel etc
+  \item \emph{Variable} -- Nature of the variable measuring. Example Precipitation, Temperature and Water Level etc
   \item \emph{Unit} -- metric unit of measuring
@@
 \subsubsection{Timeseries Type}
-Timeseries Type can be combination of Source followed by category:
+Timeseries Type can be redefine with the system setup. \acrshort{wdias} defined following types for during the setup. Timeseries type can be combination of source followed by category:
 \begin{itemize}
-  \item Sources - External or simulated
-  \item Category - Historical or forecast
+  \item Sources - External or simulated. \emph{External} means whether timeseries is taken from external source, and \emph{simulated} means it generated by simulations of the users.
+  \item Category - Historical or forecast.
+\emph{Historical} means whether timeseries have continuous data such as observations from a weather station.
+\emph{forecast} mean discrete set of timeseries data produce by forecasting.
 \end{itemize}
 \dbc{Explain each with sufficient detail.}
+\gkc{FIXED}
 
-\paragraph{Time Step}-- All Time Steps has an uniqie String identifier called as timeStepId.
-Unit should be one of Second, Minute, Hour, Day, Week, Month, Year, or NonEquidistant.
+\paragraph{Time Step}-- All Time Steps has an unique String identifier called as timeStepId.
+Unit should be one of Second, Minute, Hour, Day, Week, Month, Year, or NonEqualDistance.
 One of multiplier or divider can be use to define the interval between each measurement.
@@
 Among above key attributes; Location, Parameter and Time Step attributes are composite attributes. But each of them have an unique identifier.
-Given that, a timeseries can uniquely indentify by moduleId, valueType, parameterId, locationId, timeseriesType and timeStepId.
+Given that, a timeseries can uniquely identify by moduleId, valueType, parameterId, locationId, timeseriesType and timeStepId.
 \begin{lstlisting}[language=Python]
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Even a timeseries consist of data points, the data for each data point can vary based on the valueType.
+For Scalar data point only consist from a single value.
+And Vector data point consist of two values such as magnitude and the direction of the Vector.
+But for Grid data a point can consist with multiple values.
+In order to get the advantage of storing data efficiently, we can use set of different databases based on the advantage of using them for each valueType.
+Other than the valueType attribute, other attribute does not much impact on the data size.
+
+Further it is will be difficult to search for the timeseries data, if those are stored over multiple data sources, and avoiding duplicates.
+Thus it add low overhead to have a single data source to look into while searching for the timeseries metadata.
+The load on above data source can reduce by using a caching mechanism.
+In order to support search queries with lower latency, it required to use an indexing for fast search for timeseries metadata.
+Further Geo based indexing is required in order to support Geo based search queries based on the locations.
+
+With considering above facts, we can not achieve all of the benefits using one of database system available.
+Thus it required to have a database structure which is capable of proving all of above capabilities via combining together.
+According to the design principle of microservices architecture, we created microservice for each of the valueType with following the concept of Database per Service as described in the \emph{Database per Service} in \cref{subse:database_per_service}.
+In \cref{sebse:wdias_microservices} those microservices are group as \emph{adapters} which share an \acrshort{api} to interact with while keeping the persistent data private.
+
 \begin{figure}[htp]
     \centering
-    \includegraphics[width=0.6\textwidth]{method/microservice/hierarchical_database.jpg}
-    \caption{Hierarchical database}
-    \label{fi:hierarchical_database}
+    \includegraphics[width=0.6\textwidth]{method/microservice/wdias_database_structure.jpg}
+    \caption{\acrshort{wdias} database structure}
+    \label{fi:database_structure}
 \end{figure}
@@
 \dbc{Fig. 3.6 needs a more meaningful title.}
+\gkc{Updated. I think hierarchical database does not make sense in this case. May be that's why you asked for change few time, sir.}
 
-WDIAS is using a hierarchical database, with following the concept of Database per Service which is described in the \emph{Database per Service} in \cref{subse:database_per_service}.
-Following chapters described the usage of databases in WDIAS and reason behind the selection.
+\cref{fi:database_structure} shows the \acrshort{wdias} database structure.
+Following sections describe the database structure of \acrshort{wdias} which respect to the design with more details on how is support the microservice architecture.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{\acrshort{rdbms}}
+\subsection{Timeseries Metadata Storage}
 \label{subse:mysql}
 \dbc{Needs a more meaningful Sec. title}
+\gkc{UPDATED}
 
-%There are lots of \acrshort{rdbms} available and for 
+As describe in above section, in order to reduce the overhead while searching for timeseries and handling duplicates, it required to have a timeseries metadata store.
+Since metadata consist of multiple key attributes, the data can be efficiently store using a \acrfull{rdbms}.
+This helps to store data without any duplicates and store the data with normalization.
+As an example, the parameter attribute can have one or two dozen of values.
+Using a \acrshort{rdbms}, those values can be store once and reuse with defining timeseries against location via reference.
+
 \acrshort{wdias} is using SQL as the \acrfull{rdbms}. 
-%SQL database has fewer version of open source and it is also possible to gain better performance with commercial versions. 
 Since WDIAS scope is to using open source tools, it is using \acrshort{mysql} as persistent database for storing timeseries metadata described above.
@@
 \dbc{First start with a brief discussion on why a RDBMS is needed}
+\gkc{ADDED}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{subse:influxdb}
-Among several timeseries open source databases, \acrshort{influxdb} \cite{influxdbInfluxDBDocumentation} \hl{has higher number of usage and support.
-Database is written in Golang programming language, and} has higher performance, and has following supports;
+Among several timeseries open source databases, \acrshort{influxdb} \cite{influxdbInfluxDBDocumentation} \hl{is using an unique database indexing algorithm in order to gain higher performance while storing timeseries data} when compared to other databases available.
+Also it has better support, higher number of usage and has following supports;
 \begin{itemize}
@@
 And it also has the support for parallel file access.
-NetCDF is widely using in sciencetific domain due to it's capability of storing data in multi dementions easily and flexibility with storing many of the sciencetific data. \hl{
-Python wrapper for NetCDF-C library using in the WDIAS system, and use by adapter-grid service.}
+NetCDF is widely using in scientific domain due to it has the capability of storing data in multi dimensions easily and flexibility with storing many of the scientific data.
+Due to its capability of storing scientific data efficiently, \acrshort{wdias} using it for storing the Grid data.
 
@@
 \acrshort{mongodb} \cite{mongodbMongoDBManual} is a general purpose, document-based, distributed database. And it supports:
-\dbc{Need for a mix of relational, time series, document stores, and in-memory need to be first mentioned and justified in high-level design of EDIAS above.}
+\dbc{Need for a mix of relational, time series, document stores, and in-memory need to be first mentioned and justified in high-level design of WDIAS above.}
+\gkc{Adding those details in \cref{se:high_level_design} may confuse the reader.
+At that point it didn't go through that much of details of the wdias.
+I added some justification at the end of \cref{subse:timeseries_key_attributes}.
+Let me know if we want to highlight it with a different section there.}
 \begin{itemize}

### 2020-02-14 method/sec_5-data_preprocess.tex
Change all to \cref
Moved k8s to architectural decisions
Complete performance analysis

@@
 \section{Data Prepossessing}
+\label{se:data_preprocess}
 
@@
     \includegraphics[width=0.5\textwidth]{method/data_preprocess/weather_data_preprocessing.jpg}
-    \caption{\hl{Weather data preprocessing}}
+    \caption{\hl{Generic mathematical function model for weather data preprocessing}}
     \label{fi:weather_data_preprocessing}
@@
 
-The WDIAS provides the support via in build simple generic mathematical function structure. Each extension is considering as a mathematical function which can take p 
+The WDIAS provides the support via in build simple generic mathematical function model. Each extension is considering as a mathematical function which can take p 
 number of input timeseries variables and output n number of timeseries variables. Other than that, at the time of processing the system can configure to provide
@@
     \includegraphics[width=0.6\textwidth]{method/data_preprocess/transformation.jpg}
-    \caption{\hl{Transformation}}
+    \caption{\hl{Time interval transformation.}}
     \label{fi:transformation}
@@
     \includegraphics[width=0.6\textwidth]{method/data_preprocess/validation.jpg}
-    \caption{\hl{Validation}}
+    \caption{\hl{Timeseries data validation against set of rules.}}
     \label{fi:validation}
@@
 
-\subsection{\hl{Extension API}}
+\subsection{\hl{Data Preprocessing API}}
 In the WDIAS, it is possible to create new trigger for an extension via POST request to /extension endpoint.
@@
 Interpolation/Transformation/Validation support for the moment.
-    \item function -- Name of the microservice which is handling the input to output mapping. Fn() function in the Figure \ref{fi:weather_data_preprocessing}.
+    \item function -- Name of the microservice which is handling the input to output mapping. Fn() function in the \cref{fi:weather_data_preprocessing}.
     \item variables -- Array timeseries mapping to variables.
@@
 \subsubsection{Extension Handler}
-Extension Handler is responsible for triggering the correct Extension with metadata when there is any change on subscribed extension trigger's OnChange timeseries.
+Extension Handler is responsible for triggering the correct Extension with metadata when there is any change on subscribed extension trigger's \emph{OnChange} timeseries.
 \begin{figure}[htp]
@@
 
-\hl{In further elaboration,} when new data imported into one of adapter-scalar or adapter-vector, those notify the extension-handler.
+\hl{As an example,} when new data imported into one of adapter-scalar or adapter-vector, those notify the extension-handler.
 Then extension handler check whether there is any extension subscribed for particular timeseries, and trigger it via triggering an event on particular extensions.

### 2020-02-14 summary/sec_1-conclusions.tex
Complete performance analysis

@@
 Also most of existing systems are not up to date with the cloud computing technologies, or bias to some research community.}
+
 /dbc{Look some of the changes in abstract and revise this para. However, don't repeat the same from abstract.}

### 2020-02-14 summary/sec_2-research_limitations.tex
Complete performance analysis

@@
 \section{Research Limitations}
+\gkc{Previously you asked to rename this section.
+Why can't it have the title of \emph{Future Work}.
+There are some of the requirements that can be done for the system, in order to gain more of it.
+Which part is misleading?}
 This section discussed about the lacking features in the \acrshort{wdias}, and some of the improvement that can add for improve the performance and usability of the system.
@@
 \dbc{Need a new section for Conclusions.}
+\gkc{It did not make sense for me to adding another section as Conclusion.
+We already add a \cref{se:summary_conclusion} above.
+Do we need to rearrange the content of this Chapter?
+No point of adding another section with repeating the same content.
+May be I didn't understand your suggestion here.}
+\gkc{DO we need to move the \cref{se:discussion} here? Normally where should we include the analysis of observations?}

### 2020-02-15 results/sec_1-test_plan.tex
Fixed:  workload

@@
 \section{Load Testing Plan}
+\label{se:test_plan}
 
-\hl{The system consists of three modules in functionality perspective of interacting with the} \acrshort{wdias}.
+In \cref{subse:modules_weather_data_integration_sys} \hl{we discussed three modules of a weather data system such as integration, assimilation and dissemination.
+Each of those modules are mapped and handled in the WDIAS as below.}
 \begin{enumerate}
-    \item Import modules
-    \item Export modules
-    \item Extension modules
+    \item \emph{Import} modules (integration modules)
+    \item \emph{Export} modules (Dissemination modules)
+    \item \emph{Extension} modules (Assimilation modules)
 \end{enumerate}
-Other than above, adapter modules act as the core modules and the base of the system.
+Other than above, \emph{adapter modules} act as the core modules and the base of the system.
 Also, query modules allow the users to query for the timeseries based on the metadata, and enable performing Geo based queries based on the locations.
@@
 
-\subsection{\hl{Load Testing Flow}}
+\begin{figure}[htp]
+    \centering
+    \includegraphics[width=0.8\textwidth]{results/work_load/performance_study_v4.jpg}
+    \caption{\acrshort{wdias} load testing plan with changing the request size and \acrshort{rps}}
+    \label{fi:performance_study_load}
+\end{figure}
+
+\cref{fi:performance_study_load} show the summary of this section, load testing plan with changing the request size and perform load testing with increasing the \acrshort{rps} over the time.
+As shown in the figure, for a given request size the \acrshort{rps} increased in steps.
+In each step, the \acrshort{rps} hold for a moment in order to give some time for the system to get stabilize.
+Thus at each milestone, we can measure the performance of the system and study the stability of the system.
+After it come to the peak time, the \acrshort{rps} holds for more time than the previous milestones.
+During the \acrshort{wdias} load testing, we are planning to have a peak of 18,000 requests per minute.
+Holding the peak load will help to show that whether system is capable of scaling more than proposed load testing plan.
+After the peak, test case goes through a cool down period in order to measure the ability of shrink down the resources when there is not any load on the system.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{\hl{Test Scenarios}}
 \label{subse:test_plan_flow}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Performance Metrics}% of Load Testing}

### 2020-02-15 results/sec_2-workload.tex
Fixed:  workload

@@
 \section{Workload Generation}
+\label{se:workload}
 
@@
 During the performance test, it creates 1000 timeseries and keep adding data against those timeseries.
-For each location, it creates four timeseries \hl{with vary with module Id} key attribute with four values.
+For each location, it creates four timeseries \hl{as a combination four values of moduleId key attribute}.
 Thus combining all together, those creates 1000 timeseries.
@@
 Which is known as the \emph{closed workload}.
-With using Throughput Shaping Timer, it only need to configure the \acrfull{rps}.
+With using \emph{Throughput Shaping Timer}, it only need to configure the \acrfull{rps}.
 When combine this \acrshort{jmeter} plugin with Concurrency Thread Group using Schedule Feedback Function to dynamically maintain thread count required to achieve target RPS \cite{KarunarathneGihanWdias/wdias-performance-test:JMeter.}.
 
+\begin{figure}[htp]
+    \centering
+    \includegraphics[width=0.8\textwidth]{results/work_load/test_prod_throughtput_shaping_timer.png}
+    \caption{\acrshort{wdias} load testing throughput shaping timer \acrshort{rps} configurations}
+    \label{fi:test_prod_throughtput_shaping_timer}
+\end{figure}
+
+In the \cref{fi:test_prod_throughtput_shaping_timer} shows the throughput shaping timer configurations use while load testing.
+The configurations as similar to the load test plan described in \cref{se:test_plan}.
+In order to get maximum peak of 18,000 request per minutes, which is equivalent to 300 \acrshort{rps} is setup according the the figure.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 The test plans mentioned in \cref{se:test_plan} are implemented via the \acrshort{jmeter}. The following list shows the all the test cases used for the performance testing:
@@
 
-\hl{Following list of test steps shows intensively test the query timeseries features.}
+As mentioned in \cref{se:test_plan} \hl{, we planned to perform another test scenario on query timeseries module.
+During this test scenario, we use following test steps in order to cover most of the timeseries metadata search queries and Geo queries which are defined in the} \cref{se:query}.
 
@@
 
-In the \cref{fi:test_prod_throughtput_shaping_timer} shows the Throughput Shaping Timer configurations for the All test case.
-
-\begin{figure}[htp]
-    \centering
-    \includegraphics[width=0.6\textwidth]{results/work_load/test_prod_throughtput_shaping_timer.png}
-    \caption{\acrshort{wdias} performance test - Throughput \hl{shaping timer graph}}
-    \label{fi:test_prod_throughtput_shaping_timer}
-\end{figure}
-
 \dbc{Top of Fig. 4.2 useless as it's black. Anyway, this figure isn't needed}
+\gkc{Since we described about throughput shaping timer graph in \ref{subse:closed_vs_open_workload}, better to include it here.
+It include the details on RPS and how it's increasing over time.
+Will remove the black part.
+Also move this paragraph to the \cref{subse:closed_vs_open_workload}}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{\hl{System Configuration}}
+\subsection{\hl{Test System Setup}}
 \label{subse:test_sys_config}
@@
 \begin{table}[ht]
+\centering
 \caption{\acrshort{eks} nodes}
 \footnotesize
-\begin{tabular}{lccccl}
+\begin{tabular}{|l|c|c|c|c|l|}
 \hline
-\multicolumn{1}{c}{\textbf{Node Label}} & \textbf{vCPU} & \textbf{RAM (GB)} & \textbf{Storage (GB)} & \textbf{Quantity} & \multicolumn{1}{c}{\textbf{EC2 Name}} \\ \hline
-core & 16 & 32 & 15 & 1 & c5.4xlarge \\
-grid & 8 & 16 & 25 & 1 & c5.2xlarge \\
-scalar & 8 & 16 & 20 & 1 & c5.2xlarge \\
+\textbf{Node Label} & \textbf{vCPU} & \textbf{RAM (GB)} & \textbf{Storage (GB)} & \textbf{Quantity} & \textbf{EC2 Name} \\ \hline
+core & 16 & 32 & 15 & 1 & c5.4xlarge \\ \hline
+grid & 8 & 16 & 25 & 1 & c5.2xlarge \\ \hline
+scalar & 8 & 16 & 20 & 1 & c5.2xlarge \\ \hline
 test & 4 & 10.5 & 5 & 1 & c5n.xlarge \\ \hline
@@
 \dbc{Center table on page}
+\gkc{FIXED}
 

### 2020-02-15 summary/sec_1-conclusions.tex
Address all the comments. Next proofreading

@@
 To enhance the accuracy of the weather prediction, it is essential to provide reliable and timely weather data for \acrshort{nwm}.
-Even though there are many data integration systems, most of them are proprietary or close sourced.
+Even though there are many weather data integration systems, most of them are proprietary or close sourced.
 Which means for an island like Sri Lanka that having different kinds of weather seasons over the year those software needs to be highly customized.
-\hl{Throughout the operations and maintenance, it is required to get support with paying lots of charges, and difficult to debug into a closed source system without maintenance support from the vendors.
+%\hl{Throughout the operations and maintenance, it is required to get support with paying lots of charges, and difficult to debug into a closed source system without maintenance support from the vendors.
 Also most of existing systems are not up to date with the cloud computing technologies, or bias to some research community.}
+\hl{Also most of existing systems are based on basic client-server architectures or monolithic distributed system architectures which are popular or available at the time of developing those systems.
+Because of this, those are unable to get the advantage of modern computational models such as containerized applications and using the could computing in order to gain benefits of scalability, high availability and low-cost operations.}
 
-/dbc{Look some of the changes in abstract and revise this para. However, don't repeat the same from abstract.}
+\dbc{Look some of the changes in abstract and revise this para. However, don't repeat the same from abstract.}
+\gkc{UPDATED}
 

### 2020-02-15 introduction/sec_1-motivation.tex
Grammarly: Chapter 1

@@
 As an example, FLO2D is a hydrologic model that can use to predict the surface water level.
-A given FLO2D model can simulate with the initial surface water levels and the sequence of forecasted rainfall for the corresponding modeled area from \acrshort{nwm} model to forecast future water levels.
+A given FLO2D model can simulate with the initial surface water levels and the sequence of forecasted rainfall for the corresponding modeled area from the \acrshort{nwm} model to forecast future water levels.
 \dbc{Highighted part doesn't make much sense to me. Need to be reworded.}
@@
 \acrfull{curw} \cite{CUrWSL2017SL} is tasked with the mission to reduce water-related natural disasters in Sri Lanka.
-\acrshort{curw} \cite{CUrWSLObservedSL} is implementing its own system with the idea of long-term maintainability rather depend on existing weather data integration systems.
+\acrshort{curw} \cite{CUrWSLObservedSL} is implementing its system with the idea of long-term maintainability rather depend on existing weather data integration systems.
 It collected real-time data from weather stations and other government entities and generates daily forecasts.
@@
 These NWMs utilize multi-modal weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images.
-Prior to feeding such diverse data (collected from different sources that belongs to different stakeholders) into respective NWMs, it is necessary to integrate data into a common format.
-Moreover, the data integration system’s response time need to be relatively low to forecast and monitor time-sensitive weather events like hurricanes, storms, and floods which require rapid and frequent execution of NWMs.
+Before feeding such diverse data (collected from different sources that belong to different stakeholders) into respective NWMs, it is necessary to integrate data into a common format.
+Moreover, the data integration system’s response time needs to be relatively low to forecast and monitor time-sensitive weather events like hurricanes, storms, and floods which require rapid and frequent execution of NWMs.
 
-Processed weather data needs to be accessed by many third-party applications and research in order to make use of them.
-For example, logistic companies could use those data with their models to plan and schedule their deliveries.
-Agricultural insurance companies can warn the farmers in advance, as well as calculate premiums based on anticipated weather patterns.
-Also farmers rely on weather forecasts to decide what work to do on any particular day.
+Processed weather data needs to be accessed by many third-party applications and research to make use of them.
+For example, logistics companies could use those data with their models to plan and schedule their deliveries.
+Agricultural insurance companies can warn the farmers, as well as calculate premiums based on anticipated weather patterns.
+Also, farmers rely on weather forecasts to decide what work to do on any particular day.
 For example, drying hay is only feasible in dry weather.
-Further the aviation industry is especially sensitive to the weather, accurate weather forecasting is essential, since prior to takeoff on the conditions to expect en route and at their destination.
+Further, the aviation industry is especially sensitive to the weather, accurate weather forecasting is essential since before takeoff on the conditions to expect en route and at their destination.
 Thus it is required a platform to provide such 3rd party access, and use the data or process those based on their applications.
@@
 Further \acrfull{fews} \cite{Werner2013TheSystem} is free to use, it is not open source.
-Even though there are many data integration systems, most of them are proprietary or close sourced.
-Which means for an island like Sri Lanka that having different kinds of weather seasons over the year than those software originated need to be highly customized.
+Even though there are many data integration systems, most of them are proprietary or closed source.
+Which means for an island like Sri Lanka that having different kinds of weather seasons over the year than that software originated need to be highly customized.
 Throughout the operations and maintenance, it is required to get support with paying lots of charges, and difficult to debug into a closed source system without maintenance support from the vendors.
 As an example, \acrshort{fews} does not support FLO2D model integration, and \acrshort{curw} is using FLO2D for water level forecasting in the data flow.
-In such a cases, it required to get the support from the vendor in order to integrate and configure the system.
+In such a case, it required to get support from the vendor to integrate and configure the system.
 And most of the software existing out there is not up to date with the latest technology concepts such as Cloud Computing.
-\acrfull{wdias} uses the modern architecture pattern such as microservice in order to achieve scalability, rather using monolithic architecture or client service architecture.
-Most existing systems required to shutdown in order to update the system configuration such as \acrshort{fews}, but a systems which is access by many third parties should be operate 99.9\% without any downtime and should allows to add new features on the fly with rollover capabilities.
+\acrfull{wdias} uses the modern architecture pattern such as microservice to achieve scalability, rather using monolithic architecture or client service architecture.
+Most existing systems required to shut down to update the system configuration such as \acrshort{fews}, but a system that is accessed by any third parties should be operating 99.9\% without any downtime and should allow adding new features on the fly with rollover capabilities.
 The proposed system should be independent of the platform.
-But most software out there is not, as example \acrshort{fews} can run on Windows and Linux.
-And should be independent underline infrastructure providers which give much flexibility for the users to decide the best cost effective way to host it.
-Given the above facts, there is a necessary for such a systems to be implemented.
+But most software out there is not, as an example \acrshort{fews} can run on Windows and Linux.
+And should be independent underline infrastructure providers which gives much flexibility for the users to decide the best cost-effective way to host it.
+Given the above facts, there is a necessity for such a system to be implemented.
 

### 2020-02-15 introduction/sec_2-problem_and_objectives.tex
Grammarly: Chapter 1

--- 2020-02-12 introduction/sec_2-problem_and_objectives.tex
@@
 \section{Problem Statement}
-Handling spatio-temporal weather data is challenging \db{as ...}.
-Moreover, the data integration system needs to be capable of interacting with different data formats including spatio-temporal bulk stream data.
-Furthermore, it should support geographical and time-base queries, as well as provide third-party access to data with easy integration.
+Handling Spatio-temporal weather data is challenging \dbc{as} it involves large data volumes required to have a higher number of resources such as computation, storage, and network bandwidth.
+Moreover, the data integration system needs to be capable of interacting with different data formats including Spatio-temporal bulk stream data.
+Furthermore, it should support geographical and time-based queries, as well as provide third-party access to data with easy integration.
 Scalability and high availability are also essential to support different use cases and mission-critical nature of applications.
-Therefore, we need an extendable system to support weather models by efficiently ingesting, storing, and retrieving data.
+And users should be able to easily deploy and manage the system with modern technologies and should be able to get the advantage of technology advancement.
 In this context, the research problem can be stated as follows:
 
-\emph{design and implement an extendable weather data integration, assimilation and dissemination system which is capable of handling bulk data efficiently with providing scalability and high throughput with using open source tools and modern cloud computing technologies}
+\emph{Design and implement an extendable weather data integration, assimilation, and dissemination system which is capable of handling bulk data efficiently with providing scalability and high throughput with using open source tools and modern cloud computing technologies.}
 \dbc{Give a proper problem statement.}
@@
 \section{Objectives}
-We address above problem statement by achieving the following research objectives:
+We address the above problem statement by achieving the following research objectives:
 \begin{itemize}

### 2020-02-15 introduction/sec_3-outline.tex
Grammarly: Chapter 1

@@
 The rest of the thesis is organized as follows.
-Literature review is presented in \cref{ch:literature}, and discuss about the existing Weather Data Integration Systems such as \acrshort{lead}, \acrshort{fews}, \acrshort{madis}, and \acrshort{dias}.
+The literature review is presented in \cref{ch:literature}, and discuss the existing Weather Data Integration Systems such as \acrshort{lead}, \acrshort{fews}, \acrshort{madis}, and \acrshort{dias}.
 Solution approach with the proposed system architectures and adaptation with problem occurred are presented in Chapter \ref{ch:method}.
-It provides details about how the \acrshort{wdias} is design by following a microservice architecture and the date preprocessing capabilities of the system.
+It provides details about how the \acrshort{wdias} is designed by following a microservice architecture and the date preprocessing capabilities of the system.
 Performance analysis is presented in Chapter \ref{ch:results}.
-Here we discuss experiment setup of the \acrshort{wdias} and analyze the observations with respect to performance metrics.
-Finally, in Chapter \ref{ch:summary}, we conclude and summarize the work and further discussed about the research limitations and future work.
+Here we discuss the experimental setup of the \acrshort{wdias} and analyze the observations concerning performance metrics.
+Finally, in Chapter \ref{ch:summary}, we conclude and summarize the work and further discussed the research limitations and future work.

### 2020-02-15 lit/sec_1-fews.tex
Grammarly FEWS

@@
-Several weather forecasting, assimilation, and dissemination systems are developed to reduce the damage causing by natural disasters such as flood, storms, hurricanes, and even droughts.
+Many weather forecasting, assimilation, and dissemination systems are developed to reduce the damage causing by natural disasters such as floods, storms, hurricanes, and even droughts.
 %Such natural disasters heavily affected on the economy and the life conditions of the country, researchers have developed systems and many of these systems are using as proprietary systems.
 Other countries are also using those systems while adopting them %with own version of system which effective for the 
-to specific weather condition.% in a particular country.
+to specific weather conditions.% in a particular country.
 This chapter presents a literature review on existing systems and their architecture approach and design.
@@
 % \acrshort{lead} is following the \acrfull{soa} for system architecture.
-In \cref{se:dias}, we discussed about \acrfull{dias} which is a common data platform that can work with weather data.
-\acrfull{madis} is another widely use data integration system, which also provide data access with quality control, which we discuss in \cref{se:madis}.
-Under each system we explore both system architecture, scalability, and flexibility of the system.
+In \cref{se:dias}, we discussed \acrfull{dias} which is a common data platform that can work with weather data.
+\acrfull{madis} is another widely used data integration system, which also provides data access with quality control, which we discuss in \cref{se:madis}.
+Under each system, we explore both system architecture, scalability, and flexibility of the system.
 
@@
 
-\acrshort{fews} \cite{Werner2013TheSystem} is developed by Deltares in the Nethaland with targeted for use by operational forecasting agencies.
-The code base of \acrshort{fews} is currently not fully open source.
-Most if the models are using model-centric approach such as inputs need to be in the format of specific to the model.
-Also, the outputs produced by the model are specific to the model and hard to utilize by another systems (e.g., FLO2D).
+\acrshort{fews} \cite{Werner2013TheSystem} is developed by Deltares in the Netherland with targeted for use by operational forecasting agencies.
+The codebase of \acrshort{fews} is currently not fully open source.
+Most, if the models are using a model-centric approach such as inputs, need to be in the format of specific to the model.
+Also, the outputs produced by the model are specific to the model and hard to utilize by other systems (e.g., FLO2D).
 As \acrshort{fews} uses a modular approach it is easier to integrate new models.
-Thus, \acrshort{fews} can be consider as an integration framework or a middleware for the models.
+Thus, \acrshort{fews} can be considered as an integration framework or a middleware for the models.
 
 Forecasting processes are constructed as a combination of modelling steps and data transformation algorithms.
-These are then combined to provide required forecast capabilities.
-Flexibility is achieved through integrating new models and algorithms into the code base \cite{Werner2013TheSystem}.
-\acrshort{fews} system contains no inherent hydrological modelling capabilities within its code base.
-Rather it is a framework which can use to integrate into the system and create work flows for forecasting.
+These are then combined to the provide required forecast capabilities.
+Flexibility is achieved by integrating new models and algorithms into the codebase \cite{Werner2013TheSystem}.
+\acrshort{fews} system contains no inherent hydrological modeling capabilities within its codebase.
+Rather it is a framework that can use to integrate into the system and create workflows for forecasting.
 
@@
 The primary objective of this step is to provide additional lead time through predictions of short term future hydro-meteorological conditions \cite{Werner2005FloodCatchments}.
-It is true that, with providing accurate predictions with greater lead time can reduce the level of destruction.
-In order to do the forecasting, the system should be capable of integrating real-time data from hydrological and meteorological observation networks, and the dissemination of prediction results through appropriate products to the warning process.
+It is a valid argument that providing accurate predictions with greater lead time can reduce the level of destruction.
+To do the forecasting, the system should be capable of integrating real-time data from hydrological and meteorological observation networks, and the dissemination of prediction results through appropriate products to the warning process.
 
-In \db{Figure} \cref{fi:fews_schematic} show a schematic view of the connection between the forecasting system to real time data acquisition systems and dissemination systems.
-The widely using concept is using meteorological forecast data to get precipitation and, then using hydrological and hydraulic model chain to predict the level affect on the ground.
+In \db{Figure} \cref{fi:fews_schematic} show a schematic view of the connection between the forecasting system to real-time data acquisition systems and dissemination systems.
+The widely used concept is using meteorological forecast data to get precipitation and, then using a hydrological and hydraulic model chain to predict the level affect on the ground.
 The hydrological and hydraulic model should be design based on the ground.
-Basically ground should be analyze geographically and divide into the catchments.
-Based on the affected catchment, it can be further divide into sub areas to reduce the complexity of the simulation task.
-Ideally the forecasting system should therefore be flexible to allow change to models and data, while keeping the way forecasters work with it as constant as possible.
+The ground should be analyzed geographically and divide into the catchments.
+Based on the affected catchment, it can be further divided into sub-catchments to reduce the complexity of the simulation task.
+Ideally, the forecasting system should be flexible to allow change to models and data, while keeping the way forecasters work with it as constant as possible.
 \dbc{F is capital and T is capital when referring to Figures and Tables. Fix all other places.}
@@
 The foundation of \acrshort{fews} is data-centric, with a common data-model through which all components interact.
-All time series data (both scalar and gridded) are stored in this common data-model in a database.
+All timeseries data (both scalar and gridded) are stored in this common data model in a database.
 Modeling capabilities are then linked to the system through one of the interfaces provided to the data-model \cite{Werner2013TheSystem}.
-As mention in the paper, having a common data-model make easy to store data in an efficient way.
-Operations like reporting and sharing the data also make it easy for integrate models.
+As mention in the paper, having a common data-model make easy to store data efficiently.
+Operations like reporting and sharing the data also make it easy by integrating models.
 But the problem with this approach is, handling the multiple data formats.
-\acrshort{fews} overcome this issue with introducing adapters for most of commonly used data formats.
-This is a good feature which enable users to easily import data into the system.
-But at the same time, it's adding additional complexity into the system.
+\acrshort{fews} overcome this issue by introducing adapters for most of the commonly used data formats.
+This is a good feature that enables users to easily import data into the system.
+But at the same time, it's adding additional complexity to the system.
 
-Time series data is additionally either scalar, vector, or gridded data, though all different types are uniformly stored as binary objects in a time series table.
+Timeseries data is additionally either scalar, vector, or gridded data, though all different types are uniformly stored as binary objects in a time series table.
 None of the functional components (including the linked models) have direct access to the times series table, which is accessible only through the data access module \cite{Werner2013TheSystem}.
-As it explained in the system interpretation, every time all the data access need to go through the data access module which causing to adding more cost in data access.
-Since it is storing the different data types as binary objects, there is a penalty in converting data into binary objects and vice a versa.
-Storing all the data in a time series table causing all the request come into a single data point.
-Even it gives the advantage of accessing all the data at one place.
-Since screaming big amount of data is causing a heavy load on the system, causing to slow down the performance on trying to use the system on large set of data.
+As explained in the system interpretation, every time all the data access needs to go through the data access module which causing adding more cost in data access.
+Since it is storing the different data types as binary objects, there is a penalty in converting data into binary objects and vice versa.
+Storing all the data in a timeseries table causing all the requests to come into a single data point.
+Even it gives the advantage of accessing all the data in one place.
+Since screaming big amount of data is causing a heavy load on the system, causing to slow down in the performance of trying to use the system on a large set of data.
 
 Given above drawback on storing the data in the system, within the \acrshort{fews} data model, time series are uniquely identified by their location and data type, as well as an id related to the source of the data (e.g., the external source or hydrological model of which the time series are a result) \cite{Werner2013TheSystem}.
-This gives an opportunity to index the data base on above key fields and store the data separately, to take the advantage of putting multiple data resources into the system.
-As an example, instead of storing the data at a single timeseries table, it is possible to separate and index the database based on source such as external source or hydrological model of which the time series are a result.
-Or separate by data type and store in multiple storage give the capability for the system to scale with factor of identical types that can be identified.
+This allows indexing the database on the above key fields and stores the data separately, to take advantage of putting multiple data resources into the system.
+As an example, instead of storing the data at a single timeseries table, it is possible to separate and index the database based on the source such as an external source or hydrological model of which the timeseries is a result.
+Or separate by data type and store in multiple storages give the capability for the system to scale with a factor of identical types that can be identified.
 Example of separation by data types of scalar, vector and gridded will increase the scaling factor by 3x.
@@
 As a consequence, generic data processing steps form the predominant effort in most applications of models in the forecast environment.
-Some examples include data validation, serial and spatial interpolation, aggregation and dis-aggregation, and merging data \cite{Werner2013TheSystem}.
-This a vital feature in a forecasting system, and affect on the quality and accuracy of the predicted data outputs.
-Because of the common data model concept in \acrshort{fews}, data processing via these function is much effective.
-The system is self provided some of the generic functions for data processing, but for more complex algorithms can be developed as a new Java class coded to communicate with the \acrfull{api}.
-It is obvious that for additional feature integration, user should implement the new functional extensions via Java programming language.
-Users does not have the flexibility of develop with some other languages they are familiar with or use the support from another language.
-As an example, Python language is easy to use for beginners and many of data scientists are using this programming language for development and it has many data available libraries for data processing.
-But in \acrshort{fews}, users do not have the capability to take the advantage of such existing things.
+Some examples include data validation, serial and spatial interpolation, aggregation and disaggregation, and merging data \cite{Werner2013TheSystem}.
+This a vital feature in a forecasting system, and affect the quality and accuracy of the predicted data outputs.
+Because of the common data model concept in \acrshort{fews}, data processing via these functions is much effective.
+The system is self-provided some of the generic functions for data processing, but for more complex algorithms can be developed as a new Java class coded to communicate with the \acrfull{api}.
+It is obvious that for additional feature integration, users should implement the new functional extensions via Java programming language.
+Users do not have the flexibility of developement with some other languages they are familiar with or use the support from another language.
+As an example, Python language is easy to use for beginners and many data scientists are using this programming language for development and it has many data available libraries for data processing.
+But in \acrshort{fews}, users cannot take advantage of such existing tools.
 \dbc{Define Abb. for API in Chapter 1.}
@@
 Most of the library of functions provided work equally on scalar and gridded time series.
-As with all other modules this communicates with the database solely through the data access layer as shown in \cref{fi:fews_data_layer} \cite{Werner2013TheSystem}.
-As it shown in the figure, it is clearly showing that, the system is depends on single database and via the data access layer all the requests are coming to the database though a connection.
-It is possible to setup and connect to a enterprise level database with clustering and shading as a paid solution, to serve many requests as possible.
-But the design it self inherently suffer with the database bottleneck which effected on running a large set of timeseries or models.
+As with all other modules, this communicates with the database solely through the data access layer as shown in \cref{fi:fews_data_layer} \cite{Werner2013TheSystem}.
+As it is shown in the figure, it is clearly showing that the system depends on a single database and via the data access layer, all the requests are coming to the database through a connection.
+It is possible to setup and connect to an enterprise-level database with clustering and shading as a paid solution, to serve many requests as possible.
+But the design itself inherently suffers from the database bottleneck which effected by running a large set of timeseries or models.
 \dbc{When referring to a section you need to use the word "Section" as highlighted above. Fix all other places.}
@@
 \end{figure}
-On of the simple and most effective feature in the \acrshort{fews} is open approach to integration of models and data.
+One of the simple and most effective features in the \acrshort{fews} is an open approach to the integration of models and data.
 This approaches the concept of the open modeling framework proposed by Open model integration \cite{Kokkonen2003InterfacingXML}.
 It simply gives the flexibility to allow operators to integrate more models as well as variations of the same model and come up with new integration flows as much as possible.
-\acrshort{fews} generates the input data as a set of XML files to a defined location; an adapter developed specifically for the model in question transforms this to the required native format in a pre-processing step; \acrshort{fews} executes the model; and the adapter to that model then converts the native formatted results into XML formatted files in a post processing step.
+\acrshort{fews} generates the input data as a set of XML files to a defined location; an adapter developed specifically for the model in question transforms this to the required native format in a pre-processing step; \acrshort{fews} executes the model, and the adapter to that model then converts the native formatted results into XML formatted files in a post processing step.
 \acrshort{fews} subsequently imports the results into the database from the XML files (see \cref{fi:fews_general_adapter}) \cite{Werner2013TheSystem}.
-The process is simple and consistence through out all the model integration.
+The process is simple and consistent throughout all the model integration.
 The model execution is done by the \acrshort{fews} or the model adapter which is causing tide coupling into the execution process in the system.
-Users does not have the flexibility to run the models with different configurations such as running with parallel execution.
-That may be overcome by triggering a external process at the execution time, but it introducing more difficulty for handling after model executed successfully, preceding to the next step in the process.
-This part of the system feature is not focus on the \acrshort{wdias} and user has to come up with own flow or use existing scientific flow management system.
-But it is a concept that need to be discuss and understand properly to design a data integration and assimilation system.
+Users do not have the flexibility to run the models with different configurations such as running with parallel execution.
+That may be overcome by triggering an external process at the execution time, but it introduces more difficulty for handling after model executed successfully, preceding to the next step in the process.
+This part of the system feature is not focused on the \acrshort{wdias} and user has to come up with own flow or use existing scientific flow management system.
+But it is a concept that needs to be discussed and understand properly to design a data integration and assimilation system.
 
 Exchanging data with the model is primarily through XML files.
-In some cases these XML files may become very large, which may lead to I/O bottlenecks and subsequent performance issues \cite{Werner2013TheSystem}.
-This issue is thoroughly discussed previous paragraphs and the authors of the \acrshort{fews} \cite{Werner2013TheSystem} seems to be notice and accept it here.
-For overcome this issue they introduced the file-based exchange of data.
+In some cases, these XML files may become very large, which may lead to I/O bottlenecks and subsequent performance issues \cite{Werner2013TheSystem}.
+This issue is thoroughly discussed in previous paragraphs and the authors of the \acrshort{fews} \cite{Werner2013TheSystem} seem to be noticed and accept it here.
+For overcoming this issue they introduced the file-based exchange of data.
 This includes the use of binary-XML files, streaming files through memory, and the use of \acrshort{netCDF} files.
-But far as for users it seems to be adding more complexity and context to get higher performance via the system.
+But far as for the users, it seems to be adding more complexity and context to get higher performance via the system.
 
-If particular adapter for a model is not present in the list of \acrshort{fews} adapter, user has the flexibility to implement an adapter for it.
+If a particular adapter for a model is not present in the list of \acrshort{fews} adapter, the user has the flexibility to implement an adapter for it.
 The effort of developing an adapter for a model code not previously integrated with \acrshort{fews} will vary depending on the complexity of the model I/O formats \cite{Werner2013TheSystem}.
-If user wants to use existing adapter and need to configure something not supported via the existing adapter, it is hard to get done.
-Also there are some cases it is hard to develop an adapter or running alongside with the \acrshort{fews}.
-As an example FLO2D model is using for hydrologic modeling and the model is only support only on Windows based operating systems.
-If you setup the system on Linux base operating system and using Linux based models, it is hard for users to come up with a solution for integrating the FLO2D models.
+If the users want to use an existing adapter and need to configure something not supported via the existing adapter, it is hard to get done.
+Also, there are some cases it is hard to develop an adapter or running alongside the \acrshort{fews}.
+As an example, the FLO2D model is using for hydrologic modeling and the model only supports only on Windows based operating systems.
+If you setup the system on Linux based operating system and using Linux based models, it is hard for users to come up with a solution for integrating the FLO2D models.
 The final step and one of important feature is exporting the data from the system in useful manner.
-The forecasting process is often a sequence of steps, starting with the import of data, a number of data processing and modeling steps, and culminating in the generation of products to be disseminated to the warning process.
-This is supported via the work flow process in \acrshort{fews}.
-The scope of the \acrshort{wdias} is not focus on adding such a feature in the system, rather user have to use scientific work flow management system or come up with own version of work flow.
+The forecasting process is often a sequence of steps, starting with the import of data, a several data processing, and modeling steps, and culminating in the generation of products to be disseminated to the warning process.
+This is supported via the workflow process in \acrshort{fews}.
+The scope of the \acrshort{wdias} is not focused on adding such a feature in the system, rather user has to use a scientific workflow management system or come up with own version of workflow.
 
-When running sequential steps within a work flow in \acrshort{fews}, each step is run for the full time window required (e.g., the lead time of the forecast) before moving on to the next step.
+When running sequential steps within a workflow in \acrshort{fews}, each step is run for the full-time window required (e.g., the lead time of the forecast) before moving on to the next step.
 This precludes tightly coupling of models, even explicitly \cite{Werner2013TheSystem}.
-As it mentioned above, users can run multiple models parallel or run those sequentially as needed.
+As mentioned above, users can run multiple models parallel or run those sequentially as needed.

### 2020-02-15 lit/sec_2-lead.tex
Grammarly LEAD

@@
 \acrfull{lead} addresses the fundamental research challenges needed to create an integrated, scalable framework for adaptive analyzing and predicting the atmosphere \cite{Droegemeier2005Service-OrientedWeather}.
-To predict and analysis weather models by researchers, it required many resources.
-Rather than each researcher is running and handling own computer resources to do the weather experiments, \acrshort{lead} is providing pool of resources, then the researchers can use this resource pool to run their experiment in shorter amounts of time and in higher scale.
-At the time, researchers are developing their experiment flow, they are not using the resources many, and other are using it at the same time.
-LEAD's foundation is dynamic work flow orchestration and data management in a Web services framework \cite{Droegemeier2005Service-OrientedWeather}.
+To predict and analyze weather models by researchers, it required many resources.
+Rather than each researcher is running and handling their computer resources to do the weather experiments, \acrshort{lead} is providing pool of resources, then the researchers can use this resource a pool to run their experiment in shorter amounts of time and higher scale.
+At the time, researchers are developing their experiment flow, they are not using the resources many, and others are using it at the same time.
+LEAD's foundation is dynamic workflow orchestration and data management in a Web services framework \cite{Droegemeier2005Service-OrientedWeather}.
 
-LEAD's complex array of services, applications, interfaces, and local and remote computing, networking, and storage resources is assembled by users in work flows to study mesoscale weather as it evolves \cite{Droegemeier2005Service-OrientedWeather}.
+LEAD's complex array of services, applications, interfaces, and local and remote computing, networking, and storage resources is assembled by users in workflows to study mesoscale weather as it evolves \cite{Droegemeier2005Service-OrientedWeather}.
 As it follows the \acrshort{soa}, everything is implemented as independent services.
-This enable \acrshort{lead} to scale each service as required, and update each service without affecting other services.
-New models which are required for implementing a new forecast flow also has to be implement as a service and then integrate into the system.
+This enables \acrshort{lead} to scale each service as required and update each service without affecting other services.
+New models that are required for implementing a new forecast flow also has to be implemented as a service and then integrate into the system.
 
 \cref{fi:lead_system} shows the fundamental capabilities of the \acrshort{lead} system.
-From the high-level view, \acrshort{lead} lets users query for and acquire information, simulate and predict weather by using numerical atmospheric models, assimilate data, analyze, mine, and visualize data and model output.
+From the high-level view, \acrshort{lead} lets users query for and acquire information, simulate and predict the weather by using numerical atmospheric models, assimilate data, analyze, mine, and visualize data and model output.
 
@@
 
-The second level contains the fundamental tools that help to link services together. This include following tools \cite{Droegemeier2005Service-OrientedWeather};
+The second level contains the fundamental tools that help to link services together. This includes the following tools \cite{Droegemeier2005Service-OrientedWeather};
 \begin{itemize}
@@
     \item myLEAD, a flexible metadata catalog service
-    \item \acrfull{wrf} a next-generation atmospheric prediction and simulation model
+    \item \acrfull{wrf} a next-generation atmospheric prediction and the simulation model
     \item ADaM (Algorithm Development and Mining), a powerful suite of tools for mining observational data, assimilated data sets, and model output 
@@
 The Concept of the \acrshort{lead} is, the workflow orchestration for on-demand, real-time, dynamically adaptive systems, called as WOORDS.
-The system is doing the work flow orchestration as given in each procedure.
-Those procedural rules are define by researcher and feed into the system.
-The system is trying to perform the action immediate after the submission, and also it transmit the data, run the models and send back the put put with lower time delay as possible.
-According to the load and other requirement, the system will respond to those requirements automatically.
+The system is doing the workflow orchestration as given in each procedure.
+Those procedural rules are defined by the researcher and feed into the system.
+The system is trying to act immediately after the submission, and also it transmits the data, run the models and send back the put with a lower time delay as possible.
+According to the load and other requirements, the system will respond to those requirements automatically.
 
@@
 
-As shown in the \cref{fi:lead_framework} LEAD consists of the following sub components, and it provides a distributed test bed for developing, integrating, and testing LEAD's components.
+As shown in \cref{fi:lead_framework} LEAD consists of the following sub-components, and it provides a distributed testbed for developing, integrating, and testing LEAD's components.
 \begin{itemize}
     \item User subsystem -- comprises the LEAD portal and enable user can access services
-    \item Data subsystem -- handles data and metadata, any numerical model output produced by operational or experimental models, and user generated information.
+    \item Data subsystem -- handles data and metadata, any numerical model output produced by operational or experimental models, and user-generated information.
     \item Tools subsystem -- consists of all meteorological and IT tools
-    \item Orchestration subsystem -- provides the technologies that let users manage data flows and model execution streams, and create and mine output.
+    \item Orchestration subsystem -- provides the technologies that let users manage data flows and model execution streams, and create and own output.
 It also provides linkages to other software and processes for continuous or on-demand applications.
@@
 \acrshort{soa}s are widely deployed in the commercial enterprise sector, and they form the foundation of many scientific "grid" technologies at the time of \acrshort{lead} design and developed.
-A variant of \acrshort{soa} is evolved later called as microservice architecture, and widely use in the industry nowadays.
+A variant of \acrshort{soa} is evolved later called microservice architecture and widely used in the industry nowadays.
 
@@
 The bottom layer represents raw computation, application, and data resources distributed throughout the LEAD grid and elsewhere.
-The next level up holds the Web services that provide access to raw services \cite{Droegemeier2005Service-OrientedWeather}.
-These two layers are working together, since \acrshort{lead} system resources are distributed over multiple locations and creating a pool of resources.
-The upper layer to the raw resources is abstracting the complexity of managing and accessing the resources, and provide a simplified access to the upper layer.
-In the Upper layers, it view as a unlimited resource pool for storing and handling data.
+The next level upholds the Web services that provide access to raw services \cite{Droegemeier2005Service-OrientedWeather}.
+These two layers are working together since \acrshort{lead} system resources are distributed over multiple locations and creating a pool of resources.
+The upper layer to the raw resources is abstracting the complexity of managing and accessing the resources, and provide simplified access to the upper layer.
+In the Upper layers, its view as an unlimited resource pool for storing and handling data.
 
 The configuration and execution services in the middle layer, consisting of five elements, represent services invoked by LEAD workflows.
-These are some critical aspects on a weather data management system.
-Most of the services listed here are required for creating work flows for weather data forecasting.
+These are some critical aspects of a weather data management system.
+Most of the services listed here are required for creating workflows for weather data forecasting.
 Thus it is important to review them and understand the basic needs of a weather data management system.
@@
 \item The application-oriented configuration service that manages the deployment and execution of real applications such as the \acrshort{wrf} simulation model, ADAS, and the ADaM tools \cite{Droegemeier2005Service-OrientedWeather}.
-When creating weather work flow, it is required to change the behaviour of model by changing some of the configurations of the model or run a different version of the model.
+When creating weather workflow, it is required to change the behavior of the model by changing some of the configurations of the model or run a different version of the model.
 \item The application resource broker, which matches the appropriate host for execution to each application task, based on the execution’s time constraints \cite{Droegemeier2005Service-OrientedWeather}.
-This service is a critical part of the system, and responsible of using the resources of the system in optimized manner.
-When designing the weather data system, it is required to increase the capacity of the system automatically, and adopt into the system.
+This service is a critical part of the system, and responsible for using the resources of the system in an optimized manner.
+When designing the weather data system, it is required to increase the capacity of the system automatically, and adopt it into the system.
 \item The workflow engine service, which drives experimental workflow instances, invokes both the configuration service and application resource broker \cite{Droegemeier2005Service-OrientedWeather}.
-This is a part of work flow orchestration.
-\item The catalog services, represents the manner in which a user or application service discovers public-domain data products, or \acrshort{lead} services \cite{Droegemeier2005Service-OrientedWeather}.
-This is an important feature that should be available in a weather data system, and it is important to users to search for the availability of the data.
+This is a part of workflow orchestration.
+\item The catalog services represent how a user or application service discovers public-domain data products or \acrshort{lead} services \cite{Droegemeier2005Service-OrientedWeather}.
+This is an important feature that should be available in a weather data system, and users need to search for the availability of the data.
 Further wants to analyze the existing data for decision making.
 \item Users require a host of data services to support rich query, access, and transformation operations on data products.
-An important goal behind LEAD is access transparency—facilitating user queries across all available heterogeneous data sources without adverse affects from different formats and naming schemes \cite{Droegemeier2005Service-OrientedWeather}.
-Users need to have transformation services to read data in different format.
-The query service gives the capability to search via available data without any affect on the data formats.
+An important goal behind LEAD is access transparency facilitating user queries across all available heterogeneous data sources without adverse effects from different formats and naming schemes \cite{Droegemeier2005Service-OrientedWeather}.
+Users need to have transformation services to read data in different formats.
+The query service gives the capability to search via available data without any effect on the data formats.
 \end{itemize}
-The top of the \cref{fi:lead_soa}, shows the user interface to the system.
-This give the access to individual services.
-When user logs into the system, based on the authentication and authorization setting bind to the individual account, the portlets can access the services on behalf of the user.
-Look into further details is not relevant to developing the \acrshort{wdias}, since the focus is not about workflow orchestration.
+The top of \cref{fi:lead_soa}, shows the user interface to the system.
+This gives access to individual services.
+When the user logs into the system, based on the authentication and authorization setting bind to the individual account, the portlets can access the services on behalf of the user.
+Look into further details is not relevant to developing the \acrshort{wdias} since the focus is not on workflow orchestration.
 
-\acrshort{lead} is a more advanced system which can support for mesoscale weather prediction with the effort of multiple universities in the United State America with the effort of many of researchers and using many of computer resources.
-At the time it was building, it uses the \acrshort{soa} architecture as into its depth, and with the implementation each service can scale as needed and possible to enhance the service without interrupting other services.
-\acrshort{wdias} only focuses on creating a framework that is extendable as system needs more features as like \acrshort{lead} services.
+\acrshort{lead} is a more advanced system which can support for mesoscale weather prediction with the effort of multiple universities in the United State America with the effort of many researchers and using many computer resources.
+At the time it was building, it uses the \acrshort{soa} architecture as into its depth, and with the implementation, each service can scale as needed and possible to enhance the service without interrupting other services.
+\acrshort{wdias} only focuses on creating a framework that is extendable as system needs more features similar to \acrshort{lead} services.

### 2020-02-15 lit/sec_3-other-systems.tex
Grammarly DIAS and MASDIS

@@
 Once this data is integrated with geographic and socio-economic information, DIAS generates results for managing global environmental issues and natural disasters \cite{Kawasaki2018DataReduction}.
-As mentioned above, \acrshort{dias} has the capability of collecting weather data form multiple data sources which are inherently in different formats.
-After successfully ingest the data, it generate results which can use for different kind of purposes.
+As mentioned above, \acrshort{dias} has the capability of collecting weather data from multiple data sources which are inherently in different formats.
+After successfully ingest the data, it generates results which can use for different kind of purposes.
 
@@
 The mechanism of storing data in \acrshort{dias}, similar to the other systems discussed.
-These data sets are stored in an extra large volume disk array system with API (Application Programming Interface) software used to import the data.
+These data sets are stored in an extra largee volume disk array system with API (Application Programming Interface) software used to import the data.
 APIs work to convert or re-format data into manageable forms and are useful in creating the DIAS storage archive.
 API software consists of several tools, including the real-time data crawling and archiving system, data upload system, quality control system, and metadata management system \cite{Kawasaki2018DataReduction}.
-To store on the large volume of disk space, it convert the data via provided set of APIs.
-This can be consider same as the open data model provide by the \acrshort{fews}.
-Other than that, \acrshort{dias} consist of additional tools which provide the functionality of quality control of the data, and metadata management which is similar to some of services in \acrshort{lead}.
+To store on the large volume of disk space, it converts the data via a provided set of APIs.
+This can be considered the same as the open data model provided by the \acrshort{fews}.
+Other than that, \acrshort{dias} consist of additional tools that provide the functionality of quality control of the data, and metadata management which is similar to some of the services in \acrshort{lead}.
 
-As shown in \cref{fi:dias_common_platform}, it provides an application layer which allows domain scientists to working on research tasks, and to develop specific tools and applications by working together with Information Technology experts \cite{Kawasaki2018DataReduction}.
-Once the data is achieved on the \acrshort{dias} system, it share those details via Shared API layer.
+As shown in \cref{fi:dias_common_platform}, it provides an application layer that allows domain scientists to work on research tasks, and to develop specific tools and applications by working together with Information Technology experts \cite{Kawasaki2018DataReduction}.
+Once the data is achieved on the \acrshort{dias} system, it shares those details via the Shared API layer.
 Thus it allows users to remote access to the data, and easy integration via the APIs.
@@
 \acrfull{madis} is a data ingest and assimilation system, which is collecting data over dozen of providers, then quality control over the data and store in \acrshort{netCDF} format.
-Later allow users to access the data via supporting different type of protocols.
+Later allow users to access the data via supporting different types of protocols.
 
@@
 \acrshort{madis} comprises a distributed architecture for ingest, processing, and data distribution functions.
-In addition, in a recent architectural advance, the various functional hosts are arranged in pairs using High-Availability (HA) Linux to provide auto mated failover in case of system failure.
+Besides, in a recent architectural advance, the various functional hosts are arranged in pairs using High-Availability (HA) Linux to provide automated failover in case of system failure.
 Real-time data distribution methods include FTP, Local Data Manager (LDM), and the Web-based OPeNDAP (OPen source project for Network Data Access Protocol) \cite{Macdermaid2005ARCHITECTUREP2.39}.
-As it mentioned above, the \acrshort{madis} is implemented based on a distributed architecture which is available at the time of it's development.
-Even it is not clear mentioned, it is using functional call like Remote Procedure Call (RPC) to invoke among a cluster of nodes.
-In \cref{fi:madis_flow}, data are transported from input and preprocessing systems to the central compute systems and then out to other hosts for storage and distribution \cite{Macdermaid2005ARCHITECTUREP2.39}.
-To get high availability, it has added some update to it's architecture as mentioned in the paper.
-The conclusion of this statement is, these kind of functionalities are available at the modern the Cloud Computing tools, and out of the box those tools are providing the scalability and high availability.
-Using those tools, it possible to implement a such system with less effort and high confidence.
+As mentioned above, the \acrshort{madis} is implemented based on a distributed architecture that is available at the time of its development.
+Even it is not mentioned, it is using functional calls like Remote Procedure Call (RPC) to invoke among a cluster of nodes.
+In \cref{fi:madis_flow}, data are transported from the input and preprocessing systems to the central computer systems and then out to other hosts for storage and distribution \cite{Macdermaid2005ARCHITECTUREP2.39}.
+To get high availability, it has added some updates to its architecture as mentioned in the paper.
+The conclusion of this statement is, these kinds of functionalities are available at the modern the Cloud Computing tools, and out of the box, those tools are providing the scalability and high availability.
+Using those tools, it possible to implement such a system with less effort and high confidence.
 
@@
 The NetCDF files are then transferred to the MADIS compute nodes \cite{Macdermaid2005ARCHITECTUREP2.39}.
-This provide an overview of the level of data that \acrshort{madis} handling.
+This provides an overview of the level of data that \acrshort{madis} handling.
 This could be a good reference for implementing \acrshort{wdias}, and it's performance testing.
 As same as \acrshort{fews}, it is also converting the data into a common format which is \acrshort{netCDF}.
-Those files are transferred to the computer nodes, and allow users to access via OPeNDAP.
+Those files are transferred to the compute nodes and allow users to access via OPeNDAP.
 
-The MADIS compute platforms comprise Intel based servers running the Red Hat Enterprise Linux operating system.
+The MADIS compute platforms comprise Intel-based servers running the Red Hat Enterprise Linux operating system.
 Many of these computers are configured using High-Availability Linux clustering \cite{Macdermaid2005ARCHITECTUREP2.39}.
-As it indicated above, the system is heavily depend on the platform.
-There is a cost involving purchasing those license.
+As indicated above, the system heavily depends on the platform.
+There are some costs involving purchasing their licenses.
 
-Since some MADIS data are considered proprietary by the provider, access to these data need to be controlled.
+Since some MADIS data are considered proprietary by the provider, access to these data needs to be controlled.
 To accommodate this, MADIS data are split into six different versions based on the level of access allowed by the data provider \cite{Macdermaid2005ARCHITECTUREP2.39}.
-When compared to \acrshort{fews}, \acrshort{madis} provide a control based access to the data.
+When compared to \acrshort{fews}, \acrshort{madis} provides control based access to the data.
 
@@
 \label{se:lit_summary}
-Several related work that discussed above in this chapter, mainly focus on issue of storing data which are ingest from different sources with different formats efficiently.
-The \acrshort{fews} and \acrshort{madis} are using the \acrshort{netCDF} as the common data format to store the data which is one of best solution available with modern technologies as well.
-Even it is not clearly mentioned, the \acrshort{dias} and \acrshort{lead} also following a method of having common storage space in order to store bulk data.
-\acrshort{fews} and \acrshort{lead} have the capability of handling workflow of forecasting, but other system are mainly focus on providing a weather data management system.
-\acrshort{fews} provide a modular approach via it's general adapter which is shown on \cref{fi:fews_general_adapter}, and according to the \acrshort{soa} architecture of \acrshort{lead} provide the same functionality via services.
+Several related works discussed above in this chapter, mainly focus on the issue of storing data which are ingested from different sources with different formats efficiently.
+The \acrshort{fews} and \acrshort{madis} are using the \acrshort{netCDF} as the common data format to store the data which is one of the best solutions available with modern technologies as well.
+Even it is not mentioned, the \acrshort{dias} and \acrshort{lead} also following a method of having common storage space to store bulk data.
+\acrshort{fews} and \acrshort{lead} have the capability of handling the workflow of forecasting, but other systems are mainly focused on providing a weather data management system.
+\acrshort{fews} provides a modular approach via its general adapter which is shown in \cref{fi:fews_general_adapter}, and according to the \acrshort{soa} architecture of \acrshort{lead} provides the same functionality via services.
 
-Most of the above systems develop by many developers and researcher via many of funding.
-And most of them are depend on underline platform, and not up to date with the modern technologies such as cloud computing.
+Most of the above systems developed by many developers and researchers via sufficient funding, and developed specifically to address issues like natural disasters.
+When I required to establish a system in another country, it required to remodeling the models and defining the forecasting flows.
+Even some of the systems try to follow a generic approach to integrate new modules, it is challenging to deploy modules for a closed source or proprietary software.
+And most of them are depending on the underline platform, and not up to date with modern technologies such as cloud computing.

### 2020-02-15 method/sec_0_introduction.tex
Complete performance analysis
Grammarly method introduction

@@
 This chapter includes the design decision taken while implementing the \acrfull{wdias}, and how is the system got adapted from the systems analyzed in Chapter \ref{ch:literature}.
-In \cref{se:high_level_design} a brief discussion on how the weather forecasting is happening and why it need to interact with multiple data formats is presented.
+In \cref{se:high_level_design} a brief discussion on how the weather forecasting is happening and why it needs to interact with multiple data formats is presented.
 \cref{se:architectural_decisions} that we evolve architectural design while designing and implementing the \acrshort{wdias}.
-The \cref{se:microservice} gives better understanding of the microservice architectural concepts follows while implementing the \acrshort{wdias}.
-Then the reason behind developing Hierarchical Database and technologies use for that discussed in the \cref{se:db_struct}.
-Through out the \cref{se:data_preprocess} discussed about how the \acrshort{wdias} enable for data preprocessing and adding capabilities via concept of Extensions.
-Final \cref{se:query} includes details on how to perform timeseries search and Geo based queries.
+\cref{se:microservice} gives a better understanding of the microservice architectural concepts that follow while implementing the \acrshort{wdias}.
+Then the reason behind developing \acrshort{wdias} database structure and technologies use for that discussed in \cref{se:db_struct}.
+\cref{se:data_preprocess} discussed how the \acrshort{wdias} enables for data preprocessing and adding capabilities via the concept of Extensions.
+Final \cref{se:query} includes details on how to perform timeseries search and Geo-based queries.
 
@@
 
-To get overall idea on the flow of weather prediction, let us look into one of flows using in \acrshort{curw} \cite{CUrWSL2017SL}.
+To get an overall idea of the flow of weather prediction, let us look into one of the flows using in \acrshort{curw} \cite{CUrWSL2017SL}.
 \dbc{Use CUrW-SL}
@@
 \end{enumerate}
-When looked into the above flow, it clear understanding on multiple data formats using while weather predictions.
-Other than that, to correct the model outputs, it required to collect real time data such as;
+When looked into the above flow, it gives a clear understanding of multiple data formats using while weather predictions.
+Other than that, to correct the model outputs, it required to collect real-time data such as;
 \begin{itemize}
@@
 \end{itemize}
-Other than above there are many data formats using for handling data based on devices and standards which are using.
+Other than above many data formats using for handling data based on devices and standards which are using.
 Also, for data modeling, it needs to convert the data into model compatible data format, then after successfully run the model it needs to collect data from the model output data formats.
@@
 
-\paragraph{Integration}-- The system should capable of integrating data from different source such as satellite data, high end and low end weather station etc.
+\paragraph{Integration}-- The system should capable of integrating data from different sources such as satellite data, high end, and low-end weather station, etc.
 And the system should be able to handle multidimensional spatial and temporal weather data efficiently and optimally.
@@
 Then the system should be able to fulfill weather models varying data requirements.
-Also those models reproduce large set of redundant data, thus system should store the bulk data while optimizing the disk space.
+Also, those models reproduce a large set of redundant data, thus the system should store the bulk data while optimizing the disk space.
 \paragraph{Dissemination}-- Then different users should be able to retrieve data as they required.
-Also the users should be able to easy to search into the available that in the system base on timeseries metadata or based on Geo queries.
+Also, the users should be able to easy to search into the available that in the system base on timeseries metadata or based on Geo queries.
 
@@
 \dbc{What's Base of WDIAS architecture?}
-\gkc{Moved to WDIAS microservices section \cref{sebse:wdias_microservices}}
+\gkc{Moved to WDIAS database structure section \cref{sebse:wdias_microservices}}
 

### 2020-02-15 method/sec_1-architectural_decisions.tex
Grammarly method introduction

@@
 
-Initial design of \acrshort{wdias} used the \acrfull{soa}.
-Moreover, it tried to use an \acrfull{esb} to integrate different modules, as \acrshort{esb} is acting as a common layer for all of modules.
+The initial design of \acrshort{wdias} used the \acrfull{soa}.
+Moreover, it tried to use an \acrfull{esb} to integrate different modules, as \acrshort{esb} is acting as a common layer for all of the modules.
 By default, \acrshort{esb} also provides publisher/subscribe (pub/sub) capabilities.
-\hl{Because} \acrshort{esb} \hl{mediator can be used to integrate the modules which are described in Section} \ref{subse:modules_weather_data_integration_sys}. 
+\hl{Because} \acrshort{esb} \hl{mediators can be used to integrate the modules which are described in Section} \ref{subse:modules_weather_data_integration_sys}. 
 \gkc{FIXED}
@@
 A mediator can take a message, carry out some predefined actions on it, and output the modified message.
-This mediator capabilities can use to integrate the modules of a weather data system as shown in \cref{fi:wdia_components}.
-\acrshort{esb} also support different transportation protocols such as HTTP and Web sockets.
-However, it turned out that \acrshort{esb} is not a suitable for data streaming or bulk data processing.
-Also, \acrshort{esb} suffer from single point of failure, as all the messages are going though a common bus and slower communication (can’t use for transfer data).
+These mediator capabilities can use to integrate the modules of a weather data system as shown in \cref{fi:wdia_components}.
+\acrshort{esb} also supports different transportation protocols such as HTTP and Web sockets.
+However, it turned out that \acrshort{esb} is not suitable for data streaming or bulk data processing.
+Also, \acrshort{esb} suffers from a single point of failure, as all the messages are going through a common bus and slower communication (cant use for transfer data).
 
-In the second design phase of \acrshort{wdias}, we attempted to use the actor model using AKKA framework \cite{HewittWhyModel} in order to overcome above \acrshort{esb} drawbacks.
+In the second design phase of \acrshort{wdias}, we attempted to use the actor model using the AKKA framework \cite{HewittWhyModel} to overcome above \acrshort{esb} drawbacks.
 At the same time, we moved away from the \acrshort{soa} architecture design to the microservice architecture design.
-Thus we redesign the system architecture with decompose into microservices and used actors to implement each microservice in the system.
-In that case, an actor or an actor with slave actors were map to each microservice in \acrshort{wdias}.
-\acrshort{soa} focuses on imperative programming, whereas microservices architecture focuses on a responsive-actor programming style using faster messaging mechanisms.
+Thus we redesign the system architecture with decomposing into microservices and used actors to implement each microservice in the system.
+In that case, an actor or an actor with slave actors was a map to each microservice in \acrshort{wdias}.
+\acrshort{soa} focuses on imperative programming, whereas microservices architecture focuses on a responsive actor programming style using faster messaging mechanisms.
 
@@
     \item Follow the Single Responsibility principle
-    \item Resilient/flexible as failure in one service does not impact other services. If you have monolithic or bulky service errors in one service/module it can impact other modules/functionality.
+    \item Resilient/flexible as a failure in one service does not impact other services. If you have monolithic or bulky service errors in one service/module it can impact other modules/functionality.
     \item High scalable as demanding services can be deployed in multiple servers to enhance performance and keep away from other services so that they do not impact other services.
-Will be difficult to achieve the same with single, large monolithic service.
-    \item Easy to enhance as dependencies are less. Is also easier to change and test.
+It will be difficult to achieve the same with single, large monolithic service.
+    \item Easy to enhance as dependencies are less. It is also easier to change and test.
     \item Low impact on other services as each service is independent. % service., this has less chance to impact other services
@@
 
-Even with using the AKKA framework, it has some of the disadvantage with implementing each microservice as an actor as described in AKKA documentation \cite{Akka.ioWhenCluster}.
-One of the attractive feature of microservice architecture is independent nature of the microservices.
-This allows to choose a different technology for each microservice based on the advantage that could bring in.
+Even with using the AKKA framework, it has some of the disadvantages of implementing each microservice as an actor as described in AKKA documentation \cite{Akka.ioWhenCluster}.
+One of the attractive features of microservice architecture is the independent nature of the microservices.
+This allows choosing a different technology for each microservice based on the advantage that could bring in.
 Also allowed to independently develop and maintain by multiple smaller and more focused teams/communities.
-But using the actors as microservice, the actors messaging between different services cause to result in a too tight code coupling between the services and difficulties deploying these independent of each other, which is one of the main reasons for using a microservices architecture \cite{Akka.ioWhenCluster}.
+But using the actors as microservice, the actors messaging between different services cause to result in a too-tight code coupling between the services and difficulties deploying these independent of each other, which is one of the main reasons for using a microservices architecture \cite{Akka.ioWhenCluster}.
 To overcome these issues, we moved to the concept of container-orchestration based architecture.
@@
 
-Containerization is an alternative to the virtualization that supports via virtual machines or Hypervisors.
+Containerization is an alternative to the virtualization that supports virtual machines or Hypervisors.
 It involves encapsulating or packaging up software code and all its dependencies so that it can run uniformly and consistently on any infrastructure \cite{IBMContainerizationExplained}.
-The concept of containerization and process isolation is emerged after the open source Docker Engine \cite{DockerAppContainerization}, an industry standard for package software into standardized units for development, shipment and deployment.
+The concept of containerization and process isolation has emerged after the open-source Docker Engine \cite{DockerAppContainerization}, an industry standard for package software into standardized units for development, shipment, and deployment.
 
@@
 It groups containers that make up an application into logical units for easy management and discovery.
-While implementing the \acrshort{wdias}, we used \acrshort{k8s} as the container-orchestration system, in order to deploy each microservice as container and manage with providing scalability and availability.
+While implementing the \acrshort{wdias}, we used \acrshort{k8s} as the container-orchestration system, to deploy each microservice as container and manage with providing scalability and availability.
 
@@
     \item Pods -- Cluster of containers that can group other container images in a single unit.
-    \item Nodes -- the machines (VMs, physical servers, etc) in a cluster that run your applications and cloud workflows.
+    \item Nodes -- the machines (VMs, physical servers, etc) in a cluster that runs your applications and cloud workflows.
     \item kubelet -- An agent that runs on each node in the cluster. It makes sure that containers are running in a pod.
@@
 
-Users can add much as required Nodes into the \acrshort{k8s} cluster, and \acrshort{k8s} manage and deploy application as pods into cluster nodes.
-Each microservice can deploy as a Pod which is a group of containerize applications. And \acrshort{k8s} able to scale as much as user want as described above.
+Users can add much as required Nodes into the \acrshort{k8s} cluster, and \acrshort{k8s} manage and deploy applications as pods into cluster nodes.
+Each microservice can deploy as a Pod which is a group of containerized applications. And \acrshort{k8s} able to scale as much as the user wants as described above.
 By separating each microservice as a container, and running them as multiple pods inside the \acrshort{k8s} removes the tight coupling of microservices when compared to the actors.

### 2020-02-15 method/sec_3-microservice.tex
Grammarly microservice

@@
 
-The microservice architectural style is an approach to developing a single application as a suite of small services, each running in its own process and communicating with lightweight mechanisms, often via providing \hl{an RESTful API}.
+A microservice architecture style is an approach to developing a single application as a suite of small services, each running in its own process and communicating with lightweight mechanisms, often via providing \hl{a RESTful API}.
 These services are built around business capabilities and independently deployable by fully automated deployment machinery \cite{LewisMicroservices}.
-\hl{These services are implement independently with minimising the centralized dependencies.
+\hl{These services are implemented independently with minimizing the centralized dependencies.
 Thus each microservice may be written in different programming languages and use different data storage technologies}.
@@
 
-There are lots of microservice patterns developed and evolved over the time.
-Through out the following sections, we will discuss in brief about some of the microservice design patterns mostly used on the context of designing \acrshort{wdias} architecture.
-Next, we will discuss about how microservice architecture promote to only to create endpoints which are only belongs to each service logical domain.
-Next discuss about only using database per service which allows to loosely couple between system and achieve high scalability.
-In Sagas, we discuss about how distributed transaction can achieve over microservices.
-Next, we will discuss about a concept called as \emph{scale cube}, which explains the scalability in perspective of x,y and z axis.
+There are lots of microservice patterns developed and evolved.
+Throughout the following sections, we will discuss in brief some of the microservice design patterns mostly used in the context of designing \acrshort{wdias} architecture.
+Next, we will discuss how microservice architecture promote to only to create endpoints which only belong to each service logical domain.
+Next, discuss only using database per service which allows to loosely couple between systems and achieves high scalability.
+In Sagas, we discuss how distributed transactions can achieve over microservices.
+Next, we will discuss a concept called \emph{the scale cube}, which explains the scalability from the perspective of x,y, and z-axis.
 
@@
 When building communication endpoints, \hl{many architectural approaches are adding significant smart by providing different protocol supports and complex logic support via the endpoints.} As an example \acrshort{esb} support multiple protocols and endpoints can use complex logic.
-But microservice follows alternative approach: \emph{Smart endpoints and dumb pipes} \cite{LewisMicroservicesPipes}.
+But microservice follows an alternative approach: \emph{Smart endpoints and dumb pipes} \cite{LewisMicroservicesPipes}.
 Applications built from microservices aim to be as decoupled and as cohesive as possible.
-They own their own domain logic and act more as filters in the classical Unix sense.
+They own their domain logic and act more as filters in the classical Unix sense.
 After receiving a request, applying logic as appropriate and producing a response.
@@
 
-\acrshort{microservice} prefer letting each service manages its own database, either different instances of the same database technology, or entirely different database systems - an approach called \emph{Polyglot Persistence} \cite{LewisMicroservicesManagement}.
+\acrshort{microservice} prefer letting each service manages its database, either different instances of the same database technology, or entirely different database systems - an approach called \emph{Polyglot Persistence} \cite{LewisMicroservicesManagement}.
 
@@
 There are a few different ways to keep a service's persistent data private.
-It is not need to provision a database server for each service.
-For example, in the case of using a relational database then following methods can be use to keep data private \cite{RichardsonMicroservicesService}:
+It does not need to provision a database server for each service.
+For example, in the case of using a relational database then the following methods can be used to keep data private \cite{RichardsonMicroservicesService}:
 \begin{itemize}
     \item \emph{Private tables per service} –- each service owns a set of tables that must only be accessed by that service
-    \item \emph{Schema per service} –- each service has a database schema that’s private to that service
-    \item \emph{Database server per service} -– each service has its own database server.
+    \item \emph{Schema per service} –- each service has a database schema that private to that service
+    \item \emph{Database server per service} -– each service has its database server.
 \end{itemize}
@@
 Using a \emph{schema per service} is appealing since it makes ownership clearer.
-Some high throughput services might need their own database server.
+Some high throughput services might need their database server.
 
@@
 \label{subse:sagas}
-In order to ensure loose coupling, each microservice better to have own database.
+To ensure loose coupling, each microservice better to have own database.
 Maintaining data consistency between services is a challenge because 2 phase-commit/distributed transactions is not an option for many applications.
@@
 Other services consume that event and update their data \cite{RichardsonMicroservicesSagas}.
-This is also called as \emph{Saga pattern}.
+This is also called the \emph{Saga pattern}.
 
@@
 \gkc{I can not think about any other title than this.}
-The scalability of a system can explain via a concept called \emph{Scale Cube} which talk about the scalability of the application by defining over X, Y and Z axis.
+The scalability of a system can explain via a concept called \emph{Scale Cube} which talks about the scalability of the application by defining over X, Y and Z axis.
 
@@
 If there are \textit{n} copies then each copy handles 1/\textit{n} of the load.
-This is a simple, commonly used approach of scaling a service.
+This is a simple, commonly used approach to scaling a service.
 
-\paragraph{Y-axis Scaling}-- Unlike X-axis and Z-axis, which consist of running multiple, identical copies of the application, Y-axis axis scaling splits the application into multiple, different services.
+\paragraph{Y-axis Scaling}-- Unlike the X-axis and Z-axis, which consist of running multiple, identical copies of the application, Y-axis axis scaling splits the application into multiple, different services.
 Each service is responsible for one or more closely related functions.
@@
 \begin{itemize}
-    \item verb-based decomposition e.g., checkout.
-    \item decompose the application by noun, for e.g., customer management. 
+    \item verb-based decomposition. e.g., checkout.
+    \item decompose the application by noun. e.g., customer management. 
     \item an application might use a combination of verb-based and noun-based decomposition.
@@
 
-Even \acrshort{wdias} is design based on the Y-axis scaling, it's possible to use the Z-axis scaling to scalability of the system further. This will be more discuss in the \cref{se:discussion}.
+Even \acrshort{wdias} is a design based on the Y-axis scaling, it's possible to use the Z-axis scaling to scaling the system further. This will be more discussion in \cref{se:discussion}.
 
@@
 \end{figure}
-Left side of \cref{fi:wdias_micro_on_demand} shows the import modules of the \acrshort{wdias}, and right side shows the export modules.
-As it explained section \cref{subse:dumb_pipes}, each import microservice only do specific task of converting and forwarding the request to the correct data adapter module.
-For each data type, there is a adapter microservice is running which is optimized to storing such type of data.
+The left side of \cref{fi:wdias_micro_on_demand} shows the import modules of the \acrshort{wdias}, and the right side shows the export modules.
+As explained section \cref{subse:dumb_pipes}, each import microservice only does the specific task of converting and forwarding the request to the correct data adapter module.
+For each data type, there is an adapter microservice is running which is optimized to storing such type of data.
 And the metadata data of the timeseries store using \acrshort{rdbms} which gives more performance over retrieving metadata data.
-The metadata is cached with In-Memory database to fast access as mentioned in \cref{subse:redis}.
-The system generate a unique identifier for each timeseries, and through out the \acrshort{wdias}, other microservice use it to handle data for fast access.
+The metadata is cached with the In-Memory database to fast access as mentioned in \cref{subse:redis}.
+The system generates a unique identifier for each timeseries, and throughout the \acrshort{wdias}, other microservice use it to handle data for fast access.
 
@@
 \end{figure}
-Export module microservice follows the same concepts and provide the capability to export the data into required formats of the weather models.
-Each adapter follows the concept of database per service as mentioned in the section \cref{subse:database_per_service}. This gives the freedom for \acrshort{wdias} to scale better with \acrshort{k8s}.
+Export module microservice follows the same concepts and provides the capability to export the data into required formats of the weather models.
+Each adapter follows the concept of database per service as mentioned in \cref{subse:database_per_service}.
+This gives the freedom for \acrshort{wdias} to scale better with \acrshort{k8s}.
 
-As shown in \cref{fi:wdias_micro_on_demand}, when a smaller size request come to the system, it handle on demand and response back.
-However, as shown in \cref{fi:wdias_micro_async}, when a request with larger size come to the system, it store the data for asynchronously process the data and response with a unique id which can use to verify whether data processed successfully or not.
-Here is uses the microservice pattern of \cref{subse:sagas} while processing the Grid data.
-First it store the data and respond back to the user.
-Then publish an event, and another service listen to those events and process the data and update the system status.
+As shown in \cref{fi:wdias_micro_on_demand}, when a smaller size request comes to the system, it handles on-demand and response back.
+However, as shown in \cref{fi:wdias_micro_async}, when a request with a larger size comes to the system, it stores the data for asynchronously process the data and responds with a unique id that can use to verify whether data processed successfully or not.
+Here is uses the microservice concept of Saga as mentioned in \cref{subse:sagas} while processing the Grid data.
+First, it stores the data and responds to the user.
+Then publish an event, and another service listens to those events and process the data and update the system status.
 
@@
 \end{figure}
-The \cref{fi:wdias_micro_on_demand} show the clear separation of microservices into the modules of the \acrshort{wdias}.
-As it shown, each adapter has isolated database, and database is hosted separately for the high performance.
-Apart from that, as we further discuss in \cref{se:data_preprocess}, the extension modules are running separately such as Interpolation, Transformation and Validation etc.
-The Extension Adapter allow users to register new triggers for the extensions. And extension scheduler triggers the events based on time and extension handler triggers event based on data change.
+\cref{fi:wdias_micro_on_demand} shows the clear separation of microservices into the modules of the \acrshort{wdias}.
+As shown, each adapter has an isolated database, and the database is hosted separately for the high performance.
+Apart from that, as we further discuss in \cref{se:data_preprocess}, the extension modules are running separately such as Interpolation, Transformation, and Validation, etc. 
+The Extension Adapter allows users to register new triggers for the extensions. And extension scheduler triggers the events based on time and extension handler triggers event based on data change.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{\acrshort{wdias} API}
+\subsection{\acrshort{wdias} \acrfull{api}}
 \label{sebse:wdias_api}
-One of the main design consideration in \acrshort{wdias} is the convention of defining the \acrshort{api}. It follows a simple RESTful \acrshort{api}, and allow users to interact with HTTP methods.
+One of the main design considerations in \acrshort{wdias} is the convention of defining the \acrshort{api}. It follows a simple RESTful \acrshort{api}, and allow users to interact with HTTP methods.
 
-\emph{Timeseries} endpoints allow to interact with Metadata Adapter, and those are cache on the Query Handler in order to perform search queries.
+\emph{Timeseries} endpoints allow users to interact with Metadata Adapter, and those are cache on the Query Handler to perform search queries.
 These are the main endpoints to handle timeseries metadata which defines unique timeseries identifier based on the metadata values.
@@
 
-As it mentioned above, other than the timeseries metadata which is the core of the data system, other module endpoints start with the module name such as import, export and extension.
-This allows to add new module system if required.
-For import and export modules, then follows by the data format. This provide the flexibility to integrate new data format modules.
+As mentioned above, other than the timeseries metadata which is the core of the data system, other module endpoints start with the module name such as import, export, and extension.
+This allows adding a new module system if required.
+For import and export modules, then follows by the data format. This provides the flexibility to integrate new data format modules. 
 Then the endpoint name ends with the data upload/insert data type.
-Data can upload as a single file with binary or multiple files with upload.
-Or in the body of the request as raw, and need to send the required headers has mentioned by particular module.
+Data can upload as a single file with binary or multiple files with the upload.
+Or in the body of the request as raw, and need to send the required headers has mentioned by a particular module.
 Thus the \acrshort{api} convention of \texttt{\hl{/MODULE/DATA\_FORMAT/DATA\_TYPE}} allows users to integrate new import or export modules into the system as well as add new data types.

### 2020-02-15 method/sec_4-db_struct.tex
Grammarly DB structure

@@
 
-In order to understand the underline design decisions of \acrshort{wdias} database structure, it need to deeply look into the weather data timeseries.
+To understand the underline design decisions of the \acrshort{wdias} database structure, it needs to deeply look into the weather data timeseries.
 \paragraph{Timeseries}-- \emph{A timeseries is simply a series of data points ordered in time}.
-In weather domain, it interest in timeseries in perspective of observations to forecasting.
-Each timeseries, the data points can be form in different formats as well.
+In the weather domain, its interest in timeseries in perspective of observations to forecasting.
+Each timeseries, the data points can be formed in different formats as well.
 For example, scalar (0D), vector (1D), grid (2D), and polygon (2D).
@@
 As per the above interpretation, a timeseries have data points ordered in time.
-Other than that, timeseries have other information which are known as \emph{timeseries metadata} which can use to uniquely identify one timeseries from another.
-As an example, a weather station can placed on a location and it can keep measure variables which are called as \emph{parameters} such as temperature, precipitation and wind direction which can produce different timeseries.
+Other than that, timeseries have other information which is known as \emph{timeseries metadata} which can use to uniquely identify one timeseries from another.
+As an example, a weather station can be placed on a location and it can keep measure variables which are called \emph{parameters} such as temperature, precipitation and wind direction which can produce different timeseries.
 Even we can use the location as metadata to identify the timeseries, that is not enough to separately identify the parameters.
-Thus we need to use set of attributes to uniquely identify a timeseries.
-In the next \cref{subse:timeseries_key_attributes}, we describe about key attributes which are using by the \acrshort{wdias} to uniquely identify a timeseries.
+Thus we need to use a set of attributes to uniquely identify a timeseries.
+In the next \cref{subse:timeseries_key_attributes}, we describe key attributes which are using by the \acrshort{wdias} to uniquely identify a timeseries.
 
@@
 \label{subse:timeseries_key_attributes}
-\paragraph{Module ID}-- String field which describe the source of the data generated. e.g., hec-hms, flow2d, weather-station etc
+\paragraph{Module ID}-- String field which describe the source of the data generated. e.g., hec-hms, flow2d, weather-station, etc
 
-\paragraph{Value Type}-- Scalar, Vector, Grid are the Value Types which are interested in the \acrshort{wdias}.
+\paragraph{Value Type}-- Scalar, Vector, Grid are the Value Types that are interested in the \acrshort{wdias}.
 
-\paragraph{Location}-- Location of the timeseries. All locations have unique String identifier called locationId. Further, there are two type of location types that is interested in the WDIAS, namely:
+\paragraph{Location}-- Location of the timeseries. All locations have a unique String identifier called locationId. Further, two types of location types are interested in the WDIAS, namely:
 \begin{itemize}
-  \item \emph{Point locations}-- Contains a name which is human readable. lat and lon of the location on earth surface.
+  \item \emph{Point locations}-- Contains a name that is human readable. lat and lon of the location on the earth surface.
   \begin{lstlisting}[language=Python]
@@
   \gkc{This space is adding by itemize. I applied in all the places. Could not find how to remove it. Otherwise, need to remove itemize.}
-  \item \emph{Regular Grid locations} -- Contains a name which is human readable. The grid presents by dividing into equal size cells. Thus, it need the number of rows and columns. 
+  \item \emph{Regular Grid locations} -- Contains a name that is human readable. The grid presents by dividing into equal size cells. Thus, it needs the number of rows and columns. 
   And the location of the first cell and the width and height of it.
@@
   \end{lstlisting}
-  \item \emph{Irregular Grid locations} -- (endpoints are available with in the WDIAS system, but skipped since it is out of the interest of the scope.)
+  \item \emph{Irregular Grid locations} -- (endpoints are available within the WDIAS system, but skipped since it is out of the interest of the scope.)
 \end{itemize}
@@
 \paragraph{Parameter}
-Parameter describe the variable measuring against a location. All parameters have a unique String identifier called as \textit{parameterId}. A parameter can be use in multiple locations.
-While defining a parameter, there are three required fields which need to be provided such as variable, unit and \textit{parameterType}.
+Parameter describes the variable measuring against a location.
+All parameters have a unique String identifier called \emph{parameterId}.
+A parameter can be used in multiple locations.
+While defining a parameter, three required fields need to be provided such as variable, unit and \emph{parameterType}.
+
 \begin{itemize}  
@@
 \subsubsection{Timeseries Type}
-Timeseries Type can be redefine with the system setup. \acrshort{wdias} defined following types for during the setup. Timeseries type can be combination of source followed by category:
+Timeseries Type can be redefined with the system setup. \acrshort{wdias} defined the following types for during the setup. Timeseries type can be a combination of a source followed by category:
 \begin{itemize}
-  \item Sources - External or simulated. \emph{External} means whether timeseries is taken from external source, and \emph{simulated} means it generated by simulations of the users.
+  \item Sources - External or simulated. \emph{External} means whether timeseries is taken from an external source, and \emph{simulated} means it generated by simulations of the users.
   \item Category - Historical or forecast.
 \emph{Historical} means whether timeseries have continuous data such as observations from a weather station.
-\emph{forecast} mean discrete set of timeseries data produce by forecasting.
+\emph{forecast} means discrete set of timeseries data produce by forecasting.
 \end{itemize}
@@
 
-\paragraph{Time Step}-- All Time Steps has an unique String identifier called as timeStepId.
+\paragraph{Time Step}-- All TimeSteps has a unique String identifier called timeStepId.
 Unit should be one of Second, Minute, Hour, Day, Week, Month, Year, or NonEqualDistance.
-One of multiplier or divider can be use to define the interval between each measurement.
+One of multiplier or divider can be used to define the interval between each measurement.
 \begin{lstlisting}[language=Python]
@@
 
-Among above key attributes; Location, Parameter and Time Step attributes are composite attributes. But each of them have an unique identifier.
+Among the above key attributes; Location, Parameter and Time Step attributes are composite attributes. But each of them has a unique identifier.
 Given that, a timeseries can uniquely identify by moduleId, valueType, parameterId, locationId, timeseriesType and timeStepId.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Even a timeseries consist of data points, the data for each data point can vary based on the valueType.
-For Scalar data point only consist from a single value.
-And Vector data point consist of two values such as magnitude and the direction of the Vector.
-But for Grid data a point can consist with multiple values.
-In order to get the advantage of storing data efficiently, we can use set of different databases based on the advantage of using them for each valueType.
+Even a timeseries consists of data points, the data for each data point can vary based on the valueType.
+Scalar data point only consist of a single value.
+And Vector data point consists of two values such as magnitude and the direction of the Vector.
+But for Grid data, a point can consist of multiple values.
+To get the advantage of storing data efficiently, we can use a set of different databases based on the advantage of using them for each valueType.
 Other than the valueType attribute, other attribute does not much impact on the data size.
 
-Further it is will be difficult to search for the timeseries data, if those are stored over multiple data sources, and avoiding duplicates.
-Thus it add low overhead to have a single data source to look into while searching for the timeseries metadata.
-The load on above data source can reduce by using a caching mechanism.
-In order to support search queries with lower latency, it required to use an indexing for fast search for timeseries metadata.
-Further Geo based indexing is required in order to support Geo based search queries based on the locations.
+Further, it is will be difficult to search for the timeseries data, if those are stored over multiple data sources, and difficult to avoid having duplicates.
+Thus it adds low overhead to have a single data source to look into while searching for the timeseries metadata.
+The load on the above data source can reduce by using a caching mechanism.
+To support search queries with lower latency, it required to use indexing for the fast search for timeseries metadata.
+Further, Geo-based indexing is required to support Geo-based search queries based on the locations.
 
-With considering above facts, we can not achieve all of the benefits using one of database system available.
-Thus it required to have a database structure which is capable of proving all of above capabilities via combining together.
+Considering the above facts, we can not achieve all of the benefits using one of the database systems available.
+Thus it required to have a database structure that is capable of proving all of the above capabilities via combining.
 According to the design principle of microservices architecture, we created microservice for each of the valueType with following the concept of Database per Service as described in the \emph{Database per Service} in \cref{subse:database_per_service}.
-In \cref{sebse:wdias_microservices} those microservices are group as \emph{adapters} which share an \acrshort{api} to interact with while keeping the persistent data private.
+In \cref{sebse:wdias_microservices} those microservices are group as \emph{adapters} that share an \acrshort{api} to interact with while keeping the persistent data private.
 
@@
 \cref{fi:database_structure} shows the \acrshort{wdias} database structure.
-Following sections describe the database structure of \acrshort{wdias} which respect to the design with more details on how is support the microservice architecture.
+The following sections describe the database structure of \acrshort{wdias} with compare to the design with more details on how is support the microservice architecture.
 
@@
 
-As describe in above section, in order to reduce the overhead while searching for timeseries and handling duplicates, it required to have a timeseries metadata store.
-Since metadata consist of multiple key attributes, the data can be efficiently store using a \acrfull{rdbms}.
+As described in the above section, to reduce the overhead while searching for timeseries and handling duplicates, it required to have a timeseries metadata store.
+Since metadata consists of multiple key attributes, the data can be efficiently store using a \acrfull{rdbms}.
 This helps to store data without any duplicates and store the data with normalization.
 As an example, the parameter attribute can have one or two dozen of values.
-Using a \acrshort{rdbms}, those values can be store once and reuse with defining timeseries against location via reference.
+Using an \acrshort{rdbms}, those values can be stored once and reuse with defining timeseries against location via reference.
 
 \acrshort{wdias} is using SQL as the \acrfull{rdbms}. 
-Since WDIAS scope is to using open source tools, it is using \acrshort{mysql} as persistent database for storing timeseries metadata described above.
+Since the \acrshort{wdias} scope is to use open source tools, it is using \acrshort{mysql} as a persistent database for storing timeseries metadata described above.
 One instance of \acrshort{mysql} is using only by adapter-metadata service.
-Other than that, another instance of \acrshort{mysql} is using for adapter-extension which will be describe in more detail \cref{se:data_preprocess}.
+Other than that, another instance of \acrshort{mysql} is using for adapter-extension which will be described in more detail \cref{se:data_preprocess}.
 \acrshort{mysql} is used only for these services, those will only keep the consistency of the schema for timeseries metadata and extension metadata.
 As mentioned in \cref{subse:redis}, it uses \acrshort{redis} instance is using for caching the data from \acrshort{mysql}, since the \acrshort{mysql} database instances, itself not going to get much load.
-Other than MySQL, there are many open source databases can be used to replace the same functionality.
+Other than MySQL, many open source databases can be used to replace the same functionality.
 \dbc{First start with a brief discussion on why a RDBMS is needed}
@@
 \label{subse:influxdb}
-Among several timeseries open source databases, \acrshort{influxdb} \cite{influxdbInfluxDBDocumentation} \hl{is using an unique database indexing algorithm in order to gain higher performance while storing timeseries data} when compared to other databases available.
-Also it has better support, higher number of usage and has following supports;
+Among several timeseries open source databases, \acrshort{influxdb} \cite{influxdbInfluxDBDocumentation} \hl{is using a unique database indexing algorithm to gain higher performance while storing timeseries data} when compared to other databases available.
+Also, it has better support, higher usage and has following supports;
 \begin{itemize}
@@
 With changing the configurations of the \acrshort{influxdb}, it is possible to adapt as required. As mention in \cite{influxdbInfluxDBDocumentation}, 
-\acrshort{influxdb} can setup on a computer which will give the required performance. Going further, users can use commercial version of \acrshort{influxdb} in order to gain more performance.
+\acrshort{influxdb} can setup on a computer that will give the required performance. Going further, users can use the commercial version of \acrshort{influxdb} to gain more performance.
 
-Two instance of \acrshort{influxdb} is using in the WDIAS system by adapter-scalar and adapter-vector services.
+Two instances of \acrshort{influxdb} is using in the WDIAS system by adapter-scalar and adapter-vector services.
 For the scalability, the system uses \emph{Database per Service} as mentioned in \cref{subse:database_per_service}.
-But further, it split into two services, referring to the \cref{subse:scale_cube}, the Z-axis scaling, the data is partitioned among few servers based on valueType key attribute of timeseries.
+But further, it split into two services, referring to \cref{subse:scale_cube}, the Z-axis scaling, the data is partitioned among a few servers based on valueType key attribute of timeseries.
 Which also conclude the concept of splitting into more services based on other key attributes such as timeseriesType, if further performance required.
@@
 \label{subse:netcdf}
-\acrshort{netCDF} \cite{unidataUnidataNetCDF} is a self-describing, machine-independent data formats that support creation, access, and sharing of array-oriented scientific data.
+\acrshort{netCDF} \cite{unidataUnidataNetCDF} is a self-describing, machine-independent data formats that support the creation, access, and sharing of array-oriented scientific data.
 And it also has the support for parallel file access.
-NetCDF is widely using in scientific domain due to it has the capability of storing data in multi dimensions easily and flexibility with storing many of the scientific data.
+NetCDF is widely using in the scientific domain due to it has the capability of storing data in multi-dimensions easily and flexibility with storing many of the scientific data.
 Due to its capability of storing scientific data efficiently, \acrshort{wdias} using it for storing the Grid data.
@@
 
-\acrshort{wdias} is using \acrshort{mongodb} as the document-oriented databse, as it has the Geo searching capabilities.
-\acrshort{mongodb} \cite{mongodbMongoDBManual} is a general purpose, document-based, distributed database. And it supports:
+\acrshort{wdias} is using \acrshort{mongodb} as the document-oriented database, as it has the Geo searching capabilities.
+\acrshort{mongodb} \cite{mongodbMongoDBManual} is a general-purpose, document-based, distributed database. And it supports:
 \dbc{Need for a mix of relational, time series, document stores, and in-memory need to be first mentioned and justified in high-level design of WDIAS above.}
@@
 \begin{itemize}
-  \item Supports query operations on geo-spatial data \cite{mongodbMongoDBManual}
+  \item Supports query operations on geospatial data \cite{mongodbMongoDBManual}
   \item Clustering and Sharding available for scalability and reliability
 \end{itemize}
-\acrshort{mongodb} geo-spatial features are using for support Geo queries in the WDIAS. Other than that, external timeseries metadata queries are served by the indexed timeseries metadata data.
-If metadata not present in the adapter-query, if fetch data from the adapter-metadata, then indexed and cache in the \acrshort{mongodb}.
-Vise a versa, if new timeseries create in the adapter-metadata, it trigger an event to adapter-query to index the new timeseries.
-In \cref{subse:scale_cube}, the Y-axis scaling concept is using here by splitting into the multiple services based on the functionality and scale the system.
+\acrshort{mongodb} geospatial features are using to support Geo queries in the WDIAS. Other than that, external timeseries metadata queries are served by the indexed timeseries metadata data.
+If metadata not present in the adapter-query if fetch data from the adapter-metadata, then indexed and cache in the \acrshort{mongodb}.
+Vise a versa, if new timeseries create in the adapter-metadata, it triggers an event to adapter-query to index the new timeseries.
+In \cref{subse:scale_cube}, the Y-axis scaling concept is using here by splitting into the multiple services based on the functionality and scale of the system.
 
@@
 \label{subse:redis}
-\acrshort{wdias} is using \acrshort{redis} \cite{redisRedisDocumentation} as the In-Memory database, since it's widely using tool with good support, and it support few other features such as Publisher Subscriber capabilities.
-\acrshort{redis} is an open source (BSD licensed), used as a database, cache. Clustering is available for scalability.
-\acrshort{redis} uses as in-memory caching for fast access of repreative access data in adapter-metadata and adapter-extension.
-Other than that, adapter-status uses \acrshort{redis} as key value pair store for getting the status for async handling requests such as storing Grid data.
-In adapter-extension uses Redis's Publisher Subscriber capabilities in order to create a cron job in extension-scheduler when new extension create on \cref{se:data_preprocess}
+\acrshort{wdias} is using \acrshort{redis} \cite{redisRedisDocumentation} as the In-Memory database, since it is a widely used tool with good support, and it supports few other features such as Publisher Subscriber capabilities.
+\acrshort{redis} is an open-source (BSD licensed), used as a database, cache. Clustering is available for scalability.
+\acrshort{redis} uses as in-memory caching for fast access the frequent access data in adapter-metadata and adapter-extension.
+Other than that, adapter-status uses \acrshort{redis} as a key-value pair store for getting the status for async handling requests such as storing Grid data.
+In adapter-extension uses Redis's Publisher Subscriber capabilities to create a cronjob in extension-scheduler when new extension creates on \cref{se:data_preprocess}

### 2020-02-15 method/sec_4-db_struct.tex
Grammarly data preprocessing

@@
 Other than that, adapter-status uses \acrshort{redis} as a key-value pair store for getting the status for async handling requests such as storing Grid data.
-In adapter-extension uses Redis's Publisher Subscriber capabilities to create a cronjob in extension-scheduler when new extension creates on \cref{se:data_preprocess}
+In adapter-extension uses Redis's Publisher Subscriber capabilities to create a cronjob in extension-scheduler when a new extension creates on \cref{se:data_preprocess}

### 2020-02-15 method/sec_5-data_preprocess.tex
Grammarly data preprocessing

@@
 
-The data imported via imported modules may have incorrect data, missing data and not compatible with directly feed into simulation modules. 
-Thus it required to preprocess data before going to use in such cases. The WDIAS supports these capabilities via Extensions. Current system has
-in build few extensions such as Interpolation, Transformation and Validation. Other than those, it possible to add more extensions as required.
+The data imported via imported modules may have incorrect data, missing data and not compatible with direct feed into simulation modules. 
+Thus it required to preprocess data before going to use it in such cases.
+The WDIAS supports these capabilities via Extensions.
+The current system has a few inbuilt extensions such as Interpolation, Transformation, and Validation.
+Other than those, it possible to add more extensions as required.
 \begin{figure}[htp]
@@
 
-The WDIAS provides the support via in build simple generic mathematical function model. Each extension is considering as a mathematical function which can take p 
-number of input timeseries variables and output n number of timeseries variables. Other than that, at the time of processing the system can configure to provide
-bind constant which can provide while configuring an extension. Which means, it is possible to change the behaviour of a existing function by providing different bind
-constant at the time of creating new triggers for an extension.
+The WDIAS provides the support via a simple generic mathematical function model.
+Each extension is considering as a mathematical function which can take \texttt{p} number of input timeseries variables and output \texttt{n} number of timeseries variables.
+Other than that, at the time of processing the system can configure to provide bind constant which can provide while configuring an extension.
+This means it is possible to change the behavior of an existing function by providing different bind constant at the time of creating new triggers for an extension.
 
 \subsection{Interpolation}
-The Interpolation module generates data at desired locations or at desired points in time by means of either a serial or spatial interpolation technique.
-It is applied for the filling in of data gaps in measured on-line data, as well as to derive spatially distributed data for meteorological time series, such as precipitation and temperature, based on information available at neighbouring locations.
+The Interpolation module generates data at desired locations or desired points in time using either a serial or spatial interpolation technique.
+It is applied for the filling in of data gaps in measured on-line data, as well as to derive spatially distributed data for meteorological time series, such as precipitation and temperature, based on information available at neighboring locations.
 
@@
 \paragraph{Spatial Interpolation}-- In spatial interpolation mode, the interpolation can be either applied to fill gaps in time series, or to create a new time series for a location using data from other (spatially distributed) locations.
-Spatial interpolation can also be applied for sampling scalar time series from grid time series, for re-sampling grids, or for creating grids from time series data.
+Spatial interpolation can also be applied for sampling scalar time series from grid time series, for re-sampling grids, or for creating grids from timeseries data.
 \begin{figure}[htp]
@@
     \includegraphics[width=0.6\textwidth]{method/data_preprocess/validation.jpg}
-    \caption{\hl{Timeseries data validation against set of rules.}}
+    \caption{\hl{Timeseries data validation against a set of rules.}}
     \label{fi:validation}
@@
 \subsubsection{Extension Handler}
-Extension Handler is responsible for triggering the correct Extension with metadata when there is any change on subscribed extension trigger's \emph{OnChange} timeseries.
+Extension Handler is responsible for triggering the correct Extension with metadata when there is any change on the subscribed extension trigger's \emph{OnChange} timeseries.
 \begin{figure}[htp]
@@
 
-\hl{As an example,} when new data imported into one of adapter-scalar or adapter-vector, those notify the extension-handler.
-Then extension handler check whether there is any extension subscribed for particular timeseries, and trigger it via triggering an event on particular extensions.
+\hl{As an example,} when new data imported into one of the adapter-scalar or adapter-vector, those notify the extension-handler.
+Then extension handler checks whether there is any extension subscribed for particular timeseries, and triggers it via triggering an event on particular extensions.
 
@@
 For the separation of service responsibilities, those functionalities reside in the adapter-extension and expose via an endpoint.
-First, other than storing extension metadata in MySQL instance of adapter-extension, it also store the data in reverse lookup table called triggers.
+First, other than storing extension metadata in MySQL instance of adapter-extension, it also stores the data in reverse lookup table called triggers.
 Using this reverse lookup table, for a given trigger\_type and timeseries, it can retrieve the extensions which are part of given timeseries.
 Thus, the response which is received by the
-extension-handler only contains the extensions to be triggered. No additional filtering need to be done at the extension-handler service.
-Second, cache the resulting trigger\_type and timeseries data in \acrshort{redis} database for fast access and avoid too much queries on \acrshort{mysql} database.
+extension-handler only contains the extensions to be triggered. No additional filtering needs to be done at the extension-handler service.
+Second, cache the resulting trigger\_type and timeseries data in the \acrshort{redis} database for fast access and avoid too many queries on the \acrshort{mysql} database.
 
-\paragraph{Extension Scheduler}-- Extension Handler is responsible for triggering the correct Extension with metadata at given time which is provided at the creation on extension trigger's with the value of OnTime cronjob string value.
+\paragraph{Extension Scheduler}-- Extension Handler is responsible for triggering the correct Extension with metadata at a given time which is provided at the creation on extension trigger with the value of OnTime cronjob string value.
 To improve the performance of triggering cronjobs at given time schedules, the WDIAS added few optimization mechanisms.
-Same as for extension-handler, the adapter-extension expose an endpoint to retrieve extension metadata grouped by cronjob time.
+Same as for extension-handler, the adapter-extension exposes an endpoint to retrieve extension metadata grouped by cronjob time.
 Then use \acrshort{go} to implement the extension-handler to fast processing the extensions.
-After retrieve extension which are grouped by cronjob time; within the extension-handler, it schedules programatic cronjobs to trigger at given times.
-When each cronjob triggers at given time, it also contains the extensions to be triggered.
-Fetching extension data and creating cronjobs occur with long period of time in order to avoid heavy overhead.
-When a new extension trigger created, those data push into a \acrshort{redis} List.
+After retrieve extensions which is grouped by cronjob time; within the extension-handler, it schedules programmatic cronjobs to trigger at given times.
+When each cronjob triggers at the given time, it also contains the extensions to be triggered.
+Fetching extension data and creating cronjobs occur with a long period to avoid heavy overhead.
+When a new extension trigger created, those data push into a \acrshort{redis} list.
 Then pulling from the extension-handler in regular time intervals and create new cronjobs for mentioned cronjob time.
-As mentioned above, in order to avoid the expansion of the programmatic cronjob list which are created for new extension triggers, all cronjobs fetch again in long period of time and flush the previously scheduled cronjobs.
-The extension-handler should be run as a single entity for the atrocity, in order to avoid triggering same extension twice.
+As mentioned above, to avoid the expansion of the programmatic cronjob list which are created for new extension triggers, all cronjobs fetch again in a long period and flush the previously scheduled cronjobs.
+The extension-handler should be run as a single entity for the atrocity, to avoid triggering the same extension twice.

### 2020-02-15 method/sec_6-query.tex
Change all to \cref
Moved k8s to architectural decisions
Fixed:  workload
Grammarly Query

@@
 \section{Query Timeseries}
+\label{se:query}
 
-As described in Section \ref{subse:mongodb}, adapter-query is primarily using for support Geo-spatial queries.
+As described in \cref{subse:mongodb}, adapter-query is primarily using to support Geospatial queries.
 Other than that, as the primary service for searching for timeseries, it also supports for retrieval of timeseries metadata for external queries as well.
@@
 \begin{itemize}
-    \item moduleId(Optional), e.g., HEC-HMS
-    \item valueType(Optional), e.g., Scalar
-    \item parameterId(Optional), e.g., O.Precipitation
-    \item locationId(Optional), e.g., wdias\_hanwella
-    \item timeseriesType(Optional), e.g., ExternalHistorical
-    \item timeStepId(Optional), e.g., each\_15\_min
+    \item \texttt{moduleId} (Optional), e.g., HEC-HMS
+    \item \texttt{valueType} (Optional), e.g., Scalar
+    \item \texttt{parameterId} (Optional), e.g., O.Precipitation
+    \item \texttt{locationId} (Optional), e.g., wdias\_hanwella
+    \item \texttt{timeseriesType} (Optional), e.g., ExternalHistorical
+    \item \texttt{timeStepId} (Optional), e.g., each\_15\_min
 \end{itemize}
@@
 
-\paragraph{Query Locations within Area}-- Using following API endpoint, it is possible to query the locations which are exists within the area provided by the geoJson data in the JSON payload.
+\paragraph{Query Locations within Area}-- Using the following API endpoint, it is possible to query the locations which exist within the area provided by the GeoJson data in the JSON payload.
 \begin{lstlisting}
@@
 paragraph{Query parameters in Locations}-- Using the following API endpoint, it is possible to query the parameters stored against given locations.
-Location IDs should be provide as list of JSON payload.
+Location IDs should be provided as a list of JSON payload.
 \begin{lstlisting}

### 2020-02-16 results/sec_0-introduction.tex
Grammaly test plan

@@
 
-This chapter includes performance study of the \acrshort{wdias}. In \cref{se:test_plan} describes the planned method of testing the system.
+This chapter includes the performance study of the \acrshort{wdias}. \cref{se:test_plan} describes the planned method of testing the system.
 In the next \cref{se:workload} describes the logic behind creating the workload to do the performance testing planned in \cref{se:test_plan}.
-Following \cref{se:observations} includes the results observed while performance study. And summarised the observations in the next \cref{se:discussion}.
+\cref{se:observations} includes the results observed while performance study. And summarised the observations in the next \cref{se:discussion}.

### 2020-02-16 results/sec_1-test_plan.tex
Grammaly test plan

@@
 
-In \cref{subse:modules_weather_data_integration_sys} \hl{we discussed three modules of a weather data system such as integration, assimilation and dissemination.
-Each of those modules are mapped and handled in the WDIAS as below.}
+In \cref{subse:modules_weather_data_integration_sys} \hl{we discussed three modules of a weather data system such as integration, assimilation, and dissemination.
+Each of those modules is mapped and handled in the WDIAS as below.}
 \begin{enumerate}
@@
 Other than above, \emph{adapter modules} act as the core modules and the base of the system.
-Also, query modules allow the users to query for the timeseries based on the metadata, and enable performing Geo based queries based on the locations.
+Also, query modules allow the users to query for the timeseries based on the metadata and enable performing Geo-based queries based on the locations.
 
-The test plan is to perform the load test on each above module as separate entity in order to analyse the individual module scalability.
-Then perform load testing on whole system, and analyse the scalability in the system. There are two variables that can vary while doing the performance testing.
+The test plan is to perform the load test on each above module as a separate entity to analyze the individual module scalability.
+Then perform load testing on the whole system, and analyze the scalability in the system. Two variables can vary while doing performance testing.
 \begin{enumerate}
@@
 \begin{itemize}
-    \item A weather station may send current water level in a regular period of 1 minute. In such case, it always comes as a request with one data point with higher frequency.
-    \item Due to resource issue such as batteries, a weather station can collect data points for a given period of time and send as a batch. Another example would be,
-A weather station can collect the precipitation at each 5 minute period and send all the data in 1 hour intervals.
-    \item The forecast precipitation data from \acrshort{wrf} model can be extract for a day in one hour interval and store in the system.
+    \item A weather station may send the current water level in a regular period of 1 minute. In such a case, it always comes as a request with one data point with higher frequency.
+    \item Due to resource issue such as batteries, a weather station can collect data points for a given period and send as a batch. Another example would be,
+A weather station can collect the precipitation at each 5 minute period and send all the data in 1-hour intervals.
+    \item The forecast precipitation data from the \acrshort{wrf} model can be extracted for a day in a one-hour interval and store in the system.
 \end{itemize}
 
-The percentage of each data type can be vary depend on the situation.
-But most of the applications collect many data from the weather stations in order to correct and validate the models data.
-These weather stations can send the data in different frequencies with different parameters such as precipitation, temperature, humidity, wind direction etc.
+The percentage of each data type can be varied depending on the situation.
+But most of the applications collect much data from the weather stations to correct and validate the models' data.
+These weather stations can send the data in different frequencies with different parameters such as precipitation, temperature, humidity, wind direction, etc.
 Most of these are scalar data.
 Parameters such as wind direct are vector data which has less percentage compared to scalar data.
-On other side, most of the grid data generate from models and simulations.
-Those produce in less frequency due to cost of the computer resource to produce results.
+On the other side, most of the grid data generate from models and simulations.
+Those produce in less frequency due to the cost of the computer resource to produce results.
 After considering those factor we came up with 70\% scalar, 20\% vector, and 10\% grid values.
@@
 
-As a upper limit of such scenarios while designing the performance testing, it uses following;
+As an upper limit of such scenarios while designing the performance testing, it uses the following;
 \begin{itemize}
@@
 
-\cref{fi:performance_study_load} show the summary of this section, load testing plan with changing the request size and perform load testing with increasing the \acrshort{rps} over the time.
+\cref{fi:performance_study_load} shows the summary of this section, load testing plan with changing the request size and perform load testing with increasing the \acrshort{rps} over time.
 As shown in the figure, for a given request size the \acrshort{rps} increased in steps.
-In each step, the \acrshort{rps} hold for a moment in order to give some time for the system to get stabilize.
+In each step, the \acrshort{rps} holds for a moment to give some time for the system to get stabilized.
 Thus at each milestone, we can measure the performance of the system and study the stability of the system.
-After it come to the peak time, the \acrshort{rps} holds for more time than the previous milestones.
+After it comes to the peak time, the \acrshort{rps} holds for more time than the previous milestones.
 During the \acrshort{wdias} load testing, we are planning to have a peak of 18,000 requests per minute.
-Holding the peak load will help to show that whether system is capable of scaling more than proposed load testing plan.
-After the peak, test case goes through a cool down period in order to measure the ability of shrink down the resources when there is not any load on the system.
+Holding the peak load will help to show whether the system is capable of scaling more than the proposed load testing plan.
+After the peak, the test case goes through a cool-down period to measure the ability to shrink down the resources when there is not any load on the system.
 
@@
     \begin{itemize}
-        \item Plan for 30 minutes of test run with the request size of 1hr (60min) data.
-        \item Plan for 30 minutes of test run with the request size of 30min data.
-        \item Plan for 30 minutes of test run with the request size of 15min data.
-        \item Plan for 30 minutes of test run with the request size of 15min data with Auto Scaling.
-        \item All test plan run against 60min, 30min and 15min request size of data. Another test plan run with enabling the Auto Scaling. (total 2 hours)
+        \item Plan for 30 minutes of the test run with the request size of 1hr (60min) data.
+        \item Plan for 30 minutes of the test run with the request size of 30min data.
+        \item Plan for 30 minutes of the test run with the request size of 15min data.
+        \item Plan for 30 minutes of the test run with the request size of 15min data with Auto Scaling.
+        \item All test plan run against 60min, 30min and 15min request size of data. Another test plan runs with enabling the Auto Scaling. (total of 2 hours)
     \end{itemize}
@@
 \label{subse:test_plan_metrics}
-During the performance analysis, following metrics are use to measure the performance of the system.
+During the performance analysis, the following metrics are used to measure the performance of the system.
 \begin{itemize}
-    \item \emph{Throughput} -- Number of requests that can be process per unit time. Normally for \acrshort{wdias} performance observations, it uses \acrfull{rps} in order to measure the throughput.
-    \item \emph{Latency} -- Time taken for response back to the sent request to the system.
+    \item \emph{Throughput} -- Number of requests that can processed per unit time. Normally for \acrshort{wdias} performance observations, it uses \acrfull{rps} to measure the throughput.
+    \item \emph{Latency} -- Time is taken to respond to the sent request to the system.
 Normally it measures with milliseconds (ms) in the \acrshort{wdias}.
@@
 So, if the deviation value is low compared to the mean value, it will indicate that the measures are not dispersed (or mostly close to the mean value) and that the mean value is significant.
-Other than that, it measure the response time into 90\% percentile, while gives best response time up to 90\% percent of the responses.
-    \item \emph{Resource utilization} -- Resource Utilization is calculated based on the CPU and Memory usage via \acrshort{k8s} metrics server.
-It calculates the resource utilization over 60 seconds of time window.
+Other than that, it measures the response time into 90\% percentile, while gives the best response time up to 90\% percent of the responses.
+    \item \emph{Resource utilization} -- Resource Utilization is calculated based on the CPU and Memory usage via the \acrshort{k8s} metrics server.
+It calculates the resource utilization over 60 seconds time window.
 Network usage is getting based on the actual physical machines.
-    \item \emph{Auto scaling} -- The \acrshort{wdias} is running with two configurations.
-First is, since it is running the microservice as docker containers, it allow to increase or shrink the resource usage and share the resources within a physical machine.
-Second is, running with auto scaling enabled for the microservice which are using higher resources.
+    \item \emph{Auto-scaling} -- The \acrshort{wdias} is running with two configurations.
+First is, since it is running the microservice as docker containers, it allows to increase or shrink the resource usage and share the resources within a physical machine.
+Second is, running with auto-scaling enabled for the microservice which are using higher resources.
 \end{itemize}

### 2020-02-16 results/sec_2-workload.tex
Grammarly workload

@@
 
-As explained in Chapter \ref{ch:method}, timeseries has six primary attributes. In order to create a timeseries for performance testing, it needs data for each key attribute.
+As explained in Chapter \ref{ch:method}, timeseries has six primary attributes. To create a timeseries for performance testing, it needs data for each key attribute.
 While generating the timeseries for performance testing, it selected locations all over the world as a generic case to include all the locations without binding to a specific area.
@@
 These locations are taken from Google's Countries Public Data set \cite{GoogleGoogleCounties}, and consider static though out the testing, and data added to the wdias-performance-test.
-During the performance test, it creates 1000 timeseries and keep adding data against those timeseries.
-For each location, it creates four timeseries \hl{as a combination four values of moduleId key attribute}.
-Thus combining all together, those creates 1000 timeseries.
+During the performance test, it creates 1000 timeseries and keeps adding data against those timeseries.
+For each location, it creates four timeseries \hl{as a combination of four values of moduleId key attribute}.
+Thus combining all together, those create 1000 timeseries.
 But test cases generate these values before starts the performance tests, and able to increase the timeseries as wanted.
 
-For grid data, it uses static 100 grid locations which based on how is \acrshort{api} exposed.
-Since grid locations have different metadata structure as described in \cref{se:db_struct}, those data handle separately.
-But the locationId of grid and scalar data types have the same effect when define a timeseries.
+For grid data, it uses static 100 grid locations based on how is \acrshort{api} exposed.
+Since grid locations have different metadata structures as described in \cref{se:db_struct}, those data handle separately.
+But the locationId of grid and scalar data types have the same effect when defining a timeseries.
 
-In the \acrshort{jmeter} Best Practices, \say{If your test needs large amounts of data - particularly if it needs to be \emph{randomised} create the test data in a file that can be read with CSV Data set.
-This avoids wasting resources at run-time.
-jmeter best practices lean\_mean}.
-Rather providing the randomness in run time, the timeseries stored with the random order which satisfy the percentage of 70\% Scalar, 20\% Vector and 10\% Grid as mentioned in \cref{se:test_plan}.
-Before running the test cases, it generate the metadata for timeseries and write into a CSV file which is shared among the threads in the \acrshort{jmeter}.
+In the \acrshort{jmeter} Best Practices, \say{If your test needs large amounts of data - particularly if it needs to be \emph{randomized} create the test data in a file that can be read with CSV Data set.
+This avoids wasting resources at run-time}.
+Rather providing the randomness in run time, the timeseries stored with the random order which satisfy the percentage of 70\% Scalar, 20\% Vector, and 10\% Grid as mentioned in \cref{se:test_plan}.
+Before running the test cases, it generates the metadata for timeseries and writes into a CSV file which is shared among the threads in the \acrshort{jmeter}.
 This occurs in the setup phase of the test cases.
-The metadata CSV file arrange in a way that within each 10 lines, 7 lines are Scalar timeseries, 2 lines are Vector timeseries, and 1 line is a Grid timeseries.
+The metadata CSV file arrange in a way that within every 10 lines, 7 lines are Scalar timeseries, 2 lines are Vector timeseries, and 1 line is a Grid timeseries.
 
 The system is capable of storing any numeric value up to 3 decimal points.
-It does not make any different based on the parameter type whether it is the precipitation or the temperature.
+It does not make any difference based on the parameter type whether it is the precipitation or the temperature.
 Thus during the performance testing, \acrshort{jmeter} uses real precipitation data from \acrshort{curw}.
-One month period of data for five weather stations have been using for prepare the test data.
-The script to cleanup and prepare the precipitation data is available as \emph{setup\_precipitation.sh} in wdias-performance.
+One month period of data for five weather stations has been using to prepare the test data.
+The script to clean up and prepare the precipitation data is available as \emph{setup\_precipitation.sh} in wdias-performance.
 
@@
 \end{lstlisting}
-When preparing the data, it create three set of data based on the time interval such as hourly (60min), 30min, and 15min data with modifying the replicated data.
+When preparing the data, it creates three sets of data based on the time interval such as hourly (60min), 30min, and 15min data with modifying the replicated data.
 This will reduce the overhead in performance testing and increase the performance itself.
-Extract function use while creating the containers, and extract the data into the container. This reduce the context loading while creating the container images.
-While performing the load testing, \acrshort{jmeter} keep update a date counter, and create over the one month data.
-At the end of current month, the date counter advance to the next month.
-But data is repeat using from the beginning.
-In order to provide more randomness, it switch over five locations as well.
-The JSR223 scripts were written in a generic way such that is possible to tweak and use if there are more location data available.
+Extract function use while creating the containers, and extract the data into the container. This reduces the context loading while creating the container images.
+While performing the load testing, \acrshort{jmeter} keeps update a date counter and creates over the one-month data.
+At the end of the current month, the date counter advance to the next month.
+But data is repeated using from the beginning.
+To provide more randomness, it switches over five locations as well.
+The JSR223 scripts were written generically such that is possible to tweak and use if there are more location data available.
 
-Almost similar to how was the precipitation data proceed, the water level are prepared for Grid data.
-One exception with Grid data during this test cases was, the maximum time step is 30min, instead of 15min due to larger size of the data.
+Almost similar to how was the precipitation data proceed, the water level is prepared for Grid data.
+One exception with Grid data during these test cases was, the maximum time step is 30min, instead of 15min due to the larger size of the data.
 But the \acrshort{wdias} is capable of supporting such request.
-The main purpose of the \acrshort{wdias} is to provide a extensible architecture framework, during the performance testing it is not much consider about scaling the Grid data handling as it using \acrshort{netCDF}, and it is another domain with an attraction up to some extend.
+The main purpose of the \acrshort{wdias} is to provide an extensible architecture framework, during the performance testing it is not much considered about scaling the Grid data handling as it using \acrshort{netCDF}, and it is another domain with an attraction up to some extent.
 
@@
 \end{lstlisting}
-The water level also contains the real data for one month of period, and \emph{setup\_waterlevel.sh} script provide the functionality of prepare, cleanup and extract.
-Also it reset and repeat reading from the beginning when the \acrshort{jmeter} date counter keep increasing.
+The water level also contains the real data for one month of period and \emph{setup\_waterlevel.sh} script provides the functionality of preparation, cleanup, and extract.
+Also, it reset and repeat reading from the beginning when the \acrshort{jmeter} date counter keeps increasing.
 
@@
 \subsection{Experimental Setup}
-In order to create higher workload using the \acrshort{jmeter}, it has Distributed Testing feature.
-It uses the master slave approach and it allowed to handle all the test cases via single instance, rather handling separate instances.
-But it has following limitation;
-The same test plan runs by all the servers.
-JMeter does not distribute the load between servers, each runs the full test plan.
-So if you set 1,000 threads and have 6 JMeter server, you end up injecting 6,000 threads.
-When test cases runs with \acrshort{jmeter} Distributed mode, the server node trigger same copy of test case on configured slave nodes parallel.
-At the end of the test cases, it gather results into the master node.
+\label{subse:experimental_setup}
+
+To create a higher workload using the \acrshort{jmeter}, it has a Distributed Testing feature.
+It uses the master-slave approach and it allowed to handle all the test cases via single instance, rather handling separate instances.
+But it has the following limitation of \emph{the same test plan runs by all the servers}.
+\acrshort{jmeter} does not distribute the load between servers, each runs the full test plan.
+So if you set 1,000 threads and have 6 \acrshort{jmeter} servers, you end up injecting 6,000 threads.
+When test cases run with \acrshort{jmeter} Distributed mode, the server node trigger the same copy of the test case on configured slave nodes parallel.
+At the end of the test cases, it gathers results into the master node.
 
@@
 The root component of a test create is a thread group.
-There are different kind of thread groups are available such as thread group (basic thread group), arrivals thread Group, free form arrivals thread group, stepping thread group, concurrency thread group, and ultimate thread group.
+There are different kinds of thread groups are available such as thread group (basic thread group), arrivals thread Group, free form arrivals thread group, stepping thread group, concurrency thread group, and ultimate thread group.
 
@@
 \begin{itemize}
-    \item \emph{closed system model} \cite{Haggett1998AnWales} a new request is only triggered by the completion of a previous request, following by a think time.
-System has negative feedback that makes it impossible to bury-out the service, so users wait for the responses before making new requests.
-    \item \emph{open system model} new requests arrival independently of completions, e.g.,according to a stochastic process or fixed trace. System has no negative feedback.
+    \item \emph{closed system model} \cite{Haggett1998AnWales} -- a new request is only triggered by the completion of a previous request, following by a think time.
+The system has negative feedback that makes it impossible to bury-out the service, so users wait for the responses before making new requests.
+    \item \emph{open system model} -- new requests arrival independently of completions, e.g., according to a stochastic process or fixed trace. The system has no negative feedback.
 \end{itemize}
-While implementing the test cases for \acrshort{wdias}, it uses Concurrency Thread Group with Throughput Shaping Timer because of it support the open workload approach.
-Using other thread groups, it required to find exact number of threads and timer delays that produce desired number of requests per second (RPS) to server.
-Which is known as the \emph{closed workload}.
-With using \emph{Throughput Shaping Timer}, it only need to configure the \acrfull{rps}.
-When combine this \acrshort{jmeter} plugin with Concurrency Thread Group using Schedule Feedback Function to dynamically maintain thread count required to achieve target RPS \cite{KarunarathneGihanWdias/wdias-performance-test:JMeter.}.
+While implementing the test cases for \acrshort{wdias}, it uses the Concurrency Thread Group with Throughput Shaping Timer because it supports the open workload approach.
+Using other thread groups, it required to find the exact number of threads and timer delays that produce the desired number of \acrfull{rps} to server. It is known as the \emph{closed workload}.
+With using \emph{Throughput Shaping Timer}, it only needs to configure the \acrshort{rps}.
+When combining this \acrshort{jmeter} plugin with Concurrency Thread Group using Schedule Feedback Function to dynamically maintain thread count required to achieve target \acrshort{rps} \cite{KarunarathneGihanWdias/wdias-performance-test:JMeter.}.
 
@@
 
-In the \cref{fi:test_prod_throughtput_shaping_timer} shows the throughput shaping timer configurations use while load testing.
+\cref{fi:test_prod_throughtput_shaping_timer} shows the throughput shaping timer configurations use while load testing.
 The configurations as similar to the load test plan described in \cref{se:test_plan}.
-In order to get maximum peak of 18,000 request per minutes, which is equivalent to 300 \acrshort{rps} is setup according the the figure.
+To get the maximum peak of 18,000 request per minutes, which is equivalent to 300 \acrshort{rps} is setup according the the figure.
 
@@
 
-In the first step of the plan consist of setting up the timeseries metadata.
-At the same time, it creates the timeseries entry in the \acrshort{wdias} system as well as shown in following list of test steps and configurations.
+The first step of the plan consists of setting up the timeseries metadata.
+At the same time, it creates the timeseries entry in the \acrshort{wdias} system as well as shown in the following list of test steps and configurations.
 
@@
 By creating the timeseries before help to reduce the overhead during the performance testing, and cause to more accurate \acrshort{rps} at the run time.
-Otherwise \acrshort{jmeter} need to allocate another set of threads for timeseries creation.
-Since the test cases insert data again set of timeseries, most of the time it about retrieving the timeseries metadata, rather creation a new timeseries in the \acrshort{wdias} system.
+Otherwise, \acrshort{jmeter} needs to allocate another set of threads for timeseries creation.
+Since the test cases insert data again set of timeseries, most of the time it about retrieving the timeseries metadata, rather than creating new timeseries in the \acrshort{wdias} system.
 
-Following list shows the test steps of \acrshort{jmeter} while performing the load testing and the configurations.
+The following list shows the test steps of \acrshort{jmeter} while performing the load testing and the configurations.
 
@@
 
-As mentioned in \cref{se:test_plan} \hl{, we planned to perform another test scenario on query timeseries module.
-During this test scenario, we use following test steps in order to cover most of the timeseries metadata search queries and Geo queries which are defined in the} \cref{se:query}.
+As mentioned in \cref{se:test_plan}\hl{, we planned to perform another test scenario on the query timeseries module.
+During this test scenario, we use the following test steps to cover most of the timeseries metadata search queries and Geo queries which are defined in the} \cref{se:query}.
 
@@
 
-With the above \acrshort{jmeter} test case setup, it need to enable each test case separately and before running via the command line in the server.
-To do it in much efficient way, a scripting tool has implemented, and accessible with the code base \cite{KarunarathneWdias-performance-test/TEST_PLAN.md:Plan} as \emph{test-dev}.
+With the above \acrshort{jmeter} test case setup, it needs to enable each test case separately and before running via the command line in the server.
+To do it in a much efficient way, a scripting tool has implemented, and accessible with the codebase \cite{KarunarathneWdias-performance-test/TEST_PLAN.md:Plan} as \emph{test-dev}.
 
@@
 
-As per the usage description of test-dev, it has the features of enable a test case, disable a test case, and run the test case while enabled.
-Another wrapper was implemented around the test-dev as \emph{test-plan.sh} which is also available with the code base \cite{KarunarathneWdias-performance-test/TEST_PLAN.md:Plan}.
+As per the usage description of test-dev, it has the features of enabling a test case, disable a test case, and run the test case while enabled.
+Another wrapper was implemented around the test-dev as \emph{test-plan.sh} which is also available with the codebase \cite{KarunarathneWdias-performance-test/TEST_PLAN.md:Plan}.
 
@@
 
-It allows to run particular test plan which are described in \cref{se:test_plan}. Also possible to run the all the test plans in order with given \emph{REQ\_SIZE} or for all the \emph{REQ\_SIZE}.
+It allows running a particular test plan which is described in \cref{se:test_plan}. Also possible to run all the test plans in order with given \emph{REQ\_SIZE} or for all the \emph{REQ\_SIZE}.
 
@@
 \label{subse:test_sys_config}
-As described in the \cref{se:microservice}, the \acrshort{wdias} is mainly focus on microservice architecture and implemented on top of kubernetes.
+As described in the \cref{se:microservice}, the \acrshort{wdias} is mainly focused on microservice architecture and implemented on top of Kubernetes.
 \acrfull{k8s} is an open-source system for automating deployment, scaling, and management of containerized applications.
@@
 \acrshort{k8s} is a planet scaling tool \cite{LinuxFoundationProduction-GradeKubernetes}, and users can tweak the configuration to run the \acrshort{wdias} as per the required level of load on the system.
-During the performance test of the \acrshort{wdias}, it uses maximum of 300 \acrshort{rps} with providing to the system with increasing load, and monitor the auto scalability of the system with measuring other performance parameters mentioned in \cref{tab:aws_eks_nodes}.
+During the performance test of the \acrshort{wdias}, it uses a maximum of 300 \acrshort{rps} with providing to the system with increasing load, and monitor the auto scalability of the system with measuring other performance parameters mentioned in \cref{tab:aws_eks_nodes}.
 
@@
 
-The \acrshort{wdias} uses the Helm \cite{CNCFHelmDocs} which is a package manager for \acrshort{k8s}.
-Each microservice within the system deploy and maintain as a helm chart, and the Helm Charts \cite{KarunarathneWdias-helm-charts:Deployments} can be found within the code base.
+The \acrshort{wdias} uses Helm \cite{CNCFHelmDocs} which is a package manager for \acrshort{k8s}.
+Each microservice within the system deploys and maintains as a helm chart, and the Helm Charts \cite{KarunarathneWdias-helm-charts:Deployments} can be found within the codebase.
 For the databases, it uses the official helm charts.
@@
     \item \emph{nodeSelector} -- Hard rules match for node schedule. If not match, pods will not schedule.
-    \item \emph{node Affinity and Anti-Affinity} -- Soft rules for node schedule. Based on the rules, pods will schedule on most appropriate node.
+    \item \emph{node Affinity and Anti-Affinity} -- Soft rules for node schedule. Based on the rules, pods will schedule on the most appropriate node.
     \item \emph{Taints and Tolerations} -- Opposite of nodeSelector, repel mismatching pods away from the nodes.
@@
 
-Users can use one of above features to fine-tune the \acrshort{wdias} to perform better.
-For the moment, \acrshort{wdias} helm charts uses node Affinity in order to use the same charts within local setup with one node and work the same charts on a \acrshort{k8s} cluster with multiple nodes.
+Users can use one of the above features to fine-tune the \acrshort{wdias} to perform better.
+For the moment, \acrshort{wdias} helm charts use node Affinity to use the same charts within local setup with one node and work the same charts on a \acrshort{k8s} cluster with multiple nodes.
 Pods are assigned to the nodes \cref{tab:aws_eks_nodes} based on the node label as below;
@@
     \item \emph{scalar} -- scalar and vector adapters, import and export of same data types
-    \item \emph{test} -- jMeter and metric server
+    \item \emph{test} -- \acrshort{jmeter} and metric server
 \end{itemize}
-\cref{fi:eks_node_setup} show the overview of show the nodes are setup and each microservices are assigned to each node, the connectivity of the nodes, and the data interactions via the arrows.
-The databases uses for data consistency and performance in storage optimization with search capabilities.
+\cref{fi:eks_node_setup} shows the overview of the show the nodes are setup and each microservices are assigned to each node, the connectivity of the nodes, and the data interactions via the arrows.
+The databases used for data consistency and performance in storage optimization with search capabilities.
 But because of that, it only possible to run one instance of those.
-In the \acrshort{wdias}, the MySQL and MongoDb are not getting higher load as adapter databases such as InfluxDB for scalar and vector data types, and netCDF for grid data type.
-In order to keep up with the pace, those microservice pods are assign to dedicated nodes in order to increase the performance of inter-service communication.
+In the \acrshort{wdias}, the MySQL and MongoDB are not getting higher load as adapter databases such as InfluxDB for scalar and vector data types, and netCDF for the grid data type.
+To keep up with the pace, those microservice pods are assigned to dedicated nodes to increase the performance of inter-service communication.

### 2020-02-16 results/sec_3-observations.tex
Fixed:  workload
Change observations to Performance Evaluation
Grammarly obs - change fig

--- 2020-02-14 results/sec_3-observations.tex
@@
-\section{\hl{Observations}}
+\section{\hl{Performance Evaluation}}
+\label{se:observations}
 
-According the \cref{se:test_plan} section, this section includes the observations after performing the test plans on the \acrshort{wdias} system setup and test plan test up which is explained in the \cref{se:workload}.
+According to \cref{se:test_plan} section, this section includes the observations after performing the test plans on the \acrshort{wdias} system setup and test plan test up which is explained in \cref{se:workload}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Load Testing with hourly data (\db{Request size = 24})}
+\subsection{Load Testing with hourly data}
 \label{subse:obs_test_plan_all_60min}
@@
 On average it takes 28ms to insert data into the \acrshort{wdias}, and up to 90\% percentile inserted data within 31ms.
-Noticeably it has 0\% of errors which means that all the request are completed successfully.
+Noticeably it has 0\% of errors which means that all the requests are completed successfully.
 On average, \acrshort{wdias} handled 40.5 \acrshort{rps} with the given workload.
-The performance of the Retrieve of Scalar and Vector Timeseries are similar to insert timeseries due to it depends on it.
-On the other hand, Insert Grid Timeseries data perform with 23ms with almost all the request perform within same amount of time, hence the standard deviation is smaller.
-Retrieve Grid Timeseries data perform the same but with bit higher value of latency of 68ms.
-Both of insert and retrieve grid timeseries data have 4.5 \acrshort{rps} since it only get 10\% of the number of request per given time via the test plan as explain in the data ration in \cref{se:test_plan}.
+The performance of the Retrieve of Scalar and Vector Timeseries is similar to insert timeseries due to it depends on it.
+On the other hand, Insert Grid Timeseries data perform with 23ms with almost all the requests perform within the same amount of time, hence the standard deviation is smaller.
+Retrieve Grid Timeseries data perform the same but with a bit higher value of latency of 68ms.
+Both insert and retrieve grid timeseries data have 4.5 \acrshort{rps} since it only gets 10\% of the number of requests per given time via the test plan as explained in the data ration in \cref{se:test_plan}.
 
@@
 \cref{fi:test_obs_all_60m_response_vs_threads} shows the response time against the number of active threads.
-As the graph show, the response time kept same while increasing the number of active threads against each test case.
-This shows the scalability of the \acrshort{wdias}, since the system able to process more requests without a significant change in the latency.
-When number of active threads increased more than 122, the \cref{fi:test_obs_all_60m_response_vs_threads} show uncertainty in the inserting and retrieving Scalar and Vector data.
+As the graph shows, the response time kept the same while increasing the number of active threads against each test case.
+This shows the scalability of the \acrshort{wdias} since the system able to process more requests without a significant change in the latency.
+When the number of active threads increased more than 122, \cref{fi:test_obs_all_60m_response_vs_threads} shows uncertainty in the inserting and retrieving Scalar and Vector data.
 
@@
 
-\cref{fi:test_obs_all_60m_latency} graph provides a better overview of the variation of latency over elapsed time of the test plan against number of server hits per second.
-The conclusion of giving static latency while increasing the number of requests in \cref{fi:test_obs_all_60m_response_vs_threads} can further prove with this graph, since \cref{fi:test_obs_all_60m_latency} graph gives in details overview over the test plan time span.
+\cref{fi:test_obs_all_60m_latency} graph provides a better overview of the variation of latency over the elapsed time of the test plan against the number of server hits per second.
+The conclusion of giving static latency while increasing the number of requests in \cref{fi:test_obs_all_60m_response_vs_threads} can further prove with this graph since \cref{fi:test_obs_all_60m_latency} graph gives in detail an overview of the test plan period.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Load Testing with 30min data (Request size = 48)}
+\subsection{Load Testing with 30min data}
 \label{subse:obs_test_plan_all_30min}
-This \cref{subse:obs_test_plan_all_30min} discussed about the All test plan performance with 30 minutes data which means 48 data points per each request in Scalar and Vector timeseries, and 48 ASCII grid files per each insert request.
-It performed round up to 311k of sample requests which is almost similar to \cref{subse:obs_test_plan_all_60min} processed samples.
+
+\cref{subse:obs_test_plan_all_30min} discussed the All test plan performance with 30 minutes data which means 48 data points per each request in Scalar and Vector timeseries, and 48 ASCII grid files per each insert request.
+It performed round up to 311k of sample requests which are almost similar to \cref{subse:obs_test_plan_all_60min} processed samples.
 
@@
 \end{table}
+
 \cref{tab:obs_all_30_min_summary} shows the response latency summary details and \acrshort{rps} as explained in \cref{subse:obs_test_plan_all_60min}.
 And the results are almost similar to the observations in \cref{tab:obs_all_60_min_summary}.
-This implies that, even the request size is increased, the \acrshort{wdias} can perform better same as the with smaller size of data.
+This implies that even the request size is increased, the \acrshort{wdias} can perform better the same as the with smaller size of data.
 
@@
 \end{figure}
-\cref{fi:test_obs_all_30m_response_vs_threads} show the response time against the number of active threads for 30min data.
-As the graph show, the response time kept same while increasing the number of active threads against each test case.
-This shows the scalability of the \acrshort{wdias}, since the system able to process more requests without a significant change in the latency.
-When number of active threads increased more than 110, the \cref{fi:test_obs_all_30m_response_vs_threads} show uncertainty in the inserting and retrieving Scalar and Vector data.
+
+\cref{fi:test_obs_all_30m_response_vs_threads} shows the response time against the number of active threads for 30min data.
+As the graph shows, the response time kept the same while increasing the number of active threads against each test case.
+This shows the scalability of the \acrshort{wdias} since the system able to process more requests without a significant change in the latency.
+When the number of active threads increased more than 110, \cref{fi:test_obs_all_30m_response_vs_threads} shows uncertainty in the inserting and retrieving Scalar and Vector data.
 This graph is similar to the \cref{fi:test_obs_all_60m_response_vs_threads}, but the active thread count goes down as a result of increasing the request size.
@@
 \end{figure}
-\cref{fi:test_obs_all_30m_latency} graph provides a better overview of the variation of latency over elapsed time of the test plan against number of server hits per second.
-This graph also conclude that, over the time latency does not change very much. But during the peak load, it shows some variation in insert and retrieve of Grid timeseries.
+\cref{fi:test_obs_all_30m_latency} graph provides a better overview of the variation of latency over the elapsed time of the test plan against the number of server hits per second.
+This graph also concludes that over time latency does not change very much.
+But during the peak load, it shows some variation in the insert and retrieves of Grid timeseries.
 When compared to \cref{fi:test_obs_all_60m_latency}, the latency for insert and retrieve Grid timeseries increase by some amount.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Load Testing with 15min data (96 Request Size)}
+\subsection{Load Testing with 15min data}
 \label{subse:obs_test_plan_all_15min}
-This \cref{subse:obs_test_plan_all_15min} discussed about the All test plan performance with 15 minutes data which means 96 data points per each request in Scalar and Vector timeseries, and 96 ASCII Grid files per each insert Grid timeseries request.
+
+\cref{subse:obs_test_plan_all_15min} discussed about the test plan performance with 15 minutes data which means 96 data points per each request in Scalar and Vector timeseries, and 96 ASCII Grid files per each insert Grid timeseries request.
 These requests are four times larger than the \cref{subse:obs_test_plan_all_60min} request size.
-It performed approximately 311k of sample requests which is almost similar to \cref{subse:obs_test_plan_all_30min} processed samples.
+It performed approximately 311k of sample requests which are almost similar to \cref{subse:obs_test_plan_all_30min} processed samples.
 \begin{table}[ht]
@@
 \end{table}
+
 \cref{tab:obs_all_15_min_summary} shows the response latency summary details and \acrshort{rps} as same as explained in \cref{subse:obs_test_plan_all_30min}.
 And the latency observations are increased by some amount when compared to the observations in \cref{tab:obs_all_30_min_summary}.
-Noticeably retrieving latency of all type of data types increased by considerable amount.
-Same following the trend, standard deviation of retrieve timeseries data increased my considerable amount for all the types.
-We can assume that more writing to the databases affected on reads as well.
+Noticeably retrieving latency of all types of data types increased by a considerable amount.
+The same following the trend, the standard deviation of retrieve timeseries data increased my considerable amount for all the types.
+We can assume that more writing to the databases affected reads as well.
 Event the request data size increased by 4x time, the \acrshort{wdias} were able to handle them without any significant performance issues.
-And the system able to provide the same throughput as \cref{tab:obs_all_30_min_summary}.
+And the system able to provide the same throughput as shown in \cref{tab:obs_all_30_min_summary}.
 
@@
 \end{figure}
-\cref{fi:test_obs_all_15m_response_vs_threads} show the response time against the number of active threads for 15min data.
-As the graph show, the response time kept same while increasing the number of active threads against each test case.
-When number of active threads increased more than 140, the \ref{fi:test_obs_all_15m_response_vs_threads} show uncertainty in the inserting and retrieving all data types.
+
+\cref{fi:test_obs_all_15m_response_vs_threads} shows the response time against the number of active threads for 15min data.
+As the graph shows, the response time kept the same while increasing the number of active threads against each test case.
+When the number of active threads increased more than 140, the \ref{fi:test_obs_all_15m_response_vs_threads} show uncertainty in the inserting and retrieving all data types.
 The latency of insert and retrieve Grid timeseries data goes up compared to \ref{fi:test_obs_all_30m_response_vs_threads}.
-With higher request size, it become to notice the latency also increase by a small factor when the number of active thread increased.
-This can clearly notice on with insert and retrieval of Grid timeseries data.
+With higher request size, it becomes to notice the latency also increase by a small factor when the number of active thread increased.
+This can notice on with insert and retrieval of Grid timeseries data.
 
@@
 \end{figure}
-\ref{fi:test_obs_all_15m_latency} graph provides a overview of the variation of latency over elapsed time of the test plan against number of server hits per second for 15min data.
-This graph show that over the time \acrshort{wdias} were able to keep the latency constant over the test plan. But at the peak time, it tend to vary from the mean value a lot.
-One noticeable fact is, throw out the test time period, it shows spikes in latency when compared to \ref{fi:test_obs_all_60m_latency} and \cref{fi:test_obs_all_30m_latency}.
+
+\cref{fi:test_obs_all_15m_latency} graph provides a overview of the variation of latency over elapsed time of the test plan against the number of server hits per second for 15min data.
+This graph shows that over time \acrshort{wdias} was able to keep the latency constant over the test plan. But at peak time, it tends to vary from the mean value a lot.
+One noticeable fact is, throughout the test period, it shows spikes in latency when compared to \cref{fi:test_obs_all_60m_latency} and \cref{fi:test_obs_all_30m_latency}.
 
@@
 \end{figure}
-\ref{fi:test_obs_all_15m_throughtput} shows the total server's transaction throughput against number of active threads.
+
+\ref{fi:test_obs_all_15m_throughtput} shows the total server's transaction throughput against the number of active threads.
 The formula for total server transaction throughput is \(<active threads> * 1 second / <1  thread response time>\) \cite{JMeterPluginsTransactionPlugin}.
-Basically, it shows the statistical maximum possible number of transactions based on number of users accessing the application.
-With combining the \ref{fi:test_obs_all_15m_latency}, this graph show that the throughput of the system get increased without much change in the latency, thus it proves the scalability of the \acrshort{wdias}.
+It shows the statistical maximum possible number of transactions based on the number of users accessing the application.
+By combining the \ref{fi:test_obs_all_15m_latency}, this graph shows that the throughput of the system gets increased without much change in the latency, thus it proves the scalability of the \acrshort{wdias}.
 
@@
 \ref{fi:test_obs_all_15m_latency_percentile} visually shows the summary of \cref{tab:obs_all_15_min_summary} latency up to 90\% percentile.
-With a higher request size data, the \acrshort{wdias} able to process the requests without significant change in latency up to 90\% percentile.
+With higher request size data, the \acrshort{wdias} able to process the requests without significant change in latency up to 90\% percentile.
 
@@
 \label{subse:obs_test_plan_all_auto_15min}
-This \cref{subse:obs_test_plan_all_auto_15min} discussed about the All test plan performance with 15 minutes data which means 96 data points per each request in Scalar and Vector timeseries, and 96 ASCII Grid files per each insert Grid timeseries request.
+
+This \cref{subse:obs_test_plan_all_auto_15min} discussed the test plan performance with 15 minutes data which means 96 data points per each request in Scalar and Vector timeseries, and 96 ASCII Grid files per each insert Grid timeseries request.
 These requests are four times larger than the \cref{subse:obs_test_plan_all_60min} request size.
-It performed approximately 311k of sample requests which is almost similar to \cref{subse:obs_test_plan_all_15min} processed samples.
-Other than that, this test plan runs with enabling \acrshort{k8s} Auto Scaling for the high resource utilized microservice as explained in the \cref{subse:test_plan_metrics}.
+It performed approximately 311k of sample requests which are almost similar to \cref{subse:obs_test_plan_all_15min} processed samples.
+Other than that, this test plan runs with enabling \acrshort{k8s} Auto-scaling for the high resource utilized microservice as explained in \cref{subse:test_plan_metrics}.
 With the test load used for the performance test, import-ascii-grid-upload microservice is using lots of CPU, and adapter-grid microservice is using lots of Memory.
 During this test plan, \acrshort{wdias} start with the auto scaling enabled for import-ascii-grid-upload microservice.
-Since adapter-grid is a consistence service for storing netCDF files, it is not possible to auto scale, since \acrshort{eks} does not support multiple read write support volumes \cite{LinuxFoundationPersistentKubernetes}.
+Since adapter-grid is a consistent service for storing netCDF files, it is not possible to auto scale, since \acrshort{eks} does not support multiple reads writes support volumes \cite{LinuxFoundationPersistentKubernetes}.
 
@@
 \end{table}
+
 \cref{tab:obs_all_auto_15_min_summary} shows the response latency summary details and \acrshort{rps} as same as explained in \cref{subse:obs_test_plan_all_15min}.
 During this test plan.
-the main focus on the auto scaling enabled microservice.
+the main focus on the auto-scaling enabled microservice.
 As per the insert grid latency in the \cref{tab:obs_all_auto_15_min_summary}, the average insert latency is reduced from 91ms to 87ms.
-Also error percentage reduced from 1.42\% to 0.18\%.
+Also, the error percentage reduced from 1.42\% to 0.18\%.
 Standard deviation reduced from 19.58 to 14.07 which means the latency is much closer to the average latency.
-These improvements in insert Grid timeseries data seems to affect on out put of retrieve Grid timeseries data as well.
+These improvements in insert Grid timeseries data seem to affect on output of retrieve Grid timeseries data as well.
 
@@
 \end{figure}
-\ref{fi:test_obs_all_auto_15m_latency} graph provides an overview of the variation of latency over elapsed time of the test plan against number of server hits per second for 15min data while auto scaling enabled for \acrshort{k8s}.
+\ref{fi:test_obs_all_auto_15m_latency} graph provides an overview of the variation of latency over the elapsed time of the test plan against the number of server hits per second for 15min data while auto-scaling enabled for \acrshort{k8s}.
 This graph show that over the time \acrshort{wdias} were able to keep the latency constant over the test plan.
-When compared to \ref{fi:test_obs_all_15m_latency}, throw out the test time period, the latency spikes become less.
+When compared to \ref{fi:test_obs_all_15m_latency}, throughout the test period, the latency spikes become less.
 
@@
 \end{figure}
+
 \ref{fi:test_obs_all_auto_15m_throughtput} shows the total server's transaction throughput against number of active threads.
-When compared to \ref{fi:test_obs_all_15m_throughtput}, estimated throughput with higher number of active threads become stable at the graph.
-Which means enabling auto scaling improve the throughput with higher number of active users as well.
+When compared to \ref{fi:test_obs_all_15m_throughtput}, the estimated throughput with a higher number of active threads become stable at the graph.
+This means enabling auto-scaling also improves the throughput with a higher number of active users as well.
 
-Following charts show the resource usage while running the all test plan while enabling the auto scaling.
+The following charts show the resource usage while running the all test plan while enabling the auto-scaling.
 \begin{figure}[htp]
@@
 \end{figure}
-\ref{fi:obs_all_auto_15m_import_export_res} show the CPU usage and Memory usage for import timeseries modules and export timeseries modules.
-The CPU usage shown with milli CPUs \cite{LinuxFoundationManagingKubernetes} (1 CPU = 1000m CPUs) and the Memory usage shown with Megabytes (Mi) \cite{LinuxFoundationManagingKubernetes}.
+
+\ref{fi:obs_all_auto_15m_import_export_res} shows the CPU usage and Memory usage for import timeseries modules and export timeseries modules.
+The CPU usage is shown with milli CPUs \cite{LinuxFoundationManagingKubernetes} (1 CPU = 1000m CPUs) and the Memory usage shown with Megabytes (Mi) \cite{LinuxFoundationManagingKubernetes}.
 Noticeable, the import-ascii-grid-upload microservice used around 10 CPUs at the peak time while using 3.6 Gb of Memory.
-Another important fact is, after the test cases finished, the \acrshort{wdias} cool down the system via \acrshort{k8s} auto scaling and release the resources.
+Another important fact is, after the test cases finished, the \acrshort{wdias} cool down the system via \acrshort{k8s} auto-scaling and release the resources.
 This clearly shows the elasticity of the \acrshort{wdias} according to the workload.

### 2020-02-16 Paper.tex
change API with texttt
cref tables and auto-scaling

@@
 Also the inbuilt extension module system allow users to add new features.
-The open source tools that are using for \acrshort{wdias} allows to run on Cloud Computing platforms without much hassle with the auto scaling feature allow to run \acrshort{wdias} from 1 CPU node to nodes with few hundred CPUs.
+The open source tools that are using for \acrshort{wdias} allows to run on Cloud Computing platforms without much hassle with the auto-scaling feature allow to run \acrshort{wdias} from 1 CPU node to nodes with few hundred CPUs.
 The paper describes the initial design goals, evolve over few architectures to get desired performance, and explains how the system in way to achieve scalability.
@@
 \centerline{\includegraphics[width=0.5\textwidth]{results/obs/all_auto/obs_all_auto_15m_res_latencies_against_hits.png}}
-\caption{Performance test 15min data enabled auto scaling - response latencies against server hits over the elapsed time.}
+\caption{Performance test 15min data enabled auto-scaling - response latencies against server hits over the elapsed time.}
 \label{fi:test_obs_auto_all_15_min_latency_vs_hits}
@@
 \centerline{\includegraphics[width=0.5\textwidth]{results/obs/all_auto/obs_all_auto_15m_transaction_throughtput_vs_threads.png}}
-\caption{Performance test 15min data enabled auto scaling - transnational throughput vs number of active threads.}
+\caption{Performance test 15min data enabled auto-scaling - transnational throughput vs number of active threads.}
 \label{fi:test_obs_auto_all_15_min_throughput_vs_threads}
@@
 The latency for each operation type kept constant over the whole test plan run time without any significant change.
-When the request size increased from 24 data points to 96 data points, the latency increase throw out the whole test plan with a smaller number.
+When the request size increased from 24 data points to 96 data points, the latency increase throughout the whole test plan with a smaller number.
 But for each test run the latency kept constant over the time.
@@
 \paragraph{Auto Scaling}
-The \acrshort{wdias} supports auto scaling by out of the box with \acrshort{k8s}.
+The \acrshort{wdias} supports auto-scaling by out of the box with \acrshort{k8s}.
 Services can configure with maximum number of pods in order to avoid over resource usage.
@@
 If the usage of \acrshort{wdias} want to reduce the risk of unable to process data, then system can configure to run with redundant pods in order to handle spike of workloads.
-Also while configure for the auto scaling, the \acrshort{k8s} can configure to maintain lower amount of CPU usage such as 50\% to 60\% rather 80\%.
+Also while configure for the auto-scaling, the \acrshort{k8s} can configure to maintain lower amount of CPU usage such as 50\% to 60\% rather 80\%.
 Such configuration with always spawn new pods to handle double of current peak load.
@@
 During the performance test plans, the system were able to provide constant throughput by keeping the latency constant while increasing the workload. Which exhibit the scalability of the system.
-With the \acrshort{k8s} auto scaling, the \acrshort{wdias} were able to elastically adjust the number of pods according to the workload with the given configurations.
+With the \acrshort{k8s} auto-scaling, the \acrshort{wdias} were able to elastically adjust the number of pods according to the workload with the given configurations.
 

### 2020-02-16 results/sec_1-test_plan.tex
cref tables and auto-scaling

@@
         \item Plan for 30 minutes of the test run with the request size of 15min data.
-        \item Plan for 30 minutes of the test run with the request size of 15min data with Auto Scaling.
-        \item All test plan run against 60min, 30min and 15min request size of data. Another test plan runs with enabling the Auto Scaling. (total of 2 hours)
+        \item Plan for 30 minutes of the test run with the request size of 15min data with auto-scaling.
+        \item All test plan run against 60min, 30min and 15min request size of data. Another test plan runs with enabling the auto-scaling. (total of 2 hours)
     \end{itemize}

### 2020-02-16 results/sec_3-observations.tex
cref tables and auto-scaling

@@
 Sections \ref{subse:obs_test_plan_all_60min} to \ref{subse:obs_test_plan_all_auto_15min} discuss the observations collected with performing the Load test plans over 60 minutes (24 data points), 30 minutes (48 data points) and 15 minutes (96 data points) by variate the request size.
-Then another performance test with enabling Auto Scaling as explained in \cref{subse:test_plan_metrics} for high resource utilized microservice.
+Then another performance test with enabling auto-scaling as explained in \cref{subse:test_plan_metrics} for high resource utilized microservice.
 
@@
 As the graph shows, the response time kept the same while increasing the number of active threads against each test case.
-When the number of active threads increased more than 140, the \ref{fi:test_obs_all_15m_response_vs_threads} show uncertainty in the inserting and retrieving all data types.
-The latency of insert and retrieve Grid timeseries data goes up compared to \ref{fi:test_obs_all_30m_response_vs_threads}.
+When the number of active threads increased more than 140, the \cref{fi:test_obs_all_15m_response_vs_threads} show uncertainty in the inserting and retrieving all data types.
+The latency of insert and retrieve Grid timeseries data goes up compared to \cref{fi:test_obs_all_30m_response_vs_threads}.
 With higher request size, it becomes to notice the latency also increase by a small factor when the number of active thread increased.
@@
 
-\ref{fi:test_obs_all_15m_throughtput} shows the total server's transaction throughput against the number of active threads.
+\cref{fi:test_obs_all_15m_throughtput} shows the total server's transaction throughput against the number of active threads.
 The formula for total server transaction throughput is \(<active threads> * 1 second / <1  thread response time>\) \cite{JMeterPluginsTransactionPlugin}.
 It shows the statistical maximum possible number of transactions based on the number of users accessing the application.
-By combining the \ref{fi:test_obs_all_15m_latency}, this graph shows that the throughput of the system gets increased without much change in the latency, thus it proves the scalability of the \acrshort{wdias}.
+By combining the \cref{fi:test_obs_all_15m_latency}, this graph shows that the throughput of the system gets increased without much change in the latency, thus it proves the scalability of the \acrshort{wdias}.
 
@@
 \end{figure}
-\ref{fi:test_obs_all_15m_latency_percentile} visually shows the summary of \cref{tab:obs_all_15_min_summary} latency up to 90\% percentile.
+\cref{fi:test_obs_all_15m_latency_percentile} visually shows the summary of \cref{tab:obs_all_15_min_summary} latency up to 90\% percentile.
 With higher request size data, the \acrshort{wdias} able to process the requests without significant change in latency up to 90\% percentile.
@@
 With the test load used for the performance test, import-ascii-grid-upload microservice is using lots of CPU, and adapter-grid microservice is using lots of Memory.
-During this test plan, \acrshort{wdias} start with the auto scaling enabled for import-ascii-grid-upload microservice.
+During this test plan, \acrshort{wdias} start with the auto-scaling enabled for import-ascii-grid-upload microservice.
 Since adapter-grid is a consistent service for storing netCDF files, it is not possible to auto scale, since \acrshort{eks} does not support multiple reads writes support volumes \cite{LinuxFoundationPersistentKubernetes}.
@@
 \begin{table}[ht]
-\caption{Throughput and Latency of load testing with 15min data while enabled \acrshort{k8s} Auto Scaling}
+\caption{Throughput and Latency of load testing with 15min data while enabled \acrshort{k8s} auto-scaling}
 \footnotesize
@@
     \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_transaction_throughtput_vs_threads.png}
-    \caption{Load testing with 15 minutes data with enabled auto scaling - Latency against server hits}
+    \caption{Load testing with 15 minutes data with enabled auto-scaling - Latency against server hits}
     \label{fi:test_obs_all_auto_15m_latency}
 \end{figure}
-\ref{fi:test_obs_all_auto_15m_latency} graph provides an overview of the variation of latency over the elapsed time of the test plan against the number of server hits per second for 15min data while auto-scaling enabled for \acrshort{k8s}.
+\cref{fi:test_obs_all_auto_15m_latency} graph provides an overview of the variation of latency over the elapsed time of the test plan against the number of server hits per second for 15min data while auto-scaling enabled for \acrshort{k8s}.
 This graph show that over the time \acrshort{wdias} were able to keep the latency constant over the test plan.
-When compared to \ref{fi:test_obs_all_15m_latency}, throughout the test period, the latency spikes become less.
+When compared to \cref{fi:test_obs_all_15m_latency}, throughout the test period, the latency spikes become less.
 
@@
     \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_transaction_throughtput_vs_threads.png}
-    \caption{Load testing with 15 minutes data with enabled auto scaling - Transaction Throughput vs Threads}
+    \caption{Load testing with 15 minutes data with enabled auto-scaling - Transaction Throughput vs Threads}
     \label{fi:test_obs_all_auto_15m_throughtput}
@@
 
-\ref{fi:test_obs_all_auto_15m_throughtput} shows the total server's transaction throughput against number of active threads.
-When compared to \ref{fi:test_obs_all_15m_throughtput}, the estimated throughput with a higher number of active threads become stable at the graph.
+\cref{fi:test_obs_all_auto_15m_throughtput} shows the total server's transaction throughput against number of active threads.
+When compared to \cref{fi:test_obs_all_15m_throughtput}, the estimated throughput with a higher number of active threads become stable at the graph.
 This means enabling auto-scaling also improves the throughput with a higher number of active users as well.
@@
     \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_import_export_res.png}
-    \caption{Load testing with auto scaling resource usage of import and export modules.}
+    \caption{Load testing with auto-scaling resource usage of import and export modules.}
     \label{fi:obs_all_auto_15m_import_export_res}
@@
 
-\ref{fi:obs_all_auto_15m_import_export_res} shows the CPU usage and Memory usage for import timeseries modules and export timeseries modules.
+\cref{fi:obs_all_auto_15m_import_export_res} shows the CPU usage and Memory usage for import timeseries modules and export timeseries modules.
 The CPU usage is shown with milli CPUs \cite{LinuxFoundationManagingKubernetes} (1 CPU = 1000m CPUs) and the Memory usage shown with Megabytes (Mi) \cite{LinuxFoundationManagingKubernetes}.
@@
     \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_import_grid_pod.png}
-    \caption{Load testing with auto scaling import ascii grid number of pods over time.}
+    \caption{Load testing with auto-scaling import ascii grid number of pods over time.}
     \label{fi:obs_all_auto_15m_import_grid_pod}
 \end{figure}
-\ref{fi:obs_all_auto_15m_import_grid_pod} shows the number of import-ascii-grid-upload pods scheduled over time.
-The auto scaling enabled with the configurations of 1 to 10 pods with the recommended CPU usage with 80\%.
+\cref{fi:obs_all_auto_15m_import_grid_pod} shows the number of import-ascii-grid-upload pods scheduled over time.
+The auto-scaling enabled with the configurations of 1 to 10 pods with the recommended CPU usage with 80\%.
 And the pods scheduled with 1 CPU requested, and limit with 2 CPUs per pod.
@@
     \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_adapter_dbs_res.png}
-    \caption{Load testing with auto scaling resource usage of database adapters.}
+    \caption{Load testing with auto-scaling resource usage of database adapters.}
     \label{fi:obs_all_auto_15m_adapter_dbs_res}
 \end{figure}
-\ref{fi:obs_all_auto_15m_adapter_dbs_res} shows the resource utilization of database adapters in the \acrshort{wdias}.
+\cref{fi:obs_all_auto_15m_adapter_dbs_res} shows the resource utilization of database adapters in the \acrshort{wdias}.
 
@@
 \end{figure}
-\ref{fi:test_obs_query_5m_response_latency} shows the response latency over time for the query test plan.
+\cref{fi:test_obs_query_5m_response_latency} shows the response latency over time for the query test plan.
 When the number of request get higher, the latency also get increased.
@@
 \end{figure}
-\ref{fi:test_obs_query_5m_response_times_vs_threads} shows the response latency against number of active threads for the query test plan.
+\cref{fi:test_obs_query_5m_response_times_vs_threads} shows the response latency against number of active threads for the query test plan.
 When the number of server hits get higher, the latency also get increased.

### 2020-02-16 results/sec_4-discussion.tex
change API with texttt
Fixed:  workload
cref tables and auto-scaling

@@
 \section{Performance Metrics Analysis}
+\label{se:discussion}
 
@@
 The \emph{Latency} for each operation type kept constant over the whole test plan run time without any significant change.
-When the request size increased from 24 data points to 96 data points, the latency increase throw out the whole test plan with a smaller number.
+When the request size increased from 24 data points to 96 data points, the latency increase throughout the whole test plan with a smaller number.
 But for each test run the latency kept constant over the time.

### 2020-02-16 summary/sec_1-conclusions.tex
cref tables and auto-scaling

@@
 Which exhibit the scalability of the system.
-With the \acrshort{k8s} auto scaling, the \acrshort{wdias} were able to elastically adjust the number of pods according to the workload with auto scaling configurations. 
+With the \acrshort{k8s} auto-scaling, the \acrshort{wdias} were able to elastically adjust the number of pods according to the workload with auto-scaling configurations. 
 The results of \acrshort{wdias} shows that the system can run from 1 CPU node to nodes with few hundred CPUs.

### 2020-02-16 results/sec_3-observations.tex
Grammarly Obs

@@
 \end{figure}
-\cref{fi:obs_all_auto_15m_import_grid_pod} shows the number of import-ascii-grid-upload pods scheduled over time.
+
+\cref{fi:obs_all_auto_15m_import_grid_pod} shows the number of import-ascii-grid-upload pods scheduled overtime.
 The auto-scaling enabled with the configurations of 1 to 10 pods with the recommended CPU usage with 80\%.
@@
 While increasing the workload, new pods get spawn while keeping the constraint of 80\% of recommended CPU utilization.
-After \acrshort{k8s} spawn 10 maximum pods, it stop spawning new pods.
-But the pods were able to perform with vertical scaling, since those are not hit the CPU limit of 2.
+After \acrshort{k8s} spawn 10 maximum pods, it stops spawning new pods.
+But the pods were able to perform with vertical scaling since those are not hit the CPU limit of 2.
 
@@
 \label{subse:obs_test_plan_query_15min}
-This \cref{subse:obs_test_plan_query_15min} discussed about the Query test plan performance.
-It performs multiple information retrieval queries such as query over locations, parameters and timeseries etc which are described over \cref{se:query}.
+
+This \cref{subse:obs_test_plan_query_15min} discussed the Query test plan performance.
+It performs multiple information retrieval queries such as query over locations, parameters, and timeseries, etc which are described over \cref{se:query}.
 It performed approximately 123k of sample requests.
-Query test plan perform over 5 minutes of time period, and with a higher number of requests than other test plan with a peak of 600 hits per seconds.
+Query test plan performs over 5 minutes, and with a higher number of requests than other test plans with a peak of 600 hits per seconds.
 
@@
 \end{table}
+
 \cref{tab:obs_query_15_min_summary} shows the response latency summary details.
 The average latency is much higher than the minimum value.
-Also it reported higher maximum values as well.
-Standard deviation showed as quiet higher value which means the response latency values are not closer to the average value.
-Noticeably, it does not reported any errors, which means all the requests successfully process.
+Also, it reported higher maximum values as well.
+Standard deviation showed a quiet higher value which means the response latency values are not closer to the average value.
+Noticeably, it does not report any errors, which means all the requests successfully process.
 The throughput for each test case is much higher and similar to all the requests.
-This is happening since all of these requests are handle via the adapter-query, it depends on the \acrshort{mongodb} database performance.
+This is happening since all of these requests are handled via the adapter-query, it depends on the \acrshort{mongodb} database performance.
 
@@
 \end{figure}
-\cref{fi:test_obs_query_5m_response_latency} shows the response latency over time for the query test plan.
-When the number of request get higher, the latency also get increased.
+\cref{fi:test_obs_query_5m_response_latency} shows the response latency overtime for the query test plan.
+When the number of requests gets higher, the latency also gets increased.
 That means adapter-query is not very much scalable with the current configurations.
@@
 
-When ever the timeseries data not found in the adapter-query, it read data from adapter-metadata and index for search over timeseries metadata.
+Whenever the timeseries data not found in the adapter-query, it read data from adapter-metadata and index for search over timeseries metadata.
 This will cause to higher performance with geo timeseries searches.
-The performance of the \acrshort{mongodb} can further improve with using it features like Replication for high availability, and Sharding for higher throughput.
-Those attempts are beyond the scope of \acrshort{wdias} performance test and users can use those to get higher results from the \acrshort{wdias}.
+The performance of the \acrshort{mongodb} can further improve with using its features like Replication for high availability, and Sharding for higher throughput.
+Those attempts are beyond the scope of the \acrshort{wdias} performance test and users can use those to get higher results from the \acrshort{wdias}.

### 2020-02-16 results/sec_4-discussion.tex
Grammarly discussion

@@
 
-In this section concludes the observations in \cref{se:observations} section against the performance metrics defines in \cref{subse:test_plan_metrics}.
+This section concludes the observations in \cref{se:observations} section against the performance metrics defines in \cref{subse:test_plan_metrics}.
 
@@
 When the request size increased from 24 data points to 96 data points, the latency increase throughout the whole test plan with a smaller number.
-But for each test run the latency kept constant over the time.
-During the \cref{subse:obs_test_plan_all_auto_15min} test run, the performance of the Grid data got better when compared to the \cref{subse:obs_test_plan_all_15min}.
-Which means by adding more resources to the \acrshort{wdias}, it can handle more workload on the system.
+But for each test run, the latency kept constant over time.
+During the \cref{subse:obs_test_plan_all_auto_15min} test run, the performance of the Grid data got better when compared to \cref{subse:obs_test_plan_all_15min}.
+This means by adding more resources to the \acrshort{wdias}, it can handle more workload on the system.
 
-While keeping the latency constant without significant change, the \emph{throughput} of the \acrshort{wdias} kept constant while increasing the request size from 60min data (24 data points) to 15min data (96 data points) for all the data types such as Scalar, Vector and Grid.
-When number of active threads increased, the \acrshort{wdias} able to provide the same throughput with maintaining the latency stable.
+While keeping the latency constant without significant change, the \emph{throughput} of the \acrshort{wdias} kept constant while increasing the request size from 60min data (24 data points) to 15min data (96 data points) for all the data types such as Scalar, Vector, and Grid.
+When the number of active threads increased, the \acrshort{wdias} able to provide the same throughput with maintaining the latency stable.
 
-One of the reason to having deviations at the peak time due to use of single instance for the data consistency such as \acrshort{influxdb} for Scalar and Vector data, and netCDF with parallel support for Grid data.
-Further it is possible to increase the performance of these bottlenecks much higher such as using \acrshort{influxdb} Commercial cluster support for high availability or horizontal scaling of \acrshort{influxdb}.
+One of the reasons for having deviations at the peak time due to uses of single instance for the data consistency such as \acrshort{influxdb} for Scalar and Vector data, and netCDF with parallel support for Grid data.
+Further, it is possible to increase the performance of these bottlenecks much higher such as using the \acrshort{influxdb} Commercial cluster support for high availability or horizontal scaling of \acrshort{influxdb}.
 With \acrshort{influxdb} cluster, it is possible to run multiple pods of adapter-scalar and adapter-vector for support more server hits per second.
@@
 This has some performance issues as well as memory leak issues.
-Since each microservice in the \acrshort{wdias} independent of technology that can use to implement the service, it will increase the performance if the adapter-grid directly ported to netCDF with a low level language such as C or FORTRAN.
-Other than \acrshort{eks}, if users can use a \acrshort{k8s} cluster which support Persistent Volumes with the access of Read Write  Many \cite{LinuxFoundationPersistentKubernetes} , then it is possible to run multiple pods of adapter-grid and increase the throughput of the \acrshort{wdias}.
+Since each microservice in the \acrshort{wdias} independent of technology that can use to implement the service, it will increase the performance if the adapter-grid directly ported to netCDF with a low-level language such as C or FORTRAN.
+Other than \acrshort{eks}, if users can use a \acrshort{k8s} cluster that supports Persistent Volumes with the access of Read Write  Many \cite{LinuxFoundationPersistentKubernetes} , then it is possible to run multiple pods of adapter-grid and increase the throughput of the \acrshort{wdias}.
 
-When look into the \emph{resource utilization} of \acrshort{wdias}; since it is using the \acrshort{k8s} as the container orchestration system, it allows to scale up and cool down the system as required based on the workload.
-This demonstrate on the test plan of \cref{subse:obs_test_plan_all_auto_15min}, and the system get scale up to the maximum at the peak time.
-Then cool down to single pod after finishing the test cases.
+When looking into the \emph{resource utilization} of \acrshort{wdias}; since it is using the \acrshort{k8s} as the container orchestration system, it allows us to scale up and cool down the system as required based on the workload.
+This demonstrates the test plan of \cref{subse:obs_test_plan_all_auto_15min}, and the system gets scale up to the maximum at the peak time.
+Then cool down to a single pod after finishing the test cases.
 Given above \acrshort{wdias} can run from 1 CPU node to nodes with 100 CPUs.
-As described in the \cref{se:microservice}, it uses the many of the concept of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities.
+As described in the \cref{se:microservice}, it uses many of the concepts of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities.
 
 The \acrshort{wdias} supports \emph{auto scaling} by out of the box with \acrshort{k8s}.
-Services can configure with maximum number of pods in order to avoid over resource usage.
-When there is not much workload on the system, system cool down to less pods in order to save more resources.
-When there is any issue with a pod, \acrshort{k8s} auto schedule another pod and remove the unhealthy pod.
-Also it allows to update the system without any down time with rollback updates.
+Services can configure with a maximum number of pods to avoid over resource usage.
+When there is not much workload on the system, the system cools down to fewer pods to save more resources.
+When there is an issue with a pod, \acrshort{k8s} auto-schedule another pod and remove the unhealthy pod.
+Also, it allows updating the system without any downtime with rollback updates.
 
-\emph{Risk of unable to process data} during the test performance, the \acrshort{wdias} processed many requests with higher request size than the normal usage with lower rate of failures to process the requests, mainly with insert Grid data.
-If the usage of \acrshort{wdias} want to reduce the risk of unable to process data, then system can configure to run with redundant pods in order to handle spike of workloads.
-Also while configure for the auto-scaling, the \acrshort{k8s} can configure to maintain lower amount of CPU usage such as 50\% to 60\% rather 80\%.
+\emph{Risk of unable to process data} during the test performance, the \acrshort{wdias} processed many requests with higher request size than the normal usage with a lower rate of failures to process the requests, mainly with insert Grid data.
+If the usage of \acrshort{wdias} wants to reduce the risk of unable to process data, then the system can configure to run with redundant pods to handle spike of workloads.
+Also while configuring for the auto-scaling, the \acrshort{k8s} can configure to maintain a lower amount of CPU usage such as 50\% to 60\% rather  than 80\%.
 Such configuration with always spawn new pods to handle double of current peak load.

### 2020-02-16 summary/sec_1-conclusions.tex
Grammarly Conclusion

@@
 To enhance the accuracy of the weather prediction, it is essential to provide reliable and timely weather data for \acrshort{nwm}.
-Even though there are many weather data integration systems, most of them are proprietary or close sourced.
-Which means for an island like Sri Lanka that having different kinds of weather seasons over the year those software needs to be highly customized.
+Even though there are many weather data integration systems, most of them are proprietary or closed source.
+This means for an island like Sri Lanka that having different kinds of weather seasons over the year those software needs to be highly customized.
 %\hl{Throughout the operations and maintenance, it is required to get support with paying lots of charges, and difficult to debug into a closed source system without maintenance support from the vendors.
 Also most of existing systems are not up to date with the cloud computing technologies, or bias to some research community.}
-\hl{Also most of existing systems are based on basic client-server architectures or monolithic distributed system architectures which are popular or available at the time of developing those systems.
-Because of this, those are unable to get the advantage of modern computational models such as containerized applications and using the could computing in order to gain benefits of scalability, high availability and low-cost operations.}
+\hl{Also, most of the existing systems are based on basic client-server architectures or monolithic distributed system architectures which are popular or available at the time of developing those systems.
+Because of this, those are unable to get the advantage of modern computational models such as containerized applications and using the could computing to gain benefits of scalability, high availability and low-cost operations.}
 
@@
 
-First the architecture of \acrshort{wdias} starts with \acrshort{soa} using a \acrfull{esb}, and then moved to Actor model based architecture.
-After comparing the disadvantages of using such architectures with the system requirements, we came up with a modern microservice architecture.
+First, the architecture of \acrshort{wdias} starts with \acrshort{soa} using an \acrfull{esb} and then moved to Actor model-based architecture.
+After comparing the disadvantages of using such architectures with the system requirements, we came up with modern microservice architecture.
 \acrshort{wdias} implemented the microservice architecture on top of the \acrshort{k8s}.
 Each microservice of \acrshort{wdias} is mapped to a pod in the \acrshort{k8s}.
-Also, each microservice follows the concept of Smart endpoints dumb pipes, and do specific operations which are related to the data format that responsible for handling.
+Also, each microservice follows the concept of Smart endpoints dumb pipes and does specific operations that are related to the data format that responsible for handling.
 
-Based on the microservice architecture patterns and the nature of the weather metadata, the \acrshort{wdias} came up with the idea of hierarchical database structure in order to provide higher performance while store the weather data optimum.
-The system uses timeseries database for storing Scalar and Vector timeseries data, and using \acrshort{netCDF} for storing Grid timeseries data.
-And each database adapter uses concept of database per service which allows each microservice service to scale without interference from other microservices.
+Based on the microservice architecture patterns and the nature of the weather metadata, the \acrshort{wdias} came up with the idea of hierarchical database structure to provide higher performance while storing the weather data optimum.
+The system uses a timeseries database for storing Scalar and Vector timeseries data and using \acrshort{netCDF} for storing Grid timeseries data.
+And each database adapter uses the concept of database per service which allows each microservice service to scale without interference from other microservices.
 And it uses microservice sagas pattern for asynchronous data handling for requests with higher size.
-According to the \cref{se:microservice}, it uses the many of the concept of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities.
+According to the \cref{se:microservice}, it uses many of the concepts of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities.
 
-Also, the system provide a generic open mechanism to integrate new modules as extension to enhance the features of the system.
-This capability enable to integrate weather data preprocessing flows as extension modules.
-The extension API provide easy access to create and modify the extension triggers on the fly without stopping the system or any downtime in order to change the configurations.
-The system provides extensive timeseries query endpoints to easy search over the system timeseries metadata with supporting Geo based queries.
+Also, the system provides a generic open mechanism to integrate new modules as an extension to enhance the features of the system.
+This capability enables to integrate weather data preprocessing flows as extension modules.
+The extension API provides easy access to create and modify the extension triggers on the fly without stopping the system or any downtime to change the configurations.
+The system provides extensive timeseries query endpoints to easy search over the system timeseries metadata with supporting Geo-based queries.
 
 Load testing of \acrshort{wdias} was perform using the \acrshort{jmeter} tool's distributed testing capabilities.
-Then the test plans are performed with increasing the request size, and monitored the performance metrics.
+Then the test plans are performed with increasing the request size and monitoring the performance metrics.
 The system is setup on the \acrfull{eks} as per the configurations of \cref{subse:test_sys_config}.
-Based on the observations, the system were able to handle 300 \acrshort{rps} (which means 18,000 requests per minute) successfully with minimizing the error rate to zero.
-Also, while increasing the request size from 24 to 96 data points per scalar and vector timeseries, and number of ASCII Grid files from 24 to 96, the \acrshort{wdias} was able to perform same while keeping the latency constant without any significant change.
-During the performance test plans, the system were able to provide increase the throughput by keeping the latency constant while increasing the workload.
-Which exhibit the scalability of the system.
+Based on the observations, the system was able to handle 300 \acrshort{rps} (which means 18,000 requests per minute) successfully with minimizing the error rate to zero.
+Also, while increasing the request size from 24 to 96 data points per scalar and vector timeseries, and the number of ASCII Grid files from 24 to 96, the \acrshort{wdias} was able to perform the same while keeping the latency constant without any significant change.
+During the performance test plans, the system was able to provide an increase in the throughput by keeping the latency constant while increasing the workload.
+Which exhibits the scalability of the system.
 With the \acrshort{k8s} auto-scaling, the \acrshort{wdias} were able to elastically adjust the number of pods according to the workload with auto-scaling configurations. 
-The results of \acrshort{wdias} shows that the system can run from 1 CPU node to nodes with few hundred CPUs.
+The results of \acrshort{wdias} shows that the system can run from 1 CPU node to nodes with a few hundred CPUs.

### 2020-02-16 summary/sec_2-research_limitations.tex
Fixed:  workload
Grammarly research limitations

@@
 \section{Research Limitations}
-\gkc{Previously you asked to rename this section.
+\label{se:research_limitations}
+\gkc{Previously you asked to rename this section sir.
 Why can't it have the title of \emph{Future Work}.
@@
 Which part is misleading?}
-This section discussed about the lacking features in the \acrshort{wdias}, and some of the improvement that can add for improve the performance and usability of the system.
 
-\emph{Lack of data preprossessing modules}:
-The extension module enable plugin system to integrate prepossessing modules which can use for process the data which are inserted to the system or based on regular intervals.
-Also \acrshort{wdias} provide a more generic open interface approach to create more preprocessing modules.
-Since \acrshort{wdias} is an open source system, it expect more modules to be create by the community.
-When compared to other system like \acrshort{fews}, current system only have few extension for the testing purpose.
-This is one of the major area that need to be improved.
+This section discussed the lacking features in the \acrshort{wdias} and some of the improvements that can add to improve the performance and usability of the system.
+
+\emph{Lack of data preprocessing modules}:
+The extension module enables the plugin system to integrate prepossessing modules that can use for process the data which are inserted to the system or based on regular intervals.
+Also, \acrshort{wdias} provides a more generic open interface approach to create more preprocessing modules.
+Since \acrshort{wdias} is an open-source system, it expects more modules to be created by the community.
+When compared to other systems like \acrshort{fews}, the current system only have few extension for the testing purpose.
+This is one of the major areas that need to be improved.
 
 \emph{Supporting Irregular Grids}:
-At the moment \acrshort{wdias} does not support Irregular Grids, but it has the API endpoints define for the implementation which can follow the same microservice architecture.
-The scope of the \acrshort{wdias} does not belong such level of implementation and the scope has reduced by removing such components from the system.
+At the moment \acrshort{wdias} does not support Irregular Grids, but it has the API endpoints defined for the implementation which can follow the same microservice architecture.
+The scope of the \acrshort{wdias} does not belong to such level of implementation and the scope was reduced by removing such components from the system.
 
 \emph{Grid data performance}:
-As mentioned in the \cref{se:discussion}, the adapter-grid is using a Python wrapper for netCDF FORTRAN implementation with parallel IO enabled.
+As mentioned in the \cref{se:discussion}, adapter-grid is using a Python wrapper for netCDF FORTRAN implementation with parallel IO enabled.
 This has some performance issues as well as memory leak issues.
-Since each microservice in the \acrshort{wdias} independent of technology that can use to implement the service, it will increase the performance if the adapter-grid directly ported to netCDF with a low level language such as C or FORTRAN.
+Since each microservice in the \acrshort{wdias} independent of technology that can use to implement the service, it will increase the performance if the adapter-grid directly ported to netCDF with a low-level language such as C or FORTRAN.
 They are some future work that can focus on improving the performance of grid data.
@@
 Physical nodes for the \acrshort{k8s} cluster created using Cloud Computing provider such as \acrshort{eks}.
-And defining the each pod resource limitations at the helm chart level.
-But the infrastructure that need to deploy the \acrshort{wdias} can define as code such as using tools like Teraform which is independent of the Cloud Computing provider.
-Using such tool, users will able to easy deploy the \acrshort{wdias} on any Cloud provider without much hassle.
+And defining each pod resource limitations at the helm chart level.
+But the infrastructure that needs to deploy the \acrshort{wdias} can define as code such as using tools like Terraform which is independent of the Cloud Computing provider.
+Using such a tool, users will able to easily deploy the \acrshort{wdias} on any Cloud provider without much hassle.
 
 \emph{Improve test cases}:
-As described in detail with \cref{subse:closed_vs_open_workload}, for \acrshort{wdias} performance test uses Time Stepping Feedback loop with Concurrent Threads which is the best approach support by \acrshort{jmeter} at the moment.
-But using that it is not possible to get desired \acrshort{rps} for each test case within the test plan.
+As described in detail with \cref{subse:closed_vs_open_workload}, for \acrshort{wdias} performance test uses the \emph{Time Stepping Feedback} loop with Concurrent Threads which is the best approach support by \acrshort{jmeter} at the moment.
+But using that it is not possible to get the desired \acrshort{rps} for each test case within the test plan.
 Because of this issue, the \acrshort{wdias} test plans further improved by removing redundant test cases such as create timeseries at the beginning.
-Having create timeseries at the beginning causes some issues such as most of the thread are working on that test case rather on required test cases.
-Still there may be some improvement that can be done.
+Having created timeseries at the beginning causes some issues such as most of the thread are working on that test case rather on required test cases.
+Still, there may be some improvement that can be done.
 
-\emph{Further improve hierarchical database performance}:
+\emph{Tune \acrshort{wdias} database structure performance}:
 As further described in \cref{se:discussion}, it is possible to increase the performance of these bottlenecks much higher such as using \acrshort{influxdb} Commercial cluster support for high availability or horizontal scaling of \acrshort{influxdb}.
-With \acrshort{influxdb} cluster, it is possible to run multiple pods of adapter-scalar and adapter-vector for support more server hits per second.
+With the \acrshort{influxdb} cluster, it is possible to run multiple pods of adapter-scalar and adapter-vector for support more server hits per second.
 Other than that, the \acrshort{wdias} performance can improve via partitioning the timeseries key space into multiple \acrshort{influxdb} instances.
-The adapter-scalar or adapter-vector can improve to plug multiple instance of \acrshort{influxdb} instances by changing the configurations.
-As an example, based on the key attribute \cref{subse:timeseries_key_attributes} Timeseries Type, the adapter-scalar can connect to four instance of \acrshort{influxdb} instances such as  External Historical, External Forecast, Simulated Historical, and Simulated Forecast etc.
+The adapter-scalar or adapter-vector can improve to plug multiple instances of \acrshort{influxdb} instances by changing the configurations.
+As an example, based on the key attribute \cref{subse:timeseries_key_attributes} Timeseries Type, the adapter-scalar can connect to four instances of \acrshort{influxdb} instances such as  External Historical, External Forecast, Simulated Historical, and Simulated Forecast, etc.
 
 \emph{Alerting extension modules}:
-At the moment, extensions only support On Change and On Time events. But it will be good to have event trigger support based on reconfigured alert level.
+At the moment, extensions only support \emph{OnChange} and \emph{OnTime} events. But it will be good to have event trigger support based on reconfigured alert level.
 
 \emph{Publisher Subscriber extension modules}:
-The \acrshort{wdias} better to be capable of triggering external systems based on the events such as web hooks.
+The \acrshort{wdias} better to be capable of triggering external systems based on events such as webhooks.
 
@@
 May be I didn't understand your suggestion here.}
-\gkc{DO we need to move the \cref{se:discussion} here? Normally where should we include the analysis of observations?}
+\gkc{Do we need to move the \cref{se:discussion} here? Normally where should we include the analysis of observations?}

### 2020-02-16 results/sec_3-observations.tex
Fix: All test plan

@@
 
-After running the All test plan with 60 minutes (24 data points), it observed the data summary of \cref{tab:obs_all_60_min_summary}. It performed 311k of sample requests.
+After running the test plan with 60 minutes (24 data points), it observed the data summary of \cref{tab:obs_all_60_min_summary}. It performed 311k of sample requests.
 
@@
 
-\cref{subse:obs_test_plan_all_30min} discussed the All test plan performance with 30 minutes data which means 48 data points per each request in Scalar and Vector timeseries, and 48 ASCII grid files per each insert request.
+\cref{subse:obs_test_plan_all_30min} discussed the test plan performance with 30 minutes data which means 48 data points per each request in Scalar and Vector timeseries, and 48 ASCII grid files per each insert request.
 It performed round up to 311k of sample requests which are almost similar to \cref{subse:obs_test_plan_all_60min} processed samples.
@@
     \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_30m_response_times_vs_threads.png}
-    \caption{Load testing with 30 minutes data - Response Time vs Threads}
+    \caption{Load testing with 30 minutes of data - Response Time vs Threads}
     \label{fi:test_obs_all_30m_response_vs_threads}
@@
     \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_30m_res_latencies_against_hits.png}
-    \caption{Load testing with 30 minutes data - Latency against server hits}
+    \caption{Load testing with 30 minutes of data - Latency against server hits}
     \label{fi:test_obs_all_30m_latency}
@@
     \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_15m_response_times_vs_threads.png}
-    \caption{Load testing with 15 minutes data - Response Time vs Active Threads}
+    \caption{Load testing with 15 minutes of data - Response Time vs Active Threads}
     \label{fi:test_obs_all_15m_response_vs_threads}
@@
     \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_15m_res_latencies_against_hits.png}
-    \caption{Load testing with 15 minutes data - Latency against server hits}
+    \caption{Load testing with 15 minutes of data - Latency against server hits}
     \label{fi:test_obs_all_15m_latency}
@@
     \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_15m_transaction_throughtput_vs_threads.png}
-    \caption{Load testing with 15 minutes data - Transaction Throughput vs Threads}
+    \caption{Load testing with 15 minutes of data - Transaction Throughput vs Threads}
     \label{fi:test_obs_all_15m_throughtput}
@@
     \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_15m_response_times_percentiles.png}
-    \caption{Load testing with 15 minutes data - Response times Percentiles}
+    \caption{Load testing with 15 minutes of data - Response times Percentiles}
     \label{fi:test_obs_all_15m_latency_percentile}
@@
     \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_transaction_throughtput_vs_threads.png}
-    \caption{Load testing with 15 minutes data with enabled auto-scaling - Latency against server hits}
+    \caption{Load testing with 15 minutes of data with enabled auto-scaling - Latency against server hits}
     \label{fi:test_obs_all_auto_15m_latency}
@@
     \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_transaction_throughtput_vs_threads.png}
-    \caption{Load testing with 15 minutes data with enabled auto-scaling - Transaction Throughput vs Threads}
+    \caption{Load testing with 15 minutes of data with enabled auto-scaling - Transaction Throughput vs Threads}
     \label{fi:test_obs_all_auto_15m_throughtput}

### 2020-02-20 Paper.tex
Draft paper up to lit review

@@
 \newcommand{\dbc}[1]{\todo[author=Dilum, inline, color=blue!40]{#1}}
+
+\usepackage{hyperref}
+\usepackage[noabbrev,capitalise]{cleveref}
 
@@
 \begin{IEEEkeywords}
-\db{Data assimilation, data integration, hierarchical databases, microservice, weather}
+\db{Cloud computing, data assimilation, data integration, }
 \end{IEEEkeywords}
@@
 \section{INTRODUCTION}
-%I'm going to do this today \cite{Haggett1998AnWales}.
-Give general idea on weather data integration systems.
-Talk about the existing systems. And they're proprietary or close source.
-(Don't dedicate another section, otherwise need to do a comparison at the performance analysis)
-At the end the structure of rest of the paper
+Weather prediction is essential to reduce impact due to natural disasters and to gain
+effectively manage natural resources like water.
+Center for Urban Water, Sri Lanka (CUrW-SL) [3] is tasked with the mission to reduce water-related natural disasters in Sri Lanka.
+It collected real-time data from weather stations and other government entities and generates daily forecasts.
+Then the generated results are shared with relevant public departments responsible for disaster planning, mitigation, and management.
+To enhance the accuracy of weather predictions, it is necessary to provide reliable and
+detailed weather data as inputs to NWMs.
+Before feeding such diverse data collected from different sources, it is necessary to a data format that can be ingest by the NWMs.
+Further these data need to be process with less time, and need to handle bulk stream weather data.
 
-To enhance the accuracy of weather predictions, it is necessary to provide reliable and detailed weather data as inputs to \acrfull{nwm}.
-These NWMs utilize weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images.
-Prior to feeding such diverse data (collected from different sources that belong to different stakeholders) into respective NWMs, it is necessary to integrate data into a common format.
-Moreover, the data integration system’s response time needs to be relatively low to accommodate critical situations like hurricanes, storms, and floods which require rapid and frequent execution of NWMs.
+There are many forecasting systems developed with considering above factors for disaster management.
+The \acrshort{fews} is developed in the Netherland by Deltares for operational forecasting.
+It uses a model-centric approach with considering forecasting process as a combination of data modeling steps and data transformation algorithms.
+So, it is a flexible framework with no inherent hydrological modeling capabilities and system and capable of creating forecasting workflows by integrating new models and algorithms.
+Also it follows a common data-model and allow models to interact with the system via one of the interfaces provided, and all the timeseries data are stored via this common data model.
+Even this approach is efficient in data storing and accessing, but it has the inherent issues of performance of accessing data via a single data model in a database.
+One of interesting concept of \acrshort{fews} is using unique fields to identify timeseries such by their location and data type, as well as an id related to the source of the data.
+Even it provide an simple but most effective feature by following the concept of the open modeling framework proposed by Open model integration \cite{Kokkonen2003InterfacingXML}, the model adapter is causing tide coupling into the execution process with the \acrshort{fews}.
+This causing some issue with unit testing models separately and does not easily allow users to run the models in flexible manner such as parallel execution or external process.
 
-Providing public access to weather data is also useful to enable many third-party applications and research.
-For example, logistic companies can use that data with their own model to plan and schedule their deliveries.
-Agricultural insurance companies can warn the farmers in advance, as well as calculate premiums based on anticipated weather patterns.
+\acrfull{lead} is using the fundamental concept of  dynamic workflow orchestration and
+data management in a Web services framework \cite{Droegemeier2005Service-OrientedWeather}. To predict and analyze weather models
+by researchers, it required many resources. Rather than each researcher is running and
+handling their computer resources to do the weather experiments, LEAD is providing pool of resources, then the researchers can use this resource a pool to run their
+experiment in shorter amounts of time and higher scale.
+It is following the \acrfull{soa} with different service layers, and expose services via drag and drop interface to create new flow by users to run new forecast workflows.
+Workflow service in the \acrshort{lead} schedule and run those with promising the full use of underline resources in the system.
+\acrfull{dias} and \acrfull{madis} mostly provide the functionality of integration and sharing of data.
+When compared to other systems, those do not have the workflow capabilities.
+To store on the large volume of disk space, \acrshort{dias} converts the data via a provided set of \acrshort{api}s and provide the functionality of quality control of the data, and metadata management and  shares the data via the Shared API layer.
+\acrshort{madis} also store the data by converting the data into a common format, and provide access to the data based on role access.
 
-While Data Integration and Analysis System (DIAS) and Meteorological Assimilation Data Ingest System (MADIS) are some of well-known Weather Data Integration and Assimilation (WDIA) systems, they are proprietary.
-Further Delft-FEWS is free to use, it is not open source.
-Hence, users of WDIA are forced to pay heavy licenses and are unable to extend the solutions to cater to their country-specific requirements.
-Therefore, the objective of this research is to develop a WDIA system for Sri Lanka, as well as make it open source, so that others could use and contribute to the solution.
-
-TODO: Specify the \acrshort{lead} service as a building block approach. \acrshort{fews} more modular approach with general adapter. And \acrshort{wdias} using microservice as module.
-Similar to the \acrfull{fews} \cite{Werner2013TheSystem}
-
-The main purpose of this framework is to provide a platform through which opera- tional forecasting systems can be constructed, and that allows flexibility in the integration of models and data.
-In contrast to the NWSRFS and the RFFS systems that also follow a modular approach, the Delft-FEWS system contains no inherent hydrological model- ling capabilities within its code base.
-I
+Even though there are many data integration systems, most of them are proprietary or closed source.
+For an island like Sri Lanka that having different kinds of weather seasons
+over the year than that software originated need to be highly customized.
+Thus it required to get support from the vendor to integrate and configure the
+system.
+And most of the software existing out there is not up to date with the latest
+technology concepts such as Cloud Computing.
+The modern architecture pattern such as microservice architecture was able to provide high scalability and availability, rather using monolithic architecture or client service architecture.
+Since most of existing systems are dependent underline infrastructure providers, the users do not have much flexibility to decide the best cost-effective way to host it.
+Above facts has been considered while we proposed the \acrfull{wdias}.
+The main purpose of this system is to design and implement an extendable weather data integration, assimilation, and dissemination system which is capable of handling bulk data efficiently with providing scalability and high throughput with using open source tools and modern cloud computing technologies.
 
@@
 Section 6 finally provides a summary of the paper, as well as an outlook on the future development of Delft-FEWS.
+
+This paper first provides a brief review on necessity of weather forecasting and some of existing weather data systems.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{figure}[htbp]
-\centerline{\includegraphics[width=0.4\textwidth]{method/microservice/hierarchical_database.jpg}}
+\centerline{\includegraphics[width=0.4\textwidth]{method/microservice/wdias_database_structure.jpg}}
 \caption{Hierarchical database.}
@@
 \input{glossary.tex}
-% \bibliographystyle{plain}
-% \addbibresource{mendeley.bib}
 \printbibliography[title={References}]

### 2020-02-20 introduction/sec_1-motivation.tex
Tried href links package
Draft paper up to lit review

@@
 Weather prediction is essential to reduce impact due to natural disasters and to gain effectively manage natural resources like water.
+It will give more understanding of weather prediction if we look into a weather prediction flow that can use to predict the surface water level.
 The weather predictions/forecasts are performed using \acrfull{nwm} that use a set of configuration parameters and the current status of the environment such as temperature, rainfall, and wind direction as the input.
@@
 \dbc{Highighted part doesn't make much sense to me. Need to be reworded.}
+\gkc{Highlighted parts modified and kept also.}
 \dbc{cite both NWM and WRF}
@@
 These NWMs utilize multi-modal weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images.
-Before feeding such diverse data (collected from different sources that belong to different stakeholders) into respective NWMs, it is necessary to integrate data into a common format.
+Before feeding such diverse data (collected from different sources that belong to different stakeholders) into respective NWMs, it is necessary to a data format that can be ingest by the model.
 Moreover, the data integration system’s response time needs to be relatively low to forecast and monitor time-sensitive weather events like hurricanes, storms, and floods which require rapid and frequent execution of NWMs.
@@
 Even though there are many data integration systems, most of them are proprietary or closed source.
-Which means for an island like Sri Lanka that having different kinds of weather seasons over the year than that software originated need to be highly customized.
+For an island like Sri Lanka that having different kinds of weather seasons over the year than that software originated need to be highly customized.
 Throughout the operations and maintenance, it is required to get support with paying lots of charges, and difficult to debug into a closed source system without maintenance support from the vendors.
@@
 And most of the software existing out there is not up to date with the latest technology concepts such as Cloud Computing.
-\acrfull{wdias} uses the modern architecture pattern such as microservice to achieve scalability, rather using monolithic architecture or client service architecture.
+The modern architecture pattern such as microservice architecture was able to provide high scalability and availability, rather using monolithic architecture or client service architecture.
 Most existing systems required to shut down to update the system configuration such as \acrshort{fews}, but a system that is accessed by any third parties should be operating 99.9\% without any downtime and should allow adding new features on the fly with rollover capabilities.

### 2020-02-20 introduction/sec_3-outline.tex
Draft paper up to lit review

@@
 Solution approach with the proposed system architectures and adaptation with problem occurred are presented in Chapter \ref{ch:method}.
-It provides details about how the \acrshort{wdias} is designed by following a microservice architecture and the date preprocessing capabilities of the system.
+It provides details about how the \acrshort{wdias} is designed by following a microservice architecture and the data preprocessing capabilities of the system.
 Performance analysis is presented in Chapter \ref{ch:results}.

### 2020-02-20 lit/sec_1-fews.tex
Draft paper up to lit review

@@
 to specific weather conditions.% in a particular country.
-This chapter presents a literature review on existing systems and their architecture approach and design.
-In \cref{se:fews}, we present \acrshort{fews}.
+This chapter presents a literature review on existing systems and their architectural approaches and designs.
+In \cref{se:fews}, we present \acrfull{fews} that is developed as an open model integration framework.
 \acrfull{lead}, an open data handling platform distributed as closed-source software, is presented in \cref{se:lead}.
 % \acrshort{lead} is following the \acrfull{soa} for system architecture.
-In \cref{se:dias}, we discussed \acrfull{dias} which is a common data platform that can work with weather data.
+In \cref{se:dias}, we discussed \acrfull{dias} which is a common data platform that can manage weather data.
 \acrfull{madis} is another widely used data integration system, which also provides data access with quality control, which we discuss in \cref{se:madis}.
@@
 The widely used concept is using meteorological forecast data to get precipitation and, then using a hydrological and hydraulic model chain to predict the level affect on the ground.
-The hydrological and hydraulic model should be design based on the ground.
+The hydrological and hydraulic model should be design based on the Geographical data.
 The ground should be analyzed geographically and divide into the catchments.
@@
 Since it is storing the different data types as binary objects, there is a penalty in converting data into binary objects and vice versa.
-Storing all the data in a timeseries table causing all the requests to come into a single data point.
+Storing all the data in a timeseries table causing all the requests to come into a single data model in a database.
 Even it gives the advantage of accessing all the data in one place.
@@
 \dbc{When referring to a section you need to use the word "Section" as highlighted above. Fix all other places.}
-\gkc{FIXED}
+\gkc{FIXED. I did not remove highlited places as you need to verify.}
 
@@
 But it is a concept that needs to be discussed and understand properly to design a data integration and assimilation system.
+But the \acrshort{wdias} is capable of integrating workflow mechanism with its extendable architecture.
 
@@
 This is supported via the workflow process in \acrshort{fews}.
-The scope of the \acrshort{wdias} is not focused on adding such a feature in the system, rather user has to use a scientific workflow management system or come up with own version of workflow.
+As mentioned above, the scope of the \acrshort{wdias} is not focused on adding such a feature in the system, rather user has to use a scientific workflow management system or come up with own version of workflow.
 

### 2020-02-20 Paper.tex
Paper - microservice architecture

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{INTRODUCTION}
+\section{Introduction}
+\label{pse:Introduction}
 Weather prediction is essential to reduce impact due to natural disasters and to gain
@@
 This paper first provides a brief review on necessity of weather forecasting and some of existing weather data systems.
+\cref{pse:background} provides an overview of modern architectural patterns used in \acrshort{wdias} and the important components and features of the \acrshort{wdias} discussed in \cref{pse:wdias_architecture}, next \cref{pse:performance_analysis} discusses the test workload performance analysis with comparing with the metrics.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{\db{Background}}
-%\section{Modules of Weather Data System}
-\cref{fi:wdia_components} shows the basic functions of a Weather data integration and assimilation system.
+\label{pse:background}
+
+\cref{fi:wdia_components} shows the basic functions of a Weather data integration and assimilation system such as Integration, Assimilation, and Dissemination.
+
 \begin{figure}[htbp]
@@
 \caption{Components of a weather data system.}
-\label{fi:wdia_components}
+\label{pfi:wdia_components}
 \end{figure}
-\paragraph{Integration} The system should capable of integrating data from different source such as satellite data, high end and low end weather station etc.
-And the system should be able to handle multidimensional spatial and temporal weather data efficiently and optimally.
-\paragraph{Assimilation} Then the system should be able to fulfill weather models varying data requirements.
-Also those models reproduce large set of redundant data, thus system should store the bulk data while optimizing the disk space.
-\paragraph{Dissemination} Then different users should be able to retrieve data as they required.
-Also the users should be able to easy to search into the available that in the system base on timeseries metadata or based on Geo queries.
+
+The system should capable of integrating data from different source such as satellite data, high end and low end weather station etc in the form of multidimensional spatial and temporal weather data as shown in the \emph{Integration} modules.
+Then the system should be able to fulfill weather models varying data requirements and should be able to store large set of redundant model data during the \emph{Assimilation} module.
+The users should be able to easy to search into the available that in the system base on timeseries metadata or based on Geo queries, and the \emph{Dissemination} module should be capable of sharing data among different users.
+
+The \acrshort{wdias} is supporting all three above modules. It iterate through few architectures with concerning about the scalability and high availability.
+The initial design of WDIAS used the Service Oriented Architecture (SOA).
+Moreover, it tried to use an Enterprise Service Bus (ESB) to integrate different modules, as ESB is acting as a common layer for all of the modules.
+However, it turned out that ESB is not suitable for data streaming or bulk data processing and ESB suffers from a single point of failure since it is using a common bus.
+In the second design phase of WDIAS, we attempted to use the actor model using the AKKA framework [9] to overcome above ESB drawbacks and followed the microservice architecture.
+The system architecture redesign with decomposing into microservices and
+used actors to implement each microservice in the system.
+
+Microservice architecture is resilient and flexible as one service is independent of another service.
+And it is highly scalable as demanding services can be deployed in multiple servers.
+One of the attractive features of microservice architecture is the independent nature of the microservices which allows to choose different technologies and maintain separately.
+But using AKKA framework for implement microservice architecture has some disadvantages such as unable to choose independent technologies and the actors messaging between different services cause to result in a too-tight code coupling between the services.
+To overcome these issues, we moved to the concept of container orchestration based microservice architecture.
 
@@
 \subsection{Microservice Architecture}
-Brief mentioned about soa and Actor model and why moved away from them.
+\label{psubse:microservice_architecture}
+
+A microservice architecture style is an approach to developing a single application as
+a suite of small services, each running in its own process and communicating with
+lightweight mechanisms, often via providing a RESTful API. Follow are some of the microservice design patterns mostly used in the context of designing WDIAS architecture.
+\begin{itemize}
+    \item \emph{Smart Endpoints and Dumb Pipes} - rather than implementing smart endpoints with supporting multiple protocols and complex logic, microservices aim to be as decoupled and as cohesive as possible with only focusing one own domain.
+    \item \emph{Database per microservice} - The idea is to keep each microservices persistent data private to that service and accessible only via its API.
+    \item \emph{Distributed Transactions over microservices via event processing} - A service publishes an event when its data changes. Other services consume that event and update their data.
+    \item \emph{X-axis Scaling} -  running multiple copies of an application behind a load balancer
+    \item \emph{Y-axis Scaling} - splits the application into multiple, different services.
+Each service is responsible for one or more closely related functions.
+The microservice architecture is an application of Y-axis scaling.
+    \item \emph{Z-axis Scaling} - each server runs an identical copy of the code (similar to X-axis scaling). The big difference is that each server is responsible for only a subset of the data.
+\end{itemize}
+
+The \acrshort{wdias} is using \acrfull{k8s} as the container orchestration system which is an open-source tool for automating deployment, scaling, and management of containerized applications.
+
 \begin{figure}[htbp]
@@
 \caption{\acrfull{k8s} architecture.}
-\label{fi:k8s_architecture}
+\label{pfi:k8s_architecture}
 \end{figure}
+
+\cref{fi:k8s_architecture} gives an overall idea on the components of \acrshort{k8s},
+\begin{itemize}
+    \item Pods -- Cluster of containers that can group other container images in a single unit.
+    \item Nodes -- the machines (VMs, physical servers, etc) in a cluster that runs your applications and cloud workflows.
+    \item kubelet -- An agent that runs on each node in the cluster. It makes sure that containers are running in a pod.
+    \item kube-proxy -- A network proxy that runs on each node in the cluster, and maintains network rules on nodes.
+    \item Kubernetes master -- Responsible for maintaining the desired state for your cluster.
+    \item etcd -- Consistent and highly-available key value store used as Kubernetes’ backing store for all cluster data.
+\end{itemize}
+Users can add much as required Nodes into the K8s cluster, and K8s manage and
+deploy applications as pods into cluster nodes. Thus it allow users to implement the microservice architecture concepts above easily.
 
@@
 \section{\acrfull{wdias} Architecture}
-%\section{Structure of \acrshort{wdias}}
+\label{pse:wdias_architecture}
+
 \begin{figure}[htbp]
@@
 \caption{microservice architecture - handle on demand.}
-\label{fi:microservice_architecture_on_demand}
+\label{pfi:microservice_architecture_on_demand}
 \end{figure}
@@
 \caption{microservice architecture - handle asynchronously.}
-\label{fi:microservice_architecture_async}
+\label{pfi:microservice_architecture_async}
 \end{figure}
 
-\subsection{Hierarchical Database}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{\acrshort{wdias} Database Structure}
+\label{subse:wdias_database}
 \begin{figure}[htbp]
@@
 \caption{Hierarchical database.}
-\label{fi:hierarchical_database}
+\label{pfi:hierarchical_database}
 \end{figure}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Weather Data Preprocessing}
+\label{psubse:data_preprocessing}
+
 \begin{figure}[htbp]
@@
 \caption{Generic functional approach to weather data preprocessing.}
-\label{fi:summary_weather_data_preprocessing}
+\label{pfi:summary_weather_data_preprocessing}
 \end{figure}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Query Timeseries Metadata}
+\label{psubse:query_timeseries}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Performance \db{Evaluation}}
+\section{Performance Analysis}
+\label{pse:performance_analysis}
 %\section{Performance Analysis}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Test Plan and Workload}
@@
 \caption{Performance study.}
-\label{fi:performance_Study}
+\label{pfi:performance_Study}
 \end{figure}
 
-\subsection{Observations}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Performance Evaluation}
+\label{psubse:performance_evaluation}
 \begin{table}[htbp]
@@
 \end{tabular}
-\label{tab:obs_all_auto_15_min_summary_latency}
+\label{ptab:obs_all_auto_15_min_summary_latency}
 \end{center}
@@
 \end{tabular}
-\label{tab:obs_all_auto_15_min_summary_throughput}
+\label{ptab:obs_all_auto_15_min_summary_throughput}
 \end{center}
@@
 \caption{Performance test 15min data enabled auto-scaling - response latencies against server hits over the elapsed time.}
-\label{fi:test_obs_auto_all_15_min_latency_vs_hits}
+\label{pfi:test_obs_auto_all_15_min_latency_vs_hits}
 \end{figure}
@@
 \caption{Performance test 15min data enabled auto-scaling - transnational throughput vs number of active threads.}
-\label{fi:test_obs_auto_all_15_min_throughput_vs_threads}
+\label{pfi:test_obs_auto_all_15_min_throughput_vs_threads}
 \end{figure}
 
-\subsection{Discussion}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Performance Metrics Analysis}
+\label{psubse:performance_metrics}
 \paragraph{Latency}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Strengths and Limitations}
+\subsection{Strengths and Limitations}
+\label{psubse:limitations}
 \dbc{Make this the dicussion and a sub-section of Sec. 4}
@@
 \section{Summary}
+\label{pse:summary}
 \dbc{Summary is too long. Should not be more than a single para}
@@
 \section*{Acknowledgment}
+\label{pse:ack}
 \db{This research is supported in part by the grant from the Center for Urban Water, Sri Lanka.}

### 2020-02-20 method/sec_0_introduction.tex
Paper - microservice architecture

@@
 This chapter includes the design decision taken while implementing the \acrfull{wdias}, and how is the system got adapted from the systems analyzed in Chapter \ref{ch:literature}.
-In \cref{se:high_level_design} a brief discussion on how the weather forecasting is happening and why it needs to interact with multiple data formats is presented.
-\cref{se:architectural_decisions} that we evolve architectural design while designing and implementing the \acrshort{wdias}.
+\cref{se:high_level_design} includes a brief discussion on how the weather forecasting is happening and why it needs to interact with multiple data formats is presented.
+\cref{se:architectural_decisions} discussed about how did we evolve over the architectural design while designing and implementing the \acrshort{wdias}.
 \cref{se:microservice} gives a better understanding of the microservice architectural concepts that follow while implementing the \acrshort{wdias}.
-Then the reason behind developing \acrshort{wdias} database structure and technologies use for that discussed in \cref{se:db_struct}.
+Then the reasons behind developing \acrshort{wdias} database structure and technologies use for that discussed in \cref{se:db_struct}.
 \cref{se:data_preprocess} discussed how the \acrshort{wdias} enables for data preprocessing and adding capabilities via the concept of Extensions.
-Final \cref{se:query} includes details on how to perform timeseries search and Geo-based queries.
+Final \cref{se:query} includes details on how to perform timeseries search and Geo-based queries on the \acrshort{wdias}.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Modules of a Weather Data System}
@@
 \cref{fi:wdia_components} shows the basic functions of a Weather data integration and assimilation system which consists of the following modules:
+
 \begin{figure}[htbp]

### 2020-02-20 method/sec_1-architectural_decisions.tex
Paper - microservice architecture

@@
 
-\acrfull{k8s} is an open-source system for automating deployment, scaling, and management of containerized applications \cite{LinuxFoundationProduction-GradeKubernetes}.
+The \acrshort{wdias} is using \acrfull{k8s} as the container orchestration system which is an open-source tool for automating deployment, scaling, and management of containerized applications \cite{LinuxFoundationProduction-GradeKubernetes}.
 It groups containers that make up an application into logical units for easy management and discovery.

### 2020-02-20 Paper.tex
Add methodology summary

@@
 
-TODO: Update content as below, overview of rest of the paper
-This paper first provides a short review of the operational forecasting process and the role of Delft-FEWS within that process.
-Section 3 provides an overview of the philosophy and the most important components and features of Delft-FEWS, while Section 4 discusses some example applications of the Delft-FEWS system in research and operations.
-A discussion of the systems strengths and limitations is provided in Section 5.
-Section 6 finally provides a summary of the paper, as well as an outlook on the future development of Delft-FEWS.
-
 This paper first provides a brief review on necessity of weather forecasting and some of existing weather data systems.
@@
 
+\cref{pfi:microservice_separation} shows the clear separation of microservices into the modules of the \acrshort{wdias}.
+As seen in Figure of \cref{fi:wdias_micro_on_demand} and \cref{fi:wdias_micro_async} each circle represents a microservice in the \acrshort{wdias}, and those are implemented as containerized applications.
+
 \begin{figure}[htbp]
-\centerline{\includegraphics[width=0.5\textwidth]{method/microservice/microservice_architecture-handle_on_demand-v3.jpg}}
-\caption{microservice architecture - handle on demand.}
-\label{pfi:microservice_architecture_on_demand}
+\centerline{\includegraphics[width=0.5\textwidth]{method/microservice/separation_microservices-v3.jpg}}
+\caption{Separation of \acrshort{wdias} microservices.}
+\label{pfi:microservice_separation}
 \end{figure}
+
+The left side of Figure 3.3
+shows the import modules of the WDIAS, and the right side shows the export modules. each import microservice only does the specific
+task of converting and forwarding the request to the correct data adapter module. each data type, there is an adapter microservice is running which is optimized to storing
+such type of data. Each adapter has an isolated database, and the database is hosted separately for the high performance.
+And timeseries metadata stored using RDBMS which gives more performance over retrieving metadata data, and cached with the In-Memory database to fast access. The system
+generates a unique identifier for each timeseries, and throughout the WDIAS, other
+microservice use it to handle data for fast access.
+Export module microservice follows the same concepts and provides the capability
+to export the data into required formats of the weather models.
 
@@
 
+as shown in Figure 3.4, when a request
+with a larger size comes to the system, it stores the data for asynchronously process
+the data and responds with a unique id that can use to verify whether data processed
+successfully or not. First it stores the data and publish an event to another service to process it. After successfully process the data by other service, it updates the system status.
+
+The \acrshort{wdias} provides a simple RESTful API to interact with timeseries metadata and other modules.
+\begin{itemize}
+    \item \texttt{/parameter} - CRUD operations on parameters
+    \item \texttt{/timestep} - CRUD operations on time step
+    \item \texttt{/location/point and /location/regualr-grid} - CRUD operations on point location and regular grid locations
+    \item \texttt{/timeseries} - CRUD operations on timeseries
+    \item Import
+    \begin{itemize}
+        \item \texttt{/import/json/raw} - Import JSON data in raw format
+        \item \texttt{/import/csv/raw} - Import CSV data in raw format
+        \item \texttt{/import/ascii-grid/upload} - Upload ASCII JSON Grid files
+    \end{itemize}
+    \item Export
+    \begin{itemize}
+        \item \texttt{/export/json/raw} - Export JSON data in raw format
+        \item \texttt{/export/ascii-grid/binary} - Download ASCII JSON Grid file
+    \end{itemize}
+    \item Extensions
+\end{itemize}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{subse:wdias_database}
+
+The foundation of the \acrshort{wdias} is data-centric and build around the timeseries data.
+
+\paragraph{Timeseries}-- \emph{A timeseries is simply a series of data points ordered in time}.
+In the weather domain, its interest in timeseries in perspective of observations to forecasting.
+Each timeseries, the data points can be formed in different formats as well.
+For example, scalar (0D), vector (1D), grid (2D), and polygon (2D).
+
+Following list is the timeseries metadata which can use to uniquely identify one timeseries from another which are call as \emph{key attributes}.
+
+\begin{itemize}
+    \item \textbf{Module ID} -  String field which describe the source of the data generated.
+    \item \textbf{Value Type} -  Scalar, Vector, Grid type
+    \item \textbf{Location} - Location of the timeseries. Point location, regular grid location or irregular grid location.
+    \item \textbf{Parameter} - variable measuring against a location
+    \item \textbf{Timeseries Type} - Such as Historical or forecast
+    \item \textbf{Time Step} - Unit of Second, Minute, Hour, Day, Week, Month, Year, or NonEqualDistance. One of multiplier or divider can be used to define the interval between each measurement.
+\end{itemize}
+
+Scalar data point only consist of a single value.
+And Vector data point consists of two values such as magnitude and the direction of the Vector.
+But for Grid data, a point can consist of multiple values.
+To get the advantage of storing data efficiently, we can use a set of different databases based on the advantage of using them for each valueType.
+To support search queries with lower latency, it required to use indexing for the fast search for timeseries metadata.
+Further, Geo-based indexing is required to support Geo-based search queries based on the locations.
+Above capabilities achieved by using a database structure with compose of multiple databases as shown in \cref{pfi:database_structure}.
+
 \begin{figure}[htbp]
 \centerline{\includegraphics[width=0.4\textwidth]{method/microservice/wdias_database_structure.jpg}}
-\caption{Hierarchical database.}
-\label{pfi:hierarchical_database}
+\caption{\acrshort{wdias} database structure.}
+\label{pfi:database_structure}
 \end{figure}
+
+Since metadata consists of multiple key attributes, the data can be efficiently store using a Relational Database Management System (RDBMS).
+Two instances of Timeseries database is using in the WDIAS system by adapter-scalar and adapter-vector services.
+Use \acrfull{netCDF} for store the Grid data which support the creation, access, and sharing of array-oriented scientific data.
+And  in-memory database for caching for fast access the frequent access data in adapter-metadata and adapter-extension.
+Using a document-oriented database with support the Geo searching capabilities.
 
@@
 \label{psubse:data_preprocessing}
+
+The \acrshort{wdias} provides the data preprocessing capabilities via extension modules with a simple generic mathematical function model.
 
@@
 
+Each extension is considering as a mathematical function which can take \texttt{p} number of input timeseries variables and output \texttt{n} number of timeseries variables.
+Other than that, at the time of processing the system can configure to provide bind constant which can provide while configuring an extension.
+This means it is possible to change the behavior of an existing function by providing different bind constant at the time of creating new triggers for an extension.
+The system allow to create new triggers and update them at the run time via POST requests.
+
+\begin{lstlisting}[language=Python]
+{
+    "extensionId": "", // An unique identifier for new extension trigger
+    "extension": "Interpolation/Transformation/Validation",
+    "function": "", // microservice which handles the function mapping
+    "variables": [ // Array of timeseries mapping to variables
+        {
+            "variableId": "",
+            "metadata/metadtaIds": {
+            }
+        }
+    ],
+    "inputVariables": [], // Input timeseries
+    "outputVariables": [], // Output timeseries
+    "trigger": [ // When to trigger the function
+        {
+            "trigger_type": "OnChange/OnTime",
+            "trigger_on": []
+        }
+    ],
+    "options": { // Run time bind contant data for the extension
+    }
+}
+\end{lstlisting}
+
+Extension Handler is responsible for triggering the correct Extension with metadata when there is any change on the subscribed extension trigger's \emph{OnChange} timeseries.
+Extension Handler is responsible for triggering the correct Extension with metadata at a given time which is provided at the creation on extension trigger with the value of OnTime cronjob string value.
+To improve the performance of triggering cronjobs at given time schedules, the WDIAS added few optimization mechanisms.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+Other than the metadata manipulation API mentioned in \cref{psubse:microservice_architecture}, the \acrshort{wdias} also supports timeseries search queries and Geo queries.
+As an example it can \emph{query timeseries in an area} This operation uses \texttt{geoWithin} search operator for the simplicity.
+Other than it can also support query timeseries in an area by parameter, query available timeseries by locations and query locations within an area etc.
+\begin{lstlisting}
+    POST <HOST_NAME>/query/timeseries
+    JSON Body:
+    {
+        "geoJson": {
+            "type": "Polygon",
+            "coordinates": [
+                [
+                    [
+                        <longitude>,
+                        <latitude>
+                    ],
+                    ...
+                ]
+            ]
+        }
+    }
+\end{lstlisting}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{pse:performance_analysis}
-%\section{Performance Analysis}
 

### 2020-02-20 lit/sec_3-other-systems.tex
Reduce image size of DIAS
Add methodology summary

@@
     \centering
-    \includegraphics[width=1\textwidth]{lit/other/dias_common_base_application_platform.png}
+    \includegraphics[width=1\textwidth]{lit/other/dias_common_base_application_platform.jpg}
     \caption[DIAS’s common base application platform.]{DIAS’s common base application platform \cite{Kawasaki2018DataReduction}.}
@@
 \label{se:lit_summary}
-Several related works discussed above in this chapter, mainly focus on the issue of storing data which are ingested from different sources with different formats efficiently.
+Several related works discussed above in this Chapter, mainly focus on the issue of storing data which are ingested from different sources with different formats efficiently.
 The \acrshort{fews} and \acrshort{madis} are using the \acrshort{netCDF} as the common data format to store the data which is one of the best solutions available with modern technologies as well.

### 2020-02-20 method/sec_3-microservice.tex
Add methodology summary

@@
 \label{sebse:wdias_microservices}
-As seen in Figure of \cref{fi:wdias_micro_on_demand} and \cref{fi:wdias_micro_async} each circle represents a microservice, and those are implemented as containerized applications.
+As seen in Figure of \cref{fi:wdias_micro_on_demand} and \cref{fi:wdias_micro_async} each circle represents a microservice in the \acrshort{wdias}, and those are implemented as containerized applications.
 \begin{figure}[htp]
@@
 \end{figure}
-\cref{fi:wdias_micro_on_demand} shows the clear separation of microservices into the modules of the \acrshort{wdias}.
+\cref{fi:wdias_micro_separation} shows the clear separation of microservices into the modules of the \acrshort{wdias}.
 As shown, each adapter has an isolated database, and the database is hosted separately for the high performance.

### 2020-02-20 method/sec_5-data_preprocess.tex
Add methodology summary

@@
 
-The data imported via imported modules may have incorrect data, missing data and not compatible with direct feed into simulation modules. 
-Thus it required to preprocess data before going to use it in such cases.
-The WDIAS supports these capabilities via Extensions.
+The data imported via import modules may have incorrect data, missing data and not compatible with direct feed into simulation modules. 
+Thus it required to preprocess the data before use it.
+The WDIAS supports these capabilities via the \emph{extension} modules.
 The current system has a few inbuilt extensions such as Interpolation, Transformation, and Validation.

### 2020-02-20 method/sec_7-summary.tex
Add methodology summary

\section{Summary}
\label{se:method_summary}

Throughout this Chapter, it discussed about the methodology of designing and implementing the \acrshort{wdias} based on the concepts studied on \cref{ch:literature}. It uses microservice architecture over using \acrshort{soa} with a \acrshort{esb} to avoid the draw back of streaming bulk data over an \acrshort{esb}. In order to take the full advantage of using microservice architecture, we moved to container orchestration based architecture rather building tightly coupled microservices with actor model.
While implementing the import and export modules, those modules follows the architecture style of \emph{Smart Endpoints and Dumb Pipes} and many other places. It implement each microservice as a containerized application which can deploy independent of other microservices. Also it uses the pattern of \emph{database per service} with combining different type of database systems to create the \acrshort{wdias} database structure. Further it provides a comprehensive extension modules system which allow users to preprocess data with creating new trigger without any downtime for system configuration. It indexing mechanism with Geo query support most of the required queries to search for any timeseries data.

### 2020-02-21 Paper.tex
Peper workload generation

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Test Plan and Workload}
+\subsection{Load Testing Plan}
+\label{psubse:test_plan}
+
+The test plan is to perform load testing on whole system, and analyze the scalability of the system while measuring the operations perform on each module.
+Two variables can vary while doing performance testing.
+\begin{enumerate}
+    \item Number of requests made to the system at a given time (\acrfull{rps})
+    \item Request size
+\end{enumerate}
+
+\acrshort{wdias} is getting a mix of all the data types in the percentages of 70\% scalar, 20\% vector, and 10\% grid values.
+\cref{pfi:performance_study} shows for a given request size the RPS increased in steps.
+In each step, the RPS holds for a moment to give some time for the system to get stabilized.
+
 \begin{figure}[htbp]
 \centerline{\includegraphics[width=0.5\textwidth]{results/work_load/performance_study_v4.jpg}}
-\caption{Performance study.}
-\label{pfi:performance_Study}
+\caption{\acrshort{wdias} load testing plan with changing the request size and \acrshort{rps}}
+\label{pfi:performance_study}
 \end{figure}
+
+Holding the peak load will help to show whether the system is capable of scaling more than the proposed load testing plan.
+After the peak, the test case goes through a cool-down period to measure the ability to shrink down the resources when there is not any load on the system.
+During the test plan, it runs for 30minutes of period with changing the request size form 1-hour data to 15 minutes data.
+Then another 30 minutes load test enabling the auto scaling of container orchestration system, and perform 5minutes test run with timeseries queries.
+The the results are evaluate against the performance metrics of throughput, latency, resource utilization and auto-scaling.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Experimental Setup}
+\label{psubse:experimental_setup}
+
+During the performance test, it creates 1000 timeseries using the locations are taken from Google's Countries Public Data set \cite{GoogleGoogleCounties}, and uses static 100 Grid locations for store Grid data.
+Load test perform using \acrshort{jmeter} and used the Distributed Testing feature to generate higher load.
+It uses the master-slave approach and it allowed to handle all the test cases via single instance, rather handling separate instances.
+The system is capable of storing any numeric value up to 3 decimal points.
+It does not make any difference based on the parameter type whether it is the precipitation or the temperature.
+Thus during the performance testing, \acrshort{jmeter} uses real precipitation data from \acrshort{curw}.
+One month period of data for five weather stations has been using to prepare the test data.
+
+While implementing the test cases for WDIAS, it uses the Concurrency Thread Group
+with Throughput Shaping Timer because it supports the open workload approach.
+
+\begin{itemize}
+    \item \emph{closed system model} \cite{Haggett1998AnWales} -- a new request is only triggered by the completion of a previous request, following by a think time.
+    \item \emph{open system model} -- new requests arrival independently of completions.
+\end{itemize}
+
+\acrshort{wdias} is using the \acrfull{k8s} as the container orchestration system which is an open-source system for automating deployment, scaling, and management of containerized applications.
+They are many \acrshort{k8s} solutions available as a cloud service, we used \acrfull{eks} based on the availability.
+\cref{ptab:aws_eks_nodes} shows the list of nodes/computers used during the performance test.
+
+\begin{table}[ht]
+\centering
+\caption{\acrshort{eks} nodes}
+\footnotesize
+\begin{tabular}{|l|c|c|c|c|l|}
+\hline
+\textbf{Node Label} & \textbf{vCPU} & \textbf{RAM (GB)} & \textbf{Storage (GB)} & \textbf{Quantity} & \textbf{EC2 Name} \\ \hline
+core & 16 & 32 & 15 & 1 & c5.4xlarge \\ \hline
+grid & 8 & 16 & 25 & 1 & c5.2xlarge \\ \hline
+scalar & 8 & 16 & 20 & 1 & c5.2xlarge \\ \hline
+test & 4 & 10.5 & 5 & 1 & c5n.xlarge \\ \hline
+\end{tabular}
+\label{ptab:aws_eks_nodes}
+\end{table}
+
+To get better performance using the available resources, it is possible to schedule each microservice into a predefined set of nodes.
+Pods are assigned to the nodes \cref{tab:aws_eks_nodes} based on the node label as below;
+\begin{itemize}
+    \item \emph{core} -- metadata, extensions, query, status and extension services
+    \item \emph{grid} -- grid adapter, import and export grid data
+    \item \emph{scalar} -- scalar and vector adapters, import and export of same data types
+    \item \emph{test} -- \acrshort{jmeter} and metric server
+\end{itemize}
 

### 2020-02-21 method/sec_5-data_preprocess.tex
Peper workload generation

@@
 
-\subsection{Transformation}-- Simple arithmetic manipulation, Time interval transformation and Shifting the series in time Specific hydro-meteorological transformation such as stage discharge relationships.
+\subsection{Transformation}- Simple arithmetic manipulation, Time interval transformation and Shifting the series in time Specific hydro-meteorological transformation such as stage discharge relationships.
 \begin{figure}[htp]
@@
 
-\subsection{Validation}-- Checks for counting reliable, doubtful, unreliable, and missing values
+\subsection{Validation}- Checks for counting reliable, doubtful, unreliable, and missing values
 \begin{figure}[htp]

### 2020-02-21 results/sec_1-test_plan.tex
Fix: All test plan
Peper workload generation

@@
 \begin{enumerate}
-    \item \emph{Import} modules (integration modules)
-    \item \emph{Export} modules (Dissemination modules)
-    \item \emph{Extension} modules (Assimilation modules)
+    \item \emph{Import} modules \leftarrow Integration modules)
+    \item \emph{Export} modules \leftarrow Dissemination modules
+    \item \emph{Extension} modules \leftarrow Assimilation modules
 \end{enumerate}
 Other than above, \emph{adapter modules} act as the core modules and the base of the system.
-Also, query modules allow the users to query for the timeseries based on the metadata and enable performing Geo-based queries based on the locations.
+Also, \emph{query module} allows the users to query for the timeseries based on the metadata and enable performing Geo-based queries based on the locations.
 
-The test plan is to perform the load test on each above module as a separate entity to analyze the individual module scalability.
-Then perform load testing on the whole system, and analyze the scalability in the system. Two variables can vary while doing performance testing.
+% The test plan is to perform the load test on each above module as a separate entity to analyze the individual module scalability.
+% Then perform load testing on the whole system, and analyze the scalability in the system. Two variables can vary while doing performance testing.
+The test plan is to perform load testing on whole system, and analyze the scalability of the system while measuring the operations perform on each module.
+Two variables can vary while doing performance testing.
 \begin{enumerate}
@@
 
-\cref{fi:performance_study_load} shows the summary of this section, load testing plan with changing the request size and perform load testing with increasing the \acrshort{rps} over time.
+\cref{fi:performance_study_load} shows the summary of this Section, load testing plan with changing the request size and perform load testing with increasing the \acrshort{rps} over time.
 As shown in the figure, for a given request size the \acrshort{rps} increased in steps.
@@
         \item Plan for 30 minutes of the test run with the request size of 15min data with auto-scaling.
-        \item All test plan run against 60min, 30min and 15min request size of data. Another test plan runs with enabling the auto-scaling. (total of 2 hours)
+        \item Test plan run against 60min, 30min and 15min request size of data. Another test plan runs with enabling the auto-scaling. (total of 2 hours)
     \end{itemize}

### 2020-02-21 Paper.tex
Paper: fixed table width

@@
 \usepackage{biblatex}
+\usepackage{adjustbox}
 
@@
 \begin{itemize}
-    \item \textbf{Module ID} -  String field which describe the source of the data generated.
-    \item \textbf{Value Type} -  Scalar, Vector, Grid type
-    \item \textbf{Location} - Location of the timeseries. Point location, regular grid location or irregular grid location.
-    \item \textbf{Parameter} - variable measuring against a location
-    \item \textbf{Timeseries Type} - Such as Historical or forecast
-    \item \textbf{Time Step} - Unit of Second, Minute, Hour, Day, Week, Month, Year, or NonEqualDistance. One of multiplier or divider can be used to define the interval between each measurement.
+    \item \texttt{Module ID}--  String field which describe the source of the data generated.
+    \item \texttt{Value Type}--  Scalar, Vector, Grid type
+    \item \texttt{Location}-- Location of the timeseries. Point location, regular grid location or irregular grid location.
+    \item \texttt{Parameter}-- variable measuring against a location
+    \item \texttt{Timeseries Type} - Such as Historical or forecast
+    \item \texttt{Time Step}-- Unit of Second, Minute, Hour, Day, Week, Month, Year, or NonEqualDistance. One of multiplier or divider can be used to define the interval between each measurement.
 \end{itemize}
@@
 \begin{enumerate}
-    \item Number of requests made to the system at a given time (\acrfull{rps})
+    \item \acrfull{rps}
     \item Request size
@@
 \caption{\acrshort{eks} nodes}
+\begin{adjustbox}{width=0.45\textwidth}
 \footnotesize
@@
 \end{tabular}
+\end{adjustbox}
 \label{ptab:aws_eks_nodes}
@@
 \label{psubse:performance_evaluation}
+
+While performing the load testing, each test plan performed around 310k of total sample requests within 30minutes.
+The ratio between Scalar and Vector to Grid operations around 71k:8k with the ratio of 90\%:10\%.
+This implies that test cases were able to perform as planned in the \cref{psubse:test_plan}.
+Insert
+
 \begin{table}[htbp]
-\caption{Table type styles}
+\caption{ Throughput and Latency of load testing with 60min data}
 \begin{center}
+\begin{adjustbox}{width=0.45\textwidth}
+\footnotesize
 \begin{tabular}{|c|c|c|c|c|c|c|}
 \hline
-\textbf{Label} & \textbf{Samples} & \textbf{Avg} & \textbf{Min} & \textbf{Max} & \textbf{Std} & \textbf{90\% Line} \\ \hline
-Insert Scalar & 71727 & 34 & 13 & 1777 & 118.78 & 27 \\ \hline
-Retrieve Scalar & 71693 & 7 & 5 & 1608 & 18.72 & 9 \\ \hline
-Insert Grid & 7968 & 87 & 77 & 233 & 14.07 & 98 \\ \hline
-Retrieve Grid & 7965 & 89 & 63 & 1694 & 37.79 & 110 \\ \hline
-Query & 71704 & 1 & 0 & 203 & 2.05 & 2 \\ \hline
-\textbf{TOTAL} & 310734 & 130 & 0 & 1777 & 212.35 & 501 \\ \hline
-\multicolumn{4}{l}{$^{\mathrm{a}}$Avg: Average Latency, Std: Standard Deviation.}
+\textbf{Label} & \textbf{Samples} & \textbf{Avg$^{\mathrm{a}}$} & \textbf{90\%$^{\mathrm{b}}$} & \textbf{S.D.$^{\mathrm{c}}$} & \textbf{Error \%} & \textbf{RPS} \\ \hline
+Insert Timeseries & 71826 & 28 & 31 & 58.74 & 0.00\% & 40.5 \\ \hline
+Retrieve Timeseries & 71796 & 8 & 10 & 4.18 & 0.00\% & 40.7 \\ \hline
+Insert Grid & 7982 & 23 & 26 & 4.23 & 0.06\% & 4.5 \\ \hline
+Retrieve Grid & 7979 & 68 & 75 & 10.11 & 0.00\% & 4.5 \\ \hline
+Query: Location & 71804 & 3 & 3 & 1.52 & 0.00\% & 40.5 \\ \hline
+\textbf{TOTAL} & 311182 & 127 & 503 & 207.80 & 0.00\% & 175.4 \\ \hline
+\multicolumn{4}{l}{$^{\mathrm{a}}$Avg: Average Latency, $^{\mathrm{b}}$S.D.: Standard Deviation, $^{\mathrm{c}}$90\%: 90\% percentile.}
 \end{tabular}
-\label{ptab:obs_all_auto_15_min_summary_latency}
+\end{adjustbox}
+\label{ptab:obs_all_60_min_summary_throughput}
 \end{center}
@@
 \begin{table}[htbp]
-\caption{Table type styles}
+\caption{ Throughput and Latency of load testing with 30min data}
 \begin{center}
-\begin{tabular}{|c|c|c|c|c|c|}
+\begin{adjustbox}{width=0.45\textwidth}
+\footnotesize
+\begin{tabular}{|c|c|c|c|c|c|c|}
 \hline
-\textbf{Label} & \textbf{Samples} & \textbf{Avg} & \textbf{Std. Dev.} & \textbf{Error \%} & \textbf{RPS} \\ \hline
-Insert Scalar & 71727 & 34 & 118.78 & 0.00\% & 40.5 \\ \hline
-Retrieve Vector & 71693 & 7 & 18.72 & 0.00\% & 40.5 \\ \hline
-Insert Grid & 7968 & 87 & 14.07 & 0.18\% & 4.5 \\ \hline
-Retrieve Grid & 7965 & 89 & 37.79 & 0.00\% & 4.5 \\ \hline
-Query & 71704 & 1 & 2.05 & 0.00\% & 40.5 \\ \hline
-\textbf{TOTAL} & 310734 & 130 & 212.35 & 0.00\% & 175.3 \\ \hline
-\multicolumn{4}{l}{$^{\mathrm{a}}$Avg: Average Latency.}
+\textbf{Label} & \textbf{Samples} & \textbf{Avg$^{\mathrm{a}}$} & \textbf{90\%$^{\mathrm{b}}$} & \textbf{S.D.$^{\mathrm{c}}$} & \textbf{Error \%} & \textbf{RPS} \\ \hline
+Insert Timeseries & 71759 & 29 & 32 & 50.97 & 0.00\% & 40.5 \\ \hline
+Retrieve Timeseries & 71730 & 9 & 10 & 6.04 & 0.00\% & 40.6 \\ \hline
+Insert Grid & 7972 & 44 & 49 & 8.17 & 0.08\% & 4.5 \\ \hline
+Retrieve Grid & 7971 & 81 & 93 & 15.15 & 0.00\% & 4.5 \\ \hline
+Query: Location & 71734 & 3 & 3 & 1.90 & 0.00\% & 40.5 \\ \hline
+TOTAL & 310878 & 129 & 0 & 207.10 & 0.00\% & 175.3 \\ \hline
+\multicolumn{4}{l}{$^{\mathrm{a}}$Avg: Average Latency, $^{\mathrm{b}}$S.D.: Standard Deviation, $^{\mathrm{c}}$90\%: 90\% percentile.}
 \end{tabular}
+\end{adjustbox}
+\label{ptab:obs_all_30_min_summary_throughput}
+\end{center}
+\end{table}
+
+\begin{table}[htbp]
+\caption{ Throughput and Latency of load testing with 15min data}
+\begin{center}
+\begin{adjustbox}{width=0.45\textwidth}
+\footnotesize
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline
+\textbf{Label} & \textbf{Samples} & \textbf{Avg$^{\mathrm{a}}$} & \textbf{90\%$^{\mathrm{b}}$} & \textbf{S.D.$^{\mathrm{c}}$} & \textbf{Error \%} & \textbf{RPS} \\ \hline
+Insert Timeseries & 71775 & 30 & 41 & 51.71 & 0.00\% & 40.5 \\ \hline
+Retrieve Timeseries & 71736 & 23 & 32 & 50.18 & 0.00\% & 40.6 \\ \hline
+Insert Grid & 7975 & 91 & 112 & 19.58 & 1.42\% & 4.5 \\ \hline
+Retrieve Grid & 7972 & 118 & 165 & 56.15 & 0.00\% & 4.5 \\ \hline
+Query: Location & 71749 & 3 & 4 & 2.32 & 0.00\% & 40.5 \\ \hline
+\textbf{TOTAL} & 310934 & 134 & 503 & 206.40 & 0.04\% & 175.4 \\ \hline
+\multicolumn{4}{l}{$^{\mathrm{a}}$Avg: Average Latency, $^{\mathrm{b}}$S.D.: Standard Deviation, $^{\mathrm{c}}$90\%: 90\% percentile.}
+\end{tabular}
+\end{adjustbox}
+\label{ptab:obs_all_15_min_summary_throughput}
+\end{center}
+\end{table}
+
+\begin{table}[htbp]
+\caption{Throughput and Latency of load testing with 15min data while enabled K8s
+auto-scaling}
+\begin{center}
+\begin{adjustbox}{width=0.45\textwidth}
+\footnotesize
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline
+\textbf{Label} & \textbf{Samples} & \textbf{Avg$^{\mathrm{a}}$} & \textbf{90\%$^{\mathrm{b}}$} & \textbf{S.D.$^{\mathrm{c}}$} & \textbf{Error \%} & \textbf{RPS} \\ \hline
+Insert Timeseries & 71727 & 34 & 27 & 118.78 & 0.00\% & 40.5 \\ \hline
+Retrieve Timeseries & 71693 & 7 & 9 & 18.72 & 0.00\% & 40.5 \\ \hline
+Insert Grid & 7968 & 87 & 98 & 14.07 & 0.18\% & 4.5 \\ \hline
+Retrieve Grid & 7965 & 89 & 110 & 37.79 & 0.00\% & 4.5 \\ \hline
+Query: Location & 71704 & 1 & 2 & 2.05 & 0.00\% & 40.5 \\ \hline
+\textbf{TOTAL} & 310734 & 130 & 501 & 212.35 & 0.00\% & 175.3 \\ \hline
+\multicolumn{4}{l}{$^{\mathrm{a}}$Avg: Average Latency, $^{\mathrm{b}}$S.D.: Standard Deviation, $^{\mathrm{c}}$90\%: 90\% percentile.}
+\end{tabular}
+\end{adjustbox}
 \label{ptab:obs_all_auto_15_min_summary_throughput}

### 2020-02-21 results/sec_2-workload.tex
Paper: fixed table width

@@
 Almost similar to how was the precipitation data proceed, the water level is prepared for Grid data.
-One exception with Grid data during these test cases was, the maximum time step is 30min, instead of 15min due to the larger size of the data.
+The Grid data files are real data output of FLO2D 150 meter hydrology model which uses in the \acrshort{curw}.
+Each file follow the format of ASCII Grid file and consist of 120 rows and 139 columns with using the \texttt{-9} for the missing data as an optimization.
+Each file size is 50,337 Bytes (50 Kilobytes).
+% One exception with Grid data during these test cases was, the maximum time step is 30min, instead of 15min due to the larger size of the data.
 But the \acrshort{wdias} is capable of supporting such request.

### 2020-02-21 results/sec_3-observations.tex
Paper: fixed table width

@@
 
-According to \cref{se:test_plan} section, this section includes the observations after performing the test plans on the \acrshort{wdias} system setup and test plan test up which is explained in \cref{se:workload}.
-
-Sections \ref{subse:obs_test_plan_all_60min} to \ref{subse:obs_test_plan_all_auto_15min} discuss the observations collected with performing the Load test plans over 60 minutes (24 data points), 30 minutes (48 data points) and 15 minutes (96 data points) by variate the request size.
-Then another performance test with enabling auto-scaling as explained in \cref{subse:test_plan_metrics} for high resource utilized microservice.
+According to \cref{se:test_plan} section, This section includes the observations based one the test plans in \cref{se:test_plan} and test plan test up which is explained in \cref{se:workload}.
+Sections \ref{subse:obs_test_plan_all_60min} to \ref{subse:obs_test_plan_all_auto_15min} discuss the observations collected with performing the Load test plans over 60 minutes data (24 data points), 30 minutes data (48 data points) and 15 minutes data (96 data points) by variate the request size.
+Then another performance test with enabling auto-scaling for the higher resource utilized microservices as explained in \cref{subse:test_plan_metrics}.
 
@@
 Noticeably it has 0\% of errors which means that all the requests are completed successfully.
-On average, \acrshort{wdias} handled 40.5 \acrshort{rps} with the given workload.
+On average, \acrshort{wdias} handled 40.5 \acrshort{rps} for Scalar and Vector data with the given workload.
 The performance of the Retrieve of Scalar and Vector Timeseries is similar to insert timeseries due to it depends on it.
 On the other hand, Insert Grid Timeseries data perform with 23ms with almost all the requests perform within the same amount of time, hence the standard deviation is smaller.
+The delay in inserting Grid timeseries smaller because those requests are handling asynchronously.
 Retrieve Grid Timeseries data perform the same but with a bit higher value of latency of 68ms.
-Both insert and retrieve grid timeseries data have 4.5 \acrshort{rps} since it only gets 10\% of the number of requests per given time via the test plan as explained in the data ration in \cref{se:test_plan}.
+Both insert and retrieve grid timeseries data have 4.5 \acrshort{rps} since it only gets 10\% of the number of requests per given time via the test plan as explained in the data ratio in \cref{se:test_plan}.
 
@@
 When the number of active threads increased more than 122, \cref{fi:test_obs_all_60m_response_vs_threads} shows uncertainty in the inserting and retrieving Scalar and Vector data.
+This is because of those data handle on demand and depend on the timeseries database performance.
 

### 2020-02-21 Paper.tex
Paper: performance analysis

@@
 \usepackage{adjustbox}
+\usepackage{tabulary}
 
@@
 
-While performing the load testing, each test plan performed around 310k of total sample requests within 30minutes.
+While performing the load testing, each test plan performed around 310k of total sample requests within 30minutes according to the \cref{ptab:obs_all_60_min_summary_throughput} to \cref{ptab:obs_all_15_min_summary_throughput}.
 The ratio between Scalar and Vector to Grid operations around 71k:8k with the ratio of 90\%:10\%.
 This implies that test cases were able to perform as planned in the \cref{psubse:test_plan}.
-Insert
+Other than insert Grid timeseries, other operations succeed with 0\% error rate.
 
@@
 \begin{center}
-\begin{adjustbox}{width=0.45\textwidth}
 \footnotesize
+\begin{adjustbox}{width=0.49\textwidth}
 \begin{tabular}{|c|c|c|c|c|c|c|}
@@
 \end{table}
+
+The average latency of inserting Scalar and Vector timeseries data increased by 1ms when the request size increased.
+But for the 90\% percentile of insertions increased from 31ms to 41ms.
+But the standard deviation kept same.
+\acrshort{wdias} were able to perform with the same throughput of 40.5 \acrshort{rps} without significant change in latency which shows the scalability of the system.
+While retrieving the Scalar and Vector timeseries data, the system was able to respond with in 10ms for 60minutes and 30minutes data with lesser standard deviation.
+But the latency got double when handling the 15minutes data.
+This caused by heavy writes on the timeseries database.
 
@@
 
+When inserting the Grid timeseries data, the average latency was less than the insert Scalar or Vector data, because of the Grid data handle asynchronously.
+When the number of Grid files doubled, each time the latency also got doubled.
+Notably, the \acrshort{wdias} was able to perform with same throughput with lesser standard deviation.
+Also, for each test case the system was able to kept the same latency throughout test run without any significant change.
+This also show the scalability of the Grid data in the \acrshort{wdias}.
+Retrieving of Grid timeseries data happens on demand during the load test.
+But it is possible to upgrade the system to support asynchronously download alongside with direct download.
+Because of that, the latency of download the the Grid data is bit higher than the other test cases.
+In that case also, the \acrshort{wdias} perform with keeping the same throughput with lower standard deviation which shows the scalability of the export Grid data module.
+
 \begin{table}[htbp]
@@
 \end{table}
+
+Throughout all test plans, the \acrshort{wdias} system performed better on serving the search queries based locations for Scalar and Vector timeseries.
+This is due to using indexing for server such queries.
+The \acrshort{wdias} was able to respond with 3ms most of the cases with keeping lower standard deviation.
+% To get better performance test on the query module, we performed set of complex queries as shown in the \cref{ptab}
 
@@
 
+\cref{ptab:obs_all_auto_15_min_summary_throughput} shows the \acrshort{wdias} performance with 15minutes data, but enabled auto-scaling.
+During above test cases, most resource utilized module was importing Grid data.
+The observations are almost similar to \cref{ptab:obs_all_15_min_summary_throughput}, but notably the error rate of insert Grid timeseries got reduced after enabled the auto-scaling for import Grid data module.
+Also the standard deviation for handling Grid data reduced which means system was able to perform more better than the previous test plan.
+
 \begin{figure}[htbp]
@@
 
+\cref{pfi:test_obs_auto_all_15_min_latency_vs_hits} shows the latency of each test case throughout total time of load testing with 15minutes data while enabled auto-scaling.
+As the Figure clearly shows while increasing the number of server hits for each test case, the system kept the latency constant without significant change.
+At the peak time, handling Grid data has some disturbances and inserting Scalar and Vector data has some random spikes in the latencies.
+
 \begin{figure}[htbp]
@@
 \end{figure}
+
+\cref{pfi:test_obs_auto_all_15_min_throughput_vs_threads} shows the total server's transaction throughput against the number of active threads.
+The formula for total server transaction throughput is \(<active threads> * 1 second / <1  thread response time>\) \cite{JMeterPluginsTransactionPlugin}.
+It shows the statistical maximum possible number of transactions based on the number of users accessing the application.
+By combining the \cref{pfi:test_obs_auto_all_15_min_latency_vs_hits}, this graph shows that the throughput of the system gets increased without much change in the latency, thus it proves the scalability of the \acrshort{wdias}.
+
+\begin{figure}[htp]
+    \centering
+    \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_import_grid_pod.png}
+    \caption{Load testing with auto-scaling import ascii grid number of pods over time.}
+    \label{pfi:obs_all_auto_15m_import_grid_pod}
+\end{figure}
+
+\cref{pfi:obs_all_auto_15m_import_grid_pod} shows the number of import-ascii-grid-upload pods scheduled overtime.
+The auto-scaling enabled with the configurations of 1 to 10 pods with the recommended CPU usage with 80\%.
+And the pods scheduled with 1 CPU requested, and limit with 2 CPUs per pod.
+As the graph shows, 3 pods scheduled at the initial as per the configuration of the helm chart.
+While increasing the workload, new pods get spawn while keeping the constraint of 80\% of recommended CPU utilization.
+After \acrshort{k8s} spawn 10 maximum pods, it stops spawning new pods.
+But the pods were able to perform with vertical scaling since those are not hit the CPU limit of 2.
 

### 2020-02-21 Paper.tex
Paper finished with summary

@@
     \centering
-    \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_import_grid_pod.png}
+    \includegraphics[width=0.5\textwidth]{results/obs/all_auto/obs_all_auto_15m_import_grid_pod.png}
     \caption{Load testing with auto-scaling import ascii grid number of pods over time.}
@@
 \label{psubse:performance_metrics}
-\paragraph{Latency}
-The latency for each operation type kept constant over the whole test plan run time without any significant change.
+
+The \emph{Latency} for each operation type kept constant over the whole test plan run time without any significant change.
 When the request size increased from 24 data points to 96 data points, the latency increase throughout the whole test plan with a smaller number.
-But for each test run the latency kept constant over the time.
-During the \cref{subse:obs_test_plan_all_auto_15min} test run, the performance of the Grid data got better when compared to the \cref{subse:obs_test_plan_all_15min}.
-Which means by adding more resources to the \acrshort{wdias}, it can handle more workload on the system.
+But for each test run, the latency kept constant over time.
+During the \cref{ptab:obs_all_auto_15_min_summary_throughput} test run, the performance of the Grid data got better when compared to \cref{ptab:obs_all_15_min_summary_throughput}.
+This means by adding more resources to the \acrshort{wdias}, it can handle more workload on the system.
 
-\paragraph{Throughput}
-While keeping the latency constant without significant change, the throughput of the \acrshort{wdias} kept constant while increasing the request size from 60min data (24 data points) to 15min data (96 data points) for all the data types such as Scalar, Vector and Grid.
-When number of active threads increased, the \acrshort{wdias} able to provide the same throughput with maintaining the latency stable.
+While keeping the latency constant without significant change, the \emph{throughput} of the \acrshort{wdias} kept constant while increasing the request size from 60min data (24 data points) to 15min data (96 data points) for all the data types such as Scalar, Vector, and Grid.
+When the number of active threads increased, the \acrshort{wdias} able to provide the same throughput with maintaining the latency stable.
 
-One of the reason to having deviations at the peak time due to use of single instance for the data consistency such as \acrshort{influxdb} for Scalar and Vector data, and netCDF with parallel support for Grid data.
-Further it is possible to increase the performance of these bottlenecks much higher such as using \acrshort{influxdb} Commercial cluster support for high availability or horizontal scaling of \acrshort{influxdb}.
-With \acrshort{influxdb} cluster, it is possible to run multiple pods of adapter-scalar and adapter-vector for support more server hits per second.
+One of the reasons for having deviations at the peak time due to uses of single instance for the data consistency such as \acrshort{influxdb} for Scalar and Vector data, and netCDF with parallel support for Grid data.
+Further, it is possible to gain more performance using the databases with configure with high scalability and high availability features such as Sharding and Replication.
 
-Adapter-grid is using a Python wrapper for netCDF FORTRAN implementation with parallel IO enabled.
-This has some performance issues as well as memory leak issues.
-Since each microservice in the \acrshort{wdias} independent of technology that can use to implement the service, it will increase the performance if the adapter-grid directly ported to netCDF with a low level language such as C or FORTRAN.
-Other than \acrshort{eks}, if users can use a \acrshort{k8s} cluster which support Persistent Volumes with the access of Read Write  Many \cite{LinuxFoundationPersistentKubernetes} , then it is possible to run multiple pods of adapter-grid and increase the throughput of the \acrshort{wdias}.
+When looking into the \emph{resource utilization} of \acrshort{wdias}; since it is using the \acrshort{k8s} as the container orchestration system, it allows us to scale up and cool down the system as required based on the workload.
+This demonstrates the test plan of \cref{subse:obs_test_plan_all_auto_15min}, and the system gets scale up to the maximum at the peak time.
+Then cool down to a single pod after finishing the test cases.
+Given above \acrshort{wdias} can run from 1 CPU node to nodes with 100 CPUs.
+As described in the \cref{psubse:microservice_architecture}, it uses many of the concepts of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities.
 
-\paragraph{Resource Utilization}
-Since \acrshort{wdias} using the \acrshort{k8s} as the container orchestration system, it allows to scale up and cool down the system as required based on the workload.
-This demonstrate on the test plan of \cref{subse:obs_test_plan_all_auto_15min}, and the system get scale up to the maximum at the peak time.
-Then cool down to single pod after finishing the test cases.
-Given above \acrshort{wdias} can run from 1 CPU node to nodes with 100 CPUs.
-As described in the \cref{se:microservice}, it uses the many of the concept of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities.
+The \acrshort{wdias} supports \emph{auto scaling} by out of the box with \acrshort{k8s}.
+Services can configure with a maximum number of pods to avoid over resource usage.
+When there is not much workload on the system, the system cools down to fewer pods to save more resources.
+When there is an issue with a pod, \acrshort{k8s} auto-schedule another pod and remove the unhealthy pod.
+Also, it allows updating the system without any downtime with rollback updates.
 
-\paragraph{Auto Scaling}
-The \acrshort{wdias} supports auto-scaling by out of the box with \acrshort{k8s}.
-Services can configure with maximum number of pods in order to avoid over resource usage.
-When there is not much workload on the system, system cool down to less pods in order to save more resources.
-When there is any issue with a pod, \acrshort{k8s} auto schedule another pod and remove the unhealthy pod.
-Also it allows to update the system without any down time with rollback updates.
-
-\paragraph{Risk of Unable to Process Data}
-During the test performance, the \acrshort{wdias} processed many requests with higher request size than the normal usage with lower rate of failures to process the requests, mainly with insert Grid data.
-If the usage of \acrshort{wdias} want to reduce the risk of unable to process data, then system can configure to run with redundant pods in order to handle spike of workloads.
-Also while configure for the auto-scaling, the \acrshort{k8s} can configure to maintain lower amount of CPU usage such as 50\% to 60\% rather 80\%.
+\emph{Risk of unable to process data} during the test performance, the \acrshort{wdias} processed many requests with higher request size than the normal usage with a lower rate of failures to process the requests, mainly with insert Grid data.
+If the usage of \acrshort{wdias} wants to reduce the risk of unable to process data, then the system can configure to run with redundant pods to handle spike of workloads.
+Also while configuring for the auto-scaling, the \acrshort{k8s} can configure to maintain a lower amount of CPU usage such as 50\% to 60\% rather  than 80\%.
 Such configuration with always spawn new pods to handle double of current peak load.
@@
 \label{psubse:limitations}
-\dbc{Make this the dicussion and a sub-section of Sec. 4}
+\dbc{Make this the discussion and a sub-section of Sec. 4}
 
-\paragraph{Lack of data preprossessing modules}
-The extension module enable plugin system to integrate prepossessing modules which can use for process the data which are inserted to the system or based on regular intervals.
-Also \acrshort{wdias} provide a more generic open interface approach to create more preprocessing modules.
-Since \acrshort{wdias} is an open source system, it expect more modules to be create by the community.
-When compared to other system like \acrshort{fews}, current system only have few extension for the testing purpose.
-This is one of the major area that need to be improved.
+As we showed that the \acrshort{wdias} can perform better, there are some improvements that can add to improve the performance and usability of the system.
 
-\paragraph{Supporting Irregular Grids}
-At the moment \acrshort{wdias} does not support Irregular Grids, but it has the API endpoints define for the implementation which can follow the same microservice architecture.
-The scope of the \acrshort{wdias} does not belong such level of implementation and the scope has reduced by removing such components from the system.
+\emph{Lack of data preprocessing modules}:
+The extension module enables the plugin system to integrate prepossessing modules that can use for process the data which are inserted to the system or based on regular intervals.
+Also, \acrshort{wdias} provides a more generic open interface approach to create more preprocessing modules.
+Since \acrshort{wdias} is an open-source system, it expects more modules to be created by the community.
+When compared to other systems like \acrshort{fews}, the current system only have few extensions but it is more easy to add new extensions compared to other systems.
 
-\paragraph{Grid data performance}
-As mentioned in the \cref{se:conclusion}, the adapter-grid is using a Python wrapper for netCDF FORTRAN implementation with parallel IO enabled.
-This has some performance issues as well as memory leak issues.
-Since each microservice in the \acrshort{wdias} independent of technology that can use to implement the service, it will increase the performance if the adapter-grid directly ported to netCDF with a low level language such as C or FORTRAN.
-They are some future work that can focus on improving the performance of grid data.
-
-\paragraph{Define infrastructure as code}
-Physical nodes for the \acrshort{k8s} cluster created using Cloud Computing provider such as \acrshort{eks}.
-And defining the each pod resource limitations at the helm chart level.
-But the infrastructure that need to deploy the \acrshort{wdias} can define as code such as using tools like Teraform which is independent of the Cloud Computing provider.
-Using such tool, users will able to easy deploy the \acrshort{wdias} on any Cloud provider without much hassle.
-
-\paragraph{Further improve hierarchical database performance}
-As further described in \cref{se:conclusion}, it is possible to increase the performance of these bottlenecks much higher such as using \acrshort{influxdb} Commercial cluster support for high availability or horizontal scaling of \acrshort{influxdb}.
-With \acrshort{influxdb} cluster, it is possible to run multiple pods of adapter-scalar and adapter-vector for support more server hits per second.
-Other than that, the \acrshort{wdias} performance can improve via partitioning the timeseries key space into multiple \acrshort{influxdb} instances.
-The adapter-scalar or adapter-vector can improve to plug multiple instance of \acrshort{influxdb} instances by changing the configurations.
-As an example, based on the key attribute \cref{subse:timeseries_key_attributes} Timeseries Type, the adapter-scalar can connect to four instance of \acrshort{influxdb} instances such as  External Historical, External Forecast, Simulated Historical, and Simulated Forecast etc.
+Improve the \emph{Grid data performance} by porting \acrshort{netCDF} C or FORTRAN implementation with adapter-grid rather using a Python wrapper.
+Using tools like Terraform which is independent of the Cloud Computing provider \emph{define \acrshort{wdias} infrastructure as code}, then users will able to easily deploy the \acrshort{wdias} on any Cloud provider without much hassle.
+\emph{Tune \acrshort{wdias} database structure performance} with using Z-axis scaling.
+Some of other features are alerting extension modules, publisher subscriber capabilities via extension modules, supporting irregular Grids.
 
@@
 \dbc{Summary is too long. Should not be more than a single para}
-To enhance the accuracy of the weather prediction, it is required to have reliable weather data for \acrshort{nwm}.
-Most of existing weather data systems are proprietary or close sourced, or not up to date with the existing cloud computing technologies.
-We proposed an extendable open source Weather Data Integration and Assimilation Systems which is known as \acrshort{wdias}.
-It focused on providing efficiently integrates weather data from different sources with quality control and supporting steaming large size of data.
-And compatible with current cloud computing technologies and architecture patterns.
+\hl{Just kept the important sections}
 
-First the architecture starts with SOA using a \acrfull{esb}, and then moved to Actor model based architecture.
-After comparing the disadvantages of using such architecture with the system requirements, final architecture come up with modern microservice architecture.
-Based on the microservice architecture patterns and the nature of the weather metadata, the \acrshort{wdias} came up with the idea of hierarchical database structure in order to provide higher performance while store the weather data.
-The system uses \acrshort{influxdb} timeseries database for storing Scalar and Vector timeseries data, and using \acrshort{netCDF} for storing Grid timeseries data.
-Also the system provide a generic open mechanism to integrate new modules as extension in order to enhance the features of the system.
-This capability enable to integrate weather data preprocessing flows as extension modules.
-The extension API provide easy access to create and modify the extension triggers on the fly without stopping the system or any downtime in order to change the configurations.
-The system provides extensive timeseries query endpoints to easy search over the system timeseries metadata with supporting Geo based queries.
+Even though there are many weather data integration systems, most of them are proprietary or closed source and based on basic client-server architectures or monolithic distributed system architectures.
+Thus those are unable to get the advantage of modern computational models such as containerized applications and using the could computing to gain benefits of scalability, high availability and low-cost operations.
+Also for an island like Sri Lanka that having different kinds of weather seasons over the year those software needs to be highly customized.
+In this paper, we present an extendable open source weather data integration and assimilation system known as \acrshort{wdias} which uses modern microservice architecture pattern and cloud computing tools such as container orchestration to gain high scalability and availability.
 
-\acrshort{wdias} performance test is perform using the \acrshort{jmeter} tool's distributed testing capabilities which separately testing each modules.
-Then the test plans are performed with increasing the request size, and monitored the performance metrics.
-The system is setup on the \acrfull{eks} as per the configurations of \cref{subse:test_sys_config}.
-During the performance test plans, the system were able to provide constant throughput by keeping the latency constant while increasing the workload. Which exhibit the scalability of the system.
-With the \acrshort{k8s} auto-scaling, the \acrshort{wdias} were able to elastically adjust the number of pods according to the workload with the given configurations.
+Based on the nature of the weather metadata, the \acrshort{wdias} used a database structure to provide higher performance while storing the weather data optimum.
+As described in \cref{pse:wdias_architecture}, it uses many of the concepts of microservice architecture to create stateless, failover, redundant microservice.
+Also, the system provides a generic open mechanism to integrate new modules as an extension to enhance the features of the system and weather data preprocessing.
+The \acrshort{wdias} provides an extension API to easy access to create and modify the extension triggers on the fly and support complex timeseries metadata queries with Geo-based support.
+
+The paper also presents performance analysis of the \acrshort{wdias} with load testing using \acrshort{jmeter} tool with system setup on \acrfull{k8s} cluster on Cloud infrastructure.
+Based on the observations, the system was able to handle 300 \acrshort{rps} (which means 18,000 requests per minute) successfully with minimizing the error rate to zero.
+Also, while increasing the request size, the system was able to perform the same while keeping the latency constant without any significant change and the system was able to increase the throughput by keeping the latency constant while increasing the workload which exhibits the scalability of the system.
+With the \acrshort{k8s} auto-scaling, the \acrshort{wdias} were able to elastically adjust the number of pods to handle the workload and shows that the system can run from 1 CPU node to nodes with a few hundred CPUs.
 

### 2020-02-21 summary/sec_1-conclusions.tex
Paper finished with summary

@@
 
-Based on the microservice architecture patterns and the nature of the weather metadata, the \acrshort{wdias} came up with the idea of hierarchical database structure to provide higher performance while storing the weather data optimum.
+Based on the microservice architecture patterns and the nature of the weather metadata, the \acrshort{wdias} came up with the idea of database structure to provide higher performance while storing the weather data optimum.
 The system uses a timeseries database for storing Scalar and Vector timeseries data and using \acrshort{netCDF} for storing Grid timeseries data.

### 2020-02-21 ThePaper.tex
Plagiarism: Ack fix

--- 2020-02-21 Paper.tex
@@
 \newcommand{\dbc}[1]{\todo[author=Dilum, inline, color=blue!40]{#1}}
+\newcommand{\gkc}[1]{\todo[author=Gihan, inline, color=green!50]{#1}}
 
@@
 effectively manage natural resources like water.
-Center for Urban Water, Sri Lanka (CUrW-SL) [3] is tasked with the mission to reduce water-related natural disasters in Sri Lanka.
+\acrfull{curw}\cite{CUrWSL2017SL} is tasked with the mission to reduce water-related natural disasters in Sri Lanka.
 It collected real-time data from weather stations and other government entities and generates daily forecasts.
@@
 To enhance the accuracy of weather predictions, it is necessary to provide reliable and
-detailed weather data as inputs to NWMs.
+detailed weather data as inputs to \acrfull{nwm}s.
 Before feeding such diverse data collected from different sources, it is necessary to a data format that can be ingest by the NWMs.
@@
 There are many forecasting systems developed with considering above factors for disaster management.
-The \acrshort{fews} is developed in the Netherland by Deltares for operational forecasting.
+The \acrshort{fews}\cite{Werner2013TheSystem} is developed in the Netherland by Deltares for operational forecasting.
 It uses a model-centric approach with considering forecasting process as a combination of data modeling steps and data transformation algorithms.
@@
 Workflow service in the \acrshort{lead} schedule and run those with promising the full use of underline resources in the system.
-\acrfull{dias} and \acrfull{madis} mostly provide the functionality of integration and sharing of data.
+\acrfull{dias}\cite{Kawasaki2018DataReduction} and \acrfull{madis}\cite{Macdermaid2005ARCHITECTUREP2.39} mostly provide the functionality of integration and sharing of data.
 When compared to other systems, those do not have the workflow capabilities.
@@
 Even though there are many data integration systems, most of them are proprietary or closed source.
-For an island like Sri Lanka that having different kinds of weather seasons
-over the year than that software originated need to be highly customized.
-Thus it required to get support from the vendor to integrate and configure the
-system.
-And most of the software existing out there is not up to date with the latest
-technology concepts such as Cloud Computing.
+For an island like Sri Lanka that having different kinds of weather seasons over the year than that software originated need to be highly customized.
+Thus it required to get support from the vendor to integrate and configure the system.
+And most of the software existing out there is not up to date with the latest technology concepts such as Cloud Computing.
 The modern architecture pattern such as microservice architecture was able to provide high scalability and availability, rather using monolithic architecture or client service architecture.
@@
 
-\cref{fi:wdia_components} shows the basic functions of a Weather data integration and assimilation system such as Integration, Assimilation, and Dissemination.
+\cref{pfi:wdia_components} shows the basic functions of a Weather data integration and assimilation system such as Integration, Assimilation, and Dissemination.
 
@@
 
-\cref{fi:k8s_architecture} gives an overall idea on the components of \acrshort{k8s},
+\cref{pfi:k8s_architecture} gives an overall idea on the components of \acrshort{k8s},
 \begin{itemize}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{\acrfull{wdias} Architecture}
+\section{Weather Data Integration and Assimilation System Architecture}
 \label{pse:wdias_architecture}
@@
 \cref{pfi:microservice_separation} shows the clear separation of microservices into the modules of the \acrshort{wdias}.
-As seen in Figure of \cref{fi:wdias_micro_on_demand} and \cref{fi:wdias_micro_async} each circle represents a microservice in the \acrshort{wdias}, and those are implemented as containerized applications.
+As seen in Figure of \cref{pfi:microservice_separation} and \cref{pfi:microservice_architecture_async} each circle represents a microservice in the \acrshort{wdias}, and those are implemented as containerized applications.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{\acrshort{wdias} Database Structure}
+\subsection{WDIAS Database Structure}
 \label{subse:wdias_database}
@@
 To get better performance using the available resources, it is possible to schedule each microservice into a predefined set of nodes.
-Pods are assigned to the nodes \cref{tab:aws_eks_nodes} based on the node label as below;
+Pods are assigned to the nodes \cref{ptab:aws_eks_nodes} based on the node label as below;
 \begin{itemize}
@@
 When looking into the \emph{resource utilization} of \acrshort{wdias}; since it is using the \acrshort{k8s} as the container orchestration system, it allows us to scale up and cool down the system as required based on the workload.
-This demonstrates the test plan of \cref{subse:obs_test_plan_all_auto_15min}, and the system gets scale up to the maximum at the peak time.
+This demonstrates the test plan of \cref{ptab:obs_all_15_min_summary_throughput}, and the system gets scale up to the maximum at the peak time.
 Then cool down to a single pod after finishing the test cases.
@@
 \dbc{Summary is too long. Should not be more than a single para}
-\hl{Just kept the important sections}
+\gkc{Just kept the important sections}
 

### 2020-02-21 Thesis.tex
Plagiarism: Ack fix

--- 2020-02-14 thesis.tex
@@
 
+% \usepackage{hyperref} %%% \hl{} on sections will fail this
 \usepackage[noabbrev,capitalise]{cleveref}
@@
 \chapter*{Dedication}
-I dedicate my thesis work to my family, teachers and specially friends at \acrfull{curw}.
+I dedicate this thesis work to teachers, lectures, my family and specially colleagues at \acrfull{curw}.
 A special feeling of gratitude to my loving parents, Nandawathi Dissanayake and H.M.K.
-Karunarathne whose words of encouragement and push for tenacity ring in my ears.
-My wife Jayani Kumarasinghe have never left my side and are very special.
+Karunarathne whose put countless sweats to support me throughout my entire life.
+My wife Jayani Kumarasinghe and my son Sasmitha Karunarathne who missed a lots of wonderful moments to give me freedom to work on my research.
 
-I also dedicate this thesis to my many friends at \acrshort{curw} who have supported and be with me during this period of time.
+Nevertheless I could not forget all of my friends at \acrshort{curw} who have supported and be with me during this period of time.
 Also special thanks to Dr.
@@
 \chapter*{Acknowledgements}
-I wish to thank my evaluation panel members who were more than generous with their expertise and precious time.
-A special thanks to Dr.
-Dilum Bandara, my research supervisor for his countless hours of reflecting, reading, encouraging, and most of all patience throughout the entire process.
-Thank you Dr.
+I would like to thank the members of my evaluation committee who were more than generous with their expertise and their precious time.
+Special thanks to Dr Dilum Bandara, my research supervisor for helping me with his precious time, reading, encouragement and been patient with pushing me to the next level.
+Also, I', thankful to Dr.
 Dilika Peris, and Dr.
-Indika Perera for agreeing to serve on my evaluation panel and Dr.
-Srikantha Herath for agreeing to serve as my external supervisor.
+Indika Perera for serve as my evaluation panel without any hesitation and Dr.
+Srikantha Herath for giving more knowledge on weather domain and support as my external supervisor.
 
-I would like to acknowledge and thank Department of Computer Science and Engineering, University of Moratuwa, for allowing me to conduct my research and providing any assistance requested.
-Special thanks go to both academic and non-academic staff of the department for their continued support.
-I also gratitude to the University of Moratuwa for the financial support as the research was supported in part by the Senate Research Grant of the University of Moratuwa under award number SRC/LT/2017/01,  and \acrfull{curw} for providing the grant and financial support during the research period with providing required resources and learning opportunities.
+I would like to thank the Department of Computer Science and Engineering at the University of Moratuwa for allowing me to conduct my research and provide all the assistance requested.
+Special thanks go to the academic and non-academic staff of the department for their continued support.
+I also thank the University of Moratuwa for its financial support, as the research was partially funded by the Senate research grant from the University of Moratuwa under award number SRC/LT/2017/01,  and \acrfull{curw} for providing the grant and financial support during the research period with providing required resources and learning opportunities.
 
-Finally, I would like to thank the teachers, evaluating panel and colleagues that assisted me with this project.
-Their excitement and willingness to provide feedback made the completion of this research an enjoyable experience.
+Finally, I would like to thank the lectures, the evaluation panel and the colleagues who helped me with this project.
+Their enthusiasm and willingness to provide feedback support me to go far beyond my limits and complete my research with an enjoyable experience.
 
@@
 
-% \import{introduction/}{sec_1-motivation.tex}
+\import{introduction/}{sec_1-motivation.tex}
 
-% \import{introduction/}{sec_2-problem_and_objectives.tex}
+\import{introduction/}{sec_2-problem_and_objectives.tex}
 
-% \import{introduction/}{sec_3-outline.tex}
+\import{introduction/}{sec_3-outline.tex}
 
@@
 
-% \import{lit/}{sec_1-fews.tex}
+\import{lit/}{sec_1-fews.tex}
 
-% \import{lit/}{sec_2-lead.tex}
+\import{lit/}{sec_2-lead.tex}
 
-% \import{lit/}{sec_3-other-systems.tex}
+\import{lit/}{sec_3-other-systems.tex}
 
@@
 
-\import{method/}{sec_3-microservice.tex}
+% \import{method/}{sec_3-microservice.tex}
 
@@
 
-\import{method/}{sec_5-data_preprocess.tex}
+% \import{method/}{sec_5-data_preprocess.tex}
 
 \import{method/}{sec_6-query.tex}
+
+\import{method/}{sec_7-summary.tex}
 
@@
 
-% \import{results/}{sec_0-introduction.tex}
-\label{se:results_intro}
+\import{results/}{sec_0-introduction.tex}
 
 % \import{results/}{sec_1-test_plan.tex}
-\label{se:test_plan}
 
 % \import{results/}{sec_2-workload.tex}
-\label{se:workload}
 
 % \import{results/}{sec_3-observations.tex}
-\label{se:observations}
 
-% \import{results/}{sec_4-discussion.tex}
-\label{se:discussion}
+\import{results/}{sec_4-discussion.tex}
 

### 2020-02-21 introduction/sec_1-motivation.tex
Finished fews citations

@@
-Weather prediction is essential to reduce impact due to natural disasters and to gain effectively manage natural resources like water.
+Weather prediction is essential to reduce the impact caused by natural disasters and to gain effectively manage natural resources like water.
 It will give more understanding of weather prediction if we look into a weather prediction flow that can use to predict the surface water level.
-The weather predictions/forecasts are performed using \acrfull{nwm} that use a set of configuration parameters and the current status of the environment such as temperature, rainfall, and wind direction as the input.
+The weather predictions/forecasts are performed using \acrfull{nwm} that use a set of configuration parameters and the current status of the environment such as temperature, rainfall, and wind direction as the inputs.
 For example, the \acrfull{wrf} \cite{MesoscaleMicroscaleMeteorologyLaboratoryWeatherModel} model is used to predict the rainfall, temperature, and wind direction.
@@
 After removing the bias, the extract information is then fed into another set of models/simulators.
-As an example, FLO2D is a hydrologic model that can use to predict the surface water level.
-A given FLO2D model can simulate with the initial surface water levels and the sequence of forecasted rainfall for the corresponding modeled area from the \acrshort{nwm} model to forecast future water levels.
+\db{As an example, FLO2D is a hydrologic model that can use to predict the surface water level.
+A given FLO2D model can simulate with the initial surface water levels and the sequence of forecasted rainfall for the corresponding modeled area from the \acrshort{nwm} model to forecast future water levels.}
 \dbc{Highighted part doesn't make much sense to me. Need to be reworded.}
@@
 \acrfull{curw} \cite{CUrWSL2017SL} is tasked with the mission to reduce water-related natural disasters in Sri Lanka.
-\acrshort{curw} \cite{CUrWSLObservedSL} is implementing its system with the idea of long-term maintainability rather depend on existing weather data integration systems.
+\acrshort{curw} \cite{CUrWSLObservedSL} is implementing own system with the idea of long-term maintainability rather depend on existing weather data integration systems.
 It collected real-time data from weather stations and other government entities and generates daily forecasts.
@@
 Agricultural insurance companies can warn the farmers, as well as calculate premiums based on anticipated weather patterns.
-Also, farmers rely on weather forecasts to decide what work to do on any particular day.
-For example, drying hay is only feasible in dry weather.
-Further, the aviation industry is especially sensitive to the weather, accurate weather forecasting is essential since before takeoff on the conditions to expect en route and at their destination.
+Besides, farmers rely on weather forecasts to decide what work to do on a given day.
+For example, drying hay is only possible in dry weather.
+Also, the aeronautical industry is particularly sensitive to weather conditions, precise weather forecasts are essential since before takeoff a flight need to check the conditions on expected route and at destination.
 Thus it is required a platform to provide such 3rd party access, and use the data or process those based on their applications.
@@
 In such a case, it required to get support from the vendor to integrate and configure the system.
-And most of the software existing out there is not up to date with the latest technology concepts such as Cloud Computing.
+
+Most of the software existing out there is not up to date with the latest technology concepts such as Cloud Computing.
 The modern architecture pattern such as microservice architecture was able to provide high scalability and availability, rather using monolithic architecture or client service architecture.
@@
 The proposed system should be independent of the platform.
-But most software out there is not, as an example \acrshort{fews} can run on Windows and Linux.
+But most software out there is platform dependent, as an example \acrshort{fews} can run on Windows and Linux.
 And should be independent underline infrastructure providers which gives much flexibility for the users to decide the best cost-effective way to host it.

### 2020-02-21 introduction/sec_2-problem_and_objectives.tex
Finished fews citations

@@
 \section{Problem Statement}
-Handling Spatio-temporal weather data is challenging \dbc{as} it involves large data volumes required to have a higher number of resources such as computation, storage, and network bandwidth.
+Handling Spatio-temporal weather data is challenging \db{as} it involves large data volumes required to have a higher number of resources such as computation, storage, and network bandwidth.
 Moreover, the data integration system needs to be capable of interacting with different data formats including Spatio-temporal bulk stream data.
@@
 
-\emph{Design and implement an extendable weather data integration, assimilation, and dissemination system which is capable of handling bulk data efficiently with providing scalability and high throughput with using open source tools and modern cloud computing technologies.}
+\emph{Design and implement an extendable weather data integration, assimilation, and dissemination system which is capable of handling bulk data efficiently with providing scalability and high throughput with using open source tools which support modern cloud computing advancements.}
 \dbc{Give a proper problem statement.}
@@
 \section{Objectives}
-We address the above problem statement by achieving the following research objectives:
+This research addresses the above mentioned problem statement by achieving the following research objectives:
 \begin{itemize}

### 2020-02-21 introduction/sec_3-outline.tex
Finished fews citations

@@
 \section{Outline}
-The rest of the thesis is organized as follows.
-The literature review is presented in \cref{ch:literature}, and discuss the existing Weather Data Integration Systems such as \acrshort{lead}, \acrshort{fews}, \acrshort{madis}, and \acrshort{dias}.
+The organization of the rest of the thesis as follows.
+In next \cref{ch:literature} the literature review is present and discuss the existing Weather Data Integration Systems such as \acrshort{lead}, \acrshort{fews}, \acrshort{madis}, and \acrshort{dias}.
 Solution approach with the proposed system architectures and adaptation with problem occurred are presented in Chapter \ref{ch:method}.

### 2020-02-21 lit/sec_1-fews.tex
Finished fews citations

@@
 
-\acrshort{fews} \cite{Werner2013TheSystem} is developed by Deltares in the Netherland with targeted for use by operational forecasting agencies.
-The codebase of \acrshort{fews} is currently not fully open source.
-Most, if the models are using a model-centric approach such as inputs, need to be in the format of specific to the model.
-Also, the outputs produced by the model are specific to the model and hard to utilize by other systems (e.g., FLO2D).
+\acrshort{fews} \cite{Werner2013TheSystem} is developed by Deltares in the Netherland with target audiences/customers of operational forecasting agencies.
+The \acrshort{fews} codebase is not fully open source at the moment.
+Most of models are using a model-centric approach such as inputs, need to be in the format of specific to the model.
+Also, the outputs produced by the model are specific to the model and hard to utilize by other systems (e.g., FLO2D create human readable text output files).
 As \acrshort{fews} uses a modular approach it is easier to integrate new models.
@@
 
-Forecasting processes are constructed as a combination of modelling steps and data transformation algorithms.
-These are then combined to the provide required forecast capabilities.
-Flexibility is achieved by integrating new models and algorithms into the codebase \cite{Werner2013TheSystem}.
-\acrshort{fews} system contains no inherent hydrological modeling capabilities within its codebase.
+As it describe with a simple example in \cref{ch:intro}, forecasting processes consist by creating modeling steps with combining data transformation algorithms.
+Combining such flows can use to provide the forecasting capabilities.
+The system is flexible enough to integrate new models and algorithms into the core codebase \cite{Werner2013TheSystem}.
+\acrshort{fews} does not have any inbuilt hydrological modeling capabilities within its codebase.
 Rather it is a framework that can use to integrate into the system and create workflows for forecasting.
 
-Are proposed by Haggett \cite{Haggett1998AnWales} key elements of a forecasting system include detection, forecasting, dissemination and warning, and response.
-Within these four steps, \acrshort{fews} focuses on the forecasting step.
-The primary objective of this step is to provide additional lead time through predictions of short term future hydro-meteorological conditions \cite{Werner2005FloodCatchments}.
+Are proposed by Haggett \cite{Haggett1998AnWales} key elements of a forecasting system are defined as detection, forecasting, then dissemination and warning, and response to the events.
+The \acrshort{fews} focuses on the forecasting step out from above steps.
+The main objective of this step is to provide additional lead time by forecasting future hydro-meteorological conditions \cite{Werner2005FloodCatchments}.
 It is a valid argument that providing accurate predictions with greater lead time can reduce the level of destruction.
-To do the forecasting, the system should be capable of integrating real-time data from hydrological and meteorological observation networks, and the dissemination of prediction results through appropriate products to the warning process.
+To forecasting, the system should be capable of integrating real-time data from meteorological and hydrological observation network systems, and the disseminate the forecasted results through relevant products to the warning process.
 
-In \db{Figure} \cref{fi:fews_schematic} show a schematic view of the connection between the forecasting system to real-time data acquisition systems and dissemination systems.
+In \db{Figure} \cref{fi:fews_schematic} show the connection between the forecasting system to real-time data integration systems and dissemination systems.
 The widely used concept is using meteorological forecast data to get precipitation and, then using a hydrological and hydraulic model chain to predict the level affect on the ground.
@@
 Based on the affected catchment, it can be further divided into sub-catchments to reduce the complexity of the simulation task.
-Ideally, the forecasting system should be flexible to allow change to models and data, while keeping the way forecasters work with it as constant as possible.
+Ideally, the forecasting system should be flexible enough to allow modification of models and data, while keeping the most constant way possible of working with forecasters.
 \dbc{F is capital and T is capital when referring to Figures and Tables. Fix all other places.}
@@
     \includegraphics[width=0.7\textwidth]{lit/fews/Schematic-structure-of-a-fl-ood-forecasting-system-showing-the-position-of-Delft-FEWS_W640.png}
-    \caption[Schematic structure of a flood forecasting system including \acrshort{fews} and links to other primary systems within the operational environment]{Schematic structure of a flood forecasting system including \acrshort{fews} and links to other primary systems within the operational environment \cite{Werner2013TheSystem}.}
+    \caption[Schematic structure of a flood forecasting system including \acrshort{fews} and communication between other operational systems]{Schematic structure of a flood forecasting system including \acrshort{fews} and communication between other operational systems \cite{Werner2013TheSystem}.}
     \label{fi:fews_schematic}
@@
 
-The foundation of \acrshort{fews} is data-centric, with a common data-model through which all components interact.
-All timeseries data (both scalar and gridded) are stored in this common data model in a database.
-Modeling capabilities are then linked to the system through one of the interfaces provided to the data-model \cite{Werner2013TheSystem}.
+The \acrshort{fews} follows a data-centric approach, with providing a common data-model to interact from all other components.
+All the timeseries data types are stored in a database which follows a common data model.
+New models are integrate to the system via using a one of the interfaces provided to interact with the common data-model \cite{Werner2013TheSystem}.
 As mention in the paper, having a common data-model make easy to store data efficiently.
@@
 
-Timeseries data is additionally either scalar, vector, or gridded data, though all different types are uniformly stored as binary objects in a time series table.
-None of the functional components (including the linked models) have direct access to the times series table, which is accessible only through the data access module \cite{Werner2013TheSystem}.
+The timeseries data is one of scalar, vector, or grid data, and all of different types are uniformly stored as binary objects in a time series table inside the \acrshort{fews}.
+Functional compenents or any integrated models do not have direct access to the timeseries table which mentioned above, and those should use the data access module to access the data \cite{Werner2013TheSystem}.
 As explained in the system interpretation, every time all the data access needs to go through the data access module which causing adding more cost in data access.
@@
 
-Given above drawback on storing the data in the system, within the \acrshort{fews} data model, time series are uniquely identified by their location and data type, as well as an id related to the source of the data (e.g., the external source or hydrological model of which the time series are a result) \cite{Werner2013TheSystem}.
+Given above drawback on storing the data in the system, the \acrshort{fews} data model store the timeseries by uniquely identifying based on the location, data type, and source of the data \cite{Werner2013TheSystem}.
 This allows indexing the database on the above key fields and stores the data separately, to take advantage of putting multiple data resources into the system.
-As an example, instead of storing the data at a single timeseries table, it is possible to separate and index the database based on the source such as an external source or hydrological model of which the timeseries is a result.
+As an example, instead of storing the data at a single timeseries table, it is possible to separate and index the database based on the source such as an external source of data or hydrological model of which the timeseries is a result.
 Or separate by data type and store in multiple storages give the capability for the system to scale with a factor of identical types that can be identified.
@@
 Data processing and manipulation is a required process in weather forecasting. 
-Most of the data that is imported from external sources is not at the appropriate temporal and spatial scale to be applied as an input to a forecasting model, or to be used directly in product generation.
-As a consequence, generic data processing steps form the predominant effort in most applications of models in the forecast environment.
-Some examples include data validation, serial and spatial interpolation, aggregation and disaggregation, and merging data \cite{Werner2013TheSystem}.
+The data integrated from the external sources are not in the appropriate temporal and spatial format that can directly feed as an input to a forecasting model or use in other application.
+Therefore, generic data processing steps are a required effort in most model applications in the forecasting environment.
+Few examples are serial and spatial interpolation, data validation, aggregation and disaggregation, and data fusion \cite{Werner2013TheSystem}.
 This a vital feature in a forecasting system, and affect the quality and accuracy of the predicted data outputs.
 Because of the common data model concept in \acrshort{fews}, data processing via these functions is much effective.
-The system is self-provided some of the generic functions for data processing, but for more complex algorithms can be developed as a new Java class coded to communicate with the \acrfull{api}.
+The system is self-provided some of the generic functions for data processing, but required complex algorithms can be implement as a new Java class via communicate with the \acrfull{api}.
 It is obvious that for additional feature integration, users should implement the new functional extensions via Java programming language.
-Users do not have the flexibility of developement with some other languages they are familiar with or use the support from another language.
+Users do not have the flexibility of development with some other languages they are familiar with or use the support from another language.
 As an example, Python language is easy to use for beginners and many data scientists are using this programming language for development and it has many data available libraries for data processing.
@@
 \end{figure}
-Most of the library of functions provided work equally on scalar and gridded time series.
-As with all other modules, this communicates with the database solely through the data access layer as shown in \cref{fi:fews_data_layer} \cite{Werner2013TheSystem}.
+Most of the function library has provided equal work on scalar and grid time series.
+But the communicates with the database only via the data access layer as shown in \cref{fi:fews_data_layer} \cite{Werner2013TheSystem}.
 As it is shown in the figure, it is clearly showing that the system depends on a single database and via the data access layer, all the requests are coming to the database through a connection.
@@
     \includegraphics[width=0.8\textwidth]{lit/fews/Linking-Delft-FEWS-with-external-models-The-fi-gure-shows-the-fl-ow-of-data-through-XML_W640.png}
-    \caption[Linking \acrshort{fews} with external models]{Linking \acrshort{fews} with external models \cite{Werner2013TheSystem}.}
+    \caption[\acrshort{fews} integration with external models]{\acrshort{fews} integration with external models \cite{Werner2013TheSystem}.}
     \label{fi:fews_general_adapter}
@@
 One of the simple and most effective features in the \acrshort{fews} is an open approach to the integration of models and data.
-This approaches the concept of the open modeling framework proposed by Open model integration \cite{Kokkonen2003InterfacingXML}.
+The concept of the open modeling framework is used by the \acrshort{fews} which is proposed by Open model integration \cite{Kokkonen2003InterfacingXML}.
 It simply gives the flexibility to allow operators to integrate more models as well as variations of the same model and come up with new integration flows as much as possible.
-\acrshort{fews} generates the input data as a set of XML files to a defined location; an adapter developed specifically for the model in question transforms this to the required native format in a pre-processing step; \acrshort{fews} executes the model, and the adapter to that model then converts the native formatted results into XML formatted files in a post processing step.
-\acrshort{fews} subsequently imports the results into the database from the XML files (see \cref{fi:fews_general_adapter}) \cite{Werner2013TheSystem}.
+The users need to mentioned the input timeseries via XML configurations, and \acrshort{fews} generates the input data as XML files.
+Then using an adapter developed for the model transforms the data into required format for the model as a preprocessing step.
+Next \acrshort{fews} executes the model and model generates the output after successful completion.
+In the post processing step, the model result data transform to the XML files which can import into the data model as shown in \cref{fi:fews_general_adapter} \cite{Werner2013TheSystem}.
 The process is simple and consistent throughout all the model integration.
-The model execution is done by the \acrshort{fews} or the model adapter which is causing tide coupling into the execution process in the system.
+The model execute by the \acrshort{fews} or the model adapter which is causing tide coupling into the execution process in the system.
 Users do not have the flexibility to run the models with different configurations such as running with parallel execution.
@@
 
-Exchanging data with the model is primarily through XML files.
-In some cases, these XML files may become very large, which may lead to I/O bottlenecks and subsequent performance issues \cite{Werner2013TheSystem}.
+Data exchange with the model is mainly done via XML files.
+It is possible to happen, these XML files become very large, which can lead to I/O bottlenecks and causing performance issues \cite{Werner2013TheSystem}.
 This issue is thoroughly discussed in previous paragraphs and the authors of the \acrshort{fews} \cite{Werner2013TheSystem} seem to be noticed and accept it here.
 For overcoming this issue they introduced the file-based exchange of data.
-This includes the use of binary-XML files, streaming files through memory, and the use of \acrshort{netCDF} files.
+This includes the use of binary XML files, the streaming of files via memory and the use of \acrshort{netCDF} files.
 But far as for the users, it seems to be adding more complexity and context to get higher performance via the system.
 
-If a particular adapter for a model is not present in the list of \acrshort{fews} adapter, the user has the flexibility to implement an adapter for it.
-The effort of developing an adapter for a model code not previously integrated with \acrshort{fews} will vary depending on the complexity of the model I/O formats \cite{Werner2013TheSystem}.
+The \acrshort{fews} provides a list of adapter available.
+If an adapter is not available for a given model, the user has to implement the adapter for the model and \acrshort{fews} has the flexibility creating a new adapter.
+But the effort that required to develop an adapter for a model will vary depending on the complexity of the model required data formats \cite{Werner2013TheSystem}.
 If the users want to use an existing adapter and need to configure something not supported via the existing adapter, it is hard to get done.
@@
 If you setup the system on Linux based operating system and using Linux based models, it is hard for users to come up with a solution for integrating the FLO2D models.
-The final step and one of important feature is exporting the data from the system in useful manner.
-The forecasting process is often a sequence of steps, starting with the import of data, a several data processing, and modeling steps, and culminating in the generation of products to be disseminated to the warning process.
-This is supported via the workflow process in \acrshort{fews}.
-As mentioned above, the scope of the \acrshort{wdias} is not focused on adding such a feature in the system, rather user has to use a scientific workflow management system or come up with own version of workflow.
-
-When running sequential steps within a workflow in \acrshort{fews}, each step is run for the full-time window required (e.g., the lead time of the forecast) before moving on to the next step.
-This precludes tightly coupling of models, even explicitly \cite{Werner2013TheSystem}.
-As mentioned above, users can run multiple models parallel or run those sequentially as needed.
+The \acrshort{fews} support creating workflow process and allow users to run multiple models parallel or run those sequentially as needed, but the scope of the \acrshort{wdias} is not focused on adding such a feature in the system, rather user has to use a scientific workflow management system or come up with own version of workflow.

### 2020-02-21 method/sec_6-query.tex
Change HOST_NAME to avoid plagiarism

@@
 \begin{lstlisting}
-    GET <HOST_NAME>/metadata/timeseries/<TIMESERIES_ID>
+    GET <HOST_ADDR>/metadata/timeseries/<TIMESERIES_ID>
 \end{lstlisting}
@@
 \begin{lstlisting}
-    GET <HOST_NAME>/metadata/timeseries?<QUERY_STRING}
+    GET <HOST_ADDR>/metadata/timeseries?<QUERY_STRING}
 \end{lstlisting}
@@
 \begin{lstlisting}
-    POST <HOST_NAME>/query/location
+    POST <HOST_ADDR>/query/location
     JSON Body:
@@
 \begin{lstlisting}
-    POST <HOST_NAME>/query/parameter
+    POST <HOST_ADDR>/query/parameter
     JSON Body:
@@
 \begin{lstlisting}
-    POST <HOST_NAME>/query/timeseries
+    POST <HOST_ADDR>/query/timeseries
     JSON Body:

### 2020-02-21 lit/sec_2-lead.tex
Plagiarism fix lead

@@
 
-\acrfull{lead} addresses the fundamental research challenges needed to create an integrated, scalable framework for adaptive analyzing and predicting the atmosphere \cite{Droegemeier2005Service-OrientedWeather}.
+\acrfull{lead} addresses the fundamental research challenges needed to create an integrated and scalable framework for adaptive analysis and prediction of the atmosphere \cite{Droegemeier2005Service-OrientedWeather}.
 To predict and analyze weather models by researchers, it required many resources.
@@
 At the time, researchers are developing their experiment flow, they are not using the resources many, and others are using it at the same time.
-LEAD's foundation is dynamic workflow orchestration and data management in a Web services framework \cite{Droegemeier2005Service-OrientedWeather}.
+The foundation of \acrshort{lead} system is to create a dynamic workflow orchestration and data management in a Web services framework \cite{Droegemeier2005Service-OrientedWeather}.
 
-LEAD's complex array of services, applications, interfaces, and local and remote computing, networking, and storage resources is assembled by users in workflows to study mesoscale weather as it evolves \cite{Droegemeier2005Service-OrientedWeather}.
+LEAD's complex range of services, applications, interfaces and IT resources, local and external networks and storage is compiled by users in workflows to study mesoscale incremental manner \cite{Droegemeier2005Service-OrientedWeather}.
 As it follows the \acrshort{soa}, everything is implemented as independent services.
@@
 \cref{fi:lead_system} shows the fundamental capabilities of the \acrshort{lead} system.
-From the high-level view, \acrshort{lead} lets users query for and acquire information, simulate and predict the weather by using numerical atmospheric models, assimilate data, analyze, mine, and visualize data and model output.
+From the high-level view, \acrshort{lead} enables users to search and acquire information, simulate and predict weather conditions using digital atmospheric models, assimilate, analyze, use and visualize data and output of models.
 
@@
 \begin{itemize}
-    \item a Web portal, the primary (though not exclusive) user entry point
-    \item the ARPS Data Assimilation System (ADAS), a sophisticated tool for data quality control and assimilation
-    \item myLEAD, a flexible metadata catalog service
-    \item \acrfull{wrf} a next-generation atmospheric prediction and the simulation model
-    \item ADaM (Algorithm Development and Mining), a powerful suite of tools for mining observational data, assimilated data sets, and model output 
-    \item Integrated Data Viewer (IDV) 
+    \item the users interact with \acrshort{lead} via a Web portal
+    \item data quality control and assimilation happends via ARPS Data Assimilation System (ADAS)
+    \item myLEAD is the metadata catalog
+    \item \acrfull{wrf} \cite{MesoscaleMicroscaleMeteorologyLaboratoryWeatherModel}
+    \item Algorithm Development and Mining is a set of tools for analyze observational data, assimilated data sets, and model output 
+    \item Integrated Data Viewer 
 \end{itemize}
 
-The Concept of the \acrshort{lead} is, the workflow orchestration for on-demand, real-time, dynamically adaptive systems, called as WOORDS.
+The concept of the \acrshort{lead} is a workflow orchestration for on-demand, real-time and dynamically adaptive systems called WOORDS.
 The system is doing the workflow orchestration as given in each procedure.
@@
 
-As shown in \cref{fi:lead_framework} LEAD consists of the following sub-components, and it provides a distributed testbed for developing, integrating, and testing LEAD's components.
+As shown in \cref{fi:lead_framework} LEAD consists of the following sub-components, and it provides a distributed system for integrating, and testing LEAD's components.
 \begin{itemize}
     \item User subsystem -- comprises the LEAD portal and enable user can access services
-    \item Data subsystem -- handles data and metadata, any numerical model output produced by operational or experimental models, and user-generated information.
-    \item Tools subsystem -- consists of all meteorological and IT tools
-    \item Orchestration subsystem -- provides the technologies that let users manage data flows and model execution streams, and create and own output.
-It also provides linkages to other software and processes for continuous or on-demand applications.
+    \item Data subsystem -- manages data and metadata, all output of digital models produced by operational or experimental models, and information generated by users.
+    \item Tools subsystem -- provides all IT toles and  meteorological tools
+    \item Orchestration subsystem -- offers the technologies with which users can manage data flows and model execution flows and can create and own output.
+It also provides links to other software and processes for continuous or on-demand applications.
 \end{itemize}
@@
 
-\acrshort{soa}s are widely deployed in the commercial enterprise sector, and they form the foundation of many scientific "grid" technologies at the time of \acrshort{lead} design and developed.
-A variant of \acrshort{soa} is evolved later called microservice architecture and widely used in the industry nowadays.
+\acrshort{soa}s are widely used in the commercial enterprise sector and form the basis of many scientific "grid" technologies in lead design and development.
+A variant of \acrshort{soa} was developed later, called microservices architecture, and is now widely used in industry nowadays.
 
-As shown in \cref{fi:lead_soa}, \acrshort{lead} \acrshort{soa} has five distinct yet highly interconnected layers. 
-The bottom layer represents raw computation, application, and data resources distributed throughout the LEAD grid and elsewhere.
-The next level upholds the Web services that provide access to raw services \cite{Droegemeier2005Service-OrientedWeather}.
+As shown in \cref{fi:lead_soa}, \acrshort{lead} \acrshort{soa} has five different but highly interconnected layers.
+The bottom layer represents the calculation, application, and raw data sources that are distributed in the LEAD grid and elsewhere.
+The next level supports web services that provide access to raw services \cite{Droegemeier2005Service-OrientedWeather}.
 These two layers are working together since \acrshort{lead} system resources are distributed over multiple locations and creating a pool of resources.
@@
 
-The configuration and execution services in the middle layer, consisting of five elements, represent services invoked by LEAD workflows.
+The configuration and execution services of the middle layer, consisting of five elements, represent the services that call LEAD workflows.
 These are some critical aspects of a weather data management system.
@@
 \begin{itemize}
-\item The application-oriented configuration service that manages the deployment and execution of real applications such as the \acrshort{wrf} simulation model, ADAS, and the ADaM tools \cite{Droegemeier2005Service-OrientedWeather}.
+\item The application-oriented configuration service that manages the implementation and execution of real applications, such as the \acrshort{wrf} simulation model, ADAS and ADaM tools \cite{Droegemeier2005Service-OrientedWeather}.
 When creating weather workflow, it is required to change the behavior of the model by changing some of the configurations of the model or run a different version of the model.
@@
 When designing the weather data system, it is required to increase the capacity of the system automatically, and adopt it into the system.
-\item The workflow engine service, which drives experimental workflow instances, invokes both the configuration service and application resource broker \cite{Droegemeier2005Service-OrientedWeather}.
+\item The workflow engine service, which manages the experimental workflow instances, invokes both the configuration service and the application resource broker \cite{Droegemeier2005Service-OrientedWeather}.
 This is a part of workflow orchestration.
-\item The catalog services represent how a user or application service discovers public-domain data products or \acrshort{lead} services \cite{Droegemeier2005Service-OrientedWeather}.
+\item Catalog services represent how a user or application service discovers data products in the public domain or \acrshort{lead} services \cite{Droegemeier2005Service-OrientedWeather}.
 This is an important feature that should be available in a weather data system, and users need to search for the availability of the data.
 Further wants to analyze the existing data for decision making.
-\item Users require a host of data services to support rich query, access, and transformation operations on data products.
-An important goal behind LEAD is access transparency facilitating user queries across all available heterogeneous data sources without adverse effects from different formats and naming schemes \cite{Droegemeier2005Service-OrientedWeather}.
+\item Users need a multitude of data services to support comprehensive query, access, and transformation operations on data products.
+An important goal behind LEAD is transparency of access that facilitates user requests on all available heterogeneous data sources without the negative effects of different formats and naming schemes \cite{Droegemeier2005Service-OrientedWeather}.
 Users need to have transformation services to read data in different formats.
@@
 \end{itemize}
-The top of \cref{fi:lead_soa}, shows the user interface to the system.
-This gives access to individual services.
+The top of \cref{fi:lead_soa}, shows the user interface of the \acrshort{lead} which gives individual services access.
 When the user logs into the system, based on the authentication and authorization setting bind to the individual account, the portlets can access the services on behalf of the user.

### 2020-02-21 lit/sec_3-other-systems.tex
Plagiarism fix dias madis

@@
 
-\acrfull{dias} collects and files data from satellites, ground observation stations, numerical weather prediction models and climate change projection models.
-Once this data is integrated with geographic and socio-economic information, DIAS generates results for managing global environmental issues and natural disasters \cite{Kawasaki2018DataReduction}.
+\acrfull{dias} collects and archives data from satellites, weather stations, numerical forecasting models and climate projection models.
+Once this data is integrated into geographic useful information, DIAS generates results for managing global environmental problems and natural disasters \cite{Kawasaki2018DataReduction}.
 As mentioned above, \acrshort{dias} has the capability of collecting weather data from multiple data sources which are inherently in different formats.
@@
 The mechanism of storing data in \acrshort{dias}, similar to the other systems discussed.
-These data sets are stored in an extra largee volume disk array system with API (Application Programming Interface) software used to import the data.
-APIs work to convert or re-format data into manageable forms and are useful in creating the DIAS storage archive.
-API software consists of several tools, including the real-time data crawling and archiving system, data upload system, quality control system, and metadata management system \cite{Kawasaki2018DataReduction}.
+These data sets are stored in a larger array system with Application Programming Interface (API) software that is used to import the data.
+APIs work to convert or reformat data into manageable forms and are useful for creating the DIAS storage archive.
+The API software contains various tools, including the real-time data exploration and archiving system, the data download system, the quality control system and the metadata management system \cite{Kawasaki2018DataReduction}.
 To store on the large volume of disk space, it converts the data via a provided set of APIs.
@@
 
-As shown in \cref{fi:dias_common_platform}, it provides an application layer that allows domain scientists to work on research tasks, and to develop specific tools and applications by working together with Information Technology experts \cite{Kawasaki2018DataReduction}.
+As shown in \cref{fi:dias_common_platform}, it offers an application layer that allows scientists in the field to work on research tasks and to develop specific tools and applications by collaborating with experts in information technology \cite{Kawasaki2018DataReduction}.
 Once the data is achieved on the \acrshort{dias} system, it shares those details via the Shared API layer.
@@
 \label{se:madis}
-\acrfull{madis} is a data ingest and assimilation system, which is collecting data over dozen of providers, then quality control over the data and store in \acrshort{netCDF} format.
-Later allow users to access the data via supporting different types of protocols.
+\acrfull{madis} is a data integration and assimilation system that collects data from dozens of suppliers, then checks the quality of the data and saves it in \acrshort{netCDF} format.
+Give users later access to data through support for different types of protocols.
 
@@
 
-\acrshort{madis} comprises a distributed architecture for ingest, processing, and data distribution functions.
-Besides, in a recent architectural advance, the various functional hosts are arranged in pairs using High-Availability (HA) Linux to provide automated failover in case of system failure.
-Real-time data distribution methods include FTP, Local Data Manager (LDM), and the Web-based OPeNDAP (OPen source project for Network Data Access Protocol) \cite{Macdermaid2005ARCHITECTUREP2.39}.
+\acrshort{madis} contains a distributed architecture for data acquisition, processing and distribution functions.
+In addition, the paper mentioned architectural advancement at that time, the various functional hosts have been paired using Linux High Availability (HA) to provide automated failover in the event of a system failure.
+And it uses following method for data dissemination such as FTP, Local Data Manager (LDM) and the Web OPeNDAP (OPen source project for Network Data Access Protocol) \cite{Macdermaid2005ARCHITECTUREP2.39}.
 As mentioned above, the \acrshort{madis} is implemented based on a distributed architecture that is available at the time of its development.
 Even it is not mentioned, it is using functional calls like Remote Procedure Call (RPC) to invoke among a cluster of nodes.
-In \cref{fi:madis_flow}, data are transported from the input and preprocessing systems to the central computer systems and then out to other hosts for storage and distribution \cite{Macdermaid2005ARCHITECTUREP2.39}.
+In \cref{fi:madis_flow}, data is transported from the input and preprocessing systems to the central computer systems and then to other hosts for storage and distribution \cite{Macdermaid2005ARCHITECTUREP2.39}.
 To get high availability, it has added some updates to its architecture as mentioned in the paper.
@@
 
-MADIS routinely acquires mesonet data from several dozen network providers representing over 14,000 stations.
-This translates into over 30,000 station reports each hour.
-Several systems running both inside and outside the firewall acquire the data.
-These data are sent to the Central Facility's Advanced Weather Interactive Processing System (AWIPS) data server for preprocessing and conversion to a common format, NetCDF.
-The NetCDF files are then transferred to the MADIS compute nodes \cite{Macdermaid2005ARCHITECTUREP2.39}.
+MADIS regularly acquires Mesonet data from dozens of network providers representing more than 14,000 stations.
+This translates into more than 30,000 station reports every hour.
+Different systems that work inside and outside the firewall collect the data.
+This data is sent to the data server of the advanced weather-interactive processing system (AWIPS) of the central installation for processing and conversion to a common format, NetCDF.
+NetCDF files are then transferred to MADIS compute nodes \cite{Macdermaid2005ARCHITECTUREP2.39}.
 This provides an overview of the level of data that \acrshort{madis} handling.
@@
 
-The MADIS compute platforms comprise Intel-based servers running the Red Hat Enterprise Linux operating system.
-Many of these computers are configured using High-Availability Linux clustering \cite{Macdermaid2005ARCHITECTUREP2.39}.
+MADIS computer platforms include Intel-based servers with the Red Hat Enterprise Linux operating system.
+Many of these computers are configured using Linux clustering with high availability \cite{Macdermaid2005ARCHITECTUREP2.39}.
 As indicated above, the system heavily depends on the platform.
@@
 
-Since some MADIS data are considered proprietary by the provider, access to these data needs to be controlled.
-To accommodate this, MADIS data are split into six different versions based on the level of access allowed by the data provider \cite{Macdermaid2005ARCHITECTUREP2.39}.
+As certain MADIS data is considered to be the property of the supplier, access to this data must be checked.
+To respond to this, MADIS data is divided into six different versions, depending on the access level authorized by the data provider \cite{Macdermaid2005ARCHITECTUREP2.39}.
 When compared to \acrshort{fews}, \acrshort{madis} provides control based access to the data.

### 2020-02-21 method/sec_0_introduction.tex
Plagiarism microservices

@@
 
-To get an overall idea of the flow of weather prediction, let us look into one of the flows using in \acrshort{curw} \cite{CUrWSL2017SL}.
+To get an overall idea of the flow of weather prediction, let us look into one of the flows using at \acrshort{curw} \cite{CUrWSL2017SL}.
 \dbc{Use CUrW-SL}
@@
 
-\paragraph{Integration}-- The system should capable of integrating data from different sources such as satellite data, high end, and low-end weather station, etc.
+\subsubsection{Integration}
+The system should capable of integrating data from different sources such as satellite data, high end, and low-end weather station, etc.
 And the system should be able to handle multidimensional spatial and temporal weather data efficiently and optimally.
@@
 Also, those models reproduce a large set of redundant data, thus the system should store the bulk data while optimizing the disk space.
-\paragraph{Dissemination}-- Then different users should be able to retrieve data as they required.
+\subsubsection{Dissemination}
+Then different users should be able to retrieve data as they required.
 Also, the users should be able to easy to search into the available that in the system base on timeseries metadata or based on Geo queries.

### 2020-02-21 method/sec_1-architectural_decisions.tex
Plagiarism microservices

@@
 \hl{Because} \acrshort{esb} \hl{mediators can be used to integrate the modules which are described in Section} \ref{subse:modules_weather_data_integration_sys}. 
-\gkc{FIXED}
+\gkc{FIXED below}
 The \acrshort{esb} has the processing units called \emph{mediators}.
@@
 In that case, an actor or an actor with slave actors was a map to each microservice in \acrshort{wdias}.
-\acrshort{soa} focuses on imperative programming, whereas microservices architecture focuses on a responsive actor programming style using faster messaging mechanisms.
+\acrshort{soa} focuses on imperative programming, while the microservices architecture focuses on a reactive actor programming style using faster messaging mechanisms.
 
@@
 \begin{itemize}
-    \item Follow the Single Responsibility principle
-    \item Resilient/flexible as a failure in one service does not impact other services. If you have monolithic or bulky service errors in one service/module it can impact other modules/functionality.
-    \item High scalable as demanding services can be deployed in multiple servers to enhance performance and keep away from other services so that they do not impact other services.
-It will be difficult to achieve the same with single, large monolithic service.
-    \item Easy to enhance as dependencies are less. It is also easier to change and test.
-    \item Low impact on other services as each service is independent. % service., this has less chance to impact other services
-    \item Easy to understand since they represent a small piece of functionality
-    \item Ease of deployment
+    \item Follow the principle of a single responsibility.
+    \item Resilient / flexible because a failure of a service has no influence on other services.
+If you have monolithic or major service errors in a service / module, this can have an impact on other modules / functionalities.
+    \item High scalability because demanding services can be implemented on different servers to improve performance and stay away from other services so that they do not affect other services.
+It will be difficult to achieve the same with a single large monolithic service.
+    \item Easy to improve because the dependencies are less. It is also easier to change and test.
+    \item Little impact on other services because each service is independent.
+    \item Easy to understand because they represent a small functionality.
+    \item Ease of deployment.
 \end{itemize}
@@
 
-Containerization is an alternative to the virtualization that supports virtual machines or Hypervisors.
-It involves encapsulating or packaging up software code and all its dependencies so that it can run uniformly and consistently on any infrastructure \cite{IBMContainerizationExplained}.
+Containerization is an alternative to virtualization that supports virtual machines or hypervisors.
+This includes encapsulating or grouping the software code and all its dependencies so that it can work uniformly and consistently in any infrastructure.
+\cite{IBMContainerizationExplained}.
 The concept of containerization and process isolation has emerged after the open-source Docker Engine \cite{DockerAppContainerization}, an industry standard for package software into standardized units for development, shipment, and deployment.
@@
 The \acrshort{wdias} is using \acrfull{k8s} as the container orchestration system which is an open-source tool for automating deployment, scaling, and management of containerized applications \cite{LinuxFoundationProduction-GradeKubernetes}.
-It groups containers that make up an application into logical units for easy management and discovery.
+It groups the containers that make up an application into logical units for easy management and detection.
 While implementing the \acrshort{wdias}, we used \acrshort{k8s} as the container-orchestration system, to deploy each microservice as container and manage with providing scalability and availability.
@@
 \begin{itemize}
-    \item Pods -- Cluster of containers that can group other container images in a single unit.
-    \item Nodes -- the machines (VMs, physical servers, etc) in a cluster that runs your applications and cloud workflows.
+    \item pods -- Cluster of containers that can group other container images in a single unit.
+    \item nodes -- The machines (VMs, physical servers, etc) in a cluster that runs your applications and cloud workflows.
     \item kubelet -- An agent that runs on each node in the cluster. It makes sure that containers are running in a pod.
     \item kube-proxy -- A network proxy that runs on each node in the cluster, and maintains network rules on nodes.
-    \item Kubernetes master -- Responsible for maintaining the desired state for your cluster.
+    \item kubernetes master -- Responsible for maintaining the desired state for your cluster.
     \item etcd -- Consistent and highly-available key value store used as Kubernetes’ backing store for all cluster data.
@@
 Users can add much as required Nodes into the \acrshort{k8s} cluster, and \acrshort{k8s} manage and deploy applications as pods into cluster nodes.
-Each microservice can deploy as a Pod which is a group of containerized applications. And \acrshort{k8s} able to scale as much as the user wants as described above.
+Each microservice can deploy as a pod which is a group of containerized applications. And \acrshort{k8s} able to scale as much as the user wants as described above.
 By separating each microservice as a container, and running them as multiple pods inside the \acrshort{k8s} removes the tight coupling of microservices when compared to the actors.

### 2020-02-21 method/sec_3-microservice.tex
Plagiarism microservices

@@
 
-A microservice architecture style is an approach to developing a single application as a suite of small services, each running in its own process and communicating with lightweight mechanisms, often via providing \hl{a RESTful API}.
-These services are built around business capabilities and independently deployable by fully automated deployment machinery \cite{LewisMicroservices}.
+A microservice architecture style is an approach to developing a single application as a package of small services, each working in their own process and communicating with lightweight mechanisms, often through the delivery of \hl{a RESTful API}.
+These services are built around commercial capacities and can be used independently by fully automated implementation machines \cite{LewisMicroservices}.
 \hl{These services are implemented independently with minimizing the centralized dependencies.
@@
 When building communication endpoints, \hl{many architectural approaches are adding significant smart by providing different protocol supports and complex logic support via the endpoints.} As an example \acrshort{esb} support multiple protocols and endpoints can use complex logic.
-But microservice follows an alternative approach: \emph{Smart endpoints and dumb pipes} \cite{LewisMicroservicesPipes}.
-Applications built from microservices aim to be as decoupled and as cohesive as possible.
-They own their domain logic and act more as filters in the classical Unix sense.
-After receiving a request, applying logic as appropriate and producing a response.
-And it uses simple RESTful protocols rather than complex protocols.
+But microservice architecture follows an alternative approach called as \emph{Smart endpoints and dumb pipes} \cite{LewisMicroservicesPipes}.
+Applications built on the basis of microservices are intended to be as disconnected and as coherent as possible.
+They have their domain logic and work more like filters in the classical Unix meaning.
+After receiving a request, apply the correct logic and produce a response.
+And it uses simple RESTful protocols instead of complex protocols.
 \dbc{RESTish or RESTful?}
@@
 
-\acrshort{microservice} prefer letting each service manages its database, either different instances of the same database technology, or entirely different database systems - an approach called \emph{Polyglot Persistence} \cite{LewisMicroservicesManagement}.
+\acrshort{microservice} prefers to have each service manage its database, either different instances of the same database technology or entirely different database systems - an approach called \emph{Polyglot Persistence} \cite{LewisMicroservicesManagement}.
 
-The idea is to keep each microservice’s persistent data private to that service and accessible only via its \acrshort{api}. 
-There are a few different ways to keep a service's persistent data private.
-It does not need to provision a database server for each service.
-For example, in the case of using a relational database then the following methods can be used to keep data private \cite{RichardsonMicroservicesService}:
+The idea is to keep the persistent data of each microservice private for this service and only to make it accessible via the \acrshort{api}.
+There are different ways to keep the permanent data of a service private.
+It is not necessary to set up a database server for each service.
+For example, when you use a relational database, the following methods can be used to keep the data private.
+\cite{RichardsonMicroservicesService}:
 \begin{itemize}
-    \item \emph{Private tables per service} –- each service owns a set of tables that must only be accessed by that service
-    \item \emph{Schema per service} –- each service has a database schema that private to that service
+    \item \emph{Private tables per service} –- each service has a set of tables that this service should not have access to.
+    \item \emph{Schema per service} –- each service has a private database schedule for this service.
     \item \emph{Database server per service} -– each service has its database server.
 \end{itemize}
-\emph{Private tables per service} and \emph{schema per service} have the lowest overhead.
-Using a \emph{schema per service} is appealing since it makes ownership clearer.
-Some high throughput services might need their database server.
+\emph{private tables per service} and \emph{schedule per service} have the lowest overhead.
+The use of an \emph{schedule per service} is interesting because it makes the property clearer.
+Some high throughput services may require their database server.
 
@@
 \label{subse:sagas}
-To ensure loose coupling, each microservice better to have own database.
-Maintaining data consistency between services is a challenge because 2 phase-commit/distributed transactions is not an option for many applications.
-A service publishes an event when its data changes.
-Other services consume that event and update their data \cite{RichardsonMicroservicesSagas}.
+To guarantee a loose coupling, every microservice can have its own database.
+Maintaining data consistency between services is a challenge because 2 phase-commit/distribution transactions are not an option for many applications.
+A service publishes an event when the data changes.
+Other services use this event and update their data \cite{RichardsonMicroservicesSagas}.
 This is also called the \emph{Saga pattern}.
@@
 
-\paragraph{X-axis Scaling}-- X-axis scaling consists of running multiple copies of an application behind a load balancer.
+\paragraph{X-axis Scaling}-- When scaling the X-axis, multiple instances of an application execute behind a load balancer.
 If there are \textit{n} copies then each copy handles 1/\textit{n} of the load.
-This is a simple, commonly used approach to scaling a service.
+A commonly used simple approach to scaling a service.
 
-\paragraph{Y-axis Scaling}-- Unlike the X-axis and Z-axis, which consist of running multiple, identical copies of the application, Y-axis axis scaling splits the application into multiple, different services.
-Each service is responsible for one or more closely related functions.
-There are a couple of different ways of decomposing the application into services.
+\paragraph{Y-axis Scaling}-- When compared to the Z-axis and X-axis scaling, which follows the concept of running multiple identical copies of the application, but Y-axis axis scaling segregate the application into multiple services in same domain.
+So, the end services are responsible for one or more closely related functions.
+There are different ways to split the application into services.
 \begin{itemize}
     \item verb-based decomposition. e.g., checkout.
-    \item decompose the application by noun. e.g., customer management. 
-    \item an application might use a combination of verb-based and noun-based decomposition.
+    \item decompose the application by noun. e.g., order management. 
+    \item it possible to use a combination of verb-based and noun-based decomposition for an application.
 \end{itemize}
@@
 
-\paragraph{Z-axis Scaling}-- When using Z-axis scaling each server runs an identical copy of the code (similar to X-axis scaling).
-The big difference is that each server is responsible for only a subset of the data.
+\paragraph{Z-axis Scaling}-- The Z-axis scaling is following the concept of each service runs an same application code (similar to X-axis scaling).
+The big difference is that each service is responsible for only a subset of the data.
 Z-axis splits are commonly used to scale databases. Data is partitioned (a.k.a. sharded) across a set of servers based on an attribute of each record.

### 2020-02-21 method/sec_5-data_preprocess.tex
Plagiarism microservices

@@
     \includegraphics[width=0.5\textwidth]{method/data_preprocess/weather_data_preprocessing.jpg}
-    \caption{\hl{Generic mathematical function model for weather data preprocessing}}
+    \caption{\hl{Weather data preprocessing using a generic mathematical function model}}
     \label{fi:weather_data_preprocessing}
@@
 \subsection{Interpolation}
-The Interpolation module generates data at desired locations or desired points in time using either a serial or spatial interpolation technique.
-It is applied for the filling in of data gaps in measured on-line data, as well as to derive spatially distributed data for meteorological time series, such as precipitation and temperature, based on information available at neighboring locations.
+The interpolation module generates data at desired locations or at desired data points using a serial or spatial interpolation technique.
+It is used to fill gaps in on-line measured data, and to derive spatially distributed data for weather time series, such as precipitation and temperature, based on information available at nearby locations.
 

### 2020-02-28 ThePaper.tex
Dr Dilum: After comments on the paper

@@
 
-\title{Weather Data Integration and Assimilation System\\
+\title{WDIAS : A Microservices-Based Weather Data Integration and Assimilation System\\
 % \thanks{Identify applicable funding agency here. If none, delete this.}
@@
 
+\dbc{For a paper we need to mode specific title. Is the suggested title ok?}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\db{Numerical Weather Models (NWMs) utilize data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images.
-Prior to using such multimodal data into a NWM, it is necessary to transcode data into a format that can be ingested by the NWM.
-Moreover, the data integration system’s response time needs to be relatively low to forecast and monitor time-sensitive weather events like hurricanes, storms, and flash floods that require rapid and frequent execution of NWMs.
+Numerical Weather Models (NWMs) utilize data from diverse sources such as automated weather stations, radars, air balloons, and satellite images.
+Prior to use, such multimodal data need to be transcoded into a format that can be ingested by the NWM.
+Moreover, the data integration system's response time needs to be relatively low to forecast and monitor time-sensitive weather events like hurricanes, storms, and flash floods that require rapid and frequent execution of NWMs.
 The resulting weather data also need to be accessed by many researchers and third-party applications.
-Even though there are several weather data integration systems, they are based on monolithic or client-server architectures and are unable to benefit from novel computational models such as cloud computing and containers.
-Moreover, most of this software is proprietary or closed sourced; hence, it is difficult to customize such software for an island like Sri Lanka with different weather seasons.
-Therefore, in this research, we propose Weather Data Integration and Assimilation System (WDIAS) that utilizes modern architecture pattern such as microservices to achieve scalability, high availability, and low-cost operation based on cloud computing.
+Even though there are several weather data integration systems, they are based on monolithic or client-server architectures; hence, are unable to benefit from novel computational models such as cloud computing and containers.
+Moreover, most of those systems are proprietary or closed sourced; hence, it is difficult to customize such software for an island like Sri Lanka with different weather seasons.
+Therefore, in this paper, we present a weather data integration and assimilation system (WDIAS) that utilizes modern architecture pattern such as microservices to achieve scalability, high availability, and low-cost operation based on cloud computing.
 WDIAS provides a modular architecture to integrate data from different sources, export into different formats, and the inbuilt extension module system allow users to add new features.
-We demonstrate the utility of WDIAS using cloud-based experimental setup and weather-related synthetic workloads.}
+We demonstrate the utility of WDIAS using cloud-based experimental setup and weather-related synthetic workloads.
 \end{abstract}
+
+\dbc{Reduce background by ~25\%. Add a sentence on novetly on solution. Also. add a sentence on performance. Abstarct should not exceed 200 words.}
 
@@
 \end{IEEEkeywords}
+\dbc{Update keyword list based on thesis. 4-5 keywords max}
 
@@
 Further these data need to be process with less time, and need to handle bulk stream weather data.
+\dbc{This para needs to be more specific. For e.g., some of the key motivations listed in Abstract is not listed here. Also, they should ideally be an expanded version of the motivation.}
 
-There are many forecasting systems developed with considering above factors for disaster management.
+%There are many forecasting systems 
+\db{Several forecasting systems are} developed with considering above factors for disaster management.
 The \acrshort{fews}\cite{Werner2013TheSystem} is developed in the Netherland by Deltares for operational forecasting.
@@
 The main purpose of this system is to design and implement an extendable weather data integration, assimilation, and dissemination system which is capable of handling bulk data efficiently with providing scalability and high throughput with using open source tools and modern cloud computing technologies.
+\dbc{Reduce previous 3 para into at most 2 paras. Ideally one para.}
+\dbc{Need to add a paragraph that clearly highlight the research contribution, its novelty, how we do it, and a sentence or 2 on performance.}
 
-This paper first provides a brief review on necessity of weather forecasting and some of existing weather data systems.
-\cref{pse:background} provides an overview of modern architectural patterns used in \acrshort{wdias} and the important components and features of the \acrshort{wdias} discussed in \cref{pse:wdias_architecture}, next \cref{pse:performance_analysis} discusses the test workload performance analysis with comparing with the metrics.
+%This paper first provides a brief review on necessity of weather forecasting and some of existing weather data systems. 
+\db{Rest of the paper is organized as follows:} \cref{pse:background} provides an overview of modern architectural patterns used in \acrshort{wdias} and the important components and features of the \acrshort{wdias} discussed in \cref{pse:wdias_architecture}, next \cref{pse:performance_analysis} discusses the test workload performance analysis with comparing with the metrics.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{pse:background}
+\dbc{This section should only provide essential backkground to weather as most CS readers will not know the domain.
+No need to discuss about Microservices, AKKA, ESB, etc.
+By the way, we should not add more than a couple of sentence (or a short para) on AKKA and ESB.
+We can just tell them we tried that approach and decided not to proceed in that path because of x, y, and z...}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Weather Data Integration and Assimilation System Architecture}
+\section{\db{Proposed Architecture}}
+%\section{Weather Data Integration and Assimilation System Architecture}
 \label{pse:wdias_architecture}
@@
 \end{figure}
+
+\dbc{What tool did you used to generate these figures. If it support exporting images as PDF, use them with Latex as it gives you a vector image.}
 
@@
 \end{itemize}
+\dbc{Drop the REST API. No need for a paper. You can briefly mention it.}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{WDIAS Database Structure}
+\subsection{Database Structure}
 \label{subse:wdias_database}
+\dbc{It's odd to start a sub-section after a very-long discussion. So add a sub-section for discussion up to this point.}
 
@@
 
+\dbc{Code examples should be included only if they are novel and essential for discussion. If included, key lines in code need to be explained while referring to line numbers.}
+
 Extension Handler is responsible for triggering the correct Extension with metadata when there is any change on the subscribed extension trigger's \emph{OnChange} timeseries.
@@
 
+\dbc{Drop pfi-performance_study figure. No need for paper. But explain key details in text.}
+
 Holding the peak load will help to show whether the system is capable of scaling more than the proposed load testing plan.
@@
 \end{table}
+
+\dbc{All numerical values in tables must to right aligned.}
 
@@
 \gkc{Just kept the important sections}
+\dbc{Summary should not be more than a single para for a paper.}
 
@@
 \label{pse:ack}
-\db{This research is supported in part by the grant from the Center for Urban Water, Sri Lanka.}
+This research is supported in part by the grant from the Center for Urban Water, Sri Lanka.
 
@@
 \printbibliography[title={References}]
+\dbc{References must be in IEEE standard. Some are not quite formatted for IEEE standard. For e.g., some of the paper and conference titles are in upper case.}
 

### 2020-02-29 ThePaper.tex
Paper: Updated the introduction

@@
 \dbc{For a paper we need to mode specific title. Is the suggested title ok?}
+\gkc{Looks fine for me}
 
@@
 \begin{abstract}
-%We describe our experience with implementing an extendable open source Weather Data Integration and Assimilation System, which is known as \acrshort{wdias}.
-It uses the modern architecture pattern such as microservice in order to achieve the scalability, rather using monolithic architecture or client service architecture.
-It provides a modular approach to integration data from different sources and export into different formats.
-Also the inbuilt extension module system allow users to add new features.
-The open source tools that are using for \acrshort{wdias} allows to run on Cloud Computing platforms without much hassle with the auto-scaling feature allow to run \acrshort{wdias} from 1 CPU node to nodes with few hundred CPUs.
-The paper describes the initial design goals, evolve over few architectures to get desired performance, and explains how the system in way to achieve scalability.
-Later we analyse the performance test observations with the performance metrics.
-
-Numerical Weather Models (NWMs) utilize data from diverse sources such as automated weather stations, radars, air balloons, and satellite images.
+% Numerical Weather Models (NWMs) utilize data from diverse sources such as automated weather stations, radars, air balloons, and satellite images.
 Prior to use, such multimodal data need to be transcoded into a format that can be ingested by the NWM.
@@
 We demonstrate the utility of WDIAS using cloud-based experimental setup and weather-related synthetic workloads.
+Numerical Weather Models (NWMs) utilize data from diverse sources such as automated weather stations, radars, and satellite images.
+Before use, such multimodal data need to be transcoded into a NWM compatible format.
+Moreover, the data integration system's response time needs to be relatively low to increase the lead time of forecast for events like hurricanes, and flash floods.
+The resulting data need to be accessed by many researchers and third-party applications.
+Even though there are several weather data integration systems available, those are proprietary or closed sourced or based on monolithic or client-server architectures.
+Hence, it is difficult to customize such software for an island like Sri Lanka with different weather seasons.
+Therefore, in this paper, we present a weather data integration and assimilation system (WDIAS) that uses modern microservice architecture pattern and container orchestration to run platform independently and support cloud hosting to achieve scalability, high availability with low-cost.
+WDIAS provides a modular architecture to integrate data from different sources, export into different formats, and the inbuilt extension module system allow users to add new features.
+Using an experimental setup on the cloud, we demonstrate that WDIAS is capable of handling 18,000 requests per minute with different data types.
 \end{abstract}
@@
 \dbc{Reduce background by ~25\%. Add a sentence on novetly on solution. Also. add a sentence on performance. Abstarct should not exceed 200 words.}
+\gkc{Modified. 200 words.}
 
 \begin{IEEEkeywords}
-\db{Cloud computing, data assimilation, data integration, }
+\db{Cloud computing, data assimilation, data integration, }microservice, weather
 \end{IEEEkeywords}
 \dbc{Update keyword list based on thesis. 4-5 keywords max}
-
+\gkc{Thesis keywords are Cloud computing, data assimilation, data integration, hierarchical databases, microservice, weather. Do we need different set of keywords?}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{pse:Introduction}
-Weather prediction is essential to reduce impact due to natural disasters and to gain
-effectively manage natural resources like water.
+% Weather prediction is essential to reduce impact due to natural disasters and to gain effectively manage natural resources like water.
 \acrfull{curw}\cite{CUrWSL2017SL} is tasked with the mission to reduce water-related natural disasters in Sri Lanka.
@@
 Then the generated results are shared with relevant public departments responsible for disaster planning, mitigation, and management.
-To enhance the accuracy of weather predictions, it is necessary to provide reliable and
-detailed weather data as inputs to \acrfull{nwm}s.
-Before feeding such diverse data collected from different sources, it is necessary to a data format that can be ingest by the NWMs.
-Further these data need to be process with less time, and need to handle bulk stream weather data.
+Weather prediction is essential to reduce impact due to natural disasters and to gain effectively manage natural resources like water.
+To enhance the accuracy of weather predictions, it is necessary to provide reliable and detailed weather data as inputs to \acrfull{nwm}s.
+Before feeding such diverse data collected from different sources, it is necessary to convert to a data format that can be ingest by the NWMs.
+Further these data need to be process with less time to increase the lead time of forecasting, and need to handle bulk stream weather data.
+Processed weather data needs to be accessed by many third-party applications and research to make use of them.
+For example, logistics companies could use those data with their models to plan and schedule their deliveries.
+Agricultural insurance companies can warn the farmers, as well as calculate premiums based on anticipated weather patterns.
+Even though there are many data integration systems, most of them are proprietary or closed source.
+For an island like Sri Lanka that having different kinds of weather seasons over the year than that software originated need to be highly customized.
+Thus it required to get support from the vendor to integrate and configure the system.
+And most of the software existing out there are not up to date with the latest technology concepts such as Cloud Computing, not using modern architecture pattern such as microservice architecture was able to provide high scalability and availability, and depend on the software platforms.
 \dbc{This para needs to be more specific. For e.g., some of the key motivations listed in Abstract is not listed here. Also, they should ideally be an expanded version of the motivation.}
+\gkc{Updated referring to motivation section.}
 
@@
 It uses a model-centric approach with considering forecasting process as a combination of data modeling steps and data transformation algorithms.
-So, it is a flexible framework with no inherent hydrological modeling capabilities and system and capable of creating forecasting workflows by integrating new models and algorithms.
-Also it follows a common data-model and allow models to interact with the system via one of the interfaces provided, and all the timeseries data are stored via this common data model.
+So, it is a flexible framework with no inherent hydrological modeling capabilities and capable of creating forecasting workflows by integrating new models and algorithms.
+Also it follows a common data-model approach with only allowing models to interact with the system via one of the interfaces provided, and all the timeseries data are stored via this common data model.
 Even this approach is efficient in data storing and accessing, but it has the inherent issues of performance of accessing data via a single data model in a database.
 One of interesting concept of \acrshort{fews} is using unique fields to identify timeseries such by their location and data type, as well as an id related to the source of the data.
-Even it provide an simple but most effective feature by following the concept of the open modeling framework proposed by Open model integration \cite{Kokkonen2003InterfacingXML}, the model adapter is causing tide coupling into the execution process with the \acrshort{fews}.
-This causing some issue with unit testing models separately and does not easily allow users to run the models in flexible manner such as parallel execution or external process.
+Even it provides an easy way to integrate models by following the concept of the open modeling framework proposed by Open model integration \cite{Kokkonen2003InterfacingXML}, the model adapter is causing tide coupling into the execution process with the \acrshort{fews}.
+This causing some issue with unit testing models separately and does not easily allow users to run the models in flexible manner such as parallel execution or external process execution.
 
-\acrfull{lead} is using the fundamental concept of  dynamic workflow orchestration and
-data management in a Web services framework \cite{Droegemeier2005Service-OrientedWeather}. To predict and analyze weather models
-by researchers, it required many resources. Rather than each researcher is running and
-handling their computer resources to do the weather experiments, LEAD is providing pool of resources, then the researchers can use this resource a pool to run their
-experiment in shorter amounts of time and higher scale.
-It is following the \acrfull{soa} with different service layers, and expose services via drag and drop interface to create new flow by users to run new forecast workflows.
-Workflow service in the \acrshort{lead} schedule and run those with promising the full use of underline resources in the system.
-\acrfull{dias}\cite{Kawasaki2018DataReduction} and \acrfull{madis}\cite{Macdermaid2005ARCHITECTUREP2.39} mostly provide the functionality of integration and sharing of data.
-When compared to other systems, those do not have the workflow capabilities.
-To store on the large volume of disk space, \acrshort{dias} converts the data via a provided set of \acrshort{api}s and provide the functionality of quality control of the data, and metadata management and  shares the data via the Shared API layer.
-\acrshort{madis} also store the data by converting the data into a common format, and provide access to the data based on role access.
+\acrfull{lead} is using the fundamental concept of  dynamic workflow orchestration and data management in a Web services framework \cite{Droegemeier2005Service-OrientedWeather}.
+To predict and analyze weather models by researchers, it required many resources.
+Rather than each researcher is running and handling their computer resources to do the weather experiments, \acrshort{lead} provides a pool of resources, then the researchers can use the resources pool to run their experiment in shorter amounts of time in higher scale.
+It is following the \acrfull{soa} with different service layers, and expose services via a drag and drop interface to create new flow by users to run new forecast workflows.
+A workflow service inside the \acrshort{lead} schedules and run workflows with promising the full use of underline resources in the system.
+\acrfull{dias}\cite{Kawasaki2018DataReduction} and \acrfull{madis}\cite{Macdermaid2005ARCHITECTUREP2.39} provide the functionality of integration and sharing weather data.
+When compared to other systems, \acrshort{dias} and \acrshort{madis} do not have the workflow capabilities.
+To store data on a large volume of disk space, \acrshort{dias} converts the data using a inbuilt set of \acrshort{api}s and provides the functionality of quality control of the data, and metadata management, and shares the data through a Shared API layer.
+Also, \acrshort{madis} stores the data by converting into a common data format, and provides role based data access.
+As mentioned above, most systems are using monolithic architecture or client service architecture, platform dependent, and not up to date with cloud computing technologies.
+Thus users do not have much flexibility to decide the best cost-effective way to host it.
+Since most system are proprietary or closed source, it is difficult to add new requirements and maintain the system.
 
-Even though there are many data integration systems, most of them are proprietary or closed source.
-For an island like Sri Lanka that having different kinds of weather seasons over the year than that software originated need to be highly customized.
-Thus it required to get support from the vendor to integrate and configure the system.
-And most of the software existing out there is not up to date with the latest technology concepts such as Cloud Computing.
-The modern architecture pattern such as microservice architecture was able to provide high scalability and availability, rather using monolithic architecture or client service architecture.
-Since most of existing systems are dependent underline infrastructure providers, the users do not have much flexibility to decide the best cost-effective way to host it.
-Above facts has been considered while we proposed the \acrfull{wdias}.
-The main purpose of this system is to design and implement an extendable weather data integration, assimilation, and dissemination system which is capable of handling bulk data efficiently with providing scalability and high throughput with using open source tools and modern cloud computing technologies.
 \dbc{Reduce previous 3 para into at most 2 paras. Ideally one para.}
+\gkc{Reduce to two paragraphs.}
 \dbc{Need to add a paragraph that clearly highlight the research contribution, its novelty, how we do it, and a sentence or 2 on performance.}
+\gkc{Added new paragraph below.}
+
+Therefore, in this paper, we present a weather data integration and assimilation system (WDIAS) that is an extendable weather data integration, assimilation, and dissemination system which is capable of handling bulk data efficiently with providing scalability and high throughput with using open source tools which support modern cloud computing advancements.
+When compared to other systems' architectures, \acrshort{wdias} uses modern microservice architecture that enables best use the cloud computing with achieving scalability, high availability with low-cost.
+Using container orchestration to run the system platform independently with easy setup and maintain the system on different computer resources.
+Also, the WDIAS provides a modular architecture to integrate data from different sources, export into different formats, and the inbuilt extension module system allow users to add new features without any downtime.
+Using an experimental setup on the cloud, we demonstrate that WDIAS is capable of handling 18,000 requests per minute with different data types, and each request contains 15 minutes interval data per a day.
+Also, the system is capable of scaling up and shrinking down as per given workload, and capable of running using large range of computer resources such as from few CPUs to few hundred CPUs.
 
@@
 \begin{figure}[htbp]
-\centerline{\includegraphics[width=0.5\textwidth]{method/microservice/separation_microservices-v3.jpg}}
+\centerline{\includegraphics[width=0.5\textwidth]{method/microservice/separation_microservices-v4.pdf}}
 \caption{Separation of \acrshort{wdias} microservices.}
@@
 \dbc{What tool did you used to generate these figures. If it support exporting images as PDF, use them with Latex as it gives you a vector image.}
+\gkc{Replaced with PDF images.}
 
@@
 \begin{figure}[htbp]
-\centerline{\includegraphics[width=0.5\textwidth]{method/microservice/microservice_architecture-handle_on_async-v3.jpg}}
+\centerline{\includegraphics[width=0.5\textwidth]{method/microservice/microservice_architecture-handle_on_async-v4.pdf}}
 \caption{microservice architecture - handle asynchronously.}
@@
 
-as shown in Figure 3.4, when a request
-with a larger size comes to the system, it stores the data for asynchronously process
-the data and responds with a unique id that can use to verify whether data processed
-successfully or not. First it stores the data and publish an event to another service to process it. After successfully process the data by other service, it updates the system status.
-
-The \acrshort{wdias} provides a simple RESTful API to interact with timeseries metadata and other modules.
-\begin{itemize}
-    \item \texttt{/parameter} - CRUD operations on parameters
-    \item \texttt{/timestep} - CRUD operations on time step
-    \item \texttt{/location/point and /location/regualr-grid} - CRUD operations on point location and regular grid locations
-    \item \texttt{/timeseries} - CRUD operations on timeseries
-    \item Import
-    \begin{itemize}
-        \item \texttt{/import/json/raw} - Import JSON data in raw format
-        \item \texttt{/import/csv/raw} - Import CSV data in raw format
-        \item \texttt{/import/ascii-grid/upload} - Upload ASCII JSON Grid files
-    \end{itemize}
-    \item Export
-    \begin{itemize}
-        \item \texttt{/export/json/raw} - Export JSON data in raw format
-        \item \texttt{/export/ascii-grid/binary} - Download ASCII JSON Grid file
-    \end{itemize}
-    \item Extensions
-\end{itemize}
+as shown in Figure 3.4, when a request with a larger size comes to the system, it stores the data for asynchronously process the data and responds with a unique id that can use to verify whether data processed successfully or not.
+First it stores the data and publish an event to another service to process it.
+After successfully process the data by other service, it updates the system status.
+Also the \acrshort{wdias} provides a simple RESTful API to interact with timeseries metadata and other modules such as import, export and extension modules.
 \dbc{Drop the REST API. No need for a paper. You can briefly mention it.}
+\gkc{Removed}
 
@@
 \begin{figure}[htbp]
-\centerline{\includegraphics[width=0.4\textwidth]{method/microservice/wdias_database_structure.jpg}}
+\centerline{\includegraphics[width=0.4\textwidth]{method/microservice/wdias_database_structure.pdf}}
 \caption{\acrshort{wdias} database structure.}
@@
 \acrshort{wdias} is getting a mix of all the data types in the percentages of 70\% scalar, 20\% vector, and 10\% grid values.
-\cref{pfi:performance_study} shows for a given request size the RPS increased in steps.
-In each step, the RPS holds for a moment to give some time for the system to get stabilized.
+For a given request size the RPS increased in steps such as 600, 3000, 6000, 12000, and 18000 requests per minute.
+In each step, the RPS holds for a moment to give some time for the system to get stabilized after increasing linearly.
 
-\begin{figure}[htbp]
-\centerline{\includegraphics[width=0.5\textwidth]{results/work_load/performance_study_v4.jpg}}
-\caption{\acrshort{wdias} load testing plan with changing the request size and \acrshort{rps}}
-\label{pfi:performance_study}
-\end{figure}
+% \begin{figure}[htbp]
+% \centerline{\includegraphics[width=0.5\textwidth]{results/work_load/performance_study_v4.jpg}}
+% \caption{\acrshort{wdias} load testing plan with changing the request size and \acrshort{rps}}
+% \label{pfi:performance_study}
+% \end{figure}
 
-\dbc{Drop pfi-performance_study figure. No need for paper. But explain key details in text.}
+\dbc{Drop pfi-performance-study figure. No need for paper. But explain key details in text.}
+\gkc{Dropped the figure.}
 
@@
 After the peak, the test case goes through a cool-down period to measure the ability to shrink down the resources when there is not any load on the system.
-During the test plan, it runs for 30minutes of period with changing the request size form 1-hour data to 15 minutes data.
+During the test plan, it runs for 30minutes of period with changing the request size form hourly data to 30 minutes data, then 15 minutes data.
 Then another 30 minutes load test enabling the auto scaling of container orchestration system, and perform 5minutes test run with timeseries queries.

### 2020-02-29 introduction/sec_1-motivation.tex
Paper: Updated the introduction

@@
 Weather prediction is essential to reduce the impact caused by natural disasters and to gain effectively manage natural resources like water.
-It will give more understanding of weather prediction if we look into a weather prediction flow that can use to predict the surface water level.
+It will give more understanding of weather prediction if we look into a weather prediction workflow that can use to predict the surface water level.
 The weather predictions/forecasts are performed using \acrfull{nwm} that use a set of configuration parameters and the current status of the environment such as temperature, rainfall, and wind direction as the inputs.
@@
 \acrshort{curw} \cite{CUrWSLObservedSL} is implementing own system with the idea of long-term maintainability rather depend on existing weather data integration systems.
-It collected real-time data from weather stations and other government entities and generates daily forecasts.
-Then the generated results are shared with relevant public departments responsible for disaster planning, mitigation, and management.
+The center collects real-time data from weather stations and other government entities and generates daily forecasts.
+Then the generated results are shared with relevant public departments responsible for disaster planning, risks mitigation, and disaster management.
 One of the future goals of \acrshort{curw} is to open up data to the public enabling both societal and commercial use cases.
@@
 These NWMs utilize multi-modal weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images.
-Before feeding such diverse data (collected from different sources that belong to different stakeholders) into respective NWMs, it is necessary to a data format that can be ingest by the model.
+Before feeding such diverse data (collected from different sources that belong to different stakeholders) into respective NWMs, it is necessary to convert to a data format that can be ingest by the model.
 Moreover, the data integration system’s response time needs to be relatively low to forecast and monitor time-sensitive weather events like hurricanes, storms, and floods which require rapid and frequent execution of NWMs.
@@
 Throughout the operations and maintenance, it is required to get support with paying lots of charges, and difficult to debug into a closed source system without maintenance support from the vendors.
-As an example, \acrshort{fews} does not support FLO2D model integration, and \acrshort{curw} is using FLO2D for water level forecasting in the data flow.
+As an example, \acrshort{fews} does not support FLO2D model integration, and \acrshort{curw} is using FLO2D for water level forecasting in the workflow.
 In such a case, it required to get support from the vendor to integrate and configure the system.
@@
 Most existing systems required to shut down to update the system configuration such as \acrshort{fews}, but a system that is accessed by any third parties should be operating 99.9\% without any downtime and should allow adding new features on the fly with rollover capabilities.
-The proposed system should be independent of the platform.
+The proposed system should be independent of the platforms.
 But most software out there is platform dependent, as an example \acrshort{fews} can run on Windows and Linux.

### 2020-02-29 ThePaper.tex
Paper: Fixed the summary

@@
 Therefore, in this paper, we present a weather data integration and assimilation system (WDIAS) that is an extendable weather data integration, assimilation, and dissemination system which is capable of handling bulk data efficiently with providing scalability and high throughput with using open source tools which support modern cloud computing advancements.
-When compared to other systems' architectures, \acrshort{wdias} uses modern microservice architecture that enables best use the cloud computing with achieving scalability, high availability with low-cost.
+When compared to other systems' architectures, \acrshort{wdias} uses modern microservice architecture that enables best use of the cloud computing with achieving scalability, high availability with low-cost.
 Using container orchestration to run the system platform independently with easy setup and maintain the system on different computer resources.
@@
 \label{pse:background}
-\dbc{This section should only provide essential backkground to weather as most CS readers will not know the domain.
+\dbc{This section should only provide essential background to weather as most CS readers will not know the domain.
 No need to discuss about Microservices, AKKA, ESB, etc.
@@
 We can just tell them we tried that approach and decided not to proceed in that path because of x, y, and z...}
+\gkc{Removed discussion about AKKA, ESB etc. Kept few points on microservices concepts that used.}
 
@@
 
-The \acrshort{wdias} is supporting all three above modules. It iterate through few architectures with concerning about the scalability and high availability.
-The initial design of WDIAS used the Service Oriented Architecture (SOA).
-Moreover, it tried to use an Enterprise Service Bus (ESB) to integrate different modules, as ESB is acting as a common layer for all of the modules.
-However, it turned out that ESB is not suitable for data streaming or bulk data processing and ESB suffers from a single point of failure since it is using a common bus.
-In the second design phase of WDIAS, we attempted to use the actor model using the AKKA framework [9] to overcome above ESB drawbacks and followed the microservice architecture.
-The system architecture redesign with decomposing into microservices and
-used actors to implement each microservice in the system.
-
-Microservice architecture is resilient and flexible as one service is independent of another service.
-And it is highly scalable as demanding services can be deployed in multiple servers.
+The \acrshort{wdias} is supporting all three modules shown in \cref{pfi:wdia_components}.
+Through out the design phase of \acrshort{wdias}, we iterate through few architectures with concerning about the scalability and high availability.
+Initially, we followed \acrfull{soa} with using \acrfull{esb} to integrate different modules.
+However, we understood that \acrshort{esb} is not suitable for data streaming or bulk data processing and suffers from a single point of failure since it uses a common bus.
+In second design phase, we used the Actor model with AKKA framework with following the microservice architecture such that each microservice is implemented using actors.
+Microservice architecture is resilient and flexible as one service is independent of another service enables to highly scalable individual services.
 One of the attractive features of microservice architecture is the independent nature of the microservices which allows to choose different technologies and maintain separately.
 But using AKKA framework for implement microservice architecture has some disadvantages such as unable to choose independent technologies and the actors messaging between different services cause to result in a too-tight code coupling between the services.
-To overcome these issues, we moved to the concept of container orchestration based microservice architecture.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Microservice Architecture}
-\label{psubse:microservice_architecture}
-
-A microservice architecture style is an approach to developing a single application as
-a suite of small services, each running in its own process and communicating with
-lightweight mechanisms, often via providing a RESTful API. Follow are some of the microservice design patterns mostly used in the context of designing WDIAS architecture.
-\begin{itemize}
-    \item \emph{Smart Endpoints and Dumb Pipes} - rather than implementing smart endpoints with supporting multiple protocols and complex logic, microservices aim to be as decoupled and as cohesive as possible with only focusing one own domain.
-    \item \emph{Database per microservice} - The idea is to keep each microservices persistent data private to that service and accessible only via its API.
-    \item \emph{Distributed Transactions over microservices via event processing} - A service publishes an event when its data changes. Other services consume that event and update their data.
-    \item \emph{X-axis Scaling} -  running multiple copies of an application behind a load balancer
-    \item \emph{Y-axis Scaling} - splits the application into multiple, different services.
-Each service is responsible for one or more closely related functions.
-The microservice architecture is an application of Y-axis scaling.
-    \item \emph{Z-axis Scaling} - each server runs an identical copy of the code (similar to X-axis scaling). The big difference is that each server is responsible for only a subset of the data.
-\end{itemize}
-
-The \acrshort{wdias} is using \acrfull{k8s} as the container orchestration system which is an open-source tool for automating deployment, scaling, and management of containerized applications.
-
-\begin{figure}[htbp]
-\centerline{\includegraphics[width=0.5\textwidth]{method/microservice/k8s_architecture_v3.jpg}}
-\caption{\acrfull{k8s} architecture.}
-\label{pfi:k8s_architecture}
-\end{figure}
-
-\cref{pfi:k8s_architecture} gives an overall idea on the components of \acrshort{k8s},
-\begin{itemize}
-    \item Pods -- Cluster of containers that can group other container images in a single unit.
-    \item Nodes -- the machines (VMs, physical servers, etc) in a cluster that runs your applications and cloud workflows.
-    \item kubelet -- An agent that runs on each node in the cluster. It makes sure that containers are running in a pod.
-    \item kube-proxy -- A network proxy that runs on each node in the cluster, and maintains network rules on nodes.
-    \item Kubernetes master -- Responsible for maintaining the desired state for your cluster.
-    \item etcd -- Consistent and highly-available key value store used as Kubernetes’ backing store for all cluster data.
-\end{itemize}
-Users can add much as required Nodes into the K8s cluster, and K8s manage and
-deploy applications as pods into cluster nodes. Thus it allow users to implement the microservice architecture concepts above easily.
+To overcome the issues using AKKA, we moved to the concept of container orchestration based microservice architecture.
+The \acrshort{wdias} used \acrfull{k8s} as the container orchestration system which is an open-source tool for automating deployment, scaling, and management of containerized applications.
+Using \acrshort{k8s}, users can add required resources as Nodes to the cluster, and K8s manage and deploy applications as pods into cluster nodes.
+In next \cref{pse:wdias_architecture}, we discussed about the \acrshort{wdias} used microservice concepts such as implement microservice as dumb pipes rather implementing smart endpoints, uses database per service with access via API only, distributed Transactions over microservices using event processing, and considering distributed systems scalability in directions of X-axis scaling, Y-axis scaling and Z-axis scaling.
 
@@
 \label{pse:wdias_architecture}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{WDIAS Microservice Architecture}
+\label{psubse:wdias_microservices}
 
@@
 
-The left side of Figure 3.3
-shows the import modules of the WDIAS, and the right side shows the export modules. each import microservice only does the specific
-task of converting and forwarding the request to the correct data adapter module. each data type, there is an adapter microservice is running which is optimized to storing
-such type of data. Each adapter has an isolated database, and the database is hosted separately for the high performance.
-And timeseries metadata stored using RDBMS which gives more performance over retrieving metadata data, and cached with the In-Memory database to fast access. The system
-generates a unique identifier for each timeseries, and throughout the WDIAS, other
-microservice use it to handle data for fast access.
-Export module microservice follows the same concepts and provides the capability
-to export the data into required formats of the weather models.
+The left side of Figure 3.3 shows the import modules of the WDIAS, and the right side shows the export modules.
+each import microservice only does the specific task of converting and forwarding the request to the correct data adapter module.
+each data type, there is an adapter microservice is running which is optimized to storing such type of data.
+Each adapter has an isolated database, and the database is hosted separately for the high performance.
+And timeseries metadata stored using RDBMS which gives more performance over retrieving metadata data, and cached with the In-Memory database to fast access.
+The system generates a unique identifier for each timeseries, and throughout the WDIAS, other microservice use it to handle data for fast access.
+Export module microservice follows the same concepts and provides the capability to export the data into required formats of the weather models.
 
@@
 
-as shown in Figure 3.4, when a request with a larger size comes to the system, it stores the data for asynchronously process the data and responds with a unique id that can use to verify whether data processed successfully or not.
+As shown in Figure 3.4, when a request with a larger size comes to the system, it stores the data for asynchronously process the data and responds with a unique id that can use to verify whether data processed successfully or not.
 First it stores the data and publish an event to another service to process it.
@@
 \subsection{Database Structure}
-\label{subse:wdias_database}
+\label{psubse:wdias_database}
 \dbc{It's odd to start a sub-section after a very-long discussion. So add a sub-section for discussion up to this point.}
+\gkc{Added a sub section above \cref{psubse:wdias_microservices}.}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Strengths and Limitations}
-\label{psubse:limitations}
+\subsection{Discussion}
+\label{psubse:discussion}
 \dbc{Make this the discussion and a sub-section of Sec. 4}
+\gkc{Renamed. I did not get what did you mean by sub section 4. Did you mean \cref{pse:summary}?}
 
@@
 \dbc{Summary should not be more than a single para for a paper.}
+\gkc{Reduce to one paragraph with removing some info.}
 
-Even though there are many weather data integration systems, most of them are proprietary or closed source and based on basic client-server architectures or monolithic distributed system architectures.
-Thus those are unable to get the advantage of modern computational models such as containerized applications and using the could computing to gain benefits of scalability, high availability and low-cost operations.
-Also for an island like Sri Lanka that having different kinds of weather seasons over the year those software needs to be highly customized.
-In this paper, we present an extendable open source weather data integration and assimilation system known as \acrshort{wdias} which uses modern microservice architecture pattern and cloud computing tools such as container orchestration to gain high scalability and availability.
-
+In this paper, we present an extendable open source weather data integration and assimilation system to overcome the issues in existing systems.
+Most systems are proprietary or closed source, based on client-server architectures or monolithic distributed system architectures, and depend on computer platforms unable to use could computing to gain benefits of scalability, high availability and low-cost operations.
+The proposed system uses modern microservice architecture pattern and cloud computing tools such as container orchestration to gain high scalability and availability.
 Based on the nature of the weather metadata, the \acrshort{wdias} used a database structure to provide higher performance while storing the weather data optimum.
-As described in \cref{pse:wdias_architecture}, it uses many of the concepts of microservice architecture to create stateless, failover, redundant microservice.
-Also, the system provides a generic open mechanism to integrate new modules as an extension to enhance the features of the system and weather data preprocessing.
-The \acrshort{wdias} provides an extension API to easy access to create and modify the extension triggers on the fly and support complex timeseries metadata queries with Geo-based support.
-
-The paper also presents performance analysis of the \acrshort{wdias} with load testing using \acrshort{jmeter} tool with system setup on \acrfull{k8s} cluster on Cloud infrastructure.
-Based on the observations, the system was able to handle 300 \acrshort{rps} (which means 18,000 requests per minute) successfully with minimizing the error rate to zero.
-Also, while increasing the request size, the system was able to perform the same while keeping the latency constant without any significant change and the system was able to increase the throughput by keeping the latency constant while increasing the workload which exhibits the scalability of the system.
-With the \acrshort{k8s} auto-scaling, the \acrshort{wdias} were able to elastically adjust the number of pods to handle the workload and shows that the system can run from 1 CPU node to nodes with a few hundred CPUs.
+\acrshort{wdias} uses many microservice architecture concepts to create stateless, failover, and redundant microservice with providing a generic open mechanism to integrate new modules as an extension to enhance the features of the system and weather data preprocessing.
+Further, the system provides an extension API to easy access to create and modify the extension triggers on the fly and support complex timeseries metadata queries with Geo-based support.
+We used an experimental \acrshort{k8s} setup on Cloud infrastructure for the performance analysis, and the \acrshort{wdias} able to handle 18,000 requests per minute successfully with minimizing the error rate to zero.
+Also, we repeated the test cases while increasing the request size.
+The system handled increasing workload same while keeping the latency constant without any significant change and able increase the throughput.
+With referring to above facts, it shows the scalability of the \acrshort{wdias} system.
+Using \acrshort{k8s} auto-scaling, the system were able to elastically adjust the number of pods to handle the workload and shows that the system can run from few CPU node to nodes with a few hundred CPUs.
 

### 2020-02-29 ThePaper.tex
Paper: Finalized

@@
 A workflow service inside the \acrshort{lead} schedules and run workflows with promising the full use of underline resources in the system.
-\acrfull{dias}\cite{Kawasaki2018DataReduction} and \acrfull{madis}\cite{Macdermaid2005ARCHITECTUREP2.39} provide the functionality of integration and sharing weather data.
+\acrfull{dias}\cite{Kawasaki2018DataReduction} and \acrfull{madis}\cite{Macdermaid2005ArchitectureP2.39} provide the functionality of integration and sharing weather data.
 When compared to other systems, \acrshort{dias} and \acrshort{madis} do not have the workflow capabilities.
@@
 This means it is possible to change the behavior of an existing function by providing different bind constant at the time of creating new triggers for an extension.
-The system allow to create new triggers and update them at the run time via POST requests.
+The system allow to create new triggers and update them at the run time via API with the POST request body shown in \cref{pli:extension_triggers}.
 
-\begin{lstlisting}[language=Python]
+\begin{lstlisting}[language=Python, caption=Update Extension Triggers API, label=pli:extension_triggers]
 {
-    "extensionId": "", // An unique identifier for new extension trigger
-    "extension": "Interpolation/Transformation/Validation",
-    "function": "", // microservice which handles the function mapping
-    "variables": [ // Array of timeseries mapping to variables
+    "extensionId": "", //Trigger unique identifier
+    "extension": "Interpolation | Transformation | Validation",
+    "function": "", //Mapping microservice
+    "variables": [ //Timeseries mapping to variables
         {
             "variableId": "",
-            "metadata/metadtaIds": {
-            }
+            "metadata/metadtaIds": {...}
         }
     ],
-    "inputVariables": [], // Input timeseries
-    "outputVariables": [], // Output timeseries
+    "inputVariables": [], //Input timeseries
+    "outputVariables": [], //Output timeseries
     "trigger": [ // When to trigger the function
         {
-            "trigger_type": "OnChange/OnTime",
+            "trigger_type": "OnChange | OnTime",
             "trigger_on": []
@@
     ],
-    "options": { // Run time bind contant data for the extension
+    "options": { //Run time bind constant data
     }
@@
 \dbc{Code examples should be included only if they are novel and essential for discussion. If included, key lines in code need to be explained while referring to line numbers.}
+\gkc{Updated.}
 
-Extension Handler is responsible for triggering the correct Extension with metadata when there is any change on the subscribed extension trigger's \emph{OnChange} timeseries.
-Extension Handler is responsible for triggering the correct Extension with metadata at a given time which is provided at the creation on extension trigger with the value of OnTime cronjob string value.
+We implemented the system with possible to create multiple triggers for an extension such as Transformation can have two trigger to sample 1 minute data into 5 minutes data and 1 minute data into hourly data.
+Each extension trigger need to have a unique identifier as shown in Line 2.
+Then we allowed users to define the extension type (Line 3) and the microservice which is responsible of processing it (Line 4).
+User can map timeseries into variable and use them as \emph{X} input and \emph{Y} outputs in the \cref{pfi:summary_weather_data_preprocessing} (Line 5-12).
+Then provide when to trigger the extension with providing optional data as mentioned in the extension implementation.
+
+\emph{Extension Handler} is responsible for triggering the correct Extension with metadata when there is any change on the subscribed extension trigger's \emph{OnChange} timeseries.
+\emph{Extension Handler} is responsible for triggering the correct Extension with metadata at a given time which is provided at the creation on extension trigger with the value of \emph{OnTime} cronjob string value.
 To improve the performance of triggering cronjobs at given time schedules, the WDIAS added few optimization mechanisms.
@@
 
-Other than the metadata manipulation API mentioned in \cref{psubse:microservice_architecture}, the \acrshort{wdias} also supports timeseries search queries and Geo queries.
-As an example it can \emph{query timeseries in an area} This operation uses \texttt{geoWithin} search operator for the simplicity.
+Other than the metadata manipulation API mentioned in \cref{psubse:wdias_microservices}, the \acrshort{wdias} also supports timeseries search queries and Geo queries.
+As an example it can \emph{query timeseries available in a given area}.
+This operation uses \texttt{geoWithin} search operator for the simplicity.
 Other than it can also support query timeseries in an area by parameter, query available timeseries by locations and query locations within an area etc.
-\begin{lstlisting}
+In \cref{pli:geo_search}, the \acrshort{wdias} return the timeseries available within the area of a polygon provided as \emph{geoJson} \cite{InternetEngineeringTaskForceGeoJSON}.
+
+\begin{lstlisting}[caption=Geo search timeseries, label=pli:geo_search]
     POST <HOST_NAME>/query/timeseries
@@
                 [
-                    [
-                        <longitude>,
-                        <latitude>
-                    ],
+                    [<longitude>, <latitude>],
                     ...
@@
 
-\begin{table}[ht]
-\centering
+\begin{table}[htbp]
 \caption{\acrshort{eks} nodes}
+\begin{center}
 \begin{adjustbox}{width=0.45\textwidth}
-\footnotesize
-\begin{tabular}{|l|c|c|c|c|l|}
+\begin{tabular}{|l|r|r|r|r|l|}
 \hline
@@
 \label{ptab:aws_eks_nodes}
+\end{center}
 \end{table}
@@
 \dbc{All numerical values in tables must to right aligned.}
+\gkc{Updated. Fixed the tables.}
 
@@
 \begin{table}[htbp]
-\caption{ Throughput and Latency of load testing with 60min data}
-\begin{center}
-\footnotesize
-\begin{adjustbox}{width=0.49\textwidth}
-\begin{tabular}{|c|c|c|c|c|c|c|}
+\centering
+\caption{Throughput and Latency of load testing with 60min data}
+\begin{adjustbox}{width=0.45\textwidth}
+% \footnotesize
+\begin{tabular}{|l|r|r|r|r|r|r|}
 \hline
-\textbf{Label} & \textbf{Samples} & \textbf{Avg$^{\mathrm{a}}$} & \textbf{90\%$^{\mathrm{b}}$} & \textbf{S.D.$^{\mathrm{c}}$} & \textbf{Error \%} & \textbf{RPS} \\ \hline
+\textbf{Label} & \textbf{Samples} & \textbf{Avg} & \textbf{90\%$^{\mathrm{a}}$} & \textbf{S.D.$^{\mathrm{b}}$} & \textbf{Error \%} & \textbf{RPS} \\ \hline
 Insert Timeseries & 71826 & 28 & 31 & 58.74 & 0.00\% & 40.5 \\ \hline
@@
 \textbf{TOTAL} & 311182 & 127 & 503 & 207.80 & 0.00\% & 175.4 \\ \hline
-\multicolumn{4}{l}{$^{\mathrm{a}}$Avg: Average Latency, $^{\mathrm{b}}$S.D.: Standard Deviation, $^{\mathrm{c}}$90\%: 90\% percentile.}
+\multicolumn{4}{l}{$^{\mathrm{a}}$S.D.: Standard Deviation}{$^{\mathrm{b}}$90\%: 90\% percentile}
 \end{tabular}
@@
 \label{ptab:obs_all_60_min_summary_throughput}
-\end{center}
 \end{table}
@@
 \begin{adjustbox}{width=0.45\textwidth}
-\footnotesize
-\begin{tabular}{|c|c|c|c|c|c|c|}
+% \footnotesize
+\begin{tabular}{|l|r|r|r|r|r|r|}
 \hline
-\textbf{Label} & \textbf{Samples} & \textbf{Avg$^{\mathrm{a}}$} & \textbf{90\%$^{\mathrm{b}}$} & \textbf{S.D.$^{\mathrm{c}}$} & \textbf{Error \%} & \textbf{RPS} \\ \hline
+\textbf{Label} & \textbf{Samples} & \textbf{Avg} & \textbf{90\%$^{\mathrm{a}}$} & \textbf{S.D.$^{\mathrm{b}}$} & \textbf{Error \%} & \textbf{RPS} \\ \hline
 Insert Timeseries & 71759 & 29 & 32 & 50.97 & 0.00\% & 40.5 \\ \hline
@@
 TOTAL & 310878 & 129 & 0 & 207.10 & 0.00\% & 175.3 \\ \hline
-\multicolumn{4}{l}{$^{\mathrm{a}}$Avg: Average Latency, $^{\mathrm{b}}$S.D.: Standard Deviation, $^{\mathrm{c}}$90\%: 90\% percentile.}
+\multicolumn{4}{l}{$^{\mathrm{a}}$S.D.: Standard Deviation}{$^{\mathrm{b}}$90\%: 90\% percentile}
 \end{tabular}
@@
 \begin{adjustbox}{width=0.45\textwidth}
-\footnotesize
-\begin{tabular}{|c|c|c|c|c|c|c|}
+% \footnotesize
+\begin{tabular}{|l|r|r|r|r|r|r|}
 \hline
-\textbf{Label} & \textbf{Samples} & \textbf{Avg$^{\mathrm{a}}$} & \textbf{90\%$^{\mathrm{b}}$} & \textbf{S.D.$^{\mathrm{c}}$} & \textbf{Error \%} & \textbf{RPS} \\ \hline
+\textbf{Label} & \textbf{Samples} & \textbf{Avg} & \textbf{90\%$^{\mathrm{a}}$} & \textbf{S.D.$^{\mathrm{b}}$} & \textbf{Error \%} & \textbf{RPS} \\ \hline
 Insert Timeseries & 71775 & 30 & 41 & 51.71 & 0.00\% & 40.5 \\ \hline
@@
 \textbf{TOTAL} & 310934 & 134 & 503 & 206.40 & 0.04\% & 175.4 \\ \hline
-\multicolumn{4}{l}{$^{\mathrm{a}}$Avg: Average Latency, $^{\mathrm{b}}$S.D.: Standard Deviation, $^{\mathrm{c}}$90\%: 90\% percentile.}
+\multicolumn{4}{l}{$^{\mathrm{a}}$S.D.: Standard Deviation}{$^{\mathrm{b}}$90\%: 90\% percentile}
 \end{tabular}
@@
 \begin{table}[htbp]
-\caption{Throughput and Latency of load testing with 15min data while enabled K8s
-auto-scaling}
+\caption{Throughput and Latency of load testing with 15min data while enabled K8s auto-scaling}
 \begin{center}
@@
 \footnotesize
-\begin{tabular}{|c|c|c|c|c|c|c|}
+\begin{tabular}{|l|r|r|r|r|r|r|}
 \hline
-\textbf{Label} & \textbf{Samples} & \textbf{Avg$^{\mathrm{a}}$} & \textbf{90\%$^{\mathrm{b}}$} & \textbf{S.D.$^{\mathrm{c}}$} & \textbf{Error \%} & \textbf{RPS} \\ \hline
+\textbf{Label} & \textbf{Samples} & \textbf{Avg} & \textbf{90\%$^{\mathrm{a}}$} & \textbf{S.D.$^{\mathrm{b}}$} & \textbf{Error \%} & \textbf{RPS} \\ \hline
 Insert Timeseries & 71727 & 34 & 27 & 118.78 & 0.00\% & 40.5 \\ \hline
@@
 \textbf{TOTAL} & 310734 & 130 & 501 & 212.35 & 0.00\% & 175.3 \\ \hline
-\multicolumn{4}{l}{$^{\mathrm{a}}$Avg: Average Latency, $^{\mathrm{b}}$S.D.: Standard Deviation, $^{\mathrm{c}}$90\%: 90\% percentile.}
+\multicolumn{4}{l}{$^{\mathrm{a}}$S.D.: Standard Deviation}{$^{\mathrm{b}}$90\%: 90\% percentile}
 \end{tabular}
@@
 Given above \acrshort{wdias} can run from 1 CPU node to nodes with 100 CPUs.
-As described in the \cref{psubse:microservice_architecture}, it uses many of the concepts of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities.
+As described in the \cref{pse:wdias_architecture}, it uses many of the concepts of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities.
 
@@
 \dbc{References must be in IEEE standard. Some are not quite formatted for IEEE standard. For e.g., some of the paper and conference titles are in upper case.}
+\gkc{I got your point.
+But I used this IEEE template: https://www.overleaf.com/latex/templates/ieee-conference-template-example/nsncsyjfmpxy.
+Not sure how to fix it.
+May be need to edit the Class implementation above.}
+\gkc{Updated. Mendeley has imported them in Upper case. Still is there any issue?}
 

### 2020-03-02 Thesis.tex
WDIAS_Thesis_v3.2
Dr Dilum: Review the thesis after v3.1

@@
         \vspace{32pt}
-        February 2020
+        March 2020
 
@@
 \acrfull{nwm} utilize data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images.
-Before using such multimodal data into a NWM, it is necessary to transcode data into a format that can be ingested by the NWM.
+Before using such multimodal data in a \acrshort{nwm}, it is necessary to transcode data into a format that can be ingested by the NWM.
 Moreover, the data integration system's response time needs to be relatively low to forecast and monitor time-sensitive weather events like hurricanes, storms, and flash floods that require rapid and frequent execution of \acrshort{nwm}.
-The resulting weather data also need to be accessed by many researchers and third-party applications such as logistic companies and agricultural insurance.
-Even though there are several weather data integration systems, they are based on monolithic or client-server architectures and are unable to benefit from novel computational models such as cloud computing and containers.
-Moreover, most of this software is proprietary or closed sourced; hence, it is difficult to customize such software for an island like Sri Lanka with different weather seasons.
-Therefore, in this research, we propose \acrfull{wdias} that utilizes modern architecture pattern such as microservices to achieve scalability, high availability, and low-cost operation based on cloud computing.
-\acrshort{wdias} provides a modular architecture to integrate data from different sources, export into different formats, and the inbuilt extension module system allow users to add new features.
-Due to the use of stateless microservices, \acrshort{wdias} achieves high scalability, availability, and enables the addition of new features on the fly with rollover capabilities.
+The resulting weather data also need to be accessed by many researchers and third-party applications such as logistic and agricultural insurance firms.
+%Even though there are several weather data integration systems, they
+Existing weather data integration systems are based on monolithic or client-server architectures; hence, unable to benefit from novel computational models such as cloud computing and containers.
+Moreover, most of this software is proprietary or closed-source, making it difficult to customize them for an island like Sri Lanka with different weather seasons.
+Therefore, in this research, we propose \acrfull{wdias} that utilizes modern architectural patterns such as microservices to achieve scalability, high availability, and low-cost operation based on cloud computing.
+The use of stateless microservices also enables \acrshort{wdias} to add new features on the fly with rollover capabilities.
+Moreover, \acrshort{wdias} provides a modular framework to integrate data from different sources, export into different formats, and add new functionality by adding extension modules.
+% system allow users to add new features.
+%Due to the use of stateless microservices, \acrshort{wdias} achieves high scalability, availability, and enables the addition of new features on the fly with rollover capabilities. 
 We demonstrate the utility of \acrshort{wdias} using cloud-based experimental setup and weather-related synthetic workloads.
 
-\dbc{Increase line space to 1.5}
-\gkc{FIXED}
 \vspace{4mm}
 
-\textbf{Keywords:} Cloud computing, data assimilation, data integration, hierarchical databases, microservice, weather
+\textbf{Keywords:} Cloud computing, data assimilation, data integration, microservice, weather
 %Cloud Computing, Data Management system, Distributed,  Highly Available, Scalable, Timeseries, Weather
@@
 Also special thanks to Dr.
-Dilum Bandara and Dr.
+Dilum Bandara and Prof.
 Srikantha Herath for giving me this wonderful opportunity to explore this new domain.
@@
 Special thanks to Dr Dilum Bandara, my research supervisor for helping me with his precious time, reading, encouragement and been patient with pushing me to the next level.
-Also, I', thankful to Dr.
+Also, I am, thankful to Dr.
 Dilika Peris, and Dr.
@@
 Special thanks go to the academic and non-academic staff of the department for their continued support.
-I also thank the University of Moratuwa for its financial support, as the research was partially funded by the Senate research grant from the University of Moratuwa under award number SRC/LT/2017/01,  and \acrfull{curw} for providing the grant and financial support during the research period with providing required resources and learning opportunities.
+I also thank the %University of Moratuwa for its financial support, as the research was partially funded by the Senate research grant from the University of Moratuwa under award number SRC/LT/2017/01,  and
+\acrfull{curw} for providing the domain expertise, access to resources, and financial support during the research.% period with providing required resources and learning opportunities.
 
@@
 Their enthusiasm and willingness to provide feedback support me to go far beyond my limits and complete my research with an enjoyable experience.
-
-\dbc{Need to ACK CUrW for grant.}
-\gkc{FIXED}
 
@@
 styles are not working on list style: https://www.dickimaw-books.com/gallery/glossaries-styles/}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-% \import{method/}{sec_3-microservice.tex}
+\import{method/}{sec_3-microservice.tex}
 
@@
 
-% \import{method/}{sec_5-data_preprocess.tex}
+\import{method/}{sec_5-data_preprocess.tex}
 
@@
 
-% \import{results/}{sec_1-test_plan.tex}
+\import{results/}{sec_1-test_plan.tex}
 
-% \import{results/}{sec_2-workload.tex}
+\import{results/}{sec_2-workload.tex}
 
-% \import{results/}{sec_3-observations.tex}
+\import{results/}{sec_3-observations.tex}
 

### 2020-03-02 introduction/sec_1-motivation.tex
Dr Dilum: Review the thesis after v3.1

@@
-Weather prediction is essential to reduce the impact caused by natural disasters and to gain effectively manage natural resources like water.
-It will give more understanding of weather prediction if we look into a weather prediction workflow that can use to predict the surface water level.
+Weather prediction is essential to reduce the impact caused by natural disasters and to effectively manage natural resources like water. 
+%It will give more understanding of weather prediction if we look into a weather prediction workflow that can use to predict the surface water level. 
 The weather predictions/forecasts are performed using \acrfull{nwm} that use a set of configuration parameters and the current status of the environment such as temperature, rainfall, and wind direction as the inputs.
@@
 Typically multiple \acrshort{nwm} are executed on the same data with different configuration parameters.
-Then using the real-time observations, the correct model is selected.
-After removing the bias, the extract information is then fed into another set of models/simulators.
-\db{As an example, FLO2D is a hydrologic model that can use to predict the surface water level.
+Then using the real-time observations, the most fitting model is selected.
+After removing the bias, the data extracted from a \acrshort{nwm} are then fed into another set of models/simulators.
+\db{For example, FLO2D is a hydrologic model that can use to predict the surface water level.
 A given FLO2D model can simulate with the initial surface water levels and the sequence of forecasted rainfall for the corresponding modeled area from the \acrshort{nwm} model to forecast future water levels.}
@@
 \gkc{Highlighted parts modified and kept also.}
-\dbc{cite both NWM and WRF}
-\gkc{FIXED BOTH}
+\dbc{Highighted part is still not clear to me.}
 
 \acrfull{curw} \cite{CUrWSL2017SL} is tasked with the mission to reduce water-related natural disasters in Sri Lanka.
-\acrshort{curw} \cite{CUrWSLObservedSL} is implementing own system with the idea of long-term maintainability rather depend on existing weather data integration systems.
-The center collects real-time data from weather stations and other government entities and generates daily forecasts.
+\acrshort{curw} \cite{CUrWSLObservedSL} is implementing own system with the idea of long-term maintainability rather than depending on existing weather data integration systems.
+\acrshort{curw} collects real-time data from weather stations and other relevant entities and generates daily forecasts.
 Then the generated results are shared with relevant public departments responsible for disaster planning, risks mitigation, and disaster management.
@@
 These NWMs utilize multi-modal weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images.
-Before feeding such diverse data (collected from different sources that belong to different stakeholders) into respective NWMs, it is necessary to convert to a data format that can be ingest by the model.
-Moreover, the data integration system’s response time needs to be relatively low to forecast and monitor time-sensitive weather events like hurricanes, storms, and floods which require rapid and frequent execution of NWMs.
+Before feeding such diverse data (collected from different sources that belong to different stakeholders) into respective NWMs, it is necessary to convert them to a data format that can be ingest by the models.
+Moreover, the data integration system's response time needs to be relatively low to forecast and monitor time-sensitive weather events like hurricanes, storms, and floods which require rapid and frequent execution of NWMs.
 
-Processed weather data needs to be accessed by many third-party applications and research to make use of them.
-For example, logistics companies could use those data with their models to plan and schedule their deliveries.
-Agricultural insurance companies can warn the farmers, as well as calculate premiums based on anticipated weather patterns.
-Besides, farmers rely on weather forecasts to decide what work to do on a given day.
+Weather data processed by one \acrshort{nwm} may be used by several other NWSs, as well as by many third-party applications and researcher.
+For example, logistic companies could use the processed data with their models to plan and schedule their deliveries.
+Agricultural insurance companies can warn the farmers, as well as calculate premiums based on the anticipated weather patterns.
+Besides, farmers could rely on weather forecasts to plan their work.
+% decide what work to do on a given day.
 For example, drying hay is only possible in dry weather.
 Also, the aeronautical industry is particularly sensitive to weather conditions, precise weather forecasts are essential since before takeoff a flight need to check the conditions on expected route and at destination.
-Thus it is required a platform to provide such 3rd party access, and use the data or process those based on their applications.
+%required a provide platform to provide such 3rd party access, and use the data or process those based on their applications.
+\dbc{Data is plural.}
 
-While Data Integration and Analysis System (DIAS) \cite{Kawasaki2018DataReduction} and Meteorological Assimilation Data Ingest System (MADIS) \cite{Macdermaid2005ARCHITECTUREP2.39} are some of well-known Weather Data Integration and Assimilation (WDIA) systems, they are proprietary.
-Further \acrfull{fews} \cite{Werner2013TheSystem} is free to use, it is not open source.
-Even though there are many data integration systems, most of them are proprietary or closed source.
-For an island like Sri Lanka that having different kinds of weather seasons over the year than that software originated need to be highly customized.
+Data Integration and Analysis System (DIAS) \cite{Kawasaki2018DataReduction} and Meteorological Assimilation Data Ingest System (MADIS) \cite{Macdermaid2005ARCHITECTUREP2.39} are two of the well-known Weather Data Integration and Assimilation (WDIA) systems.
+However, they are proprietary.
+Further, while \acrfull{fews} \cite{Werner2013TheSystem} is free to use, it is not open source.
+While a few other data integration systems exists, most of them are also proprietary or closed source.
+Thus, it is difficult and costly to customize such systems for an island like Sri Lanka which experience different kinds of weather seasons over the year.
+% than that software originated need to be highly customized.
 Throughout the operations and maintenance, it is required to get support with paying lots of charges, and difficult to debug into a closed source system without maintenance support from the vendors.
-As an example, \acrshort{fews} does not support FLO2D model integration, and \acrshort{curw} is using FLO2D for water level forecasting in the workflow.
-In such a case, it required to get support from the vendor to integrate and configure the system.
+For example, \acrshort{fews} does not support FLO2D model integration, which is used by \acrshort{curw}'s workflows for water-level forecasting.
+%In such a case, it required to get support from the vendor to integrate and configure the system.
+\dbc{Something seems to be wrong with reference Macdermaid2005ARCHITECTUREP2.39}
+\dbc{"island like Sri Lanka which experience different kinds of weather seasons over the year" We need to add a citation that talks about multiple types of weather patterns in Sri Lanka.}
 
-Most of the software existing out there is not up to date with the latest technology concepts such as Cloud Computing.
-The modern architecture pattern such as microservice architecture was able to provide high scalability and availability, rather using monolithic architecture or client service architecture.
-Most existing systems required to shut down to update the system configuration such as \acrshort{fews}, but a system that is accessed by any third parties should be operating 99.9\% without any downtime and should allow adding new features on the fly with rollover capabilities.
+Existing WDIA systems are based on 
+%Most of the software existing out there is not up to date with the latest technology concepts such as Cloud Computing.
+The modern architecture pattern such as microservice architecture was able to provide high scalability and availability, rather using
+the monolithic or client service architecture; hence, cannot benefit from technologies such as cloud computing to achive high scalability and availability.
+Moreover, such systems cannot be updated or reconfigured without taking the system off line.
+Furthermore, they are platform specific.
+For example, while \acrshort{fews} can run on either Windows or Linux, downtime is needed to introduce any changes to the system.
+% Most existing systems required to shut down to update the system configuration such as \acrshort{fews}, but a system that is accessed by any third parties should be operating 99.9\% without any downtime and should allow adding new features on the fly with rollover capabilities.
 The proposed system should be independent of the platforms.
@@
 And should be independent underline infrastructure providers which gives much flexibility for the users to decide the best cost-effective way to host it.
-Given the above facts, there is a necessity for such a system to be implemented.
 
-\dbc{Citations need to be given for DIAS, WDIA, FEWS, FLOW2D, etc.
-By the way, don't remove my comments (you are welcome to comment on them).
-I need them to check whether those are addressed.
-When I see them addressed, I'll remove comments.}
-\gkc{FIXED: Added citations}
+\db{Given the above facts, there is a necessity to develop a WDIA system that could ... , as well as support data sharing with other NWMs and third-party access.}
+\dbc{Complete the above sentence by adding a list of desirable features.}

### 2020-03-02 introduction/sec_2-problem_and_objectives.tex
Dr Dilum: Review the thesis after v3.1

--- 2020-02-14 introduction/sec_2-problem_and_objectives.tex
@@
 \section{Problem Statement}
-Handling spatio-temporal weather data is challenging \db{as} involve with large data volumes required to have higher number of resources such as computation, storage and network bandwidth.
+Handling spatio-temporal weather data is challenging, as it involves large data volumes requiring high computing, storage, and network resources.
 Moreover, the data integration system needs to be capable of interacting with different data formats including spatio-temporal bulk stream data.
-Furthermore, it should support geographical and time-base queries, as well as provide third-party access to data with easy integration.
+Furthermore, it should support geographical and time-based queries, as well as provide third-party access to data with easy integration.
 Scalability and high availability are also essential to support different use cases and mission-critical nature of applications.
-And users should be able to easily deployment and manage the system with modern technologies, and should be able get the advantage of technology advancement.
+Further, users should be able to easily deploy and manage the system while benefiting from technological advances.
+%with modern technologies and should be able to get the advantage of technology advancement.
 In this context, the research problem can be stated as follows:
 
-\emph{Design and implement an extendable weather data integration, assimilation and dissemination system which is capable of handling bulk data efficiently with providing scalability and high throughput with using open source tools and modern cloud computing technologies.}
-\dbc{Give a proper problem statement.}
-\gkc{UPDATED. Looked into the OneNote samples. I  should follow one of them from the beginning. :( }
+\emph{How to design an extendable weather data integration, assimilation, and dissemination system that is capable of handling large volumes of multimodel weather data while providing high throughput, scalability, and availability?}
 
 \section{Objectives}
-We address above problem statement by achieving the following research objectives:
+This research addresses the above problem statement by achieving the following research objectives:
 \begin{itemize}

### 2020-03-02 introduction/sec_3-outline.tex
Dr Dilum: Review the thesis after v3.1

--- 2020-02-20 introduction/sec_3-outline.tex
@@
 \section{Outline}
-The rest of the thesis is organized as follows.
-The literature review is presented in \cref{ch:literature}, and discuss the existing Weather Data Integration Systems such as \acrshort{lead}, \acrshort{fews}, \acrshort{madis}, and \acrshort{dias}.
-Solution approach with the proposed system architectures and adaptation with problem occurred are presented in Chapter \ref{ch:method}.
-It provides details about how the \acrshort{wdias} is designed by following a microservice architecture and the data preprocessing capabilities of the system.
+The organization of the rest of the thesis is as follows; In \cref{ch:literature} the literature review is presented.
+It discusses the existing weather data integration systems such as \acrshort{lead}, \acrshort{fews}, \acrshort{madis}, and \acrshort{dias}.
+Solution approach including the proposed system architectures and adaptation with problem occurred are presented in Chapter \ref{ch:method}.
+It provides details on how the \acrshort{wdias} is designed by following a microservice architecture and its data pre-processing capabilities.
 Performance analysis is presented in Chapter \ref{ch:results}.
 Here we discuss the experimental setup of the \acrshort{wdias} and analyze the observations concerning performance metrics.
-Finally, in Chapter \ref{ch:summary}, we conclude and summarize the work and further discussed the research limitations and future work.
+Finally, Chapter \ref{ch:summary}, summarizes the research work and further discusses the research limitations and future work.

### 2020-03-02 lit/sec_1-fews.tex
Dr Dilum: Review the thesis after v3.1

@@
 This chapter presents a literature review on existing systems and their architectural approaches and designs.
-In \cref{se:fews}, we present \acrfull{fews} that is developed as an open model integration framework.
+In \cref{se:fews}, we present \acrfull{fews}, an open model integration framework.
 \acrfull{lead}, an open data handling platform distributed as closed-source software, is presented in \cref{se:lead}.
 % \acrshort{lead} is following the \acrfull{soa} for system architecture.
-In \cref{se:dias}, we discussed \acrfull{dias} which is a common data platform that can manage weather data.
-\acrfull{madis} is another widely used data integration system, which also provides data access with quality control, which we discuss in \cref{se:madis}.
-Under each system, we explore both system architecture, scalability, and flexibility of the system.
+In \cref{se:dias}, we discuss \acrfull{dias} which is a common data platform that can manage weather data.
+\acrfull{madis} is another widely used data integration system, which also provides data access with quality controls is presented in \cref{se:madis}.
+Under each system, we explore their system architecture, scalability, and flexibility.
 
@@
 
-As it describe with a simple example in \cref{ch:intro}, forecasting processes consist by creating modeling steps with combining data transformation algorithms.
-Combining such flows can use to provide the forecasting capabilities.
+\db{As it describe with a simple example in \cref{ch:intro}, forecasting processes consist by creating modeling steps with combining data transformation algorithms.} Combining such flows can use to provide the forecasting capabilities.
 The system is flexible enough to integrate new models and algorithms into the core codebase \cite{Werner2013TheSystem}.
@@
 Rather it is a framework that can use to integrate into the system and create workflows for forecasting.
+\dbc{Reword highlighted sentence without referring to Chap 1.}
 
@@
 It is a valid argument that providing accurate predictions with greater lead time can reduce the level of destruction.
-To forecasting, the system should be capable of integrating real-time data from meteorological and hydrological observation network systems, and the disseminate the forecasted results through relevant products to the warning process.
+To forecast, the system should be capable of integrating real-time data from meteorological and hydrological observation network systems, and the disseminate the forecasted results through relevant products to the warning process.
 
-In \db{Figure} \cref{fi:fews_schematic} show the connection between the forecasting system to real-time data integration systems and dissemination systems.
-The widely used concept is using meteorological forecast data to get precipitation and, then using a hydrological and hydraulic model chain to predict the level affect on the ground.
-The hydrological and hydraulic model should be design based on the Geographical data.
+\cref{fi:fews_schematic} shows the connection between the forecasting system to real-time data integration systems and dissemination systems.
+One of the widely used use cases is to use meteorological forecast data to estimate precipitation, and then use a hydrological and hydraulic model chain to predict the surface water level affects.
+The hydrological and hydraulic model should be design based on the geographical data.
 The ground should be analyzed geographically and divide into the catchments.
@@
 Ideally, the forecasting system should be flexible enough to allow modification of models and data, while keeping the most constant way possible of working with forecasters.
-\dbc{F is capital and T is capital when referring to Figures and Tables. Fix all other places.}
-\gkc{FIXED}
 
@@
     \includegraphics[width=0.7\textwidth]{lit/fews/Schematic-structure-of-a-fl-ood-forecasting-system-showing-the-position-of-Delft-FEWS_W640.png}
-    \caption[Schematic structure of a flood forecasting system including \acrshort{fews} and communication between other operational systems]{Schematic structure of a flood forecasting system including \acrshort{fews} and communication between other operational systems \cite{Werner2013TheSystem}.}
+    \caption[Schematic structure of a flood forecasting system including \acrshort{fews} and communication among other operational systems]{Schematic structure of a flood forecasting system including \acrshort{fews} and communication among other operational systems \cite{Werner2013TheSystem}.}
     \label{fi:fews_schematic}
@@
 As an example, Python language is easy to use for beginners and many data scientists are using this programming language for development and it has many data available libraries for data processing.
-But in \acrshort{fews}, users cannot take advantage of such existing tools.
-\dbc{Define Abb. for API in Chapter 1.}
-\gkc{FIXED}
+However, in \acrshort{fews}, users cannot take advantage of such existing tools.
 
@@
 \end{figure}
-Most of the function library has provided equal work on scalar and grid time series.
-But the communicates with the database only via the data access layer as shown in \cref{fi:fews_data_layer} \cite{Werner2013TheSystem}.
+Most of the \db{function library has provided equal work on scalar and grid time series}.
+However, the communicates with the database only via the data access layer as shown in \cref{fi:fews_data_layer} \cite{Werner2013TheSystem}.
 As it is shown in the figure, it is clearly showing that the system depends on a single database and via the data access layer, all the requests are coming to the database through a connection.
 It is possible to setup and connect to an enterprise-level database with clustering and shading as a paid solution, to serve many requests as possible.
-But the design itself inherently suffers from the database bottleneck which effected by running a large set of timeseries or models.
-\dbc{When referring to a section you need to use the word "Section" as highlighted above. Fix all other places.}
-\gkc{FIXED. I did not remove highlited places as you need to verify.}
+However, the design itself inherently suffers from the database bottleneck which effected by running a large set of timeseries or models.
+\dbc{Above highlighted is not clear to me.}
 
@@
 One of the simple and most effective features in the \acrshort{fews} is an open approach to the integration of models and data.
-The concept of the open modeling framework is used by the \acrshort{fews} which is proposed by Open model integration \cite{Kokkonen2003InterfacingXML}.
+The concept of the open modeling framework is used by the \acrshort{fews} which is proposed by open model integration \cite{Kokkonen2003InterfacingXML}.
 It simply gives the flexibility to allow operators to integrate more models as well as variations of the same model and come up with new integration flows as much as possible.
@@
 This part of the system feature is not focused on the \acrshort{wdias} and user has to come up with own flow or use existing scientific flow management system.
-But it is a concept that needs to be discussed and understand properly to design a data integration and assimilation system.
-But the \acrshort{wdias} is capable of integrating workflow mechanism with its extendable architecture.
+Yet, it is a concept that needs to be discussed and understand properly to design a data integration and assimilation system.
+However, the \acrshort{wdias} is capable of integrating workflow mechanism with its extendable architecture.
 

### 2020-03-02 lit/sec_2-lead.tex
Dr Dilum: Review the thesis after v3.1

@@
 
-\cref{fi:lead_system} shows the fundamental capabilities of the \acrshort{lead} system.
+\cref{fi:lead_system} shows the key capabilities of the \acrshort{lead} system.
 From the high-level view, \acrshort{lead} enables users to search and acquire information, simulate and predict weather conditions using digital atmospheric models, assimilate, analyze, use and visualize data and output of models.
@@
 
-The second level contains the fundamental tools that help to link services together. This includes the following tools \cite{Droegemeier2005Service-OrientedWeather};
+The second level contains the basic tools that help to link services together. This includes the following tools \cite{Droegemeier2005Service-OrientedWeather};
 \begin{itemize}
@@
 
-As shown in \cref{fi:lead_framework} LEAD consists of the following sub-components, and it provides a distributed system for integrating, and testing LEAD's components.
+As shown in \cref{fi:lead_framework}, LEAD consists of the following sub-components, as well as provides a distributed system for integrating and testing LEAD's components:
 \begin{itemize}

### 2020-03-02 lit/sec_3-other-systems.tex
Dr Dilum: Review the thesis after v3.1

@@
 The mechanism of storing data in \acrshort{dias}, similar to the other systems discussed.
-These data sets are stored in a larger array system with Application Programming Interface (API) software that is used to import the data.
+These data sets are stored in a larger array system with API software that is used to import the data.
 APIs work to convert or reformat data into manageable forms and are useful for creating the DIAS storage archive.
@@
 
+\dbc{Both MADIS and netCDF need to cited. Do this at the beginging for each on the systems in this chapter (while they were cited in Chap 1, it's also important to cite them in Chap 2 as well.}
+
 \begin{figure}[htp]
@@
     \includegraphics[width=1\textwidth]{lit/other/madis_flow.png}
-    \caption[\acrshort{madis} flow]{\acrshort{madis} flow \cite{Macdermaid2005ARCHITECTUREP2.39}.}
+    \caption[\acrshort{madis} data flow]{\acrshort{madis} data flow \cite{Macdermaid2005ARCHITECTUREP2.39}.}
     \label{fi:madis_flow}
 \end{figure}
-
-\dbc{In Fig. 2.8, is it the data flow?}
-\gkc{The paper is not very much clear. I think it shows data flow with including some of it integration functions.}
 
@@
 Different systems that work inside and outside the firewall collect the data.
-This data is sent to the data server of the advanced weather-interactive processing system (AWIPS) of the central installation for processing and conversion to a common format, NetCDF.
+This data is sent to the data server of the Advanced Weather-Interactive Processing System (AWIPS) of the central installation for processing and conversion to a common format, NetCDF.
 NetCDF files are then transferred to MADIS compute nodes \cite{Macdermaid2005ARCHITECTUREP2.39}.
 This provides an overview of the level of data that \acrshort{madis} handling.
-This could be a good reference for implementing \acrshort{wdias}, and it's performance testing.
+This could be a good reference for implementing \acrshort{wdias} and its performance testing.
 As same as \acrshort{fews}, it is also converting the data into a common format which is \acrshort{netCDF}.
 Those files are transferred to the compute nodes and allow users to access via OPeNDAP.
-
-MADIS computer platforms include Intel-based servers with the Red Hat Enterprise Linux operating system.
-Many of these computers are configured using Linux clustering with high availability \cite{Macdermaid2005ARCHITECTUREP2.39}.
-As indicated above, the system heavily depends on the platform.
+%MADIS computer platforms include Intel-based servers with the Red Hat Enterprise Linux operating system. 
+Many of these computers are configured using Linux clustering with high availability \cite{Macdermaid2005ARCHITECTUREP2.39}.% As indicated above, the system heavily depends on the platform.
 There are some costs involving purchasing their licenses.
@@
 \label{se:lit_summary}
-Several related works discussed above in this Chapter, mainly focus on the issue of storing data which are ingested from different sources with different formats efficiently.
+\db{We presented several related work on ...} We forced mainly focus on the issue of storing data which are ingested from different sources with different formats efficiently.
 The \acrshort{fews} and \acrshort{madis} are using the \acrshort{netCDF} as the common data format to store the data which is one of the best solutions available with modern technologies as well.
@@
 \acrshort{fews} and \acrshort{lead} have the capability of handling the workflow of forecasting, but other systems are mainly focused on providing a weather data management system.
-\acrshort{fews} provides a modular approach via its general adapter which is shown in \cref{fi:fews_general_adapter}, and according to the \acrshort{soa} architecture of \acrshort{lead} provides the same functionality via services.
+\acrshort{fews} provides a modular approach via its general adapter, and according to the \acrshort{soa} architecture of \acrshort{lead} provides the same functionality via services.
+\dbc{Complete highlighted sentence}
 
-Most of the above systems developed by many developers and researchers via sufficient funding, and developed specifically to address issues like natural disasters.
-When I required to establish a system in another country, it required to remodeling the models and defining the forecasting flows.
+Most of the above systems developed by many developers and researchers, and were developed specifically to address issues like natural disasters.
+To address use cases such as CUrW, it required to remodel the systems  and define the forecasting flows.
 Even some of the systems try to follow a generic approach to integrate new modules, it is challenging to deploy modules for a closed source or proprietary software.
-And most of them are depending on the underline platform, and not up to date with modern technologies such as cloud computing.
+Further, most of them are depend on the underline platform, and does not support more resource efficient and highly-scalable technologies such as cloud computing.
+
+\dbc{You are making lots of mistakes when using "ing" form of a verb. It seems checking with Grammalee didn't help either.}

### 2020-03-02 method/sec_3-microservice.tex
Used PDF and removed JMeter images

@@
     \centering
-    \includegraphics[width=1\textwidth]{method/microservice/microservice_architecture-handle_on_demand-v3.jpg}
+    \includegraphics[width=1\textwidth]{method/microservice/microservice_architecture-handle_on_demand-v4.pdf}
     \caption{\acrshort{wdias} architecture for handling requests on demand}
@@
     \centering
-    \includegraphics[width=1\textwidth]{method/microservice/microservice_architecture-handle_on_async-v3.jpg}
+    \includegraphics[width=1\textwidth]{method/microservice/microservice_architecture-handle_on_async-v4.pdf}
     \caption{\acrshort{wdias} architecture for handling requests asynchronously.}
@@
     \centering
-    \includegraphics[width=1\textwidth]{method/microservice/separation_microservices-v3.jpg}
+    \includegraphics[width=1\textwidth]{method/microservice/separation_microservices-v4.pdf}
     \caption{Separation of \acrshort{wdias} microservices.}

### 2020-03-02 Thesis.tex
Fixed glossary

@@
 \usepackage{tabu}
-\usepackage[acronym]{glossaries}
+\usepackage[acronym,nopostdot,nonumberlist]{glossaries}
 \makeglossaries
@@
 \newglossarystyle{custom-glossary-style}{%
-  \setglossarystyle{list}%
+  \setglossarystyle{long}%
+  \renewcommand{\glsgroupskip}{}
   \renewenvironment{theglossary}%
-    % {\begin{longtable}[l]{@{}p{\dimexpr 2cm-\tabcolsep}p{0.8\hsize}}}% <-- change the value here
-    {\begin{longtable}{p{3cm}p{\glsdescwidth}}}%
+    {\begin{longtable}[l]{@{}p{\dimexpr 3cm-\tabcolsep}p{0.8\hsize}}}% <-- change the value here
     {\end{longtable}}%
@@
 \addcontentsline{toc}{chapter}{List of Abbreviations} 
-\printglossary[style=altlist, type=\acronymtype, title=List of Abbreviations, toctitle=List of Abbreviations, nonumberlist]
-\dbc{Make sure line spacing is consistent here.}
-\gkc{Could not figure out how to fix this.
-Those spaces are because of grouping by first letter with style long.
-What is needed is style list.
-styles are not working on list style: https://www.dickimaw-books.com/gallery/glossaries-styles/}
+\printglossary[style=custom-glossary-style, type=\acronymtype, title=List of Abbreviations, toctitle=List of Abbreviations]
 
@@
 
-\import{results/}{sec_3-observations.tex}
+% \import{results/}{sec_3-observations.tex}
 

### 2020-03-02 method/sec_4-db_struct.tex
Tried href links package
Draft paper up to lit review
Used PDF and removed JMeter images
Replace noun acronym with full word

@@
 
+The foundation of the \acrshort{wdias} is data-centric.
 To understand the underline design decisions of the \acrshort{wdias} database structure, it needs to deeply look into the weather data timeseries.
@@
     \centering
-    \includegraphics[width=0.6\textwidth]{method/microservice/wdias_database_structure.jpg}
+    \includegraphics[width=0.8\textwidth]{method/microservice/wdias_database_structure.pdf}
     \caption{\acrshort{wdias} database structure}
@@
 \acrshort{wdias} is using SQL as the \acrfull{rdbms}. 
-Since the \acrshort{wdias} scope is to use open source tools, it is using \acrshort{mysql} as a persistent database for storing timeseries metadata described above.
-One instance of \acrshort{mysql} is using only by adapter-metadata service.
-Other than that, another instance of \acrshort{mysql} is using for adapter-extension which will be described in more detail \cref{se:data_preprocess}.
-\acrshort{mysql} is used only for these services, those will only keep the consistency of the schema for timeseries metadata and extension metadata.
-As mentioned in \cref{subse:redis}, it uses \acrshort{redis} instance is using for caching the data from \acrshort{mysql}, since the \acrshort{mysql} database instances, itself not going to get much load.
+Since the \acrshort{wdias} scope is to use open source tools, it is using  MySQL as a persistent database for storing timeseries metadata described above.
+One instance of  MySQL is using only by adapter-metadata service.
+Other than that, another instance of  MySQL is using for adapter-extension which will be described in more detail \cref{se:data_preprocess}.
+ MySQL is used only for these services, those will only keep the consistency of the schema for timeseries metadata and extension metadata.
+As mentioned in \cref{subse:redis}, it uses  Redis instance is using for caching the data from  MySQL, since the  MySQL database instances, itself not going to get much load.
 Other than MySQL, many open source databases can be used to replace the same functionality.
@@
 \label{subse:influxdb}
-Among several timeseries open source databases, \acrshort{influxdb} \cite{influxdbInfluxDBDocumentation} \hl{is using a unique database indexing algorithm to gain higher performance while storing timeseries data} when compared to other databases available.
+Among several timeseries open source databases,  InfluxDB \cite{influxdbInfluxDBDocumentation} \hl{is using a unique database indexing algorithm to gain higher performance while storing timeseries data} when compared to other databases available.
 Also, it has better support, higher usage and has following supports;
@@
 \end{itemize}
-Other than \acrshort{influxdb}, another database is Elastic Search which is mainly using for indexing for searching.
-With changing the configurations of the \acrshort{influxdb}, it is possible to adapt as required. As mention in \cite{influxdbInfluxDBDocumentation}, 
-\acrshort{influxdb} can setup on a computer that will give the required performance. Going further, users can use the commercial version of \acrshort{influxdb} to gain more performance.
+Other than  InfluxDB, another database is Elastic Search which is mainly using for indexing for searching.
+With changing the configurations of the  InfluxDB, it is possible to adapt as required. As mention in \cite{influxdbInfluxDBDocumentation}, 
+ InfluxDB can setup on a computer that will give the required performance. Going further, users can use the commercial version of  InfluxDB to gain more performance.
 
-Two instances of \acrshort{influxdb} is using in the WDIAS system by adapter-scalar and adapter-vector services.
+Two instances of  InfluxDB is using in the WDIAS system by adapter-scalar and adapter-vector services.
 For the scalability, the system uses \emph{Database per Service} as mentioned in \cref{subse:database_per_service}.
@@
 
-\acrshort{wdias} is using \acrshort{mongodb} as the document-oriented database, as it has the Geo searching capabilities.
-\acrshort{mongodb} \cite{mongodbMongoDBManual} is a general-purpose, document-based, distributed database. And it supports:
+\acrshort{wdias} is using  MongoDB as the document-oriented database, as it has the Geo searching capabilities.
+ MongoDB \cite{mongodbMongoDBManual} is a general-purpose, document-based, distributed database. And it supports:
 \dbc{Need for a mix of relational, time series, document stores, and in-memory need to be first mentioned and justified in high-level design of WDIAS above.}
@@
 \end{itemize}
-\acrshort{mongodb} geospatial features are using to support Geo queries in the WDIAS. Other than that, external timeseries metadata queries are served by the indexed timeseries metadata data.
-If metadata not present in the adapter-query if fetch data from the adapter-metadata, then indexed and cache in the \acrshort{mongodb}.
+ MongoDB geospatial features are using to support Geo queries in the WDIAS. Other than that, external timeseries metadata queries are served by the indexed timeseries metadata data.
+If metadata not present in the adapter-query if fetch data from the adapter-metadata, then indexed and cache in the  MongoDB.
 Vise a versa, if new timeseries create in the adapter-metadata, it triggers an event to adapter-query to index the new timeseries.
@@
 \label{subse:redis}
-\acrshort{wdias} is using \acrshort{redis} \cite{redisRedisDocumentation} as the In-Memory database, since it is a widely used tool with good support, and it supports few other features such as Publisher Subscriber capabilities.
-\acrshort{redis} is an open-source (BSD licensed), used as a database, cache. Clustering is available for scalability.
-\acrshort{redis} uses as in-memory caching for fast access the frequent access data in adapter-metadata and adapter-extension.
-Other than that, adapter-status uses \acrshort{redis} as a key-value pair store for getting the status for async handling requests such as storing Grid data.
+\acrshort{wdias} is using  Redis \cite{redisRedisDocumentation} as the In-Memory database, since it is a widely used tool with good support, and it supports few other features such as Publisher Subscriber capabilities.
+ Redis is an open-source (BSD licensed), used as a database, cache. Clustering is available for scalability.
+ Redis uses as in-memory caching for fast access the frequent access data in adapter-metadata and adapter-extension.
+Other than that, adapter-status uses  Redis as a key-value pair store for getting the status for async handling requests such as storing Grid data.
 In adapter-extension uses Redis's Publisher Subscriber capabilities to create a cronjob in extension-scheduler when a new extension creates on \cref{se:data_preprocess}

### 2020-03-02 method/sec_5-data_preprocess.tex
Replace noun acronym with full word

@@
 extension-handler only contains the extensions to be triggered. No additional filtering needs to be done at the extension-handler service.
-Second, cache the resulting trigger\_type and timeseries data in the \acrshort{redis} database for fast access and avoid too many queries on the \acrshort{mysql} database.
+Second, cache the resulting trigger\_type and timeseries data in the  Redis database for fast access and avoid too many queries on the  MySQL database.
 
@@
 Fetching extension data and creating cronjobs occur with a long period to avoid heavy overhead.
-When a new extension trigger created, those data push into a \acrshort{redis} list.
-Then pulling from the extension-handler in regular time intervals and create new cronjobs for mentioned cronjob time.
+When a new extension trigger created, those data push into a  Redis list. Then pulling from the extension-handler in regular time intervals and create new cronjobs for mentioned cronjob time.
 As mentioned above, to avoid the expansion of the programmatic cronjob list which are created for new extension triggers, all cronjobs fetch again in a long period and flush the previously scheduled cronjobs.

### 2020-03-02 results/sec_2-workload.tex
WDIAS_Thesis_v3.2
Replace noun acronym with full word

@@
 
-In the \acrshort{jmeter} Best Practices, \say{If your test needs large amounts of data - particularly if it needs to be \emph{randomized} create the test data in a file that can be read with CSV Data set.
+In the  JMeter Best Practices, \say{If your test needs large amounts of data - particularly if it needs to be \emph{randomized} create the test data in a file that can be read with CSV Data set.
 This avoids wasting resources at run-time}.
 Rather providing the randomness in run time, the timeseries stored with the random order which satisfy the percentage of 70\% Scalar, 20\% Vector, and 10\% Grid as mentioned in \cref{se:test_plan}.
-Before running the test cases, it generates the metadata for timeseries and writes into a CSV file which is shared among the threads in the \acrshort{jmeter}.
+Before running the test cases, it generates the metadata for timeseries and writes into a CSV file which is shared among the threads in the  JMeter.
 This occurs in the setup phase of the test cases.
@@
 It does not make any difference based on the parameter type whether it is the precipitation or the temperature.
-Thus during the performance testing, \acrshort{jmeter} uses real precipitation data from \acrshort{curw}.
+Thus during the performance testing,  JMeter uses real precipitation data from \acrshort{curw}.
 One month period of data for five weather stations has been using to prepare the test data.
@@
 Extract function use while creating the containers, and extract the data into the container. This reduces the context loading while creating the container images.
-While performing the load testing, \acrshort{jmeter} keeps update a date counter and creates over the one-month data.
+While performing the load testing,  JMeter keeps update a date counter and creates over the one-month data.
 At the end of the current month, the date counter advance to the next month.
@@
 The water level also contains the real data for one month of period and \emph{setup\_waterlevel.sh} script provides the functionality of preparation, cleanup, and extract.
-Also, it reset and repeat reading from the beginning when the \acrshort{jmeter} date counter keeps increasing.
+Also, it reset and repeat reading from the beginning when the  JMeter date counter keeps increasing.
 
@@
 
-To create a higher workload using the \acrshort{jmeter}, it has a Distributed Testing feature.
+To create a higher workload using the  JMeter, it has a Distributed Testing feature.
 It uses the master-slave approach and it allowed to handle all the test cases via single instance, rather handling separate instances.
 But it has the following limitation of \emph{the same test plan runs by all the servers}.
-\acrshort{jmeter} does not distribute the load between servers, each runs the full test plan.
-So if you set 1,000 threads and have 6 \acrshort{jmeter} servers, you end up injecting 6,000 threads.
-When test cases run with \acrshort{jmeter} Distributed mode, the server node trigger the same copy of the test case on configured slave nodes parallel.
+JMeter does not distribute the load between servers, each runs the full test plan.
+So if you set 1,000 threads and have 6  JMeter servers, you end up injecting 6,000 threads.
+When test cases run with  JMeter Distributed mode, the server node trigger the same copy of the test case on configured slave nodes parallel.
 At the end of the test cases, it gathers results into the master node.
@@
 
-When implementing load test cases with \acrshort{jmeter}, it uses threads to simulate the users.
+When implementing load test cases with  JMeter, it uses threads to simulate the users.
 The root component of a test create is a thread group.
@@
 With using \emph{Throughput Shaping Timer}, it only needs to configure the \acrshort{rps}.
-When combining this \acrshort{jmeter} plugin with Concurrency Thread Group using Schedule Feedback Function to dynamically maintain thread count required to achieve target \acrshort{rps} \cite{KarunarathneGihanWdias/wdias-performance-test:JMeter.}.
+When combining this  JMeter plugin with Concurrency Thread Group using Schedule Feedback Function to dynamically maintain thread count required to achieve target \acrshort{rps} \cite{KarunarathneGihanWdias/wdias-performance-test:JMeter.}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The test plans mentioned in \cref{se:test_plan} are implemented via the \acrshort{jmeter}. The following list shows the all the test cases used for the performance testing:
+The test plans mentioned in \cref{se:test_plan} are implemented via the  JMeter. The following list shows the all the test cases used for the performance testing:
 
@@
 By creating the timeseries before help to reduce the overhead during the performance testing, and cause to more accurate \acrshort{rps} at the run time.
-Otherwise, \acrshort{jmeter} needs to allocate another set of threads for timeseries creation.
+Otherwise,  JMeter needs to allocate another set of threads for timeseries creation.
 Since the test cases insert data again set of timeseries, most of the time it about retrieving the timeseries metadata, rather than creating new timeseries in the \acrshort{wdias} system.
 
-The following list shows the test steps of \acrshort{jmeter} while performing the load testing and the configurations.
+The following list shows the test steps of  JMeter while performing the load testing and the configurations.
 
@@
 
-With the above \acrshort{jmeter} test case setup, it needs to enable each test case separately and before running via the command line in the server.
+With the above  JMeter test case setup, it needs to enable each test case separately and before running via the command line in the server.
 To do it in a much efficient way, a scripting tool has implemented, and accessible with the codebase \cite{KarunarathneWdias-performance-test/TEST_PLAN.md:Plan} as \emph{test-dev}.
@@
 As described in the \cref{se:microservice}, the \acrshort{wdias} is mainly focused on microservice architecture and implemented on top of Kubernetes.
-\acrfull{k8s} is an open-source system for automating deployment, scaling, and management of containerized applications.
+\acrfull{k8s} is an open-source system which is capable of automating deployment, scaling, and management of containerized applications.
 For the performance study uses \acrfull{eks}.
@@
     \item \emph{scalar} -- scalar and vector adapters, import and export of same data types
-    \item \emph{test} -- \acrshort{jmeter} and metric server
+    \item \emph{test} --  JMeter and metric server
 \end{itemize}

### 2020-03-02 results/sec_3-observations.tex
Paper: performance analysis
Replace noun acronym with full word

@@
 But the pods were able to perform with vertical scaling since those are not hit the CPU limit of 2.
+\cref{fi:obs_all_auto_15m_adapter_dbs_res} shows the resource utilization of database adapters in the \acrshort{wdias}.
 
@@
 \end{figure}
-\cref{fi:obs_all_auto_15m_adapter_dbs_res} shows the resource utilization of database adapters in the \acrshort{wdias}.
 
@@
 The throughput for each test case is much higher and similar to all the requests.
-This is happening since all of these requests are handled via the adapter-query, it depends on the \acrshort{mongodb} database performance.
+This is happening since all of these requests are handled via the adapter-query, it depends on the  MongoDB database performance.
 
@@
 This will cause to higher performance with geo timeseries searches.
-The performance of the \acrshort{mongodb} can further improve with using its features like Replication for high availability, and Sharding for higher throughput.
+The performance of the  MongoDB can further improve with using its features like Replication for high availability, and Sharding for higher throughput.
 Those attempts are beyond the scope of the \acrshort{wdias} performance test and users can use those to get higher results from the \acrshort{wdias}.

### 2020-03-02 results/sec_4-discussion.tex
Replace noun acronym with full word

@@
 
-One of the reasons for having deviations at the peak time due to uses of single instance for the data consistency such as \acrshort{influxdb} for Scalar and Vector data, and netCDF with parallel support for Grid data.
-Further, it is possible to increase the performance of these bottlenecks much higher such as using the \acrshort{influxdb} Commercial cluster support for high availability or horizontal scaling of \acrshort{influxdb}.
-With \acrshort{influxdb} cluster, it is possible to run multiple pods of adapter-scalar and adapter-vector for support more server hits per second.
+One of the reasons for having deviations at the peak time due to uses of single instance for the data consistency such as  InfluxDB for Scalar and Vector data, and netCDF with parallel support for Grid data.
+Further, it is possible to increase the performance of these bottlenecks much higher such as using the  InfluxDB Commercial cluster support for high availability or horizontal scaling of  InfluxDB.
+With  InfluxDB cluster, it is possible to run multiple pods of adapter-scalar and adapter-vector for support more server hits per second.
 

### 2020-03-02 summary/sec_2-research_limitations.tex
Replace noun acronym with full word

@@
 \emph{Improve test cases}:
-As described in detail with \cref{subse:closed_vs_open_workload}, for \acrshort{wdias} performance test uses the \emph{Time Stepping Feedback} loop with Concurrent Threads which is the best approach support by \acrshort{jmeter} at the moment.
+As described in detail with \cref{subse:closed_vs_open_workload}, for \acrshort{wdias} performance test uses the \emph{Time Stepping Feedback} loop with Concurrent Threads which is the best approach support by  JMeter at the moment.
 But using that it is not possible to get the desired \acrshort{rps} for each test case within the test plan.
@@
 \emph{Tune \acrshort{wdias} database structure performance}:
-As further described in \cref{se:discussion}, it is possible to increase the performance of these bottlenecks much higher such as using \acrshort{influxdb} Commercial cluster support for high availability or horizontal scaling of \acrshort{influxdb}.
-With the \acrshort{influxdb} cluster, it is possible to run multiple pods of adapter-scalar and adapter-vector for support more server hits per second.
-Other than that, the \acrshort{wdias} performance can improve via partitioning the timeseries key space into multiple \acrshort{influxdb} instances.
-The adapter-scalar or adapter-vector can improve to plug multiple instances of \acrshort{influxdb} instances by changing the configurations.
-As an example, based on the key attribute \cref{subse:timeseries_key_attributes} Timeseries Type, the adapter-scalar can connect to four instances of \acrshort{influxdb} instances such as  External Historical, External Forecast, Simulated Historical, and Simulated Forecast, etc.
+As further described in \cref{se:discussion}, it is possible to increase the performance of these bottlenecks much higher such as using  InfluxDB Commercial cluster support for high availability or horizontal scaling of  InfluxDB.
+With the  InfluxDB cluster, it is possible to run multiple pods of adapter-scalar and adapter-vector for support more server hits per second.
+Other than that, the \acrshort{wdias} performance can improve via partitioning the timeseries key space into multiple  InfluxDB instances.
+The adapter-scalar or adapter-vector can improve to plug multiple instances of  InfluxDB instances by changing the configurations.
+As an example, based on the key attribute \cref{subse:timeseries_key_attributes} Timeseries Type, the adapter-scalar can connect to four instances of  InfluxDB instances such as  External Historical, External Forecast, Simulated Historical, and Simulated Forecast, etc.
 

### 2020-03-02 introduction/sec_1-motivation.tex
Updated Lit Review comments

@@
 After removing the bias, the data extracted from a \acrshort{nwm} are then fed into another set of models/simulators.
-\db{For example, FLO2D is a hydrologic model that can use to predict the surface water level.
+% \db{For example, FLO2D is a hydrologic model that can use to predict the surface water level.
 A given FLO2D model can simulate with the initial surface water levels and the sequence of forecasted rainfall for the corresponding modeled area from the \acrshort{nwm} model to forecast future water levels.}
@@
 \dbc{Highighted part is still not clear to me.}
+\gkc{Removed the sentence. I tried to use the FLO2D as a model which can use WRF output to forecast water levels.}
 
@@
 \dbc{Data is plural.}
+\gkc{Got it. Data needs -> Data need}
 
-Data Integration and Analysis System (DIAS) \cite{Kawasaki2018DataReduction} and Meteorological Assimilation Data Ingest System (MADIS) \cite{Macdermaid2005ARCHITECTUREP2.39} are two of the well-known Weather Data Integration and Assimilation (WDIA) systems.
+Data Integration and Analysis System (DIAS) \cite{Kawasaki2018DataReduction} and Meteorological Assimilation Data Ingest System (MADIS) \cite{Macdermaid2005ArchitectureP2.39} are two of the well-known Weather Data Integration and Assimilation (WDIA) systems.
 However, they are proprietary.
@@
 \dbc{Something seems to be wrong with reference Macdermaid2005ARCHITECTUREP2.39}
-\dbc{"island like Sri Lanka which experience different kinds of weather seasons over the year" We need to add a citation that talks about multiple types of weather patterns in Sri Lanka.}
+\gkc{Seems to be issue with Mendeley.}
+\dbc{"Island like Sri Lanka which experience different kinds of weather seasons over the year" We need to add a citation that talks about multiple types of weather patterns in Sri Lanka} 
+Island like Sri Lanka which experience different kinds of weather seasons over the year \cite{NaveendrakumarFiveLanka}.
+\gkc{Added a reference.}
 
@@
 The modern architecture pattern such as microservice architecture was able to provide high scalability and availability, rather using
-the monolithic or client service architecture; hence, cannot benefit from technologies such as cloud computing to achive high scalability and availability.
+the monolithic or client service architecture; hence, cannot benefit from technologies such as cloud computing to achieve high scalability and availability.
 Moreover, such systems cannot be updated or reconfigured without taking the system off line.
@@
 
-\db{Given the above facts, there is a necessity to develop a WDIA system that could ... , as well as support data sharing with other NWMs and third-party access.}
+\db{Given the above facts, there is a necessity to develop a WDIA system that could capable of handling large multimodel data efficiently with providing scalability and high throughput with using open source tools which support modern cloud computing advancement, as well as support data sharing with other NWMs and third-party access.}
 \dbc{Complete the above sentence by adding a list of desirable features.}

### 2020-03-02 lit/sec_1-fews.tex
Updated Lit Review comments

@@
 Many weather forecasting, assimilation, and dissemination systems are developed to reduce the damage causing by natural disasters such as floods, storms, hurricanes, and even droughts.
-%Such natural disasters heavily affected on the economy and the life conditions of the country, researchers have developed systems and many of these systems are using as proprietary systems.
-Other countries are also using those systems while adopting them %with own version of system which effective for the 
-to specific weather conditions.% in a particular country.
+Other countries are also using those systems while adopting them to specific weather conditions.
 This chapter presents a literature review on existing systems and their architectural approaches and designs.
@@
 \acrfull{lead}, an open data handling platform distributed as closed-source software, is presented in \cref{se:lead}.
-% \acrshort{lead} is following the \acrfull{soa} for system architecture.
 In \cref{se:dias}, we discuss \acrfull{dias} which is a common data platform that can manage weather data.
@@
 
-\db{As it describe with a simple example in \cref{ch:intro}, forecasting processes consist by creating modeling steps with combining data transformation algorithms.} Combining such flows can use to provide the forecasting capabilities.
-The system is flexible enough to integrate new models and algorithms into the core codebase \cite{Werner2013TheSystem}.
+Forecasting processes is creation of modeling steps with combining data transformation algorithms.
+In the flow, each step process and feed data into the next step.
+The \acrshort{fews} is flexible enough to integrate new models and algorithms into the core codebase that can use to create new workflows \cite{Werner2013TheSystem}.
 \acrshort{fews} does not have any inbuilt hydrological modeling capabilities within its codebase.
 Rather it is a framework that can use to integrate into the system and create workflows for forecasting.
-\dbc{Reword highlighted sentence without referring to Chap 1.}
 
@@
 \end{figure}
-Most of the \db{function library has provided equal work on scalar and grid time series}.
+\db{The \acrshort{fews} supports data processing and modeling library to access scalar and grid timeseries same way}.
 However, the communicates with the database only via the data access layer as shown in \cref{fi:fews_data_layer} \cite{Werner2013TheSystem}.
@@
 \dbc{Above highlighted is not clear to me.}
+\gkc{Updated}
 

### 2020-03-02 lit/sec_2-lead.tex
Updated Lit Review comments

@@
 
-\acrfull{lead} addresses the fundamental research challenges needed to create an integrated and scalable framework for adaptive analysis and prediction of the atmosphere \cite{Droegemeier2005Service-OrientedWeather}.
+\acrfull{lead} \cite{Droegemeier2005Service-OrientedWeather} addresses the fundamental research challenges needed to create an integrated and scalable framework for adaptive analysis and prediction of the atmosphere.
 To predict and analyze weather models by researchers, it required many resources.

### 2020-03-02 lit/sec_3-other-systems.tex
Updated Lit Review comments

@@
 
-\acrfull{dias} collects and archives data from satellites, weather stations, numerical forecasting models and climate projection models.
+\acrfull{dias} \cite{Kawasaki2018DataReduction} collects and archives data from satellites, weather stations, numerical forecasting models and climate projection models.
 Once this data is integrated into geographic useful information, DIAS generates results for managing global environmental problems and natural disasters \cite{Kawasaki2018DataReduction}.
@@
 \label{se:madis}
-\acrfull{madis} is a data integration and assimilation system that collects data from dozens of suppliers, then checks the quality of the data and saves it in \acrshort{netCDF} format.
+\acrfull{madis} \cite{Macdermaid2005ArchitectureP2.39} is a data integration and assimilation system that collects data from dozens of suppliers, then checks the quality of the data and saves it in \acrshort{netCDF} format.
 Give users later access to data through support for different types of protocols.
 
-\dbc{Both MADIS and netCDF need to cited. Do this at the beginging for each on the systems in this chapter (while they were cited in Chap 1, it's also important to cite them in Chap 2 as well.}
+\dbc{Both MADIS and netCDF need to cited. Do this at the beginning for each on the systems in this chapter (while they were cited in Chap 1, it's also important to cite them in Chap 2 as well.}
+\gkc{Updated.}
 
@@
     \includegraphics[width=1\textwidth]{lit/other/madis_flow.png}
-    \caption[\acrshort{madis} data flow]{\acrshort{madis} data flow \cite{Macdermaid2005ARCHITECTUREP2.39}.}
+    \caption[\acrshort{madis} data flow]{\acrshort{madis} data flow \cite{Macdermaid2005ArchitectureP2.39}.}
     \label{fi:madis_flow}
@@
 In addition, the paper mentioned architectural advancement at that time, the various functional hosts have been paired using Linux High Availability (HA) to provide automated failover in the event of a system failure.
-And it uses following method for data dissemination such as FTP, Local Data Manager (LDM) and the Web OPeNDAP (OPen source project for Network Data Access Protocol) \cite{Macdermaid2005ARCHITECTUREP2.39}.
+And it uses following method for data dissemination such as FTP, Local Data Manager (LDM) and the Web OPeNDAP (OPen source project for Network Data Access Protocol) \cite{Macdermaid2005ArchitectureP2.39}.
 As mentioned above, the \acrshort{madis} is implemented based on a distributed architecture that is available at the time of its development.
 Even it is not mentioned, it is using functional calls like Remote Procedure Call (RPC) to invoke among a cluster of nodes.
-In \cref{fi:madis_flow}, data is transported from the input and preprocessing systems to the central computer systems and then to other hosts for storage and distribution \cite{Macdermaid2005ARCHITECTUREP2.39}.
+In \cref{fi:madis_flow}, data is transported from the input and preprocessing systems to the central computer systems and then to other hosts for storage and distribution \cite{Macdermaid2005ArchitectureP2.39}.
 To get high availability, it has added some updates to its architecture as mentioned in the paper.
@@
 This data is sent to the data server of the Advanced Weather-Interactive Processing System (AWIPS) of the central installation for processing and conversion to a common format, NetCDF.
-NetCDF files are then transferred to MADIS compute nodes \cite{Macdermaid2005ARCHITECTUREP2.39}.
+NetCDF files are then transferred to MADIS compute nodes \cite{Macdermaid2005ArchitectureP2.39}.
 This provides an overview of the level of data that \acrshort{madis} handling.
@@
 %MADIS computer platforms include Intel-based servers with the Red Hat Enterprise Linux operating system. 
-Many of these computers are configured using Linux clustering with high availability \cite{Macdermaid2005ARCHITECTUREP2.39}.% As indicated above, the system heavily depends on the platform.
+Many of these computers are configured using Linux clustering with high availability \cite{Macdermaid2005ArchitectureP2.39}.% As indicated above, the system heavily depends on the platform.
 There are some costs involving purchasing their licenses.
@@
 As certain MADIS data is considered to be the property of the supplier, access to this data must be checked.
-To respond to this, MADIS data is divided into six different versions, depending on the access level authorized by the data provider \cite{Macdermaid2005ARCHITECTUREP2.39}.
+To respond to this, MADIS data is divided into six different versions, depending on the access level authorized by the data provider \cite{Macdermaid2005ArchitectureP2.39}.
 When compared to \acrshort{fews}, \acrshort{madis} provides control based access to the data.
@@
 \label{se:lit_summary}
-\db{We presented several related work on ...} We forced mainly focus on the issue of storing data which are ingested from different sources with different formats efficiently.
+\db{We presented several related work on WDIA system implementations such as \acrshort{fews}, \acrshort{lead}, \acrshort{dias}, and \acrshort{madis}}.
+In this research one of major issue that we focused on storing data which are ingested from different sources with different formats efficiently.
 The \acrshort{fews} and \acrshort{madis} are using the \acrshort{netCDF} as the common data format to store the data which is one of the best solutions available with modern technologies as well.
@@
 \dbc{Complete highlighted sentence}
+\gkc{Updated. Do I need to elaborate more?}
 
@@
 
-\dbc{You are making lots of mistakes when using "ing" form of a verb. It seems checking with Grammalee didn't help either.}
+\dbc{You are making lots of mistakes when using "ing" form of a verb. It seems checking with Grammaly didn't help either.}
+\gkc{I fixed all the issues one by one which are shown by Grammarly free version. Can you highlight with a specific example. I'll add more effort to improve.}

### 2020-03-18 ThePaper.tex
Thesis 4.0

@@
 \label{pse:Introduction}
-% Weather prediction is essential to reduce impact due to natural disasters and to gain effectively manage natural resources like water.
-\acrfull{curw}\cite{CUrWSL2017SL} is tasked with the mission to reduce water-related natural disasters in Sri Lanka.
-It collected real-time data from weather stations and other government entities and generates daily forecasts.
-Then the generated results are shared with relevant public departments responsible for disaster planning, mitigation, and management.
-Weather prediction is essential to reduce impact due to natural disasters and to gain effectively manage natural resources like water.
-To enhance the accuracy of weather predictions, it is necessary to provide reliable and detailed weather data as inputs to \acrfull{nwm}s.
-Before feeding such diverse data collected from different sources, it is necessary to convert to a data format that can be ingest by the NWMs.
-Further these data need to be process with less time to increase the lead time of forecasting, and need to handle bulk stream weather data.
-Processed weather data needs to be accessed by many third-party applications and research to make use of them.
-For example, logistics companies could use those data with their models to plan and schedule their deliveries.
+Weather prediction is essential to reduce the impacts caused by natural disasters and to effectively manage natural water resources.
+To enhance the accuracy of weather predictions, it requires to provide reliable and detailed weather data as inputs to \acrfull{nwm}s.
+Before feeding such diverse data collected from different sources, we need to convert data into NWMs compatible data format.
+Further we need to process data with lesser time to increase the lead time of forecasting, and need to handle bulk stream weather data.
+Many third-party applications and researcher need to accessed processed weather data to make use of them.
+As few examples, logistics companies could use those data with their models to plan and schedule their deliveries.
 Agricultural insurance companies can warn the farmers, as well as calculate premiums based on anticipated weather patterns.
-Even though there are many data integration systems, most of them are proprietary or closed source.
-For an island like Sri Lanka that having different kinds of weather seasons over the year than that software originated need to be highly customized.
+Even though there are many data integration systems, most systems are proprietary or closed source.
+For an island like Sri Lanka that having different kinds of weather seasons over the year than that software originated countries, those systems need to be highly customized.
 Thus it required to get support from the vendor to integrate and configure the system.
-And most of the software existing out there are not up to date with the latest technology concepts such as Cloud Computing, not using modern architecture pattern such as microservice architecture was able to provide high scalability and availability, and depend on the software platforms.
-\dbc{This para needs to be more specific. For e.g., some of the key motivations listed in Abstract is not listed here. Also, they should ideally be an expanded version of the motivation.}
-\gkc{Updated referring to motivation section.}
+Most of the software existing out there are not up to date with the latest technology concepts such as Cloud Computing, and not using modern architecture pattern like microservice architecture that can use to build highly scalable and available systems, and use containerized applications to run systems independ of software platforms.
 
-%There are many forecasting systems 
 \db{Several forecasting systems are} developed with considering above factors for disaster management.
-The \acrshort{fews}\cite{Werner2013TheSystem} is developed in the Netherland by Deltares for operational forecasting.
-It uses a model-centric approach with considering forecasting process as a combination of data modeling steps and data transformation algorithms.
-So, it is a flexible framework with no inherent hydrological modeling capabilities and capable of creating forecasting workflows by integrating new models and algorithms.
-Also it follows a common data-model approach with only allowing models to interact with the system via one of the interfaces provided, and all the timeseries data are stored via this common data model.
-Even this approach is efficient in data storing and accessing, but it has the inherent issues of performance of accessing data via a single data model in a database.
-One of interesting concept of \acrshort{fews} is using unique fields to identify timeseries such by their location and data type, as well as an id related to the source of the data.
-Even it provides an easy way to integrate models by following the concept of the open modeling framework proposed by Open model integration \cite{Kokkonen2003InterfacingXML}, the model adapter is causing tide coupling into the execution process with the \acrshort{fews}.
-This causing some issue with unit testing models separately and does not easily allow users to run the models in flexible manner such as parallel execution or external process execution.
+Deltares developed the The \acrfull{fews}\cite{Werner2013TheSystem} in the Netherland for operational forecasting.
+It uses a model-centric approach, and implements the forecasting process as a combination of data modeling steps and data transformation algorithms.
+This framework does not have inherent hydrological modeling capabilities.
+But it capable of providing capability to create forecast workflows by integrate new models and algorithms.
+Also it uses a common data-model approach, and only allows models to interact with the system data via using one of the interfaces provided.
+All the timeseries data store in the common data model.
+This approach can consider as efficient for data store and access, but it has the inherent performance issues of access data in the database through a single data model.
+Interestingly, the \acrshort{fews} uses set of unique fields to identify timeseries one from another such as using timeseries's location and data type, as well as an id related to the source of the data.
+It provides an easy model integration with using the concept of the open modeling framework proposed by Open model integration \cite{Kokkonen2003InterfacingXML}.
+But the model adapter causes tide couple between models and the execution process of the \acrshort{fews}.
+This can cause issues when it required to do model unit testing and restrict the flexibility of running the models with parallel execution or external process execution.
 
-\acrfull{lead} is using the fundamental concept of  dynamic workflow orchestration and data management in a Web services framework \cite{Droegemeier2005Service-OrientedWeather}.
-To predict and analyze weather models by researchers, it required many resources.
-Rather than each researcher is running and handling their computer resources to do the weather experiments, \acrshort{lead} provides a pool of resources, then the researchers can use the resources pool to run their experiment in shorter amounts of time in higher scale.
-It is following the \acrfull{soa} with different service layers, and expose services via a drag and drop interface to create new flow by users to run new forecast workflows.
-A workflow service inside the \acrshort{lead} schedules and run workflows with promising the full use of underline resources in the system.
-\acrfull{dias}\cite{Kawasaki2018DataReduction} and \acrfull{madis}\cite{Macdermaid2005ArchitectureP2.39} provide the functionality of integration and sharing weather data.
-When compared to other systems, \acrshort{dias} and \acrshort{madis} do not have the workflow capabilities.
-To store data on a large volume of disk space, \acrshort{dias} converts the data using a inbuilt set of \acrshort{api}s and provides the functionality of quality control of the data, and metadata management, and shares the data through a Shared API layer.
-Also, \acrshort{madis} stores the data by converting into a common data format, and provides role based data access.
-As mentioned above, most systems are using monolithic architecture or client service architecture, platform dependent, and not up to date with cloud computing technologies.
-Thus users do not have much flexibility to decide the best cost-effective way to host it.
-Since most system are proprietary or closed source, it is difficult to add new requirements and maintain the system.
+\acrfull{lead} \cite{Droegemeier2005Service-OrientedWeather} uses the concept of dynamic workflow orchestration and data management in a Web services framework.
+To predict and analyze weather models by researchers, it requires many resources.
+Rather than each researcher runs and maintain own computer resources for the weather experiments, the \acrshort{lead} provides a pool of resources.
+The researchers use the resources pool to run their experiment in shorter amounts of time in higher scale.
+The \acrshort{lead} follows \acrfull{soa} with different service layers.
+Also it exposes services through a drag and drop interface to create new workflows.
+A workflow service in the \acrshort{lead} schedules and run built workflows with promising the maximum use of underline resource pool.
+\acrfull{dias} \cite{Kawasaki2018DataReduction} and \acrfull{madis} \cite{Macdermaid2005ArchitectureP2.39} provide the functionality of integration and sharing weather data.
+When compared to other discussed systems, \acrshort{dias} and \acrshort{madis} do not provide the workflow capabilities.
+The \acrshort{dias} converts data using a inbuilt set of \acrshort{api}s to store data on a large volume of disk space.
+It also provides some functionalities to quality control the data, and metadata management, and shares the data through a shared API layer.
+The \acrshort{madis} stores the data after converts into a common data format, and allow role based data access.
+As mentioned above, most systems uses monolithic architecture or client service architecture, platform dependent, and not up to date with cloud computing technologies.
+Thus users can not benefit from modern cloud platforms and not able to decide the best cost-effective way to host the system.
+Since most systems are proprietary or closed source, it is difficult to add new requirements and maintain the system in long-term.
 
-\dbc{Reduce previous 3 para into at most 2 paras. Ideally one para.}
-\gkc{Reduce to two paragraphs.}
-\dbc{Need to add a paragraph that clearly highlight the research contribution, its novelty, how we do it, and a sentence or 2 on performance.}
-\gkc{Added new paragraph below.}
-
-Therefore, in this paper, we present a weather data integration and assimilation system (WDIAS) that is an extendable weather data integration, assimilation, and dissemination system which is capable of handling bulk data efficiently with providing scalability and high throughput with using open source tools which support modern cloud computing advancements.
+Therefore, in this paper, we present a \acrfull{wdias} that is an extendable weather data integration, assimilation, and dissemination system which is capable of handling bulk data efficiently with providing scalability and high throughput.
+Further it uses open source tools that support modern cloud computing advancements.
 When compared to other systems' architectures, \acrshort{wdias} uses modern microservice architecture that enables best use of the cloud computing with achieving scalability, high availability with low-cost.
 Using container orchestration to run the system platform independently with easy setup and maintain the system on different computer resources.
-Also, the WDIAS provides a modular architecture to integrate data from different sources, export into different formats, and the inbuilt extension module system allow users to add new features without any downtime.
-Using an experimental setup on the cloud, we demonstrate that WDIAS is capable of handling 18,000 requests per minute with different data types, and each request contains 15 minutes interval data per a day.
-Also, the system is capable of scaling up and shrinking down as per given workload, and capable of running using large range of computer resources such as from few CPUs to few hundred CPUs.
+Also, the \acrshort{wdias} provides a modular approach to integrate data from different sources, export into different data formats, and the inbuilt extension module system allow users to add new features without any system downtime.
+Using an experimental setup on the cloud, we prove that \acrshort{wdias} is capable of handling 18,000 requests per minute with different data types, and each request contains 15 minutes interval data per a day.
+Also, the system is capable of scaling up and shrinking down as per given workload, and capable of running on large range of computer resources such as from few CPUs to few hundred CPUs.
 
-%This paper first provides a brief review on necessity of weather forecasting and some of existing weather data systems. 
-\db{Rest of the paper is organized as follows:} \cref{pse:background} provides an overview of modern architectural patterns used in \acrshort{wdias} and the important components and features of the \acrshort{wdias} discussed in \cref{pse:wdias_architecture}, next \cref{pse:performance_analysis} discusses the test workload performance analysis with comparing with the metrics.
+\db{Rest of the paper is organized as follows:} \cref{pse:background} provides an overview of weather data integration and assimilation systems and architectural decision taken with \acrshort{wdias}.
+The important components and features of the \acrshort{wdias} discussed in \cref{pse:wdias_architecture}, next \cref{pse:performance_analysis} discusses the test workload performance analysis with comparing with the metrics.
 
@@
 During the performance test, it creates 1000 timeseries using the locations are taken from Google's Countries Public Data set \cite{GoogleGoogleCounties}, and uses static 100 Grid locations for store Grid data.
-Load test perform using \acrshort{jmeter} and used the Distributed Testing feature to generate higher load.
+Load test perform using  JMeter and used the Distributed Testing feature to generate higher load.
 It uses the master-slave approach and it allowed to handle all the test cases via single instance, rather handling separate instances.
@@
 
-One of the reasons for having deviations at the peak time due to uses of single instance for the data consistency such as \acrshort{influxdb} for Scalar and Vector data, and netCDF with parallel support for Grid data.
+One of the reasons for having deviations at the peak time due to uses of single instance for the data consistency such as  InfluxDB for Scalar and Vector data, and netCDF with parallel support for Grid data.
 Further, it is possible to gain more performance using the databases with configure with high scalability and high availability features such as Sharding and Replication.

### 2020-03-18 introduction/sec_1-motivation.tex
Thesis 4.0

@@
 After removing the bias, the data extracted from a \acrshort{nwm} are then fed into another set of models/simulators.
-% \db{For example, FLO2D is a hydrologic model that can use to predict the surface water level.
-A given FLO2D model can simulate with the initial surface water levels and the sequence of forecasted rainfall for the corresponding modeled area from the \acrshort{nwm} model to forecast future water levels.}
-\dbc{Highighted part doesn't make much sense to me. Need to be reworded.}
-\gkc{Highlighted parts modified and kept also.}
-\dbc{Highighted part is still not clear to me.}
+For example, FLO2D, a hydrologic model that predicts surface water level, could use precipitation estimates from \acrshort{wrf} to forecast flood levels.
 \gkc{Removed the sentence. I tried to use the FLO2D as a model which can use WRF output to forecast water levels.}
+\dbc{I fixed the sentence. Check whether it was ok. It was a pathetic effort to remove the sentence than trying to fix it.}
 
@@
 %required a provide platform to provide such 3rd party access, and use the data or process those based on their applications.
-\dbc{Data is plural.}
-\gkc{Got it. Data needs -> Data need}
 
@@
 While a few other data integration systems exists, most of them are also proprietary or closed source.
-Thus, it is difficult and costly to customize such systems for an island like Sri Lanka which experience different kinds of weather seasons over the year.
+Thus, it is difficult and costly to customize such systems for an island like Sri Lanka which experience different kinds of weather seasons over the year \cite{NaveendrakumarFiveLanka}.
 % than that software originated need to be highly customized.
@@
 %In such a case, it required to get support from the vendor to integrate and configure the system.
-\dbc{Something seems to be wrong with reference Macdermaid2005ARCHITECTUREP2.39}
-\gkc{Seems to be issue with Mendeley.}
-\dbc{"Island like Sri Lanka which experience different kinds of weather seasons over the year" We need to add a citation that talks about multiple types of weather patterns in Sri Lanka} 
-Island like Sri Lanka which experience different kinds of weather seasons over the year \cite{NaveendrakumarFiveLanka}.
-\gkc{Added a reference.}
 
@@
 
-\db{Given the above facts, there is a necessity to develop a WDIA system that could capable of handling large multimodel data efficiently with providing scalability and high throughput with using open source tools which support modern cloud computing advancement, as well as support data sharing with other NWMs and third-party access.}
-\dbc{Complete the above sentence by adding a list of desirable features.}
+Given the above reasons, there is a necessity to develop a WDIA system that could handle large volumes of multimodel data efficiently while providing scalability and high throughput.
+Moreover, it is desirable to support controlled data sharing with other NWMs and third-party access to enable multiple use cases.
+Furthermore, such a system should be architectured to benefit from technologies such as cloud computing and microservices.

### 2020-03-18 lit/sec_1-fews.tex
Don't use shortened words like it's, isn't, don't,... in writing
Thesis 4.0

@@
 Other countries are also using those systems while adopting them to specific weather conditions.
-This chapter presents a literature review on existing systems and their architectural approaches and designs.
+This chapter presents a literature review on existing systems and their architectural designs.
 In \cref{se:fews}, we present \acrfull{fews}, an open model integration framework.
@@
 
-\acrshort{fews} \cite{Werner2013TheSystem} is developed by Deltares in the Netherland with target audiences/customers of operational forecasting agencies.
-The \acrshort{fews} codebase is not fully open source at the moment.
-Most of models are using a model-centric approach such as inputs, need to be in the format of specific to the model.
-Also, the outputs produced by the model are specific to the model and hard to utilize by other systems (e.g., FLO2D create human readable text output files).
-As \acrshort{fews} uses a modular approach it is easier to integrate new models.
+\acrshort{fews} \cite{Werner2013TheSystem} was developed by Deltares in the Netherland for operational forecasting agencies. The \acrshort{fews} codebase is not fully open source at the moment.
+\hl{Most of models are using a model-centric approach such as inputs, need to be in the format of specific to the model}.
+Also, the outputs produced by the models are specific to the model; hence, difficult to integrate with other systems.
+For example, FLO2D creates human readable text output files.
+However, as \acrshort{fews} uses a modular approach it is easier to integrate new models.
 Thus, \acrshort{fews} can be considered as an integration framework or a middleware for the models.
 
-Forecasting processes is creation of modeling steps with combining data transformation algorithms.
-In the flow, each step process and feed data into the next step.
+\hl{Forecasting processes is creation of modeling steps with combining data transformation algorithms.
+In the flow}, each step process and feed data into the next step.
 The \acrshort{fews} is flexible enough to integrate new models and algorithms into the core codebase that can use to create new workflows \cite{Werner2013TheSystem}.
-\acrshort{fews} does not have any inbuilt hydrological modeling capabilities within its codebase.
-Rather it is a framework that can use to integrate into the system and create workflows for forecasting.
+%\acrshort{fews} does not have any inbuilt hydrological modeling capabilities within its codebase.
+Rather it
+\acrshort{fews} is a framework that can be used to integrate into the system and create workflows for forecasting.
 
-Are proposed by Haggett \cite{Haggett1998AnWales} key elements of a forecasting system are defined as detection, forecasting, then dissemination and warning, and response to the events.
+Are proposed by Haggett \cite{Haggett1998AnWales} key elements of a forecasting system are defined as detection, forecasting, dissemination and warning, and responding to the events.
 The \acrshort{fews} focuses on the forecasting step out from above steps.
@@
     \centering
-    \includegraphics[width=0.7\textwidth]{lit/fews/Schematic-structure-of-a-fl-ood-forecasting-system-showing-the-position-of-Delft-FEWS_W640.png}
-    \caption[Schematic structure of a flood forecasting system including \acrshort{fews} and communication among other operational systems]{Schematic structure of a flood forecasting system including \acrshort{fews} and communication among other operational systems \cite{Werner2013TheSystem}.}
+    \includegraphics[width=0.8\textwidth]{lit/fews/Schematic-structure-of-a-fl-ood-forecasting-system-showing-the-position-of-Delft-FEWS_W640.png}
+    \caption[Schematic structure of a flood forecasting system including \acrshort{fews} and communication among other operational systems]{Schematic structure of a flood forecasting system including \acrshort{fews} and communication with other operational systems \cite{Werner2013TheSystem}.}
     \label{fi:fews_schematic}
@@
 
-The \acrshort{fews} follows a data-centric approach, with providing a common data-model to interact from all other components.
+The \acrshort{fews} follows a data-centric approach, where it provides a common data-model to interact with other components.
 All the timeseries data types are stored in a database which follows a common data model.
 New models are integrate to the system via using a one of the interfaces provided to interact with the common data-model \cite{Werner2013TheSystem}.
-As mention in the paper, having a common data-model make easy to store data efficiently.
-Operations like reporting and sharing the data also make it easy by integrating models.
-But the problem with this approach is, handling the multiple data formats.
+\hl{As mention in the paper}, having a common data-model makes it easier to store data efficiently.
+Operations like reporting and sharing the data \hl{also make it easy by integrating models.} %But the problem with
+However, this approach cannot handle multiple data formats.
 \acrshort{fews} overcome this issue by introducing adapters for most of the commonly used data formats.
-This is a good feature that enables users to easily import data into the system.
-But at the same time, it's adding additional complexity to the system.
+While this enables users to easily import data into the system, it also introduces adding additional complexity to the system.
 
-The timeseries data is one of scalar, vector, or grid data, and all of different types are uniformly stored as binary objects in a time series table inside the \acrshort{fews}.
+The timeseries data is \hl{one of scalar, vector, or grid data, and all of different types are uniformly stored} as binary objects in a time series table inside the \acrshort{fews}.
 Functional compenents or any integrated models do not have direct access to the timeseries table which mentioned above, and those should use the data access module to access the data \cite{Werner2013TheSystem}.
-As explained in the system interpretation, every time all the data access needs to go through the data access module which causing adding more cost in data access.
-Since it is storing the different data types as binary objects, there is a penalty in converting data into binary objects and vice versa.
-Storing all the data in a timeseries table causing all the requests to come into a single data model in a database.
-Even it gives the advantage of accessing all the data in one place.
-Since screaming big amount of data is causing a heavy load on the system, causing to slow down in the performance of trying to use the system on a large set of data.
+As explained in the system interpretation, all data access requests need to go through the data access module increasing the cost of data access.
+Because it stores different data types as binary objects, there is a penalty to convert data into binary objects and vice versa.
+\hl{Storing all the data in a timeseries table causing all the requests to come into a single data model in a database.
+Even it gives the advantage of accessing all the data in one place.} Further the performance goes down due to the need to scream high volume of data.% cause a heavy load on the system, causing to slow down in the performance of trying to use the system on a large set of data.
 
-Given above drawback on storing the data in the system, the \acrshort{fews} data model store the timeseries by uniquely identifying based on the location, data type, and source of the data \cite{Werner2013TheSystem}.
-This allows indexing the database on the above key fields and stores the data separately, to take advantage of putting multiple data resources into the system.
+Given the above drawback on storing the data in the system, the \acrshort{fews} data model store the timeseries by \hl{uniquely identifying based on the location, data type, and source of the data} \cite{Werner2013TheSystem}.
+This allows indexing the database using above key fields \hl{and stores the data separately}, to take advantage of \hl{putting multiple data resources into the system}.
 As an example, instead of storing the data at a single timeseries table, it is possible to separate and index the database based on the source such as an external source of data or hydrological model of which the timeseries is a result.
@@
 
-Data processing and manipulation is a required process in weather forecasting. 
-The data integrated from the external sources are not in the appropriate temporal and spatial format that can directly feed as an input to a forecasting model or use in other application.
-Therefore, generic data processing steps are a required effort in most model applications in the forecasting environment.
-Few examples are serial and spatial interpolation, data validation, aggregation and disaggregation, and data fusion \cite{Werner2013TheSystem}.
+Data processing and manipulation \hl{is} a required process in weather forecasting. 
+The data integrated from external sources are not in the appropriate temporal and spatial format that can directly feed as an input to a forecasting model or use in other application.
+Therefore, generic data processing steps are required for most models in a forecasting environment.
+Such examples are serial and spatial interpolation, data validation, aggregation and disaggregation, and data fusion \cite{Werner2013TheSystem}.
 This a vital feature in a forecasting system, and affect the quality and accuracy of the predicted data outputs.
 Because of the common data model concept in \acrshort{fews}, data processing via these functions is much effective.
-The system is self-provided some of the generic functions for data processing, but required complex algorithms can be implement as a new Java class via communicate with the \acrfull{api}.
-It is obvious that for additional feature integration, users should implement the new functional extensions via Java programming language.
-Users do not have the flexibility of development with some other languages they are familiar with or use the support from another language.
+The system is \hl{self-provided some of the generic functions for data processing}, but required algorithms can be implement as a new Java class via \hl{communicate} with the \acrfull{api}.
+%It is obvious that
+For additional feature integration, users should implement the new functional extensions using Java.
+%Users do not have the flexibility to development with some other languages they are familiar with or use the support from another language.
 As an example, Python language is easy to use for beginners and many data scientists are using this programming language for development and it has many data available libraries for data processing.
 However, in \acrshort{fews}, users cannot take advantage of such existing tools.
+\dbc{I removed part of where you are trying to say support for Python is good.
+Rather than pointing out such minor issues (these are special purpose software), in Chap 3 and 5 you can highlight that by using microservices models/functions can be developed by any language of choice.}
 
@@
 \end{figure}
-\db{The \acrshort{fews} supports data processing and modeling library to access scalar and grid timeseries same way}.
-However, the communicates with the database only via the data access layer as shown in \cref{fi:fews_data_layer} \cite{Werner2013TheSystem}.
-As it is shown in the figure, it is clearly showing that the system depends on a single database and via the data access layer, all the requests are coming to the database through a connection.
-It is possible to setup and connect to an enterprise-level database with clustering and shading as a paid solution, to serve many requests as possible.
-However, the design itself inherently suffers from the database bottleneck which effected by running a large set of timeseries or models.
-\dbc{Above highlighted is not clear to me.}
-\gkc{Updated}
+
+\acrshort{fews} provides data processing and modeling library to access scalar and grid timeseries the same way.
+However, \hl{the communicates with the database} only via the data access layer as shown in \cref{fi:fews_data_layer} \cite{Werner2013TheSystem}.
+As %it is shown in the figure, it is clearly showing that
+shown in figure, the system depends on a single database and \hl{via} the data access layer, all the requests are coming to the database through a connection.
+It is possible to setup and connect to an enterprise-level database with clustering and shading as a paid solution to enhance the throughput.
+%serve many requests as possible.
+However, the design itself inherently suffers from the database bottleneck which \hl{effected} by running a large set of timeseries or models.
 
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{lit/fews/Linking-Delft-FEWS-with-external-models-The-fi-gure-shows-the-fl-ow-of-data-through-XML_W640.png}
-    \caption[\acrshort{fews} integration with external models]{\acrshort{fews} integration with external models \cite{Werner2013TheSystem}.}
+    \includegraphics[width=0.9\textwidth]{lit/fews/Linking-Delft-FEWS-with-external-models-The-fi-gure-shows-the-fl-ow-of-data-through-XML_W640.png}
+    \caption[\acrshort{fews} integration with external models]{Integrating \acrshort{fews} with external models \cite{Werner2013TheSystem}.}
     \label{fi:fews_general_adapter}
@@
 The users need to mentioned the input timeseries via XML configurations, and \acrshort{fews} generates the input data as XML files.
-Then using an adapter developed for the model transforms the data into required format for the model as a preprocessing step.
-Next \acrshort{fews} executes the model and model generates the output after successful completion.
-In the post processing step, the model result data transform to the XML files which can import into the data model as shown in \cref{fi:fews_general_adapter} \cite{Werner2013TheSystem}.
-The process is simple and consistent throughout all the model integration.
+Then using an adapter \hl{developed for the model transforms the data into required format for the model as a preprocessing step}.
+Next, \acrshort{fews} executes the model which generates the output.
+In the post processing step, the results of the model is transformed to an XML file, which \hl{can import} into the data model as shown in \cref{fi:fews_general_adapter} \cite{Werner2013TheSystem}.
+%The process is simple and consistent throughout all the model integration.
 The model execute by the \acrshort{fews} or the model adapter which is causing tide coupling into the execution process in the system.
@@
 That may be overcome by triggering an external process at the execution time, but it introduces more difficulty for handling after model executed successfully, preceding to the next step in the process.
-This part of the system feature is not focused on the \acrshort{wdias} and user has to come up with own flow or use existing scientific flow management system.
+\hl{This part of the system feature} is not focused on the \acrshort{wdias} and user has to come up with own flow or use existing scientific flow management system.
 Yet, it is a concept that needs to be discussed and understand properly to design a data integration and assimilation system.
@@
 Data exchange with the model is mainly done via XML files.
-It is possible to happen, these XML files become very large, which can lead to I/O bottlenecks and causing performance issues \cite{Werner2013TheSystem}.
-This issue is thoroughly discussed in previous paragraphs and the authors of the \acrshort{fews} \cite{Werner2013TheSystem} seem to be noticed and accept it here.
-For overcoming this issue they introduced the file-based exchange of data.
+\hl{It is possible to happen}, these XML files become very large, which can lead to I/O bottlenecks and causing performance issues \cite{Werner2013TheSystem}.
+%This issue is discussed in previous paragraphs and
+The authors of the \acrshort{fews} \cite{Werner2013TheSystem} seem to have noticed and accepted this issue. % it here. 
+\hl{For overcoming this issue} they introduced file-based exchange of data.
 This includes the use of binary XML files, the streaming of files via memory and the use of \acrshort{netCDF} files.
@@
 Also, there are some cases it is hard to develop an adapter or running alongside the \acrshort{fews}.
-As an example, the FLO2D model is using for hydrologic modeling and the model only supports only on Windows based operating systems.
-If you setup the system on Linux based operating system and using Linux based models, it is hard for users to come up with a solution for integrating the FLO2D models.
+For example, the FLO2D model used for hydrologic modeling only runs on Windows.\hl{ If you setup the system on Linux based operating system and using Linux based models, it is hard for users to come up with a solution for integrating} the FLO2D models.
 The \acrshort{fews} support creating workflow process and allow users to run multiple models parallel or run those sequentially as needed, but the scope of the \acrshort{wdias} is not focused on adding such a feature in the system, rather user has to use a scientific workflow management system or come up with own version of workflow.

### 2020-03-18 lit/sec_2-lead.tex
Thesis 4.0

@@
 \acrfull{lead} \cite{Droegemeier2005Service-OrientedWeather} addresses the fundamental research challenges needed to create an integrated and scalable framework for adaptive analysis and prediction of the atmosphere.
-To predict and analyze weather models by researchers, it required many resources.
+To predict and analyze weather models by researchers, \hl{it required} many resources.
 Rather than each researcher is running and handling their computer resources to do the weather experiments, \acrshort{lead} is providing pool of resources, then the researchers can use this resource a pool to run their experiment in shorter amounts of time and higher scale.
-At the time, researchers are developing their experiment flow, they are not using the resources many, and others are using it at the same time.
-The foundation of \acrshort{lead} system is to create a dynamic workflow orchestration and data management in a Web services framework \cite{Droegemeier2005Service-OrientedWeather}.
+\hl{At the time, researchers are developing their experiment flow, they are not using the resources many, and others are using it at the same time.} The foundation of \acrshort{lead} system is to create a dynamic workflow orchestration and data management in a Web services framework \cite{Droegemeier2005Service-OrientedWeather}.
 
@@
 \cref{fi:lead_system} shows the key capabilities of the \acrshort{lead} system.
-From the high-level view, \acrshort{lead} enables users to search and acquire information, simulate and predict weather conditions using digital atmospheric models, assimilate, analyze, use and visualize data and output of models.
+\hl{From the high-level view}, \acrshort{lead} enables users to search and acquire information, simulate and predict weather conditions using digital atmospheric models, assimilate, analyze, use and visualize data and output of models.
 
@@
 
-The second level contains the basic tools that help to link services together. This includes the following tools \cite{Droegemeier2005Service-OrientedWeather};
+The second level contains basic tools such as the following to help to link services together  \cite{Droegemeier2005Service-OrientedWeather}:
 \begin{itemize}
@@
 
-The concept of the \acrshort{lead} is a workflow orchestration for on-demand, real-time and dynamically adaptive systems called WOORDS.
-The system is doing the workflow orchestration as given in each procedure.
+\hl{The concept of the \acrshort{lead} is a workflow orchestration for on-demand, real-time and dynamically adaptive systems called WOORDS.} The system is doing the workflow orchestration as given in each procedure.
 Those procedural rules are defined by the researcher and feed into the system.
 The system is trying to act immediately after the submission, and also it transmits the data, run the models and send back the put with a lower time delay as possible.
-According to the load and other requirements, the system will respond to those requirements automatically.
+\hl{According to the load and other requirements, the system will respond to those requirements automatically.}
 
@@
 
-\acrshort{soa}s are widely used in the commercial enterprise sector and form the basis of many scientific "grid" technologies in lead design and development.
+%\acrshort{soa}s are widely used in the commercial enterprise sector and form the basis of many scientific "grid" technologies in lead design and development.
 A variant of \acrshort{soa} was developed later, called microservices architecture, and is now widely used in industry nowadays.
@@
 These are some critical aspects of a weather data management system.
-Most of the services listed here are required for creating workflows for weather data forecasting.
-Thus it is important to review them and understand the basic needs of a weather data management system.
+Most of the services listed below are required for creating workflows for weather data forecasting.
+\hl{Thus it} is important to review them and understand the basic needs of a weather data management system.
 
@@
 This is an important feature that should be available in a weather data system, and users need to search for the availability of the data.
-Further wants to analyze the existing data for decision making.
+\hl{Further wants to analyze} existing data for decision making.
 \item Users need a multitude of data services to support comprehensive query, access, and transformation operations on data products.
@@
 \end{itemize}
-The top of \cref{fi:lead_soa}, shows the user interface of the \acrshort{lead} which gives individual services access.
-When the user logs into the system, based on the authentication and authorization setting bind to the individual account, the portlets can access the services on behalf of the user.
-Look into further details is not relevant to developing the \acrshort{wdias} since the focus is not on workflow orchestration.
 
-\acrshort{lead} is a more advanced system which can support for mesoscale weather prediction with the effort of multiple universities in the United State America with the effort of many researchers and using many computer resources.
+Top of \cref{fi:lead_soa} shows the user interface of the \acrshort{lead} which \hl{gives individual services access.} When the user logs into the system, based on the authentication and authorization setting of the account, the portlets can access the services on behalf of the user.
+%Look into further details is not relevant to developing the \acrshort{wdias} since the focus is not on workflow orchestration.
+
+\acrshort{lead} is a more advanced system which can support mesoscale weather prediction with the effort of multiple universities in the United State America with the effort of many researchers and using many computer resources.
 At the time it was building, it uses the \acrshort{soa} architecture as into its depth, and with the implementation, each service can scale as needed and possible to enhance the service without interrupting other services.

### 2020-03-18 lit/sec_3-other-systems.tex
Thesis 4.0

@@
 Once this data is integrated into geographic useful information, DIAS generates results for managing global environmental problems and natural disasters \cite{Kawasaki2018DataReduction}.
-As mentioned above, \acrshort{dias} has the capability of collecting weather data from multiple data sources which are inherently in different formats.
-After successfully ingest the data, it generates results which can use for different kind of purposes.
+\acrshort{dias} has the \hl{capability of collecting} weather data from multiple data sources which are inherently in different formats.
+\hl{After successfully ingest} the data, it generates results which can use for different kind of purposes.
 
@@
 
-The mechanism of storing data in \acrshort{dias}, similar to the other systems discussed.
-These data sets are stored in a larger array system with API software that is used to import the data.
+\hl{The mechanism of storing data in \acrshort{dias}, similar to the other systems discussed.}
+These data sets are \hl{stored in a larger array system with API software} that is used to import the data.
 APIs work to convert or reformat data into manageable forms and are useful for creating the DIAS storage archive.
@@
 
-As shown in \cref{fi:dias_common_platform}, it offers an application layer that allows scientists in the field to work on research tasks and to develop specific tools and applications by collaborating with experts in information technology \cite{Kawasaki2018DataReduction}.
+As shown in \cref{fi:dias_common_platform}, it offers an application layer that allows scientists %in the field 
+to work on research tasks and to develop specific tools and applications by collaborating with IT experts \cite{Kawasaki2018DataReduction}.
 Once the data is achieved on the \acrshort{dias} system, it shares those details via the Shared API layer.
-Thus it allows users to remote access to the data, and easy integration via the APIs.
+\hl{Thus it} allows users to remote access to the data, and easy integration via the APIs.
 
@@
 Give users later access to data through support for different types of protocols.
-
-\dbc{Both MADIS and netCDF need to cited. Do this at the beginning for each on the systems in this chapter (while they were cited in Chap 1, it's also important to cite them in Chap 2 as well.}
-\gkc{Updated.}
 
@@
 \acrshort{madis} contains a distributed architecture for data acquisition, processing and distribution functions.
-In addition, the paper mentioned architectural advancement at that time, the various functional hosts have been paired using Linux High Availability (HA) to provide automated failover in the event of a system failure.
-And it uses following method for data dissemination such as FTP, Local Data Manager (LDM) and the Web OPeNDAP (OPen source project for Network Data Access Protocol) \cite{Macdermaid2005ArchitectureP2.39}.
-As mentioned above, the \acrshort{madis} is implemented based on a distributed architecture that is available at the time of its development.
-Even it is not mentioned, it is using functional calls like Remote Procedure Call (RPC) to invoke among a cluster of nodes.
+In addition, \hl{the paper mentioned architectural advancement at that time,} the various functional hosts have been paired using Linux High Availability (HA) to provide automated failover in the event of a system failure.
+It uses several methods for data dissemination such as FTP, Local Data Manager (LDM) and the Web OPeNDAP (OPen source project for Network Data Access Protocol) \cite{Macdermaid2005ArchitectureP2.39}.
+%As mentioned above, the \acrshort{madis} is implemented based on a distributed architecture that is available at the time of its development.
+Even it is not mentioned, it is
+It users functional calls like Remote Procedure Call (RPC) to invoke among a cluster of nodes.
 In \cref{fi:madis_flow}, data is transported from the input and preprocessing systems to the central computer systems and then to other hosts for storage and distribution \cite{Macdermaid2005ArchitectureP2.39}.
@@
 NetCDF files are then transferred to MADIS compute nodes \cite{Macdermaid2005ArchitectureP2.39}.
-This provides an overview of the level of data that \acrshort{madis} handling.
-This could be a good reference for implementing \acrshort{wdias} and its performance testing.
-As same as \acrshort{fews}, it is also converting the data into a common format which is \acrshort{netCDF}.
-Those files are transferred to the compute nodes and allow users to access via OPeNDAP.
+%This provides an overview of the level of data that \acrshort{madis} handling.
+This could be a good reference for implementing \acrshort{wdias} and its performance testing. As same as \acrshort{fews}, it is also \hl{converting} the data into %a common format which is 
+\acrshort{netCDF}. Those files are transferred to the compute nodes and accessible via OPeNDAP. 
 %MADIS computer platforms include Intel-based servers with the Red Hat Enterprise Linux operating system. 
@@
 To respond to this, MADIS data is divided into six different versions, depending on the access level authorized by the data provider \cite{Macdermaid2005ArchitectureP2.39}.
-When compared to \acrshort{fews}, \acrshort{madis} provides control based access to the data.
+When compared to \acrshort{fews}, \acrshort{madis} provides control-based access to the data.
 
@@
 \label{se:lit_summary}
-\db{We presented several related work on WDIA system implementations such as \acrshort{fews}, \acrshort{lead}, \acrshort{dias}, and \acrshort{madis}}.
-In this research one of major issue that we focused on storing data which are ingested from different sources with different formats efficiently.
+We presented several related work on WDIA system implementations such as \acrshort{fews}, \acrshort{lead}, \acrshort{dias}, and \acrshort{madis}.
+In this research one of major issue that we focused on is storing data ingested from different sources with different formats efficiently.
 The \acrshort{fews} and \acrshort{madis} are using the \acrshort{netCDF} as the common data format to store the data which is one of the best solutions available with modern technologies as well.
@@
 \acrshort{fews} provides a modular approach via its general adapter, and according to the \acrshort{soa} architecture of \acrshort{lead} provides the same functionality via services.
-\dbc{Complete highlighted sentence}
-\gkc{Updated. Do I need to elaborate more?}
 
-Most of the above systems developed by many developers and researchers, and were developed specifically to address issues like natural disasters.
-To address use cases such as CUrW, it required to remodel the systems  and define the forecasting flows.
+Most of the \hl{above systems developed} by many researchers, and were developed specifically to address issues like natural disasters.
+To address use cases such as CUrW, \hl{it required} to remodel the systems  and define the forecasting flows.
 Even some of the systems try to follow a generic approach to integrate new modules, it is challenging to deploy modules for a closed source or proprietary software.
-Further, most of them are depend on the underline platform, and does not support more resource efficient and highly-scalable technologies such as cloud computing.
-
-\dbc{You are making lots of mistakes when using "ing" form of a verb. It seems checking with Grammaly didn't help either.}
-\gkc{I fixed all the issues one by one which are shown by Grammarly free version. Can you highlight with a specific example. I'll add more effort to improve.}
+Further, most of them \hl{are depend} on the underline platform, and does not support more resource efficient and highly-scalable technologies such as cloud computing.

### 2020-03-18 method/sec_0_introduction.tex
Thesis 4.0

@@
-This chapter includes the design decision taken while implementing the \acrfull{wdias}, and how is the system got adapted from the systems analyzed in Chapter \ref{ch:literature}.
-\cref{se:high_level_design} includes a brief discussion on how the weather forecasting is happening and why it needs to interact with multiple data formats is presented.
-\cref{se:architectural_decisions} discussed about how did we evolve over the architectural design while designing and implementing the \acrshort{wdias}.
-\cref{se:microservice} gives a better understanding of the microservice architectural concepts that follow while implementing the \acrshort{wdias}.
-Then the reasons behind developing \acrshort{wdias} database structure and technologies use for that discussed in \cref{se:db_struct}.
-\cref{se:data_preprocess} discussed how the \acrshort{wdias} enables for data preprocessing and adding capabilities via the concept of Extensions.
-Final \cref{se:query} includes details on how to perform timeseries search and Geo-based queries on the \acrshort{wdias}.
+This chapter presents the design decisions taken while implementing \acrfull{wdias}, and how is the system got \hl{adapted from the systems analyzed in Chapter} \ref{ch:literature}.
+\cref{se:high_level_design} presents a brief discussion on how the weather forecasting is happening and why it needs to interact with multiple data formats.
+\cref{se:architectural_decisions} presents how the architectural design of proposed solution evolved while designing and implementing \acrshort{wdias}.
+\cref{se:microservice} presents %gives a better understanding of the 
+microservice architectural concepts followed while implementing \acrshort{wdias}.
+Then the reasons behind developing \acrshort{wdias} database structure and technologies used are discussed in \cref{se:db_struct}.
+\cref{se:data_preprocess} discusses how \acrshort{wdias} enables data preprocessing and adding capabilities using extensions.
+Finally, \cref{se:query} includes details on how to perform timeseries search and geo-based queries on the \acrshort{wdias}.
 
+\dbc{It's just WDIAS. "the" should be used only on essential places to being the meaning. }
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-To get an overall idea of the flow of weather prediction, let us look into one of the flows using at \acrshort{curw} \cite{CUrWSL2017SL}.
-\dbc{Use CUrW-SL}
-\gkc{FIXED}
+To get an overall idea of the flow of weather prediction, let us look into one of the \hl{flows using} at the \acrshort{curw} \cite{CUrWSL2017SL}.
 
@@
     \item Extract \acrshort{GRIB} \acrshort{wrf} model data to \acrshort{netCDF}
-    \item From \acrshort{netCDF} to \acrshort{csv} of each location data, then feed to HEC-HMS hydro-dynamic model and get the output as \acrshort{csv}
-    \item \acrshort{csv} and Rain cell Grid feed into the FLO2D hydro-logic model, and get the water level as ASCII Grid files after completion of simulation
-    \item Upload ASCII files to ArcGIS create Raster files, then use for the LOSS Estimation
+    \item \hl{From} \acrshort{netCDF} to \acrshort{csv} of each location data, then feed to HEC-HMS hydro-dynamic model and get the output as a \acrshort{csv} file.
+    \item \acrshort{csv} and \hl{Rain cell Grid feed} into the FLO2D hydrologic model, and get the water level as ASCII Grid files after the simulation is complete.
+    \item Upload ASCII files to \hl{ArcGIS create raster files, then use for the LOSS Estimation}
 \end{enumerate}
-When looked into the above flow, it gives a clear understanding of multiple data formats using while weather predictions.
-Other than that, to correct the model outputs, it required to collect real-time data such as;
+
+\hl{When looked into the above flow, it gives a clear understanding of multiple data formats using while weather predictions.}
+Also, to correct the model outputs, \hl{it required} to collect real-time data such as:
 \begin{itemize}
-    \item Automated weather station sending data in higher frequent intervals via HTTP protocol
-    \item Automated water level stations send data in higher frequency
+    \item Frequently collected automated weather station data via HTTP protocol
+    \item Frequently collected automated water level stations data
 \end{itemize}
-Other than above many data formats using for handling data based on devices and standards which are using.
-Also, for data modeling, it needs to convert the data into model compatible data format, then after successfully run the model it needs to collect data from the model output data formats.
+
+\hl{Other than above many data formats using for handling data based on devices and standards which are using.} Also, for data modeling, it needs to convert the data \hl{into model compatible data format}.
+Then \hl{after successfully run the model it needs to collect data from the model output data formats.}
 
@@
 
-\cref{fi:wdia_components} shows the basic functions of a Weather data integration and assimilation system which consists of the following modules:
+\cref{fi:wdia_components} shows the basic functions of a weather data integration and assimilation system consisting of the following modules:
 
 \begin{figure}[htbp]
-\centerline{\includegraphics[width=0.8\textwidth]{method/misc/weather_data_system_components.jpg}}
+\centerline{\includegraphics[width=1\textwidth]{method/misc/weather_data_system_components.jpg}}
 \caption{Modules of a weather data system.}
@@
 
-\dbc{Why are you referring to timeseries here? It's not one of the 3 key components in Fig. 3.1.}
-\gkc{Move this to WDIAS microservices \cref{sebse:wdias_microservices}. It need to describe the reason behind decompose into microservices. Seems to be this is confusing at this point.}
-
 % In the proof of concept design described below, WDIAS focuses on handling scalar, vector and grid timeseries data. However, the system could be extended to handle polygon-based timeseries as well.
@@
 % \subsubsection{Base of WDIAS architecture}
-\dbc{What's Base of WDIAS architecture?}
-\gkc{Moved to WDIAS database structure section \cref{sebse:wdias_microservices}}
-
 % \hl{The base of WDIAS architecture origins based on attributes of a timeseries.} There are many attributes to differentiate timeseries one from another. But 
 % Among many attribute to differentiate a timeseries from another, the following can be consider as the key attributes in uniquely identify a timeseries from another: % for the \acrshort{wdias}.
-\dbc{Highlighted sentence doesn't make sense to me. All yellow highlights mean they are not clear.}
 

### 2020-03-18 method/sec_1-architectural_decisions.tex
Updates from Overleaf
Thesis 4.0

@@
 The initial design of \acrshort{wdias} used the \acrfull{soa}.
-Moreover, it tried to use an \acrfull{esb} to integrate different modules, as \acrshort{esb} is acting as a common layer for all of the modules.
+Moreover, it tried to use an \acrfull{esb} to integrate different modules, as \acrshort{esb} could act as a \hl{common layer} for all of the modules.
 By default, \acrshort{esb} also provides publisher/subscribe (pub/sub) capabilities.
-\hl{Because} \acrshort{esb} \hl{mediators can be used to integrate the modules which are described in Section} \ref{subse:modules_weather_data_integration_sys}. 
-\gkc{FIXED below}
+\hl{Because \acrshort{esb} mediators can be used to integrate the modules which are described in Section} \ref{subse:modules_weather_data_integration_sys}. 
+\dbc{Last sentence incomplete too.}
+
 The \acrshort{esb} has the processing units called \emph{mediators}.
@@
 
-\dbc{Kubernetes is a product. What you need to refer is to the concept of container-orchestration. Fix.}
-
 % \begin{itemize}
@@
 % \end{itemize}
-
-\dbc{What are these 2 bullets?}
-\gkc{Absorbed those two points into above paragraph}
-\dbc{Don't use shortened words like it's, isn't, don't,... in writing}
 

### 2020-03-18 method/sec_3-microservice.tex
Don't use shortened words like it's, isn't, don't,... in writing
Thesis 4.0

@@
 % \hl{Among the characteristics of microservice, a few characteristics heavily affect while moving from} \acrshort{soa} to microservice.
-\dbc{M in Microservice should be capitalized only on begining of a sentence.}
-
 There are lots of microservice patterns developed and evolved.
@@
 
-Even \acrshort{wdias} is a design based on the Y-axis scaling, it's possible to use the Z-axis scaling to scaling the system further. This will be more discussion in \cref{se:discussion}.
+Even \acrshort{wdias} is a design based on the Y-axis scaling, it is possible to use the Z-axis scaling to scaling the system further. This will be more discussion in \cref{se:discussion}.
 

### 2020-03-18 results/sec_3-observations.tex
Thesis 4.0

@@
 \footnotesize
-\begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
+\begin{tabulary}{\linewidth}{|L|R|R|R|R|R|R|R|R|}
 \hline
-Label & \# Samples & Avg & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
+Label & Samples & Avg & Min & Max & 90\% Line & Std.Dev. & Error & RPS \\ \hline
 Insert Timeseries & 71826 & 28 & 13 & 2773 & 31 & 58.74 & 0.00\% & 40.5 \\ \hline
@@
 \footnotesize
-\begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
+\begin{tabulary}{\linewidth}{|L|R|R|R|R|R|R|R|R|}
 \hline
-Label & \# Samples & Average & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
+Label & Samples & Avg & Min & Max & 90\% Line & Std.Dev. & Error & RPS \\ \hline
 Insert Timeseries & 71759 & 29 & 14 & 1699 & 32 & 50.97 & 0.00\% & 40.5 \\ \hline
@@
 \footnotesize
-\begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
+\begin{tabulary}{\linewidth}{|L|R|R|R|R|R|R|R|R|}
 \hline
-Label & \# Samples & Average & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
+Label & Samples & Avg & Min & Max & 90\% Line & Std.Dev. & Error & RPS \\ \hline
 Insert Timeseries & 71775 & 30 & 12 & 1719 & 41 & 51.71 & 0.00\% & 40.5 \\ \hline
@@
 \footnotesize
-\begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
+\begin{tabulary}{\linewidth}{|L|R|R|R|R|R|R|R|R|}
 \hline
-Label & Samples & Avg & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
+Label & Samples & Avg & Min & Max & 90\% Line & Std.Dev. & Error & RPS \\ \hline
 Insert Timeseries & 71727 & 34 & 13 & 1777 & 27 & 118.78 & 0.00\% & 40.5 \\ \hline
@@
 \footnotesize
-\begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
+\begin{tabulary}{\linewidth}{|L|R|R|R|R|R|R|R|R|}
 \hline

### 2020-04-21 lit/sec_2-lead.tex
Before copy back from Google docs

@@
 
-\hl{The concept of the \acrshort{lead} is a workflow orchestration for on-demand, real-time and dynamically adaptive systems called WOORDS.} The system is doing the workflow orchestration as given in each procedure.
+The concept of the \acrshort{lead} \hl{is a workflow orchestration for on-demand, real-time and dynamically adaptive systems called WOORDS.} The system is doing the workflow orchestration as given in each procedure.
 Those procedural rules are defined by the researcher and feed into the system.

### 2020-04-21 method/sec_3-microservice.tex
Before copy back from Google docs

@@
 The left side of \cref{fi:wdias_micro_on_demand} shows the import modules of the \acrshort{wdias}, and the right side shows the export modules.
-As explained section \cref{subse:dumb_pipes}, each import microservice only does the specific task of converting and forwarding the request to the correct data adapter module.
+As explained \cref{subse:dumb_pipes}, each import microservice only does the specific task of converting and forwarding the request to the correct data adapter module.
 For each data type, there is an adapter microservice is running which is optimized to storing such type of data.

### 2020-04-24 lit/sec_1-fews.tex
Updated Lit review - FEWS

@@
-Many weather forecasting, assimilation, and dissemination systems are developed to reduce the damage causing by natural disasters such as floods, storms, hurricanes, and even droughts.
+Many weather forecasting, assimilation, and dissemination systems are developed to reduce the damage-causing by natural disasters such as floods, storms, hurricanes, and even droughts.
 Other countries are also using those systems while adopting them to specific weather conditions.
@@
 In \cref{se:fews}, we present \acrfull{fews}, an open model integration framework.
-\acrfull{lead}, an open data handling platform distributed as closed-source software, is presented in \cref{se:lead}.
-In \cref{se:dias}, we discuss \acrfull{dias} which is a common data platform that can manage weather data.
+\acrfull{lead}, a distributed open data handling platform as closed-source software, is presented in \cref{se:lead}.
+In \cref{se:dias}, we discuss \acrfull{dias}, which is a common data platform that can manage weather data.
 \acrfull{madis} is another widely used data integration system, which also provides data access with quality controls is presented in \cref{se:madis}.
@@
 
-\acrshort{fews} \cite{Werner2013TheSystem} was developed by Deltares in the Netherland for operational forecasting agencies. The \acrshort{fews} codebase is not fully open source at the moment.
-\hl{Most of models are using a model-centric approach such as inputs, need to be in the format of specific to the model}.
-Also, the outputs produced by the models are specific to the model; hence, difficult to integrate with other systems.
-For example, FLO2D creates human readable text output files.
-However, as \acrshort{fews} uses a modular approach it is easier to integrate new models.
-Thus, \acrshort{fews} can be considered as an integration framework or a middleware for the models.
+Deltares developed \acrshort{fews} \cite{Werner2013TheSystem} in Netherland for operational forecasting agencies.
+The \acrshort{fews} codebase is not fully open source at the moment.
+The main objective of a forecasting system is to run multiple NWMs, hydrologic, and hydrodynamic models which are required for the predictions.
+This approach is known as a model-centric approach \cite{Werner2005FloodCatchments}.
+In the model-centric approach, the inputs need to be in the format specific to the model.
+Also, the outputs produced by the models are specific to the model; hence, difficult to integrate with other models.
+For example, FLO2D creates human-readable text output files.
+However, the Delft-FEWS uses a more modular approach, which is easier to integrate new models and redevelop the system for new requirements.
+Thus, Delft-FEWS is an integration framework or middleware for the models, rather specific model workflow for weather forecasting.
 
-\hl{Forecasting processes is creation of modeling steps with combining data transformation algorithms.
-In the flow}, each step process and feed data into the next step.
-The \acrshort{fews} is flexible enough to integrate new models and algorithms into the core codebase that can use to create new workflows \cite{Werner2013TheSystem}.
-%\acrshort{fews} does not have any inbuilt hydrological modeling capabilities within its codebase.
-Rather it
-\acrshort{fews} is a framework that can be used to integrate into the system and create workflows for forecasting.
+A forecasting flow creates a sequence of modeling steps by combining data transformation algorithms.
+In a forecasting flow, each step processes and feeds data into the next step.
+The \acrshort{fews} is flexible enough to integrate new models and algorithms into the core codebase that can be used to create new workflows \cite{Werner2013TheSystem}.
+So, the \acrshort{fews} framework is capable of integrating models into the system and creating workflows for forecasting.
 
@@
 
-\cref{fi:fews_schematic} shows the connection between the forecasting system to real-time data integration systems and dissemination systems.
-One of the widely used use cases is to use meteorological forecast data to estimate precipitation, and then use a hydrological and hydraulic model chain to predict the surface water level affects.
-The hydrological and hydraulic model should be design based on the geographical data.
-The ground should be analyzed geographically and divide into the catchments.
-Based on the affected catchment, it can be further divided into sub-catchments to reduce the complexity of the simulation task.
-Ideally, the forecasting system should be flexible enough to allow modification of models and data, while keeping the most constant way possible of working with forecasters.
+Haggett \cite{Haggett1998AnWales} summarized the key elements of a forecasting system as detection, forecasting, dissemination, and warning, and responding to the events.
+The \acrshort{fews} focuses on the forecasting step out above four steps.
+The main objective of this step is to provide additional lead time by forecasting future hydrometeorological conditions \cite{Werner2005FloodCatchments}.
+It is a valid argument that providing accurate predictions with more considerable lead time can reduce the level of destruction.
+Further, the forecasting system should be capable of integrating real-time data from weather data observation networks and disseminate the forecasted results through relevant parties to the warning process.
+
+\cref{fi:fews_schematic} shows the connection between a forecasting system to real-time data integration systems and dissemination systems.
+One of the widely practiced use cases is to use meteorological forecast data to estimate precipitation, and then use a hydrological and hydraulic model chain to predict the surface water level affected.
+The hydrological and hydrodynamic models should design based on geographical data.
+The ground surface should be examined geographically and divided into catchments.
+Based on the affected catchment, it can be further divided into sub-catchments to reduce the complexity of the simulation task, and reduce simulation time with parallel processing.
+Ideally, the forecasting system flexible enough to allow modification of models and data while keeping the system interaction method constant as working with multiple forecasters.
 
@@
 The \acrshort{fews} follows a data-centric approach, where it provides a common data-model to interact with other components.
-All the timeseries data types are stored in a database which follows a common data model.
-New models are integrate to the system via using a one of the interfaces provided to interact with the common data-model \cite{Werner2013TheSystem}.
-\hl{As mention in the paper}, having a common data-model makes it easier to store data efficiently.
-Operations like reporting and sharing the data \hl{also make it easy by integrating models.} %But the problem with
+All the timeseries data stored in a database by converting them to a common data model.
+New models are integrated into the system by using one of the interfaces provided to interact with the common data-model \cite{Werner2013TheSystem}.
+The common data-model allows storing data efficiently without duplicates.
+Then, the system supports operations like creating forecast reports and sharing the data by integrating new codebase as adapters.
 However, this approach cannot handle multiple data formats.
-\acrshort{fews} overcome this issue by introducing adapters for most of the commonly used data formats.
-While this enables users to easily import data into the system, it also introduces adding additional complexity to the system.
+The \acrshort{fews} overcome this issue by introducing adapters for most of the commonly used data formats such as CSV, NetCDF, and JSON.
+While this enables users to import data into the system; it also introduces adding additional complexity to the system.
 
-The timeseries data is \hl{one of scalar, vector, or grid data, and all of different types are uniformly stored} as binary objects in a time series table inside the \acrshort{fews}.
-Functional compenents or any integrated models do not have direct access to the timeseries table which mentioned above, and those should use the data access module to access the data \cite{Werner2013TheSystem}.
-As explained in the system interpretation, all data access requests need to go through the data access module increasing the cost of data access.
-Because it stores different data types as binary objects, there is a penalty to convert data into binary objects and vice versa.
-\hl{Storing all the data in a timeseries table causing all the requests to come into a single data model in a database.
-Even it gives the advantage of accessing all the data in one place.} Further the performance goes down due to the need to scream high volume of data.% cause a heavy load on the system, causing to slow down in the performance of trying to use the system on a large set of data.
+The timeseries data is one of scalar, vector, or grid data type.
+And different types of data stored as binary objects in a timeseries table inside the \acrshort{fews} system.
+Functional components or any integrated models do not have direct access to the timeseries table, and those should use the data access module to access the data \cite{Werner2013TheSystem}.
+As explained in the system interpretation, all data access requests need to go through the data access module cause to increase the cost of data access.
+Because the \acrshort{fews} stores different data types as binary objects, there is a penalty for converting data into binary objects and vice versa.
+Since all timeseries data is stored within a single data source, it allows the system to handle data without much system complexity.
+However, a single data source becomes a bottleneck when it is required to fulfill all the timeseries data requirements.
+Further, the performance goes down due to the need to scream Spatio-temporal weather data.
 
-Given the above drawback on storing the data in the system, the \acrshort{fews} data model store the timeseries by \hl{uniquely identifying based on the location, data type, and source of the data} \cite{Werner2013TheSystem}.
-This allows indexing the database using above key fields \hl{and stores the data separately}, to take advantage of \hl{putting multiple data resources into the system}.
-As an example, instead of storing the data at a single timeseries table, it is possible to separate and index the database based on the source such as an external source of data or hydrological model of which the timeseries is a result.
-Or separate by data type and store in multiple storages give the capability for the system to scale with a factor of identical types that can be identified.
-Example of separation by data types of scalar, vector and gridded will increase the scaling factor by 3x.
+Given the above drawback on storing the data in the system, the Delft-FEWS data model uses a set of primary attributes from weather data to identify a timeseries uniquely.
+Those primary attributes are location, data type, and source of the data \cite{Werner2013TheSystem}.
+The primary attributes are always required, and there are some secondary attributes to add timeseries metadata further.
+Also, primary attributes used to index data for making data queries faster.
+Moreover, Delft-FEWS is able to create separate indexes for each attribute while storing large amounts of data.
+As an example, the system can separate timeseries data into multiple databases based on the source of timeseries, such as an external source of data or a hydrological model, which creates the timeseries and then index each database on other attributes.
+Alternatively, separate timeseries by data type and stored in multiple storages give the capability for the system to scale with a factor of identical types.
+An example of separation by data types of scalar, vector, and gridded will increase the scaling factor by 3x.
 
-Data processing and manipulation \hl{is} a required process in weather forecasting. 
-The data integrated from external sources are not in the appropriate temporal and spatial format that can directly feed as an input to a forecasting model or use in other application.
-Therefore, generic data processing steps are required for most models in a forecasting environment.
+Data preprocessing and manipulation are necessary processes in weather forecasting.
+The data integrated from external sources are not in the appropriate temporal and spatial format that can directly feed as an input to forecasting models or use in other applications.
+Therefore, the forecasting environment provides generic data processing steps to convert data into model compatible formats.
 Such examples are serial and spatial interpolation, data validation, aggregation and disaggregation, and data fusion \cite{Werner2013TheSystem}.
-This a vital feature in a forecasting system, and affect the quality and accuracy of the predicted data outputs.
-Because of the common data model concept in \acrshort{fews}, data processing via these functions is much effective.
-The system is \hl{self-provided some of the generic functions for data processing}, but required algorithms can be implement as a new Java class via \hl{communicate} with the \acrfull{api}.
-%It is obvious that
-For additional feature integration, users should implement the new functional extensions using Java.
-%Users do not have the flexibility to development with some other languages they are familiar with or use the support from another language.
-As an example, Python language is easy to use for beginners and many data scientists are using this programming language for development and it has many data available libraries for data processing.
-However, in \acrshort{fews}, users cannot take advantage of such existing tools.
-\dbc{I removed part of where you are trying to say support for Python is good.
-Rather than pointing out such minor issues (these are special purpose software), in Chap 3 and 5 you can highlight that by using microservices models/functions can be developed by any language of choice.}
+This is a vital feature in a forecasting system and affects the quality and accuracy of the predicted data outputs.
+Because of the common data model concept in the Delft-FEWS, data processing via these functions are much useful.
+The system contains a set of default data processing functions, but required algorithms can implement as a new Java class integrated with the \acrfull{api} provided by the Delft-FEWS.
+The Delft-FEWS has language dependency while additional features integration since users need to implement the new functional extensions using Java.
 
@@
 
-\acrshort{fews} provides data processing and modeling library to access scalar and grid timeseries the same way.
-However, \hl{the communicates with the database} only via the data access layer as shown in \cref{fi:fews_data_layer} \cite{Werner2013TheSystem}.
-As %it is shown in the figure, it is clearly showing that
-shown in figure, the system depends on a single database and \hl{via} the data access layer, all the requests are coming to the database through a connection.
+Delft-FEWS provides data processing and modeling libraries to access scalar and grid timeseries using the same method.
+However, the database access only allows through the data access layer, as shown in \cref{fi:fews_data_layer} \cite{Werner2013TheSystem}.
+The system depends on a single database instance, and all the requests are coming to the database through the data access layer.
 It is possible to setup and connect to an enterprise-level database with clustering and shading as a paid solution to enhance the throughput.
-%serve many requests as possible.
-However, the design itself inherently suffers from the database bottleneck which \hl{effected} by running a large set of timeseries or models.
+Still, the design itself inherently suffers from a single database bottleneck when accessing a large set of timeseries by the models.
 
@@
 \end{figure}
-One of the simple and most effective features in the \acrshort{fews} is an open approach to the integration of models and data.
-The concept of the open modeling framework is used by the \acrshort{fews} which is proposed by open model integration \cite{Kokkonen2003InterfacingXML}.
-It simply gives the flexibility to allow operators to integrate more models as well as variations of the same model and come up with new integration flows as much as possible.
-The users need to mentioned the input timeseries via XML configurations, and \acrshort{fews} generates the input data as XML files.
-Then using an adapter \hl{developed for the model transforms the data into required format for the model as a preprocessing step}.
-Next, \acrshort{fews} executes the model which generates the output.
-In the post processing step, the results of the model is transformed to an XML file, which \hl{can import} into the data model as shown in \cref{fi:fews_general_adapter} \cite{Werner2013TheSystem}.
-%The process is simple and consistent throughout all the model integration.
-The model execute by the \acrshort{fews} or the model adapter which is causing tide coupling into the execution process in the system.
-Users do not have the flexibility to run the models with different configurations such as running with parallel execution.
-That may be overcome by triggering an external process at the execution time, but it introduces more difficulty for handling after model executed successfully, preceding to the next step in the process.
-\hl{This part of the system feature} is not focused on the \acrshort{wdias} and user has to come up with own flow or use existing scientific flow management system.
-Yet, it is a concept that needs to be discussed and understand properly to design a data integration and assimilation system.
-However, the \acrshort{wdias} is capable of integrating workflow mechanism with its extendable architecture.
 
-Data exchange with the model is mainly done via XML files.
-\hl{It is possible to happen}, these XML files become very large, which can lead to I/O bottlenecks and causing performance issues \cite{Werner2013TheSystem}.
-%This issue is discussed in previous paragraphs and
-The authors of the \acrshort{fews} \cite{Werner2013TheSystem} seem to have noticed and accepted this issue. % it here. 
-\hl{For overcoming this issue} they introduced file-based exchange of data.
-This includes the use of binary XML files, the streaming of files via memory and the use of \acrshort{netCDF} files.
-But far as for the users, it seems to be adding more complexity and context to get higher performance via the system.
+One of the simple and most useful features in the Delft-FEWS is the use of an open approach to integrate models and data.
+The concept of the open modeling framework is used by the Delft-FEWS, which is proposed by open model integration \cite{Kokkonen2003InterfacingXML}.
+It merely gives the flexibility to allow operators to integrate more models as well as variations of the same model and come up with new forecasting flows as much as possible.
 
-The \acrshort{fews} provides a list of adapter available.
-If an adapter is not available for a given model, the user has to implement the adapter for the model and \acrshort{fews} has the flexibility creating a new adapter.
-But the effort that required to develop an adapter for a model will vary depending on the complexity of the model required data formats \cite{Werner2013TheSystem}.
-If the users want to use an existing adapter and need to configure something not supported via the existing adapter, it is hard to get done.
-Also, there are some cases it is hard to develop an adapter or running alongside the \acrshort{fews}.
-For example, the FLO2D model used for hydrologic modeling only runs on Windows.\hl{ If you setup the system on Linux based operating system and using Linux based models, it is hard for users to come up with a solution for integrating} the FLO2D models.
-The \acrshort{fews} support creating workflow process and allow users to run multiple models parallel or run those sequentially as needed, but the scope of the \acrshort{wdias} is not focused on adding such a feature in the system, rather user has to use a scientific workflow management system or come up with own version of workflow.
+The users need to configure the input timeseries data via XML configurations, and Delft-FEWS generates the model input data as XML files.
+As shown in \cref{fi:fews_general_adapter}, a model adapter transforms the data into the required format for the model as a preprocessing step.
+The Delft-FEWS has prebuilt a set of model adapters, and users can use available model adapters.
+Next, the Delft-FEWS executes the external model, which generates the model output, and allows users to run multiple models parallel or run those sequentially as needed.
+In the post-processing step, the results of the model transform into an XML file, which imports into the database through the data access layer, as shown in \cref{fi:fews_general_adapter} \cite{Werner2013TheSystem}.
+The general adapter used by the Delft-FEWS for the model execution is causing tide coupling into the execution process in the system.
+Users do not have the flexibility to run the models with different configurations, such as parallel execution of a particular model.
+Those issues may be overcome by triggering an external process at the execution time.
+But, it introduces more difficulty in handling the next step in the forecasting flow, after the successful execution of the model.
+
+In this research, we do not focus on implementing workflow management, and the user has to come up with their flow mechanism or use an existing scientific flow management system.
+However, it is a concept that needs to be discussed and understood properly to design a data integration and assimilation system.
+However, the proposed architecture within the research should be capable of integrating workflow mechanisms with its extendable architecture.
+
+The Delft-FEWS exchanges data with the models using XML files.
+Thus, it causes XML files to become very large when trying to access a large set of data, which can lead to I/O bottlenecks and causing performance problems \cite{Werner2013TheSystem}.
+The authors of the Delft-FEWS \cite{Werner2013TheSystem} seem to have noticed and accepted this problem.
+To overcome the issue mentioned above, they have introduced a file-based exchange of data.
+The proposed solution includes the use of binary XML files, the streaming of files via memory, and the use of netCDF files.
+Nevertheless, as far as for the users, it seems to be adding more complexity and context to get higher performance via the system.
+
+If the user is unable to find a model adapter among available Delft-FEWS adapters, then the user has to implement the adapter for the model.
+The user has the flexibility to create a new adapter within Delft-FEWS, but the effort required to develop an adapter for a model will vary depending on the complexity of the data formats required by the model \cite{Werner2013TheSystem}.
+If the users want to use an existing adapter and need to configure something not supported via the existing adapter, it is difficult without technical support since source code is not available.
+Also, there are some cases it is hard to develop an adapter or running alongside the Delft-FEWS.
+For example, the FLO2D model used for hydrologic modeling only runs on the Windows platform.
+If the user sets up the Delft-FEWS on a Linux platform and uses Linux based model adapters, it is hard for users to develop a solution for integrating the FLO2D model.

### 2020-04-24 lit/sec_2-lead.tex
Updated Lit: LEAD

@@
 \acrfull{lead} \cite{Droegemeier2005Service-OrientedWeather} addresses the fundamental research challenges needed to create an integrated and scalable framework for adaptive analysis and prediction of the atmosphere.
-To predict and analyze weather models by researchers, \hl{it required} many resources.
-Rather than each researcher is running and handling their computer resources to do the weather experiments, \acrshort{lead} is providing pool of resources, then the researchers can use this resource a pool to run their experiment in shorter amounts of time and higher scale.
-\hl{At the time, researchers are developing their experiment flow, they are not using the resources many, and others are using it at the same time.} The foundation of \acrshort{lead} system is to create a dynamic workflow orchestration and data management in a Web services framework \cite{Droegemeier2005Service-OrientedWeather}.
+The weather forecasting researchers require many computer resources to predict and analyze weather models in the mesoscale with less time.
+Rather than each researcher run and handle their computer resources for the weather experiments, LEAD provides a shared pool of resources.
+Then the researchers can use the resource pool to run their experiment in shorter amounts of time and a more massive scale.
+At the time, some researchers are developing their experiment forecasting flows, they are not using the resources, and other researchers can run their forecasting flows using available resources.
+The foundation of the LEAD system is to create a dynamic workflow orchestration and data management in a Web services framework \cite{Droegemeier2005Service-OrientedWeather}.
 
-LEAD's complex range of services, applications, interfaces and IT resources, local and external networks and storage is compiled by users in workflows to study mesoscale incremental manner \cite{Droegemeier2005Service-OrientedWeather}.
-As it follows the \acrshort{soa}, everything is implemented as independent services.
-This enables \acrshort{lead} to scale each service as required and update each service without affecting other services.
-New models that are required for implementing a new forecast flow also has to be implemented as a service and then integrate into the system.
+LEAD's complex range of services, applications, interfaces, and IT resources, local and external networks, and storage is compiled by users in workflows to study mesoscale incremental manner \cite{Droegemeier2005Service-OrientedWeather}.
+As it follows the SOA, all the features are implemented as independent services.
+The above implementation enables LEAD to scale up each service as required and update each service without affecting other services.
+New models that are required for implementing a new forecast flow also have to be implemented as a service and then integrate into the system.
 
-\cref{fi:lead_system} shows the key capabilities of the \acrshort{lead} system.
-\hl{From the high-level view}, \acrshort{lead} enables users to search and acquire information, simulate and predict weather conditions using digital atmospheric models, assimilate, analyze, use and visualize data and output of models.
+\cref{fi:lead_system} shows the key capabilities of the LEAD system.
+The top layer of the LEAD enables users to search and acquire information, simulate and predict weather conditions using digital atmospheric models, assimilate, analyze, use and visualize data and output of models.
 
@@
 
-The second level contains basic tools such as the following to help to link services together  \cite{Droegemeier2005Service-OrientedWeather}:
+The second layer contains fundamental tools such as the following to help to link services together \cite{Droegemeier2005Service-OrientedWeather}:
 \begin{itemize}
-    \item the users interact with \acrshort{lead} via a Web portal
-    \item data quality control and assimilation happends via ARPS Data Assimilation System (ADAS)
+    \item the users interact with LEAD via a Web portal
+    \item data quality control and assimilation happens via ARPS Data Assimilation System (ADAS)
     \item myLEAD is the metadata catalog
-    \item \acrfull{wrf} \cite{MesoscaleMicroscaleMeteorologyLaboratoryWeatherModel}
-    \item Algorithm Development and Mining is a set of tools for analyze observational data, assimilated data sets, and model output 
+    \item Weather Research and Forecast \acrfull{wrf} \cite{MesoscaleMicroscaleMeteorologyLaboratoryWeatherModel}
+    \item Algorithm Development and Mining is a set of tools for analyzing observational data, assimilated data sets, and model output
     \item Integrated Data Viewer 
@@
 
-The concept of the \acrshort{lead} \hl{is a workflow orchestration for on-demand, real-time and dynamically adaptive systems called WOORDS.} The system is doing the workflow orchestration as given in each procedure.
-Those procedural rules are defined by the researcher and feed into the system.
-The system is trying to act immediately after the submission, and also it transmits the data, run the models and send back the put with a lower time delay as possible.
-\hl{According to the load and other requirements, the system will respond to those requirements automatically.}
+The LEAD follows a concept of the workflow orchestration for on-demand, real-time, and dynamically adaptive systems called WOORDS.
+The system is doing the workflow orchestration as given in each procedure.
+The forecast researchers define the procedural rules and feed them into the system.
+The system is trying to act immediately after the submission, and also it transmits the data, runs the models, and sends back the put with a lower time delay as possible.
+Based on the system load and priority of the workflow, the system will schedule the workflows automatically.
 
@@
 \begin{itemize}
-    \item User subsystem -- comprises the LEAD portal and enable user can access services
-    \item Data subsystem -- manages data and metadata, all output of digital models produced by operational or experimental models, and information generated by users.
-    \item Tools subsystem -- provides all IT toles and  meteorological tools
-    \item Orchestration subsystem -- offers the technologies with which users can manage data flows and model execution flows and can create and own output.
+    \item User subsystem – comprises the LEAD portal and enable user can access services
+    \item Data subsystem – manages data and metadata, all output of digital models produced by operational or experimental models, and information generated by users.
+    \item Tools subsystem – provides all IT tools and meteorological tools
+    \item Orchestration subsystem – offers the technologies with which users can manage data flows and model execution flows and can create and own output.
 It also provides links to other software and processes for continuous or on-demand applications.
@@
 
-%\acrshort{soa}s are widely used in the commercial enterprise sector and form the basis of many scientific "grid" technologies in lead design and development.
-A variant of \acrshort{soa} was developed later, called microservices architecture, and is now widely used in industry nowadays.
-
 As shown in \cref{fi:lead_soa}, \acrshort{lead} \acrshort{soa} has five different but highly interconnected layers.
@@
 The next level supports web services that provide access to raw services \cite{Droegemeier2005Service-OrientedWeather}.
-These two layers are working together since \acrshort{lead} system resources are distributed over multiple locations and creating a pool of resources.
-The upper layer to the raw resources is abstracting the complexity of managing and accessing the resources, and provide simplified access to the upper layer.
-In the Upper layers, its view as an unlimited resource pool for storing and handling data.
+These two layers are working together since LEAD system resources are distributed over multiple locations and creating a pool of resources.
+The upper layer of the raw resources is abstracting the complexity of managing and accessing the resources and provides simplified access.
+In the Upper layers, the underline system is viewed as an unlimited resource pool for storing and handling data.
 
@@
 Most of the services listed below are required for creating workflows for weather data forecasting.
-\hl{Thus it} is important to review them and understand the basic needs of a weather data management system.
+While analyzing the LEAD, we realized that it is essential to understand the following basic needs of a weather data management system.
 
 \begin{itemize}
-\item The application-oriented configuration service that manages the implementation and execution of real applications, such as the \acrshort{wrf} simulation model, ADAS and ADaM tools \cite{Droegemeier2005Service-OrientedWeather}.
-When creating weather workflow, it is required to change the behavior of the model by changing some of the configurations of the model or run a different version of the model.
-\item The application resource broker, which matches the appropriate host for execution to each application task, based on the execution’s time constraints \cite{Droegemeier2005Service-OrientedWeather}.
-This service is a critical part of the system, and responsible for using the resources of the system in an optimized manner.
-When designing the weather data system, it is required to increase the capacity of the system automatically, and adopt it into the system.
-\item The workflow engine service, which manages the experimental workflow instances, invokes both the configuration service and the application resource broker \cite{Droegemeier2005Service-OrientedWeather}.
-This is a part of workflow orchestration.
-\item Catalog services represent how a user or application service discovers data products in the public domain or \acrshort{lead} services \cite{Droegemeier2005Service-OrientedWeather}.
-This is an important feature that should be available in a weather data system, and users need to search for the availability of the data.
-\hl{Further wants to analyze} existing data for decision making.
+    \item The application-oriented configuration service manages the implementation and execution of real applications, such as the WRF simulation model, ADAS, and ADaM tools [5].
+While creating weather forecast workflows, the researchers require to change the behavior of the model by changing some of the configurations of the model or run a different version of the model.
+    \item The application resource broker, which matches the appropriate host for execution to each application task, based on the execution time constraints [5].
+This service is a critical part of the LEAD system and responsible for using the resource pool in an optimized manner.
+One important fact is, while we are designing weather data systems, it is required to increase the capacity of the system automatically, and manage the system.
+    \item The workflow engine service, which manages the experimental workflow instances, invokes both the configuration service and the application resource broker [5].
+The above service is a part of workflow orchestration.
+    \item Catalog services represent how a user or an application service discovers data products in the public domain or LEAD services [5].
+Most systems need a catalog service and essential to have such features because users need to search for the availability of the data, and users want to analyze existing data for decision making.
     \item Users need a multitude of data services to support comprehensive query, access, and transformation operations on data products.
-An important goal behind LEAD is transparency of access that facilitates user requests on all available heterogeneous data sources without the negative effects of different formats and naming schemes \cite{Droegemeier2005Service-OrientedWeather}.
+An essential goal behind LEAD is the transparency of access that facilitates user requests on all available heterogeneous data sources without the negative effects of different formats and naming schemes [5].
 Users need to have transformation services to read data in different formats.
@@
 
-Top of \cref{fi:lead_soa} shows the user interface of the \acrshort{lead} which \hl{gives individual services access.} When the user logs into the system, based on the authentication and authorization setting of the account, the portlets can access the services on behalf of the user.
-%Look into further details is not relevant to developing the \acrshort{wdias} since the focus is not on workflow orchestration.
+The top of \cref{fi:lead_soa} shows the user interface of the LEAD, and each user gets individual access to services via the interface.
+After the user login into the system, the LEAD system allows portlets to access the services on half of the users based on the authentication and authorization setting of the account.
 
-\acrshort{lead} is a more advanced system which can support mesoscale weather prediction with the effort of multiple universities in the United State America with the effort of many researchers and using many computer resources.
-At the time it was building, it uses the \acrshort{soa} architecture as into its depth, and with the implementation, each service can scale as needed and possible to enhance the service without interrupting other services.
-\acrshort{wdias} only focuses on creating a framework that is extendable as system needs more features similar to \acrshort{lead} services.
+LEAD is a more advanced system which can support mesoscale weather prediction with the effort of multiple universities in the United State America with the effort of many researchers and using many computer resources.
+At the time of  building, it uses the \acrshort{soa} architecture into its depth, and at the implementation, each service can scale as needed and possible to enhance the service without interrupting other services.
+However, during our research, we only focus on creating a framework that is extendable as a system needs more features similar to LEAD services.

### 2020-04-24 lit/sec_3-other-systems.tex
Update Lit review

@@
 
-\acrfull{dias} \cite{Kawasaki2018DataReduction} collects and archives data from satellites, weather stations, numerical forecasting models and climate projection models.
-Once this data is integrated into geographic useful information, DIAS generates results for managing global environmental problems and natural disasters \cite{Kawasaki2018DataReduction}.
-\acrshort{dias} has the \hl{capability of collecting} weather data from multiple data sources which are inherently in different formats.
-\hl{After successfully ingest} the data, it generates results which can use for different kind of purposes.
+\acrfull{dias} \cite{Kawasaki2018DataReduction} collects and archives data from satellites, weather stations, numerical forecasting models, and climate projection models.
+Once these data integrate into useful geographic information, DIAS generates results for managing global environmental problems and natural disasters \cite{Kawasaki2018DataReduction}.
+The DIAS can assimilate weather data from multiple data sources with different data formats.
+After successfully storing the data, it generates results which can be used for different kinds of purposes by other parties.
 
@@
 
-\hl{The mechanism of storing data in \acrshort{dias}, similar to the other systems discussed.}
-These data sets are \hl{stored in a larger array system with API software} that is used to import the data.
-APIs work to convert or reformat data into manageable forms and are useful for creating the DIAS storage archive.
-The API software contains various tools, including the real-time data exploration and archiving system, the data download system, the quality control system and the metadata management system \cite{Kawasaki2018DataReduction}.
+The data storing mechanism is similar to the other systems discussed above.
+The DIAS provides an API to import the data and store them in a large array of storage after converting to the required data format.
+The APIs work to convert or reformat data into manageable forms and are useful for creating the DIAS storage archive.
+The DIAS's API contains various tools, including the real-time data exploration and archiving system, the data download system, the quality control system, and the metadata management system \cite{Kawasaki2018DataReduction}.
 To store on the large volume of disk space, it converts the data via a provided set of APIs.
-This can be considered the same as the open data model provided by the \acrshort{fews}.
-Other than that, \acrshort{dias} consist of additional tools that provide the functionality of quality control of the data, and metadata management which is similar to some of the services in \acrshort{lead}.
+The above concept is similar to Delft-FEWs open data model approach.
+Further, the DIAS contains additional tools that provide the functionality of quality control of the data and metadata management, which is similar to some of the services in LEAD.
 
-As shown in \cref{fi:dias_common_platform}, it offers an application layer that allows scientists %in the field 
-to work on research tasks and to develop specific tools and applications by collaborating with IT experts \cite{Kawasaki2018DataReduction}.
-Once the data is achieved on the \acrshort{dias} system, it shares those details via the Shared API layer.
-\hl{Thus it} allows users to remote access to the data, and easy integration via the APIs.
+As shown in \cref{fi:dias_common_platform}, it offers an application layer that allows scientists to work on research tasks and to develop specific tools and applications by collaborating with IT experts \cite{Kawasaki2018DataReduction}.
+Once the data is stored on the DIAS system, it shares those data via the Shared API layer and allows users to remote access to the data and easy integration via the APIs.
 
@@
 \label{se:madis}
+
 \acrfull{madis} \cite{Macdermaid2005ArchitectureP2.39} is a data integration and assimilation system that collects data from dozens of suppliers, then checks the quality of the data and saves it in \acrshort{netCDF} format.
-Give users later access to data through support for different types of protocols.
+Later, users can access the data with the support of the different types of data access protocols.
 
@@
 
-\acrshort{madis} contains a distributed architecture for data acquisition, processing and distribution functions.
-In addition, \hl{the paper mentioned architectural advancement at that time,} the various functional hosts have been paired using Linux High Availability (HA) to provide automated failover in the event of a system failure.
-It uses several methods for data dissemination such as FTP, Local Data Manager (LDM) and the Web OPeNDAP (OPen source project for Network Data Access Protocol) \cite{Macdermaid2005ArchitectureP2.39}.
-%As mentioned above, the \acrshort{madis} is implemented based on a distributed architecture that is available at the time of its development.
-Even it is not mentioned, it is
-It users functional calls like Remote Procedure Call (RPC) to invoke among a cluster of nodes.
-In \cref{fi:madis_flow}, data is transported from the input and preprocessing systems to the central computer systems and then to other hosts for storage and distribution \cite{Macdermaid2005ArchitectureP2.39}.
-To get high availability, it has added some updates to its architecture as mentioned in the paper.
-The conclusion of this statement is, these kinds of functionalities are available at the modern the Cloud Computing tools, and out of the box, those tools are providing the scalability and high availability.
-Using those tools, it possible to implement such a system with less effort and high confidence.
+MADIS contains a distributed architecture for data acquisition, processing, and distribution functions.
+Besides, the MADIS was developed based on the distributed architectural patterns available at the time of implementation.
+The various functional hosts have been paired using Linux High Availability (HA) to provide automated failover in the event of a system failure.
+It uses several methods for data dissemination such as FTP, Local Data Manager (LDM), and the Web OPeNDAP (OPen source project for Network Data Access Protocol) \cite{Macdermaid2005ArchitectureP2.39}.
+It uses functional calls like Remote Procedure Call (RPC) to invoke among the cluster of nodes.
+In \cref{fi:madis_flow}, the data is transported from the input and preprocessing systems to the central computer systems and then to other hosts for storage and distribution \cite{Macdermaid2005ArchitectureP2.39}.
+To get high availability, it has added some updates to its architecture, as mentioned in the paper.
 
-MADIS regularly acquires Mesonet data from dozens of network providers representing more than 14,000 stations.
-This translates into more than 30,000 station reports every hour.
+Based on the above statements, we can conclude that these kinds of functionalities are available at the modern Cloud Computing tools, and out of the box, those tools are providing the scalability and high availability.
+Using those tools, it is possible to implement such a system with less effort and high confidence.
+
+The MADIS regularly acquires Mesonet data from dozens of network providers representing more than 14,000 stations, and the system translates into more than 30,000 station reports every hour.
 Different systems that work inside and outside the firewall collect the data.
-This data is sent to the data server of the Advanced Weather-Interactive Processing System (AWIPS) of the central installation for processing and conversion to a common format, NetCDF.
-NetCDF files are then transferred to MADIS compute nodes \cite{Macdermaid2005ArchitectureP2.39}.
-%This provides an overview of the level of data that \acrshort{madis} handling.
-This could be a good reference for implementing \acrshort{wdias} and its performance testing. As same as \acrshort{fews}, it is also \hl{converting} the data into %a common format which is 
-\acrshort{netCDF}. Those files are transferred to the compute nodes and accessible via OPeNDAP. 
-%MADIS computer platforms include Intel-based servers with the Red Hat Enterprise Linux operating system. 
-Many of these computers are configured using Linux clustering with high availability \cite{Macdermaid2005ArchitectureP2.39}.% As indicated above, the system heavily depends on the platform.
-There are some costs involving purchasing their licenses.
+The collected data is sent to the data server of the Advanced Weather-Interactive Processing System (AWIPS) of the central installation for processing and conversion to a common data format, NetCDF.
+The NetCDF files are then transferred to MADIS compute nodes \cite{Macdermaid2005ArchitectureP2.39}.
+After reading the statistics of the MADIS system, I realized the paper is a useful reference for system architecture design and its performance testing.
+When compared to the Delft-FEWS, the MADIS also converts the assimilated data into netCDF format.
+After converting to netCDF format, the netCDF files are transferred to the compute nodes and accessible via OPeNDAP.
+Many of these computers are configured using Linux clustering with high availability \cite{Macdermaid2005ArchitectureP2.39}.
 
-As certain MADIS data is considered to be the property of the supplier, access to this data must be checked.
-To respond to this, MADIS data is divided into six different versions, depending on the access level authorized by the data provider \cite{Macdermaid2005ArchitectureP2.39}.
-When compared to \acrshort{fews}, \acrshort{madis} provides control-based access to the data.
+Some of the MADIS data is considered to be the property of the supplier, and data access should be provided based on the authorization.
+In order to address the issue, MADIS data is divided into six different versions, depending on the access level authorized by the data provider \cite{Macdermaid2005ArchitectureP2.39}.
+When compared to Delft-FEWS, MADIS provides control-based access to the data.
 
@@
 \label{se:lit_summary}
-We presented several related work on WDIA system implementations such as \acrshort{fews}, \acrshort{lead}, \acrshort{dias}, and \acrshort{madis}.
-In this research one of major issue that we focused on is storing data ingested from different sources with different formats efficiently.
-The \acrshort{fews} and \acrshort{madis} are using the \acrshort{netCDF} as the common data format to store the data which is one of the best solutions available with modern technologies as well.
-Even it is not mentioned, the \acrshort{dias} and \acrshort{lead} also following a method of having common storage space to store bulk data.
-\acrshort{fews} and \acrshort{lead} have the capability of handling the workflow of forecasting, but other systems are mainly focused on providing a weather data management system.
-\acrshort{fews} provides a modular approach via its general adapter, and according to the \acrshort{soa} architecture of \acrshort{lead} provides the same functionality via services.
 
-Most of the \hl{above systems developed} by many researchers, and were developed specifically to address issues like natural disasters.
-To address use cases such as CUrW, \hl{it required} to remodel the systems  and define the forecasting flows.
-Even some of the systems try to follow a generic approach to integrate new modules, it is challenging to deploy modules for a closed source or proprietary software.
-Further, most of them \hl{are depend} on the underline platform, and does not support more resource efficient and highly-scalable technologies such as cloud computing.
+We presented several related works on WDIA system implementations such as \acrshort{fews}, \acrshort{lead}, \acrshort{dias}, and \acrshort{madis}.
+During our research, one of the significant issues that we focused on, store the data ingested from different sources with different formats efficiently.
+The Delft-FEWS and MADIS are using the netCDF as the common data format to store the data, which is one of the best solutions available with modern technologies as well.
+Even the LEAD and DIAS papers are not mentioned directly; those systems are also following a method of having common storage space to store bulk data.
+The Delft-FEWS and LEAD have the capability of handling the workflow of forecasting, but other systems are mainly focused on providing a weather data management system.
+The Delft-FEWS provides a modular approach via its general adapter, and according to the \acrshort{soa} architecture of LEAD provides the same functionality via services.
+
+Above WDIA systems are developed with the contributions from lots of researchers, and were implemented specifically to address issues like natural disasters.
+A use case such as CUrW, a given WDIA system requires to remodel the systems and define the forecasting flows to support the country-specific requirements.
+Even some of the systems try to follow a generic approach to integrate new modules, but it is challenging to deploy modules for a closed source or proprietary software.
+Further, most of the systems depend on the underline software platform and do not support more resource-efficient and highly-scalable technologies such as cloud computing.

### 2020-04-25 results/sec_0-introduction.tex
Up to results->workload

@@
 
-This chapter includes the performance study of the \acrshort{wdias}. \cref{se:test_plan} describes the planned method of testing the system.
-In the next \cref{se:workload} describes the logic behind creating the workload to do the performance testing planned in \cref{se:test_plan}.
-\cref{se:observations} includes the results observed while performance study. And summarised the observations in the next \cref{se:discussion}.
+This chapter includes the performance study of the \acrshort{wdias}. \cref{se:test_plan} describes the test plans for the performance testing.
+\cref{se:workload} describes the logic behind creating the workload to do the performance testing planned in \cref{se:test_plan}.
+\cref{se:observations} includes the results observed during performance study and summarised the observations in \cref{se:discussion}.

### 2020-04-25 results/sec_1-test_plan.tex
WDIAS_Thesis_v3.2
Up to results->workload

--- 2020-02-16 results/sec_1-test_plan.tex
@@
 
-In \cref{subse:modules_weather_data_integration_sys} \hl{we discussed three modules of a weather data system such as integration, assimilation, and dissemination.
-Each of those modules is mapped and handled in the WDIAS as below.}
+In \cref{subse:modules_weather_data_integration_sys} we discussed three modules of weather data integration and assimilation systems such as integration, assimilation, and dissemination.
+We can map each of those modules to WDIAS modules, which provide the same functionalities as below.
 \begin{enumerate}
-    \item \emph{Import} modules (integration modules)
-    \item \emph{Export} modules (Dissemination modules)
-    \item \emph{Extension} modules (Assimilation modules)
+    \item \emph{Import} modules - Integration modules
+    \item \emph{Export} modules - Dissemination modules
+    \item \emph{Extension} modules - Assimilation modules
 \end{enumerate}
-Other than above, \emph{adapter modules} act as the core modules and the base of the system.
-Also, query modules allow the users to query for the timeseries based on the metadata and enable performing Geo-based queries based on the locations.
 
-The test plan is to perform the load test on each above module as a separate entity to analyze the individual module scalability.
-Then perform load testing on the whole system, and analyze the scalability in the system. Two variables can vary while doing performance testing.
+Other than the above modules, \emph{adapter modules} act as the core modules and the base of the system.
+Also, the \emph{query module} allows the users to query for the timeseries based on the metadata and perform Geo-based queries based on the locations.
+
+The test plan is to perform load testing on the whole system and analyze the scalability of the system while measuring the operations performed on each module.
+Two variables can vary while doing performance testing.
 \begin{enumerate}
-    \item Number of requests made to the system at a given time (\acrfull{rps})
+    \item Number of requests made to the system at a given time (Requests Per Second (RPS))
     \item Request size
 \end{enumerate}
-A timeseries is a series of data points in time order. The system may receive the data points in multiple requests.
-The request size can vary based on the use case from one data point to multiple data points. As few examples;
+
+A timeseries is a series of data points in time order.
+The system may receive the data points of a timeseries in multiple requests.
+The request size can vary based on the use case from one data point to multiple data points.
+For example;
 \begin{itemize}
-    \item A weather station may send the current water level in a regular period of 1 minute. In such a case, it always comes as a request with one data point with higher frequency.
-    \item Due to resource issue such as batteries, a weather station can collect data points for a given period and send as a batch. Another example would be,
-A weather station can collect the precipitation at each 5 minute period and send all the data in 1-hour intervals.
-    \item The forecast precipitation data from the \acrshort{wrf} model can be extracted for a day in a one-hour interval and store in the system.
+    \item A weather station may send the current water level in a regular period of 1 minute. In such a case, it always comes as a request with one data point with a higher frequency.
+    \item Due to resource issues such as batteries, a weather station can collect data points for a given period and send as a batch.
+An example scenario would be, a weather station can collect the precipitation at each 5 minute period and send all the data after collecting for one hour.
+    \item The forecast precipitation data from the \acrshort{wrf} model extract for a few days in hourly intervals and store them.
 \end{itemize}
 
-The percentage of each data type can be varied depending on the situation.
-But most of the applications collect much data from the weather stations to correct and validate the models' data.
-These weather stations can send the data in different frequencies with different parameters such as precipitation, temperature, humidity, wind direction, etc.
-Most of these are scalar data.
-Parameters such as wind direct are vector data which has less percentage compared to scalar data.
-On the other side, most of the grid data generate from models and simulations.
-Those produce in less frequency due to the cost of the computer resource to produce results.
-After considering those factor we came up with 70\% scalar, 20\% vector, and 10\% grid values.
-%\begin{itemize}
-%    \item Scalar - 70\%
-%    \item Vector - 20\%
-%    \item Grid - 10\%
-%\end{itemize}
-
+The percentage of number of requests per each data type that comes to the system at a given time can be varied depending on the situation.
+The Majority of weather data requests come from weather stations and other observation tools.
+Then we need to validate and modify those timesereis data and store them as new timeseries that can directly feed into the NWMs..
+These weather stations can send the weather data at different frequencies with different parameters such as precipitation, temperature, humidity, and wind direction.
+Most of the timeseries mentioned above are scalar timeseries.
+When compared to scalar data, parameters such as wind direction are vector timeseries with a lesser percentage of requests.
+On the other hand, most of the grid type data was generated as results of NWMs.
+But those grid data produce in less frequency due to the cost of the computer resource to produce results.
+After considering those factors, we came up with 70\% scalar, 20\% vector, and 10\% grid percentage values at the expected requests rate ratios.
 As an upper limit of such scenarios while designing the performance testing, it uses the following;
@@
     \item Every 30 minutes (48 data points)
-    \item Every 15 minutes (96 data points) - One request is equivalent to a data points send by a weather station in 15 minutes interval for a single day
+    \item Every 15 minutes (96 data points) - One request is equivalent to a set of data points sent by a weather station in 15 minutes interval for a single day
 \end{itemize}
@@
 
-\cref{fi:performance_study_load} shows the summary of this section, load testing plan with changing the request size and perform load testing with increasing the \acrshort{rps} over time.
-As shown in the figure, for a given request size the \acrshort{rps} increased in steps.
+\cref{fi:performance_study_load} shows the summary of the load testing plan with changing the request size and performing load testing with increasing the \acrshort{rps} over time.
+As shown in the figure, for a given request size, the \acrshort{rps} increased in steps over the elapsed time.
 In each step, the \acrshort{rps} holds for a moment to give some time for the system to get stabilized.
-Thus at each milestone, we can measure the performance of the system and study the stability of the system.
-After it comes to the peak time, the \acrshort{rps} holds for more time than the previous milestones.
-During the \acrshort{wdias} load testing, we are planning to have a peak of 18,000 requests per minute.
-Holding the peak load will help to show whether the system is capable of scaling more than the proposed load testing plan.
-After the peak, the test case goes through a cool-down period to measure the ability to shrink down the resources when there is not any load on the system.
+Thus at each step, we can measure the performance of the system and study the stability of the system.
+After the test plan comes to the peak \acrshort{rps}, the system holds for more time than the previous steps.
+By holding the peak load for some time, we are planning to show the system is capable of scaling more than the proposed peak load in the testing plan.
+During the WDIAS load testing, we are planning to have a peak of 300 requests per second at peak time.
+After the peak \acrshort{rps} is over, the test case goes through a cool-down period to measure the ability to shrink down the system resources when there is not any load on the system.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{\hl{Test Scenarios}}
+\subsection{List of Test Plans}
 \label{subse:test_plan_flow}
@@
         \item Plan for 30 minutes of the test run with the request size of 15min data with auto-scaling.
-        \item All test plan run against 60min, 30min and 15min request size of data. Another test plan runs with enabling the auto-scaling. (total of 2 hours)
+        % \item Test plan run against 60min, 30min and 15min request size of data. Another test plan runs with enabling the auto-scaling. (total of 2 hours)
     \end{itemize}
@@
         \item Query Timeseries
-        \item Plan for the 5 minutes of test run. (total 1/12 hours)
+        \item Plan for the 5 minutes of test run.
     \end{itemize}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Performance Metrics}% of Load Testing}
+\subsection{Performance Metrics}
 \label{subse:test_plan_metrics}
-During the performance analysis, the following metrics are used to measure the performance of the system.
+
+During the performance analysis, we used the following metrics to measure the performance of the system.
 \begin{itemize}
-    \item \emph{Throughput} -- Number of requests that can processed per unit time. Normally for \acrshort{wdias} performance observations, it uses \acrfull{rps} to measure the throughput.
-    \item \emph{Latency} -- Time is taken to respond to the sent request to the system.
-Normally it measures with milliseconds (ms) in the \acrshort{wdias}.
-During the performance analysis, it measures the minimum response time, maximum response time, the average response time, and standard deviation.
-The standard deviation measures the mean distance of the values to their average.It gives an idea of the dispersion or variability of the measures to their mean value.
-So, if the deviation value is low compared to the mean value, it will indicate that the measures are not dispersed (or mostly close to the mean value) and that the mean value is significant.
-Other than that, it measures the response time into 90\% percentile, while gives the best response time up to 90\% percent of the responses.
-    \item \emph{Resource utilization} -- Resource Utilization is calculated based on the CPU and Memory usage via the \acrshort{k8s} metrics server.
-It calculates the resource utilization over 60 seconds time window.
+    \item \emph{Throughput} -- Number of requests that can be processed per unit time. 
+    Normally for \acrshort{wdias} performance observations, it uses \acrfull{rps} to measure the throughput.
+    \item \emph{Latency} -- Taken time to respond to the request sent to the system. 
+    Normally we measure with milliseconds (ms) in the \acrshort{wdias}.
+During the performance analysis, we measure the minimum response time, maximum response time, the average response time, and standard deviation.
+The standard deviation measures the mean distance of the values to their average value.
+It gives an idea of the dispersion or variability of the measures to their mean value.
+So, if the deviation value is low compared to the mean value, it will indicate that the measures are not dispersed (or mostly close to the mean value), and the mean value is significant.
+Other than that, we measure the response time into 90\% percentile while giving the best response time up to 90\% percent of the responses.
+    \item \emph{Resource utilization} -- Resource Utilization is calculated based on the CPU and Memory usage via the K8s metrics server.
+It calculates the resource utilization over a 60 seconds time window.
 Network usage is getting based on the actual physical machines.
-    \item \emph{Auto-scaling} -- The \acrshort{wdias} is running with two configurations.
-First is, since it is running the microservice as docker containers, it allows to increase or shrink the resource usage and share the resources within a physical machine.
-Second is, running with auto-scaling enabled for the microservice which are using higher resources.
+    \item \emph{Auto-scaling} -- We performed the load testing with two system configurations.
+First, we ran the microservices with a fixed number of pods inside the K8s cluster.
+Then k8s are only allowed to vertically scale each microservice until a container hits the CPU and memory limits defined per container or overwhelm the physical node resources.
+Secondly, we ran the load testing with auto-scaling enabled only for microservices, which are using higher resources with the above system configurations.
+Auto-scaling spawns new copies of the same microservice when the microservice gets more load than the configured percentage, and shrink the running instances when there is a lesser load.
 \end{itemize}

### 2020-04-25 results/sec_2-workload.tex
Up to results->workload

--- 2020-02-16 results/sec_2-workload.tex
@@
 
-As explained in Chapter \ref{ch:method}, timeseries has six primary attributes. To create a timeseries for performance testing, it needs data for each key attribute.
-While generating the timeseries for performance testing, it selected locations all over the world as a generic case to include all the locations without binding to a specific area.
+As explained in the research methodology (\cref{ch:method}), we selected six primary attributes from the timeseries metadata while implementing the system architecture.
+Before storing the data in \acrshort{wdias}, we need to register timeseries metadata for the timeseries, and are required to provide values for the six attributes.
+During the test for location attribute, we selected the locations all over the world as a generic case to include all the locations without binding to a specific area.
 
-These locations are taken from Google's Countries Public Data set \cite{GoogleGoogleCounties}, and consider static though out the testing, and data added to the wdias-performance-test.
-During the performance test, it creates 1000 timeseries and keeps adding data against those timeseries.
-For each location, it creates four timeseries \hl{as a combination of four values of moduleId key attribute}.
-Thus combining all together, those create 1000 timeseries.
-But test cases generate these values before starts the performance tests, and able to increase the timeseries as wanted.
+We used 250 locations from Google’s Countries Public Data set \cite{GoogleGoogleCounties}, and considered static throughout the testing.
+For each location, we created four timeseries metadata by using four different values for the moduleId key attribute.
+Thus combining all together first, we created 1000 timeseries metadata during the performance test and then stored the timeseries data against timeseries unique identifiers.
+We have written automated scripts to generate these data for the performance testing, and scripts are generic enough to create more timeseries metadata by changing the configurations.
 
-For grid data, it uses static 100 grid locations based on how is \acrshort{api} exposed.
-Since grid locations have different metadata structures as described in \cref{se:db_struct}, those data handle separately.
-But the locationId of grid and scalar data types have the same effect when defining a timeseries.
+For storing grid data, we used static 100 grid locations.
+Since grid locations have different metadata structures, we had to generate metadata for them separately.
+However, the locationID of the grid timeseries metadata is similar to scalar timeseries metadata that have the same effect when defining timeseries metadata.
 
-In the \acrshort{jmeter} Best Practices, \say{If your test needs large amounts of data - particularly if it needs to be \emph{randomized} create the test data in a file that can be read with CSV Data set.
-This avoids wasting resources at run-time}.
-Rather providing the randomness in run time, the timeseries stored with the random order which satisfy the percentage of 70\% Scalar, 20\% Vector, and 10\% Grid as mentioned in \cref{se:test_plan}.
-Before running the test cases, it generates the metadata for timeseries and writes into a CSV file which is shared among the threads in the \acrshort{jmeter}.
-This occurs in the setup phase of the test cases.
-The metadata CSV file arrange in a way that within every 10 lines, 7 lines are Scalar timeseries, 2 lines are Vector timeseries, and 1 line is a Grid timeseries.
+We used the Apache JMeter for performing the load test since it is open source and supports distributed load testing.
+As mentioned in the JMeter Best Practices, "If your test needs large amounts of data - particularly if it needs to be \emph{randomized}, create the test data in a file that can be read with CSV Data set.
+This avoids wasting resources at run-time".
+While running the load test, JMeter iterates over the timeseries metadata CSV file and assigns a new thread to work on the test scenario with given timeseries metadata.
+Instead of providing the randomness at run time, we stored the timeseries metadata in random order that satisfies the percentage of 70\% scalar, 20\% vector, and 10\% grid, as mentioned in \cref{se:test_plan}.
+Before running the test cases, we generated the timeseries metadata in random order and wrote them into a CSV file during the setup phase.
+The metadata CSV file arranges in a way that, within every ten lines, seven lines are Scalar timeseries, two lines are Vector timeseries, and 1 line is a Grid timeseries.
 
-The system is capable of storing any numeric value up to 3 decimal points.
-It does not make any difference based on the parameter type whether it is the precipitation or the temperature.
-Thus during the performance testing, \acrshort{jmeter} uses real precipitation data from \acrshort{curw}.
-One month period of data for five weather stations has been using to prepare the test data.
-The script to clean up and prepare the precipitation data is available as \emph{setup\_precipitation.sh} in wdias-performance.
+\acrshort{wdias} is capable of storing any numeric value up to 3 decimal points as per the default configuration.
+Even the parameter type is either precipitation or temperature does not make any difference, because in storage perspective, it's a number.
+Thus, during the performance testing, we only use real precipitation data from \acrshort{curw}.
+So, we used data from five weather stations for a month while preparing the test data for scalar timeseries.
+We used a script to clean up and prepare the precipitation data, and it is available as setup precipitation in \acrshort{wdias} codebase.
 
@@
 \end{lstlisting}
-When preparing the data, it creates three sets of data based on the time interval such as hourly (60min), 30min, and 15min data with modifying the replicated data.
-This will reduce the overhead in performance testing and increase the performance itself.
-Extract function use while creating the containers, and extract the data into the container. This reduces the context loading while creating the container images.
-While performing the load testing, \acrshort{jmeter} keeps update a date counter and creates over the one-month data.
-At the end of the current month, the date counter advance to the next month.
-But data is repeated using from the beginning.
-To provide more randomness, it switches over five locations as well.
-The JSR223 scripts were written generically such that is possible to tweak and use if there are more location data available.
 
-Almost similar to how was the precipitation data proceed, the water level is prepared for Grid data.
-One exception with Grid data during these test cases was, the maximum time step is 30min, instead of 15min due to the larger size of the data.
-But the \acrshort{wdias} is capable of supporting such request.
-The main purpose of the \acrshort{wdias} is to provide an extensible architecture framework, during the performance testing it is not much considered about scaling the Grid data handling as it using \acrshort{netCDF}, and it is another domain with an attraction up to some extent.
+While preparing the data, we created three sets of timeseries based on the time interval, such as hourly (60min), 30min, and 15min data, with modifying the replicated data.
+The above method reduced the overhead of filtering data during performance testing.
+We also set up the JMeter as a containerized application, which allows us to run inside the k8s cluster.
+As an optimization for the JMeter container creation, we avoid adding extensive test timeseries data, which causes the container size to be large and making the build process slower.
+Rather than doing that, we used extract scripts while running the container and extract the data into the container.
+For each test plan, we used a date counter and increment the date after one full cycle of timeseries metadata CSV file is processed.
+When the date counter increases, it reads the real data for that day.
+After the date counter advances to the next month, we repeat reading data from the beginning of the month.
+To provide more randomness, we switch over five locations during the date increment.
+The JMeter reads the data via the JSR223 scripts, and we have written those scripts in a generalized style such that it is possible to tweak and use if there are more location data available.
+
+Similar to the scalar test data prepared, we prepared the test grid data using the real water-level output of the FLO2D 150 meter hydrology model that is used in the \acrshort{curw} The FLO2D timeseries are produced as ASCII Grid files, and each data point represents a grid file that consists of 120 rows and 139 columns.
+To represent missing cell values of the ASCII grid file, we used the \texttt{-9} instead of \texttt{-999} as an optimization.
+Even with that, each file size is around 50,337 Bytes (50 Kilobytes).
 
@@
 \end{lstlisting}
-The water level also contains the real data for one month of period and \emph{setup\_waterlevel.sh} script provides the functionality of preparation, cleanup, and extract.
-Also, it reset and repeat reading from the beginning when the \acrshort{jmeter} date counter keeps increasing.
+
+We also used the real water level data for one month period and developed a script to do the data preparation, cleanup, and extract.
+Similar to the scalar test scenario, the JMeter repeats reading from the beginning of test data when the date counter increments to the next month.
 
@@
 
-To create a higher workload using the \acrshort{jmeter}, it has a Distributed Testing feature.
-It uses the master-slave approach and it allowed to handle all the test cases via single instance, rather handling separate instances.
-But it has the following limitation of \emph{the same test plan runs by all the servers}.
-\acrshort{jmeter} does not distribute the load between servers, each runs the full test plan.
-So if you set 1,000 threads and have 6 \acrshort{jmeter} servers, you end up injecting 6,000 threads.
-When test cases run with \acrshort{jmeter} Distributed mode, the server node trigger the same copy of the test case on configured slave nodes parallel.
-At the end of the test cases, it gathers results into the master node.
+To create a higher workload, we used JMeter's Distributed Testing capabilities.
+JMeter uses the master-slave approach for distributed testing and allows us to handle all the test cases via a single master instance.
+However, it has the limitation of \emph{the same test plan runs by all the servers} rather than distributing the work among slave instances.
+In other words, JMeter does not distribute the load between servers, and each slave service runs the full test plan.
+So if we set 1,000 threads per test plan and run the test using six JMeter servers, the distributed test setup ends up injecting 6,000 threads.
+During JMeter distributed mode, the master server triggers the same copy of the test plan on configured slave nodes in parallel.
+After successfully running the test plans, the master server gathers results from slave servers.
 
@@
 
-When implementing load test cases with \acrshort{jmeter}, it uses threads to simulate the users.
-The root component of a test create is a thread group.
-There are different kinds of thread groups are available such as thread group (basic thread group), arrivals thread Group, free form arrivals thread group, stepping thread group, concurrency thread group, and ultimate thread group.
+While implementing JMeter test plans, it uses threads to simulate the users.
+The root component of a test plan is the thread group.
+There are different kinds of thread groups available such as thread group (basic thread group), arrivals thread Group, free form arrivals thread group, stepping thread group, concurrency thread group, and ultimate thread group.
 
@@
 \label{subse:closed_vs_open_workload}
+
 \begin{itemize}
@@
 \end{itemize}
-While implementing the test cases for \acrshort{wdias}, it uses the Concurrency Thread Group with Throughput Shaping Timer because it supports the open workload approach.
-Using other thread groups, it required to find the exact number of threads and timer delays that produce the desired number of \acrfull{rps} to server. It is known as the \emph{closed workload}.
-With using \emph{Throughput Shaping Timer}, it only needs to configure the \acrshort{rps}.
-When combining this \acrshort{jmeter} plugin with Concurrency Thread Group using Schedule Feedback Function to dynamically maintain thread count required to achieve target \acrshort{rps} \cite{KarunarathneGihanWdias/wdias-performance-test:JMeter.}.
+
+While implementing the test cases for \acrshort{wdias}, we used the concurrency thread group with the throughput shaping timer extension of JMeter because it supports the open workload approach.
+Using other thread groups, we are required to find the exact number of threads and timer delays that produce the desired number of \acrfull{rps} to the server, which is known as the \emph{closed workload}.
+By using the \emph{throughput shaping timer}, we only need to configure the \acrshort{rps} throughout the test plan.
+Then the throughput shaping timer provides a feedback loop to the concurrency thread group via schedule feedback function to dynamically maintain thread count required to achieve target \acrshort{rps} \cite{KarunarathneGihanWdias/wdias-performance-test:JMeter.}.
 
@@
 
-\cref{fi:test_prod_throughtput_shaping_timer} shows the throughput shaping timer configurations use while load testing.
-The configurations as similar to the load test plan described in \cref{se:test_plan}.
-To get the maximum peak of 18,000 request per minutes, which is equivalent to 300 \acrshort{rps} is setup according the the figure.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The test plans mentioned in \cref{se:test_plan} are implemented via the \acrshort{jmeter}. The following list shows the all the test cases used for the performance testing:
+\cref{fi:test_prod_throughtput_shaping_timer} shows the throughput shaping timer configurations that we used for the load testing, and it is similar to the load test plan described in \cref{se:test_plan}.
+The maximum peak load that can be had during the load test is 300 \acrshort{rps} (equivalent to 18,000 requests per minute).
+The following list shows all the test plans that we used during the performance testing:
 
@@
 
-The first step of the plan consists of setting up the timeseries metadata.
-At the same time, it creates the timeseries entry in the \acrshort{wdias} system as well as shown in the following list of test steps and configurations.
+The first step of the test plan consists of setting up the timeseries metadata.
+At the same time, we create the timeseries metadata in the \acrshort{wdias} system.
+Even with the real use case, users only have to register timeseries metadata once and reuse the generated timeseries identifier to insert the data.
+The following list of test steps shows the test plan for setting up the timeseries metadata.
 
@@
 
-By creating the timeseries before help to reduce the overhead during the performance testing, and cause to more accurate \acrshort{rps} at the run time.
-Otherwise, \acrshort{jmeter} needs to allocate another set of threads for timeseries creation.
-Since the test cases insert data again set of timeseries, most of the time it about retrieving the timeseries metadata, rather than creating new timeseries in the \acrshort{wdias} system.
+By creating the timeseries metadata before, we can reduce the overhead during the performance testing with only focus on essential data storing, and cause more accurate \acrshort{rps} at the run time.
+Otherwise, JMeter needs to allocate another set of threads for registering timeseries metadata.
+Further, when we consider real use cases, most of the time, the users want to search for timeseries metadata and retrieve relevant metadata, rather than registering new timeseries metadata in the system.
 
-The following list shows the test steps of \acrshort{jmeter} while performing the load testing and the configurations.
+The following list shows the test steps of the JMeter test plan for all modules while performing the load testing.
 
@@
 
-As mentioned in \cref{se:test_plan}\hl{, we planned to perform another test scenario on the query timeseries module.
-During this test scenario, we use the following test steps to cover most of the timeseries metadata search queries and Geo queries which are defined in the} \cref{se:query}.
+As mentioned in \cref{se:test_plan}, we performed another separate test plan on the query timeseries module.
+Here, we used the following test steps to cover most of the timeseries metadata search queries and Geo queries supported by the \acrshort{wdias}.
 
@@
 
-\dbc{Top of Fig. 4.2 useless as it's black. Anyway, this figure isn't needed}
-\gkc{Since we described about throughput shaping timer graph in \ref{subse:closed_vs_open_workload}, better to include it here.
-It include the details on RPS and how it's increasing over time.
-Will remove the black part.
-Also move this paragraph to the \cref{subse:closed_vs_open_workload}}
-
-With the above \acrshort{jmeter} test case setup, it needs to enable each test case separately and before running via the command line in the server.
-To do it in a much efficient way, a scripting tool has implemented, and accessible with the codebase \cite{KarunarathneWdias-performance-test/TEST_PLAN.md:Plan} as \emph{test-dev}.
+With the above JMeter test plans, we have to enable each test plan separately and before running with JMeter distributed mode.
+In order to make the process faster, we implemented a script tool to interact with the JMeter test stored files.
+The script is available within the code base \cite{KarunarathneWdias-performance-test/TEST_PLAN.md:Plan} as \emph{test-dev} and supports the following features.
 
@@
 
-As per the usage description of test-dev, it has the features of enabling a test case, disable a test case, and run the test case while enabled.
-Another wrapper was implemented around the test-dev as \emph{test-plan.sh} which is also available with the codebase \cite{KarunarathneWdias-performance-test/TEST_PLAN.md:Plan}.
-
-\begin{lstlisting}[language=sh, caption=Test Plan Help]
--h | --help: Usage
-    <ROOT_DIR> <COMMAND> <REQ_SIZE>
-    - COMMAND: setup | import | create_extension | extension | export | all | query
-    - REQ_SIZE (optional): 24(1) | 288(2) | 1044(3)
-  NOTE: Modify test.conf as necessary
-  e.g.
-  test_plan.sh ~/wdias/wdias-performance-test run 2
-  - Run all the steps in order of setup, import, create_extension, extension, export, all, query
-  test_plan.sh ~/wdias/wdias-performance-test run
-  - Run all steps for all REQ_SIZE
-
-  test_plan.sh ~/wdias/wdias-performance-test setup
-  test_plan.sh ~/wdias/wdias-performance-test import 24
-  test_plan.sh ~/wdias/wdias-performance-test all 24
-
-  Distributed Mode
-  SERVER_IPS=<IP1,IP2...> test_plan.sh ~/wdias/wdias-performance-test run
-\end{lstlisting}
-
-It allows running a particular test plan which is described in \cref{se:test_plan}. Also possible to run all the test plans in order with given \emph{REQ\_SIZE} or for all the \emph{REQ\_SIZE}.
-
 \subsubsection{JMeter performance tuning}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{\hl{Test System Setup}}
+\subsection{Configure Experimental Setup on Cloud}
 \label{subse:test_sys_config}
-As described in the \cref{se:microservice}, the \acrshort{wdias} is mainly focused on microservice architecture and implemented on top of Kubernetes.
-\acrfull{k8s} is an open-source system for automating deployment, scaling, and management of containerized applications.
-For the performance study uses \acrfull{eks}.
-There are many \acrshort{k8s} solutions available such as GCP, Azure, and Digital Ocean on the cloud.
+As we described in the \cref{se:microservice}, the \acrshort{wdias} is mainly based on microservice architecture and implemented on top of Kubernetes.
+\acrfull{k8s} is an open-source system that is capable of automating deployment, scaling, and management of containerized applications.
+During the performance study, we used \acrfull{eks}.
+There are many \acrshort{k8s} solutions available such as GCP, Azure, and Digital Ocean on the cloud other than Amazon EKS.
 
-A detailed description of setting up the \acrshort{eks} available as \cite{KarunarathneWdias/Amazon_EKS.md:EKS} within the main repository of the \acrshort{wdias}.
+We have documented a detailed description of setting up the \acrshort{eks} \cite{KarunarathneWdias/Amazon_EKS.md:EKS}, and it is available in the codebase of the \acrshort{wdias}.
 \acrshort{k8s} is a planet scaling tool \cite{LinuxFoundationProduction-GradeKubernetes}, and users can tweak the configuration to run the \acrshort{wdias} as per the required level of load on the system.
-During the performance test of the \acrshort{wdias}, it uses a maximum of 300 \acrshort{rps} with providing to the system with increasing load, and monitor the auto scalability of the system with measuring other performance parameters mentioned in \cref{tab:aws_eks_nodes}.
+We used a set of physical nodes, as mentioned in \cref{tab:aws_eks_nodes}, to set up the \acrshort{k8s} for the performance testing with a peak of 300 \acrshort{rps}.
 
@@
 The \acrshort{wdias} uses Helm \cite{CNCFHelmDocs} which is a package manager for \acrshort{k8s}.
-Each microservice within the system deploys and maintains as a helm chart, and the Helm Charts \cite{KarunarathneWdias-helm-charts:Deployments} can be found within the codebase.
-For the databases, it uses the official helm charts.
+Each Also, we used Helm \cite{CNCFHelmDocs} that is a package manager for \acrshort{k8s}.
+Each microservice within the system deploys and maintains as a Helm chart and the Helm charts \cite{KarunarathneWdias-helm-charts:Deployments} for each microservice available within the codebase.
+For the databases, we used the official helm charts.
+Using Helm, we can configure resources, the number of replicas needed, deploy new changes, and manage credentials, storage, and proxy settings that are needed for each microservice.
 
@@
 \label{se:performance_tuning}
-To get better performance using the available resources, it is possible to schedule each microservice into a predefined set of nodes. There are few ways to do in the \acrshort{k8s};
+According to \cref{tab:aws_eks_nodes}, we selected a few physical nodes with different resource capacities.
+The grid and test labeled nodes have higher network bandwidth.
+To get better performance using the available resources, we can schedule each microservice into a predefined set of nodes.
+Thus we tried to deploy all JMeter microservices on test labeled nodes since the test plans need to interact with all the services and transfer bulk timeseries data.
+Also, the grid microservices are hosted inside the grid labeled node due to the massive size of grid data timeseries that need to be transferred during the load testing.
+There are few ways to assign microservice to a particular physical node in the \acrshort{k8s};
+
 \begin{itemize}
@@
 
-Users can use one of the above features to fine-tune the \acrshort{wdias} to perform better.
-For the moment, \acrshort{wdias} helm charts use node Affinity to use the same charts within local setup with one node and work the same charts on a \acrshort{k8s} cluster with multiple nodes.
-Pods are assigned to the nodes \cref{tab:aws_eks_nodes} based on the node label as below;
+Users can use one of the above methods to schedule microservice on physical nodes for better performance.
+For the moment, we used node affinity to schedule the microservices.
+We chose the above method since it allows us to schedule all the microservices in a node when there is only a single physical node available.
+Microservices are assigned to each node in \cref{tab:aws_eks_nodes} based on the node label as below;
 \begin{itemize}
@@
     \item \emph{scalar} -- scalar and vector adapters, import and export of same data types
-    \item \emph{test} -- \acrshort{jmeter} and metric server
+    \item \emph{test} --  JMeter and metric server
 \end{itemize}
-\cref{fi:eks_node_setup} shows the overview of the show the nodes are setup and each microservices are assigned to each node, the connectivity of the nodes, and the data interactions via the arrows.
-The databases used for data consistency and performance in storage optimization with search capabilities.
-But because of that, it only possible to run one instance of those.
-In the \acrshort{wdias}, the MySQL and MongoDB are not getting higher load as adapter databases such as InfluxDB for scalar and vector data types, and netCDF for the grid data type.
-To keep up with the pace, those microservice pods are assigned to dedicated nodes to increase the performance of inter-service communication.
+\cref{fi:eks_node_setup} shows the overview of the microservices assignment to each node in the \acrshort{eks} setup.
+Further, it shows the connectivity of the nodes and the data interactions via the arrows.
+We scheduled the microservices in the core labeled node together, since most of those services are communicating together, and running them inside one physical node reduces the latency.
+Then we separate scalar and vector microservices and their databases, in order to separate the load from the core node while storing scalar and vector timeseries data.
+As same as, we assigned microservices to grid and test nodes based on the higher bandwidth requirements.

### 2020-04-25 results/sec_3-observations.tex
Updated results chapter-4

@@
-\section{\hl{Performance Evaluation}}
+\section{Performance Test Observations}
 \label{se:observations}
 
-According to \cref{se:test_plan} section, This section includes the observations based one the test plans in \cref{se:test_plan} and test plan test up which is explained in \cref{se:workload}.
-Sections \ref{subse:obs_test_plan_all_60min} to \ref{subse:obs_test_plan_all_auto_15min} discuss the observations collected with performing the Load test plans over 60 minutes data (24 data points), 30 minutes data (48 data points) and 15 minutes data (96 data points) by variate the request size.
-Then another performance test with enabling auto-scaling for the higher resource utilized microservices as explained in \cref{subse:test_plan_metrics}.
+This section includes the observations based on the test plans discussed in Section \cref{se:test_plan}, and the experimental system setup explained in \cref{se:workload}.
+Sections \ref{subse:obs_test_plan_all_60min} to \ref{subse:obs_test_plan_all_auto_15min}, we discuss the observations collected with performing the Load test plans over 60 minutes data (24 data points per request), 30 minutes data (48 data points per request), and 15 minutes data (96 data points per request) by varying the request size.
+Then we perform another round of 15 minutes data with enabling auto-scaling for the higher resource utilized microservices.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Load Testing with hourly data}
+\subsection{Load Testing with hourly resolution data}
 \label{subse:obs_test_plan_all_60min}
 
-After running the test plan with 60 minutes (24 data points), it observed the data summary of \cref{tab:obs_all_60_min_summary}. It performed 311k of sample requests.
+After running the test plan with 60-minute resolution data (24 data points per request), we observed the data summary of \cref{tab:obs_all_60_min_summary}.
+The test plan performed 311k of sample requests within 30 minutes of elapsed time.
 
@@
 \end{table}
-Insert Timeseries performed over Scalar and Vector data types with each request send with 24 data points.
-On average it takes 28ms to insert data into the \acrshort{wdias}, and up to 90\% percentile inserted data within 31ms.
-Noticeably it has 0\% of errors which means that all the requests are completed successfully.
-On average, \acrshort{wdias} handled 40.5 \acrshort{rps} for Scalar and Vector data with the given workload.
-The performance of the Retrieve of Scalar and Vector Timeseries is similar to insert timeseries due to it depends on it.
-On the other hand, Insert Grid Timeseries data perform with 23ms with almost all the requests perform within the same amount of time, hence the standard deviation is smaller.
-The delay in inserting Grid timeseries smaller because those requests are handling asynchronously.
-Retrieve Grid Timeseries data perform the same but with a bit higher value of latency of 68ms.
-Both insert and retrieve grid timeseries data have 4.5 \acrshort{rps} since it only gets 10\% of the number of requests per given time via the test plan as explained in the data ratio in \cref{se:test_plan}.
+Insert timeseries performed over scalar and vector data types with each request sent with 24 data points.
+On average, it took 28ms to insert scalar and vector data into the \acrshort{wdias}, and up to 90\% percentile inserted data within 31ms.
+Noticeably it has 0\% of errors, which means that all the requests completed successfully.
+Also, \acrshort{wdias} handled 40.5 \acrshort{rps} of scalar and vector data requests with the given workload.
+The retrieval of scalar and vector timeseries has lesser delay than the insertion.
+On the other hand, insert grid timeseries data performed within 23ms, and almost all the requests perform within the same amount of time.
+Hence the standard deviation is smaller.
+Delay with inserting grid timeseries smaller because those requests are handled asynchronously.
+Retrieve grid timeseries data performed with a bit higher value of latency of 68ms due to performed the retrieve request on-demand.
+Both insert and retrieve grid timeseries data have 4.5 \acrshort{rps} since it only gets 10\% of the number of requests per given time during the load test.
 
@@
 \end{figure}
-\cref{fi:test_obs_all_60m_response_vs_threads} shows the response time against the number of active threads.
+\cref{fi:test_obs_all_60m_response_vs_threads} shows the response time against the number of active threads for 60-minute data requests.
 As the graph shows, the response time kept the same while increasing the number of active threads against each test case.
-This shows the scalability of the \acrshort{wdias} since the system able to process more requests without a significant change in the latency.
-When the number of active threads increased more than 122, \cref{fi:test_obs_all_60m_response_vs_threads} shows uncertainty in the inserting and retrieving Scalar and Vector data.
-This is because of those data handle on demand and depend on the timeseries database performance.
+The above graph shows the scalability of the \acrshort{wdias} since the system is able to process more requests without a significant change in the latency.
+When the number of active threads increased more than 122, \cref{fi:test_obs_all_60m_response_vs_threads} shows uncertainty in the inserting and retrieving scalar and vector data.
+The performance degrades because those data handles on-demand and depends on the timeseries database performance.
 
@@
 \cref{fi:test_obs_all_60m_latency} graph provides a better overview of the variation of latency over the elapsed time of the test plan against the number of server hits per second.
-The conclusion of giving static latency while increasing the number of requests in \cref{fi:test_obs_all_60m_response_vs_threads} can further prove with this graph since \cref{fi:test_obs_all_60m_latency} graph gives in detail an overview of the test plan period.
+This graph further proves that the system was able to handle the increasing workload without any significant change in the delay.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Load Testing with 30min data}
+\subsection{Load Testing with 30-min resolution data}
 \label{subse:obs_test_plan_all_30min}
 
-\cref{subse:obs_test_plan_all_30min} discussed the test plan performance with 30 minutes data which means 48 data points per each request in Scalar and Vector timeseries, and 48 ASCII grid files per each insert request.
-It performed round up to 311k of sample requests which are almost similar to \cref{subse:obs_test_plan_all_60min} processed samples.
+Next, we performed the test plan with 30-minutes resolution data, which means 48 data points per each request for the scalar and vector data types, and 48 ASCII grid files per each insertion request for the grid data type.
+Also, the test plan performed round up to 311k number of sample requests, which is almost similar to the number of samples processed with hourly resolution data.
 
@@
 
-\cref{tab:obs_all_30_min_summary} shows the response latency summary details and \acrshort{rps} as explained in \cref{subse:obs_test_plan_all_60min}.
-And the results are almost similar to the observations in \cref{tab:obs_all_60_min_summary}.
-This implies that even the request size is increased, the \acrshort{wdias} can perform better the same as the with smaller size of data.
+\cref{tab:obs_all_30_min_summary}shows the response latency summary details and \acrshort{rps} with 30-min resolution data.
+The results are almost similar to the observations in \cref{subse:obs_test_plan_all_60min}.
+Even though we doubled the request size, \acrshort{wdias} was able to keep the performance almost the same instead of increasing the latency twice.
 
@@
 
-\cref{fi:test_obs_all_30m_response_vs_threads} shows the response time against the number of active threads for 30min data.
-As the graph shows, the response time kept the same while increasing the number of active threads against each test case.
-This shows the scalability of the \acrshort{wdias} since the system able to process more requests without a significant change in the latency.
-When the number of active threads increased more than 110, \cref{fi:test_obs_all_30m_response_vs_threads} shows uncertainty in the inserting and retrieving Scalar and Vector data.
-This graph is similar to the \cref{fi:test_obs_all_60m_response_vs_threads}, but the active thread count goes down as a result of increasing the request size.
+\cref{fi:test_obs_all_30m_response_vs_threads} shows the latency against the number of active threads for the test plan with 30-min resolution data.
+As the graph shows, the response time kept almost constant while increasing the number of active threads.
+Thus, we can say that \acrshort{wdias} is a scalable system since it was able to increase the throughput without a significant change in the latency.
+When the number of active threads increased, \cref{fi:test_obs_all_30m_response_vs_threads} shows uncertainty in the insertion and retrieval of scalar and vector data.
+Some of the facts cause this is, those operations are handled on-demand.
+At the same time, the system is writing timeseries while reading from the timeseries database.
+The InfluxDB can fine-tune for writes or read based on the requirements, but we used it with default configurations.
 
@@
 \end{figure}
-\cref{fi:test_obs_all_30m_latency} graph provides a better overview of the variation of latency over the elapsed time of the test plan against the number of server hits per second.
-This graph also concludes that over time latency does not change very much.
-But during the peak load, it shows some variation in the insert and retrieves of Grid timeseries.
-When compared to \cref{fi:test_obs_all_60m_latency}, the latency for insert and retrieve Grid timeseries increase by some amount.
+\cref{fi:test_obs_all_30m_latency} graph provides a better overview of the variation of latency over the elapsed time of the test plan against the \acrshort{rps}.
+By referring to the graph, we can see that over time the latency does not change very significantly.
+However, during the peak load, it shows a minor variation in latency of the insertion and retrieval of grid timeseries.
+When compared to \cref{fi:test_obs_all_60m_latency}, the latency of insertion grid timeseries data almost doubled.
+The grid timeseries data was handled asynchronously after successfully storing, thus the latency for storing the data increased by a factor of two since the request data size also increased twice.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Load Testing with 15min data}
+\subsection{Load Testing with 15-min resolution data}
 \label{subse:obs_test_plan_all_15min}
 
-\cref{subse:obs_test_plan_all_15min} discussed about the test plan performance with 15 minutes data which means 96 data points per each request in Scalar and Vector timeseries, and 96 ASCII Grid files per each insert Grid timeseries request.
-These requests are four times larger than the \cref{subse:obs_test_plan_all_60min} request size.
-It performed approximately 311k of sample requests which are almost similar to \cref{subse:obs_test_plan_all_30min} processed samples.
+During this section, we performed the test plan with 15-minutes resolution data, which means 96 data points per each request for the scalar and vector data types, and 96 ASCII grid files per each insertion request for the grid data type.
+The size of each request is four times larger than the 60-min resolution data.
+Here also, the test plan performed approximately 311k of sample requests, which are almost similar to sample requests made during 60-min and 30-min resolution data.
 \begin{table}[ht]
@@
 
-\cref{tab:obs_all_15_min_summary} shows the response latency summary details and \acrshort{rps} as same as explained in \cref{subse:obs_test_plan_all_30min}.
-And the latency observations are increased by some amount when compared to the observations in \cref{tab:obs_all_30_min_summary}.
-Noticeably retrieving latency of all types of data types increased by a considerable amount.
-The same following the trend, the standard deviation of retrieve timeseries data increased my considerable amount for all the types.
-We can assume that more writing to the databases affected reads as well.
-Event the request data size increased by 4x time, the \acrshort{wdias} were able to handle them without any significant performance issues.
-And the system able to provide the same throughput as shown in \cref{tab:obs_all_30_min_summary}.
+\cref{tab:obs_all_15_min_summary} shows the response latency summary details and \acrshort{rps} of the test plan with 15-min resolution data.
+When compared to the observations from the performance test with 30-min data, the request latency also increased for all sample requests.
+Also, the standard deviation of retrieval timeseries data increased by a considerable amount for all the data type's sample requests.
+One of the reasons for increasing the retrieval data delay was while performing heavy database writes on the database has effects on the database reads.
+Even though we increased the request data size by four times higher, the system was able to handle all requests without significant performance issues.
+Also, the system provided the same throughput as with 60-min and 30-min resolution data.
 
@@
 
-\cref{fi:test_obs_all_15m_response_vs_threads} shows the response time against the number of active threads for 15min data.
-As the graph shows, the response time kept the same while increasing the number of active threads against each test case.
-When the number of active threads increased more than 140, the \cref{fi:test_obs_all_15m_response_vs_threads} show uncertainty in the inserting and retrieving all data types.
-The latency of insert and retrieve Grid timeseries data goes up compared to \cref{fi:test_obs_all_30m_response_vs_threads}.
-With higher request size, it becomes to notice the latency also increase by a small factor when the number of active thread increased.
-This can notice on with insert and retrieval of Grid timeseries data.
+\cref{fi:test_obs_all_15m_response_vs_threads} shows the latency against the number of active threads for the test plan with 15-min resolution data.
+As per the graph, the system was able to keep the response latency constant while increasing the number of active threads.
+However, when the number of active threads became higher, there was a disturbance with the response delay during the insertion and retrieval of timeseries data.
+The latency of insert and retrieval of grid timeseries data increased twice when compared to 30-min resolution data.
+With a larger request size, we can notice the latency also increased by a smaller factor when we increased the number of active threads.
 
@@
 
-\cref{fi:test_obs_all_15m_latency} graph provides a overview of the variation of latency over elapsed time of the test plan against the number of server hits per second for 15min data.
-This graph shows that over time \acrshort{wdias} was able to keep the latency constant over the test plan. But at peak time, it tends to vary from the mean value a lot.
-One noticeable fact is, throughout the test period, it shows spikes in latency when compared to \cref{fi:test_obs_all_60m_latency} and \cref{fi:test_obs_all_30m_latency}.
+\cref{fi:test_obs_all_15m_latency} graph provides an overview of the variation of latency over the elapsed time of the test plan against the number of server hits per second for 15-min resolution data.
+As per the graph, the system was able to keep the latency constant all over the test plan.
+However, at the peak, the latency tends to vary from the mean value by a smaller factor.
+Also, we can observe that there were lots of latency spikes throughout the test plan when we increased the request size.
 
@@
 
-\begin{figure}[htp]
-    \centering
-    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_15m_response_times_percentiles.png}
-    \caption{Load testing with 15 minutes of data - Response times Percentiles}
-    \label{fi:test_obs_all_15m_latency_percentile}
-\end{figure}
-\cref{fi:test_obs_all_15m_latency_percentile} visually shows the summary of \cref{tab:obs_all_15_min_summary} latency up to 90\% percentile.
-With higher request size data, the \acrshort{wdias} able to process the requests without significant change in latency up to 90\% percentile.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Load Testing with Auto Pod Scaling}
+\subsection{Load Testing with 15-min resolution data while Auto Pod Scaling enabled}
 \label{subse:obs_test_plan_all_auto_15min}
 
-This \cref{subse:obs_test_plan_all_auto_15min} discussed the test plan performance with 15 minutes data which means 96 data points per each request in Scalar and Vector timeseries, and 96 ASCII Grid files per each insert Grid timeseries request.
-These requests are four times larger than the \cref{subse:obs_test_plan_all_60min} request size.
-It performed approximately 311k of sample requests which are almost similar to \cref{subse:obs_test_plan_all_15min} processed samples.
-Other than that, this test plan runs with enabling \acrshort{k8s} Auto-scaling for the high resource utilized microservice as explained in \cref{subse:test_plan_metrics}.
-With the test load used for the performance test, import-ascii-grid-upload microservice is using lots of CPU, and adapter-grid microservice is using lots of Memory.
-During this test plan, \acrshort{wdias} start with the auto-scaling enabled for import-ascii-grid-upload microservice.
-Since adapter-grid is a consistent service for storing netCDF files, it is not possible to auto scale, since \acrshort{eks} does not support multiple reads writes support volumes \cite{LinuxFoundationPersistentKubernetes}.
+Here we did the performance test plan with 15-minutes resolution data, which is similar to the above section.
+However, during the test plan, we enabled the K8s auto-scaling only for higher resource utilized microservices, as explained in \cref{subse:test_plan_metrics}.
+While performing the above test plans, we noticed the import-ascii-grid-upload microservice is using lots of CPU, and the adapter-grid microservice is using lots of memory.
+Before starting the test plan, we configured auto-scaling for the import-ascii-grid-upload microservices.
+However, the adapter-grid microservice is a consistent service for storing netCDF files.
+If we want to enable the auto-scaling for the service, all microservice instances of adapter-grid need to share data via shared storage.
+Since \acrshort{eks} does not support multiple reads and writes support volumes \cite{LinuxFoundationPersistentKubernetes}, we are unable to enable auto-scaling during the test plan.
+However, the test plan performed approximately 311k of almost similar sample requests during the above sections.
 
@@
 
-\cref{tab:obs_all_auto_15_min_summary} shows the response latency summary details and \acrshort{rps} as same as explained in \cref{subse:obs_test_plan_all_15min}.
-During this test plan.
-the main focus on the auto-scaling enabled microservice.
-As per the insert grid latency in the \cref{tab:obs_all_auto_15_min_summary}, the average insert latency is reduced from 91ms to 87ms.
-Also, the error percentage reduced from 1.42\% to 0.18\%.
-Standard deviation reduced from 19.58 to 14.07 which means the latency is much closer to the average latency.
-These improvements in insert Grid timeseries data seem to affect on output of retrieve Grid timeseries data as well.
+\cref{tab:obs_all_auto_15_min_summary} shows the response latency summary details and \acrshort{rps} as explained in \cref{subse:obs_test_plan_all_15min}.
+If we analyzed the performance of the auto-scaling enabled microservice, the average grid data insertion latency was reduced from 91ms to 87ms.
+Also, we can notice that the error percentage reduced from 1.42\% to 0.18\%.
+Since the standard deviation also reduced, we can conclude that the latencies are closer to the average latency.
+Further, these improvements in insert Grid timeseries data seem to affect the output of retrieve Grid timeseries data as well.
 
@@
 \end{figure}
-\cref{fi:test_obs_all_auto_15m_latency} graph provides an overview of the variation of latency over the elapsed time of the test plan against the number of server hits per second for 15min data while auto-scaling enabled for \acrshort{k8s}.
-This graph show that over the time \acrshort{wdias} were able to keep the latency constant over the test plan.
-When compared to \cref{fi:test_obs_all_15m_latency}, throughout the test period, the latency spikes become less.
+\cref{fi:test_obs_all_auto_15m_latency} graph provides an overview of the variation of latency over the elapsed time of the test plan against the number of server hits per second for 15min data while auto-scaling enabled for K8s.
+According to the graph, the \acrshort{wdias} was able to keep the latency constant all over the elapsed time.
+When compared to \cref{fi:test_obs_all_15m_latency} without auto-scaling, we can see lesser latency spikes throughout the test period.
 
@@
 
-\cref{fi:test_obs_all_auto_15m_throughtput} shows the total server's transaction throughput against number of active threads.
-When compared to \cref{fi:test_obs_all_15m_throughtput}, the estimated throughput with a higher number of active threads become stable at the graph.
-This means enabling auto-scaling also improves the throughput with a higher number of active users as well.
+\cref{fi:test_obs_all_auto_15m_throughtput} shows the total server's transaction throughput against the number of active threads.
+When compared to \cref{fi:test_obs_all_15m_throughtput} without auto-scaling, the estimated throughput with a higher number of active threads becomes stable, according to the graph.
+Thus, we can conclude that enabling auto-scaling also improves the throughput by supporting a higher number of active users.
+During the next paragraphs, we discuss the resource usage while running the test plan while enabling the auto-scaling.
 
-The following charts show the resource usage while running the all test plan while enabling the auto-scaling.
 \begin{figure}[htp]
@@
 
-\cref{fi:obs_all_auto_15m_import_export_res} shows the CPU usage and Memory usage for import timeseries modules and export timeseries modules.
-The CPU usage is shown with milli CPUs \cite{LinuxFoundationManagingKubernetes} (1 CPU = 1000m CPUs) and the Memory usage shown with Megabytes (Mi) \cite{LinuxFoundationManagingKubernetes}.
-Noticeable, the import-ascii-grid-upload microservice used around 10 CPUs at the peak time while using 3.6 Gb of Memory.
-Another important fact is, after the test cases finished, the \acrshort{wdias} cool down the system via \acrshort{k8s} auto-scaling and release the resources.
-This clearly shows the elasticity of the \acrshort{wdias} according to the workload.
+\cref{fi:obs_all_auto_15m_import_export_res} shows the CPU usage and memory usage for import timeseries modules and export timeseries modules with 1 minutes resolution.
+We show the CPU usage with milli CPUs \cite{LinuxFoundationManagingKubernetes} (1 CPU = 1000m CPUs) and the memory usage shown with Megabytes (Mi) \cite{LinuxFoundationManagingKubernetes} in the graphs.
+Noticeably, the import-ascii-grid-upload microservice used around 10 CPUs at the peak time while using 3.6 Gigabytes (Gb) of memory.
+Another important fact is, after the test cases finished, the \acrshort{wdias} cooled down the system via K8s auto-scaling and released the resources.
+Thus, we can see the elasticity of the \acrshort{wdias} according to the workload.
 
@@
 
-\cref{fi:obs_all_auto_15m_import_grid_pod} shows the number of import-ascii-grid-upload pods scheduled overtime.
-The auto-scaling enabled with the configurations of 1 to 10 pods with the recommended CPU usage with 80\%.
-And the pods scheduled with 1 CPU requested, and limit with 2 CPUs per pod.
-As the graph shows, 3 pods scheduled at the initial as per the configuration of the helm chart.
-While increasing the workload, new pods get spawn while keeping the constraint of 80\% of recommended CPU utilization.
-After \acrshort{k8s} spawn 10 maximum pods, it stops spawning new pods.
-But the pods were able to perform with vertical scaling since those are not hit the CPU limit of 2.
+\cref{fi:obs_all_auto_15m_import_grid_pod} shows the number of import-ascii-grid-upload pods scheduled overtime during the test plan.
+As mentioned in the previous paragraph, we enabled the auto-scaling with a maximum of 10 pods and 80\% recommended CPU usage.
+As the graph shows, we scheduled three pods before initialing the test plan.
+When the workload increased, K8s spawned new pods while keeping the total CPU utilization up to 80\%, as we configured above.
+After K8s spawned ten maximum pods, it stopped spawning new pods.
+However, each pod was able to vertical scale up to the limit of 2 CPUs.
+Even we saw the resources released after the peak load, but the number of pods did not decrease according to the graph.
+K8s has a threshold of reducing the number of pods, and it waits for 5 minutes before terminating a pod after a resource is released.
 \cref{fi:obs_all_auto_15m_adapter_dbs_res} shows the resource utilization of database adapters in the \acrshort{wdias}.
+The adapter-scalar and adapter-vector are not getting heavy load since they only process a scalar array of data points.
+However, we can see the CPU usage over time increased according to the test plan workload and cool down after the peak.
+For the adapter-grid, the CPU resource utilization increased and cooled down similarly to other adapters.
+However, the memory resources are not released due to the caching of netCDF files by the application.
 
@@
 
-This \cref{subse:obs_test_plan_query_15min} discussed the Query test plan performance.
-It performs multiple information retrieval queries such as query over locations, parameters, and timeseries, etc which are described over \cref{se:query}.
-It performed approximately 123k of sample requests.
-Query test plan performs over 5 minutes, and with a higher number of requests than other test plans with a peak of 600 hits per seconds.
+This \cref{subse:obs_test_plan_query_15min} discussed the query test plan performance.
+During the test plan, we performed multiple information retrievals queries such as queries over locations, parameters, and timeseries, which we described in the test planning phase.
+The test plan performed approximately 123k of sample requests only with the query microservice during the test period.
+We performed the query test plan over 5 minutes with a higher number of requests than other test plans with a peak of 600 hits per second.
 
@@
 The average latency is much higher than the minimum value.
-Also, it reported higher maximum values as well.
-Standard deviation showed a quiet higher value which means the response latency values are not closer to the average value.
-Noticeably, it does not report any errors, which means all the requests successfully process.
-The throughput for each test case is much higher and similar to all the requests.
-This is happening since all of these requests are handled via the adapter-query, it depends on the  MongoDB database performance.
+Also, the summary reported higher maximum values as well.
+Standard deviation showed a quiet higher value, which means the response latency values are not closer to the average value.
+Noticeably, we can not see any errors in the table, which means all the requests successfully process.
+The throughput is similar among all the requests.
+The performance of the adapter-query depends on the performance of the document storage database performance and geo-indexing performance.
 
@@
 When the number of requests gets higher, the latency also gets increased.
-That means adapter-query is not very much scalable with the current configurations.
+Further, \cref{fi:test_obs_query_5m_response_times_vs_threads} shows the response latency against the number of active threads for the query test plan.
+When the number of server hits gets higher, the latency also increases.
+According to the Figures, we can conclude that the performance of the adapter-query depends on the database.
+Even if we increase the number of adapter-query pods, the throughput of the microservice is not going to increase until we increase the performance by using the z-axis scaling of scale cube concept.
 
@@
 \end{figure}
-\cref{fi:test_obs_query_5m_response_times_vs_threads} shows the response latency against number of active threads for the query test plan.
-When the number of server hits get higher, the latency also get increased.
-That means adapter-query is not very much scalable with the current configurations.
 
-Whenever the timeseries data not found in the adapter-query, it read data from adapter-metadata and index for search over timeseries metadata.
-This will cause to higher performance with geo timeseries searches.
-The performance of the  MongoDB can further improve with using its features like Replication for high availability, and Sharding for higher throughput.
-Those attempts are beyond the scope of the \acrshort{wdias} performance test and users can use those to get higher results from the \acrshort{wdias}.
+Whenever the timeseries data is not found in the adapter-query, it reads data from adapter-metadata and index for search over timeseries metadata.
+We used the above mechanism to increase the performance with geo timeseries searches.
+The performance of the document storage can further improve with using its features like Replication for high availability, and Sharding for higher throughput.
+We did not attempt those performance improvements during the test plan since it was beyond the scope of the research.
+However, the users of the \acrshort{wdias} system can enable such features and get higher performance.

### 2020-04-25 results/sec_4-discussion.tex
Updated results chapter-4

@@
 
-This section concludes the observations in \cref{se:observations} section against the performance metrics defines in \cref{subse:test_plan_metrics}.
+This section concludes the observations in \cref{se:observations} section against the performance metrics defined in \cref{subse:test_plan_metrics}.
 
-The \emph{Latency} for each operation type kept constant over the whole test plan run time without any significant change.
-When the request size increased from 24 data points to 96 data points, the latency increase throughout the whole test plan with a smaller number.
-But for each test run, the latency kept constant over time.
-During the \cref{subse:obs_test_plan_all_auto_15min} test run, the performance of the Grid data got better when compared to \cref{subse:obs_test_plan_all_15min}.
-This means by adding more resources to the \acrshort{wdias}, it can handle more workload on the system.
+During each test plan, we showed the \emph{latency} for data insertion, and retrieval operation type kept constant over the whole test plan run time without any significant change.
+When we increased the request size from 60-minute resolution data to 15-minute resolution data, the latency also increased throughout the whole test plan with a smaller number.
+During \cref{subse:obs_test_plan_all_auto_15min} test run with auto-scaling, the performance of the grid data got better when compared to \cref{subse:obs_test_plan_all_15min} without auto-scaling.
+Thus, we can assume by adding more resources to the \acrshort{wdias}, it can handle more workload on the system by providing higher throughput.
 
-While keeping the latency constant without significant change, the \emph{throughput} of the \acrshort{wdias} kept constant while increasing the request size from 60min data (24 data points) to 15min data (96 data points) for all the data types such as Scalar, Vector, and Grid.
-When the number of active threads increased, the \acrshort{wdias} able to provide the same throughput with maintaining the latency stable.
+While keeping the latency constant without significant change, we showed the \emph{throughput} of the \acrshort{wdias} kept constant while increasing the request size from 60-minute resolution data (24 data points) to 15-minute resolution data (96 data points) for all the data types such as Scalar, Vector, and Grid.
+When the number of active threads increased, the \acrshort{wdias} able to provide the same throughput while maintaining the latency stable.
 
-One of the reasons for having deviations at the peak time due to uses of single instance for the data consistency such as  InfluxDB for Scalar and Vector data, and netCDF with parallel support for Grid data.
-Further, it is possible to increase the performance of these bottlenecks much higher such as using the  InfluxDB Commercial cluster support for high availability or horizontal scaling of  InfluxDB.
-With  InfluxDB cluster, it is possible to run multiple pods of adapter-scalar and adapter-vector for support more server hits per second.
+One of the reasons for having deviations at the peak time due to uses of a single database instance for the data consistency such as using InfluxDB for scalar and vector data, and netCDF with parallel access support for Grid data.
+Further, it is possible to increase the performance of the before-mentioned bottleneck places such as using the InfluxDB commercial cluster support for high availability or horizontal scaling of InfluxDB.
+By using the InfluxDB cluster, we can run multiple pods of adapter-scalar and adapter-vector to support more workload.
 
 Adapter-grid is using a Python wrapper for netCDF FORTRAN implementation with parallel IO enabled.
-This has some performance issues as well as memory leak issues.
-Since each microservice in the \acrshort{wdias} independent of technology that can use to implement the service, it will increase the performance if the adapter-grid directly ported to netCDF with a low-level language such as C or FORTRAN.
-Other than \acrshort{eks}, if users can use a \acrshort{k8s} cluster that supports Persistent Volumes with the access of Read Write  Many \cite{LinuxFoundationPersistentKubernetes} , then it is possible to run multiple pods of adapter-grid and increase the throughput of the \acrshort{wdias}.
+However, it has some performance issues as well as memory leak issues.
+Since each microservice in the \acrshort{wdias} is independent of technology, we can use a different technology stack to implement the service.
+Doing so, we can increase the performance as an example by directly porting the adapter-grid to netCDF with a low-level language such as C or FORTRAN.
+Other than \acrshort{eks}, users can use a different \acrshort{k8s} cluster that supports Persistent Volumes with the access of Read Write Many \cite{LinuxFoundationPersistentKubernetes}.
+Then they can run multiple pods of adapter-grid and increase the throughput of handling grid data.
 
-When looking into the \emph{resource utilization} of \acrshort{wdias}; since it is using the \acrshort{k8s} as the container orchestration system, it allows us to scale up and cool down the system as required based on the workload.
-This demonstrates the test plan of \cref{subse:obs_test_plan_all_auto_15min}, and the system gets scale up to the maximum at the peak time.
+When we looked into the \emph{resource utilization} of \acrshort{wdias}, by using the \acrshort{k8s} as the container orchestration system, we were able to scale up and cool down the system as required based on the workload.
+During the test plan with auto-scaling enabled in \cref{subse:obs_test_plan_all_auto_15min}, we demonstrated the system gets scale up to the maximum at the peak time.
 Then cool down to a single pod after finishing the test cases.
-Given above \acrshort{wdias} can run from 1 CPU node to nodes with 100 CPUs.
-As described in the \cref{se:microservice}, it uses many of the concepts of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities.
+Given the above facts, we can run the \acrshort{wdias} on a cluster from 1 CPU node to nodes with 100 CPUs.
+As described in \cref{se:microservice}, we used many of the concepts of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities.
 
-The \acrshort{wdias} supports \emph{auto scaling} by out of the box with \acrshort{k8s}.
-Services can configure with a maximum number of pods to avoid over resource usage.
+The \acrshort{wdias} supports \emph{auto-scaling} out of the box with \acrshort{k8s} support.
+Services can be configured with a maximum number of pods to avoid over resource usage.
 When there is not much workload on the system, the system cools down to fewer pods to save more resources.
-When there is an issue with a pod, \acrshort{k8s} auto-schedule another pod and remove the unhealthy pod.
+When there is an issue with a pod, \acrshort{k8s} auto-schedule a new pod and remove the unhealthy pod.
 Also, it allows updating the system without any downtime with rollback updates.
+By doing that, the \acrshort{k8s} create new pods with upgraded microservice and forward the traffic to new pods after spawning enough new pods, and terminate the old pods.
 
-\emph{Risk of unable to process data} during the test performance, the \acrshort{wdias} processed many requests with higher request size than the normal usage with a lower rate of failures to process the requests, mainly with insert Grid data.
-If the usage of \acrshort{wdias} wants to reduce the risk of unable to process data, then the system can configure to run with redundant pods to handle spike of workloads.
-Also while configuring for the auto-scaling, the \acrshort{k8s} can configure to maintain a lower amount of CPU usage such as 50\% to 60\% rather  than 80\%.
-Such configuration with always spawn new pods to handle double of current peak load.
+The \acrshort{wdias} processed many requests with a larger request size than the normal usage with a lower rate of failures to process the requests, mainly with insert Grid data.
+If we want to \emph{reduce the risk of unable to process data}, then the system can be configured to run with redundant pods to handle spikes of workloads.
+Also, while configuring the auto-scaling, the \acrshort{k8s} can be configured to maintain a lower amount of CPU usage, such as 50\% to 60\% rather than 80\%.
+Such configuration will always spawn new pods to handle double of current peak load that the system can handle at a given time.

### 2020-04-25 summary/sec_1-conclusions.tex
Replace noun acronym with full word
Updated Summary - Chapter5

@@
 
-To enhance the accuracy of the weather prediction, it is essential to provide reliable and timely weather data for \acrshort{nwm}.
+To enhance the accuracy of the weather prediction, we need to provide reliable and timely weather data for NWMs.
 Even though there are many weather data integration systems, most of them are proprietary or closed source.
-This means for an island like Sri Lanka that having different kinds of weather seasons over the year those software needs to be highly customized.
-%\hl{Throughout the operations and maintenance, it is required to get support with paying lots of charges, and difficult to debug into a closed source system without maintenance support from the vendors.
-Also most of existing systems are not up to date with the cloud computing technologies, or bias to some research community.}
-\hl{Also, most of the existing systems are based on basic client-server architectures or monolithic distributed system architectures which are popular or available at the time of developing those systems.
-Because of this, those are unable to get the advantage of modern computational models such as containerized applications and using the could computing to gain benefits of scalability, high availability and low-cost operations.}
+Thus, for an island like Sri Lanka that has different kinds of weather seasons yearly, those software needs to be highly customized.
+Also, most of the existing systems are based on basic client-server architectures or monolithic distributed system architectures or developed based on the best technology available at the time of developing those systems.
+However, most of the concepts are outdated with the technology advancement, and we can not get the full advantage of modern computational models such as containerized applications and using the cloud computing to gain benefits of scalability, high availability, and low-cost operations.
 
-\dbc{Look some of the changes in abstract and revise this para. However, don't repeat the same from abstract.}
-\gkc{UPDATED}
-
-We proposed an extendable open source weather data integration and assimilation system known as \acrshort{wdias}.
-\acrshort{wdias} focuses on providing efficiently integrates weather data from different sources with quality control and supporting steaming large size of data.
-And compatible with current cloud computing technologies and architecture patterns.
+During our research, we proposed an extendable open source weather data integration and assimilation system known as \acrshort{wdias}.
+\acrshort{wdias} focuses on providing a system to efficiently integrate weather data from different sources with quality control and supporting steaming large size of data.
+Furthermore, the proposed system is compatible with current cloud computing technologies, architecture patterns, and compatible with modern cloud computing architectures.
 
@@
 After comparing the disadvantages of using such architectures with the system requirements, we came up with modern microservice architecture.
-\acrshort{wdias} implemented the microservice architecture on top of the \acrshort{k8s}.
-Each microservice of \acrshort{wdias} is mapped to a pod in the \acrshort{k8s}.
-Also, each microservice follows the concept of Smart endpoints dumb pipes and does specific operations that are related to the data format that responsible for handling.
+\acrshort{wdias} implemented the microservice architecture on top of the \acrshort{k8s}, which is a container orchestration platform.
+We mapped each microservice of \acrshort{wdias} to a pod in the \acrshort{k8s} cluster.
+Also, each microservice follows the concept of smart endpoints dumb pipes[?] and does specific operations that are related to the data format that responsible for handling.
 
-Based on the microservice architecture patterns and the nature of the weather metadata, the \acrshort{wdias} came up with the idea of database structure to provide higher performance while storing the weather data optimum.
-The system uses a timeseries database for storing Scalar and Vector timeseries data and using \acrshort{netCDF} for storing Grid timeseries data.
-And each database adapter uses the concept of database per service which allows each microservice service to scale without interference from other microservices.
-And it uses microservice sagas pattern for asynchronous data handling for requests with higher size.
-According to the \cref{se:microservice}, it uses many of the concepts of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities.
+Based on the microservice architecture patterns and the nature of the weather metadata, we came up with the idea of database structure for the \acrshort{wdias} to provide higher performance while storing the weather data optimum.
+The system uses a timeseries database for storing scalar and vector timeseries data and using netCDF for storing grid timeseries data.
+Also, each database has an adapter, and each adapter uses the concept of database per service, which allows each microservice service to scale without getting interference from other microservices.
+Moreover, it uses the microservice sagas pattern for asynchronous data handling for requests with a larger size.
+As discussed in \cref{se:microservice}, we used many of the concepts of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities.
 
 Also, the system provides a generic open mechanism to integrate new modules as an extension to enhance the features of the system.
-This capability enables to integrate weather data preprocessing flows as extension modules.
-The extension API provides easy access to create and modify the extension triggers on the fly without stopping the system or any downtime to change the configurations.
-The system provides extensive timeseries query endpoints to easy search over the system timeseries metadata with supporting Geo-based queries.
+This capability enables us to integrate weather data preprocessing flows as extension modules.
+We designed an extension API to easily access to create and modify the extension triggers at runtime without stopping the system or any downtime for the system reconfiguration.
+The system provides extensive timeseries query endpoints to easy search over the stored timeseries metadata with supporting Geo-based queries.
 
-Load testing of \acrshort{wdias} was perform using the \acrshort{jmeter} tool's distributed testing capabilities.
+Further, we performed load tests using the JMeter tool’s distributed testing capabilities.
 Then the test plans are performed with increasing the request size and monitoring the performance metrics.
-The system is setup on the \acrfull{eks} as per the configurations of \cref{subse:test_sys_config}.
-Based on the observations, the system was able to handle 300 \acrshort{rps} (which means 18,000 requests per minute) successfully with minimizing the error rate to zero.
-Also, while increasing the request size from 24 to 96 data points per scalar and vector timeseries, and the number of ASCII Grid files from 24 to 96, the \acrshort{wdias} was able to perform the same while keeping the latency constant without any significant change.
-During the performance test plans, the system was able to provide an increase in the throughput by keeping the latency constant while increasing the workload.
-Which exhibits the scalability of the system.
-With the \acrshort{k8s} auto-scaling, the \acrshort{wdias} were able to elastically adjust the number of pods according to the workload with auto-scaling configurations. 
-The results of \acrshort{wdias} shows that the system can run from 1 CPU node to nodes with a few hundred CPUs.
+The system is setup on the Amazon Elastic Kubernetes Service (Amazon EKS) as per the system setup configurations of \cref{subse:test_sys_config}.
+Based on the observations, we were able to perform 300 \acrshort{rps} of peak load, and the system handled the workload successfully with minimizing the error rate to zero.
+Also, while we increased the request size from 24 to 96 data points per scalar and vector timeseries, and the number of ASCII Grid files from 24 to 96, the \acrshort{wdias} was able to provide the same throughput while keeping the latency constant without any significant change.
+Likewise, the system was able to provide an increase in the throughput by keeping the latency constant while increasing the workload.
+Thus, we can conclude that the system is further scalable.
+With \acrshort{k8s} auto-scaling enabled, the \acrshort{k8s} elastically adjust the number of pods according to the workload with provided auto-scaling configurations.
+The results of \acrshort{wdias} shows that the system can run on a cluster from 1 CPU node to nodes with a few hundred CPUs.

### 2020-04-25 summary/sec_2-research_limitations.tex
Updated Summary - Chapter5

@@
 \label{se:research_limitations}
-\gkc{Previously you asked to rename this section sir.
-Why can't it have the title of \emph{Future Work}.
-There are some of the requirements that can be done for the system, in order to gain more of it.
-Which part is misleading?}
 
-This section discussed the lacking features in the \acrshort{wdias} and some of the improvements that can add to improve the performance and usability of the system.
+During this Section, we discussed the lacking features of the \acrshort{wdias} and the set of improvements that we can add to improve the performance and usability of the system.
 
 \emph{Lack of data preprocessing modules}:
-The extension module enables the plugin system to integrate prepossessing modules that can use for process the data which are inserted to the system or based on regular intervals.
-Also, \acrshort{wdias} provides a more generic open interface approach to create more preprocessing modules.
-Since \acrshort{wdias} is an open-source system, it expects more modules to be created by the community.
-When compared to other systems like \acrshort{fews}, the current system only have few extension for the testing purpose.
-This is one of the major areas that need to be improved.
+We implemented the extension modules as an eco-system of integrating different preprocessing modules as add-ons to the system.
+Then, users can use these modules for process the data which are inserted into the system in real time or process later based on regular intervals.
+Also, we provide a more generic open interface approach to create more preprocessing modules and trigger them via the extension API.
+Since \acrshort{wdias} is an open-source system, we are expecting that the community will create more modules, and provide them as contributions for future users.
+When compared to other systems like \acrshort{fews}, the current system only has few extensions for the testing purpose.
+Thus, we can consider that as one of the major areas that need to be improved.
 
 \emph{Supporting Irregular Grids}:
-At the moment \acrshort{wdias} does not support Irregular Grids, but it has the API endpoints defined for the implementation which can follow the same microservice architecture.
-The scope of the \acrshort{wdias} does not belong to such level of implementation and the scope was reduced by removing such components from the system.
+At the moment, \acrshort{wdias} does not support Irregular Grids, but it has the API endpoints defined for the implementation of such support with following the microservice architecture.
+We reduced the scope of the research by removing such components from the system, and such level of implementation does not belong to the \acrshort{wdias} scope as well.
 
 \emph{Grid data performance}:
-As mentioned in the \cref{se:discussion}, adapter-grid is using a Python wrapper for netCDF FORTRAN implementation with parallel IO enabled.
-This has some performance issues as well as memory leak issues.
-Since each microservice in the \acrshort{wdias} independent of technology that can use to implement the service, it will increase the performance if the adapter-grid directly ported to netCDF with a low-level language such as C or FORTRAN.
-They are some future work that can focus on improving the performance of grid data.
+As mentioned in \cref{se:discussion}, adapter-grid is using a Python wrapper for netCDF FORTRAN implementation with parallel IO enabled.
+However, it has some performance issues and memory leak issues as well.
+Since each microservice in the \acrshort{wdias} is independent of technology, we can use a different technology stack to implement the service.
+As an example, we can use a low-level language such as C or FORTRAN to implement the adapter-grid, which will affect performance improvements and lesser issues.
+There is some future work that can focus on improving the performance of storing grid data.
 
 \emph{Define infrastructure as code}:
-Physical nodes for the \acrshort{k8s} cluster created using Cloud Computing provider such as \acrshort{eks}.
-And defining each pod resource limitations at the helm chart level.
-But the infrastructure that needs to deploy the \acrshort{wdias} can define as code such as using tools like Terraform which is independent of the Cloud Computing provider.
-Using such a tool, users will able to easily deploy the \acrshort{wdias} on any Cloud provider without much hassle.
+Physical nodes for the \acrshort{k8s} cluster created using cloud computing providers such as Amazon EKS, Google Cloud, and Microsoft Azure cloud.
+However, the infrastructure that needs to deploy the \acrshort{wdias} can be defined as code such as using tools like Terraform, which is independent of the cloud computing provider.
+Using such a tool, users will be able to quickly deploy the \acrshort{wdias} on any cloud provider without much hassle.
 
-\emph{Improve test cases}:
-As described in detail with \cref{subse:closed_vs_open_workload}, for \acrshort{wdias} performance test uses the \emph{Time Stepping Feedback} loop with Concurrent Threads which is the best approach support by  JMeter at the moment.
-But using that it is not possible to get the desired \acrshort{rps} for each test case within the test plan.
-Because of this issue, the \acrshort{wdias} test plans further improved by removing redundant test cases such as create timeseries at the beginning.
-Having created timeseries at the beginning causes some issues such as most of the thread are working on that test case rather on required test cases.
-Still, there may be some improvement that can be done.
+\emph{Improvements to test cases}:
+As described in detail with \cref{subse:closed_vs_open_workload}, the \acrshort{wdias} test plans use the time-stepping feedback loop with concurrent threads, which is the best approach support by JMeter at the moment.
+However, using the above approach, we can not get the desired \acrshort{rps} for each test case within the test plan.
+Because of the above issue, the \acrshort{wdias} test plans further improved by removing redundant test cases such as create timeseries at the beginning.
+Having created timeseries at the beginning causes some issues such as most of the thread are working on that test case, rather than running the required test cases.
+Thus, the test plans need to be further improved with running more test cases with the desired \acrshort{rps}.
 
 \emph{Tune \acrshort{wdias} database structure performance}:
-As further described in \cref{se:discussion}, it is possible to increase the performance of these bottlenecks much higher such as using  InfluxDB Commercial cluster support for high availability or horizontal scaling of  InfluxDB.
-With the  InfluxDB cluster, it is possible to run multiple pods of adapter-scalar and adapter-vector for support more server hits per second.
-Other than that, the \acrshort{wdias} performance can improve via partitioning the timeseries key space into multiple  InfluxDB instances.
-The adapter-scalar or adapter-vector can improve to plug multiple instances of  InfluxDB instances by changing the configurations.
-As an example, based on the key attribute \cref{subse:timeseries_key_attributes} Timeseries Type, the adapter-scalar can connect to four instances of  InfluxDB instances such as  External Historical, External Forecast, Simulated Historical, and Simulated Forecast, etc.
-
-\emph{Alerting extension modules}:
-At the moment, extensions only support \emph{OnChange} and \emph{OnTime} events. But it will be good to have event trigger support based on reconfigured alert level.
-
-\emph{Publisher Subscriber extension modules}:
-The \acrshort{wdias} better to be capable of triggering external systems based on events such as webhooks.
-
-\dbc{Need a new section for Conclusions.}
-\gkc{It did not make sense for me to adding another section as Conclusion.
-We already add a \cref{se:summary_conclusion} above.
-Do we need to rearrange the content of this Chapter?
-No point of adding another section with repeating the same content.
-May be I didn't understand your suggestion here.}
-\gkc{Do we need to move the \cref{se:discussion} here? Normally where should we include the analysis of observations?}
+As further described in \cref{se:discussion}, we can increase the performance of adapter microservices by using InfluxDB commercial cluster support for high availability or horizontal scaling of InfluxDB.
+With the InfluxDB cluster, it is possible to run multiple pods of adapter-scalar and adapter-vector to support more server hits per second.
+Other than that, the \acrshort{wdias} performance can improve via partitioning the timeseries keyspace into multiple InfluxDB instances.
+As an example, based on the key attribute \cref{subse:timeseries_key_attributes} Timeseries Type, the adapter-scalar can connect to four instances of InfluxDB instances such as External Historical, External Forecast, Simulated Historical, and Simulated Forecast.
+\emph{Alerting extension modules}: At the moment, extensions only support OnChange and OnTime events.
+However, it will be useful to have event trigger support based on the configured alert level or threshold level.
+\emph{Publisher Subscriber extension modules}: The \acrshort{wdias} better to be capable of triggering external systems based on events such as webhooks.

### 2020-04-26 glossary.tex
Removed commercial database names
Problem statement
Moved k8s to architectural decisions
Updated -> Method - Microservices

@@
 
-\newacronym{fews}{Delft-FEWS} {Delft-FEWS, Deltares}
+\newacronym{fews}{Delft-FEWS} {Deltares FEWS}
 \newacronym{lead}{LEAD}{Linked Environments for Atmospheric Discovery}
@@
 \newacronym{nwm}{NWMs}{Numerical Weather Models}
-\newacronym{netCDF}{netCDF}{Network Common Data Form}
 \newacronym{soa}{SOA}{Service Oriented Architecture}
@@
 
-\newacronym{mysql}{MySQL}{MySQL}
-\newacronym{influxdb}{InfluxDB}{InfluxDB}
-\newacronym{redis}{Redis}{Redis}
-\newacronym{mongodb}{MongoDB}{MongoDB}
+\newacronym{netCDF}{netCDF}{Network Common Data Form}
+\newacronym{GRIB}{GRIB}{General Regularly-distributed Information in Binary form}
+\newacronym{csv}{CSV}{Comma-separated Values}
+
+\newacronym{rdbms}{RDBMS}{Relational Database Management System}
 \newacronym{k8s}{K8s}{Kubernetes}
-\newacronym{eks}{AWS EKS}{Amazon Elastic Kubernetes Service}
+\newacronym{eks}{Amazon EKS}{Amazon Elastic Kubernetes Service}
 
@@
 \newacronym{api}{API}{Application Programming Interface}
-\newacronym{jmeter}{JMeter}{Apache JMeter}
-\newacronym{rps}{RPS}{Request per Second}
+\newacronym{rest}{REST}{Representational State Transfer}
 
-\newacronym{curw}{CUrW SL}{Urban Center for Water, Sri Lanka}
+\newacronym{curw}{CUrW-SL}{Center for Urban Water, Sri Lanka}

### 2020-04-26 method/sec_0_introduction.tex
Updated -> Method - Microservices

@@
-This chapter presents the design decisions taken while implementing \acrfull{wdias}, and how is the system got \hl{adapted from the systems analyzed in Chapter} \ref{ch:literature}.
-\cref{se:high_level_design} presents a brief discussion on how the weather forecasting is happening and why it needs to interact with multiple data formats.
-\cref{se:architectural_decisions} presents how the architectural design of proposed solution evolved while designing and implementing \acrshort{wdias}.
-\cref{se:microservice} presents %gives a better understanding of the 
-microservice architectural concepts followed while implementing \acrshort{wdias}.
+This Chapter presents the design decisions taken while implementing \acrfull{wdias} and how we adopt from the systems analyzed in \ref{ch:literature}.
+\cref{se:high_level_design} presents a brief discussion on how  the weather forecasting is happening and why does it need to interact with multiple data formats.
+\cref{se:architectural_decisions} shows how the architectural design of the proposed solution evolved while designing and implementing \acrshort{wdias}.
+\cref{se:microservice} presents microservice architectural concepts followed while developing the \acrshort{wdias}.
 Then the reasons behind developing \acrshort{wdias} database structure and technologies used are discussed in  \cref{se:db_struct}.
@@
 
-\dbc{It's just WDIAS. "the" should be used only on essential places to being the meaning. }
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-To get an overall idea of the flow of weather prediction, let us look into one of the \hl{flows using} at the \acrshort{curw} \cite{CUrWSL2017SL}.
+To get an overall idea of the flow of weather prediction, let us look into one of the weather forecastings flows using the \acrshort{curw} \cite{CUrWSL2017SL}.
 
 \begin{enumerate}
-    \item Extract \acrshort{GRIB} \acrshort{wrf} model data to \acrshort{netCDF}
-    \item \hl{From} \acrshort{netCDF} to \acrshort{csv} of each location data, then feed to HEC-HMS hydro-dynamic model and get the output as a \acrshort{csv} file.
-    \item \acrshort{csv} and \hl{Rain cell Grid feed} into the FLO2D hydrologic model, and get the water level as ASCII Grid files after the simulation is complete.
-    \item Upload ASCII files to \hl{ArcGIS create raster files, then use for the LOSS Estimation}
+    \item Extract \acrshort{GRIB} \acrshort{wrf} model data to the \acrshort{netCDF} format
+    \item Extract \acrshort{netCDF} data to \acrshort{csv} format for each location data, then feed to HEC-HMS hydrodynamic model and get the output as a \acrshort{csv} file.
+    \item HEC-HMS's \acrshort{csv} output and precipitation as Grid files feed into the FLO2D hydrologic model and get the water level as ASCII Grid files after the simulation is complete.
+    \item Upload above ASCII files to a geographic information system after convert to a compatible format, then use for the loss estimation
 \end{enumerate}
 
-\hl{When looked into the above flow, it gives a clear understanding of multiple data formats using while weather predictions.}
-Also, to correct the model outputs, \hl{it required} to collect real-time data such as:
+In the above weather forecasting steps, we can see that the weather data need to convert to different formats while feeding from one model or step to another.
+After the models run successfully, the resulting output data may not be accurate or biased based on different factors.
+In such situations, we need to correct predicted weather data by comparing them with accurate real-time weather data.
+So, we are required to collect real-time data such as:
 \begin{itemize}
-    \item Frequently collected automated weather station data via HTTP protocol
-    \item Frequently collected automated water level stations data
+    \item Frequently collect automated weather station data via HTTP protocol
+    \item Collect accumulated weather data over a given period by automatic water level stations
 \end{itemize}
 
-\hl{Other than above many data formats using for handling data based on devices and standards which are using.} Also, for data modeling, it needs to convert the data \hl{into model compatible data format}.
-Then \hl{after successfully run the model it needs to collect data from the model output data formats.}
+Most weather data collecting devices use their data formats and different standard protocols to transmit the data.
+Then we need to validate the data and modify the data to remove errors.
+Also, these data need to convert into model compatible data format before feeding into models.
+The models output data in different formats and need to store those bulk data efficiently, and the system should be flexible enough to upgrade to support new data formats easily.
+Essentially, the system should share the real data, forecasted data, and other created data with relevant parties based on authorization.
 
@@
 
-\subsubsection{Integration}
-The system should capable of integrating data from different sources such as satellite data, high end, and low-end weather station, etc.
+\subsubsection{Integration }
+The system should be capable of integrating data from different sources such as satellite data, high end, and low-end weather station.
 And the system should be able to handle multidimensional spatial and temporal weather data efficiently and optimally.
@@
 Then the system should be able to fulfill weather models varying data requirements.
-Also, those models reproduce a large set of redundant data, thus the system should store the bulk data while optimizing the disk space.
+Also, those models reproduce a large set of redundant data.
+Thus the system should store the bulk data while optimizing the disk space.
 \subsubsection{Dissemination}
-Then different users should be able to retrieve data as they required.
-Also, the users should be able to easy to search into the available that in the system base on timeseries metadata or based on Geo queries.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% \paragraph{Timeseries}-- A timeseries is simply a series of data points ordered in time.
-In weather domain, it interest in timeseries in perspective of observations to forecasting.
-Each timeseries, the data points can be form in different formats as well.
-For example, scalar (0D), vector (1D), grid (2D), and polygon (2D).
-
-% In the proof of concept design described below, WDIAS focuses on handling scalar, vector and grid timeseries data. However, the system could be extended to handle polygon-based timeseries as well.
-
-% \subsubsection{Base of WDIAS architecture}
-% \hl{The base of WDIAS architecture origins based on attributes of a timeseries.} There are many attributes to differentiate timeseries one from another. But 
-% Among many attribute to differentiate a timeseries from another, the following can be consider as the key attributes in uniquely identify a timeseries from another: % for the \acrshort{wdias}.
-
-% \begin{itemize}
-%     \item Module -- module that generates the timeseries
-%     \item Value type -- Scalar, vector, grid, or polygon
-%     \item Location of readings
-%     \item Parameter -- measuared parameter
-%     \item hl{Timeseries type}
-%     \begin{itemize}
-%         \item Sources -- External or simulated
-%         \item Category -- Historical or forecast
-%     \end{itemize}
-%     \item Time step
-% \end{itemize}
-% \dbc{Use bullets only when essential. Other places use paragraphs.}
-
-% A detail description of the above attributes are presented in \cref{se:db_struct}.
+Then different users should be able to retrieve data as they require.
+Also, the users should be able to easily search into the available information in the system based on timeseries metadata or based on Geo queries.

### 2020-04-26 method/sec_1-architectural_decisions.tex
Updated -> Method - Microservices

@@
 The initial design of \acrshort{wdias} used the \acrfull{soa}.
-Moreover, it tried to use an \acrfull{esb} to integrate different modules, as \acrshort{esb} could act as a \hl{common layer} for all of the modules.
+Moreover, it tried to use an \acrfull{esb} to integrate different modules, as \acrshort{esb} could act as a shared layer for all of the modules to interact together.
 By default, \acrshort{esb} also provides publisher/subscribe (pub/sub) capabilities.
-\hl{Because \acrshort{esb} mediators can be used to integrate the modules which are described in Section} \ref{subse:modules_weather_data_integration_sys}. 
-\dbc{Last sentence incomplete too.}
 
@@
 A mediator can take a message, carry out some predefined actions on it, and output the modified message.
-These mediator capabilities can use to integrate the modules of a weather data system as shown in \cref{fi:wdia_components}.
+These mediator capabilities can be used to integrate the modules of a weather data system, as shown in \cref{fi:wdia_components}.
 \acrshort{esb} also supports different transportation protocols such as HTTP and Web sockets.
-However, it turned out that \acrshort{esb} is not suitable for data streaming or bulk data processing.
-Also, \acrshort{esb} suffers from a single point of failure, as all the messages are going through a common bus and slower communication (cant use for transfer data).
-
+However, we realized that \acrshort{esb} is not suitable for data streaming or bulk data processing.
+Also, \acrshort{esb} suffers from a single point of failure, as all the messages are going through a common shared bus and slower communication (can not be used for transfer data).
 In the second design phase of \acrshort{wdias}, we attempted to use the actor model using the AKKA framework \cite{HewittWhyModel} to overcome above \acrshort{esb} drawbacks.
 At the same time, we moved away from the \acrshort{soa} architecture design to the microservice architecture design.
-Thus we redesign the system architecture with decomposing into microservices and used actors to implement each microservice in the system.
-In that case, an actor or an actor with slave actors was a map to each microservice in \acrshort{wdias}.
+
+Thus we redesigned the system architecture with decomposing into microservices and used actors to implement each microservice in the system.
+In that case, we mapped each microservice in \acrshort{wdias} to an actor or an actor with slave actors.
 \acrshort{soa} focuses on imperative programming, while the microservices architecture focuses on a reactive actor programming style using faster messaging mechanisms.
-
-When compare to \acrshort{soa}, the microservice architecture has several advantages such as the following:
+When compared to \acrshort{soa}, the microservice architecture has several advantages:
 \begin{itemize}
     \item Follow the principle of a single responsibility.
-    \item Resilient / flexible because a failure of a service has no influence on other services.
-If you have monolithic or major service errors in a service / module, this can have an impact on other modules / functionalities.
-    \item High scalability because demanding services can be implemented on different servers to improve performance and stay away from other services so that they do not affect other services.
-It will be difficult to achieve the same with a single large monolithic service.
-    \item Easy to improve because the dependencies are less. It is also easier to change and test.
+    \item Resilient/flexible because a failure of service does not influence other services.
+If you have monolithic or significant service errors in a service/module, this can have an impact on other modules/functionalities.
+    \item High scalability because demanding services can be deployed on different servers to improve performance and stay away from other services so that they do not affect other services.
+It will be challenging to achieve the same with a single large monolithic service.
+    \item Easy to improve the system because the microservices are decoupled from other services. It is also easier to change and test each microservices.
     \item Little impact on other services because each service is independent.
@@
 
-% /hl{The typical \acrshort{soa} model, for example, usually has more dependent \acrshort{esb}s, with microservices using faster messaging mechanisms.
-\acrshort{soa} also focuses on imperative programming, whereas microservices architecture focuses on a responsive-actor programming style.}
-\dbc{Multiple design rounds and decisions are mixed in the para. First finish discussing ESB. Then finish actor model in another para. Then focus on mircoservice details.}
-
-Even with using the AKKA framework, it has some of the disadvantages of implementing each microservice as an actor as described in AKKA documentation \cite{Akka.ioWhenCluster}.
+The AKKA framework has some of the disadvantages of implementing each microservice as an actor, as described in AKKA documentation \cite{Akka.ioWhenCluster}.
 One of the attractive features of microservice architecture is the independent nature of the microservices.
-This allows choosing a different technology for each microservice based on the advantage that could bring in.
-Also allowed to independently develop and maintain by multiple smaller and more focused teams/communities.
-But using the actors as microservice, the actors messaging between different services cause to result in a too-tight code coupling between the services and difficulties deploying these independent of each other, which is one of the main reasons for using a microservices architecture \cite{Akka.ioWhenCluster}.
-To overcome these issues, we moved to the concept of container-orchestration based architecture.
-
-% \begin{itemize}
-%     \item \hl{Unable to choose technology. But} \acrshort{k8s} \hl{allows you to choose technology that is best suited for a particular functionality}
-%     \item \hl{As mentioned in the AKKA documentation} \cite{Akka.ioWhenCluster}, \hl{it is better for developing one microservice within the whole} \acrshort{wdias} design.
-% \end{itemize}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \subsection{Brief introduction to the \acrfull{k8s}}
-% \label{sebse:k8s_intro}
+The above concept allows choosing different technologies for each microservice based on the advantage that could bring in.
+Also, the microservice architecture will enable us to independently develop and maintain a system by multiple smaller and more focused teams/communities.
+But using the actors as microservice, the actors communicate using message passing cause to result in a too-tight code coupling between the services and difficulty to deploy services independent of each other, which is one of the main reasons for using a microservices architecture \cite{Akka.ioWhenCluster}.
+To overcome these problems, we moved to the concept of container orchestration based microservice architecture.
 
 Containerization is an alternative to virtualization that supports virtual machines or hypervisors.
-This includes encapsulating or grouping the software code and all its dependencies so that it can work uniformly and consistently in any infrastructure.
-\cite{IBMContainerizationExplained}.
-The concept of containerization and process isolation has emerged after the open-source Docker Engine \cite{DockerAppContainerization}, an industry standard for package software into standardized units for development, shipment, and deployment.
+It includes encapsulating or grouping the software code and all its dependencies so that it can work uniformly and consistently in any infrastructure \cite{IBMContainerizationExplained}.
+The concept of containerization and process isolation has emerged after the open source Docker Engine \cite{DockerAppContainerization}, an industry standard for package software into standardized units for development, shipment, and deployment.
 
-The \acrshort{wdias} is using \acrfull{k8s} as the container orchestration system which is an open-source tool for automating deployment, scaling, and management of containerized applications \cite{LinuxFoundationProduction-GradeKubernetes}.
+The \acrshort{wdias} used \acrfull{k8s} as the container orchestration system.
+\acrshort{k8s} is an open-source tool for automating deployment, scaling, and management of containerized applications [15].
 It groups the containers that make up an application into logical units for easy management and detection.
-While implementing the \acrshort{wdias}, we used \acrshort{k8s} as the container-orchestration system, to deploy each microservice as container and manage with providing scalability and availability.
+Using \acrshort{k8s}, we deploy each microservice as a container and manage it by providing scalability and availability.
 
@@
 \end{figure}
+
 \cref{fi:k8s_architecture} gives an overall idea on the components of \acrshort{k8s},
 \begin{itemize}
-    \item pods -- Cluster of containers that can group other container images in a single unit.
-    \item nodes -- The machines (VMs, physical servers, etc) in a cluster that runs your applications and cloud workflows.
-    \item kubelet -- An agent that runs on each node in the cluster. It makes sure that containers are running in a pod.
-    \item kube-proxy -- A network proxy that runs on each node in the cluster, and maintains network rules on nodes.
-    \item kubernetes master -- Responsible for maintaining the desired state for your cluster.
-    \item etcd -- Consistent and highly-available key value store used as Kubernetes’ backing store for all cluster data.
+    \item pods – Cluster of containers that can group other container images in a single unit.
+    \item nodes – The machines (VMs, physical servers, etc) in a cluster that runs your applications and cloud workflows.
+    \item kubelet – An agent that runs on each node in the cluster. It makes sure that containers are running in a pod.
+    \item kube-proxy – A network proxy that runs on each node in the cluster, and maintains network rules on nodes.
+    \item kubernetes master – Responsible for maintaining the desired state for your cluster.
+    \item etcd – Consistent and highly-available key value store used as Kubernetes backing store for all cluster data.
 \end{itemize}
 
-Users can add much as required Nodes into the \acrshort{k8s} cluster, and \acrshort{k8s} manage and deploy applications as pods into cluster nodes.
-Each microservice can deploy as a pod which is a group of containerized applications. And \acrshort{k8s} able to scale as much as the user wants as described above.
+Users can add much as Nodes required into the \acrshort{k8s} cluster, and \acrshort{k8s} manage and deploy applications as pods into cluster nodes.
+Each microservice can deploy as a pod, which is a group of containerized applications.
+And \acrshort{k8s} is able to scale as much as the user requirements by deploying multiple copies of the same pod.
 By separating each microservice as a container, and running them as multiple pods inside the \acrshort{k8s} removes the tight coupling of microservices when compared to the actors.
-This preserves the independent nature of the microservices which allows to high scale the system.
+It preserves the independent nature of the microservices and supports the high scalability of the system.

### 2020-04-26 method/sec_3-microservice.tex
Updated -> Method - Microservices

@@
 
-A microservice architecture style is an approach to developing a single application as a package of small services, each working in their own process and communicating with lightweight mechanisms, often through the delivery of \hl{a RESTful API}.
+A microservice architecture style is an approach to developing a single application as a package of small services, each working in their process and communicating using lightweight mechanisms, often through the delivery of a \acrfull{rest} \acrshort{api}.
 These services are built around commercial capacities and can be used independently by fully automated implementation machines \cite{LewisMicroservices}.
-\hl{These services are implemented independently with minimizing the centralized dependencies.
-Thus each microservice may be written in different programming languages and use different data storage technologies}.
+In a microservice architecture, each microservice implements decoupling from other microservices and minimizing the centralized dependencies.
+Thus, we can use different programming languages and data storage technologies to implement each microservice.
 
-% \hl{Among the characteristics of microservice, a few characteristics heavily affect while moving from} \acrshort{soa} to microservice.
 There are lots of microservice patterns developed and evolved.
-Throughout the following sections, we will discuss in brief some of the microservice design patterns mostly used in the context of designing \acrshort{wdias} architecture.
-Next, we will discuss how microservice architecture promote to only to create endpoints which only belong to each service logical domain.
-Next, discuss only using database per service which allows to loosely couple between systems and achieves high scalability.
-In Sagas, we discuss how distributed transactions can achieve over microservices.
-Next, we will discuss a concept called \emph{the scale cube}, which explains the scalability from the perspective of x,y, and z-axis.
+Through the following sections, we will discuss some of the microservice design patterns mostly used in the context of designing the software architecture for our research in brief.
+Next, we will discuss how microservice architecture promotes only to create endpoints that solely belong to each service logical domain.
+Next, consider only using a database per service, which allows it to be loosely coupled between systems and achieves high scalability.
+Then we will discuss how distributed transactions can makeover microservices.
+Last, we will discuss a concept called \emph{the scale cube}, which explains the scalability from the perspective of x,y, and z-axis.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Smart Endpoints and Dumb Pipes}
+\subsection{Smart Endpoints and Dumb Pipes  Microservice Pattern}
 \label{subse:dumb_pipes}
-\dbc{At the end of previous para tell what will be discussed in the next set of sub-section. A single sentence like "Next, we will discusss ...." is enough}
-\gkc{FIXED}
 
-When building communication endpoints, \hl{many architectural approaches are adding significant smart by providing different protocol supports and complex logic support via the endpoints.} As an example \acrshort{esb} support multiple protocols and endpoints can use complex logic.
+When building communication endpoints, many architectural approaches are adding significant smart by providing different protocol supports and complex logic support through the endpoints.
+As an example, \acrshort{esb} supports multiple protocols, and endpoints can be used to implement complex logic.
 But microservice architecture follows an alternative approach called as \emph{Smart endpoints and dumb pipes} \cite{LewisMicroservicesPipes}.
-Applications built on the basis of microservices are intended to be as disconnected and as coherent as possible.
-They have their domain logic and work more like filters in the classical Unix meaning.
-After receiving a request, apply the correct logic and produce a response.
-And it uses simple RESTful protocols instead of complex protocols.
-\dbc{RESTish or RESTful?}
-\gkc{Yes. Changed.}
+Applications built based on microservice architecture are intended to be as disconnected and as coherent as possible.
+Each microservice has its domain logic and independent of other microservices logic and works more like filters in the classical Unix pipelines.
+Each microservice provides its functionalities as a \acrshort{rest} \acrshort{api} instead of using complex protocols.
+After receiving a request for each microservice through its \acrshort{rest} \acrshort{api}, it applies the correct logic and produces a response.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{\hl{Database per Microservice}}
+\subsection{Database per Microservice Microservice Pattern}
 \label{subse:database_per_service}
 
-\acrshort{microservice} prefers to have each service manage its database, either different instances of the same database technology or entirely different database systems - an approach called \emph{Polyglot Persistence} \cite{LewisMicroservicesManagement}.
+\acrshort{microservice} prefers to have each microservice manages its database, either different instances of the same database technology or entirely different database systems - an approach called \emph{Polyglot Persistence} \cite{LewisMicroservicesManagement}.
 
-The idea is to keep the persistent data of each microservice private for this service and only to make it accessible via the \acrshort{api}.
-There are different ways to keep the permanent data of a service private.
-It is not necessary to set up a database server for each service.
-For example, when you use a relational database, the following methods can be used to keep the data private.
-\cite{RichardsonMicroservicesService}:
+The idea is to keep the persistent data of each microservice private for this service and only to make it accessible through an \acrshort{api}.
+There are different ways to keep the permanent data of a microservice private.
+But it is not required to set up a database instance for each microservice.
+For example, when you use a relational database, the following methods can be used to keep the data private \cite{RichardsonMicroservicesService}:
 \begin{itemize}
-    \item \emph{Private tables per service} –- each service has a set of tables that this service should not have access to.
-    \item \emph{Schema per service} –- each service has a private database schedule for this service.
-    \item \emph{Database server per service} -– each service has its database server.
+    \item Individual tables per service - each microservice has a set of tables that restricts access for other microservices.
+    \item Schema per service - each service has a private database schedule for a given microservice.
+    \item Database server per service - each service has its database server.
 \end{itemize}
-\emph{private tables per service} and \emph{schedule per service} have the lowest overhead.
-The use of an \emph{schedule per service} is interesting because it makes the property clearer.
+
+\emph{Private tables per service} and \emph{schema per service} have the lowest overhead.
+The use of a schema per service is interesting because it makes the property clearer.
 Some high throughput services may require their database server.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{\hl{Distributed Transactions over Microservices}}
+\subsection{Distributed Transactions over Microservices Pattern}
 \label{subse:sagas}
-To guarantee a loose coupling, every microservice can have its own database.
-Maintaining data consistency between services is a challenge because 2 phase-commit/distribution transactions are not an option for many applications.
-A service publishes an event when the data changes.
+
+Every microservice can have its database to guarantee a loose couple between microservices.
+Maintaining data consistency between services is a challenge because two phase-commit/distribution transactions are not an option for many applications.
+To archive distributed transactions, a service publishes an event when the data changes.
 Other services use this event and update their data \cite{RichardsonMicroservicesSagas}.
-This is also called the \emph{Saga pattern}.
+The above approach is also called the \emph{Saga pattern}.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{\hl{Concept of Scale Cube}}
+\subsection{The Scale Cube Concept}
 \label{subse:scale_cube}
-\gkc{I can not think about any other title than this.}
-The scalability of a system can explain via a concept called \emph{Scale Cube} which talks about the scalability of the application by defining over X, Y and Z axis.
 
-\paragraph{X-axis Scaling}-- When scaling the X-axis, multiple instances of an application execute behind a load balancer.
-If there are \textit{n} copies then each copy handles 1/\textit{n} of the load.
-A commonly used simple approach to scaling a service.
+The scalability of a system can be explained via a concept called \emph{the Scale Cube}, which talks about the scalability of the application by defining over X, Y, and Z axes.
 
-\paragraph{Y-axis Scaling}-- When compared to the Z-axis and X-axis scaling, which follows the concept of running multiple identical copies of the application, but Y-axis axis scaling segregate the application into multiple services in same domain.
-So, the end services are responsible for one or more closely related functions.
+\paragraph{X-axis Scaling}-- When scaling an application through the X-axis, multiple instances of the application execute behind a load balancer.
+If there are \textit{n} copies, then each copy handles 1/\textit{n} of the load.
+The above simple approach is commonly to scale a service.
+
+\paragraph{Y-axis Scaling}-- When compared to the Z-axis and X-axis scaling, which follows the concept of running multiple identical copies of the application, but Y-axis scaling segregates the application into multiple services in the same domain.
+So, the end services are responsible for one or more closely related functions of the previous service before the segregation.
 There are different ways to split the application into services.
 \begin{itemize}
-    \item verb-based decomposition. e.g., checkout.
-    \item decompose the application by noun. e.g., order management. 
-    \item it possible to use a combination of verb-based and noun-based decomposition for an application.
+    \item Verb-based decomposition. e.g., checkout.
+    \item Decompose the application by the noun. e.g., order management.
+    \item It is possible to use a combination of verb-based and noun-based decomposition for an application.
 \end{itemize}
-
 \emph{The microservice architecture is an application of Y-axis scaling}.
 
-\paragraph{Z-axis Scaling}-- The Z-axis scaling is following the concept of each service runs an same application code (similar to X-axis scaling).
+\paragraph{Z-axis Scaling}-- The Z-axis scaling follows the concept of each service running the same application code (similar to X-axis scaling).
 The big difference is that each service is responsible for only a subset of the data.
-Z-axis splits are commonly used to scale databases. Data is partitioned (a.k.a. sharded) across a set of servers based on an attribute of each record.
-
-Even \acrshort{wdias} is a design based on the Y-axis scaling, it is possible to use the Z-axis scaling to scaling the system further. This will be more discussion in \cref{se:discussion}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \subsection{Brief introduction to the \acrfull{k8s}}
-% \label{sebse:k8s_intro}
-\dbc{Don't present this as a separate section. Either this need to be in the literature survey, or integrate key ideas into another section as a paragraph.}
-\gkc{Move this as a paragraph at the end of the architectural decisions}
+Z-axis splits are commonly used to scale databases.
+As an example, data partition (a.k.a.
+sharded) across a set of servers based on an attribute of each record.
+Even our research is a design based on the Y-axis scaling; it is possible to use the Z-axis scaling to further scaling the system. We will discuss more detail in \cref{se:discussion}.
 
@@
 \label{sebse:wdias_microservices}
-As seen in Figure of \cref{fi:wdias_micro_on_demand} and \cref{fi:wdias_micro_async} each circle represents a microservice in the \acrshort{wdias}, and those are implemented as containerized applications.
+
+\cref{fi:wdias_micro_on_demand} and \cref{fi:wdias_micro_async} show the system interaction of the WDIA microservices architecture while handling the requests.
+Each circle in the Figures represents a microservice in the \acrshort{wdias}.
+And each microservice is implemented as a containerized application.
+The left side of \cref{fi:wdias_micro_on_demand} shows the import modules of the \acrshort{wdias}, and the right side shows the export modules.
+Also, we implemented each module as a microservice to independent maintainability and upgradability.
+We followed the concept of smart endpoints and dumb pipes explained in \cref{subse:dumb_pipes}, and each import microservice only does the specific task of converting and forwarding the request to the correct data adapter module.
+For scalar, vector, and grid data types, we created adapter microservices that are optimized for storing such kinds of data.
+And the metadata data of the timeseries store using an RDBMS, which gives more performance over retrieving timeseries metadata.
+The metadata is cached using an In-Memory database to fast access while implementing the database structure.
+The system generates a unique identifier for each timeseries, and throughout the \acrshort{wdias} system, all microservices use it to handle data for fast access.
+
 \begin{figure}[htp]
@@
 \end{figure}
-The left side of \cref{fi:wdias_micro_on_demand} shows the import modules of the \acrshort{wdias}, and the right side shows the export modules.
-As explained \cref{subse:dumb_pipes}, each import microservice only does the specific task of converting and forwarding the request to the correct data adapter module.
-For each data type, there is an adapter microservice is running which is optimized to storing such type of data.
-And the metadata data of the timeseries store using \acrshort{rdbms} which gives more performance over retrieving metadata data.
-The metadata is cached with the In-Memory database to fast access as mentioned in \cref{subse:redis}.
-The system generates a unique identifier for each timeseries, and throughout the \acrshort{wdias}, other microservice use it to handle data for fast access.
+
+Export module microservices also follow the concepts of single responsibility and provide the capability to export the data into required formats of the weather models.
+Each data type adapter follows the microservice architecture concept of database per service, as mentioned in \cref{subse:database_per_service} When the system requires more database throughput, it is easy to scale each database instance by adding more resources or using Z-axis scaling concepts.
 
@@
 \end{figure}
-Export module microservice follows the same concepts and provides the capability to export the data into required formats of the weather models.
-Each adapter follows the concept of database per service as mentioned in \cref{subse:database_per_service}.
-This gives the freedom for \acrshort{wdias} to scale better with \acrshort{k8s}.
 
-As shown in \cref{fi:wdias_micro_on_demand}, when a smaller size request comes to the system, it handles on-demand and response back.
-However, as shown in \cref{fi:wdias_micro_async}, when a request with a larger size comes to the system, it stores the data for asynchronously process the data and responds with a unique id that can use to verify whether data processed successfully or not.
-Here is uses the microservice concept of Saga as mentioned in \cref{subse:sagas} while processing the Grid data.
-First, it stores the data and responds to the user.
-Then publish an event, and another service listens to those events and process the data and update the system status.
+As shown in \cref{fi:wdias_micro_on_demand}, when a request with a smaller payload comes to the system, the system handles the request on-demand and response back.
+However, as shown in \cref{fi:wdias_micro_async}, when a request with a larger payload comes to the system, it stores the data for an asynchronous process and responds with a unique id that can be used to verify whether data processed successfully or not.
+We used the microservice concept of Saga, as mentioned in \cref{subse:sagas}, while processing the Grid data.
+First, it stores the data and responds with a unique identifier to the user.
+After successfully storing the data, the microservice publishes an event.
+Another microservice listens to those events and processes the data and updates the system status.
 
@@
 \end{figure}
+
 \cref{fi:wdias_micro_separation} shows the clear separation of microservices into the modules of the \acrshort{wdias}.
-As shown, each adapter has an isolated database, and the database is hosted separately for the high performance.
-Apart from that, as we further discuss in \cref{se:data_preprocess}, the extension modules are running separately such as Interpolation, Transformation, and Validation, etc. 
-The Extension Adapter allows users to register new triggers for the extensions. And extension scheduler triggers the events based on time and extension handler triggers event based on data change.
+Each adapter has a separate database, and the database is hosted separately for the high performance and to avoid interferences.
+Apart from that, as we further discuss in \cref{se:data_preprocess}, the extension modules are running independently, such as Interpolation, Transformation, and Validation, and we will also discuss in \cref{se:data_preprocess}.
+The Extension Adapter allows users to register new event-based or time-based triggers for the extensions.
+The extension scheduler triggers the events based on time and the extension handler triggers events based on data change.
 
@@
 \label{sebse:wdias_api}
-One of the main design considerations in \acrshort{wdias} is the convention of defining the \acrshort{api}. It follows a simple RESTful \acrshort{api}, and allow users to interact with HTTP methods.
 
-\emph{Timeseries} endpoints allow users to interact with Metadata Adapter, and those are cache on the Query Handler to perform search queries.
-These are the main endpoints to handle timeseries metadata which defines unique timeseries identifier based on the metadata values.
-As an example, if it needs to extend the system to store irregular grid data, then it should add another set of location endpoints for storing irregular grid location details.
+We defined an \acrfull{rest} as the communication layer for \acrshort{wdias}, and it affects the microservice architecture design as well.
+It follows a simple \acrshort{rest} \acrshort{api} and allows users to interact with the system through HTTP methods.
+
+We provided a set of timeseries endpoints to register new timeseries metadata before storing the real data.
+Timeseries endpoints allow users to interact with Metadata Adapter to create and update the timeseries metadata.
+And create timeseries metadata, we cached on the Query Handler to perform search queries and geo-indexed to support geo-based queries.
+When a user registers a timeseries metadata, the system generates a unique timeseries identifier based on the metadata values.
+Then the user can use that identifier to store the real weather data and retrieve stored data.
+
 \begin{itemize}
@@
     \end{itemize}
-\dbc{Format others as above}
-\gkc{FIXED}
     \item location
@@
 
+Current \acrshort{wdias} only supports handling point locations and grid locations.
+If it needs to extend the system to store irregular grid data, then it should add another set of location endpoints for storing irregular grid location details.
+
 \emph{Import} endpoints allow to upload data into the \acrshort{wdias} system.
@@
 
-\emph{Extensions} endpoints for configure extensions. These details describes in the \cref{se:data_preprocess}.
-
-As mentioned above, other than the timeseries metadata which is the core of the data system, other module endpoints start with the module name such as import, export, and extension.
-This allows adding a new module system if required.
-For import and export modules, then follows by the data format. This provides the flexibility to integrate new data format modules. 
-Then the endpoint name ends with the data upload/insert data type.
+Other than the above endpoints, we exposed another set of endpoints to configure extensions, and we will describe further in \cref{se:data_preprocess}.
+Other than the timeseries metadata, as mentioned in the list of endpoints, other module endpoints start with the module name such as import, export, and extension.
+Using the above convention, we allowed adding a new module system if required.
+For import and export modules, the names of the endpoints defined as the modules name then follow the data format.
+The above endpoint naming convention provides the flexibility to integrate new data format modules for import and export.
+Then the endpoint name ends with the type of data operation.
 Data can upload as a single file with binary or multiple files with the upload.
-Or in the body of the request as raw, and need to send the required headers has mentioned by a particular module.
+Other than that, users can send requests with raw data with required headers has mentioned by a particular import module.
 Thus the \acrshort{api} convention of \texttt{\hl{/MODULE/DATA\_FORMAT/DATA\_TYPE}} allows users to integrate new import or export modules into the system as well as add new data types.

### 2020-04-26 method/sec_4-db_struct.tex
Updated: DB Structure

@@
 
-The foundation of the \acrshort{wdias} is data-centric.
-To understand the underline design decisions of the \acrshort{wdias} database structure, it needs to deeply look into the weather data timeseries.
+The foundation of the \acrshort{wdias} is data-centric. We need to look into the weather data timeseries deeply to understand the underline design decisions of the \acrshort{wdias} database structure.
+
 \paragraph{Timeseries}-- \emph{A timeseries is simply a series of data points ordered in time}.
-In the weather domain, its interest in timeseries in perspective of observations to forecasting.
+In the weather domain, we are interested in observation and forecasting timeseries data.
 Each timeseries, the data points can be formed in different formats as well.
@@
 
-As per the above interpretation, a timeseries have data points ordered in time.
-Other than that, timeseries have other information which is known as \emph{timeseries metadata} which can use to uniquely identify one timeseries from another.
-As an example, a weather station can be placed on a location and it can keep measure variables which are called \emph{parameters} such as temperature, precipitation and wind direction which can produce different timeseries.
-Even we can use the location as metadata to identify the timeseries, that is not enough to separately identify the parameters.
-Thus we need to use a set of attributes to uniquely identify a timeseries.
-In the next \cref{subse:timeseries_key_attributes}, we describe key attributes which are using by the \acrshort{wdias} to uniquely identify a timeseries.
-
-\dbc{Clearly mention why a hierarchical design is needed.}
-\gkc{Added it after the \cref{subse:timeseries_key_attributes}}
+Based on the above interpretation, a timeseries have data points ordered in time.
+Other than that, timeseries have additional information that is known as \emph{timeseries metadata}, which can use to identify one timeseries from another uniquely.
+As an example, we can place a weather station on a \emph{location}, and it can measure different types of weather data that are called \emph{parameters} such as temperature, precipitation, and wind direction.
+Each parameter can produce different timeseries.
+Even we can use the location as metadata to identify the timeseries, but that is not enough to distinctly identify the parameters.
+Thus we need to use a set of attributes to identify a timeseries uniquely.
+In the next \cref{subse:timeseries_key_attributes}, we describe key attributes that are used by the \acrshort{wdias} to identify a timeseries uniquely.
 
@@
 
-\paragraph{Location}-- Location of the timeseries. All locations have a unique String identifier called locationId. Further, two types of location types are interested in the WDIAS, namely:
+\paragraph{Location}-- Location of the timeseries.
+All locations have a unique String identifier called \emph{locationId}.
+Further, two types of location types are interested in the \acrshort{wdias}, namely:
 \begin{itemize}
   \item \emph{Point locations}-- Contains a name that is human readable. lat and lon of the location on the earth surface.
-  \begin{lstlisting}[language=Python]
+  \begin{lstlisting}[language=Python, lastline=-1]
     {
@@
   \end{lstlisting}
-  \dbc{Remove additional line.}
-  \gkc{This space is adding by itemize. I applied in all the places. Could not find how to remove it. Otherwise, need to remove itemize.}
   \item \emph{Regular Grid locations} -- Contains a name that is human readable. The grid presents by dividing into equal size cells. Thus, it needs the number of rows and columns. 
@@
 Parameter describes the variable measuring against a location.
-All parameters have a unique String identifier called \emph{parameterId}.
+All parameters should have a unique string identifier called \emph{parameterId}.
 A parameter can be used in multiple locations.
-While defining a parameter, three required fields need to be provided such as variable, unit and \emph{parameterType}.
+While defining a parameter, three required fields need to be provided, such as variable, unit, and \emph{parameterType}.
 
@@
 \subsubsection{Timeseries Type}
-Timeseries Type can be redefined with the system setup. \acrshort{wdias} defined the following types for during the setup. Timeseries type can be a combination of a source followed by category:
+Users can define timeseries type while setup the system. We determined the following types as the default values. Timeseries type can be a combination of a source followed by category:
 \begin{itemize}
@@
 \end{itemize}
-\dbc{Explain each with sufficient detail.}
-\gkc{FIXED}
 
 \paragraph{Time Step}-- All TimeSteps has a unique String identifier called timeStepId.
-Unit should be one of Second, Minute, Hour, Day, Week, Month, Year, or NonEqualDistance.
-One of multiplier or divider can be used to define the interval between each measurement.
+The unit should be one of Second, Minute, Hour, Day, Week, Month, Year, or NonEqualDistance.
+One of multipliers or dividers can be used to define the interval between each measurement.
 \begin{lstlisting}[language=Python]
@@
 Among the above key attributes; Location, Parameter and Time Step attributes are composite attributes. But each of them has a unique identifier.
-Given that, a timeseries can uniquely identify by moduleId, valueType, parameterId, locationId, timeseriesType and timeStepId.
+Given that, a timeseries can uniquely identify by \emph{moduleId, valueType, parameterId, locationId, timeseriesType and timeStepId}.
 \begin{lstlisting}[language=Python]
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Even a timeseries consists of data points, the data for each data point can vary based on the valueType.
-Scalar data point only consist of a single value.
-And Vector data point consists of two values such as magnitude and the direction of the Vector.
+Even if a timeseries consists of data points in time ordered, the data for each data point can vary based on the valueType.
+The scalar data point consists of a single value.
+And the vector data point consists of two values, such as magnitude and the direction of the vector.
 But for Grid data, a point can consist of multiple values.
-To get the advantage of storing data efficiently, we can use a set of different databases based on the advantage of using them for each valueType.
-Other than the valueType attribute, other attribute does not much impact on the data size.
+To store data efficiently, we used a set of different databases based on the advantage of using them for each valueType.
+Other attributes do not have much impact on classifying the timeseries data.
 
-Further, it is will be difficult to search for the timeseries data, if those are stored over multiple data sources, and difficult to avoid having duplicates.
+It is difficult to search for the timeseries data if those are stored over multiple data sources and trying to avoid having duplicates.
 Thus it adds low overhead to have a single data source to look into while searching for the timeseries metadata.
-The load on the above data source can reduce by using a caching mechanism.
-To support search queries with lower latency, it required to use indexing for the fast search for timeseries metadata.
-Further, Geo-based indexing is required to support Geo-based search queries based on the locations.
+The efficiency of searching for timeseries metadata can increase by using a caching mechanism.
+To support search queries with lower latency, we used an index for the fast search for timeseries metadata, and a geo-based index to support geo-based search queries.
 
-Considering the above facts, we can not achieve all of the benefits using one of the database systems available.
-Thus it required to have a database structure that is capable of proving all of the above capabilities via combining.
-According to the design principle of microservices architecture, we created microservice for each of the valueType with following the concept of Database per Service as described in the \emph{Database per Service} in \cref{subse:database_per_service}.
-In \cref{sebse:wdias_microservices} those microservices are group as \emph{adapters} that share an \acrshort{api} to interact with while keeping the persistent data private.
+Many modern database systems give a higher performance on a specific type of application.
+Thus, we need to use the correct database system based on application requirements.
+Considering the aforementioned database requirements, we can not get all of the benefits using a single general database system available.
+Thus we created a database structure after carefully choosing database systems per the system requirements and combining their capabilities.
+According to the design principle of microservices architecture, we created microservice for each of the valueType.
+Here we followed the concept of \emph{database per service} as described in in \cref{subse:database_per_service}.
+In \cref{sebse:wdias_microservices}, those microservices are grouped as \emph{adapters} that share an \acrshort{api} to interact with while keeping the persistent data private.
 
@@
 
-\dbc{Fig. 3.6 needs a more meaningful title.}
-\gkc{Updated. I think hierarchical database does not make sense in this case. May be that's why you asked for change few time, sir.}
-
 \cref{fi:database_structure} shows the \acrshort{wdias} database structure.
@@
 \label{subse:mysql}
-\dbc{Needs a more meaningful Sec. title}
-\gkc{UPDATED}
 
-As described in the above section, to reduce the overhead while searching for timeseries and handling duplicates, it required to have a timeseries metadata store.
-Since metadata consists of multiple key attributes, the data can be efficiently store using a \acrfull{rdbms}.
-This helps to store data without any duplicates and store the data with normalization.
-As an example, the parameter attribute can have one or two dozen of values.
-Using an \acrshort{rdbms}, those values can be stored once and reuse with defining timeseries against location via reference.
+To reduce the overhead while searching for timeseries and handling duplicates, we used a timeseries metadata store.
+Since metadata consists of multiple key attributes, the data can be efficiently stored using a \acrfull{rdbms}.
+It helps to store data without any duplicates and optimize the data with normalization.
+As an example, the parameter attribute can only have a dozen possible values.
+Using an \acrshort{rdbms}, those values can be stored once and reuse with defining timeseries against location via references.
 
-\acrshort{wdias} is using SQL as the \acrfull{rdbms}. 
-Since the \acrshort{wdias} scope is to use open source tools, it is using  MySQL as a persistent database for storing timeseries metadata described above.
-One instance of  MySQL is using only by adapter-metadata service.
-Other than that, another instance of  MySQL is using for adapter-extension which will be described in more detail \cref{se:data_preprocess}.
- MySQL is used only for these services, those will only keep the consistency of the schema for timeseries metadata and extension metadata.
-As mentioned in \cref{subse:redis}, it uses  Redis instance is using for caching the data from  MySQL, since the  MySQL database instances, itself not going to get much load.
-Other than MySQL, many open source databases can be used to replace the same functionality.
-\dbc{First start with a brief discussion on why a RDBMS is needed}
-\gkc{ADDED}
+We used SQL as the \acrshort{rdbms}.
+Since one of \acrshort{wdias} main goals is to use open source tools, it used MySQL as a persistent database for storing timeseries metadata described above.
+One MySQL instance used only for adapter-metadata service.
+Other than that, another MySQL instance used for adapter-extension.
+We will explain in more detail in \cref{se:data_preprocess}.
+We used MySQL only for the above services, and those database instances keep the consistency of the schema for timeseries metadata and extension metadata.
+Further, we used an In-Memory database instance for caching the requested metadata to reduce the load on the MySQL database instances while repeated queries.
+Other than MySQL, many open-source SQL databases can be used to replace the same functionality.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{In-Memory Database}
+\label{subse:redis}
+
+We used Redis \cite{redisRedisDocumentation} as the In-Memory database since it is a widely used database system with excellent support.
+It also supports Publisher Subscriber capabilities as an inbuilt feature.
+Redis is an open-source (BSD licensed).
+Clustering is available for scalability.
+Redis uses in-memory caching for fast access to the frequent access data in adapter-metadata and adapter-extension.
+Other than that, adapter-status uses Redis as a key-value pair store to maintain the status for async requests handling while storing grid data.
+The adapter-extension uses Redis's Publisher Subscriber capabilities to create a cronjob in extension-scheduler when a new extension creates with a trigger on time during data preprocessing.
 
@@
 \label{subse:influxdb}
-Among several timeseries open source databases,  InfluxDB \cite{influxdbInfluxDBDocumentation} \hl{is using a unique database indexing algorithm to gain higher performance while storing timeseries data} when compared to other databases available.
-Also, it has better support, higher usage and has following supports;
+
+Among several timeseries open source databases, InfluxDB \cite{influxdbInfluxDBDocumentation} uses a unique database indexing algorithm to gain higher performance while storing timeseries data when compared to other modern databases available.
+Also, it has better support, higher usage, and following supports;
+
 \begin{itemize}
@@
 \end{itemize}
-Other than  InfluxDB, another database is Elastic Search which is mainly using for indexing for searching.
-With changing the configurations of the  InfluxDB, it is possible to adapt as required. As mention in \cite{influxdbInfluxDBDocumentation}, 
- InfluxDB can setup on a computer that will give the required performance. Going further, users can use the commercial version of  InfluxDB to gain more performance.
 
-Two instances of  InfluxDB is using in the WDIAS system by adapter-scalar and adapter-vector services.
-For the scalability, the system uses \emph{Database per Service} as mentioned in \cref{subse:database_per_service}.
-But further, it split into two services, referring to \cref{subse:scale_cube}, the Z-axis scaling, the data is partitioned among a few servers based on valueType key attribute of timeseries.
-Which also conclude the concept of splitting into more services based on other key attributes such as timeseriesType, if further performance required.
+Other than InfluxDB, the ElasticSearch database can be used, but it mainly uses indexing for searching.
+InfluxDB allows us to change the read/write behavior and indexing mechanism via database configurations.
+Further, users can use the commercial version of InfluxDB to gain more performance, like database sharding and replicas.
+
+Two individual instances of InfluxDB used for adapter-scalar and adapter-vector services in the \acrshort{wdias} system.
+For the scalability, the system uses \emph{database per service}, as mentioned in \cref{subse:database_per_service}.
+If users want further performance, the database can split into another set of partitions based on other key attributes based on the Z-axis scaling described in \cref{subse:scale_cube}.
+As an example, scalar and vector adapters can further split into more services based on other key attributes such as timeseriesType.
 
@@
 \label{subse:netcdf}
-\acrshort{netCDF} \cite{unidataUnidataNetCDF} is a self-describing, machine-independent data formats that support the creation, access, and sharing of array-oriented scientific data.
-And it also has the support for parallel file access.
-NetCDF is widely using in the scientific domain due to it has the capability of storing data in multi-dimensions easily and flexibility with storing many of the scientific data.
-Due to its capability of storing scientific data efficiently, \acrshort{wdias} using it for storing the Grid data.
+
+\acrshort{netCDF} \cite{unidataUnidataNetCDF} is a self-describing, machine-independent data format that supports the creation, access, and sharing of array-oriented scientific data.
+Moreover, NetCDF also supports parallel file access.
+NetCDF is widely used in the scientific domain due to the capability of storing multi-dimensions data efficiently and flexibly.
+Thus, we used NetCDF for storing the grid data due to its capability of storing array-oriented scientific data efficiently when compared to other database systems.
 
@@
 
-\acrshort{wdias} is using  MongoDB as the document-oriented database, as it has the Geo searching capabilities.
- MongoDB \cite{mongodbMongoDBManual} is a general-purpose, document-based, distributed database. And it supports:
-\dbc{Need for a mix of relational, time series, document stores, and in-memory need to be first mentioned and justified in high-level design of WDIAS above.}
-\gkc{Adding those details in \cref{se:high_level_design} may confuse the reader.
-At that point it didn't go through that much of details of the wdias.
-I added some justification at the end of \cref{subse:timeseries_key_attributes}.
-Let me know if we want to highlight it with a different section there.}
+To provide fast geo-search queries, we have to use a database system that supports geo indexing.
+We used MongoDB, which is a document-oriented database with Geo indexing capabilities.
+Also, MongoDB \cite{mongodbMongoDBManual} is a general-purpose, document-based, distributed database, and supports:
+
 \begin{itemize}
@@
 \end{itemize}
- MongoDB geospatial features are using to support Geo queries in the WDIAS. Other than that, external timeseries metadata queries are served by the indexed timeseries metadata data.
-If metadata not present in the adapter-query if fetch data from the adapter-metadata, then indexed and cache in the  MongoDB.
-Vise a versa, if new timeseries create in the adapter-metadata, it triggers an event to adapter-query to index the new timeseries.
-In \cref{subse:scale_cube}, the Y-axis scaling concept is using here by splitting into the multiple services based on the functionality and scale of the system.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{In-Memory Database}
-\label{subse:redis}
-\acrshort{wdias} is using  Redis \cite{redisRedisDocumentation} as the In-Memory database, since it is a widely used tool with good support, and it supports few other features such as Publisher Subscriber capabilities.
- Redis is an open-source (BSD licensed), used as a database, cache. Clustering is available for scalability.
- Redis uses as in-memory caching for fast access the frequent access data in adapter-metadata and adapter-extension.
-Other than that, adapter-status uses  Redis as a key-value pair store for getting the status for async handling requests such as storing Grid data.
-In adapter-extension uses Redis's Publisher Subscriber capabilities to create a cronjob in extension-scheduler when a new extension creates on \cref{se:data_preprocess}
+We used MongoDB geospatial features to support Geo queries in the \acrshort{wdias}.
+Also, we indexed the timeseries metadata with other indexing features to serve external timeseries metadata queries.
+If particular timeseries metadata not present in the adapter-query, then fetch metadata from the adapter-metadata and indexed in the MongoDB.
+Vise a versa; when a new timeseries created in the adapter-metadata, it triggers an event to index metadata in the adapter-query.
+Here we used the \emph{Y-axis scaling} concept by splitting metadata search into multiple services.
+Within the system, it uses In-Memory database cache to support internal metadata access, and external search queries fulfill by the adapter-query with using MongoDB.

### 2020-04-26 method/sec_5-data_preprocess.tex
Updated -> Method

@@
 
-The data imported via import modules may have incorrect data, missing data and not compatible with direct feed into simulation modules. 
-Thus it required to preprocess the data before use it.
-The WDIAS supports these capabilities via the \emph{extension} modules.
-The current system has a few inbuilt extensions such as Interpolation, Transformation, and Validation.
-Other than those, it possible to add more extensions as required.
+The data imported via import modules may have incorrect data, missing data, and incompatible data which can not directly feed into simulation modules.
+Thus we need to preprocess imported data before using it for forecasting.
+The WDIAS supports data preprocessing capabilities via the extension modules.
+The current system has a few inbuilt extensions such as Interpolation, Transformation, and Validation, but users can add more extensions as required.
+
 \begin{figure}[htp]
@@
 
-The WDIAS provides the support via a simple generic mathematical function model.
-Each extension is considering as a mathematical function which can take \texttt{p} number of input timeseries variables and output \texttt{n} number of timeseries variables.
-Other than that, at the time of processing the system can configure to provide bind constant which can provide while configuring an extension.
-This means it is possible to change the behavior of an existing function by providing different bind constant at the time of creating new triggers for an extension.
+The data preprocess functionalities support simple generic mathematical function models.
+Each extension is considered as a mathematical function that can take \texttt{p} number of input timeseries variables and output \texttt{n} number of timeseries variables after applying the given function.
+Further, the system supports to provide a bind constant as configurations to the extension at the time of preprocessing.
+Thus, users can change the behavior of an existing function by providing different bind constants at the time of creating new triggers for an extension and produce different behaviors.
 
 \subsection{Interpolation}
-The interpolation module generates data at desired locations or at desired data points using a serial or spatial interpolation technique.
-It is used to fill gaps in on-line measured data, and to derive spatially distributed data for weather time series, such as precipitation and temperature, based on information available at nearby locations.
+The interpolation module generates data at desired locations or at desired data points using a serial The interpolation module generates data at desired locations or desired data points using a serial or spatial interpolation technique.
+It is used to fill gaps in on-line measured data and to derive spatially distributed data for weather time series, such as precipitation and temperature, based on information available at nearby locations.
 
-\paragraph{Serial Interpolation}-- In serial interpolation mode, interpolation is done to fill any gaps in a time series.
-The interpolation module will only consider the time series itself in filling these gaps.
+\paragraph{Serial Interpolation}-- During serial interpolation, we use interpolation to fill any gaps in a time series.
+The interpolation module will only consider a single time series, which is itself in filling these gaps.
+
 \begin{figure}[htp]
@@
 
-\paragraph{Spatial Interpolation}-- In spatial interpolation mode, the interpolation can be either applied to fill gaps in time series, or to create a new time series for a location using data from other (spatially distributed) locations.
-Spatial interpolation can also be applied for sampling scalar time series from grid time series, for re-sampling grids, or for creating grids from timeseries data.
+\paragraph{Spatial Interpolation}-- During spatial interpolation, we use interpolation to either fill gaps in timeseries or to create a new time series for a location using data from other (spatially distributed) locations.
+Spatial interpolation can also be applied for sampling scalar timeseries from grid timeseries, for re-sampling grids, or for creating grids from timeseries data.
 \begin{figure}[htp]
@@
 
-\subsection{\hl{Data Preprocessing API}}
-In the WDIAS, it is possible to create new trigger for an extension via POST request to /extension endpoint.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Extension \acrfull{api} for Data Prepossessing}
+
+We exposed an \acrshort{api} to create new triggers for extensions via /extension endpoint.
+Following is the accepted payload of the request while creating a new trigger.
+Later we discussed the \acrshort{api} in detail and how we can use the \acrshort{api} to create new triggers to use extension modules.
+
 \begin{lstlisting}[language=Python]
@@
 Interpolation/Transformation/Validation support for the moment.
-    \item function -- Name of the microservice which is handling the input to output mapping. Fn() function in the \cref{fi:weather_data_preprocessing}.
+    \item function -- Name of the microservice which is handling the input to output mapping. \texttt{Fn()} function in the \cref{fi:weather_data_preprocessing}.
     \item variables -- Array timeseries mapping to variables.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{Extension Handler}
-Extension Handler is responsible for triggering the correct Extension with metadata when there is any change on the subscribed extension trigger's \emph{OnChange} timeseries.
+
+Extension Handler is responsible for triggering the correct extension with timeseries metadata when there is any change in the subscribed timeseries with a list of \emph{OnChange} timeseries while creating an extension trigger.
+
 \begin{figure}[htp]
@@
 
-\hl{As an example,} when new data imported into one of the adapter-scalar or adapter-vector, those notify the extension-handler.
-Then extension handler checks whether there is any extension subscribed for particular timeseries, and triggers it via triggering an event on particular extensions.
+When new data is inserted into one of the adapter-scalar or adapter-vector, those microservices notify the extension-handler.
+Then the extension-handler checks whether there is any extension subscribed for inserted timeseries.
+If there is an extension needed to be triggered, then it invokes the given extension with the required data.
 
-To improve the performance of matching triggers against a timeseries, the WDIAS added two mechanisms.
-For the separation of service responsibilities, those functionalities reside in the adapter-extension and expose via an endpoint.
-First, other than storing extension metadata in MySQL instance of adapter-extension, it also stores the data in reverse lookup table called triggers.
-Using this reverse lookup table, for a given trigger\_type and timeseries, it can retrieve the extensions which are part of given timeseries.
-Thus, the response which is received by the
-extension-handler only contains the extensions to be triggered. No additional filtering needs to be done at the extension-handler service.
-Second, cache the resulting trigger\_type and timeseries data in the  Redis database for fast access and avoid too many queries on the  MySQL database.
+To improve the performance of matching triggers against a timeseries, we used two mechanisms as below.
+First, other than only storing extension metadata in a MySQL instance of adapter-extension, we also store extension data in a reverse lookup table called triggers while creating new extension triggers.
+Using this reverse lookup table, we can retrieve the extensions against a given timeseries without heavy processing and less delay.
+Second, we cache the resulting trigger type and timeseries data using the Redis database inside the extension-handler for fast access and avoid too many queries on the MySQL database.
+For the separation of service responsibilities, the extension data stored in the persistence database of the adapter-extension and exposed via an endpoint.
 
-\paragraph{Extension Scheduler}-- Extension Handler is responsible for triggering the correct Extension with metadata at a given time which is provided at the creation on extension trigger with the value of OnTime cronjob string value.
-To improve the performance of triggering cronjobs at given time schedules, the WDIAS added few optimization mechanisms.
-Same as for extension-handler, the adapter-extension exposes an endpoint to retrieve extension metadata grouped by cronjob time.
-Then use \acrshort{go} to implement the extension-handler to fast processing the extensions.
-After retrieve extensions which is grouped by cronjob time; within the extension-handler, it schedules programmatic cronjobs to trigger at given times.
-When each cronjob triggers at the given time, it also contains the extensions to be triggered.
-Fetching extension data and creating cronjobs occur with a long period to avoid heavy overhead.
-When a new extension trigger created, those data push into a  Redis list. Then pulling from the extension-handler in regular time intervals and create new cronjobs for mentioned cronjob time.
-As mentioned above, to avoid the expansion of the programmatic cronjob list which are created for new extension triggers, all cronjobs fetch again in a long period and flush the previously scheduled cronjobs.
-The extension-handler should be run as a single entity for the atrocity, to avoid triggering the same extension twice.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Extension Scheduler}
+
+Extension scheduler is responsible for triggering the correct extension with metadata at a given time that provided at the time of creation as OnTime cron job values to the extension trigger.
+To improve the performance of triggering cron jobs at given time schedules, we used a few optimization mechanisms as described below.
+Same as for extension-handler, the adapter-extension exposed an endpoint to retrieve extension metadata grouped by cronjob time.
+Then we create cron jobs as per the data retrieved via adapter-extension.
+We used a low-level programming language to simulate the cron jobs for fast processing the extensions.
+After getting extension triggers, the extension-handler grouped them based on cronjob time and scheduled cron jobs programmatically to trigger at given times.
+When each cron job triggers at the scheduled time, each cron job also contains the extensions to be triggered.
+Fetching extension triggers data, and creating cron jobs occur with a long period to avoid huge overhead on adapter-extension.
+When a user creates a new extension trigger, those data push into a queue in the Redis database.
+Then the extension-handler pulls data from the queue in regular time intervals and creates new cron jobs for mentioned cronjob time.
+As mentioned above, to avoid the expansion of the programmatic cron job list that we created for new extension triggers, all cronjobs fetch again in a long period and flush the previously scheduled cron jobs.
+While doing that, we also flush the Redis queue.
+The extension-handler should be run as a single process for the atomicity, to avoid triggering the same extension twice.

### 2020-04-26 method/sec_6-query.tex
Replace noun acronym with full word
Updated -> Method

@@
 
-As described in \cref{subse:mongodb}, adapter-query is primarily using to support Geospatial queries.
-Other than that, as the primary service for searching for timeseries, it also supports for retrieval of timeseries metadata for external queries as well.
+We used the adapter-query primarily for supporting Geospatial queries.
+As the primary service for searching for timeseries, it supports retrieval of timeseries metadata for external queries as well.
+The following sections described the search query capabilities of \acrshort{wdias}.
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Timeseries Metadata}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Timeseries Geo Queries}
 
-\paragraph{Query Locations within Area}-- Using the following API endpoint, it is possible to query the locations which exist within the area provided by the GeoJson data in the JSON payload.
+\paragraph{Query Locations within Area}-- Following endpoint supports to query the locations which exist within the area provided by the GeoJson data in the JSON payload.
 \begin{lstlisting}
@@
 
-paragraph{Query parameters in Locations}-- Using the following API endpoint, it is possible to query the parameters stored against given locations.
-Location IDs should be provided as a list of JSON payload.
+paragraph{Query parameters in Locations}-- Following endpoint supports to query the parameters stored against given locations. Location IDs should be provided as a list of JSON payload.payload.
 \begin{lstlisting}
@@
 
-\paragraph{Query Timeseries by Location}-- Using the following API endpoint, it is possible to query the timeseries metadata for a given location.
+\paragraph{Query Timeseries by Location}-- Following endpoint supports to query the timeseries metadata for a given location.
 \begin{lstlisting}
@@
 \subsubsection{Query Timeseries by Locations}
-Using the following API endpoint, it is possible to query the timeseries metadata for a given location set. Location IDs should be provide as list in the locations field.
+Following endpoint supports to query the timeseries metadata for a given location set. Location IDs should be provided as a list in the locations field.
 \begin{lstlisting}
@@
 \subsubsection{Query Timeseries by Parameter}
-Using the following API endpoint, it is possible to query the timeseries metadata by parameter for given location/locations.
+Following endpoint supports to query the timeseries metadata by parameter for given location/locations.
 \begin{lstlisting}
@@
 
-\paragraph{Query Timeseries in Area} -- Using the following API endpoint, it is possible to query the timeseries metadata within a given area.
-This operation uses geoWithin \acrshort{mongodb} operator for the simplicity.
+\paragraph{Query Timeseries in Area} -- Following endpoint supports to query the timeseries metadata within a given area (specified as a polygon in geoJson format).
 \begin{lstlisting}
@@
 
-\paragraph{Query Timeseries in Area by Parameter}-- Using the following API endpoint, it is possible to query the timeseries metadata within a given area for given parameter.
-This is an extension to the above endpoint.
+\paragraph{Query Timeseries in Area by Parameter}-- Following endpoint supports to query the timeseries metadata within a given area for a given parameter.
+This endpoint is an extension of the above endpoint.
 \begin{lstlisting}
@@
 
-\paragraph{Query All Timeseries} -- Send a request with empty JSON body will respond with all the timeseries.
+\paragraph{Query All Timeseries} -- Send a request with an empty JSON body that will respond with all the timeseries.
 \begin{lstlisting}

### 2020-04-26 method/sec_7-summary.tex
Updated -> Method

@@
 
-Throughout this Chapter, it discussed about the methodology of designing and implementing the \acrshort{wdias} based on the concepts studied on \cref{ch:literature}.
-It uses microservice architecture over using \acrshort{soa} with a \acrshort{esb} to avoid the draw back of streaming bulk data over an \acrshort{esb}.
-In order to take the full advantage of using microservice architecture, we moved to container orchestration based architecture rather building tightly coupled microservices with actor model.
-While implementing the import and export modules, those modules follows the architecture style of \emph{Smart Endpoints and Dumb Pipes} and many other places.
-It implement each microservice as a containerized application which can deploy independent of other microservices.
-Also it uses the pattern of \emph{database per service} with combining different type of database systems to create the \acrshort{wdias} database structure.
-Further it provides a comprehensive extension modules system which allow users to preprocess data with creating new trigger without any downtime for system configuration.
-It indexing mechanism with Geo query support most of the required queries to search for any timeseries data.
+Throughout this Chapter, we discussed the methodology of designing and implementing the \acrshort{wdias} based on the concepts studied in the literature review of \cref{ch:literature}.
+We used microservice architecture over \acrshort{soa} with an \acrshort{esb} to avoid the drawback of streaming bulk data through an \acrshort{esb}.
+In order to take the full advantage of using the microservices architecture, we moved to container orchestration based architecture rather than building tightly coupled microservices with the actor model.
+While implementing the import and export modules, those modules followed the microservice architecture style of \emph{smart endpoints and dumb pipes}.
+Each microservice is implemented as a containerized application that can deploy independent of other microservices.
+Also, we used the microservice architecture pattern of \emph{database per service} by combining different types of database systems to create the \acrshort{wdias} database structure.
+Further, we provided a comprehensive extension module system that allows users to preprocess data by creating new triggers without any downtime for system configuration.
+We used a geo indexing mechanism to support Geo search queries and indexed the timeseries metadata to support the search for any timeseries in \acrshort{wdias}.

### 2020-04-26 method/sec_3-microservice.tex
v5.0

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{\acrshort{wdias} Microservices}
+\subsection{WDIAS Microservices}
 \label{sebse:wdias_microservices}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{\acrshort{wdias} \acrfull{api}}
+\subsection{WDIAS Application Programming Interface}
 \label{sebse:wdias_api}
@@
 Other than the above endpoints, we exposed another set of endpoints to configure extensions, and we will describe further in \cref{se:data_preprocess}.
-Other than the timeseries metadata, as mentioned in the list of endpoints, other module endpoints start with the module name such as import, export, and extension.
+Other than the timeseries metadata endpoints, other module endpoints start with the module name such as import, export, and extension when compared to timeseries metadata endpoints.
 Using the above convention, we allowed adding a new module system if required.
@@
 Other than that, users can send requests with raw data with required headers has mentioned by a particular import module.
-Thus the \acrshort{api} convention of \texttt{\hl{/MODULE/DATA\_FORMAT/DATA\_TYPE}} allows users to integrate new import or export modules into the system as well as add new data types.
+Thus the \acrshort{api} convention of \texttt{/MODULE/DATA\_FORMAT/DATA\_TYPE} allows users to integrate new import or export modules into the system as well as add new data types.

### 2020-04-26 method/sec_5-data_preprocess.tex
v5.0

@@
     \includegraphics[width=0.5\textwidth]{method/data_preprocess/weather_data_preprocessing.jpg}
-    \caption{\hl{Weather data preprocessing using a generic mathematical function model}}
+    \caption{A generic mathematical function model for weather data preprocessing}
     \label{fi:weather_data_preprocessing}
@@
 
-\subsection{Transformation}- Simple arithmetic manipulation, Time interval transformation and Shifting the series in time Specific hydro-meteorological transformation such as stage discharge relationships.
+\subsection{Transformation}
+Simple arithmetic manipulation, Time interval transformation and Shifting the series in time Specific hydro-meteorological transformation such as stage discharge relationships.
 \begin{figure}[htp]
@@
     \includegraphics[width=0.6\textwidth]{method/data_preprocess/transformation.jpg}
-    \caption{\hl{Time interval transformation.}}
+    \caption{Time interval aggregration.}
     \label{fi:transformation}
@@
 
-\subsection{Validation}- Checks for counting reliable, doubtful, unreliable, and missing values
+\subsection{Validation}
+Checks for counting reliable, doubtful, unreliable, and missing values
 \begin{figure}[htp]
@@
     \includegraphics[width=0.6\textwidth]{method/data_preprocess/validation.jpg}
-    \caption{\hl{Timeseries data validation against a set of rules.}}
+    \caption{Timeseries data validation.}
     \label{fi:validation}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Extension \acrfull{api} for Data Prepossessing}
+\subsection{Extension API for Data Prepossessing}
 

### 2020-05-04 introduction/sec_2-problem_and_objectives.tex
Thesis 4.0
v5.1
After Dilum sir fixes

@@
 \begin{itemize}
-    \item To develop an open platform to integrate weather data from different sources in different formats
+    \item To develop a platform to integrate weather data from different sources in different formats
     \item To design and develop a schema to store multidimensional weather timeseries data while optimizing access time, availability, and storage
-    \item To optimize schema to support data queries based on geography and time
+    \item To optimize data schema to support geospatial and time-based queries
     \item To develop an API for third-party data sharing
+\dbc{Add a another objective for performance analysis}
 %    \item To use open source tools and provide the source publicly with appropriate liecense.

### 2020-05-04 summary/sec_1-conclusions.tex
v5.1
After Dilum sir fixes

@@
 
-During our research, we proposed an extendable open source weather data integration and assimilation system known as \acrshort{wdias}.
+In this research, we proposed an extendable weather data integration and assimilation system known as \acrfull{wdias}.
 \acrshort{wdias} focuses on providing a system to efficiently integrate weather data from different sources with quality control and supporting steaming large size of data.
@@
 
-First, the architecture of \acrshort{wdias} starts with \acrshort{soa} using an \acrfull{esb} and then moved to Actor model-based architecture.
+First, the architecture of \acrshort{wdias} starts with \acrshort{soa} using an \acrfull{esb} and then moved to actor model-based architecture.
 After comparing the disadvantages of using such architectures with the system requirements, we came up with modern microservice architecture.
@@
 Also, each microservice follows the concept of smart endpoints dumb pipes[?] and does specific operations that are related to the data format that responsible for handling.
+\dbc{Need to explain the solution based on microservices as it's the most important. Also, a reference is missing here}
 
-Based on the microservice architecture patterns and the nature of the weather metadata, we came up with the idea of database structure for the \acrshort{wdias} to provide higher performance while storing the weather data optimum.
+Based on the microservice architecture patterns and the nature of the weather metadata, we designed database structure of \acrshort{wdias} to provide higher performance while storing the weather data efficiently.
 The system uses a timeseries database for storing scalar and vector timeseries data and using netCDF for storing grid timeseries data.
@@
 
-Further, we performed load tests using the JMeter tool’s distributed testing capabilities.
-Then the test plans are performed with increasing the request size and monitoring the performance metrics.
-The system is setup on the Amazon Elastic Kubernetes Service (Amazon EKS) as per the system setup configurations of \cref{subse:test_sys_config}.
-Based on the observations, we were able to perform 300 \acrshort{rps} of peak load, and the system handled the workload successfully with minimizing the error rate to zero.
-Also, while we increased the request size from 24 to 96 data points per scalar and vector timeseries, and the number of ASCII Grid files from 24 to 96, the \acrshort{wdias} was able to provide the same throughput while keeping the latency constant without any significant change.
+%Further, we performed load tests using the JMeter tool’s distributed testing capabilities. Then the test plans are performed with increasing the request size and monitoring the performance metrics. 
+We evaluated the performance using a cloud-based setup on the Amazon Elastic Kubernetes Service (Amazon EKS). % as per the system setup configurations of \cref{subse:test_sys_config}. 
+Based on the performance analysis, we were able to perform 300 \acrshort{rps}, and the system handled the workload successfully with minimizing the error rate.
+Also, while we increased the request size from 24 to 96 data points per scalar and vector timeseries, and the number of ASCII Grid files from 24 to 96, the \acrshort{wdias} was able to provide the same throughput while keeping the latency constant.
 Likewise, the system was able to provide an increase in the throughput by keeping the latency constant while increasing the workload.
-Thus, we can conclude that the system is further scalable.
+Thus, we can conclude that the system is scalable.
 With \acrshort{k8s} auto-scaling enabled, the \acrshort{k8s} elastically adjust the number of pods according to the workload with provided auto-scaling configurations.

### 2020-05-06 Appendix/app_1_soa_and_actor_model.tex
Fix with Figure
Change all to \cref
Added fixes
Error Term,Correct Term,Description,No of Occurrences,Pages (absolute)
a.k.a.,aka.,,Shoudl be aka and need a comma,1,-1
[a-z] as well as,, as well as,Needs a comma before,3,-1
Also,Also,,Comma should be used at beginning of a sentence,1,-1
can not,cannot,Is a single word,4,-1
[fF]igure.\d,Figure n,There has to be a space like Figure 2.7,82,-1
Hence,Hence,,Comma should be used at beginning of a sentence,1,-1
in order to,to,Can be replaced with just to in many cases,4,-1
in to,into,Is a single word,1,-1
may be,maybe,Is a single word,2,-1
section,Se

@@
 
-In the initial phase of WDIAS architecture, it proposed with a \acrfull{soa} as shown in the \ref{fi:proposed_soa_arch_design}. Mainly it consist of 4 modules, namely:
+In the initial phase of WDIAS architecture, it proposed with a \acrfull{soa} as shown in the \cref{fi:proposed_soa_arch_design}. Mainly it consist of 4 modules, namely:
 - Import modules
@@
 Extension modules are capable of providing the data assimilation functionalities by providing some of key functionalities such as transformation, interpolation and validation.
-While data assimilation, existing timeseries may be modified or create new timeseries based on the system configurations.
+While data assimilation, existing timeseries maybe modified or create new timeseries based on the system configurations.
 - Adapter module

### 2020-05-06 ThePaper.tex
Added fixes
Error Term,Correct Term,Description,No of Occurrences,Pages (absolute)
a.k.a.,aka.,,Shoudl be aka and need a comma,1,-1
[a-z] as well as,, as well as,Needs a comma before,3,-1
Also,Also,,Comma should be used at beginning of a sentence,1,-1
can not,cannot,Is a single word,4,-1
[fF]igure.\d,Figure n,There has to be a space like Figure 2.7,82,-1
Hence,Hence,,Comma should be used at beginning of a sentence,1,-1
in order to,to,Can be replaced with just to in many cases,4,-1
in to,into,Is a single word,1,-1
may be,maybe,Is a single word,2,-1
section,Section,S should be capital if used li

@@
 
-\dbc{Reduce background by ~25\%. Add a sentence on novetly on solution. Also. add a sentence on performance. Abstarct should not exceed 200 words.}
-\gkc{Modified. 200 words.}
-
 \begin{IEEEkeywords}
@@
 For an island like Sri Lanka that having different kinds of weather seasons over the year than that software originated countries, those systems need to be highly customized.
-Thus it required to get support from the vendor to integrate and configure the system.
+Thus, it required to get support from the vendor to integrate and configure the system.
 Most of the software existing out there are not up to date with the latest technology concepts such as Cloud Computing, and not using modern architecture pattern like microservice architecture that can use to build highly scalable and available systems, and use containerized applications to run systems independ of software platforms.
@@
 \db{Several forecasting systems are} developed with considering above factors for disaster management.
-Deltares developed the The \acrfull{fews}\cite{Werner2013TheSystem} in the Netherland for operational forecasting.
+Deltares developed the The \acrfull{fews} \cite{Werner2013TheSystem} in the Netherland for operational forecasting.
 It uses a model-centric approach, and implements the forecasting process as a combination of data modeling steps and data transformation algorithms.
@@
 But it capable of providing capability to create forecast workflows by integrate new models and algorithms.
-Also it uses a common data-model approach, and only allows models to interact with the system data via using one of the interfaces provided.
+Also, it uses a common data-model approach, and only allows models to interact with the system data via using one of the interfaces provided.
 All the timeseries data store in the common data model.
@@
 The \acrshort{lead} follows \acrfull{soa} with different service layers.
-Also it exposes services through a drag and drop interface to create new workflows.
+Also, it exposes services through a drag and drop interface to create new workflows.
 A workflow service in the \acrshort{lead} schedules and run built workflows with promising the maximum use of underline resource pool.
@@
 As mentioned above, most systems uses monolithic architecture or client service architecture, platform dependent, and not up to date with cloud computing technologies.
-Thus users can not benefit from modern cloud platforms and not able to decide the best cost-effective way to host the system.
+Thus, users cannot benefit from modern cloud platforms and not able to decide the best cost-effective way to host the system.
 Since most systems are proprietary or closed source, it is difficult to add new requirements and maintain the system in long-term.
@@
 After successfully process the data by other service, it updates the system status.
-Also the \acrshort{wdias} provides a simple RESTful API to interact with timeseries metadata and other modules such as import, export and extension modules.
+Also, the \acrshort{wdias} provides a simple RESTful API to interact with timeseries metadata and other modules such as import, export and extension modules.
 \dbc{Drop the REST API. No need for a paper. You can briefly mention it.}
@@
 It does not make any difference based on the parameter type whether it is the precipitation or the temperature.
-Thus during the performance testing,  JMeter uses real precipitation data from \acrshort{curw}.
+Thus, during the performance testing,  JMeter uses real precipitation data from \acrshort{curw}.
 One month period of data for five weather stations has been using to prepare the test data.
@@
 The observations are almost similar to \cref{ptab:obs_all_15_min_summary_throughput}, but notably the error rate of insert Grid timeseries got reduced after enabled the auto-scaling for import Grid data module.
-Also the standard deviation for handling Grid data reduced which means system was able to perform more better than the previous test plan.
+Also, the standard deviation for handling Grid data reduced which means system was able to perform more better than the previous test plan.
 
@@
 If the usage of \acrshort{wdias} wants to reduce the risk of unable to process data, then the system can configure to run with redundant pods to handle spike of workloads.
-Also while configuring for the auto-scaling, the \acrshort{k8s} can configure to maintain a lower amount of CPU usage such as 50\% to 60\% rather  than 80\%.
+Also, while configuring for the auto-scaling, the \acrshort{k8s} can configure to maintain a lower amount of CPU usage such as 50\% to 60\% rather  than 80\%.
 Such configuration with always spawn new pods to handle double of current peak load.
@@
 \dbc{Make this the discussion and a sub-section of Sec. 4}
-\gkc{Renamed. I did not get what did you mean by sub section 4. Did you mean \cref{pse:summary}?}
+\gkc{Renamed. I did not get what did you mean by sub Section 4. Did you mean \cref{pse:summary}?}
 

### 2020-05-06 introduction/sec_1-motivation.tex
v5.0
v5.1
After Dilum sir fixes
Added fixes
Error Term,Correct Term,Description,No of Occurrences,Pages (absolute)
a.k.a.,aka.,,Shoudl be aka and need a comma,1,-1
[a-z] as well as,, as well as,Needs a comma before,3,-1
Also,Also,,Comma should be used at beginning of a sentence,1,-1
can not,cannot,Is a single word,4,-1
[fF]igure.\d,Figure n,There has to be a space like Figure 2.7,82,-1
Hence,Hence,,Comma should be used at beginning of a sentence,1,-1
in order to,to,Can be replaced with just to in many cases,4,-1
in to,into,Is a single word,1,-1
may be,maybe,Is a single word,2,-1
section,Sectio

@@
 For example, FLO2D, a hydrologic model that predicts surface water level, could use precipitation estimates from \acrshort{wrf} to forecast flood levels.
-\gkc{Removed the sentence. I tried to use the FLO2D as a model which can use WRF output to forecast water levels.}
-\dbc{I fixed the sentence. Check whether it was ok. It was a pathetic effort to remove the sentence than trying to fix it.}
 
@@
 One of the future goals of \acrshort{curw} is to open up data to the public enabling both societal and commercial use cases.
+\dbc{Tru to use ``weather forecast'' than ``weather prediction''}
 
@@
 
-Weather data processed by one \acrshort{nwm} may be used by several other NWSs, as well as by many third-party applications and researcher.
+Weather data processed by one \acrshort{nwm} maybe used by several other NWSs, as well as by many third-party applications and researcher.
 For example, logistic companies could use the processed data with their models to plan and schedule their deliveries.

### 2020-05-06 lit/sec_1-fews.tex
v5.0
Added fixes
Error Term,Correct Term,Description,No of Occurrences,Pages (absolute)
a.k.a.,aka.,,Shoudl be aka and need a comma,1,-1
[a-z] as well as,, as well as,Needs a comma before,3,-1
Also,Also,,Comma should be used at beginning of a sentence,1,-1
can not,cannot,Is a single word,4,-1
[fF]igure.\d,Figure n,There has to be a space like Figure 2.7,82,-1
Hence,Hence,,Comma should be used at beginning of a sentence,1,-1
in order to,to,Can be replaced with just to in many cases,4,-1
in to,into,Is a single word,1,-1
may be,maybe,Is a single word,2,-1
section,Section,S should be capital if us

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{\acrshort{fews} flow forecasting system}
+\section{Delft-FEWS flow forecasting system}
 \label{se:fews}
@@
 The concept of the open modeling framework is used by the Delft-FEWS, which is proposed by open model integration \cite{Kokkonen2003InterfacingXML}.
-It merely gives the flexibility to allow operators to integrate more models as well as variations of the same model and come up with new forecasting flows as much as possible.
+It merely gives the flexibility to allow operators to integrate more models, as well as variations of the same model and come up with new forecasting flows as much as possible.
 
@@
 Users do not have the flexibility to run the models with different configurations, such as parallel execution of a particular model.
-Those issues may be overcome by triggering an external process at the execution time.
+Those issues maybe overcome by triggering an external process at the execution time.
 But, it introduces more difficulty in handling the next step in the forecasting flow, after the successful execution of the model.

### 2020-05-06 lit/sec_3-other-systems.tex
Added fixes
Error Term,Correct Term,Description,No of Occurrences,Pages (absolute)
a.k.a.,aka.,,Shoudl be aka and need a comma,1,-1
[a-z] as well as,, as well as,Needs a comma before,3,-1
Also,Also,,Comma should be used at beginning of a sentence,1,-1
can not,cannot,Is a single word,4,-1
[fF]igure.\d,Figure n,There has to be a space like Figure 2.7,82,-1
Hence,Hence,,Comma should be used at beginning of a sentence,1,-1
in order to,to,Can be replaced with just to in many cases,4,-1
in to,into,Is a single word,1,-1
may be,maybe,Is a single word,2,-1
section,Section,S should be capital if used li

@@
 Some of the MADIS data is considered to be the property of the supplier, and data access should be provided based on the authorization.
-In order to address the issue, MADIS data is divided into six different versions, depending on the access level authorized by the data provider \cite{Macdermaid2005ArchitectureP2.39}.
+To address the issue, MADIS data is divided into six different versions, depending on the access level authorized by the data provider \cite{Macdermaid2005ArchitectureP2.39}.
 When compared to Delft-FEWS, MADIS provides control-based access to the data.

### 2020-05-06 method/sec_1-architectural_decisions.tex
Added fixes
Error Term,Correct Term,Description,No of Occurrences,Pages (absolute)
a.k.a.,aka.,,Shoudl be aka and need a comma,1,-1
[a-z] as well as,, as well as,Needs a comma before,3,-1
Also,Also,,Comma should be used at beginning of a sentence,1,-1
can not,cannot,Is a single word,4,-1
[fF]igure.\d,Figure n,There has to be a space like Figure 2.7,82,-1
Hence,Hence,,Comma should be used at beginning of a sentence,1,-1
in order to,to,Can be replaced with just to in many cases,4,-1
in to,into,Is a single word,1,-1
may be,maybe,Is a single word,2,-1
section,Section,S should be capital if used li

@@
 However, we realized that \acrshort{esb} is not suitable for data streaming or bulk data processing.
-Also, \acrshort{esb} suffers from a single point of failure, as all the messages are going through a common shared bus and slower communication (can not be used for transfer data).
+Also, \acrshort{esb} suffers from a single point of failure, as all the messages are going through a common shared bus and slower communication (cannot be used for transfer data).
 In the second design phase of \acrshort{wdias}, we attempted to use the actor model using the AKKA framework \cite{HewittWhyModel} to overcome above \acrshort{esb} drawbacks.
@@
 
-Thus we redesigned the system architecture with decomposing into microservices and used actors to implement each microservice in the system.
+Thus, we redesigned the system architecture with decomposing into microservices and used actors to implement each microservice in the system.
 In that case, we mapped each microservice in \acrshort{wdias} to an actor or an actor with slave actors.

### 2020-05-06 method/sec_3-microservice.tex
Added fixes
Error Term,Correct Term,Description,No of Occurrences,Pages (absolute)
a.k.a.,aka.,,Shoudl be aka and need a comma,1,-1
[a-z] as well as,, as well as,Needs a comma before,3,-1
Also,Also,,Comma should be used at beginning of a sentence,1,-1
can not,cannot,Is a single word,4,-1
[fF]igure.\d,Figure n,There has to be a space like Figure 2.7,82,-1
Hence,Hence,,Comma should be used at beginning of a sentence,1,-1
in order to,to,Can be replaced with just to in many cases,4,-1
in to,into,Is a single word,1,-1
may be,maybe,Is a single word,2,-1
section,Section,S should be capital if used li

@@
 Z-axis splits are commonly used to scale databases.
-As an example, data partition (a.k.a.
-sharded) across a set of servers based on an attribute of each record.
+As an example, data partition (aka., sharded) across a set of servers based on an attribute of each record.
 Even our research is a design based on the Y-axis scaling; it is possible to use the Z-axis scaling to further scaling the system. We will discuss more detail in \cref{se:discussion}.
@@
 \cref{fi:wdias_micro_on_demand} and \cref{fi:wdias_micro_async} show the system interaction of the WDIA microservices architecture while handling the requests.
-Each circle in the Figures represents a microservice in the \acrshort{wdias}.
+Each circle in the figures represents a microservice in the \acrshort{wdias}.
 And each microservice is implemented as a containerized application.
@@
 Other than that, users can send requests with raw data with required headers has mentioned by a particular import module.
-Thus the \acrshort{api} convention of \texttt{/MODULE/DATA\_FORMAT/DATA\_TYPE} allows users to integrate new import or export modules into the system as well as add new data types.
+Thus, the \acrshort{api} convention of \texttt{/MODULE/DATA\_FORMAT/DATA\_TYPE} allows users to integrate new import or export modules into the system, as well as add new data types.

### 2020-05-06 method/sec_4-db_struct.tex
v5.0
Added fixes
Error Term,Correct Term,Description,No of Occurrences,Pages (absolute)
a.k.a.,aka.,,Shoudl be aka and need a comma,1,-1
[a-z] as well as,, as well as,Needs a comma before,3,-1
Also,Also,,Comma should be used at beginning of a sentence,1,-1
can not,cannot,Is a single word,4,-1
[fF]igure.\d,Figure n,There has to be a space like Figure 2.7,82,-1
Hence,Hence,,Comma should be used at beginning of a sentence,1,-1
in order to,to,Can be replaced with just to in many cases,4,-1
in to,into,Is a single word,1,-1
may be,maybe,Is a single word,2,-1
section,Section,S should be capital if us

@@
-\section{\acrshort{wdias} Database Structure}
+\section{WDIAS Database Structure}
 \label{se:db_struct}
@@
 Even we can use the location as metadata to identify the timeseries, but that is not enough to distinctly identify the parameters.
-Thus we need to use a set of attributes to identify a timeseries uniquely.
+Thus, we need to use a set of attributes to identify a timeseries uniquely.
 In the next \cref{subse:timeseries_key_attributes}, we describe key attributes that are used by the \acrshort{wdias} to identify a timeseries uniquely.
@@
   \item \emph{Point locations}-- Contains a name that is human readable. lat and lon of the location on the earth surface.
-  \begin{lstlisting}[language=Python, lastline=-1]
+\begin{lstlisting}[language=Python]
 {
@@
 It is difficult to search for the timeseries data if those are stored over multiple data sources and trying to avoid having duplicates.
-Thus it adds low overhead to have a single data source to look into while searching for the timeseries metadata.
+,it adds low overhead to have a single data source to look into while searching for the timeseries metadata.
 The efficiency of searching for timeseries metadata can increase by using a caching mechanism.
@@
 Thus, we need to use the correct database system based on application requirements.
-Considering the aforementioned database requirements, we can not get all of the benefits using a single general database system available.
-Thus we created a database structure after carefully choosing database systems per the system requirements and combining their capabilities.
+Considering the aforementioned database requirements, we cannot get all of the benefits using a single general database system available.
+Thus, we created a database structure after carefully choosing database systems per the system requirements and combining their capabilities.
 According to the design principle of microservices architecture, we created microservice for each of the valueType.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{\acrfull{netCDF}}
+\subsection{Network Common Data Form}
 \label{subse:netcdf}

### 2020-05-06 method/sec_5-data_preprocess.tex
Added fixes
Error Term,Correct Term,Description,No of Occurrences,Pages (absolute)
a.k.a.,aka.,,Shoudl be aka and need a comma,1,-1
[a-z] as well as,, as well as,Needs a comma before,3,-1
Also,Also,,Comma should be used at beginning of a sentence,1,-1
can not,cannot,Is a single word,4,-1
[fF]igure.\d,Figure n,There has to be a space like Figure 2.7,82,-1
Hence,Hence,,Comma should be used at beginning of a sentence,1,-1
in order to,to,Can be replaced with just to in many cases,4,-1
in to,into,Is a single word,1,-1
may be,maybe,Is a single word,2,-1
section,Section,S should be capital if used li

@@
 
-The data imported via import modules may have incorrect data, missing data, and incompatible data which can not directly feed into simulation modules.
-Thus we need to preprocess imported data before using it for forecasting.
+The data imported via import modules may have incorrect data, missing data, and incompatible data which cannot directly feed into simulation modules.
+Thus, we need to preprocess imported data before using it for forecasting.
 The WDIAS supports data preprocessing capabilities via the extension modules.
@@
 The interpolation module generates data at desired locations or at desired data points using a serial The interpolation module generates data at desired locations or desired data points using a serial or spatial interpolation technique.
-It is used to fill gaps in on-line measured data and to derive spatially distributed data for weather time series, such as precipitation and temperature, based on information available at nearby locations.
+It is used to fill gaps in on-line measured data and to derive spatially distributed data for weather timeseries, such as precipitation and temperature, based on information available at nearby locations.
 
-\paragraph{Serial Interpolation}-- During serial interpolation, we use interpolation to fill any gaps in a time series.
-The interpolation module will only consider a single time series, which is itself in filling these gaps.
+\paragraph{Serial Interpolation}-- During serial interpolation, we use interpolation to fill any gaps in a timeseries.
+The interpolation module will only consider a single timeseries, which is itself in filling these gaps.
 
@@
 
-\paragraph{Spatial Interpolation}-- During spatial interpolation, we use interpolation to either fill gaps in timeseries or to create a new time series for a location using data from other (spatially distributed) locations.
+\paragraph{Spatial Interpolation}-- During spatial interpolation, we use interpolation to either fill gaps in timeseries or to create a new timeseries for a location using data from other (spatially distributed) locations.
 Spatial interpolation can also be applied for sampling scalar timeseries from grid timeseries, for re-sampling grids, or for creating grids from timeseries data.

### 2020-05-06 method/sec_7-summary.tex
Added fixes
Error Term,Correct Term,Description,No of Occurrences,Pages (absolute)
a.k.a.,aka.,,Shoudl be aka and need a comma,1,-1
[a-z] as well as,, as well as,Needs a comma before,3,-1
Also,Also,,Comma should be used at beginning of a sentence,1,-1
can not,cannot,Is a single word,4,-1
[fF]igure.\d,Figure n,There has to be a space like Figure 2.7,82,-1
Hence,Hence,,Comma should be used at beginning of a sentence,1,-1
in order to,to,Can be replaced with just to in many cases,4,-1
in to,into,Is a single word,1,-1
may be,maybe,Is a single word,2,-1
section,Section,S should be capital if used li

@@
 We used microservice architecture over \acrshort{soa} with an \acrshort{esb} to avoid the drawback of streaming bulk data through an \acrshort{esb}.
-In order to take the full advantage of using the microservices architecture, we moved to container orchestration based architecture rather than building tightly coupled microservices with the actor model.
+To take the full advantage of using the microservices architecture, we moved to container orchestration based architecture rather than building tightly coupled microservices with the actor model.
 While implementing the import and export modules, those modules followed the microservice architecture style of \emph{smart endpoints and dumb pipes}.

### 2020-05-06 results/sec_2-workload.tex
Added fixes
Error Term,Correct Term,Description,No of Occurrences,Pages (absolute)
a.k.a.,aka.,,Shoudl be aka and need a comma,1,-1
[a-z] as well as,, as well as,Needs a comma before,3,-1
Also,Also,,Comma should be used at beginning of a sentence,1,-1
can not,cannot,Is a single word,4,-1
[fF]igure.\d,Figure n,There has to be a space like Figure 2.7,82,-1
Hence,Hence,,Comma should be used at beginning of a sentence,1,-1
in order to,to,Can be replaced with just to in many cases,4,-1
in to,into,Is a single word,1,-1
may be,maybe,Is a single word,2,-1
section,Section,S should be capital if used li

@@
 For each location, we created four timeseries metadata by using four different values for the moduleId key attribute.
-Thus combining all together first, we created 1000 timeseries metadata during the performance test and then stored the timeseries data against timeseries unique identifiers.
+Thus, combining all together first, we created 1000 timeseries metadata during the performance test and then stored the timeseries data against timeseries unique identifiers.
 We have written automated scripts to generate these data for the performance testing, and scripts are generic enough to create more timeseries metadata by changing the configurations.
@@
 With the above JMeter test plans, we have to enable each test plan separately and before running with JMeter distributed mode.
-In order to make the process faster, we implemented a script tool to interact with the JMeter test stored files.
+To make the process faster, we implemented a script tool to interact with the JMeter test stored files.
 The script is available within the code base \cite{KarunarathneWdias-performance-test/TEST_PLAN.md:Plan} as \emph{test-dev} and supports the following features.
@@
 \end{table}
-\dbc{Center table on page}
-\gkc{FIXED}
 
@@
 To get better performance using the available resources, we can schedule each microservice into a predefined set of nodes.
-Thus we tried to deploy all JMeter microservices on test labeled nodes since the test plans need to interact with all the services and transfer bulk timeseries data.
+Thus, we tried to deploy all JMeter microservices on test labeled nodes since the test plans need to interact with all the services and transfer bulk timeseries data.
 Also, the grid microservices are hosted inside the grid labeled node due to the massive size of grid data timeseries that need to be transferred during the load testing.
@@
 We scheduled the microservices in the core labeled node together, since most of those services are communicating together, and running them inside one physical node reduces the latency.
-Then we separate scalar and vector microservices and their databases, in order to separate the load from the core node while storing scalar and vector timeseries data.
+Then we separate scalar and vector microservices and their databases to separate the load from the core node while storing scalar and vector timeseries data.
 As same as, we assigned microservices to grid and test nodes based on the higher bandwidth requirements.

### 2020-05-06 results/sec_3-observations.tex
v5.0
Added fixes
Error Term,Correct Term,Description,No of Occurrences,Pages (absolute)
a.k.a.,aka.,,Shoudl be aka and need a comma,1,-1
[a-z] as well as,, as well as,Needs a comma before,3,-1
Also,Also,,Comma should be used at beginning of a sentence,1,-1
can not,cannot,Is a single word,4,-1
[fF]igure.\d,Figure n,There has to be a space like Figure 2.7,82,-1
Hence,Hence,,Comma should be used at beginning of a sentence,1,-1
in order to,to,Can be replaced with just to in many cases,4,-1
in to,into,Is a single word,1,-1
may be,maybe,Is a single word,2,-1
section,Section,S should be capital if us

@@
 On the other hand, insert grid timeseries data performed within 23ms, and almost all the requests perform within the same amount of time.
-Hence the standard deviation is smaller.
+Hence, the standard deviation is smaller.
 Delay with inserting grid timeseries smaller because those requests are handled asynchronously.
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_transaction_throughtput_vs_threads.png}
+    \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_res_latencies_against_hits.png}
     \caption{Load testing with 15 minutes of data with enabled auto-scaling - Latency against server hits}
@@
 Standard deviation showed a quiet higher value, which means the response latency values are not closer to the average value.
-Noticeably, we can not see any errors in the table, which means all the requests successfully process.
+Noticeably, we cannot see any errors in the table, which means all the requests successfully process.
 The throughput is similar among all the requests.
@@
 When the number of server hits gets higher, the latency also increases.
-According to the Figures, we can conclude that the performance of the adapter-query depends on the database.
+According to the figures, we can conclude that the performance of the adapter-query depends on the database.
 Even if we increase the number of adapter-query pods, the throughput of the microservice is not going to increase until we increase the performance by using the z-axis scaling of scale cube concept.

### 2020-05-06 results/sec_4-discussion.tex
Added fixes
Error Term,Correct Term,Description,No of Occurrences,Pages (absolute)
a.k.a.,aka.,,Shoudl be aka and need a comma,1,-1
[a-z] as well as,, as well as,Needs a comma before,3,-1
Also,Also,,Comma should be used at beginning of a sentence,1,-1
can not,cannot,Is a single word,4,-1
[fF]igure.\d,Figure n,There has to be a space like Figure 2.7,82,-1
Hence,Hence,,Comma should be used at beginning of a sentence,1,-1
in order to,to,Can be replaced with just to in many cases,4,-1
in to,into,Is a single word,1,-1
may be,maybe,Is a single word,2,-1
section,Section,S should be capital if used li

@@
 
-This section concludes the observations in \cref{se:observations} section against the performance metrics defined in \cref{subse:test_plan_metrics}.
+This section concludes the observations in \cref{se:observations} against the performance metrics defined in \cref{subse:test_plan_metrics}.
 
@@
 Adapter-grid is using a Python wrapper for netCDF FORTRAN implementation with parallel IO enabled.
-However, it has some performance issues as well as memory leak issues.
+However, it has some performance issues, as well as memory leak issues.
 Since each microservice in the \acrshort{wdias} is independent of technology, we can use a different technology stack to implement the service.

### 2020-05-06 summary/sec_1-conclusions.tex
Added fixes
Error Term,Correct Term,Description,No of Occurrences,Pages (absolute)
a.k.a.,aka.,,Shoudl be aka and need a comma,1,-1
[a-z] as well as,, as well as,Needs a comma before,3,-1
Also,Also,,Comma should be used at beginning of a sentence,1,-1
can not,cannot,Is a single word,4,-1
[fF]igure.\d,Figure n,There has to be a space like Figure 2.7,82,-1
Hence,Hence,,Comma should be used at beginning of a sentence,1,-1
in order to,to,Can be replaced with just to in many cases,4,-1
in to,into,Is a single word,1,-1
may be,maybe,Is a single word,2,-1
section,Section,S should be capital if used li

@@
 Also, most of the existing systems are based on basic client-server architectures or monolithic distributed system architectures or developed based on the best technology available at the time of developing those systems.
-However, most of the concepts are outdated with the technology advancement, and we can not get the full advantage of modern computational models such as containerized applications and using the cloud computing to gain benefits of scalability, high availability, and low-cost operations.
+However, most of the concepts are outdated with the technology advancement, and we cannot get the full advantage of modern computational models such as containerized applications and using the cloud computing to gain benefits of scalability, high availability, and low-cost operations.
 

### 2020-05-07 Thesis.tex
Thesis 4.0
Before copy back from Google docs
v5.0
Added fixes
Error Term,Correct Term,Description,No of Occurrences,Pages (absolute)
a.k.a.,aka.,,Shoudl be aka and need a comma,1,-1
[a-z] as well as,, as well as,Needs a comma before,3,-1
Also,Also,,Comma should be used at beginning of a sentence,1,-1
can not,cannot,Is a single word,4,-1
[fF]igure.\d,Figure n,There has to be a space like Figure 2.7,82,-1
Hence,Hence,,Comma should be used at beginning of a sentence,1,-1
in order to,to,Can be replaced with just to in many cases,4,-1
in to,into,Is a single word,1,-1
may be,maybe,Is a single word,2

@@
 
-% \usepackage{hyperref} %%% \hl{} on sections will fail this
+\usepackage{hyperref} %%% \hl{} on sections will fail this
 \usepackage[noabbrev,capitalise]{cleveref}
@@
 The resulting weather data also need to be accessed by many researchers and third-party applications such as logistic and agricultural insurance firms.
-%Even though there are several weather data integration systems, they
 Existing weather data integration systems are based on monolithic or client-server architectures; hence, unable to benefit from novel computational models such as cloud computing and containers.
@@
 Moreover, \acrshort{wdias} provides a modular framework to integrate data from different sources, export into different formats, and add new functionality by adding extension modules.
-% system allow users to add new features.
-%Due to the use of stateless microservices, \acrshort{wdias} achieves high scalability, availability, and enables the addition of new features on the fly with rollover capabilities. 
 We demonstrate the utility of \acrshort{wdias} using cloud-based experimental setup and weather-related synthetic workloads.
@@
 \textbf{Keywords:} Cloud computing, data assimilation, data integration, microservice, weather
-%Cloud Computing, Data Management system, Distributed,  Highly Available, Scalable, Timeseries, Weather
 }
@@
 Nevertheless I could not forget all of my friends at \acrshort{curw} who have supported and be with me during this period of time.
-Also special thanks to Dr.
+Also, special thanks to Dr.
 Dilum Bandara and Prof.
@@
 Special thanks go to the academic and non-academic staff of the department for their continued support.
-I also thank the %University of Moratuwa for its financial support, as the research was partially funded by the Senate research grant from the University of Moratuwa under award number SRC/LT/2017/01,  and
-\acrfull{curw} for providing the domain expertise, access to resources, and financial support during the research.% period with providing required resources and learning opportunities.
+I also thank the \acrfull{curw} for providing the domain expertise, access to resources, and financial support during the research.
 
@@
 
-% \import{results/}{sec_3-observations.tex}
+\import{results/}{sec_3-observations.tex}
 

### 2020-05-07 lit/sec_2-lead.tex
v5.0
replace with weather forecast

@@
 \begin{itemize}
-    \item the users interact with LEAD via a Web portal
-    \item data quality control and assimilation happens via ARPS Data Assimilation System (ADAS)
+    \item The users interact with LEAD via a Web portal
+    \item Data quality control and assimilation happens via ARPS Data Assimilation System (ADAS)
     \item myLEAD is the metadata catalog
@@
 
-LEAD is a more advanced system which can support mesoscale weather prediction with the effort of multiple universities in the United State America with the effort of many researchers and using many computer resources.
+LEAD is a more advanced system which can support mesoscale weather forecast with the effort of multiple universities in the United State America with the effort of many researchers and using many computer resources.
 At the time of  building, it uses the \acrshort{soa} architecture into its depth, and at the implementation, each service can scale as needed and possible to enhance the service without interrupting other services.

### 2020-05-07 Thesis.tex
Updates from Overleaf

@@
 
-\usepackage{hyperref} %%% \hl{} on sections will fail this
+% \usepackage{hyperref} %%% \hl{} on sections will fail this
 \usepackage[noabbrev,capitalise]{cleveref}
@@
         \vspace{32pt}
-        March 2020
+        May 2020
 
@@
 \noindent
-\begin{tabu} to 1.0\textwidth { X[l] X[l] }
+\begin{tabu} to 1.0\textwidth { X[6.5,l] X[3.5,l] }
   Signature: & Date:
@@
 \noindent
-\begin{tabu} to 1.0\textwidth { X[l] X[l] }
-  Name of the supervisor: & Dr. HMN Dilum Bandara\\ [1.5ex]
+\begin{tabu} to 1.0\textwidth { X[6.5,l] X[3.5,l] }
+  Name of the supervisor: & Dr. HMN Dilum Bandara\\ [2.5ex]
   Signature of the supervisor: & Date:
@@
 
-\import{results/}{sec_2-workload.tex}
+% \import{results/}{sec_2-workload.tex}
 
-\import{results/}{sec_3-observations.tex}
+% \import{results/}{sec_3-observations.tex}
 

### 2020-05-07 ThePaper.tex

@@
 \label{pse:Introduction}
-Weather prediction is essential to reduce the impacts caused by natural disasters and to effectively manage natural water resources.
-To enhance the accuracy of weather predictions, it requires to provide reliable and detailed weather data as inputs to \acrfull{nwm}s.
+Weather forecast is essential to reduce the impacts caused by natural disasters and to effectively manage natural water resources.
+To enhance the accuracy of weather forecast, it requires to provide reliable and detailed weather data as inputs to \acrfull{nwm}s.
 Before feeding such diverse data collected from different sources, we need to convert data into NWMs compatible data format.

### 2020-05-07 introduction/sec_1-motivation.tex
Updates from Overleaf

@@
-Weather prediction is essential to reduce the impact caused by natural disasters and to effectively manage natural resources like water. 
-%It will give more understanding of weather prediction if we look into a weather prediction workflow that can use to predict the surface water level. 
-The weather predictions/forecasts are performed using \acrfull{nwm} that use a set of configuration parameters and the current status of the environment such as temperature, rainfall, and wind direction as the inputs.
+Weather forecast is essential to reduce the impact caused by natural disasters and to effectively manage natural resources like water.
+The weather forecasts are performed using \acrfull{nwm} that use a set of configuration parameters and the current status of the environment such as temperature, rainfall, and wind direction as the inputs.
 For example, the \acrfull{wrf} \cite{MesoscaleMicroscaleMeteorologyLaboratoryWeatherModel} model is used to predict the rainfall, temperature, and wind direction.
@@
 One of the future goals of \acrshort{curw} is to open up data to the public enabling both societal and commercial use cases.
-\dbc{Tru to use ``weather forecast'' than ``weather prediction''}
 
@@
 \section{Motivation}
-To enhance the accuracy of weather predictions, it is necessary to provide reliable and detailed weather data as inputs to \acrshort{nwm}.
+To enhance the accuracy of weather forecast, it is necessary to provide reliable and detailed weather data as inputs to \acrshort{nwm}.
 These NWMs utilize multi-modal weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images.

### 2020-05-07 method/sec_0_introduction.tex
Added fixes
Error Term,Correct Term,Description,No of Occurrences,Pages (absolute)
a.k.a.,aka.,,Shoudl be aka and need a comma,1,-1
[a-z] as well as,, as well as,Needs a comma before,3,-1
Also,Also,,Comma should be used at beginning of a sentence,1,-1
can not,cannot,Is a single word,4,-1
[fF]igure.\d,Figure n,There has to be a space like Figure 2.7,82,-1
Hence,Hence,,Comma should be used at beginning of a sentence,1,-1
in order to,to,Can be replaced with just to in many cases,4,-1
in to,into,Is a single word,1,-1
may be,maybe,Is a single word,2,-1
section,Section,S should be capital if used li

@@
 
-To get an overall idea of the flow of weather prediction, let us look into one of the weather forecastings flows using the \acrshort{curw} \cite{CUrWSL2017SL}.
+To get an overall idea of the flow of weather forecast, let us look into one of the weather forecastings flows using the \acrshort{curw} \cite{CUrWSL2017SL}.
 
@@
 Also, those models reproduce a large set of redundant data.
-Thus the system should store the bulk data while optimizing the disk space.
+Thus, the system should store the bulk data while optimizing the disk space.
 \subsubsection{Dissemination}

### 2020-05-07 structure.tex
Plagiarism: Ack fix
Added fixes
Error Term,Correct Term,Description,No of Occurrences,Pages (absolute)
a.k.a.,aka.,,Shoudl be aka and need a comma,1,-1
[a-z] as well as,, as well as,Needs a comma before,3,-1
Also,Also,,Comma should be used at beginning of a sentence,1,-1
can not,cannot,Is a single word,4,-1
[fF]igure.\d,Figure n,There has to be a space like Figure 2.7,82,-1
Hence,Hence,,Comma should be used at beginning of a sentence,1,-1
in order to,to,Can be replaced with just to in many cases,4,-1
in to,into,Is a single word,1,-1
may be,maybe,Is a single word,2,-1
section,Section,S should b

--- 2019-12-01 struct.tex
@@
 
-To enhance the accuracy of weather predictions, it is necessary to provide reliable and detailed weather data as inputs to Numerical Weather Models (NWM).
+To enhance the accuracy of weather forecast, it is necessary to provide reliable and detailed weather data as inputs to Numerical Weather Models (NWM).
 These NWMs utilize weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images.
@@
 I also dedicate this thesis to my many friends at CUrW SL who have supported and be with me during this period of time.
-Also special thanks to Dr.
+Also, special thanks to Dr.
 Dilum Bandara and Dr.
@@
 \end{figure}
-Figure \ref{fi:orchid} shows an orchid.
+\cref{fi:orchid} shows an orchid.
 
@@
 
-Reviews literature and place your work within the existing body of literature here. In chapter \ref{ch:intro} you introduced your thesis.
+Reviews literature and place your work within the existing body of literature here. In Chapter \ref{ch:intro} you introduced your thesis.
 
@@
 
-\section{Work Load Creation}
+\section{Workload Creation}
 
@@
 \chapter{Conclusions}
-\label{ch:conc}
+\label{ch:summary}
 

### 2020-05-08 method/sec_4-db_struct.tex
v5.1.1

@@
 Thus, we need to use a set of attributes to identify a timeseries uniquely.
-In the next \cref{subse:timeseries_key_attributes}, we describe key attributes that are used by the \acrshort{wdias} to identify a timeseries uniquely.
+Next, we describe key attributes that are used by the \acrshort{wdias} to identify a timeseries uniquely.
 
@@
 
-\paragraph{Value Type}-- Scalar, Vector, Grid are the Value Types that are interested in the \acrshort{wdias}.
+\paragraph{Value Type}-- Scalar, vector, grid are the Value Types that are interested in the \acrshort{wdias}.
 
@@
 \begin{itemize}  
-  \item \emph{Variable} -- Nature of the variable measuring. Example Precipitation, Temperature and Water Level etc
+  \item \emph{Variable} -- Nature of the variable measuring. Example precipitation, temperature and water level
   \item \emph{Unit} -- metric unit of measuring
@@
 
-\cref{fi:database_structure} shows the \acrshort{wdias} database structure.
-The following sections describe the database structure of \acrshort{wdias} with compare to the design with more details on how is support the microservice architecture.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{subse:mysql}
+
+\cref{fi:database_structure} shows the \acrshort{wdias} database structure.
+The following sections describe the database structure of \acrshort{wdias} with compare to the design with more details on how is support the microservice architecture.
 
@@
 
-We used SQL as the \acrshort{rdbms}.
 Since one of \acrshort{wdias} main goals is to use open source tools, it used MySQL as a persistent database for storing timeseries metadata described above.
@@
 It also supports Publisher Subscriber capabilities as an inbuilt feature.
-Redis is an open-source (BSD licensed).
+Redis is an open-source.
 Clustering is available for scalability.

### 2020-05-08 method/sec_5-data_preprocess.tex
v5.1.1

@@
     \centering
-    \includegraphics[width=0.5\textwidth]{method/data_preprocess/weather_data_preprocessing.jpg}
+    \includegraphics[width=0.8\textwidth]{method/data_preprocess/weather_data_preprocessing.pdf}
     \caption{A generic mathematical function model for weather data preprocessing}
@@
 The data preprocess functionalities support simple generic mathematical function models.
-Each extension is considered as a mathematical function that can take \texttt{p} number of input timeseries variables and output \texttt{n} number of timeseries variables after applying the given function.
+Each extension is considered as a mathematical function that can take \texttt{p} input timeseries variables and output \texttt{n} timeseries variables after applying the given function.
 Further, the system supports to provide a bind constant as configurations to the extension at the time of preprocessing.
@@
     \centering
-    \includegraphics[width=0.6\textwidth]{method/data_preprocess/serial_interpolation.jpg}
+    \includegraphics[width=0.8\textwidth]{method/data_preprocess/serial_interpolation.pdf}
     \caption{Serial interpolation.}
@@
     \centering
-    \includegraphics[width=0.6\textwidth]{method/data_preprocess/spatial_interpolation.jpg}
+    \includegraphics[width=0.8\textwidth]{method/data_preprocess/spatial_interpolation.pdf}
     \caption{Spatial interpolation.}
@@
     \centering
-    \includegraphics[width=0.6\textwidth]{method/data_preprocess/transformation.jpg}
+    \includegraphics[width=0.8\textwidth]{method/data_preprocess/transformation.pdf}
     \caption{Time interval aggregration.}
@@
     \centering
-    \includegraphics[width=0.6\textwidth]{method/data_preprocess/validation.jpg}
+    \includegraphics[width=0.8\textwidth]{method/data_preprocess/validation.pdf}
     \caption{Timeseries data validation.}
@@
     \centering
-    \includegraphics[width=0.6\textwidth]{method/data_preprocess/validation.jpg}
+    \includegraphics[width=0.8\textwidth]{method/data_preprocess/validation.pdf}
     \caption{Extension handler.}

### 2020-05-08 results/sec_1-test_plan.tex
Added fixes
Error Term,Correct Term,Description,No of Occurrences,Pages (absolute)
a.k.a.,aka.,,Shoudl be aka and need a comma,1,-1
[a-z] as well as,, as well as,Needs a comma before,3,-1
Also,Also,,Comma should be used at beginning of a sentence,1,-1
can not,cannot,Is a single word,4,-1
[fF]igure.\d,Figure n,There has to be a space like Figure 2.7,82,-1
Hence,Hence,,Comma should be used at beginning of a sentence,1,-1
in order to,to,Can be replaced with just to in many cases,4,-1
in to,into,Is a single word,1,-1
may be,maybe,Is a single word,2,-1
section,Section,S should be capital if used li

@@
-\section{Load Testing Plan}
+\section{Test Plan}
 \label{se:test_plan}
 
-In \cref{subse:modules_weather_data_integration_sys} we discussed three modules of weather data integration and assimilation systems such as integration, assimilation, and dissemination.
+In \cref{se:high_level_design} we discussed three modules of weather data integration and assimilation systems such as integration, assimilation, and dissemination.
 We can map each of those modules to WDIAS modules, which provide the same functionalities as below.
@@
 \begin{itemize}
-    \item A weather station may send the current water level in a regular period of 1 minute. In such a case, it always comes as a request with one data point with a higher frequency.
+    \item A weather station may send the current water level in a regular 1 minute intervals. In such a case, it always comes as a request with one data point with a higher frequency.
     \item Due to resource issues such as batteries, a weather station can collect data points for a given period and send as a batch.
@@
 The Majority of weather data requests come from weather stations and other observation tools.
-Then we need to validate and modify those timesereis data and store them as new timeseries that can directly feed into the NWMs..
+Then we need to validate and modify those timeseries data and store them as new timeseries that can directly feed into the NWMs.
 These weather stations can send the weather data at different frequencies with different parameters such as precipitation, temperature, humidity, and wind direction.
@@
 But those grid data produce in less frequency due to the cost of the computer resource to produce results.
-After considering those factors, we came up with 70\% scalar, 20\% vector, and 10\% grid percentage values at the expected requests rate ratios.
+After considering those factors we came up with 70\% scalar, 20\% vector, and 10\% grid percentage values as the expected requests rate ratios.
 As an upper limit of such scenarios while designing the performance testing, it uses the following;
@@
 In each step, the \acrshort{rps} holds for a moment to give some time for the system to get stabilized.
-Thus at each step, we can measure the performance of the system and study the stability of the system.
+At each step, we can measure the performance of the system and study the stability of the system.
 After the test plan comes to the peak \acrshort{rps}, the system holds for more time than the previous steps.
@@
 So, if the deviation value is low compared to the mean value, it will indicate that the measures are not dispersed (or mostly close to the mean value), and the mean value is significant.
-Other than that, we measure the response time into 90\% percentile while giving the best response time up to 90\% percent of the responses.
+Other than that, we measure the response time into 90\% percentile while giving the best response time up to 90\% percentile of the responses.
     \item \emph{Resource utilization} -- Resource Utilization is calculated based on the CPU and Memory usage via the K8s metrics server.

### 2020-05-08 results/sec_2-workload.tex
v5.1.1

@@
 
-We used the Apache JMeter for performing the load test since it is open source and supports distributed load testing.
+We used the Apache JMeter for performing the load test since it is open source.
+And supports distributed load testing.
 As mentioned in the JMeter Best Practices, "If your test needs large amounts of data - particularly if it needs to be \emph{randomized}, create the test data in a file that can be read with CSV Data set.
@@
 \acrshort{wdias} is capable of storing any numeric value up to 3 decimal points as per the default configuration.
-Even the parameter type is either precipitation or temperature does not make any difference, because in storage perspective, it's a number.
+Even the parameter type is either precipitation, temperature does not make any difference, because in storage perspective, we are storing numeric value.
 Thus, during the performance testing, we only use real precipitation data from \acrshort{curw}.
@@
     \centering
-    \includegraphics[width=0.6\textwidth]{results/work_load/experimental_setup_v3.jpg}
+    \includegraphics[width=0.6\textwidth]{results/work_load/experimental_setup_v3.pdf}
     \caption{Experimental setup with JMeter}
@@
     \centering
-    \includegraphics[width=0.75\textwidth]{results/work_load/eks_node_setup.jpg}
+    \includegraphics[width=0.75\textwidth]{results/work_load/eks_node_setup.pdf}
     \caption{\acrfull{eks} node setup}

### 2020-05-08 results/sec_3-observations.tex
v5.1.1

@@
 \begin{table}[ht]
-\caption{Throughput and Latency of load testing with 60min data}
+\caption{Throughput and Latency of load testing with 60-min data}
 \footnotesize
@@
 \hline
-Label & Samples & Avg & Min & Max & 90\% Line & Std.Dev. & Error & RPS \\ \hline
+\textbf{Label} & \textbf{Samples} & \textbf{Avg} & \textbf{Min} & \textbf{Max} & \textbf{90\% Line} & \textbf{Std.Dev.} & \textbf{Error} & \textbf{RPS} \\ \hline
 Insert Timeseries & 71826 & 28 & 13 & 2773 & 31 & 58.74 & 0.00\% & 40.5 \\ \hline
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_60m_response_times_vs_threads.png}
+    \includegraphics[width=1.0\textwidth]{results/obs/all/obs_all_60m_response_times_vs_threads.png}
     \caption{Load testing with hourly data - Response Time vs Threads}
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_60m_res_latencies_against_hits.png}
+    \includegraphics[width=1.0\textwidth]{results/obs/all/obs_all_60m_res_latencies_against_hits.png}
     \caption{Load testing with hourly data - Latency against server hits}
@@
 \begin{table}[ht]
-\caption{Throughput and Latency of load test with 30min data}
+\caption{Throughput and Latency of load test with 30-min data}
 \footnotesize
@@
 \hline
-Label & Samples & Avg & Min & Max & 90\% Line & Std.Dev. & Error & RPS \\ \hline
+\textbf{Label} & \textbf{Samples} & \textbf{Avg} & \textbf{Min} & \textbf{Max} & \textbf{90\% Line} & \textbf{Std.Dev.} & \textbf{Error} & \textbf{RPS} \\ \hline
 Insert Timeseries & 71759 & 29 & 14 & 1699 & 32 & 50.97 & 0.00\% & 40.5 \\ \hline
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_30m_response_times_vs_threads.png}
+    \includegraphics[width=1.0\textwidth]{results/obs/all/obs_all_30m_response_times_vs_threads.png}
     \caption{Load testing with 30 minutes of data - Response Time vs Threads}
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_30m_res_latencies_against_hits.png}
+    \includegraphics[width=1.0\textwidth]{results/obs/all/obs_all_30m_res_latencies_against_hits.png}
     \caption{Load testing with 30 minutes of data - Latency against server hits}
@@
 \begin{table}[ht]
-\caption{Throughput and Latency of load testing with 15min data}
+\caption{Throughput and Latency of load testing with 15-min data}
 \footnotesize
@@
 \hline
-Label & Samples & Avg & Min & Max & 90\% Line & Std.Dev. & Error & RPS \\ \hline
+\textbf{Label} & \textbf{Samples} & \textbf{Avg} & \textbf{Min} & \textbf{Max} & \textbf{90\% Line} & \textbf{Std.Dev.} & \textbf{Error} & \textbf{RPS} \\ \hline
 Insert Timeseries & 71775 & 30 & 12 & 1719 & 41 & 51.71 & 0.00\% & 40.5 \\ \hline
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_15m_response_times_vs_threads.png}
+    \includegraphics[width=1.0\textwidth]{results/obs/all/obs_all_15m_response_times_vs_threads.png}
     \caption{Load testing with 15 minutes of data - Response Time vs Active Threads}
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_15m_res_latencies_against_hits.png}
+    \includegraphics[width=1.0\textwidth]{results/obs/all/obs_all_15m_res_latencies_against_hits.png}
     \caption{Load testing with 15 minutes of data - Latency against server hits}
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_15m_transaction_throughtput_vs_threads.png}
+    \includegraphics[width=1.0\textwidth]{results/obs/all/obs_all_15m_transaction_throughtput_vs_threads.png}
     \caption{Load testing with 15 minutes of data - Transaction Throughput vs Threads}
@@
 \begin{table}[ht]
-\caption{Throughput and Latency of load testing with 15min data while enabled \acrshort{k8s} auto-scaling}
+\caption{Throughput and Latency of load testing with 15-min data while enabled \acrshort{k8s} auto-scaling}
 \footnotesize
@@
 \hline
-Label & Samples & Avg & Min & Max & 90\% Line & Std.Dev. & Error & RPS \\ \hline
+\textbf{Label} & \textbf{Samples} & \textbf{Avg} & \textbf{Min} & \textbf{Max} & \textbf{90\% Line} & \textbf{Std.Dev.} & \textbf{Error} & \textbf{RPS} \\ \hline
 Insert Timeseries & 71727 & 34 & 13 & 1777 & 27 & 118.78 & 0.00\% & 40.5 \\ \hline
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_res_latencies_against_hits.png}
+    \includegraphics[width=1.0\textwidth]{results/obs/all_auto/obs_all_auto_15m_res_latencies_against_hits.png}
     \caption{Load testing with 15 minutes of data with enabled auto-scaling - Latency against server hits}
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_transaction_throughtput_vs_threads.png}
+    \includegraphics[width=1.0\textwidth]{results/obs/all_auto/obs_all_auto_15m_transaction_throughtput_vs_threads.png}
     \caption{Load testing with 15 minutes of data with enabled auto-scaling - Transaction Throughput vs Threads}
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_import_export_res.png}
+    \includegraphics[width=1.0\textwidth]{results/obs/all_auto/obs_all_auto_15m_import_export_res.png}
     \caption{Load testing with auto-scaling resource usage of import and export modules.}
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_import_grid_pod.png}
+    \includegraphics[width=1.0\textwidth]{results/obs/all_auto/obs_all_auto_15m_import_grid_pod.png}
     \caption{Load testing with auto-scaling import ascii grid number of pods over time.}
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_adapter_dbs_res.png}
+    \includegraphics[width=1.0\textwidth]{results/obs/all_auto/obs_all_auto_15m_adapter_dbs_res.png}
     \caption{Load testing with auto-scaling resource usage of database adapters.}
@@
 \begin{table}[ht]
-\caption{Throughput and Latency of Query test cases with 15min data}
+\caption{Throughput and Latency of Query test cases with 15-min data}
 \footnotesize
@@
 \hline
-Label & Samples & Avg & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
+\textbf{Label} & \textbf{Samples} & \textbf{Avg} & \textbf{Min} & \textbf{Max} & \textbf{90\% Line} & \textbf{Std.Dev.} & \textbf{Error} & \textbf{RPS} \\ \hline
 * → Locations & 11462 & 992 & 5 & 17569 & 1740 & 704.67 & 0.00\% & 38.3 \\ \hline
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{results/obs/query/obs_query_5m_latency_over_time.png}
+    \includegraphics[width=1.0\textwidth]{results/obs/query/obs_query_5m_latency_over_time.png}
     \caption{Load testing query test over 5 minutes - Response Latency over Time}
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{results/obs/query/obs_query_5m_response_times_vs_threads.png}
+    \includegraphics[width=1.0\textwidth]{results/obs/query/obs_query_5m_response_times_vs_threads.png}
     \caption{Load testing query test over 5 minutes - Response Latency Times vs Threads}

### 2020-05-08 summary/sec_1-conclusions.tex
replace with weather forecast
v5.1.1

@@
+This chapter includes the summary of the WDIAS.
+In \cref{se:summary_conclusion}, we summarize and conclude the research.
+\cref{se:research_limitations} includes the limitations of this research, and future improvements that can increase the performance and usability of the WDIAS.
+
 \section{Conclusions}
@@
 
-To enhance the accuracy of the weather prediction, we need to provide reliable and timely weather data for NWMs.
+To enhance the accuracy of the weather forecast, we need to provide reliable and timely weather data for NWMs.
 Even though there are many weather data integration systems, most of them are proprietary or closed source.

### 2020-05-08 ThePaper.tex
in-moemory

@@
 Each adapter has an isolated database, and the database is hosted separately for the high performance.
-And timeseries metadata stored using RDBMS which gives more performance over retrieving metadata data, and cached with the In-Memory database to fast access.
+And timeseries metadata stored using RDBMS which gives more performance over retrieving metadata data, and cached with the in-memory database to fast access.
 The system generates a unique identifier for each timeseries, and throughout the WDIAS, other microservice use it to handle data for fast access.

### 2020-05-08 method/sec_3-microservice.tex
v5.1.1
in-moemory

@@
 Then we will discuss how distributed transactions can makeover microservices.
-Last, we will discuss a concept called \emph{the scale cube}, which explains the scalability from the perspective of x,y, and z-axis.
+Last, we will discuss a concept called \emph{the scale cube}, which explains the scalability from the perspective of x-axis, y-axis, and z-axis.
 
@@
 And the metadata data of the timeseries store using an RDBMS, which gives more performance over retrieving timeseries metadata.
-The metadata is cached using an In-Memory database to fast access while implementing the database structure.
+The metadata is cached using an in-memory database to fast access while implementing the database structure.
 The system generates a unique identifier for each timeseries, and throughout the \acrshort{wdias} system, all microservices use it to handle data for fast access.

### 2020-05-08 method/sec_4-db_struct.tex
in-moemory

@@
 We used MySQL only for the above services, and those database instances keep the consistency of the schema for timeseries metadata and extension metadata.
-Further, we used an In-Memory database instance for caching the requested metadata to reduce the load on the MySQL database instances while repeated queries.
+Further, we used an in-memory database instance for caching the requested metadata to reduce the load on the MySQL database instances while repeated queries.
 Other than MySQL, many open-source SQL databases can be used to replace the same functionality.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{In-Memory Database}
+\subsection{In-memory Database}
 \label{subse:redis}
 
-We used Redis \cite{redisRedisDocumentation} as the In-Memory database since it is a widely used database system with excellent support.
+We used Redis \cite{redisRedisDocumentation} as the in-memory database since it is a widely used database system with excellent support.
 It also supports Publisher Subscriber capabilities as an inbuilt feature.
@@
 Here we used the \emph{Y-axis scaling} concept by splitting metadata search into multiple services.
-Within the system, it uses In-Memory database cache to support internal metadata access, and external search queries fulfill by the adapter-query with using MongoDB.
+Within the system, it uses in-memory database cache to support internal metadata access, and external search queries fulfill by the adapter-query with using MongoDB.

### 2020-05-08 ThePaper.tex
x-axis, y-axis, z-axis

@@
 Using \acrshort{k8s}, users can add required resources as Nodes to the cluster, and K8s manage and deploy applications as pods into cluster nodes.
-In next \cref{pse:wdias_architecture}, we discussed about the \acrshort{wdias} used microservice concepts such as implement microservice as dumb pipes rather implementing smart endpoints, uses database per service with access via API only, distributed Transactions over microservices using event processing, and considering distributed systems scalability in directions of X-axis scaling, Y-axis scaling and Z-axis scaling.
+In next \cref{pse:wdias_architecture}, we discussed about the \acrshort{wdias} used microservice concepts such as implement microservice as dumb pipes rather implementing smart endpoints, uses database per service with access via API only, distributed Transactions over microservices using event processing, and considering distributed systems scalability in directions of x-axis scaling, y-axis scaling and z-axis scaling.
 
@@
 Using tools like Terraform which is independent of the Cloud Computing provider \emph{define \acrshort{wdias} infrastructure as code}, then users will able to easily deploy the \acrshort{wdias} on any Cloud provider without much hassle.
-\emph{Tune \acrshort{wdias} database structure performance} with using Z-axis scaling.
+\emph{Tune \acrshort{wdias} database structure performance} with using z-axis scaling.
 Some of other features are alerting extension modules, publisher subscriber capabilities via extension modules, supporting irregular Grids.

### 2020-05-08 method/sec_3-microservice.tex
x-axis, y-axis, z-axis

@@
 
-\paragraph{X-axis Scaling}-- When scaling an application through the X-axis, multiple instances of the application execute behind a load balancer.
+\paragraph{X-axis Scaling}-- When scaling an application through the x-axis, multiple instances of the application execute behind a load balancer.
 If there are \textit{n} copies, then each copy handles 1/\textit{n} of the load.
@@
 
-\paragraph{Y-axis Scaling}-- When compared to the Z-axis and X-axis scaling, which follows the concept of running multiple identical copies of the application, but Y-axis scaling segregates the application into multiple services in the same domain.
+\paragraph{Y-axis Scaling}-- When compared to the z-axis and x-axis scaling, which follows the concept of running multiple identical copies of the application, but y-axis scaling segregates the application into multiple services in the same domain.
 So, the end services are responsible for one or more closely related functions of the previous service before the segregation.
@@
 \end{itemize}
-\emph{The microservice architecture is an application of Y-axis scaling}.
+\emph{The microservice architecture is an application of y-axis scaling}.
 
-\paragraph{Z-axis Scaling}-- The Z-axis scaling follows the concept of each service running the same application code (similar to X-axis scaling).
+\paragraph{Z-axis Scaling}-- The z-axis scaling follows the concept of each service running the same application code (similar to x-axis scaling).
 The big difference is that each service is responsible for only a subset of the data.
-Z-axis splits are commonly used to scale databases.
+z-axis splits are commonly used to scale databases.
 As an example, data partition (aka., sharded) across a set of servers based on an attribute of each record.
-Even our research is a design based on the Y-axis scaling; it is possible to use the Z-axis scaling to further scaling the system. We will discuss more detail in \cref{se:discussion}.
+Even our research is a design based on the y-axis scaling; it is possible to use the z-axis scaling to further scaling the system. We will discuss more detail in \cref{se:discussion}.
 
@@
 Export module microservices also follow the concepts of single responsibility and provide the capability to export the data into required formats of the weather models.
-Each data type adapter follows the microservice architecture concept of database per service, as mentioned in \cref{subse:database_per_service} When the system requires more database throughput, it is easy to scale each database instance by adding more resources or using Z-axis scaling concepts.
+Each data type adapter follows the microservice architecture concept of database per service, as mentioned in \cref{subse:database_per_service} When the system requires more database throughput, it is easy to scale each database instance by adding more resources or using z-axis scaling concepts.
 

### 2020-05-08 method/sec_4-db_struct.tex
x-axis, y-axis, z-axis

@@
 For the scalability, the system uses \emph{database per service}, as mentioned in \cref{subse:database_per_service}.
-If users want further performance, the database can split into another set of partitions based on other key attributes based on the Z-axis scaling described in \cref{subse:scale_cube}.
+If users want further performance, the database can split into another set of partitions based on other key attributes based on the z-axis scaling described in \cref{subse:scale_cube}.
 As an example, scalar and vector adapters can further split into more services based on other key attributes such as timeseriesType.
@@
 Vise a versa; when a new timeseries created in the adapter-metadata, it triggers an event to index metadata in the adapter-query.
-Here we used the \emph{Y-axis scaling} concept by splitting metadata search into multiple services.
+Here we used the \emph{y-axis scaling} concept by splitting metadata search into multiple services.
 Within the system, it uses in-memory database cache to support internal metadata access, and external search queries fulfill by the adapter-query with using MongoDB.

### 2020-05-08 results/sec_3-observations.tex
milliseconds

@@
 Insert timeseries performed over scalar and vector data types with each request sent with 24 data points.
-On average, it took 28ms to insert scalar and vector data into the \acrshort{wdias}, and up to 90\% percentile inserted data within 31ms.
+On average, it took 28 milliseconds to insert scalar and vector data into the \acrshort{wdias}, and up to 90\% percentile inserted data within 31ms.
 Noticeably it has 0\% of errors, which means that all the requests completed successfully.
@@
 Delay with inserting grid timeseries smaller because those requests are handled asynchronously.
-Retrieve grid timeseries data performed with a bit higher value of latency of 68ms due to performed the retrieve request on-demand.
+Retrieve grid timeseries data performed with a bit higher value of latency of 68 milliseconds due to performed the retrieve request on-demand.
 Both insert and retrieve grid timeseries data have 4.5 \acrshort{rps} since it only gets 10\% of the number of requests per given time during the load test.
@@
 \cref{tab:obs_all_auto_15_min_summary} shows the response latency summary details and \acrshort{rps} as explained in \cref{subse:obs_test_plan_all_15min}.
-If we analyzed the performance of the auto-scaling enabled microservice, the average grid data insertion latency was reduced from 91ms to 87ms.
+If we analyzed the performance of the auto-scaling enabled microservice, the average grid data insertion latency was reduced from 91 milliseconds to 87 milliseconds.
 Also, we can notice that the error percentage reduced from 1.42\% to 0.18\%.

### 2020-05-08 Appendix/apx_1_rest_api.tex
Separate appendix: v5.1.2

--- 2020-05-06 method/sec_3-microservice.tex
@@
-\section{Microservice Architecture}
-\label{se:microservice}
+\chapter{WDIAS REST API}
 
-A microservice architecture style is an approach to developing a single application as a package of small services, each working in their process and communicating using lightweight mechanisms, often through the delivery of a \acrfull{rest} \acrshort{api}.
-These services are built around commercial capacities and can be used independently by fully automated implementation machines \cite{LewisMicroservices}.
-In a microservice architecture, each microservice implements decoupling from other microservices and minimizing the centralized dependencies.
-Thus, we can use different programming languages and data storage technologies to implement each microservice.
-
-There are lots of microservice patterns developed and evolved.
-Through the following sections, we will discuss some of the microservice design patterns mostly used in the context of designing the software architecture for our research in brief.
-Next, we will discuss how microservice architecture promotes only to create endpoints that solely belong to each service logical domain.
-Next, consider only using a database per service, which allows it to be loosely coupled between systems and achieves high scalability.
-Then we will discuss how distributed transactions can makeover microservices.
-Last, we will discuss a concept called \emph{the scale cube}, which explains the scalability from the perspective of x,y, and z-axis.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Smart Endpoints and Dumb Pipes  Microservice Pattern}
-\label{subse:dumb_pipes}
-
-When building communication endpoints, many architectural approaches are adding significant smart by providing different protocol supports and complex logic support through the endpoints.
-As an example, \acrshort{esb} supports multiple protocols, and endpoints can be used to implement complex logic.
-But microservice architecture follows an alternative approach called as \emph{Smart endpoints and dumb pipes} \cite{LewisMicroservicesPipes}.
-Applications built based on microservice architecture are intended to be as disconnected and as coherent as possible.
-Each microservice has its domain logic and independent of other microservices logic and works more like filters in the classical Unix pipelines.
-Each microservice provides its functionalities as a \acrshort{rest} \acrshort{api} instead of using complex protocols.
-After receiving a request for each microservice through its \acrshort{rest} \acrshort{api}, it applies the correct logic and produces a response.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Database per Microservice Microservice Pattern}
-\label{subse:database_per_service}
-
-\acrshort{microservice} prefers to have each microservice manages its database, either different instances of the same database technology or entirely different database systems - an approach called \emph{Polyglot Persistence} \cite{LewisMicroservicesManagement}.
-
-The idea is to keep the persistent data of each microservice private for this service and only to make it accessible through an \acrshort{api}.
-There are different ways to keep the permanent data of a microservice private.
-But it is not required to set up a database instance for each microservice.
-For example, when you use a relational database, the following methods can be used to keep the data private \cite{RichardsonMicroservicesService}:
-\begin{itemize}
-    \item Individual tables per service - each microservice has a set of tables that restricts access for other microservices.
-    \item Schema per service - each service has a private database schedule for a given microservice.
-    \item Database server per service - each service has its database server.
-\end{itemize}
-
-\emph{Private tables per service} and \emph{schema per service} have the lowest overhead.
-The use of a schema per service is interesting because it makes the property clearer.
-Some high throughput services may require their database server.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Distributed Transactions over Microservices Pattern}
-\label{subse:sagas}
-
-Every microservice can have its database to guarantee a loose couple between microservices.
-Maintaining data consistency between services is a challenge because two phase-commit/distribution transactions are not an option for many applications.
-To archive distributed transactions, a service publishes an event when the data changes.
-Other services use this event and update their data \cite{RichardsonMicroservicesSagas}.
-The above approach is also called the \emph{Saga pattern}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{The Scale Cube Concept}
-\label{subse:scale_cube}
-
-The scalability of a system can be explained via a concept called \emph{the Scale Cube}, which talks about the scalability of the application by defining over X, Y, and Z axes.
-
-\paragraph{X-axis Scaling}-- When scaling an application through the X-axis, multiple instances of the application execute behind a load balancer.
-If there are \textit{n} copies, then each copy handles 1/\textit{n} of the load.
-The above simple approach is commonly to scale a service.
-
-\paragraph{Y-axis Scaling}-- When compared to the Z-axis and X-axis scaling, which follows the concept of running multiple identical copies of the application, but Y-axis scaling segregates the application into multiple services in the same domain.
-So, the end services are responsible for one or more closely related functions of the previous service before the segregation.
-There are different ways to split the application into services.
-\begin{itemize}
-    \item Verb-based decomposition. e.g., checkout.
-    \item Decompose the application by the noun. e.g., order management.
-    \item It is possible to use a combination of verb-based and noun-based decomposition for an application.
-\end{itemize}
-\emph{The microservice architecture is an application of Y-axis scaling}.
-
-\paragraph{Z-axis Scaling}-- The Z-axis scaling follows the concept of each service running the same application code (similar to X-axis scaling).
-The big difference is that each service is responsible for only a subset of the data.
-Z-axis splits are commonly used to scale databases.
-As an example, data partition (aka., sharded) across a set of servers based on an attribute of each record.
-Even our research is a design based on the Y-axis scaling; it is possible to use the Z-axis scaling to further scaling the system. We will discuss more detail in \cref{se:discussion}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{WDIAS Microservices}
-\label{sebse:wdias_microservices}
-
-\cref{fi:wdias_micro_on_demand} and \cref{fi:wdias_micro_async} show the system interaction of the WDIA microservices architecture while handling the requests.
-Each circle in the figures represents a microservice in the \acrshort{wdias}.
-And each microservice is implemented as a containerized application.
-The left side of \cref{fi:wdias_micro_on_demand} shows the import modules of the \acrshort{wdias}, and the right side shows the export modules.
-Also, we implemented each module as a microservice to independent maintainability and upgradability.
-We followed the concept of smart endpoints and dumb pipes explained in \cref{subse:dumb_pipes}, and each import microservice only does the specific task of converting and forwarding the request to the correct data adapter module.
-For scalar, vector, and grid data types, we created adapter microservices that are optimized for storing such kinds of data.
-And the metadata data of the timeseries store using an RDBMS, which gives more performance over retrieving timeseries metadata.
-The metadata is cached using an In-Memory database to fast access while implementing the database structure.
-The system generates a unique identifier for each timeseries, and throughout the \acrshort{wdias} system, all microservices use it to handle data for fast access.
-
-\begin{figure}[htp]
-    \centering
-    \includegraphics[width=1\textwidth]{method/microservice/microservice_architecture-handle_on_demand-v4.pdf}
-    \caption{\acrshort{wdias} architecture for handling requests on demand}
-    \label{fi:wdias_micro_on_demand}
-\end{figure}
-
-Export module microservices also follow the concepts of single responsibility and provide the capability to export the data into required formats of the weather models.
-Each data type adapter follows the microservice architecture concept of database per service, as mentioned in \cref{subse:database_per_service} When the system requires more database throughput, it is easy to scale each database instance by adding more resources or using Z-axis scaling concepts.
-
-\begin{figure}[htp]
-    \centering
-    \includegraphics[width=1\textwidth]{method/microservice/microservice_architecture-handle_on_async-v4.pdf}
-    \caption{\acrshort{wdias} architecture for handling requests asynchronously.}
-    \label{fi:wdias_micro_async}
-\end{figure}
-
-As shown in \cref{fi:wdias_micro_on_demand}, when a request with a smaller payload comes to the system, the system handles the request on-demand and response back.
-However, as shown in \cref{fi:wdias_micro_async}, when a request with a larger payload comes to the system, it stores the data for an asynchronous process and responds with a unique id that can be used to verify whether data processed successfully or not.
-We used the microservice concept of Saga, as mentioned in \cref{subse:sagas}, while processing the Grid data.
-First, it stores the data and responds with a unique identifier to the user.
-After successfully storing the data, the microservice publishes an event.
-Another microservice listens to those events and processes the data and updates the system status.
-
-\begin{figure}[htp]
-    \centering
-    \includegraphics[width=1\textwidth]{method/microservice/separation_microservices-v4.pdf}
-    \caption{Separation of \acrshort{wdias} microservices.}
-    \label{fi:wdias_micro_separation}
-\end{figure}
-
-\cref{fi:wdias_micro_separation} shows the clear separation of microservices into the modules of the \acrshort{wdias}.
-Each adapter has a separate database, and the database is hosted separately for the high performance and to avoid interferences.
-Apart from that, as we further discuss in \cref{se:data_preprocess}, the extension modules are running independently, such as Interpolation, Transformation, and Validation, and we will also discuss in \cref{se:data_preprocess}.
-The Extension Adapter allows users to register new event-based or time-based triggers for the extensions.
-The extension scheduler triggers the events based on time and the extension handler triggers events based on data change.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{WDIAS Application Programming Interface}
-\label{sebse:wdias_api}
-
-We defined an \acrfull{rest} as the communication layer for \acrshort{wdias}, and it affects the microservice architecture design as well.
-It follows a simple \acrshort{rest} \acrshort{api} and allows users to interact with the system through HTTP methods.
-
-We provided a set of timeseries endpoints to register new timeseries metadata before storing the real data.
-Timeseries endpoints allow users to interact with Metadata Adapter to create and update the timeseries metadata.
-And create timeseries metadata, we cached on the Query Handler to perform search queries and geo-indexed to support geo-based queries.
-When a user registers a timeseries metadata, the system generates a unique timeseries identifier based on the metadata values.
-Then the user can use that identifier to store the real weather data and retrieve stored data.
-
+\emph{Timeseries Metadata} endpoints allow to register new timeseries into the \acrshort{wdias} system before upload data.
 \begin{itemize}
@@
 
-Current \acrshort{wdias} only supports handling point locations and grid locations.
-If it needs to extend the system to store irregular grid data, then it should add another set of location endpoints for storing irregular grid location details.
-
 \emph{Import} endpoints allow to upload data into the \acrshort{wdias} system.
@@
 \end{itemize}
-
-Other than the above endpoints, we exposed another set of endpoints to configure extensions, and we will describe further in \cref{se:data_preprocess}.
-Other than the timeseries metadata endpoints, other module endpoints start with the module name such as import, export, and extension when compared to timeseries metadata endpoints.
-Using the above convention, we allowed adding a new module system if required.
-For import and export modules, the names of the endpoints defined as the modules name then follow the data format.
-The above endpoint naming convention provides the flexibility to integrate new data format modules for import and export.
-Then the endpoint name ends with the type of data operation.
-Data can upload as a single file with binary or multiple files with the upload.
-Other than that, users can send requests with raw data with required headers has mentioned by a particular import module.
-Thus, the \acrshort{api} convention of \texttt{/MODULE/DATA\_FORMAT/DATA\_TYPE} allows users to integrate new import or export modules into the system, as well as add new data types.

### 2020-05-08 Appendix/apx_2_query_api.tex
Separate appendix: v5.1.2

--- 2020-04-26 method/sec_6-query.tex
@@
-\section{Query Timeseries}
-\label{se:query}
+\addtocontents{toc}{\protect\setcounter{tocdepth}{0}} 
+\chapter{WDIAS Query API}
 
-We used the adapter-query primarily for supporting Geospatial queries.
-As the primary service for searching for timeseries, it supports retrieval of timeseries metadata for external queries as well.
-The following sections described the search query capabilities of \acrshort{wdias}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Timeseries Metadata}
+\subsection{Timeseries Metadata Queries}
 Get timeseries metadata by timeseriesID.
@@
 \end{lstlisting}
-
-\dbc{Need a chapter summary Sec.}

### 2020-05-08 method/sec_3-microservice.tex
Separate appendix: v5.1.2

@@
 
-We provided a set of timeseries endpoints to register new timeseries metadata before storing the real data.
+We provided a set of timeseries endpoints to register new timeseries metadata before storing the real data, and a detailed description appears in Appendix A.
 Timeseries endpoints allow users to interact with Metadata Adapter to create and update the timeseries metadata.
@@
 
-\begin{itemize}
-    \item parameter
-    \begin{itemize}
-        \item \texttt{GET /parameter} -- Get parameters
-        \item \texttt{POST /parameter} -- Create parameter
-        \item \texttt{PUT /parameter/id} -- Update parameter
-        \item \texttt{DELETE /parameter/id} -- Delete parameter
-    \end{itemize}
-    \item timeStep
-    \begin{itemize}
-        \item \texttt{GET /timestep} -- Get TimeSteps
-        \item \texttt{POST /timestep} -- Create TimeStep
-        \item \texttt{PUT /timestep/id} -- Update TimeStep
-        \item \texttt{DELETE /timestep/id} -- Delete TimeStep
-    \end{itemize}
-    \item location
-    \begin{itemize}
-        \item \texttt{GET /location} -- Get location points
-        \item \texttt{POST /location} -- Create location point
-        \item \texttt{PUT /location/id} -- Update location point
-        \item \texttt{DELETE /location/id} -- Delete location point
-        \item \texttt{GET /location/regular-grid} -- Get regular grids
-        \item \texttt{POST /location/regular-grid} -- Create regular grid
-        \item \texttt{PUT /location/regular-grid/id} -- Update regular grid
-        \item \texttt{DELETE /location/regular-grid/id} -- Delete regular grid
-    \end{itemize}
-    \item timeseries
-    \begin{itemize}
-        \item \texttt{GET /timeseries} -- Get timeseries
-        \item \texttt{POST /timeseries} -- Create timeseries
-        \item \texttt{PUT /timeseries/id} -- Update timeseries
-        \item \texttt{DELETE /timeseries/id} -- Delete timeseries
-    \end{itemize}
-\end{itemize}
-
 Current \acrshort{wdias} only supports handling point locations and grid locations.
@@
 
-\emph{Import} endpoints allow to upload data into the \acrshort{wdias} system.
-\begin{itemize}
-    \item \texttt{POST /import/json/raw} -- Insert Scalar/Vector timeseries data with JSON body
-    \item \texttt{POST /import/csv/raw} -- Insert Scalar/Vector timeseries data in CSV format
-    \item \texttt{POST /import/ascii-grid/upload} -- Upload set of ASCII Grid files
-    \item \texttt{POST /import/ascii-grid/binary} -- Upload a single ASCII Grid file
-\end{itemize}
-
-\emph{Export} endpoints allow to get/download data from the \acrshort{wdias} system.
-\begin{itemize}
-    \item \texttt{GET /export/json/raw} -- Get Scalar/Vector timeseries data in JSON format
-    \item \texttt{GET /export/json/raw?start=2000-01-01\&end=2000-01-03} -- Get Scalar/Vector timeseries data in JSON format for given time period
-    \item \texttt{GET /export/netcdf/binary} -- Download Grid data timeseries data in \acrshort{netCDF} format
-\end{itemize}
-
-Other than the above endpoints, we exposed another set of endpoints to configure extensions, and we will describe further in \cref{se:data_preprocess}.
+Other than the endpoints in Appendix A, we exposed another set of endpoints to configure extensions, and we will describe further in \cref{se:data_preprocess}.
 Other than the timeseries metadata endpoints, other module endpoints start with the module name such as import, export, and extension when compared to timeseries metadata endpoints.

### 2020-05-08 method/sec_6-query.tex
v5.0
Separate appendix: v5.1.2

@@
 
-We used the adapter-query primarily for supporting Geospatial queries.
+We used the adapter-query primarily for supporting Geo-spatial queries.
 As the primary service for searching for timeseries, it supports retrieval of timeseries metadata for external queries as well.
-The following sections described the search query capabilities of \acrshort{wdias}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Timeseries Metadata}
-Get timeseries metadata by timeseriesID.
-\begin{lstlisting}
-    GET <HOST_ADDR>/metadata/timeseries/<TIMESERIES_ID>
-\end{lstlisting}
-
-Search for timeseries metadata with key attributes of the timeseries.
-\begin{lstlisting}
-    GET <HOST_ADDR>/metadata/timeseries?<QUERY_STRING}
-\end{lstlisting}
-
-QUERY\_STRING can be consist of zero to multiple parameters. Multiple query parameters are separated by the ampersand, "\&".
+The Appendix B described the search query capabilities of \acrshort{wdias}.
+The system provides timeseries metadata query endpoints to search for existing timeseries metadata within the system using primary key attributes.
+Also, it provides a set of Geo query endpoints, and users can perform Geo search queries with sending geo-information in geoJson format.
+The following Geo queries are supported by the system, and a detailed description appears in Appendix B.
 \begin{itemize}
-    \item \texttt{moduleId} (Optional), e.g., HEC-HMS
-    \item \texttt{valueType} (Optional), e.g., Scalar
-    \item \texttt{parameterId} (Optional), e.g., O.Precipitation
-    \item \texttt{locationId} (Optional), e.g., wdias\_hanwella
-    \item \texttt{timeseriesType} (Optional), e.g., ExternalHistorical
-    \item \texttt{timeStepId} (Optional), e.g., each\_15\_min
+    \item Query Locations within Area
+    \item Query parameters in Locations
+    \item Query Timeseries by Location
+    \item Query Timeseries by Locations
+    \item Query Timeseries by Parameter
+    \item Query Timeseries in Area
+    \item Query Timeseries in Area by Parameter
+    \item Query All Timeseries
 \end{itemize}
-For the moment, query are only support by strict matching with above parameter values.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Timeseries Geo Queries}
-
-\paragraph{Query Locations within Area}-- Following endpoint supports to query the locations which exist within the area provided by the GeoJson data in the JSON payload.
-\begin{lstlisting}
-    POST <HOST_ADDR>/query/location
-    JSON Body:
-    {
-        "geoJson": {
-            "type": "Polygon",
-            "coordinates": [
-                [
-                    [
-                        <longitude>,
-                        <latitude>
-                    ],
-                    ...
-                ]
-            ]
-        }
-    }
-\end{lstlisting}
-
-paragraph{Query parameters in Locations}-- Following endpoint supports to query the parameters stored against given locations. Location IDs should be provided as a list of JSON payload.payload.
-\begin{lstlisting}
-    POST <HOST_ADDR>/query/parameter
-    JSON Body:
-    ["<locationID>", ...]
-\end{lstlisting}
-
-\paragraph{Query Timeseries by Location}-- Following endpoint supports to query the timeseries metadata for a given location.
-\begin{lstlisting}
-    POST <HOST_ADDR>/query/timeseries
-    JSON Body:
-    {
-        "location": "<LOCATION_ID>"
-    }
-\end{lstlisting}
-
-\subsubsection{Query Timeseries by Locations}
-Following endpoint supports to query the timeseries metadata for a given location set. Location IDs should be provided as a list in the locations field.
-\begin{lstlisting}
-    POST <HOST_ADDR>/query/timeseries
-    JSON Body:
-    {
-        "locations": ["LOCATION_ID", ...]
-    }
-\end{lstlisting}
-
-\subsubsection{Query Timeseries by Parameter}
-Following endpoint supports to query the timeseries metadata by parameter for given location/locations.
-\begin{lstlisting}
-    POST <HOST_ADDR>/query/timeseries
-    JSON Body:
-    {
-        "locations": [""],
-        "parameter": ""
-    }
-\end{lstlisting}
-
-\paragraph{Query Timeseries in Area} -- Following endpoint supports to query the timeseries metadata within a given area (specified as a polygon in geoJson format).
-\begin{lstlisting}
-    POST <HOST_ADDR>/query/timeseries
-    JSON Body:
-    {
-        "geoJson": {
-            "type": "Polygon",
-            "coordinates": [
-                [
-                    [
-                        <longitude>,
-                        <latitude>
-                    ],
-                    ...
-                ]
-            ]
-        }
-    }
-\end{lstlisting}
-
-\paragraph{Query Timeseries in Area by Parameter}-- Following endpoint supports to query the timeseries metadata within a given area for a given parameter.
-This endpoint is an extension of the above endpoint.
-\begin{lstlisting}
-    POST <HOST_ADDR>/query/timeseries
-    JSON Body:
-    {
-        "geoJson": {
-            "type": "Polygon",
-            "coordinates": [
-                [
-                    [
-                        <longitude>,
-                        <latitude>
-                    ],
-                    ...
-                ]
-            ]
-        },
-        "parameter": "<PARAMETER_ID>"
-    }
-\end{lstlisting}
-
-\paragraph{Query All Timeseries} -- Send a request with an empty JSON body that will respond with all the timeseries.
-\begin{lstlisting}
-    POST <HOST_ADDR>/query/timeseries
-    JSON Body:
-    {}
-\end{lstlisting}
-
-\dbc{Need a chapter summary Sec.}

### 2020-05-08 summary/sec_1-conclusions.tex
Separate appendix: v5.1.2

@@
 This capability enables us to integrate weather data preprocessing flows as extension modules.
-We designed an extension API to easily access to create and modify the extension triggers at runtime without stopping the system or any downtime for the system reconfiguration.
+We designed an extension API to easily access to create and modify the extension triggers at run time without stopping the system or any downtime for the system reconfiguration.
 The system provides extensive timeseries query endpoints to easy search over the stored timeseries metadata with supporting Geo-based queries.
 
-%Further, we performed load tests using the JMeter tool’s distributed testing capabilities. Then the test plans are performed with increasing the request size and monitoring the performance metrics. 
-We evaluated the performance using a cloud-based setup on the Amazon Elastic Kubernetes Service (Amazon EKS). % as per the system setup configurations of \cref{subse:test_sys_config}. 
+We evaluated the performance using a cloud-based setup on the Amazon Elastic Kubernetes Service (Amazon EKS).
 Based on the performance analysis, we were able to perform 300 \acrshort{rps}, and the system handled the workload successfully with minimizing the error rate.

### 2020-05-08 method/sec_0_introduction.tex
v5.1.1
Make geo- consistent

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Modules of a Weather Data System}
-\label{subse:modules_weather_data_integration_sys}
+% \subsection{Modules of a Weather Data System}
+% \label{subse:modules_weather_data_integration_sys}
 
@@
 \begin{figure}[htbp]
-\centerline{\includegraphics[width=1\textwidth]{method/misc/weather_data_system_components.jpg}}
+\centerline{\includegraphics[width=1\textwidth]{method/misc/weather_data_system_components.pdf}}
 \caption{Modules of a weather data system.}
@@
 Then different users should be able to retrieve data as they require.
-Also, the users should be able to easily search into the available information in the system based on timeseries metadata or based on Geo queries.
+Also, the users should be able to easily search into the available information in the system based on timeseries metadata or based on geo-queries.

### 2020-05-08 method/sec_4-db_struct.tex
Make geo- consistent

@@
 To provide fast geo-search queries, we have to use a database system that supports geo indexing.
-We used MongoDB, which is a document-oriented database with Geo indexing capabilities.
+We used MongoDB, which is a document-oriented database with geo indexing capabilities.
 Also, MongoDB \cite{mongodbMongoDBManual} is a general-purpose, document-based, distributed database, and supports:
@@
 
-We used MongoDB geospatial features to support Geo queries in the \acrshort{wdias}.
+We used MongoDB geospatial features to support geo-queries in the \acrshort{wdias}.
 Also, we indexed the timeseries metadata with other indexing features to serve external timeseries metadata queries.

### 2020-05-08 method/sec_6-query.tex
Make geo- consistent

@@
 
-We used the adapter-query primarily for supporting Geo-spatial queries.
+We used the adapter-query primarily for supporting geo-spatial queries.
 As the primary service for searching for timeseries, it supports retrieval of timeseries metadata for external queries as well.
@@
 The system provides timeseries metadata query endpoints to search for existing timeseries metadata within the system using primary key attributes.
-Also, it provides a set of Geo query endpoints, and users can perform Geo search queries with sending geo-information in geoJson format.
-The following Geo queries are supported by the system, and a detailed description appears in Appendix B.
+Also, it provides a set of geo-query endpoints, and users can perform geo-search queries with sending geo-information in geoJson format.
+The following geo-queries are supported by the system, and a detailed description appears in Appendix B.
 \begin{itemize}

### 2020-05-08 method/sec_7-summary.tex
Make geo- consistent

@@
 Further, we provided a comprehensive extension module system that allows users to preprocess data by creating new triggers without any downtime for system configuration.
-We used a geo indexing mechanism to support Geo search queries and indexed the timeseries metadata to support the search for any timeseries in \acrshort{wdias}.
+We used a geo indexing mechanism to support geo-search queries and indexed the timeseries metadata to support the search for any timeseries in \acrshort{wdias}.

### 2020-05-08 results/sec_1-test_plan.tex
Make geo- consistent

@@
 Other than the above modules, \emph{adapter modules} act as the core modules and the base of the system.
-Also, the \emph{query module} allows the users to query for the timeseries based on the metadata and perform Geo-based queries based on the locations.
+Also, the \emph{query module} allows the users to query for the timeseries based on the metadata and perform geo-based queries based on the locations.
 

### 2020-05-08 Thesis.tex
v5.1.1
Separate appendix: v5.1.2
code listing - single space and avoid span over pages

@@
 \usepackage{biblatex}
+\usepackage[titletoc]{appendix}
 
@@
   backgroundcolor=\color{backcolour}, commentstyle=\color{codegreen},
-  basicstyle=\ttfamily\footnotesize,
+  basicstyle=\linespread{1.0}\ttfamily\footnotesize,
   breakatwhitespace=false,
@@
 
-% \import{results/}{sec_2-workload.tex}
+\import{results/}{sec_2-workload.tex}
 
-% \import{results/}{sec_3-observations.tex}
+\import{results/}{sec_3-observations.tex}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \appendix
-% \import{Appendix/}{app_1_soa_and_actor_model.tex}
 
@@
 % \addbibresource{mendeley.bib}
+
+\addcontentsline{toc}{chapter}{References} 
 \printbibliography[title={References}]
+
+\begin{appendices}
+\input{Appendix/apx_1_rest_api}
+\end{appendices}
+
+\begin{appendices}
+\input{Appendix/apx_2_query_api}
+\end{appendices}
+
 \end{document}

### 2020-05-08 summary/sec_1-conclusions.tex
Make geo- consistent
code listing - single space and avoid span over pages

@@
 We mapped each microservice of \acrshort{wdias} to a pod in the \acrshort{k8s} cluster.
-Also, each microservice follows the concept of smart endpoints dumb pipes[?] and does specific operations that are related to the data format that responsible for handling.
+Also, each microservice follows the concept of smart endpoints dumb pipes in \cref{subse:dumb_pipes} and does specific operations that are related to the data format that responsible for handling.
 \dbc{Need to explain the solution based on microservices as it's the most important. Also, a reference is missing here}

### 2020-05-08 introduction/sec_2-problem_and_objectives.tex

@@
 Further, users should be able to easily deploy and manage the system while benefiting from technological advances. 
-%with modern technologies and should be able to get the advantage of technology advancement.
 In this context, the research problem can be stated as follows:
 
-\emph{How to design an extendable weather data integration, assimilation, and dissemination system that is capable of handling large volumes of multimodel weather data while providing high throughput, scalability, and availability?}
+\emph{How to design an extendable weather data integration, assimilation, and dissemination system that is capable of handling large volumes of multi-model weather data while providing high throughput, scalability, and availability?}
 
@@
     \item To develop an API for third-party data sharing
-\dbc{Add a another objective for performance analysis}
-%    \item To use open source tools and provide the source publicly with appropriate liecense.
+    \item To perform a load test to analyse throughput, scalability of the system
 \end{itemize}

### 2020-05-09 summary/sec_1-conclusions.tex
Final v5.2 - Submit for supervisor

@@
 Also, each microservice follows the concept of smart endpoints dumb pipes in \cref{subse:dumb_pipes} and does specific operations that are related to the data format that responsible for handling.
-\dbc{Need to explain the solution based on microservices as it's the most important. Also, a reference is missing here}
+We handle importing different format data into the system via The import microservices.
+Then we store timeseries data using appropriate data adapter microservices.
+By using export microservices, users can fetch data in the required format.
+The extension microservices enables data preprocessing capabilities.
+Also, users can integrate new features into the system as new extension microservices.
+The query microservice support timeseries metadata search queries and geo-based search queries.
+Also, the system provides asynchronous request handling with exposing the status via the status handler.
 
@@
 We designed an extension API to easily access to create and modify the extension triggers at run time without stopping the system or any downtime for the system reconfiguration.
-The system provides extensive timeseries query endpoints to easy search over the stored timeseries metadata with supporting Geo-based queries.
+The system provides extensive timeseries query endpoints to easy search over the stored timeseries metadata with supporting geo-based queries.
 
-We evaluated the performance using a cloud-based setup on the Amazon Elastic Kubernetes Service (Amazon EKS).
+We evaluated the performance using a cloud-based setup on the \acrfull{eks}.
 Based on the performance analysis, we were able to perform 300 \acrshort{rps}, and the system handled the workload successfully with minimizing the error rate.

### 2020-05-16 Thesis.tex
Final v5.2 - Submit for supervisor
NWMs

@@
 
-\acrfull{nwm} utilize data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images.
+\acrfull{nwm}s utilize data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images.
 Before using such multimodal data in a \acrshort{nwm}, it is necessary to transcode data into a format that can be ingested by the NWM.
-Moreover, the data integration system's response time needs to be relatively low to forecast and monitor time-sensitive weather events like hurricanes, storms, and flash floods that require rapid and frequent execution of \acrshort{nwm}.
+Moreover, the data integration system's response time needs to be relatively low to forecast and monitor time-sensitive weather events like hurricanes, storms, and flash floods that require rapid and frequent execution of \acrshort{nwm}s.
 The resulting weather data also need to be accessed by many researchers and third-party applications such as logistic and agricultural insurance firms.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{appendices}
+    \chapter{WDIAS REST API}
     \input{Appendix/apx_1_rest_api}
-\end{appendices}
-
-\begin{appendices}
+    \chapter{WDIAS Query API}
     \input{Appendix/apx_2_query_api}
@@
 
+% \appendix
+% \addcontentsline{toc}{section}{Appendix~\ref{apx:rest_api}: WDIAS REST API}
+% \chapter{WDIAS REST API}
+% \input{Appendix/apx_1_rest_api}
+% \addtocontents{toc}{\protect\setcounter{tocdepth}{0}} % Issue with List of figures
+% \chapter{WDIAS Query API}
+% \input{Appendix/apx_2_query_api}
+
 \end{document}

### 2020-05-16 introduction/sec_1-motivation.tex
NWMs

@@
 Weather forecast is essential to reduce the impact caused by natural disasters and to effectively manage natural resources like water.
-The weather forecasts are performed using \acrfull{nwm} that use a set of configuration parameters and the current status of the environment such as temperature, rainfall, and wind direction as the inputs.
+The weather forecasts are performed using \acrfull{nwm}s that use a set of configuration parameters and the current status of the environment such as temperature, rainfall, and wind direction as the inputs.
 For example, the \acrfull{wrf} \cite{MesoscaleMicroscaleMeteorologyLaboratoryWeatherModel} model is used to predict the rainfall, temperature, and wind direction.
@@
 
-Weather data processed by one \acrshort{nwm} maybe used by several other NWSs, as well as by many third-party applications and researcher.
+Weather data processed by one \acrshort{nwm} maybe used by several other \acrshort{nwm}s, as well as by many third-party applications and researcher.
 For example, logistic companies could use the processed data with their models to plan and schedule their deliveries.

### 2020-05-16 Thesis.tex
v5.2.2 Intro

--- 2020-05-08 Thesis.tex
@@
 \acrfull{nwm} utilize data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images.
-Before using such multimodal data in a \acrshort{nwm}, it is necessary to transcode data into a format that can be ingested by the NWM.
+Before using such multimodal data in a NWM, it is necessary to transcode data into a format that can be ingested by the \acrshort{nwm}.
 Moreover, the data integration system's response time needs to be relatively low to forecast and monitor time-sensitive weather events like hurricanes, storms, and flash floods that require rapid and frequent execution of \acrshort{nwm}.
 The resulting weather data also need to be accessed by many researchers and third-party applications such as logistic and agricultural insurance firms.
-Existing weather data integration systems are based on monolithic or client-server architectures; hence, unable to benefit from novel computational models such as cloud computing and containers.
-Moreover, most of this software is proprietary or closed-source, making it difficult to customize them for an island like Sri Lanka with different weather seasons.
+Existing weather data integration systems are based on monolithic or client-server architectures; hence, unable to benefit from novel computational models such as cloud computing and containerized applications.
+Moreover, most of these software are proprietary or closed-source, making it difficult to customize them for an island like Sri Lanka with different weather seasons.
 Therefore, in this research, we propose \acrfull{wdias} that utilizes modern architectural patterns such as microservices to achieve scalability, high availability, and low-cost operation based on cloud computing.
@@
 Karunarathne whose put countless sweats to support me throughout my entire life.
-My wife Jayani Kumarasinghe and my son Sasmitha Karunarathne who missed a lots of wonderful moments to give me freedom to work on my research.
+My wife Jayani Kumarasinghe and my son Sasmitha Karunarathne who missed a lots of wonderful moments to give me freedom to work on this research.
 

### 2020-05-16 introduction/sec_1-motivation.tex
v5.2.2 Intro

--- 2020-05-07 introduction/sec_1-motivation.tex
@@
 
-Weather data processed by one \acrshort{nwm} maybe used by several other NWSs, as well as by many third-party applications and researcher.
-For example, logistic companies could use the processed data with their models to plan and schedule their deliveries.
+Weather data processed by a NWM maybe used by several other \acrshort{nwm}, as well as by many third-party applications and researcher.
+For example, logistic companies could use the processed data with their data models to plan and schedule their deliveries.
 Agricultural insurance companies can warn the farmers, as well as calculate premiums based on the anticipated weather patterns.
 Besides, farmers could rely on weather forecasts to plan their work.
-% decide what work to do on a given day.
-For example, drying hay is only possible in dry weather.
-Also, the aeronautical industry is particularly sensitive to weather conditions, precise weather forecasts are essential since before takeoff a flight need to check the conditions on expected route and at destination.
-%required a provide platform to provide such 3rd party access, and use the data or process those based on their applications.
 
 Data Integration and Analysis System (DIAS) \cite{Kawasaki2018DataReduction} and Meteorological Assimilation Data Ingest System (MADIS) \cite{Macdermaid2005ArchitectureP2.39} are two of the well-known Weather Data Integration and Assimilation (WDIA) systems.
-However, they are proprietary.
-Further, while \acrfull{fews} \cite{Werner2013TheSystem} is free to use, it is not open source.
+However, those are proprietary systems.
+Further, while \acrfull{fews} \cite{Werner2013TheSystem} is free to use, but it is not open source.
 While a few other data integration systems exists, most of them are also proprietary or closed source.
 Thus, it is difficult and costly to customize such systems for an island like Sri Lanka which experience different kinds of weather seasons over the year \cite{NaveendrakumarFiveLanka}.
-% than that software originated need to be highly customized.
-Throughout the operations and maintenance, it is required to get support with paying lots of charges, and difficult to debug into a closed source system without maintenance support from the vendors.
-For example, \acrshort{fews} does not support FLO2D model integration, which is used by \acrshort{curw}'s workflows for water-level forecasting.
-%In such a case, it required to get support from the vendor to integrate and configure the system.
+For example, \acrshort{fews} does not support FLO2D model integration, which is used by \acrshort{curw} to forecast water level.
 
-Existing WDIA systems are based on 
-%Most of the software existing out there is not up to date with the latest technology concepts such as Cloud Computing.
-The modern architecture pattern such as microservice architecture was able to provide high scalability and availability, rather using
-the monolithic or client service architecture; hence, cannot benefit from technologies such as cloud computing to achieve high scalability and availability.
+Existing WDIA systems are based on the monolithic or client service architecture; hence, cannot benefit from technologies such as cloud computing to achieve high scalability and availability.
 Moreover, such systems cannot be updated or reconfigured without taking the system off line.
-Furthermore, they are platform specific.
+Furthermore, these systems are platform specific.
 For example, while \acrshort{fews} can run on either Windows or Linux, downtime is needed to introduce any changes to the system.
-% Most existing systems required to shut down to update the system configuration such as \acrshort{fews}, but a system that is accessed by any third parties should be operating 99.9\% without any downtime and should allow adding new features on the fly with rollover capabilities.
-The proposed system should be independent of the platforms.
-But most software out there is platform dependent, as an example \acrshort{fews} can run on Windows and Linux.
-And should be independent underline infrastructure providers which gives much flexibility for the users to decide the best cost-effective way to host it.
 

### 2020-05-24 lit/sec_1-fews.tex
Proofread chapter 2

@@
 The \acrshort{fews} codebase is not fully open source at the moment.
-The main objective of a forecasting system is to run multiple NWMs, hydrologic, and hydrodynamic models which are required for the predictions.
+The main objective of a forecasting system is to run multiple NWMs, hydrologic models, and hydrodynamic models which are required for the predictions.
 This approach is known as a model-centric approach \cite{Werner2005FloodCatchments}.
@@
 Also, the outputs produced by the models are specific to the model; hence, difficult to integrate with other models.
-For example, FLO2D creates human-readable text output files.
-However, the Delft-FEWS uses a more modular approach, which is easier to integrate new models and redevelop the system for new requirements.
+For example, FLO2D creates human-readable text files as output.
+However, the Delft-FEWS uses a more modular approach, which is easier to integrate new models and update the system for new requirements.
 Thus, Delft-FEWS is an integration framework or middleware for the models, rather specific model workflow for weather forecasting.
@@
 So, the \acrshort{fews} framework is capable of integrating models into the system and creating workflows for forecasting.
-
-Are proposed by Haggett \cite{Haggett1998AnWales} key elements of a forecasting system are defined as detection, forecasting, dissemination and warning, and responding to the events.
-The \acrshort{fews} focuses on the forecasting step out from above steps.
-The main objective of this step is to provide additional lead time by forecasting future hydro-meteorological conditions \cite{Werner2005FloodCatchments}.
-It is a valid argument that providing accurate predictions with greater lead time can reduce the level of destruction.
-To forecast, the system should be capable of integrating real-time data from meteorological and hydrological observation network systems, and the disseminate the forecasted results through relevant products to the warning process.
 
@@
 One of the widely practiced use cases is to use meteorological forecast data to estimate precipitation, and then use a hydrological and hydraulic model chain to predict the surface water level affected.
-The hydrological and hydrodynamic models should design based on geographical data.
+The hydrological and hydrodynamic models should design based on geographical surface data.
 The ground surface should be examined geographically and divided into catchments.
@@
 The \acrshort{fews} follows a data-centric approach, where it provides a common data-model to interact with other components.
-All the timeseries data stored in a database by converting them to a common data model.
+All the timeseries data stored in a database by converting them to the common data model.
 New models are integrated into the system by using one of the interfaces provided to interact with the common data-model \cite{Werner2013TheSystem}.
@@
 The \acrshort{fews} overcome this issue by introducing adapters for most of the commonly used data formats such as CSV, NetCDF, and JSON.
-While this enables users to import data into the system; it also introduces adding additional complexity to the system.
+While this enables users to import multiple data formats into the system; it also introduces adding additional complexity to the system.
 
@@
 However, a single data source becomes a bottleneck when it is required to fulfill all the timeseries data requirements.
-Further, the performance goes down due to the need to scream Spatio-temporal weather data.
+Further, the performance goes down due to the need to stream spatio-temporal weather data.
 
@@
 Alternatively, separate timeseries by data type and stored in multiple storages give the capability for the system to scale with a factor of identical types.
-An example of separation by data types of scalar, vector, and gridded will increase the scaling factor by 3x.
+An example of separation of database by data types of scalar, vector, and gridded into three independently hosted databases will increase the performance factor by three times.
 
@@
 The system contains a set of default data processing functions, but required algorithms can implement as a new Java class integrated with the \acrfull{api} provided by the Delft-FEWS.
-The Delft-FEWS has language dependency while additional features integration since users need to implement the new functional extensions using Java.
+The Delft-FEWS has language dependency while additional features integration since users need to implement the new functional extensions using Java programming language.
 

### 2020-05-24 lit/sec_2-lead.tex
Proofread chapter 2

@@
 At the time, some researchers are developing their experiment forecasting flows, they are not using the resources, and other researchers can run their forecasting flows using available resources.
-The foundation of the LEAD system is to create a dynamic workflow orchestration and data management in a Web services framework \cite{Droegemeier2005Service-OrientedWeather}.
+The foundation of the LEAD system is to create a dynamic workflow orchestration and data management in a web services framework \cite{Droegemeier2005Service-OrientedWeather}.
 
@@
 \begin{itemize}
-    \item The users interact with LEAD via a Web portal
+    \item The users interact with LEAD via a web portal
     \item Data quality control and assimilation happens via ARPS Data Assimilation System (ADAS)
     \item myLEAD is the metadata catalog
-    \item Weather Research and Forecast \acrfull{wrf} \cite{MesoscaleMicroscaleMeteorologyLaboratoryWeatherModel}
-    \item Algorithm Development and Mining is a set of tools for analyzing observational data, assimilated data sets, and model output
-    \item Integrated Data Viewer 
+    \item \acrfull{wrf} \cite{MesoscaleMicroscaleMeteorologyLaboratoryWeatherModel}
+    \item Algorithm development and mining is a set of tools for analyzing observational data, assimilated data sets, and model output
+    \item Integrated data viewer 
 \end{itemize}
@@
     \item User subsystem – comprises the LEAD portal and enable user can access services
-    \item Data subsystem – manages data and metadata, all output of digital models produced by operational or experimental models, and information generated by users.
+    \item Data subsystem – manages data and metadata, all output of digital models produced by operational or experimental models, and information generated by users
     \item Tools subsystem – provides all IT tools and meteorological tools
-    \item Orchestration subsystem – offers the technologies with which users can manage data flows and model execution flows and can create and own output.
-It also provides links to other software and processes for continuous or on-demand applications.
+    \item Orchestration subsystem – offers the technologies with which users can manage data flows and model execution flows and can create and own output
 \end{itemize}
@@
 The upper layer of the raw resources is abstracting the complexity of managing and accessing the resources and provides simplified access.
-In the Upper layers, the underline system is viewed as an unlimited resource pool for storing and handling data.
+In the upper layers, the underline system is viewed as an unlimited resource pool for storing and handling data.
 

### 2020-05-24 lit/sec_3-other-systems.tex
Proofread chapter 2

@@
 To store on the large volume of disk space, it converts the data via a provided set of APIs.
-The above concept is similar to Delft-FEWs open data model approach.
+The above concept is similar to Delft-FEW's open data model approach.
 Further, the DIAS contains additional tools that provide the functionality of quality control of the data and metadata management, which is similar to some of the services in LEAD.
@@
 As shown in \cref{fi:dias_common_platform}, it offers an application layer that allows scientists to work on research tasks and to develop specific tools and applications by collaborating with IT experts \cite{Kawasaki2018DataReduction}.
-Once the data is stored on the DIAS system, it shares those data via the Shared API layer and allows users to remote access to the data and easy integration via the APIs.
+Once the data is stored on the DIAS system, it shares those data via the shared API layer and allows users to remote access to the data and easy integration via the APIs.
 
@@
 
-Based on the above statements, we can conclude that these kinds of functionalities are available at the modern Cloud Computing tools, and out of the box, those tools are providing the scalability and high availability.
+Based on the above statements, we can conclude that these kinds of functionalities are available at the modern cloud computing tools, and out of the box, those tools are providing the scalability and high availability.
 Using those tools, it is possible to implement such a system with less effort and high confidence.
 
-The MADIS regularly acquires Mesonet data from dozens of network providers representing more than 14,000 stations, and the system translates into more than 30,000 station reports every hour.
+The MADIS regularly acquires mesonet data from dozens of network providers representing more than 14,000 stations, and the system translates into more than 30,000 station reports every hour.
 Different systems that work inside and outside the firewall collect the data.

### 2020-05-29 method/sec_0_introduction.tex
4.2 Done

@@
-This Chapter presents the design decisions taken while implementing \acrfull{wdias} and how we adopt from the systems analyzed in \ref{ch:literature}.
+This Chapter presents the design decisions taken while implementing \acrfull{wdias} and how we adopt from the systems analyzed in \cref{ch:literature}.
 \cref{se:high_level_design} presents a brief discussion on how  the weather forecasting is happening and why does it need to interact with multiple data formats.
@@
 
-To get an overall idea of the flow of weather forecast, let us look into one of the weather forecastings flows using the \acrshort{curw} \cite{CUrWSL2017SL}.
+To get an overall idea of the flow of weather forecast, let us look into one of the weather forecasting flows in the \acrshort{curw} \cite{CUrWSL2017SL}.
 
 \begin{enumerate}
-    \item Extract \acrshort{GRIB} \acrshort{wrf} model data to the \acrshort{netCDF} format
+    \item Extract \acrshort{GRIB} \acrshort{wrf} model data to the \acrshort{netCDF} format.
     \item Extract \acrshort{netCDF} data to \acrshort{csv} format for each location data, then feed to HEC-HMS hydrodynamic model and get the output as a \acrshort{csv} file.
     \item HEC-HMS's \acrshort{csv} output and precipitation as Grid files feed into the FLO2D hydrologic model and get the water level as ASCII Grid files after the simulation is complete.
-    \item Upload above ASCII files to a geographic information system after convert to a compatible format, then use for the loss estimation
+    \item Upload above ASCII files to a geographic information system after convert to a compatible format, then use for the loss estimation.
 \end{enumerate}
@@
 In such situations, we need to correct predicted weather data by comparing them with accurate real-time weather data.
-So, we are required to collect real-time data such as:
-\begin{itemize}
-    \item Frequently collect automated weather station data via HTTP protocol
-    \item Collect accumulated weather data over a given period by automatic water level stations
-\end{itemize}
+We are required to collect real-time data from automated weather stations and accumulated weather data over a given period by automatic water level stations.
 
-Most weather data collecting devices use their data formats and different standard protocols to transmit the data.
+Most weather data collecting devices use own data formats and different standard protocols to transmit the data.
 Then we need to validate the data and modify the data to remove errors.

### 2020-05-29 method/sec_1-architectural_decisions.tex
4.2 Done

@@
 
-The \acrshort{esb} has the processing units called \emph{mediators}.
+The \acrshort{esb} processing units called \emph{mediators}.
 A mediator can take a message, carry out some predefined actions on it, and output the modified message.
 These mediator capabilities can be used to integrate the modules of a weather data system, as shown in \cref{fi:wdia_components}.
-\acrshort{esb} also supports different transportation protocols such as HTTP and Web sockets.
+\acrshort{esb} also supports different transportation protocols such as HTTP and web sockets.
 However, we realized that \acrshort{esb} is not suitable for data streaming or bulk data processing.
@@
 \begin{itemize}
-    \item pods – Cluster of containers that can group other container images in a single unit.
-    \item nodes – The machines (VMs, physical servers, etc) in a cluster that runs your applications and cloud workflows.
-    \item kubelet – An agent that runs on each node in the cluster. It makes sure that containers are running in a pod.
-    \item kube-proxy – A network proxy that runs on each node in the cluster, and maintains network rules on nodes.
-    \item kubernetes master – Responsible for maintaining the desired state for your cluster.
-    \item etcd – Consistent and highly-available key value store used as Kubernetes backing store for all cluster data.
+    \item Pods -- Cluster of containers that can group other container images in a single unit.
+    \item Nodes -- The machines (VMs, physical servers, etc) in a cluster that runs your applications and cloud workflows.
+    \item Kubelet -- An agent that runs on each node in the cluster. It makes sure that containers are running in a pod.
+    \item Kube-proxy -- A network proxy that runs on each node in the cluster, and maintains network rules on nodes.
+    \item Kubernetes master -- Responsible for maintaining the desired state for your cluster.
+    \item etcd -- Consistent and highly-available key value store used as \acrshort{k8s} backing store for all cluster data.
 \end{itemize}
 
-Users can add much as Nodes required into the \acrshort{k8s} cluster, and \acrshort{k8s} manage and deploy applications as pods into cluster nodes.
+Users can add nodes much as required into the \acrshort{k8s} cluster, and \acrshort{k8s} manage and deploy applications as pods into cluster nodes.
 Each microservice can deploy as a pod, which is a group of containerized applications.
-And \acrshort{k8s} is able to scale as much as the user requirements by deploying multiple copies of the same pod.
+\acrshort{k8s} is able to scale as much as the user requirements by deploying multiple copies of the same pod.
 By separating each microservice as a container, and running them as multiple pods inside the \acrshort{k8s} removes the tight coupling of microservices when compared to the actors.

### 2020-05-29 method/sec_3-microservice.tex
4.2 Done

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Database per Microservice Microservice Pattern}
+\subsection{Database per Microservice Pattern}
 \label{subse:database_per_service}
@@
 \begin{itemize}
-    \item Individual tables per service - each microservice has a set of tables that restricts access for other microservices.
-    \item Schema per service - each service has a private database schedule for a given microservice.
-    \item Database server per service - each service has its database server.
+    \item Individual tables per service -- each microservice has a set of tables that restricts access for other microservices.
+    \item Schema per service -- each service has a private database schedule for a given microservice.
+    \item Database server per service -- each service has its database server.
 \end{itemize}
@@
 
-\paragraph{X-axis Scaling}-- When scaling an application through the x-axis, multiple instances of the application execute behind a load balancer.
+\paragraph{X-axis scaling} -- When scaling an application through the x-axis, multiple instances of the application execute behind a load balancer.
 If there are \textit{n} copies, then each copy handles 1/\textit{n} of the load.
@@
 
-\paragraph{Y-axis Scaling}-- When compared to the z-axis and x-axis scaling, which follows the concept of running multiple identical copies of the application, but y-axis scaling segregates the application into multiple services in the same domain.
+\paragraph{Y-axis scaling} -- When compared to the z-axis and x-axis scaling, which follows the concept of running multiple identical copies of the application, but y-axis scaling segregates the application into multiple services in the same domain.
 So, the end services are responsible for one or more closely related functions of the previous service before the segregation.
@@
 \end{itemize}
-\emph{The microservice architecture is an application of y-axis scaling}.
+The microservice architecture is an application of y-axis scaling.
 
-\paragraph{Z-axis Scaling}-- The z-axis scaling follows the concept of each service running the same application code (similar to x-axis scaling).
+\paragraph{Z-axis scaling} -- The z-axis scaling follows the concept of each service running the same application code (similar to x-axis scaling).
 The big difference is that each service is responsible for only a subset of the data.
@@
 
-\cref{fi:wdias_micro_on_demand} and \cref{fi:wdias_micro_async} show the system interaction of the WDIA microservices architecture while handling the requests.
+\cref{fi:wdias_micro_on_demand} and \ref{fi:wdias_micro_async} show the system interaction of the WDIA microservices architecture while handling requests.
 Each circle in the figures represents a microservice in the \acrshort{wdias}.
@@
 For scalar, vector, and grid data types, we created adapter microservices that are optimized for storing such kinds of data.
-And the metadata data of the timeseries store using an RDBMS, which gives more performance over retrieving timeseries metadata.
+The metadata data of the timeseries store using an RDBMS, which gives more performance over retrieving timeseries metadata.
 The metadata is cached using an in-memory database to fast access while implementing the database structure.
@@
     \includegraphics[width=1\textwidth]{method/microservice/microservice_architecture-handle_on_demand-v4.pdf}
-    \caption{\acrshort{wdias} architecture for handling requests on demand}
+    \caption{\acrshort{wdias} architecture for handling requests on demand.}
     \label{fi:wdias_micro_on_demand}
@@
 However, as shown in \cref{fi:wdias_micro_async}, when a request with a larger payload comes to the system, it stores the data for an asynchronous process and responds with a unique id that can be used to verify whether data processed successfully or not.
-We used the microservice concept of Saga, as mentioned in \cref{subse:sagas}, while processing the Grid data.
+We used the microservice concept of Saga, as mentioned in \cref{subse:sagas}, while processing the grid data.
 First, it stores the data and responds with a unique identifier to the user.
@@
 \cref{fi:wdias_micro_separation} shows the clear separation of microservices into the modules of the \acrshort{wdias}.
-Each adapter has a separate database, and the database is hosted separately for the high performance and to avoid interferences.
+Each adapter has a separate database, and the database is hosted separately for the high performance and to avoid interference.
 Apart from that, as we further discuss in \cref{se:data_preprocess}, the extension modules are running independently, such as Interpolation, Transformation, and Validation, and we will also discuss in \cref{se:data_preprocess}.
@@
 
-We defined an \acrfull{rest} as the communication layer for \acrshort{wdias}, and it affects the microservice architecture design as well.
+We defined an \acrshort{rest} as the communication layer for \acrshort{wdias}, and it affects the microservice architecture design as well.
 It follows a simple \acrshort{rest} \acrshort{api} and allows users to interact with the system through HTTP methods.
@@
 Timeseries endpoints allow users to interact with Metadata Adapter to create and update the timeseries metadata.
-And create timeseries metadata, we cached on the Query Handler to perform search queries and geo-indexed to support geo-based queries.
+After creating timeseries metadata, we cached on the Query Handler to perform search queries and geo-indexed to support geo-based queries.
 When a user registers a timeseries metadata, the system generates a unique timeseries identifier based on the metadata values.
@@
 Other than the endpoints in Appendix A, we exposed another set of endpoints to configure extensions, and we will describe further in \cref{se:data_preprocess}.
-Other than the timeseries metadata endpoints, other module endpoints start with the module name such as import, export, and extension when compared to timeseries metadata endpoints.
+Also, other module endpoints start with the module name such as import, export, and extension when compared to timeseries metadata endpoints.
 Using the above convention, we allowed adding a new module system if required.

### 2020-05-29 method/sec_4-db_struct.tex
4.2 Done

@@
 \label{subse:timeseries_key_attributes}
-\paragraph{Module ID}-- String field which describe the source of the data generated. e.g., hec-hms, flow2d, weather-station, etc
 
-\paragraph{Value Type}-- Scalar, vector, grid are the Value Types that are interested in the \acrshort{wdias}.
+\paragraph{Module ID} String field which describe the source of the data generated. e.g., HEC-HMS, FLOW2D, weather-station, etc
 
-\paragraph{Location}-- Location of the timeseries.
-All locations have a unique String identifier called \emph{locationId}.
-Further, two types of location types are interested in the \acrshort{wdias}, namely:
+\paragraph{Value Type} Scalar, vector, grid are the value types that are interested in the \acrshort{wdias}.
+
+\paragraph{Location}
+Location of the timeseries. All locations have a unique String identifier called \emph{locationId}. Further, two types of location types are interested in the \acrshort{wdias}, namely:
 \begin{itemize}
-  \item \emph{Point locations}-- Contains a name that is human readable. lat and lon of the location on the earth surface.
+  \item \emph{Point locations} -- Contains a name that is human readable. lat and lon of the location on the earth surface.
 \begin{lstlisting}[language=Python]
@@
 
-\subsubsection{Timeseries Type}
+\paragraph{Timeseries Type}
 Users can define timeseries type while setup the system. We determined the following types as the default values. Timeseries type can be a combination of a source followed by category:
 \begin{itemize}
-  \item Sources - External or simulated. \emph{External} means whether timeseries is taken from an external source, and \emph{simulated} means it generated by simulations of the users.
-  \item Category - Historical or forecast.
+  \item \emph{Sources} -- External or simulated. \emph{External} means whether timeseries is taken from an external source, and \emph{simulated} means it generated by simulations of the users.
+  \item \emph{Category} -- Historical or forecast.
 \emph{Historical} means whether timeseries have continuous data such as observations from a weather station.
@@
 
-\paragraph{Time Step}-- All TimeSteps has a unique String identifier called timeStepId.
+\paragraph{Time Step}
+All TimeSteps has a unique String identifier called timeStepId.
 The unit should be one of Second, Minute, Hour, Day, Week, Month, Year, or NonEqualDistance.
@@
 And the vector data point consists of two values, such as magnitude and the direction of the vector.
-But for Grid data, a point can consist of multiple values.
-To store data efficiently, we used a set of different databases based on the advantage of using them for each valueType.
+But for grid data, a point can consist of multiple values.
+To store data efficiently, we used a set of different databases based on the advantage of using them for each value type.
 Other attributes do not have much impact on classifying the timeseries data.
@@
 It is difficult to search for the timeseries data if those are stored over multiple data sources and trying to avoid having duplicates.
-,it adds low overhead to have a single data source to look into while searching for the timeseries metadata.
+Thus, it adds low overhead to have a single data source to look into while searching for the timeseries metadata.
 The efficiency of searching for timeseries metadata can increase by using a caching mechanism.
@@
 Thus, we created a database structure after carefully choosing database systems per the system requirements and combining their capabilities.
-According to the design principle of microservices architecture, we created microservice for each of the valueType.
-Here we followed the concept of \emph{database per service} as described in in \cref{subse:database_per_service}.
-In \cref{sebse:wdias_microservices}, those microservices are grouped as \emph{adapters} that share an \acrshort{api} to interact with while keeping the persistent data private.
+According to the design principle of microservices architecture, we created microservice for each of the value type.
+Here we followed the concept of \emph{database per service} as described in \cref{subse:database_per_service}.
+\cref{sebse:wdias_microservices}, those microservices are grouped as \emph{adapters} that share an \acrshort{api} to interact with while keeping the persistent data private.
 
@@
 Since one of \acrshort{wdias} main goals is to use open source tools, it used MySQL as a persistent database for storing timeseries metadata described above.
-One MySQL instance used only for adapter-metadata service.
-Other than that, another MySQL instance used for adapter-extension.
+One MySQL instance used only for Metadata Adapter service.
+Other than that, another MySQL instance used for Extension Adapter.
 We will explain in more detail in \cref{se:data_preprocess}.
@@
 Redis uses in-memory caching for fast access to the frequent access data in adapter-metadata and adapter-extension.
-Other than that, adapter-status uses Redis as a key-value pair store to maintain the status for async requests handling while storing grid data.
-The adapter-extension uses Redis's Publisher Subscriber capabilities to create a cronjob in extension-scheduler when a new extension creates with a trigger on time during data preprocessing.
+Other than that, Status Adapter uses Redis as a key-value pair store to maintain the status for asynchronous requests handling while storing grid data.
+The Extension Adapter uses Redis's Publisher Subscriber capabilities to create a cronjob in extension-scheduler when a new extension creates with a trigger on time during data preprocessing.
 
@@
 Among several timeseries open source databases, InfluxDB \cite{influxdbInfluxDBDocumentation} uses a unique database indexing algorithm to gain higher performance while storing timeseries data when compared to other modern databases available.
-Also, it has better support, higher usage, and following supports;
+Also, it has better support, higher usage, and following supports,
 
@@
 
-Two individual instances of InfluxDB used for adapter-scalar and adapter-vector services in the \acrshort{wdias} system.
+Two individual instances of InfluxDB used for Scalar Adapter and Vector Adapter services in the \acrshort{wdias} system.
 For the scalability, the system uses \emph{database per service}, as mentioned in \cref{subse:database_per_service}.
 If users want further performance, the database can split into another set of partitions based on other key attributes based on the z-axis scaling described in \cref{subse:scale_cube}.
-As an example, scalar and vector adapters can further split into more services based on other key attributes such as timeseriesType.
+As an example, scalar and vector adapters can further split into more services based on other key attributes such as timeseries type.
 
@@
 We used MongoDB, which is a document-oriented database with geo indexing capabilities.
-Also, MongoDB \cite{mongodbMongoDBManual} is a general-purpose, document-based, distributed database, and supports:
+Also, MongoDB \cite{mongodbMongoDBManual} is a general-purpose, document-based, distributed database, and supports,
 
@@
 Also, we indexed the timeseries metadata with other indexing features to serve external timeseries metadata queries.
-If particular timeseries metadata not present in the adapter-query, then fetch metadata from the adapter-metadata and indexed in the MongoDB.
-Vise a versa; when a new timeseries created in the adapter-metadata, it triggers an event to index metadata in the adapter-query.
+If particular timeseries metadata not present in the Query Adapter, then fetch metadata from the Metadata Adapter and indexed in the MongoDB.
+Vise a versa; when a new timeseries created in the Metadata Adapter, it triggers an event to index metadata in the Query Adapter.
 Here we used the \emph{y-axis scaling} concept by splitting metadata search into multiple services.
-Within the system, it uses in-memory database cache to support internal metadata access, and external search queries fulfill by the adapter-query with using MongoDB.
+Within the system, it uses in-memory database cache to support internal metadata access, and external search queries fulfill by the Query Adapter with using MongoDB.

### 2020-05-29 method/sec_5-data_preprocess.tex
4.2 Done

@@
 The data imported via import modules may have incorrect data, missing data, and incompatible data which cannot directly feed into simulation modules.
-Thus, we need to preprocess imported data before using it for forecasting.
-The WDIAS supports data preprocessing capabilities via the extension modules.
+Thus, we need to preprocess imported data before using them for weather forecasting.
+The WDIAS supports data preprocessing capabilities via extension modules.
 The current system has a few inbuilt extensions such as Interpolation, Transformation, and Validation, but users can add more extensions as required.
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{method/data_preprocess/weather_data_preprocessing.pdf}
+    \includegraphics[width=0.6\textwidth]{method/data_preprocess/weather_data_preprocessing.pdf}
     \caption{A generic mathematical function model for weather data preprocessing}
@@
 \subsection{Interpolation}
-The interpolation module generates data at desired locations or at desired data points using a serial The interpolation module generates data at desired locations or desired data points using a serial or spatial interpolation technique.
+The interpolation module generates data at desired locations or desired data points using a serial or spatial interpolation technique.
 It is used to fill gaps in on-line measured data and to derive spatially distributed data for weather timeseries, such as precipitation and temperature, based on information available at nearby locations.
 
-\paragraph{Serial Interpolation}-- During serial interpolation, we use interpolation to fill any gaps in a timeseries.
+\paragraph{Serial Interpolation} -- During serial interpolation, we use interpolation to fill any gaps in a timeseries.
 The interpolation module will only consider a single timeseries, which is itself in filling these gaps.
@@
 
-\paragraph{Spatial Interpolation}-- During spatial interpolation, we use interpolation to either fill gaps in timeseries or to create a new timeseries for a location using data from other (spatially distributed) locations.
+\paragraph{Spatial Interpolation} -- During spatial interpolation, we use interpolation to either fill gaps in timeseries or to create a new timeseries for a location using data from other (spatially distributed) locations.
 Spatial interpolation can also be applied for sampling scalar timeseries from grid timeseries, for re-sampling grids, or for creating grids from timeseries data.
@@
 \subsection{Transformation}
-Simple arithmetic manipulation, Time interval transformation and Shifting the series in time Specific hydro-meteorological transformation such as stage discharge relationships.
+Simple arithmetic manipulation of time interval transformation and shifting the series in time specific hydro-meteorological transformation such as stage discharge relationships.
 \begin{figure}[htp]
@@
 \begin{itemize}
-    \item extensionId -- An unique identifier for new extension trigger. Should be unique among all extensions.
-    \item extension -- The main extension category which is responsible for handling the extension with extracting data required and storing the output.
+    \item \emph{extensionId} -- An unique identifier for new extension trigger. Should be unique among all extensions.
+    \item \emph{extension} -- The main extension category which is responsible for handling the extension with extracting data required and storing the output.
 Interpolation/Transformation/Validation support for the moment.
-    \item function -- Name of the microservice which is handling the input to output mapping. \texttt{Fn()} function in the \cref{fi:weather_data_preprocessing}.
-    \item variables -- Array timeseries mapping to variables.
+    \item \emph{function} -- Name of the microservice which is handling the input to output mapping. \texttt{Fn()} function in the \cref{fi:weather_data_preprocessing}.
+    \item \emph{variables} -- Array timeseries mapping to variables.
 Multiple variables can be define with metadata or metadataIds of timeseries.
 Can be use same variable on inputVariables and outputVariables below.
-    \item inputVariables -- Timeseries that need to be provide into the function
-    \item outputVariables -- Timeseries that output from the function
-    \item trigger -- Type of trigger for the extension. Should be one of OnTime or OnChange.
+    \item \emph{inputVariables} -- Timeseries that need to be provide into the function.
+    \item \emph{outputVariables} -- Timeseries that output from the function.
+    \item \emph{trigger} -- Type of trigger for the extension. Should be one of OnTime or OnChange.
         \begin{itemize}
-        \item trigger -- OnChange
-        \item trigger\_on -- List of timeseries to listen on change and trigger the extension
+            \item \emph{OnChange}: \textit{trigger\_on} --- List of timeseries to listen on change and trigger the extension
+            \item \emph{OnTime}: \textit{trigger\_on} -- List of schedules that need to be trigger the extension in cronjob string format
         \end{itemize}
-    \begin{itemize}
-        \item trigger -- OnTime
-        \item trigger\_on -- List of schedules that need to be trigger the extension in cronjob string format
-    \end{itemize}
-    \item options -- Bind Constant which is bind at the time of creating new extension trigger and pass on triggering the extension.
+    \item \emph{options} -- Bind Constant which is bind at the time of creating new extension trigger and pass on triggering the extension.
 \end{itemize}
@@
 
-Extension Handler is responsible for triggering the correct extension with timeseries metadata when there is any change in the subscribed timeseries with a list of \emph{OnChange} timeseries while creating an extension trigger.
-
-\begin{figure}[htp]
-    \centering
-    \includegraphics[width=0.8\textwidth]{method/data_preprocess/validation.pdf}
-    \caption{Extension handler.}
-    \label{fi:extension_handler}
-\end{figure}
-
-When new data is inserted into one of the adapter-scalar or adapter-vector, those microservices notify the extension-handler.
-Then the extension-handler checks whether there is any extension subscribed for inserted timeseries.
+Extension handler is responsible for triggering the correct extension with timeseries metadata when there is any change in the subscribed timeseries which are provided as a list of \emph{OnChange} timeseries while creating an extension trigger.
+When new data is imported into one of the scalar adapter or vector adapter, those microservices notify the extension handler.
+Then the extension-handler checks whether there is any extension subscribed for imported timeseries.
 If there is an extension needed to be triggered, then it invokes the given extension with the required data.
@@
 To improve the performance of matching triggers against a timeseries, we used two mechanisms as below.
-First, other than only storing extension metadata in a MySQL instance of adapter-extension, we also store extension data in a reverse lookup table called triggers while creating new extension triggers.
+First, other than only storing extension metadata in a MySQL instance of extension adapter, we also store extension data in a reverse lookup table called triggers while creating new extension triggers.
 Using this reverse lookup table, we can retrieve the extensions against a given timeseries without heavy processing and less delay.
-Second, we cache the resulting trigger type and timeseries data using the Redis database inside the extension-handler for fast access and avoid too many queries on the MySQL database.
-For the separation of service responsibilities, the extension data stored in the persistence database of the adapter-extension and exposed via an endpoint.
+Second, we cache the resulting trigger type and timeseries metadata using the Redis database inside the extension handler for fast access and avoid too many queries on the MySQL database.
+For the separation of service responsibilities, the extension data stored in the persistence database of the extension adapter and exposed via an endpoint.
 
@@
 
-Extension scheduler is responsible for triggering the correct extension with metadata at a given time that provided at the time of creation as OnTime cron job values to the extension trigger.
+Extension scheduler is responsible for triggering the correct extension with timeseries metadata at a given time that provided while creating an extension trigger as \emph{OnTime} cron job values.
 To improve the performance of triggering cron jobs at given time schedules, we used a few optimization mechanisms as described below.
-Same as for extension-handler, the adapter-extension exposed an endpoint to retrieve extension metadata grouped by cronjob time.
+Same as for extension handler, the extension adapter exposed an endpoint to retrieve extension metadata grouped by cronjob time.
 Then we create cron jobs as per the data retrieved via adapter-extension.
 We used a low-level programming language to simulate the cron jobs for fast processing the extensions.
-After getting extension triggers, the extension-handler grouped them based on cronjob time and scheduled cron jobs programmatically to trigger at given times.
+After getting extension triggers, the extension handler grouped them based on cronjob time and scheduled cron jobs programmatically to trigger at given times.
 When each cron job triggers at the scheduled time, each cron job also contains the extensions to be triggered.
@@
 Then the extension-handler pulls data from the queue in regular time intervals and creates new cron jobs for mentioned cronjob time.
-As mentioned above, to avoid the expansion of the programmatic cron job list that we created for new extension triggers, all cronjobs fetch again in a long period and flush the previously scheduled cron jobs.
+As mentioned above, to avoid the expansion of the programmatic cron job list that we created for new extension triggers, all cronjobs fetch again after a long period and flush the previously scheduled cron jobs.
 While doing that, we also flush the Redis queue.

### 2020-05-29 method/sec_7-summary.tex
4.2 Done

@@
 
-Throughout this Chapter, we discussed the methodology of designing and implementing the \acrshort{wdias} based on the concepts studied in the literature review of \cref{ch:literature}.
+Throughout the \cref{ch:method}, we discussed the methodology of designing and implementing the \acrshort{wdias} based on the concepts studied in the literature review of \cref{ch:literature}.
 We used microservice architecture over \acrshort{soa} with an \acrshort{esb} to avoid the drawback of streaming bulk data through an \acrshort{esb}.

### 2020-05-29 results/sec_1-test_plan.tex
4.2 Done

@@
 Other than the above modules, \emph{adapter modules} act as the core modules and the base of the system.
-Also, the \emph{query module} allows the users to query for the timeseries based on the metadata and perform geo-based queries based on the locations.
+Also, the \emph{query module} allows the users to query for the timeseries metadata and perform geo-based queries based on the locations.
 
@@
 \begin{enumerate}
-    \item Number of requests made to the system at a given time (Requests Per Second (RPS))
+    \item Number of requests made to the system at a given time called as \acrfull{rps}
     \item Request size
@@
     \includegraphics[width=0.8\textwidth]{results/work_load/performance_study_v4.jpg}
-    \caption{\acrshort{wdias} load testing plan with changing the request size and \acrshort{rps}}
+    \caption{\acrshort{wdias} load testing plan with changing the request size and \acrshort{rps}.}
     \label{fi:performance_study_load}
@@
 \begin{enumerate}
-    \item Test Setup to create timeseries in 1hr, 30min and 15min intervals and create metadata of the timeseries
+    \item Test Setup to create timeseries in 1hr, 30min and 15min intervals, create metadata of the timeseries and create random extension triggers
     % \item Extensions
@@
     \begin{itemize}
-        \item Plan for 30 minutes of the test run with the request size of 1hr (60min) data.
-        \item Plan for 30 minutes of the test run with the request size of 30min data.
-        \item Plan for 30 minutes of the test run with the request size of 15min data.
-        \item Plan for 30 minutes of the test run with the request size of 15min data with auto-scaling.
-        % \item Test plan run against 60min, 30min and 15min request size of data. Another test plan runs with enabling the auto-scaling. (total of 2 hours)
+        \item Plan for 30 minutes of the test run with the request size of 1hr (60min) data
+        \item Plan for 30 minutes of the test run with the request size of 30min data
+        \item Plan for 30 minutes of the test run with the request size of 15min data
+        \item Plan for 30 minutes of the test run with the request size of 15min data with auto-scaling
+        % \item Test plan run against 60min, 30min and 15min request size of data. Another test plan runs with enabling the auto-scaling
     \end{itemize}
@@
         \item Query Timeseries
-        \item Plan for the 5 minutes of test run.
+        \item Plan for the 5 minutes of test run
     \end{itemize}
@@
 Other than that, we measure the response time into 90\% percentile while giving the best response time up to 90\% percentile of the responses.
-    \item \emph{Resource utilization} -- Resource Utilization is calculated based on the CPU and Memory usage via the K8s metrics server.
+    \item \emph{Resource utilization} -- Resource utilization is calculated based on the CPU and Memory usage via the K8s metrics server.
 It calculates the resource utilization over a 60 seconds time window.

### 2020-05-29 results/sec_2-workload.tex
Make geo- consistent
code listing - single space and avoid span over pages
4.2 Done

@@
 Before storing the data in \acrshort{wdias}, we need to register timeseries metadata for the timeseries, and are required to provide values for the six attributes.
-During the test for location attribute, we selected the locations all over the world as a generic case to include all the locations without binding to a specific area.
+During the test for location attribute, we selected set of locations all over the world as a generic case to include all the locations without binding to a specific area.
 
-We used 250 locations from Google’s Countries Public Data set \cite{GoogleGoogleCounties}, and considered static throughout the testing.
+We used 250 locations from Google’s countries public data set \cite{GoogleGoogleCounties}, and considered static throughout the testing.
 For each location, we created four timeseries metadata by using four different values for the moduleId key attribute.
@@
 
-We used the Apache JMeter for performing the load test since it is open source.
-And supports distributed load testing.
+We used the Apache JMeter for performing the load test since it is a widely using open source tool which supports distributed load testing.
 As mentioned in the JMeter Best Practices, "If your test needs large amounts of data - particularly if it needs to be \emph{randomized}, create the test data in a file that can be read with CSV Data set.
@@
 Before running the test cases, we generated the timeseries metadata in random order and wrote them into a CSV file during the setup phase.
-The metadata CSV file arranges in a way that, within every ten lines, seven lines are Scalar timeseries, two lines are Vector timeseries, and 1 line is a Grid timeseries.
+The metadata CSV file arranges in a way that, within every ten lines, seven lines are scalar timeseries, two lines are vector timeseries, and 1 line is a grid timeseries.
 
@@
 
+\begin{minipage}{\linewidth}
 \begin{lstlisting}[language=sh, caption=Preparation of precipitation data.]
@@
 \end{lstlisting}
+\end{minipage}
 
@@
 
-Similar to the scalar test data prepared, we prepared the test grid data using the real water-level output of the FLO2D 150 meter hydrology model that is used in the \acrshort{curw} The FLO2D timeseries are produced as ASCII Grid files, and each data point represents a grid file that consists of 120 rows and 139 columns.
+Similar to the scalar test data prepared, we prepared the test grid data using the real water-level output of the FLO2D 150 meter hydrology model that is used in the \acrshort{curw}.
+The FLO2D timeseries are produced as ASCII Grid files, and each data point represents a grid file that consists of 120 rows and 139 columns.
 To represent missing cell values of the ASCII grid file, we used the \texttt{-9} instead of \texttt{-999} as an optimization.
@@
 
+\begin{minipage}{\linewidth}
 \begin{lstlisting}[language=sh, caption= Preparation of water-level data.]
@@
 As mentioned in \cref{se:test_plan}, we performed another separate test plan on the query timeseries module.
-Here, we used the following test steps to cover most of the timeseries metadata search queries and Geo queries supported by the \acrshort{wdias}.
+Here, we used the following test steps to cover most of the timeseries metadata search queries and geo-queries supported by the \acrshort{wdias}.
 

### 2020-05-30 method/sec_6-query.tex
4.2 Done
Work load done

@@
 
-We used the adapter-query primarily for supporting geo-spatial queries.
+We used the query adapter primarily for supporting geo-spatial queries.
 As the primary service for searching for timeseries, it supports retrieval of timeseries metadata for external queries as well.
-The Appendix B described the search query capabilities of \acrshort{wdias}.
+The Appendix B described the search query capabilities within \acrshort{wdias}.
+
 The system provides timeseries metadata query endpoints to search for existing timeseries metadata within the system using primary key attributes.
@@
 \begin{itemize}
-    \item Query Locations within Area
-    \item Query parameters in Locations
-    \item Query Timeseries by Location
-    \item Query Timeseries by Locations
-    \item Query Timeseries by Parameter
-    \item Query Timeseries in Area
-    \item Query Timeseries in Area by Parameter
-    \item Query All Timeseries
+    \item Query locations within area
+    \item Query parameters in locations
+    \item Query timeseries by location
+    \item Query timeseries by locations
+    \item Query timeseries by Parameter
+    \item Query timeseries in area
+    \item Query timeseries in area by parameter
+    \item Query all timeseries
 \end{itemize}

### 2020-05-30 results/sec_2-workload.tex
Work load done

@@
 
-To create a higher workload, we used JMeter's Distributed Testing capabilities.
+To create a higher workload, we used JMeter's distributed testing capabilities.
 JMeter uses the master-slave approach for distributed testing and allows us to handle all the test cases via a single master instance.
@@
 In other words, JMeter does not distribute the load between servers, and each slave service runs the full test plan.
-So if we set 1,000 threads per test plan and run the test using six JMeter servers, the distributed test setup ends up injecting 6,000 threads.
+So, if we set 1,000 threads per test plan and run the test using six JMeter servers, the distributed test setup ends up injecting 6,000 threads.
 During JMeter distributed mode, the master server triggers the same copy of the test plan on configured slave nodes in parallel.
@@
 The root component of a test plan is the thread group.
-There are different kinds of thread groups available such as thread group (basic thread group), arrivals thread Group, free form arrivals thread group, stepping thread group, concurrency thread group, and ultimate thread group.
+There are different kinds of thread groups available such as thread group (basic thread group), arrivals thread group, free form arrivals thread group, stepping thread group, concurrency thread group, and ultimate thread group.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Closed vs. open workload models}
+\subsubsection{Closed vs. Open Workload Models}
 \label{subse:closed_vs_open_workload}
@@
 \begin{itemize}
-    \item \emph{closed system model} \cite{Haggett1998AnWales} -- a new request is only triggered by the completion of a previous request, following by a think time.
+    \item \emph{closed system model} \cite{Haggett1998AnWales} -- A new request is only triggered by the completion of a previous request, following by a think time.
 The system has negative feedback that makes it impossible to bury-out the service, so users wait for the responses before making new requests.
-    \item \emph{open system model} -- new requests arrival independently of completions, e.g., according to a stochastic process or fixed trace. The system has no negative feedback.
+    \item \emph{open system model} -- New requests arrival independently of completions, e.g., according to a stochastic process or fixed trace. The system has no negative feedback.
 \end{itemize}
@@
 While implementing the test cases for \acrshort{wdias}, we used the concurrency thread group with the throughput shaping timer extension of JMeter because it supports the open workload approach.
-Using other thread groups, we are required to find the exact number of threads and timer delays that produce the desired number of \acrfull{rps} to the server, which is known as the \emph{closed workload}.
+Using other thread groups, we are required to find the exact number of threads and timer delays that produce the desired number of \acrshort{rps} to the server, which is known as the \emph{closed workload}.
 By using the \emph{throughput shaping timer}, we only need to configure the \acrshort{rps} throughout the test plan.
@@
     \includegraphics[width=0.8\textwidth]{results/work_load/test_prod_throughtput_shaping_timer.png}
-    \caption{\acrshort{wdias} load testing throughput shaping timer \acrshort{rps} configurations}
+    \caption{\acrshort{wdias} load testing throughput shaping timer \acrshort{rps} configurations.}
     \label{fi:test_prod_throughtput_shaping_timer}
@@
 \begin{itemize}
-    \item HTTP Request Defaults
-    \item HTTP Header Manager
-    \item Timeseries Metadata CSV
-    \item If Scalar or Vector
+    \item HTTP request defaults
+    \item HTTP header manager
+    \item Timeseries metadata CSV
+    \item If scalar or vector
         \begin{itemize}
-            \item Insert Timeseries
+            \item Insert timeseries
         \end{itemize}
-    \item If a Grid
+    \item If a grid
     \begin{itemize}
-        \item Insert Grid Timeseries
+        \item Insert grid timeseries
     \end{itemize}
     \item Wait for extensions timeseries
-    \item Interest Area preprocessor
-    \item Query If Scalar Or Vector
-    \item Retrieve If Scalar or Vector
+    \item Interest area preprocessor
+    \item Query if scalar or vector
+    \item Retrieve if scalar or vector
         \begin{itemize}
-            \item Retrieve Timeseries
+            \item Retrieve timeseries
         \end{itemize}
-    \item Retrieve If a Grid
+    \item Retrieve if a grid
     \begin{itemize}
-        \item Retrieve Grid Timeseries
+        \item Retrieve grid timeseries
     \end{itemize}
@@
 \begin{itemize}
-    \item HTTP Request Defaults
-    \item HTTP Header Manager
+    \item HTTP request defaults
+    \item HTTP header manager
     \item Locations CSV
-    \item Interest Area preprocessor
+    \item Interest area preprocessor
     \begin{itemize}
@@
     \item Use JSR223 scripts with Groovy for data processing for test cases
-    \item Using Throughput Shaping Timer to get more accurate \acrshort{rps}
+    \item Using throughput shaping timer to get more accurate \acrshort{rps}
 \end{itemize}
@@
 The \acrshort{wdias} uses Helm \cite{CNCFHelmDocs} which is a package manager for \acrshort{k8s}.
-Each Also, we used Helm \cite{CNCFHelmDocs} that is a package manager for \acrshort{k8s}.
 Each microservice within the system deploys and maintains as a Helm chart and the Helm charts \cite{KarunarathneWdias-helm-charts:Deployments} for each microservice available within the codebase.

### 2020-05-30 results/sec_3-observations.tex
Work load done

@@
 
-This section includes the observations based on the test plans discussed in Section \cref{se:test_plan}, and the experimental system setup explained in \cref{se:workload}.
-Sections \ref{subse:obs_test_plan_all_60min} to \ref{subse:obs_test_plan_all_auto_15min}, we discuss the observations collected with performing the Load test plans over 60 minutes data (24 data points per request), 30 minutes data (48 data points per request), and 15 minutes data (96 data points per request) by varying the request size.
+This section includes the observations based on the test plans discussed in \cref{se:test_plan}, and the experimental system setup explained in \cref{se:workload}.
+Sections \ref{subse:obs_test_plan_all_60min} to \ref{subse:obs_test_plan_all_auto_15min}, we discuss the observations collected with performing the load test plans over 60 minutes data (24 data points per request), 30 minutes data (48 data points per request), and 15 minutes data (96 data points per request) by varying the request size.
 Then we perform another round of 15 minutes data with enabling auto-scaling for the higher resource utilized microservices.
@@
 Insert timeseries performed over scalar and vector data types with each request sent with 24 data points.
-On average, it took 28 milliseconds to insert scalar and vector data into the \acrshort{wdias}, and up to 90\% percentile inserted data within 31ms.
+On average, it took 28 milliseconds to insert scalar and vector data into the \acrshort{wdias}, and up to 90\% percentile inserted data within 31 milliseconds.
 Noticeably it has 0\% of errors, which means that all the requests completed successfully.
@@
 The retrieval of scalar and vector timeseries has lesser delay than the insertion.
-On the other hand, insert grid timeseries data performed within 23ms, and almost all the requests perform within the same amount of time.
+On the other hand, insert grid timeseries data performed within 23 milliseconds, and almost all the requests perform within the same amount of time.
 Hence, the standard deviation is smaller.
@@
 
-Next, we performed the test plan with 30-minutes resolution data, which means 48 data points per each request for the scalar and vector data types, and 48 ASCII grid files per each insertion request for the grid data type.
+Next, we performed the test plan with 30-minute resolution data, which means 48 data points per each request for the scalar and vector data types, and 48 ASCII grid files per each insertion request for the grid data type.
 Also, the test plan performed round up to 311k number of sample requests, which is almost similar to the number of samples processed with hourly resolution data.
@@
 
-\cref{tab:obs_all_30_min_summary}shows the response latency summary details and \acrshort{rps} with 30-min resolution data.
+\cref{tab:obs_all_30_min_summary} shows the response latency summary details and \acrshort{rps} with 30-minute resolution data.
 The results are almost similar to the observations in \cref{subse:obs_test_plan_all_60min}.
@@
 
-\cref{fi:test_obs_all_30m_response_vs_threads} shows the latency against the number of active threads for the test plan with 30-min resolution data.
+\cref{fi:test_obs_all_30m_response_vs_threads} shows the latency against the number of active threads for the test plan with 30-minute resolution data.
 As the graph shows, the response time kept almost constant while increasing the number of active threads.

### 2020-05-31 method/sec_6-query.tex
Proofread Chapter 4

@@
 As the primary service for searching for timeseries, it supports retrieval of timeseries metadata for external queries as well.
-The Appendix B described the search query capabilities within \acrshort{wdias}.
+Appendix B described the search query capabilities within \acrshort{wdias}.
 
@@
 Also, it provides a set of geo-query endpoints, and users can perform geo-search queries with sending geo-information in geoJson format.
-The following geo-queries are supported by the system, and a detailed description appears in Appendix B.
+The following geo-queries are supported by the system, and a detailed description is presented in Appendix B.
 \begin{itemize}

### 2020-05-31 results/sec_1-test_plan.tex
Work load done
Proofread Chapter 4

@@
 \begin{enumerate}
-    \item Number of requests made to the system at a given time called as \acrfull{rps}
+    \item Number of requests made to the system at a given time i.e., \acrfull{rps}
     \item Request size
@@
     \item Due to resource issues such as batteries, a weather station can collect data points for a given period and send as a batch.
-An example scenario would be, a weather station can collect the precipitation at each 5 minute period and send all the data after collecting for one hour.
+An example scenario would be, a weather station can collect the precipitation and send all the data as a batch.
     \item The forecast precipitation data from the \acrshort{wrf} model extract for a few days in hourly intervals and store them.
@@
 When compared to scalar data, parameters such as wind direction are vector timeseries with a lesser percentage of requests.
-On the other hand, most of the grid type data was generated as results of NWMs.
+Alternatively, most of the grid type data was generated as results of NWMs.
 But those grid data produce in less frequency due to the cost of the computer resource to produce results.
@@
     \item Every 30 minutes (48 data points)
-    \item Every 15 minutes (96 data points) - One request is equivalent to a set of data points sent by a weather station in 15 minutes interval for a single day
+    \item Every 15 minutes (96 data points) - One request is equivalent to a set of data points sent by a weather station in 15-minute interval for a single day
 \end{itemize}
@@
 \begin{enumerate}
-    \item Test Setup to create timeseries in 1hr, 30min and 15min intervals, create metadata of the timeseries and create random extension triggers
+    \item Test setup to create timeseries in 1-hour, 30-minute and 15-minute intervals, create metadata of the timeseries and create random extension triggers
     % \item Extensions
@@
     % \end{itemize}
-    \item Import + Extension + Export + Timeseries Queries
+    \item Import + Extension + Export + Timeseries queries
     \begin{itemize}
-        \item Plan for 30 minutes of the test run with the request size of 1hr (60min) data
-        \item Plan for 30 minutes of the test run with the request size of 30min data
-        \item Plan for 30 minutes of the test run with the request size of 15min data
-        \item Plan for 30 minutes of the test run with the request size of 15min data with auto-scaling
+        \item Plan for 30 minutes of the test run with the request size of 1-hour (60-minute) data
+        \item Plan for 30 minutes of the test run with the request size of 30-minute data
+        \item Plan for 30 minutes of the test run with the request size of 15-minute data
+        \item Plan for 30 minutes of the test run with the request size of 15-minute data with auto-scaling
         % \item Test plan run against 60min, 30min and 15min request size of data. Another test plan runs with enabling the auto-scaling
@@
     \begin{itemize}
-        \item Query Timeseries
+        \item Query timeseries
         \item Plan for the 5 minutes of test run

### 2020-05-31 results/sec_2-workload.tex
Proofread Chapter 4

@@
 
-As explained in the research methodology (\cref{ch:method}), we selected six primary attributes from the timeseries metadata while implementing the system architecture.
+As explained in the research methodology (in \cref{subse:timeseries_key_attributes}), we selected six primary attributes from the timeseries metadata while implementing the system architecture.
 Before storing the data in \acrshort{wdias}, we need to register timeseries metadata for the timeseries, and are required to provide values for the six attributes.
@@
 
-We used the Apache JMeter for performing the load test since it is a widely using open source tool which supports distributed load testing.
-As mentioned in the JMeter Best Practices, "If your test needs large amounts of data - particularly if it needs to be \emph{randomized}, create the test data in a file that can be read with CSV Data set.
+We used the Apache JMeter 5.0 version \cite{ApacheSoftwareFoundationApacheJMeter} for performing the load test since it is a widely using open source tool which supports distributed load testing.
+As mentioned in the JMeter best practices, "If your test needs large amounts of data - particularly if it needs to be \emph{randomized}, create the test data in a file that can be read with CSV data set.
 This avoids wasting resources at run-time".
@@
 
-While preparing the data, we created three sets of timeseries based on the time interval, such as hourly (60min), 30min, and 15min data, with modifying the replicated data.
+While preparing the data, we created three sets of timeseries based on the time interval, such as hourly (60-minute), 30-minute, and 15-minute data, with modifying the replicated data.
 The above method reduced the overhead of filtering data during performance testing.
@@
 The maximum peak load that can be had during the load test is 300 \acrshort{rps} (equivalent to 18,000 requests per minute).
-The following list shows all the test plans that we used during the performance testing:
+The following the test plans that we used during the performance testing:
 
@@
 
-\begin{lstlisting}[language=sh, caption=Performance Test Help]
+\begin{lstlisting}[language=sh, caption=Automated performance test plans.]
 -h | --help: Usage
@@
 Then we separate scalar and vector microservices and their databases to separate the load from the core node while storing scalar and vector timeseries data.
-As same as, we assigned microservices to grid and test nodes based on the higher bandwidth requirements.
+Similarly, we assigned microservices to grid and test nodes based on the higher bandwidth requirements.

### 2020-05-31 results/sec_3-observations.tex
Proofread Chapter 4

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Load Testing with hourly resolution data}
+\subsection{Load Testing with Hourly Resolution Data}
 \label{subse:obs_test_plan_all_60min}
@@
 After running the test plan with 60-minute resolution data (24 data points per request), we observed the data summary of \cref{tab:obs_all_60_min_summary}.
-The test plan performed 311k of sample requests within 30 minutes of elapsed time.
+The test plan performed \num{311e3} of sample requests within 30 minutes of elapsed time.
 
@@
 Retrieve grid timeseries data performed with a bit higher value of latency of 68 milliseconds due to performed the retrieve request on-demand.
-Both insert and retrieve grid timeseries data have 4.5 \acrshort{rps} since it only gets 10\% of the number of requests per given time during the load test.
+Both insert and retrieve grid timeseries data have 4.5 \acrshort{rps} since it only gets 10\% of the number of requests from total number of requests during the load test.
 
@@
     \includegraphics[width=1.0\textwidth]{results/obs/all/obs_all_60m_res_latencies_against_hits.png}
-    \caption{Load testing with hourly data - Latency against server hits}
+    \caption{Load testing with hourly data - Latency against server hits.}
     \label{fi:test_obs_all_60m_latency}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Load Testing with 30-min resolution data}
+\subsection{Load Testing with 30-minute Resolution Data}
 \label{subse:obs_test_plan_all_30min}
@@
 Next, we performed the test plan with 30-minute resolution data, which means 48 data points per each request for the scalar and vector data types, and 48 ASCII grid files per each insertion request for the grid data type.
-Also, the test plan performed round up to 311k number of sample requests, which is almost similar to the number of samples processed with hourly resolution data.
+Also, the test plan performed round up to \num{311e3} number of sample requests, which is almost similar to the number of samples processed with hourly resolution data.
 
 \begin{table}[ht]
-\caption{Throughput and Latency of load test with 30-min data}
+\caption{Throughput and Latency of load test with 30-minute data.}
 \footnotesize
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Load Testing with 15-min resolution data}
+\subsection{Load Testing with 15-minute Resolution Data}
 \label{subse:obs_test_plan_all_15min}
 
-During this section, we performed the test plan with 15-minutes resolution data, which means 96 data points per each request for the scalar and vector data types, and 96 ASCII grid files per each insertion request for the grid data type.
-The size of each request is four times larger than the 60-min resolution data.
-Here also, the test plan performed approximately 311k of sample requests, which are almost similar to sample requests made during 60-min and 30-min resolution data.
+During this section, we performed the test plan with 15-minute resolution data, which means 96 data points per each request for the scalar and vector data types, and 96 ASCII grid files per each insertion request for the grid data type.
+The size of each request is four times larger than the 60-minute resolution data.
+Here also, the test plan performed approximately \num{311e3} of sample requests, which are almost similar to sample requests made during 60-minute and 30-minute resolution data.
 \begin{table}[ht]
-\caption{Throughput and Latency of load testing with 15-min data}
+\caption{Throughput and Latency of load testing with 15-minute data}
 \footnotesize
@@
 
-\cref{tab:obs_all_15_min_summary} shows the response latency summary details and \acrshort{rps} of the test plan with 15-min resolution data.
-When compared to the observations from the performance test with 30-min data, the request latency also increased for all sample requests.
+\cref{tab:obs_all_15_min_summary} shows the response latency summary details and \acrshort{rps} of the test plan with 15-minute resolution data.
+When compared to the observations from the performance test with 30-minute data, the request latency also increased for all sample requests.
 Also, the standard deviation of retrieval timeseries data increased by a considerable amount for all the data type's sample requests.
@@
 Even though we increased the request data size by four times higher, the system was able to handle all requests without significant performance issues.
-Also, the system provided the same throughput as with 60-min and 30-min resolution data.
+Also, the system provided the same throughput as with 60-minute and 30-minute resolution data.
 
@@
     \includegraphics[width=1.0\textwidth]{results/obs/all/obs_all_15m_response_times_vs_threads.png}
-    \caption{Load testing with 15 minutes of data - Response Time vs Active Threads}
+    \caption{Load testing with 15-minute of data - Response Time vs Active Threads.}
     \label{fi:test_obs_all_15m_response_vs_threads}
@@
 
-\cref{fi:test_obs_all_15m_response_vs_threads} shows the latency against the number of active threads for the test plan with 15-min resolution data.
+\cref{fi:test_obs_all_15m_response_vs_threads} shows the latency against the number of active threads for the test plan with 15-minute resolution data.
 As per the graph, the system was able to keep the response latency constant while increasing the number of active threads.
 However, when the number of active threads became higher, there was a disturbance with the response delay during the insertion and retrieval of timeseries data.
-The latency of insert and retrieval of grid timeseries data increased twice when compared to 30-min resolution data.
+The latency of insert and retrieval of grid timeseries data increased twice when compared to 30-minute resolution data.
 With a larger request size, we can notice the latency also increased by a smaller factor when we increased the number of active threads.
@@
     \includegraphics[width=1.0\textwidth]{results/obs/all/obs_all_15m_res_latencies_against_hits.png}
-    \caption{Load testing with 15 minutes of data - Latency against server hits}
+    \caption{Load testing with 15-minute of data - Latency against server hits.}
     \label{fi:test_obs_all_15m_latency}
@@
 
-\cref{fi:test_obs_all_15m_latency} graph provides an overview of the variation of latency over the elapsed time of the test plan against the number of server hits per second for 15-min resolution data.
+\cref{fi:test_obs_all_15m_latency} graph provides an overview of the variation of latency over the elapsed time of the test plan against the number of server hits per second for 15-minute resolution data.
 As per the graph, the system was able to keep the latency constant all over the test plan.
@@
     \includegraphics[width=1.0\textwidth]{results/obs/all/obs_all_15m_transaction_throughtput_vs_threads.png}
-    \caption{Load testing with 15 minutes of data - Transaction Throughput vs Threads}
+    \caption{Load testing with 15-minute of data - Transaction Throughput vs Thread.}
     \label{fi:test_obs_all_15m_throughtput}
@@
 \cref{fi:test_obs_all_15m_throughtput} shows the total server's transaction throughput against the number of active threads.
-The formula for total server transaction throughput is \(<active threads> * 1 second / <1  thread response time>\) \cite{JMeterPluginsTransactionPlugin}.
+The formula for total server transaction throughput \cite{JMeterPluginsTransactionPlugin} is;
+\[
+    \displaystyle \frac{<active \quad threads> \times \quad 1 \quad second}{<1 \quad thread \quad response \quad time>}
+\]
 It shows the statistical maximum possible number of transactions based on the number of users accessing the application.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Load Testing with 15-min resolution data while Auto Pod Scaling enabled}
+\subsection{Load Testing with 15-min Resolution Data with Auto Pod Scaling}
 \label{subse:obs_test_plan_all_auto_15min}
 
-Here we did the performance test plan with 15-minutes resolution data, which is similar to the above section.
+Here we did the performance test plan with 15-minute resolution data, which is similar to the above section.
 However, during the test plan, we enabled the K8s auto-scaling only for higher resource utilized microservices, as explained in \cref{subse:test_plan_metrics}.
@@
 Since \acrshort{eks} does not support multiple reads and writes support volumes \cite{LinuxFoundationPersistentKubernetes}, we are unable to enable auto-scaling during the test plan.
-However, the test plan performed approximately 311k of almost similar sample requests during the above sections.
+However, the test plan performed approximately \num{311e3} of almost similar sample requests during the above sections.
 
 \begin{table}[ht]
-\caption{Throughput and Latency of load testing with 15-min data while enabled \acrshort{k8s} auto-scaling}
+\caption{Throughput and Latency of load testing with 15-minute data while enabled \acrshort{k8s} auto-scaling}
 \footnotesize
@@
 Since the standard deviation also reduced, we can conclude that the latencies are closer to the average latency.
-Further, these improvements in insert Grid timeseries data seem to affect the output of retrieve Grid timeseries data as well.
+Further, these improvements in insert grid timeseries data seem to affect the output of retrieve grid timeseries data as well.
 
@@
     \includegraphics[width=1.0\textwidth]{results/obs/all_auto/obs_all_auto_15m_res_latencies_against_hits.png}
-    \caption{Load testing with 15 minutes of data with enabled auto-scaling - Latency against server hits}
+    \caption{Load testing with 15-minute of data with enabled auto-scaling - Latency against server hits}
     \label{fi:test_obs_all_auto_15m_latency}
 \end{figure}
-\cref{fi:test_obs_all_auto_15m_latency} graph provides an overview of the variation of latency over the elapsed time of the test plan against the number of server hits per second for 15min data while auto-scaling enabled for K8s.
+\cref{fi:test_obs_all_auto_15m_latency} graph provides an overview of the variation of latency over the elapsed time of the test plan against the number of server hits per second for 15-minute data while auto-scaling enabled for K8s.
 According to the graph, the \acrshort{wdias} was able to keep the latency constant all over the elapsed time.
@@
 
-\cref{fi:obs_all_auto_15m_import_export_res} shows the CPU usage and memory usage for import timeseries modules and export timeseries modules with 1 minutes resolution.
+\cref{fi:obs_all_auto_15m_import_export_res} shows the CPU usage and memory usage for import timeseries modules and export timeseries modules with 1-minute resolution.
 We show the CPU usage with milli CPUs \cite{LinuxFoundationManagingKubernetes} (1 CPU = 1000m CPUs) and the memory usage shown with Megabytes (Mi) \cite{LinuxFoundationManagingKubernetes} in the graphs.
@@
 \cref{fi:obs_all_auto_15m_adapter_dbs_res} shows the resource utilization of database adapters in the \acrshort{wdias}.
-The adapter-scalar and adapter-vector are not getting heavy load since they only process a scalar array of data points.
+The scalar adapter and vector adapter are not getting heavy load since they only process a scalar array of data points.
 However, we can see the CPU usage over time increased according to the test plan workload and cool down after the peak.
-For the adapter-grid, the CPU resource utilization increased and cooled down similarly to other adapters.
+For the grid adapter, the CPU resource utilization increased and cooled down similarly to other adapters.
 However, the memory resources are not released due to the caching of netCDF files by the application.
@@
 During the test plan, we performed multiple information retrievals queries such as queries over locations, parameters, and timeseries, which we described in the test planning phase.
-The test plan performed approximately 123k of sample requests only with the query microservice during the test period.
+The test plan performed approximately \num{123e3} of sample requests only with the query microservice during the test period.
 We performed the query test plan over 5 minutes with a higher number of requests than other test plans with a peak of 600 hits per second.
@@
 \begin{table}[ht]
-\caption{Throughput and Latency of Query test cases with 15-min data}
+\caption{Throughput and latency of query test cases with 15-minute data}
 \footnotesize
@@
 When the number of server hits gets higher, the latency also increases.
-According to the figures, we can conclude that the performance of the adapter-query depends on the database.
-Even if we increase the number of adapter-query pods, the throughput of the microservice is not going to increase until we increase the performance by using the z-axis scaling of scale cube concept.
+According to the figures, we can conclude that the performance of the query adapter depends on the database.
+Even if we increase the number of query adapter pods, the throughput of the microservice is not going to increase until we increase the performance by using the z-axis scaling of scale cube concept.
 
@@
     \includegraphics[width=1.0\textwidth]{results/obs/query/obs_query_5m_response_times_vs_threads.png}
-    \caption{Load testing query test over 5 minutes - Response Latency Times vs Threads}
+    \caption{Load testing query test over 5 minutes - Response Latency Times vs Threads.}
     \label{fi:test_obs_query_5m_response_times_vs_threads}
@@
 
-Whenever the timeseries data is not found in the adapter-query, it reads data from adapter-metadata and index for search over timeseries metadata.
+Whenever the timeseries data is not found in the query adapter, it reads data from metadata adapter and index for search over timeseries metadata.
 We used the above mechanism to increase the performance with geo timeseries searches.
-The performance of the document storage can further improve with using its features like Replication for high availability, and Sharding for higher throughput.
+The performance of the document storage can further improve with using its features like replication for high availability, and sharding for higher throughput.
 We did not attempt those performance improvements during the test plan since it was beyond the scope of the research.

### 2020-05-31 results/sec_3-observations_other.tex
Paper - Updated the Structure of the paper
Reduce table font size all
change to footnotesize table font size
Wrap Results chapter
Caption top of table
Proofread Chapter 4

@@
+% Not planing to include in the thesis
 \subsection{Import module load test}
 \label{subse:obs_test_plan_import_15min}
-\begin{table}[]
+
+\begin{table}[ht]
+\caption{Throughput and Latency of Import test cases with 15min data}
+\footnotesize
 \begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
@@
 \end{tabulary}
-\caption{Throughput and Latency of Import test cases with 15min data}
 \label{tab:obs_import_15_min_summary}
 \end{table}
+
+\dbc{Table names go on top of table.}
 
@@
 Need to redo just after the import
-\begin{table}[]
+\begin{table}[ht]
+\caption{Throughput and Latency of Export test cases with 15min data}
+\footnotesize
 \begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
@@
 \end{tabulary}
-\caption{Throughput and Latency of Export test cases with 15min data}
 \label{tab:obs_export_15_min_summary}
@@
     \includegraphics[width=0.8\textwidth]{results/obs/export/obs_export_15m_transaction_throughtput_vs_threads.png}
-    \caption{Performance Export Test 15 minutes Interval - Transaction Throughput vs Threads}
+    \caption{Performance export test 15 minutes interval - Transaction throughput vs threads.}
     \label{fi:test_obs_export_15m_throughtput}
@@
     \includegraphics[width=0.8\textwidth]{results/obs/export/obs_export_15m_res_latencies_against_hits.png}
-    \caption{Performance Export Test 15 minutes Interval - Latency against server hits}
+    \caption{Performance export test 15 minutes interval - Latency against server hits.}
     \label{fi:test_obs_export_15m_latency}

### 2020-05-31 results/sec_4-discussion.tex
v5.1.1
code listing - single space and avoid span over pages
Proofread Chapter 4

@@
-\section{Performance Metrics Analysis}
+\section{WDIAS Performance Evaluation}
 \label{se:discussion}
@@
 
-During each test plan, we showed the \emph{latency} for data insertion, and retrieval operation type kept constant over the whole test plan run time without any significant change.
+During each test plan, we showed the latency for data insertion, and retrieval operation type kept constant over the whole test plan run time without any significant change.
 When we increased the request size from 60-minute resolution data to 15-minute resolution data, the latency also increased throughout the whole test plan with a smaller number.
-During \cref{subse:obs_test_plan_all_auto_15min} test run with auto-scaling, the performance of the grid data got better when compared to \cref{subse:obs_test_plan_all_15min} without auto-scaling.
+During load testing with 15-minute resolution data with auto pod
+scaling (see \cref{subse:obs_test_plan_all_auto_15min}) test run, the performance of the grid data got better when compared to load testing with 15-minute resolution data (see \cref{subse:obs_test_plan_all_15min}) without auto-scaling.
 Thus, we can assume by adding more resources to the \acrshort{wdias}, it can handle more workload on the system by providing higher throughput.
 
-While keeping the latency constant without significant change, we showed the \emph{throughput} of the \acrshort{wdias} kept constant while increasing the request size from 60-minute resolution data (24 data points) to 15-minute resolution data (96 data points) for all the data types such as Scalar, Vector, and Grid.
+While keeping the latency constant without significant change, we showed the throughput of the \acrshort{wdias} kept constant while increasing the request size from 60-minute resolution data (24 data points) to 15-minute resolution data (96 data points) for all the data types such as scalar, vector, and grid.
 When the number of active threads increased, the \acrshort{wdias} able to provide the same throughput while maintaining the latency stable.
 
-One of the reasons for having deviations at the peak time due to uses of a single database instance for the data consistency such as using InfluxDB for scalar and vector data, and netCDF with parallel access support for Grid data.
+One of the reasons for having deviations at the peak time due to uses of a single database instance for the data consistency such as using InfluxDB for scalar and vector data, and netCDF with parallel access support for grid data.
 Further, it is possible to increase the performance of the before-mentioned bottleneck places such as using the InfluxDB commercial cluster support for high availability or horizontal scaling of InfluxDB.
-By using the InfluxDB cluster, we can run multiple pods of adapter-scalar and adapter-vector to support more workload.
+By using the InfluxDB cluster, we can run multiple pods of scalar adapter and vector adapter to support more workload.
 
-Adapter-grid is using a Python wrapper for netCDF FORTRAN implementation with parallel IO enabled.
+Grid adapter is using a Python wrapper for netCDF FORTRAN implementation with parallel IO enabled.
 However, it has some performance issues, as well as memory leak issues.
@@
 Doing so, we can increase the performance as an example by directly porting the adapter-grid to netCDF with a low-level language such as C or FORTRAN.
-Other than \acrshort{eks}, users can use a different \acrshort{k8s} cluster that supports Persistent Volumes with the access of Read Write Many \cite{LinuxFoundationPersistentKubernetes}.
-Then they can run multiple pods of adapter-grid and increase the throughput of handling grid data.
+Other than \acrshort{eks}, users can use a different \acrshort{k8s} cluster that supports persistent volumes with the access of Read Write Many \cite{LinuxFoundationPersistentKubernetes}.
+Then they can run multiple pods of grid adapter and increase the throughput of handling grid data.
 
-When we looked into the \emph{resource utilization} of \acrshort{wdias}, by using the \acrshort{k8s} as the container orchestration system, we were able to scale up and cool down the system as required based on the workload.
+When we looked into the resource utilization of \acrshort{wdias}, by using the \acrshort{k8s} as the container orchestration system, we were able to scale up and cool down the system as required based on the workload.
 During the test plan with auto-scaling enabled in \cref{subse:obs_test_plan_all_auto_15min}, we demonstrated the system gets scale up to the maximum at the peak time.
@@
 Given the above facts, we can run the \acrshort{wdias} on a cluster from 1 CPU node to nodes with 100 CPUs.
-As described in \cref{se:microservice}, we used many of the concepts of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities.
+As described in microservice architecture (see \cref{se:microservice}), we used many of the concepts of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities.
 
-The \acrshort{wdias} supports \emph{auto-scaling} out of the box with \acrshort{k8s} support.
+The \acrshort{wdias} supports auto-scaling out of the box with \acrshort{k8s} support.
 Services can be configured with a maximum number of pods to avoid over resource usage.
@@
 
-The \acrshort{wdias} processed many requests with a larger request size than the normal usage with a lower rate of failures to process the requests, mainly with insert Grid data.
-If we want to \emph{reduce the risk of unable to process data}, then the system can be configured to run with redundant pods to handle spikes of workloads.
+The \acrshort{wdias} processed many requests with a larger request size than the normal usage with a lower rate of failures to process the requests, mainly with insert grid data.
+If we want to reduce the risk of unable to process data, then the system can be configured to run with redundant pods to handle spikes of workloads.
 Also, while configuring the auto-scaling, the \acrshort{k8s} can be configured to maintain a lower amount of CPU usage, such as 50\% to 60\% rather than 80\%.

### 2020-06-07 method/sec_3-microservice.tex
Completed v5.3

@@
 
-\cref{fi:wdias_micro_on_demand} and \ref{fi:wdias_micro_async} show the system interaction of the WDIA microservices architecture while handling requests.
+Figures \ref{fi:wdias_micro_on_demand} and \ref{fi:wdias_micro_async} show the system interaction of the WDIA microservices architecture while handling requests.
 Each circle in the figures represents a microservice in the \acrshort{wdias}.
@@
 We provided a set of timeseries endpoints to register new timeseries metadata before storing the real data, and a detailed description appears in Appendix A.
-Timeseries endpoints allow users to interact with Metadata Adapter to create and update the timeseries metadata.
-After creating timeseries metadata, we cached on the Query Handler to perform search queries and geo-indexed to support geo-based queries.
+Timeseries endpoints allow users to interact with metadata adapter to create and update the timeseries metadata.
+After creating timeseries metadata, we cached on the query handler to perform search queries and geo-indexed to support geo-based queries.
 When a user registers a timeseries metadata, the system generates a unique timeseries identifier based on the metadata values.

### 2020-06-07 method/sec_4-db_struct.tex
Completed v5.3

@@
 
-\paragraph{Module ID} String field which describe the source of the data generated. e.g., HEC-HMS, FLOW2D, weather-station, etc
+\subsubsection{Module ID}
+String field which describe the source of the data generated. e.g., HEC-HMS, FLOW2D, weather-station, etc
 
-\paragraph{Value Type} Scalar, vector, grid are the value types that are interested in the \acrshort{wdias}.
+\subsubsection{Value Type}
+Scalar, vector, grid are the value types that are interested in the \acrshort{wdias}.
 
-\paragraph{Location}
+\subsubsection{Location}
 Location of the timeseries. All locations have a unique String identifier called \emph{locationId}. Further, two types of location types are interested in the \acrshort{wdias}, namely:
@@
 
-\paragraph{Parameter}
+\subsubsection{Parameter}
 Parameter describes the variable measuring against a location.
@@
 
-\paragraph{Timeseries Type}
+\subsubsection{Timeseries Type}
 Users can define timeseries type while setup the system. We determined the following types as the default values. Timeseries type can be a combination of a source followed by category:
@@
 
-\paragraph{Time Step}
+\subsubsection{Time Step}
 All TimeSteps has a unique String identifier called timeStepId.
@@
 Since one of \acrshort{wdias} main goals is to use open source tools, it used MySQL as a persistent database for storing timeseries metadata described above.
-One MySQL instance used only for Metadata Adapter service.
-Other than that, another MySQL instance used for Extension Adapter.
+One \acrshort{rdbms} instance used only for metadata adapter service.
+Other than that, another \acrshort{rdbms} instance used for extension adapter.
 We will explain in more detail in \cref{se:data_preprocess}.
 We used MySQL only for the above services, and those database instances keep the consistency of the schema for timeseries metadata and extension metadata.
-Further, we used an in-memory database instance for caching the requested metadata to reduce the load on the MySQL database instances while repeated queries.
+Further, we used an in-memory database instance for caching the requested metadata to reduce the load on the \acrshort{rdbms} database instances while repeated queries.
 Other than MySQL, many open-source SQL databases can be used to replace the same functionality.
@@
 It also supports Publisher Subscriber capabilities as an inbuilt feature.
-Redis is an open-source.
-Clustering is available for scalability.
+Redis is an open-source tool, and clustering is also available for scalability.
 Redis uses in-memory caching for fast access to the frequent access data in adapter-metadata and adapter-extension.
-Other than that, Status Adapter uses Redis as a key-value pair store to maintain the status for asynchronous requests handling while storing grid data.
-The Extension Adapter uses Redis's Publisher Subscriber capabilities to create a cronjob in extension-scheduler when a new extension creates with a trigger on time during data preprocessing.
+Other than that, status adapter uses Redis as a key-value pair store to maintain the status for asynchronous requests handling while storing grid data.
+The extension adapter uses Redis's Publisher Subscriber capabilities to create a cronjob in extension scheduler service when a new extension creates with a trigger on time during data preprocessing.
 
@@
 
-Two individual instances of InfluxDB used for Scalar Adapter and Vector Adapter services in the \acrshort{wdias} system.
+Two individual instances of InfluxDB used for scalar adapter and vector adapter services in the \acrshort{wdias} system.
 For the scalability, the system uses \emph{database per service}, as mentioned in \cref{subse:database_per_service}.
@@
 Also, we indexed the timeseries metadata with other indexing features to serve external timeseries metadata queries.
-If particular timeseries metadata not present in the Query Adapter, then fetch metadata from the Metadata Adapter and indexed in the MongoDB.
-Vise a versa; when a new timeseries created in the Metadata Adapter, it triggers an event to index metadata in the Query Adapter.
+If particular timeseries metadata not present in the query adapter, then fetch metadata from the metadata adapter and indexed in the MongoDB.
+Vise a versa; when a new timeseries created in the metadata adapter, it triggers an event to index metadata in the query adapter.
 Here we used the \emph{y-axis scaling} concept by splitting metadata search into multiple services.
-Within the system, it uses in-memory database cache to support internal metadata access, and external search queries fulfill by the Query Adapter with using MongoDB.
+Within the system, it uses in-memory database cache to support internal metadata access, and external search queries fulfill by the query adapter with using MongoDB.

### 2020-06-07 method/sec_5-data_preprocess.tex
Completed v5.3

@@
     \includegraphics[width=0.6\textwidth]{method/data_preprocess/weather_data_preprocessing.pdf}
-    \caption{A generic mathematical function model for weather data preprocessing}
+    \caption{A generic mathematical function model for weather data preprocessing.}
     \label{fi:weather_data_preprocessing}
@@
 
-\paragraph{Serial Interpolation} -- During serial interpolation, we use interpolation to fill any gaps in a timeseries.
-The interpolation module will only consider a single timeseries, which is itself in filling these gaps.
+\subsubsection{Serial Interpolation}
+During serial interpolation, we use interpolation to fill any gaps in a timeseries. The interpolation module will only consider a single timeseries, which is itself in filling these gaps.
 
@@
 
-\paragraph{Spatial Interpolation} -- During spatial interpolation, we use interpolation to either fill gaps in timeseries or to create a new timeseries for a location using data from other (spatially distributed) locations.
+\subsubsection{Spatial Interpolation}
+During spatial interpolation, we use interpolation to either fill gaps in timeseries or to create a new timeseries for a location using data from other (spatially distributed) locations.
 Spatial interpolation can also be applied for sampling scalar timeseries from grid timeseries, for re-sampling grids, or for creating grids from timeseries data.
@@
         \begin{itemize}
-            \item \emph{OnChange}: \textit{trigger\_on} --- List of timeseries to listen on change and trigger the extension
-            \item \emph{OnTime}: \textit{trigger\_on} -- List of schedules that need to be trigger the extension in cronjob string format
+            \item \emph{OnChange}: \textit{trigger\_on} --- List of timeseries to listen on change and trigger the extension.
+            \item \emph{OnTime}: \textit{trigger\_on} -- List of schedules that need to be trigger the extension in cronjob string format.
         \end{itemize}
@@
 To improve the performance of matching triggers against a timeseries, we used two mechanisms as below.
-First, other than only storing extension metadata in a MySQL instance of extension adapter, we also store extension data in a reverse lookup table called triggers while creating new extension triggers.
+First, other than only storing extension metadata in a \acrshort{rdbms} instance of extension adapter, we also store extension data in a reverse lookup table called triggers while creating new extension triggers.
 Using this reverse lookup table, we can retrieve the extensions against a given timeseries without heavy processing and less delay.
-Second, we cache the resulting trigger type and timeseries metadata using the Redis database inside the extension handler for fast access and avoid too many queries on the MySQL database.
+Second, we cache the resulting trigger type and timeseries metadata using the Redis database inside the extension handler for fast access and avoid too many queries on the \acrshort{rdbms} database.
 For the separation of service responsibilities, the extension data stored in the persistence database of the extension adapter and exposed via an endpoint.
@@
 Same as for extension handler, the extension adapter exposed an endpoint to retrieve extension metadata grouped by cronjob time.
-Then we create cron jobs as per the data retrieved via adapter-extension.
+Then we create cron jobs as per the data retrieved via extension adapter.
 We used a low-level programming language to simulate the cron jobs for fast processing the extensions.
@@
 When each cron job triggers at the scheduled time, each cron job also contains the extensions to be triggered.
-Fetching extension triggers data, and creating cron jobs occur with a long period to avoid huge overhead on adapter-extension.
+Fetching extension triggers data, and creating cron jobs occur with a long period to avoid huge overhead on extension adapter.
 When a user creates a new extension trigger, those data push into a queue in the Redis database.
-Then the extension-handler pulls data from the queue in regular time intervals and creates new cron jobs for mentioned cronjob time.
+Then the extension handler pulls data from the queue in regular time intervals and creates new cron jobs for mentioned cronjob time.
 As mentioned above, to avoid the expansion of the programmatic cron job list that we created for new extension triggers, all cronjobs fetch again after a long period and flush the previously scheduled cron jobs.
 While doing that, we also flush the Redis queue.
-The extension-handler should be run as a single process for the atomicity, to avoid triggering the same extension twice.
+The extension handler should be run as a single process for the atomicity, to avoid triggering the same extension twice.

### 2020-06-07 summary/sec_1-conclusions.tex
Completed v5.3

--- 2020-05-08 summary/sec_1-conclusions.tex
@@
 To enhance the accuracy of the weather forecast, we need to provide reliable and timely weather data for NWMs.
+Also, most of the existing weather data integration systems are based on basic client-server architectures or monolithic distributed system architectures or developed based on the best technology available at the time of developing those systems.
+However, most of the concepts are outdated with the technology advancement, and we cannot get the full advantage of modern computational models such as containerized applications and using the cloud computing to gain benefits of scalability, high availability, and low-cost operations.
 Even though there are many weather data integration systems, most of them are proprietary or closed source.
-Thus, for an island like Sri Lanka that has different kinds of weather seasons yearly, those software needs to be highly customized.
-Also, most of the existing systems are based on basic client-server architectures or monolithic distributed system architectures or developed based on the best technology available at the time of developing those systems.
-However, most of the concepts are outdated with the technology advancement, and we cannot get the full advantage of modern computational models such as containerized applications and using the cloud computing to gain benefits of scalability, high availability, and low-cost operations.
+Thus, for an island like Sri Lanka that has different kinds of weather seasons yearly, those software needs to be highly customized
 
 In this research, we proposed an extendable weather data integration and assimilation system known as \acrfull{wdias}.
-\acrshort{wdias} focuses on providing a system to efficiently integrate weather data from different sources with quality control and supporting steaming large size of data.
+\acrshort{wdias} focuses on providing a system to efficiently integrate weather data from different sources with supporting quality control.
 Furthermore, the proposed system is compatible with current cloud computing technologies, architecture patterns, and compatible with modern cloud computing architectures.
@@
 After comparing the disadvantages of using such architectures with the system requirements, we came up with modern microservice architecture.
+One of attractive feature of microservice architecture is independent nature of microservices enables to design a highly scalable modular system which can use to handle large volumes of data using a large resource pool.
+Also, we used many of the concepts of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities.
 \acrshort{wdias} implemented the microservice architecture on top of the \acrshort{k8s}, which is a container orchestration platform.
 We mapped each microservice of \acrshort{wdias} to a pod in the \acrshort{k8s} cluster.
-Also, each microservice follows the concept of smart endpoints dumb pipes[?] and does specific operations that are related to the data format that responsible for handling.
-\dbc{Need to explain the solution based on microservices as it's the most important. Also, a reference is missing here}
+Also, each microservice exposed endpoints to the users which are only focus on supporting a specific operation or functionality which follows the concept of smart endpoints dumb pipes in \cref{subse:dumb_pipes}.
+For importing different format data into the system, we added microservice for each data format that known as import microservices.
+Then, these import microservices store the data via an appropriate database adapter microservice after converting to compatible data format.
+For handling multiple data formats efficiently, we introduced a database structure in WDIAS.
+Then, users can fetch data in the required format via using export microservices.
+Further, we enabled integrating extensional microservices which provides the data preprocessing capabilities, and it allow users to integrate new features as new extension microservices.
+We used geo-index to support geo-based search queries and metadata search queries.
+Also, the system provides asynchronous request handling based on the request size with maintaining status per request.
 
-Based on the microservice architecture patterns and the nature of the weather metadata, we designed database structure of \acrshort{wdias} to provide higher performance while storing the weather data efficiently.
-The system uses a timeseries database for storing scalar and vector timeseries data and using netCDF for storing grid timeseries data.
+Based on the microservice architecture patterns and the nature of the weather metadata, we designed database structure of \acrshort{wdias} to provide higher performance and efficient storage.
+The system uses a timeseries database to store scalar and vector timeseries data and use netCDF for grid timeseries data.
 Also, each database has an adapter, and each adapter uses the concept of database per service, which allows each microservice service to scale without getting interference from other microservices.
 Moreover, it uses the microservice sagas pattern for asynchronous data handling for requests with a larger size.
-As discussed in \cref{se:microservice}, we used many of the concepts of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities.
 
-Also, the system provides a generic open mechanism to integrate new modules as an extension to enhance the features of the system.
+Also, the system provides a generic mechanism to integrate new modules as an extension to enhance the features of the system.
 This capability enables us to integrate weather data preprocessing flows as extension modules.
-We designed an extension API to easily access to create and modify the extension triggers at run time without stopping the system or any downtime for the system reconfiguration.
-The system provides extensive timeseries query endpoints to easy search over the stored timeseries metadata with supporting Geo-based queries.
+We designed an extension API to easily create and modify the extension triggers at run time without stopping the system or any downtime for the system reconfiguration.
+The system provides extensive timeseries query endpoints to easy search over the stored timeseries metadata with supporting geo-based queries.
 
-We evaluated the performance using a cloud-based setup on the Amazon Elastic Kubernetes Service (Amazon EKS).
+We evaluated the performance using a cloud-based setup on the \acrfull{eks}.
 Based on the performance analysis, we were able to perform 300 \acrshort{rps}, and the system handled the workload successfully with minimizing the error rate.
@@
 With \acrshort{k8s} auto-scaling enabled, the \acrshort{k8s} elastically adjust the number of pods according to the workload with provided auto-scaling configurations.
-The results of \acrshort{wdias} shows that the system can run on a cluster from 1 CPU node to nodes with a few hundred CPUs.
+The results of \acrshort{wdias} shows that the system can run on a cluster from few CPU node to nodes with a few hundred CPUs.

### 2020-06-07 summary/sec_2-research_limitations.tex
Added fixes
Error Term,Correct Term,Description,No of Occurrences,Pages (absolute)
a.k.a.,aka.,,Shoudl be aka and need a comma,1,-1
[a-z] as well as,, as well as,Needs a comma before,3,-1
Also,Also,,Comma should be used at beginning of a sentence,1,-1
can not,cannot,Is a single word,4,-1
[fF]igure.\d,Figure n,There has to be a space like Figure 2.7,82,-1
Hence,Hence,,Comma should be used at beginning of a sentence,1,-1
in order to,to,Can be replaced with just to in many cases,4,-1
in to,into,Is a single word,1,-1
may be,maybe,Is a single word,2,-1
section,Section,S should be capital if used li

@@
 
-During this Section, we discussed the lacking features of the \acrshort{wdias} and the set of improvements that we can add to improve the performance and usability of the system.
+Next, we discussed the lacking features of the \acrshort{wdias} and the set of improvements.
 
@@
 
-\emph{Supporting Irregular Grids}:
-At the moment, \acrshort{wdias} does not support Irregular Grids, but it has the API endpoints defined for the implementation of such support with following the microservice architecture.
-We reduced the scope of the research by removing such components from the system, and such level of implementation does not belong to the \acrshort{wdias} scope as well.
-
 \emph{Grid data performance}:
@@
 
-\emph{Define infrastructure as code}:
-Physical nodes for the \acrshort{k8s} cluster created using cloud computing providers such as Amazon EKS, Google Cloud, and Microsoft Azure cloud.
-However, the infrastructure that needs to deploy the \acrshort{wdias} can be defined as code such as using tools like Terraform, which is independent of the cloud computing provider.
-Using such a tool, users will be able to quickly deploy the \acrshort{wdias} on any cloud provider without much hassle.
-
 \emph{Improvements to test cases}:
 As described in detail with \cref{subse:closed_vs_open_workload}, the \acrshort{wdias} test plans use the time-stepping feedback loop with concurrent threads, which is the best approach support by JMeter at the moment.
-However, using the above approach, we can not get the desired \acrshort{rps} for each test case within the test plan.
+However, using the above approach, we cannot get the desired \acrshort{rps} for each test case within the test plan.
 Because of the above issue, the \acrshort{wdias} test plans further improved by removing redundant test cases such as create timeseries at the beginning.
@@
 With the InfluxDB cluster, it is possible to run multiple pods of adapter-scalar and adapter-vector to support more server hits per second.
-Other than that, the \acrshort{wdias} performance can improve via partitioning the timeseries keyspace into multiple InfluxDB instances.
+Other than that, the \acrshort{wdias} performance can improve via partitioning the timeseries key space into multiple InfluxDB instances.
 As an example, based on the key attribute \cref{subse:timeseries_key_attributes} Timeseries Type, the adapter-scalar can connect to four instances of InfluxDB instances such as External Historical, External Forecast, Simulated Historical, and Simulated Forecast.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Future Work}
+\label{se:future_work}
+Here, we discussed the enhancements that we can add to improve the performance and usability of the system.
+
+\emph{Supporting Irregular Grids}:
+At the moment, \acrshort{wdias} does not support Irregular Grids, but it has the API endpoints defined for the implementation of such support with following the microservice architecture.
+We reduced the scope of the research by removing such components from the system, and such level of implementation does not belong to the \acrshort{wdias} scope as well.
+
+\emph{Define infrastructure as code}:
+Physical nodes for the \acrshort{k8s} cluster created using cloud computing providers such as Amazon EKS, Google Cloud, and Microsoft Azure cloud.
+However, the infrastructure that needs to deploy the \acrshort{wdias} can be defined as code such as using tools like Terraform, which is independent of the cloud computing provider.
+Using such a tool, users will be able to quickly deploy the \acrshort{wdias} on any cloud provider without much hassle.
+
 \emph{Alerting extension modules}: At the moment, extensions only support OnChange and OnTime events.
 However, it will be useful to have event trigger support based on the configured alert level or threshold level.
+
 \emph{Publisher Subscriber extension modules}: The \acrshort{wdias} better to be capable of triggering external systems based on events such as webhooks.

### 2020-06-07 results/sec_3-observations.tex
Caption .

@@
     \includegraphics[width=1.0\textwidth]{results/obs/all/obs_all_60m_response_times_vs_threads.png}
-    \caption{Load testing with hourly data - Response Time vs Threads}
+    \caption{Load testing with hourly data - Response Time vs Threads.}
     \label{fi:test_obs_all_60m_response_vs_threads}
@@
     \includegraphics[width=1.0\textwidth]{results/obs/all/obs_all_30m_response_times_vs_threads.png}
-    \caption{Load testing with 30 minutes of data - Response Time vs Threads}
+    \caption{Load testing with 30 minutes of data - Response Time vs Threads.}
     \label{fi:test_obs_all_30m_response_vs_threads}
@@
     \includegraphics[width=1.0\textwidth]{results/obs/all/obs_all_30m_res_latencies_against_hits.png}
-    \caption{Load testing with 30 minutes of data - Latency against server hits}
+    \caption{Load testing with 30 minutes of data - Latency against server hits.}
     \label{fi:test_obs_all_30m_latency}
@@
     \includegraphics[width=1.0\textwidth]{results/obs/all_auto/obs_all_auto_15m_res_latencies_against_hits.png}
-    \caption{Load testing with 15-minute of data with enabled auto-scaling - Latency against server hits}
+    \caption{Load testing with 15-minute of data with enabled auto-scaling - Latency against server hits.}
     \label{fi:test_obs_all_auto_15m_latency}
@@
     \includegraphics[width=1.0\textwidth]{results/obs/all_auto/obs_all_auto_15m_transaction_throughtput_vs_threads.png}
-    \caption{Load testing with 15 minutes of data with enabled auto-scaling - Transaction Throughput vs Threads}
+    \caption{Load testing with 15 minutes of data with enabled auto-scaling - Transaction Throughput vs Threads.}
     \label{fi:test_obs_all_auto_15m_throughtput}
@@
     \includegraphics[width=1.0\textwidth]{results/obs/query/obs_query_5m_latency_over_time.png}
-    \caption{Load testing query test over 5 minutes - Response Latency over Time}
+    \caption{Load testing query test over 5 minutes - Response Latency over Time.}
     \label{fi:test_obs_query_5m_response_latency}

### 2020-06-10 lit/sec_2-lead.tex
Fixed: Bib IEEE style

@@
 
-\acrfull{lead} \cite{Droegemeier2005Service-OrientedWeather} addresses the fundamental research challenges needed to create an integrated and scalable framework for adaptive analysis and prediction of the atmosphere.
+\acrfull{lead} \cite{Droegemeier2005Service-orientedWeather} addresses the fundamental research challenges needed to create an integrated and scalable framework for adaptive analysis and prediction of the atmosphere.
 The weather forecasting researchers require many computer resources to predict and analyze weather models in the mesoscale with less time.
@@
 At the time, some researchers are developing their experiment forecasting flows, they are not using the resources, and other researchers can run their forecasting flows using available resources.
-The foundation of the LEAD system is to create a dynamic workflow orchestration and data management in a web services framework \cite{Droegemeier2005Service-OrientedWeather}.
+The foundation of the LEAD system is to create a dynamic workflow orchestration and data management in a web services framework \cite{Droegemeier2005Service-orientedWeather}.
 
-LEAD's complex range of services, applications, interfaces, and IT resources, local and external networks, and storage is compiled by users in workflows to study mesoscale incremental manner \cite{Droegemeier2005Service-OrientedWeather}.
+LEAD's complex range of services, applications, interfaces, and IT resources, local and external networks, and storage is compiled by users in workflows to study mesoscale incremental manner \cite{Droegemeier2005Service-orientedWeather}.
 As it follows the SOA, all the features are implemented as independent services.
@@
     \includegraphics[width=1.0\textwidth]{lit/lead/LEAD-system-Fundamental-capabilities-familiar-to-meteorologists-are-shown-in-the-top_W640.png}
-    \caption[Layered architecture of LEAD]{Layered architecture of LEAD \cite{Droegemeier2005Service-OrientedWeather}.}
+    \caption[Layered architecture of LEAD]{Layered architecture of LEAD \cite{Droegemeier2005Service-orientedWeather}.}
     \label{fi:lead_system}
@@
 
-The second layer contains fundamental tools such as the following to help to link services together \cite{Droegemeier2005Service-OrientedWeather}:
+The second layer contains fundamental tools such as the following to help to link services together \cite{Droegemeier2005Service-orientedWeather}:
 \begin{itemize}
@@
     \includegraphics[width=1.0\textwidth]{lit/lead/LEAD-system-framework-LEAD-is-composed-of-several-interacting-subsystems-with-the-LEAD_W640.png}
-    \caption[LEAD system framework]{LEAD system framework \cite{Droegemeier2005Service-OrientedWeather}.}
+    \caption[LEAD system framework]{LEAD system framework \cite{Droegemeier2005Service-orientedWeather}.}
     \label{fi:lead_framework}
@@
     \includegraphics[width=1\textwidth]{lit/lead/LEADs-service-oriented-architecture-A-wide-variety-of-services-and-resources-grouped_W640.png}
-    \caption[LEAD's service-oriented architecture]{LEAD's service-oriented architecture \cite{Droegemeier2005Service-OrientedWeather}.}
+    \caption[LEAD's service-oriented architecture]{LEAD's service-oriented architecture \cite{Droegemeier2005Service-orientedWeather}.}
     \label{fi:lead_soa}
@@
 The bottom layer represents the calculation, application, and raw data sources that are distributed in the LEAD grid and elsewhere.
-The next level supports web services that provide access to raw services \cite{Droegemeier2005Service-OrientedWeather}.
+The next level supports web services that provide access to raw services \cite{Droegemeier2005Service-orientedWeather}.
 These two layers are working together since LEAD system resources are distributed over multiple locations and creating a pool of resources.

### 2020-06-10 method/sec_0_introduction.tex
Fixed: Bib IEEE style

@@
 
-To get an overall idea of the flow of weather forecast, let us look into one of the weather forecasting flows in the \acrshort{curw} \cite{CUrWSL2017SL}.
+To get an overall idea of the flow of weather forecast, let us look into one of the weather forecasting flows in the \acrshort{curw} \cite{CUrWSL2017Lanka}.
 

### 2020-06-10 method/sec_4-db_struct.tex
Caption .
Fixed: Bib IEEE style

@@
     \includegraphics[width=0.8\textwidth]{method/microservice/wdias_database_structure.pdf}
-    \caption{\acrshort{wdias} database structure}
+    \caption{\acrshort{wdias} database structure.}
     \label{fi:database_structure}
@@
 
-We used Redis \cite{redisRedisDocumentation} as the in-memory database since it is a widely used database system with excellent support.
+We used Redis \cite{RedisRedisDocumentation} as the in-memory database since it is a widely used database system with excellent support.
 It also supports Publisher Subscriber capabilities as an inbuilt feature.
@@
 
-Among several timeseries open source databases, InfluxDB \cite{influxdbInfluxDBDocumentation} uses a unique database indexing algorithm to gain higher performance while storing timeseries data when compared to other modern databases available.
+Among several timeseries open source databases, InfluxDB \cite{InfluxDBInfluxDBDocumentation} uses a unique database indexing algorithm to gain higher performance while storing timeseries data when compared to other modern databases available.
 Also, it has better support, higher usage, and following supports,
@@
 
-\acrshort{netCDF} \cite{unidataUnidataNetCDF} is a self-describing, machine-independent data format that supports the creation, access, and sharing of array-oriented scientific data.
+\acrshort{netCDF} \cite{UnidataNetworkForm} is a self-describing, machine-independent data format that supports the creation, access, and sharing of array-oriented scientific data.
 Moreover, NetCDF also supports parallel file access.
@@
 We used MongoDB, which is a document-oriented database with geo indexing capabilities.
-Also, MongoDB \cite{mongodbMongoDBManual} is a general-purpose, document-based, distributed database, and supports,
+Also, MongoDB \cite{MongoDBMongoDBManual} is a general-purpose, document-based, distributed database, and supports,
 
 \begin{itemize}
-  \item Supports query operations on geospatial data \cite{mongodbMongoDBManual}
+  \item Supports query operations on geospatial data \cite{MongoDBMongoDBManual}
   \item Clustering and Sharding available for scalability and reliability

### 2020-06-10 results/sec_2-workload.tex
Caption .
Fixed: Bib IEEE style

@@
 
-We used 250 locations from Google’s countries public data set \cite{GoogleGoogleCounties}, and considered static throughout the testing.
+We used 250 locations from Google’s countries public data set \cite{GoogleGoogleCountries}, and considered static throughout the testing.
 For each location, we created four timeseries metadata by using four different values for the moduleId key attribute.
@@
     \includegraphics[width=0.6\textwidth]{results/work_load/experimental_setup_v3.pdf}
-    \caption{Experimental setup with JMeter}
+    \caption{Experimental setup with JMeter.}
     \label{fi:experimental_setup}
@@
 By using the \emph{throughput shaping timer}, we only need to configure the \acrshort{rps} throughout the test plan.
-Then the throughput shaping timer provides a feedback loop to the concurrency thread group via schedule feedback function to dynamically maintain thread count required to achieve target \acrshort{rps} \cite{KarunarathneGihanWdias/wdias-performance-test:JMeter.}.
+Then the throughput shaping timer provides a feedback loop to the concurrency thread group via schedule feedback function to dynamically maintain thread count required to achieve target \acrshort{rps} \cite{KarunarathneWDIASJMeter}.
 
@@
 To make the process faster, we implemented a script tool to interact with the JMeter test stored files.
-The script is available within the code base \cite{KarunarathneWdias-performance-test/TEST_PLAN.md:Plan} as \emph{test-dev} and supports the following features.
+The script is available within the code base \cite{KarunarathneWDIASPlan} as \emph{test-dev} and supports the following features.
 
@@
 
-We have documented a detailed description of setting up the \acrshort{eks} \cite{KarunarathneWdias/Amazon_EKS.md:EKS}, and it is available in the codebase of the \acrshort{wdias}.
-\acrshort{k8s} is a planet scaling tool \cite{LinuxFoundationProduction-GradeKubernetes}, and users can tweak the configuration to run the \acrshort{wdias} as per the required level of load on the system.
+We have documented a detailed description of setting up the \acrshort{eks} \cite{KarunarathneWDIASService}, and it is available in the codebase of the \acrshort{wdias}.
+\acrshort{k8s} is a planet scaling tool \cite{LinuxFoundationKubernetes:Orchestration}, and users can tweak the configuration to run the \acrshort{wdias} as per the required level of load on the system.
 We used a set of physical nodes, as mentioned in \cref{tab:aws_eks_nodes}, to set up the \acrshort{k8s} for the performance testing with a peak of 300 \acrshort{rps}.
@@
 
-The \acrshort{wdias} uses Helm \cite{CNCFHelmDocs} which is a package manager for \acrshort{k8s}.
-Each microservice within the system deploys and maintains as a Helm chart and the Helm charts \cite{KarunarathneWdias-helm-charts:Deployments} for each microservice available within the codebase.
+The \acrshort{wdias} uses Helm \cite{CNCFHelmDocumentations} which is a package manager for \acrshort{k8s}.
+Each microservice within the system deploys and maintains as a Helm chart and the Helm charts \cite{KarunarathneHelmDeployments} for each microservice available within the codebase.
 For the databases, we used the official helm charts.
@@
     \includegraphics[width=0.75\textwidth]{results/work_load/eks_node_setup.pdf}
-    \caption{\acrfull{eks} node setup}
+    \caption{\acrfull{eks} node setup.}
     \label{fi:eks_node_setup}

### 2020-06-10 results/sec_3-observations.tex
Fixed: Bib IEEE style

@@
 \cref{fi:test_obs_all_15m_throughtput} shows the total server's transaction throughput against the number of active threads.
-The formula for total server transaction throughput \cite{JMeterPluginsTransactionPlugin} is;
+The formula for total server transaction throughput \cite{ApacheSoftwareFoundationJMeter:Plugin} is;
 \[
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Load Testing with 15-min Resolution Data with Auto Pod Scaling}
+\subsection{Load Testing with 15-minute Resolution Data with Auto Pod Scaling}
 \label{subse:obs_test_plan_all_auto_15min}
@@
 If we want to enable the auto-scaling for the service, all microservice instances of adapter-grid need to share data via shared storage.
-Since \acrshort{eks} does not support multiple reads and writes support volumes \cite{LinuxFoundationPersistentKubernetes}, we are unable to enable auto-scaling during the test plan.
+Since \acrshort{eks} does not support multiple reads and writes support volumes \cite{LinuxFoundationKubernetesVolumes}, we are unable to enable auto-scaling during the test plan.
 However, the test plan performed approximately \num{311e3} of almost similar sample requests during the above sections.
@@
 \cref{fi:obs_all_auto_15m_import_export_res} shows the CPU usage and memory usage for import timeseries modules and export timeseries modules with 1-minute resolution.
-We show the CPU usage with milli CPUs \cite{LinuxFoundationManagingKubernetes} (1 CPU = 1000m CPUs) and the memory usage shown with Megabytes (Mi) \cite{LinuxFoundationManagingKubernetes} in the graphs.
+We show the CPU usage with milli CPUs \cite{LinuxFoundationKubernetes:Containers} (1 CPU = 1000m CPUs) and the memory usage shown with Megabytes (Mi) \cite{LinuxFoundationKubernetes:Containers} in the graphs.
 Noticeably, the import-ascii-grid-upload microservice used around 10 CPUs at the peak time while using 3.6 Gigabytes (Gb) of memory.

### 2020-06-10 results/sec_2-workload.tex
misc ref fix

@@
 By using the \emph{throughput shaping timer}, we only need to configure the \acrshort{rps} throughout the test plan.
-Then the throughput shaping timer provides a feedback loop to the concurrency thread group via schedule feedback function to dynamically maintain thread count required to achieve target \acrshort{rps} \cite{KarunarathneWDIASJMeter}.
+Then the throughput shaping timer provides a feedback loop to the concurrency thread group via schedule feedback function to dynamically maintain thread count required to achieve target \acrshort{rps} \cite{KarunarathneWDIASJMeter.}.
 

### 2020-06-10 results/sec_4-discussion.tex
misc ref fix

@@
 Doing so, we can increase the performance as an example by directly porting the adapter-grid to netCDF with a low-level language such as C or FORTRAN.
-Other than \acrshort{eks}, users can use a different \acrshort{k8s} cluster that supports persistent volumes with the access of Read Write Many \cite{LinuxFoundationPersistentKubernetes}.
+Other than \acrshort{eks}, users can use a different \acrshort{k8s} cluster that supports persistent volumes with the access of Read Write Many \cite{LinuxFoundationKubernetesVolumes}.
 Then they can run multiple pods of grid adapter and increase the throughput of handling grid data.

### 2020-06-10 method/sec_3-microservice.tex
Done scan reading

@@
 Each adapter has a separate database, and the database is hosted separately for the high performance and to avoid interference.
-Apart from that, as we further discuss in \cref{se:data_preprocess}, the extension modules are running independently, such as Interpolation, Transformation, and Validation, and we will also discuss in \cref{se:data_preprocess}.
+Apart from that, as we further discuss in \cref{se:data_preprocess}, the extension modules are running independently, such as interpolation, transformation, and validation, and we will also discuss in \cref{se:data_preprocess}.
 The Extension Adapter allows users to register new event-based or time-based triggers for the extensions.

### 2020-06-10 method/sec_4-db_struct.tex
Done scan reading

@@
 Other than that, status adapter uses Redis as a key-value pair store to maintain the status for asynchronous requests handling while storing grid data.
-The extension adapter uses Redis's Publisher Subscriber capabilities to create a cronjob in extension scheduler service when a new extension creates with a trigger on time during data preprocessing.
+The extension adapter uses Redis's publisher subscriber capabilities to create a cronjob in extension scheduler service when a new extension creates with a trigger on time during data preprocessing.
 
@@
 \begin{itemize}
-  \item Open timeseries DB with MIT license
+  \item Open timeseries database with MIT license
   \item Support SQL-Like query language
@@
   \item Supports query operations on geospatial data \cite{MongoDBMongoDBManual}
-  \item Clustering and Sharding available for scalability and reliability
+  \item Clustering and sharding available for scalability and reliability
 \end{itemize}

### 2020-06-10 method/sec_5-data_preprocess.tex
Done scan reading

@@
 The WDIAS supports data preprocessing capabilities via extension modules.
-The current system has a few inbuilt extensions such as Interpolation, Transformation, and Validation, but users can add more extensions as required.
+The current system has a few inbuilt extensions such as interpolation, transformation, and validation, but users can add more extensions as required.
 
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{method/data_preprocess/serial_interpolation.pdf}
+    \includegraphics[width=1.0\textwidth]{method/data_preprocess/serial_interpolation.pdf}
     \caption{Serial interpolation.}
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{method/data_preprocess/spatial_interpolation.pdf}
+    \includegraphics[width=1.0\textwidth]{method/data_preprocess/spatial_interpolation.pdf}
     \caption{Spatial interpolation.}
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{method/data_preprocess/transformation.pdf}
+    \includegraphics[width=1.0\textwidth]{method/data_preprocess/transformation.pdf}
     \caption{Time interval aggregration.}
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{method/data_preprocess/validation.pdf}
+    \includegraphics[width=1.0\textwidth]{method/data_preprocess/validation.pdf}
     \caption{Timeseries data validation.}

### 2020-06-10 results/sec_1-test_plan.tex
Done scan reading

@@
 
-In \cref{se:high_level_design} we discussed three modules of weather data integration and assimilation systems such as integration, assimilation, and dissemination.
+In \cref{se:high_level_design}, we discussed three modules of weather data integration and assimilation systems such as integration, assimilation, and dissemination.
 We can map each of those modules to WDIAS modules, which provide the same functionalities as below.
@@
 The percentage of number of requests per each data type that comes to the system at a given time can be varied depending on the situation.
-The Majority of weather data requests come from weather stations and other observation tools.
+The majority of weather data requests come from weather stations and other observation tools.
 Then we need to validate and modify those timeseries data and store them as new timeseries that can directly feed into the NWMs.

### 2020-06-10 results/sec_2-workload.tex
Done scan reading
Remove And start

@@
   setup_precipitation.sh prepare
-    Segregate single file data into multiple files based on date. And Separate into main directories of 15min, 30min, 60min and create tar files
+    Segregate single file data into multiple files based on date. And separate into main directories of 15min, 30min, 60min and create tar files
   setup_precipitation.sh extract
@@
   setup_water-level.sh prepare
-    Segregate single file data into multiple grid file directories based on date. And Separate into main directories of 15min, 30min, 60min and create tar files
+    Segregate single file data into multiple grid file directories based on date. And separate into main directories of 15min, 30min, 60min and create tar files
   setup_water-level.sh extract
@@
     \item Timeseries metadata CSV
-    \item If scalar or vector
-        \begin{itemize}
-            \item Insert timeseries
-        \end{itemize}
-    \item If a grid
-    \begin{itemize}
-        \item Insert grid timeseries
-    \end{itemize}
+    \item If scalar or vector then insert timeseries, otherwise insert grid timeseries
     \item Wait for extensions timeseries
@@
     \item Query if scalar or vector
-    \item Retrieve if scalar or vector
-        \begin{itemize}
-            \item Retrieve timeseries
-        \end{itemize}
-    \item Retrieve if a grid
-    \begin{itemize}
-        \item Retrieve grid timeseries
-    \end{itemize}
+    \item If scalar or vector then retrieve timeseries, otherwise retrieve grid timeseries
     \item Increment date
@@
     \begin{itemize}
-        \item /Location: * → Locations
-    	\item /Location: Area → Locations
-    	\item /Parameter: Location → Parameters
-    	\item /Parameter: Locations → Parameters
-    	\item /Timeseries: Location → Timeseries
-    	\item /Timeseries: Locations → Timeseries
-    	\item /Timeseries: Locations, Parameter → Timeseries
-    	\item /Timeseries: Area → Timeseries
-    	\item /Timeseries: Area, Parameter → Timeseries
-    	\item /Timeseries: *, Parameter → Timeseries
-    	\item /Timeseries: * → Timeseries
+        \item /Location: * $\rightarrow$ Locations
+    	\item /Location: Area $\rightarrow$ Locations
+    	\item /Parameter: Location $\rightarrow$ Parameters
+    	\item /Parameter: Locations $\rightarrow$ Parameters
+    	\item /Timeseries: Location $\rightarrow$ Timeseries
+    	\item /Timeseries: Locations $\rightarrow$ Timeseries
+    	\item /Timeseries: Locations, Parameter $\rightarrow$ Timeseries
+    	\item /Timeseries: Area $\rightarrow$ Timeseries
+    	\item /Timeseries: Area, Parameter $\rightarrow$ Timeseries
+    	\item /Timeseries: *, Parameter $\rightarrow$ Timeseries
+    	\item /Timeseries: * $\rightarrow$ Timeseries
 	\end{itemize}

### 2020-06-15 lit/sec_1-fews.tex
Send to Dr Dilum

@@
 
-The timeseries data is one of scalar, vector, or grid data type.
-And different types of data stored as binary objects in a timeseries table inside the \acrshort{fews} system.
+The timeseries data is one of scalar, vector, or grid data type, and different types of data stored as binary objects in a timeseries table inside the \acrshort{fews} system.
 Functional components or any integrated models do not have direct access to the timeseries table, and those should use the data access module to access the data \cite{Werner2013TheSystem}.

### 2020-06-15 lit/sec_3-other-systems.tex
Send to Dr Dilum

@@
 To store on the large volume of disk space, it converts the data via a provided set of APIs.
-The above concept is similar to Delft-FEW's open data model approach.
+The above concept is similar to Delft-FEWS's open data model approach.
 Further, the DIAS contains additional tools that provide the functionality of quality control of the data and metadata management, which is similar to some of the services in LEAD.
@@
 Above WDIA systems are developed with the contributions from lots of researchers, and were implemented specifically to address issues like natural disasters.
-A use case such as CUrW, a given WDIA system requires to remodel the systems and define the forecasting flows to support the country-specific requirements.
+A use case such as \acrshort{curw}, a given WDIA system requires to remodel the systems and define the forecasting flows to support the country-specific requirements.
 Even some of the systems try to follow a generic approach to integrate new modules, but it is challenging to deploy modules for a closed source or proprietary software.

### 2020-06-15 method/sec_3-microservice.tex
Remove And start
Send to Dr Dilum

@@
 As an example, \acrshort{esb} supports multiple protocols, and endpoints can be used to implement complex logic.
-But microservice architecture follows an alternative approach called as \emph{Smart endpoints and dumb pipes} \cite{LewisMicroservicesPipes}.
+But microservice architecture follows an alternative approach called as \emph{smart endpoints and dumb pipes} \cite{LewisMicroservicesPipes}.
 Applications built based on microservice architecture are intended to be as disconnected and as coherent as possible.
@@
 
-\acrshort{microservice} prefers to have each microservice manages its database, either different instances of the same database technology or entirely different database systems - an approach called \emph{Polyglot Persistence} \cite{LewisMicroservicesManagement}.
+\acrshort{microservice} prefers to have each microservice manages its database, either different instances of the same database technology or entirely different database systems - an approach called \emph{polyglot persistence} \cite{LewisMicroservicesManagement}.
 
@@
 Other services use this event and update their data \cite{RichardsonMicroservicesSagas}.
-The above approach is also called the \emph{Saga pattern}.
+The above approach is also called the \emph{saga pattern}.
 
@@
 
-The scalability of a system can be explained via a concept called \emph{the Scale Cube}, which talks about the scalability of the application by defining over X, Y, and Z axes.
+The scalability of a system can be explained via a concept called \emph{the scale cube}, which talks about the scalability of the application by defining over X, Y, and Z axes.
 
@@
 Figures \ref{fi:wdias_micro_on_demand} and \ref{fi:wdias_micro_async} show the system interaction of the WDIA microservices architecture while handling requests.
-Each circle in the figures represents a microservice in the \acrshort{wdias}.
-And each microservice is implemented as a containerized application.
+Each circle in the figures represents a microservice in the \acrshort{wdias}, and each microservice is implemented as a containerized application.
 The left side of \cref{fi:wdias_micro_on_demand} shows the import modules of the \acrshort{wdias}, and the right side shows the export modules.
@@
 However, as shown in \cref{fi:wdias_micro_async}, when a request with a larger payload comes to the system, it stores the data for an asynchronous process and responds with a unique id that can be used to verify whether data processed successfully or not.
-We used the microservice concept of Saga, as mentioned in \cref{subse:sagas}, while processing the grid data.
+We used the microservice concept of saga pattern, as mentioned in \cref{subse:sagas}, while processing the grid data.
 First, it stores the data and responds with a unique identifier to the user.
@@
 Apart from that, as we further discuss in \cref{se:data_preprocess}, the extension modules are running independently, such as interpolation, transformation, and validation, and we will also discuss in \cref{se:data_preprocess}.
-The Extension Adapter allows users to register new event-based or time-based triggers for the extensions.
+The extension adapter allows users to register new event-based or time-based triggers for the extensions.
 The extension scheduler triggers the events based on time and the extension handler triggers events based on data change.

### 2020-06-15 method/sec_4-db_struct.tex
Remove And start
Send to Dr Dilum

@@
 \begin{itemize}
-  \item \emph{Point locations} -- Contains a name that is human readable. lat and lon of the location on the earth surface.
+  \item \emph{Point locations} -- Contains a name that is human readable. latitude(lat) and longitude(lon) of the location on the earth surface.
 \begin{lstlisting}[language=Python]
@@
 \end{lstlisting}
-  \item \emph{Irregular Grid locations} -- (endpoints are available within the WDIAS system, but skipped since it is out of the interest of the scope.)
+  \item \emph{Irregular Grid locations} -- (endpoints are available within the WDIAS system, but skipped the implementation since it is out of the interest of the scope.)
 \end{itemize}
@@
   \item \emph{Unit} -- metric unit of measuring
-  \item \emph{Parameter Type} -- Should be one of Instantaneous, Accumulative, or Mean
+  \item \emph{Parameter Type} -- Should be one of instantaneous, accumulative, or mean
 \begin{lstlisting}[language=Python]
@@
 \emph{Historical} means whether timeseries have continuous data such as observations from a weather station.
-\emph{forecast} means discrete set of timeseries data produce by forecasting.
+\emph{Forecast} means discrete set of timeseries data produce by forecasting.
 \end{itemize}
@@
 \subsubsection{Time Step}
-All TimeSteps has a unique String identifier called timeStepId.
+All time steps has a unique String identifier called timeStepId.
 The unit should be one of Second, Minute, Hour, Day, Week, Month, Year, or NonEqualDistance.
@@
 
-Among the above key attributes; Location, Parameter and Time Step attributes are composite attributes. But each of them has a unique identifier.
+Among the above key attributes; location, parameter and time step attributes are composite attributes. But each of them has a unique identifier.
 Given that, a timeseries can uniquely identify by \emph{moduleId, valueType, parameterId, locationId, timeseriesType and timeStepId}.
@@
 The scalar data point consists of a single value.
-And the vector data point consists of two values, such as magnitude and the direction of the vector.
+The vector data point consists of two values, such as magnitude and the direction of the vector.
 But for grid data, a point can consist of multiple values.
@@
 Redis is an open-source tool, and clustering is also available for scalability.
-Redis uses in-memory caching for fast access to the frequent access data in adapter-metadata and adapter-extension.
+Redis uses in-memory caching for fast access to the frequent access data in metadata adapter and extension adapter.
 Other than that, status adapter uses Redis as a key-value pair store to maintain the status for asynchronous requests handling while storing grid data.

### 2020-06-15 method/sec_5-data_preprocess.tex
Send to Dr Dilum

@@
 \subsection{Validation}
-Checks for counting reliable, doubtful, unreliable, and missing values
+Checks for counting reliable, doubtful, unreliable, and missing values.
 \begin{figure}[htp]
@@
 
-We exposed an \acrshort{api} to create new triggers for extensions via /extension endpoint.
+We exposed an \acrshort{api} to create new triggers for extensions via /extension endpoints.
 Following is the accepted payload of the request while creating a new trigger.
@@
 When new data is imported into one of the scalar adapter or vector adapter, those microservices notify the extension handler.
-Then the extension-handler checks whether there is any extension subscribed for imported timeseries.
+Then the extension handler checks whether there is any extension subscribed for imported timeseries.
 If there is an extension needed to be triggered, then it invokes the given extension with the required data.

### 2020-06-15 results/sec_2-workload.tex
Send to Dr Dilum

@@
 \begin{minipage}{\linewidth}
-\begin{lstlisting}[language=sh, caption= Preparation of water-level data.]
+\begin{lstlisting}[language=sh, caption= Preparation of water level data.]
 Set ROOT_DIR=~/wdias/wdias-performance-test
@@
     \includegraphics[width=0.6\textwidth]{results/work_load/experimental_setup_v3.pdf}
-    \caption{Experimental setup with JMeter.}
+    \caption{Experimental setup with Apache JMeter.}
     \label{fi:experimental_setup}

### 2020-06-15 results/sec_3-observations.tex
Send to Dr Dilum

@@
 This section includes the observations based on the test plans discussed in \cref{se:test_plan}, and the experimental system setup explained in \cref{se:workload}.
-Sections \ref{subse:obs_test_plan_all_60min} to \ref{subse:obs_test_plan_all_auto_15min}, we discuss the observations collected with performing the load test plans over 60 minutes data (24 data points per request), 30 minutes data (48 data points per request), and 15 minutes data (96 data points per request) by varying the request size.
-Then we perform another round of 15 minutes data with enabling auto-scaling for the higher resource utilized microservices.
+Sections \ref{subse:obs_test_plan_all_60min} to \ref{subse:obs_test_plan_all_auto_15min}, we discuss the observations collected with performing the load test plans over 60-minute data (24 data points per request), 30-minute data (48 data points per request), and 15-minute data (96 data points per request) by varying the request size.
+Then we perform another round of 15-minute data with enabling auto-scaling for the higher resource utilized microservices.
 
@@
 \begin{table}[ht]
-\caption{Throughput and Latency of load testing with 60-min data}
+\caption{Throughput and latency of load test with 60-minute data}
 \footnotesize
@@
     \includegraphics[width=1.0\textwidth]{results/obs/all/obs_all_60m_response_times_vs_threads.png}
-    \caption{Load testing with hourly data - Response Time vs Threads.}
+    \caption{Response time vs threads while load testing with hourly data.}
     \label{fi:test_obs_all_60m_response_vs_threads}
@@
     \includegraphics[width=1.0\textwidth]{results/obs/all/obs_all_60m_res_latencies_against_hits.png}
-    \caption{Load testing with hourly data - Latency against server hits.}
+    \caption{Latency against server hits while load testing with hourly data.}
     \label{fi:test_obs_all_60m_latency}
@@
 \begin{table}[ht]
-\caption{Throughput and Latency of load test with 30-minute data.}
+\caption{Throughput and latency of load test with 30-minute data}
 \footnotesize
@@
     \includegraphics[width=1.0\textwidth]{results/obs/all/obs_all_30m_response_times_vs_threads.png}
-    \caption{Load testing with 30 minutes of data - Response Time vs Threads.}
+    \caption{Response time vs threads while load testing with 30-minute of data.}
     \label{fi:test_obs_all_30m_response_vs_threads}
@@
     \includegraphics[width=1.0\textwidth]{results/obs/all/obs_all_30m_res_latencies_against_hits.png}
-    \caption{Load testing with 30 minutes of data - Latency against server hits.}
+    \caption{Latency against server hits while load testing with 30 minute of data.}
     \label{fi:test_obs_all_30m_latency}
@@
 \begin{table}[ht]
-\caption{Throughput and Latency of load testing with 15-minute data}
+\caption{Throughput and latency of load test with 15-minute data}
 \footnotesize
@@
     \includegraphics[width=1.0\textwidth]{results/obs/all/obs_all_15m_response_times_vs_threads.png}
-    \caption{Load testing with 15-minute of data - Response Time vs Active Threads.}
+    \caption{Response time vs active threads while load testing with 15-minute of data.}
     \label{fi:test_obs_all_15m_response_vs_threads}
@@
     \includegraphics[width=1.0\textwidth]{results/obs/all/obs_all_15m_res_latencies_against_hits.png}
-    \caption{Load testing with 15-minute of data - Latency against server hits.}
+    \caption{Latency against server hits while load testing with 15-minute of data.}
     \label{fi:test_obs_all_15m_latency}
@@
     \includegraphics[width=1.0\textwidth]{results/obs/all/obs_all_15m_transaction_throughtput_vs_threads.png}
-    \caption{Load testing with 15-minute of data - Transaction Throughput vs Thread.}
+    \caption{Transaction throughput vs thread while load testing with 15-minute of data.}
     \label{fi:test_obs_all_15m_throughtput}
@@
 \begin{table}[ht]
-\caption{Throughput and Latency of load testing with 15-minute data while enabled \acrshort{k8s} auto-scaling}
+\caption{Throughput and latency of load test with 15-minute data while enabled \acrshort{k8s} auto-scaling}
 \footnotesize
@@
     \includegraphics[width=1.0\textwidth]{results/obs/all_auto/obs_all_auto_15m_res_latencies_against_hits.png}
-    \caption{Load testing with 15-minute of data with enabled auto-scaling - Latency against server hits.}
+    \caption{Latency against server hits while load testing with 15-minute of data with enabled auto-scaling.}
     \label{fi:test_obs_all_auto_15m_latency}
@@
     \includegraphics[width=1.0\textwidth]{results/obs/all_auto/obs_all_auto_15m_transaction_throughtput_vs_threads.png}
-    \caption{Load testing with 15 minutes of data with enabled auto-scaling - Transaction Throughput vs Threads.}
+    \caption{Transaction throughput vs threads while load testing with 15-minute of data with enabled auto-scaling.}
     \label{fi:test_obs_all_auto_15m_throughtput}
@@
     \includegraphics[width=1.0\textwidth]{results/obs/all_auto/obs_all_auto_15m_import_export_res.png}
-    \caption{Load testing with auto-scaling resource usage of import and export modules.}
+    \caption{Load testing with auto-scaling resource usage of import and export modules over time.}
     \label{fi:obs_all_auto_15m_import_export_res}
@@
     \centering
-    \includegraphics[width=1.0\textwidth]{results/obs/all_auto/obs_all_auto_15m_import_grid_pod.png}
-    \caption{Load testing with auto-scaling import ascii grid number of pods over time.}
-    \label{fi:obs_all_auto_15m_import_grid_pod}
+    \includegraphics[width=1.0\textwidth]{results/obs/all_auto/obs_all_auto_15m_import_export_pods.png}
+    \caption{Load testing with auto-scaling number of pods of import and export modules over time.}
+    \label{fi:obs_all_auto_15m_import_export_pods}
 \end{figure}
 
-\cref{fi:obs_all_auto_15m_import_grid_pod} shows the number of import-ascii-grid-upload pods scheduled overtime during the test plan.
+\cref{fi:obs_all_auto_15m_import_export_pods} shows the number of import-ascii-grid-upload pods scheduled overtime during the test plan.
 As mentioned in the previous paragraph, we enabled the auto-scaling with a maximum of 10 pods and 80\% recommended CPU usage.
@@
     \includegraphics[width=1.0\textwidth]{results/obs/all_auto/obs_all_auto_15m_adapter_dbs_res.png}
-    \caption{Load testing with auto-scaling resource usage of database adapters.}
+    \caption{Load testing with auto-scaling resource usage of database adapters over time.}
     \label{fi:obs_all_auto_15m_adapter_dbs_res}
@@
 The throughput is similar among all the requests.
-The performance of the adapter-query depends on the performance of the document storage database performance and geo-indexing performance.
+The performance of the query adapter depends on the performance of the document storage database performance and geo-indexing performance.
 
@@
     \includegraphics[width=1.0\textwidth]{results/obs/query/obs_query_5m_latency_over_time.png}
-    \caption{Load testing query test over 5 minutes - Response Latency over Time.}
+    \caption{Response latency over time while load testing query test over 5 minutes.}
     \label{fi:test_obs_query_5m_response_latency}
@@
     \includegraphics[width=1.0\textwidth]{results/obs/query/obs_query_5m_response_times_vs_threads.png}
-    \caption{Load testing query test over 5 minutes - Response Latency Times vs Threads.}
+    \caption{Response latency times vs threads load testing query test over 5 minutes.}
     \label{fi:test_obs_query_5m_response_times_vs_threads}

### 2020-06-15 results/sec_4-discussion.tex
Send to Dr Dilum

@@
 Since each microservice in the \acrshort{wdias} is independent of technology, we can use a different technology stack to implement the service.
-Doing so, we can increase the performance as an example by directly porting the adapter-grid to netCDF with a low-level language such as C or FORTRAN.
+Doing so, we can increase the performance as an example by directly porting the grid adapter to netCDF with a low-level language such as C or FORTRAN.
 Other than \acrshort{eks}, users can use a different \acrshort{k8s} cluster that supports persistent volumes with the access of Read Write Many \cite{LinuxFoundationKubernetesVolumes}.

### 2020-06-15 summary/sec_2-research_limitations.tex
Send to Dr Dilum

@@
 \emph{Lack of data preprocessing modules}:
-We implemented the extension modules as an eco-system of integrating different preprocessing modules as add-ons to the system.
+We implemented the extension modules as an eco-system of integrating different preprocessing modules as add-ons to the \acrshort{wdias}.
 Then, users can use these modules for process the data which are inserted into the system in real time or process later based on regular intervals.
@@
 \emph{Grid data performance}:
-As mentioned in \cref{se:discussion}, adapter-grid is using a Python wrapper for netCDF FORTRAN implementation with parallel IO enabled.
+As mentioned in \cref{se:discussion}, grid adapter is using a Python language wrapper for netCDF FORTRAN implementation with parallel IO enabled.
 However, it has some performance issues and memory leak issues as well.
 Since each microservice in the \acrshort{wdias} is independent of technology, we can use a different technology stack to implement the service.
-As an example, we can use a low-level language such as C or FORTRAN to implement the adapter-grid, which will affect performance improvements and lesser issues.
+As an example, we can use a low-level language such as C or FORTRAN to implement the grid adapter, which will affect performance improvements and lesser issues.
 There is some future work that can focus on improving the performance of storing grid data.
@@
 As further described in \cref{se:discussion}, we can increase the performance of adapter microservices by using InfluxDB commercial cluster support for high availability or horizontal scaling of InfluxDB.
-With the InfluxDB cluster, it is possible to run multiple pods of adapter-scalar and adapter-vector to support more server hits per second.
+With the InfluxDB cluster, it is possible to run multiple pods of scalar adapter and vector adapter to support more server hits per second.
 Other than that, the \acrshort{wdias} performance can improve via partitioning the timeseries key space into multiple InfluxDB instances.
-As an example, based on the key attribute \cref{subse:timeseries_key_attributes} Timeseries Type, the adapter-scalar can connect to four instances of InfluxDB instances such as External Historical, External Forecast, Simulated Historical, and Simulated Forecast.
+As an example, based on the key attribute \cref{subse:timeseries_key_attributes} Timeseries Type, the scalar adapter can connect to four instances of InfluxDB instances such as external historical, external forecast, simulated historical, and simulated forecast.
 
@@
 
-\emph{Supporting Irregular Grids}:
-At the moment, \acrshort{wdias} does not support Irregular Grids, but it has the API endpoints defined for the implementation of such support with following the microservice architecture.
+\emph{Supporting irregular grids}:
+At the moment, \acrshort{wdias} does not support irregular grids, but it has the API endpoints defined for the implementation of such support with following the microservice architecture.
 We reduced the scope of the research by removing such components from the system, and such level of implementation does not belong to the \acrshort{wdias} scope as well.

### 2020-12-22 method/sec_0_introduction.tex
Remove And start
Upgrade Future work

--- 2020-05-29 method/sec_0_introduction.tex
@@
 
-To get an overall idea of the flow of weather forecast, let us look into one of the weather forecasting flows in the \acrshort{curw} \cite{CUrWSL2017SL}.
+To get an overall idea of the weather forecast flows, let us look into one of the weather forecasting flows in the \acrshort{curw} \cite{CUrWSL2017Lanka}.
 
 \begin{enumerate}
-    \item Extract \acrshort{GRIB} \acrshort{wrf} model data to the \acrshort{netCDF} format.
-    \item Extract \acrshort{netCDF} data to \acrshort{csv} format for each location data, then feed to HEC-HMS hydrodynamic model and get the output as a \acrshort{csv} file.
-    \item HEC-HMS's \acrshort{csv} output and precipitation as Grid files feed into the FLO2D hydrologic model and get the water level as ASCII Grid files after the simulation is complete.
-    \item Upload above ASCII files to a geographic information system after convert to a compatible format, then use for the loss estimation.
+    \item First, the researchers fetch the weather forecast data from global model which is in the \acrshort{GRIB} format.
+After extracting \acrshort{GRIB} data, they run the \acrshort{wrf} with geographical coordinates for a given area, and generates \acrshort{wrf} model forecast in \acrshort{netCDF} format.
+    \item Then they extract forecast precipitation weather data in \acrshort{netCDF} to \acrshort{csv} file format as scalar timeseries for each interested location.
+Next they feed forecasted precipitation data to HEC-HMS hydrodynamic model and get the water discharge forecast of a water canal as the output in the \acrshort{csv} file format.
+    \item They use a developed 2D FLO2D hydrologic model for a given area to simulate the water level.
+By feeding HEC-HMS's water discharge forecast and \acrshort{wrf} precipitation forecast as Grid files into the FLO2D hydrologic model, the researchers forecast the water level of the modeled area as ASCII Grid files after the simulation is completed.
+    \item By uploading above water level forecasts in ASCII Grid files into a geographic information system after convert to a compatible format, they calculate the loss estimation.
 \end{enumerate}
@@
 The system should be capable of integrating data from different sources such as satellite data, high end, and low-end weather station.
-And the system should be able to handle multidimensional spatial and temporal weather data efficiently and optimally.
+Also, the system should be able to handle multidimensional spatial and temporal weather data efficiently and optimally.
 \subsubsection{Assimilation}

### 2020-12-22 method/sec_1-architectural_decisions.tex
Send to Dr Dilum
Upgrade Future work

@@
 Moreover, it tried to use an \acrfull{esb} to integrate different modules, as \acrshort{esb} could act as a shared layer for all of the modules to interact together.
-By default, \acrshort{esb} also provides publisher/subscribe (pub/sub) capabilities.
+By default, \acrshort{esb} also provides publisher/subscriber capabilities.
 
@@
 
-\cref{fi:k8s_architecture} gives an overall idea on the components of \acrshort{k8s},
+\cref{fi:k8s_architecture} give an overall idea on the components of \acrshort{k8s},
 \begin{itemize}

### 2020-12-22 method/sec_3-microservice.tex
Upgrade Future work

@@
 
-\acrshort{microservice} prefers to have each microservice manages its database, either different instances of the same database technology or entirely different database systems - an approach called \emph{polyglot persistence} \cite{LewisMicroservicesManagement}.
+\acrshort{microservice} prefers to have each microservice manages its database, either different instances of the same database technology or entirely different database systems - \emph{polyglot persistence} \cite{LewisMicroservicesManagement}.
 

### 2020-12-22 method/sec_4-db_struct.tex
Upgrade Future work

@@
 
-The foundation of the \acrshort{wdias} is data-centric. We need to look into the weather data timeseries deeply to understand the underline design decisions of the \acrshort{wdias} database structure.
+The architecture and the storage management of the \acrshort{wdias} is designed and developed based on the weather data.
+We need to look into the weather data timeseries deeply to understand the underline design decisions of the \acrshort{wdias} database structure.
 
@@
 \subsubsection{Module ID}
-String field which describe the source of the data generated. e.g., HEC-HMS, FLOW2D, weather-station, etc
+String field which describe the source of the data generate. e.g., HEC-HMS, FLOW2D, weather-station.
 
@@
 \begin{itemize}
-  \item \emph{Point locations} -- Contains a name that is human readable. latitude(lat) and longitude(lon) of the location on the earth surface.
+  \item \emph{Point locations} -- Contains a name that is human readable.
+latitude(lat) and longitude(lon) of the location on the earth surface.
+Following is an example of define a location using \acrfull{json}.
 \begin{lstlisting}[language=Python]
@@
   \item \emph{Regular Grid locations} -- Contains a name that is human readable. The grid presents by dividing into equal size cells. Thus, it needs the number of rows and columns. 
-  And the location of the first cell and the width and height of it.
+  And the location of the first cell and the width and height of it. Below \acrshort{json} format shows an example of the regular grid location. 
 \begin{lstlisting}[language=Python]
@@
 A parameter can be used in multiple locations.
-While defining a parameter, three required fields need to be provided, such as variable, unit, and \emph{parameterType}.
-
-\begin{itemize}  
-  \item \emph{Variable} -- Nature of the variable measuring. Example precipitation, temperature and water level
-  \item \emph{Unit} -- metric unit of measuring
-  \item \emph{Parameter Type} -- Should be one of instantaneous, accumulative, or mean
+While defining a parameter, three required fields need to be provided, such as variable, unit, and \emph{parameterType} as shown in the below example \acrshort{json} format.
 \begin{lstlisting}[language=Python]
@@
 \end{lstlisting}
+
+\begin{itemize}  
+  \item \emph{Variable} -- Nature of the variable measuring. Example precipitation, temperature and water level
+  \item \emph{Unit} -- metric unit of measuring
+  \item \emph{Parameter Type} -- Should be one of instantaneous, accumulative, or mean
 \end{itemize}
@@
 One of multipliers or dividers can be used to define the interval between each measurement.
+We can represent each minute time step in following \acrshort{json} format.
 \begin{lstlisting}[language=Python]
@@
 Given that, a timeseries can uniquely identify by \emph{moduleId, valueType, parameterId, locationId, timeseriesType and timeStepId}.
+Here is an example of an unique weather data timeseries using \acrshort{json} format.
 \begin{lstlisting}[language=Python]

### 2020-12-22 results/sec_2-workload.tex
Upgrade Future work

@@
 
-\acrshort{wdias} is capable of storing any numeric value up to 3 decimal points as per the default configuration.
+\acrshort{wdias} is capable of storing any numeric value up to three decimal points as per the default configuration.
 Even the parameter type is either precipitation, temperature does not make any difference, because in storage perspective, we are storing numeric value.
@@
 The above method reduced the overhead of filtering data during performance testing.
-We also set up the JMeter as a containerized application, which allows us to run inside the k8s cluster.
+We also set up the JMeter as a containerized application, which allows us to run inside the \acrshort{k8s} cluster.
 As an optimization for the JMeter container creation, we avoid adding extensive test timeseries data, which causes the container size to be large and making the build process slower.

### 2020-12-22 results/sec_3-observations.tex
Upgrade Future work

@@
 \cref{fi:test_obs_all_15m_throughtput} shows the total server's transaction throughput against the number of active threads.
-The formula for total server transaction throughput \cite{ApacheSoftwareFoundationJMeter:Plugin} is;
-\[
-    \displaystyle \frac{<active \quad threads> \times \quad 1 \quad second}{<1 \quad thread \quad response \quad time>}
-\]
+The formula for total server transaction throughput is \emph{active threads per second / thread response time} \cite{ApacheSoftwareFoundationJMeter:Plugin}.
 It shows the statistical maximum possible number of transactions based on the number of users accessing the application.

### 2020-12-22 summary/sec_2-research_limitations.tex
Upgrade Future work

@@
 
-Next, we discussed the lacking features of the \acrshort{wdias} and the set of improvements.
-
-\emph{Lack of data preprocessing modules}:
+Next, we discussed \emph{Lack of data preprocessing modules}:
 We implemented the extension modules as an eco-system of integrating different preprocessing modules as add-ons to the \acrshort{wdias}.
@@
 With the InfluxDB cluster, it is possible to run multiple pods of scalar adapter and vector adapter to support more server hits per second.
-Other than that, the \acrshort{wdias} performance can improve via partitioning the timeseries key space into multiple InfluxDB instances.
+The \acrshort{wdias} performance can improve via partitioning the timeseries key space into multiple InfluxDB instances.
 As an example, based on the key attribute \cref{subse:timeseries_key_attributes} Timeseries Type, the scalar adapter can connect to four instances of InfluxDB instances such as external historical, external forecast, simulated historical, and simulated forecast.
@@
 \emph{Supporting irregular grids}:
+\gkc{When consider about 2D grid, there are two types of grids such as regular grids and irregular grids.
+In regular grid system, each shell consist of fix width and height.
+But for irregular grid system, each shell define as a 2D polygon with there's coordinates.}
 At the moment, \acrshort{wdias} does not support irregular grids, but it has the API endpoints defined for the implementation of such support with following the microservice architecture.
@@
 \emph{Define infrastructure as code}:
-Physical nodes for the \acrshort{k8s} cluster created using cloud computing providers such as Amazon EKS, Google Cloud, and Microsoft Azure cloud.
+Physical nodes for the \acrshort{k8s} cluster can be created using cloud computing providers such as Amazon EKS, Google Cloud, Microsoft Azure cloud, or even using own cluster.
+\gkc{During the load testing, we used Amazon cloud based physical machines as nodes for the test setup.
+And users need to have some basic understanding on Amazon cloud and it's technologies to setup the system, and the \acrshort{k8s} cluster}.
 However, the infrastructure that needs to deploy the \acrshort{wdias} can be defined as code such as using tools like Terraform, which is independent of the cloud computing provider.
 Using such a tool, users will be able to quickly deploy the \acrshort{wdias} on any cloud provider without much hassle.
+\gkc{The \acrshort{wdias} resource requirements are configured as code in the Terraform, and user can easily interact with those clouds using Terraform provider modules without much prior knowledge.}
 
-\emph{Alerting extension modules}: At the moment, extensions only support OnChange and OnTime events.
-However, it will be useful to have event trigger support based on the configured alert level or threshold level.
+\emph{Alerting extension modules}: At the moment in the \acrshort{wdias} basic framework, the extensions only support OnChange and OnTime event triggers.
+However, it is useful to have event triggers support based on the configured alert level or threshold level.
+\gkc{Here, users should be able to register triggers based on given alert levels, and the alerting extension should trigger a webhook which is provide by the user while registering the trigger.
+As an example, a user can register an alert event on particular timeseries such as waterlevel, and also provide the threshold value based on historical flood events.
+When the waterlevel exceeds the given threshold value, the system will trigger the provided webhook.
+Then the user will be notified or the webhook endpoint will take necessary actions.}
 
-\emph{Publisher Subscriber extension modules}: The \acrshort{wdias} better to be capable of triggering external systems based on events such as webhooks.
+\emph{Publisher Subscriber extension modules}: The \acrshort{wdias} better to be capable of triggering external systems based via Publisher Subscriber support.
+\gkc{As an example, we may required to sync weather station's precipitation timeseries data into an external system through \acrshort{wdias} when there is a rain.
+One possibility is, the external system can sync data with timeseries data via polling through the \acrshort{wdias}.
+But it is inefficient, since the external system needs to fetch the data via export modules even there is not any rain.
+Rather, we can use Publisher Subscriber capabilities to efficiently sync the data.
+With this extension modules, users can create topics and publishers extensions will push data into the topics when particular criteria is met, such as when there is rain in above example.
+Then external systems will subscribes to topic above topics while providing a webhook endpoint.
+Whenever there is data pushed into the topic, the extension modules will send data to the subscribers via webhooks.}

### 2020-12-22 summary/sec_2-research_limitations.tex
Add not explicitly testing for high-availability as a limitation

@@
 As an example, based on the key attribute \cref{subse:timeseries_key_attributes} Timeseries Type, the scalar adapter can connect to four instances of InfluxDB instances such as external historical, external forecast, simulated historical, and simulated forecast.
+
+\emph{Explicitly not testing for high availability}:
+\gkc{By default, the container orchestration framework is handling service failures, auto scaling, auto down scaling, and independent service deployments.
+Also, when considering about modern cloud resources in data centers have better availability as well and failure handling.
+Combining both of factors will enable high availability for the \acrshort{wdias} system.
+But in this research, we are not heavily rely on those third party tools.
+Also, we do not explicitly test for the high availability with performing manually terminating services, and letting crash some of the services to measure how is it affect on the \acrshort{wdias} system high availability.}
 

### 2020-12-24 results/sec_3-observations.tex
Fixed overlap lables

@@
 This section includes the observations based on the test plans discussed in \cref{se:test_plan}, and the experimental system setup explained in \cref{se:workload}.
-Sections \ref{subse:obs_test_plan_all_60min} to \ref{subse:obs_test_plan_all_auto_15min}, we discuss the observations collected with performing the load test plans over 60-minute data (24 data points per request), 30-minute data (48 data points per request), and 15-minute data (96 data points per request) by varying the request size.
+Sections \ref{subse:obs_test_plan_all_60min} to \ref{subse:obs_test_plan_all_auto_15min}, we discuss the observations collected with performing the load test plans with 60-minute data (24 data points per request), 30-minute data (48 data points per request), and 15-minute data (96 data points per request) by varying the request size for scalar and vector timeseries.
+\gkc{For grid timeseries, we performed the load test plans with ASCII grid file as data for each time step which has the size of 52 kilobyte.
+On average, each sample grid data for 60-minute data requests consist of 1.2 megabyte, 30-minute data requests consist of 2.4 megabyte, and 15-minute data requests consist of 4.9 megabyte}.
 Then we perform another round of 15-minute data with enabling auto-scaling for the higher resource utilized microservices.
@@
 
-After running the test plan with 60-minute resolution data (24 data points per request), we observed the data summary of \cref{tab:obs_all_60_min_summary}.
+After running the test plan with 60-minute resolution data (24 data points per scalar and vector requests, and 24 ASCII grid files per grid requests), we observed the data summary of \cref{tab:obs_all_60_min_summary}.
 The test plan performed \num{311e3} of sample requests within 30 minutes of elapsed time.
@@
 Noticeably it has 0\% of errors, which means that all the requests completed successfully.
-Also, \acrshort{wdias} handled 40.5 \acrshort{rps} of scalar and vector data requests with the given workload.
-The retrieval of scalar and vector timeseries has lesser delay than the insertion.
-On the other hand, insert grid timeseries data performed within 23 milliseconds, and almost all the requests perform within the same amount of time.
+Also, \acrshort{wdias} handled 40.5 \acrshort{rps} of scalar and vector data requests on average with the given workload.
+The retrieval of scalar and vector timeseries has lesser delay than the insertion such that retrieve on average 8 milliseconds, and up to 90\% percentile retrieve data within 10 milliseconds.
+On the other hand, insert grid timeseries data performed within 23 milliseconds on average, and almost all the requests perform within the same amount of time.
 Hence, the standard deviation is smaller.
 Delay with inserting grid timeseries smaller because those requests are handled asynchronously.
-Retrieve grid timeseries data performed with a bit higher value of latency of 68 milliseconds due to performed the retrieve request on-demand.
-Both insert and retrieve grid timeseries data have 4.5 \acrshort{rps} since it only gets 10\% of the number of requests from total number of requests during the load test.
+Retrieve grid timeseries data performed with a bit higher value of latency of 68 milliseconds on average due to performed the retrieve request on-demand.
+Both insert and retrieve grid timeseries data have 4.5 \acrshort{rps} on average since it only gets 10\% of the number of requests from total number of requests during the load test.
+Location query test case runs for the scalar and vector timeseries metadata, and it was able to fulfill the requests within 3 milliseconds on average.
 
@@
     \centering
-    \includegraphics[width=1.0\textwidth]{results/obs/all_auto/obs_all_auto_15m_import_export_res.png}
+    \includegraphics[width=1.0\textwidth]{results/obs/all_auto/obs_all_auto_15m_import_export_res.pdf}
     \caption{Load testing with auto-scaling resource usage of import and export modules over time.}
@@
     \centering
-    \includegraphics[width=1.0\textwidth]{results/obs/all_auto/obs_all_auto_15m_import_export_pods.png}
+    \includegraphics[width=1.0\textwidth]{results/obs/all_auto/obs_all_auto_15m_import_export_pods.pdf}
     \caption{Load testing with auto-scaling number of pods of import and export modules over time.}
@@
     \centering
-    \includegraphics[width=1.0\textwidth]{results/obs/all_auto/obs_all_auto_15m_adapter_dbs_res.png}
+    \includegraphics[width=1.0\textwidth]{results/obs/all_auto/obs_all_auto_15m_adapter_dbs_res.pdf}
     \caption{Load testing with auto-scaling resource usage of database adapters over time.}

### 2020-12-24 results/sec_3-observations.tex
in Slide 19 - We should explain the unstable area on the right of the graph. There are a couple of similar graphs in the thesis

@@
 Both insert and retrieve grid timeseries data have 4.5 \acrshort{rps} on average since it only gets 10\% of the number of requests from total number of requests during the load test.
-Location query test case runs for the scalar and vector timeseries metadata, and it was able to fulfill the requests within 3 milliseconds on average.
+\gkc{Location query test case runs for the scalar and vector timeseries metadata, and it was able to fulfill the requests within 3 milliseconds on average.}
 
@@
 The performance degrades because those data handles on-demand and depends on the timeseries database performance.
+\gkc{But the \acrshort{wdias} was able to perform insert and retrieval of grid data with same latency when the request sizes are smaller.}
 
@@
 This graph further proves that the system was able to handle the increasing workload without any significant change in the delay.
+\gkc{The stepped red colour graph for server hits per second shows the number of requests that was send by the load test ever the elapsed time.
+And other horizontal lines with spikes show the latency for each of test case such as insertion and retrieval of scalar, vector, and grid data over elapsed time.}
 
@@
 
-Next, we performed the test plan with 30-minute resolution data, which means 48 data points per each request for the scalar and vector data types, and 48 ASCII grid files per each insertion request for the grid data type.
+Next, we performed the test plan with 30-minute resolution data, which means 48 data points per each request for the scalar and vector data types, and 48 ASCII grid files with 2.4 megabytes of size per each insertion request for the grid data type.
 Also, the test plan performed round up to \num{311e3} number of sample requests, which is almost similar to the number of samples processed with hourly resolution data.
+\gkc{That means \acrshort{wdias} system was able to process same amount of request while increasing the request size with providing higher throughput.}
 
@@
 Even though we doubled the request size, \acrshort{wdias} was able to keep the performance almost the same instead of increasing the latency twice.
+\gkc{Insertion and retrieval of scalar and vector data increased by 1 millisecond on average.
+But the grid data insert latency increased from 23 milliseconds to 40 milliseconds, which is almost double of the previous latency.
+This is expected because of the grid data size was increased from 1.2 megabytes to 2.4 megabytes, and it is taking time for stream the data into the \acrshort{wdias} system.
+Retrieval of grid data also increased by 22 milliseconds, since during the test cases we try to retrieve the inserted grid data in different format, but the export data size also get increased due to increase of the insert grid data size.}
 
@@
 The InfluxDB can fine-tune for writes or read based on the requirements, but we used it with default configurations.
+Also, the InfluxDB commercial version support horizontal database scaling with sharding, and we are using the basic open source support in this test setup.
 
@@
 \cref{fi:test_obs_all_30m_latency} graph provides a better overview of the variation of latency over the elapsed time of the test plan against the \acrshort{rps}.
-By referring to the graph, we can see that over time the latency does not change very significantly.
-However, during the peak load, it shows a minor variation in latency of the insertion and retrieval of grid timeseries.
+By referring to the graph, we can see that over the elapsed time the latency does not change very significantly.
+However, during the peak load, it shows a minor spikes in latency of the insertion and retrieval of grid timeseries.
 When compared to \cref{fi:test_obs_all_60m_latency}, the latency of insertion grid timeseries data almost doubled.
-The grid timeseries data was handled asynchronously after successfully storing, thus the latency for storing the data increased by a factor of two since the request data size also increased twice.
+The grid timeseries data was handled asynchronously after successfully steamed the data into the \acrshort{wdias} system, thus the latency for storing the data increased by a factor of two since the request data size also increased twice.
 
@@
 
-During this section, we performed the test plan with 15-minute resolution data, which means 96 data points per each request for the scalar and vector data types, and 96 ASCII grid files per each insertion request for the grid data type.
+During this section, we performed the test plan with 15-minute resolution data, which means 96 data points per each request for the scalar and vector data types, and 96 ASCII grid files per each insertion request with the size of 4.9 megabyte for the grid data type.
 The size of each request is four times larger than the 60-minute resolution data.
 Here also, the test plan performed approximately \num{311e3} of sample requests, which are almost similar to sample requests made during 60-minute and 30-minute resolution data.
+\gkc{This means the \acrshort{wdias} system was able to increase the throughput while increasing load with the request size, and processed the same amount of requests within given elapsed time.}
 \begin{table}[ht]
@@
 When compared to the observations from the performance test with 30-minute data, the request latency also increased for all sample requests.
-Also, the standard deviation of retrieval timeseries data increased by a considerable amount for all the data type's sample requests.
-One of the reasons for increasing the retrieval data delay was while performing heavy database writes on the database has effects on the database reads.
-Even though we increased the request data size by four times higher, the system was able to handle all requests without significant performance issues.
-Also, the system provided the same throughput as with 60-minute and 30-minute resolution data.
+\gkc{The scalar and vector data insertion increased by 1 milliseconds, and retrieval of those data increased significantly by doubling the latency.} Also, the standard deviation of retrieval timeseries data increased by a considerable amount for all the data type's sample requests.
+One of the reasons for increasing the retrieval data delay was while performing heavy database writes on the InfluxDB database instance has effects on the database reads.
+\gkc{The grid data insert and retrieve latency also doubled approximately since the stream data size increase by a factor of two compared to 30-minute data.
+Noticeably, the error rate of inserting grid data increased up to 1.42\%.} Even though we increased the request data size by four times higher, the system was able to handle all requests without significant performance issues.
+Also, the system was able to process same number of request as with 60-minute and 30-minute resolution data while increasing the throughput of the system with the request size.
 
@@
 As per the graph, the system was able to keep the response latency constant while increasing the number of active threads.
-However, when the number of active threads became higher, there was a disturbance with the response delay during the insertion and retrieval of timeseries data.
-The latency of insert and retrieval of grid timeseries data increased twice when compared to 30-minute resolution data.
+However, when the number of active threads became higher, there was a disturbance with the response delay during the insertion and retrieval of scalar and vector timeseries data.
+\gkc{As we mentioned about, this may happened due to the system reached it's resource limitation, or caused by heavy database read and writes on the InfluxDB free database version.} The latency of insert and retrieval of grid timeseries data increased twice when compared to 30-minute resolution data.
 With a larger request size, we can notice the latency also increased by a smaller factor when we increased the number of active threads.
+\gkc{When compare to the load testing with 60-minute and 30-minute data, we can see higher number of 192 active threads used by the JMeter to maintain the \acrshort{rps}.
+When we increase the request size, the latency also increase.
+Then the active threads have to wait for the response from the system rather doing any other work.
+To maintain the server hits, the JMeter has to spawn more active threads.}
 
@@
 As per the graph, the system was able to keep the latency constant all over the test plan.
-However, at the peak, the latency tends to vary from the mean value by a smaller factor.
-Also, we can observe that there were lots of latency spikes throughout the test plan when we increased the request size.
+However, at the peak, the latency tends to vary from the mean value.
+Also, we can observe that there were lots of latency spikes throughout the test plan when we increased the request size four times.
 
@@
 \cref{fi:test_obs_all_15m_throughtput} shows the total server's transaction throughput against the number of active threads.
-The formula for total server transaction throughput is \emph{active threads per second / thread response time} \cite{ApacheSoftwareFoundationJMeter:Plugin}.
-It shows the statistical maximum possible number of transactions based on the number of users accessing the application.
+The formula for total server transaction throughput is \emph{active threads per second / one thread response time} \cite{ApacheSoftwareFoundationJMeter:Plugin}.
+It shows the statistical maximum possible number of transactions based on the number of active threads accessing the application at a given time.
+\gkc{This gives an estimated transaction throughput based on the latency of requests against the number of active threads at a given time.
+We can assume that the highest number of active threads occur at the peak time of the load testing.
+But the number of latency sample are limit with the higher number of active threads.
+Because of that, in \cref{fi:test_obs_all_15m_throughtput} we can see missing data points, and spikes with graph drawing with available data points.
+Further we can analyze this graph against \cref{fi:test_obs_all_15m_response_vs_threads}, and derive this output based on latency fluctuation in that graph.}
 By combining the \cref{fi:test_obs_all_15m_latency}, this graph shows that the throughput of the system gets increased without much change in the latency, thus it proves the scalability of the \acrshort{wdias}.
@@
 Since \acrshort{eks} does not support multiple reads and writes support volumes \cite{LinuxFoundationKubernetesVolumes}, we are unable to enable auto-scaling during the test plan.
+But some of other \acrshort{k8s} platforms support multiple reads, and writes volumes.
 However, the test plan performed approximately \num{311e3} of almost similar sample requests during the above sections.
@@
 Since the standard deviation also reduced, we can conclude that the latencies are closer to the average latency.
-Further, these improvements in insert grid timeseries data seem to affect the output of retrieve grid timeseries data as well.
+Further, these improvements in insert grid timeseries data seem to affect the output of retrieve grid timeseries data as well \gkc{, and decrease the latency from 118 milliseconds to 89 milliseconds.
+Regarding the scalar and vector timeseries data insertion latency was bit increased.
+But we can notice that, the retrieval of scalar and vector timeseries latency improved from 23 milliseconds to 7 milliseconds.
+Specially, the latency for query location timeseries metadata was improved from 3 milliseconds to 2 milliseconds.
+It was constant with 3 milliseconds in previous load testings.
+Other than inserting scalar and vector data, other test cases standard deviation was improved, and we can conclude that the overall system performance is enhance with auto-scaling enabled.}
 
@@
 \end{figure}
-\cref{fi:test_obs_all_auto_15m_latency} graph provides an overview of the variation of latency over the elapsed time of the test plan against the number of server hits per second for 15-minute data while auto-scaling enabled for K8s.
+\cref{fi:test_obs_all_auto_15m_latency} graph provides an overview of the variation of latency over the elapsed time of the test plan against the number of server hits per second for 15-minute data while auto-scaling enabled for \acrshort{k8s}.
 According to the graph, the \acrshort{wdias} was able to keep the latency constant all over the elapsed time.
@@
 When compared to \cref{fi:test_obs_all_15m_throughtput} without auto-scaling, the estimated throughput with a higher number of active threads becomes stable, according to the graph.
-Thus, we can conclude that enabling auto-scaling also improves the throughput by supporting a higher number of active users.
-During the next paragraphs, we discuss the resource usage while running the test plan while enabling the auto-scaling.
+Thus, we can conclude that enabling auto-scaling also improves the throughput by supporting a higher number of active threads.
+\gkc{We can see fluctuation when increase the number of active threads due to lack of sample latency with higher number of active threads during the peak of load testing.
+Further, we can see estimated throughput for insert and retrieve grid data also increased by a small factor, and it more smooth than 15-minute data load testing without auto-scaling.} During the next paragraphs, we will discuss the resource usage while running the test plan while enabling the auto-scaling.
 

### 2020-12-25 Thesis.tex
Proofread Chapter 4
Fix: NWM
Fixed: Bib IEEE style
Upgrade Future work
Proof read: Chapter 1

@@
 \usepackage{tabulary}
-\usepackage{biblatex}
+\usepackage[style=ieee]{biblatex}
 \usepackage[titletoc]{appendix}
+\usepackage{siunitx}
 
@@
 \newcommand{\gkc}[1]{\todo[author=Gihan, inline, color=green!50]{#1}}
+\newcommand{\gc}[1]{\todo[author=Gihan Revisit, inline, color=orange!50]{#1}}
 
@@
         \vspace{32pt}
-        May 2020
+        August 2020
 
@@
        % \normalsize
-        178008U\\
+        178004U\\
          \vspace{72pt}
@@
 \acrfull{nwm} utilize data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images.
-Before using such multimodal data in a NWM, it is necessary to transcode data into a format that can be ingested by the \acrshort{nwm}.
+Before using such multimodal data in a \acrshort{nwm}, it is necessary to transcode data into a format that can be ingested by the \acrshort{nwm}.
 Moreover, the data integration system's response time needs to be relatively low to forecast and monitor time-sensitive weather events like hurricanes, storms, and flash floods that require rapid and frequent execution of \acrshort{nwm}.
@@
 \addcontentsline{toc}{chapter}{References}
+\renewcommand*{\UrlFont}{\rmfamily}
 \printbibliography[title={References}]

### 2020-12-25 introduction/sec_1-motivation.tex
Fixed: Bib IEEE style
Proof read: Chapter 1

@@
 
-\acrfull{curw} \cite{CUrWSL2017SL} is tasked with the mission to reduce water-related natural disasters in Sri Lanka.
+\acrfull{curw} \cite{CUrWSL2017Lanka} is tasked with the mission to reduce water-related natural disasters in Sri Lanka.
 \acrshort{curw} \cite{CUrWSLObservedSL} is implementing own system with the idea of long-term maintainability rather than depending on existing weather data integration systems.
-\acrshort{curw} collects real-time data from weather stations and other relevant entities and generates daily forecasts.
+\gkc{Because of existing weather systems are not open source to configure as required, and not flexible enough to change without much help from the maintainers.} \acrshort{curw} collects real-time data from weather stations and other relevant entities and generates daily forecasts.
 Then the generated results are shared with relevant public departments responsible for disaster planning, risks mitigation, and disaster management.
@@
 To enhance the accuracy of weather forecast, it is necessary to provide reliable and detailed weather data as inputs to \acrshort{nwm}.
-These NWMs utilize multi-modal weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images.
-Before feeding such diverse data (collected from different sources that belong to different stakeholders) into respective NWMs, it is necessary to convert them to a data format that can be ingest by the models.
-Moreover, the data integration system's response time needs to be relatively low to forecast and monitor time-sensitive weather events like hurricanes, storms, and floods which require rapid and frequent execution of NWMs.
+These \acrshort{nwm}s utilize multi-modal weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images.
+Before feeding such diverse data (collected from different sources that belong to different stakeholders) into respective \acrshort{nwm}s, it is necessary to convert them to a data format that can be ingest by the models.
+Moreover, the data integration system's response time needs to be relatively low to forecast and monitor time-sensitive weather events like hurricanes, storms, and floods which require rapid and frequent execution of \acrshort{nwm}s.
 
-Weather data processed by a NWM maybe used by several other \acrshort{nwm}, as well as by many third-party applications and researcher.
+Weather data processed by a \acrshort{nwm} maybe used by several other \acrshort{nwm}, as well as by many third-party applications and researcher.
 For example, logistic companies could use the processed data with their data models to plan and schedule their deliveries.
@@
 
-Data Integration and Analysis System (DIAS) \cite{Kawasaki2018DataReduction} and Meteorological Assimilation Data Ingest System (MADIS) \cite{Macdermaid2005ArchitectureP2.39} are two of the well-known Weather Data Integration and Assimilation (WDIA) systems.
+\acrfull{dias} \cite{Kawasaki2018DataReduction} and \acrfull{madis} \cite{Macdermaid2005ArchitectureP2.39} are two of the well-known Weather Data Integration and Assimilation (WDIA) systems.
 However, those are proprietary systems.
@@
 
-Existing WDIA systems are based on the monolithic or client service architecture; hence, cannot benefit from technologies such as cloud computing to achieve high scalability and availability.
+\gc{To address such issues, there is a parallel researches also try to implement an open-data open-model framework called as Meta Scientific Modeling (MSM).} But the existing WDIA systems and emerging systems are also based on the monolithic or client service architecture; hence, cannot benefit from technologies such as cloud computing to achieve high scalability and availability.
 Moreover, such systems cannot be updated or reconfigured without taking the system off line.
@@
 Moreover, it is desirable to support controlled data sharing with other NWMs and third-party access to enable multiple use cases.
-Furthermore, such a system should be architectured to benefit from technologies such as cloud computing and microservices.
+Furthermore, such a system should be architectured to benefit from technologies such as cloud computing, microservices, and loosely coupled containerized applications.

### 2020-12-25 introduction/sec_2-problem_and_objectives.tex
v5.2.2 Intro
Upgrade Future work
Proof read: Chapter 1

@@
 Scalability and high availability are also essential to support different use cases and mission-critical nature of applications.
-Further, users should be able to easily deploy and manage the system while benefiting from technological advances. 
+Further, users should be able to easily deploy and manage the system while benefiting from technological advancements. 
 In this context, the research problem can be stated as follows:
@@
     \item To develop an API for third-party data sharing
-    \item To perform a load test to analyse throughput, scalability of the system
+    \item To efficiently utilize cloud computing infrastructure with low-cost
 \end{itemize}

### 2020-12-25 introduction/sec_3-outline.tex
Done scan reading
Proof read: Chapter 1

@@
 \section{Outline}
-The organization of the rest of the thesis is as follows; In \cref{ch:literature} the literature review is presented.
-It discusses the existing weather data integration systems such as \acrshort{lead}, \acrshort{fews}, \acrshort{madis}, and \acrshort{dias}.
+The organization of the rest of the thesis is as follows; In \cref{ch:literature}, the literature review is presented.
+It discusses the existing weather data integration systems such as \acrshort{lead}, \acrshort{fews}, \acrshort{madis}, \acrshort{dias}, and \acrshort{msm}.
 Solution approach including the proposed system architectures and adaptation with problem occurred are presented in Chapter \ref{ch:method}.

### 2020-12-26 lit/sec_1-fews.tex
Upgrade Future work
Lit: Added MSM framework

@@
 \cref{fi:fews_schematic} shows the connection between a forecasting system to real-time data integration systems and dissemination systems.
-One of the widely practiced use cases is to use meteorological forecast data to estimate precipitation, and then use a hydrological and hydraulic model chain to predict the surface water level affected.
+\gkc{The \acrshort{fews} is capable of integrate data from different sources via import modules into the central servers, and allow forecasters to forecasting and disseminate the results into the dissemination systems.} One of the widely practiced use cases is to use meteorological forecast data to estimate precipitation, and then use a hydrological and hydraulic model chain to predict the surface water level affected.
 The hydrological and hydrodynamic models should design based on geographical surface data.
@@
 The \acrshort{fews} overcome this issue by introducing adapters for most of the commonly used data formats such as CSV, NetCDF, and JSON.
-While this enables users to import multiple data formats into the system; it also introduces adding additional complexity to the system.
+While this enables users to import multiple data formats into the system; it also introduces additional complexity to the system.
 
@@
 
-\begin{figure}[htp]
+\begin{figure}[ht]
     \centering
-    \includegraphics[width=0.9\textwidth]{lit/fews/Linking-Delft-FEWS-with-external-models-The-fi-gure-shows-the-fl-ow-of-data-through-XML_W640.png}
+    \includegraphics[width=0.99\textwidth]{lit/fews/Linking-Delft-FEWS-with-external-models-The-fi-gure-shows-the-fl-ow-of-data-through-XML_W640.png}
     \caption[\acrshort{fews} integration with external models]{Integrating \acrshort{fews} with external models \cite{Werner2013TheSystem}.}
@@
 
-In this research, we do not focus on implementing workflow management, and the user has to come up with their flow mechanism or use an existing scientific flow management system.
+In this research, we do not focus on implementing workflow management for forecasting, and the user has to come up with their flow mechanism or use an existing scientific flow management system.
 However, it is a concept that needs to be discussed and understood properly to design a data integration and assimilation system.

### 2020-12-26 lit/sec_2-lead.tex
Lit: Added MSM framework

@@
 However, during our research, we only focus on creating a framework that is extendable as a system needs more features similar to LEAD services.
+When compared to the \acrshort{fews}, the \acrshort{lead} is more dynamic and auto scaling system which is capable of using a distributed large resource pool.
+But it is a proprietary system, thus others cannot get benefit of it, and the user need to own the resource pool and manage them.
+In critical situations the system need more resource for the forecasts, and users need to pre-owned the resources to get ready for such scenarios.
+But with modern cloud computing concepts, users can lease much as resources to handle the critical situation, and release the resource after that while only paying for the utilized resource duration.

### 2020-12-26 lit/sec_3-other-systems.tex
Lit: Added MSM framework

@@
-\section{Data Integration and Assimilation Systems}
+\section{Data Integration and Analysis System}
 \label{se:dias}
@@
 Once these data integrate into useful geographic information, DIAS generates results for managing global environmental problems and natural disasters \cite{Kawasaki2018DataReduction}.
-The DIAS can assimilate weather data from multiple data sources with different data formats.
+The \acrshort{dias} can assimilate weather data from multiple data sources with different data formats.
 After successfully storing the data, it generates results which can be used for different kinds of purposes by other parties.
@@
 To store on the large volume of disk space, it converts the data via a provided set of APIs.
-The above concept is similar to Delft-FEWS's open data model approach.
+The above concept is similar to Delft-FEWS's open data model approach, but it has extra-large storage volume and a database management system which abstract for the upper layer to access the data.
 Further, the DIAS contains additional tools that provide the functionality of quality control of the data and metadata management, which is similar to some of the services in LEAD.
@@
 As shown in \cref{fi:dias_common_platform}, it offers an application layer that allows scientists to work on research tasks and to develop specific tools and applications by collaborating with IT experts \cite{Kawasaki2018DataReduction}.
-Once the data is stored on the DIAS system, it shares those data via the shared API layer and allows users to remote access to the data and easy integration via the APIs.
+Once the data is stored on the \acrshort{dias} system, it shares those data via the shared API layer and allows users to remote access to the data and easy integration via the APIs.
 
@@
 
-\acrfull{madis} \cite{Macdermaid2005ArchitectureP2.39} is a data integration and assimilation system that collects data from dozens of suppliers, then checks the quality of the data and saves it in \acrshort{netCDF} format.
+\acrfull{madis} \cite{Macdermaid2005ArchitectureP2.39} is a data integration and assimilation system as the name implies that collects data from dozens of suppliers, then checks the quality of the data and saves it in \acrshort{netCDF} format.
 Later, users can access the data with the support of the different types of data access protocols.
@@
 
-Based on the above statements, we can conclude that these kinds of functionalities are available at the modern cloud computing tools, and out of the box, those tools are providing the scalability and high availability.
+Based on the above statements, we can conclude that these kinds of functionalities are available at the modern cloud computing tools out of the box, and those tools are providing the scalability and high availability.
 Using those tools, it is possible to implement such a system with less effort and high confidence.
@@
 To address the issue, MADIS data is divided into six different versions, depending on the access level authorized by the data provider \cite{Macdermaid2005ArchitectureP2.39}.
-When compared to Delft-FEWS, MADIS provides control-based access to the data.
+When compared to Delft-FEWS, MADIS provides data assimilation with control-based access to the data.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Meta Scientific Modeling}
+\label{se:msm}
+
+Meta Scientific Modeling framework develops an open system architecture which consists of open-data concept to access heterogeneous data sources via data agents, and open-model concept to allow individual model handling via model agents.
+Even these features are provided by other systems such as Delft-FEWS, they do not provide decentralized model execution and data integration.
+Specifically, this framework provides a graphical user interface for workflow creation similar to LEAD, rather than providing a configuration-based workflow system similar to Delft-FEWS.
+During our research we are not mainly focusing on implementing a workflow engine, we will not very much look into such features here.
+Then MSM tries to effectively address the drawbacks of the existing modeling systems by providing features such as an independent open-source and graphical-based workflow engine, facilitates users to obtain data directly from popular sources, decentralized model administration by modelers, and enables models to be freely connected with each other in the MSM framework.
+
+\begin{figure}[htp]
+    \centering
+    \includegraphics[width=1\textwidth]{lit/other/msm_architecture.jpg}
+    \caption[The top-level design and overall architecture of \acrshort{msm} system]{The top-level design and overall architecture of \acrshort{msm} system \cite{Salas2020AnApplication}.}
+    \label{fi:msm_architecture}
+\end{figure}
+
+\cref{fi:msm_architecture} shows the MSM system framework from a top-level design point of view, and it mainly composed of the MSM core which is an interface with the workflow engine, data agents, and model agents.
+Thus, the MSM core can become the bottleneck of the system, and a single point of failure in critical situations.
+The MSM core also controls all other components and by using corresponding model agents and data agents allows to connect with external models and remote data sources.
+The MSM core is connected to the workflow engine and provides the end-user with all workflow control capabilities, and it contains data persistence services that can be used by all MSM components.
+Another drawback is, implementing new data agents and model agents are programming language-dependent.
+In order to implement Model Agents and Data agents, users need to inherit MSM classes in the provided language.
+Then users need to upload the code into a folder (not a containerized mechanism, or continuous service deployments).
+
+The open-data architecture of MSM is using for access multiple and heterogeneous external data sources.
+The users able to integrate data from any source via data agents, but the data agents are depending on inheriting a genric class to do so.
+Which means there is a language dependency.
+The open model architecture allow users to independently develop and deploy own model via model agents.
+Here also users have to use a genric agent provided by the MSM framework, but the models can be implemented independently.
+Users can deploy new model agents by copy pasting the source code to a specific folder, but it is possible to run the models which can be written in C, C++, Fortran, Python, Java, etc.
+During the model execution, it follow a flow similar to the Delft-FEW model adapter with prepare input file, execute the model, and processing output files.
+The MSM framework has a data management layer, which store the data as an inmemory and local data caching, featuring a non-relational database scheme that supports high throughput.
+It stores particular timeseries data as msmDataSets, and create unique identifier for each msmDataSet.
+The msmDataSets storage in framework contains the time-steps. Each time-step contains a reference to the msmDataSet it belongs to, and a Document (the data oriented structure) with a 2D image.
+
+In this paper, it present a use case of using the MSM system, and does not provide detailed evaluation regarding a performance load testing.
+In this use case, it demonstrates the usefulness and effectiveness of the framework in various aspects of scientific modeling activities.
+The msm has only been fully tested on Windows 10 operating system, which means the framework has some operating system dependency.
+Further, It is not very clear how is it parallel running data agents, model agents, and the MSM core.
+Even it mentioned it follow the decentralized agents approach, based on the available data we can conclude it also have a monolithic distributed architecture.
 
@@
 
-We presented several related works on WDIA system implementations such as \acrshort{fews}, \acrshort{lead}, \acrshort{dias}, and \acrshort{madis}.
+We presented several related works on WDIA system implementations such as \acrshort{fews}, \acrshort{lead}, \acrshort{dias}, \acrshort{madis}, and \acrshort{msm}.
 During our research, one of the significant issues that we focused on, store the data ingested from different sources with different formats efficiently.
-The Delft-FEWS and MADIS are using the netCDF as the common data format to store the data, which is one of the best solutions available with modern technologies as well.
-Even the LEAD and DIAS papers are not mentioned directly; those systems are also following a method of having common storage space to store bulk data.
-The Delft-FEWS and LEAD have the capability of handling the workflow of forecasting, but other systems are mainly focused on providing a weather data management system.
-The Delft-FEWS provides a modular approach via its general adapter, and according to the \acrshort{soa} architecture of LEAD provides the same functionality via services.
+The \acrshort{fews} and \acrshort{madis} are using the netCDF as the common data format to store the data, which is one of the best solutions available with modern technologies as well.
+Even the \acrshort{lead} and \acrshort{dias} papers are not mentioned directly; those systems are also following a method of having common storage space to store bulk data.
+The \acrshort{fews}, \acrshort{lead}, and \acrshort{msm} have the capability of handling forecasting workflow, but other systems are mainly focused on providing a weather integration and data management system.
+The \acrshort{fews} provides a modular approach via its general adapter, and according to the \acrshort{soa} architecture of \acrshort{lead} provides the same functionality via services.
 

### 2020-12-26 lit/sec_3-other-systems.tex
Revised MSM Lit

@@
 
-Meta Scientific Modeling framework develops an open system architecture which consists of open-data concept to access heterogeneous data sources via data agents, and open-model concept to allow individual model handling via model agents.
-Even these features are provided by other systems such as Delft-FEWS, they do not provide decentralized model execution and data integration.
-Specifically, this framework provides a graphical user interface for workflow creation similar to LEAD, rather than providing a configuration-based workflow system similar to Delft-FEWS.
-During our research we are not mainly focusing on implementing a workflow engine, we will not very much look into such features here.
-Then MSM tries to effectively address the drawbacks of the existing modeling systems by providing features such as an independent open-source and graphical-based workflow engine, facilitates users to obtain data directly from popular sources, decentralized model administration by modelers, and enables models to be freely connected with each other in the MSM framework.
+\acrfull{msm} framework develops an open system architecture which consists of open-data concept to access heterogeneous data sources via data agents, and open-model concept to allow individual model handling via model agents.
+Even through these features are provided by other systems such as \acrshort{fews}, they do not provide decentralized model execution and data integration.
+Specifically, this framework provides a graphical user interface for workflow creation similar to \acrshort{lead}, rather than providing a configuration-based workflow system as in \acrshort{fews}.
+In our research, we are not mainly focusing on implementing a workflow engine, we will not look deep into such features here.
+Then \acrshort{msm} tries to effectively address the drawbacks of the existing modeling systems by providing features such as an independent open-source and graphical-based workflow engine, facilitating  users to obtain data directly from popular sources, decentralized model administration by modelers, and enables models to be freely connected with each other in the \acrshort{msm} framework.
 
@@
 
-\cref{fi:msm_architecture} shows the MSM system framework from a top-level design point of view, and it mainly composed of the MSM core which is an interface with the workflow engine, data agents, and model agents.
-Thus, the MSM core can become the bottleneck of the system, and a single point of failure in critical situations.
-The MSM core also controls all other components and by using corresponding model agents and data agents allows to connect with external models and remote data sources.
-The MSM core is connected to the workflow engine and provides the end-user with all workflow control capabilities, and it contains data persistence services that can be used by all MSM components.
+\cref{fi:msm_architecture} shows the \acrshort{msm} system framework from a top-level design point of view, and it is mainly composed of the \acrshort{msm} core which is an interface with the workflow engine, data agents, and model agents.
+Thus, the \acrshort{msm} core can become the bottleneck of the system, and a single point of failure in critical situations.
+The \acrshort{msm} core also controls all other components and by using corresponding model agents and data agents allows it to connect with external models and remote data sources.
+The \acrshort{msm} core is connected to the workflow engine and provides the end-user with all workflow control capabilities, and it contains data persistence services that can be used by all \acrshort{msm} components.
 Another drawback is, implementing new data agents and model agents are programming language-dependent.
-In order to implement Model Agents and Data agents, users need to inherit MSM classes in the provided language.
+In order to implement Model Agents and Data agents, users need to inherit \acrshort{msm} classes in the provided language.
 Then users need to upload the code into a folder (not a containerized mechanism, or continuous service deployments).
 
-The open-data architecture of MSM is using for access multiple and heterogeneous external data sources.
-The users able to integrate data from any source via data agents, but the data agents are depending on inheriting a genric class to do so.
+The open-data architecture of \acrshort{msm} is using to access multiple and heterogeneous external data sources.
+The users are able to integrate data from any source via data agents, but the data agents are depending on inheriting a generic class to do so.
 Which means there is a language dependency.
-The open model architecture allow users to independently develop and deploy own model via model agents.
-Here also users have to use a genric agent provided by the MSM framework, but the models can be implemented independently.
-Users can deploy new model agents by copy pasting the source code to a specific folder, but it is possible to run the models which can be written in C, C++, Fortran, Python, Java, etc.
-During the model execution, it follow a flow similar to the Delft-FEW model adapter with prepare input file, execute the model, and processing output files.
-The MSM framework has a data management layer, which store the data as an inmemory and local data caching, featuring a non-relational database scheme that supports high throughput.
-It stores particular timeseries data as msmDataSets, and create unique identifier for each msmDataSet.
-The msmDataSets storage in framework contains the time-steps. Each time-step contains a reference to the msmDataSet it belongs to, and a Document (the data oriented structure) with a 2D image.
+The open model architecture allows users to independently develop and deploy their own model via model agents.
+Here also users have to use a generic agent provided by the \acrshort{msm} framework, but the models can be implemented independently.
+Users can deploy new model agents by copy pasting the source code to a specific folder, but it is possible to run the models which can be written in C, C++, FORTRAN, Python, Java, etc.
+During the model execution, it follows a flow similar to the Delft-FEW model adapter with a prepared input file, execute the model, and processing output files.
+The \acrshort{msm} framework has a data management layer, which stores the data as an in memory and local data caching, featuring a non-relational database scheme that supports high throughput.
+It stores particular timeseries data as msmDataSets, and creates a unique identifier for each msmDataSet.
+The msmDataSets storage framework contains the time-steps. Each time-step contains a reference to the msmDataSet it belongs to, and a Document (the data oriented structure) with a 2D image.
 
-In this paper, it present a use case of using the MSM system, and does not provide detailed evaluation regarding a performance load testing.
+In this paper, it presents a use case of using the \acrshort{msm} system, and does not provide detailed evaluation regarding a performance load testing.
 In this use case, it demonstrates the usefulness and effectiveness of the framework in various aspects of scientific modeling activities.
 The msm has only been fully tested on Windows 10 operating system, which means the framework has some operating system dependency.
-Further, It is not very clear how is it parallel running data agents, model agents, and the MSM core.
-Even it mentioned it follow the decentralized agents approach, based on the available data we can conclude it also have a monolithic distributed architecture.
+Further, It is not very clear how is it parallel running data agents, model agents, and the \acrshort{msm} core are.
+Even though it mentioned it follows the decentralized agents approach, based on the available data we can conclude it also has a monolithic distributed architecture.
 

### 2020-12-30 lit/sec_3-other-systems.tex
Chap 5: Added discussion paragraph regarding existing systems vs WDIAS

@@
 
-\acrfull{msm} framework develops an open system architecture which consists of open-data concept to access heterogeneous data sources via data agents, and open-model concept to allow individual model handling via model agents.
+\gc{\acrfull{msm} framework develops an open system architecture which consists of open-data concept to access heterogeneous data sources via data agents, and open-model concept to allow individual model handling via model agents.
 Even through these features are provided by other systems such as \acrshort{fews}, they do not provide decentralized model execution and data integration.
@@
 In our research, we are not mainly focusing on implementing a workflow engine, we will not look deep into such features here.
-Then \acrshort{msm} tries to effectively address the drawbacks of the existing modeling systems by providing features such as an independent open-source and graphical-based workflow engine, facilitating  users to obtain data directly from popular sources, decentralized model administration by modelers, and enables models to be freely connected with each other in the \acrshort{msm} framework.
+Then \acrshort{msm} tries to effectively address the drawbacks of the existing modeling systems by providing features such as an independent open-source and graphical-based workflow engine, facilitating  users to obtain data directly from popular sources, decentralized model administration by modelers, and enables models to be freely connected with each other in the \acrshort{msm} framework.}
 
@@
 
-\cref{fi:msm_architecture} shows the \acrshort{msm} system framework from a top-level design point of view, and it is mainly composed of the \acrshort{msm} core which is an interface with the workflow engine, data agents, and model agents.
+\gc{\cref{fi:msm_architecture} shows the \acrshort{msm} system framework from a top-level design point of view, and it is mainly composed of the \acrshort{msm} core which is an interface with the workflow engine, data agents, and model agents.
 Thus, the \acrshort{msm} core can become the bottleneck of the system, and a single point of failure in critical situations.
@@
 In order to implement Model Agents and Data agents, users need to inherit \acrshort{msm} classes in the provided language.
-Then users need to upload the code into a folder (not a containerized mechanism, or continuous service deployments).
+Then users need to upload the code into a folder (not a containerized mechanism, or continuous service deployments).}
 
-The open-data architecture of \acrshort{msm} is using to access multiple and heterogeneous external data sources.
+\gc{The open-data architecture of \acrshort{msm} is using to access multiple and heterogeneous external data sources.
 The users are able to integrate data from any source via data agents, but the data agents are depending on inheriting a generic class to do so.
@@
 It stores particular timeseries data as msmDataSets, and creates a unique identifier for each msmDataSet.
-The msmDataSets storage framework contains the time-steps. Each time-step contains a reference to the msmDataSet it belongs to, and a Document (the data oriented structure) with a 2D image.
+The msmDataSets storage framework contains the time-steps. Each time-step contains a reference to the msmDataSet it belongs to, and a Document (the data oriented structure) with a 2D image.}
 
-In this paper, it presents a use case of using the \acrshort{msm} system, and does not provide detailed evaluation regarding a performance load testing.
+\gc{In this paper, it presents a use case of using the \acrshort{msm} system, and does not provide detailed evaluation regarding a performance load testing.
 In this use case, it demonstrates the usefulness and effectiveness of the framework in various aspects of scientific modeling activities.
@@
 Further, It is not very clear how is it parallel running data agents, model agents, and the \acrshort{msm} core are.
-Even though it mentioned it follows the decentralized agents approach, based on the available data we can conclude it also has a monolithic distributed architecture.
+Even though it mentioned it follows the decentralized agents approach, based on the available data we can conclude it also has a monolithic distributed architecture.}
 

### 2020-12-30 method/sec_5-data_preprocess.tex
Chap 5: Added discussion paragraph regarding existing systems vs WDIAS

@@
 Thus, users can change the behavior of an existing function by providing different bind constants at the time of creating new triggers for an extension and produce different behaviors.
+\gkc{Next, we explain how can we derive interpolation, transformation, and validation by using the generic mathematical function model that we described above.}
 
 \subsection{Interpolation}
-The interpolation module generates data at desired locations or desired data points using a serial or spatial interpolation technique.
-It is used to fill gaps in on-line measured data and to derive spatially distributed data for weather timeseries, such as precipitation and temperature, based on information available at nearby locations.
+\gkc{The interpolation extension generates data at desired locations or desired data points using a serial or spatial interpolation technique.
+It is used to fill gaps in linear measured data and to derive spatially distributed data for weather timeseries, such as precipitation and temperature, based on information available at nearby locations.
+Here, we will discuss two types of interpolation such as serial interpolation and spatial interpolation below.}
 
 \subsubsection{Serial Interpolation}
-During serial interpolation, we use interpolation to fill any gaps in a timeseries. The interpolation module will only consider a single timeseries, which is itself in filling these gaps.
+\gkc{During serial interpolation, we use interpolation to fill any gaps in a linear timeseries.
+The interpolation module will only consider a single timeseries, which is itself filling the missing data points.
+As an example, there can be timeseries which has the data points of temperature which are collected using a weather station.
+There can be missing data in this timeseries, and we can use a simple linear interpolation algorithm to fill the missing values based on the existing data points.}
 
@@
 \subsubsection{Spatial Interpolation}
-During spatial interpolation, we use interpolation to either fill gaps in timeseries or to create a new timeseries for a location using data from other (spatially distributed) locations.
+\gkc{During spatial interpolation, we use interpolation to either fill gaps in timeseries or to create a new timeseries for a location using data from other (spatially distributed) locations' timeseries.
 Spatial interpolation can also be applied for sampling scalar timeseries from grid timeseries, for re-sampling grids, or for creating grids from timeseries data.
+As an example, let’s assume that there are precipitation timeseries data available for the location A and location B as shown in Figure x.
+Then we want to calculate the mean precipitation of nearby location using these two timeseries.
+We can use the spatial interpolation to get the mean precipitation of nearby location.}
 \begin{figure}[htp]
@@
 \subsection{Transformation}
-Simple arithmetic manipulation of time interval transformation and shifting the series in time specific hydro-meteorological transformation such as stage discharge relationships.
+\gkc{Simple arithmetic manipulation of time interval transformation and shifting the series in time-specific hydro-meteorological transformation such as stage-discharge relationships.
+As an example, there can be a timeseries of precipitation with 1-minute sample data.
+There will be a model requirement that needs hourly data.
+So, we need to do accumulation data manipulation to create a timeseries of hourly data using 1-minute sample data.}
 \begin{figure}[htp]
@@
     \includegraphics[width=1.0\textwidth]{method/data_preprocess/transformation.pdf}
-    \caption{Time interval aggregration.}
+    \caption{Time interval aggregation.}
     \label{fi:transformation}
@@
 \subsection{Validation}
-Checks for counting reliable, doubtful, unreliable, and missing values.
+\gkc{Checks for counting reliable, doubtful, unreliable, and missing values.
+The weather stations can produce invalid observations due to technical errors in the sensors of the devices.
+If we feed those values directly to the models, the models will produce inaccurate forecasting.
+To avoid that, we need to modify or flag those values before feeding them to the numerical models.
+We can use validation extensions to modify or flag invalid data.
+As an example, a weather station can record temperature above 70 celsius due to sensor error or calibration issues.
+But in real-world, it is not possible to have such a temperature in nature.
+Thus we need to flag such temperature issues and need to repair the weather station as soon as possible.}
 \begin{figure}[htp]

### 2020-12-30 method/sec_6-query.tex
Chap 5: Added discussion paragraph regarding existing systems vs WDIAS

@@
 
-The system provides timeseries metadata query endpoints to search for existing timeseries metadata within the system using primary key attributes.
+The system provides timeseries metadata query endpoints to search for existing timeseries metadata within the system using primary key attributes mentioned in the \cref{subse:timeseries_key_attributes}.
 Also, it provides a set of geo-query endpoints, and users can perform geo-search queries with sending geo-information in geoJson format.
@@
 \begin{itemize}
-    \item Query locations within area
-    \item Query parameters in locations
-    \item Query timeseries by location
-    \item Query timeseries by locations
-    \item Query timeseries by Parameter
-    \item Query timeseries in area
-    \item Query timeseries in area by parameter
-    \item Query all timeseries
+    \item Search for available locations within the provided geoJson area in the query.
+    \item Search for available parameters in provided locations in the query.
+    \item Search for available timeseries for a provided location in the query.
+    \item Search for available timeseries for the given locations in the query.
+    \item Search for available timeseries for given parameter. E.g., get available waterlevel timeseries in the system.
+    \item Search for available timeseries within the provided geoJson area in the query.
+    \item Search for available timeseries within the provided geoJson area by parameter. E.g., get available waterlevel timeseries within a given area.
+    \item Query for all timeseries in the system.
 \end{itemize}

### 2020-12-30 summary/sec_1-conclusions.tex
Upgrade Future work
Chap 5: Added discussion paragraph regarding existing systems vs WDIAS

@@
 Even though there are many weather data integration systems, most of them are proprietary or closed source.
-Thus, for an island like Sri Lanka that has different kinds of weather seasons yearly, those software needs to be highly customized
+Thus, for an island like Sri Lanka that has different kinds of weather seasons yearly, those software needs to be highly customize.
 
@@
 We mapped each microservice of \acrshort{wdias} to a pod in the \acrshort{k8s} cluster.
-Also, each microservice exposed endpoints to the users which are only focus on supporting a specific operation or functionality which follows the concept of smart endpoints dumb pipes in \cref{subse:dumb_pipes}.
+Also, each microservice exposed endpoints to the users which are only focus on supporting a specific operation or functionality which follows the concept of smart endpoints dumb pipes.
 For importing different format data into the system, we added microservice for each data format that known as import microservices.
@@
 Also, the system provides asynchronous request handling based on the request size with maintaining status per request.
+
+\gc{When compared to other existing weather data integration and assimilation systems, the WDIAS has the advantage of taking full advantage of modern cloud computing technologies to implement a highly scalable and high-available system with low-cost.
+Since it uses containerized applications to implement the microservices, it allows independent service deployments.
+Each microservice can scale independently without affecting other microservices, and capable of using suitable technology stack for the task.
+The \acrshort{fews}, \acrshort{madis} and \acrshort{\acrshort{msm}} have platform dependencies, and some of the deployments are done with copy-pasting source codes.
+The \acrshort{fews} and \acrshort{msm} provide centralized data storage mechanism which can become a bottleneck while processing a huge set of data in critical situations.
+The \acrshort{madis} and \acrshort{dias} also support data storage array to store data.
+The WDIAS and \acrshort{lead} can support a pool of resources based on the requirement.
+Similar to other systems, WDIAS provides the data preprocessing capabilities, and users can integrate new data preprocessing capabilities by implementing as independent containerized microservice applications.
+Even though \acrshort{fews}, \acrshort{lead} and \acrshort{msm} provide workflow engine support and model execution support, these can be achieved using an external workflow management system by fulfilling the data requirements via WDIAS system.
+Further, WDIAS is an extendable open framework such that similar capabilities can be integrated as a new extension module system.
+Compared to other existing systems, the \acrshort{lead} is more scalable which is implemented using \acrshort{soa} architecture as a result of contributions of lots of research from multiple universities.
+But with the help of modern container orchestration frameworks such as Kubernetes and cloud computing technologies, those are able to provide high scalability and high availability as inherent capabilities.
+And those are mature enough to automatically provide fault-tolerance \cite{Scolati2019ADevices}.
+By implementing the deployment units as containerized applications based on the modern architecture patterns allow WDIAS to implement a highly scalable and high available system without heavy effort on those features.}
 

### 2020-12-31 method/sec_1-architectural_decisions.tex
Chap 5: Added discussion paragraph regarding existing systems vs WDIAS
Added feature comparison of the systems

@@
 It preserves the independent nature of the microservices and supports the high scalability of the system.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Architecture Comparison with Existing Systems
+
+\begin{figure}[htp]
+    \centering
+    \includegraphics[width=1.05\textwidth]{method/misc/architecture_comparison_pros_cons.pdf}
+    \caption{Comparison of available features among existing weather data assimilation and integration systems and \acrshort{wdias}.
+An "X" in the table represents a feature offered by the corresponding tool.
+An "-" in the table represents that information available are not enough to make an statement, and empty presents a feature is not offered.
+}
+    \label{fi:architecture_comparison}
+\end{figure}
+
+\gc{\cref{fi:architecture_comparison} shows a summarized architecture comparison between existing systems that we discussed in the WDIAS.
+Here, we analyze the systems under a few categories such as data resources of the system, performance, architecture of the system, and other available main features.
+The fews and msm frameworks store the data through a central data service which can be a bottleneck handling large amounts of data in a critical situation.
+Other systems are capable of using a resource pool which allows them to grow the performance while adding more resources to the system.
+Regarding the performance of the systems, we consider scalability, availability, cloud computing support, and system deployment capabilities.
+All of the systems are capable of scaling up to some extent by adding resources beforehand or in real time.
+But the LEAD, DIAS and WDIAS are capable of scaling on demand by adding more resources, and also support auto scaling up and scaling down.
+The LEAD, MADIS, DIAS and WDIAS able to provide availability, since those were able to run using a resource pool which can run on different locations, and systems are capable of automatically handling partial system failures, hence supporting fault tolerance.
+When we discuss about the modern cloud computing support, the system should support easy integration with clouds.
+It is possible to rent virtual servers and deploy the local services in the cloud infrastructure, but some systems may not allow access to them remotely.
+Even some systems able to deploy in such manner, they may not be capable of automatically resource allocation on demand.
+Hence, we can not consider that those systems are full cloud infrastructures.
+Furthermore, we can easily maintain a system if it consists of independent subsystems, and each subsystem is capable of deploying or upgrading independently.
+Independent service deployment is a more flexible and better way to handle this, rather than copy pasting codes in order to deploy changes.}
+
+\gc{We discuss the architecture of the systems in their pattern, dependencies of the subsystems, extendable with adding more features easily, source code availability, and data preprocessing capabilities specific to the weather domain.
+While other existing systems are using distributed client server architecture or monolithic distributed architecture, LEAD is using the SOA architecture, but WDIAS has the more advantage of using modern cloud computing technologies with implementing microservices as containerized applications.
+The architecture implementation of independent subsystems allow users to maintain subsystems independently.
+Further, WDIAS allow to use own technology stack for each subsystem with using different programming languages.
+Specially the WDIAS and MSM provide open source framework which gives the capability for users to enhance or modify the system as per the requirement.
+All of these systems provide data preprocessing capabilities for weather data, and adding new preprocessing capabilities.
+But WDIAS is capable of providing auto scaling with data preprocessing as well.
+Workflow engine and model execution support are some other extra features that are helpful with weather forecasting.
+But the WDIAS focus is about implementing a WDIA system with supporting main features, and it provides an extendable open framework to integrate such features easily.}

### 2020-12-31 summary/sec_1-conclusions.tex
Added feature comparison of the systems

@@
 Each microservice can scale independently without affecting other microservices, and capable of using suitable technology stack for the task.
-The \acrshort{fews}, \acrshort{madis} and \acrshort{\acrshort{msm}} have platform dependencies, and some of the deployments are done with copy-pasting source codes.
+The \acrshort{fews}, \acrshort{madis} and \acrshort{msm} have platform dependencies, and some of the deployments are done with copy-pasting source codes.
 The \acrshort{fews} and \acrshort{msm} provide centralized data storage mechanism which can become a bottleneck while processing a huge set of data in critical situations.

### 2021-01-01 Thesis.tex
Added feature comparison of the systems
After Dr. Dilum reviewed the Viva thesis

@@
 \usepackage{tabulary}
+\usepackage{multirow}
 \usepackage[style=ieee]{biblatex}
@@
         \vspace{32pt}
-        August 2020
+        January 2021
 
@@
 
-\acrfull{nwm} utilize data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images.
-Before using such multimodal data in a \acrshort{nwm}, it is necessary to transcode data into a format that can be ingested by the \acrshort{nwm}.
-Moreover, the data integration system's response time needs to be relatively low to forecast and monitor time-sensitive weather events like hurricanes, storms, and flash floods that require rapid and frequent execution of \acrshort{nwm}.
+\acrfull{nwms} utilize data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images.
+Before using such multimodal data in a \acrshort{nwm}, it is necessary to transcode data into a format  %that can be
+ingested by the \acrshort{nwm}.
+Moreover, the data integration system's response time needs to be relatively low to forecast and monitor time-sensitive weather events like hurricanes, storms, and flash floods that require rapid and frequent execution of \acrshort{nwms}.
 The resulting weather data also need to be accessed by many researchers and third-party applications such as logistic and agricultural insurance firms.
 Existing weather data integration systems are based on monolithic or client-server architectures; hence, unable to benefit from novel computational models such as cloud computing and containerized applications.
-Moreover, most of these software are proprietary or closed-source, making it difficult to customize them for an island like Sri Lanka with different weather seasons.
-Therefore, in this research, we propose \acrfull{wdias} that utilizes modern architectural patterns such as microservices to achieve scalability, high availability, and low-cost operation based on cloud computing.
+Moreover, most of these softwares are proprietary or closed-source, making it difficult to customize them for an island like Sri Lanka with different weather seasons.
+Therefore, in this research, we propose \acrfull{wdias} that utilizes %modern architectural patterns such as 
+microservices to achieve scalability, high availability, and low-cost operation based on cloud computing.
 The use of stateless microservices also enables \acrshort{wdias} to add new features on the fly with rollover capabilities.
 Moreover, \acrshort{wdias} provides a modular framework to integrate data from different sources, export into different formats, and add new functionality by adding extension modules.
-We demonstrate the utility of \acrshort{wdias} using cloud-based experimental setup and weather-related synthetic workloads.
+We demonstrate the utility of \acrshort{wdias} using a cloud-based experimental setup and weather-related synthetic workloads.
 

### 2021-01-01 introduction/sec_1-motivation.tex
After Dr. Dilum reviewed the Viva thesis

@@
 Weather forecast is essential to reduce the impact caused by natural disasters and to effectively manage natural resources like water.
-The weather forecasts are performed using \acrfull{nwm} that use a set of configuration parameters and the current status of the environment such as temperature, rainfall, and wind direction as the inputs.
+The weather forecasts are performed using \acrfull{nwms} that use a set of configuration parameters and the current status of the environment such as temperature, rainfall, and wind direction as the inputs.
 For example, the \acrfull{wrf} \cite{MesoscaleMicroscaleMeteorologyLaboratoryWeatherModel} model is used to predict the rainfall, temperature, and wind direction.
-Typically multiple \acrshort{nwm} are executed on the same data with different configuration parameters.
+Typically multiple \acrshort{nwms} are executed on the same data with different configuration parameters.
 Then using the real-time observations, the most fitting model is selected.
@@
 \acrfull{curw} \cite{CUrWSL2017Lanka} is tasked with the mission to reduce water-related natural disasters in Sri Lanka. 
-\acrshort{curw} \cite{CUrWSLObservedSL} is implementing own system with the idea of long-term maintainability rather than depending on existing weather data integration systems.
-\gkc{Because of existing weather systems are not open source to configure as required, and not flexible enough to change without much help from the maintainers.} \acrshort{curw} collects real-time data from weather stations and other relevant entities and generates daily forecasts.
+However, as the existing weather data integration systems are not open source and not flexible enough to change without much help from the maintainers, the \acrshort{curw} \cite{CUrWSLObservedSL} is implementing own system with the idea of long-term maintainability.
+%\acrshort{curw} \cite{CUrWSLObservedSL} is implementing own system with the idea of long-term maintainability rather than depending on existing weather data integration systems.
+\gkc{Because of existing weather systems are not open source to configure as required, and not flexible enough to change without much help from the maintainers.}
+\acrshort{curw} collects real-time data from weather stations and other relevant entities and generates daily forecasts.
 Then the generated results are shared with relevant public departments responsible for disaster planning, risks mitigation, and disaster management.
@@
 For example, \acrshort{fews} does not support FLO2D model integration, which is used by \acrshort{curw} to forecast water level.
-
-\gc{To address such issues, there is a parallel researches also try to implement an open-data open-model framework called as Meta Scientific Modeling (MSM).} But the existing WDIA systems and emerging systems are also based on the monolithic or client service architecture; hence, cannot benefit from technologies such as cloud computing to achieve high scalability and availability.
+To address such issues, there is also an initiative to implement an open-data open-model framework called Meta Scientific Modeling (MSM). 
+But the existing WDIA systems and emerging systems are also based on the monolithic or client service architecture; hence, cannot benefit from technologies such as cloud computing to achieve high scalability and availability.
 Moreover, such systems cannot be updated or reconfigured without taking the system off line.

### 2021-01-01 lit/sec_1-fews.tex
After Dr. Dilum reviewed the Viva thesis

@@
 \cref{fi:fews_schematic} shows the connection between a forecasting system to real-time data integration systems and dissemination systems.
-\gkc{The \acrshort{fews} is capable of integrate data from different sources via import modules into the central servers, and allow forecasters to forecasting and disseminate the results into the dissemination systems.} One of the widely practiced use cases is to use meteorological forecast data to estimate precipitation, and then use a hydrological and hydraulic model chain to predict the surface water level affected.
+The \acrshort{fews} can integrate data from different sources via import modules into the central servers, and allow forecasters to forecast and disseminate the results into the dissemination systems.
+One of the widely practiced use cases is to use meteorological forecast data to estimate precipitation, and then use a hydrological and hydraulic model chain to predict the surface water level affected.
 The hydrological and hydrodynamic models should design based on geographical surface data.

### 2021-01-01 lit/sec_3-other-systems.tex
After Dr. Dilum reviewed the Viva thesis

--- 2020-12-26 lit/sec_3-other-systems.tex
@@
 
-\acrfull{msm} framework develops an open system architecture which consists of open-data concept to access heterogeneous data sources via data agents, and open-model concept to allow individual model handling via model agents.
-Even through these features are provided by other systems such as \acrshort{fews}, they do not provide decentralized model execution and data integration.
+\acrfull{msm} framework developed an open system architecture that consists of open-data concept to access heterogeneous data sources via data agents, and open-model concept to allow management of individual model via model agents.
+Even though other systems like \acrshort{fews} provide these features, they do not provide decentralized model execution and data integration.
 Specifically, this framework provides a graphical user interface for workflow creation similar to \acrshort{lead}, rather than providing a configuration-based workflow system as in \acrshort{fews}.
-In our research, we are not mainly focusing on implementing a workflow engine, we will not look deep into such features here.
-Then \acrshort{msm} tries to effectively address the drawbacks of the existing modeling systems by providing features such as an independent open-source and graphical-based workflow engine, facilitating  users to obtain data directly from popular sources, decentralized model administration by modelers, and enables models to be freely connected with each other in the \acrshort{msm} framework.
+\acrshort{msm} tries to effectively address the drawbacks of the existing modeling systems by providing features such as an independent open-source and graphical-based workflow engine, facilitating  users to obtain data directly from popular sources, decentralized model administration by modelers, and enables models to be freely connected with each other in the \acrshort{msm} framework.
+However, in our research, we focus on data ingress and egress aspects than the workflow engine.
+
+\cref{fi:msm_architecture} shows the \acrshort{msm} framework from a top-level design point of view, and it is mainly composed of the \acrshort{msm} core which is an interface with the workflow engine, data agents, and model agents.
+Thus, the \acrshort{msm} core can lead to a bottleneck and a single point of failure in critical situations.
+The \acrshort{msm} core also controls all other components, and by using corresponding model agents and data agents allows it to connect with external models and remote data sources.
+The \acrshort{msm} core is connected to the workflow engine and provides the end-user with all workflow control capabilities, and it contains data persistence services that can be used by all \acrshort{msm} components.
+Another drawback is, implementing new data agents and model agents are programming language dependent.
+To implement model and data agents, users need to inherit \acrshort{msm} classes in the provided language.
+Then the users need to upload the code into a folder (not a containerized mechanism, or continuous service deployments).
 
@@
 
-\cref{fi:msm_architecture} shows the \acrshort{msm} system framework from a top-level design point of view, and it is mainly composed of the \acrshort{msm} core which is an interface with the workflow engine, data agents, and model agents.
-Thus, the \acrshort{msm} core can become the bottleneck of the system, and a single point of failure in critical situations.
-The \acrshort{msm} core also controls all other components and by using corresponding model agents and data agents allows it to connect with external models and remote data sources.
-The \acrshort{msm} core is connected to the workflow engine and provides the end-user with all workflow control capabilities, and it contains data persistence services that can be used by all \acrshort{msm} components.
-Another drawback is, implementing new data agents and model agents are programming language-dependent.
-In order to implement Model Agents and Data agents, users need to inherit \acrshort{msm} classes in the provided language.
-Then users need to upload the code into a folder (not a containerized mechanism, or continuous service deployments).
-
-The open-data architecture of \acrshort{msm} is using to access multiple and heterogeneous external data sources.
+The open-data architecture of \acrshort{msm} is used to access multiple and heterogeneous external data sources.
 The users are able to integrate data from any source via data agents, but the data agents are depending on inheriting a generic class to do so.
 Which means there is a language dependency.
-The open model architecture allows users to independently develop and deploy their own model via model agents.
-Here also users have to use a generic agent provided by the \acrshort{msm} framework, but the models can be implemented independently.
-Users can deploy new model agents by copy pasting the source code to a specific folder, but it is possible to run the models which can be written in C, C++, FORTRAN, Python, Java, etc.
-During the model execution, it follows a flow similar to the Delft-FEW model adapter with a prepared input file, execute the model, and processing output files.
-The \acrshort{msm} framework has a data management layer, which stores the data as an in memory and local data caching, featuring a non-relational database scheme that supports high throughput.
+The open model architecture allows users to develop and deploy their own model via model agents.
+Here users also have to use a generic agent provided by the \acrshort{msm} framework, but the models can be implemented independently.
+Users can deploy new model agents by copy-pasting the source code to a specific folder, but it is possible to run the models written in languages such as C, C++, FORTRAN, Python, and Java.
+The model execution follows a flow similar to the \acrshort{fews} model adapter with a prepared input file, execute the model, and processing output files.
+The \acrshort{msm} framework has a data management layer that stores the data as an in memory and local data caching, featuring a non-relational database scheme that supports high throughput.
 It stores particular timeseries data as msmDataSets, and creates a unique identifier for each msmDataSet.
-The msmDataSets storage framework contains the time-steps. Each time-step contains a reference to the msmDataSet it belongs to, and a Document (the data oriented structure) with a 2D image.
+The msmDataSets storage framework contains the time-steps.
+Each time-step contains a reference to the msmDataSet it belongs to, and a document (the data-oriented structure) with a 2D image.
 
-In this paper, it presents a use case of using the \acrshort{msm} system, and does not provide detailed evaluation regarding a performance load testing.
-In this use case, it demonstrates the usefulness and effectiveness of the framework in various aspects of scientific modeling activities.
-The msm has only been fully tested on Windows 10 operating system, which means the framework has some operating system dependency.
-Further, It is not very clear how is it parallel running data agents, model agents, and the \acrshort{msm} core are.
-Even though it mentioned it follows the decentralized agents approach, based on the available data we can conclude it also has a monolithic distributed architecture.
+While the authors presented a use case of using the \acrshort{msm} system, detailed evaluation regarding its performance was not given.
+Nevertheless, it demonstrates the usefulness and effectiveness of the framework in various aspects of scientific modeling activities.
+The \acrshort{msm} has only been fully tested on Windows 10 operating system, which means the framework has some operating system dependency.
+Further, details on how it parallellize data agents, model agents, and the \acrshort{msm} core are not presented.
+Even though the authors mentioned that \acrshort{msm} follows a decentralized agents approach, it seems to have a monolithic distributed architecture based on the available data.
 

### 2021-01-01 method/sec_0_introduction.tex
After Dr. Dilum reviewed the Viva thesis

@@
 \cref{se:architectural_decisions} shows how the architectural design of the proposed solution evolved while designing and implementing \acrshort{wdias}.
-\cref{se:microservice} presents microservice architectural concepts followed while developing the \acrshort{wdias}.
+\cref{se:microservice} presents microservice architectural concepts followed while developing \acrshort{wdias}.
 Then the reasons behind developing \acrshort{wdias} database structure and technologies used are discussed in  \cref{se:db_struct}.
 \cref{se:data_preprocess} discusses how \acrshort{wdias} enables data preprocessing and adding capabilities using extensions.
-Finally, \cref{se:query} includes details on how to perform timeseries search and geo-based queries on the \acrshort{wdias}.
+Finally, \cref{se:query} includes details on how to perform timeseries search and geo-based queries on \acrshort{wdias}.
 

### 2021-01-01 method/sec_1-architectural_decisions.tex
After Dr. Dilum reviewed the Viva thesis

--- 2020-12-22 method/sec_1-architectural_decisions.tex
@@
 
-The \acrshort{wdias} used \acrfull{k8s} as the container orchestration system.
+\acrshort{wdias} used \acrfull{k8s} as the container orchestration system.
 \acrshort{k8s} is an open-source tool for automating deployment, scaling, and management of containerized applications [15].
@@
 It preserves the independent nature of the microservices and supports the high scalability of the system.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Architecture Comparison with Existing Systems
+
+\cref{fi:architecture_comparison} shows a comparison between existing systems and WDIAS concerning software architectural aspects.
+Here, we compare systems under categories such as data storage, performance, architecture, and other features.
+The \acrshort{fews} and \acrshort{msm} frameworks store the data on a central data service, which could become a bottleneck while handling large volumes of data in a critical situation.
+Other systems can use a pool of resources allowing them to increase the performance by adding more resources to the system.
+Regarding the performance of the systems, we consider scalability, availability, cloud computing support, and system deployment capabilities.
+All the systems can scale up to some extent by adding resources beforehand or in real-time.
+However, LEAD, DIAS, and WDIAS could scale on-demand by adding more resources and support automatic elasticity (i.e., scaling up and down).
+LEAD, MADIS, DIAS, and WDIAS have high availability, as they use a resource pool that can run on different locations.
+Further, these systems are capable of automatically handling partial system failures enabling fault tolerance.
+When we consider cloud computing support, the system should support easy integration with clouds.
+It is possible to rent virtual servers and deploy the local services in the cloud infrastructure, but some systems may not allow access to them remotely.
+Even though some systems can deploy in such a manner, they may not be capable of automatically allocating resources on demand.
+Hence, we cannot consider that those systems can utilize cloud infrastructures fully.
+Furthermore, we can easily maintain a system if it consists of independent subsystems, and each subsystem is capable of deploying or upgrading independently.
+Independent service deployment is a more flexible and better way to handle this, rather than copy-pasting codes to deploy changes.
+
+\begin{figure}[htp]
+    \centering
+    \includegraphics[width=1.05\textwidth]{method/misc/architecture_comparison_pros_cons.pdf}
+    \caption{Comparison of features among existing weather data assimilation and integration systems and \acrshort{wdias}.
+%An "X" in the table represents a feature offered by the corresponding tool.
+An "-" in the table represents that information available are not enough to make an statement, and empty presents a feature is not offered.
+    }
+    \label{fi:architecture_comparison}
+\end{figure}
+
+We discuss the architecture of the systems in terms of their design, dependencies of the subsystems, extensibility, availability of source code, and data preprocessing capabilities specific to the weather domain.
+While other existing systems use distributed client-server architecture or monolithic distributed architecture, LEAD uses the SOA architecture.
+However, WDIAS has the advantage of using modern cloud computing technologies to implement microservices as containerized applications.
+The architecture implementation of independent subsystems allows users to maintain subsystems independently.
+Further, WDIAS enables different subsystems to be implemented using different technology stacks.
+Specially WDIAS and MSM provide an open-source framework that gives users the capability to enhance or modify the system as per the requirement.
+These systems provide data preprocessing capabilities for weather data and the ability to add new preprocessing capabilities.
+However, WDIAS is also capable of providing auto-scaling with data preprocessing.
+Workflow engine and model execution support are some other extra features that are helpful with weather forecasting.
+However, the WDIAS focuses on implementing a WDIA system with supporting main features, and it provides an extendable open framework to integrate such features easily.

### 2021-01-01 method/sec_3-microservice.tex
After Dr. Dilum reviewed the Viva thesis

@@
 Figures \ref{fi:wdias_micro_on_demand} and \ref{fi:wdias_micro_async} show the system interaction of the WDIA microservices architecture while handling requests.
-Each circle in the figures represents a microservice in the \acrshort{wdias}, and each microservice is implemented as a containerized application.
-The left side of \cref{fi:wdias_micro_on_demand} shows the import modules of the \acrshort{wdias}, and the right side shows the export modules.
+Each circle in the figures represents a microservice in \acrshort{wdias}, and each microservice is implemented as a containerized application.
+The left side of \cref{fi:wdias_micro_on_demand} shows the import modules of \acrshort{wdias}, and the right side shows the export modules.
 Also, we implemented each module as a microservice to independent maintainability and upgradability.
@@
 
-\cref{fi:wdias_micro_separation} shows the clear separation of microservices into the modules of the \acrshort{wdias}.
+\cref{fi:wdias_micro_separation} shows the clear separation of microservices into the modules of \acrshort{wdias}.
 Each adapter has a separate database, and the database is hosted separately for the high performance and to avoid interference.

### 2021-01-01 method/sec_4-db_struct.tex
After Dr. Dilum reviewed the Viva thesis

@@
 
-The architecture and the storage management of the \acrshort{wdias} is designed and developed based on the weather data.
+The architecture and the storage management of \acrshort{wdias} is designed and developed based on the weather data.
 We need to look into the weather data timeseries deeply to understand the underline design decisions of the \acrshort{wdias} database structure.
@@
 Thus, we need to use a set of attributes to identify a timeseries uniquely.
-Next, we describe key attributes that are used by the \acrshort{wdias} to identify a timeseries uniquely.
+Next, we describe key attributes that are used by \acrshort{wdias} to identify a timeseries uniquely.
 
@@
 \subsubsection{Value Type}
-Scalar, vector, grid are the value types that are interested in the \acrshort{wdias}.
+Scalar, vector, grid are the value types that are interested in \acrshort{wdias}.
 
 \subsubsection{Location}
-Location of the timeseries. All locations have a unique String identifier called \emph{locationId}. Further, two types of location types are interested in the \acrshort{wdias}, namely:
+Location of the timeseries. All locations have a unique String identifier called \emph{locationId}. Further, two types of location types are interested in \acrshort{wdias}, namely:
 \begin{itemize}
@@
 
-\cref{fi:database_structure} shows the \acrshort{wdias} database structure.
+\cref{fi:database_structure} shows \acrshort{wdias}'s database structure.
 The following sections describe the database structure of \acrshort{wdias} with compare to the design with more details on how is support the microservice architecture.
@@
 
-Two individual instances of InfluxDB used for scalar adapter and vector adapter services in the \acrshort{wdias} system.
+Two individual instances of InfluxDB used for scalar adapter and vector adapter services in \acrshort{wdias} system.
 For the scalability, the system uses \emph{database per service}, as mentioned in \cref{subse:database_per_service}.
@@
 
-We used MongoDB geospatial features to support geo-queries in the \acrshort{wdias}.
+We used MongoDB geospatial features to support geo-queries in \acrshort{wdias}.
 Also, we indexed the timeseries metadata with other indexing features to serve external timeseries metadata queries.

### 2021-01-01 method/sec_5-data_preprocess.tex
After Dr. Dilum reviewed the Viva thesis

--- 2020-06-15 method/sec_5-data_preprocess.tex
@@
 Thus, users can change the behavior of an existing function by providing different bind constants at the time of creating new triggers for an extension and produce different behaviors.
+Next, we explain how to derive interpolation, transformation, and validation functions using the generic mathematical function model described above.
 
 \subsection{Interpolation}
-The interpolation module generates data at desired locations or desired data points using a serial or spatial interpolation technique.
-It is used to fill gaps in on-line measured data and to derive spatially distributed data for weather timeseries, such as precipitation and temperature, based on information available at nearby locations.
+The interpolation extension generates data at desired locations or desired data points using a serial or spatial interpolation technique.
+It is used to fill gaps in linear measured data and to derive spatially distributed data for weather timeseries, such as precipitation and temperature based on information available at nearby locations.
+Here, we will discuss two types of interpolation, such as serial interpolation and spatial interpolation, below.
 
 \subsubsection{Serial Interpolation}
-During serial interpolation, we use interpolation to fill any gaps in a timeseries. The interpolation module will only consider a single timeseries, which is itself in filling these gaps.
+During serial interpolation, we use interpolation to fill any gaps in a linear timeseries.
+The interpolation module will only consider a single timeseries, which is itself filling the missing data points.
+For example, as seen in Figure \ref{fi:serial_interpolation}, there can be timeseries that has data points of temperature collected using a weather station.
+There can be missing data in this timeseries, and we can use a simple linear interpolation algorithm to fill the missing values based on the existing data points.
 
@@
 \subsubsection{Spatial Interpolation}
-During spatial interpolation, we use interpolation to either fill gaps in timeseries or to create a new timeseries for a location using data from other (spatially distributed) locations.
+During spatial interpolation, we use interpolation to either fill gaps in timeseries or create a new timeseries for a location using data from other (spatially distributed) locations' timeseries.
 Spatial interpolation can also be applied for sampling scalar timeseries from grid timeseries, for re-sampling grids, or for creating grids from timeseries data.
+For example, let us assume that there are precipitation timeseries data available for location \textit{A} and location \textit{B} as shown in Figure \ref{fi:spatial_interpolation}.
+Then we want to calculate the mean precipitation of nearby locations using these two timeseries.
+We can use the spatial interpolation to get the mean precipitation of nearby locations.
+
 \begin{figure}[htp]
@@
 \subsection{Transformation}
-Simple arithmetic manipulation of time interval transformation and shifting the series in time specific hydro-meteorological transformation such as stage discharge relationships.
+Simple arithmetic manipulation of time interval transformation and shifting the series in time-specific hydro-meteorological transformation such as stage-discharge relationships are considered transformation.
+For example, as seen in Figure \ref{fi:transformation}, there can be a timeseries of precipitation with 1-minute sample data.
+There will be a model requirement that needs hourly data.
+Therefore, we need to accumulation data manipulation to create a timeseries of hourly data using 1-minute sample data.
+
 \begin{figure}[htp]
@@
 \subsection{Validation}
-Checks for counting reliable, doubtful, unreliable, and missing values.
+Validation functions check for counting reliable, doubtful, unreliable, and missing values.
+The weather stations can produce invalid observations due to technical errors in the sensors of the devices.
+If we feed those values directly to the models, the models will produce inaccurate forecasting.
+To avoid that, we need to modify or flag those values before feeding them to the numerical models.
+As seen in Figure \ref{fi:validation} We can use validation extensions to modify or flag invalid data.
+For example, a weather station can record temperature above 70 celsius due to sensor error or calibration issues.
+However, in the real world, it is not possible to have such a temperature in nature.
+Thus, we need to flag such temperature issues and repair the weather station as soon as possible.
+
 \begin{figure}[htp]

### 2021-01-01 method/sec_7-summary.tex
Proof read: Chapter 1
After Dr. Dilum reviewed the Viva thesis

--- 2020-05-08 method/sec_7-summary.tex
@@
 
-Throughout this Chapter, we discussed the methodology of designing and implementing the \acrshort{wdias} based on the concepts studied in the literature review of \cref{ch:literature}.
+Throughout the \cref{ch:method}, we discussed the methodology of designing and implementing \acrshort{wdias} based on the concepts studied in the literature review of \cref{ch:literature}.
 We used microservice architecture over \acrshort{soa} with an \acrshort{esb} to avoid the drawback of streaming bulk data through an \acrshort{esb}.

### 2021-01-01 results/sec_3-observations.tex
After Dr. Dilum reviewed the Viva thesis

--- 2020-12-24 results/sec_3-observations.tex
@@
 Sections \ref{subse:obs_test_plan_all_60min} to \ref{subse:obs_test_plan_all_auto_15min}, we discuss the observations collected with performing the load test plans with 60-minute data (24 data points per request), 30-minute data (48 data points per request), and 15-minute data (96 data points per request) by varying the request size for scalar and vector timeseries.
-\gkc{For grid timeseries, we performed the load test plans with ASCII grid file as data for each time step which has the size of 52 kilobyte.
-On average, each sample grid data for 60-minute data requests consist of 1.2 megabyte, 30-minute data requests consist of 2.4 megabyte, and 15-minute data requests consist of 4.9 megabyte}.
+For grid timeseries, we performed the load test with ASCII grid file as data for each time step (with the size of 52 KB).
+On average, each sample grid data for 60-minute data requests consist of 1.2 MB, 30-minute data requests consist of 2.4 MB, and 15-minute data requests consist of 4.9 MB.
 Then we perform another round of 15-minute data with enabling auto-scaling for the higher resource utilized microservices.
@@
 The performance degrades because those data handles on-demand and depends on the timeseries database performance.
+However, when the request sizes are smaller, \acrshort{wdias} was able to perform insert and retrieval of grid data with the same latency.
 
@@
 This graph further proves that the system was able to handle the increasing workload without any significant change in the delay.
+The stepped red colour graph for server hits per second shows the number of requests that was sent by the load test with time.
+Other horizontal lines with spikes show the latency for each of test case, such as insertion and retrieval of scalar, vector, and grid data with time.
 
@@
 
-Next, we performed the test plan with 30-minute resolution data, which means 48 data points per each request for the scalar and vector data types, and 48 ASCII grid files per each insertion request for the grid data type.
+Next, we performed the test plan with 30-minute resolution data, which means 48 data points per each request for the scalar and vector data types, and 48 ASCII grid files with 2.4 MB of size per each insertion request for the grid data type.
 Also, the test plan performed round up to \num{311e3} number of sample requests, which is almost similar to the number of samples processed with hourly resolution data.
+That means \acrshort{wdias}-based system was able to process same number of request while increasing the request size with providing higher throughput.
 
@@
 Even though we doubled the request size, \acrshort{wdias} was able to keep the performance almost the same instead of increasing the latency twice.
+Insertion and retrieval of scalar and vector data increased by 1 millisecond on average.
+However, the grid data insert latency increased from 23 milliseconds to 40 milliseconds.
+Such doubling of latency is expected, as the grid data size was increased from 1.2 MB to 2.4 MB, and it is taking time to stream the data into \acrshort{wdias}-based system.
+Retrieval of grid data also increased by 22 milliseconds, because during the test cases, we try to retrieve the inserted grid data in a different format, but the export data size also gets increased due to the increase of the insert grid data size.
 
@@
 
-During this section, we performed the test plan with 15-minute resolution data, which means 96 data points per each request for the scalar and vector data types, and 96 ASCII grid files per each insertion request for the grid data type.
+During this section, we performed the test plan with 15-minute resolution data, which means 96 data points per each request for the scalar and vector data types, and 96 ASCII grid files per each insertion request with the size of 4.9 MB for the grid data type.
 The size of each request is four times larger than the 60-minute resolution data.
 Here also, the test plan performed approximately \num{311e3} of sample requests, which are almost similar to sample requests made during 60-minute and 30-minute resolution data.
+This means \acrshort{wdias}-based system was able to increase the throughput while increasing load with the request size, and processed the same amount of requests within the elapsed time.
+
 \begin{table}[ht]
@@
 When compared to the observations from the performance test with 30-minute data, the request latency also increased for all sample requests.
+The scalar and vector data insertion increased by 1 milliseconds, and retrieval of those data increased significantly by doubling the latency.
 Also, the standard deviation of retrieval timeseries data increased by a considerable amount for all the data type's sample requests.
-One of the reasons for increasing the retrieval data delay was while performing heavy database writes on the database has effects on the database reads.
+One of the reasons for increasing the retrieval data delay was while performing heavy database writes on the InfluxDB database instance has effects on the database reads.
+The grid data insert and retrieve latency also doubled approximately because the stream data size increase by a factor of two compared to 30-minute data.
+Noticeably, the error rate of inserting grid data increased up to 1.42\%.
 Even though we increased the request data size by four times higher, the system was able to handle all requests without significant performance issues.
-Also, the system provided the same throughput as with 60-minute and 30-minute resolution data.
+Also, the system was able to process same number of request as with 60-minute and 30-minute resolution data while increasing the throughput of the system with the request size.
 
@@
 As per the graph, the system was able to keep the response latency constant while increasing the number of active threads.
-However, when the number of active threads became higher, there was a disturbance with the response delay during the insertion and retrieval of timeseries data.
+However, when the number of active threads became higher, there was a disturbance with the response delay during the insertion and retrieval of scalar and vector timeseries data.
+As mentioned above, this may happened due to the system reaching its maximum capacity as per the allocated resources, or caused by heavy database read and writes on the InfluxDB free database version.
 The latency of insert and retrieval of grid timeseries data increased twice when compared to 30-minute resolution data.
 With a larger request size, we can notice the latency also increased by a smaller factor when we increased the number of active threads.
+When compared to the load testing with 60-minute and 30-minute data, we can see 192 active threads used by the JMeter to maintain the \acrshort{rps}.
+When we increase the request size, the latency also increases.
+Then the active threads have to wait for the response from the system rather than doing any other work.
+To maintain the server hits, the JMeter has to spawn more active threads.
 
@@
 \cref{fi:test_obs_all_15m_throughtput} shows the total server's transaction throughput against the number of active threads.
-The formula for total server transaction throughput is \emph{active threads per second / thread response time} \cite{ApacheSoftwareFoundationJMeter:Plugin}.
-It shows the statistical maximum possible number of transactions based on the number of users accessing the application.
+The formula for total server transaction throughput is \emph{active threads per second / one thread response time} \cite{ApacheSoftwareFoundationJMeter:Plugin}.
+It shows the statistical maximum possible number of transactions based on the number of active threads accessing the application at a given time.
+This estimates the transaction throughput based on the latency of requests against the number of active threads at a given time.
+We can assume that the highest number of active threads occur at the peak time of the load testing.
+However, the number of latency samples are limit with the higher number of active threads.
+Consequently, in \cref{fi:test_obs_all_15m_throughtput} we can see missing data points, and spikes with graph drawing with available data points.
+Further we can analyze this graph against \cref{fi:test_obs_all_15m_response_vs_threads}, and derive this output based on latency fluctuation in that graph.
 By combining the \cref{fi:test_obs_all_15m_latency}, this graph shows that the throughput of the system gets increased without much change in the latency, thus it proves the scalability of the \acrshort{wdias}.
@@
 Since the standard deviation also reduced, we can conclude that the latencies are closer to the average latency.
-Further, these improvements in insert grid timeseries data seem to affect the output of retrieve grid timeseries data as well.
+Further, these improvements in insert grid timeseries data seem to affect the output of retrieve grid timeseries data as well, and decrease the latency from 118 milliseconds to 89 milliseconds.
+When it comes to scalar and vector timeseries data insertion, latency was increased a bit.
+However, we can notice that, the retrieval of scalar and vector timeseries latency improved from 23 milliseconds to 7 milliseconds.
+Specially, the latency for query location timeseries metadata was improved from 3 milliseconds to 2 milliseconds.
+It was constant with 3 milliseconds in previous load testings.
+Other than inserting scalar and vector data, other test cases standard deviation was improved, and we can conclude that the overall system performance is enhanced when auto-scaling is enabled.
 
@@
 When compared to \cref{fi:test_obs_all_15m_throughtput} without auto-scaling, the estimated throughput with a higher number of active threads becomes stable, according to the graph.
-Thus, we can conclude that enabling auto-scaling also improves the throughput by supporting a higher number of active users.
-During the next paragraphs, we discuss the resource usage while running the test plan while enabling the auto-scaling.
+Thus, we can conclude that enabling auto-scaling also improves the throughput by supporting a higher number of active threads.
+We can see fluctuation when increase the number of active threads due to lack of sample latency with higher number of active threads during the peak of load testing.
+Further, we can see estimated throughput for insert and retrieve grid data also increased by a small factor, and it more smooth than 15-minute data load testing without auto-scaling.
+During the next paragraphs, we will discuss the resource usage while running the test plan while enabling the auto-scaling.
 

### 2021-01-01 summary/sec_1-conclusions.tex
After Dr. Dilum reviewed the Viva thesis

--- 2020-06-07 summary/sec_1-conclusions.tex
@@
 Also, the system provides asynchronous request handling based on the request size with maintaining status per request.
+
+Compared to other existing weather data integration and assimilation systems, WDIAS has the advantage of taking full advantage of cloud computing technologies to implement a highly scalable and available system at low-cost.
+Because it uses containerized applications to implement the microservices, it allows independent service deployments.
+Each microservice can scale independently without affecting other microservices.
+Further, each microservice could use a suitable technology stack for the task.
+\acrshort{fews}, \acrshort{madis}, and \acrshort{msm} have platform dependencies, and some of the deployments are performed by copy-pasting source codes.
+The \acrshort{fews} and \acrshort{msm} provide a centralized data storage mechanism that  can become a bottleneck while processing a large volume of data in critical situations.
+\acrshort{madis} and \acrshort{dias} also support data storage arrays to store data.
+WDIAS and \acrshort{lead} can support a pool of resources based on the requirement.
+Like other systems, WDIAS provides data preprocessing capabilities, and users can integrate new data preprocessing capabilities by implementing them as independent containerized microservice applications.
+Even though \acrshort{fews}, \acrshort{lead}, and \acrshort{msm} provide workflow engine support and model execution support, these can be achieved using an external workflow management system by fulfilling the data requirements via WDIAS.
+Further, WDIAS is an extendable open framework such that similar capabilities can be integrated as a new extension module system.
+Compared to other existing systems, the \acrshort{lead} is more scalable and is implemented using \acrshort{soa} architecture.
+However, with the help of modern container orchestration frameworks, such as Kubernetes and cloud computing technologies, those can provide high scalability and high availability as inherent capabilities.
+Those are mature enough to provide fault-tolerance automatically \cite{Scolati2019ADevices}.
+Implementing the deployment units as containerized applications based on the modern architecture patterns allows WDIAS to implement a highly scalable and high available system without heavy effort on those features.
+A comparison  between WDIAS and other systems are presented in Table \ref{fi:architecture_comparison}.
 
@@
 Based on the performance analysis, we were able to perform 300 \acrshort{rps}, and the system handled the workload successfully with minimizing the error rate.
-Also, while we increased the request size from 24 to 96 data points per scalar and vector timeseries, and the number of ASCII Grid files from 24 to 96, the \acrshort{wdias} was able to provide the same throughput while keeping the latency constant.
+Also, while we increased the request size from 24 to 96 data points per scalar and vector timeseries, and the number of ASCII Grid files from 24 to 96, \acrshort{wdias} was able to provide the same throughput while keeping the latency constant.
 Likewise, the system was able to provide an increase in the throughput by keeping the latency constant while increasing the workload.

### 2021-01-01 summary/sec_2-research_limitations.tex
After Dr. Dilum reviewed the Viva thesis

--- 2020-06-15 summary/sec_2-research_limitations.tex
@@
 
-Next, we discussed the lacking features of the \acrshort{wdias} and the set of improvements.
-
-\emph{Lack of data preprocessing modules}:
-We implemented the extension modules as an eco-system of integrating different preprocessing modules as add-ons to the \acrshort{wdias}.
+Next, we discussed \emph{Lack of data preprocessing modules}:
+We implemented the extension modules as an eco-system of integrating different preprocessing modules as add-ons to \acrshort{wdias}.
 Then, users can use these modules for process the data which are inserted into the system in real time or process later based on regular intervals.
@@
 However, it has some performance issues and memory leak issues as well.
-Since each microservice in the \acrshort{wdias} is independent of technology, we can use a different technology stack to implement the service.
+Since each microservice in \acrshort{wdias} is independent of technology, we can use a different technology stack to implement the service.
 As an example, we can use a low-level language such as C or FORTRAN to implement the grid adapter, which will affect performance improvements and lesser issues.
@@
 \emph{Improvements to test cases}:
-As described in detail with \cref{subse:closed_vs_open_workload}, the \acrshort{wdias} test plans use the time-stepping feedback loop with concurrent threads, which is the best approach support by JMeter at the moment.
+As described in detail with \cref{subse:closed_vs_open_workload}, \acrshort{wdias} test plans use the time-stepping feedback loop with concurrent threads, which is the best approach support by JMeter at the moment.
 However, using the above approach, we cannot get the desired \acrshort{rps} for each test case within the test plan.
-Because of the above issue, the \acrshort{wdias} test plans further improved by removing redundant test cases such as create timeseries at the beginning.
+Because of the above issue, \acrshort{wdias} test plans further improved by removing redundant test cases such as create timeseries at the beginning.
 Having created timeseries at the beginning causes some issues such as most of the thread are working on that test case, rather than running the required test cases.
@@
 With the InfluxDB cluster, it is possible to run multiple pods of scalar adapter and vector adapter to support more server hits per second.
-Other than that, the \acrshort{wdias} performance can improve via partitioning the timeseries key space into multiple InfluxDB instances.
-As an example, based on the key attribute \cref{subse:timeseries_key_attributes} Timeseries Type, the scalar adapter can connect to four instances of InfluxDB instances such as external historical, external forecast, simulated historical, and simulated forecast.
+\acrshort{wdias}'s performance can be improved by partitioning the timeseries key space into multiple InfluxDB instances.
+For example, based on the key attribute \cref{subse:timeseries_key_attributes} Timeseries Type, the scalar adapter can connect to four instances of InfluxDB instances such as external historical, external forecast, simulated historical, and simulated forecast.
+
+\emph{Explicitly not testing for high availability}:
+By default, the container orchestration framework handles service failures, auto scaling, auto down scaling, and independent service deployments.
+Also, when considering about modern cloud resources in data centers have better availability and failure handling.
+Combining both factors enables high availability for \acrshort{wdias}-based systems.
+However, in this research, we do not rely on third party tools.
+Also, we do not explicitly test for the high availability with performing manually terminating services, and letting crash some of the services to measure how is it affect on \acrshort{wdias}-based system's high availability.
 
@@
 \emph{Supporting irregular grids}:
+When consider about 2D grid, there are two types of grids such as regular grids and irregular grids.
+In regular grid system, each shell consist of fix width and height.
+However, for irregular grid system, each shell define as a 2D polygon with there's coordinates.
 At the moment, \acrshort{wdias} does not support irregular grids, but it has the API endpoints defined for the implementation of such support with following the microservice architecture.
-We reduced the scope of the research by removing such components from the system, and such level of implementation does not belong to the \acrshort{wdias} scope as well.
+We reduced the scope of the research by removing such components from the system, and such level of implementation does not belong to the scope of \acrshort{wdias} as well.
 
 \emph{Define infrastructure as code}:
-Physical nodes for the \acrshort{k8s} cluster created using cloud computing providers such as Amazon EKS, Google Cloud, and Microsoft Azure cloud.
-However, the infrastructure that needs to deploy the \acrshort{wdias} can be defined as code such as using tools like Terraform, which is independent of the cloud computing provider.
-Using such a tool, users will be able to quickly deploy the \acrshort{wdias} on any cloud provider without much hassle.
+Physical nodes for the \acrshort{k8s} cluster can be created using cloud computing providers such as Amazon EKS, Google Cloud, Microsoft Azure cloud, or even using own cluster.
+During the load testing, we used Amazon cloud resources.
+Thus, users need to have some understanding of Amazon cloud and its technologies to setup the system, and the \acrshort{k8s} cluster.
+However, the infrastructure that needs to deploy \acrshort{wdias} can be defined as code such as using tools like Terraform, which is independent of the cloud computing provider.
+Using such a tool, users will be able to quickly deploy \acrshort{wdias} on any cloud provider without much hassle.
+\acrshort{wdias} resource requirements are configured as code in the Terraform, and user can easily interact with those clouds using Terraform provider modules without much prior knowledge.
 
-\emph{Alerting extension modules}: At the moment, extensions only support OnChange and OnTime events.
-However, it will be useful to have event trigger support based on the configured alert level or threshold level.
+\emph{Alerting extension modules}: At the moment, in the basic framework of \acrshort{wdias}, the extensions only support OnChange and OnTime event triggers.
+However, it is useful to have event triggers support based on the configured alert level or threshold level.
+Here, users should be able to register triggers based on given alert levels, and the alerting extension should trigger a webhook provide by the user while registering the trigger.
+For example, a user can register an alert event on particular timeseries such as waterlevel, and also provide the threshold value based on historical flood events.
+When the waterlevel exceeds the given threshold value, the system will trigger the provided webhook.
+Then the user will be notified or the webhook endpoint will take necessary actions.
 
-\emph{Publisher Subscriber extension modules}: The \acrshort{wdias} better to be capable of triggering external systems based on events such as webhooks.
+\emph{Publisher-Subscriber extension modules}: \acrshort{wdias} could be extended to trigger external systems via publisher-subscriber support.
+For example, we may sync a weather station's precipitation timeseries data into an external system through \acrshort{wdias} when there is rain.
+One possibility is, the external system can sync data with timeseries data via polling through \acrshort{wdias}.
+However, it is inefficient as the external system needs to fetch the data via export modules, even there is no rain.
+Instead, we can use publisher-subscriber capabilities to sync the data efficiently.
+With these extension modules, users can create topics, and publishers extensions can push data into the topics when particular criteria are met, such as when there is rain in the above example.
+Then external systems could subscribe to the topic above topics while providing a webhook endpoint.
+Whenever data is pushed into the topic, the extension modules will send data to the subscribers via webhooks.

### 2021-01-01 Thesis.tex
Fix NWMs plural

@@
 
-\acrfull{nwms} utilize data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images.
-Before using such multimodal data in a \acrshort{nwm}, it is necessary to transcode data into a format  %that can be
-ingested by the \acrshort{nwm}.
-Moreover, the data integration system's response time needs to be relatively low to forecast and monitor time-sensitive weather events like hurricanes, storms, and flash floods that require rapid and frequent execution of \acrshort{nwms}.
+\acrfull{nwm}s utilize data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images.
+Before using such multimodal data in a \acrshort{nwm}, it is necessary to transcode data into a format ingested by the \acrshort{nwm}.
+Moreover, the data integration system's response time needs to be relatively low to forecast and monitor time-sensitive weather events like hurricanes, storms, and flash floods that require rapid and frequent execution of \acrshort{nwm}s.
 The resulting weather data also need to be accessed by many researchers and third-party applications such as logistic and agricultural insurance firms.
@@
 Moreover, most of these softwares are proprietary or closed-source, making it difficult to customize them for an island like Sri Lanka with different weather seasons.
-Therefore, in this research, we propose \acrfull{wdias} that utilizes %modern architectural patterns such as 
-microservices to achieve scalability, high availability, and low-cost operation based on cloud computing.
+Therefore, in this research, we propose \acrfull{wdias} that utilizes microservices to achieve scalability, high availability, and low-cost operation based on cloud computing.
 The use of stateless microservices also enables \acrshort{wdias} to add new features on the fly with rollover capabilities.

### 2021-01-01 introduction/sec_1-motivation.tex
Fix NWMs plural

@@
 Weather forecast is essential to reduce the impact caused by natural disasters and to effectively manage natural resources like water.
-The weather forecasts are performed using \acrfull{nwms} that use a set of configuration parameters and the current status of the environment such as temperature, rainfall, and wind direction as the inputs.
+The weather forecasts are performed using \acrfull{nwm}s that use a set of configuration parameters and the current status of the environment such as temperature, rainfall, and wind direction as the inputs.
 For example, the \acrfull{wrf} \cite{MesoscaleMicroscaleMeteorologyLaboratoryWeatherModel} model is used to predict the rainfall, temperature, and wind direction.
-Typically multiple \acrshort{nwms} are executed on the same data with different configuration parameters.
+Typically multiple \acrshort{nwm}s are executed on the same data with different configuration parameters.
 Then using the real-time observations, the most fitting model is selected.
@@
 
-Weather data processed by a \acrshort{nwm} maybe used by several other \acrshort{nwm}, as well as by many third-party applications and researcher.
+Weather data processed by a \acrshort{nwm} maybe used by several other \acrshort{nwm}s, as well as by many third-party applications and researcher.
 For example, logistic companies could use the processed data with their data models to plan and schedule their deliveries.
@@
 Given the above reasons, there is a necessity to develop a WDIA system that could handle large volumes of multimodel data efficiently while providing scalability and high throughput.
-Moreover, it is desirable to support controlled data sharing with other NWMs and third-party access to enable multiple use cases.
+Moreover, it is desirable to support controlled data sharing with other \acrshort{nwm}s and third-party access to enable multiple use cases.
 Furthermore, such a system should be architectured to benefit from technologies such as cloud computing, microservices, and loosely coupled containerized applications.

### 2021-01-01 structure.tex
Fix NWMs plural

@@
 To enhance the accuracy of weather forecast, it is necessary to provide reliable and detailed weather data as inputs to Numerical Weather Models (NWM).
-These NWMs utilize weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images.
-Prior to feeding such diverse data (collected from different sources that belongs to different stakeholders) into respective NWMs, it is necessary to integrate data into a common format.
-Moreover, the data integration system’s response time need to be relatively low to accommodate critical situations like hurricanes, storms, and floods which require rapid and frequent execution of NWMs.
+These \acrshort{nwm}s utilize weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images.
+Prior to feeding such diverse data (collected from different sources that belongs to different stakeholders) into respective \acrshort{nwm}s, it is necessary to integrate data into a common format.
+Moreover, the data integration system’s response time need to be relatively low to accommodate critical situations like hurricanes, storms, and floods which require rapid and frequent execution of \acrshort{nwm}s.
 

### 2021-01-01 method/sec_1-architectural_decisions.tex
Fixed comparison table

@@
 % Architecture Comparison with Existing Systems
+\begin{table}[htp]
+    \caption{Comparison of features among existing weather data assimilation and integration systems and \acrshort{wdias}. }
+    \includegraphics[width=1.05\textwidth]{method/misc/architecture_comparison_pros_cons.pdf}
+    \label{tab:architecture_comparison}
+    {\raggedright \footnotesize An "\Cross" in the table represents a feature offered by the corresponding tool.
+An "\SmallHBar" in the table represents that information available are not enough to make an statement, and empty presents a feature is not offered.
+\par}
+\end{table}
 
-\cref{fi:architecture_comparison} shows a comparison between existing systems and WDIAS concerning software architectural aspects.
+\cref{tab:architecture_comparison} shows a comparison between existing systems and WDIAS concerning software architectural aspects.
 Here, we compare systems under categories such as data storage, performance, architecture, and other features.
@@
 
-\begin{figure}[htp]
-    \centering
-    \includegraphics[width=1.05\textwidth]{method/misc/architecture_comparison_pros_cons.pdf}
-    \caption{Comparison of features among existing weather data assimilation and integration systems and \acrshort{wdias}.
-%An "X" in the table represents a feature offered by the corresponding tool.
-An "-" in the table represents that information available are not enough to make an statement, and empty presents a feature is not offered.
-    }
-    \label{fi:architecture_comparison}
-\end{figure}
-
 We discuss the architecture of the systems in terms of their design, dependencies of the subsystems, extensibility, availability of source code, and data preprocessing capabilities specific to the weather domain.
-While other existing systems use distributed client-server architecture or monolithic distributed architecture, LEAD uses the SOA architecture.
+While other existing systems use distributed client-server architecture or monolithic distributed architecture \cite{ChristensenBenDontMonolith}, LEAD uses the SOA architecture.
 However, WDIAS has the advantage of using modern cloud computing technologies to implement microservices as containerized applications.

### 2021-01-01 summary/sec_1-conclusions.tex
Fix NWMs plural
Fixed comparison table

@@
 
-To enhance the accuracy of the weather forecast, we need to provide reliable and timely weather data for NWMs.
+To enhance the accuracy of the weather forecast, we need to provide reliable and timely weather data for \acrshort{nwm}s.
 Also, most of the existing weather data integration systems are based on basic client-server architectures or monolithic distributed system architectures or developed based on the best technology available at the time of developing those systems.
@@
 Implementing the deployment units as containerized applications based on the modern architecture patterns allows WDIAS to implement a highly scalable and high available system without heavy effort on those features.
-A comparison  between WDIAS and other systems are presented in Table \ref{fi:architecture_comparison}.
+A comparison  between WDIAS and other systems are presented in Table \ref{tab:architecture_comparison}.
 

### 2021-01-01 Thesis.tex
Fixed comparison table
Added news abbr

--- 2021-01-01 Thesis.tex
@@
 \usepackage{siunitx}
+\usepackage[misc,geometry]{ifsym} % https://tex.stackexchange.com/a/107112/181545, http://tug.ctan.org/info/symbols/comprehensive/symbols-a4.pdf
 
@@
 \acrfull{nwms} utilize data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images.
-Before using such multimodal data in a \acrshort{nwm}, it is necessary to transcode data into a format  %that can be
-ingested by the \acrshort{nwm}.
+Before using such multimodal data in a \acrshort{nwm}, it is necessary to transcode data into a format ingested by the \acrshort{nwm}.
 Moreover, the data integration system's response time needs to be relatively low to forecast and monitor time-sensitive weather events like hurricanes, storms, and flash floods that require rapid and frequent execution of \acrshort{nwms}.

### 2021-01-01 introduction/sec_1-motivation.tex
Added news abbr

--- 2021-01-01 introduction/sec_1-motivation.tex
@@
 To enhance the accuracy of weather forecast, it is necessary to provide reliable and detailed weather data as inputs to \acrshort{nwm}.
-These \acrshort{nwm}s utilize multi-modal weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images.
-Before feeding such diverse data (collected from different sources that belong to different stakeholders) into respective \acrshort{nwm}s, it is necessary to convert them to a data format that can be ingest by the models.
-Moreover, the data integration system's response time needs to be relatively low to forecast and monitor time-sensitive weather events like hurricanes, storms, and floods which require rapid and frequent execution of \acrshort{nwm}s.
+These \acrshort{nwms} utilize multi-modal weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images.
+Before feeding such diverse data (collected from different sources that belong to different stakeholders) into respective \acrshort{nwms}, it is necessary to convert them to a data format that can be ingest by the models.
+Moreover, the data integration system's response time needs to be relatively low to forecast and monitor time-sensitive weather events like hurricanes, storms, and floods which require rapid and frequent execution of \acrshort{nwms}.
 
-Weather data processed by a \acrshort{nwm} maybe used by several other \acrshort{nwm}, as well as by many third-party applications and researcher.
+Weather data processed by a \acrshort{nwm} maybe used by several other \acrshort{nwms}, as well as by many third-party applications and researcher.
 For example, logistic companies could use the processed data with their data models to plan and schedule their deliveries.
@@
 Given the above reasons, there is a necessity to develop a WDIA system that could handle large volumes of multimodel data efficiently while providing scalability and high throughput.
-Moreover, it is desirable to support controlled data sharing with other NWMs and third-party access to enable multiple use cases.
+Moreover, it is desirable to support controlled data sharing with other \acrshort{nwms} and third-party access to enable multiple use cases.
 Furthermore, such a system should be architectured to benefit from technologies such as cloud computing, microservices, and loosely coupled containerized applications.

### 2021-01-01 lit/sec_1-fews.tex
Added news abbr

@@
 The \acrshort{fews} codebase is not fully open source at the moment.
-The main objective of a forecasting system is to run multiple NWMs, hydrologic models, and hydrodynamic models which are required for the predictions.
+The main objective of a forecasting system is to run multiple \acrshort{nwms}, hydrologic models, and hydrodynamic models which are required for the predictions.
 This approach is known as a model-centric approach \cite{Werner2005FloodCatchments}.

### 2021-01-01 results/sec_1-test_plan.tex
Added news abbr

@@
 The majority of weather data requests come from weather stations and other observation tools.
-Then we need to validate and modify those timeseries data and store them as new timeseries that can directly feed into the NWMs.
+Then we need to validate and modify those timeseries data and store them as new timeseries that can directly feed into the \acrshort{nwms}.
 These weather stations can send the weather data at different frequencies with different parameters such as precipitation, temperature, humidity, and wind direction.
@@
 When compared to scalar data, parameters such as wind direction are vector timeseries with a lesser percentage of requests.
-Alternatively, most of the grid type data was generated as results of NWMs.
+Alternatively, most of the grid type data was generated as results of \acrshort{nwms}.
 But those grid data produce in less frequency due to the cost of the computer resource to produce results.

### 2021-01-03 results/sec_2-workload.tex
Finalized WDIAS Thesis

@@
 The maximum peak load that can be had during the load test is 300 \acrshort{rps} (equivalent to 18,000 requests per minute).
-The following the test plans that we used during the performance testing:
+The followings are the test plans that we used during the performance testing:
 
 \begin{itemize}
-    \item User-defined variables
-    \item Setup thread group
-    \item Create timeseries thread group
-    \item Create extensions thread group
-    \item Load test timeseries concurrency thread group
-    \item Load test timeseries concurrency thread group
-    \item Test flow thread group
+    \item User-defined variables such as for change variable size 
+    \item Setup thread group for test setup before load testing
+    \item Create timeseries thread group for create timeseries metadata before import and export timeseries data
+    \item Create extensions thread group for create triggers for basic extensions
+    \item Load test timeseries with concurrency thread group
 \end{itemize}
@@
 \begin{itemize}
-    \item HTTP request defaults
-    \item HTTP header manager
-    \item Timeseries metadata CSV
+    \item Load the timeseries metadata CSV
     \item Create timeseries
-    \item Get timeseries
-    \item Query timeseries
+    \item Check with get timeseries
+    \item Query for timeseries
 \end{itemize}
@@
 \begin{itemize}
-    \item HTTP request defaults
-    \item HTTP header manager
-    \item Timeseries metadata CSV
-    \item If scalar or vector then insert timeseries, otherwise insert grid timeseries
+    \item Load the timeseries metadata CSV
+    \item If scalar or vector then insert relevant timeseries data, otherwise insert grid timeseries data
     \item Wait for extensions timeseries
-    \item Interest area preprocessor
-    \item Query if scalar or vector
-    \item If scalar or vector then retrieve timeseries, otherwise retrieve grid timeseries
+    \item Query for timeseries metadata
+    \item If scalar or vector then retrieve timeseries data, otherwise retrieve grid timeseries data
     \item Increment date
-    \item Throughput shaping timer prod
 \end{itemize}
@@
 \begin{itemize}
-    \item HTTP request defaults
-    \item HTTP header manager
-    \item Locations CSV
-    \item Interest area preprocessor
+    \item Load the locations CSV
+    \item Prepare interest area for search for the timeseries
     \begin{itemize}

### 2021-01-03 summary/sec_1-conclusions.tex
Added news abbr
Finalized WDIAS Thesis

@@
 
-To enhance the accuracy of the weather forecast, we need to provide reliable and timely weather data for \acrshort{nwm}s.
+To enhance the accuracy of the weather forecast, we need to provide reliable and timely weather data for \acrshort{nwms}.
 Also, most of the existing weather data integration systems are based on basic client-server architectures or monolithic distributed system architectures or developed based on the best technology available at the time of developing those systems.
@@
 
-In this research, we proposed an extendable weather data integration and assimilation system known as \acrfull{wdias}.
+In this research, we proposed an extendable open source weather data integration and assimilation system known as \acrfull{wdias} \cite{KarunarathneWeatherCode}.
 \acrshort{wdias} focuses on providing a system to efficiently integrate weather data from different sources with supporting quality control.

### 2021-01-03 Thesis.tex
Fixed: Removed NWMs abbreviation

--- 2021-01-01 Thesis.tex
@@
 
-\acrfull{nwm}s utilize data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images.
+Numerical Weather Models (NWMs) utilize data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images.
 Before using such multimodal data in a \acrshort{nwm}, it is necessary to transcode data into a format ingested by the \acrshort{nwm}.

### 2021-01-03 lit/sec_1-fews.tex
Fixed: Removed NWMs abbreviation

--- 2021-01-01 lit/sec_1-fews.tex
@@
 The \acrshort{fews} codebase is not fully open source at the moment.
-The main objective of a forecasting system is to run multiple NWMs, hydrologic models, and hydrodynamic models which are required for the predictions.
+The main objective of a forecasting system is to run multiple \acrshort{nwm}s, hydrologic models, and hydrodynamic models which are required for the predictions.
 This approach is known as a model-centric approach \cite{Werner2005FloodCatchments}.

### 2021-01-03 results/sec_1-test_plan.tex
Fixed: Removed NWMs abbreviation

--- 2020-06-10 results/sec_1-test_plan.tex
@@
 The majority of weather data requests come from weather stations and other observation tools.
-Then we need to validate and modify those timeseries data and store them as new timeseries that can directly feed into the NWMs.
+Then we need to validate and modify those timeseries data and store them as new timeseries that can directly feed into the \acrshort{nwm}s.
 These weather stations can send the weather data at different frequencies with different parameters such as precipitation, temperature, humidity, and wind direction.
@@
 When compared to scalar data, parameters such as wind direction are vector timeseries with a lesser percentage of requests.
-Alternatively, most of the grid type data was generated as results of NWMs.
+Alternatively, most of the grid type data was generated as results of \acrshort{nwm}s.
 But those grid data produce in less frequency due to the cost of the computer resource to produce results.

### 2021-01-03 introduction/sec_1-motivation.tex
Finalized WDIAS Thesis
Fixed: Removed NWMs abbreviation
WDIAS_Final_Submission

--- 2021-01-01 introduction/sec_1-motivation.tex
@@
 Weather forecast is essential to reduce the impact caused by natural disasters and to effectively manage natural resources like water.
-The weather forecasts are performed using \acrfull{nwm}s that use a set of configuration parameters and the current status of the environment such as temperature, rainfall, and wind direction as the inputs.
+The weather forecasts are performed using Numerical Weather Models (NWMs) that use a set of configuration parameters and the current status of the environment such as temperature, rainfall, and wind direction as the inputs.
 For example, the \acrfull{wrf} \cite{MesoscaleMicroscaleMeteorologyLaboratoryWeatherModel} model is used to predict the rainfall, temperature, and wind direction.
@@
 However, as the existing weather data integration systems are not open source and not flexible enough to change without much help from the maintainers, the \acrshort{curw} \cite{CUrWSLObservedSL} is implementing own system with the idea of long-term maintainability.
-%\acrshort{curw} \cite{CUrWSLObservedSL} is implementing own system with the idea of long-term maintainability rather than depending on existing weather data integration systems.
-\gkc{Because of existing weather systems are not open source to configure as required, and not flexible enough to change without much help from the maintainers.}
 \acrshort{curw} collects real-time data from weather stations and other relevant entities and generates daily forecasts.

### 2021-01-04 summary/sec_1-conclusions.tex
Fixed: Removed NWMs abbreviation
Added Reference to IEEE Research Paper

@@
 
-To enhance the accuracy of the weather forecast, we need to provide reliable and timely weather data for \acrshort{nwms}.
+To enhance the accuracy of the weather forecast, we need to provide reliable and timely weather data for \acrshort{nwm}s.
 Also, most of the existing weather data integration systems are based on basic client-server architectures or monolithic distributed system architectures or developed based on the best technology available at the time of developing those systems.
@@
 Also, we used many of the concepts of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities.
-\acrshort{wdias} implemented the microservice architecture on top of the \acrshort{k8s}, which is a container orchestration platform.
+\acrshort{wdias} implemented the microservice architecture on top of the \acrshort{k8s}, which is a container orchestration platform \cite{GihanChanukaKarunarathne2020WDIAS:System}.
 We mapped each microservice of \acrshort{wdias} to a pod in the \acrshort{k8s} cluster.
